### 2017-10-09 textm.Rmd
presentation

---
title: "Text as Data"
author: "Franziska Löw"
date: "08. Oktober 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

***
- Most empirical work in economics relies on inherently quantitative data: prices, demand, votes, etc.
- But a large amount of unstructured text is also generated in economic environments: 
    - company reports, 
    - policy committee deliberations, 
    - court decisions, 
    - media articles, 
    - political speeches, etc. 
- One can use such data qualitatively, but increasing interest in treating text quantitatively.

## What is Text?

At an abstract level, text is simply a string of characters.

- Some of these may be from the Latin alphabet ('a', 'A', 'p' and so on) but there may also be: 
    - Punctuation (e.g. !), 
    - Numbers, 
    - Non-alphanumerical characters (e.g. @)

**Key Question:** How can we obtain an informative, quantitative representation of these character strings? This is the goal of text mining.

# Representing Text as Data

## Textual Database

- A single observation in a textual database is called a document $D$.

- The set of documents that make up the dataset is called a corpus.

- We often have covariates associated with each document that are sometimes called metadata.

## Reduce Dimensionality

Textmining analysis take the following steps to reduce dimensionality to a managable size:

1. **Represent Text as Data** Bag-of-words model, n-grams, Text-preprocessing

2. **Statistical Methods** Map $\boldsymbol{C}$ to predict values $\boldsymbol{\hat{V}}$ of unknown outcomes $\boldsymbol{V}$. 
	E.g. the variable of interest $\boldsymbol{V}$ is an indicator whether the email is spam. The prediction $\boldsymbol{\hat{V}}$ determines whether or not to send the email to a spam filter. Sometimes the attribute of interest is latent, such as the topics of a newspaper article.

3. Use $\boldsymbol{\hat{V}}$ in subsequent **descriptive or causal analysis.**

# Represent text as Data

## Represent text as Data
Convert raw text $D$ to a numerical array $\boldsymbol{C}$:
A basic quantitative representation of a corpus is the bag-of-words model:

- Index each unique term in the corpus by some $v \in {1,...,V}$ where $V$ is the number of unique terms.
- For each document $d \in {1,...,D}$ compute the count $x_{d,v}$ as the number of occurrences of term $v$ in document $d$.
- The $D x V$ matrix $\boldsymbol{X}$ of all such counts is called the document-term matrix.

## Example

```{r}
Doc1 <- 
  c("text", "mining", "is", "more", "fun", "than", "coal", "mining")
```
has the bag-of-words representation

```{r, comment= ""}
table(Doc1)
```

But this has the same represantation:
```{r}
Doc1 <- 
  c("coal", "mining", "is", "more", "fun", "than", "text", "mining")
```

## Text Mining and Information

The bag-of-words model is useful for describing content, but we lose all information about sentence structure.

- Any useful representation of text will throw away some information; that’s the essential purpose of text mining.

- The question is whether we are keeping the relevant information for our needs, and getting rid of the extraneous information.

## Text Pre-Processing

Pre-process strings to obtain a cleaner representation:

1. **Tokenization** splitting of a raw character string into individual elements of interest.

2. **Stopword Removal** The frequency distribution of words in natural languages is highly skewed.

3. **Linguistic Roots** For many applications, the relevant information in tokens is their linguistic root, not their grammatical form. (Stemming or Lemmatizing)

4. **Multi-Word Phrases** Sometimes groups of individual tokens like “donald trump” or “fc bayern” have a specific meaning.

## Example: Twitter

Tweets after Stopword Removal.

```{r, echo=FALSE}
rm(list = ls())
load(file = "~/GitHub/politsentiment_data/out/tweets_18_24.rda")

htmlTable::htmlTable(tweets[1:3,c("text","text_cleaned")], align="l")
```

## Tokenization & Term Frequency

How to reflect the importance of a term? 3 concepts:

- TF: Term-Frenquency $tf_{v,d}$ for term $v$ and document $d$
- IDF: Inverse Document Frequency $idf_v = log(D/df_v)$, where $df_v$ is the number of documents that contain term $v$ and $D$ ist die number of Documents
- TF-IDF: $tf-idf_{d,v}=tf_{d,v} * idf_v$
  - Gives prominence to words that occur many times in few documents.

***
```{r, include=FALSE}
# load the packages
libs <- c("tidytext","tidyr",
          "plyr","dplyr",
          "htmlTable")
lapply(libs, library, character.only = TRUE)
```

```{r, include=FALSE}
rm(list = ls())
load(file = "~/GitHub/politsentiment_data/out/tweets_18_24.rda")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# get the tweets that are retweeted 
tweets$isretweet <- ifelse(grepl('^RT', tweets$text),TRUE,FALSE)

# Extract the retweets
tweets %>%
  distinct(text,name, .keep_all = TRUE) %>%
  filter(isretweet == TRUE) -> rt

# pull the original author's name
rt$sender <- substr(rt$text, 5, regexpr(':', rt$text) - 1)

# Extract the retweets
orig <-  tweets[which(tweets$isretweet==FALSE),]
```

```{r, include=FALSE}
news.token <- tweets %>%
  group_by(partei) %>%
  unnest_tokens(word, text_cleaned) %>%
  count(partei, word, sort = TRUE)  %>%
  bind_tf_idf(word, partei, n) %>%
  arrange(desc(tf_idf))
```

```{r, echo=FALSE, comment = ""}
news.token[1:10,]
```

# Statistical Methods

***
Methods to connect counts $\boldsymbol{c}_i$ to attributes $\boldsymbol{v}_i$ can be roughly divided into four categories:

**1. Dictionary-based methods**

No statistical inference. Simply specify $\boldsymbol{\hat{v}_i}=f(\boldsymbol{c}_i)$ for some unknown function $f(\cdot)$. Sometimes based on a specific dictionary of terms.

**2. Text regression methods**

Directly estimate the conditional outcome distribution $p(\boldsymbol{v}_i|\boldsymbol{c}_i)$.

**3. Generative model** of $p(\boldsymbol{c}_i|\boldsymbol{v}_i)$.

**4. Deep learning techniques** neural networks, distributed language models.

## Dictionary-based methods

- In **Tetlock (2007)** $c_i$ is a bag-of-words representation and the outcome of interest $v_i$ is the latent “sentiment” of *Wall
Street Journal* columns, defined along a number of dimensions such as “positive,” “optimistic,” etc.

- In **Baker et al. (2016)** $c_i$ is the count of articles in a given newspaper-month containing a set of pre-specified terms such as “policy,” “uncertainty,” and “Federal Reserve,” and the outcome of interest $v_i$ is the degree of “policy uncertainty” in the economy.

## Text Regression Methods

**Intuition** if we want to predict $v_i$ from $c_i$: regress the observed values of the former ($V^{train}$) on the corresponding values of the latter ($C^{train}$)

- Any generic regression technique can be applied, depending upon the nature of $v_i$

- high-dimensionality of $c_i$, ($p > n^{train}), requires use of regression techniques appropriate (e.g. $L1$ regularized linear or logistic regression)

## Generative Model

**Intuition** In many cases the underlying causal relationship runs from outcomes to language rather than the other way around. (E.g. Google searches about flu do not cause flu cases to occur, rather, people with flu are more likely to produce such searches.)

**1. Observed attributes** (supervised methods):

  - Fitting the model based on the observed training data $\boldsymbol{V}^{train}$, say $f_{\boldsymbol{\theta}}(\boldsymbol{c}_i;\boldsymbol{v}_i)$ for a vector of parameters $\boldsymbol{\theta}$, to this training set.

  - The fitted model $f_{\hat{\boldsymbol{\theta}}}$ can be inverted in order to infer $\boldsymbol{v}_i$ for documents in the test set.

***
**2. Latent attributes** (unsupervised methods):

  - The function relating $\boldsymbol{c}_i$ to $\boldsymbol{v}_i$ is unknown, as we cannot observe the true value of $v_i$. Unsupervised machine learning involves taking unclassified observations and uncovering hidden patterns that structure them in some meaningful way.

  - The outputs of algorithms for unsupervised machine learning can be used as inputs into econometric models for predicting some variable of interest, but this is a different approach from intentionally choosing the dimensions of content based on their predictive ability.

  - E.g.: Principal Component Analysis, latent Dirichlet Allocation

### 2017-10-09 textm.Rmd
new

@@
 
-2. **Statistical Methods** Map $\boldsymbol{C}$ to predict values $\boldsymbol{\hat{V}}$ of unknown outcomes $\boldsymbol{V}$. 
-	E.g.
-the variable of interest $\boldsymbol{V}$ is an indicator whether the email is spam.
-The prediction $\boldsymbol{\hat{V}}$ determines whether or not to send the email to a spam filter.
-Sometimes the attribute of interest is latent, such as the topics of a newspaper article.
+2. **Statistical Methods**
+
+  - Map $\boldsymbol{C}$ to predict values $\boldsymbol{\hat{V}}$ of unknown outcomes $\boldsymbol{V}$. 
+	- E.g. the variable of interest $\boldsymbol{V}$ is an indicator whether the email is spam. The prediction $\boldsymbol{\hat{V}}$ determines whether or not to send the email to a spam filter. 
+	- Sometimes the attribute of interest is latent (e.g. topics of a newspaper article)
 

### 2017-10-10 textm.Rmd
typo
update

@@
 ---
-title: "Text as Data"
+title: "Textmining in Economics"
 author: "Franziska Löw"
@@
 
+```{r, include=FALSE}
+# load the packages
+libs <- c("tidytext","tidyr","readr","lubridate","tm","stm",
+          "plyr","dplyr","class","knitr","kableExtra","cldr",'network', 'sna', 'qdap',
+          "htmlTable","ggplot2","gridExtra","jsonlite","stringr","scales")
+lapply(libs, library, character.only = TRUE)
+```
+
 # Introduction
 
-***
-- Most empirical work in economics relies on inherently quantitative data: prices, demand, votes, etc.
-- But a large amount of unstructured text is also generated in economic environments: 
-    - company reports, 
-    - policy committee deliberations, 
-    - court decisions, 
-    - media articles, 
-    - political speeches, etc. 
-- One can use such data qualitatively, but increasing interest in treating text quantitatively.
+## Introduction
 
-## What is Text?
-
-At an abstract level, text is simply a string of characters.
-
-- Some of these may be from the Latin alphabet ('a', 'A', 'p' and so on) but there may also be: 
+- In economics, empirical work is largely based on quantitative data (e.g. prices, demand, votes, etc.)
+- But a large amount of unstructured text is also generated in economic environments (e.g. company reports, court decisions, media articles, etc.)
+- At an abstract level, text is simply a string of characters.
+    - Latin alphabet ('a', 'A', 'p' and so on)
     - Punctuation (e.g. !), 
@@
 
-**Key Question:** How can we obtain an informative, quantitative representation of these character strings? This is the goal of text mining.
+**Key Question:** How can we obtain an informative, quantitative representation of these character strings?
 
-# Representing Text as Data
+## Concepts
 
-## Textual Database
+- A single observation in a textual database is called a *document*.
 
-- A single observation in a textual database is called a document $D$.
+- The set of documents that make up the dataset is called a *corpus*.
 
-- The set of documents that make up the dataset is called a corpus.
+- Covariates associated with each document are called *metadata*.
 
-- We often have covariates associated with each document that are sometimes called metadata.
+## Example
 
-## Reduce Dimensionality
+In the text analysis ["Bundestagswahl 2017"](https://franziloew.github.io/politsentiment/election.html) we use a corpus of Tweets containing one of the parliamentary parties during the german parliamentary elections 2017:
 
-Textmining analysis take the following steps to reduce dimensionality to a managable size:
+- 151930 Tweets (without retweets) from 12am to 12pm on the 24-10-2017
 
-1. **Represent Text as Data** Bag-of-words model, n-grams, Text-preprocessing
+- A document is a single Tweet
+
+- Associated Metadata: time, user name, if the user is a news outlet or a "privat" twitter-user, etc.
+
+```{r, include=FALSE}
+rm(list = ls())
+load(file = "~/GitHub/politsentiment_data/out/tweets_18_24.rda")
+# during and after elecction
+tweets <- tweets[which(tweets$day == "24"),]
+tweets <- with(tweets, tweets[hour(date) >= 12 & hour(date) <= 23, ])
+```
+
+```{r, message=FALSE, warning=FALSE, include=FALSE}
+# get the tweets that are retweeted 
+tweets$isretweet <- ifelse(grepl('^RT', tweets$text),TRUE,FALSE)
+
+# Extract the retweets
+tweets %>%
+  distinct(text,name, .keep_all = TRUE) %>%
+  filter(isretweet == TRUE) -> rt
+
+# pull the original author's name
+rt$sender <- substr(rt$text, 5, regexpr(':', rt$text) - 1)
+
+# Extract the retweets
+orig <-  tweets[which(tweets$isretweet==FALSE),]
+```
+
+***
+
+Text data is inherently high-dimensional, so an analysis of text usually tries to reduce this dimensionality following these steps:
+
+1. Represent the textual database $D$ (**document**) as a numerical array $\boldsymbol{C}$ (**corpus**)
+  - *Text-preprocessing, Bag-of-words model*
 
 2. **Statistical Methods** 
-
   - Map $\boldsymbol{C}$ to predict values $\boldsymbol{\hat{V}}$ of unknown outcomes $\boldsymbol{V}$. 
-	- E.g. the variable of interest $\boldsymbol{V}$ is an indicator whether the email is spam. The prediction $\boldsymbol{\hat{V}}$ determines whether or not to send the email to a spam filter. 
 	- Sometimes the attribute of interest is latent (e.g. topics of a newspaper article)
@@
 
-## Represent text as Data
-Convert raw text $D$ to a numerical array $\boldsymbol{C}$:
-A basic quantitative representation of a corpus is the bag-of-words model:
+## Text Pre-Processing
+
+1. **Tokenization** splitting of a raw character string into individual elements of interest: words, numbers, punctuation.
+
+2. **Stopword Removal** Stopwords (highly frequent terms) are stripped out of token lists as they do not help distinguish one document from another.
+
+3. **Linguistic Roots** For many applications, the relevant information in tokens is their linguistic root, not their grammatical form (e.g. treat "looking", "look", "looks" as equivalent tokens)
+
+4. **Multi-Word Phrases** Sometimes groups of individual tokens like “United Kingdom”  have a specific meaning (Use Ngrams)
+
+## Cleaning Data
+
+```{r, echo=FALSE}
+htmlTable(orig[1:4,c("text","text_cleaned")], align = "l")
+```
+
+## Tokenization
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+orig$text_cleaned <- removeWords(orig$text_cleaned, c("cdu","csu","union","spd","fdp","grüne","grünen","linke","afd"))
+
+orig %>%
+  #group_by(partei) %>%
+  unnest_tokens(word, text_cleaned) %>%
+  count(word, sort = TRUE)  %>%
+  top_n(15) %>%
+  htmlTable()
+```
+
+## Tokenization (Bigrams)
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+orig %>%
+  #group_by(partei) %>%
+  unnest_tokens(bigram, text_cleaned, token="ngrams", n=2) %>%
+  count(bigram, sort = TRUE)  %>%
+  top_n(15) %>%
+  htmlTable()
+```
+
+## What is the data?
+
+After pre-processing, each document is a finite list of terms.
+
+A basic quantitative representation of a corpus is the **bag-of-words model**
 
@@
 
-## Text Mining and Information
+## bag-of-words model
 
@@
 
-## Text Pre-Processing
+# Term Frequency
 
-Pre-process strings to obtain a cleaner representation:
-
-1. **Tokenization** splitting of a raw character string into individual elements of interest.
-
-2. **Stopword Removal** The frequency distribution of words in natural languages is highly skewed.
-
-3. **Linguistic Roots** For many applications, the relevant information in tokens is their linguistic root, not their grammatical form. (Stemming or Lemmatizing)
-
-4. **Multi-Word Phrases** Sometimes groups of individual tokens like “donald trump” or “fc bayern” have a specific meaning.
-
-## Example: Twitter
-
-Tweets after Stopword Removal.
-
-```{r, echo=FALSE}
-rm(list = ls())
-load(file = "~/GitHub/politsentiment_data/out/tweets_18_24.rda")
-
-htmlTable::htmlTable(tweets[1:3,c("text","text_cleaned")], align="l")
-```
-
-## Tokenization & Term Frequency
-
+***
 How to reflect the importance of a term? 3 concepts:
@@
 ***
-```{r, include=FALSE}
-# load the packages
-libs <- c("tidytext","tidyr",
-          "plyr","dplyr",
-          "htmlTable")
-lapply(libs, library, character.only = TRUE)
-```
-
-```{r, include=FALSE}
-rm(list = ls())
-load(file = "~/GitHub/politsentiment_data/out/tweets_18_24.rda")
-```
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
-# get the tweets that are retweeted 
-tweets$isretweet <- ifelse(grepl('^RT', tweets$text),TRUE,FALSE)
-
-# Extract the retweets
-tweets %>%
-  distinct(text,name, .keep_all = TRUE) %>%
-  filter(isretweet == TRUE) -> rt
-
-# pull the original author's name
-rt$sender <- substr(rt$text, 5, regexpr(':', rt$text) - 1)
-
-# Extract the retweets
-orig <-  tweets[which(tweets$isretweet==FALSE),]
-```
 
@@
 
-- high-dimensionality of $c_i$, ($p > n^{train}), requires use of regression techniques appropriate (e.g. $L1$ regularized linear or logistic regression)
+- high-dimensionality of $c_i$, ($p > n^{train}$), requires use of regression techniques appropriate (e.g. $L1$ regularized linear or logistic regression)
 

### 2017-10-13 textm.Rmd
more

@@
 
-  - E.g.: Principal Component Analysis, latent Dirichlet Allocation
+  - E.g.: Principal Component Analysis, Topic Modeling (latent Dirichlet Allocation)
+
+# Topic Modeling
+## Topic Modeling
+
+method for finding a group of words (i.e topic) from a collection of documents that best represents the information in the collection.
+
+  - Discovering hidden topical patterns that are present across the collection
+  - Annotating documents according to these topics
+  - Using these annotations to organize, search and summarize texts
+
+There are many techniques that are used to obtain topic models: Latent Dirichlet allocation
+
+## Latent Dirichlet Allocation (LDA)
+
+consider the following set of documents as the corpus:
+```{r}
+doc1 <- "I had a peanut butter sandwich for breakfast"
+doc2 <- "I like to eat almonds, peanut and walnuts."
+doc3 <- "My neighbor got a little dog yesterday."
+doc4 <- "Cats and dogs are mortal enemies."
+doc5 <- "You must not feed peanuts to your dog."
+```
+
+This gives the following Document-Term-Matrix
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+library(tm)
+
+# Build corpus 
+corpus <- rbind(doc1, doc2, doc3, doc4, doc5)
+
+# clean corpus
+corpus <- tolower(corpus)
+corpus <- removeWords(corpus, stopwords("english"))
+corpus <- gsub( "[^[:alnum:]]", " ", corpus)
+corpus <- gsub("^\\s+|\\s+$", "", corpus)
+
+#Create document-term matrix
+dtm <- Corpus(VectorSource(corpus))
+dtm <- DocumentTermMatrix(dtm)
+
+inspect(dtm)
+```
+
+***
+Now we set the model parameter
+
+```{r, include=FALSE}
+library(lda)
+
+corpusLDA <- lexicalize(corpus)
+```
+
+```{r, echo=FALSE}
+ldaModel <- lda.collapsed.gibbs.sampler(corpusLDA$documents,K=2,vocab=corpusLDA$vocab,burnin=9999,num.iterations=100000,alpha=0.8,eta=0.1)
+
+top.words <- top.topic.words(ldaModel$topics, 3, by.score=TRUE)
+print(top.words)
+```

### 2017-10-14 textm.Rmd
new examples

@@
 - But a large amount of unstructured text is also generated in economic environments (e.g. company reports, court decisions, media articles, etc.)
-- At an abstract level, text is simply a string of characters.
-    - Latin alphabet ('a', 'A', 'p' and so on)
-    - Punctuation (e.g. !), 
-    - Numbers, 
-    - Non-alphanumerical characters (e.g. @)
+- At an abstract level, text is simply a string of characters 
+    - Latin alphabet ('a', 'A', 'p' and so on), Punctuation (e.g. !), Numbers,Non-alphanumerical characters (e.g. @)
 
@@
 - Associated Metadata: time, user name, if the user is a news outlet or a "privat" twitter-user, etc.
+
+***
 
@@
 
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+ggplot(tweets, aes(date, fill = partei)) + 
+    geom_histogram(alpha = .8, adjust = .25, binwidth = 500) +
+    scale_fill_manual(name = "", values = c("deepskyblue1", "black","limegreen", "darkorchid2","gold", "red2")) +
+    xlab("") +
+    ylab("Anzahl der Tweets") +
+    scale_x_datetime(breaks = date_breaks("2 hour"), labels=date_format("%a-%d\n%H:%M", tz="CET"))
+```
+
 ***
@@
 
-1. Represent the textual database $D$ (**document**) as a numerical array $\boldsymbol{C}$ (**corpus**)
-  - *Text-preprocessing, Bag-of-words model*
+1. Pre-process the text (Stopword removal, tokenization, stemming) and Represent(**document** $D$ as a numerical array $\boldsymbol{C}$ (e.g. *bag-of-words model*)
 

### 2017-10-14 textm.Rmd
new

@@
 
+***
 This gives the following Document-Term-Matrix
@@
 
-***
-Now we set the model parameter
-
-```{r, include=FALSE}
+```{r, eval=FALSE}
 library(lda)
@@
 
-```{r, echo=FALSE}
+```{r, eval=FALSE}
 ldaModel <- lda.collapsed.gibbs.sampler(corpusLDA$documents,K=2,vocab=corpusLDA$vocab,burnin=9999,num.iterations=100000,alpha=0.8,eta=0.1)

### 2017-10-14 textm.Rmd
new

@@
 
-```{r, eval=FALSE}
+```{r, eval=FALSE, include=FALSE}
 library(lda)
@@
 
-```{r, eval=FALSE}
+```{r, eval=FALSE, include=FALSE}
 ldaModel <- lda.collapsed.gibbs.sampler(corpusLDA$documents,K=2,vocab=corpusLDA$vocab,burnin=9999,num.iterations=100000,alpha=0.8,eta=0.1)

### 2017-10-17 textm.Rmd
little bit more on slides

@@
 tweets <- with(tweets, tweets[hour(date) >= 12 & hour(date) <= 23, ])
+
+col <- c("deepskyblue1", "black","limegreen", "darkorchid2","gold", "red2")
+names(col) <- levels(tweets$partei)
 ```
@@
 
-1. Pre-process the text (Stopword removal, tokenization, stemming) and Represent(**document** $D$ as a numerical array $\boldsymbol{C}$ (e.g. *bag-of-words model*)
+1. **Pre-process** the text (Stopword removal, tokenization, stemming) and represent document $D$ as a numerical array $\boldsymbol{C}$ (e.g. bag-of-words model)
 
@@
 
-## Cleaning Data
+## Cleaning Data (Example)
 
 ```{r, echo=FALSE}
-htmlTable(orig[1:4,c("text","text_cleaned")], align = "l")
+orig$retweet_count <- as.numeric(orig$retweet_count)
+
+orig %>%
+  arrange(desc(retweet_count)) -> orig
+
+htmlTable(orig[c(1,4,5,7),c("text","text_cleaned")], align = "l")
 ```
@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE}
-orig$text_cleaned <- removeWords(orig$text_cleaned, c("cdu","csu","union","spd","fdp","grüne","grünen","linke","afd"))
+orig$text_cleaned <- removeWords(orig$text_cleaned, c("cdu","csu","union","spd","fdp","grüne","grünen","linke","afd","btw"))
 
@@
   unnest_tokens(word, text_cleaned) %>%
-  count(word, sort = TRUE)  %>%
-  top_n(15) %>%
-  htmlTable()
-```
+  count(word, sort = TRUE) -> tokens
 
-## Tokenization (Bigrams)
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
 orig %>%
@@
   unnest_tokens(bigram, text_cleaned, token="ngrams", n=2) %>%
-  count(bigram, sort = TRUE)  %>%
-  top_n(15) %>%
-  htmlTable()
+  count(bigram, sort = TRUE) -> bigrams
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+tokens %>%
+  top_n(20) %>%
+  ggplot() +
+  aes(x= reorder(word, n), y=n) +
+  geom_col() +
+  labs(title = "Tokens") +
+  xlab("") +
+  coord_flip() -> p1
+
+bigrams %>%
+  top_n(20) %>%
+  ggplot() +
+  aes(x= reorder(bigram, n), y=n) +
+  geom_col() +
+  labs(title = "Bigrams") +
+  xlab("") +
+  coord_flip() -> p2
+
+grid.arrange(p1, p2, ncol = 2)
+```
+
+## Wordclouds
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+library(wordcloud)
+# WordClouds ####
+# get text
+cdu <- orig[which(orig$partei=="CDU"),]
+spd <- orig[which(orig$partei=="SPD"),]
+fdp <- orig[which(orig$partei=="FDP"),]
+gruene <- orig[which(orig$partei=="Die Grünen"),]
+linke <- orig[which(orig$partei=="DIE LINKE"),]
+afd <- orig[which(orig$partei=="AfD"),]
+
+# Join texts in a vector 
+cdu <- paste(cdu$text_cleaned, collapse = " ")
+spd <- paste(spd$text_cleaned, collapse = " ")
+fdp <- paste(fdp$text_cleaned, collapse = " ")
+gruene <- paste(gruene$text_cleaned, collapse = " ")
+linke <- paste(linke$text_cleaned, collapse = " ")
+afd <- paste(afd$text_cleaned, collapse = " ")
+
+# put everything in a single vector
+all <- c(cdu, spd, fdp,gruene, linke, afd)
+
+ignore <- paste(c("cdu","bündnis", "spd","fdp","gruene","grüne","grünen", "linke","dielinke","afd","gen","merkel","schulz","csu","union"), collapse = "|")
+all <- gsub(ignore,"", all)
+
+# Step 2: Corpus and term-docs_cleaned matrix ####
+# create corpus
+corp <- Corpus(VectorSource(all))
+
+# create term-docs_cleaned matrix
+tdm <- TermDocumentMatrix(corp)
+
+# convert as matrix
+tdm <- as.matrix(tdm)
+
+# add column names
+colnames(tdm) <- c("CDU","SPD","FDP","Die Grünen", "DIE LINKE","AfD")
+
+# Step 3: Plot comparison wordcloud ####
+comparison.cloud(tdm, random.order=FALSE, colors = c("black","red2", "gold","limegreen", "darkorchid2","deepskyblue1"), scale=c(3,.5),
+                 title.size=1.2, max.words=100)
 ```
@@
 
-***
+## Term Frequency
+
 How to reflect the importance of a term? 3 concepts:
 
-- TF: Term-Frenquency $tf_{v,d}$ for term $v$ and document $d$
-- IDF: Inverse Document Frequency $idf_v = log(D/df_v)$, where $df_v$ is the number of documents that contain term $v$ and $D$ ist die number of Documents
-- TF-IDF: $tf-idf_{d,v}=tf_{d,v} * idf_v$
+- **TF** Term-Frenquency $tf_{v,d}$ for term $v$ and document $d$
+- **IDF** Inverse Document Frequency $idf_v = log(\frac{D}{df_v})$, where $df_v$ is the number of documents that contain term $v$ and $D$ ist die number of Documents
+- **TF-IDF** $tf-idf_{d,v}=tf_{d,v} * idf_v$
   - Gives prominence to words that occur many times in few documents.
 
-***
+## Term Frequency (Example)
 
 ```{r, include=FALSE}
-news.token <- tweets %>%
+tokens <- orig %>%
   group_by(partei) %>%
@@
   count(partei, word, sort = TRUE)  %>%
-  bind_tf_idf(word, partei, n) %>%
-  arrange(desc(tf_idf))
+  bind_tf_idf(word, partei, n)
 ```
 
-```{r, echo=FALSE, comment = ""}
-news.token[1:10,]
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+tokens %>%
+  top_n(5) %>%
+  ggplot() +
+  aes(x= reorder(word, tf_idf), y=tf_idf, fill = partei) +
+  geom_col(alpha=.8, show.legend = FALSE) +
+  labs(x = NULL, y = "tf-idf") +
+  scale_fill_manual(name="", values=col) +
+  coord_flip() -> p1
+
+tokens %>%
+  top_n(5) %>%
+  ggplot() +
+  aes(x= reorder(word, tf), y=tf, fill = partei) +
+  geom_col(alpha=.8, show.legend = FALSE) +
+  labs(x = NULL, y = "tf") +
+  scale_fill_manual(name="", values=col) +
+  coord_flip() -> p2
+
+grid.arrange(p1, p2, ncol = 2)
 ```
@@
 
-  - The function relating $\boldsymbol{c}_i$ to $\boldsymbol{v}_i$ is unknown, as we cannot observe the true value of $v_i$.
-Unsupervised machine learning involves taking unclassified observations and uncovering hidden patterns that structure them in some meaningful way.
+  - **Starting Point** The true value of $v_i$ is unobserved -> The function relating $\boldsymbol{c}_i$ to $\boldsymbol{v}_i$ is unknown
 
-  - The outputs of algorithms for unsupervised machine learning can be used as inputs into econometric models for predicting some variable of interest, but this is a different approach from intentionally choosing the dimensions of content based on their predictive ability.
+  - **Idea** Uncover hidden patterns that structure the observations in some meaningful way.
 
-  - E.g.: Principal Component Analysis, Topic Modeling (latent Dirichlet Allocation)
+  - **Use** The outputs of algorithms can be used as inputs into econometric models for predicting some variable of interest.
+
+  - **E.g.** Principal Component Analysis, Topic Modeling (latent Dirichlet Allocation)
 
@@
 
-method for finding a group of words (i.e topic) from a collection of documents that best represents the information in the collection.
+A method for finding a group of words (i.e topic) from a collection of documents that best represents the information in the collection.
 
-  - Discovering hidden topical patterns that are present across the collection
+  - Discovering **hidden topical patterns** that are present across the collection
   - Annotating documents according to these topics
@@
 
-There are many techniques that are used to obtain topic models: Latent Dirichlet allocation
+Very popular topic model is the **Latent Dirichlet allocation**
 

### 2017-10-18 paper/R/eventregist_analysis.Rmd
lit

---
title: "Topic Modeling of News"
author: "Franziska Löw"
date: "`r format(Sys.Date())`"
output: github_document
---

```{r, include=FALSE}
# load the packages
libs <- c("tidytext","tidyr","readr","lubridate","tm","stm",
          "plyr","dplyr","class","knitr","kableExtra","cldr","data.table",
          "htmlTable","ggplot2","gridExtra","jsonlite","stringr","scales")
lapply(libs, library, character.only = TRUE)
```

# Load and prepare Dataframe

```{r, message=FALSE, include=FALSE}
opts_knit$set(root.dir = "/Users/Franzi/CloudStation/textmining")
rm(list=ls())

theme_set(new = theme_bw())
set.seed(95616)

# set color
library(grDevices)
col <- c("#FF61CC","#C77CFF","#00A9FF","#00BFC4","#00BE67","#7CAE00","#CD9600","#F8766D")

# load the dataframe
news <- read_feather('/Users/Franzi/CloudStation/textmining/data/news_sep2')

# Format the time Variable
news$date <- as.POSIXct(news$date, format ="%Y-%m-%d")
```

## Subset Data

```{r}
# keep only german articles
news <- news[which(news$lang == "deu"),]

# Delete Articel "Die Welt"
news %>%
  filter(source != "DIE WELT") -> news

news %>%
  arrange(date) -> news
```

### Number of published Articels by News Source

```{r}
news %>%
  group_by(source) %>%
  tally(sort = TRUE)%>%
  ggplot(aes(source, n)) +
  geom_col(fill = col, alpha = 0.7)
```

### Number of published Articels by News Source and Date

```{r}
news %>%
  group_by(date, source) %>%
  tally(sort = TRUE) -> news.count

ggplot(news.count, aes(x = date, y = n,  group = source)) + 
  geom_line(aes(color = source)) +
  xlab('Publish Date') +
  ylab("Number of Articels")

```

# Pre-Process Text

```{r, message=FALSE, warning=FALSE, include=FALSE}
clean.text = function(x)
{
  x = tolower(x)
  x = gsub("[[:punct:]]", " ", x)  # replace punctuation with space
  x = gsub("[[:cntrl:]]", " ", x)  # replace control characters with space
  x = gsub("[[:digit:]]", "", x)  # remove numbers
  x = gsub("ὣ", " ", x)
  x = gsub("\n{1,}Anzeige\n{1,}", " ", x)
  x = gsub("^[[:space:]]+", "", x) # remove whitespace at beginning of documents
  x = gsub("[[:space:]]+$", "", x) # remove whitespace at end of documents 
  x = gsub("[\n{2,}]", "", x)
  return(x)
}

# apply function to the "orig" dataframe
news$text_cleaned <- clean.text(news$text)

# get stopwords from online dict and add costum stopwords
#exceptions   <- c("nicht")
#my_stopwords <- setdiff(stopwords("german"), exceptions)
my_stopwords <- c(stopwords("german"), 'stern','spiegel','focus','n-tv',"spon","zeitmagazin","sz", "seitennavigation","startseite","gibt","immer","uhr","dass","mehr","sagte","sei","wurde","twitterfacebookgoogle","bildplus","whatsappteilen","kartengeschichte","elbvertiefung","econa","dpa","prozent","freepik","colourbox")

# Remove stopwords
news$text_cleaned<- removeWords(news$text_cleaned, my_stopwords)

# save file
write.csv(news, file = "/Users/Franzi/CloudStation/textmining/data/news_cleaned.csv")
```

## Tokenize terms

```{r}
news.token <- news %>%
  group_by(source) %>%
  unnest_tokens(word, text_cleaned) %>%
  count(source, word, sort = TRUE)  %>%
  bind_tf_idf(word, source, n) %>%
  arrange(desc(tf_idf)) 
```

# Topic Modeling
## LDA
```{r}
# Build corpus
btw.lda <- Corpus(VectorSource(btw$text_cleaned))
# Create document-term matrix
dtm <- DocumentTermMatrix(btw.lda)
```

```{r}
# Run LDA using Gibbs sampling
library(topicmodels)

k = 20 # Topics

t1 <- Sys.time()
lda20 <-LDA(dtm, 20, method="Gibbs", control=list(nstart=5, iter = 10000))
t2 <- Sys.time()
t2 - t1
```

## Structural Topic Model

```{r}
btw <- btw[,c("date","source","text_cleaned")]

# Process data
processed <- textProcessor(btw$text_cleaned, metadata = btw,
                           wordLengths = c(2,Inf),
                           lowercase = F,
                           removestopwords = F,
                           removenumbers = F,
                           removepunctuation = F,
                           stem = F)
out <- prepDocuments(processed$documents, processed$vocab, processed$meta)
```

### Estimation
```{r, echo=FALSE, message=FALSE, warning=FALSE}
t1 <- Sys.time()
stm <- stm(documents = out$documents, vocab = out$vocab, K=20, prevalence = ~source+s(date), data=out$meta, init.type = "Spectral")
t2 <- Sys.time()
t2 - t1

#save(stm, file = "stm_k40.RDa")
```

### Interpret the results

#### Wordclouds by topic
```{r}
cloud(stm, topic =8, scale = c(5,.25))
```

```{r}
# get document - topic distribution 
theta <- as.data.frame(stm$theta)
theta$source <- out$meta$source
theta$date <- out$meta$date
```

#### get the mean distribution of topics  ...
##### ... by date
```{r}
theta %>% 
  select(- source) %>%
  group_by(date) %>% 
  summarise_all(funs(mean)) -> date_mean

# plot 
melt1 = melt(date_mean, id = "date")

ggplot(melt1, aes(x=date, y = variable)) +   
  geom_raster(aes(fill=value)) + 
  scale_fill_gradient(low = "light blue", high = "dark blue") +
  labs(x="Date", y="Topics", title="Average Topic Weights") + 
  theme_bw()

```

##### ... by source
```{r, message=FALSE, warning=TRUE}
theta %>% 
  select(- date) %>%
  group_by(source) %>% 
  summarise_all(funs(mean)) -> source_mean

# plot 
melt2 = melt(source_mean, id = "source")

ggplot(melt2, aes(x=source, y = variable)) +   
  geom_raster(aes(fill=value)) + 
  scale_fill_gradient(low = "light blue", high = "dark blue") +
  labs(x="Source", y="Topics", title="Average Topic Weights") + 
  theme_bw()

```

### compute cosine similarity

```{r, message=FALSE}
library(proxy)
cosine_dist <- as.matrix(dist(as.matrix(source_mean[,1:20]), method = "cosine"))
colnames(cosine_dist) <- unique(out$meta$source)
rownames(cosine_dist) <- unique(out$meta$source)
```

### Correlogram
```{r, message=FALSE}
devtools::install_github("sinhrks/ggfortify")
library("ggfortify")
devtools::install_github("kassambara/ggcorrplot")
library(ggcorrplot)
library("ggthemes")

ggcorrplot(cosine_dist, hc.order = TRUE, 
           type = "lower", 
           lab = TRUE, 
           lab_size = 3, 
           method="circle", 
           #colors = c("tomato2", "white", "springgreen3"), 
           title="", 
           ggtheme=theme_bw)
```

### correlations between topics
```{r}
mod.out.corr <- topicCorr(stm)
plot(mod.out.corr)
```

### stmBrowser
```{r}
library(stmBrowser)
setwd(tempdir())
stmBrowser(stm, data=out$meta, c("source","date"), text="text_cleaned")

```

### 2017-10-18 paper/R/webhoseio.Rmd
lit

---
title: "Topic Modeling of News"
author: "Franziska Löw"
date: "`r format(Sys.Date())`"
output: github_document
---

```{r, include=FALSE}
# load the packages
libs <- c("tidytext","tidyr","readr","lubridate","tm","stm","RColorBrewer",
          "plyr","dplyr","class","knitr","kableExtra","cldr","data.table",
          "htmlTable","ggplot2","gridExtra","jsonlite","stringr","scales","rjson")
lapply(libs, library, character.only = TRUE)

```

# Load and prepare Dataframe

```{r, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
rm(list = ls())

# create a character vector, with each file name represented by an entry
#june <- list.files("~/CloudStation/textmining/data/webhoseio/2017-06", pattern="*.json", full.names=TRUE) 
#july <- list.files("~/CloudStation/textmining/data/webhoseio/2017-07", pattern="*.json", full.names=TRUE) 
aug <- list.files("~/CloudStation/textmining/data/webhoseio/2017-08", pattern="*.json", full.names=TRUE) 
#sep <- list.files("~/CloudStation/textmining/data/webhoseio/2017-09", pattern="*.json", full.names=TRUE)

# a list in which each element is one of your original JSON files
#myJSON <- lapply(c(june,july,aug,sep), function(x) fromJSON(file=x)) 
myJSON <- lapply(aug, function(x) fromJSON(file=x))

length(myJSON)
```

## Convert List to Dataframe

```{r, eval=FALSE, include=FALSE}
site <- NULL
title <- NULL
text <- NULL
published <- NULL
fb_shares <- NULL
fb_likes <- NULL
section <- NULL
external_links <- NULL

for (i in 1:length(myJSON)){
  site <- append(site, myJSON[[i]]["thread"][[1]]["site"][[1]])
  title <- append(title, myJSON[[i]]["title"][[1]])
  text <- append(text, myJSON[[i]]["text"][[1]])
  published <- append(published, myJSON[[i]]["published"][[1]])

  fb_shares <- append(fb_shares, myJSON[[i]]["thread"][[1]]["social"][[1]]["facebook"][[1]][["shares"]])
  fb_likes <- append(fb_likes, myJSON[[i]]["thread"][[1]]["social"][[1]]["facebook"][[1]][["likes"]])

  section <- append(section, myJSON[[i]]["thread"][[1]]["section_title"][[1]])
  external_links <- append(external_links, length(myJSON[[i]]["external_links"][[1]]))

}

df <- cbind(site, title, text, published, fb_shares, fb_likes, section, external_links)
df <- data.frame(df, stringsAsFactors = FALSE)

rm(site, title, text, published, fb_shares, fb_likes, section, external_links)
```

## Define private and public service operators

```{r, eval=FALSE, include=FALSE}
private <- c("bild.de","focus.de","handelsblatt.com","spiegel.de","stern.de","welt.de","zeit.de")

df %>%
  mutate(owned = ifelse(site %in% private, "private", "public")) -> df
```

## Subset by
```{r, eval=FALSE, include=FALSE}
# .... date
df$date <- substr(df$published, 1,10)
df$date <- as.POSIXct(df$date, format ="%Y-%m-%d")

df <- subset(df, df$date > "2017-09-01")
```

```{r, eval=FALSE, include=FALSE}
# ... content
content <- c("Bundestagswahl","Merkel","Schulz","Wagenknecht","Lindner","Gauland","Özdemir",
             "CDU","SPD","FDP","AfD","Die Grünen","Die Linke")

btw <- df[which(grepl(paste(content, collapse = "|"), df$title)),]

# Save file
write.csv(btw, file="~/CloudStation/textmining/R/output/btw.csv")
```

## Load Data

```{r}
rm(list = ls())
df <- read.csv("output/btw.csv")
```

### Number of published Articels by News Source

```{r}
col <- brewer.pal(12, name = "Paired")

df %>%
  group_by(site) %>%
  tally(sort = TRUE) %>%
  ggplot(aes(site, n)) +
  geom_col(fill = col, alpha = .8) +
  xlab("") +
  ylab("") +
  theme(axis.text.x = element_text(angle = 40, hjust = 1))
```

### Number of published Articels by Ownership

```{r}
df %>%
  group_by(owned) %>%
  tally(sort = TRUE) %>%
  ggplot(aes(owned, n)) +
  geom_col(fill = col[c(6,2)], alpha = .8) +
  geom_text(aes(label=n), position = position_stack(vjust = 0.5)) +
  xlab("") +
  ylab("") +
  theme(axis.text.x = element_text(angle = 40, hjust = 1))
```

# Pre-Process Text

```{r, echo=FALSE, message=FALSE, warning=FALSE}
clean.text = function(x)
  {
  x = gsub("[[:punct:]]", " ", x)  # replace punctuation with space

  x = gsub("DIE WELT", "", x)
  x = gsub("SPIEGEL ONLINE", "", x)
  x = gsub("FOCUS Online", "", x)
  x = gsub("ZEIT ONLINE", "", x)
  x = gsub("stern de", "", x)
  x = gsub("Handelsblatt", "", x)
  x = gsub("Politik Inland Bild de", "", x)
  x = gsub("BILDplus Inhalt", "", x)
  x = gsub("Bild de", "", x)
  x = gsub("SWR Aktuell", "", x)
  x = gsub("SWR de", "", x)
  x = gsub("[ ]NDR[ ]", "", x)
  x = gsub('ZDF \"\"Morgenmagazin\"\"', "", x)
  x = gsub("ZDFmediathek", "", x)
  x = gsub("[ ]ZDF[ ]", "", x)
  x = gsub("[ ]ARD[ ]", "", x)

  x = gsub("die neuesten Nachrichten", "", x)
  x = gsub("RSS Feed", "", x)
  x = gsub("Der Überblick   7 mal 17   Alle Artikel", "", x)
  x = gsub("Der Tag im Überblick", "", x)
  x = gsub("Inhalt Seite 1", "", x)
  x = gsub("Seite 2", "", x)
  x = gsub("dpa", "", x)
  x = gsub("Twitter Anzeige", "", x)
  x = gsub("Anzeige", "", x)
  x = gsub("Foto  \\w+", "", x)
  x = gsub("Video", "", x)
  x = gsub("Quelle \\w+", "", x)
  x = gsub("\\w+ \\w+ Getty Images", "", x)
  x = gsub("AFP", "", x)
  x = gsub("August", "", x)
  x = gsub("Live-Ticker", "", x)
  x = gsub("Deutsche Presse Agentur GmbH   Nachrichtenagentur Alle Beiträge von  anzeigen", "", x)
  x = gsub("Deutsche Presse Agentur", "", x)

  x = gsub("[[:punct:]]", " ", x)  # replace punctuation with space
  x = gsub("[[:cntrl:]]", " ", x)  # replace control characters with space
  x = gsub("[[:digit:]]", "", x)  # remove numbers
  x = gsub("^[[:space:]]+", "", x) # remove whitespace at beginning of documents
  x = gsub("[[:space:]]+$", "", x) # remove whitespace at end of documents 
  x = gsub("[\n{2,}]", "", x)
  x = tolower(x)
  return(x)
}

# apply function to the "orig" dataframe
df$text_cleaned <- clean.text(df$text)

df %>%
  filter(grepl("Getty Images", text)) %>%
  select(text, text_cleaned) %>%
  htmlTable(align = "l")
```

```{r}
# get stopwords from online dict and add costum stopwords
#exceptions   <- c("nicht")
#my_stopwords <- setdiff(stopwords("german"), exceptions)
my_stopwords <- c(stopwords("german"), "spon","zeitmagazin","sz", "seitennavigation","startseite","gibt","immer","uhr","dass","mehr","sagte","sei","wurde","twitterfacebookgoogle","whatsappteilen","kartengeschichte","elbvertiefung","econa","prozent","freepik","colourbox")

# Remove stopwords
df$text_cleaned<- removeWords(df$text_cleaned, my_stopwords)

# save file
write.csv(df, file = "/Users/Franzi/CloudStation/textmining/data/news_cleaned.csv")
```

## Tokenize terms
```{r}
news.token <- df %>%
  group_by(site) %>%
  unnest_tokens(word, text_cleaned) %>%
  count(site, word, sort = TRUE)  %>%
  bind_tf_idf(word, site, n) %>%
  arrange(desc(tf_idf)) 
```

# Topic Modeling
## LDA
```{r}
# Build corpus
btw.lda <- Corpus(VectorSource(df$text_cleaned))
# Create document-term matrix
dtm <- DocumentTermMatrix(btw.lda)
```

```{r}
# Run LDA using Gibbs sampling
library(topicmodels)

k = 20 # Topics

t1 <- Sys.time()
lda20 <-LDA(dtm, 20, method="Gibbs", control=list(nstart=5, iter = 10000))
t2 <- Sys.time()
t2 - t1
```

## Structural Topic Model

```{r, eval=FALSE, include=FALSE}
# Process data
processed <- textProcessor(df$text_cleaned, metadata = df[,c("date","site","text_cleaned","text")],
                           wordLengths = c(2,Inf),
                           lowercase = F,
                           removestopwords = F,
                           removenumbers = F,
                           removepunctuation = F,
                           stem = F)
out <- prepDocuments(processed$documents, processed$vocab, processed$meta)
```

### Run the Model 
```{r}

t1 <- Sys.time()
stm <- stm(documents = out$documents, 
           vocab = out$vocab, 
           K=25, 
           prevalence = ~site, 
           content = ~site, 
           data=out$meta, 
           init.type = "Spectral")
t2 <- Sys.time()
t2 - t1

save(stm, out, file = "stm.RDa")
#load(file = "stm.RDa")

```

### Interpret the results

#### Wordclouds by topic
```{r}
cloud(stm, topic =8, scale = c(5,.25))
```

```{r}
# get document - topic distribution 
theta <- as.data.frame(stm$theta)
theta$source <- out$meta$source
theta$date <- out$meta$date
```

#### get the mean distribution of topics  ...
##### ... by date
```{r}
theta %>% 
  select(- source) %>%
  group_by(date) %>% 
  summarise_all(funs(mean)) -> date_mean

# plot 
melt1 = melt(date_mean, id = "date")

ggplot(melt1, aes(x=date, y = variable)) +   
  geom_raster(aes(fill=value)) + 
  scale_fill_gradient(low = "light blue", high = "dark blue") +
  labs(x="Date", y="Topics", title="Average Topic Weights") + 
  theme_bw()

```

##### ... by source
```{r, message=FALSE, warning=TRUE}
theta %>% 
  select(- date) %>%
  group_by(source) %>% 
  summarise_all(funs(mean)) -> source_mean

# plot 
melt2 = melt(source_mean, id = "source")

ggplot(melt2, aes(x=source, y = variable)) +   
  geom_raster(aes(fill=value)) + 
  scale_fill_gradient(low = "light blue", high = "dark blue") +
  labs(x="Source", y="Topics", title="Average Topic Weights") + 
  theme_bw()

```

### compute cosine similarity

```{r, message=FALSE}
library(proxy)
cosine_dist <- as.matrix(dist(as.matrix(source_mean[,1:20]), method = "cosine"))
colnames(cosine_dist) <- unique(out$meta$source)
rownames(cosine_dist) <- unique(out$meta$source)
```

### Correlogram
```{r, message=FALSE}
devtools::install_github("sinhrks/ggfortify")
library("ggfortify")
devtools::install_github("kassambara/ggcorrplot")
library(ggcorrplot)
library("ggthemes")

ggcorrplot(cosine_dist, hc.order = TRUE, 
           type = "lower", 
           lab = TRUE, 
           lab_size = 3, 
           method="circle", 
           #colors = c("tomato2", "white", "springgreen3"), 
           title="", 
           ggtheme=theme_bw)
```

### correlations between topics
```{r}
mod.out.corr <- topicCorr(stm)
plot(mod.out.corr)
```

### stmBrowser
```{r}
library(stmBrowser)
setwd(tempdir())
stmBrowser(stm, data=out$meta, c("source","date"), text="text_cleaned")

```

### 2017-10-18 paper/python/NewsDownloader.py

@@ -1,0 +1,67 @@
+# Mining data from news sources
+# (http://students.washington.edu/adelak/2017/01/?p=209)
+
+import pickle
+from eventregistry import *
+
+
+# Class NewsDownloader, will download all of the articles it can get from
+# the EventRegistry database and then save them to file -
+# given a list of source URIs1 (e.g. ['www.stern.de', 'www.spiegel.de'])
+
+class NewsDownloader(object):
+    er = EventRegistry(apiKey = "7564c27a-9e81-4f7e-bc65-540e1eb0d9a0")
+
+    def __init__(self, name, source_uris):
+        # input
+        self.name = name
+        self.source_uris = source_uris
+
+        # These 3 functions will be defined below
+        self.art_uris = self._get_article_uris()
+        self.full_articles = self._get_articles()
+        self.save_obj()
+
+    ## Get article URIs
+
+    def _get_article_uris(self):
+        results = []
+        for uri in self.source_uris:
+            # for each source URI in the original list,
+            # set up a query using EventRegistry’s QueryArticles() class:
+            query = QueryArticles(sourceUri=uri)
+            # Only return articles from our source
+            query.setRequestedResult(RequestArticlesUriList())
+            # only give a list of the article URIs:
+            results += NewsDownloader.er.execQuery(query).get("uriList", {}).get("results", [])
+        return results
+
+    ## Get articles
+
+    def _get_articles(self, n_arts=200): # Max of 200 articles returned per call
+        # assert statement is basically a dummy check to make sure the previous step succeeded
+        assert self.art_uris is not None
+
+        art_uri_list = self.art_uris
+        results = []
+        # Take the self.art_uris list and break it into smaller chunks of 200 articles each
+        for i in range(0, len(art_uri_list), n_arts):
+            small_uri_list = art_uri_list[i:i + n_arts]
+            q = QueryArticles.initWithArticleUriList(small_uri_list)
+            q.addRequestedResult(
+                RequestArticlesInfo(
+                    count=n_arts,
+                    returnInfo=ReturnInfo(
+                        articleInfo=ArticleInfoFlags(bodyLen=-1, socialScore = True)
+                    )))
+            results += NewsDownloader.er.execQuery(q)['articles']['results']
+        return results
+
+    ## Save object
+
+    def save_obj(self, obj=None):
+        if obj is None:
+            assert self.full_articles is not None
+            obj = self.full_articles
[…]

### 2017-10-18 paper/doc/doc.tex
doc

\documentclass[12pt,a4paper,notitlepage]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{mathtools}
\usepackage{titling}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{pgfplots}
\usepackage[caption = false]{subfig}
\usepackage{caption}
\usepackage{graphicx}
\usepackage{tikz-3dplot}
\usepackage{subcaption}
\usepackage{float}
\usepackage{adjustbox}
\usepackage{multirow,rotating}
\usepackage[autostyle]{csquotes}
\usepackage[toc,page]{appendix}
\DeclareUnicodeCharacter{20AC}{\euro}
\usepackage[backend=biber,
			style=authoryear-comp,
			isbn=false,
			doi=false,
			bibstyle=authoryear,
			natbib,
			]{biblatex}

\begin{document}

\section{Introduction}

Markt für Online-Texte.
Presseverlage beklagen immer mehr eine Wettbewerbsverzerrung durch öffentlich-rechtliche Online-Angebote. "Wir erleben im Netz nach wie vor eine mit öffentlich-rechtlichen Geldern finanzierte Flut textbasierter Gratis-Angebote, nichts anderes als eine gebührenfinanzierte digitale Staatspresse, die den Wettbewerb verzerrt und uns Presseverlagen kaum Entfaltungsmöglichkeiten lässt" %(http://www.sz-online.de/nachrichten/ard-und-zdf-gebuehrenfinanzierte-staatspresse-3776123.html)

Wettbewerb im "Gemischten Oligopol": Die kostenlosen Nachrichtenangebote von ZDF.de oder tagesschau.de im Internet konkurrieren hier mit den Online Angeboten der klassischen Printmedien. Die beitragsfinanzierten Angebote behindern in der Tendenz Prozesse, durch die sich ein selbst tragendes, qualitativ hochwertiges Subskriptionssystem privatwirtschaftlicher Anbieter (spiegel.de, faz.net, welt.de, ...) entwickeln kann.

die öffentlich-rechtlichen Anbieter sollten nur da auftreten, wo das privatwirtschaftliche Angebot klare Defizite aufweist.

\begin{itemize}
	\item Reserach Question
	\begin{itemize}
		\item Analyzing news reports about german elections, where we allow prevalence of topics to evolve over time (before and after the elections) and vary across newswire services.
		\item Quantify the effect of news wire source on both topical prevalence (topic distribution) and topical content (word-topic distribution).
	\end{itemize}
	\item Method
	\begin{itemize}
		\item Topical content of documents, in which mixing weights are parameterized by observed covariates
		\item Topic distribution word-topic distribution are specified as a simple generalized linear model on an arbitrary number of document-level covariates (news source, time of release).
	\end{itemize}
\end{itemize}

Text as a data source is becoming increasingly popular in empirical economics, as the information encoded in text is a rich complement to conventional data (e.g. price, wage, votes, etc.) (\citet{grimmer_bayesian_2010}; \citet{grimmer_text_2013}; \citet{quinn_how_2010}; \citet{gentzkow_text_2017}; \citet{roberts_model_2016}). On interesting question is, how document metadata such as author or date influence its content. Depending on the characteristics of a corpus (a collection of documents), documents contain more than one topic, as well as terms most likely appear in multiple topics, thus the use of mixed-membership models \citep{airoldi_handbook_2014} - or topic model as they are often referred in the literature of text analysis \citep{blei_probabilistic_2012} - are a popular approach.

Within these models the Latent Dirichlet Allocation (LDA hencefirth) is a widely used topic modelling technique, where each document is viewed as a mixture of topics (represented by the document-topic distribution) and each topic is a mixture of unique terms (represented by the topic-term distribution). To "learn" the topic prevalence and the topic-term distribution, collapsed Gibbs sampling\footnote{See Section \ref{section_gibbs} for a non-formal description of the Gibbs sampler} can be used. LDA makes a statistical assumption that all texts in the modeled corpus are generated by the same underlying process \citep{blei_latent_2003}. Thus, it is not ideally suited to examining differences in topical content that are affected by covariates such as author identity or time of writing.

\citet{roberts_model_2016} develop a structural topic model (STM) that allows to incorporate external variables that effect both topical content and topical prevalence. We use this approach to analyze online news about the german federal elections, where we allow prevalence of topics to change over time (before and after the elections) and vary across newswire services (private or public) to quantify the effect of news wire source on both topical prevalence and topical content.

\section{Related Literature}

% Quantitative approaches
% -----------------------

% Politics and Newspaper
% ----------------------

In \citet{tetlock_giving_2007}, $c_i$ is a bag-of-words representation and the outcome of interest $v_i$ is the latent “sentiment” of Wall Street Journal columns, defined along a number of dimensions such as “positive,” “optimistic,” and so on. The author defines the function $f (\cdot)$ using a dictionary called the General Inquirer, which provides lists of words associated with each of these sentiment categories.2 The elements of $f(c_i)$ are defined to be the sum of the counts of words in each category.

% Topic Modeling / LDA
% ---------------------------

Topic modeling is a statistical and computational technique for discerning information about the contents of a large corpus of documents without reading or annotating the original texts. A topic model uncovers patterns of word co-occurrence across the corpus, yielding a set of word clusters, together with associated probabilities of occurrence, which constitute the topics.

See \citep{taddy_estimation_2012} for a review of topic estimation techniques)

Since its introduction into text analysis, topic modeling has become hugely popular.8 (See \citet{blei_probabilistic_2012} for an overview.) The model has been especially useful in political science (e.g., \citep{grimmer_bayesian_2010}), where researchers have been successful in attaching political issues and beliefs to the estimated latent topics.

Topic modeling is alternatively labeled as “latent Dirichlet allocation,” (LDA) which refers to the Bayesian model in \citet{blei_latent_2003} that treats each $\boldsymbol{v}_i$ and $\boldsymbol{\theta}_l$ as generated from a Dirichlet - distributed prior.
The same model was independently introduced in genetics by \citet{pritchard_inference_2000} for factorizing gene expression as a function of latent populations; it has been similarly successful in that field.

The basic topic model has been generalized and extended in variety of ways. A prominent example is the dynamic topic model of \citet{blei_dynamic_2006}, which considers documents that are indexed by date (e.g., publication date for academic articles) and allows the topics, say $\boldsymbol{\Theta}_t$, to evolve smoothly in time.

% Structural topic models (STM)
% ----------------------------
A typical application of topic modeling in the social sciences first estimates LDA, then uses estimates of $\theta_d$ as the dependent variable in an regression on covariates to test whether different types of documents have different content.

This is contradictory because documents are assumed to be generated by a statistical process that we subsequently reject.

The structural topic model (STM) of Roberts et. al. (2016) explicitly introduces covariates into a topic model, and allows one to estimate the impact of document-level covariates on topic content and prevalence as part of the topic model itself.

% ---------------------------------
% Statistical Analysis of Text Data
% ----------------------------------
\section{Statistical Analysis of Text Data}

Consider a collection of documents by $d \in \lbrace 1 ... D \rbrace$, each containing $n \in \lbrace 1 ... N_d \rbrace$ words. Primary observations consist of words $w_{d,n,}$ that are instances of unique terms from a vocabulary of terms, indexed by $v \in \lbrace 1 ... V \rbrace$.

To use text as data and reduce the dimensionality, a common strategy is to (a) pre-process the text by imposing some preliminary restrictions (stop-word removal, tokenization) based on the nature of the data (twitter text, newspaper articles, speeches, etc.) and (b) to represent a document $d$ as a vector of word counts, $\boldsymbol{n}_d \in \boldsymbol{N}^V$. This representation is often referred to as the bag of words model, since the order in which words are used within a document is completely disregarded. Nowadays, the bag of words model is a common representation for most of statistic literature about text data analysis (\citet{blei_latent_2003}; \citet{erosheva_mixed-membership_2004}; \citet{griffiths_finding_2004}; \citet{genkin_large-scale_2007}).

Term-Document matrices represent frequency distribution of unique terms in the documents. Any one document will contain only a subset of all unique terms, and the rows corresponding to unused terms will all be zero.The key task then becomes how to extract low-dimensional information from documents that are high-dimensional by nature. This is analogous to a situation in which a researcher has a database with thousands of covariates and is attempting to choose which subset of them, or which summary statistics, should be included in regression analysis.
% The description of the data and how it was processed in order to reduce it to a manageable scale without losing significant information can be found in chapter ...

\begin{enumerate}
	\item Represent raw text $D$ as a numerical array $\boldsymbol{C}$.

	\item Map $\boldsymbol{C}$ to predict values $\boldsymbol{\hat{V}}$ of unknown outcomes $\boldsymbol{V}$.

	E.g. the variable of interest $\boldsymbol{V}$ is an indicator whether the email is spam. The prediction $\boldsymbol{\hat{V}}$ determines whether or not to send the email to a spam filter. Sometimes the attribute of interest is latent, such as the topics of a newspaper article.
	\item Use $\boldsymbol{\hat{V}}$ in subsequent descriptive or causal analysis.
\end{enumerate}

Regarding 2, the methods to connect counts $\boldsymbol{c}_i$ to attributes $\boldsymbol{v}_i$ can be roughly divided into four categories \citep{gentzkow_text_2017}:
\begin{enumerate}
	\item Dictionary-based methods: 
	No statistical inference. Simply specify $\boldsymbol{\hat{v}_i}=f(\boldsymbol{c}_i)$ for some unknown function $f(\cdot)$. Sometimes based on a specific dictionary of terms (\citet{tetlock_giving_2007}, \citet{baker_measuring_2015}).
	\item Text regression methods:
	Directly estimate the conditional outcome distribution $p(\boldsymbol{v}_i|\boldsymbol{c}_i)$. Intuition: If we want to predict $\boldsymbol{v_i}$ from $\boldsymbol{c}_i$, we would regress the observed values of the former ($\boldsymbol{V}^{train}$) on the corresponding latter ($\boldsymbol{C}^{train}$). High dimensionality of $\boldsymbol{c}_i$ ($p > n^{train}$) requires use of appropriate regression techniques to avoid overfitting (e.g. $L_1$ regularized linear or logistic regression)
	\item Generative model of $p(\boldsymbol{c}_i|\boldsymbol{v}_i)$.
	Intuition: In many cases the underlying causal relationship runs from outcomes to language rather than the other way around. E.g. Google searches about flu do not cause flu cases to occur, rather, people with flu are more likely to produce such searches.
	\begin{enumerate}
		\item Observed attributes (supervised methods):
		Supervised machine learning starts with a researcher classifying observations to ‘train’ an algorithm under human ‘supervision’ – to ‘learn’ the correlation between the researcher’s ascribed classes and words characteristic of documents in those classes (Grimmer and Stewart (2013)). Fitting the model based on the observed training data $\boldsymbol{V}^{train}$, say $f_{\boldsymbol{\theta}}(\boldsymbol{c}_i;\boldsymbol{v}_i)$ for a vector of parameters $\boldsymbol{\theta}$, to this training set. The fitted model $f_{\hat{\boldsymbol{\theta}}}$ can be inverted in order to infer $\boldsymbol{v}_i$ for documents in the test set.
		\item Latent attributes (unsupervised methods): The function relating $\boldsymbol{c}_i$ to $\boldsymbol{v}_i$ is unknown, as we cannot observe the true value of $v_i$. Principal component analysis (PCA), latent Dirichlet allocation (LDA, topic modeling, structural-topic modeling). Unsupervised machine learning involves taking unclassified observations and uncovering hidden patterns that structure them in some meaningful way. The outputs of algorithms for unsupervised machine learning can be used as inputs into econometric models for predicting some variable of interest, but this is a different approach from intentionally choosing the dimensions of content based on their predictive ability.
	\end{enumerate}
	\item Deep learning techniques: neural networks, distributed language models.
\end{enumerate}

The goal of this paper is to find the latent topics within newspaper articles and how different types of media outlets (as well as the date?) influence the topic prevalence as well as the language to describe a topic (the word-topic distribution). We implement generative model (topic model). 
% A description of the generative process can be found in chapter ...

\section{Generative Process}

In this unsupervised method, the words in a document are viewed as the realization of some stochastic process. The generative process is defined through a probability model for $p(\boldsymbol{c}_i|\boldsymbol{v}_i)$.

Each observation $\boldsymbol{c}_i$ is a conditionally independent draw from the vocabulary of possible tokens accodring to some document-specific token probability vector $\boldsymbol{q}_i=[q_{i1}...q_{ip}]'$. Conditioning on document length, $m_i=\sum_jc_{ij}$, this implies a multinomial distribution for the counts

\begin{equation}\label{eq_1}
	\boldsymbol{c}_i \sim \boldsymbol{MN}(\boldsymbol{q}_i,m_i). 
\end{equation}

Under the basic model in \ref{eq_1}, a connection between text and attributes is defined through the link function $\boldsymbol{q}_i=q(\boldsymbol{v}_i)$.

\begin{equation}\label{eq_2}
	\boldsymbol{E} \bigg[\frac{\boldsymbol{c}_i}{m_i}\bigg]=\boldsymbol{q}_i =v_{i1}\boldsymbol{\theta}_1+v_{i2}\boldsymbol{\theta}_2+v_{ik}\boldsymbol{\theta}_k=\boldsymbol{\Theta v}_i
\end{equation}

where attributes $v_{il}$ are referred as topic wights, restricting $v_{il}\geq 0$ and $\sum^k_{l=1}v_{il}=1$, and each topic $\boldsymbol{\theta}_l$ is a probability vector over possible tokens: $\theta_{lj}\geq 0$ and $\sum^p_{j=1}\theta_{il}=1$. Each $\boldsymbol{v}_i$ and $\boldsymbol{\theta}_l$ is generated from a Dirichlet-distributed prior.

Latent Dirichlet allocation (LDA) is a particularly popular method for fitting a topic model. It treats each document as a mixture of topics, and each topic as a mixture of words. This allows documents to “overlap” each other in terms of content, rather than being separated into discrete groups, in a way that mirrors typical use of natural language. Formally speaking, each document has its own probability distribution over topics. Then, for each word in each document, a topic assignment is made and then, conditional on the assignment, a word from the corresponding topic.

Estimation of topic models make use of some alternating inference for $\boldsymbol{V|\Theta}$ and $\boldsymbol{\Theta|V}$.

\begin{enumerate}
	\item Expectation-maximization algorithm (EM)
	Either maximize the likelihood implied by \ref{eq_1} and \ref{eq_2} or, after incorporating the usual Dirichlet priors on $\boldsymbol{v}_i$ and $\boldsymbol{\theta}_l$ \citep{taddy_estimation_2012} 
	\item Target full posterior distribution $p(\boldsymbol{\Theta,V|c}_i})$
\end{enumerate}

Choice of number of topics $k$ is often fairly arbitrary. In practice it is very common to simply start with a number of topics on the order of ten, and then adjust the number of topics in whatever direction seems to improve interpretability. Whether this ad hoc procedure is problematic depends on the application. In many applications of topic models to date the goal is to provide an intuitive description of text rather than inference on some underlying “true” parameters; in these cases, the ad hoc selection of the number of topics may be reasonable.

Data-driven approaches: 
\begin{enumerate}
	\item \citet{taddy_estimation_2012} describes a model selection process for $k$ that is based upon Bayes factors.
	\item \citet{airoldi_reconceptualizing_2010} provide a cross-validation (CV) scheme
	\item \citet{teh_hierarchical_2006} use Bayesian nonparametric techniques that view $k$ as an unknown model parameter.
\end{enumerate}

\subsection{Structural Topic Model}

The process for generating individual words is the same as for plain LDA conditional on the $\beta_k$ and $\pi_d$ terms.

However both objects can depend on potentially different sets of document-level covariates. Each document has:
\begin{enumerate}
	\item Topic Prevalence. Attributes $r_d$ that affect the likelihood of discussing topic $k$. how much of a document is associated with a topic
	\item Topic Content. Attributes $r_d$ that affect the likelihood of discussing term $v$ overall, and of discussing it within topic $k$. the words used within a topic
\end{enumerate}

The generation of the $k$ and $d$ terms is via multinomial logistic regression, which breaks local conjugacy.

The standard topic modeling technique, Latent Dirichlet Allocation (LDA), may have limited utility in the realm of social media. LDA makes a statistical assumption that all texts in the modeled corpus are generated by the same underlying process (Blei). Thus, it is not ideally suited to examining differences in topical content that are affected by external variables such as author identity or time of writing.

Structural topic modeling (STM) is a recently introduced variant of LDA that is designed to address precisely this limitation . STM can represent the effect of external variables on both topical content and topical prevalence. The external variables can consist of any metadata that distinguishes one text from another, including variables relating to author identity (gender, age, political affiliation, etc.), textual genre (for example, news stories versus academic articles), and time of production.

stmVigenette: "The goal of the Structural Topic Model is to allow researchers to discover topics and estimate their relationship to document metadata. Outputs of the model can be used to conduct hypothesis testing about these relationships."

\subsubsection{Estimation of the STM}
In STM, metadata can be entered in the topic model in two ways: topical prevalence and topical content. Metadata covariates for topical prevalence allow the observed metadata to affect the frequency with which a topic is discussed. Covariates in topical content allow the observed metadata to affect the word rate use within a given topic{that is, how a particular topic is discussed.

We use the online magazine-type as a covariate in the topic prevalence portion of the model with the  data described above. Each document is modeled as a mixture of multiple topics. Topical prevalence captures how much each topic contributes to a document. Because different documents come from different sources, it is natural then to want to allow this prevalence to vary with metadata that we have about document sources.

We will simply let prevalence be a function of the magazine variable, which is coded as either
Spiegel Online or FOCUS Online and the variable day which is an integer measure of days running from 01-01-2017 to 31-07-2017.

\subsection{Gibbs Sampler}\label{section_gibbs}

Strategy for discovering topics  \cite{griffiths_finding_2004}
\begin{itemize}
	\item Considering the posterior distribution over the assignments of words to topics, $P(z|w)$. (and not explicitly representing $\phi$ or $\theta$ as parameters to be estimated)
	\item Examine this posterior distribution to obtain $\phi$ or $\theta$
\end{itemize}

After making assumptions about the parameters (number of topics $K$, prior distributions $\alpha$ and $\beta$), the procedure of Gibbs sampling is as follows:

\begin{enumerate}
	\item Go through each document and randomly assign each word in the document to one of $K$ topics, based on the prior distributions.
	\item For each document $d$, go through each word $w$ and compute:
	\begin{enumerate}
		\item The document-topic distribution $\theta = p(t|d)$
		\item The topic-term distribution $\phi = p(w|t)$
	\end{enumerate}
	\item Reassign word $w$ a new topic $t^*$, where we choose topic $t^*$ with probability $p(t^*|d)*p(w|t^*)$
\end{enumerate}

On repeating the last step a large number of times, the algorithm reaches a steady state where topic assignments are pretty good. These posterior distributions $\theta$ and $\phi$ are then used to determine the topic mixtures of each document.

\subsection{Validate accuracy}

\begin{itemize}
	\item Manual audits: cross checking some subset of the fitted values against the coding a human would produce by hand
	\item Inspection of fitted parameters
	\item Interpretation of fitted topics usually proceeds by ranking the tokens in each topic according to token probability.
\end{itemize}

Caution against the over-interpretation of unsupervised models: posterior distributions informing parameter estimates are highly multimodal, and multiple topic model runs can lead to multiple different interpretations. Add some supervision (\citet{airoldi_improving_2016}, \citet{gentzkow_text_2017})

\end{document}

### 2017-10-18 paper/doc/doc.tex
intro

@@
 
+The debate about the role of public media and their mission in a rapidly changing media world is a recurring theme.
+If the right to use digital media were to be withdrawn from the public media outlets, they would not only be deprived of the possibility of improved information provision.
+They also threatened to lose their competitiveness with commercial media.
+But it is precisely this competitiveness that is constitutionally guaranteed.
+On the other hand, there is the concern of commercial providers who are registering an ever-increasing number of digital services financed by fees.
+They complain about a bias in competition caused by public media offering online text-content because of their fee financing.
+The regulator recognizes this inequality and has banned advertising and sponsorship in its online services.
+
+The fundamental question in this debate is whether the offer of public news on the internet is justified.
+They should only occur where there are clear deficits in private sector supply.
+A frequently cited argument is that only the public media make it possible to provide information that is free of self-interest.
+Due to their public mandate and financing, they can afford what private providers cannot or only to a limited extent because of their economic dependency: a journalistic and editorial self-observation of society in the public interest.
+Due to their constitutional determination, they are obliged to the diversity and representation of the political and social spectrum of opinion in its entire breadth, including minority positions.
+
 Markt für Online-Texte.
@@
 Die beitragsfinanzierten Angebote behindern in der Tendenz Prozesse, durch die sich ein selbst tragendes, qualitativ hochwertiges Subskriptionssystem privatwirtschaftlicher Anbieter (spiegel.de, faz.net, welt.de, ...) entwickeln kann.
-
-die öffentlich-rechtlichen Anbieter sollten nur da auftreten, wo das privatwirtschaftliche Angebot klare Defizite aufweist.
 

### 2017-10-22 paper/R/webhoseio_explore.Rmd
process webhoseio data

--- 2017-10-18 paper/R/webhoseio.Rmd
@@
 lapply(libs, library, character.only = TRUE)
-
-```
-
-# Load and prepare Dataframe
-
-```{r, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
-rm(list = ls())
-
-# create a character vector, with each file name represented by an entry
-#june <- list.files("~/CloudStation/textmining/data/webhoseio/2017-06", pattern="*.json", full.names=TRUE) 
-#july <- list.files("~/CloudStation/textmining/data/webhoseio/2017-07", pattern="*.json", full.names=TRUE) 
-aug <- list.files("~/CloudStation/textmining/data/webhoseio/2017-08", pattern="*.json", full.names=TRUE) 
-#sep <- list.files("~/CloudStation/textmining/data/webhoseio/2017-09", pattern="*.json", full.names=TRUE)
-
-# a list in which each element is one of your original JSON files
-#myJSON <- lapply(c(june,july,aug,sep), function(x) fromJSON(file=x)) 
-myJSON <- lapply(aug, function(x) fromJSON(file=x))
-
-length(myJSON)
-```
-
-## Convert List to Dataframe
-
-```{r, eval=FALSE, include=FALSE}
-site <- NULL
-title <- NULL
-text <- NULL
-published <- NULL
-fb_shares <- NULL
-fb_likes <- NULL
-section <- NULL
-external_links <- NULL
-
-for (i in 1:length(myJSON)){
-  site <- append(site, myJSON[[i]]["thread"][[1]]["site"][[1]])
-  title <- append(title, myJSON[[i]]["title"][[1]])
-  text <- append(text, myJSON[[i]]["text"][[1]])
-  published <- append(published, myJSON[[i]]["published"][[1]])
-
-  fb_shares <- append(fb_shares, myJSON[[i]]["thread"][[1]]["social"][[1]]["facebook"][[1]][["shares"]])
-  fb_likes <- append(fb_likes, myJSON[[i]]["thread"][[1]]["social"][[1]]["facebook"][[1]][["likes"]])
-
-  section <- append(section, myJSON[[i]]["thread"][[1]]["section_title"][[1]])
-  external_links <- append(external_links, length(myJSON[[i]]["external_links"][[1]]))
-
-}
-
-df <- cbind(site, title, text, published, fb_shares, fb_likes, section, external_links)
-df <- data.frame(df, stringsAsFactors = FALSE)
-
-rm(site, title, text, published, fb_shares, fb_likes, section, external_links)
-```
-
-## Define private and public service operators
-
-```{r, eval=FALSE, include=FALSE}
-private <- c("bild.de","focus.de","handelsblatt.com","spiegel.de","stern.de","welt.de","zeit.de")
-
-df %>%
-  mutate(owned = ifelse(site %in% private, "private", "public")) -> df
-```
-
-## Subset by
-```{r, eval=FALSE, include=FALSE}
-# .... date
-df$date <- substr(df$published, 1,10)
-df$date <- as.POSIXct(df$date, format ="%Y-%m-%d")
-
-df <- subset(df, df$date > "2017-09-01")
-```
-
-```{r, eval=FALSE, include=FALSE}
-# ... content
-content <- c("Bundestagswahl","Merkel","Schulz","Wagenknecht","Lindner","Gauland","Özdemir",
-             "CDU","SPD","FDP","AfD","Die Grünen","Die Linke")
-
-btw <- df[which(grepl(paste(content, collapse = "|"), df$title)),]
-
-# Save file
-write.csv(btw, file="~/CloudStation/textmining/R/output/btw.csv")
 ```
@@
 ## Load Data
+```{r}
+rm(list = ls())
+load("../output/news_cleaned.Rda")
+
+df %>% filter(site != "zdf.de") -> df
+col <- brewer.pal(12, name = "Paired")
+```
+
+## Count number of terms in a string
+```{r}
+df$text_lenght <- sapply(gregexpr("\\S+", df$text), length)
+```
+
+## Summary Stats
+```{r}
+df %>%
+  group_by(site) %>%
+  summarise(obs = n(),
+    fb_shares.mean = mean(fb_shares),
+            fb_shares.max = max(fb_shares),
+            fb_likes.mean = mean(fb_likes),
+            fb_likes.max = max(fb_likes),
+            external_links.mean = mean(external_links),
+            external_links.max = max(external_links),
+            text_length.mean = mean(text_lenght),
+            text_length.max = max(text_lenght))
+  htmlTable(align = "l")
+```
+
+### Text Length
+```{r}
+ggplot(df, aes(x=as.factor(site), y=text_lenght)) +
+  stat_summary(fun.y="median", geom="bar", fill = "blue", alpha = .5) +
+  labs(title = "") +
+  labs(x="", y="Median Text Length") +
+  theme(axis.text.x = element_text(angle = 40, hjust = 1))
+```
+
+### Facebook Likes
+```{r}
+ggplot(df, aes(x=as.factor(site), y=fb_likes)) +
+  stat_summary(fun.y="sum", geom="bar", fill = "blue", alpha = .5) +
+  labs(title = "") +
+  labs(x="", y="Sum of Facebook Likes") +
+  theme(axis.text.x = element_text(angle = 40, hjust = 1))
+```
 
 ```{r}
-rm(list = ls())
-df <- read.csv("output/btw.csv")
+df$btw <- ifelse(grepl("Bundestagswahl", df$text, ignore.case = TRUE), 1,0)
 ```
@@
 ```{r}
-col <- brewer.pal(12, name = "Paired")
-
-df %>%
-  group_by(site) %>%
-  tally(sort = TRUE) %>%
-  ggplot(aes(site, n)) +
-  geom_col(fill = col, alpha = .8) +
+ggplot(df, aes(site)) +
+  geom_bar(fill="blue", alpha = .5) +
   xlab("") +
-  ylab("") +
+  ylab("Number of Articles") +
   theme(axis.text.x = element_text(angle = 40, hjust = 1))
@@
 
-### Number of published Articels by Ownership
+### Share of Articles mentioning Bundestagwahl
+```{r}
+df %>%
+  group_by(site, btw) %>%
+  tally() %>%
+  group_by(site) %>%
+  mutate(n_total = sum(n)) -> count
+
+count %>%
+  filter(btw == 1) %>%
+  ggplot(aes(site, n/n_total)) +
+  geom_col(fill="blue", alpha=.5) +
+  xlab("") +
+  ylab("Share of Articles mentioning Bundestagwahl") +
+  theme(axis.text.x = element_text(angle = 40, hjust = 1))
+```
 
 ```{r}
-df %>%
-  group_by(owned) %>%
-  tally(sort = TRUE) %>%
-  ggplot(aes(owned, n)) +
-  geom_col(fill = col[c(6,2)], alpha = .8) +
-  geom_text(aes(label=n), position = position_stack(vjust = 0.5)) +
-  xlab("") +
-  ylab("") +
-  theme(axis.text.x = element_text(angle = 40, hjust = 1))
+btw <- df[which(df$btw == 1),]
 ```
@@
   {
-  x = gsub("[[:punct:]]", " ", x)  # replace punctuation with space
-
   x = gsub("DIE WELT", "", x)
@@
 # apply function to the "orig" dataframe
-df$text_cleaned <- clean.text(df$text)
-
-df %>%
-  filter(grepl("Getty Images", text)) %>%
-  select(text, text_cleaned) %>%
-  htmlTable(align = "l")
+btw$text_cleaned <- clean.text(btw$text)
 ```
 
+## Remove Stopwords
 ```{r}
-# get stopwords from online dict and add costum stopwords
-#exceptions   <- c("nicht")
-#my_stopwords <- setdiff(stopwords("german"), exceptions)
-my_stopwords <- c(stopwords("german"), "spon","zeitmagazin","sz", "seitennavigation","startseite","gibt","immer","uhr","dass","mehr","sagte","sei","wurde","twitterfacebookgoogle","whatsappteilen","kartengeschichte","elbvertiefung","econa","prozent","freepik","colourbox")
-
-# Remove stopwords
-df$text_cleaned<- removeWords(df$text_cleaned, my_stopwords)
-
-# save file
-write.csv(df, file = "/Users/Franzi/CloudStation/textmining/data/news_cleaned.csv")
+btw$text_cleaned<- removeWords(btw$text_cleaned, stopwords("german"))
 ```
@@
 ```{r}
-news.token <- df %>%
-  group_by(site) %>%
+news_words <- btw %>%
   unnest_tokens(word, text_cleaned) %>%
-  count(site, word, sort = TRUE)  %>%
-  bind_tf_idf(word, site, n) %>%
-  arrange(desc(tf_idf)) 
+  count(site, word, sort = TRUE)
+
+## TF-IDF
+news_words <- news_words %>%
+  bind_tf_idf(word, site, n)
+
+### Terms with high tf-idf
+news_words %>%
+  #filter(site == "spiegel.de") %>%
+  arrange(desc(n))
+```
+
+### Add customized stopwords
+```{r}
+mystopwords <- c("ich","sie","passwort","uhr","bitte","videolänge","dass","mindestens","das","mail","die","zdf","schon","die","neuer abschnitt", "datenschutzerklärung","premium","nutzungsbedingungen","pflichtfelder","registrierung","anzeige","großbuchstaben","sonderzeichen","html","seitennavigation","swr","fullscreen","wochit","statista","club","sagte","mehr")
+
+btw$text_cleaned<- removeWords(btw$text_cleaned, mystopwords)
+```
+
+## Tokenize terms
+```{r}
+news_words <- btw %>%
+  unnest_tokens(word, text_cleaned) %>%
+  count(site, word, sort = TRUE)
+
+## TF-IDF
+news_words <- news_words %>%
+  bind_tf_idf(word, site, n)
+
+### Terms with high tf-idf
+news_words %>%
+  #filter(site == "spiegel.de") %>%
+  arrange(desc(n))
+```
+
+## Bigrams
+
+```{r}
+news_bigrams <- btw %>%
+  unnest_tokens(bigram, text_cleaned, token="ngrams", n=2)
+
+news_bigrams %>%
+  count(bigram, sort = TRUE)
 ```
@@
 # Build corpus
-btw.lda <- Corpus(VectorSource(df$text_cleaned))
+btw.lda <- Corpus(VectorSource(btw$text_cleaned))
 # Create document-term matrix
 dtm <- DocumentTermMatrix(btw.lda)
+
+inspect(dtm)
 ```
@@
 
-k = 20 # Topics
+#Set parameters for Gibbs sampling (see https://eight2late.wordpress.com/2015/09/29/a-gentle-introduction-to-topic-modeling-using-r/)
+burnin <- 4000
+iter <- 2000
+thin <- 500
+seed <-list(2003,5,63,100001,765)
+nstart <- 5
+best <- TRUE
 
+k = 10 # Topics
+```
+
+```{r}
 t1 <- Sys.time()
-lda20 <-LDA(dtm, 20, method="Gibbs", control=list(nstart=5, iter = 10000))
+lda10 <-LDA(dtm, k, method="Gibbs", control=list(nstart=nstart, seed=seed, best=best, burnin=burnin, iter = iter, thin=thin))
 t2 <- Sys.time()
 t2 - t1
+```
+
+```{r}
+#write out results
+lda10.topics <- as.matrix(topics(lda10))
+lda10.topics
+```
+
+```{r}
+#top 6 terms in each topic
+lda10.terms <- as.matrix(terms(lda10,6))
+```
+
+```{r}
+#probabilities associated with each topic assignment
+topicProbabilities <- as.data.frame(lda10@gamma)
+```
+
+```{r}
+#Find relative importance of top 2 topics
+topic1ToTopic2 <- lapply(1:nrow(dtm),function(x)
+sort(topicProbabilities[x,])[k]/sort(topicProbabilities[x,])[k-1])
+```
+
+```{r}
+#Find relative importance of second and third most important topics
+topic2ToTopic3 <- lapply(1:nrow(dtm),function(x)
+sort(topicProbabilities[x,])[k-1]/sort(topicProbabilities[x,])[k-2])
 ```

### 2017-10-22 paper/R/webhoseio_prepare.Rmd
process webhoseio data

---
title: "Topic Modeling of News"
author: "Franziska Löw"
date: "`r format(Sys.Date())`"
output: github_document
---

```{r, include=FALSE}
# load the packages
libs <- c("tidytext","tidyr","readr","lubridate","tm","stm","RColorBrewer",
          "plyr","dplyr","class","knitr","kableExtra","cldr","data.table",
          "htmlTable","ggplot2","gridExtra","jsonlite","stringr","scales","rjson")
lapply(libs, library, character.only = TRUE)

```

# Load and prepare Dataframe

```{r, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
rm(list = ls())

# create a character vector, with each file name represented by an entry
june <- list.files("../data/webhoseio/2017-06", pattern="*.json", full.names=TRUE) 
july <- list.files("../data/webhoseio/2017-07", pattern="*.json", full.names=TRUE) 
aug <- list.files("../data/webhoseio/2017-08", pattern="*.json", full.names=TRUE) 
sep <- list.files("../data/webhoseio/2017-09", pattern="*.json", full.names=TRUE)

# a list in which each element is one of your original JSON files
myJSON <- lapply(c(june,july,aug,sep), function(x) fromJSON(file=x)) 
#myJSON <- lapply(june, function(x) fromJSON(file=x))

length(myJSON)
```

## Convert List to Dataframe

```{r, eval=FALSE, include=FALSE}
site <- NULL
title <- NULL
text <- NULL
published <- NULL
section <- NULL

fb_shares <- NULL
fb_likes <- NULL
fb_comments <- NULL
gplus_shares <- NULL
linkedin_shares <- NULL
stumbledupon_shares <- NULL

#external_links <- NULL

for (i in 1:length(myJSON)){
  site <- append(site, myJSON[[i]]["thread"][[1]]["site"][[1]])
  title <- append(title, myJSON[[i]]["title"][[1]])
  text <- append(text, myJSON[[i]]["text"][[1]])
  published <- append(published, myJSON[[i]]["published"][[1]])
  section <- append(section, myJSON[[i]]["thread"][[1]]["section_title"][[1]])

  fb_shares <- append(fb_shares, myJSON[[i]]["thread"][[1]]["social"][[1]]["facebook"][[1]][["shares"]])
  fb_likes <- append(fb_likes, myJSON[[i]]["thread"][[1]]["social"][[1]]["facebook"][[1]][["likes"]])
  fb_comments <- append(fb_likes, myJSON[[i]]["thread"][[1]]["social"][[1]]["facebook"][[1]][["comments"]])

  gplus_shares <- append(gplus_shares, myJSON[[i]]["thread"][[1]]["social"][[1]]["gplus"][[1]][["shares"]])
  linkedin_shares <- append(gplus_shares, myJSON[[i]]["thread"][[1]]["social"][[1]]["linkedin"][[1]][["shares"]])
  stumbledupon_shares <- append(stumbledupon_shares, myJSON[[i]]["thread"][[1]]["social"][[1]]["stumbledupon"][[1]]["shares"][[1]])

  external_links <- append(external_links, length(myJSON[[i]]["external_links"][[1]]))

}

df <- cbind(site, title, text, published, section, fb_shares, fb_likes, gplus_shares, external_links)
df <- data.frame(df, stringsAsFactors = FALSE)
```

```{r}
rm(site, title, text, published, fb_shares, fb_likes, section, external_links)
```

## Clean Data
```{r}
df %>%
  mutate(fb_shares = as.numeric(fb_shares),
         fb_likes = as.numeric(fb_likes),
         gplus_shares = as.numeric(gplus_shares),
         external_links = as.numeric(external_links)) -> df
```

### Date
```{r, eval=FALSE, include=FALSE}
# .... date
df$date <- substr(df$published, 1,10)
df$date <- as.POSIXct(df$date, format ="%Y-%m-%d")

#df <- subset(df, df$date > "2017-09-01")
```

```{r, eval=FALSE, include=FALSE}
# Save file
save(df, linkedin_shares, file="../output/news_cleaned.Rda")
```

### 2017-10-23 paper/R/webhoseio_explore.Rmd
bla

@@
             text_length.mean = mean(text_lenght),
-            text_length.max = max(text_lenght))
+            text_length.max = max(text_lenght)) %>%
   htmlTable(align = "l")
@@
   theme(axis.text.x = element_text(angle = 40, hjust = 1))
+```
+
+```{r}
+save(df, file="../output/news_cleaned.Rda")
 ```

### 2017-10-23 paper/R/webhoseio_explore.Rmd
new

@@
 
-df %>% filter(site != "zdf.de") -> df
 col <- brewer.pal(12, name = "Paired")
-```
-
-## Count number of terms in a string
-```{r}
-df$text_lenght <- sapply(gregexpr("\\S+", df$text), length)
 ```
@@
   theme(axis.text.x = element_text(angle = 40, hjust = 1))
-```
-
-```{r}
-save(df, file="../output/news_cleaned.Rda")
-```
-
-```{r}
-df$btw <- ifelse(grepl("Bundestagswahl", df$text, ignore.case = TRUE), 1,0)
-```
-
-### Number of published Articels by News Source
-
-```{r}
-ggplot(df, aes(site)) +
-  geom_bar(fill="blue", alpha = .5) +
-  xlab("") +
-  ylab("Number of Articles") +
-  theme(axis.text.x = element_text(angle = 40, hjust = 1))
-```
-
-### Share of Articles mentioning Bundestagwahl
-```{r}
-df %>%
-  group_by(site, btw) %>%
-  tally() %>%
-  group_by(site) %>%
-  mutate(n_total = sum(n)) -> count
-
-count %>%
-  filter(btw == 1) %>%
-  ggplot(aes(site, n/n_total)) +
-  geom_col(fill="blue", alpha=.5) +
-  xlab("") +
-  ylab("Share of Articles mentioning Bundestagwahl") +
-  theme(axis.text.x = element_text(angle = 40, hjust = 1))
-```
-
-```{r}
-btw <- df[which(df$btw == 1),]
 ```
@@
 ```{r}
-btw$text_cleaned<- removeWords(btw$text_cleaned, stopwords("german"))
+df$text_cleaned<- removeWords(df$text, stopwords("german"))
 ```
@@
 ```{r}
-news_words <- btw %>%
-  unnest_tokens(word, text_cleaned) %>%
+news_words <- df %>%
+  unnest_tokens(word, text) %>%
   count(site, word, sort = TRUE)
@@
 
-```
+```.

### 2017-10-24 paper/R/webhoseio_prepare.Rmd
new
add more cleaning

@@
 
+## Count number of terms in a string
+```{r}
+df %>% filter(site != "zdf.de") -> df
+
+df$text_lenght <- sapply(gregexpr("\\S+", df$text), length)
+```
+
 ```{r, eval=FALSE, include=FALSE}
@@
 ```
+
+## Save by Site
+```{r}
+df %>% filter(site=="stern.de") %>% write.csv(.,file = "../output/stern.csv")
+df %>% filter(site=="focus.de") %>% write.csv(.,file = "../output/focus.csv")
+df %>% filter(site=="zeit.de") %>% write.csv(.,file = "../output/zeit.csv")
+df %>% filter(site=="wdr.de") %>% write.csv(.,file = "../output/wdr.csv")
+df %>% filter(site=="spiegel.de") %>% write.csv(.,file = "../output/spiegel.csv")
+df %>% filter(site=="welt.de") %>% write.csv(.,file = "../output/welt.csv")
+df %>% filter(site=="handelsblatt.com") %>% write.csv(.,file = "../output/handelsblatt.csv")
+df %>% filter(site=="tagesschau.de") %>% write.csv(.,file = "../output/tagesschau.csv")
+df %>% filter(site=="swr.de") %>% write.csv(.,file = "../output/swr.csv")
+df %>% filter(site=="bild.de") %>% write.csv(.,file = "../output/bild.csv")
+df %>% filter(site=="ndr.de") %>% write.csv(.,file = "../output/ndr.csv")
+```
+
+## Load by site
+```{r}
+focus <- read.csv("../output/focus.csv")
+#spiegel <- read.csv("../output/spiegel.csv")
+#bild <- read.csv("../output/bild.csv")
+
+df_reduced <- rbind(focus, spiegel, bild)
+```
+
+```{r}
+save(df_reduced, file="../output/df_reduced")
+```

### 2017-10-25 paper/R/05_lda_eight2late.Rmd
add lda model

---
title: "Topic Modeling of News"
author: "Franziska Löw"
date: "`r format(Sys.Date())`"
output: github_document
---

```{r, include=FALSE}
# load the packages
libs <- c("tidytext","tidyr","readr","lubridate","tm","stm","RColorBrewer","topicmodels",
          "plyr","dplyr","class","knitr","kableExtra","cldr","data.table",
          "htmlTable","ggplot2","gridExtra","jsonlite","stringr","scales","rjson")
lapply(libs, library, character.only = TRUE)
```

## Load Data
```{r}
rm(list = ls())

load("../output/news_cleaned2.Rda")
write.csv(btw, file="../output/btw.csv")

df$date <- as.Date(df$date)

#col <- brewer.pal(12, name = "Paired")
```

## Reduce Dataframe
```{r}
df %>%
  filter(fb_shares > 0) %>%
  filter(!site %in% c("ndr.de","wdr.de")) %>%
  filter(grepl("bundestagswahl", text_cleaned)) -> btw

```

# Topic Modeling
## Build Corpus
```{r}
btw %>%
  filter(nchar(text_cleaned) > 5) -> btw
```

```{r}
# Build corpus
df.lda <- Corpus(VectorSource(btw$text_cleaned))
# Create document-term matrix
dtm <- DocumentTermMatrix(df.lda)
# Assign name to docs
rownames(dtm) <- make.unique(btw$title)

inspect(dtm)
```

## Run LDA using Gibbs sampling
```{r}
#Set parameters for Gibbs sampling (see https://eight2late.wordpress.com/2015/09/29/a-gentle-introduction-to-topic-modeling-using-r/)
burnin <- 1000
iter <- 1000
keep <- 50

k = 50 # Topics
```

```{r}
t1 <- Sys.time()
lda50 <-LDA(dtm, k, method="Gibbs", control=list(burnin=burnin, iter = iter, keep = keep))
t2 <- Sys.time()
t2 - t1

save(ldaOut, file=paste("../output/models/LDAGibbs",k,".Rda"))
```

```{r}
#write out results (docs to topics)
ldaOut.topics <- as.matrix(topics(ldaOut))
write.csv(ldaOut.topics,file=paste("../output/models/LDAGibbs",k,"DocsToTopics.csv"))
```

```{r}
#top 6 terms in each topic
ldaOut.terms <- as.matrix(terms(ldaOut,6))
write.csv(ldaOut.terms,file=paste("../output/models/LDAGibbs",k,"TopicsToTerms.csv"))
```

```{r}
#probabilities associated with each topic assignment
topicProbabilities <- as.data.frame(ldaOut@gamma)
#rownames(topicProbabilities) <- make.unique(btw$title)

write.csv(topicProbabilities,file=paste("../output/models/LDAGibbs",k,"TopicProbabilities.csv"))
```

```{r}
#Find relative importance of top 2 topics
topic1ToTopic2 <- lapply(1:nrow(dtm),function(x)
sort(topicProbabilities[x,])[k]/sort(topicProbabilities[x,])[k-1])
```

```{r}
#Find relative importance of second and third most important topics
topic2ToTopic3 <- lapply(1:nrow(dtm),function(x)
sort(topicProbabilities[x,])[k-1]/sort(topicProbabilities[x,])[k-2])
```

```{r}
#write to file
write.csv(topic1ToTopic2,file=paste("../output/models/LDAGibbs",k,"Topic1ToTopic2.csv"))
write.csv(topic2ToTopic3,file=paste("../output/models/LDAGibbs",k,"Topic2ToTopic3.csv"))
```

### 2017-10-25 paper/R/02_prepare.Rmd
add lda model

---
title: "Topic Modeling of News"
author: "Franziska Löw"
date: "`r format(Sys.Date())`"
output: github_document
---

```{r, include=FALSE}
# load the packages
libs <- c("tidytext","tidyr","readr","lubridate","tm","stm","RColorBrewer",
          "plyr","dplyr","class","knitr","kableExtra","cldr","data.table",
          "htmlTable","ggplot2","gridExtra","jsonlite","stringr","scales","rjson")
lapply(libs, library, character.only = TRUE)

```

# Load and prepare Dataframe

```{r}
rm(list =ls())

load("../output/news_cleaned.Rda")
```

# Pre-Process Text

```{r}
df %>%
  distinct(text, .keep_all = TRUE) -> df
```

```{r}
pat <- 'Hinweis.+?(?=(einfügen))'
btw %>%
  filter(grepl(pat, text, perl = TRUE)) %>%
  group_by(site) %>%
  tally(sort = TRUE)
```
```{r}
as.data.frame(str_match(btw$text, pat)) ->test
test %>%
  filter(!is.na(test)) %>%
  .[1]
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
clean.text <- function(x)
  {
  # All
  x = gsub("Getty Images", "", x)

  # Bild.de
  x = gsub("Shopübersicht Top Gutscheine", "", x)

  # Handelsblatt.com
  x = gsub("RSS Feed", "", x)
  x = gsub("Deutsche Presse Agentur", "", x)

  # FOCUS.de
  x = gsub("FOCUS Online/Wochit", "", x)
  x = gsub("Vielen Dank! Ihr Kommentar wurde abgeschickt.", "", x)
  x = gsub('Im Interesse unserer User[^"]*', "", x, perl = TRUE)
  x = gsub('Sie haben noch 800[^"]*', "", x, perl = TRUE)
  x = gsub('Erzählen Sie auf FOCUS Online über Ihren Heimatort Teilen Sie Ihren Artikel und Ihr Foto', "", x, perl = TRUE)
  x = gsub("Bericht schreiben", "", x)
  x = gsub("Vielen Dank! Ihr Kommentar wurde abgeschickt.", "", x)
  x = gsub("Hier können Sie selbst Artikel verfassen:","", x)
  x = gsub("Live-Ticker", "", x)

  # Spiegel.de
  x = gsub("7 mal 17", "", x)
  x = gsub("Zur Startseite Diesen Artikel... Drucken Feedback Nutzungsrechte", "", x)
  x = gsub('Liebe Leserin, lieber Leser,\num diesen[^"]*', "", x)
  x = gsub('Liebe Leserin, lieber Leser, um diesen[^"]*', "", x)
  x = gsub('ejf[^"]*', "", x)
  x = gsub('tjf[^"]*', "", x)

  # Zeit.de
  x = gsub("Inhalt Seite", "", x)

  # Tagesschau
  x = gsub('Hinweis.+?(?=(einfügen))', "", x, perl = TRUE)

  return(x)
}

# apply function to dataframe
df$text_cleaned <- clean.text(df$text)
```

```{r}
df$text_cleaned <- gsub("[[:punct:]]", " ", df$text_cleaned)
df$text_cleaned <- gsub("[[:cntrl:]]", " ", df$text_cleaned)
df$text_cleaned <- gsub("[[:digit:]]", " ", df$text_cleaned)
df$text_cleaned <- gsub("^[[:space:]]+", " ", df$text_cleaned)
df$text_cleaned <- gsub("[[:space:]]+$", " ", df$text_cleaned)
df$text_cleaned <- tolower(df$text_cleaned)
```

## Remove Stopwords
```{r}
df$text_cleaned<- removeWords(df$text_cleaned, stopwords("german"))
```

### Remove customized stopwords
```{r}
mystopwords <- c("focus","online","spiegel", "stern", "handelsblatt", "de", "bild","bildplus", "zeit", "ersten", "tagesschau", "wdr", "ndr", "ich","sie","passwort","kommentar","wurde","ihr","der","im","artikel","mehr","ihren","foto","e", "uhr","videolänge","dass","mindestens","das","mail","die","schon","neuer abschnitt", "login", "loggen", "inaktiv", "nwmi", "nwnoa", "polizei","beim","dpa","video","quelle","afp","witters","fotogalerie", "registrierter","als","spiegel","vielen","in","es","bitte","dank","unserer","nutzer","sei","beitrag","user","seit","zeichen", "datenschutzerklärung","premium","nutzungsbedingungen","nutzungsrechte","pflichtfelder","registrierung","anzeige","großbuchstaben","sonderzeichen","html","seitennavigation","fullscreen","statista","club","sagte","borenda","spreepicture","shopübersicht")

mystopwords <- distinct(as.data.frame(mystopwords))

df$text_cleaned<- removeWords(df$text_cleaned, mystopwords$mystopwords)
```

```{r}
save(df, file="../output/news_cleaned2.Rda")
```

## Save by Site
```{r}
save_by_site <- function(DF) {
  write.csv(DF, paste0("../output/single/",as.character(DF),".csv"))
  return(DF)
}

df %>%
  group_by(site) %>%
  do(save_by_site(.))
```

```{r}
df %>% filter(site=="stern.de") %>% write.csv(.,file = "../output/single/stern.csv")
df %>% filter(site=="focus.de") %>% write.csv(.,file = "../output/single/focus.csv")
df %>% filter(site=="zeit.de") %>% write.csv(.,file = "../output/single/zeit.csv")
df %>% filter(site=="wdr.de") %>% write.csv(.,file = "../output/single/wdr.csv")
df %>% filter(site=="spiegel.de") %>% write.csv(.,file = "../output/single/spiegel.csv")
df %>% filter(site=="welt.de") %>% write.csv(.,file = "../output/single/welt.csv")
df %>% filter(site=="handelsblatt.com") %>% write.csv(.,file = "../output/single/handelsblatt.csv")
df %>% filter(site=="tagesschau.de") %>% write.csv(.,file = "../output/single/tagesschau.csv")
df %>% filter(site=="swr.de") %>% write.csv(.,file = "../output/single/swr.csv")
df %>% filter(site=="bild.de") %>% write.csv(.,file = "../output/single/bild.csv")
df %>% filter(site=="ndr.de") %>% write.csv(.,file = "../output/single/ndr.csv")
```

## Load by site
```{r}
focus <- read.csv("../output/focus.csv")
spiegel <- read.csv("../output/spiegel.csv")
bild <- read.csv("../output/bild.csv")

df_reduced <- rbind(focus, spiegel, bild)
```

```{r}
save(df_reduced, file="../output/df_reduced.Rda")
```

### 2017-10-25 paper/R/03_explore.Rmd
add lda model

--- 2017-10-23 paper/R/webhoseio_explore.Rmd
@@
 rm(list = ls())
-load("../output/news_cleaned.Rda")
+load("../output/news_cleaned2.Rda")
 
@@
 
-# Pre-Process Text
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
-clean.text = function(x)
-  {
-  x = gsub("DIE WELT", "", x)
-  x = gsub("SPIEGEL ONLINE", "", x)
-  x = gsub("FOCUS Online", "", x)
-  x = gsub("ZEIT ONLINE", "", x)
-  x = gsub("stern de", "", x)
-  x = gsub("Handelsblatt", "", x)
-  x = gsub("Politik Inland Bild de", "", x)
-  x = gsub("BILDplus Inhalt", "", x)
-  x = gsub("Bild de", "", x)
-  x = gsub("SWR Aktuell", "", x)
-  x = gsub("SWR de", "", x)
-  x = gsub("[ ]NDR[ ]", "", x)
-  x = gsub('ZDF \"\"Morgenmagazin\"\"', "", x)
-  x = gsub("ZDFmediathek", "", x)
-  x = gsub("[ ]ZDF[ ]", "", x)
-  x = gsub("[ ]ARD[ ]", "", x)
-
-  x = gsub("die neuesten Nachrichten", "", x)
-  x = gsub("RSS Feed", "", x)
-  x = gsub("Der Überblick   7 mal 17   Alle Artikel", "", x)
-  x = gsub("Der Tag im Überblick", "", x)
-  x = gsub("Inhalt Seite 1", "", x)
-  x = gsub("Seite 2", "", x)
-  x = gsub("dpa", "", x)
-  x = gsub("Twitter Anzeige", "", x)
-  x = gsub("Anzeige", "", x)
-  x = gsub("Foto  \\w+", "", x)
-  x = gsub("Video", "", x)
-  x = gsub("Quelle \\w+", "", x)
-  x = gsub("\\w+ \\w+ Getty Images", "", x)
-  x = gsub("AFP", "", x)
-  x = gsub("August", "", x)
-  x = gsub("Live-Ticker", "", x)
-  x = gsub("Deutsche Presse Agentur GmbH   Nachrichtenagentur Alle Beiträge von  anzeigen", "", x)
-  x = gsub("Deutsche Presse Agentur", "", x)
-
-  x = gsub("[[:punct:]]", " ", x)  # replace punctuation with space
-  x = gsub("[[:cntrl:]]", " ", x)  # replace control characters with space
-  x = gsub("[[:digit:]]", "", x)  # remove numbers
-  x = gsub("^[[:space:]]+", "", x) # remove whitespace at beginning of documents
-  x = gsub("[[:space:]]+$", "", x) # remove whitespace at end of documents 
-  x = gsub("[\n{2,}]", "", x)
-  x = tolower(x)
-  return(x)
-}
-
-# apply function to the "orig" dataframe
-btw$text_cleaned <- clean.text(btw$text)
-```
-
-## Remove Stopwords
-```{r}
-df$text_cleaned<- removeWords(df$text, stopwords("german"))
-```
-
 ## Tokenize terms
@@
   arrange(desc(n))
-```
-
-### Add customized stopwords
-```{r}
-mystopwords <- c("ich","sie","passwort","uhr","bitte","videolänge","dass","mindestens","das","mail","die","zdf","schon","die","neuer abschnitt", "datenschutzerklärung","premium","nutzungsbedingungen","pflichtfelder","registrierung","anzeige","großbuchstaben","sonderzeichen","html","seitennavigation","swr","fullscreen","wochit","statista","club","sagte","mehr")
-
-btw$text_cleaned<- removeWords(btw$text_cleaned, mystopwords)
 ```

### 2017-10-25 paper/R/04_reduced.Rmd
add lda model

--- 2017-10-25 paper/R/03_explore.Rmd
@@
 # load the packages
-libs <- c("tidytext","tidyr","readr","lubridate","tm","stm","RColorBrewer",
+libs <- c("tidytext","tidyr","readr","lubridate","tm","stm","RColorBrewer","topicmodels",
           "plyr","dplyr","class","knitr","kableExtra","cldr","data.table",
@@
 rm(list = ls())
+
 load("../output/news_cleaned2.Rda")
+write.csv(btw, file="../output/btw.csv")
 
-col <- brewer.pal(12, name = "Paired")
+df$date <- as.Date(df$date)
+
+#col <- brewer.pal(12, name = "Paired")
+```
+
+## Reduce Dataframe
+```{r}
+df %>%
+  filter(fb_shares > 0) %>%
+  filter(!site %in% c("ndr.de","wdr.de")) %>%
+  filter(grepl("bundestagswahl", text_cleaned)) -> btw
+
 ```
@@
 ```{r}
-df %>%
+btw %>%
   group_by(site) %>%
@@
 ```{r}
-ggplot(df, aes(x=as.factor(site), y=text_lenght)) +
+ggplot(btw, aes(x=as.factor(site), y=text_lenght)) +
   stat_summary(fun.y="median", geom="bar", fill = "blue", alpha = .5) +
@@
 ```{r}
-ggplot(df, aes(x=as.factor(site), y=fb_likes)) +
-  stat_summary(fun.y="sum", geom="bar", fill = "blue", alpha = .5) +
+ggplot(btw, aes(x=as.factor(site), y=fb_likes)) +
+  stat_summary(fun.y="median", geom="bar", fill = "blue", alpha = .5) +
   labs(title = "") +
-  labs(x="", y="Sum of Facebook Likes") +
+  labs(x="", y="Median of Facebook Likes") +
   theme(axis.text.x = element_text(angle = 40, hjust = 1))
@@
 
-## Tokenize terms
+## What are the news with the highest fb-shares?
 ```{r}
-news_words <- df %>%
-  unnest_tokens(word, text) %>%
-  count(site, word, sort = TRUE)
+btw %>%
+  filter(site == "tagesschau.de") %>%
+  arrange(desc(fb_shares)) %>%
+  select(text) %>%
+  .[1,]
+```
+
+```{r}
+btw %>%
+  ggplot(aes(date, fill = site)) +
+  geom_histogram(bins = 100, alpha = .8)
+```
+
+## Tokenize
+```{r}
+btw %>%
+  unnest_tokens(word, text_cleaned) %>%
+  count(site, word, sort = TRUE) -> news_count
 
 ## TF-IDF
-news_words <- news_words %>%
+news_count <- news_count %>%
   bind_tf_idf(word, site, n)
@@
 ### Terms with high tf-idf
-news_words %>%
+news_count %>%
   #filter(site == "spiegel.de") %>%
-  arrange(desc(n))
+  arrange(desc(tf_idf))
 ```
 
-## Tokenize terms
+### Bigrams
 ```{r}
-news_words <- btw %>%
-  unnest_tokens(word, text_cleaned) %>%
-  count(site, word, sort = TRUE)
+btw %>%
+  unnest_tokens(bigram, text_cleaned, token="ngrams", n=2) %>%
+  count(site, bigram, sort = TRUE) -> news_bigrams
 
-## TF-IDF
-news_words <- news_words %>%
-  bind_tf_idf(word, site, n)
-
-### Terms with high tf-idf
-news_words %>%
-  #filter(site == "spiegel.de") %>%
-  arrange(desc(n))
-```
-
-## Bigrams
-
-```{r}
-news_bigrams <- btw %>%
-  unnest_tokens(bigram, text_cleaned, token="ngrams", n=2)
-
-news_bigrams %>%
-  count(bigram, sort = TRUE)
+news_bigrams
 ```
@@
 # Topic Modeling
-## LDA
+## Build Corpus
+```{r}
+btw %>%
+  filter(nchar(text_cleaned) > 5) -> btw
+```
+
 ```{r}
 # Build corpus
-btw.lda <- Corpus(VectorSource(btw$text_cleaned))
+df.lda <- Corpus(VectorSource(btw$text_cleaned))
 # Create document-term matrix
-dtm <- DocumentTermMatrix(btw.lda)
+dtm <- DocumentTermMatrix(df.lda)
 
@@
 
+## Select Number of K Topics
+(http://davidmeza1.github.io/2015/07/20/topic-modeling-in-R.html)
+
 ```{r}
+seqk <- seq(30, 100, 5) #
+burnin <- 1000
+iter <- 1000
+keep <- 50
+system.time(fitted_many <- lapply(seqk, function(k) topicmodels::LDA(dtm, k = k,
+                                                     method = "Gibbs",control = list(burnin = burnin,
+                                                                         iter = iter, keep = keep) )))
+```
+
+### The harmonic mean function
+```{r}
+harmonicMean <- function(logLikelihoods, precision = 2000L) {
+  llMed <- median(logLikelihoods)
+  as.double(llMed - log(mean(exp(-mpfr(logLikelihoods,
+                                       prec = precision) + llMed))))
+}
+```
+
 # Run LDA using Gibbs sampling
-library(topicmodels)
+```{r}
+#Set parameters for Gibbs sampling (see https://eight2late.wordpress.com/2015/09/29/a-gentle-introduction-to-topic-modeling-using-r/)
+burnin <- 1000
+iter <- 1000
+keep <- 50
 
-#Set parameters for Gibbs sampling (see https://eight2late.wordpress.com/2015/09/29/a-gentle-introduction-to-topic-modeling-using-r/)
-burnin <- 4000
-iter <- 2000
-thin <- 500
-seed <-list(2003,5,63,100001,765)
-nstart <- 5
-best <- TRUE
-
-k = 10 # Topics
+k = 50 # Topics
 ```
@@
 t1 <- Sys.time()
-lda10 <-LDA(dtm, k, method="Gibbs", control=list(nstart=nstart, seed=seed, best=best, burnin=burnin, iter = iter, thin=thin))
+lda50 <-LDA(dtm, k, method="Gibbs", control=list(burnin=burnin, iter = iter, keep = keep))
 t2 <- Sys.time()
 t2 - t1
+
+save(ldaOut, file=paste("../output/models/LDAGibbs",k,".Rda"))
 ```
@@
 ```{r}
-#write out results
-lda10.topics <- as.matrix(topics(lda10))
-lda10.topics
+#write out results (docs to topics)
+ldaOut.topics <- as.matrix(topics(ldaOut))
+write.csv(ldaOut.topics,file=paste("../output/models/LDAGibbs",k,"DocsToTopics.csv"))
 ```
@@
 #top 6 terms in each topic
-lda10.terms <- as.matrix(terms(lda10,6))
+ldaOut.terms <- as.matrix(terms(ldaOut,6))
+write.csv(ldaOut.terms,file=paste("../output/models/LDAGibbs",k,"TopicsToTerms.csv"))
 ```
@@
 #probabilities associated with each topic assignment
-topicProbabilities <- as.data.frame(lda10@gamma)
+topicProbabilities <- as.data.frame(ldaOut@gamma)
+rownames(topicProbabilities) <- make.unique(btw$title)
+
+write.csv(topicProbabilities,file=paste("../output/models/LDAGibbs",k,"TopicProbabilities.csv"))
 ```
@@
 sort(topicProbabilities[x,])[k-1]/sort(topicProbabilities[x,])[k-2])
+```
+
+```{r}
+#write to file
+write.csv(topic1ToTopic2,file=paste("../output/models/LDAGibbs",k,"Topic1ToTopic2.csv"))
+write.csv(topic2ToTopic3,file=paste("../output/models/LDAGibbs",k,"Topic2ToTopic3.csv"))
 ```

### 2017-10-25 paper/R/06_stm.Rmd
add lda model

--- 2017-10-25 paper/R/03_explore.Rmd
@@
 rm(list = ls())
+
 load("../output/news_cleaned2.Rda")
+write.csv(btw, file="../output/btw.csv")
 
-col <- brewer.pal(12, name = "Paired")
+df$date <- as.Date(df$date)
+
+#col <- brewer.pal(12, name = "Paired")
 ```
 
-## Summary Stats
+## Reduce Dataframe
 ```{r}
 df %>%
-  group_by(site) %>%
-  summarise(obs = n(),
-    fb_shares.mean = mean(fb_shares),
-            fb_shares.max = max(fb_shares),
-            fb_likes.mean = mean(fb_likes),
-            fb_likes.max = max(fb_likes),
-            external_links.mean = mean(external_links),
-            external_links.max = max(external_links),
-            text_length.mean = mean(text_lenght),
-            text_length.max = max(text_lenght)) %>%
-  htmlTable(align = "l")
-```
+  filter(fb_shares > 0) %>%
+  filter(!site %in% c("ndr.de","wdr.de")) %>%
+  filter(grepl("bundestagswahl", text_cleaned)) -> btw
 
-### Text Length
-```{r}
-ggplot(df, aes(x=as.factor(site), y=text_lenght)) +
-  stat_summary(fun.y="median", geom="bar", fill = "blue", alpha = .5) +
-  labs(title = "") +
-  labs(x="", y="Median Text Length") +
-  theme(axis.text.x = element_text(angle = 40, hjust = 1))
-```
-
-### Facebook Likes
-```{r}
-ggplot(df, aes(x=as.factor(site), y=fb_likes)) +
-  stat_summary(fun.y="sum", geom="bar", fill = "blue", alpha = .5) +
-  labs(title = "") +
-  labs(x="", y="Sum of Facebook Likes") +
-  theme(axis.text.x = element_text(angle = 40, hjust = 1))
-```
-
-## Tokenize terms
-```{r}
-news_words <- df %>%
-  unnest_tokens(word, text) %>%
-  count(site, word, sort = TRUE)
-
-## TF-IDF
-news_words <- news_words %>%
-  bind_tf_idf(word, site, n)
-
-### Terms with high tf-idf
-news_words %>%
-  #filter(site == "spiegel.de") %>%
-  arrange(desc(n))
-```
-
-## Tokenize terms
-```{r}
-news_words <- btw %>%
-  unnest_tokens(word, text_cleaned) %>%
-  count(site, word, sort = TRUE)
-
-## TF-IDF
-news_words <- news_words %>%
-  bind_tf_idf(word, site, n)
-
-### Terms with high tf-idf
-news_words %>%
-  #filter(site == "spiegel.de") %>%
-  arrange(desc(n))
-```
-
-## Bigrams
-
-```{r}
-news_bigrams <- btw %>%
-  unnest_tokens(bigram, text_cleaned, token="ngrams", n=2)
-
-news_bigrams %>%
-  count(bigram, sort = TRUE)
 ```
@@
 # Topic Modeling
-## LDA
-```{r}
-# Build corpus
-btw.lda <- Corpus(VectorSource(btw$text_cleaned))
-# Create document-term matrix
-dtm <- DocumentTermMatrix(btw.lda)
-
-inspect(dtm)
-```
-
-```{r}
-# Run LDA using Gibbs sampling
-library(topicmodels)
-
-#Set parameters for Gibbs sampling (see https://eight2late.wordpress.com/2015/09/29/a-gentle-introduction-to-topic-modeling-using-r/)
-burnin <- 4000
-iter <- 2000
-thin <- 500
-seed <-list(2003,5,63,100001,765)
-nstart <- 5
-best <- TRUE
-
-k = 10 # Topics
-```
-
-```{r}
-t1 <- Sys.time()
-lda10 <-LDA(dtm, k, method="Gibbs", control=list(nstart=nstart, seed=seed, best=best, burnin=burnin, iter = iter, thin=thin))
-t2 <- Sys.time()
-t2 - t1
-```
-
-```{r}
-#write out results
-lda10.topics <- as.matrix(topics(lda10))
-lda10.topics
-```
-
-```{r}
-#top 6 terms in each topic
-lda10.terms <- as.matrix(terms(lda10,6))
-```
-
-```{r}
-#probabilities associated with each topic assignment
-topicProbabilities <- as.data.frame(lda10@gamma)
-```
-
-```{r}
-#Find relative importance of top 2 topics
-topic1ToTopic2 <- lapply(1:nrow(dtm),function(x)
-sort(topicProbabilities[x,])[k]/sort(topicProbabilities[x,])[k-1])
-```
-
-```{r}
-#Find relative importance of second and third most important topics
-topic2ToTopic3 <- lapply(1:nrow(dtm),function(x)
-sort(topicProbabilities[x,])[k-1]/sort(topicProbabilities[x,])[k-2])
-```
 

### 2017-10-25 paper/R/webhoseio_preprare2.Rmd

--- 2017-10-25 paper/R/02_prepare.Rmd
@@
 ```{r}
-rm(list =ls())
-
 load("../output/news_cleaned.Rda")
@@
 ```{r}
-pat <- 'Hinweis.+?(?=(einfügen))'
-btw %>%
+pat <- 'ejf[^"]*'
+df %>%
   filter(grepl(pat, text, perl = TRUE)) %>%
@@
 ```{r}
-as.data.frame(str_match(btw$text, pat)) ->test
+as.data.frame(str_match(df$text, pat)) ->test
 test %>%
@@
 
-  # Tagesschau
-  x = gsub('Hinweis.+?(?=(einfügen))', "", x, perl = TRUE)
-
   return(x)
@@
 
-# apply function to dataframe
+# apply function to the "orig" dataframe
 df$text_cleaned <- clean.text(df$text)
@@
 ```{r}
-df$text_cleaned <- gsub("[[:punct:]]", " ", df$text_cleaned)
-df$text_cleaned <- gsub("[[:cntrl:]]", " ", df$text_cleaned)
-df$text_cleaned <- gsub("[[:digit:]]", " ", df$text_cleaned)
-df$text_cleaned <- gsub("^[[:space:]]+", " ", df$text_cleaned)
-df$text_cleaned <- gsub("[[:space:]]+$", " ", df$text_cleaned)
-df$text_cleaned <- tolower(df$text_cleaned)
+preprocess.text <- function(x) {
+  x = gsub("[[:punct:]]", " ", x)  # replace punctuation with space
+  x = gsub("[[:cntrl:]]", " ", x)  # replace control characters with space
+  x = gsub("[[:digit:]]", "", x)  # remove numbers
+  x = gsub("^[[:space:]]+", "", x) # remove whitespace at beginning of documents
+  x = gsub("[[:space:]]+$", "", x) # remove whitespace at end of documents 
+  x = tolower(x)
+  return(x)
+}
+
+# apply function to the "orig" dataframe
+df$text_cleaned <- clean.text(df$text_cleaned)
 ```

### 2017-10-27 paper/R/01_prepare.Rmd
explore model

--- 2017-10-22 paper/R/webhoseio_prepare.Rmd
@@
 
-```{r, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
+```{r}
 rm(list = ls())
@@
 myJSON <- lapply(c(june,july,aug,sep), function(x) fromJSON(file=x)) 
-#myJSON <- lapply(june, function(x) fromJSON(file=x))
-
-length(myJSON)
 ```
@@
 
-```{r, eval=FALSE, include=FALSE}
+```{r}
 site <- NULL
@@
 fb_comments <- NULL
-gplus_shares <- NULL
-linkedin_shares <- NULL
-stumbledupon_shares <- NULL
 
@@
 
-  gplus_shares <- append(gplus_shares, myJSON[[i]]["thread"][[1]]["social"][[1]]["gplus"][[1]][["shares"]])
-  linkedin_shares <- append(gplus_shares, myJSON[[i]]["thread"][[1]]["social"][[1]]["linkedin"][[1]][["shares"]])
-  stumbledupon_shares <- append(stumbledupon_shares, myJSON[[i]]["thread"][[1]]["social"][[1]]["stumbledupon"][[1]]["shares"][[1]])
-
-  external_links <- append(external_links, length(myJSON[[i]]["external_links"][[1]]))
-
 }
 
-df <- cbind(site, title, text, published, section, fb_shares, fb_likes, gplus_shares, external_links)
+df <- cbind(site, title, text, published, section, fb_shares, fb_likes, fb_comments)
 df <- data.frame(df, stringsAsFactors = FALSE)
@@
 ```{r}
-rm(site, title, text, published, fb_shares, fb_likes, section, external_links)
+rm(site, title, text, published, fb_shares, fb_likes, section, fb_comments)
 ```
@@
          fb_likes = as.numeric(fb_likes),
-         gplus_shares = as.numeric(gplus_shares),
-         external_links = as.numeric(external_links)) -> df
+         fb_comments = as.numeric(fb_comments)) -> df
 ```
@@
 
-```{r, eval=FALSE, include=FALSE}
+## Count number of terms in a string
+```{r}
+df %>% filter(site != "zdf.de") -> df
+
+df$text_lenght <- sapply(gregexpr("\\S+", df$text), length)
+```
+
+```{r}
 # Save file
-save(df, linkedin_shares, file="../output/news_cleaned.Rda")
+save(df, file="../output/news_cleaned.Rda")
 ```

### 2017-10-27 paper/R/05_lda_eight2late.Rmd
explore model

@@
 load("../output/news_cleaned2.Rda")
-write.csv(btw, file="../output/btw.csv")
 
@@
 ```
+
+## Explore the model
+```{r}
+load(file ="../output/models/LDAGibbs 50 .Rda")
+```
+
+### Most likely Topics per Article
+```{r}
+# The topics function from the package is used to extract the most likely topic for each document 
+btw.topics <- topics(ldaOut, 3)
+
+# Create Dataframe
+doctopics.df <- as.data.frame(t(btw.topics))
+
+doctopics.df %>%
+  transmute(ArticleID = rownames(.),
+            Topic1 = V1,
+            Topic2 = V2,
+            Topic3 = V3) -> doctopics.df
+
+doctopics.df$ArticleID <- as.integer(doctopics.df$ArticleID)
+doctopics.df[1:10,]
+
+# Add Topic to origian DF
+```
+
+### Most likely Words per Topic
+```{r}
+## Return the top 30 terms.
+btw.terms <- as.data.frame(terms(ldaOut, 30), stringAsFactors = FALSE)
+btw.terms[1:5,1:10]
+```
+
+### Create Topic Labels
+As part of the visualization I will construct later, a topic label needs be used to created. The terms are gathered in rank order and then the label is created by concatenating the first three terms.
+
+```{r}
+topicTerms <- btw.terms %>% gather(Topic)
+topicTerms <- cbind(topicTerms, Rank = rep(1:30))
+topicTerms <- topicTerms %>% filter(Rank < 5)
+
+topicTerms <- topicTerms %>% mutate(Topic = stringr::word(Topic, 2))
+topicTerms$Topic <- as.numeric(topicTerms$Topic)
+
+topicLabel <- data.frame()
+for (i in 1:50){
+  z <- dplyr::filter(topicTerms, Topic==i)
+  l <- as.data.frame(paste(z[1,2], z[2,2], z[3,2], z[4,2], sep = " "), stringAsFactors = FALSE)
+  topicLabel <- rbind(topicLabel, l)
+}
+colnames(topicLabel) <- c("Label")
+
+topicLabel
+```
+
+### Working with Theta (Topic prevalence)
+```{r}
+theta <- as.data.frame(posterior(ldaOut)$topics)
+head(theta)
+```
+
+```{r}
+x <- as.data.frame(row.names(theta), stringsAsFactors = FALSE)
+#colnames(x) <- c("ArticleID")
+#x$ArticleID <- as.numeric(x$ArticleID)
+
+#theta2 <- cbind(x,theta)
+```
+
+```{r}
+library(corrplot)
+
+c <- cor(theta)
+corrplot(c, method = "circle")
+```

### 2017-10-27 paper/R/02_prepare.Rmd
facebook paper

@@
 ```{r}
-pat <- 'Hinweis.+?(?=(einfügen))'
+pat <- 'Aus unserem Netzwerk[^"]*'
 btw %>%
@@
   x = gsub("Live-Ticker", "", x)
+  x = gsub('Aus unserem Netzwerk[^"]*', "", x, perl = TRUE)
 
@@
 
+```{r}
+# Save file
+save(df, file="../output/news_cleaned2.Rda")
+```
+
 ## Remove Stopwords
@@
 
-## Save by Site
+## Generate new variables 
 ```{r}
-save_by_site <- function(DF) {
-  write.csv(DF, paste0("../output/single/",as.character(DF),".csv"))
-  return(DF)
-}
+df$video <- ifelse(grepl("video", df$title, ignore.case = TRUE),1,0)
+df$date <- as.Date(df$date)
+```
 
+## Reduce Dataframe
+```{r}
 df %>%
-  group_by(site) %>%
-  do(save_by_site(.))
+  filter(!site %in% c("ndr.de","wdr.de", "swr.de","tagessschau.de")) %>%
+  filter(grepl("bundestagswahl", text, ignore.case = TRUE)) -> btw
+
+btw$ArticleID <- rownames(btw)
 ```
@@
 ```{r}
-df %>% filter(site=="stern.de") %>% write.csv(.,file = "../output/single/stern.csv")
-df %>% filter(site=="focus.de") %>% write.csv(.,file = "../output/single/focus.csv")
-df %>% filter(site=="zeit.de") %>% write.csv(.,file = "../output/single/zeit.csv")
-df %>% filter(site=="wdr.de") %>% write.csv(.,file = "../output/single/wdr.csv")
-df %>% filter(site=="spiegel.de") %>% write.csv(.,file = "../output/single/spiegel.csv")
-df %>% filter(site=="welt.de") %>% write.csv(.,file = "../output/single/welt.csv")
-df %>% filter(site=="handelsblatt.com") %>% write.csv(.,file = "../output/single/handelsblatt.csv")
-df %>% filter(site=="tagesschau.de") %>% write.csv(.,file = "../output/single/tagesschau.csv")
-df %>% filter(site=="swr.de") %>% write.csv(.,file = "../output/single/swr.csv")
-df %>% filter(site=="bild.de") %>% write.csv(.,file = "../output/single/bild.csv")
-df %>% filter(site=="ndr.de") %>% write.csv(.,file = "../output/single/ndr.csv")
+save(df, btw, file="../output/news_btw.Rda")
 ```
-
-## Load by site
-```{r}
-focus <- read.csv("../output/focus.csv")
-spiegel <- read.csv("../output/spiegel.csv")
-bild <- read.csv("../output/bild.csv")
-
-df_reduced <- rbind(focus, spiegel, bild)
-```
-
-```{r}
-save(df_reduced, file="../output/df_reduced.Rda")
-```

### 2017-10-27 paper/R/03_explore.Rmd
facebook paper

@@
 ```
-
-## Tokenize terms
-```{r}
-news_words <- df %>%
-  unnest_tokens(word, text) %>%
-  count(site, word, sort = TRUE)
-
-## TF-IDF
-news_words <- news_words %>%
-  bind_tf_idf(word, site, n)
-
-### Terms with high tf-idf
-news_words %>%
-  #filter(site == "spiegel.de") %>%
-  arrange(desc(n))
-```
-
-## Tokenize terms
-```{r}
-news_words <- btw %>%
-  unnest_tokens(word, text_cleaned) %>%
-  count(site, word, sort = TRUE)
-
-## TF-IDF
-news_words <- news_words %>%
-  bind_tf_idf(word, site, n)
-
-### Terms with high tf-idf
-news_words %>%
-  #filter(site == "spiegel.de") %>%
-  arrange(desc(n))
-```
-
-## Bigrams
-
-```{r}
-news_bigrams <- btw %>%
-  unnest_tokens(bigram, text_cleaned, token="ngrams", n=2)
-
-news_bigrams %>%
-  count(bigram, sort = TRUE)
-```
-
-# Topic Modeling
-## LDA
-```{r}
-# Build corpus
-btw.lda <- Corpus(VectorSource(btw$text_cleaned))
-# Create document-term matrix
-dtm <- DocumentTermMatrix(btw.lda)
-
-inspect(dtm)
-```
-
-```{r}
-# Run LDA using Gibbs sampling
-library(topicmodels)
-
-#Set parameters for Gibbs sampling (see https://eight2late.wordpress.com/2015/09/29/a-gentle-introduction-to-topic-modeling-using-r/)
-burnin <- 4000
-iter <- 2000
-thin <- 500
-seed <-list(2003,5,63,100001,765)
-nstart <- 5
-best <- TRUE
-
-k = 10 # Topics
-```
-
-```{r}
-t1 <- Sys.time()
-lda10 <-LDA(dtm, k, method="Gibbs", control=list(nstart=nstart, seed=seed, best=best, burnin=burnin, iter = iter, thin=thin))
-t2 <- Sys.time()
-t2 - t1
-```
-
-```{r}
-#write out results
-lda10.topics <- as.matrix(topics(lda10))
-lda10.topics
-```
-
-```{r}
-#top 6 terms in each topic
-lda10.terms <- as.matrix(terms(lda10,6))
-```
-
-```{r}
-#probabilities associated with each topic assignment
-topicProbabilities <- as.data.frame(lda10@gamma)
-```
-
-```{r}
-#Find relative importance of top 2 topics
-topic1ToTopic2 <- lapply(1:nrow(dtm),function(x)
-sort(topicProbabilities[x,])[k]/sort(topicProbabilities[x,])[k-1])
-```
-
-```{r}
-#Find relative importance of second and third most important topics
-topic2ToTopic3 <- lapply(1:nrow(dtm),function(x)
-sort(topicProbabilities[x,])[k-1]/sort(topicProbabilities[x,])[k-2])
-```
-
-## Structural Topic Model
-
-```{r, eval=FALSE, include=FALSE}
-# Process data
-processed <- textProcessor(df$text_cleaned, metadata = df[,c("date","site","text_cleaned","text")],
-                           wordLengths = c(2,Inf),
-                           lowercase = F,
-                           removestopwords = F,
-                           removenumbers = F,
-                           removepunctuation = F,
-                           stem = F)
-out <- prepDocuments(processed$documents, processed$vocab, processed$meta)
-```
-
-### Run the Model 
-```{r}
-
-t1 <- Sys.time()
-stm <- stm(documents = out$documents, 
-           vocab = out$vocab, 
-           K=25, 
-           prevalence = ~site, 
-           content = ~site, 
-           data=out$meta, 
-           init.type = "Spectral")
-t2 <- Sys.time()
-t2 - t1
-
-save(stm, out, file = "stm.RDa")
-#load(file = "stm.RDa")
-
-```
-
-### Interpret the results
-
-#### Wordclouds by topic
-```{r}
-cloud(stm, topic =8, scale = c(5,.25))
-```
-
-```{r}
-# get document - topic distribution 
-theta <- as.data.frame(stm$theta)
-theta$source <- out$meta$source
-theta$date <- out$meta$date
-```
-
-#### get the mean distribution of topics  ...
-##### ... by date
-```{r}
-theta %>% 
-  select(- source) %>%
-  group_by(date) %>% 
-  summarise_all(funs(mean)) -> date_mean
-
-# plot 
-melt1 = melt(date_mean, id = "date")
-
-ggplot(melt1, aes(x=date, y = variable)) +   
-  geom_raster(aes(fill=value)) + 
-  scale_fill_gradient(low = "light blue", high = "dark blue") +
-  labs(x="Date", y="Topics", title="Average Topic Weights") + 
-  theme_bw()
-
-```
-
-##### ... by source
-```{r, message=FALSE, warning=TRUE}
-theta %>% 
-  select(- date) %>%
-  group_by(source) %>% 
-  summarise_all(funs(mean)) -> source_mean
-
-# plot 
-melt2 = melt(source_mean, id = "source")
-
-ggplot(melt2, aes(x=source, y = variable)) +   
-  geom_raster(aes(fill=value)) + 
-  scale_fill_gradient(low = "light blue", high = "dark blue") +
-  labs(x="Source", y="Topics", title="Average Topic Weights") + 
-  theme_bw()
-
-```
-
-### compute cosine similarity
-
-```{r, message=FALSE}
-library(proxy)
-cosine_dist <- as.matrix(dist(as.matrix(source_mean[,1:20]), method = "cosine"))
-colnames(cosine_dist) <- unique(out$meta$source)
-rownames(cosine_dist) <- unique(out$meta$source)
-```
-
-### Correlogram
-```{r, message=FALSE}
-devtools::install_github("sinhrks/ggfortify")
-library("ggfortify")
-devtools::install_github("kassambara/ggcorrplot")
-library(ggcorrplot)
-library("ggthemes")
-
-ggcorrplot(cosine_dist, hc.order = TRUE, 
-           type = "lower", 
-           lab = TRUE, 
-           lab_size = 3, 
-           method="circle", 
-           #colors = c("tomato2", "white", "springgreen3"), 
-           title="", 
-           ggtheme=theme_bw)
-```
-
-### correlations between topics
-```{r}
-mod.out.corr <- topicCorr(stm)
-plot(mod.out.corr)
-```
-
-### stmBrowser
-```{r}
-library(stmBrowser)
-setwd(tempdir())
-stmBrowser(stm, data=out$meta, c("source","date"), text="text_cleaned")
-
-```.

### 2017-10-27 paper/R/04_paper.Rmd
facebook paper

---
title: "Data Description"
author: "Franziska Löw"
date: "`r format(Sys.Date())`"
output: pdf_document
---

```{r, include=FALSE}
# load the packages
libs <- c("tidytext","tidyr","readr","lubridate","tm","stm","RColorBrewer","topicmodels",
          "plyr","dplyr","class","knitr","kableExtra","cldr","data.table",
          "htmlTable","ggplot2","gridExtra","jsonlite","stringr","scales","rjson")
lapply(libs, library, character.only = TRUE)
```

```{r, include=FALSE}
#Load Data
rm(list = ls())

load("../output/news_btw.Rda")

df$date <- as.Date(df$date)
```

```{r, include=FALSE}
df %>%
  #filter(fb_shares > 0) %>%
  filter(!site %in% c("ndr.de","wdr.de","swr.de","tagesschau.de")) %>%
  filter(grepl("bundestagswahl", text_cleaned)) -> btw

btw 
```

To explore the effect of topic prevalence of an article on the times this article is shared on Facebook, we analyze a sample of 1768 news articles containing the term "Bundestagswahl" (Federal Election) dated from 01.06.2017 to 30.09.2017\footnote{German federal elections took place on 24th of September 2017.} and originated from seven different german news sources.\footnote{Bild.de, Focus.de, Handelsblatt.com, Spiegel.de, Stern.de, Tagesschau.de, Welt.de, Zeit.de} For each document in our sample, we observe the day it was written, the number of shares on Facebook and the newswire service publishing the report. We include the news agency as covariates on topical prevalence. We also include news agency as a covariate affecting topical content to estimate how topics are discussed in different ways by different news agencies.

Figure -- shows the total sum of all Facebook S, that most of the documents in our corpus

```{r echo=FALSE}
btw %>%
  filter(!grepl("video", title, ignore.case = TRUE)) %>%
  ggplot(aes(x=as.factor(site), y=fb_shares)) +
  stat_summary(fun.y="sum", geom="bar", fill = "blue", alpha = .5) +
  labs(title = "") +
  labs(x="", y="Sum of Facebook Shares") +
  theme(axis.text.x = element_text(angle = 40, hjust = 1))
```

### 2017-10-27 paper/R/05_lda_eight2late.Rmd
facebook paper

@@
 
+btw$ArticleID <- rownames(btw)
 ```
@@
 
-save(ldaOut, file=paste("../output/models/LDAGibbs",k,".Rda"))
+save(ldaOut, btw, file=paste("../output/models/LDAGibbs",k,".Rda"))
 ```
@@
 ### Create Topic Labels
-As part of the visualization I will construct later, a topic label needs be used to created. The terms are gathered in rank order and then the label is created by concatenating the first three terms.
-
 ```{r}

### 2017-10-27 paper/R/06_explore_LDA.Rmd
facebook paper

--- 2017-10-27 paper/R/05_lda_eight2late.Rmd
@@
 ```{r}
-rm(list = ls())
+rm(list=ls())
 
-load("../output/news_cleaned2.Rda")
-
-df$date <- as.Date(df$date)
-
-#col <- brewer.pal(12, name = "Paired")
-```
-
-## Reduce Dataframe
-```{r}
-df %>%
-  filter(fb_shares > 0) %>%
-  filter(!site %in% c("ndr.de","wdr.de")) %>%
-  filter(grepl("bundestagswahl", text_cleaned)) -> btw
-
-btw$ArticleID <- rownames(btw)
-```
-
-# Topic Modeling
-## Build Corpus
-```{r}
-btw %>%
-  filter(nchar(text_cleaned) > 5) -> btw
-```
-
-```{r}
-# Build corpus
-df.lda <- Corpus(VectorSource(btw$text_cleaned))
-# Create document-term matrix
-dtm <- DocumentTermMatrix(df.lda)
-# Assign name to docs
-rownames(dtm) <- make.unique(btw$title)
-
-inspect(dtm)
-```
-
-## Run LDA using Gibbs sampling
-```{r}
-#Set parameters for Gibbs sampling (see https://eight2late.wordpress.com/2015/09/29/a-gentle-introduction-to-topic-modeling-using-r/)
-burnin <- 1000
-iter <- 1000
-keep <- 50
-
-k = 50 # Topics
-```
-
-```{r}
-t1 <- Sys.time()
-lda50 <-LDA(dtm, k, method="Gibbs", control=list(burnin=burnin, iter = iter, keep = keep))
-t2 <- Sys.time()
-t2 - t1
-
-save(ldaOut, btw, file=paste("../output/models/LDAGibbs",k,".Rda"))
-```
-
-```{r}
-#write out results (docs to topics)
-ldaOut.topics <- as.matrix(topics(ldaOut))
-write.csv(ldaOut.topics,file=paste("../output/models/LDAGibbs",k,"DocsToTopics.csv"))
-```
-
-```{r}
-#top 6 terms in each topic
-ldaOut.terms <- as.matrix(terms(ldaOut,6))
-write.csv(ldaOut.terms,file=paste("../output/models/LDAGibbs",k,"TopicsToTerms.csv"))
-```
-
-```{r}
-#probabilities associated with each topic assignment
-topicProbabilities <- as.data.frame(ldaOut@gamma)
-#rownames(topicProbabilities) <- make.unique(btw$title)
-
-write.csv(topicProbabilities,file=paste("../output/models/LDAGibbs",k,"TopicProbabilities.csv"))
-```
-
-```{r}
-#Find relative importance of top 2 topics
-topic1ToTopic2 <- lapply(1:nrow(dtm),function(x)
-sort(topicProbabilities[x,])[k]/sort(topicProbabilities[x,])[k-1])
-```
-
-```{r}
-#Find relative importance of second and third most important topics
-topic2ToTopic3 <- lapply(1:nrow(dtm),function(x)
-sort(topicProbabilities[x,])[k-1]/sort(topicProbabilities[x,])[k-2])
-```
-
-```{r}
-#write to file
-write.csv(topic1ToTopic2,file=paste("../output/models/LDAGibbs",k,"Topic1ToTopic2.csv"))
-write.csv(topic2ToTopic3,file=paste("../output/models/LDAGibbs",k,"Topic2ToTopic3.csv"))
-```
-
-## Explore the model
-```{r}
 load(file ="../output/models/LDAGibbs 50 .Rda")
@@
 doctopics.df$ArticleID <- as.integer(doctopics.df$ArticleID)
-doctopics.df[1:10,]
 
 # Add Topic to origian DF
+btw <- btw %>%
+  mutate(ArticleID = as.integer(ArticleID)) %>%
+  inner_join(.,doctopics.df, by="ArticleID")
 ```
@@
 btw.terms <- as.data.frame(terms(ldaOut, 30), stringAsFactors = FALSE)
-btw.terms[1:5,1:10]
+btw.terms[1:10,10:12]
 ```
@@
 
+Correlate the topic by news source of the documents. The column means of theta, grouped by news source is calculated.
+
 ```{r}
 x <- as.data.frame(row.names(theta), stringsAsFactors = FALSE)
-#colnames(x) <- c("ArticleID")
-#x$ArticleID <- as.numeric(x$ArticleID)
+colnames(x) <- c("ArticleID")
+x$ArticleID <- as.numeric(x$ArticleID)
 
-#theta2 <- cbind(x,theta)
+theta2 <- cbind(x,theta)
+theta2 <- dplyr::left_join(theta2, btw[,c("site", "ArticleID")], by="ArticleID")
+
+## Column means grouped by news outlet
+theta.mean.by <- by(theta2[,2:51], theta2$site, colMeans)
+theta.mean <- do.call("rbind", theta.mean.by)
 ```
@@
 
-c <- cor(theta)
+c <- cor(theta.mean)
 corrplot(c, method = "circle")
 ```
+
+Using the categories mean theta, it is possible to select the most diagnostic topic for each of the categories.
+
+```{r}
+theta.mean.ratios <- theta.mean
+for (ii in 1:nrow(theta.mean)) {
+  for (jj in 1:ncol(theta.mean)) {
+    theta.mean.ratios[ii,jj] <-
+      theta.mean[ii,jj] / sum(theta.mean[ii,-jj])
+  }
+}
+
+topics.by.ratio <- apply(theta.mean.ratios, 1, function(x) sort(x, decreasing = TRUE, index.return = TRUE)$ix)
+
+# the most diagnostic topics per news source are found in the thea 1st row of index matrix
+topics.by.ratio[1:10,]
+```
+
+### compute cosine similarity
+
+```{r, message=FALSE}
+library(proxy)
+cosine_dist <- as.matrix(dist(topics.by.ratio, by_rows = FALSE, method = "cosine"))
+```
+
+### Correlogram
+```{r, message=FALSE}
+devtools::install_github("sinhrks/ggfortify")
+library("ggfortify")
+devtools::install_github("kassambara/ggcorrplot")
+library(ggcorrplot)
+library("ggthemes")
+
+ggcorrplot(cosine_dist, hc.order = TRUE, 
+           type = "lower", 
+           lab = TRUE, 
+           lab_size = 3, 
+           method="circle", 
+           #colors = c("tomato2", "white", "springgreen3"), 
+           title="", 
+           ggtheme=theme_bw)
+```
+
+## Regression
+```{r message=FALSE, warning=FALSE, paged.print=FALSE}
+#library(GGally)
+
+btw_reduced <- btw[,c(1,6,10,13,14,15)]
+
+ggpairs(btw_reduced, aes(color = site, alpha=.5))
+```
+
+```{r}
+library(plm)
+
+lm1 <- lm(fb_shares ~ Topic1 * site, data = btw)
+summary(lm1)
+```

### 2017-10-27 paper/R/06_stm.Rmd
facebook paper

@@
 # Process data
-processed <- textProcessor(df$text_cleaned, metadata = df[,c("date","site","text_cleaned","text")],
+processed <- textProcessor(btw$text_cleaned, metadata = btw[,c("date","site","text_cleaned","text")],
                            wordLengths = c(2,Inf),
@@
 ```{r}
+k = 50 # Topics
 
 t1 <- Sys.time()
-stm <- stm(documents = out$documents, 
+stmOut <- stm(documents = out$documents, 
            vocab = out$vocab, 
-           K=25, 
+           K=k, 
            prevalence = ~site, 
@@
 
-save(stm, out, file = "stm.RDa")
-#load(file = "stm.RDa")
+save(stmOut, btw, file=paste("../output/models/STM",k,".Rda"))
 
@@
 
-### compute cosine similarity
-
-```{r, message=FALSE}
-library(proxy)
-cosine_dist <- as.matrix(dist(as.matrix(source_mean[,1:20]), method = "cosine"))
-colnames(cosine_dist) <- unique(out$meta$source)
-rownames(cosine_dist) <- unique(out$meta$source)
-```
-
-### Correlogram
-```{r, message=FALSE}
-devtools::install_github("sinhrks/ggfortify")
-library("ggfortify")
-devtools::install_github("kassambara/ggcorrplot")
-library(ggcorrplot)
-library("ggthemes")
-
-ggcorrplot(cosine_dist, hc.order = TRUE, 
-           type = "lower", 
-           lab = TRUE, 
-           lab_size = 3, 
-           method="circle", 
-           #colors = c("tomato2", "white", "springgreen3"), 
-           title="", 
-           ggtheme=theme_bw)
-```
-
 ### correlations between topics
@@
 
-```.
+```

### 2017-10-27 paper/doc/doc2.tex
facebook paper

--- 2017-10-18 paper/doc/doc.tex
@@
 
-Markt für Online-Texte.
-Presseverlage beklagen immer mehr eine Wettbewerbsverzerrung durch öffentlich-rechtliche Online-Angebote.
-"Wir erleben im Netz nach wie vor eine mit öffentlich-rechtlichen Geldern finanzierte Flut textbasierter Gratis-Angebote, nichts anderes als eine gebührenfinanzierte digitale Staatspresse, die den Wettbewerb verzerrt und uns Presseverlagen kaum Entfaltungsmöglichkeiten lässt" %(http://www.sz-online.de/nachrichten/ard-und-zdf-gebuehrenfinanzierte-staatspresse-3776123.html)
+Social networks such as Facebook are becoming increasingly important for online news services: an increasing number of their readers access the news pages via links in the networks.
+Users of Facebook, for example, can use their profile to share links to external websites - such as news portals - with their online friends.
+This has led to the development of social media into an important generator of traffic on the internet pages.
+In Germany, 94\% of online news articles are shared on Facebook in 2015, followed by Twitter with 3.5\% and Google+ with 2.3\% \citep{schiller_development_2016}.
+The advertising-financed business model of the media houses is based on the premise that users visit their websites in order to achieve high advertising revenues.
+For this reason, news agencies are particularly interested in finding out which topics are often shared on Facebook.
+\citet{schiller_development_2016} show, that social media users choose a certain site depending on the researched topic.
+FOCUS Online is targeted for articles from politics and business, sports news is more likely to be shared from Bild.de.
 
-Wettbewerb im "Gemischten Oligopol": Die kostenlosen Nachrichtenangebote von ZDF.de oder tagesschau.de im Internet konkurrieren hier mit den Online Angeboten der klassischen Printmedien.
-Die beitragsfinanzierten Angebote behindern in der Tendenz Prozesse, durch die sich ein selbst tragendes, qualitativ hochwertiges Subskriptionssystem privatwirtschaftlicher Anbieter (spiegel.de, faz.net, welt.de, ...) entwickeln kann.
+While these static resorts give an indication on the content of an article, multiple articles in the same resort probably don't cover the same topics (and are not equally shared).
+Especially if the articles originate from different news portals.
+Furthermore, articles can contain more than one topic.
+To take these factors into account, we use a mixed-membership model \citep{airoldi_handbook_2014} - or topic model as they are often referred in the literature of text analysis \citep{blei_probabilistic_2012} to reveal the underlying topics of a collection of articles (a corpus), and how the articles exhibit them.
+We then estimate the effect of topic prevalence on the number of Facebook shares.
 
-die öffentlich-rechtlichen Anbieter sollten nur da auftreten, wo das privatwirtschaftliche Angebot klare Defizite aufweist.
-
-\begin{itemize}
-	\item Reserach Question
-	\begin{itemize}
-		\item Analyzing news reports about german elections, where we allow prevalence of topics to evolve over time (before and after the elections) and vary across newswire services.
-		\item Quantify the effect of news wire source on both topical prevalence (topic distribution) and topical content (word-topic distribution).
-	\end{itemize}
-	\item Method
-	\begin{itemize}
-		\item Topical content of documents, in which mixing weights are parameterized by observed covariates
-		\item Topic distribution word-topic distribution are specified as a simple generalized linear model on an arbitrary number of document-level covariates (news source, time of release).
-	\end{itemize}
-\end{itemize}
-
-Text as a data source is becoming increasingly popular in empirical economics, as the information encoded in text is a rich complement to conventional data (e.g.
-price, wage, votes, etc.) (\citet{grimmer_bayesian_2010}; \citet{grimmer_text_2013}; \citet{quinn_how_2010}; \citet{gentzkow_text_2017}; \citet{roberts_model_2016}).
-On interesting question is, how document metadata such as author or date influence its content.
-Depending on the characteristics of a corpus (a collection of documents), documents contain more than one topic, as well as terms most likely appear in multiple topics, thus the use of mixed-membership models \citep{airoldi_handbook_2014} - or topic model as they are often referred in the literature of text analysis \citep{blei_probabilistic_2012} - are a popular approach.
-
-Within these models the Latent Dirichlet Allocation (LDA hencefirth) is a widely used topic modelling technique, where each document is viewed as a mixture of topics (represented by the document-topic distribution) and each topic is a mixture of unique terms (represented by the topic-term distribution).
+Within topic models the Latent Dirichlet Allocation (LDA henceforth) is a widely used topic modeling technique, where each document (article) is viewed as a mixture of topics (represented by the document-topic distribution) and each topic is a mixture of unique terms (represented by the topic-term distribution).
 To "learn" the topic prevalence and the topic-term distribution, collapsed Gibbs sampling\footnote{See Section \ref{section_gibbs} for a non-formal description of the Gibbs sampler} can be used.
@@
 \citet{roberts_model_2016} develop a structural topic model (STM) that allows to incorporate external variables that effect both topical content and topical prevalence.
-We use this approach to analyze online news about the german federal elections, where we allow prevalence of topics to change over time (before and after the elections) and vary across newswire services (private or public) to quantify the effect of news wire source on both topical prevalence and topical content.
+We use this approach to analyze online news about the german federal elections, where we allow prevalence of topics to vary across newswire services.
+We then estimate the effect of topical prevalence (the posterior document-topic distribution) on the number of Facebook shares.
 
@@
 % -----------------------
-
-% Politics and Newspaper
-% ----------------------
-
-In \citet{tetlock_giving_2007}, $c_i$ is a bag-of-words representation and the outcome of interest $v_i$ is the latent “sentiment” of Wall Street Journal columns, defined along a number of dimensions such as “positive,” “optimistic,” and so on.
-The author defines the function $f (\cdot)$ using a dictionary called the General Inquirer, which provides lists of words associated with each of these sentiment categories.2 The elements of $f(c_i)$ are defined to be the sum of the counts of words in each category.
 
@@
 % A description of the generative process can be found in chapter ...
+
+% -----
+% Data
+% -----
+
+\section{Data}
+
+To explore the effect of topic prevalence of an article on the times this article is shared on Facebook, we analyze a sample of 1768 news articles containing the term "Bundestagswahl" (Federal Election) dated from 01.06.2017 to 30.09.2017\footnote{German federal elections took place on 24th of September 2017.} and originated from f
+
+% ---------------------------------
+% Generative Process
+% ----------------------------------
 

### 2017-10-28 paper/python/NewsDownloader.py
update python eventbride loader

@@ -1,67 +1,0 @@
-# Mining data from news sources
-# (http://students.washington.edu/adelak/2017/01/?p=209)
-
-import pickle
-from eventregistry import *
-
-
-# Class NewsDownloader, will download all of the articles it can get from
-# the EventRegistry database and then save them to file -
-# given a list of source URIs1 (e.g. ['www.stern.de', 'www.spiegel.de'])
-
-class NewsDownloader(object):
-    er = EventRegistry(apiKey = "7564c27a-9e81-4f7e-bc65-540e1eb0d9a0")
-
-    def __init__(self, name, source_uris):
-        # input
-        self.name = name
-        self.source_uris = source_uris
-
-        # These 3 functions will be defined below
-        self.art_uris = self._get_article_uris()
-        self.full_articles = self._get_articles()
-        self.save_obj()
-
-    ## Get article URIs
-
-    def _get_article_uris(self):
-        results = []
-        for uri in self.source_uris:
-            # for each source URI in the original list,
-            # set up a query using EventRegistry’s QueryArticles() class:
-            query = QueryArticles(sourceUri=uri)
-            # Only return articles from our source
-            query.setRequestedResult(RequestArticlesUriList())
-            # only give a list of the article URIs:
-            results += NewsDownloader.er.execQuery(query).get("uriList", {}).get("results", [])
-        return results
-
-    ## Get articles
-
-    def _get_articles(self, n_arts=200): # Max of 200 articles returned per call
-        # assert statement is basically a dummy check to make sure the previous step succeeded
-        assert self.art_uris is not None
-
-        art_uri_list = self.art_uris
-        results = []
-        # Take the self.art_uris list and break it into smaller chunks of 200 articles each
-        for i in range(0, len(art_uri_list), n_arts):
-            small_uri_list = art_uri_list[i:i + n_arts]
-            q = QueryArticles.initWithArticleUriList(small_uri_list)
-            q.addRequestedResult(
-                RequestArticlesInfo(
-                    count=n_arts,
-                    returnInfo=ReturnInfo(
-                        articleInfo=ArticleInfoFlags(bodyLen=-1, socialScore = True)
-                    )))
-            results += NewsDownloader.er.execQuery(q)['articles']['results']
-        return results
-
-    ## Save object
-
-    def save_obj(self, obj=None):
-        if obj is None:
-            assert self.full_articles is not None
-            obj = self.full_articles
[…]

### 2017-10-31 paper/R/01_prepare.Rmd
fancy graphs

@@
 df %>%
-  mutate(fb_shares = as.numeric(fb_shares),
-         fb_likes = as.numeric(fb_likes),
-         fb_comments = as.numeric(fb_comments)) -> df
+  mutate(fb_shares = as.integer(fb_shares),
+         fb_likes = as.integer(fb_likes),
+         fb_comments = as.integer(fb_comments)) -> df
 ```
@@
 ```{r}
-df %>% filter(site != "zdf.de") -> df
-
-df$text_lenght <- sapply(gregexpr("\\S+", df$text), length)
+df$text_length <- sapply(gregexpr("\\S+", df$text), length)
 ```

### 2017-10-31 paper/R/01_prepare_eventbride.Rmd
fancy graphs

--- 2017-10-27 paper/R/02_prepare.Rmd
@@
 lapply(libs, library, character.only = TRUE)
-
 ```
@@
 
-load("../output/news_cleaned.Rda")
+df <- read_csv("../data/eventbride/eventbride_okt_18.csv")
 ```
 
-# Pre-Process Text
+# Generate new variables 
+```{r}
+## Extract site
+df$site <- str_extract(df$source, "(?<='uri': ')[A-z][^']*")
 
-```{r}
-df %>%
-  distinct(text, .keep_all = TRUE) -> df
+# Is video
+df$video <- ifelse(grepl("video", df$title, ignore.case = TRUE),1,0)
+
+# number of Facebook shares
+df$fb_shares <- str_extract(df$shares, "(?<='facebook': )[0-9]*")
+df$fb_shares <- ifelse(is.na(df$fb_shares),0, df$fb_shares)
+df$fb_shares <- as.integer(df$fb_shares)
+
+# Text Length
+names(df) <- gsub("body", "text", names(df))
+df$text_length <- sapply(gregexpr("\\S+", df$text), length)
 ```
@@
 ```{r}
-pat <- 'Aus unserem Netzwerk[^"]*'
-btw %>%
+ggplot(df, aes(site, fill=as.factor(isDuplicate))) +
+  geom_bar(alpha=.6) +
+  labs(x="", y="", fill="is Duplicate") +
+  theme(axis.text.x = element_text(angle = 40, hjust = 1))
+```
+
+```{r}
+# Save file
+save(df, file="../output/news_cleaned_eventbride.Rda")
+```
+
+```{r}
+pat <- 'ejf[^"]*'
+df %>%
   filter(grepl(pat, text, perl = TRUE)) %>%
@@
 ```
+
 ```{r}
-as.data.frame(str_match(btw$text, pat)) ->test
+as.data.frame(str_match(df$text, pat)) ->test
 test %>%
@@
 ```
+
+# Pre-Process Text
 
@@
 # Save file
-save(df, file="../output/news_cleaned2.Rda")
+save(df, file="../output/news_cleaned_eventbride.Rda")
 ```
@@
 ```{r}
-save(df, file="../output/news_cleaned2.Rda")
+df -> df2
 ```
 
-## Generate new variables 
 ```{r}
-df$video <- ifelse(grepl("video", df$title, ignore.case = TRUE),1,0)
-df$date <- as.Date(df$date)
+save(df2, file="../output/news_cleaned_eventbride.Rda")
 ```
@@
 ```{r}
-df %>%
-  filter(!site %in% c("ndr.de","wdr.de", "swr.de","tagessschau.de")) %>%
-  filter(grepl("bundestagswahl", text, ignore.case = TRUE)) -> btw
+keeps <- c( "welt.de","spiegel.de","stern.de","focus.de","zeit.de","bild.de" )
 
-btw$ArticleID <- rownames(btw)
+df2 %>%
+  filter(isDuplicate == "False") %>%
+  filter(site %in% keeps) %>%
+  filter(grepl("bundestagswahl", text, ignore.case = TRUE)) -> btw2
 ```
@@
 ```{r}
-save(df, btw, file="../output/news_btw.Rda")
+save(df2, btw2, file="../output/news_btw2.Rda")
 ```

### 2017-10-31 paper/R/02_combine.Rmd
fancy graphs

--- 2017-10-27 paper/R/02_prepare.Rmd
@@
 
-# Load and prepare Dataframe
-
+# Load and prepare Dataframes
 ```{r}
@@
 load("../output/news_cleaned.Rda")
+df2 <- read_csv("../data/eventbride/eventbride_okt_18.csv")
+```
+
+## Generate new variables 
+```{r}
+## Extract site
+df2$site <- str_extract(df2$source, "(?<='uri': ')[A-z][^']*")
+
+# number of Facebook shares
+df2$fb_shares <- str_extract(df2$shares, "(?<='facebook': )[0-9]*")
+df2$fb_shares <- ifelse(is.na(df2$fb_shares),0, df2$fb_shares)
+df2$fb_shares <- as.integer(df2$fb_shares)
+
+# Text Length
+names(df2) <- gsub("body", "text", names(df2))
+df2$text_length <- sapply(gregexpr("\\S+", df2$text), length)
+```
+
+## Reduce Dataframe
+```{r}
+keeps <- c( "welt.de","spiegel.de","stern.de","focus.de","zeit.de","bild.de" )
+
+df %>%
+  filter(site %in% keeps) %>%
+  filter(grepl("bundestagswahl", text, ignore.case = TRUE)) -> btw1
+
+df2 %>%
+  filter(site %in% keeps) %>%
+  filter(grepl("bundestagswahl", text, ignore.case = TRUE)) -> btw2
+```
+
+## Combine Dataframes
+```{r}
+common_cols <- intersect(colnames(btw1), colnames(btw2))
+
+btw <- rbind(
+  btw1[, common_cols], 
+  btw2[, common_cols]
+)
+```
+
+```{r}
+btw$title.text <- paste(btw$title, btw$text, sep = " ")
 ```
@@
 
+## Filtering
 ```{r}
-df %>%
-  distinct(text, .keep_all = TRUE) -> df
+btw %>%
+  # Keep unique observations
+  distinct(title, site, .keep_all = TRUE) %>%
+  # Remove Articles after 10.10.2017
+  filter(date < as.Date("2017-10-10")) -> btw
 ```
@@
 ```
+
 ```{r}
@@
 # apply function to dataframe
-df$text_cleaned <- clean.text(df$text)
+btw$text_cleaned <- clean.text(btw$title.text)
 ```
@@
 ```{r}
-df$text_cleaned <- gsub("[[:punct:]]", " ", df$text_cleaned)
-df$text_cleaned <- gsub("[[:cntrl:]]", " ", df$text_cleaned)
-df$text_cleaned <- gsub("[[:digit:]]", " ", df$text_cleaned)
-df$text_cleaned <- gsub("^[[:space:]]+", " ", df$text_cleaned)
-df$text_cleaned <- gsub("[[:space:]]+$", " ", df$text_cleaned)
-df$text_cleaned <- tolower(df$text_cleaned)
-```
-
-```{r}
-# Save file
-save(df, file="../output/news_cleaned2.Rda")
+btw$text_cleaned <- gsub("[[:punct:]]", " ", btw$text_cleaned)
+btw$text_cleaned <- gsub("[[:cntrl:]]", " ", btw$text_cleaned)
+btw$text_cleaned <- gsub("[[:digit:]]", " ", btw$text_cleaned)
+btw$text_cleaned <- gsub("^[[:space:]]+", " ", btw$text_cleaned)
+btw$text_cleaned <- gsub("[[:space:]]+$", " ", btw$text_cleaned)
+btw$text_cleaned <- tolower(btw$text_cleaned)
 ```
@@
 ```{r}
-df$text_cleaned<- removeWords(df$text_cleaned, stopwords("german"))
+btw$text_cleaned<- removeWords(btw$text_cleaned, stopwords("german"))
 ```
@@
 
-df$text_cleaned<- removeWords(df$text_cleaned, mystopwords$mystopwords)
+btw$text_cleaned<- removeWords(btw$text_cleaned, mystopwords$mystopwords)
+```
+
+## Stemming
+```{r}
+stem_text<- function(text, language = "porter", mc.cores = 1) {
+  # stem each word in a block of text
+  stem_string <- function(str, language) {
+    str <- strsplit(x = str, split = "\\s")
+    str <- wordStem(unlist(str), language = language)
+    str <- paste(str, collapse = " ")
+    return(str)
+  }
+
+  # stem each text block in turn
+  x <- mclapply(X = text, FUN = stem_string, language, mc.cores = mc.cores)
+
+  # return stemed text blocks
+  return(unlist(x))
+}
+
+btw$text_cleaned <- stem_text(btw$text_cleaned)
 ```
@@
 ```{r}
-save(df, file="../output/news_cleaned2.Rda")
+save(btw, file="../output/btw_combined.Rda")
 ```
-
-## Generate new variables 
-```{r}
-df$video <- ifelse(grepl("video", df$title, ignore.case = TRUE),1,0)
-df$date <- as.Date(df$date)
-```
-
-## Reduce Dataframe
-```{r}
-df %>%
-  filter(!site %in% c("ndr.de","wdr.de", "swr.de","tagessschau.de")) %>%
-  filter(grepl("bundestagswahl", text, ignore.case = TRUE)) -> btw
-
-btw$ArticleID <- rownames(btw)
-```
-
-```{r}
-save(df, btw, file="../output/news_btw.Rda")
-```

### 2017-10-31 paper/R/03_topic model.Rmd
fancy graphs

---
title: "News Topic Modeling"
subtitle: ""
author: "Franziska Löw"
date: ""
output: 
  html_document:
    toc: true
    toc_float: true
    theme: "lumen"
    highlight: "tango"
    code_folding: show
    self_contained: true
---

## Introduction

Social networks such as Facebook are becoming more and more important for online news services: an increasing number of their readers access the news pages via links in the networks. Users of Facebook, for example, can use their profile to share links to external websites - such as news portals - with their online friends. This has led to the development of social media into an important generator of traffic on the internet pages. In Germany, 94\% of online shared news articles in 2015 are distributed via Facebook, followed by Twitter with 3.5\% and Google+ with 2.3\% \citep{schiller_development_2016}. The advertising-financed business model of the media houses is based on the premise that users visit their websites in order to achieve high advertising revenues. For this reason, news agencies are particularly interested in finding out which topics are more likely shared on these platforms. \citet{schiller_development_2016} show, that social media users choose a certain site depending on the researched topic. FOCUS Online for example is targeted for articles from politics and business, sports news is more likely to be shared from Bild.de.

While these static resorts give an indication on the content of an article, multiple articles in the same resort probably don't cover the same topics (and are not equally shared). Especially if the articles originate from different news portals. Furthermore, articles can contain more than one topic. We use a structural topic model to reveal the underlying topics of a collection of articles (a corpus), and how the articles exhibit them. We then estimate the effect of topic prevalence on the number of Facebook shares.

## Methodology

Mapping raw text to one or more topics, without having prior knowledge on what those topics are, translates to an unsupervised classification problem on natural language. Within topic models the Latent Dirichlet Allocation (LDA) is a widely used technique, where each document (article) is viewed as a mixture of topics (represented by the document-topic distribution) and each topic is a mixture of unique terms (represented by the topic-term distribution).\cite{blei_latent_2003}

This model views the text generation process as conforming to the following characteristics:

  * A topic is a mixture of words. A topic is comprised of many words, and each word maps to one or more topics.
  * A document (in this case, a news article), is a mixture of topics. Each document can be thought of as containing a proportion of words from each topic.

To "learn" the topic prevalence and the topic-term distribution, collapsed Gibbs sampling\footnote{See Section \ref{section_gibbs} for a non-formal description of the Gibbs sampler} can be used. One of the important considerations of this model is that the number of topics $k$ must be known a-priori.

## Preliminaries

We load libraries needed for this analysis.

```{r Setup}
suppressPackageStartupMessages({
  library(dplyr)       # Data manipulation
  library(stringr)     # String manipulation
  library(lubridate)   # Date and time manipulation
  library(purrr)       # Functional programming
  library(tidyr)       # Reshaping
  library(magrittr)    # Advanced piping
  library(pushoverr)   # Pushover notifications
  library(doMC)        # Parallel Computing
  library(readr)       # Importing data
  library(tibble)      # Better data frames

  library(ggplot2)     # Static data visualization
  library(ggrepel)     # Repel text labels
  library(ggiraph)     # GGplot interactive
  library(scales)      # Scales
  library(viridis)     # Viridis color scales
  library(htmlwidgets) # JS visuliaztions
  library(htmltools)   # Arbitrary html
  library(ggjoy)       # Create joyplots
  library(gganimate)   # Animating ggplots
  library(tweenr)      # Tweening charts

  library(httr)        # HTTP functions
  library(jsonlite)    # JSON parsing

  library(tidytext)    # Tidy text mining
  library(tm)    # Tidy text mining
  library(hunspell)    # Text processing
  library(stringdist)  # String distances
  library(topicmodels) # Topic modelling
  library(proxy)       # Distance measures
  library(SnowballC)   # Stemming
})

# Theming
quartzFonts(
  Roboto = 
    c("Roboto-Light",
      "Roboto-Bold",
      "Roboto-Regular",
      "Roboto-Thin")
)

theme_set(
  theme_bw(base_family = "Roboto", base_size = 14) +
    theme(
      plot.title = element_text(face = "bold", size = 14, 
                                margin = margin(0, 0, 4, 0, "pt")),
      plot.subtitle = element_text(size = 12),
      plot.caption = element_text(size = 6, hjust = 0),
      axis.title = element_text(size = 10),
      panel.border = element_blank()
    )
)

rm(list=ls())
# Functions
source("func/02-topic-modelling-functions.R")

```

```{r caching, echo = FALSE}
load("../output/models/LDAGibbs 40 .Rda")

#load("../output/btw_combined.Rda")
knitr::opts_chunk$set(eval = TRUE, warning = FALSE)

btw$articleID <- rownames(btw)
```

## Pre-processing

### Shaping
```{r}
btw %>% 
  # Tokenize by word
  unnest_tokens(word, text_cleaned, token = "words") ->
  # Assign to variable
  posts_tokenized.dt
```

We remove words that are less than 3 characters long.

```{r Remove short words}

# Remove short words
posts_tokenized.dt %>% 
  filter(str_length(word) >= 3) ->
  posts_tokenized.dt

```

### Filtering and Casting

We summarise the data format into a more compressed form and convert it into a document term matrix.

```{r Term Frequency}

# Summarise
posts_tokenized.dt %>% 
  group_by(articleID, word) %>%
  dplyr::summarise(term_frequency = n()) %>%
  ungroup() ->
  posts_tokenized.dt

```

```{r Cast to DTM, eval=FALSE, include=FALSE}
# Convert to document term matrix
posts_tokenized.dt %>% 
  cast_dtm(articleID, word, term_frequency) ->
  posts_tokenized.dtm
```

## Analysis

### Topic modelling

#### LDA Training

##### Build Corpus
```{r eval=FALSE, include=FALSE}
btw %>%
  filter(nchar(text_cleaned) > 5) -> btw

# Build corpus
df.lda <- Corpus(VectorSource(btw$text_cleaned))
# Create document-term matrix
dtm <- DocumentTermMatrix(df.lda)
# Assign name to docs
rownames(dtm) <- make.unique(btw$title)
```

##### Run LDA using Gibbs sampling

We then train the LDA on the full dataset, with $k = 40$.

```{r eval=FALSE, include=FALSE}
#Set parameters for Gibbs sampling (see https://eight2late.wordpress.com/2015/09/29/a-gentle-introduction-to-topic-modeling-using-r/)
burnin <- 1000
iter <- 1000
keep <- 50

k = 40 # Topics
```

```{r eval=FALSE, include=FALSE}
t1 <- Sys.time()
ldaOut <-LDA(dtm, k, method="Gibbs", control=list(burnin=burnin, iter = iter, keep = keep))
t2 <- Sys.time()
t2 - t1

save(ldaOut, btw, file=paste("../output/models/LDAGibbs",k,".Rda"))
```

Training took 50 minutes on the full dataset. We extract the word-topic probabilities, and the document-topic probabilities produced by the model.

alternatively...
```{r eval=FALSE, include=FALSE}
# Train the LDA model
LDA(
  x       = posts_tokenized.dtm,
  k       = 40,
  method  = "Gibbs",
  control = list(seed = 7292)
) -> posts.lda
```

#### Topic Labeling

```{r Extract wtp and dtp}

# Word-topic probabilities
ldaOut %>% tidy("beta") -> posts.wtp

# Document-topic probabilities
ldaOut %>% tidy("gamma") -> posts.dtp

```

We can then assess the word-topic probabilities in order to get an idea of the topic that is most.

Since we have over 30,000 unique terms in the corpus, we need to extract the top few words that most uniquely define each topic, so that we can more easily visualize and label them. We use the measure of relevance defined by Sievert and Shirley (2014)^[[Sievert and Shirley (2014). LDAvis: A method for visualizing and interpreting topics. *Stanford University.*](http://nlp.stanford.edu/events/illvi2014/papers/sievert-illvi2014.pdf)]. Relevance of term $w$ to topic $k$ given a weight parameter $\lambda$ between 0 and 1 $r(w, k | \lambda)$ is computed as:

$$
r(w, k | \lambda) = \lambda\log(\phi_{kw}) + (1-\lambda)\log(\frac{\phi_{kw}}{p_w})
$$

where $\phi_{kw}$ is the probability of term $w$ for topic $k$, and $p_w$ is the empirical probability of the word in the corpus. $\lambda$ can be thought of as a weighting term between ranking by the probability of that word within the topic, and ranking by the lift over the overall probability in the corpus.

In user studies, Sievert and Shirley (2004) found that a lambda value of 0.6 as an optimal value for allowing humans to identify the topics associated with the top words ranked by relevance. We use this same value for lambda.

```{r Compute relevance}

posts.wtp %>%
  # Compute lambda and phi_kw
  mutate(lambda = 0.6, phi_kw = beta) %>% 
  # Compute and join the p_w
  left_join(
    posts_tokenized.dt %>%
      group_by(word) %>% 
      dplyr::summarise(frequency = sum(term_frequency)) %>% 
      ungroup() %>% 
      mutate(p_w = frequency/sum(frequency)) %>% 
      select(-frequency),
    by = c("term" = "word")
  ) %>%
  # Compute the relevance
  mutate(relevance = lambda * log(phi_kw) + (1 - lambda) * log(phi_kw/p_w)) ->
  word_relevance.dt

```

We take a look at samples of articles labeled with the topics and the most relevant words that use them, and label them according to the prevalent theme. These are recorded in a csv file and loaded in:

```{r Loading topic mappings}
### Most likely Topics per Article

# The topics function from the package is used to extract the most likely topic for each document 
btw.topics <- topics(ldaOut, 2)

# Create Dataframe
doctopics.df <- as.data.frame(t(btw.topics))

doctopics.df %>%
  transmute(title = rownames(.),
            topic = V1) -> doctopics.df

doctopics.df$articleID <- as.integer(rownames(doctopics.df))

# Add Topic to origian DF
topics_mapping.dt <- btw %>%
  mutate(articleID = as.integer(articleID)) %>%
  inner_join(.,doctopics.df, by="articleID") %>%

  group_by(topic) %>%
  slice(1) %>%
  select(topic, title.text, articleID) 
```
### Create Topic Labels
```{r}
## Return the top 30 terms.
btw.terms <- as.data.frame(terms(ldaOut, 30), stringAsFactors = FALSE)

topicTerms <- btw.terms %>% gather(Topic)
topicTerms <- cbind(topicTerms, Rank = rep(1:30))
topicTerms <- topicTerms %>% filter(Rank < 5)

topicTerms <- topicTerms %>% mutate(topic = stringr::word(Topic, 2))
topicTerms$topic <- as.numeric(topicTerms$topic)

topicLabel <- data.frame()
for (i in 1:40){
  z <- dplyr::filter(topicTerms, topic==i)
  l <- as.data.frame(paste(z[1,2], z[2,2], z[3,2], z[4,2], sep = " "), stringAsFactors = FALSE)
  topicLabel <- rbind(topicLabel, l)
}
colnames(topicLabel) <- c("topic_name")
topicLabel$topic <- as.integer(rownames(topicLabel))
```

```{r}
## Combine with Topic label
topics_mapping.dt %>%
  left_join(., topicLabel, by="topic") -> topics_mapping.dt
```

We extract the top 30 most relevant words and plot them as follows:

  1. Compute the Jensen-Shannon divergence between each of the topics according to the differences in their word-topic probabilities and construct a distance matrix,
  2. Apply principal coordinates analysis in order to project the distance matrix down to two dimensions.
  3. Plot each word near the center of the topic mass and repel them from each other.

```{r eval=FALSE, include=FALSE}
posts.wtp %>% 
  # Compute Jensen-Shannon
  computeJensenShannonPCA() %>% {

    # Assign positions to top 30 most relevant words
    left_join(
      .,
      word_relevance.dt %>% 
        group_by(topic) %>% 
        top_n(30, relevance) %>% 
        ungroup(),
      by = "topic"
    ) -> topic_labelling_top30words.dt

    # Assign positions to topic labels
    left_join(
      .,
      topics_mapping.dt,
      by = "topic"
    ) -> topic_labelling_topics.dt

    ggsave(
      plot = {
        topic_labelling_top30words.dt %>% 
          ggplot(aes(x = x, y = y)) +
          geom_text_repel(
            aes(label = term, 
                color = factor(topic, levels = 1:40), 
                size = phi_kw * p_w), 
            lineheight = 0.6, 
            segment.size = NA,
            box.padding = unit(0, "lines"),
            force = 0.05,
            family = "Roboto"
          ) +
          geom_text_repel(
            data = topic_labelling_topics.dt,
            aes(label = str_wrap(topic_name, 15),
                color = factor(topic, levels = 1:40)),
            size = 2.25, lineheight = 0.7,
            segment.size = 0.5, alpha = 0.7,
            family = "Roboto", fontface = 2,
            force = 0.3
          ) +
          scale_size_continuous(range = c(1, 4)) +
          scale_color_manual(
            values = rainbow(40) %>% 
              adjustcolor(red.f = 0.6, green.f = 0.6, blue.f = 0.6)
          ) +
          theme(
            axis.title = element_blank(),
            axis.text  = element_blank(),
            axis.ticks = element_blank(),
            panel.grid = element_blank(),
            panel.border = element_blank(),
            plot.background = element_rect(fill = "#FAFAFA"),
            legend.position = "none"
          ) +
          labs(
            title    = "GERMAN NEWS LANDSCAPE",
            subtitle = "Online News Articles about Federal Elections June-Oct 2017",
            caption = 
"DATA SOURCE: Webhose.io, Eventbride.com

CHART NOTES:
  1. Topics were derived through Latent Dirichlet Allocation (LDA) with 40 topics
  2. For each topic, the top 30 words in terms of relevance as defined in Sievert and Shirley (2014) are displayed
  3. The centers of each topic mass were determined by applying principal components analysis to the distance matrix, with the Jensen-Shannon divergence as the distance measure. 
      This layout is intended to display the degree of semantic distance.
"
          )
      },
      filename = "../figs/01-news-landscape-map.png",
      device = "png",
      dpi = 600
    )

  }

```

![Facebook News Map](../figs/01-news-landscape-map.png)

Now that we have labelled each topic, we produce sample documents classified to that topic for reference. We produce a random sample of 10 posts from the 300 highest probability fits per topic.

```{r Document classification}

set.seed(9272)
posts.dtp %>% 
  group_by(title = document) %>% 
  summarise(topic = min(topic[gamma == max(gamma)]), gamma = max(gamma)) %>% 
  ungroup() %>% 
  inner_join(btw %>% select(title, articleID), by = "title") %>% 
  inner_join(topics_mapping.dt, by = "topic") %>% 
  mutate(topic_title = 
           paste0("Topic ", formatC(topic, flag = "0", width = 2), 
                  " - ", topic_name)) %>% 
  group_by(topic_name) %>% 
  top_n(300, gamma) %>%
  sample_n(10) %>% 
  mutate(row = row_number()) %>% 
  ungroup() ->
  posts_classification.sdt

```

We produce a chart that shows this in a presentable manner.

```{r Document classification chart, eval=FALSE, include=FALSE}

ggsave(
  plot = {
    posts_classification.sdt %>% 
      ggplot(aes(x = 0, y = row, color = factor(topic, levels = 1:40))) +
      facet_wrap(~topic_title, ncol = 5) +
      geom_text(
        aes(label = title),
        size = 2, hjust = 0, family = "Roboto"
      ) +
      geom_point(aes(x = -0.025), size = 0.5) +
      scale_x_continuous(limits = c(-0.05, 1), expand = c(0, 0)) +
      scale_color_manual(
        values = rainbow(40) %>% 
          adjustcolor(red.f = 0.6, green.f = 0.6, blue.f = 0.6)
      ) +
      theme(
        axis.title       = element_blank(),
        axis.text        = element_blank(),
        axis.ticks       = element_blank(),
        panel.grid       = element_blank(),
        strip.background = element_blank(),
        panel.border     = element_blank(),
        strip.text       = element_text(face = "bold", hjust = 0, size = 6),
        plot.background  = element_rect(fill = "#FAFAFA"),
        legend.position  = "none"
      ) +
      labs(
        title    = "GERMAN NEWS LANDSCAPE",
        subtitle = "Sample online news articles in the year 2017",
        caption  = 
"DATA SOURCE: Webhose.io, Eventbride.com

CHART NOTES:
  1. Topics were derived through Latent Dirichlet Allocation (LDA) with 40 topics
  2. Documents were classified according to the topic that has the highest probability
"
      )
  },
  device = "png",
  filename = "../figs/02-topic-classification-sample.png",
  dpi = 600, height = 10, width = 16
)

```

![Facebook news samples](../figs/02-topic-classification-sample.png)

### Topic Trends

We classify each document based on which topic has the highest probability. If one or more topics have equal probability, then the count is assigned equally to all the topics.

```{r Topic classification}

posts.dtp %>% 
  group_by(document) %>% 
  filter(gamma == max(gamma)) %>% 
  mutate(allocation = 1/n()) %>% 
  ungroup() ->
  posts_classification.dt

```

We construct a chart that allows us to explore topic trends, both in terms of document count and the total number of reactions on the articles of that particular topic.

```{r Data for topic trends chart}

set.seed(7292)
posts_classification.dt %>% 
  # Add post information
  inner_join(
    btw %>% 
      select(document = title, date, 
             title, articleID) %>% 
      mutate(post_period = 
               date %>% 
               with_tz("Europe/Paris") %>% 
               floor_date("week")),
    by = "document"
  ) %>%
  # Add topic information
  left_join(topics_mapping.dt, by = "topic") %>%
  # Summarise into tidy dataframe
  group_by(post_period, topic_name) %>% 
  summarise(
    articles = sum(allocation),
    sample_articles = 
      paste0("<li>", sample(document, 3, replace = TRUE ), "</li>", collapse = "<br>")
  ) %>% 
  ungroup() %>% 
  mutate(
    tooltip_text = 
      paste0(
        "<b>", topic_name, "</b> in period of <b>", post_period, "</b><br>",
        "<b>Number of Articles:</b> ", comma(round(articles, 0)), "<br>",
        "<b>Sample Articles:</b><br><ul>", sample_articles, "</ul>"
      )
  ) %>% 
  # Mark peaks 
  group_by(topic_name) %>% 
  mutate_at(
    vars(articles), 
    funs(mean = mean(.), sd = sd(.), zscore = (. - mean(.))/sd(.))
  ) %>% 
  ungroup() %>% 
  mutate_at(
    vars(ends_with("zscore")),
    funs(peak = . >	1.96)
  ) %>% 
  mutate(tooltip_text = str_replace_all(tooltip_text, "'", "")) ->
  chart_topic_trends.dt
```

```{r Topic trends chart, eval = TRUE}

{
  chart_topic_trends.dt %>% 
    ggplot(
      aes(
        x = post_period, 
        y = factor(
          topic_name, 
          chart_topic_trends.dt %>% 
            group_by(topic_name) %>% 
            summarise(post_period = mean(post_period[peak], na.rm = TRUE)) %>% 
            ungroup() %>% 
            arrange(desc(post_period)) %$%
            unique(topic_name)
        )
      )
    ) +
    geom_tile_interactive(aes(tooltip = tooltip_text, fill = log(articles))) +
    geom_point_interactive(
      mapping = aes(tooltip = tooltip_text),
      data = chart_topic_trends.dt %>% filter(peak),
      color = "red"
    ) +
    scale_fill_viridis(
      labels = function(x) comma(round(exp(x))), 
      name = "Number of Articles",
      option = "plasma"
    ) +
    scale_x_datetime(expand = c(0, 0)) +
    labs(
      title = "ZEITGEIST", 
      subtitle = "Topic distribution of news articles over time, 2017\n(Hover over each tile to see sample articles)",
      caption = "
DATA SOURCE: Webhose.io, Eventbride.com

CHART NOTES:
  1. Red dots indicate weeks where the number of articles exceeds 1.96 SD above mean for that topic
  2. Hover over each tile to see infomration and to see sample articles
  3. Topics were derived through Latent Dirichlet Allocation (LDA) with 40 topics
  4. Articles were classified according to the topic that has the highest probability

TROY JAMES PALANCA | TJPALANCA.COM
      "
    ) +
    theme(
      legend.position   = "bottom",
      legend.key.width  = unit(0.1, "npc"),
      legend.background = element_rect("#fafafa"),
      plot.background   = element_rect("#fafafa", "#fafafa"),
      plot.title        = element_text(size = 18),
      plot.subtitle     = element_text(size = 8),
      plot.caption      = element_text(size = 7),
      panel.grid        = element_blank(),
      panel.background  = element_rect("#fafafa"),
      axis.title        = element_blank(),
      axis.ticks        = element_blank(),
      axis.text.y       = element_text(size = 8)
    ) 
} %>% 
  ggiraph(
    ggobj = .,
    # width_svg  = 8,
    # height_svg = 7,
    width = 1,
    tooltip_extra_css = "
    font-family: Roboto; 
    background-color: #000; 
    color: #fff; font-size: 10px;
    padding: 5px;"
  ) %>% 
  prependContent(
    tags$link(
      href = "https://fonts.googleapis.com/css?family=Roboto:400,700", 
      rel = "stylesheet"
    )
  ) -> chart_topic_trends.wdgt

saveWidget(
  widget = chart_topic_trends.wdgt,
  file = "../figs/03-topic-trends.html",
  selfcontained = FALSE,
  libdir = "../figs/js",
  background = "#fafafa"
)

chart_topic_trends.wdgt

```

```{r Topic trends line chart, eval = TRUE}

{ 
  chart_topic_trends.dt %>%
  select(post_period, topic_name, articles) %>% 
  mutate(data_id = row_number() %>% as.character()) %>% 
  ggplot(aes(x = post_period, y = articles)) +
  geom_path_interactive(
    aes(group = topic_name, 
        tooltip = str_replace_all(topic_name, "'", ""),
        data_id = data_id), 
    color = "gray"
  ) +
    scale_y_continuous(labels = comma) +
    labs(
      title = "PEAKS AND TROUGHS",
      subtitle = "Hover over each line to see the trend of news articles for a particular topic",
      y = "Number of Articles"
    ) +
    theme(
      plot.background   = element_rect("#fafafa", "#fafafa"),
      plot.title        = element_text(size = 18),
      plot.subtitle     = element_text(size = 8),
      plot.caption      = element_text(size = 7),
      panel.grid        = element_blank(),
      panel.background  = element_rect("#fafafa"),
      axis.title.x      = element_blank(),
      axis.text.y       = element_text(size = 8)
    )
} %>% 
  ggiraph(
    ggobj = .,
    hover_css = "stroke: red; stroke-width: 3px;",
    width = 1,
    width_svg = 8,
    height_svg = 4,
    tooltip_extra_css = "
    font-family: Roboto; 
    background-color: #000; 
    color: #fff; font-size: 10px;
    padding: 5px;"
  ) %>% 
  prependContent(
    tags$link(
      href = "https://fonts.googleapis.com/css?family=Roboto:400,700", 
      rel = "stylesheet"
    )
  ) -> chart_trends_line.wdgt

saveWidget(
  widget = chart_trends_line.wdgt,
  file = "../figs/06-topic-trends-line.html",
  selfcontained = FALSE,
  libdir = "../figs/js",
  background = "#fafafa"
)

chart_trends_line.wdgt

```

```{r Trend to reactions, eval = TRUE}

# Prepare dataset for joy plot
posts_classification.dt %>% 
  inner_join(
    btw %>% 
      select(
        document = title, 
        news_page = site, 
        title, 
        date
      ),
    by = "document"
  ) %>% 
  inner_join(topics_mapping.dt, by = "topic") %>% 
  inner_join(
    btw %>% 
      group_by(document = title) %>%
      summarise(reactions = sum(fb_shares)) %>%
      ungroup(),
    by = "document"
  ) %>%
  group_by(
    topic_name, 
    # 8 hour time difference (Manila)
    week = floor_date(date, "week")
  ) %>% 
  summarise(
    num_articles  = sum(allocation),
    num_reactions = sum(reactions * allocation)
  ) %>%
  #mutate(peak = week[num_articles == max(num_articles)]) %>%
  ungroup() %>%
  arrange(week) %>%
  mutate(
    topic_name = factor(topic_name, levels = rev(unique(topic_name))),
    # ID needed for linking back information after tweening frames
    id = as.character(row_number()),
    # Maximum height for ridgeline is 9
    articles_height = num_articles/max(num_articles) * 9,
    reactions_height = num_reactions/max(num_reactions) * 9
  ) ->
  posts_time_trend.dt

# Prepare animated dataset
bind_rows(
  # Articles
  posts_time_trend.dt %>% 
    transmute(id, time = 0,  ht = articles_height , op = 0),
  # Reactions
  posts_time_trend.dt %>% 
    transmute(id, time = 10, ht = reactions_height, op = 1),
  # Return to articles
  posts_time_trend.dt %>% 
    transmute(id, time = 20, ht = articles_height , op = 0)
) %>%
  # Add cubic easing
  mutate(ease = "cubic-in-out") %>%
  tween_elements("time", "id", "ease") %>%
  # Add back the topic name and week
  inner_join(
    posts_time_trend.dt %>% select(topic_name, week, id), 
    by = c(".group" = "id")
  ) ->
  posts_time_trend.adt

# Create labels above the chart (what news outlets post vs what we react to)
posts_time_trend.adt %>%
  group_by(.frame) %>%
  summarise(
    opacity    = mean(op),
    range_week = max(week) - min(week),
    min_week   = min(week),
    num_topics = n_distinct(topic_name)
  ) %>% 
  ungroup() -> 
  posts_time_trend_labels.adt

```

```{r Trend to reactions plot, eval = TRUE}

# Create animated pot
posts_time_trend.adt %>%
  ggplot(aes(x = week, y = topic_name, height = ht, 
             fill = topic_name, frame = .frame)) +
  geom_ridgeline(color = NA, alpha = 0.5) +
  geom_text(
    data = posts_time_trend_labels.adt,
    aes(x = min_week + 0.25 * range_week, 
        y = num_topics + 3.5, 
        alpha = 1 - opacity, 
        frame = .frame),
    label = "What news outlets publish", color = "forestgreen",
    family = "Roboto", fontface = "bold", size = 9,
    inherit.aes = FALSE
  ) +
  geom_text(
    data = posts_time_trend_labels.adt,
    aes(x = min_week + 0.75 * range_week, 
        y = num_topics + 3.5, 
        alpha = opacity, 
        frame = .frame),
    label = "What we react to", color = "firebrick",
    family = "Roboto", fontface = "bold", size = 9,
    inherit.aes = FALSE
  ) +
  geom_text(
    data = posts_time_trend_labels.adt,
    aes(x = min_week + 0.55 * range_week, 
        y = num_topics + 3.5, 
        frame = .frame),
    label = "VS",
    family = "Roboto", fontface = "bold", size = 7,
    inherit.aes = FALSE
  ) +
  scale_x_datetime(expand = c(0, 0)) +
  theme(
    legend.position = "none",
    panel.border    = element_blank(),
    axis.title      = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    plot.caption      = element_text(size = 9)
  ) + 
  labs(
    caption = "
DATA SOURCE: Webhose.io, Eventbride.com
CHART NOTE: Topics were derived through Latent Dirichlet Allocation (LDA) with 40 topics for online news articles in 2017 containing the term 'Bundestagswahl'
    "
  ) ->
  posts_time_trend.agg

gganimate(
  p = posts_time_trend.agg,
  filename = "../figs/09-reactions-vs-articles.gif",
  title_frame = FALSE,
  interval = 1/10,
  ani.width = 900,
  ani.height = 600
)

```

![Articles to Reactions](../figs/09-reactions-vs-articles.gif)

### Topic Distribution by News Page

#### Distribution

A common accusation leveled against traditional news media is the amount of bias in reporting various topics. We try to explore the topic distribution of news articles.

```{r Data for topic distribution chart}

set.seed(7292)
posts_classification.dt %>% 
  inner_join(
    btw %>% select(document = title, news_page = site, title),
    by = "document"
  ) %>%
  inner_join(topics_mapping.dt, by = "topic") %>% 
  group_by(news_page, topic_name) %>%
  summarise(
    articles = sum(allocation),
    sample_articles = 
      paste0(
        "<li>", sample(document, pmin(3, length(document))), "</li>",
        collapse = "<br>"
      )
  ) %>%
  ungroup() %>% 
  group_by(news_page) %>% 
  mutate(perc_articles = articles/sum(articles)) %>% 
  ungroup() %>%
  # left_join(
  #   top_100_fbpages.dt %>% select(news_page = page_name, page_title), 
  #   by = "news_page"
  # ) %>% 
  mutate(
    tooltip_text = 
      paste0(
        "<b>", comma(round(articles, 0)), " (", percent(perc_articles), 
        ") </b> of articles from <b>", news_page, 
        "</b> fall under <b>", topic_name, "</b><br><br>Sample Articles:<br><ul>",
        sample_articles, "</ul>"
      ) %>% str_replace_all("'", "")
  ) ->
  news_page_distribution.dt
```

```{r Topic distribution chart, eval = TRUE}
{
  news_page_distribution.dt %>% 
    ggplot(aes(x = news_page, y = perc_articles, fill = topic_name)) +
    geom_bar_interactive(
      aes(tooltip = tooltip_text),
      position = position_stack(), 
      stat = "identity", color = "darkgray"
    ) +
    scale_y_continuous(
      name = "Percent of Articles", 
      labels = percent,
      expand = c(0, 0)
    ) +
    theme(
      legend.position = "none",
      axis.title.y = element_blank(),
      legend.background = element_rect("#fafafa"),
      plot.background   = element_rect("#fafafa", "#fafafa"),
      plot.subtitle     = element_text(size = 8),
      plot.caption      = element_text(size = 7),
      plot.title        = element_text(size = 18)
    ) +
    coord_flip() +
    scale_fill_viridis(discrete = TRUE) +
    labs(
      title = "BIAS AND BALANCE",
      subtitle = "Topic distribution of online news articles per news page, 2017\n(Hover over each bar to see the topic and sample articles)",
      caption = "
DATA SOURCE: Facebook Graph API

CHART NOTES:
  1. The news pages are arranged in descending order in terms of number of articles
  2. Topics were derived through Latent Dirichlet Allocation (LDA) with 40 topics
  3. Articles were classified according to the topic that has the highest probability
      "
    )
} %>% 
  ggiraph(
    ggobj = .,
    width_svg = 12,
    height_svg = 8,
    width = 1,
    tooltip_extra_css = "
    font-family: Roboto; 
    background-color: #000; 
    color: #fff; font-size: 10px;
    padding: 5px;"
  ) %>% 
  prependContent(
    tags$link(
      href = "https://fonts.googleapis.com/css?family=Roboto:400,700", 
      rel = "stylesheet"
    )
  ) -> chart_topic_distribution.wdgt

saveWidget(
  widget = chart_topic_distribution.wdgt,
  file = "../figs/04-topic-distribution-pages.html",
  selfcontained = FALSE,
  libdir = "../figs/js",
  background = "#fafafa"
)

chart_topic_distribution.wdgt

```

#### Topic Concentration

A common criticism leveled against news media sites is that there is undue emphasis on a particular topic. One way to measure concentration across different topics is the Herfindahl-Hirschman Index (HHI) which is simply $\Sigma_n{s^2}$ where $s$ is the share of each topic.

```{r Topic concentration chart, eval = TRUE}

{
  news_page_distribution.dt %>% 
    group_by(news_page) %>% 
    arrange(desc(articles)) %>% 
    summarise(
      hh_index  = sum(perc_articles ^ 2),
      t3_topics = paste0(topic_name %>% head(3), collapse = "<br>")
    ) %>% 
    ungroup() %>% 
    arrange(hh_index) %>% 
    mutate(news_page = factor(news_page, unique(news_page))) %>% 
    ggplot(aes(x = news_page, y = hh_index * 100)) +
    geom_bar_interactive(
      aes(
        tooltip = 
          paste0("<b>Top Topics:</b><br>", t3_topics) %>% 
          str_replace_all("'", "")
      ),
      stat = "identity", 
      fill = c("#008B45")
    ) +
    geom_text(aes(label = comma(round(hh_index * 100, 1))), hjust = 1.5, 
              color = "white", family = "Roboto") +
    scale_y_log10(
      name = "Herfindahl-Hirschman Index (HHI)\n(100 = most concentrated)",
      expand = c(0, 0)
    ) +
    labs(
      title = "TOPIC CONCENTRATION OF PHILIPPINE NEWS PAGES",
      subtitle = "Herfindahl-Hirschman Index (HHI)",
      caption = "
DATA SOURCE: Facebook Graph API

CHART NOTES:
  1. Hover over each tile to see infomration and to see top topics
  2. Topics were derived through Latent Dirichlet Allocation (LDA) with 40 topics
  3. Articles were classified according to the topic that has the highest probability

TROY JAMES PALANCA | TJPALANCA.COM
      "
    ) +
    coord_flip() +
    theme(
      axis.title.y       = element_blank(),
      panel.grid.major.y = element_blank(),
      plot.background   = element_rect("#fafafa", "#fafafa"),
      plot.subtitle      = element_text(size = 10),
      plot.caption       = element_text(size = 8),
      plot.title         = element_text(size = 16)
    )
} %>% 
  ggiraph(
    ggobj = .,
    width_svg = 10,
    height_svg = 8,
    width = 1,
    tooltip_extra_css = "
    font-family: Roboto; 
    background-color: #000; 
    color: #fff; font-size: 16px;
    padding: 5px;"
  ) %>% 
  prependContent(
    tags$link(
      href = "https://fonts.googleapis.com/css?family=Roboto:400,700", 
      rel = "stylesheet"
    )
  ) -> chart_topic_concentration.wdgt

saveWidget(
  widget = chart_topic_concentration.wdgt,
  file = "../figs/05-topic-concentration.html",
  selfcontained = FALSE,
  libdir = "../figs/js",
  background = "#fafafa"
)

chart_topic_concentration.wdgt

```

### 2017-10-31 paper/R/04_paper.Rmd
fancy graphs

@@
           "plyr","dplyr","class","knitr","kableExtra","cldr","data.table",
-          "htmlTable","ggplot2","gridExtra","jsonlite","stringr","scales","rjson")
+          "htmlTable","ggplot2","ggthemes","stringr","scales","rjson")
 lapply(libs, library, character.only = TRUE)
@@
 
-load("../output/news_btw.Rda")
-
-df$date <- as.Date(df$date)
+load("../output/btw_combined.Rda")
 ```
 
-```{r, include=FALSE}
-df %>%
-  #filter(fb_shares > 0) %>%
-  filter(!site %in% c("ndr.de","wdr.de","swr.de","tagesschau.de")) %>%
-  filter(grepl("bundestagswahl", text_cleaned)) -> btw
+To explore the effect of topic prevalence of an article on the times this article is shared on Facebook, we analyze a sample of 6578 news articles containing the term "Bundestagswahl" (Federal Election) dated from 01.06.2017 to 10.10.2017\footnote{German federal elections took place on 24th of September 2017.} and originated from seven different german news sources.\footnote{Bild.de, Focus.de, Spiegel.de, Stern.de, Welt.de, Zeit.de} For each document in our sample, we observe the day it was written, the number of shares on Facebook and the newswire service publishing the report.
+We include the month the document was writte and the news agency as covariates on topical prevalence.
+We also include news agency as a covariate affecting topical content to estimate how topics are discussed in different ways by different news agencies \citep{roberts_model_2016}.
+To determine the number of topics, we use a cross-validation scheme and maximize topics' coherence while changing the number of topics \citep{airoldi_reconceptualizing_2010}.
 
-btw 
+Figure -- shows the number of articles by news agency and the how many of these articles were shared on Facebook.
+
+```{r echo=FALSE}
+btw$shared <- ifelse(btw$fb_shares == 0, "0", NA)
+btw$shared <- ifelse(btw$fb_shares > 0 | btw$fb_shares >= 100, "0-100", btw$shared)
+btw$shared <- ifelse(btw$fb_shares > 100, "> 100", btw$shared)
+
+btw %>%
+  ggplot(aes(site, fill=shared)) +
+  geom_bar(alpha = .9) +
+  labs(x="", y="Count") +
+  scale_fill_ptol("Shared on\n Facebook") +
+  theme_minimal()
 ```
 
-To explore the effect of topic prevalence of an article on the times this article is shared on Facebook, we analyze a sample of 1768 news articles containing the term "Bundestagswahl" (Federal Election) dated from 01.06.2017 to 30.09.2017\footnote{German federal elections took place on 24th of September 2017.} and originated from seven different german news sources.\footnote{Bild.de, Focus.de, Handelsblatt.com, Spiegel.de, Stern.de, Tagesschau.de, Welt.de, Zeit.de} For each document in our sample, we observe the day it was written, the number of shares on Facebook and the newswire service publishing the report.
-We include the news agency as covariates on topical prevalence.
-We also include news agency as a covariate affecting topical content to estimate how topics are discussed in different ways by different news agencies.
-
-Figure -- shows the total sum of all Facebook S, that most of the documents in our corpus
-
-```{r echo=FALSE}
+```{r}
 btw %>%
-  filter(!grepl("video", title, ignore.case = TRUE)) %>%
-  ggplot(aes(x=as.factor(site), y=fb_shares)) +
-  stat_summary(fun.y="sum", geom="bar", fill = "blue", alpha = .5) +
-  labs(title = "") +
-  labs(x="", y="Sum of Facebook Shares") +
-  theme(axis.text.x = element_text(angle = 40, hjust = 1))
+  filter(site=="zeit.de") %>%
+  select(title) %>%
+  .[2,]
 ```

### 2017-10-31 paper/R/06_explore_LDA.Rmd
fancy graphs

@@
 
-load(file ="../output/models/LDAGibbs 50 .Rda")
+load(file ="../output/models/LDAGibbs 40 .Rda")
 ```
@@
 doctopics.df %>%
-  transmute(ArticleID = rownames(.),
-            Topic1 = V1,
+  transmute(title = rownames(.),
+            topic1 = V1,
             Topic2 = V2,
@@
 
-doctopics.df$ArticleID <- as.integer(doctopics.df$ArticleID)
+doctopics.df$ArticleID <- as.integer(rownames(doctopics.df))
 
 # Add Topic to origian DF
-btw <- btw %>%
+btw1 <- btw %>%
   mutate(ArticleID = as.integer(ArticleID)) %>%
@@
 ```{r}
+## Return the top 30 terms.
+btw.terms <- as.data.frame(terms(ldaOut, 30), stringAsFactors = FALSE)
+
 topicTerms <- btw.terms %>% gather(Topic)
@@
 
-topicTerms <- topicTerms %>% mutate(Topic = stringr::word(Topic, 2))
-topicTerms$Topic <- as.numeric(topicTerms$Topic)
+topicTerms <- topicTerms %>% mutate(topic = stringr::word(Topic, 2))
+topicTerms$topic <- as.numeric(topicTerms$topic)
 
 topicLabel <- data.frame()
-for (i in 1:50){
-  z <- dplyr::filter(topicTerms, Topic==i)
+for (i in 1:40){
+  z <- dplyr::filter(topicTerms, topic==i)
   l <- as.data.frame(paste(z[1,2], z[2,2], z[3,2], z[4,2], sep = " "), stringAsFactors = FALSE)
@@
 colnames(topicLabel) <- c("Label")
-
-topicLabel
+topicLabel$topic <- rownames(topicLabel)
 ```
@@
 theta <- as.data.frame(posterior(ldaOut)$topics)
-head(theta)
+gamma <- as.data.frame(posterior(ldaOut)$terms)
 ```

### 2017-10-31 paper/R/07_stm.Rmd
fancy graphs

--- 2017-10-27 paper/R/06_stm.Rmd
@@
 libs <- c("tidytext","tidyr","readr","lubridate","tm","stm","RColorBrewer","topicmodels",
-          "plyr","dplyr","class","knitr","kableExtra","cldr","data.table",
+          "dplyr","class","knitr","kableExtra","cldr","data.table",
           "htmlTable","ggplot2","gridExtra","jsonlite","stringr","scales","rjson")
@@
 
-load("../output/news_cleaned2.Rda")
-
-df$date <- as.Date(df$date)
-
-#col <- brewer.pal(12, name = "Paired")
+load("../output/btw_combined.Rda")
 ```
 
-## Reduce Dataframe
 ```{r}
-df %>%
-  filter(fb_shares > 0) %>%
-  filter(!site %in% c("ndr.de","wdr.de")) %>%
-  filter(grepl("bundestagswahl", text_cleaned)) -> btw
-
-btw$ArticleID <- rownames(btw)
+btw$month <- month(btw$date)
 ```
@@
 # Process data
-processed <- textProcessor(btw$text_cleaned, metadata = btw[,c("date","site","text_cleaned","text")],
+processed <- textProcessor(btw$text_cleaned, metadata = btw[,c("date","month","site","text_cleaned","text")],
                            wordLengths = c(2,Inf),
@@
 ```{r}
-k = 50 # Topics
+k = 40 # Topics
 
@@
            K=k, 
-           prevalence = ~site, 
+           prevalence = ~site+s(month), 
            content = ~site, 

### 2017-10-31 paper/R/backup.Rmd
fancy graphs

---
title: "Topic Modeling of News"
author: "Franziska Löw"
date: "`r format(Sys.Date())`"
output: github_document
---

```{r, include=FALSE}
# load the packages
libs <- c("tidytext","tidyr","readr","lubridate","tm","stm","RColorBrewer",
          "plyr","dplyr","class","knitr","kableExtra","cldr","data.table",
          "htmlTable","ggplot2","gridExtra","jsonlite","stringr","scales","rjson")
lapply(libs, library, character.only = TRUE)
```

## Load Data
```{r, include=FALSE}
#Load Data
rm(list = ls())

load("../output/news_btw.Rda")
load("../output/news_btw2.Rda")
```

```{r}
common_cols <- intersect(colnames(btw1), colnames(btw2))

btw <- rbind(
  btw1[, common_cols], 
  btw2[, common_cols]
)
```

## Remove Articles after 10.10.2017
```{r}
btw %>%
  filter(date < as.Date("2017-10-10")) -> btw
```

## Generate new variables
```{r}
btw$video <- ifelse(grepl("video", btw$title, ignore.case = TRUE), 1,0)
```

## Save data
```{r}
save(btw, file="../output/btw_combined.Rda")
```

```{r}
ggplot(btw, aes(site)) + 
  geom_bar()
```

```{r}
btw %>%
  filter(site == "stern.de") %>%
  arrange(desc(fb_shares)) %>%
  select(title, fb_shares) %>%
  .[1:100,]
```

```{r}
ggplot(btw, aes(date, fill=site)) +
  geom_bar()
```

## Summary Stats
```{r}
df %>%
  group_by(site) %>%
  summarise(obs = n(),
    fb_shares.mean = mean(fb_shares),
            fb_shares.max = max(fb_shares),
            text_length.mean = mean(text_lenght),
            text_length.max = max(text_lenght)) %>%
  htmlTable(align = "l")
```

### Text Length
```{r}
ggplot(btw, aes(x=as.factor(site), y=text_length)) +
  stat_summary(fun.y="median", geom="bar", fill = "blue", alpha = .5) +
  labs(title = "") +
  labs(x="", y="Median Text Length") +
  theme(axis.text.x = element_text(angle = 40, hjust = 1))
```

### Facebook Likes
```{r}
ggplot(btw, aes(x=as.factor(site), y=fb_shares)) +
  stat_summary(fun.y="median", geom="bar", fill = "blue", alpha = .5) +
  labs(title = "") +
  labs(x="", y="Median of Facebook Shares") +
  theme(axis.text.x = element_text(angle = 40, hjust = 1))
```

### 2017-10-31 paper/doc/doc2.tex
fancy graphs

@@
 
-Social networks such as Facebook are becoming increasingly important for online news services: an increasing number of their readers access the news pages via links in the networks.
+Social networks such as Facebook are becoming more and more important for online news services: an increasing number of their readers access the news pages via links in the networks.
 Users of Facebook, for example, can use their profile to share links to external websites - such as news portals - with their online friends.
 This has led to the development of social media into an important generator of traffic on the internet pages.
-In Germany, 94\% of online news articles are shared on Facebook in 2015, followed by Twitter with 3.5\% and Google+ with 2.3\% \citep{schiller_development_2016}.
+In Germany, 94\% of online shared news articles in 2015 are distributed via Facebook, followed by Twitter with 3.5\% and Google+ with 2.3\% \citep{schiller_development_2016}.
 The advertising-financed business model of the media houses is based on the premise that users visit their websites in order to achieve high advertising revenues.
-For this reason, news agencies are particularly interested in finding out which topics are often shared on Facebook.
+For this reason, news agencies are particularly interested in finding out which topics are more likely shared on these platforms.
 \citet{schiller_development_2016} show, that social media users choose a certain site depending on the researched topic.
-FOCUS Online is targeted for articles from politics and business, sports news is more likely to be shared from Bild.de.
+FOCUS Online for example is targeted for articles from politics and business, sports news is more likely to be shared from Bild.de.
 
@@
 To "learn" the topic prevalence and the topic-term distribution, collapsed Gibbs sampling\footnote{See Section \ref{section_gibbs} for a non-formal description of the Gibbs sampler} can be used.
+
 LDA makes a statistical assumption that all texts in the modeled corpus are generated by the same underlying process \citep{blei_latent_2003}.
 Thus, it is not ideally suited to examining differences in topical content that are affected by covariates such as author identity or time of writing.
-
 \citet{roberts_model_2016} develop a structural topic model (STM) that allows to incorporate external variables that effect both topical content and topical prevalence.

### 2017-11-02 paper/R/02_combine.Rmd
new model estimation

@@
 ```{r}
-mystopwords <- c("focus","online","spiegel", "stern", "handelsblatt", "de", "bild","bildplus", "zeit", "ersten", "tagesschau", "wdr", "ndr", "ich","sie","passwort","kommentar","wurde","ihr","der","im","artikel","mehr","ihren","foto","e", "uhr","videolänge","dass","mindestens","das","mail","die","schon","neuer abschnitt", "login", "loggen", "inaktiv", "nwmi", "nwnoa", "polizei","beim","dpa","video","quelle","afp","witters","fotogalerie", "registrierter","als","spiegel","vielen","in","es","bitte","dank","unserer","nutzer","sei","beitrag","user","seit","zeichen", "datenschutzerklärung","premium","nutzungsbedingungen","nutzungsrechte","pflichtfelder","registrierung","anzeige","großbuchstaben","sonderzeichen","html","seitennavigation","fullscreen","statista","club","sagte","borenda","spreepicture","shopübersicht")
+mystopwords <- c("focus","online","spiegel", "stern", "handelsblatt", "de", "bild","bildplus", "zeit", "ersten", "tagesschau", "wdr", "ndr", "ich","sie","passwort","kommentar","wurde","ihr","der","im","artikel","mehr","ihren","foto","e", "uhr","videolänge","dass","mindestens","das","mail","die","schon","neuer abschnitt", "login", "loggen", "inaktiv", "nwmi", "nwnoa", "polizei","beim","dpa","video","quelle","afp","witters","fotogalerie","wurden","worden","wegen","sagt","immer","gibt","geht", "registrierter","als","spiegel","vielen","in","es","bitte","dank","unserer","nutzer","sei","beitrag","user","seit","zeichen", "datenschutzerklärung","premium","nutzungsbedingungen","nutzungsrechte","pflichtfelder","registrierung","anzeige","großbuchstaben","sonderzeichen","html","seitennavigation","fullscreen","statista","club","sagte","borenda","spreepicture","shopübersicht")
 

### 2017-11-02 paper/R/03_stm.Rmd
new model estimation

--- 2017-10-31 paper/R/03_topic model.Rmd
@@
 
-## Introduction
-
-Social networks such as Facebook are becoming more and more important for online news services: an increasing number of their readers access the news pages via links in the networks.
-Users of Facebook, for example, can use their profile to share links to external websites - such as news portals - with their online friends.
-This has led to the development of social media into an important generator of traffic on the internet pages.
-In Germany, 94\% of online shared news articles in 2015 are distributed via Facebook, followed by Twitter with 3.5\% and Google+ with 2.3\% \citep{schiller_development_2016}.
-The advertising-financed business model of the media houses is based on the premise that users visit their websites in order to achieve high advertising revenues.
-For this reason, news agencies are particularly interested in finding out which topics are more likely shared on these platforms.
-\citet{schiller_development_2016} show, that social media users choose a certain site depending on the researched topic.
-FOCUS Online for example is targeted for articles from politics and business, sports news is more likely to be shared from Bild.de.
-
-While these static resorts give an indication on the content of an article, multiple articles in the same resort probably don't cover the same topics (and are not equally shared).
-Especially if the articles originate from different news portals.
-Furthermore, articles can contain more than one topic.
-We use a structural topic model to reveal the underlying topics of a collection of articles (a corpus), and how the articles exhibit them.
-We then estimate the effect of topic prevalence on the number of Facebook shares.
-
-## Methodology
-
-Mapping raw text to one or more topics, without having prior knowledge on what those topics are, translates to an unsupervised classification problem on natural language.
-Within topic models the Latent Dirichlet Allocation (LDA) is a widely used technique, where each document (article) is viewed as a mixture of topics (represented by the document-topic distribution) and each topic is a mixture of unique terms (represented by the topic-term distribution).\cite{blei_latent_2003}
-
-This model views the text generation process as conforming to the following characteristics:
-
-  * A topic is a mixture of words. A topic is comprised of many words, and each word maps to one or more topics.
-  * A document (in this case, a news article), is a mixture of topics. Each document can be thought of as containing a proportion of words from each topic.
-
-To "learn" the topic prevalence and the topic-term distribution, collapsed Gibbs sampling\footnote{See Section \ref{section_gibbs} for a non-formal description of the Gibbs sampler} can be used.
-One of the important considerations of this model is that the number of topics $k$ must be known a-priori.
-
-## Preliminaries
-
-We load libraries needed for this analysis.
-
 ```{r Setup}
@@
   library(topicmodels) # Topic modelling
+  library(stm)         # Sructural Topic Model
   library(proxy)       # Distance measures
@@
 load("../output/models/LDAGibbs 40 .Rda")
-
+load("../output/models/STM 40 .Rda")
 #load("../output/btw_combined.Rda")
@@
 
-## Pre-processing
-
-### Shaping
+## Introduction
+
+Social networks such as Facebook are becoming more and more important for online news services: an increasing number of their readers access the news pages via links in the networks.
+Users of Facebook, for example, can use their profile to share links to external websites - such as news portals - with their online friends.
+This has led to the development of social media into an important generator of traffic on the internet pages.
+In Germany, 94\% of online shared news articles in 2015 are distributed via Facebook, followed by Twitter with 3.5\% and Google+ with 2.3\% \citep{schiller_development_2016}.
+The advertising-financed business model of the media houses is based on the premise that users visit their websites in order to achieve high advertising revenues.
+For this reason, news agencies are particularly interested in finding out which topics are more likely shared on these platforms.
+\citet{schiller_development_2016} show, that social media users choose a certain site depending on the researched topic.
+FOCUS Online for example is targeted for articles from politics and business, sports news is more likely to be shared from Bild.de.
+
+While these static resorts give an indication on the content of an article, multiple articles in the same resort probably don't cover the same topics (and are not equally shared).
+Especially if the articles originate from different news portals.
+Furthermore, articles can contain more than one topic.
+We use a structural topic model to reveal the underlying topics of a collection of articles (a corpus), and how the articles exhibit them.
+We then estimate the effect of topic prevalence on the number of Facebook shares.
+
+## Methodology
+
+Mapping raw text to one or more topics, without having prior knowledge on what those topics are, translates to an unsupervised classification problem on natural language.
+Within topic models the Latent Dirichlet Allocation (LDA) is a widely used technique, where each document (article) is viewed as a mixture of topics (represented by the document-topic distribution) and each topic is a mixture of unique terms (represented by the topic-term distribution).\cite{blei_latent_2003}
+
+This model views the text generation process as conforming to the following characteristics:
+
+  * A topic is a mixture of words. A topic is comprised of many words, and each word maps to one or more topics.
+  * A document (in this case, a news article), is a mixture of topics. Each document can be thought of as containing a proportion of words from each topic.
+
+To "learn" the topic prevalence and the topic-term distribution, collapsed Gibbs sampling\footnote{See Section \ref{section_gibbs} for a non-formal description of the Gibbs sampler} can be used.
+One of the important considerations of this model is that the number of topics $k$ must be known a-priori.
+
+![Research Strategy](../figs/research_strategy.png)
+
+## Dataset
+
+To explore the effect of topic prevalence of an article on the times this article is shared on Facebook, we analyze a sample of 6307 news articles containing the term "Bundestagswahl" (Federal Election) dated from 01.06.2017 to 10.10.2017\footnote{German federal elections took place on 24th of September 2017.} and originated from six different german news sources.\footnote{Bild.de, Focus.de, Spiegel.de, Stern.de, Welt.de, Zeit.de} For each document in our sample, we observe the day it was written, the number of shares on Facebook and the newswire service publishing the article.
+We include the month the document was written and the news agency as covariates on topical prevalence.
+We also include news agency as a covariate affecting topical content to estimate how topics are discussed in different ways by different news agencies \citep{roberts_model_2016}.
+
+Figure -- shows the number of articles by news agency and the how many of these articles were shared on Facebook.
+
+```{r echo=FALSE}
+btw$shared <- ifelse(btw$fb_shares == 0, "0", NA)
+btw$shared <- ifelse(btw$fb_shares > 0 | btw$fb_shares >= 100, "0-100", btw$shared)
+btw$shared <- ifelse(btw$fb_shares > 100, "> 100", btw$shared)
+
+btw %>%
+  ggplot(aes(site, fill=shared)) +
+  geom_bar(alpha = .7) +
+  labs(x="", y="Count") 
+```
+
 ```{r}
@@
   posts_tokenized.dt
-```
-
-We remove words that are less than 3 characters long.
-
-```{r Remove short words}
 
@@
   posts_tokenized.dt
-
-```
-
-### Filtering and Casting
-
-We summarise the data format into a more compressed form and convert it into a document term matrix.
-
-```{r Term Frequency}
 
@@
   posts_tokenized.dt
-
-```
-
-```{r Cast to DTM, eval=FALSE, include=FALSE}
-# Convert to document term matrix
-posts_tokenized.dt %>% 
-  cast_dtm(articleID, word, term_frequency) ->
-  posts_tokenized.dtm
 ```
@@
 
-### Topic modelling
-
-#### LDA Training
-
-##### Build Corpus
+### LDA Training
+
 ```{r eval=FALSE, include=FALSE}
+# Build Corpus
 btw %>%
@@
 rownames(dtm) <- make.unique(btw$title)
-```
-
-##### Run LDA using Gibbs sampling
+
+# ---------- STM ----------- #
+
+btw$month <- month(btw$date)
+# Process data
+processed <- textProcessor(btw$text_cleaned, metadata = btw[,c("date","month","site","text_cleaned","text")],
+                           wordLengths = c(2,Inf),
+                           lowercase = F,
+                           removestopwords = F,
+                           removenumbers = F,
+                           removepunctuation = F,
+                           stem = F)
+out <- prepDocuments(processed$documents, processed$vocab, processed$meta)
+```
 
@@
 ```{r eval=FALSE, include=FALSE}
+## Run LDA using Gibbs sampling
+
 #Set parameters for Gibbs sampling (see https://eight2late.wordpress.com/2015/09/29/a-gentle-introduction-to-topic-modeling-using-r/)
@@
 
-```{r eval=FALSE, include=FALSE}
+```{r}
 t1 <- Sys.time()
@@
 
-save(ldaOut, btw, file=paste("../output/models/LDAGibbs",k,".Rda"))
-```
-
-Training took 50 minutes on the full dataset. We extract the word-topic probabilities, and the document-topic probabilities produced by the model.
-
-alternatively...
-```{r eval=FALSE, include=FALSE}
-# Train the LDA model
-LDA(
-  x       = posts_tokenized.dtm,
-  k       = 40,
-  method  = "Gibbs",
-  control = list(seed = 7292)
-) -> posts.lda
+save(ldaOut, btw, dtm, file=paste("../output/models/LDAGibbs",k,".Rda"))
+
+# ---------- STM ----------- #
+
+t1 <- Sys.time()
+stmOut <- stm(documents = out$documents, 
+           vocab = out$vocab, 
+           K=k, 
+           prevalence = ~site+s(month), 
+           content = ~site, 
+           data=out$meta, 
+           init.type = "Spectral")
+t2 <- Sys.time()
+t2 - t1
+
+save(stmOut, btw, out, file=paste("../output/models/STM",k,".Rda"))
+
 ```
@@
 
-We take a look at samples of articles labeled with the topics and the most relevant words that use them, and label them according to the prevalent theme.
-These are recorded in a csv file and loaded in:
-
 ```{r Loading topic mappings}
@@
 ```
+
+```{r}
 ### Create Topic Labels
-```{r}
+
 ## Return the top 30 terms.
@@
 
-We extract the top 30 most relevant words and plot them as follows:
-
-  1. Compute the Jensen-Shannon divergence between each of the topics according to the differences in their word-topic probabilities and construct a distance matrix,
-  2. Apply principal coordinates analysis in order to project the distance matrix down to two dimensions.
-  3. Plot each word near the center of the topic mass and repel them from each other.
-
-```{r eval=FALSE, include=FALSE}
+### Sample articles
+
+To test, wheather the topic classification make sense, we pull out sample articles classified by the model to see if they match the assigned topic.
+
+Now that we have labelled each topic, we produce sample documents classified to that topic for reference. We produce a random sample of 10 posts from the 300 highest probability fits per topic.
+
+```{r Document classification}
+
+set.seed(9272)
+posts.dtp %>% 
+  group_by(title = document) %>% 
+  summarise(topic = min(topic[gamma == max(gamma)]), gamma = max(gamma)) %>% 
+  ungroup() %>% 
+  inner_join(btw %>% select(title, articleID), by = "title") %>% 
+  inner_join(topics_mapping.dt, by = "topic") %>% 
+  mutate(topic_title = 
+           paste0("Topic ", formatC(topic, flag = "0", width = 2), 
+                  " - ", topic_name)) %>% 
+  group_by(topic_name) %>% 
+  top_n(300, gamma) %>%
+  sample_n(5, replace = TRUE) %>% 
+  mutate(row = row_number()) %>% 
+  ungroup() ->
+  posts_classification.sdt
+
+```
+
+We produce a chart that shows this in a presentable manner.
+
+```{r Document classification chart, echo=TRUE}
+
+ggsave(
+  plot = {
+    posts_classification.sdt %>% 
+      ggplot(aes(x = 0, y = row, color = factor(topic, levels = 1:40))) +
+      facet_wrap(~topic_title, ncol = 5) +
+      geom_text(
+        aes(label = title),
+        size = 2, hjust = 0, family = "Roboto"
+      ) +
+      geom_point(aes(x = -0.025), size = 0.5) +
+      scale_x_continuous(limits = c(-0.05, 1), expand = c(0, 0)) +
+      scale_color_manual(
+        values = rainbow(40) %>% 
+          adjustcolor(red.f = 0.6, green.f = 0.6, blue.f = 0.6)
+      ) +
+      theme(
+        axis.title       = element_blank(),
+        axis.text        = element_blank(),
+        axis.ticks       = element_blank(),
+        panel.grid       = element_blank(),
+        strip.background = element_blank(),
+        panel.border     = element_blank(),
+        strip.text       = element_text(face = "bold", hjust = 0, size = 6),
+        plot.background  = element_rect(fill = "#FAFAFA"),
+        legend.position  = "none"
+      ) +
+      labs(
+        title    = "GERMAN NEWS LANDSCAPE",
+        subtitle = "Sample online news articles in the year 2017",
+        caption  = 
+"DATA SOURCE: Webhose.io, Eventbride.com
+
+CHART NOTES:
+  1. Topics were derived through Latent Dirichlet Allocation (LDA) with 40 topics
+  2. Documents were classified according to the topic that has the highest probability
+"
+      )
+  },
+  device = "png",
+  filename = "../figs/02-topic-classification-sample.png",
+  dpi = 600, height = 10, width = 16
+)
+
+```
+
+![Facebook news samples](../figs/02-topic-classification-sample.png)
+
+### News landscape
+
+After performing the topic modeling, we can generate an overview of the news landscape about the german elections, each group is composed of the most relevant words for that topic, and a manually-determined label.
+The distances that the topics have from each other reflect their semantic distance, or basically how different the words are for that topic.
+It is computed as the Jensen-Shannon divergence between each of the topics according to the differences in their word-topic probabilities.
+We then apply principal coordinates analysis in order to project the distance matrix down to two dimensions.
+
+```{r echo=TRUE}
 posts.wtp %>% 
@@
 ![Facebook News Map](../figs/01-news-landscape-map.png)
-
-Now that we have labelled each topic, we produce sample documents classified to that topic for reference. We produce a random sample of 10 posts from the 300 highest probability fits per topic.
-
-```{r Document classification}
-
-set.seed(9272)
-posts.dtp %>% 
-  group_by(title = document) %>% 
-  summarise(topic = min(topic[gamma == max(gamma)]), gamma = max(gamma)) %>% 
-  ungroup() %>% 
-  inner_join(btw %>% select(title, articleID), by = "title") %>% 
-  inner_join(topics_mapping.dt, by = "topic") %>% 
-  mutate(topic_title = 
-           paste0("Topic ", formatC(topic, flag = "0", width = 2), 
-                  " - ", topic_name)) %>% 
-  group_by(topic_name) %>% 
-  top_n(300, gamma) %>%
-  sample_n(10) %>% 
-  mutate(row = row_number()) %>% 
-  ungroup() ->
-  posts_classification.sdt
-
-```
-
-We produce a chart that shows this in a presentable manner.
-
-```{r Document classification chart, eval=FALSE, include=FALSE}
-
-ggsave(
-  plot = {
-    posts_classification.sdt %>% 
-      ggplot(aes(x = 0, y = row, color = factor(topic, levels = 1:40))) +
-      facet_wrap(~topic_title, ncol = 5) +
-      geom_text(
-        aes(label = title),
-        size = 2, hjust = 0, family = "Roboto"
-      ) +
-      geom_point(aes(x = -0.025), size = 0.5) +
-      scale_x_continuous(limits = c(-0.05, 1), expand = c(0, 0)) +
-      scale_color_manual(
-        values = rainbow(40) %>% 
-          adjustcolor(red.f = 0.6, green.f = 0.6, blue.f = 0.6)
-      ) +
-      theme(
-        axis.title       = element_blank(),
-        axis.text        = element_blank(),
-        axis.ticks       = element_blank(),
-        panel.grid       = element_blank(),
-        strip.background = element_blank(),
-        panel.border     = element_blank(),
-        strip.text       = element_text(face = "bold", hjust = 0, size = 6),
-        plot.background  = element_rect(fill = "#FAFAFA"),
-        legend.position  = "none"
-      ) +
-      labs(
-        title    = "GERMAN NEWS LANDSCAPE",
-        subtitle = "Sample online news articles in the year 2017",
-        caption  = 
-"DATA SOURCE: Webhose.io, Eventbride.com
-
-CHART NOTES:
-  1. Topics were derived through Latent Dirichlet Allocation (LDA) with 40 topics
-  2. Documents were classified according to the topic that has the highest probability
-"
-      )
-  },
-  device = "png",
-  filename = "../figs/02-topic-classification-sample.png",
-  dpi = 600, height = 10, width = 16
-)
-
-```
-
-![Facebook news samples](../figs/02-topic-classification-sample.png)
 

### 2017-11-02 paper/R/03_topic model.Rmd
new model estimation

@@
 load("../output/models/LDAGibbs 40 .Rda")
-
 #load("../output/btw_combined.Rda")
@@
 
-## Pre-processing
-
-### Shaping
-```{r}
+## Introduction
+
+Social networks such as Facebook are becoming more and more important for online news services: an increasing number of their readers access the news pages via links in the networks.
+Users of Facebook, for example, can use their profile to share links to external websites - such as news portals - with their online friends.
+This has led to the development of social media into an important generator of traffic on the internet pages.
+In Germany, 94\% of online shared news articles in 2015 are distributed via Facebook, followed by Twitter with 3.5\% and Google+ with 2.3\% \citep{schiller_development_2016}.
+The advertising-financed business model of the media houses is based on the premise that users visit their websites in order to achieve high advertising revenues.
+For this reason, news agencies are particularly interested in finding out which topics are more likely shared on these platforms.
+\citet{schiller_development_2016} show, that social media users choose a certain site depending on the researched topic.
+FOCUS Online for example is targeted for articles from politics and business, sports news is more likely to be shared from Bild.de.
+
+While these static resorts give an indication on the content of an article, multiple articles in the same resort probably don't cover the same topics (and are not equally shared).
+Especially if the articles originate from different news portals.
+Furthermore, articles can contain more than one topic.
+We use a structural topic model to reveal the underlying topics of a collection of articles (a corpus), and how the articles exhibit them.
+We then estimate the effect of topic prevalence on the number of Facebook shares.
+
+## Methodology
+
+Mapping raw text to one or more topics, without having prior knowledge on what those topics are, translates to an unsupervised classification problem on natural language.
+Within topic models the Latent Dirichlet Allocation (LDA) is a widely used technique, where each document (article) is viewed as a mixture of topics (represented by the document-topic distribution) and each topic is a mixture of unique terms (represented by the topic-term distribution).\cite{blei_latent_2003}
+
+This model views the text generation process as conforming to the following characteristics:
+
+  * A topic is a mixture of words. A topic is comprised of many words, and each word maps to one or more topics.
+  * A document (in this case, a news article), is a mixture of topics. Each document can be thought of as containing a proportion of words from each topic.
+
+To "learn" the topic prevalence and the topic-term distribution, collapsed Gibbs sampling\footnote{See Section \ref{section_gibbs} for a non-formal description of the Gibbs sampler} can be used.
+One of the important considerations of this model is that the number of topics $k$ must be known a-priori.
+
+![Research Strategy](../figs/research_strategy.png)
+
+## Dataset
+
+To explore the effect of topic prevalence of an article on the times this article is shared on Facebook, we analyze a sample of 6307 news articles containing the term "Bundestagswahl" (Federal Election) dated from 01.06.2017 to 10.10.2017\footnote{German federal elections took place on 24th of September 2017.} and originated from six different german news sources.\footnote{Bild.de, Focus.de, Spiegel.de, Stern.de, Welt.de, Zeit.de} For each document in our sample, we observe the day it was written, the number of shares on Facebook and the newswire service publishing the article.
+We include the month the document was written and the news agency as covariates on topical prevalence.
+We also include news agency as a covariate affecting topical content to estimate how topics are discussed in different ways by different news agencies \citep{roberts_model_2016}.
+
+We can see the number of articles by news agency and the how many of these articles were shared on Facebook on the following figure.
+
+```{r echo=FALSE}
+btw$shared <- ifelse(btw$fb_shares == 0, "0", NA)
+btw$shared <- ifelse(btw$fb_shares > 0 | btw$fb_shares >= 100, "0-100", btw$shared)
+btw$shared <- ifelse(btw$fb_shares > 100, "> 100", btw$shared)
+
+btw %>%
+  ggplot(aes(site, fill=shared)) +
+  geom_bar(alpha = .7) +
+  labs(x="", y="Count") 
+```
+
+```{r include=FALSE}
 btw %>% 
@@
 
-##### Run LDA using Gibbs sampling
-
 We then train the LDA on the full dataset, with $k = 40$.
@@
 
-save(ldaOut, btw, file=paste("../output/models/LDAGibbs",k,".Rda"))
-```
-
-Training took 50 minutes on the full dataset. We extract the word-topic probabilities, and the document-topic probabilities produced by the model.
-
-alternatively...
-```{r eval=FALSE, include=FALSE}
-# Train the LDA model
-LDA(
-  x       = posts_tokenized.dtm,
-  k       = 40,
-  method  = "Gibbs",
-  control = list(seed = 7292)
-) -> posts.lda
+save(ldaOut, btw, dtm, file=paste("../output/models/LDAGibbs",k,".Rda"))
 ```
@@
 ```
+
+```{r message=FALSE, warning=FALSE}
 ### Create Topic Labels
-```{r}
+
 ## Return the top 30 terms.
@@
 
-We extract the top 30 most relevant words and plot them as follows:
-
-  1. Compute the Jensen-Shannon divergence between each of the topics according to the differences in their word-topic probabilities and construct a distance matrix,
-  2. Apply principal coordinates analysis in order to project the distance matrix down to two dimensions.
-  3. Plot each word near the center of the topic mass and repel them from each other.
+### Sample articles
+
+To test, wheather the topic classification make sense, we pull out sample articles classified by the model to see if they match the assigned topic.
+
+Now that we have labelled each topic, we produce sample documents classified to that topic for reference. We produce a random sample of 10 posts from the 300 highest probability fits per topic.
+
+```{r Document classification}
+
+set.seed(9272)
+posts.dtp %>% 
+  group_by(title = document) %>% 
+  summarise(topic = min(topic[gamma == max(gamma)]), gamma = max(gamma)) %>% 
+  ungroup() %>% 
+  inner_join(btw %>% select(title, articleID), by = "title") %>% 
+  inner_join(topics_mapping.dt, by = "topic") %>% 
+  mutate(topic_title = 
+           paste0("Topic ", formatC(topic, flag = "0", width = 2), 
+                  " - ", topic_name)) %>% 
+  group_by(topic_name) %>% 
+  top_n(300, gamma) %>%
+  sample_n(5, replace = TRUE) %>% 
+  mutate(row = row_number()) %>% 
+  ungroup() ->
+  posts_classification.sdt
+
+```
+
+We produce a chart that shows this in a presentable manner.
+
+```{r Document classification chart, eval=FALSE, include=FALSE}
+
+ggsave(
+  plot = {
+    posts_classification.sdt %>% 
+      ggplot(aes(x = 0, y = row, color = factor(topic, levels = 1:40))) +
+      facet_wrap(~topic_title, ncol = 5) +
+      geom_text(
+        aes(label = title),
+        size = 2, hjust = 0, family = "Roboto"
+      ) +
+      geom_point(aes(x = -0.025), size = 0.5) +
+      scale_x_continuous(limits = c(-0.05, 1), expand = c(0, 0)) +
+      scale_color_manual(
+        values = rainbow(40) %>% 
+          adjustcolor(red.f = 0.6, green.f = 0.6, blue.f = 0.6)
+      ) +
+      theme(
+        axis.title       = element_blank(),
+        axis.text        = element_blank(),
+        axis.ticks       = element_blank(),
+        panel.grid       = element_blank(),
+        strip.background = element_blank(),
+        panel.border     = element_blank(),
+        strip.text       = element_text(face = "bold", hjust = 0, size = 6),
+        plot.background  = element_rect(fill = "#FAFAFA"),
+        legend.position  = "none"
+      ) +
+      labs(
+        title    = "GERMAN NEWS LANDSCAPE",
+        subtitle = "Sample online news articles in the year 2017",
+        caption  = 
+"DATA SOURCE: Webhose.io, Eventbride.com
+
+CHART NOTES:
+  1. Topics were derived through Latent Dirichlet Allocation (LDA) with 40 topics
+  2. Documents were classified according to the topic that has the highest probability
+"
+      )
+  },
+  device = "png",
+  filename = "../figs/02-topic-classification-sample.png",
+  dpi = 600, height = 10, width = 16
+)
+
+```
+
+![Facebook news samples](../figs/02-topic-classification-sample.png)
+
+### News landscape
+
+After performing the topic modeling, we can generate an overview of the news landscape about the german elections, each group is composed of the most relevant words for that topic, and a manually-determined label.
+The distances that the topics have from each other reflect their semantic distance, or basically how different the words are for that topic.
+It is computed as the Jensen-Shannon divergence between each of the topics according to the differences in their word-topic probabilities.
+We then apply principal coordinates analysis in order to project the distance matrix down to two dimensions.
 

### 2017-11-02 paper/R/03_stm.Rmd
stm

@@
 ```{r caching, echo = FALSE}
-load("../output/models/LDAGibbs 40 .Rda")
+#load("../output/models/LDAGibbs 40 .Rda")
 load("../output/models/STM 40 .Rda")
@@
 
-btw$articleID <- rownames(btw)
+btw$articleID <- as.integer(rownames(btw))
 ```
@@
 
-### LDA Training
+### STM Training
 
@@
 # Build Corpus
-btw %>%
-  filter(nchar(text_cleaned) > 5) -> btw
-
-# Build corpus
-df.lda <- Corpus(VectorSource(btw$text_cleaned))
-# Create document-term matrix
-dtm <- DocumentTermMatrix(df.lda)
-# Assign name to docs
-rownames(dtm) <- make.unique(btw$title)
-
-# ---------- STM ----------- #
-
 btw$month <- month(btw$date)
@@
 
-```{r eval=FALSE, include=FALSE}
-## Run LDA using Gibbs sampling
-
-#Set parameters for Gibbs sampling (see https://eight2late.wordpress.com/2015/09/29/a-gentle-introduction-to-topic-modeling-using-r/)
-burnin <- 1000
-iter <- 1000
-keep <- 50
-
+```{r}
 k = 40 # Topics
-```
-
-```{r}
-t1 <- Sys.time()
-ldaOut <-LDA(dtm, k, method="Gibbs", control=list(burnin=burnin, iter = iter, keep = keep))
-t2 <- Sys.time()
-t2 - t1
-
-save(ldaOut, btw, dtm, file=paste("../output/models/LDAGibbs",k,".Rda"))
-
-# ---------- STM ----------- #
 
@@
 
+### STM Exploratiom
+
+#### Topic Summary
+```{r}
+plot(stmOut, type="summary", xlim = c(0,.14), n=5, text.cex = 0.7, main = "Topics in german online news covering the Federal Elections")
+```
+
+Assign labels to the topics based in the interpretation of word-topic probabilities.
+
+```{r}
+Labelprep <- labelTopics(stmOut)
+
+# Topic Labels
+topicLabels <- as.data.frame(Labelprep$topics)
+topicLabels %>%
+  transmute(labels = paste(V1,V2,V3, sep = ", "),
+            topic = rownames(.)) -> topicLabels
+
+# Covariate topic labels
+rown <- as.data.frame(rep(rownames(Labelprep$topics),6))
+rown <- rown %>% 
+  transmute(topics = as.numeric(.[,1])) %>% arrange(topics) %>%
+  mutate(site = rep(rownames(Labelprepr$covariate), 40))
+
+covLables <- as.data.frame(Labelprepr$interaction)
+covLables <- covLables %>%
+  transmute(topic = as.numeric(rown$topics),
+            site = rown$site,
+    labels = paste(V1,V2,V3, sep = ", "),
+            topic.site = paste0("Topic", rown$topics, ", ",rown$site))
+```
+
+We can also plot the exclusivity and semantic coherence, which are two metrics that measure the “interpretability” of each topic.
+Higher semantic coherence indicate topics that have more consistent words (more interpretable) while exclusivity measures how exclusive the words are to the topic relative to other topics (e.g.
+low values mean topics that are vague and share a lot of words with other topics while high values indicate words that are very unique/exclusive to the topic).
+
+Does not support models with content covariates.
+
+```{r}
+# par(mfrow = c(1,1),mar = c(2, 2, 2, 2))
+# 
+# topicQuality(stmOut,
+#              documents = out$documents, 
+#              main = "Topic Interpretability: Exclusivity and Semantic Coherence")
+```
+
+#### Estimating the Effect of covariates
+One of the main contributions of STM is to provide a mechanism to test (with statistical significance) the impact document-level covariates (e.g.
+party, time of post) have on the topic proportions (prevalence).
+Method used for plotting.
+"pointestimate" estimates mean topic proportions for each value of the covariate.
+
+```{r Estimating the Effect of Covariates}
+k <- 40
+
+prep <- estimateEffect(1:k ~ site+s(month), stmobj = stmOut, meta = out$meta, uncertainty = "Global")
+```
+
+```{r Plot Effect Of Covariates On Topics}
+par(mfrow = c(3,3), mar = c(4,4,2,2))
+for (i in 1:k){
+  plot(prep, "site", method = "pointestimate", topics = i, 
+       labeltype = "custom", custom.labels = prep$data$site,
+       cex = 0.6, cex.main = 0.7,
+       main = topicLabels[which(topicLabels$topic==i),])
+}
+```
+
+We can also explore the effect of a contiuous covariate like time. In this case, we use month using a b-spline to smooth out our results.
+
+For simplicity, I removed confidence intervals and only plotted the (point) estimates.
+
+```{r}
+col = palette(rainbow(6))
+
+par(mfrow = c(2,2),mar = c(4,4,2,2))
+for (i in 1:k){
+  plot(prep, "month", method = "continuous", topics = i, 
+                      main = paste0(topicNames$labels[i],"\n: Topic ", topicNames$topic[i]),
+                      cex.main = .8,
+                      printlegend = FALSE, ylab = "Exp. Topic Prob", 
+                      xlab = "Time (June 2017 to Oct 2016)",
+                      ylim = c(-0.07,0.35),
+                      cex.axis = .6,
+                      cex.label = .6,
+                      moderator = "site", moderator.value = prep$data$site[1],  linecol = col[1],
+                      ci.level = 0
+                      )
+  for (j in 2:6){
+    plot(prep, "month", method = "continuous", topics = i, 
+                      #main = paste0(topicNames$labels[i],": Topic ", topicNames$topic[i]),
+                      printlegend = FALSE, ylab = "Exp. Topic Prob", 
+                      ylim = c(-0.07,0.35),
+                      moderator = "site", moderator.value = prep$data$site[j],  linecol = col[j],
+                      ci.level = 0, add="T"
+                      )
+  }
+
+legend(-1, 1.9, prep$data$site, lwd = 2, col = col)
+}
+
+prep$parameters
+```
+
 #### Topic Labeling
@@
 ```{r Extract wtp and dtp}
+# Word-topic probabilities
+stmOut %>% tidy("beta") %>% filter(!is.na(topic)) -> posts.wtp
 
-# Word-topic probabilities
-ldaOut %>% tidy("beta") -> posts.wtp
-
-# Document-topic probabilities
-ldaOut %>% tidy("gamma") -> posts.dtp
-
+# Document-topic probablities
+stmOut %>% tidy("gamma") -> posts.dtp
 ```
 
-We can then assess the word-topic probabilities in order to get an idea of the topic that is most.
+We can then assess the word-topic probabilities in order to get an idea of the topic.
 
 Since we have over 30,000 unique terms in the corpus, we need to extract the top few words that most uniquely define each topic, so that we can more easily visualize and label them.
-We use the measure of relevance defined by Sievert and Shirley (2014)^[[Sievert and Shirley (2014).
-LDAvis: A method for visualizing and interpreting topics.
-*Stanford University.*](http://nlp.stanford.edu/events/illvi2014/papers/sievert-illvi2014.pdf)].
-Relevance of term $w$ to topic $k$ given a weight parameter $\lambda$ between 0 and 1 $r(w, k | \lambda)$ is computed as:
-
-$$
-r(w, k | \lambda) = \lambda\log(\phi_{kw}) + (1-\lambda)\log(\frac{\phi_{kw}}{p_w})
-$$
-
-where $\phi_{kw}$ is the probability of term $w$ for topic $k$, and $p_w$ is the empirical probability of the word in the corpus.
-$\lambda$ can be thought of as a weighting term between ranking by the probability of that word within the topic, and ranking by the lift over the overall probability in the corpus.
-
-In user studies, Sievert and Shirley (2004) found that a lambda value of 0.6 as an optimal value for allowing humans to identify the topics associated with the top words ranked by relevance.
-We use this same value for lambda.
-
-```{r Compute relevance}
-
-posts.wtp %>%
-  # Compute lambda and phi_kw
-  mutate(lambda = 0.6, phi_kw = beta) %>% 
-  # Compute and join the p_w
-  left_join(
-    posts_tokenized.dt %>%
-      group_by(word) %>% 
-      dplyr::summarise(frequency = sum(term_frequency)) %>% 
-      ungroup() %>% 
-      mutate(p_w = frequency/sum(frequency)) %>% 
-      select(-frequency),
-    by = c("term" = "word")
-  ) %>%
-  # Compute the relevance
-  mutate(relevance = lambda * log(phi_kw) + (1 - lambda) * log(phi_kw/p_w)) ->
-  word_relevance.dt
-
-```
-
-```{r Loading topic mappings}
-### Most likely Topics per Article
-
-# The topics function from the package is used to extract the most likely topic for each document 
-btw.topics <- topics(ldaOut, 2)
-
-# Create Dataframe
-doctopics.df <- as.data.frame(t(btw.topics))
-
-doctopics.df %>%
-  transmute(title = rownames(.),
-            topic = V1) -> doctopics.df
-
-doctopics.df$articleID <- as.integer(rownames(doctopics.df))
-
-# Add Topic to origian DF
-topics_mapping.dt <- btw %>%
-  mutate(articleID = as.integer(articleID)) %>%
-  inner_join(.,doctopics.df, by="articleID") %>%
-
-  group_by(topic) %>%
-  slice(1) %>%
-  select(topic, title.text, articleID) 
-```
 
@@
 ### Create Topic Labels
+btw.terms <- labelTopics(stmOut,1, n=30)
+btw.terms <- as.data.frame(t(btw.terms$topics))
 
-## Return the top 30 terms.
-btw.terms <- as.data.frame(terms(ldaOut, 30), stringAsFactors = FALSE)
-
-topicTerms <- btw.terms %>% gather(Topic)
+topicTerms <- btw.terms %>% gather(topic)
 topicTerms <- cbind(topicTerms, Rank = rep(1:30))
-topicTerms <- topicTerms %>% filter(Rank < 5)
-
-topicTerms <- topicTerms %>% mutate(topic = stringr::word(Topic, 2))
-topicTerms$topic <- as.numeric(topicTerms$topic)
+topicTerms <- topicTerms %>% 
+  filter(Rank < 5) %>%
+  mutate(topic = as.numeric(topic))
 
@@
 topicLabel$topic <- as.integer(rownames(topicLabel))
+```
+
+```{r Compute relevance}
+word_relevance.dt <- posts.wtp %>%
+  filter(str_length(term) >= 3) %>%
+  # Compute lambda and phi_kw
+  mutate(lambda = 0.6, phi_kw = beta) %>% 
+  # Compute and join the p_w
+  left_join(
+    posts_tokenized.dt %>%
+      group_by(word) %>% 
+      summarise(frequency = sum(term_frequency)) %>% 
+      ungroup() %>% 
+      mutate(p_w = frequency/sum(frequency)) %>% 
+      select(-frequency),
+    by = c("term" = "word")
+  ) %>%
+  # Compute the relevance
+  mutate(relevance = lambda * log(phi_kw) + (1 - lambda) * log(phi_kw/p_w))
+  filter(!is.na(relevance))
+
+```
+
+```{r Loading topic mappings}
+### Most likely Topics per Article
+btw.topics <- make.dt(stmOut)
+btw.topics %>% select(-docnum) -> btw.topics
+
+# Create Dataframe
+btw.topics$V1 <- colnames(btw.topics)[apply(btw.topics,1,which.max)]
+
+btw.topics %>%
+  select(V1) %>% 
+  transmute(articleID = as.integer(rownames(.)),
+            topic = as.integer(gsub("Topic","",V1))) -> doctopics.df
+
+# Add Topic to origian DF
+btw.dt <- btw %>%
+  inner_join(.,doctopics.df, by="articleID")
+
+topics_mapping.dt<-btw.dt %>%
+  group_by(topic) %>%
+  slice(1) %>%
+  select(topic, title.text, articleID, fb_shares) 
 ```
@@
 set.seed(9272)
-posts.dtp %>% 
-  group_by(title = document) %>% 
+
+posts_classification.sdt <- posts.dtp %>% 
+  group_by(articleID = document) %>% 
   summarise(topic = min(topic[gamma == max(gamma)]), gamma = max(gamma)) %>% 
   ungroup() %>%
-  inner_join(btw %>% select(title, articleID), by = "title") %>% 
-  inner_join(topics_mapping.dt, by = "topic") %>% 
+  inner_join(btw %>% select(title, title.text, articleID), by = "articleID") %>%
+  inner_join(topics_mapping.dt %>% select(topic, topic_name), by = "topic") %>%
   mutate(topic_title = 
@@
   top_n(300, gamma) %>%
-  sample_n(5, replace = TRUE) %>% 
+  sample_n(5) %>% 
   mutate(row = row_number()) %>% 
-  ungroup() ->
-  posts_classification.sdt
-
+  ungroup() 
 ```
@@
   device = "png",
-  filename = "../figs/02-topic-classification-sample.png",
+  filename = "../figs/02-stm-topic-classification-sample.png",
   dpi = 600, height = 10, width = 16
@@
 
-![Facebook news samples](../figs/02-topic-classification-sample.png)
-
-### News landscape
-
-After performing the topic modeling, we can generate an overview of the news landscape about the german elections, each group is composed of the most relevant words for that topic, and a manually-determined label.
-The distances that the topics have from each other reflect their semantic distance, or basically how different the words are for that topic.
-It is computed as the Jensen-Shannon divergence between each of the topics according to the differences in their word-topic probabilities.
-We then apply principal coordinates analysis in order to project the distance matrix down to two dimensions.
-
-```{r echo=TRUE}
-posts.wtp %>% 
-  # Compute Jensen-Shannon
-  computeJensenShannonPCA() %>% {
-
-    # Assign positions to top 30 most relevant words
-    left_join(
-      .,
-      word_relevance.dt %>% 
-        group_by(topic) %>% 
-        top_n(30, relevance) %>% 
-        ungroup(),
-      by = "topic"
-    ) -> topic_labelling_top30words.dt
-
-    # Assign positions to topic labels
-    left_join(
-      .,
-      topics_mapping.dt,
-      by = "topic"
-    ) -> topic_labelling_topics.dt
-
-    ggsave(
-      plot = {
-        topic_labelling_top30words.dt %>% 
-          ggplot(aes(x = x, y = y)) +
-          geom_text_repel(
-            aes(label = term, 
-                color = factor(topic, levels = 1:40), 
-                size = phi_kw * p_w), 
-            lineheight = 0.6, 
-            segment.size = NA,
-            box.padding = unit(0, "lines"),
-            force = 0.05,
-            family = "Roboto"
-          ) +
-          geom_text_repel(
-            data = topic_labelling_topics.dt,
-            aes(label = str_wrap(topic_name, 15),
-                color = factor(topic, levels = 1:40)),
-            size = 2.25, lineheight = 0.7,
-            segment.size = 0.5, alpha = 0.7,
-            family = "Roboto", fontface = 2,
-            force = 0.3
-          ) +
-          scale_size_continuous(range = c(1, 4)) +
-          scale_color_manual(
-            values = rainbow(40) %>% 
-              adjustcolor(red.f = 0.6, green.f = 0.6, blue.f = 0.6)
-          ) +
-          theme(
-            axis.title = element_blank(),
-            axis.text  = element_blank(),
-            axis.ticks = element_blank(),
-            panel.grid = element_blank(),
-            panel.border = element_blank(),
-            plot.background = element_rect(fill = "#FAFAFA"),
-            legend.position = "none"
-          ) +
-          labs(
-            title    = "GERMAN NEWS LANDSCAPE",
-            subtitle = "Online News Articles about Federal Elections June-Oct 2017",
-            caption = 
-"DATA SOURCE: Webhose.io, Eventbride.com
-
-CHART NOTES:
-  1. Topics were derived through Latent Dirichlet Allocation (LDA) with 40 topics
-  2. For each topic, the top 30 words in terms of relevance as defined in Sievert and Shirley (2014) are displayed
-  3. The centers of each topic mass were determined by applying principal components analysis to the distance matrix, with the Jensen-Shannon divergence as the distance measure. 
-      This layout is intended to display the degree of semantic distance.
-"
-          )
-      },
-      filename = "../figs/01-news-landscape-map.png",
-      device = "png",
-      dpi = 600
-    )
-
-  }
-
-```
-
-![Facebook News Map](../figs/01-news-landscape-map.png)
-
-### Topic Trends
-
-We classify each document based on which topic has the highest probability. If one or more topics have equal probability, then the count is assigned equally to all the topics.
-
-```{r Topic classification}
-
-posts.dtp %>% 
-  group_by(document) %>% 
-  filter(gamma == max(gamma)) %>% 
-  mutate(allocation = 1/n()) %>% 
-  ungroup() ->
-  posts_classification.dt
-
-```
-
-We construct a chart that allows us to explore topic trends, both in terms of document count and the total number of reactions on the articles of that particular topic.
-
-```{r Data for topic trends chart}
-
-set.seed(7292)
-posts_classification.dt %>% 
-  # Add post information
-  inner_join(
-    btw %>% 
-      select(document = title, date, 
-             title, articleID) %>% 
-      mutate(post_period = 
-               date %>% 
-               with_tz("Europe/Paris") %>% 
-               floor_date("week")),
-    by = "document"
-  ) %>%
-  # Add topic information
-  left_join(topics_mapping.dt, by = "topic") %>%
-  # Summarise into tidy dataframe
-  group_by(post_period, topic_name) %>% 
-  summarise(
-    articles = sum(allocation),
-    sample_articles = 
-      paste0("<li>", sample(document, 3, replace = TRUE ), "</li>", collapse = "<br>")
-  ) %>% 
-  ungroup() %>% 
-  mutate(
-    tooltip_text = 
-      paste0(
-        "<b>", topic_name, "</b> in period of <b>", post_period, "</b><br>",
-        "<b>Number of Articles:</b> ", comma(round(articles, 0)), "<br>",
-        "<b>Sample Articles:</b><br><ul>", sample_articles, "</ul>"
-      )
-  ) %>% 
-  # Mark peaks 
-  group_by(topic_name) %>% 
-  mutate_at(
-    vars(articles), 
-    funs(mean = mean(.), sd = sd(.), zscore = (. - mean(.))/sd(.))
-  ) %>% 
-  ungroup() %>% 
-  mutate_at(
-    vars(ends_with("zscore")),
-    funs(peak = . >	1.96)
-  ) %>% 
-  mutate(tooltip_text = str_replace_all(tooltip_text, "'", "")) ->
-  chart_topic_trends.dt
-```
-
-```{r Topic trends chart, eval = TRUE}
-
-{
-  chart_topic_trends.dt %>% 
-    ggplot(
-      aes(
-        x = post_period, 
-        y = factor(
-          topic_name, 
-          chart_topic_trends.dt %>% 
-            group_by(topic_name) %>% 
-            summarise(post_period = mean(post_period[peak], na.rm = TRUE)) %>% 
-            ungroup() %>% 
-            arrange(desc(post_period)) %$%
-            unique(topic_name)
-        )
-      )
-    ) +
-    geom_tile_interactive(aes(tooltip = tooltip_text, fill = log(articles))) +
-    geom_point_interactive(
-      mapping = aes(tooltip = tooltip_text),
-      data = chart_topic_trends.dt %>% filter(peak),
-      color = "red"
-    ) +
-    scale_fill_viridis(
-      labels = function(x) comma(round(exp(x))), 
-      name = "Number of Articles",
-      option = "plasma"
-    ) +
-    scale_x_datetime(expand = c(0, 0)) +
-    labs(
-      title = "ZEITGEIST", 
-      subtitle = "Topic distribution of news articles over time, 2017\n(Hover over each tile to see sample articles)",
-      caption = "
-DATA SOURCE: Webhose.io, Eventbride.com
-
-CHART NOTES:
-  1. Red dots indicate weeks where the number of articles exceeds 1.96 SD above mean for that topic
-  2. Hover over each tile to see infomration and to see sample articles
-  3. Topics were derived through Latent Dirichlet Allocation (LDA) with 40 topics
-  4. Articles were classified according to the topic that has the highest probability
-
-TROY JAMES PALANCA | TJPALANCA.COM
-      "
-    ) +
-    theme(
-      legend.position   = "bottom",
-      legend.key.width  = unit(0.1, "npc"),
-      legend.background = element_rect("#fafafa"),
-      plot.background   = element_rect("#fafafa", "#fafafa"),
-      plot.title        = element_text(size = 18),
-      plot.subtitle     = element_text(size = 8),
-      plot.caption      = element_text(size = 7),
-      panel.grid        = element_blank(),
-      panel.background  = element_rect("#fafafa"),
-      axis.title        = element_blank(),
-      axis.ticks        = element_blank(),
-      axis.text.y       = element_text(size = 8)
-    ) 
-} %>% 
-  ggiraph(
-    ggobj = .,
-    # width_svg  = 8,
-    # height_svg = 7,
-    width = 1,
-    tooltip_extra_css = "
-    font-family: Roboto; 
-    background-color: #000; 
-    color: #fff; font-size: 10px;
-    padding: 5px;"
-  ) %>% 
-  prependContent(
-    tags$link(
-      href = "https://fonts.googleapis.com/css?family=Roboto:400,700", 
-      rel = "stylesheet"
-    )
-  ) -> chart_topic_trends.wdgt
-
-saveWidget(
-  widget = chart_topic_trends.wdgt,
-  file = "../figs/03-topic-trends.html",
-  selfcontained = FALSE,
-  libdir = "../figs/js",
-  background = "#fafafa"
-)
-
-chart_topic_trends.wdgt
-
-```
-
-```{r Topic trends line chart, eval = TRUE}
-
-{ 
-  chart_topic_trends.dt %>%
-  select(post_period, topic_name, articles) %>% 
-  mutate(data_id = row_number() %>% as.character()) %>% 
-  ggplot(aes(x = post_period, y = articles)) +
-  geom_path_interactive(
-    aes(group = topic_name, 
-        tooltip = str_replace_all(topic_name, "'", ""),
-        data_id = data_id), 
-    color = "gray"
-  ) +
-    scale_y_continuous(labels = comma) +
-    labs(
-      title = "PEAKS AND TROUGHS",
-      subtitle = "Hover over each line to see the trend of news articles for a particular topic",
-      y = "Number of Articles"
-    ) +
-    theme(
-      plot.background   = element_rect("#fafafa", "#fafafa"),
-      plot.title        = element_text(size = 18),
-      plot.subtitle     = element_text(size = 8),
-      plot.caption      = element_text(size = 7),
-      panel.grid        = element_blank(),
-      panel.background  = element_rect("#fafafa"),
-      axis.title.x      = element_blank(),
-      axis.text.y       = element_text(size = 8)
-    )
-} %>% 
-  ggiraph(
-    ggobj = .,
-    hover_css = "stroke: red; stroke-width: 3px;",
-    width = 1,
-    width_svg = 8,
-    height_svg = 4,
-    tooltip_extra_css = "
-    font-family: Roboto; 
-    background-color: #000; 
-    color: #fff; font-size: 10px;
-    padding: 5px;"
-  ) %>% 
-  prependContent(
-    tags$link(
-      href = "https://fonts.googleapis.com/css?family=Roboto:400,700", 
-      rel = "stylesheet"
-    )
-  ) -> chart_trends_line.wdgt
-
-saveWidget(
-  widget = chart_trends_line.wdgt,
-  file = "../figs/06-topic-trends-line.html",
-  selfcontained = FALSE,
-  libdir = "../figs/js",
-  background = "#fafafa"
-)
-
-chart_trends_line.wdgt
-
-```
-
-```{r Trend to reactions, eval = TRUE}
-
-# Prepare dataset for joy plot
-posts_classification.dt %>% 
-  inner_join(
-    btw %>% 
-      select(
-        document = title, 
-        news_page = site, 
-        title, 
-        date
-      ),
-    by = "document"
-  ) %>% 
-  inner_join(topics_mapping.dt, by = "topic") %>% 
-  inner_join(
-    btw %>% 
-      group_by(document = title) %>%
-      summarise(reactions = sum(fb_shares)) %>%
-      ungroup(),
-    by = "document"
-  ) %>%
-  group_by(
-    topic_name, 
-    # 8 hour time difference (Manila)
-    week = floor_date(date, "week")
-  ) %>% 
-  summarise(
-    num_articles  = sum(allocation),
-    num_reactions = sum(reactions * allocation)
-  ) %>%
-  #mutate(peak = week[num_articles == max(num_articles)]) %>%
-  ungroup() %>%
-  arrange(week) %>%
-  mutate(
-    topic_name = factor(topic_name, levels = rev(unique(topic_name))),
-    # ID needed for linking back information after tweening frames
-    id = as.character(row_number()),
-    # Maximum height for ridgeline is 9
-    articles_height = num_articles/max(num_articles) * 9,
-    reactions_height = num_reactions/max(num_reactions) * 9
-  ) ->
-  posts_time_trend.dt
-
-# Prepare animated dataset
-bind_rows(
-  # Articles
-  posts_time_trend.dt %>% 
-    transmute(id, time = 0,  ht = articles_height , op = 0),
-  # Reactions
-  posts_time_trend.dt %>% 
-    transmute(id, time = 10, ht = reactions_height, op = 1),
-  # Return to articles
-  posts_time_trend.dt %>% 
-    transmute(id, time = 20, ht = articles_height , op = 0)
-) %>%
-  # Add cubic easing
-  mutate(ease = "cubic-in-out") %>%
-  tween_elements("time", "id", "ease") %>%
-  # Add back the topic name and week
-  inner_join(
-    posts_time_trend.dt %>% select(topic_name, week, id), 
-    by = c(".group" = "id")
-  ) ->
-  posts_time_trend.adt
-
-# Create labels above the chart (what news outlets post vs what we react to)
-posts_time_trend.adt %>%
-  group_by(.frame) %>%
-  summarise(
-    opacity    = mean(op),
-    range_week = max(week) - min(week),
-    min_week   = min(week),
-    num_topics = n_distinct(topic_name)
-  ) %>% 
-  ungroup() -> 
-  posts_time_trend_labels.adt
-
-```
-
-```{r Trend to reactions plot, eval = TRUE}
-
-# Create animated pot
-posts_time_trend.adt %>%
-  ggplot(aes(x = week, y = topic_name, height = ht, 
-             fill = topic_name, frame = .frame)) +
-  geom_ridgeline(color = NA, alpha = 0.5) +
-  geom_text(
-    data = posts_time_trend_labels.adt,
-    aes(x = min_week + 0.25 * range_week, 
-        y = num_topics + 3.5, 
-        alpha = 1 - opacity, 
-        frame = .frame),
-    label = "What news outlets publish", color = "forestgreen",
-    family = "Roboto", fontface = "bold", size = 9,
-    inherit.aes = FALSE
-  ) +
-  geom_text(
-    data = posts_time_trend_labels.adt,
-    aes(x = min_week + 0.75 * range_week, 
-        y = num_topics + 3.5, 
-        alpha = opacity, 
-        frame = .frame),
-    label = "What we react to", color = "firebrick",
-    family = "Roboto", fontface = "bold", size = 9,
-    inherit.aes = FALSE
-  ) +
-  geom_text(
-    data = posts_time_trend_labels.adt,
-    aes(x = min_week + 0.55 * range_week, 
-        y = num_topics + 3.5, 
-        frame = .frame),
-    label = "VS",
-    family = "Roboto", fontface = "bold", size = 7,
-    inherit.aes = FALSE
-  ) +
-  scale_x_datetime(expand = c(0, 0)) +
-  theme(
-    legend.position = "none",
-    panel.border    = element_blank(),
-    axis.title      = element_blank(),
-    panel.grid.major.x = element_blank(),
-    panel.grid.minor.x = element_blank(),
-    plot.caption      = element_text(size = 9)
-  ) + 
-  labs(
-    caption = "
-DATA SOURCE: Webhose.io, Eventbride.com
-CHART NOTE: Topics were derived through Latent Dirichlet Allocation (LDA) with 40 topics for online news articles in 2017 containing the term 'Bundestagswahl'
-    "
-  ) ->
-  posts_time_trend.agg
-
-gganimate(
-  p = posts_time_trend.agg,
-  filename = "../figs/09-reactions-vs-articles.gif",
-  title_frame = FALSE,
-  interval = 1/10,
-  ani.width = 900,
-  ani.height = 600
-)
-
-```
-
-![Articles to Reactions](../figs/09-reactions-vs-articles.gif)
-
-### Topic Distribution by News Page
-
-#### Distribution
-
-A common accusation leveled against traditional news media is the amount of bias in reporting various topics. We try to explore the topic distribution of news articles.
-
-```{r Data for topic distribution chart}
-
-set.seed(7292)
-posts_classification.dt %>% 
-  inner_join(
-    btw %>% select(document = title, news_page = site, title),
-    by = "document"
-  ) %>%
-  inner_join(topics_mapping.dt, by = "topic") %>% 
-  group_by(news_page, topic_name) %>%
-  summarise(
-    articles = sum(allocation),
-    sample_articles = 
-      paste0(
-        "<li>", sample(document, pmin(3, length(document))), "</li>",
-        collapse = "<br>"
-      )
-  ) %>%
-  ungroup() %>% 
-  group_by(news_page) %>% 
-  mutate(perc_articles = articles/sum(articles)) %>% 
-  ungroup() %>%
-  # left_join(
-  #   top_100_fbpages.dt %>% select(news_page = page_name, page_title), 
-  #   by = "news_page"
-  # ) %>% 
-  mutate(
-    tooltip_text = 
-      paste0(
-        "<b>", comma(round(articles, 0)), " (", percent(perc_articles), 
-        ") </b> of articles from <b>", news_page, 
-        "</b> fall under <b>", topic_name, "</b><br><br>Sample Articles:<br><ul>",
-        sample_articles, "</ul>"
-      ) %>% str_replace_all("'", "")
-  ) ->
-  news_page_distribution.dt
-```
-
-```{r Topic distribution chart, eval = TRUE}
-{
-  news_page_distribution.dt %>% 
-    ggplot(aes(x = news_page, y = perc_articles, fill = topic_name)) +
-    geom_bar_interactive(
-      aes(tooltip = tooltip_text),
-      position = position_stack(), 
-      stat = "identity", color = "darkgray"
-    ) +
-    scale_y_continuous(
-      name = "Percent of Articles", 
-      labels = percent,
-      expand = c(0, 0)
-    ) +
-    theme(
-      legend.position = "none",
-      axis.title.y = element_blank(),
-      legend.background = element_rect("#fafafa"),
-      plot.background   = element_rect("#fafafa", "#fafafa"),
-      plot.subtitle     = element_text(size = 8),
-      plot.caption      = element_text(size = 7),
-      plot.title        = element_text(size = 18)
-    ) +
-    coord_flip() +
-    scale_fill_viridis(discrete = TRUE) +
-    labs(
-      title = "BIAS AND BALANCE",
-      subtitle = "Topic distribution of online news articles per news page, 2017\n(Hover over each bar to see the topic and sample articles)",
-      caption = "
-DATA SOURCE: Facebook Graph API
-
-CHART NOTES:
-  1. The news pages are arranged in descending order in terms of number of articles
-  2. Topics were derived through Latent Dirichlet Allocation (LDA) with 40 topics
-  3. Articles were classified according to the topic that has the highest probability
-      "
-    )
-} %>% 
-  ggiraph(
-    ggobj = .,
-    width_svg = 12,
-    height_svg = 8,
-    width = 1,
-    tooltip_extra_css = "
-    font-family: Roboto; 
-    background-color: #000; 
-    color: #fff; font-size: 10px;
-    padding: 5px;"
-  ) %>% 
-  prependContent(
-    tags$link(
-      href = "https://fonts.googleapis.com/css?family=Roboto:400,700", 
-      rel = "stylesheet"
-    )
-  ) -> chart_topic_distribution.wdgt
-
-saveWidget(
-  widget = chart_topic_distribution.wdgt,
-  file = "../figs/04-topic-distribution-pages.html",
-  selfcontained = FALSE,
-  libdir = "../figs/js",
-  background = "#fafafa"
-)
-
-chart_topic_distribution.wdgt
-
-```
-
-#### Topic Concentration
-
-A common criticism leveled against news media sites is that there is undue emphasis on a particular topic.
-One way to measure concentration across different topics is the Herfindahl-Hirschman Index (HHI) which is simply $\Sigma_n{s^2}$ where $s$ is the share of each topic.
-
-```{r Topic concentration chart, eval = TRUE}
-
-{
-  news_page_distribution.dt %>% 
-    group_by(news_page) %>% 
-    arrange(desc(articles)) %>% 
-    summarise(
-      hh_index  = sum(perc_articles ^ 2),
-      t3_topics = paste0(topic_name %>% head(3), collapse = "<br>")
-    ) %>% 
-    ungroup() %>% 
-    arrange(hh_index) %>% 
-    mutate(news_page = factor(news_page, unique(news_page))) %>% 
-    ggplot(aes(x = news_page, y = hh_index * 100)) +
-    geom_bar_interactive(
-      aes(
-        tooltip = 
-          paste0("<b>Top Topics:</b><br>", t3_topics) %>% 
-          str_replace_all("'", "")
-      ),
-      stat = "identity", 
-      fill = c("#008B45")
-    ) +
-    geom_text(aes(label = comma(round(hh_index * 100, 1))), hjust = 1.5, 
-              color = "white", family = "Roboto") +
-    scale_y_log10(
-      name = "Herfindahl-Hirschman Index (HHI)\n(100 = most concentrated)",
-      expand = c(0, 0)
-    ) +
-    labs(
-      title = "TOPIC CONCENTRATION OF PHILIPPINE NEWS PAGES",
-      subtitle = "Herfindahl-Hirschman Index (HHI)",
-      caption = "
-DATA SOURCE: Facebook Graph API
-
-CHART NOTES:
-  1. Hover over each tile to see infomration and to see top topics
-  2. Topics were derived through Latent Dirichlet Allocation (LDA) with 40 topics
-  3. Articles were classified according to the topic that has the highest probability
-
-TROY JAMES PALANCA | TJPALANCA.COM
-      "
-    ) +
-    coord_flip() +
-    theme(
-      axis.title.y       = element_blank(),
-      panel.grid.major.y = element_blank(),
-      plot.background   = element_rect("#fafafa", "#fafafa"),
-      plot.subtitle      = element_text(size = 10),
-      plot.caption       = element_text(size = 8),
-      plot.title         = element_text(size = 16)
-    )
-} %>% 
-  ggiraph(
-    ggobj = .,
-    width_svg = 10,
-    height_svg = 8,
-    width = 1,
-    tooltip_extra_css = "
-    font-family: Roboto; 
-    background-color: #000; 
-    color: #fff; font-size: 16px;
-    padding: 5px;"
-  ) %>% 
-  prependContent(
-    tags$link(
-      href = "https://fonts.googleapis.com/css?family=Roboto:400,700", 
-      rel = "stylesheet"
-    )
-  ) -> chart_topic_concentration.wdgt
-
-saveWidget(
-  widget = chart_topic_concentration.wdgt,
-  file = "../figs/05-topic-concentration.html",
-  selfcontained = FALSE,
-  libdir = "../figs/js",
-  background = "#fafafa"
-)
-
-chart_topic_concentration.wdgt
-
-```
+![Facebook news samples](../figs/02-stm-topic-classification-sample.png)

### 2017-11-02 paper/R/02_combine.Rmd
new estimation

--- 2017-10-31 paper/R/02_combine.Rmd
@@
 ```{r}
-pat <- 'Aus unserem Netzwerk[^"]*'
+btw %>%
+  # remove articles that contain a daily overview
+  filter(!grepl("News des Tages", title.text)) %>%
+  # remove articles that dont contain text
+  filter(!grepl('</div>', title.text)) -> btw
+```
+
+```{r}
+pat <- '</div>'
 btw %>%
@@
 ```{r}
-mystopwords <- c("focus","online","spiegel", "stern", "handelsblatt", "de", "bild","bildplus", "zeit", "ersten", "tagesschau", "wdr", "ndr", "ich","sie","passwort","kommentar","wurde","ihr","der","im","artikel","mehr","ihren","foto","e", "uhr","videolänge","dass","mindestens","das","mail","die","schon","neuer abschnitt", "login", "loggen", "inaktiv", "nwmi", "nwnoa", "polizei","beim","dpa","video","quelle","afp","witters","fotogalerie", "registrierter","als","spiegel","vielen","in","es","bitte","dank","unserer","nutzer","sei","beitrag","user","seit","zeichen", "datenschutzerklärung","premium","nutzungsbedingungen","nutzungsrechte","pflichtfelder","registrierung","anzeige","großbuchstaben","sonderzeichen","html","seitennavigation","fullscreen","statista","club","sagte","borenda","spreepicture","shopübersicht")
+mystopwords <- c("focus","online","spiegel", "stern", "handelsblatt", "de", "bild","bildplus", "zeit", "ersten", "tagesschau", "wdr", "ndr", "ich","sie","passwort","kommentar","wurde","ihr","der","im","artikel","mehr","ihren","foto","e","seien", "uhr","videolänge","dass","mindestens","das","mail","die","schon","neuer abschnitt", "login", "loggen", "inaktiv", "nwmi", "nwnoa", "polizei","beim","dpa","video","quelle","afp","witters","fotogalerie","wurden","worden","wegen","sagt","immer","gibt","geht", "registrierter","als","spiegel","vielen","in","es","bitte","dank","unserer","nutzer","sei","beitrag","user","seit","zeichen", "datenschutzerklärung","premium","nutzungsbedingungen","nutzungsrechte","pflichtfelder","registrierung","anzeige","großbuchstaben","sonderzeichen","html","seitennavigation","fullscreen","statista","club","sagte","borenda","spreepicture","shopübersicht")
 

### 2017-11-02 paper/R/03_stm.Rmd
new estimation

--- 2017-11-02 paper/R/03_stm.Rmd
@@
   library(tibble)      # Better data frames
+  library(data.table)
 
@@
   library(tweenr)      # Tweening charts
+  library(igraph)
 
@@
 ```{r caching, echo = FALSE}
-load("../output/models/LDAGibbs 40 .Rda")
 load("../output/models/STM 40 .Rda")
-#load("../output/btw_combined.Rda")
 knitr::opts_chunk$set(eval = TRUE, warning = FALSE)
@@
 
-We then train the LDA on the full dataset, with $k = 40$.
-
-```{r eval=FALSE, include=FALSE}
-## Run LDA using Gibbs sampling
-
-#Set parameters for Gibbs sampling (see https://eight2late.wordpress.com/2015/09/29/a-gentle-introduction-to-topic-modeling-using-r/)
-burnin <- 1000
-iter <- 1000
-keep <- 50
-
+We then train the Structural Topic Model on the full dataset, with $k = 40$.
+
+```{r}
 k = 40 # Topics
-```
-
-```{r}
-t1 <- Sys.time()
-ldaOut <-LDA(dtm, k, method="Gibbs", control=list(burnin=burnin, iter = iter, keep = keep))
-t2 <- Sys.time()
-t2 - t1
-
-save(ldaOut, btw, dtm, file=paste("../output/models/LDAGibbs",k,".Rda"))
-
-# ---------- STM ----------- #
 
@@
 # Word-topic probabilities
-ldaOut %>% tidy("beta") -> posts.wtp
+stmOut %>% tidy("beta") %>% filter(!is.na(topic)) -> posts.wtp
 
 # Document-topic probabilities
-ldaOut %>% tidy("gamma") -> posts.dtp
-
+stmOut %>% tidy("gamma") -> posts.dtp
 ```
@@
 
+labelTopics(stmOut, n=7)
 ```
@@
 # The topics function from the package is used to extract the most likely topic for each document 
-btw.topics <- topics(ldaOut, 2)
+btw.topics <- topics(stmOut, 2)
 

### 2017-11-02 paper/R/03_topic model.Rmd
new estimation

@@
 ```{r caching, echo = FALSE}
-load("../output/models/LDAGibbs 40 .Rda")
-#load("../output/btw_combined.Rda")
+#load("../output/models/LDAGibbs 40 .Rda")
+load("../output/btw_combined.Rda")
 knitr::opts_chunk$set(eval = TRUE, warning = FALSE)
 
-btw$articleID <- rownames(btw)
+btw$articleID <- as.integer(rownames(btw))
 ```
@@
 # Build Corpus
-btw %>%
-  filter(nchar(text_cleaned) > 5) -> btw
-
-# Build corpus
 df.lda <- Corpus(VectorSource(btw$text_cleaned))
@@
 dtm <- DocumentTermMatrix(df.lda)
-# Assign name to docs
-rownames(dtm) <- make.unique(btw$title)
 ```
@@
 doctopics.df %>%
-  transmute(title = rownames(.),
-            topic = V1) -> doctopics.df
-
+  transmute(topic = V1) -> doctopics.df
 doctopics.df$articleID <- as.integer(rownames(doctopics.df))
@@
 # Add Topic to origian DF
+btw %>%
+  inner_join(.,doctopics.df, by="articleID") -> btw
+
 topics_mapping.dt <- btw %>%  
-  mutate(articleID = as.integer(articleID)) %>%
-  inner_join(.,doctopics.df, by="articleID") %>%
-
   group_by(topic) %>%
   slice(1) %>%
-  select(topic, title.text, articleID) 
+  select(topic,title, title.text, articleID) 
 ```
@@
 set.seed(9272)
+
+posts_classification.sdt <-
 posts.dtp %>% 
-  group_by(title = document) %>% 
+  group_by(articleID = as.numeric(document)) %>% 
   summarise(topic = min(topic[gamma == max(gamma)]), gamma = max(gamma)) %>% 
   ungroup()  %>%
-  inner_join(btw %>% select(title, articleID), by = "title") %>% 
-  inner_join(topics_mapping.dt, by = "topic") %>% 
+  inner_join(btw %>% select(title, articleID), by = "articleID") %>%
+  inner_join(topics_mapping.dt %>% select(topic, topic_name), by = "topic") %>% 
   mutate(topic_title = 
@@
   top_n(300, gamma) %>%
-  sample_n(5, replace = TRUE) %>% 
+  sample_n(7, replace = TRUE) %>% 
   mutate(row = row_number()) %>% 
-  ungroup() ->
-  posts_classification.sdt
+  ungroup()
 
@@
 ![Facebook news samples](../figs/02-topic-classification-sample.png)
+
+#### Topic-Media Distribution
+
+```{r}
+ggsave(
+  plot = {
+    btw %>%
+      ggplot(aes(as.factor(topic), fill =site)) +
+      geom_bar() +
+      scale_x_discrete(labels = paste0(topicLabel$topic,":",topicLabel$topic_name)) +
+      theme(axis.text.x = element_text(size=8, angle=90),
+        legend.text = element_text(size = 8)) +
+      labs(x = "", fill = "", 
+           title    = "Topic Frequency by Media",
+        subtitle = "")
+
+  },
+
+  filename = "../figs/01-topic-distribution.png",
+  device = "png",
+  dpi = 600
+    )
+```
+![Facebook news samples](../figs/01-topic-distribution.png)
 
@@
   mutate(allocation = 1/n()) %>% 
-  ungroup() ->
+  ungroup() %>%
+  mutate(document = as.numeric(document)) ->
   posts_classification.dt
@@
     btw %>% 
-      select(document = title, date, 
+      select(document = articleID, date, 
              title, articleID) %>% 
@@
   # Add topic information
-  left_join(topics_mapping.dt, by = "topic") %>%
+  left_join(topics_mapping.dt %>% select(topic, topic_name), by = "topic") %>%
   # Summarise into tidy dataframe
@@
     sample_articles = 
-      paste0("<li>", sample(document, 3, replace = TRUE ), "</li>", collapse = "<br>")
+      paste0("<li>", sample(title, 3, replace = TRUE ), "</li>", collapse = "<br>")
   ) %>% 
@@
       select(
-        document = title, 
+        document = articleID, 
         news_page = site, 
@@
     btw %>% 
-      group_by(document = title) %>%
+      group_by(document = articleID) %>%
       summarise(reactions = sum(fb_shares)) %>%
@@
   inner_join(
-    btw %>% select(document = title, news_page = site, title),
+    btw %>% select(document = articleID, news_page = site, title),
     by = "document"
@@
 ```
-
-#### Topic Concentration
-
-A common criticism leveled against news media sites is that there is undue emphasis on a particular topic.
-One way to measure concentration across different topics is the Herfindahl-Hirschman Index (HHI) which is simply $\Sigma_n{s^2}$ where $s$ is the share of each topic.
-
-```{r Topic concentration chart, eval = TRUE}
-
-{
-  news_page_distribution.dt %>% 
-    group_by(news_page) %>% 
-    arrange(desc(articles)) %>% 
-    summarise(
-      hh_index  = sum(perc_articles ^ 2),
-      t3_topics = paste0(topic_name %>% head(3), collapse = "<br>")
-    ) %>% 
-    ungroup() %>% 
-    arrange(hh_index) %>% 
-    mutate(news_page = factor(news_page, unique(news_page))) %>% 
-    ggplot(aes(x = news_page, y = hh_index * 100)) +
-    geom_bar_interactive(
-      aes(
-        tooltip = 
-          paste0("<b>Top Topics:</b><br>", t3_topics) %>% 
-          str_replace_all("'", "")
-      ),
-      stat = "identity", 
-      fill = c("#008B45")
-    ) +
-    geom_text(aes(label = comma(round(hh_index * 100, 1))), hjust = 1.5, 
-              color = "white", family = "Roboto") +
-    scale_y_log10(
-      name = "Herfindahl-Hirschman Index (HHI)\n(100 = most concentrated)",
-      expand = c(0, 0)
-    ) +
-    labs(
-      title = "TOPIC CONCENTRATION OF PHILIPPINE NEWS PAGES",
-      subtitle = "Herfindahl-Hirschman Index (HHI)",
-      caption = "
-DATA SOURCE: Facebook Graph API
-
-CHART NOTES:
-  1. Hover over each tile to see infomration and to see top topics
-  2. Topics were derived through Latent Dirichlet Allocation (LDA) with 40 topics
-  3. Articles were classified according to the topic that has the highest probability
-
-TROY JAMES PALANCA | TJPALANCA.COM
-      "
-    ) +
-    coord_flip() +
-    theme(
-      axis.title.y       = element_blank(),
-      panel.grid.major.y = element_blank(),
-      plot.background   = element_rect("#fafafa", "#fafafa"),
-      plot.subtitle      = element_text(size = 10),
-      plot.caption       = element_text(size = 8),
-      plot.title         = element_text(size = 16)
-    )
-} %>% 
-  ggiraph(
-    ggobj = .,
-    width_svg = 10,
-    height_svg = 8,
-    width = 1,
-    tooltip_extra_css = "
-    font-family: Roboto; 
-    background-color: #000; 
-    color: #fff; font-size: 16px;
-    padding: 5px;"
-  ) %>% 
-  prependContent(
-    tags$link(
-      href = "https://fonts.googleapis.com/css?family=Roboto:400,700", 
-      rel = "stylesheet"
-    )
-  ) -> chart_topic_concentration.wdgt
-
-saveWidget(
-  widget = chart_topic_concentration.wdgt,
-  file = "../figs/05-topic-concentration.html",
-  selfcontained = FALSE,
-  libdir = "../figs/js",
-  background = "#fafafa"
-)
-
-chart_topic_concentration.wdgt
-
-```

### 2017-11-06 paper/R/01_prepare_eventbride.Rmd
writing

@@
 
-df <- read_csv("../data/eventbride/eventbride_okt_18.csv")
+df <- read_csv("../data/eventbride/eventbride_03_sep.csv")
 ```
@@
 ```{r}
+nov <- df
 # Save file
-save(df, file="../output/news_cleaned_eventbride.Rda")
+save(nov, file="../output/news_cleaned_eventbride_nov.Rda")
 ```
-
-```{r}
-pat <- 'ejf[^"]*'
-df %>%
-  filter(grepl(pat, text, perl = TRUE)) %>%
-  group_by(site) %>%
-  tally(sort = TRUE)
-```
-
-```{r}
-as.data.frame(str_match(df$text, pat)) ->test
-test %>%
-  filter(!is.na(test)) %>%
-  .[1]
-```
-
-# Pre-Process Text
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
-clean.text <- function(x)
-  {
-  # All
-  x = gsub("Getty Images", "", x)
-
-  # Bild.de
-  x = gsub("Shopübersicht Top Gutscheine", "", x)
-
-  # Handelsblatt.com
-  x = gsub("RSS Feed", "", x)
-  x = gsub("Deutsche Presse Agentur", "", x)
-
-  # FOCUS.de
-  x = gsub("FOCUS Online/Wochit", "", x)
-  x = gsub("Vielen Dank! Ihr Kommentar wurde abgeschickt.", "", x)
-  x = gsub('Im Interesse unserer User[^"]*', "", x, perl = TRUE)
-  x = gsub('Sie haben noch 800[^"]*', "", x, perl = TRUE)
-  x = gsub('Erzählen Sie auf FOCUS Online über Ihren Heimatort Teilen Sie Ihren Artikel und Ihr Foto', "", x, perl = TRUE)
-  x = gsub("Bericht schreiben", "", x)
-  x = gsub("Vielen Dank! Ihr Kommentar wurde abgeschickt.", "", x)
-  x = gsub("Hier können Sie selbst Artikel verfassen:","", x)
-  x = gsub("Live-Ticker", "", x)
-  x = gsub('Aus unserem Netzwerk[^"]*', "", x, perl = TRUE)
-
-  # Spiegel.de
-  x = gsub("7 mal 17", "", x)
-  x = gsub("Zur Startseite Diesen Artikel... Drucken Feedback Nutzungsrechte", "", x)
-  x = gsub('Liebe Leserin, lieber Leser,\num diesen[^"]*', "", x)
-  x = gsub('Liebe Leserin, lieber Leser, um diesen[^"]*', "", x)
-  x = gsub('ejf[^"]*', "", x)
-  x = gsub('tjf[^"]*', "", x)
-
-  # Zeit.de
-  x = gsub("Inhalt Seite", "", x)
-
-  # Tagesschau
-  x = gsub('Hinweis.+?(?=(einfügen))', "", x, perl = TRUE)
-
-  return(x)
-}
-
-# apply function to dataframe
-df$text_cleaned <- clean.text(df$text)
-```
-
-```{r}
-df$text_cleaned <- gsub("[[:punct:]]", " ", df$text_cleaned)
-df$text_cleaned <- gsub("[[:cntrl:]]", " ", df$text_cleaned)
-df$text_cleaned <- gsub("[[:digit:]]", " ", df$text_cleaned)
-df$text_cleaned <- gsub("^[[:space:]]+", " ", df$text_cleaned)
-df$text_cleaned <- gsub("[[:space:]]+$", " ", df$text_cleaned)
-df$text_cleaned <- tolower(df$text_cleaned)
-```
-
-```{r}
-# Save file
-save(df, file="../output/news_cleaned_eventbride.Rda")
-```
-
-## Remove Stopwords
-```{r}
-df$text_cleaned<- removeWords(df$text_cleaned, stopwords("german"))
-```
-
-### Remove customized stopwords
-```{r}
-mystopwords <- c("focus","online","spiegel", "stern", "handelsblatt", "de", "bild","bildplus", "zeit", "ersten", "tagesschau", "wdr", "ndr", "ich","sie","passwort","kommentar","wurde","ihr","der","im","artikel","mehr","ihren","foto","e", "uhr","videolänge","dass","mindestens","das","mail","die","schon","neuer abschnitt", "login", "loggen", "inaktiv", "nwmi", "nwnoa", "polizei","beim","dpa","video","quelle","afp","witters","fotogalerie", "registrierter","als","spiegel","vielen","in","es","bitte","dank","unserer","nutzer","sei","beitrag","user","seit","zeichen", "datenschutzerklärung","premium","nutzungsbedingungen","nutzungsrechte","pflichtfelder","registrierung","anzeige","großbuchstaben","sonderzeichen","html","seitennavigation","fullscreen","statista","club","sagte","borenda","spreepicture","shopübersicht")
-
-mystopwords <- distinct(as.data.frame(mystopwords))
-
-df$text_cleaned<- removeWords(df$text_cleaned, mystopwords$mystopwords)
-```
-
-```{r}
-df -> df2
-```
-
-```{r}
-save(df2, file="../output/news_cleaned_eventbride.Rda")
-```
-
-## Reduce Dataframe
-```{r}
-keeps <- c( "welt.de","spiegel.de","stern.de","focus.de","zeit.de","bild.de" )
-
-df2 %>%
-  filter(isDuplicate == "False") %>%
-  filter(site %in% keeps) %>%
-  filter(grepl("bundestagswahl", text, ignore.case = TRUE)) -> btw2
-```
-
-```{r}
-save(df2, btw2, file="../output/news_btw2.Rda")
-```

### 2017-11-06 paper/R/02_combine.Rmd
writing

--- 2017-10-31 paper/R/02_combine.Rmd
@@
 libs <- c("tidytext","tidyr","readr","lubridate","tm","stm","RColorBrewer",
-          "plyr","dplyr","class","knitr","kableExtra","cldr","data.table",
+          "plyr","dplyr","class","knitr","data.table","parallel","SnowballC",
           "htmlTable","ggplot2","gridExtra","jsonlite","stringr","scales","rjson")
@@
 load("../output/news_cleaned.Rda")
-df2 <- read_csv("../data/eventbride/eventbride_okt_18.csv")
+okt <- read_csv("../data/eventbride/eventbride_okt_18.csv")
+nov <- read_csv("../data/eventbride/eventbride_nov_03.csv")
 ```
@@
 ```{r}
-## Extract site
-df2$site <- str_extract(df2$source, "(?<='uri': ')[A-z][^']*")
+### Oktober ###
+# Extract site
+okt$site <- str_extract(okt$source, "(?<='uri': ')[A-z][^']*")
 
 # number of Facebook shares
-df2$fb_shares <- str_extract(df2$shares, "(?<='facebook': )[0-9]*")
-df2$fb_shares <- ifelse(is.na(df2$fb_shares),0, df2$fb_shares)
-df2$fb_shares <- as.integer(df2$fb_shares)
+okt$fb_shares <- str_extract(okt$shares, "(?<='facebook': )[0-9]*")
+okt$fb_shares <- ifelse(is.na(okt$fb_shares),0, okt$fb_shares)
+okt$fb_shares <- as.integer(okt$fb_shares)
 
 # Text Length
-names(df2) <- gsub("body", "text", names(df2))
-df2$text_length <- sapply(gregexpr("\\S+", df2$text), length)
+names(okt) <- gsub("body", "text", names(okt))
+okt$text_length <- sapply(gregexpr("\\S+", okt$text), length)
+
+### November ###
+# Extract site
+nov$site <- str_extract(nov$source, "(?<='uri': ')[A-z][^']*")
+
+# number of Facebook shares
+nov$fb_shares <- str_extract(nov$shares, "(?<='facebook': )[0-9]*")
+nov$fb_shares <- ifelse(is.na(nov$fb_shares),0, nov$fb_shares)
+nov$fb_shares <- as.integer(nov$fb_shares)
+
+# Text Length
+names(nov) <- gsub("body", "text", names(nov))
+nov$text_length <- sapply(gregexpr("\\S+", nov$text), length)
 ```
@@
 keeps <- c( "welt.de","spiegel.de","stern.de","focus.de","zeit.de","bild.de" )
+keys <- paste(c("bundestagswahl","koalition"), collapse = "|")
 
@@
   filter(site %in% keeps) %>%
-  filter(grepl("bundestagswahl", text, ignore.case = TRUE)) -> btw1
+  filter(grepl(keys, text, ignore.case = TRUE)) -> btw1
 
-df2 %>%
+okt %>%
+  filter(isDuplicate == "False") %>%
   filter(site %in% keeps) %>%
-  filter(grepl("bundestagswahl", text, ignore.case = TRUE)) -> btw2
+  filter(grepl(keys, text, ignore.case = TRUE)) -> btw2
+
+nov %>%
+  filter(isDuplicate == "False") %>%
+  filter(site %in% keeps) %>%
+  filter(grepl(keys, text, ignore.case = TRUE)) -> btw3
 ```
@@
   btw1[, common_cols], 
-  btw2[, common_cols]
+  btw2[, common_cols],
+  btw3[, common_cols]
 )
+
 ```
@@
 btw %>%
-  # Keep unique observations
-  distinct(title, site, .keep_all = TRUE) %>%
-  # Remove Articles after 10.10.2017
-  filter(date < as.Date("2017-10-10")) -> btw
+  group_by(title, site) %>%
+  ungroup() %>%
+  arrange(desc(fb_shares)) %>%
+  distinct(title,site, .keep_all = TRUE) -> btw
+
+btw %>%
+  filter(date < as.Date("2017-10-29")) -> btw
 ```
@@
 ```{r}
-pat <- 'Aus unserem Netzwerk[^"]*'
 btw %>%
-  filter(grepl(pat, text, perl = TRUE)) %>%
+  # remove articles that contain daily overviews
+  filter(!grepl("Elbvertiefung", title.text)) %>%
+  filter(!grepl("News des Tages", title.text)) %>%
+  # remove articles that dont contain text
+  filter(!grepl('</div>', title.text)) -> btw
+```
+
+```{r}
+pat <- 'Florian Gathmann[^\n]*'
+btw %>%
+  filter(grepl(pat, title.text, perl = TRUE, ignore.case = TRUE)) %>%
+  #select(text) %>%
+  #.[1,] %>%
+  #htmlTable::htmlTable()
   group_by(site) %>%
@@
 ```{r}
-as.data.frame(str_match(btw$text, pat)) ->test
+as.data.frame(str_match(btw$title.text, pat)) ->test
 test %>%
   filter(!is.na(test)) %>%
-  .[1]
+  .[1:100,]
 ```
@@
   x = gsub("Getty Images", "", x)
+  x = gsub('Startseite[^\n]*', "", x, ignore.case = TRUE, perl = TRUE)
 
@@
   x = gsub("Shopübersicht Top Gutscheine", "", x)
+  x = gsub('Politik Inland[^\n]*', "", x, perl = TRUE)
 
-  # Handelsblatt.com
-  x = gsub("RSS Feed", "", x)
-  x = gsub("Deutsche Presse Agentur", "", x)
+  # welt.de
+  x = gsub('Quelle: N24[^\n]*', "", x, perl = TRUE)
+  x = gsub('infocom[^\n]*', "", x, perl = TRUE, ignore.case = TRUE)
+  x = gsub('Infografik[^\n]*', "", x, perl = TRUE, ignore.case = TRUE)
+  x = gsub('versuchen Sie es[^.]*', "", x, perl = TRUE, ignore.case = TRUE)
+  x = gsub('Video konnte nicht[^\n]*', "", x, perl = TRUE, ignore.case = TRUE)
+  x = gsub('Welt twitter', "", x, perl = TRUE, ignore.case = TRUE)
 
   # FOCUS.de
-  x = gsub("FOCUS Online/Wochit", "", x)
+  x = gsub("FOCUS Online", "", x)
+  x = gsub('Wochit[^\n]*', "", x, perl = TRUE, ignore.case = TRUE)
   x = gsub("Vielen Dank! Ihr Kommentar wurde abgeschickt.", "", x)
@@
   x = gsub('tjf[^"]*', "", x)
+  x = gsub('Fotostrecke[^"]*', "", x, perl = TRUE, ignore.case = TRUE)
+  x = gsub('Florian Gathmann[^\n]*', "", x, perl = TRUE)
 
@@
   x = gsub("Inhalt Seite", "", x)
+  x = gsub('Seitennavig[^"]*',"", x, perl=TRUE)
+  x = gsub('Kartengeschichte[^"]*', "", x, perl = TRUE, ignore.case = TRUE)
 
-  # Tagesschau
-  x = gsub('Hinweis.+?(?=(einfügen))', "", x, perl = TRUE)
+  # Stern.de
+  x = gsub('Fullscreen[^\n]*', "", x, perl = TRUE)
 
@@
 ```{r}
-mystopwords <- c("focus","online","spiegel", "stern", "handelsblatt", "de", "bild","bildplus", "zeit", "ersten", "tagesschau", "wdr", "ndr", "ich","sie","passwort","kommentar","wurde","ihr","der","im","artikel","mehr","ihren","foto","e", "uhr","videolänge","dass","mindestens","das","mail","die","schon","neuer abschnitt", "login", "loggen", "inaktiv", "nwmi", "nwnoa", "polizei","beim","dpa","video","quelle","afp","witters","fotogalerie", "registrierter","als","spiegel","vielen","in","es","bitte","dank","unserer","nutzer","sei","beitrag","user","seit","zeichen", "datenschutzerklärung","premium","nutzungsbedingungen","nutzungsrechte","pflichtfelder","registrierung","anzeige","großbuchstaben","sonderzeichen","html","seitennavigation","fullscreen","statista","club","sagte","borenda","spreepicture","shopübersicht")
+mystopwords <- c("focus","online","spiegel", "stern", "handelsblatt", "de", "bild","bildplus", "zeit", "ersten", "tagesschau", "wdr", "ndr", "ich","sie","passwort","kommentar","wurde","ihr","der","im","artikel","mehr","ihren","foto","e","seien","comment", "uhr","videolänge","dass","mindestens","das","mail","die","schon","neuer abschnitt", "login", "loggen", "inaktiv", "nwmi", "nwnoa", "polizei","beim","dpa","video","quelle","afp","witters","fotogalerie","wurden","worden","wegen","sagt","immer","gibt","geht","spon", "registrierter","als","spiegel","vielen","in","es","bitte","dank","unserer","nutzer","sei","beitrag","user","seit","zeichen", "datenschutzerklärung","premium","nutzungsbedingungen","nutzungsrechte","pflichtfelder","registrierung","anzeige","großbuchstaben","sonderzeichen","html","seitennavigation","fullscreen","statista","club","sagte","borenda","spreepicture","shopübersicht")
 

### 2017-11-06 paper/R/03_stm.Rmd
writing

@@
 load("../output/models/STM 40 .Rda")
+#load("../output/btw_combined.Rda")
 knitr::opts_chunk$set(eval = TRUE, warning = FALSE)
 
-btw$articleID <- rownames(btw)
+#btw$articleID <- rownames(btw)
 ```
@@
 
-Social networks such as Facebook are becoming more and more important for online news services: an increasing number of their readers access the news pages via links in the networks.
-Users of Facebook, for example, can use their profile to share links to external websites - such as news portals - with their online friends.
-This has led to the development of social media into an important generator of traffic on the internet pages.
-In Germany, 94\% of online shared news articles in 2015 are distributed via Facebook, followed by Twitter with 3.5\% and Google+ with 2.3\% \citep{schiller_development_2016}.
-The advertising-financed business model of the media houses is based on the premise that users visit their websites in order to achieve high advertising revenues.
-For this reason, news agencies are particularly interested in finding out which topics are more likely shared on these platforms.
-\citet{schiller_development_2016} show, that social media users choose a certain site depending on the researched topic.
-FOCUS Online for example is targeted for articles from politics and business, sports news is more likely to be shared from Bild.de.
-
-While these static resorts give an indication on the content of an article, multiple articles in the same resort probably don't cover the same topics (and are not equally shared).
-Especially if the articles originate from different news portals.
-Furthermore, articles can contain more than one topic.
-We use a structural topic model to reveal the underlying topics of a collection of articles (a corpus), and how the articles exhibit them.
-We then estimate the effect of topic prevalence on the number of Facebook shares.
-
 ## Methodology
 
-Mapping raw text to one or more topics, without having prior knowledge on what those topics are, translates to an unsupervised classification problem on natural language.
-Within topic models the Latent Dirichlet Allocation (LDA) is a widely used technique, where each document (article) is viewed as a mixture of topics (represented by the document-topic distribution) and each topic is a mixture of unique terms (represented by the topic-term distribution).\cite{blei_latent_2003}
-
-This model views the text generation process as conforming to the following characteristics:
-
-  * A topic is a mixture of words. A topic is comprised of many words, and each word maps to one or more topics.
-  * A document (in this case, a news article), is a mixture of topics. Each document can be thought of as containing a proportion of words from each topic.
-
-To "learn" the topic prevalence and the topic-term distribution, collapsed Gibbs sampling\footnote{See Section \ref{section_gibbs} for a non-formal description of the Gibbs sampler} can be used.
-One of the important considerations of this model is that the number of topics $k$ must be known a-priori.
-
-![Research Strategy](../figs/research_strategy.png)
-
 ## Dataset
-
-To explore the effect of topic prevalence of an article on the times this article is shared on Facebook, we analyze a sample of 6307 news articles containing the term "Bundestagswahl" (Federal Election) dated from 01.06.2017 to 10.10.2017\footnote{German federal elections took place on 24th of September 2017.} and originated from six different german news sources.\footnote{Bild.de, Focus.de, Spiegel.de, Stern.de, Welt.de, Zeit.de} For each document in our sample, we observe the day it was written, the number of shares on Facebook and the newswire service publishing the article.
-We include the month the document was written and the news agency as covariates on topical prevalence.
-We also include news agency as a covariate affecting topical content to estimate how topics are discussed in different ways by different news agencies \citep{roberts_model_2016}.
-
-Figure -- shows the number of articles by news agency and the how many of these articles were shared on Facebook.
-
-```{r echo=FALSE}
-btw$shared <- ifelse(btw$fb_shares == 0, "0", NA)
-btw$shared <- ifelse(btw$fb_shares > 0 | btw$fb_shares >= 100, "0-100", btw$shared)
-btw$shared <- ifelse(btw$fb_shares > 100, "> 100", btw$shared)
-
+```{r}
+library(RColorBrewer)
+
+col <- brewer.pal(6,"Dark2")
+```
+
+```{r message=FALSE, warning=FALSE}
 btw %>%
-  ggplot(aes(site, fill=shared)) +
-  geom_bar(alpha = .7) +
+  group_by(date, site) %>%
+  summarise(obs = n()) %>%
+  ggplot(aes(date, obs, color = site)) +
+  geom_line() +
+  scale_color_manual(values = col) +
+  theme(legend.position="none") +
+  labs(x="", y="Count",color="")
+
+ggsave("../figs/timeline.png", plot = last_plot(), device = "png", 
+       dpi = 600)
+```
+
+```{r message=FALSE, warning=FALSE}
+btw %>%
+  ggplot(aes(site)) +
+  geom_bar(fill=col, alpha= .8) +
   labs(x="", y="Count")
-```
-
-```{r}
+
+ggsave("../figs/bar.png", plot = last_plot(), device = "png", 
+       dpi = 600)
+```
+
+```{r message=FALSE, warning=FALSE}
+btw %>%
+  ggplot(aes(date, site, size=fb_shares, color = site)) +
+  geom_point(show.legend = FALSE, alpha = .8) +
+  scale_color_manual(values = col) +
+  labs(x="", y="")
+
+ggsave("../figs/fb_shares.png", plot = last_plot(), device = "png", 
+       dpi = 600)
+```
+
+```{r message=FALSE, warning=FALSE}
+btw %>%
+  ggplot(aes(site, fb_shares)) +
+  stat_summary(fun.y="mean", geom="bar", fill = col, alpha = .8) +
+  labs(x="", y="")
+
+ggsave("../figs/fb_shares_mean.png", plot = last_plot(), 
+       dpi = 600)
+```
+
+```{r Tokenize}
 btw %>% 
   # Tokenize by word
-  unnest_tokens(word, text_cleaned, token = "words") ->
+  unnest_tokens(word, text_cleaned, token = "words") %>%
+  # Remove short words
+  filter(str_length(word) >= 3) ->
   # Assign to variable
-  posts_tokenized.dt
-
-# Remove short words
-posts_tokenized.dt %>% 
-  filter(str_length(word) >= 3) ->
   posts_tokenized.dt
@@
 
-## Analysis
-
-### LDA Training
+## Structural Topic Model
 
@@
 # Process data
-processed <- textProcessor(btw$text_cleaned, metadata = btw[,c("date","month","site","text_cleaned","text")],
+processed <- textProcessor(btw$text_cleaned, metadata = btw[,c("site","text_cleaned")],
                            wordLengths = c(2,Inf),
@@
 
-```{r}
+```{r eval=FALSE, include=FALSE}
 k = 40 # Topics
@@
            K=k, 
-           prevalence = ~site+s(month), 
-           content = ~site, 
+           prevalence = ~site, 
            data=out$meta, 
@@
 
-We can then assess the word-topic probabilities in order to get an idea of the topic that is most.
-
-Since we have over 30,000 unique terms in the corpus, we need to extract the top few words that most uniquely define each topic, so that we can more easily visualize and label them.
-We use the measure of relevance defined by Sievert and Shirley (2014)^[[Sievert and Shirley (2014).
-LDAvis: A method for visualizing and interpreting topics.
-*Stanford University.*](http://nlp.stanford.edu/events/illvi2014/papers/sievert-illvi2014.pdf)].
-Relevance of term $w$ to topic $k$ given a weight parameter $\lambda$ between 0 and 1 $r(w, k | \lambda)$ is computed as:
-
-$$
-r(w, k | \lambda) = \lambda\log(\phi_{kw}) + (1-\lambda)\log(\frac{\phi_{kw}}{p_w})
-$$
-
-where $\phi_{kw}$ is the probability of term $w$ for topic $k$, and $p_w$ is the empirical probability of the word in the corpus.
-$\lambda$ can be thought of as a weighting term between ranking by the probability of that word within the topic, and ranking by the lift over the overall probability in the corpus.
-
-In user studies, Sievert and Shirley (2004) found that a lambda value of 0.6 as an optimal value for allowing humans to identify the topics associated with the top words ranked by relevance.
-We use this same value for lambda.
+To get an idea of the topics, we take a look at the words that are associated with topics and label them accordingly.
+We then inspect the documents that are estimated to be highly associated with each topic.
+Figure --- shows a random sample of 7 posts from the 300 highest probability fits per topic.
 
@@
 posts.wtp %>%
+    filter(str_length(term) >= 3) %>%
   # Compute lambda and phi_kw
@@
 
-labelTopics(stmOut, n=7)
-```
-
-```{r Loading topic mappings}
-### Most likely Topics per Article
-
-# The topics function from the package is used to extract the most likely topic for each document 
-btw.topics <- topics(stmOut, 2)
-
+```
+
+```{r Label Topics}
+label <- labelTopics(stmOut, n=4)
+
+topicLabel <- as.data.frame(label$prob)
+topicLabel <- topicLabel %>%
+  transmute(topic = rownames(.),
+    topic_name = paste(V1,V2,V3,V4, sep = ", "))
+
+frex <- as.data.frame(label$frex)
+topicLabel <- topicLabel %>%
+  left_join(., 
+            frex %>%
+              transmute(topic = rownames(.),
+                frex = paste(V1,V2,V3,V4, sep=", ")),
+            by = "topic")
+
+lift <- as.data.frame(label$lift)
+topicLabel <- topicLabel %>%
+  left_join(., 
+            lift %>%
+              transmute(topic = rownames(.),
+                lift = paste(V1,V2,V3,V4, sep=", ")),
+            by = "topic")
+
+score <- as.data.frame(label$score)
+topicLabel <- topicLabel %>%
+  left_join(., 
+            score %>%
+              transmute(topic = rownames(.),
+                score = paste(V1,V2,V3,V4, sep=", ")),
+            by = "topic")
+
+rm(frex, lift, score)
+```
+
+```{r}
 # Create Dataframe
-doctopics.df <- as.data.frame(t(btw.topics))
-
-doctopics.df %>%
-  transmute(title = rownames(.),
-            topic = V1) -> doctopics.df
-
-doctopics.df$articleID <- as.integer(rownames(doctopics.df))
+theta <- as.data.frame(stmOut$theta)
+theta$topic <- colnames(theta)[apply(theta,1,which.max)]
+
+doctopics.df <- theta %>%
+  transmute(articleID = rownames(.),
+    topic = as.numeric(gsub("V","",topic)))
 
 # Add Topic to origian DF
+btw %>%
+  inner_join(.,doctopics.df, by="articleID") %>%
+  ## Combine with Topic label
+  left_join(., topicLabel %>%
+              select(topic_name, topic) %>%
+              mutate(topic = as.numeric(topic)), by="topic") -> btw
+
+# subset  
 topics_mapping.dt <- btw %>%
-  mutate(articleID = as.integer(articleID)) %>%
-  inner_join(.,doctopics.df, by="articleID") %>%
-
   group_by(topic) %>%
   slice(1) %>%
-  select(topic, title.text, articleID) 
-```
-
-```{r}
-### Create Topic Labels
-
-## Return the top 30 terms.
-btw.terms <- as.data.frame(terms(ldaOut, 30), stringAsFactors = FALSE)
-
-topicTerms <- btw.terms %>% gather(Topic)
-topicTerms <- cbind(topicTerms, Rank = rep(1:30))
-topicTerms <- topicTerms %>% filter(Rank < 5)
-
-topicTerms <- topicTerms %>% mutate(topic = stringr::word(Topic, 2))
-topicTerms$topic <- as.numeric(topicTerms$topic)
-
-topicLabel <- data.frame()
-for (i in 1:40){
-  z <- dplyr::filter(topicTerms, topic==i)
-  l <- as.data.frame(paste(z[1,2], z[2,2], z[3,2], z[4,2], sep = " "), stringAsFactors = FALSE)
-  topicLabel <- rbind(topicLabel, l)
-}
-colnames(topicLabel) <- c("topic_name")
-topicLabel$topic <- as.integer(rownames(topicLabel))
+  select(topic, title.text, articleID, topic_name) 
 ```
@@
 topics_mapping.dt %>%
-  left_join(., topicLabel, by="topic") -> topics_mapping.dt
+  left_join(., topicLabel %>%
+              select(topic_name, topic) %>%
+              mutate(topic = as.numeric(topic)), by="topic") -> topics_mapping.dt
+```
+
+## Topic Summary
+```{r}
+plot(stmOut, type = "summary", xlim = c(0,.14), n = 5, #labeltype = "frex",
+         main = "Online News Topics", text.cex = 0.8)
 ```
@@
 set.seed(9272)
+
+posts_classification.sdt <-
   posts.dtp %>% 
-  group_by(title = document) %>% 
+  group_by(articleID = document) %>% 
   summarise(topic = min(topic[gamma == max(gamma)]), gamma = max(gamma)) %>% 
   ungroup() %>% 
-  inner_join(btw %>% select(title, articleID), by = "title") %>% 
+  inner_join(btw %>% select(title, articleID) %>%
+               mutate(articleID = as.numeric(articleID)), by = "articleID") %>% 
   inner_join(topics_mapping.dt, by = "topic") %>%
@@
   top_n(300, gamma) %>%
-  sample_n(5, replace = TRUE) %>% 
+  sample_n(7) %>% 
   mutate(row = row_number()) %>% 
-  ungroup() ->
-  posts_classification.sdt
+  ungroup()
 
@@
         legend.position  = "none"
-      ) +
-      labs(
-        title    = "GERMAN NEWS LANDSCAPE",
-        subtitle = "Sample online news articles in the year 2017",
-        caption  = 
-"DATA SOURCE: Webhose.io, Eventbride.com
-
-CHART NOTES:
-  1. Topics were derived through Latent Dirichlet Allocation (LDA) with 40 topics
-  2. Documents were classified according to the topic that has the highest probability
-"
       ) 
@@
   device = "png",
-  filename = "../figs/02-topic-classification-sample.png",
+  filename = "../figs/topic-classification-sample.png",
   dpi = 600, height = 10, width = 16
@@
 ![Facebook news samples](../figs/02-topic-classification-sample.png)
-
 ### News landscape
 
-After performing the topic modeling, we can generate an overview of the news landscape about the german elections, each group is composed of the most relevant words for that topic, and a manually-determined label.
+After performing the topic modeling, we can generate an overview of the news landscape about the german elections.
+Each group is composed of the most relevant words for that topic, and a manually-determined label.
 The distances that the topics have from each other reflect their semantic distance, or basically how different the words are for that topic.
@@
           labs(
-            title    = "GERMAN NEWS LANDSCAPE",
-            subtitle = "Online News Articles about Federal Elections June-Oct 2017",
-            caption = 
-"DATA SOURCE: Webhose.io, Eventbride.com
-
-CHART NOTES:
-  1. Topics were derived through Latent Dirichlet Allocation (LDA) with 40 topics
-  2. For each topic, the top 30 words in terms of relevance as defined in Sievert and Shirley (2014) are displayed
-  3. The centers of each topic mass were determined by applying principal components analysis to the distance matrix, with the Jensen-Shannon divergence as the distance measure. 
-      This layout is intended to display the degree of semantic distance.
-"
+            title    = ""
           )
       },
-      filename = "../figs/01-news-landscape-map.png",
+      filename = "../figs/news-landscape-map.png",
       device = "png",
@@
 
-![Facebook News Map](../figs/01-news-landscape-map.png)
+![Facebook News Map](../figs/news-landscape-map.png)
 
@@
     btw %>% 
-      select(document = title, date, 
-             title, articleID) %>% 
+      mutate(document = as.numeric(articleID)) %>%
+      select(document, date, 
+             title) %>% 
       mutate(post_period = 
@@
     sample_articles = 
-      paste0("<li>", sample(document, 3, replace = TRUE ), "</li>", collapse = "<br>")
+      paste0("<li>", sample(title, 4, replace = TRUE ), "</li>", collapse = "<br>")
   ) %>% 
@@
 ```
+
+```{r}
+chart_topic_trends.dt %>% 
+    ggplot(
+      aes(
+        x = post_period, 
+        y = factor(
+          topic_name, 
+          chart_topic_trends.dt %>% 
+            group_by(topic_name) %>% 
+            summarise(post_period = mean(post_period[peak], na.rm = TRUE)) %>% 
+            ungroup() %>% 
+            arrange(desc(post_period)) %$%
+            unique(topic_name)
+        )
+      )
+    ) +
+    geom_tile_interactive(aes(tooltip = tooltip_text, fill = log(articles))) +
+    geom_point_interactive(
+      mapping = aes(tooltip = tooltip_text),
+      data = chart_topic_trends.dt %>% filter(peak),
+      color = "red"
+    ) +
+    scale_fill_viridis(
+      labels = function(x) comma(round(exp(x))), 
+      name = "Number of Articles",
+      option = "plasma"
+    ) +
+    scale_x_datetime(expand = c(0, 0)) +
+    labs(
+      title = "", 
+      caption = "
+  Red dots indicate weeks where the number of articles exceeds 1.96 SD above mean for that topic
+      " ) +
+    theme(
+      legend.position   = "bottom",
+      legend.key.width  = unit(0.05, "npc"),
+      legend.background = element_rect("#fafafa"),
+      plot.background   = element_rect("#fafafa", "#fafafa"),
+      plot.title        = element_text(size = 18),
+      plot.subtitle     = element_text(size = 8),
+      plot.caption      = element_text(size = 7),
+      panel.grid        = element_blank(),
+      panel.background  = element_rect("#fafafa"),
+      axis.title        = element_blank(),
+      axis.ticks        = element_blank(),
+      axis.text.y       = element_text(size = 8)
+    )
+
+ggsave("../figs/topic-trends.png")
+```
+
+## Facebook Shares
+
+```{r}
+btw %>%
+  ggplot(aes(as.factor(topic), fb_shares)) +
+  stat_summary(fun.y="sum", geom="bar", fill = "blue", alpha=.7) +
+  labs(x="", y="Sum") +
+  scale_x_discrete(breaks=c(1:40), labels = topicLabel$topic_name) +
+  theme(axis.text.x = element_text(size=6, angle=90),
+        axis.text.y = element_text(size=7))
+
+ggsave("../figs/fb_shares_topics.png", device = "png", 
+       dpi = 600)
+```
+
+## Animated Figures
 
@@
     labs(
-      title = "ZEITGEIST", 
-      subtitle = "Topic distribution of news articles over time, 2017\n(Hover over each tile to see sample articles)",
-      caption = "
-DATA SOURCE: Webhose.io, Eventbride.com
-
-CHART NOTES:
-  1. Red dots indicate weeks where the number of articles exceeds 1.96 SD above mean for that topic
-  2. Hover over each tile to see infomration and to see sample articles
-  3. Topics were derived through Latent Dirichlet Allocation (LDA) with 40 topics
-  4. Articles were classified according to the topic that has the highest probability
-
-TROY JAMES PALANCA | TJPALANCA.COM
-      "
+      title = ""
     ) +
@@
   widget = chart_topic_trends.wdgt,
-  file = "../figs/03-topic-trends.html",
+  file = "../figs/topic-trends.html",
   selfcontained = FALSE,
@@
     btw %>% 
+      mutate(document = as.numeric(articleID)) %>%
       select(
-        document = title, 
+        document, 
         news_page = site, 
@@
     btw %>% 
-      group_by(document = title) %>%
+      mutate(document = as.numeric(articleID)) %>%
+      group_by(document) %>%
       summarise(reactions = sum(fb_shares)) %>%
@@
   inner_join(
-    btw %>% select(document = title, news_page = site, title),
+    btw %>% mutate(document = as.numeric(articleID)) %>%
+      select(document, news_page = site, title),
     by = "document"
@@
     labs(
-      title = "BIAS AND BALANCE",
-      subtitle = "Topic distribution of online news articles per news page, 2017\n(Hover over each bar to see the topic and sample articles)",
-      caption = "
-DATA SOURCE: Facebook Graph API
-
-CHART NOTES:
-  1. The news pages are arranged in descending order in terms of number of articles
-  2. Topics were derived through Latent Dirichlet Allocation (LDA) with 40 topics
-  3. Articles were classified according to the topic that has the highest probability
-      "
+      title = ""
     )

### 2017-11-06 paper/doc/doc2.tex
writing

@@
 \usepackage[english]{babel}
-\usepackage{mathtools}
+\usepackage[T1]{fontenc}
+\usepackage[backend=biber,
+			style=authoryear-comp,
+			isbn=false,
+			doi=false,
+			bibstyle=authoryear,
+			natbib,
+			]{biblatex}
+\usepackage{eurosym}
+\usepackage{enumitem}
+\usepackage{url}
+\usepackage{blindtext}
+\usepackage{hyperref}
+\usepackage{breakurl}
+\usepackage{amsmath}
 \usepackage{titling}
@@
 \usepackage{amssymb}
-\usepackage{amsthm}
-\usepackage{amsmath}
 \usepackage{pgfplots}
-\usepackage[caption = false]{subfig}
 \usepackage{caption}
+\usepackage{subcaption}
 \usepackage{graphicx}
+\usepackage{dcolumn}
 \usepackage{tikz-3dplot}
@@
 \usepackage[toc,page]{appendix}
-\DeclareUnicodeCharacter{20AC}{\euro}
-\usepackage[backend=biber,
-			style=authoryear-comp,
-			isbn=false,
-			doi=false,
-			bibstyle=authoryear,
-			natbib,
-			]{biblatex}
+\usepackage{lscape}
+\usepackage{todonotes}
+\usepackage{booktabs}
+\usepackage{multirow}
+\usepackage{bm}
+\usepackage{eurosym}
 
@@
 Furthermore, articles can contain more than one topic.
-To take these factors into account, we use a mixed-membership model \citep{airoldi_handbook_2014} - or topic model as they are often referred in the literature of text analysis \citep{blei_probabilistic_2012} to reveal the underlying topics of a collection of articles (a corpus), and how the articles exhibit them.
+We use a structural topic model to reveal the underlying topics of a collection of articles (a corpus), and how the articles exhibit them.
 We then estimate the effect of topic prevalence on the number of Facebook shares.
 
-Within topic models the Latent Dirichlet Allocation (LDA henceforth) is a widely used topic modeling technique, where each document (article) is viewed as a mixture of topics (represented by the document-topic distribution) and each topic is a mixture of unique terms (represented by the topic-term distribution).
-To "learn" the topic prevalence and the topic-term distribution, collapsed Gibbs sampling\footnote{See Section \ref{section_gibbs} for a non-formal description of the Gibbs sampler} can be used.
+Mapping raw text to one or more topics, without having prior knowledge on what those topics are, translates to an unsupervised classification problem on natural language.
+Within topic models the Latent Dirichlet Allocation (LDA) is a widely used technique, where each document (article) is viewed as a mixture of topics (represented by the document-topic distribution) and each topic is a mixture of unique terms (represented by the topic-term distribution).\cite{blei_latent_2003}
 
@@
 We then estimate the effect of topical prevalence (the posterior document-topic distribution) on the number of Facebook shares.
+
+Figure \ref{fig_research_strat} gives an overview of the applied research strategy.
+Chapter \ref{ch_data} contains a description of the text data and how it was pre-processed in order to use it as input variable.
+Chapter \ref{ch_model} explains the generative process of the mixed membership model and the results of this process are presented in chapter \ref{ch_results}.
+Chapter \ref{ch_regression} describes how we regress the estimated probabilities of topic prevalence of a document on the times, this document was shared on Facebook.
+
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=0.95\textwidth]{../figs/research_strategy.pdf} 
+	\caption{Research Strategy}
+	\label{fig_research_strat}
+\end{figure}
+
+% Related Literature
+% ------------------
 
@@
 
-% ---------------------------------
-% Statistical Analysis of Text Data
-% ----------------------------------
-\section{Statistical Analysis of Text Data}
-
-Consider a collection of documents by $d \in \lbrace 1 ...
-D \rbrace$, each containing $n \in \lbrace 1 ...
-N_d \rbrace$ words.
-Primary observations consist of words $w_{d,n,}$ that are instances of unique terms from a vocabulary of terms, indexed by $v \in \lbrace 1 ...
-V \rbrace$.
-
-To use text as data and reduce the dimensionality, a common strategy is to (a) pre-process the text by imposing some preliminary restrictions (stop-word removal, tokenization) based on the nature of the data (twitter text, newspaper articles, speeches, etc.) and (b) to represent a document $d$ as a vector of word counts, $\boldsymbol{n}_d \in \boldsymbol{N}^V$.
-This representation is often referred to as the bag of words model, since the order in which words are used within a document is completely disregarded.
-Nowadays, the bag of words model is a common representation for most of statistic literature about text data analysis (\citet{blei_latent_2003}; \citet{erosheva_mixed-membership_2004}; \citet{griffiths_finding_2004}; \citet{genkin_large-scale_2007}).
-
-Term-Document matrices represent frequency distribution of unique terms in the documents.
-Any one document will contain only a subset of all unique terms, and the rows corresponding to unused terms will all be zero.The key task then becomes how to extract low-dimensional information from documents that are high-dimensional by nature.
-This is analogous to a situation in which a researcher has a database with thousands of covariates and is attempting to choose which subset of them, or which summary statistics, should be included in regression analysis.
-% The description of the data and how it was processed in order to reduce it to a manageable scale without losing significant information can be found in chapter ...
-
-\begin{enumerate}
-	\item Represent raw text $D$ as a numerical array $\boldsymbol{C}$.
-
-	\item Map $\boldsymbol{C}$ to predict values $\boldsymbol{\hat{V}}$ of unknown outcomes $\boldsymbol{V}$.
-
-	E.g.
-the variable of interest $\boldsymbol{V}$ is an indicator whether the email is spam.
-The prediction $\boldsymbol{\hat{V}}$ determines whether or not to send the email to a spam filter.
-Sometimes the attribute of interest is latent, such as the topics of a newspaper article.
-	\item Use $\boldsymbol{\hat{V}}$ in subsequent descriptive or causal analysis.
-\end{enumerate}
-
-Regarding 2, the methods to connect counts $\boldsymbol{c}_i$ to attributes $\boldsymbol{v}_i$ can be roughly divided into four categories \citep{gentzkow_text_2017}:
-\begin{enumerate}
-	\item Dictionary-based methods: 
-	No statistical inference.
-Simply specify $\boldsymbol{\hat{v}_i}=f(\boldsymbol{c}_i)$ for some unknown function $f(\cdot)$.
-Sometimes based on a specific dictionary of terms (\citet{tetlock_giving_2007}, \citet{baker_measuring_2015}).
-	\item Text regression methods:
-	Directly estimate the conditional outcome distribution $p(\boldsymbol{v}_i|\boldsymbol{c}_i)$.
-Intuition: If we want to predict $\boldsymbol{v_i}$ from $\boldsymbol{c}_i$, we would regress the observed values of the former ($\boldsymbol{V}^{train}$) on the corresponding latter ($\boldsymbol{C}^{train}$).
-High dimensionality of $\boldsymbol{c}_i$ ($p > n^{train}$) requires use of appropriate regression techniques to avoid overfitting (e.g.
-$L_1$ regularized linear or logistic regression)
-	\item Generative model of $p(\boldsymbol{c}_i|\boldsymbol{v}_i)$.
-	Intuition: In many cases the underlying causal relationship runs from outcomes to language rather than the other way around.
-E.g.
-Google searches about flu do not cause flu cases to occur, rather, people with flu are more likely to produce such searches.
-	\begin{enumerate}
-		\item Observed attributes (supervised methods):
-		Supervised machine learning starts with a researcher classifying observations to ‘train’ an algorithm under human ‘supervision’ – to ‘learn’ the correlation between the researcher’s ascribed classes and words characteristic of documents in those classes (Grimmer and Stewart (2013)).
-Fitting the model based on the observed training data $\boldsymbol{V}^{train}$, say $f_{\boldsymbol{\theta}}(\boldsymbol{c}_i;\boldsymbol{v}_i)$ for a vector of parameters $\boldsymbol{\theta}$, to this training set.
-The fitted model $f_{\hat{\boldsymbol{\theta}}}$ can be inverted in order to infer $\boldsymbol{v}_i$ for documents in the test set.
-		\item Latent attributes (unsupervised methods): The function relating $\boldsymbol{c}_i$ to $\boldsymbol{v}_i$ is unknown, as we cannot observe the true value of $v_i$.
-Principal component analysis (PCA), latent Dirichlet allocation (LDA, topic modeling, structural-topic modeling).
-Unsupervised machine learning involves taking unclassified observations and uncovering hidden patterns that structure them in some meaningful way.
-The outputs of algorithms for unsupervised machine learning can be used as inputs into econometric models for predicting some variable of interest, but this is a different approach from intentionally choosing the dimensions of content based on their predictive ability.
-	\end{enumerate}
-	\item Deep learning techniques: neural networks, distributed language models.
-\end{enumerate}
-
-The goal of this paper is to find the latent topics within newspaper articles and how different types of media outlets (as well as the date?) influence the topic prevalence as well as the language to describe a topic (the word-topic distribution).
-We implement generative model (topic model).
-% A description of the generative process can be found in chapter ...
-
 % -----
@@
 
-\section{Data}
+\section{Dataset}\label{ch_data}
 
-To explore the effect of topic prevalence of an article on the times this article is shared on Facebook, we analyze a sample of 1768 news articles containing the term "Bundestagswahl" (Federal Election) dated from 01.06.2017 to 30.09.2017\footnote{German federal elections took place on 24th of September 2017.} and originated from f
+We conduct our estimation on a sample of 10531 news articles containing the term "Bundestagswahl" (Federal Election) dated from 01.06.2017 to 28.10.2017.\footnote{German federal elections took place on 24th of September 2017.} We first extract all online articles of six mainstream german online news portals\footnote{Bild.de, Focus.de, Spiegel.de, Stern.de, Welt.de, Zeit.de} using the the Event Regestry API.\footnote{For more information see http://eventregistry.org/documentation.
+The scraping code was written in Python and can be made available on request.} We then filter those articles that contain the term "Bundestagswahl" (Federal Election) in their text body.
 
-% ---------------------------------
-% Generative Process
-% ----------------------------------
+Figure \ref{fig_distr} shows the distribution of the number of articles from the respective news sources by date.
+There is a high peak around the federal elections on September, 24th.
+Most of the articles are published by welt.de, followed by stern.de.
 
-\section{Generative Process}
+\begin{figure}[H]
+	\caption{Article distribution...}
+	\begin{center}
+		\begin{subfigure}[normla]{0.49\textwidth}
+			\includegraphics[width=\textwidth]{../figs/timeline.png}
+			\caption{...by date \& news source}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.49\textwidth}
+			\includegraphics[width=\textwidth]{../figs/bar.png}
+			\caption{... by news source}
+		\end{subfigure}
+	\end{center}
+	\label{fig_distr}
+\end{figure}
 
-In this unsupervised method, the words in a document are viewed as the realization of some stochastic process.
-The generative process is defined through a probability model for $p(\boldsymbol{c}_i|\boldsymbol{v}_i)$.
+\begin{figure}[H]
+	\caption{Distribution of Facebook shares...}
+	\begin{center}
+		\begin{subfigure}[normla]{0.49\textwidth}
+			\includegraphics[width=\textwidth]{../figs/fb_shares.png}
+			\caption{...by date \& news source}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.49\textwidth}
+			\includegraphics[width=\textwidth]{../figs/fb_shares_mean.png}
+			\caption{... by news source (mean)}
+		\end{subfigure}
+	\end{center}
+	\label{fig_fb_shares}
+\end{figure}
 
-Each observation $\boldsymbol{c}_i$ is a conditionally independent draw from the vocabulary of possible tokens accodring to some document-specific token probability vector $\boldsymbol{q}_i=[q_{i1}...q_{ip}]'$.
-Conditioning on document length, $m_i=\sum_jc_{ij}$, this implies a multinomial distribution for the counts
+To use text as data and reduce the dimensionality, a common strategy is to (a) pre-process the text by imposing some preliminary restrictions (stop-word removal, tokenization) based on the nature of the data (twitter text, newspaper articles, speeches, etc.) to reduce the number of language elements to consider and (b) limit the extent to which the dependence among elements within a document is encoded \citep{gentzkow_text_2017}.
+A raw text can than be represented as a term-document matrix, wehere each row is a numerical vector with each element indicating the frequency of a particular term in a document.
+In our case, a document is equivalent to a news article (title and body) and the collection of these documents are aggregated within a corpus.
+Any one document will contain only a subset of all unique terms, and the rows corresponding to unused terms will all be zero.
 
-\begin{equation}\label{eq_1}
-	\boldsymbol{c}_i \sim \boldsymbol{MN}(\boldsymbol{q}_i,m_i). 
-\end{equation}
+% ------------------
+% Text Pre-Procesing
+% ------------------
+\subsection{Text pre-procesing and feature selection}
 
-Under the basic model in \ref{eq_1}, a connection between text and attributes is defined through the link function $\boldsymbol{q}_i=q(\boldsymbol{v}_i)$.
+A central task in text mining is to extract low-dimensional information from documents that are high-dimensional by nature \citep{bholat_text_2015}.
+This is related to the task of reducing the number of unique language elements in order to reduce the dimensionality of data (to avoid unnecessary computational complexity and overfitting) while at the same time keeping those words that reflect the content of a document.
+Any useful representation of text will throw away some information, as that is the essential purpose of text mining.
+The trick is to include the relevant information for our needs, and exclude the extraneous information.
 
-\begin{equation}\label{eq_2}
-	\boldsymbol{E} \bigg[\frac{\boldsymbol{c}_i}{m_i}\bigg]=\boldsymbol{q}_i =v_{i1}\boldsymbol{\theta}_1+v_{i2}\boldsymbol{\theta}_2+v_{ik}\boldsymbol{\theta}_k=\boldsymbol{\Theta v}_i
-\end{equation}
+Intuitively the term frequency (tf) of a word is a measure of how important that word may be.
+There are words in a document, however, that occur many times but may not be important like articles, conjunctions, and so on.
+These terms, often called "stop words", are important to the grammatical structure of a text, but typically don't add any additional meaning and can therefore be neglected.
+We use a pre-defined stop word list from the Snowball stemmer project\footnote{http://svn.tartarus.org/snowball/trunk/website/algorithms/*/stop.txt} together with a customized stop-word list.
+We also remove punctuation character (e.g.
+., ,, !, ?, etc.) and all numbers from our corpus.
 
-where attributes $v_{il}$ are referred as topic wights, restricting $v_{il}\geq 0$ and $\sum^k_{l=1}v_{il}=1$, and each topic $\boldsymbol{\theta}_l$ is a probability vector over possible tokens: $\theta_{lj}\geq 0$ and $\sum^p_{j=1}\theta_{il}=1$.
-Each $\boldsymbol{v}_i$ and $\boldsymbol{\theta}_l$ is generated from a Dirichlet-distributed prior.
+After pre-processing, each document (article) is a finite list of unique terms.
+Each unique term in the corpus is indexed by some $v \in \lbrace 1,...,V \rbrace$ where $V$ is the number of unique terms.
+For each document $d \in \lbrace 1,...,D \rbrace$ we compute the number of occurrences of term $v$ in document $d$ to obtain the count $x_{d,v}$.
+The $D$ x $V$ matrix $\boldsymbol{X}$ of all such counts is called the document-term matrix.
+This representation is often referred to as the bag of words model, since the order in which words are used within a document is completely disregarded.
 
-Latent Dirichlet allocation (LDA) is a particularly popular method for fitting a topic model.
-It treats each document as a mixture of topics, and each topic as a mixture of words.
-This allows documents to “overlap” each other in terms of content, rather than being separated into discrete groups, in a way that mirrors typical use of natural language.
-Formally speaking, each document has its own probability distribution over topics.
-Then, for each word in each document, a topic assignment is made and then, conditional on the assignment, a word from the corresponding topic.
+% ----------------------
+% Structural topic Model
+% ----------------------
 
-Estimation of topic models make use of some alternating inference for $\boldsymbol{V|\Theta}$ and $\boldsymbol{\Theta|V}$.
+\section{Topic detection}\label{ch_model}
 
-\begin{enumerate}
-	\item Expectation-maximization algorithm (EM)
-	Either maximize the likelihood implied by \ref{eq_1} and \ref{eq_2} or, after incorporating the usual Dirichlet priors on $\boldsymbol{v}_i$ and $\boldsymbol{\theta}_l$ \citep{taddy_estimation_2012} 
-	\item Target full posterior distribution $p(\boldsymbol{\Theta,V|c}_i})$
-\end{enumerate}
+As we do not observe the topics, we need to implement an unsupervised machine learning algorithm, that takes unclassified observations of words and uncovers hidden patterns (topics) that structure them in some meaningful way.
+We can than use the output of this process as inputs into an econometric model that predicts the number of Facebook shares \citep{gentzkow_text_2017}.
 
-Choice of number of topics $k$ is often fairly arbitrary.
-In practice it is very common to simply start with a number of topics on the order of ten, and then adjust the number of topics in whatever direction seems to improve interpretability.
-Whether this ad hoc procedure is problematic depends on the application.
-In many applications of topic models to date the goal is to provide an intuitive description of text rather than inference on some underlying “true” parameters; in these cases, the ad hoc selection of the number of topics may be reasonable.
+We use the structural topic model (STM) developed by \citet{roberts_model_2016} that allows us to incorporate document specific covariates (e.g.
+author or date).
+STM is a recent extension of the standard topic modeling technique, the Latent Dirichlet Allocation (LDA).
+Topic models formalize the idea that documents are formed by hidden variables (topics) that generate correlations among observed terms.
+LDA is a particularly popular method for fitting a topic model \citep{blei_latent_2003}, also known as the generative aspect model \citep{minka_expectation-propagation_2002}.
+It treats each document $d$, containing $N_d$ words from a vocabulary of interest of $V$ unique terms, as a mixture of $k$ topics.
+Thus, each document has its own probability distribution over topics.
+Simultaneously, each topic is associated with a $V$-dimensional probability mass function $\boldsymbol{\beta}_k$, that controls the frequency according to which terms are generated from that topic.
+This standard topic modeling technique makes the assumption that all texts in the modeled corpus are generated by the same underlying process \citep{mishler_using_2015}.
+To include additional information that improve the estimation of the topics, we estimate a structural topic model, where topical prevalence (the distribution of topics among documents) is specified as a simple generalized linear model on document-level metadata.
 
-Data-driven approaches: 
-\begin{enumerate}
-	\item \citet{taddy_estimation_2012} describes a model selection process for $k$ that is based upon Bayes factors.
-	\item \citet{airoldi_reconceptualizing_2010} provide a cross-validation (CV) scheme
-	\item \citet{teh_hierarchical_2006} use Bayesian nonparametric techniques that view $k$ as an unknown model parameter.
-\end{enumerate}
-
-\subsection{Structural Topic Model}
-
-The process for generating individual words is the same as for plain LDA conditional on the $\beta_k$ and $\pi_d$ terms.
-
-However both objects can depend on potentially different sets of document-level covariates. Each document has:
-\begin{enumerate}
-	\item Topic Prevalence. Attributes $r_d$ that affect the likelihood of discussing topic $k$. how much of a document is associated with a topic
-	\item Topic Content. Attributes $r_d$ that affect the likelihood of discussing term $v$ overall, and of discussing it within topic $k$. the words used within a topic
-\end{enumerate}
-
-The generation of the $k$ and $d$ terms is via multinomial logistic regression, which breaks local conjugacy.
-
-The standard topic modeling technique, Latent Dirichlet Allocation (LDA), may have limited utility in the realm of social media.
-LDA makes a statistical assumption that all texts in the modeled corpus are generated by the same underlying process (Blei).
-Thus, it is not ideally suited to examining differences in topical content that are affected by external variables such as author identity or time of writing.
-
-Structural topic modeling (STM) is a recently introduced variant of LDA that is designed to address precisely this limitation .
-STM can represent the effect of external variables on both topical content and topical prevalence.
-The external variables can consist of any metadata that distinguishes one text from another, including variables relating to author identity (gender, age, political affiliation, etc.), textual genre (for example, news stories versus academic articles), and time of production.
-
-stmVigenette: "The goal of the Structural Topic Model is to allow researchers to discover topics and estimate their relationship to document metadata.
-Outputs of the model can be used to conduct hypothesis testing about these relationships."
-
-\subsubsection{Estimation of the STM}
-In STM, metadata can be entered in the topic model in two ways: topical prevalence and topical content.
-Metadata covariates for topical prevalence allow the observed metadata to affect the frequency with which a topic is discussed.
-Covariates in topical content allow the observed metadata to affect the word rate use within a given topic{that is, how a particular topic is discussed.
-
-We use the online magazine-type as a covariate in the topic prevalence portion of the model with the  data described above.
+We use source of each article (the news-platform) as a covariate in the topic prevalence portion of the model with the data described above.
 Each document is modeled as a mixture of multiple topics.
@@
 Because different documents come from different sources, it is natural then to want to allow this prevalence to vary with metadata that we have about document sources.
+The observed words $w_i$ in a document are then viewed as the realization of some stochastic process.\footnote{See \citet{roberts_model_2016} for a formal description of the generative process.} We set the number of topics to be 40 after evaluating and maximizing topics' coherence using a cross-validation scheme while changing the number of topics (\citet{airoldi_reconceptualizing_2010}; \citet{roberts_model_2016}).
 
-We will simply let prevalence be a function of the magazine variable, which is coded as either
-Spiegel Online or FOCUS Online and the variable day which is an integer measure of days running from 01-01-2017 to 31-07-2017.
+\section{Probabilities and Classification}\label{ch_results}
 
-\subsection{Gibbs Sampler}\label{section_gibbs}
+After performing the topic modeling, we can generate an overview of the news landscape about the german elections.
+Each group is composed of the most relevant words for that topic, and a manually-determined label.
+The distances that the topics have from each other reflect their semantic distance, or basically how different the words are for that topic.
+It is computed as the Jensen-Shannon divergence between each of the topics according to the differences in their word-topic probabilities.
+We then apply principal coordinates analysis in order to project the distance matrix down to two dimensions.
 
-Strategy for discovering topics  \cite{griffiths_finding_2004}
-\begin{itemize}
-	\item Considering the posterior distribution over the assignments of words to topics, $P(z|w)$. (and not explicitly representing $\phi$ or $\theta$ as parameters to be estimated)
-	\item Examine this posterior distribution to obtain $\phi$ or $\theta$
-\end{itemize}
+\begin{figure}[H]
+\centering
+	\caption{News Landscape}
+	\includegraphics[width=\textwidth]{../figs/news-landscape-map.png}	
+	\label{fig_landscape}
+\end{figure}
 
-After making assumptions about the parameters (number of topics $K$, prior distributions $\alpha$ and $\beta$), the procedure of Gibbs sampling is as follows:
+To check weather the estimated topic classifications make sense, we first produce sample documents classified to that topic for reference.
+We produce a random sample of 10 posts from the 300 highest probability fits per topic.
 
-\begin{enumerate}
-	\item Go through each document and randomly assign each word in the document to one of $K$ topics, based on the prior distributions.
-	\item For each document $d$, go through each word $w$ and compute:
-	\begin{enumerate}
-		\item The document-topic distribution $\theta = p(t|d)$
-		\item The topic-term distribution $\phi = p(w|t)$
-	\end{enumerate}
-	\item Reassign word $w$ a new topic $t^*$, where we choose topic $t^*$ with probability $p(t^*|d)*p(w|t^*)$
-\end{enumerate}
+\begin{figure}[H]
+\centering
+	\caption{Sample articles}
+	\includegraphics[width=\textwidth]{../figs/topic-classification-sample.png}	
+	\label{fig_classification}
+\end{figure}
 
-On repeating the last step a large number of times, the algorithm reaches a steady state where topic assignments are pretty good.
-These posterior distributions $\theta$ and $\phi$ are then used to determine the topic mixtures of each document.
+\begin{figure}[H]
+\centering
+	\caption{Sum of Facebook shares by topic}
+	\includegraphics[width=\textwidth]{../figs/fb_shares_topics.png}	
+	\label{fig_fb_shares_topic}
+\end{figure}
 
-\subsection{Validate accuracy}
-
-\begin{itemize}
-	\item Manual audits: cross checking some subset of the fitted values against the coding a human would produce by hand
-	\item Inspection of fitted parameters
-	\item Interpretation of fitted topics usually proceeds by ranking the tokens in each topic according to token probability.
-\end{itemize}
-
-Caution against the over-interpretation of unsupervised models: posterior distributions informing parameter estimates are highly multimodal, and multiple topic model runs can lead to multiple different interpretations.
-Add some supervision (\citet{airoldi_improving_2016}, \citet{gentzkow_text_2017})
+\section{Regression}\label{ch_regression}
 

### 2017-11-06 paper/R/func/02-topic-modelling-functions.R

@@ -244,8 +244,11 @@ computeJensenShannonPCA <- function(wtp) {
   # Returns: data frame containing the x-y location of each topic 
   
   jensenShannon <- function(x, y) {
+    c = .000000001
+    x = x + c
+    y = y + c
     m <- 0.5 * (x + y)
-    0.5 * sum(x * log(x / m)) + 0.5 * sum(y * log(y / m))
+    0.5 * sum(x * log(x/m)) + 0.5 * sum(y * log(y/m))
   }
   
   wtp %>% 
@@ -272,6 +275,9 @@ computeJensenShannonPCA2 <- function(dtp) {
   # Returns: data frame containing the x-y location of each topic 
   
   jensenShannon <- function(x, y) {
+    c = .000000001
+    x = x + c
+    y = y + c
     m <- 0.5 * (x + y)
     0.5 * sum(x * log(x / m)) + 0.5 * sum(y * log(y / m))
   }

### 2017-11-09 paper/R/02_combine.Rmd
add facebook_share api

@@
 okt$fb_shares <- as.integer(okt$fb_shares)
-
-# Text Length
 names(okt) <- gsub("body", "text", names(okt))
-okt$text_length <- sapply(gregexpr("\\S+", okt$text), length)
 
@@
 nov$fb_shares <- as.integer(nov$fb_shares)
-
-# Text Length
 names(nov) <- gsub("body", "text", names(nov))
-nov$text_length <- sapply(gregexpr("\\S+", nov$text), length)
 ```
@@
 keeps <- c( "welt.de","spiegel.de","stern.de","focus.de","zeit.de","bild.de" )
-keys <- paste(c("bundestagswahl","koalition"), collapse = "|")
+keys <- paste(c("bundestagswahl","Koalition"), collapse = "|")
 
@@
 
+## Count number of terms in a string
+```{r}
+btw$text_length <- sapply(gregexpr("\\S+", btw$text), length)
+```
+
 ```{r}
@@
   ungroup() %>%
-  arrange(desc(fb_shares)) %>%
   distinct(title,site, .keep_all = TRUE) -> btw
-
-btw %>%
-  filter(date < as.Date("2017-10-29")) -> btw
 ```
@@
 
-## Stemming
-```{r}
+## Stemming (not applied)
+```{r }
 stem_text<- function(text, language = "porter", mc.cores = 1) {
@@
 ```{r}
+load(file="../output/btw_combined.Rda")
+```
+
+# Extract FB Shares
+```{r}
+library(SocialMediaMineR)
+
+facebook <- get_facebook(btw$url[1:100])
+
+page <- readLines(paste0(check,btw$url[i]))
+
+check <- "https://graph.facebook.com/?id="
+pattern <- 'share_count\\":[0-9]+'
+
+shares <- NULL
+
+for (i in (length(shares)+1):nrow(btw)){
+  page <- readLines(paste0(check,btw$url[i]))
+  string <- str_extract(page, pattern)
+  shares <- append(shares, as.numeric(str_extract(string, "[0-9]+")))
+  Sys.sleep(10)
+}
+```
+
+```{r}
 save(btw, file="../output/btw_combined.Rda")
 ```
+
+```{r}
+url_slice <- split(btw$url, ceiling(seq_along(btw$url)/1000))
+file = "../output/urls"
+
+for (i in 1:length(url_slice)){
+  url = url_slice[[i]]
+  count = as.character(i)
+  write.table(url, file=paste0(file,count,".csv"), sep ="\n", 
+              row.names = FALSE, quote = FALSE, col.names = FALSE)
+}
+
+write.table(urls1, file="../output/urls1.csv", sep ="\n", row.names = FALSE, quote = FALSE)
+write.table(urls2, file="../output/urls2.csv", sep ="\n", row.names = FALSE, quote = FALSE)
+```
+
+```{r}
+library(Rfacebook)
+
+app_id = 1580533335373831
+app_secret = "07ecdc314355649e13447278c57627f6"
+
+shares
+```

### 2017-11-09 paper/R/03_stm.Rmd
several

@@
 #load("../output/btw_combined.Rda")
-knitr::opts_chunk$set(eval = TRUE, warning = FALSE)
+knitr::opts_chunk$set(eval = TRUE, warning = FALSE, message = FALSE)
 
@@
 
-## Introduction
-
-## Methodology
-
-## Dataset
+## Explore Dataset
 ```{r}
@@
 
-```{r message=FALSE, warning=FALSE}
+```{r}
 btw %>%
@@
 
-ggsave("../figs/timeline.png", plot = last_plot(), device = "png", 
-       dpi = 600)
+#ggsave("../figs/timeline.png", plot = last_plot(), device = "png", 
+#       dpi = 600)
 ```
 
-```{r message=FALSE, warning=FALSE}
+```{r}
 btw %>%
@@
 
-ggsave("../figs/bar.png", plot = last_plot(), device = "png", 
-       dpi = 600)
+#ggsave("../figs/bar.png", plot = last_plot(), device = "png", 
+#       dpi = 600)
 ```
 
-```{r message=FALSE, warning=FALSE}
+```{r}
 btw %>%
@@
 
-ggsave("../figs/fb_shares.png", plot = last_plot(), device = "png", 
-       dpi = 600)
+#ggsave("../figs/fb_shares.png", plot = last_plot(), device = "png", 
+#       dpi = 600)
+
+btw %>%
+  filter(site == "bild.de") %>%
+  select(title, text, fb_shares) %>%
+  .[3,] %>%
+  htmlTable::htmlTable()
 ```
 
-```{r message=FALSE, warning=FALSE}
+```{r}
 btw %>%
@@
 
-ggsave("../figs/fb_shares_mean.png", plot = last_plot(), 
-       dpi = 600)
+#ggsave("../figs/fb_shares_mean.png", plot = last_plot(), 
+#       dpi = 600)
 ```
@@
 
-```{r}
+```{r Add Topic to original DF}
 # Create Dataframe
@@
               select(topic_name, topic) %>%
-              mutate(topic = as.numeric(topic)), by="topic") -> btw
+              mutate(topic = as.numeric(topic)), by="topic") -> btw2
 
 # subset  
-topics_mapping.dt <- btw %>%
+topics_mapping.dt <- btw2 %>%
   group_by(topic) %>%
@@
   select(topic, title.text, articleID, topic_name) 
-```
-
-```{r}
-## Combine with Topic label
-topics_mapping.dt %>%
-  left_join(., topicLabel %>%
-              select(topic_name, topic) %>%
-              mutate(topic = as.numeric(topic)), by="topic") -> topics_mapping.dt
 ```
@@
   ungroup() %>% 
-  inner_join(btw %>% select(title, articleID) %>%
+  inner_join(btw2 %>% select(title, articleID) %>%
                mutate(articleID = as.numeric(articleID)), by = "articleID") %>% 
@@
 ```{r Topic classification}
-
 posts.dtp %>% 
@@
   inner_join(
-    btw %>% 
+    btw2 %>% 
       mutate(document = as.numeric(articleID)) %>%
@@
 
-## Facebook Shares
+## Regression
 
-```{r}
+### Facebook Shares
+```{r Facebook Shares}
 btw %>%
@@
        dpi = 600)
+```
+
+### Prepare Data
+```{r}
+top_topics <-
+  posts.dtp %>% 
+  group_by(document) %>%
+  mutate(therank = rank(-gamma, ties.method = "random")) %>%
+  filter(therank %in% 1) %>%
+  select(- therank)
+```
+
+```{r}
+# filter documents with low posterior
+btw.reg <- 
+  btw %>%
+  mutate(document = as.numeric(articleID)) %>%
+  left_join(., top_topics, by="document") %>%
+  #filter(gamma > 0.6) %>%
+  filter(fb_shares > 0)
+
+# generate factor variables
+btw.reg %>%
+  mutate(topic.f = factor(topic),
+         site.f = factor(site)) -> btw.reg
+```
+
+```{r}
+btw.reg %>%
+  filter(fb_shares < 500) %>%
+  ggplot(aes(fb_shares, fill = site)) +
+  geom_histogram(binwidth = 10)
+```
+
+```{r}
+linreg <- lm(fb_shares ~ topic.f*site, data=btw.reg)
+
+summary(linreg)
 ```
@@
   inner_join(
-    btw %>% mutate(document = as.numeric(articleID)) %>%
+    btw2 %>% mutate(document = as.numeric(articleID)) %>%
       select(document, news_page = site, title),

### 2017-11-09 paper/R/04_regression.Rmd
several

---
title: "Regression"
subtitle: ""
author: "Franziska Löw"
date: ""
output: 
  html_document:
    toc: true
    toc_float: true
    theme: "lumen"
    highlight: "tango"
    code_folding: show
    self_contained: true
---

```{r Setup, include=FALSE}
suppressPackageStartupMessages({
  library(dplyr)       # Data manipulation
  library(stringr)     # String manipulation
  library(lubridate)   # Date and time manipulation
  library(purrr)       # Functional programming
  library(tidyr)       # Reshaping
  library(magrittr)    # Advanced piping
  library(pushoverr)   # Pushover notifications
  library(doMC)        # Parallel Computing
  library(readr)       # Importing data
  library(tibble)      # Better data frames
  library(data.table)
  library(pscl)
  library(boot)

  library(ggplot2)     # Static data visualization
  library(scales)      # Scales
  library(viridis)     # Viridis color scales

  library(tidytext)    # Tidy text mining
  library(stringdist)  # String distances
  library(proxy)       # Distance measures
})

# Theming
quartzFonts(
  Roboto =
    c("Roboto-Light",
      "Roboto-Bold",
      "Roboto-Regular",
      "Roboto-Thin")
)

theme_set(
  theme_bw(base_family = "Roboto", base_size = 14) +
    theme(
      plot.title = element_text(face = "bold", size = 14,
                                margin = margin(0, 0, 4, 0, "pt")),
      plot.subtitle = element_text(size = 12),
      plot.caption = element_text(size = 6, hjust = 0),
      axis.title = element_text(size = 10),
      panel.border = element_blank()
    )
)

rm(list=ls())
```

## Load Data
```{r caching, echo = FALSE}
load("../output/btw_combined.Rda")
btw2 <- btw

load("../output/models/STM 40 .Rda")
#load("../output/btw_combined.Rda")
knitr::opts_chunk$set(eval = TRUE, warning = FALSE, message = FALSE)

# Set color
library(RColorBrewer) 
col <- brewer.pal(6,"Dark2")
```

## Prepare Data
```{r Extract wtp and dtp}
# Word-topic probabilities
stmOut %>% tidy("beta") %>% filter(!is.na(topic)) -> posts.wtp
# Document-topic probabilities
stmOut %>% tidy("gamma") -> posts.dtp
```

```{r}
top_topics <-
  posts.dtp %>% 
  group_by(document) %>%
  mutate(therank = rank(-gamma, ties.method = "random")) %>%
  filter(therank %in% 1) %>%
  select(- therank)
```

We classify each document based on which topic has the highest probability. To estimate the true effect of a topic, we delete documents where the highest topic probability is smaller than 0.5, as topic assignment is not ambiguous. This left us with 7740 documents.

```{r}
btw.reg <- 
  btw %>%
  left_join(., btw2 %>%
              select(title.text, shares, url),
            by = "title.text")
```

```{r}
# filter documents with low posterior
btw.reg <- 
  btw.reg %>%
  mutate(document = as.numeric(articleID)) %>%
  left_join(., top_topics, by="document") %>%
  filter(gamma > 0.5)

# generate new variables and reduce df
btw.reg %>%
  mutate(topic = factor(topic),
         site = factor(site),
         shares.dummy = factor(ifelse(shares==0,0,1))) %>%
  select(site, shares, shares.dummy, date, text_length, month, 
         document, topic, gamma) -> btw.reg
```

## Description of Data
```{r}
summary(btw.reg)
```

The proportion of zeros in the independent variable (number of Facebook shares) is about 65.6\%. One way to model this type of situation is to assume that the data come from a mixture of two populations, one where the counts is always zero, and another where the count has a Poisson distribution with mean $\mu$. In this model zero counts can come from either population, while positive counts come only from the second one.

The distribution of the outcome can then be modeled in terms of two parameters, $\pi$ the probability of 'always zero', and $\mu$, the mean number of publications for those not in the 'always zero' group. A natural way to introduce covariates is to model the logit of the probability $\pi$ of always zero and the log of the mean $\mu$ for those not in the always zero class.

## Analysis
### Zero-inflated Poisson regression
```{r}
# filter NAs
btw.reg %>%
  filter(!is.na(shares)) -> btw.reg
```

```{r Zero-inflated Poisson}
library(pscl)
m1 <- zeroinfl(shares ~ topic + site | topic + site + text_length, data = btw.reg)
summary(m1)
```
Looking at the inflate equation we see that some topics are significant predictors of being in the 'always zero' class.

Looking at the equation for the mean number or Facebook fhares among those not in the always zero class, we find ...

To verify that the model solves the problem of excess zeroes we predict π and μ, and calculate the combined probability of no publications. There are options in the predict() function called "zero" and "count" to obtain these. There's also an option "prob" to compute the predicted density, but this is overkill as we only want the probability of zero.

```{r}
pr <- predict(m1, type = "zero") # π
mu <- predict(m1, type= "count") # μ

zip <- pr+(1-pr)*exp(-mu)
mean(zip)
```

So the model solves the problem of excess zeroes, predicting that 65.6% of the articles will not be shared on Facebook which is very close to the observed value.

Note that the model output above does not indicate in any way if our zero-inflated model is an improvement over a standard Poisson regression. We can determine this by running the corresponding standard Poisson model and then performing a Vuong test of the two models.

```{r}
p1 <- glm(shares ~ topic, family = poisson, data = btw.reg)
summary(p1)
```

```{r}
vuong(p1, m1)
```

The Vuong test compares the zero-inflated model with an ordinary Poisson regression model. We can see that our test statistic is significant, indicating that the zero-inflated model is superior to the standard Poisson model.

### Plot the residuals

```{r}
btw.reg$predicted <- predict(m1)
btw.reg$residuals <- residuals(m1)
```

#### Residual Plot for multiple Variables
```{r}
ggplot(btw.reg, aes(predicted, residuals)) +
  geom_point(color="blue", alpha=0.6) 
```

#### Residual Plot for single Variables

The predicted values are plotted in black. They are connected to the actual data points through a line and high residuals (in abolsute terms) are made more red on actual values. This helps to identify non-linearity in the data. We can see that there is more red for extreme values for spiegel.de as well as for the topics 12, 21 and 9. 
```{r message=FALSE, warning=FALSE}
btw.reg %>%
  select(site, shares, topic, residuals, predicted) %>%
  gather(key="iv", value="x", -shares, -predicted, -residuals) %>%
  ggplot(aes(x=x, y=shares)) +
  geom_segment(aes(xend=x, yend=predicted), alpha=.2) +
  geom_point(aes(color=residuals)) +
  scale_color_gradient2(low="black", mid="blue", high="red") +
  guides(color=FALSE) +
  geom_point(aes(y=predicted), shape=1) +
  facet_grid(~iv, scales="free") +
  theme_bw()
```

### 2017-11-09 paper/doc/doc2.tex
several

@@
 Users of Facebook, for example, can use their profile to share links to external websites - such as news portals - with their online friends.
-This has led to the development of social media into an important generator of traffic on the internet pages.
+This has led to the development of social media becoming an important generator of traffic for content providers.
 In Germany, 94\% of online shared news articles in 2015 are distributed via Facebook, followed by Twitter with 3.5\% and Google+ with 2.3\% \citep{schiller_development_2016}.
+
 The advertising-financed business model of the media houses is based on the premise that users visit their websites in order to achieve high advertising revenues.
@@
 \citet{schiller_development_2016} show, that social media users choose a certain site depending on the researched topic.
-FOCUS Online for example is targeted for articles from politics and business, sports news is more likely to be shared from Bild.de.
+FOCUS Online for example is targeted for articles from politics and business, while sports news is more likely to be shared from Bild.de.
 
-While these static resorts give an indication on the content of an article, multiple articles in the same resort probably don't cover the same topics (and are not equally shared).
+While these pre-defined resorts give an indication on the content of an article, multiple articles in the same resort probably don't cover the same topics.
 Especially if the articles originate from different news portals.
 Furthermore, articles can contain more than one topic.
-We use a structural topic model to reveal the underlying topics of a collection of articles (a corpus), and how the articles exhibit them.
+We use a structural topic model to reveal the underlying topics of a collection of articles, and how the articles exhibit them.
 We then estimate the effect of topic prevalence on the number of Facebook shares.
@@
 Mapping raw text to one or more topics, without having prior knowledge on what those topics are, translates to an unsupervised classification problem on natural language.
-Within topic models the Latent Dirichlet Allocation (LDA) is a widely used technique, where each document (article) is viewed as a mixture of topics (represented by the document-topic distribution) and each topic is a mixture of unique terms (represented by the topic-term distribution).\cite{blei_latent_2003}
-
-LDA makes a statistical assumption that all texts in the modeled corpus are generated by the same underlying process \citep{blei_latent_2003}.
-Thus, it is not ideally suited to examining differences in topical content that are affected by covariates such as author identity or time of writing.
-\citet{roberts_model_2016} develop a structural topic model (STM) that allows to incorporate external variables that effect both topical content and topical prevalence.
+Topic models generate low-dimensional representations of data and can uncover interesting latent structure in large text datasets.
+They are popular tools for automatically identifying prominent themes in text.
+Within topic models the Latent Dirichlet Allocation (LDA) is a widely used technique, where each document (article) is viewed as a mixture of topics (represented by the document-topic distribution) and each topic is a mixture of unique terms, represented by the topic-term distribution \citep{blei_latent_2003}.
+\citet{roberts_model_2016} extents the base idea of LDA by developing a structural topic model (STM) that allows to incorporate external variables that effect both topical content and topical prevalence.
 We use this approach to analyze online news about the german federal elections, where we allow prevalence of topics to vary across newswire services.
@@
 Figure \ref{fig_research_strat} gives an overview of the applied research strategy.
+Chapter \ref{ch_model} explains the generative process of the mixed membership model and the results of this process are presented in chapter \ref{ch_results}.
 Chapter \ref{ch_data} contains a description of the text data and how it was pre-processed in order to use it as input variable.
-Chapter \ref{ch_model} explains the generative process of the mixed membership model and the results of this process are presented in chapter \ref{ch_results}.
 Chapter \ref{ch_regression} describes how we regress the estimated probabilities of topic prevalence of a document on the times, this document was shared on Facebook.
@@
 
+Applications:
+
 % Structural topic models (STM)
@@
 
+Applications:
+Structural topic modeling is an alternative to LDA that allows researchers to link topics to covariate data and to model changes in topic prevalence over time.
+STM has recently been applied to scientific texts on climate change, revealing links between corporate funding and the framing of scientific studies \citep{farrell_corporate_2016}.
+It has also been applied to social media data in a variety of ways.
+One study shows that “STM can be used to detect significant events such as the downing of Malaysia Air Flight 17” when applied to twitter data \cite{mishler_using_2015}.
+Another study shows how STM can be used to explore relatively large data sets including course evaluations and discussion forum posts from a Massive Open Online Course \cite{reich_computer-assisted_2014}.
+
+\cite{roberts_structural_2014} .
+This article focuses on how the STM is helpful for survey researchers and experimentalists.
+The STM makes analyzing open-ended responses easier, more revealing, and capable of being used to estimate treatment effects.
+We illustrate these innovations with analysis of text from surveys and experiments.
+
+\cite{lucas_computer_2015} This article discusses practical issues that arise in the processing, management, translation, and analysis of textual data with a particular focus on how procedures differ across languages.
+These procedures are combined in two applied examples of automated text analysis using the recently introduced Structural Topic Model.
+We also show how the model can be used to analyze data that have been translated into a single language via machine translation tools.
+All the methods we describe here are implemented in open-source software packages available from the authors.
+
+\citet{baturo_what_2017} applies STM to countries’ annual statements in the UN General Debate.
+This paper identifies the main international development topics that states raise in these speeches between 1970 and 2016, and examine the country-specific drivers of international development rhetoric.
+
+\cite{das_trends_2017} Through the use of a structural topic model, this study introduced distinct topic models on the basis of the relative frequencies of the words used in the abstracts of 15,357 TRB compendium papers.
+With data from 7 years (2008 through 2014) of TRB annual meeting compendium papers, the 20 most dominant topics emerged from a bag of 4 million words.
+
+\cite{law_constitutional_2016}  analysis of the world’s constitutional preambles using methods from computational linguistics suggests that they consist of a combination of the three archetypes.
+Estimation of a structural topic model yields a quantitative measure of the extent to which each preamble draws upon each archetype.
+
+\cite{mueller_reading_2016} This article provides a new methodology to predict armed conflict by using newspaper text.
+They use the estimated topic shares in linear fixed effects regression to forecast conflict out-of-sample.
+
 % -----
@@
 The scraping code was written in Python and can be made available on request.} We then filter those articles that contain the term "Bundestagswahl" (Federal Election) in their text body.
+We use the URL of these articles, to check how many times they where shared on Facebook using the \textit{sharedcount} API.\footnote{http://docs.sharedcount.com/}
 
-Figure \ref{fig_distr} shows the distribution of the number of articles from the respective news sources by date.
+Figure \ref{fig_distr1} shows the distribution of the number of articles from the respective news sources by date.
 There is a high peak around the federal elections on September, 24th.
-Most of the articles are published by welt.de, followed by stern.de.
+Most of the articles are published by welt.de, followed by stern.de (see \ref{fig_distr2}).
 
@@
 			\caption{...by date \& news source}
+			\label{fig_distr1}
 		\end{subfigure}
@@
 			\caption{... by news source}
+			\label{fig_distr2}
 		\end{subfigure}
 	\end{center}
-	\label{fig_distr}
 \end{figure}
@@
 
-To use text as data and reduce the dimensionality, a common strategy is to (a) pre-process the text by imposing some preliminary restrictions (stop-word removal, tokenization) based on the nature of the data (twitter text, newspaper articles, speeches, etc.) to reduce the number of language elements to consider and (b) limit the extent to which the dependence among elements within a document is encoded \citep{gentzkow_text_2017}.
-A raw text can than be represented as a term-document matrix, wehere each row is a numerical vector with each element indicating the frequency of a particular term in a document.
-In our case, a document is equivalent to a news article (title and body) and the collection of these documents are aggregated within a corpus.
-Any one document will contain only a subset of all unique terms, and the rows corresponding to unused terms will all be zero.
+To use text as data and reduce the dimensionality, a common strategy is to pre-process the text by imposing some preliminary restrictions (stop-word removal, tokenization) based on the nature of the data (twitter text, newspaper articles, speeches, etc.) to reduce the number of language elements to consider \citep{gentzkow_text_2017}.
+An overview of how these steps were applied to our data set can be found in the next section.
+
+After pre-processing, each document $d$ is a finite list of terms.
+Each unique term in the corpus is indexed by some $v \in \lbrace 1,...,V \rbrace$ where $V$ is the number of unique terms.
+For each document $d \in \lbrace 1,...,D \rbrace$ we compute the number of occurrences of term $v$ in document $d$ to obtain the count $x_{d,v}$.
+The $D$ x $V$ matrix $\boldsymbol{X}$ of all such counts is called the document-term matrix.
+This representation is often referred to as the bag of words model, since the order in which words are used within a document is completely disregarded.
 
@@
 This is related to the task of reducing the number of unique language elements in order to reduce the dimensionality of data (to avoid unnecessary computational complexity and overfitting) while at the same time keeping those words that reflect the content of a document.
-Any useful representation of text will throw away some information, as that is the essential purpose of text mining.
-The trick is to include the relevant information for our needs, and exclude the extraneous information.
+Any useful representation of text will throw away some information, the trick is to include the relevant information for our needs, and exclude the extraneous information.
 
@@
 These terms, often called "stop words", are important to the grammatical structure of a text, but typically don't add any additional meaning and can therefore be neglected.
-We use a pre-defined stop word list from the Snowball stemmer project\footnote{http://svn.tartarus.org/snowball/trunk/website/algorithms/*/stop.txt} together with a customized stop-word list.
+We use a pre-defined stop word list from the Snowball stemmer project\footnote{http://svn.tartarus.org/snowball/trunk/website/algorithms/*/stop.txt} together with a customized list of stop-words that are redundant superfluous or distorting.
 We also remove punctuation character (e.g.
@@
 
-After pre-processing, each document (article) is a finite list of unique terms.
-Each unique term in the corpus is indexed by some $v \in \lbrace 1,...,V \rbrace$ where $V$ is the number of unique terms.
-For each document $d \in \lbrace 1,...,D \rbrace$ we compute the number of occurrences of term $v$ in document $d$ to obtain the count $x_{d,v}$.
-The $D$ x $V$ matrix $\boldsymbol{X}$ of all such counts is called the document-term matrix.
-This representation is often referred to as the bag of words model, since the order in which words are used within a document is completely disregarded.
+We use source of each article (the news-platform) as a covariate in the topic prevalence portion of the model.
+Thus, we assume that the process differs with regard to the platform.
+In other words, the probability distribution of topics depends on the editorial strategy of a media house.
+We set the number of topics to be 40 after evaluating and maximizing topics' coherence using a cross-validation scheme while changing the number of topics (\citet{airoldi_reconceptualizing_2010}; \citet{roberts_model_2016}).
 
@@
 
-As we do not observe the topics, we need to implement an unsupervised machine learning algorithm, that takes unclassified observations of words and uncovers hidden patterns (topics) that structure them in some meaningful way.
-We can than use the output of this process as inputs into an econometric model that predicts the number of Facebook shares \citep{gentzkow_text_2017}.
+As we cannot directly observe the latent topic of an article, we use an unsupervised machine learning algorithm, that takes unclassified observations of words and uncovers hidden patterns (topics) that structure them in some meaningful way.
+We can than use the output of this process as inputs into an econometric model, that predicts the number of Facebook shares conditional on the topic of an article \citep{gentzkow_text_2017}.
 
 We use the structural topic model (STM) developed by \citet{roberts_model_2016} that allows us to incorporate document specific covariates (e.g.
-author or date).
-STM is a recent extension of the standard topic modeling technique, the Latent Dirichlet Allocation (LDA).
+the author or date of a document).
+STM is a recent extension of the standard topic modeling technique, the latent Dirichlet allocation (LDA).
 Topic models formalize the idea that documents are formed by hidden variables (topics) that generate correlations among observed terms.
 LDA is a particularly popular method for fitting a topic model \citep{blei_latent_2003}, also known as the generative aspect model \citep{minka_expectation-propagation_2002}.
-It treats each document $d$, containing $N_d$ words from a vocabulary of interest of $V$ unique terms, as a mixture of $k$ topics.
+Each document $d$ is generated from the following process \citep{blei_latent_2003}: The number of words $N$ is a random  , containing $N_d$ words from a vocabulary of interest of $V$ unique terms, is a mixture of $k$ topics.
 Thus, each document has its own probability distribution over topics.
-Simultaneously, each topic is associated with a $V$-dimensional probability mass function $\boldsymbol{\beta}_k$, that controls the frequency according to which terms are generated from that topic.
+Simultaneously, each topic has a probability distribution over terms, associated with a $V$-dimensional probability mass function $\boldsymbol{\beta}_k$, that controls the frequency according to which terms are generated from that topic.
+
 This standard topic modeling technique makes the assumption that all texts in the modeled corpus are generated by the same underlying process \citep{mishler_using_2015}.
@@
 
-We use source of each article (the news-platform) as a covariate in the topic prevalence portion of the model with the data described above.
-Each document is modeled as a mixture of multiple topics.
-Topical prevalence captures how much each topic contributes to a document.
-Because different documents come from different sources, it is natural then to want to allow this prevalence to vary with metadata that we have about document sources.
-The observed words $w_i$ in a document are then viewed as the realization of some stochastic process.\footnote{See \citet{roberts_model_2016} for a formal description of the generative process.} We set the number of topics to be 40 after evaluating and maximizing topics' coherence using a cross-validation scheme while changing the number of topics (\citet{airoldi_reconceptualizing_2010}; \citet{roberts_model_2016}).
+The following description of the generative model of the STM is based on \citet{roberts_structural_2013} ans \citept{roberts_stm:_2016}.
+The process of filling a word-position in a document begins with the generation of a document-specific topic-prevalence vector $d(\boldsymbol{\theta}_d)$ drawn from a logistic-normal distribution, where the parameters are a function of the covariate values:
+
+\begin{align*}
+	\boldsymbol{\theta}_d|\boldsymbol{x}_{d\gamma},\boldsymbol{\Sigma} \sim \textrm{LogisticNormal}(\mu = \boldsymbol{x}_{d\gamma}\boldsymbol{\Sigma})
+\end{align*}
+
+$\boldsymbol{x}_d\gamma$ lists the values of all metadata covariates for document $d$, where $\gamma$ relates these covariate values to the topic-prevalence.
+The structure of $\boldsymbol{\Sigma}$ implies the possibility of correlations across documents in the topic-prevalence vector which help enhance interpretation and prevent overfitting.
+
+Given the document-specific distribution over topics, for each word in the document ($n \in \lbrace 1,...,N_d\rbrace$) is assigned to a specific topic $z_{dn}$ through the process
+
+\begin{align*}
+	z_{dn}|\boldsymbol{\theta}_d \sim \textrm{Multinomial}(\boldsymbol{\theta}_d)
+\end{align*}
+
+where the $k^{th}$ element if $z_{dn}$ is unity and all other elements are zero when topic $k$ is chosen.
+
+Conditional in the topic chosen, a specific word, $w_{dn}$, is chosen from the overall corpus vocabulary $V$ to fill position $n$ in document $d$, using the following process:
+
+\begin{align*}
+	w_{dn}|z_{dn},\beta_{dkv} \sim \textrm{Multinomial}(\beta_{dk1},...,\beta_{dkV}).
+\end{align*}
+
+where the word probability $\beta_{dkv}$ is modeled as a function of the two parameters $m_v$ (indicating the importance of that word across all documents) and $\kappa_{kv}$ (indicating the importance of the word given the topic $k$).
+Transforming the sum of these coefficients into probabilities for use in a multinomial distribution via logistic transformation, one obtains:
+
+\begin{align*}
+	\beta_{dkv}|z_{dn}\propto\textrm{exp}(\boldsymbol{m}_v+\kappa_{kv})
+\end{align*}
+
+The STM maximizes the posterior likelihood that the observed data were generated by the above data-generating process using an iterative approximation-based variational expectation-maximization algorithm available in R's stm package \citep{roberts_stm:_2016}.
+Regularizing prior distributions are used for $\gamma$, $\kappa$ and (optionally) $\Sigma$.
+To address problems due to non-convexity, we rely on the spectral initialization approach advocated by \citet{roberts_navigating_2016}.
 
@@
 
-\begin{figure}[H]
-\centering
-	\caption{News Landscape}
-	\includegraphics[width=\textwidth]{../figs/news-landscape-map.png}	
-	\label{fig_landscape}
-\end{figure}
+%\begin{figure}[H]
+%\centering
+%	\caption{News Landscape}
+%	\includegraphics[width=\textwidth]{../figs/news-landscape-map.png}	
+%	\label{fig_landscape}
+%\end{figure}
 
@@
 
-\begin{figure}[H]
-\centering
-	\caption{Sample articles}
-	\includegraphics[width=\textwidth]{../figs/topic-classification-sample.png}	
-	\label{fig_classification}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-	\caption{Sum of Facebook shares by topic}
-	\includegraphics[width=\textwidth]{../figs/fb_shares_topics.png}	
-	\label{fig_fb_shares_topic}
-\end{figure}
+%\begin{figure}[H]
+%\centering
+%	\caption{Sample articles}
+%	\includegraphics[width=\textwidth]{../figs/topic-classification-sample.png}	
+%	\label{fig_classification}
+%\end{figure}
+%
+%\begin{figure}[H]
+%\centering
+%	\caption{Sum of Facebook shares by topic}
+%	\includegraphics[width=\textwidth]{../figs/fb_shares_topics.png}	
+%	\label{fig_fb_shares_topic}
+%\end{figure}
 
@@
 
+The examination of the topic probability distribution revealed that most documents are assigned a unique topic with high probability (65\% and higher), so that we can classify each document based on which topic has the highest probability.
+We keep only those documents, where the posterior probability of this topic is greater than 0.6 which left us with 6240 documents.
+
+The proportion of zeros in the independent variable (number of Facebook shares) is about 66\%.
+One way to model this type of situation is to assume that the data come from a mixture of two populations, one where the counts is always zero, and another where the count has a Poisson distribution with mean $\mu$.
+In this model zero counts can come from either population, while positive counts come only from the second one.
+
+The distribution of the outcome can then be modeled in terms of two parameters, $\pi$ the probability of 'always zero', and $\mu$, the mean number of publications for those not in the 'always zero' group.
+A natural way to introduce covariates is to model the logit of the probability $\pi$ of always zero and the log of the mean $\mu$ for those not in the always zero class.
+
+The two-part model relaxes the assumption that the zeros (whether or not the article is shared) and positives (how often it is shared) come from the same data generating process.
+The zero-inflated model lets the zeros occur in two different ways: as a realization of the binary process (z=0) and as a realization of the count process when the binary variable z=1.
+
+If the process generating the zeros is $f_1(.)$ and the process generating the positive responses is $f_2(.)$ then the two-part hurdle model is defined by the following probabilities.
+
+\begin{align*}
+	g(y)=\begin{cases}
+		f_1(0) + 1(f_i(0))f_2(0) if y=0 \\
+		(1-f_1(0))f_2(y) if y\geq 1
+	\end{cases}
+\end{align*}
+
+The model for the zero versus positive responses is a binary model with the specified distribution, but we usually estimate it with the probit/logit model.
+
 \end{document}

### 2017-11-09 paper/R/02_combine.Rmd
add apis

@@
 ```{r}
-library(SocialMediaMineR)
+endpoint <- "https://api.sharedcount.com/?url="
+api1 <- "&apikey=24abe04472f42e5003938b0314844010d6425d37"
+api2 <- "&apikey=68d76247a02b3d39ff592aa5616ce9f73f182934"
 
-facebook <- get_facebook(btw$url[1:100])
-
-page <- readLines(paste0(check,btw$url[i]))
-
-check <- "https://graph.facebook.com/?id="
 pattern <- 'share_count\\":[0-9]+'
-
 shares <- NULL
@@
 for (i in (length(shares)+1):nrow(btw)){
-  page <- readLines(paste0(check,btw$url[i]))
+  page <- readLines(paste0(endpoint,btw$url[i],api2))
   string <- str_extract(page, pattern)
   shares <- append(shares, as.numeric(str_extract(string, "[0-9]+")))
-  Sys.sleep(10)
 }
+```
+
+```{r}
+btw <- cbind(btw, shares)
+
+btw.reg %>%
+  filter(is.na(shares)) -> test
 ```
@@
 ```
-
-```{r}
-url_slice <- split(btw$url, ceiling(seq_along(btw$url)/1000))
-file = "../output/urls"
-
-for (i in 1:length(url_slice)){
-  url = url_slice[[i]]
-  count = as.character(i)
-  write.table(url, file=paste0(file,count,".csv"), sep ="\n", 
-              row.names = FALSE, quote = FALSE, col.names = FALSE)
-}
-
-write.table(urls1, file="../output/urls1.csv", sep ="\n", row.names = FALSE, quote = FALSE)
-write.table(urls2, file="../output/urls2.csv", sep ="\n", row.names = FALSE, quote = FALSE)
-```
-
-```{r}
-library(Rfacebook)
-
-app_id = 1580533335373831
-app_secret = "07ecdc314355649e13447278c57627f6"
-
-shares
-```

### 2017-11-25 paper/R/02_combine.Rmd
some cleaning

@@
 # Load and prepare Dataframes
-```{r}
+```{r message=FALSE}
 rm(list =ls())
@@
 okt <- read_csv("../data/eventbride/eventbride_okt_18.csv")
-nov <- read_csv("../data/eventbride/eventbride_nov_03.csv")
+nov_03 <- read_csv("../data/eventbride/eventbride_nov_03.csv")
+nov_22 <- read_csv("../data/eventbride/eventbride_nov_22.csv")
 ```
 
-## Generate new variables 
+## combine dataframes
 ```{r}
-### Oktober ###
+btw1 <- bind_rows(list(okt,nov_03,nov_22)) %>%
+  mutate(text = body,
          # Extract site 
-okt$site <- str_extract(okt$source, "(?<='uri': ')[A-z][^']*")
+         site = str_extract(source, "(?<='uri': ')[A-z][^']*")) %>%
+  # Delete duplicates
+  #filter(isDuplicate=="False") %>%
+  distinct(text, site, .keep_all = TRUE) %>%
+  select(date,title,text,site,url)
 
-# number of Facebook shares
-okt$fb_shares <- str_extract(okt$shares, "(?<='facebook': )[0-9]*")
-okt$fb_shares <- ifelse(is.na(okt$fb_shares),0, okt$fb_shares)
-okt$fb_shares <- as.integer(okt$fb_shares)
-names(okt) <- gsub("body", "text", names(okt))
-
-### November ###
-# Extract site
-nov$site <- str_extract(nov$source, "(?<='uri': ')[A-z][^']*")
-
-# number of Facebook shares
-nov$fb_shares <- str_extract(nov$shares, "(?<='facebook': )[0-9]*")
-nov$fb_shares <- ifelse(is.na(nov$fb_shares),0, nov$fb_shares)
-nov$fb_shares <- as.integer(nov$fb_shares)
-names(nov) <- gsub("body", "text", names(nov))
+btw1 <- bind_rows(df %>%
+                   mutate(date = as.Date(date)) %>%
+                   select(date,title,text,site,url),
+                 btw1)
 ```
 
-## Reduce Dataframe
+# Pre-Process Text
+## select news-outlets
 ```{r}
-keeps <- c( "welt.de","spiegel.de","stern.de","focus.de","zeit.de","bild.de" )
-keys <- paste(c("bundestagswahl","Koalition"), collapse = "|")
+keeps <- c("welt.de","spiegel.de","stern.de","focus.de","zeit.de","bild.de","tagesschau.de")
 
-df %>%
-  filter(site %in% keeps) %>%
-  filter(grepl(keys, text, ignore.case = TRUE)) -> btw1
-
-okt %>%
-  filter(isDuplicate == "False") %>%
-  filter(site %in% keeps) %>%
-  filter(grepl(keys, text, ignore.case = TRUE)) -> btw2
-
-nov %>%
-  filter(isDuplicate == "False") %>%
-  filter(site %in% keeps) %>%
-  filter(grepl(keys, text, ignore.case = TRUE)) -> btw3
+btw1 %>%
+  mutate(title_text = paste(title, text, sep=" ")) %>%
+  filter(site %in% keeps) -> btw
 ```
 
-## Combine Dataframes
+## select politic section
 ```{r}
-common_cols <- intersect(colnames(btw1), colnames(btw2))
+pat1 <- "\\w\\.de/politik/deutschland"
+pat2 <- "\\w\\.de/politik/inland"
+pat3 <- "\\w\\.de/politik/wahl"
+pat4 <- "\\w\\.de/politik/bundestagswahl"
+pat5 <- "tagesschau\\.de/inland"
 
-btw <- rbind(
-  btw1[, common_cols], 
-  btw2[, common_cols],
-  btw3[, common_cols]
-)
-
+btw %>%
+  filter(grepl(paste(pat1,pat2,pat3,pat4,pat5,
+                     sep="|"), url, perl = TRUE)) -> btw
 ```
 
-## Count number of terms in a string
+## count number of terms in a string
 ```{r}
@@
 
+## ... and filter short text & other
 ```{r}
-btw$title.text <- paste(btw$title, btw$text, sep = " ")
+btw %>%
+  filter(text_length > 200) %>%
+  # remove articles that contain daily overviews
+  filter(!grepl("News des Tages", title_text)) %>%
+  filter(!startsWith(title,"News")) %>%
+  # remove articles that only contain video 
+  filter(!grepl("Video einbetten Nutzungsbedingungen Embedding Tagesschau", title_text)) %>%
+  # remove english text
+  filter(!grepl("bild-international", url)) %>%
+  filter(!grepl("german",url)) %>%
+  # remove text that mostly contain user comments
+  filter(!grepl("kommentar", title, ignore.case = TRUE)) %>%
+  filter(!grepl("ticker", title, ignore.case = TRUE)) %>%
+  filter(!grepl("stream", title, ignore.case = TRUE)) %>%
+  filter(!startsWith(text,"1.")) -> btw
 ```
 
-# Pre-Process Text
+## Clean text
 
-## Filtering
+The following two chuncks of code are just to check right regex definitions to use it inthe clean.text function.
 ```{r}
+pat <- "Dieser Artikel wurde ausgedruckt unter der Adresse: www.tagesschau.de/inland/[^.]*"
 btw %>%
-  group_by(title, site) %>%
-  ungroup() %>%
-  distinct(title,site, .keep_all = TRUE) -> btw
-```
-
-```{r}
-btw %>%
-  # remove articles that contain daily overviews
-  filter(!grepl("Elbvertiefung", title.text)) %>%
-  filter(!grepl("News des Tages", title.text)) %>%
-  # remove articles that dont contain text
-  filter(!grepl('</div>', title.text)) -> btw
-```
-
-```{r}
-pat <- 'Florian Gathmann[^\n]*'
-btw %>%
-  filter(grepl(pat, title.text, perl = TRUE, ignore.case = TRUE)) %>%
-  #select(text) %>%
+  filter(grepl(pat, title_text, perl = TRUE, ignore.case = TRUE)) %>%
+  #filter(site=="tagesschau.de") %>%
+  #select(url, title_text) %>% 
   #.[1,] %>%
@@
 ```{r}
-as.data.frame(str_match(btw$title.text, pat)) ->test
+as.data.frame(str_match(btw$title_text, pat)) ->test
 test %>%
@@
 
+### define function  
 ```{r, echo=FALSE, message=FALSE, warning=FALSE}
@@
   x = gsub('Startseite[^\n]*', "", x, ignore.case = TRUE, perl = TRUE)
+  x = gsub("deutsche presse agentur","", x, ignore.case = TRUE, perl = TRUE)
 
@@
   x = gsub('Welt twitter', "", x, perl = TRUE, ignore.case = TRUE)
+  x = gsub('\\w{1,} für Abonnenten', "", x, perl = TRUE, ignore.case = TRUE)
 
@@
 
+  # Tagesschau.de
+  x = gsub("Hinweis: Falls die [^\\.]*", "", x, perl=TRUE)
+  x = gsub("auswählen", "", x, perl = TRUE)
+  x = gsub("Dieser Artikel wurde ausgedruckt unter der Adresse: www.tagesschau.de/inland/[^.]*", "", x, perl = TRUE)
+
   return(x)
@@
 # apply function to dataframe
-btw$text_cleaned <- clean.text(btw$title.text)
+btw$text_cleaned <- clean.text(btw$title_text)
 ```
@@
 ```{r}
-mystopwords <- c("focus","online","spiegel", "stern", "handelsblatt", "de", "bild","bildplus", "zeit", "ersten", "tagesschau", "wdr", "ndr", "ich","sie","passwort","kommentar","wurde","ihr","der","im","artikel","mehr","ihren","foto","e","seien","comment", "uhr","videolänge","dass","mindestens","das","mail","die","schon","neuer abschnitt", "login", "loggen", "inaktiv", "nwmi", "nwnoa", "polizei","beim","dpa","video","quelle","afp","witters","fotogalerie","wurden","worden","wegen","sagt","immer","gibt","geht","spon", "registrierter","als","spiegel","vielen","in","es","bitte","dank","unserer","nutzer","sei","beitrag","user","seit","zeichen", "datenschutzerklärung","premium","nutzungsbedingungen","nutzungsrechte","pflichtfelder","registrierung","anzeige","großbuchstaben","sonderzeichen","html","seitennavigation","fullscreen","statista","club","sagte","borenda","spreepicture","shopübersicht")
+mystopwords <- c("focus","online","spiegel", "stern", "de", "bild","bildplus", "zeit", "ersten", "tagesschau", "zeitmagazin","seitenanfang","ja","mal","heute","ich","sie","passwort","kommentar","wurde","ihr","der","im","artikel","mehr","ihren","foto","e","seien","comment","ticker","live","laif","uhr","videolänge","dass","mindestens","das","mail","die","schon","neuer abschnitt", "login", "loggen", "inaktiv","nwmi","wäre","viele","nwnoa","morgenkolumne","beim","dpa","video","quelle","afp","witters","fotogalerie","wurden","worden","wegen","sagt","immer","gibt","geht","spon","registrierter","als","spiegel","vielen","in","es","bitte","dank","unserer","nutzer","sei","beitrag","user","seit","zeichen","tba","datenschutzerklärung","premium","nutzungsbedingungen","nutzungsrechte","pflichtfelder","registrierung","anzeige","großbuchstaben","sonderzeichen","html","seitennavigation","fullscreen","statista","club","sagte","borenda","spreepicture","shopübersicht")
 
@@
 btw$text_cleaned<- removeWords(btw$text_cleaned, mystopwords$mystopwords)
+```
+
+### check words with high tf-idf 
+```{r}
+token <- btw %>%
+  group_by(site) %>%
+  unnest_tokens(word, text_cleaned) %>%
+  count(site, word, sort = TRUE)  %>%
+  bind_tf_idf(word, site, n) %>%
+  arrange(desc(tf_idf))
+
+token %>%
+  arrange(desc(tf)) %>%
+  arrange(site) %>%
+  top_n(10)
+```
+
+### Bigrams
+```{r, include=FALSE}
+bigrams <- btw %>%
+  unnest_tokens(bigram, text_cleaned, token="ngrams", n=2)
+
+bigrams %>%
+  group_by(site) %>%
+  count(bigram) %>%
+  arrange(desc(n)) %>%
+  top_n(10)
 ```
@@
 
-```{r}
-load(file="../output/btw_combined.Rda")
-```
-
-# Extract FB Shares
+# Add new variables
+## FB Shares
 ```{r}
@@
 for (i in (length(shares)+1):nrow(btw)){
-  page <- readLines(paste0(endpoint,btw$url[i],api2))
+  page <- readLines(paste0(endpoint,btw$url[i],api1))
   string <- str_extract(page, pattern)
@@
 
-btw.reg %>%
-  filter(is.na(shares)) -> test
+btw <- btw %>% mutate(fb_shares = shares) %>%
+  select(-shares)
+```
+
+## month & document number
+```{r}
+btw %>%
+  mutate(month = month(date),
+         articleID = as.numeric(rownames(btw))) -> btw
 ```

### 2017-11-25 paper/R/03_stm.Rmd
some cleaning

@@
 source("func/02-topic-modelling-functions.R")
-
-```
-
-```{r caching, echo = FALSE}
-load("../output/models/STM 40 .Rda")
-#load("../output/btw_combined.Rda")
+```
+
+```{r caching, echo=, message=FALSE, warning=FALSE}
+load("../output/btw_combined.Rda")
+
+#load("../output/models/STM 50 .Rda")
 knitr::opts_chunk$set(eval = TRUE, warning = FALSE, message = FALSE)
-
-#btw$articleID <- rownames(btw)
 ```
@@
 library(RColorBrewer) 
-
-col <- brewer.pal(6,"Dark2")
-```
-
-```{r}
+col <- brewer.pal(7,"Dark2")
+```
+
+```{r message=FALSE, warning=FALSE}
 btw %>%
@@
   theme(legend.position="none") +
-  labs(x="", y="Count",color="")
-
-#ggsave("../figs/timeline.png", plot = last_plot(), device = "png", 
+  labs(x="", y="Count",color="") +
+  scale_x_date(breaks = date_breaks("2 weeks"), labels=date_format("%d.%m", tz="CET"))
+
+# ggsave("../figs/timeline.png", plot = last_plot(), device = "png", 
 #        dpi = 600)
@@
 
-```{r}
+```{r message=FALSE, warning=FALSE}
 btw %>%
@@
 
-#ggsave("../figs/bar.png", plot = last_plot(), device = "png", 
+# ggsave("../figs/bar.png", plot = last_plot(), device = "png", 
 #        dpi = 600)
@@
 
-```{r}
+```{r message=FALSE, warning=FALSE}
 btw %>%
-  ggplot(aes(date, site, size=fb_shares, color = site)) +
+  ggplot(aes(date, site, size=text_length, color = site)) +
   geom_point(show.legend = FALSE, alpha = .8) +
@@
 
-#ggsave("../figs/fb_shares.png", plot = last_plot(), device = "png", 
+# ggsave("../figs/fb_shares.png", plot = last_plot(), device = "png", 
 #        dpi = 600)
-
+```
+
+```{r message=FALSE, warning=FALSE}
 btw %>%
-  filter(site == "bild.de") %>%
-  select(title, text, fb_shares) %>%
-  .[3,] %>%
-  htmlTable::htmlTable()
-```
-
-```{r}
-btw %>%
-  ggplot(aes(site, fb_shares)) +
-  stat_summary(fun.y="mean", geom="bar", fill = col, alpha = .8) +
+  ggplot(aes(site, text_length)) +
+  stat_summary(fun.y="median", geom="bar", fill = col, alpha = .8) +
   labs(x="", y="")
@@
 
+# Structural Topic Model
+## Build Corpus
+```{r eval=FALSE, include=FALSE}
+# Process data
+processed <- textProcessor(btw$text_cleaned, metadata = btw[,c("site","text_cleaned","month")],
+                           wordLengths = c(2,Inf),
+                           lowercase = F,
+                           removestopwords = F,
+                           removenumbers = F,
+                           removepunctuation = F,
+                           stem = F)
+out <- prepDocuments(processed$documents, processed$vocab, processed$meta)
+```
+
+### Select number of topics
+```{r}
+K<-c(30,40,50,60,80)
+
+t1 <- Sys.time()
+kresult <- searchK(out$documents, out$vocab, K, prevalence=~site + s(btw_dummy), data = out$meta, init.type = "Spectral")
+t2 <- Sys.time()
+t2 - t1
+
+save(btw, out, kresult, file="../output/models/kresult.Rda")
+#load(file="../output/models/kresult.Rda")
+```
+
+```{r}
+plot(kresult)
+```
+
+We then train the Structural Topic Model on the full dataset, with $k = 50$.
+
+```{r}
+k = 40 # Topics
+
+t1 <- Sys.time()
+stmOut <- stm(documents = out$documents,
+           vocab = out$vocab,
+           K=k,
+           prevalence = ~site+s(month),
+           data=out$meta,
+           max.em.its = 75,
+           seed =8458159,
+           init.type = "Spectral")
+t2 <- Sys.time()
+t2 - t1
+
+save(stmOut, btw, out, file=paste("../output/models/STM",k,".Rda"))
+
+#load(file=paste("../output/models/STM",k,".Rda"))
+```
+
+## Explore Model Results
+
+### Using build-in functions
+#### Topic Summary
+```{r}
+plot(stmOut, type = "summary", xlim = c(0,.14), n = 5, #labeltype = "frex",
+         main = "Online News Topics", text.cex = 0.8)
+```
+
+The most frequent words in the model such as for topics #3, #7, and #20
+```{r}
+plot(stmOut, type="labels", topics=c(37,8))
+```
+
+A comparison of two topics 
+```{r}
+plot(stmOut, type="perspectives", topics=c(37,8))
+```
+
+The estimateEffect() function explores how prevalence of topics varies across documents according to document covariates (metadata).
+First, users must specify the variable that they wish to use for calculating an effect.
+If there are multiple variables specified in estimateEffect(), then all other variables are held at their sample median.
+These parameters include the expected proportion of a document that belongs to a topic as a function of a covariate, or a first difference type estimate, where topic prevalence for a particular topic is contrasted for two groups
+```{r}
+out$meta$site <- as.factor(out$meta$site)
+prep <- estimateEffect(1:50 ~ site+s(month), stmOut, meta=out$meta, uncertainty = "Global")
+```
+
+To see how prevalence of topics differs across values of a continuous covariate:
+```{r}
+plot(prep, "month", method="continuous", topics = c(46,42),
+     xlab="Month (2017)")
+monthseq <- seq(from=as.Date("2017-06-01"), to=as.Date("2017-11-01"), by="month")
+monthnames <- month(monthseq)
+axis(1, at=as.numeric(monthseq), labels = monthnames)
+```
+
+#### Topic Labeling
 ```{r Tokenize}
@@
 
-## Structural Topic Model
-
-```{r eval=FALSE, include=FALSE}
-# Build Corpus
-btw$month <- month(btw$date)
-# Process data
-processed <- textProcessor(btw$text_cleaned, metadata = btw[,c("site","text_cleaned")],
-                           wordLengths = c(2,Inf),
-                           lowercase = F,
-                           removestopwords = F,
-                           removenumbers = F,
-                           removepunctuation = F,
-                           stem = F)
-out <- prepDocuments(processed$documents, processed$vocab, processed$meta)
-```
-
-We then train the Structural Topic Model on the full dataset, with $k = 40$.
-
-```{r eval=FALSE, include=FALSE}
-k = 40 # Topics
-
-t1 <- Sys.time()
-stmOut <- stm(documents = out$documents, 
-           vocab = out$vocab, 
-           K=k, 
-           prevalence = ~site, 
-           data=out$meta, 
-           init.type = "Spectral")
-t2 <- Sys.time()
-t2 - t1
-
-save(stmOut, btw, out, file=paste("../output/models/STM",k,".Rda"))
-
-```
-
-#### Topic Labeling
-
 ```{r Extract wtp and dtp}
-
 # Word-topic probabilities
@@
 ```{r Compute relevance}
-
 posts.wtp %>%
@@
 doctopics.df <- theta %>%
-  transmute(articleID = rownames(.),
+  transmute(articleID = as.numeric(rownames(.)),
     topic = as.numeric(gsub("V","",topic)))
@@
               select(topic_name, topic) %>%
-              mutate(topic = as.numeric(topic)), by="topic") -> btw2
+              mutate(topic = as.numeric(topic)), by="topic") -> btw
 
 # subset  
-topics_mapping.dt <- btw2 %>%
+topics_mapping.dt <- btw %>%
   group_by(topic) %>%
-  slice(1) %>%
-  select(topic, title.text, articleID, topic_name) 
-```
-
-## Topic Summary
-```{r}
-plot(stmOut, type = "summary", xlim = c(0,.14), n = 5, #labeltype = "frex",
-         main = "Online News Topics", text.cex = 0.8)
+  slice(5) %>%
+  select(topic, articleID, topic_name)
 ```
@@
   ungroup() %>%
-  inner_join(btw2 %>% select(title, articleID) %>%
-               mutate(articleID = as.numeric(articleID)), by = "articleID") %>% 
-  inner_join(topics_mapping.dt, by = "topic") %>%
+  inner_join(btw %>% select(title, title_text, articleID, topic_name),
+              by = "articleID") %>%
+  #inner_join(topics_mapping.dt, by = "topic") %>%
   mutate(topic_title = 
@@
       scale_color_manual(
-        values = rainbow(40) %>% 
+        values = rainbow(50) %>% 
           adjustcolor(red.f = 0.6, green.f = 0.6, blue.f = 0.6)
@@
           scale_color_manual(
-            values = rainbow(40) %>% 
+            values = rainbow(39) %>% 
               adjustcolor(red.f = 0.6, green.f = 0.6, blue.f = 0.6)
@@
 
+```{r}
+btw %>%
+  #filter(topic==4) %>%
+  filter(startsWith(title,"News")) %>%
+  select(url,title, text)
+```
+
 ### Topic Trends
@@
   inner_join(
-    btw2 %>% 
-      mutate(document = as.numeric(articleID)) %>%
+    btw %>% 
+      mutate(document = as.numeric(articleID),
+             date = as.POSIXct(date)) %>%
       select(document, date, 
@@
 
-```{r}
+```{r message=FALSE, warning=FALSE}
 chart_topic_trends.dt %>% 
@@
 ```{r Facebook Shares}
-btw %>%
+btw2 %>%
   ggplot(aes(as.factor(topic), fb_shares)) +
@@
   labs(x="", y="Sum") +
-  scale_x_discrete(breaks=c(1:40), labels = topicLabel$topic_name) +
-  theme(axis.text.x = element_text(size=6, angle=90),
+  scale_x_discrete(breaks=c(1:50), labels = topicLabel$topic_name) +
+  theme(axis.text.x = element_text(size=7, angle=90),
         axis.text.y = element_text(size=7))

### 2017-11-25 paper/R/04_regression.Rmd
some cleaning

@@
 load("../output/btw_combined.Rda")
-btw2 <- btw
 
@@
 
+Have a look at the assigned topics per documents
+```{r}
+btw$articleID <- as.numeric(rownames(btw))
+
+# filter documents with low posterior
+btw.reg <- 
+  btw %>%
+  mutate(document = articleID) %>%
+  left_join(., top_topics, by="document")
+
+btw.reg %>%
+  filter(site=="focus.de") %>%
+  group_by(topic, site) %>%
+  arrange(desc(gamma)) %>%
+  select(title, topic, gamma, url) %>%
+  top_n(2) %>%
+  htmlTable::htmlTable()
+```
+
 We classify each document based on which topic has the highest probability.
@@
 ```{r}
+# filter documents with low posterior
 btw.reg <- 
   btw %>%
-  left_join(., btw2 %>%
-              select(title.text, shares, url),
-            by = "title.text")
-```
-
-```{r}
-# filter documents with low posterior
-btw.reg <- 
-  btw.reg %>%
-  mutate(document = as.numeric(articleID)) %>%
-  left_join(., top_topics, by="document") %>%
+  mutate(document = articleID) %>%
+  left_join(., top_topics, by="document") 
   filter(gamma > 0.5)

### 2017-11-25 paper/doc/doc2.tex
some cleaning

@@
 \usepackage{eurosym}
+
+\addbibresource{Textmining.bib}
 
@@
 % ------------------
+\section{Related Literature}
+% ---------------------------------------
+% Business Model in the online news market
+% --------------------------------------- 
+\subsection{The online news market}
 
-\section{Related Literature}
+Media outlets naturally appear as two-sided platforms, that allow interaction between two categories of consumers: audiences and advertisers.
+The demand on both consumer-sides are often linked via indirect network externalities.
+The market in which media outlets operate are accordingly referred to as two-sided or multi-sided markets.
+The theoretical literature on two-sided markets originates from the analysis of credit card markets \citep{rochet_platform_2003} and was later transferred to the concept of other industries, such as dating agencies, real estate agents, and internet “business-to-business” websites \citep{caillaud_chicken_2003}.
+The basic concept of two-sided markets was already discussed decades ago in several economic studies, especially on media markets \citep{corden_maximisation_1952}, \citep{gustafsson_circulation_1978}, \citep{blair_pricing_1993}.
+However, comprehensive analyses have only been carried out in the last ten years, starting with the works of \citet{rochet_platform_2003}, \citet{evans_empirical_2003} and \citet{armstrong_competition_2006}.
 
-% Quantitative approaches
-% -----------------------
+Online news are typical examples of two-sided markets where the news pages can be conceived as platforms that allow interaction between audiences ("eyeballs") and advertisers.
+The size and characteristics of the audience has a positive effect on the advertisers' willingness to pay, as advertisements are typically sold based on cost per viewer, often expressed in terms of the cost of reaching a thousand viewers (CPM).
+Advertising can also have an effect on the recipients, which can be both negative and positive, depending on the quality of the advertising.
 
-% Topic Modeling / LDA
-% ---------------------------
+Depending on the strength of the indirect network effects, publisher maximize their revenue by balancing the demand from advertisers and subscribers using different business models \citep{evans_economics_2008}.
+Many traditional newspapers follow the subscription/advertising model, where the publisher charges both market sides: The audience pays a fee to obtain access to the content, and advertisers pay to to obtain access to the viewers.
+Many online news agencies also provide a part of their editorial content as a premium service.
+However, since the Internet has considerably simplified the possibilities for obtaining information and thus reduced the marginal utility of content, such a business model can only function if the content is very exclusive.
+As a result, many publishers rely on a free-media model, in which the publishers do not charge viewers for access to the media at all, in order to attract as many readers as possible to their platform, and thus exploit the indirect network effects on the advertising site.
+% What is the share of advertising revenue in total earnings of german online newspaper ?
 
-Topic modeling is a statistical and computational technique for discerning information about the contents of a large corpus of documents without reading or annotating the original texts.
-A topic model uncovers patterns of word co-occurrence across the corpus, yielding a set of word clusters, together with associated probabilities of occurrence, which constitute the topics.
+In addition to the quantity of the audience, the demographic characteristics of recipients also have an influence on the willingness to pay on the advertiser site.
+Online advertising makes it possible to target ads to particular consumers in real time.
+Facebook instant articles facilitates this targeting, as they make the public users profile data available to the publisher.
 
-See \citep{taddy_estimation_2012} for a review of topic estimation techniques)
+The two-sided market structure of news markets results in news platforms striving to choose their content in such a way that its reach is as large as possible in order to maximize profits from advertising revenues.
+This may lead to media-bias, as advertising may affect the ability and incentives of media to provide independent news.
+On the other hand, advertising may also have a positive impact on the media, as it enables publishers to report independently of political parties.
+\citet{ellman_what_2009} found that advertising increases the intensity of competition for readers and therefore raises accuracy of media coverage.
 
-Since its introduction into text analysis, topic modeling has become hugely popular.8 (See \citet{blei_probabilistic_2012} for an overview.) The model has been especially useful in political science (e.g., \citep{grimmer_bayesian_2010}), where researchers have been successful in attaching political issues and beliefs to the estimated latent topics.
+% --------------
+% Topic Modeling
+% --------------
+\subsection{Topic Modeling}
 
-Topic modeling is alternatively labeled as “latent Dirichlet allocation,” (LDA) which refers to the Bayesian model in \citet{blei_latent_2003} that treats each $\boldsymbol{v}_i$ and $\boldsymbol{\theta}_l$ as generated from a Dirichlet - distributed prior.
-The same model was independently introduced in genetics by \citet{pritchard_inference_2000} for factorizing gene expression as a function of latent populations; it has been similarly successful in that field.
+We use the structural topic model (STM) developed by \citet{roberts_model_2016} that allows us to incorporate document specific covariates (e.g.
+the author or date of a document).
+STM is a recent extension of the standard topic modeling technique, labeled as "latent Dirichlet allocation" (LDA), which refers to the Bayesian model in \citet{blei_latent_2003} that treats each word in a topic and each topic in a document as generated from a Dirichlet - distributed prior.\footnote{See also \citet{griffiths_probabilistic_2002}, \citet{griffiths_finding_2004} and \citet{hofmann_probabilistic_1999}.
+\citet{pritchard_inference_2000} introduced the same model in genetics for factorizing gene expression as a function of latent populations.} Topic models formalize the idea that documents are formed by hidden variables (topics) that generate correlations among observed terms.
+Since its introduction into text analysis, LDA has become hugely popular and especially useful in political science.\footnote{see \citet{blei_probabilistic_2012} and \citet{grimmer_text_2013} for an overview.}
 
-The basic topic model has been generalized and extended in variety of ways.
-A prominent example is the dynamic topic model of \citet{blei_dynamic_2006}, which considers documents that are indexed by date (e.g., publication date for academic articles) and allows the topics, say $\boldsymbol{\Theta}_t$, to evolve smoothly in time.
+The basic topic model has been extended in variety of ways.
+\citet{blei_dynamic_2006} considers documents that are indexed by publication date date and allows the topics to evolve in time.
+To relax the assumption that all texts in the modeled corpus are generated by the same underlying process, \cite{roberts_model_2016} introduces the structural topic model (STM), that provides a way to include covariates.
+Using a generalized linear model on document-level metadata allows the researcher to link topics to covariate data and to model changes in topic prevalence over time.
 
-Applications:
-
-% Structural topic models (STM)
-% ----------------------------
-A typical application of topic modeling in the social sciences first estimates LDA, then uses estimates of $\theta_d$ as the dependent variable in an regression on covariates to test whether different types of documents have different content.
-
-This is contradictory because documents are assumed to be generated by a statistical process that we subsequently reject.
-
-The structural topic model (STM) of Roberts et.
-al.
-(2016) explicitly introduces covariates into a topic model, and allows one to estimate the impact of document-level covariates on topic content and prevalence as part of the topic model itself.
-
-Applications:
-Structural topic modeling is an alternative to LDA that allows researchers to link topics to covariate data and to model changes in topic prevalence over time.
-STM has recently been applied to scientific texts on climate change, revealing links between corporate funding and the framing of scientific studies \citep{farrell_corporate_2016}.
-It has also been applied to social media data in a variety of ways.
-One study shows that “STM can be used to detect significant events such as the downing of Malaysia Air Flight 17” when applied to twitter data \cite{mishler_using_2015}.
-Another study shows how STM can be used to explore relatively large data sets including course evaluations and discussion forum posts from a Massive Open Online Course \cite{reich_computer-assisted_2014}.
-
-\cite{roberts_structural_2014} .
-This article focuses on how the STM is helpful for survey researchers and experimentalists.
-The STM makes analyzing open-ended responses easier, more revealing, and capable of being used to estimate treatment effects.
-We illustrate these innovations with analysis of text from surveys and experiments.
-
-\cite{lucas_computer_2015} This article discusses practical issues that arise in the processing, management, translation, and analysis of textual data with a particular focus on how procedures differ across languages.
-These procedures are combined in two applied examples of automated text analysis using the recently introduced Structural Topic Model.
-We also show how the model can be used to analyze data that have been translated into a single language via machine translation tools.
-All the methods we describe here are implemented in open-source software packages available from the authors.
-
-\citet{baturo_what_2017} applies STM to countries’ annual statements in the UN General Debate.
-This paper identifies the main international development topics that states raise in these speeches between 1970 and 2016, and examine the country-specific drivers of international development rhetoric.
-
-\cite{das_trends_2017} Through the use of a structural topic model, this study introduced distinct topic models on the basis of the relative frequencies of the words used in the abstracts of 15,357 TRB compendium papers.
-With data from 7 years (2008 through 2014) of TRB annual meeting compendium papers, the 20 most dominant topics emerged from a bag of 4 million words.
-
-\cite{law_constitutional_2016}  analysis of the world’s constitutional preambles using methods from computational linguistics suggests that they consist of a combination of the three archetypes.
-Estimation of a structural topic model yields a quantitative measure of the extent to which each preamble draws upon each archetype.
-
-\cite{mueller_reading_2016} This article provides a new methodology to predict armed conflict by using newspaper text.
+STM has been applied to multiple academic fields: \citet{roberts_structural_2014} uses STM to analyse open-ended responses from surveys and experiments, \citet{farrell_corporate_2016} applies the model to scientific texts on climate change, revealing links between corporate funding and the framing of scientific studies and \citet{mishler_using_2015} shows that "STM can be used to detect significant events such as the downing of Malaysia Air Flight 17" when applied to twitter data.
+Another study shows how STM can be used to explore the main international development topics of countries’ annual statements in the UN General Debate and examine the country-specific drivers of international development rhetoric \citep{baturo_what_2017}.
+\citet{mueller_reading_2016} uses newspaper text to predict armed conflicts in different regions.
 They use the estimated topic shares in linear fixed effects regression to forecast conflict out-of-sample.
@@
 % -----
-
 \section{Dataset}\label{ch_data}
@@
 The scraping code was written in Python and can be made available on request.} We then filter those articles that contain the term "Bundestagswahl" (Federal Election) in their text body.
-We use the URL of these articles, to check how many times they where shared on Facebook using the \textit{sharedcount} API.\footnote{http://docs.sharedcount.com/}
+We use the URL of these articles, to check how many times they where shared on Facebook using the \textit{sharedcount} API.\footnote{http://docs.sharedcount.com/} The returned share count is the sum of (1) the number of likes of this URL, (2) the number of shares of this URL (including copy-pasting a link back to Facebook), (3) the number of likes and comments on stories on Facebook about this URL and (4) the number of inbox messages containing this URL as an attachment.\footnote{See https://developers.facebook.com/docs/graph-api for more information about the Facebook Graph API.}
 
@@
 % ------------------
-\subsection{Text pre-procesing and feature selection}
+\subsection{Text pre-procesing}
 
@@
 
-We use source of each article (the news-platform) as a covariate in the topic prevalence portion of the model.
-Thus, we assume that the process differs with regard to the platform.
-In other words, the probability distribution of topics depends on the editorial strategy of a media house.
-We set the number of topics to be 40 after evaluating and maximizing topics' coherence using a cross-validation scheme while changing the number of topics (\citet{airoldi_reconceptualizing_2010}; \citet{roberts_model_2016}).
-
 % ----------------------
@@
 % ----------------------
-
 \section{Topic detection}\label{ch_model}
 
-As we cannot directly observe the latent topic of an article, we use an unsupervised machine learning algorithm, that takes unclassified observations of words and uncovers hidden patterns (topics) that structure them in some meaningful way.
-We can than use the output of this process as inputs into an econometric model, that predicts the number of Facebook shares conditional on the topic of an article \citep{gentzkow_text_2017}.
-
-We use the structural topic model (STM) developed by \citet{roberts_model_2016} that allows us to incorporate document specific covariates (e.g.
-the author or date of a document).
-STM is a recent extension of the standard topic modeling technique, the latent Dirichlet allocation (LDA).
-Topic models formalize the idea that documents are formed by hidden variables (topics) that generate correlations among observed terms.
-LDA is a particularly popular method for fitting a topic model \citep{blei_latent_2003}, also known as the generative aspect model \citep{minka_expectation-propagation_2002}.
-Each document $d$ is generated from the following process \citep{blei_latent_2003}: The number of words $N$ is a random  , containing $N_d$ words from a vocabulary of interest of $V$ unique terms, is a mixture of $k$ topics.
-Thus, each document has its own probability distribution over topics.
-Simultaneously, each topic has a probability distribution over terms, associated with a $V$-dimensional probability mass function $\boldsymbol{\beta}_k$, that controls the frequency according to which terms are generated from that topic.
-
-This standard topic modeling technique makes the assumption that all texts in the modeled corpus are generated by the same underlying process \citep{mishler_using_2015}.
-To include additional information that improve the estimation of the topics, we estimate a structural topic model, where topical prevalence (the distribution of topics among documents) is specified as a simple generalized linear model on document-level metadata.
-
-The following description of the generative model of the STM is based on \citet{roberts_structural_2013} ans \citept{roberts_stm:_2016}.
+The following description of the generative model of the STM is based on \citet{roberts_structural_2013} and \citept{roberts_stm:_2016}.
 The process of filling a word-position in a document begins with the generation of a document-specific topic-prevalence vector $d(\boldsymbol{\theta}_d)$ drawn from a logistic-normal distribution, where the parameters are a function of the covariate values:
@@
 
-\section{Probabilities and Classification}\label{ch_results}
+% ----------------------
+% Model Selection
+% ----------------------
+\subsection{Model selection}
+
+Topic models are generally inaccurate, since the number of topics must be determined a priori.
+Furthermore, multiple solutions exist for the optimization problem.
+Ex post analysis of several model specifications helps to evaluate its quality, as well as the number of topics and metadata selected.
+
+The most common choice is the probability of held-out documents \citep{grimmer_bayesian_2010}.
+Similar to cross-validation (VC), different model specifications are compared to how well they do in predicting words within a document \citep{asuncion_smoothing_2012}, \citep{wallach_evaluation_2009}.
+Another strategy to find an appropriate number of topics is to check for residual overdispersion of the variance of the multinomial within the data generating process of the model \citep{taddy_estimation_2012}.
+Other approaches can be found in \citet{airoldi_reconceptualizing_2010} and \citet{teh_hierarchical_2006}.
+We run multiple model specifications and compare them based on held-out likelihood estimation, residual checks as well as semantic coherence to chose the number of topics that best fits the corpus to be 50.
+Furthermore, we use the source of each article (the media house) and the month it was published as a covariates in the topic prevalence portion of the model.
+In other words, the probability distribution of topics depends on the editorial strategy of a media house as well as on the month the article was published.
+
+% ----------------------
+% Evaluation
+% ----------------------
+\subsection{Evaluation}
+
+The most effective method for assessing model fit is to carefully read documents that are closely associated with particular topics to verify that the semantic concept covered by the topic is reflected in the text.
+The parameter θd provides an estimate of each document’s association with every topicmaking it straightforward to effectively direct analyst engagement with the texts (see, e.g., Roberts, Stewart, and Tingley 2014a).
+An overview of manual validation procedures can be found in Grimmer and Stewart (2013).\cite{roberts_model_2016}
+
+To validate the accuracy with which the fitted model is capturing the content of a document, we first conduct a process of informal manual audits \citep{gentzkow_text_2017}: We inspect inspect a subset of documents alongside the fitted topics to cross-check against the coding a human would produce by hand.
+Figure \ref{fig_classification} shows sample documents classified to each topic for reference.
+We produce a random sample of 7 posts from the 300 highest probability fits per topic.
+
+\begin{figure}[H]
+\centering
+	\caption{Sample articles}
+	\includegraphics[width=\textwidth]{../figs/topic-classification-sample.png}	
+	\label{fig_classification}
+\end{figure}
+
+The interpretability or semantic coherence of topics can vary considerably.
+\citet{mimno_optimizing_2011} propose a topic semantic coherence score computed from in-corpus word co-occurrence statistics, and show strong agreement with human evaluations.
+
+\cite{mimno_optimizing_2011}
+The evaluation of statistical topic models has traditionally been dominated by either extrinsic methods (i.e., using the inferred topics to perform some external task such as information retrieval \citep{wei_lda-based_2006} or quantitative intrinsic methods, such as computing the probability of held-out documents \citep{wallach_evaluation_2009}.
+Recent work has focused on evaluation of topics as semantically coherent concepts.
+For example, \citet{chang_reading_2009} found that the probability of held-out documents is not always a good predictor of human judgments.
 
@@
 
-To check weather the estimated topic classifications make sense, we first produce sample documents classified to that topic for reference.
-We produce a random sample of 10 posts from the 300 highest probability fits per topic.
-
-%\begin{figure}[H]
-%\centering
-%	\caption{Sample articles}
-%	\includegraphics[width=\textwidth]{../figs/topic-classification-sample.png}	
-%	\label{fig_classification}
-%\end{figure}
 %

### 2017-12-08 paper/R/02_cleanAndCombine.Rmd
new

--- 2017-11-25 paper/R/02_combine.Rmd
@@
 nov_22 <- read_csv("../data/eventbride/eventbride_nov_22.csv")
+nov_30 <- read_csv("../data/eventbride/eventbride_nov_30.csv")
 ```
@@
 ## combine dataframes
+
 ```{r}
-btw1 <- bind_rows(list(okt,nov_03,nov_22)) %>%
+btw1 <- bind_rows(list(okt,nov_03,nov_22,nov_30)) %>%
   mutate(text = body,
@@
 btw %>%
-  filter(grepl(paste(pat1,pat2,pat3,pat4,pat5,
-                     sep="|"), url, perl = TRUE)) -> btw
+  mutate(politics = ifelse(grepl(paste(pat1,pat2,pat3,pat4,pat5,
+                     sep="|"), url, perl = TRUE),1,0)) -> df_full
+```
+
+```{r}
+df_full %>%
+  filter(politics == 1) %>%
+  distinct(url, .keep_all = T) -> btw
 ```
@@
   filter(!grepl("News des Tages", title_text)) %>%
+  filter(!grepl("Nachrichten am Morgen", title)) %>%
   filter(!startsWith(title,"News")) %>%
@@
 
+```{r}
+btw %>%
+  filter(grepl("faktenfinder", title_text)) %>%
+  select(url, title_text)
+```
+
 ## Clean text
@@
 ```{r}
-pat <- "Dieser Artikel wurde ausgedruckt unter der Adresse: www.tagesschau.de/inland/[^.]*"
+pat <- "Eine Kolumne von \\w{1,} \\w{1,}"
 btw %>%
@@
   filter(!is.na(test)) %>%
-  .[1:100,]
+  .[1:30,]
 ```
@@
   x = gsub("deutsche presse agentur","", x, ignore.case = TRUE, perl = TRUE)
+  x = gsub("Eine Kolumne von \\w{1,} \\w{1,}", "", x, ignore.case = T, perl = TRUE)
 
@@
   x = gsub('Florian Gathmann[^\n]*', "", x, perl = TRUE)
+  x = gsub('Eine Kolumne von Jan Fleischhauer', "", x, perl = TRUE)
 
@@
   x = gsub("Dieser Artikel wurde ausgedruckt unter der Adresse: www.tagesschau.de/inland/[^.]*", "", x, perl = TRUE)
+  x = gsub("faktenfinder.tagesschau.de", "", x, perl=TRUE)
 
@@
   group_by(site) %>%
-  unnest_tokens(word, text_cleaned) %>%
+  unnest_tokens(word, title) %>%
   count(site, word, sort = TRUE)  %>%
@@
 for (i in (length(shares)+1):nrow(btw)){
-  page <- readLines(paste0(endpoint,btw$url[i],api1))
+  page <- readLines(paste0(endpoint,btw$url[i],api2))
   string <- str_extract(page, pattern)
@@
   select(-shares)
+
+unique(btw$site)
 ```
@@
   mutate(month = month(date),
-         articleID = as.numeric(rownames(btw))) -> btw
+         articleID = as.numeric(rownames(btw)),
+         site = ifelse(site=="bild.de","Bild.de",site),
+         site = ifelse(site=="focus.de","FOCUS ONLINE",site),
+         site = ifelse(site=="spiegel.de","SPIEGEL ONLINE",site),
+         site = ifelse(site=="zeit.de","ZEIT ONLINE",site),
+         site = ifelse(site=="welt.de","DIE WELT",site)) -> btw
 ```

### 2017-12-08 paper/R/03_stm.Rmd
new

@@
 
-```{r Setup}
+```{r}
 suppressPackageStartupMessages({
@@
 # Functions
-source("func/02-topic-modelling-functions.R")
+source("func/topic-modelling-functions.R")
 ```
@@
 load("../output/btw_combined.Rda")
-
-#load("../output/models/STM 50 .Rda")
-knitr::opts_chunk$set(eval = TRUE, warning = FALSE, message = FALSE)
+#load("../output/models/STM 25 .Rda")
 ```
 
-## Explore Dataset
-```{r}
-library(RColorBrewer) 
-col <- brewer.pal(7,"Dark2")
-```
+### Tokenizing
+```{r Tokenize}
+btw %>% 
+  unnest_tokens(word, text_cleaned, token = "words") %>%
+  filter(str_length(word) >= 3) ->
+  posts_tokenized.dt
 
-```{r message=FALSE, warning=FALSE}
-btw %>%
-  group_by(date, site) %>%
-  summarise(obs = n()) %>%
-  ggplot(aes(date, obs, color = site)) +
-  geom_line() +
-  scale_color_manual(values = col) +
-  theme(legend.position="none") +
-  labs(x="", y="Count",color="") +
-  scale_x_date(breaks = date_breaks("2 weeks"), labels=date_format("%d.%m", tz="CET"))
-
-# ggsave("../figs/timeline.png", plot = last_plot(), device = "png", 
-#        dpi = 600)
-```
-
-```{r message=FALSE, warning=FALSE}
-btw %>%
-  ggplot(aes(site)) +
-  geom_bar(fill=col, alpha= .8) +
-  labs(x="", y="Count")
-
-# ggsave("../figs/bar.png", plot = last_plot(), device = "png", 
-#        dpi = 600)
-```
-
-```{r message=FALSE, warning=FALSE}
-btw %>%
-  ggplot(aes(date, site, size=text_length, color = site)) +
-  geom_point(show.legend = FALSE, alpha = .8) +
-  scale_color_manual(values = col) +
-  labs(x="", y="")
-
-# ggsave("../figs/fb_shares.png", plot = last_plot(), device = "png", 
-#        dpi = 600)
-```
-
-```{r message=FALSE, warning=FALSE}
-btw %>%
-  ggplot(aes(site, text_length)) +
-  stat_summary(fun.y="median", geom="bar", fill = col, alpha = .8) +
-  labs(x="", y="")
-
-#ggsave("../figs/fb_shares_mean.png", plot = last_plot(), 
-#       dpi = 600)
+# Summarise
+posts_tokenized.dt %>% 
+  group_by(articleID, word) %>%
+  dplyr::summarise(term_frequency = n()) %>%
+  ungroup() ->
+  posts_tokenized.dt
 ```
@@
 # Structural Topic Model
-## Build Corpus
+
+## Preparation
+### Build Corpus
 ```{r eval=FALSE, include=FALSE}
@@
 ```{r}
-K<-c(30,40,50,60,80)
+K<-c(30,40,50,60)
 
 t1 <- Sys.time()
-kresult <- searchK(out$documents, out$vocab, K, prevalence=~site + s(btw_dummy), data = out$meta, init.type = "Spectral")
+kresult <- searchK(out$documents, 
+                   out$vocab, 
+                   K, 
+                   prevalence=~site + s(month), 
+                   data = out$meta,
+                   max.em.its = 75,
+                   seed =8458159,
+                   init.type = "Spectral")
 t2 <- Sys.time()
@@
 save(btw, out, kresult, file="../output/models/kresult.Rda")
-#load(file="../output/models/kresult.Rda")
+load(file="../output/models/kresult.Rda")
 ```
@@
 
-We then train the Structural Topic Model on the full dataset, with $k = 50$.
+## Run the Model
+We then train the Structural Topic Model on the full dataset, with $k = 28$.
 
 ```{r}
-k = 40 # Topics
+k = 28 # Topics
 
@@
 save(stmOut, btw, out, file=paste("../output/models/STM",k,".Rda"))
-
 #load(file=paste("../output/models/STM",k,".Rda"))
@@
 
-### Using build-in functions
-#### Topic Summary
-```{r}
-plot(stmOut, type = "summary", xlim = c(0,.14), n = 5, #labeltype = "frex",
-         main = "Online News Topics", text.cex = 0.8)
-```
-
-The most frequent words in the model such as for topics #3, #7, and #20
-```{r}
-plot(stmOut, type="labels", topics=c(37,8))
-```
-
-A comparison of two topics 
-```{r}
-plot(stmOut, type="perspectives", topics=c(37,8))
-```
-
-The estimateEffect() function explores how prevalence of topics varies across documents according to document covariates (metadata).
-First, users must specify the variable that they wish to use for calculating an effect.
-If there are multiple variables specified in estimateEffect(), then all other variables are held at their sample median.
-These parameters include the expected proportion of a document that belongs to a topic as a function of a covariate, or a first difference type estimate, where topic prevalence for a particular topic is contrasted for two groups
-```{r}
-out$meta$site <- as.factor(out$meta$site)
-prep <- estimateEffect(1:50 ~ site+s(month), stmOut, meta=out$meta, uncertainty = "Global")
-```
-
-To see how prevalence of topics differs across values of a continuous covariate:
-```{r}
-plot(prep, "month", method="continuous", topics = c(46,42),
-     xlab="Month (2017)")
-monthseq <- seq(from=as.Date("2017-06-01"), to=as.Date("2017-11-01"), by="month")
-monthnames <- month(monthseq)
-axis(1, at=as.numeric(monthseq), labels = monthnames)
-```
-
-#### Topic Labeling
-```{r Tokenize}
-btw %>% 
-  # Tokenize by word
-  unnest_tokens(word, text_cleaned, token = "words") %>%
-  # Remove short words
-  filter(str_length(word) >= 3) ->
-  # Assign to variable
-  posts_tokenized.dt
-
-# Summarise
-posts_tokenized.dt %>% 
-  group_by(articleID, word) %>%
-  dplyr::summarise(term_frequency = n()) %>%
-  ungroup() ->
-  posts_tokenized.dt
-```
-
+#### Extract posterior distributions
 ```{r Extract wtp and dtp}
@@
 
-To get an idea of the topics, we take a look at the words that are associated with topics and label them accordingly.
-We then inspect the documents that are estimated to be highly associated with each topic.
-Figure --- shows a random sample of 7 posts from the 300 highest probability fits per topic.
-
+#### Compute different word-relevance measures
 ```{r Compute relevance}
@@
   word_relevance.dt
-
 ```
 
+#### Topic Labeling
 ```{r Label Topics}
@@
 
-topicLabel <- as.data.frame(label$prob)
-topicLabel <- topicLabel %>%
+prob <- as.data.frame(label$prob, stringsAsFactors = F)
+frex <- as.data.frame(label$frex, stringsAsFactors = F)
+lift <- as.data.frame(label$lift, stringsAsFactors = F)
+score <- as.data.frame(label$score, stringsAsFactors = F)
+
+topicLabel <- prob %>% 
   transmute(topic = rownames(.),
-    topic_name = paste(V1,V2,V3,V4, sep = ", "))
+            topic_name = paste(prob$V1,prob$V2,prob$V3,score$V1,score$V2,score$V3, sep=","),
+            prob = paste(prob$V1,prob$V2,prob$V3, sep=","),
+            frex = paste(frex$V1,frex$V2,frex$V3, sep=","),
+            lift = paste(lift$V1,lift$V2,lift$V3, sep=","),
+            score = paste(score$V1,score$V2,score$V3, sep=","))
 
-frex <- as.data.frame(label$frex)
-topicLabel <- topicLabel %>%
-  left_join(., 
-            frex %>%
-              transmute(topic = rownames(.),
-                frex = paste(V1,V2,V3,V4, sep=", ")),
-            by = "topic")
-
-lift <- as.data.frame(label$lift)
-topicLabel <- topicLabel %>%
-  left_join(., 
-            lift %>%
-              transmute(topic = rownames(.),
-                lift = paste(V1,V2,V3,V4, sep=", ")),
-            by = "topic")
-
-score <- as.data.frame(label$score)
-topicLabel <- topicLabel %>%
-  left_join(., 
-            score %>%
-              transmute(topic = rownames(.),
-                score = paste(V1,V2,V3,V4, sep=", ")),
-            by = "topic")
-
-rm(frex, lift, score)
+topicLabel$topic_name <- vapply(lapply(strsplit(topicLabel$topic_name, ","), unique), paste, character(1L), collapse = " ")
+rm(prob, frex, lift, score)
 ```
@@
 theta <- as.data.frame(stmOut$theta)
+names(theta) <- as.character(1:25)
 theta$topic <- colnames(theta)[apply(theta,1,which.max)]
@@
   transmute(articleID = as.numeric(rownames(.)),
-    topic = as.numeric(gsub("V","",topic)))
+    topic = topic)
 
@@
 btw %>%
-  inner_join(.,doctopics.df, by="articleID") %>%
+  inner_join(.,doctopics.df %>%
+               mutate(topic=as.numeric(topic)), by="articleID") %>%
   ## Combine with Topic label
   left_join(., topicLabel %>%
+              mutate(topic = as.numeric(topic)) %>%
               select(topic_name, topic) %>%
@@
 ### Sample articles
-
-To test, wheather the topic classification make sense, we pull out sample articles classified by the model to see if they match the assigned topic.
 
@@
   top_n(300, gamma) %>%
-  sample_n(7) %>% 
+  sample_n(10) %>% 
   mutate(row = row_number()) %>% 
@@
     posts_classification.sdt %>% 
-      ggplot(aes(x = 0, y = row, color = factor(topic, levels = 1:40))) +
+      ggplot(aes(x = 0, y = row, color = factor(topic, levels = 1:25))) +
       facet_wrap(~topic_title, ncol = 5) +
@@
       scale_color_manual(
-        values = rainbow(50) %>% 
+        values = rainbow(25) %>% 
           adjustcolor(red.f = 0.6, green.f = 0.6, blue.f = 0.6)
@@
 
-![Facebook news samples](../figs/02-topic-classification-sample.png)
 ### News landscape
@@
             aes(label = term, 
-                color = factor(topic, levels = 1:40), 
+                color = factor(topic, levels = 1:25), 
                 size = phi_kw * p_w), 
@@
             aes(label = str_wrap(topic_name, 15),
-                color = factor(topic, levels = 1:40)),
+                color = factor(topic, levels = 1:25)),
             size = 2.25, lineheight = 0.7,
@@
           scale_color_manual(
-            values = rainbow(39) %>% 
+            values = rainbow(25) %>% 
               adjustcolor(red.f = 0.6, green.f = 0.6, blue.f = 0.6)
@@
 
-```
-
-![Facebook News Map](../figs/news-landscape-map.png)
-
-```{r}
-btw %>%
-  #filter(topic==4) %>%
-  filter(startsWith(title,"News")) %>%
-  select(url,title, text)
 ```
@@
 
-## Regression
-
-### Facebook Shares
-```{r Facebook Shares}
-btw2 %>%
-  ggplot(aes(as.factor(topic), fb_shares)) +
-  stat_summary(fun.y="sum", geom="bar", fill = "blue", alpha=.7) +
-  labs(x="", y="Sum") +
-  scale_x_discrete(breaks=c(1:50), labels = topicLabel$topic_name) +
-  theme(axis.text.x = element_text(size=7, angle=90),
-        axis.text.y = element_text(size=7))
-
-ggsave("../figs/fb_shares_topics.png", device = "png", 
-       dpi = 600)
-```
-
-### Prepare Data
-```{r}
-top_topics <-
-  posts.dtp %>% 
-  group_by(document) %>%
-  mutate(therank = rank(-gamma, ties.method = "random")) %>%
-  filter(therank %in% 1) %>%
-  select(- therank)
-```
-
-```{r}
-# filter documents with low posterior
-btw.reg <- 
-  btw %>%
-  mutate(document = as.numeric(articleID)) %>%
-  left_join(., top_topics, by="document") %>%
-  #filter(gamma > 0.6) %>%
-  filter(fb_shares > 0)
-
-# generate factor variables
-btw.reg %>%
-  mutate(topic.f = factor(topic),
-         site.f = factor(site)) -> btw.reg
-```
-
-```{r}
-btw.reg %>%
-  filter(fb_shares < 500) %>%
-  ggplot(aes(fb_shares, fill = site)) +
-  geom_histogram(binwidth = 10)
-```
-
-```{r}
-linreg <- lm(fb_shares ~ topic.f*site, data=btw.reg)
-
-summary(linreg)
-```
-
 ## Animated Figures
@@
         data_id = data_id), 
-    color = "gray"
+    color = "grey51"
   ) +
@@
     ggobj = .,
-    hover_css = "stroke: red; stroke-width: 3px;",
+    hover_css = "stroke: hotpink; stroke-width: 3px;",
     width = 1,
@@
   inner_join(
-    btw2 %>% 
-      mutate(document = as.numeric(articleID)) %>%
+    btw %>% 
+      mutate(document = as.numeric(articleID),
+             date = as.POSIXct(date) ) %>%
       select(
@@
   inner_join(
-    btw2 %>% 
+    btw %>% 
       mutate(document = as.numeric(articleID)) %>%
@@
   labs(
-    caption = "
-DATA SOURCE: Webhose.io, Eventbride.com
-CHART NOTE: Topics were derived through Latent Dirichlet Allocation (LDA) with 40 topics for online news articles in 2017 containing the term 'Bundestagswahl'
-    "
+    caption = ""
   ) ->
@@
 
-![Articles to Reactions](../figs/09-reactions-vs-articles.gif)
+#![Articles to Reactions](../figs/09-reactions-vs-articles.gif)
 
@@
   inner_join(
-    btw2 %>% mutate(document = as.numeric(articleID)) %>%
+    btw %>% mutate(document = as.numeric(articleID)) %>%
       select(document, news_page = site, title),

### 2017-12-08 paper/R/04_regression.Rmd
new

--- 2017-11-09 paper/R/04_regression.Rmd
@@
 
-```{r Setup, include=FALSE}
+```{r}
 suppressPackageStartupMessages({
@@
   library(boot)
+  library(stm)
+  library(readxl)
 
   library(ggplot2)     # Static data visualization
+  library(ggpmisc)
+  library(RColorBrewer) 
+  library(ggrepel)
+  library(plotly)
   library(scales)      # Scales
@@
 theme_set(
-  theme_bw(base_family = "Roboto", base_size = 14) +
+  theme_bw(base_family = "Roboto", base_size = 8) +
     theme(
@@
 
-rm(list=ls())
+#rm(list=ls())
+col <- brewer.pal(7,"Dark2")
 ```
 
-## Load Data
+# Load Data
 ```{r caching, echo = FALSE}
-load("../output/btw_combined.Rda")
-btw2 <- btw
-
-load("../output/models/STM 40 .Rda")
 #load("../output/btw_combined.Rda")
-knitr::opts_chunk$set(eval = TRUE, warning = FALSE, message = FALSE)
-
-# Set color
-library(RColorBrewer) 
-col <- brewer.pal(6,"Dark2")
+load("../output/models/STM 28 .Rda")
 ```
 
-## Prepare Data
+load data "Unique User"
+```{r}
+## Daily (06-2017 - 12-2017)
+unique_user1 <- read_excel("../data/uniqueUser_1.xls")
+unique_user2 <- read_excel("../data/uniqueUser_2.xls")
+
+uu_df <- rbind(unique_user1,unique_user2) %>%
+  rename(uniqueUser = `Unique User Tag Mio.`,
+         site = Dachmarke,
+         date = Tag) %>%
+  select(date, site, uniqueUser)
+
+rm(unique_user1, unique_user2)
+```
+
+# Description of Data
+
+### Unique User 
+```{r}
+p <- uu_df %>%
+  filter(date > as.Date("2017-05-31")) %>%
+  ggplot(aes(date, uniqueUser, color=site)) +
+  geom_line() +
+  geom_vline(aes(xintercept=as.POSIXct("2017-09-24")),
+             linetype = 2, color="grey50") +
+  scale_color_manual(values = col[c(1,2,3,4,6,7)]) +
+  theme(
+      #legend.position   = "none",
+      legend.text       =  element_text(size=6),
+      plot.background   = element_rect("#fafafa", "#fafafa"),
+      panel.background  = element_rect("#fafafa"),
+      axis.title.x      = element_blank(),
+      axis.text.y       = element_text(size = 8)
+    ) +
+  labs(x="", y="", color="", title = "", 
+      caption = "
+  Source: AGOF (www.agof.de)
+      " )
+
+#ggplotly(p)
+ggsave(plot= p,
+filename = "../figs/uniqueUser.png", device = "png",
+width = 6, height = 4,
+        dpi = 600
+)
+```
+
+### Distribution of articles
+```{r message=FALSE, warning=FALSE}
+ggsave({
+  btw %>%
+  ggplot(aes(site)) +
+  geom_bar(fill=col, alpha= .8) +
+  labs(x="", y="Count") +
+  theme(
+      legend.position   = "none",
+      plot.background   = element_rect("#fafafa", "#fafafa"),
+      plot.title        = element_text(size = 18),
+      plot.subtitle     = element_text(size = 8),
+      plot.caption      = element_text(size = 7),
+      panel.background  = element_rect("#fafafa"),
+      axis.title.x      = element_blank(),
+      axis.text.y       = element_text(size = 8)
+    )
+
+},
+filename = "../figs/bar.png", device = "png", 
+width = 6, height = 4,
+        dpi = 600)
+```
+
+```{r message=FALSE, warning=FALSE}
+ggsave({
+  btw %>%
+  group_by(date, site) %>%
+  summarise(obs = n()) %>%
+  ggplot(aes(date, obs, color = site)) +
+  geom_line() +
+  #geom_vline(aes(xintercept=as.Date("2017-09-24")),
+  #           linetype = 2, color="grey40") +
+  #geom_vline(aes(xintercept=as.Date("2017-11-20")),
+  #               linetype = 2, color="grey40") +
+  scale_color_manual(values = col) +
+  labs(x="", y="Count",color="") +
+  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
+  theme(
+      #legend.position   = "none",
+      plot.background   = element_rect("#fafafa", "#fafafa"),
+      plot.title        = element_text(size = 18),
+      plot.subtitle     = element_text(size = 8),
+      plot.caption      = element_text(size = 7),
+      #panel.grid        = element_blank(),
+      panel.background  = element_rect("#fafafa"),
+      axis.title.x      = element_blank(),
+      axis.text.y       = element_text(size = 8)
+    )
+},
+filename = "../figs/timeline.png", device = "png",width = 7, height = 4,
+dpi = 600
+)
+
+```
+
+# Model Results
 ```{r Extract wtp and dtp}
@@
 stmOut %>% tidy("gamma") -> posts.dtp
+```
+
+## Topic Labeling
+```{r Label Topics}
+label <- labelTopics(stmOut, n=3)
+
+prob <- as.data.frame(label$prob, stringsAsFactors = F)
+frex <- as.data.frame(label$frex, stringsAsFactors = F)
+lift <- as.data.frame(label$lift, stringsAsFactors = F)
+score <- as.data.frame(label$score, stringsAsFactors = F)
+
+topicLabel <- prob %>% 
+  transmute(topic = rownames(.),
+            topic_name = paste(prob$V1,prob$V2,prob$V3,score$V1,score$V2,score$V3, sep=","),
+            prob = paste(prob$V1,prob$V2,prob$V3, sep=","),
+            frex = paste(frex$V1,frex$V2,frex$V3, sep=","),
+            lift = paste(lift$V1,lift$V2,lift$V3, sep=","),
+            score = paste(score$V1,score$V2,score$V3, sep=","))
+
+topicLabel$topic_name <- vapply(lapply(strsplit(topicLabel$topic_name, ","), unique), paste, character(1L), collapse = " ")
+rm(prob, frex, lift, score)
 ```
@@
   select(- therank)
+
+# Add Topic to origian DF
+btw %>%
+  mutate(document = articleID) %>%
+  inner_join(.,top_topics, by="document") %>%
+  ## Combine with Topic label
+  left_join(., topicLabel %>%
+              select(topic_name, topic) %>%
+              mutate(topic = as.numeric(topic)), by="topic") -> btw
 ```
 
+## Topic Proportion
+```{r}
+png("../figs/topic_proportion.png")
+plot(stmOut, type = "summary", xlim = c(0,.16), n = 5, 
+     custom.labels = topicLabel$topic_name, 
+     family = "Roboto", main = "", text.cex = 0.7)
+dev.off()
+```
+
+## Topic Correlation
+We can correlate the topic by the metadata available. The column means of theta, grouped by category is calculated.
+```{r}
+theta <- as.data.frame(stmOut$theta)
+names(theta) <- as.character(1:28)
+
+theta2 <- theta %>% mutate(document = as.numeric(rownames(theta))) %>%
+  left_join(., btw %>% select(site, document),
+            by="document")
+
+theta.mean.by <- by(theta2[,1:28], theta2$site, colMeans)
+theta.mean <- do.call("rbind", theta.mean.by)
+
+library(corrplot)
+c <- cor(theta.mean)
+corrplot(c, method = "circle")
+```
+
+## Sample Articles
 We classify each document based on which topic has the highest probability.
-To estimate the true effect of a topic, we delete documents where the highest topic probability is smaller than 0.5, as topic assignment is not ambiguous.
-This left us with 7740 documents.
 
-```{r}
-btw.reg <- 
+```{r Document classification}
+set.seed(9272)
+posts_classification.sdt <-
+  posts.dtp %>% 
+  group_by(articleID = document) %>% 
+  summarise(topic = min(topic[gamma == max(gamma)]), gamma = max(gamma)) %>% 
+  ungroup() %>%
+  inner_join(btw %>% select(title, title_text, articleID, topic_name),
+              by = "articleID") %>%
+  #inner_join(topics_mapping.dt, by = "topic") %>%
+  mutate(topic_title = 
+           paste0("Topic ", formatC(topic, flag = "0", width = 2), 
+                  " - ", topic_name)) %>%
+  group_by(topic_name) %>% 
+  top_n(300, gamma) %>%
+  sample_n(7) %>% 
+  mutate(row = row_number()) %>% 
+  ungroup()
+
+```
+
+```{r Document classification chart, echo=TRUE}
+
+ggsave(
+  plot = {
+    posts_classification.sdt %>% 
+      ggplot(aes(x = 0, y = row, color = factor(topic, levels = 1:28))) +
+      facet_wrap(~topic_title, ncol = 4) +
+      geom_text(
+        aes(label = title),
+        size = 3, hjust = 0, family = "Roboto"
+      ) +
+      geom_point(aes(x = -0.025), size = 0.5) +
+      scale_x_continuous(limits = c(-0.05, 1), expand = c(0, 0)) +
+      scale_color_manual(
+        values = rainbow(28) %>% 
+          adjustcolor(red.f = 0.6, green.f = 0.6, blue.f = 0.6)
+      ) +
+      theme(
+        axis.title       = element_blank(),
+        axis.text        = element_blank(),
+        axis.ticks       = element_blank(),
+        panel.grid       = element_blank(),
+        strip.background = element_blank(),
+        panel.border     = element_blank(),
+        strip.text       = element_text(face = "bold", hjust = 0, size = 7),
+        plot.background  = element_rect(fill = "#FAFAFA"),
+        legend.position  = "none"
+      ) 
+  },
+  device = "png",
+  filename = "../figs/topic-classification-sample.png",
+  dpi = 600, height = 10, width = 16
+)
+```
+
+## Estimating the Effect of Covariates
+
+### Differences in Word-Topic Distribution
+How do different news sources describe the same topic with different vocabulary
+
+```{r Top Words by topic and news source}
 btw %>% 
-  left_join(., btw2 %>%
-              select(title.text, shares, url),
-            by = "title.text")
+  unnest_tokens(word, text_cleaned, token = "words") %>%
+  filter(str_length(word) >= 3) %>%
+  count(site, topic, word) %>%
+  ungroup() ->
+  posts_tokenized.dt
+
+posts_tokenized.dt %>%
+  group_by(site, topic) %>%
+  dplyr::arrange(desc(n)) %>%
+  top_n(18) %>%
+  # concatenate words
+  group_by(site, topic) %>%
+  summarise(top_words = paste(word, collapse=", ")) %>%
+  mutate(top_words = gsub("([^,]+,[^,]+,[^,]+),","\\1\n", top_words)) %>%
+  left_join(.,topicLabel %>%
+              mutate(topic=as.numeric(topic),
+                     topic_name = gsub("([^\\s]+,[^\\s]+),","\\1\n", topic_name)) %>%
+              select(topic, topic_name),
+            by="topic") ->
+  top_words.dtf
 ```
@@
 ```{r}
-# filter documents with low posterior
-btw.reg <- 
-  btw.reg %>%
-  mutate(document = as.numeric(articleID)) %>%
-  left_join(., top_topics, by="document") %>%
-  filter(gamma > 0.5)
+ggsave(
+  plot = {
+    top_words.dtf %>% 
+  filter(topic %in% c(5,6,7,12,15,16)) %>%
+  mutate(row=row_number()) %>%
+      ggplot(aes(x = topic_name, y=site, color=site)) +
+      facet_wrap(~topic_name, ncol=6) +
+      geom_text(aes(x =topic_name, y=site, label=top_words),
+                hjust="inward",
+                size = 2, family = "Roboto"
+      ) +
+      theme(
+        axis.title       = element_blank(),
+        axis.text        = element_blank(),
+        axis.ticks       = element_blank(),
+        panel.grid       = element_blank(),
+        strip.background = element_blank(),
+        panel.border     = element_blank(),
+        strip.text       = element_text(hjust = 0.5, size = 6),
+        plot.background  = element_rect(fill = "#FAFAFA"),
+        legend.title     = element_text(size=7),
+        legend.text      = element_text(size=7)
+      ) 
+      #guides(colour = guide_legend(override.aes = list(size=1)))
+  },
+  device = "png",
+  filename = "../figs/top_words_news.png",
+  dpi = 600, height = 6, width = 12
+)
+```
 
-# generate new variables and reduce df
-btw.reg %>%
+### Difference in topic prevalence
+The estimateEffect() function explores how prevalence of topics varies across documents according to document covariates (metadata).
+First, users must specify the variable that they wish to use for calculating an effect.
+If there are multiple variables specified in estimateEffect(), then all other variables are held at their sample median.
+These parameters include the expected proportion of a document that belongs to a topic as a function of a covariate, or a first difference type estimate, where topic prevalence for a particular topic is contrasted for two groups.
+
+```{r}
+prep <- estimateEffect(1:28 ~site + s(month),
+                       stmOut, meta=out$meta, uncertainty = "Global")
+```
+
+```{r}
+summary(prep)
+```
+
+Expected difference in topic probability by news source (with 95% Confidence Intervals). 
+parameter "covariate": String of the name of the main covariate of interest.
+Must be enclosed in quotes.
+All other covariates within the formula specified in estimateEffect will be kept at their median.
+```{r}
+for (i in 1:28){
+  png(paste0("../figs/estimate_effect",i,".png"))
+  plot(prep, "site", method = "pointestimate", topics = i,
+       labeltype = "custom", custom.labels = unique(prep$data$site),
+       ylab = "", xlab = "Mean topic proportion in corpus",
+       main = paste0("Topic ",i,": ",topicLabel$topic_name[i]),
+       xlim = c(-.05,0.15))
+  dev.off()
+}
+```
+
+```{r}
+for (i in 1:25){
+  plot(prep, "month", method = "continuous", topics = i,
+       printlegend = F,
+       ylab = "", xlab = "Mean topic proportion in corpus",
+       main = paste0("Topic ",i,": ",topicLabel$topic_name[i]))
+}
+
+```
+
+```{r}
+p<- posts.dtp %>%
+  left_join(., btw %>% select(document, topic_name,
+                              site, month),
+            by="document")  %>%
+  mutate(site = factor(site),
+         topic = factor(topic)) %>%
+  filter(month!=5) %>%
+  ggplot(aes(weight=gamma, x=topic, fill=topic, text=topic_name)) +
+  geom_bar() +
+  coord_flip() +
+  facet_grid(site~month) +
+  guides(fill=FALSE) +
+  xlab("Proportion")
+
+ggplotly(p)
+```
+
+# Regression
+
+What is the distribution of the gamma value?
+```{r}
+ggsave(plot={
+  btw %>%
+  ggplot(aes(gamma)) +
+  geom_density(fill="blue",alpha=.5,color="blue") 
+},
+filename = "../figs/gamma_dist.png",
+       width = 8, height = 6, device = "png", dpi=600)
+```
+
+filter documents with low posterior
+```{r}
+btw.reg <- btw %>%
+  filter(gamma >= 0.5) %>%
+  #filter(!site=="stern.de") %>%
   mutate(topic = factor(topic),
          site = factor(site),
-         shares.dummy = factor(ifelse(shares==0,0,1))) %>%
-  select(site, shares, shares.dummy, date, text_length, month, 
-         document, topic, gamma) -> btw.reg
+         month = factor(month),
+         fb_shares_log = log1p(fb_shares)) -> btw.reg
 ```
 
-## Description of Data
+Proportion of zeros
 ```{r}
-summary(btw.reg)
+nrow(btw.reg[which(btw.reg$fb_shares==0),])/nrow(btw.reg)
 ```
 
-The proportion of zeros in the independent variable (number of Facebook shares) is about 65.6\%.
-One way to model this type of situation is to assume that the data come from a mixture of two populations, one where the counts is always zero, and another where the count has a Poisson distribution with mean $\mu$.
-In this model zero counts can come from either population, while positive counts come only from the second one.
+Distribution of Facebook shares
+```{r}
+btw.reg$share.cut <- cut(btw.reg$fb_shares, 
+                         breaks = c(0,1,100,500,1000,5000,max(btw.reg$fb_shares)),
+                         right = T, include.lowest = TRUE)
 
+ggsave(plot={
+  ggplot(btw.reg, aes(x=share.cut)) + 
+  geom_bar(aes(fill=site), alpha=.7) + 
+  labs(title = "") +
+  labs(x="Facebook Shares", y="Count", fill="") +
+  scale_fill_manual(values = col) +
+  scale_x_discrete(labels = c("0","1-100","101-500","501-1000","1001-5000",">5000"))
+},
+filename = "../figs/facebook_shares.png", width = 8, height = 6, 
+       device = "png", dpi = 600
+)
+```
+
+## Topic Timeline
+```{r Data for topic trends chart, message=FALSE, warning=FALSE}
+set.seed(7292)
+btw.reg %>% 
+  mutate(date = as.POSIXct(date),
+         allocation = 1) %>%
+  mutate(post_period = 
+           date %>% with_tz("Europe/Paris") %>% 
+           floor_date("week")) %>%
+  # Summarise into tidy dataframe
+  group_by(post_period, topic, topic_name) %>% dplyr::summarise(articles = sum(allocation)) %>%
+  # Mark peaks 
+  group_by(topic_name) %>% dplyr::mutate(peak = ifelse(articles==max(articles),1,0)) -> chart_topic_trends.dt
+```
+
+```{r message=FALSE, warning=FALSE}
+ggsave(
+  plot = {
+    ggplot(chart_topic_trends.dt, 
+       aes(post_period, articles, color=topic_name)) +
+  geom_line() +
+  scale_color_manual(
+            values = rainbow(28) %>% 
+              adjustcolor(red.f = 0.6, green.f = 0.6, blue.f = 0.6)
+          ) +
+  geom_text_repel(data=subset(chart_topic_trends.dt,peak==1),
+            aes(post_period,articles,label=paste(topic,topic_name,sep=":")),
+            size=2.8) +
+      geom_vline(aes(xintercept=as.POSIXct("2017-09-23")),
+                 linetype = 2, color="grey20") +
+      geom_vline(aes(xintercept=as.POSIXct("2017-11-19")),
+                 linetype = 2, color="grey20") +
+  ylim(c(0,200)) +
+    theme(
+      legend.position   = "none",
+      #plot.background   = element_rect("#fafafa", "#fafafa"),
+      plot.title        = element_text(size = 18),
+      plot.subtitle     = element_text(size = 8),
+      plot.caption      = element_text(size = 7),
+      panel.grid        = element_blank(),
+      #panel.background  = element_rect("#fafafa"),
+      axis.title.x      = element_blank(),
+      axis.text.y       = element_text(size = 8)
+    )
+  },
+  device = "png",
+  filename = "../figs/topic-timeline.png",
+  dpi = 600, height = 5, width = 8
+)
+```
+
+## Analysis
+```{r}
+summary(btw.reg[,c("site","text_length","fb_shares","gamma")])
+```
+
+### Simple linear regression
+```{r}
+source("func/functions.R")
+
+library(stargazer)
+lm <- lm(fb_shares_log ~ topic + site + text_length, data=btw.reg)
+
+lm.t <- stargazer(lm)
+
+lm.t <- AddResizeBox(lm.t)
+
+writeLines(lm.t, con = "../doc/lm1.tex")
+```
+
+### Zero-inflated Poisson regression
 The distribution of the outcome can then be modeled in terms of two parameters, $\pi$ the probability of 'always zero', and $\mu$, the mean number of publications for those not in the 'always zero' group.
@@
 
-## Analysis
-### Zero-inflated Poisson regression
-```{r}
-# filter NAs
-btw.reg %>%
-  filter(!is.na(shares)) -> btw.reg
-```
-
 ```{r Zero-inflated Poisson}
 library(pscl)
-m1 <- zeroinfl(shares ~ topic + site | topic + site + text_length, data = btw.reg)
+m1 <- zeroinfl(fb_shares ~ topic + site | topic + site + text_length, data = btw.reg)
 summary(m1)
@@
 ```{r}
-p1 <- glm(shares ~ topic, family = poisson, data = btw.reg)
+p1 <- glm(fb_shares ~ topic, family = poisson, data = btw.reg)
 summary(p1)
@@
 btw.reg %>%
-  select(site, shares, topic, residuals, predicted) %>%
-  gather(key="iv", value="x", -shares, -predicted, -residuals) %>%
-  ggplot(aes(x=x, y=shares)) +
+  select(site, fb_shares, topic, residuals, predicted) %>%
+  gather(key="iv", value="x", -fb_shares, -predicted, -residuals) %>%
+  ggplot(aes(x=x, y=fb_shares)) +
   geom_segment(aes(xend=x, yend=predicted), alpha=.2) +

### 2017-12-08 paper/R/pageImpr.Rmd
new

---
title: "R Notebook"
output: 
---

```{r}
library(readxl)
library(tidyverse)
```

```{r}
unique_user1 <- read_excel("../data/unique_user1.xls")
unique_user2 <- read_excel("../data/unique_user2.xls")

uu_df <- rbind(unique_user1,unique_user2) %>%
  rename(uniqueUser = `Unique User Tag Mio.`,
         site = Dachmarke,
         date = Tag) %>%
  select(date, site, uniqueUser)
```

```{r}
## Monthly (2003-2017)
unique_user1 <- read_excel("../data/unique_user_2003_2017.xls")
unique_user2 <- read_excel("../data/unique_user_2003_2017_2.xls")

uu_df_full <- rbind(unique_user1,unique_user2) %>%
  mutate(date = as.POSIXct(paste(Jahr,month,"1",sep="-"))) %>%
  rename(uniqueUser = `Unique User Monat Mio.`,
         site = Dachmarke) %>%
  select(date, site, uniqueUser)
```

### 2017-12-08 paper/R/webhose.Rmd
new

---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
```

```{r}
webhose_nov_30 <- read.csv(".../data/eventbride/webhose_nov_30.csv")
```

Test string patterns
```{r}
pattern <- "(?<=main_image': ')[^']*"
str_extract(webhose_nov_30$posts[2],pattern)
```

```{r}
webhose_nov_30$posts[80]
```

```{r}
webhose_nov_30 %>%
  transmute(url = str_extract(posts,"(?<=main_image': ')[^']*"),
         section = str_extract(posts, "(?<=section_title': ')[^']*"),
         site = str_extract(posts,"(?<=site': ')[^']*"),
         title = str_extract(posts, "(?<=title_full': ')[^']*"),
         text = str_extract(posts, "(?<=text': ')[^']*"),
         date = as.POSIXct(str_extract(posts, "(?<=published': ')[^']*"))) %>%
  distinct(title,site, .keep_all = TRUE) %>%
  filter(!is.na(text)) -> df
```

## select politic section
```{r}
pat1 <- "\\w\\.de/politik/deutschland"
pat2 <- "\\w\\.de/politik/inland"
pat3 <- "\\w\\.de/politik/wahl"
pat4 <- "\\w\\.de/politik/bundestagswahl"
pat5 <- "tagesschau\\.de/inland"

df %>%
  filter(grepl(paste(pat1,pat2,pat3,pat4,pat5,
                     sep="|"), url, perl = TRUE)) -> btw
```

```{r}
df %>%
  filter(site == "focus.de") %>%
  select(url) 
```

### 2017-12-08 paper/doc/doc2.tex
new

@@
 \usepackage{eurosym}
+\usepackage{pdflscape}
 
@@
 We then estimate the effect of topic prevalence on the number of Facebook shares.
+We use a data set of online news articles about domestic politics dated from 01.06.2017 to 22.11.2017\footnote{German federal elections took place on 24th of September 2017.} from seven German content providers: Bild.de, Die Welt, Focus Online, Spiegel Online, Stern.de, Zeit Online and Tagesschau.de.
+They are all providers of online news, whereby Tagesschau.de is the only publicly funded service.
+The latter was also included in the study to verify whether the topics differ when the content is created on the basis of a different business model.
 
@@
 Media outlets naturally appear as two-sided platforms, that allow interaction between two categories of consumers: audiences and advertisers.
-The demand on both consumer-sides are often linked via indirect network externalities.
-The market in which media outlets operate are accordingly referred to as two-sided or multi-sided markets.
+As the demand on both consumer-sides are linked via indirect network externalities, the market in which media outlets operate are referred to as two-sided or multi-sided markets.
 The theoretical literature on two-sided markets originates from the analysis of credit card markets \citep{rochet_platform_2003} and was later transferred to the concept of other industries, such as dating agencies, real estate agents, and internet “business-to-business” websites \citep{caillaud_chicken_2003}.
@@
 
-Online news are typical examples of two-sided markets where the news pages can be conceived as platforms that allow interaction between audiences ("eyeballs") and advertisers.
-The size and characteristics of the audience has a positive effect on the advertisers' willingness to pay, as advertisements are typically sold based on cost per viewer, often expressed in terms of the cost of reaching a thousand viewers (CPM).
+Advertising-supported media such as online newspapers are typical examples of two-sided markets where the newspaper can be conceived as platforms that allow interaction between audiences ("eyeballs") and advertisers.
+The newspaper creates (or buys) content to attract viewers which in turn attract advertisers who pay for readers' attention.\cite{evans_industrial_2005} The size and characteristics of the audience has a positive effect on the advertisers' willingness to pay, as advertisements are typically sold based on cost per viewer, often expressed in terms of the cost of reaching a thousand viewers (CPM).
 Advertising can also have an effect on the recipients, which can be both negative and positive, depending on the quality of the advertising.
+Depending on the strength of the indirect network effects, private publisher maximize their revenue by balancing the demand from advertisers and subscribers using different business models \citep{evans_economics_2008}.\footnote{Public media such as Tagesschau.de do not depend on revenues from the advertising industry, which means that there is no two-way market structure.} Many traditional newspapers follow the subscription/advertising model, where the publisher charges both market sides: The audience pays a fee to obtain access to the content, and advertisers pay to obtain access to the viewers.
+Many online news agencies provide part of their editorial content for free and hide another, more exclusive part behind a paywall.
+However, since the Internet has considerably simplified the possibilities for obtaining information and thus reduced the marginal utility of content, such a business model can only be efficient if the content is very exclusive.
+As a result, many publishers rely on a free-media model, in which the publishers do not charge viewers for access to the media at all, in order to attract as many eyeballs as possible to their platform, and thus exploit the indirect network effects on the advertising site.
+In fact, most advertising-financed online magazines earn their gross margin from advertising.\cite{evans_industrial_2005} In order to maximize their profits, these companies have an interest in attracting as many readers as possible.
+Facebook is an important traffic supplier for news sites: Over 487.000 news articles from TOP15\footnote{Bild.de, bunte, Chip, FAZ, Focus, Handelsblatt, Heise, N-TV, Spiegel, Sport1, Stern, Süddeutsche, Tagesschau, Welt, Zeit} media were shared 123.000.000 times on Facebook (94\%), Twitter(3.5\%) and Google+(2.3\%).\cite{schiller_development_2016} In addition to the quantity of the audience, the demographic characteristics of recipients also have an influence on the willingness to pay on the advertiser site.
+Online advertising makes it possible to target ads to particular consumers in real time.
+Facebook instant articles facilitates this targeting, as they make the public users profile data available to the publisher.
+However, not all topics are equally often distributed in social media.
+\citet{schiller_development_2016} show, that social media users choose a certain site depending on the researched topic.
+FOCUS Online for example is targeted for articles from politics and business, while sports news is more likely to be shared from Bild.de.
 
-Depending on the strength of the indirect network effects, publisher maximize their revenue by balancing the demand from advertisers and subscribers using different business models \citep{evans_economics_2008}.
-Many traditional newspapers follow the subscription/advertising model, where the publisher charges both market sides: The audience pays a fee to obtain access to the content, and advertisers pay to to obtain access to the viewers.
-Many online news agencies also provide a part of their editorial content as a premium service.
-However, since the Internet has considerably simplified the possibilities for obtaining information and thus reduced the marginal utility of content, such a business model can only function if the content is very exclusive.
-As a result, many publishers rely on a free-media model, in which the publishers do not charge viewers for access to the media at all, in order to attract as many readers as possible to their platform, and thus exploit the indirect network effects on the advertising site.
+While these pre-defined resorts give an indication on the content of an article, multiple articles in the same resort probably don't cover the same topics.
+Especially if the articles originate from different news portals.
+Furthermore, articles can contain more than one topic.
+We use a structural topic model to reveal the underlying topics of a collection of articles, and how the articles exhibit them.
+We then estimate the effect of topic prevalence on the number of Facebook shares.
+We use a data set of online news articles about domestic politics dated from 01.06.2017 to 22.11.2017\footnote{German federal elections took place on 24th of September 2017.} from seven German content providers: Bild.de, Die Welt, Focus Online, Spiegel Online, Stern.de, Zeit Online and Tagesschau.de.
+They are all providers of online news, whereby Tagesschau.de is the only publicly funded service.
+The latter was also included in the study to verify whether the topics differ when the content is created on the basis of a different business model.
+
+Figure \ref{fig_uuser} shows the coverage of the six private online news provider for the period June to November 2017 in terms of unique user.\footnote{The Term unique user refers to the number of different internet users who have visited the website within a certain period of time.
+The unique user is the basis for the calculation of coverage and structures of online advertising media as well as essential factors for media planning.} It is striking that Bild.de has the greatest reach over the entire course of time, except on election day and one day after.
+Here, DIE WELT (+123\%), FOCUS ONLINE (+71\%) and SPIEGEL ONLINE (+57\%) in particular are making a big leap.
+SPIEGEL ONLINE overtakes Bild.de (+21\%) on the day after the elections (25.09.2017).
+ZEIT ONLINE and stern.de have a comparatively small coverage.
+Yet here too, there is a short-term increase in the range of coverage during the elections (+44\% for stern.de and +81\%  for ZEIT ONLINE).
+
  % What is the share of advertising revenue in total earnings of german online newspaper ?
 
-In addition to the quantity of the audience, the demographic characteristics of recipients also have an influence on the willingness to pay on the advertiser site.
-Online advertising makes it possible to target ads to particular consumers in real time.
-Facebook instant articles facilitates this targeting, as they make the public users profile data available to the publisher.
+\begin{figure}[H]
+	\caption{Unique User in Million}
+	\begin{center}
+			\includegraphics[width=.9\textwidth]{../figs/uniqueUser.png}
+			\label{fig_uuser}
+	\end{center}
+\end{figure}
 
@@
 \citet{pritchard_inference_2000} introduced the same model in genetics for factorizing gene expression as a function of latent populations.} Topic models formalize the idea that documents are formed by hidden variables (topics) that generate correlations among observed terms.
-Since its introduction into text analysis, LDA has become hugely popular and especially useful in political science.\footnote{see \citet{blei_probabilistic_2012} and \citet{grimmer_text_2013} for an overview.}
-
-The basic topic model has been extended in variety of ways.
-\citet{blei_dynamic_2006} considers documents that are indexed by publication date date and allows the topics to evolve in time.
-To relax the assumption that all texts in the modeled corpus are generated by the same underlying process, \cite{roberts_model_2016} introduces the structural topic model (STM), that provides a way to include covariates.
-Using a generalized linear model on document-level metadata allows the researcher to link topics to covariate data and to model changes in topic prevalence over time.
+Since its introduction into text analysis, LDA has become hugely popular and especially useful in political science.\footnote{see \citet{blei_probabilistic_2012}, \citet{grimmer_text_2013} and \citet{wiedmann_text_2016} for an overview in social science and \citet{gentzkow_text_2017} give an overview of text mining applications in economics.} \citet{wiedmann_text_2016} use topic model methods in on large amounts of news articles from two german newspapers published between 1959 and 2011, to reveal how democratic demarcation was performed in Germany over the past six decades.
 
@@
 
-We conduct our estimation on a sample of 10531 news articles containing the term "Bundestagswahl" (Federal Election) dated from 01.06.2017 to 28.10.2017.\footnote{German federal elections took place on 24th of September 2017.} We first extract all online articles of six mainstream german online news portals\footnote{Bild.de, Focus.de, Spiegel.de, Stern.de, Welt.de, Zeit.de} using the the Event Regestry API.\footnote{For more information see http://eventregistry.org/documentation.
-The scraping code was written in Python and can be made available on request.} We then filter those articles that contain the term "Bundestagswahl" (Federal Election) in their text body.
-We use the URL of these articles, to check how many times they where shared on Facebook using the \textit{sharedcount} API.\footnote{http://docs.sharedcount.com/} The returned share count is the sum of (1) the number of likes of this URL, (2) the number of shares of this URL (including copy-pasting a link back to Facebook), (3) the number of likes and comments on stories on Facebook about this URL and (4) the number of inbox messages containing this URL as an attachment.\footnote{See https://developers.facebook.com/docs/graph-api for more information about the Facebook Graph API.}
+We conduct our estimation on a sample of 10531 online news articles from seven news provider about domestic politics dated from 01.06.2017 to 22.11.2017.\footnote{German federal elections took place on 24th of September 2017.} We first extract all online articles of six mainstream german online news portals\footnote{Bild.de, Focus.de, Spiegel.de, Stern.de, Welt.de, Zeit.de, Tagesschau.de} using the the Event Regestry API.\footnote{For more information see http://eventregistry.org/documentation.
+The scraping code was written in Python and can be made available on request.} We then filtered all articles from the section "domestic policy" by checking the URL structure.
+We used the URL of these articles, to check how many times they where shared on Facebook using the \textit{sharedcount} API.\footnote{http://docs.sharedcount.com/} The returned share count is the sum of (1) the number of likes of this URL, (2) the number of shares of this URL (including copy-pasting a link back to Facebook), (3) the number of likes and comments on stories on Facebook about this URL and (4) the number of inbox messages containing this URL as an attachment.\footnote{See https://developers.facebook.com/docs/graph-api for more information about the Facebook Graph API.}
 
-Figure \ref{fig_distr1} shows the distribution of the number of articles from the respective news sources by date.
+Figure \ref{fig_distr1}\footnote{The first vertical line indicate the date of the federal elections (24.09.2017), and the second line indicate the date on which the "Jamaika" parties (Union, FDP, Die Grünen) announced the failure of the coalition negotiations (20.11.2017).} shows the distribution of the number of articles from the respective news sources by date.
 There is a high peak around the federal elections on September, 24th.
@@
 	\begin{center}
-		\begin{subfigure}[normla]{0.49\textwidth}
+		\begin{subfigure}[normla]{0.8\textwidth}
 			\includegraphics[width=\textwidth]{../figs/timeline.png}
@@
 		\end{subfigure}
-		\begin{subfigure}[normla]{0.49\textwidth}
+		\begin{subfigure}[normla]{0.8\textwidth}
 			\includegraphics[width=\textwidth]{../figs/bar.png}
@@
 
-\begin{figure}[H]
-	\caption{Distribution of Facebook shares...}
-	\begin{center}
-		\begin{subfigure}[normla]{0.49\textwidth}
-			\includegraphics[width=\textwidth]{../figs/fb_shares.png}
-			\caption{...by date \& news source}
-		\end{subfigure}
-		\begin{subfigure}[normla]{0.49\textwidth}
-			\includegraphics[width=\textwidth]{../figs/fb_shares_mean.png}
-			\caption{... by news source (mean)}
-		\end{subfigure}
-	\end{center}
-	\label{fig_fb_shares}
-\end{figure}
+% ------------------
+% Text Pre-Procesing
+% ------------------
 
@@
 This representation is often referred to as the bag of words model, since the order in which words are used within a document is completely disregarded.
-
-% ------------------
-% Text Pre-Procesing
-% ------------------
-\subsection{Text pre-procesing}
 
@@
 % ----------------------
-\section{Topic detection}\label{ch_model}
+\section{Topic detection using the structural topic model}\label{ch_model}
 
-The following description of the generative model of the STM is based on \citet{roberts_structural_2013} and \citept{roberts_stm:_2016}.
+The following description of the generative model of the STM is based on \citet{roberts_structural_2013} and \citet{roberts_stm:_2016}.
 The process of filling a word-position in a document begins with the generation of a document-specific topic-prevalence vector $d(\boldsymbol{\theta}_d)$ drawn from a logistic-normal distribution, where the parameters are a function of the covariate values:
@@
 
-The STM maximizes the posterior likelihood that the observed data were generated by the above data-generating process using an iterative approximation-based variational expectation-maximization algorithm available in R's stm package \citep{roberts_stm:_2016}.
-Regularizing prior distributions are used for $\gamma$, $\kappa$ and (optionally) $\Sigma$.
+% ----------------------
+% Model Selection
+% ----------------------
+\subsection{Model and parameter selection}
+
+Topic models are usually imprecise as a number of assumptions have to be made that influence the performance of the classification task.
+Furthermore, multiple solutions exist for the optimization problem.
+The STM maximizes the posterior likelihood that the observed data were generated by the above data-generating process using an iterative approximation-based variational expectation-maximization algorithm\footnote{A technical description of this maximization process can be found in \citet{roberts_model_2016}} available in R's stm package \citep{roberts_stm:_2016}.
+Regularizing prior distributions are used for $\gamma$, $\kappa$ and $\Sigma$.
+Since an ex ante valuation of a model is hardly possible, we compute a variety of different models with different parameters and compare them with respect to the research problem \citep{gentzkow_text_2017}.
+To evaluate the accuracy of a model its perplexity can be computed.
+Similar to cross-validation (VC), different model specifications are compared to how well they do in predicting words within a document \citep{asuncion_smoothing_2012}, \citep{wallach_evaluation_2009}.
+However, \citet{chang_reading_2009} have proven with large user studies that optimal held out likelihood does not correspond to human perception of semantic coherence of topics.
+\cite{mimno_optimizing_2011} introduced a measure of coherence of a topic by observing co-occurences of the top $N$ terms of each topic on a document.
+Another strategy for selecting an appropriate model is to check for residual overdispersion of the variance of the multinomial within the data generating process of the model \citep{taddy_estimation_2012}.
+Other approaches can be found in \citet{airoldi_reconceptualizing_2010} and \citet{teh_hierarchical_2006}.
+However, cross-checking some subset of assigned topic distributions to evaluate whether the estimates align with the concept of interest \citep{gentzkow_text_2017}.
+We apply these manual audits together with numeric optimization based on the topic coherence measure suggested by \citet{mimno_optimizing_2011}.
+
+This process revealed that a model with 25 topics best reflects the structure in the corpus.
+Furthermore, we use the source of each article (the media house) and the month it was published as covariates in the topic prevalence portion of the model.
+In other words, the probability distribution of topics depends on the editorial strategy of a media house as well as on the month the article was published.
 To address problems due to non-convexity, we rely on the spectral initialization approach advocated by \citet{roberts_navigating_2016}.
@@
 % ----------------------
-% Model Selection
+% Model Results
 % ----------------------
-\subsection{Model selection}
+\subsection{Visualize model results}
 
-Topic models are generally inaccurate, since the number of topics must be determined a priori.
-Furthermore, multiple solutions exist for the optimization problem.
-Ex post analysis of several model specifications helps to evaluate its quality, as well as the number of topics and metadata selected.
+To get a first overview of the semantic concept of the topics, we produce a random sample of posts with a comparatively high posterior probability for that topic (see \ref{fig_classification}).
+Figure \ref{fig_topic_proportion} displays the topics ordered by their expected frequency across the corpus.
+To assign a label to each topic, we used a combination of most frequent words in that topic and words with the highest "score", computed as the log frequency of the word in the topic divided by the log frequency of the word in other topics \citep{roberts_stm:_2016}.
+The most common topic (3) is a general topic full of words that are frequently used in policy news, and therefore is not very interpretable.
+However, the remaining labels seem to classify a certain topic.
 
-The most common choice is the probability of held-out documents \citep{grimmer_bayesian_2010}.
-Similar to cross-validation (VC), different model specifications are compared to how well they do in predicting words within a document \citep{asuncion_smoothing_2012}, \citep{wallach_evaluation_2009}.
-Another strategy to find an appropriate number of topics is to check for residual overdispersion of the variance of the multinomial within the data generating process of the model \citep{taddy_estimation_2012}.
-Other approaches can be found in \citet{airoldi_reconceptualizing_2010} and \citet{teh_hierarchical_2006}.
-We run multiple model specifications and compare them based on held-out likelihood estimation, residual checks as well as semantic coherence to chose the number of topics that best fits the corpus to be 50.
-Furthermore, we use the source of each article (the media house) and the month it was published as a covariates in the topic prevalence portion of the model.
-In other words, the probability distribution of topics depends on the editorial strategy of a media house as well as on the month the article was published.
+\begin{figure}[H]
+	\begin{center}
+	\includegraphics[width=0.8\textwidth,keepaspectratio]{../figs/topic_proportion.png}
+	\caption{Expected Topic Proportion}
+	\label{fig_topic_proportion}
+	\end{center}
+\end{figure}
+
+%\begin{landscape}
+%\begin{figure}[H]
+%\centering
+%	\caption{Sample articles}
+%	\includegraphics[width=\linewidth,height=.9\textheight,keepaspectratio]{../figs/topic-classification-sample.png}	
+%	\label{fig_classification}
+%\end{figure}
+%\end{landscape}
 
 % ----------------------
-% Evaluation
+% Effect of covariates
 % ----------------------
-\subsection{Evaluation}
+Since we included news source as a covariate in estimating topical prevalence part within the model, we can estimate the frequency a topic is discussed within a news corpus \citep{roberts_model_2016}.
+We estimate the conditional expectation of topic prevalence for given document characteristics.
+More specifically, we estimate a linear model, where the documents are observations, the dependent variable is the posterior probability of a topic and the covariates are the metadata of documents.
+The stm-package provides a function that uses the method of composition to incorporates uncertainty in the dependent variable, drawing a set of topic proportions from the variational posterior repeated times and compute the coefficients as the average over all results.
 
-The most effective method for assessing model fit is to carefully read documents that are closely associated with particular topics to verify that the semantic concept covered by the topic is reflected in the text.
-The parameter θd provides an estimate of each document’s association with every topicmaking it straightforward to effectively direct analyst engagement with the texts (see, e.g., Roberts, Stewart, and Tingley 2014a).
-An overview of manual validation procedures can be found in Grimmer and Stewart (2013).\cite{roberts_model_2016}
-
-To validate the accuracy with which the fitted model is capturing the content of a document, we first conduct a process of informal manual audits \citep{gentzkow_text_2017}: We inspect inspect a subset of documents alongside the fitted topics to cross-check against the coding a human would produce by hand.
-Figure \ref{fig_classification} shows sample documents classified to each topic for reference.
-We produce a random sample of 7 posts from the 300 highest probability fits per topic.
+Figure \ref{fig_estimateEffects_small} displays topics, where the most significant differences between the news sources are discernible.\footnote{An overview of all estimated topics can be found in the appendix \ref{fig_estimateEffects_full1} and \ref{fig_estimateEffects_full2}.} Topic 2, classifying articles about the diesel scandal, the glpyphosate decision and green policies, occur comparatively more often in tagesschau.de and bild.de, whereas tagesschau.de reports comparatively little about the riots during the G20 summit (topic 9).
+Topics 10 (about public (financial) statistics) and 13 (about the federal migration office (BAMF), asylum procedures and other issues related to refugees) also seems to be represented comparatively frequently in the tagesschau.de corpus, the latter topic is most often discussed in the DIE WELT corpus.
+However, topic 20 (the public debate between Die Grünen and FDP in the process of coalition negotiations) is represented significantly more often in the corpus of spiegel.de and bild.de.
+Topic 26, which classifies articles that deal with terrorism, mainly about the NSU trial and the main defendant Zschäpe as well es IS, is significantly more often present in the corpus of FOCUS ONLINE.
 
 \begin{figure}[H]
-\centering
-	\caption{Sample articles}
-	\includegraphics[width=\textwidth]{../figs/topic-classification-sample.png}	
-	\label{fig_classification}
+	\caption{Mean prevalence of topics within each news source corpus}
+	\begin{center}
+		\begin{subfigure}[normla]{0.3\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect2.png}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.3\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect9.png}
+		\end{subfigure}
+				\begin{subfigure}[normla]{0.3\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect11.png}
+		\end{subfigure}
+				\begin{subfigure}[normla]{0.3\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect13.png}
+		\end{subfigure}
+				\begin{subfigure}[normla]{0.3\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect20.png}
+		\end{subfigure}
+				\begin{subfigure}[normla]{0.3\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect26.png}
+		\end{subfigure}
+	\end{center}
+	\label{fig_estimateEffects_small}
 \end{figure}
 
-The interpretability or semantic coherence of topics can vary considerably.
-\citet{mimno_optimizing_2011} propose a topic semantic coherence score computed from in-corpus word co-occurrence statistics, and show strong agreement with human evaluations.
+Another interesting aspect is how the news sources discusses the different topics, that is, describe the same event with different vocabulary.
 
-\cite{mimno_optimizing_2011}
-The evaluation of statistical topic models has traditionally been dominated by either extrinsic methods (i.e., using the inferred topics to perform some external task such as information retrieval \citep{wei_lda-based_2006} or quantitative intrinsic methods, such as computing the probability of held-out documents \citep{wallach_evaluation_2009}.
-Recent work has focused on evaluation of topics as semantically coherent concepts.
-For example, \citet{chang_reading_2009} found that the probability of held-out documents is not always a good predictor of human judgments.
+% ----------------------
+% Regression
+% ----------------------
+\section{Causal relationship between topics and social media shares.}\label{ch_regression}
 
-After performing the topic modeling, we can generate an overview of the news landscape about the german elections.
-Each group is composed of the most relevant words for that topic, and a manually-determined label.
-The distances that the topics have from each other reflect their semantic distance, or basically how different the words are for that topic.
-It is computed as the Jensen-Shannon divergence between each of the topics according to the differences in their word-topic probabilities.
-We then apply principal coordinates analysis in order to project the distance matrix down to two dimensions.
-
-%\begin{figure}[H]
-%\centering
-%	\caption{News Landscape}
-%	\includegraphics[width=\textwidth]{../figs/news-landscape-map.png}	
-%	\label{fig_landscape}
-%\end{figure}
-
-%
 %\begin{figure}[H]
@@
 
-\section{Regression}\label{ch_regression}
+In order to answer the primary question of this paper, which topics are more often shared in social networks, we assign a single topic to each article.
+The examination of the topic probability distribution revealed that most documents are assigned a unique topic with a probability of 50\% and higher (see figure \ref{fig_gamma}), so that we can classify each document based on which topic has the highest probability.
+We keep only those documents, where the posterior probability of this topic is greater or equal than 0.5 which left us with 6565 documents.
+Figure \ref{fig_topic_timeline} shows the amount of articles to which a certain topic has been assigned over time.
+Some of the topics exhibit distinct peaks in the timeline.
+Topics 11 and 14 deal with the elections, although topic 11 tends to be more about incidents related to the AfD.
+This graph also illustrates the difference between topic 6 and 17, which have similar labels: topic 6 classifies articles before the negotiations for a "Jamaika" coalition failed, while topic 17 describes the articles written after failure.
+The highest peak can be found for topic 9, which classifies articles to the riots during the G20 summit.
+It becomes apparent that more articles deal with riots than with the political content of the summit (topic 8).
 
-The examination of the topic probability distribution revealed that most documents are assigned a unique topic with high probability (65\% and higher), so that we can classify each document based on which topic has the highest probability.
-We keep only those documents, where the posterior probability of this topic is greater than 0.6 which left us with 6240 documents.
+The proportion of zeros in the independent variable (number of Facebook shares) is about 15\%.
+Figure \ref{fig_fb_shares} reveals that within the bin of 0-1 facebook shares, nearly all articles are published by stern.de.
 
-The proportion of zeros in the independent variable (number of Facebook shares) is about 66\%.
-One way to model this type of situation is to assume that the data come from a mixture of two populations, one where the counts is always zero, and another where the count has a Poisson distribution with mean $\mu$.
-In this model zero counts can come from either population, while positive counts come only from the second one.
+\begin{figure}[H]
+	\caption{}
+	\begin{center}
+		\begin{subfigure}[normla]{0.49\textwidth}
+			\includegraphics[width=\textwidth,keepaspectratio]{../figs/gamma_dist.png}
+			\caption{Density of Top-Topics posterior probability}
+			\label{fig_gamma}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.49\textwidth}
+			\includegraphics[width=\textwidth,keepaspectratio]{../figs/facebook_shares.png}
+			\caption{Grouped Facebook Shares}
+			\label{fig_fb_shares}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.9\textwidth}
+			\includegraphics[width=\textwidth,keepaspectratio]{../figs/topic-timeline.png}
+			\caption{Topic Timeline}
+			\label{fig_topic_timeline}
+		\end{subfigure}
+	\end{center}
+\end{figure}
 
-The distribution of the outcome can then be modeled in terms of two parameters, $\pi$ the probability of 'always zero', and $\mu$, the mean number of publications for those not in the 'always zero' group.
-A natural way to introduce covariates is to model the logit of the probability $\pi$ of always zero and the log of the mean $\mu$ for those not in the always zero class.
-
-The two-part model relaxes the assumption that the zeros (whether or not the article is shared) and positives (how often it is shared) come from the same data generating process.
-The zero-inflated model lets the zeros occur in two different ways: as a realization of the binary process (z=0) and as a realization of the count process when the binary variable z=1.
-
-If the process generating the zeros is $f_1(.)$ and the process generating the positive responses is $f_2(.)$ then the two-part hurdle model is defined by the following probabilities.
+Model:
 
 \begin{align*}
-	g(y)=\begin{cases}
-		f_1(0) + 1(f_i(0))f_2(0) if y=0 \\
-		(1-f_1(0))f_2(y) if y\geq 1
-	\end{cases}
+	log(FBshares) =\alpha+\beta_{topic}+\beta_{site}+\beta_{textlength}+\epsilon 
 \end{align*}
 
-The model for the zero versus positive responses is a binary model with the specified distribution, but we usually estimate it with the probit/logit model.
+\include{lm1}
+%
+%One way to model this type of situation is to assume that the data come from a mixture of two populations, one where the counts is always zero, and another where the count has a Poisson distribution with mean $\mu$.
+In this model zero counts can come from either population, while positive counts come only from the second one.
+%
+%The distribution of the outcome can then be modeled in terms of two parameters, $\pi$ the probability of 'always zero', and $\mu$, the mean number of publications for those not in the 'always zero' group.
+A natural way to introduce covariates is to model the logit of the probability $\pi$ of always zero and the log of the mean $\mu$ for those not in the always zero class.
+%
+%The two-part model relaxes the assumption that the zeros (whether or not the article is shared) and positives (how often it is shared) come from the same data generating process.
+The zero-inflated model lets the zeros occur in two different ways: as a realization of the binary process (z=0) and as a realization of the count process when the binary variable z=1.
+%
+%If the process generating the zeros is $f_1(.)$ and the process generating the positive responses is $f_2(.)$ then the two-part hurdle model is defined by the following probabilities. 
+%
+%\begin{align*}
+%	g(y)=\begin{cases}
+%		f_1(0) + 1(f_i(0))f_2(0) if y=0 \\
+%		(1-f_1(0))f_2(y) if y\geq 1
+%	\end{cases}
+%\end{align*}
+%
+%The model for the zero versus positive responses is a binary model with the specified distribution, but we usually estimate it with the probit/logit model.
+
+% ----------------------
+% Appendix
+% ----------------------
+\section*{Appendix}
+
+\begin{figure}[H]
+	\caption{Mean prevalence of topics within each news source corpus 1}
+	\begin{center}
+		\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect1.png}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect2.png}
+		\end{subfigure}
+				\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect3.png}
+		\end{subfigure}
+				\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect4.png}
+		\end{subfigure}
+				\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect5.png}
+		\end{subfigure}
+				\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect6.png}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect7.png}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect8.png}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect9.png}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect10.png}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect11.png}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect12.png}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect13.png}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect14.png}
+		\end{subfigure}
+	\end{center}
+	\label{fig_estimateEffects_full1}
+\end{figure}
+
+\begin{figure}[H]
+	\caption{Mean prevalence of topics within each news source corpus 2}
+	\begin{center}
+			\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect15.png}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect16.png}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect17.png}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect18.png}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect19.png}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect20.png}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect21.png}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect22.png}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect23.png}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect24.png}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect25.png}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect26.png}
+		\end{subfigure}
+				\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect26.png}
+		\end{subfigure}
+				\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect28.png}
+		\end{subfigure}
+	\end{center}
+	\label{fig_estimateEffects_full2}
+\end{figure}
 

### 2017-12-08 paper/R/func/01-page-scraping-functions.R

@@ -1,745 +1,0 @@
-# Facebook Page Scraping Functions
-# mail@tjpalanca.com | 1 Jan 2017
-
-# This section contains functions to be used in scraping Facebook page posts,
-# likes, comments, and the likes and comments of such comments.
-
-# Pushover functions
-load("../bin/pushover_auth.rda")
-
-pushNotification <- function(text = "Execution Completed") {
-  pushover(
-    title = text,
-    url = "http://adhoc01.tjpalanca.com",
-    message = "adhoc01.tjpalanca.com",
-    user = pushover_user_key,
-    app = pushover_app_key
-  )
-}
-
-getNAforNULL <- function(x) {
-  # returns NA when object is null
-  if (is.null(x)) {
-    return(NA)
-  } else{
-    return(x)
-  }
-}
-
-convertTimeStamp <- function(ts) {
-  # Converts string timestamp ts into POSIXct format
-  as.POSIXct(strptime(ts, "%Y-%m-%dT%H:%M:%S%z"))
-}
-
-getAppAccessToken <- function(fb_app_id, fb_app_secret) {
-  # Get app access token 
-  #
-  # Args:
-  #   fb_app_id:      character scalar containing the Facebook App ID
-  #   fb_app_secret:  character scalar containing the Facebook App Secret
-  #
-  # Returns:
-  #   App Access Token in fb.tkn (do not assign)
-  
-  GET(
-    url   = "https://graph.facebook.com/oauth/access_token",
-    query = list(
-      client_id     = fb_app_id,
-      client_secret = fb_app_secret,
-      grant_type    = "client_credentials"
-    )
-  ) %>% 
-    content(as = "text") %>% 
-    str_replace("^access_token=", "") ->> fb.tkn 
-}
-
-callFBGraphAPI <- function(node = "", query = NULL, url = "", 
-                           version = "v2.8", access_token = fb.tkn) {
-  # Function to generate a generic Facebook Graph API Call and parse results. 
-  # Uses API v2.8 by default.
-  #
-  # Args:
-  #   node:         the node to be pinged
-  #   query:        list of queries
-  #   url:          if url is already provided (as in pagination), 
-  #                   url will be fetched directly
-  #   access_token: the access token (not needed if fb.tkn is present)
-  # 
-  # Returns:
-  #   Parsed resuts from the FB API call.
-  
-  # Query string out until satisfactory result or error
-  if (url != "") {
[…]

### 2017-12-08 paper/R/func/02-topic-modelling-functions.R

@@ -1,295 +1,0 @@
-# Topic Modelling Functions
-# mail@tjpalanca.com
-# 15 Feb 2017
-
-# This section contains functions that assist with topic modelling.
-
-stemWords <- function(df, patterns, lang) {
-  # Applies a simple, conservative stemming algorithm
-  #
-  # Args:
-  #   df:       data frame containing words (`word`)
-  #   patterns: list of regex expressions containing the prefixes, suffixes, and mid-fixes
-  #   lang:     en_US or tl_PH, depending on the language in question
-  # 
-  # Returns:
-  #   A unique mapping between the identified words and the suggested stem
-  
-  df %>% 
-    # Get all distinct words
-    distinct(word) %>%
-    # Filter to language
-    filter(hunspell_check(word, lang)) %>% 
-    # Remove words too short for any modification
-    filter(str_length(word) > 3) %>% 
-    # Generate pattern matches
-    mutate(
-      pattern = 
-        map(
-          word,
-          function(word, patterns) patterns[map_lgl(patterns, ~str_detect(word, .))],
-          patterns = patterns
-        )
-    ) %>% 
-    unnest(pattern) %>% 
-    # Remove pattern from word
-    mutate(stem_word = str_replace(word, pattern, "")) %>%
-    # Add pattern exceptions if no words pass spell check
-    mutate(
-      stem_word = 
-        map(
-          stem_word,
-          function(stem_word) {
-            append(
-              stem_word,
-              c(
-                # ENGLISH
-                ifelse(
-                  lang == "en_US",
-                  paste0(stem_word, "e"), NA
-                ),
-                ifelse(
-                  lang == "en_US" & 
-                    str_detect(stem_word, "i$"), 
-                  stem_word %>% str_replace("i$", "y"), NA
-                ),
-                ifelse(
-                  lang == "en_US" &
-                    str_sub(stem_word, -1, -1) == str_sub(stem_word, -2, -2),
-                  str_sub(stem_word, 1, -2), NA
-                ),
-                # TAGALOG
-                ifelse(
-                  lang == "tl_PH",
-                  str_replace_all(stem_word, "u", "o"), NA
-                ),
-                ifelse(
-                  lang == "tl_PH",
-                  str_replace(stem_word, "r$", "d$"), NA
-                )
[…]

### 2017-12-08 paper/R/func/functions.R

@@ -1,0 +1,32 @@
+AddAdjustBox <- function(sg.table){
+  after.location <- grep(" \\\\label\\{t_*", sg.table)
+  sg.table <- append(sg.table,
+                     "\\begin{adjustbox}{totalheight=\\textheight-2\\baselineskip}",
+                     after = after.location)
+  after.location <- grep("\\\\end\\{tabular\\}", sg.table)
+  sg.table <- append(sg.table, "\\end{adjustbox}", after = after.location)
+  return(sg.table)
+}
+
+AddResizeBox <- function(sg.table){
+  after.location <- grep(" \\\\label\\{t_*", sg.table)
+  sg.table <- append(sg.table,
+                     "\\resizebox{\\textwidth}{!}{",
+                     after = after.location)
+  after.location <- grep("\\\\end\\{tabular\\}", sg.table)
+  sg.table <- append(sg.table, "}", after = after.location)
+  return(sg.table)
+}
+
+Mode = function(x){ 
+  ta = table(x)
+  tam = max(ta)
+  if (all(ta == tam))
+    mod = NA
+  else
+    if(is.numeric(x))
+      mod = as.numeric(names(ta)[ta == tam])
+  else
+    mod = names(ta)[ta == tam]
+  return(mod)
+}

### 2017-12-08 paper/presentation/phd-workshop.Rmd
phd presentation

---
title: "Whats inside the news?"
author: Franziska Löw
date: December 16, 2017
output: 
  revealjs::revealjs_presentation:
    theme: simple
    highlight: haddock
    center: true
    transition: slide
    css: style.css
    #self_contained: false
    incremental: true
---

```{r include=FALSE}
suppressPackageStartupMessages({
  library(dplyr)       # Data manipulation
  library(stringr)     # String manipulation
  library(lubridate)   # Date and time manipulation
  library(purrr)       # Functional programming
  library(tidyr)       # Reshaping
  library(magrittr)    # Advanced piping
  library(pushoverr)   # Pushover notifications
  library(doMC)        # Parallel Computing
  library(readr)       # Importing data
  library(tibble)      # Better data frames
  library(data.table)
  library(pscl)
  library(boot)
  library(stm)
  library(tm)
  library(readxl)

  library(ggplot2)     # Static data visualization
  library(ggpmisc)
  library(RColorBrewer) 
  library(ggrepel)
  library(plotly)
  library(scales)      # Scales
  library(viridis)     # Viridis color scales

  library(tidytext)    # Tidy text mining
  library(stringdist)  # String distances
  library(proxy)       # Distance measures
})

# Theming
quartzFonts(
  Roboto =
    c("Roboto-Light",
      "Roboto-Bold",
      "Roboto-Regular",
      "Roboto-Thin")
)

theme_set(
  theme_bw(base_family = "Roboto", base_size = 10) +
    theme(
      plot.title = element_text(size = 12,
                                margin = margin(0, 0, 4, 0, "pt")),
      plot.subtitle = element_text(size = 12),
      plot.caption = element_text(size = 6, hjust = 0),
      axis.title = element_text(size = 8),
      panel.border = element_blank()
    )
)
col <- brewer.pal(8,"Dark2")
```

## Agenda

1. **Introduction**

2. **Methodology**

3. **Literature Review**

4. **First Results**

5. **Conclusion**

# Introduction
## Online News
<div style="position:relative; width:640px; height:480px; margin:0 auto;">
  <img class="fragment" src="../figs/screenshot-spon.png" style="position:absolute;top:0;left:0;" />
  <img class="fragment" src="../figs/screenshot-focus.png" style="position:absolute;top:0;left:0;" />
  <img class="fragment" src="../figs/screenshot-bild.png" style="position:absolute;top:0;left:0;" />
  <img class="fragment" src="../figs/screenshot-tagesschau.png" style="position:absolute;top:0;left:0;" />
</div>

## Business Model of online News

<img class="fragment" src="../figs/onlinenews-2.png" width="900"/>

---------------------------

### Research Question: 
Does the business model have an effect on the editorial content?

### Methodology: 
  1. Estimate a Structural Topic Model
  2. Use posterior distribution to estimate the effect of document metadata.

## Data
Online news articles about domestic politics from 01.06.2017 - 22.11.2017

<img class="fragment" src="../figs/timeline.png" width="850"/>

----------------------
```{r eval=FALSE, include=FALSE}
load("../output/models/STM 28 .Rda")

tidy.df <- btw %>%
  unnest_tokens(word, text_cleaned) %>%
  count(word, articleID, sort =TRUE)

dtm <- tidy.df %>% dplyr::filter(nchar(word)>1) %>%
  cast_dtm(articleID, word, n)
save(stmOut, btw, dtm, tidy.df, file="../output/presentation_files.Rda")
```

```{r message=FALSE, warning=FALSE, include=FALSE}
load("../output/presentation_files.Rda")
table <- inspect(dtm[1:5,1:10])
```

> - Documents (articles) are stored on a "Document-Term-Matrix"
```{r echo=FALSE}
htmlTable::htmlTable(table)
```

  - Documents are seen as "bag of words"
  - Each article has metadata: publisher (news platform) and the day it was published.

- How to find out latent topics in an article?

# Methodology

## Topic Model

<img src="../figs/lda-2.png">
<small>Credits: Christine Doig</small>

## The intuition behind LDA

<img src="../figs/lda-blei.png" width="750"/>

<small>Credits: Blei (2012)</small>

* Model the generation of documents with latent topic structure
    * a topic ~ a distribution over words
    * a document ~ a mixture over topics
    * a word ~ a sample drawn from one topic

<aside class="notes">
 - Documents are seen as "bag of words". 
 - Mixed memberhip model: Population of topics stays the same, but distrubution over topics changes for ech document
 - Each document is comming from a mixture model, where the mixture proportions change from document to document but mixture components are fixed a cross all documents.
 - Each document arises as follows: 
    1. chose a distribution over topics (histogram) 
    2. For each word in the document, chose a colored button
    3. look up the distribution over terms associated with that button and draw a word
</aside>

## LDA as a graphical model

<img src="../figs/lda-plate.png" width="800">

> - Nodes a random variables; edges indicate dependence
> - Shaded nodes are observed; unshaded nodes are hidden.
> - Plates indicate replicated variables.

<aside class="notes">
		-Generative Process:
  1. chose Number of topics (e.g. K=100)
  2. Each topic has a $\beta$, which is a distribution over the full vocabulary
  3. For each Document (D) I chose a distribution over topics ($\theta$)
  4. For each word in each document (N) I chose a colored button from $\theta$ 
  5. Chose a word from the corresponding distribution over terms
- Diagram:
    - defines a factorization of the joint probability distribution of hidden and observed random variables.
    - encodes indepence assumptions about the variables (which variables are dependent and conditionally independent) 
    - Connects to algorithm for computing with data: Inference problem: finding the hidden variables given the observations.
	</aside>

------------------------
<img src="../figs/lda-plate-2.png" width="800">

- The posterior is: $p(\theta,z,\beta|w) = \frac{p(\theta,\beta,z,w)}{p(w)}$

    - **numerator**: joint distribution of all random variables (can be easily computed for any setting of hidden variables.)
    - **denominator**: marginal probability of the observations (probability of seeing the observed corpus under any topic model.)

- From a collection of documents, infer
    - Per-word topic assignment $z_{d,n}$
    - Per-document topic proportions $\theta_d$
    - Per-corpus topic distributions $\beta_k$

- Then use posterior expectations to perform the task at hand: information retrieval, document similarity, exploration, and others.

<aside class="notes">
  - the joint distribution defines a posterior. 
  - In theory, it can be computed by summing the joint distribution over every possible instantiation of the hidden topic structure.
  - $p(\theta,z,\beta|w)$ the probability of the hidden structures given the observed words in a document.
  - - That number of possible topic structures, however, is exponentially large; this sum is intractable to compute. As for many modern probabilistic models of interest—and for much of modern Bayesian statistics—we cannot compute the posterior because of the denominator, which is known as the evidence. A central research goal of modern probabilistic modeling is to develop efficient methods for approximating it. Topic modeling algorithms—like the algorithms used to create Figures 1 and 3—are often adaptations of general-purpose methods for approximating the posterior distribution.
  - First uncover the structure (calculate th posterior) - use the discovered distributions to perform task
</aside>

## Research Process

<img class="fragment" src="../figs/research_strategy.png" width="1000"/>

<aside class="notes">
  1. We have knowledge about the world and want to answer a specific question: We know that newspapers are based on different business models. does that have an effect on the topics discussed in the newspaper?
  2. We make assumptions and bring them together with our data to uncover patterns.
  3. We use these patterns (posterior distributions) to predict a variable
</aside>

## Strucutral Topic Model
- We want to use estimates of $\theta_d$ as the dependent variable in an regression on covariates to test whether different types of documents have different content.

- This is contradictory because documents are assumed to be generated by the same statistical process.

- The structural topic model (STM) of Roberts et. al. (2016) explicitly introduces covariates into a topic model, and allows one to estimate the impact of document-level covariates on topic content and prevalence as part of the topic model itself.

## Topic Prevalence vs. Content
- The process for generating individual words is the same as for plain LDA conditional on the $\beta_k$ and $\pi_d$ terms.

- However both objects can depend on potentially different sets of document- level covariates. Each document has:
    1. **Topic Prevalence**: Attributes that affect the likelihood of discussing topic $k$
    2. **Topic Content**: Attributes that affect the likelihood of including term $v$ overall, and of including it within topic $k$

- The generation of the $\beta_k$ and $\pi_k$ terms is via multinomial logistic regression, which breaks local conjugacy.

## Model Selection
- There are three parameters we need to make assumptions about: number of topics $K$ and priors $\alpha, \eta$:
  - Priors don’t receive too much attention in literature: 
    - Griffiths & Steyvers (2002) recommend $\eta = 200/V$ and $\alpha = 50/K$. 
    - Smaller values will tend to generate more concentrated distributions. (See also Wallach et.al. (2009)).
  - $K$ is clearer. Two potential goals:
    1. Predict text well. Statistical criteria to select $K$.
    2. Interpretability. General versus specific.

## Approximate Posterior
- Mean field variational methods (Blei et al., 2001, 2003)
- Expectation propagation (Minka and Lafferty, 2002)
- Collapsed Gibbs sampling (Griffiths and Steyvers, 2002)
- Distributed samplung (Newsman et al., 2008; Ahmed et al., 2012)
- Stochastic inference (Hoffman et al., 2010, 2013; Mimno et al., 2012)
- Factorization inference (Arora et al., 2012; Anandkumar et al., 2012)
- Amortized inference (Srivastava and Sutton, 2019)
- ...

<aside class="notes">
  - We cannot obtain exact solutions for our posterior
  - Instead of obtaining a closed-form solution for the posterior distribution, we must approximate it.
</aside>

## Predicitve Distributions

$\beta_{k,v} = \frac{m_{k,v}+\eta}{\sum_{v=1}^V(m_{k,v}+\eta)}$

$\theta_{k,v} = \frac{n_{d,k}+\alpha}{\sum_{k=1}^K(n_{d,k}+\alpha)}$

## Formalizing Interpretability
- Chang et. al. (2009) propose an objective way of determining whether topics are indeed interpretable.
- Two tests:
  1. *Word intrusion*:
      - Form set of words consisting of top five words from topic k + word with low probability in topic k. 
      - Ask subjects to identify inserted word.
  2. *Topic intrusion*: 
      - Show subjects a snippet of a document + top three topics associated to it + randomly drawn other topic. 
      - Ask to identify inserted topic.

# Model Results

```{r Extract wtp and dtp, include=FALSE}
load("../output/models/STM 28 .Rda")

# Word-topic probabilities
stmOut %>% tidy("beta") %>% filter(!is.na(topic)) -> posts.wtp
# Document-topic probabilities
stmOut %>% tidy("gamma") -> posts.dtp

# Label Topics
label <- labelTopics(stmOut, n=3)

prob <- as.data.frame(label$prob, stringsAsFactors = F)
frex <- as.data.frame(label$frex, stringsAsFactors = F)
lift <- as.data.frame(label$lift, stringsAsFactors = F)
score <- as.data.frame(label$score, stringsAsFactors = F)

topicLabel <- prob %>% 
  transmute(topic = rownames(.),
            topic_name = paste(prob$V1,prob$V2,prob$V3,score$V1,score$V2,score$V3, sep=","),
            prob = paste(prob$V1,prob$V2,prob$V3, sep=","),
            frex = paste(frex$V1,frex$V2,frex$V3, sep=","),
            lift = paste(lift$V1,lift$V2,lift$V3, sep=","),
            score = paste(score$V1,score$V2,score$V3, sep=","))

topicLabel$topic_name <- vapply(lapply(strsplit(topicLabel$topic_name, ","), unique), paste, character(1L), collapse = " ")
rm(prob, frex, lift, score)
```

## Topic Proportions

<img src="../figs/topic_proportion.png" width="600">

## Sample Articles

### 2017-12-08 simulations.Rmd
simulations

---
title: "Understanding Probabilistic Topic Models by Simulation"
subtitle: ""
author: "Franziska Löw"
date: ""
output: 
  html_document:
    toc: true
    toc_float: true
    theme: "lumen"
    highlight: "tango"
    code_folding: show
    self_contained: true
---

```{r echo=TRUE, message=FALSE, warning=FALSE}
library(tidyverse)
library(ggplot2)
library(MCMCpack)
library(Compositional)
library(data.table)
library(utf8)
#install.packages("emojifont")
#library(emojifont)
library(htmlTable)
```

**This is basically a R-version of [Timothy Hoppers](https://github.com/tdhopper/pydata-nyc-2015) presentation.

```{r}
data("iris")
set.seed(1235)

df <- as.data.frame(iris)
```

# Naive Clustering

Can we discriminate between Setosa and Virginica irises by modeling their sepal length as a mixture of Gaussians?
```{r}
df %>%
  filter(!Species == "versicolor") -> df

ggplot(df, aes(Sepal.Length)) +
  geom_histogram(fill="blue", alpha=.5, bins = 10) +
  labs(x="", y="", title="Sepal Length for Iris-Setosa and Iris-Virginica")
```

# Naive Clustering
```{r}
ggplot(df, aes(Sepal.Length)) +
  geom_histogram(fill="blue", alpha=.5, bins = 10) +
  geom_vline(aes(xintercept=5.8)) +
  labs(x="", y="", title="Sepal Length for Iris-Setosa and Iris-Virginica")
```

# Gaussian Mixture Models
Here's what our actual underlying data looks like.
Without knowing the latent classes, we could assume that each class is drawn from a normal distribution.
```{r}
ggplot(df, aes(Sepal.Length, fill=factor(Species))) +
  geom_histogram(alpha=.5, bins = 10) +
  labs(x="", y="", title="Sepal Length for Iris-Setosa and Iris-Virginica") +
  theme(legend.position = "none")
```

# Sampling
```{r echo=FALSE, message=FALSE, warning=FALSE}
mixture_proportions = c(0.5,0.5)
mixture_proportions = c(0.5,0.5)
mean = c(5.01,6.59)
std = c(0.35,0.64)

i = 100
data = data.frame(iris_type=rep(0,i), 
                  sepal_length=rep(0,i))

for (i in 1:i) {
  iris_type = sample(c(1,2),1,prob=mixture_proportions)
  sepal_length = rnorm(1,mean = mean[iris_type], sd= std[iris_type])

  data[i,] = c(iris_type,sepal_length)
}

ggplot(data, aes(sepal_length, fill=factor(iris_type))) +
  geom_histogram(alpha=.6, bins=10) +
  labs(x="", y="",
    title="Simulated Sepal Length for Iris-Setosa and Iris-Virginica") +
  theme(legend.position = "none")
```

# Insert uncertainty

Instead of fixed parameters, we could also sample parameters from probability distributions.

## What is a Dirichlet Distribution?
Continuous distribution over unit vectors.
Each sample is often regarded as a probability distribution; i.e. this is a distribution of distributions.
In our example problem, the sample from the Dirichlet distribution determines the relative number of data points for each flower type.

```{r}
rdirichlet(10, c(1,1,2))
```

The higher value of $\alpha_i$, the greater “weight” of $X_i$ and the greater amount of the total “mass” is assigned to it (recall that in total it must be $x_1+⋯+x_k=1$). If all $\alpha_i$ are equal, the distribution is symmetric. If $\alpha_i<1$ it can be thought as anti-weight that pushes away $x_i$ toward extremes, while when it is high, it attracts $x_i$ toward some central value (central in the sense that all points are concentrated around it, not in the sense that it is symmetrically central).

If $\alpha_1=\alpha_2=\alpha_3=1$ then the points are uniformly distributed:

```{r}
bivt.contour(rdirichlet(100, c(1,1,1)))
```

$\alpha_1=\alpha_2=\alpha_3=.1$ 
```{r}
bivt.contour(rdirichlet(100, c(.1,.1,.1)))
```

$\alpha_1=\alpha_2=\alpha_3 = 100$ 
```{r}
bivt.contour(rdirichlet(100, c(100,100,100)))
```
$\alpha_1=\alpha_2 = 10, \alpha_3=100$ 
```{r}
bivt.contour(rdirichlet(100, c(10,10,100)))
```

### Sampling

```{r echo=FALSE, message=FALSE, warning=FALSE}
mixture_proportions = rdirichlet(2, alpha=c(1,1))[1,]
mean = rnorm(2, mean=6, sd=1)
std = rnorm(2, mean=.5, sd=.2)

i = 100
data = data.frame(iris_type=rep(0,i), 
                  sepal_length=rep(0,i))

for (i in 1:i) {
  iris_type = sample(c(1,2),1,prob=mixture_proportions)
  sepal_length = rnorm(1,mean = mean[iris_type], sd= std[iris_type])

  data[i,] = c(iris_type,sepal_length)
}

ggplot(data, aes(sepal_length, fill=factor(iris_type))) +
  geom_histogram(alpha=.6) +
  labs(x="", y="", title="Simulated Sepal Length for Iris-Setosa and Iris-Virginica") +
  theme(legend.position = "none")
```

If we run sample again, our data looks completely different. These are samples from the distribution over this model.

```{r echo=FALSE, message=FALSE, warning=FALSE}
mixture_proportions = rdirichlet(2, alpha=c(1,1))[1,]
mean = rnorm(2, mean=6, sd=1)
std = rnorm(2, mean=.5, sd=.2)

i = 100
data = data.frame(iris_type=rep(0,i), 
                  sepal_length=rep(0,i))

for (i in 1:i) {
  iris_type = sample(c(1,2),1,prob=mixture_proportions)
  sepal_length = rnorm(1,mean = mean[iris_type], sd= std[iris_type])

  data[i,] = c(iris_type,sepal_length)
}

ggplot(data, aes(sepal_length, fill=factor(iris_type))) +
  geom_histogram(alpha=.6) +
  labs(x="", y="", title="Simulated Sepal Length for Iris-Setosa and Iris-Virginica") +
  theme(legend.position = "none")
```

--------------------------
--> Reversing the process

Given data without cluster assignments (in no particular order)...
...find the cluster for each point
...find the parameters of each cluster (or distribution over parameters)
...find the mixture proportion (or distribution proportions)

# Discrete Mixture Model
```{r}
mixture_proportions = c(0.3,0.7)
cluster_distributions = cbind(c(0.33, 0.33, 0.34),c(0.2, 0.8, 0.0))

i <- 100
docs <- list(cluster1=NULL, cluster2=NULL)

for (i in 1:i) {
  cluster = sample(length(mixture_proportions),1, 
                   prob = mixture_proportions)
  docs[[cluster]] = append(docs[[cluster]], sample(c("elephant","panda_face","hamster"), 1,
                             prob = cluster_distributions[,cluster]))

}

docs
```

## Baysian style!
```{r}
num_clusters = 2
mixture_proportions = rdirichlet(1, alpha = rep(1,num_clusters))
cluster_distributions = rdirichlet(num_clusters,alpha = c(1,1,1))

i <- 100
docs <- list(cluster1=NULL, cluster2=NULL)

for (i in 1:i) {
  cluster = sample(num_clusters,1, 
                   prob = mixture_proportions)
  docs[[cluster]] = append(docs[[cluster]], sample(c("elephant","panda_face","hamster"), 1,
                             prob = cluster_distributions[cluster,]))

}

docs
```

# Mixture Model for Documents
```{r}
vocabulary = c("elephant","panda_face","hamster")
num_terms = length(vocabulary)

# Topics are distributions over vocabulary words
topic_labels = c('runner','bicyclist')
topics = rbind(c(0.1,  0.3,  0.6),
          c(0.8,  0.1,  0.1))

# Proportion of documents of each topic
mixture_proportion = c(0.3, 0.7)
```

```{r}
dd=data.frame(x=topic_labels, y=mixture_proportion)

ggplot(dd, aes(x, y)) + geom_col(fill="blue",alpha=.6) + 
  #theme(axis.text.x = emoji_text) + 
  labs(x="", y="", title="Mixture Proportions") 
```

```{r}
dd <- as.data.frame(topics)
names(dd) <- vocabulary
dd$topic_label <- topic_labels

melt(dd, id.vars="topic_label") %>%
  ggplot(aes(x=as.factor(topic_label), y=value, fill=variable)) +
  geom_col(position = "dodge") +
    #theme(axis.text.x = emoji_text,
    #      legend.text = emoji_text) +
    labs(x="", y="", title="Mixture Proportions", fill="")  
```

Lets generate some documents
```{r}
i = 11

topic_num <- NULL
docs <- list()

# Generate documents
for (doc_index in 1:i) {
  topic = sample(topic_labels, 1, p=mixture_proportions)
  topic_num <- append(topic_num, topic)

  doc_len = rpois(1,10)

  # Generate words in documents
  vocab <- NULL
  for (x in 1:doc_len) {
     vocab <- append(vocab, sort(sample(vocabulary,1,
                   p=topics[which(topic_labels==topic),])))

  }
  #print(paste("Document",doc_index,"(",topic,"):",vocab))
  docs[[doc_index]] <- paste(vocab, sep = ",")
}
names(docs) <- topic_num

docs
```

### 2017-12-10 simulations.Rmd
graphs with emojis

@@
 ```{r echo=TRUE, message=FALSE, warning=FALSE}
-library(tidyverse)
+library(dplyr)
 library(ggplot2)
@@
 library(data.table)
-library(utf8)
-#install.packages("emojifont")
+#library(utf8)
 #library(emojifont)
-library(htmlTable)
+#library(htmlTable)
 ```
@@
 
-```{r}
-dd=data.frame(x=topic_labels, y=mixture_proportion)
+```{r eval=FALSE, include=FALSE}
+#list.emojifonts()
+#load.emojifont('OpenSansEmoji.ttf')
 
+emoji_text=element_text(family="OpenSansEmoji", size=20)
+
+dd=data.frame(x=emoji(topic_labels), y=mixture_proportion)
+
+ggsave(plot={
   ggplot(dd, aes(x, y)) + geom_col(fill="blue",alpha=.6) + 
-  #theme(axis.text.x = emoji_text) + 
+  theme(axis.text.x = emoji_text) + 
   labs(x="", y="", title="Mixture Proportions") 
+},
+file = "images/simulations-1.png", dpi=600,
+width = 7, height = 4
+)
 ```
 
-```{r}
+![Mixture Proportions](images/simulations-1.png)
+
+```{r eval=FALSE, include=FALSE}
 dd <- as.data.frame(topics)
-names(dd) <- vocabulary
-dd$topic_label <- topic_labels
+names(dd) <- emoji(vocabulary)
+dd$topic_label <- emoji(topic_labels)
 
+ggsave(plot={
   melt(dd, id.vars="topic_label") %>%
@@
   geom_col(position = "dodge") +
-    #theme(axis.text.x = emoji_text,
-    #      legend.text = emoji_text) +
+    theme(axis.text.x = emoji_text,
+          legend.text = emoji_text) +
     labs(x="", y="", title="Mixture Proportions", fill="") 
+},
+file="images/simulations-2.png",
+dpi = 600,
+width=7,
+height = 4
+)
 ```
+![Mixture Proportions 2](images/simulations-2.png)
 
@@
 for (doc_index in 1:i) {
-  topic = sample(topic_labels, 1, p=mixture_proportions)
+  topic = sample(topic_labels, 1, p=mixture_proportion)
   topic_num <- append(topic_num, topic)

### 2017-12-11 phd_slides/phd-workshop.Rmd
slides

--- 2017-12-08 paper/presentation/phd-workshop.Rmd
@@
   library(lubridate)   # Date and time manipulation
-  library(purrr)       # Functional programming
-  library(tidyr)       # Reshaping
   library(magrittr)    # Advanced piping
   library(pushoverr)   # Pushover notifications
-  library(doMC)        # Parallel Computing
   library(readr)       # Importing data
-  library(tibble)      # Better data frames
   library(data.table)
@@
   library(readxl)
+  library(tidytext)
+  library(MCMCpack)
+  library(Compositional)
 
@@
 
-  library(tidytext)    # Tidy text mining
   library(stringdist)  # String distances
@@
 ## Online News
+
 <div style="position:relative; width:640px; height:480px; margin:0 auto;">
-  <img class="fragment" src="../figs/screenshot-spon.png" style="position:absolute;top:0;left:0;" />
-  <img class="fragment" src="../figs/screenshot-focus.png" style="position:absolute;top:0;left:0;" />
-  <img class="fragment" src="../figs/screenshot-bild.png" style="position:absolute;top:0;left:0;" />
-  <img class="fragment" src="../figs/screenshot-tagesschau.png" style="position:absolute;top:0;left:0;" />
+  <img class="fragment" src="img/screenshot-spon.png" style="position:absolute;top:0;left:0;" />
+  <img class="fragment" src="img/screenshot-focus.png" style="position:absolute;top:0;left:0;" />
+  <img class="fragment" src="img/screenshot-bild.png" style="position:absolute;top:0;left:0;" />
+  <img class="fragment" src="img/screenshot-tagesschau.png" style="position:absolute;top:0;left:0;" />
 </div>
@@
 
-<img class="fragment" src="../figs/onlinenews-2.png" width="900"/>
+<img class="fragment" src="img/onlinenews-2.png" width="900"/>
 
@@
 
-<img class="fragment" src="../figs/timeline.png" width="850"/>
+<img class="fragment" src="img/timeline.png" width="850"/>
 
-----------------------
-```{r eval=FALSE, include=FALSE}
-load("../output/models/STM 28 .Rda")
+## Concepts
 
-tidy.df <- btw %>%
-  unnest_tokens(word, text_cleaned) %>%
-  count(word, articleID, sort =TRUE)
+- A single observation in a textual database is called a *document*.
 
-dtm <- tidy.df %>% dplyr::filter(nchar(word)>1) %>%
-  cast_dtm(articleID, word, n)
-save(stmOut, btw, dtm, tidy.df, file="../output/presentation_files.Rda")
-```
+- The set of documents that make up the dataset is called a *corpus*.
 
+- Covariates associated with each document are called *metadata*.
+
+## Data Structure
 ```{r message=FALSE, warning=FALSE, include=FALSE}
-load("../output/presentation_files.Rda")
+load("data/presentation-data.Rda")
 table <- inspect(dtm[1:5,1:10])
@@
 
-> - Documents (articles) are stored on a "Document-Term-Matrix"
+- Documents (articles) are stored on a "Document-Term-Matrix"
+-
 ```{r echo=FALSE}
@@
 
-- How to find out latent topics in an article?
+## How to find out latent topics in an article?
 
@@
 
-<img src="../figs/lda-2.png">
+<img src="img/lda-2.png">
 <small>Credits: Christine Doig</small>
@@
 
-<img src="../figs/lda-blei.png" width="750"/>
+<img src="img/lda-blei.png" width="750"/>
 
@@
 <aside class="notes">
- - Documents are seen as "bag of words". 
- - Mixed memberhip model: Population of topics stays the same, but distrubution over topics changes for ech document
- - Each document is comming from a mixture model, where the mixture proportions change from document to document but mixture components are fixed a cross all documents.
- - Each document arises as follows: 
-    1. chose a distribution over topics (histogram) 
-    2. For each word in the document, chose a colored button
-    3. look up the distribution over terms associated with that button and draw a word
+Mixed memberhip model: Population of topics stays the same, but distrubution over topics changes for each document.
+Each document is comming from a mixture model, where the mixture proportions change from document to document but mixture components are fixed a cross all documents.
 </aside>
@@
 
-<img src="../figs/lda-plate.png" width="800">
+* Nodes are random variables; arrows indicate dependence
 
-> - Nodes a random variables; edges indicate dependence
-> - Shaded nodes are observed; unshaded nodes are hidden.
-> - Plates indicate replicated variables.
+* Plates indicate replicated variables:
+    * $N =$ collection of words within a document.
+    * $D =$ collection of documents within a corpus.
+
+* Shaded nodes are observed; unshaded nodes are hidden
+    * observed: word in a document $w_{d,n}$
+    * fixed: mixture components (number of topics $K$ & vocabulary)
+    * hidden: mixture proportions (per-document topic proportions $\theta_d$ & word-topic distribution $\beta_k$)
+
+----------------------------
+<img src="img/lda-plate-2.png" width="600">
+----------------------------
 
 <aside class="notes">
-		-Generative Process:
-  1. chose Number of topics (e.g. K=100)
-  2. Each topic has a $\beta$, which is a distribution over the full vocabulary
-  3. For each Document (D) I chose a distribution over topics ($\theta$)
-  4. For each word in each document (N) I chose a colored button from $\theta$ 
-  5. Chose a word from the corresponding distribution over terms
-- Diagram:
-    - defines a factorization of the joint probability distribution of hidden and observed random variables.
-    - encodes indepence assumptions about the variables (which variables are dependent and conditionally independent) 
-    - Connects to algorithm for computing with data: Inference problem: finding the hidden variables given the observations.
+Diagram:
+(1)defines a factorization of the joint probability distribution of hidden and observed random variables.
+(2)encodes indepence assumptions about the variables (which variables are dependent and conditionally independent) 
+(3)Connects to algorithm for computing with data: Inference problem: finding the hidden variables given the observations.
 </aside>
 
-------------------------
-<img src="../figs/lda-plate-2.png" width="800">
+## Generative Process I
+* Generative Process for the $n^{th}$ word-position in document $d$: 
+    1. $K$: choose the number of topics;
+    2. $\theta_d$: for each document $d$, choose a distribution over topics;
+    3. $z_{d,n}$: according to $\theta_d$, assign a topic for the $n^{th}$ word;
+    4. $w_{d,n}$: choose a term from that topic according to $\beta_k$
+    5. $N$: repead this process for all $n$ word-positions in the document.
+    6. $D$: conduct this process for all $d$ documents in the corpus
 
-- The posterior is: $p(\theta,z,\beta|w) = \frac{p(\theta,\beta,z,w)}{p(w)}$
+## R Markdown
 
-    - **numerator**: joint distribution of all random variables (can be easily computed for any setting of hidden variables.)
-    - **denominator**: marginal probability of the observations (probability of seeing the observed corpus under any topic model.)
+test 1
 
-- From a collection of documents, infer
-    - Per-word topic assignment $z_{d,n}$
-    - Per-document topic proportions $\theta_d$
-    - Per-corpus topic distributions $\beta_k$
+***
+
+test 2
+
+## Generative Process II
+
+$p(\beta_{1:K},\theta_{1:D},z_{1:D}, w_{1:D})=\displaystyle \prod_{i=1}^{K}p(\beta_i)\displaystyle \prod_{d=1}^{D}p(\theta_d)(\prod_{n=1}^Np(z_{d,n,}|\theta_d)p(w_{d,n}|\beta_{1:K},z_{d,n}))$
+
+```{r}
+draws <- rdirichlet(200, c(1,1,1) )
+bivt.contour(draws)
+```
+
+## Bayesian inference
+
+Posterior probability: $P(A|B)=\frac{P(B|A)P(A)}{P(B)}$
+
+$p(\theta_{1:D},z_{1:D},\beta_{1:K}|w_{1:D}) = \frac{p(\theta_{1:D},\beta_{1:K},z_{1:D})(w_{1:D})}{p(w_{1:D})}$
+
+  * **numerator**: joint distribution of all random variables (can be easily computed for any setting of hidden variables.)
+  * **denominator**: marginal probability of the observations (probability of seeing the observed corpus under any topic model.)
 
@@
 <aside class="notes">
-  - the joint distribution defines a posterior. 
-  - In theory, it can be computed by summing the joint distribution over every possible instantiation of the hidden topic structure.
-  - $p(\theta,z,\beta|w)$ the probability of the hidden structures given the observed words in a document.
-  - - That number of possible topic structures, however, is exponentially large; this sum is intractable to compute.
+the joint distribution defines a posterior. 
+In theory, it can be computed by summing the joint distribution over every possible instantiation of the hidden topic structure.
+$p(\theta,z,\beta|w)$ the probability of the hidden structures given the observed words in a document.
+That number of possible topic structures, however, is exponentially large; this sum is intractable to compute.
 As for many modern probabilistic models of interest—and for much of modern Bayesian statistics—we cannot compute the posterior because of the denominator, which is known as the evidence.
@@
 Topic modeling algorithms—like the algorithms used to create Figures 1 and 3—are often adaptations of general-purpose methods for approximating the posterior distribution.
-  - First uncover the structure (calculate th posterior) - use the discovered distributions to perform task
+First uncover the structure (calculate th posterior) - use the discovered distributions to perform task
 </aside>
@@
 
-<img class="fragment" src="../figs/research_strategy.png" width="1000"/>
+<img class="fragment" src="img/research_strategy.png" width="1000"/>
 
@@
 ```{r Extract wtp and dtp, include=FALSE}
-load("../output/models/STM 28 .Rda")
-
 # Word-topic probabilities
@@
 
-<img src="../figs/topic_proportion.png" width="600">
+<img src="img/topic_proportion.png" width="600">
 

### 2017-12-11 paper/R/04_regression.Rmd
new figs

@@
 
-#rm(list=ls())
+rm(list=ls())
 col <- brewer.pal(7,"Dark2")
@@
 ```{r caching, echo = FALSE}
-#load("../output/btw_combined.Rda")
-load("../output/models/STM 28 .Rda")
+load("../output/models/STM 28 2.Rda")
 ```
@@
 ## Topic Proportion
-```{r}
+```{r fig.height=7, fig.width=9}
+library(stm)
 png("../figs/topic_proportion.png")
@@
      custom.labels = topicLabel$topic_name, 
-     family = "Roboto", main = "", text.cex = 0.7)
+     family = "Roboto", main = "", text.cex = 1)
 dev.off()

### 2017-12-11 phd_slides/phd-workshop.Rmd
new figs

@@
   revealjs::revealjs_presentation:
-    theme: simple
+    theme: serif
     highlight: haddock
@@
     css: style.css
-    #self_contained: false
+    self_contained: true
     incremental: true
@@
   library(lubridate)   # Date and time manipulation
+  library(purrr)       # Functional programming
+  library(tidyr)       # Reshaping
   library(magrittr)    # Advanced piping
   library(pushoverr)   # Pushover notifications
+  library(doMC)        # Parallel Computing
   library(readr)       # Importing data
+  library(tibble)      # Better data frames
   library(data.table)
@@
   library(tm)
+  library(knitr)
   library(readxl)
-  library(tidytext)
   library(MCMCpack)
-  library(Compositional)
+  library(xkcd)
+  library(extrafont)
 
@@
   library(ggpmisc)
+  library(ggtern)
   library(RColorBrewer) 
@@
 
+  library(tidytext)    # Tidy text mining
   library(stringdist)  # String distances
@@
 theme_set(
-  theme_bw(base_family = "Roboto", base_size = 10) +
+  theme_bw(base_family = "Roboto", base_size = 8) +
     theme(
-      plot.title = element_text(size = 12,
+      plot.title = element_text(face = "bold", size = 14,
                                 margin = margin(0, 0, 4, 0, "pt")),
@@
       plot.caption = element_text(size = 6, hjust = 0),
-      axis.title = element_text(size = 8),
+      axis.title = element_text(size = 10),
       panel.border = element_blank()
@@
 )
-col <- brewer.pal(8,"Dark2")
+
+rm(list=ls())
+col <- brewer.pal(7,"Dark2")
+load("data/presentation-data.Rda")
 ```
@@
 
-3. **Literature Review**
-
 4. **First Results**
 
-5. **Conclusion**
+5. **Whats next**
 
 # Introduction
+
 ## Online News
 
-<div style="position:relative; width:640px; height:480px; margin:0 auto;">
+<div style="position:relative; width:900px; height:750px; margin:0 auto;">
   <img class="fragment" src="img/screenshot-spon.png" style="position:absolute;top:0;left:0;" />
@@
 
-<img class="fragment" src="img/onlinenews-2.png" width="900"/>
+<div style="position:relative; width:800px; height:450px; margin:0 auto;">
+  <img class="fragment" src="img/onlinenews-1.png" style="position:absolute;width:800px;top:0;left:0;" />
+  <img class="fragment" src="img/onlinenews-2.png" 
+  style="position:absolute;width:800px;top:0;left:0;" />
+</div>
 
----------------------------
-
-### Research Question: 
-Does the business model have an effect on the editorial content?
-
-### Methodology: 
+- **Does the business model have an effect on the editorial content?**
+- **Methodology:**
   1. Estimate a Structural Topic Model
@@
 ## Data
-Online news articles about domestic politics from 01.06.2017 - 22.11.2017
+
+Online news articles about domestic politics from 01.06.2017 - 01.12.2017
 
@@
 ## Data Structure
+
 ```{r message=FALSE, warning=FALSE, include=FALSE}
-load("data/presentation-data.Rda")
 table <- inspect(dtm[1:5,1:10])
@@
 
-- Documents (articles) are stored on a "Document-Term-Matrix"
--
 ```{r echo=FALSE}
-htmlTable::htmlTable(table)
+kable(table)
 ```
 
+- Documents (articles) are stored on a "Document-Term-Matrix"
+
 - Documents are seen as "bag of words"
+
 - Each article has metadata: publisher (news platform) and the day it was published.
@@
 
-<img src="img/lda-blei.png" width="750"/>
-
+<img src="img/lda-blei.png" width="900"/>
 <small>Credits: Blei (2012)</small>
 
-* Model the generation of documents with latent topic structure
-    * a topic ~ a distribution over words
-    * a document ~ a mixture over topics
-    * a word ~ a sample drawn from one topic
-
 <aside class="notes">
+Model the generation of documents with latent topic structure
+(1)a topic ~ a distribution over words
+(2)a document ~ a mixture over topics
+(3)a word ~ a sample drawn from one topic
 Mixed memberhip model: Population of topics stays the same, but distrubution over topics changes for each document.
@@
 
+<img src="img/lda-plate-2.png" width="600">
+
 * Nodes are random variables; arrows indicate dependence
-
 * Plates indicate replicated variables:
@@
 
-----------------------------
-<img src="img/lda-plate-2.png" width="600">
-----------------------------
-
 <aside class="notes">
@@
 
-## Generative Process I
-* Generative Process for the $n^{th}$ word-position in document $d$: 
-    1. $K$: choose the number of topics;
-    2. $\theta_d$: for each document $d$, choose a distribution over topics;
-    3. $z_{d,n}$: according to $\theta_d$, assign a topic for the $n^{th}$ word;
-    4. $w_{d,n}$: choose a term from that topic according to $\beta_k$
-    5. $N$: repead this process for all $n$ word-positions in the document.
-    6. $D$: conduct this process for all $d$ documents in the corpus
+## LDA - joint distribution
 
-## R Markdown
+$$
+\begin{aligned}
+p(\beta_{1:K},\theta_{1:D},z_{1:D}, w_{1:D}) \propto
+\end{aligned}
+$$
 
-test 1
+$$
+\begin{aligned}
+\displaystyle \prod_{i=1}^{K}p(\beta_i)\displaystyle \prod_{d=1}^{D}p(\theta_d)(\prod_{n=1}^Np(z_{d,n,}|\theta_d)p(w_{d,n}|\beta_{1:K},z_{d,n}))
+\end{aligned}
+$$
 
-***
+## Generative process
 
-test 2
+```{r eval=FALSE, include=FALSE}
+set.seed(456)
 
-## Generative Process II
+####### 1 
+ggsave(plot={
+  ggtern(data.frame(rdirichlet(200, c(1,1,1)),
+                     alpha = "a1=a2=a3=1"), 
+         aes(x = X1, y = X2, z = X3)) + 
+  geom_density_tern() +
+  geom_point(size=0.5) +
+    labs(title="a1=a2=a3=1")+
+  ggtern::theme_bvbg() 
+},
+file="img/dirichlet1.png",
+dpi=600,
+width = 4,
+height = 4
+)
 
-$p(\beta_{1:K},\theta_{1:D},z_{1:D}, w_{1:D})=\displaystyle \prod_{i=1}^{K}p(\beta_i)\displaystyle \prod_{d=1}^{D}p(\theta_d)(\prod_{n=1}^Np(z_{d,n,}|\theta_d)p(w_{d,n}|\beta_{1:K},z_{d,n}))$
+######## 2
+ggsave(plot={
+  ggtern(data.frame(rdirichlet(200, c(10,10,10)),
+                     alpha = "a1=a2=a3=10"),
+         aes(x = X1, y = X2, z = X3)) + 
+  geom_density_tern() +
+  geom_point(size=0.5) +
+    labs(title="a1=a2=a3=10")+
+  ggtern::theme_bvbg() 
+},
+file="img/dirichlet2.png",
+dpi=600,
+width = 4,
+height = 4
+)
 
-```{r}
-draws <- rdirichlet(200, c(1,1,1) )
-bivt.contour(draws)
+########## 3
+ggsave(plot={
+  ggtern(data.frame(rdirichlet(200, c(1,10,10)),
+                     alpha = "a1=1, a2=a3=10"), 
+         aes(x = X1, y = X2, z = X3)) + 
+  geom_density_tern() +
+  geom_point(size=0.5) +
+    labs(title="a1=1, a2=a3=10")+
+  ggtern::theme_bvbg() 
+},
+file="img/dirichlet3.png",
+dpi=600,
+width = 4,
+height = 4
+)
+
+########### 4
+ggsave(plot={
+  ggtern(data.frame(rdirichlet(200, c(1,1,10)),
+                     alpha = "a1=a2=1, a3=10"), 
+         aes(x = X1, y = X2, z = X3)) + 
+  geom_density_tern() +
+  geom_point(size=0.5) +
+    labs(title="a1=a2=1, a3=10")+
+  ggtern::theme_bvbg() 
+},
+file="img/dirichlet4.png",
+dpi=600,
+width = 4,
+height = 4
+)
 ```
+
+* **$K$**: choose the number of topics
+
+    * $K=3$
+
+* **$\theta_d$**: for each document $d$, choose a distribution over topics;
+
+    * $\theta_d$ ~ Dirichlet($\alpha$)
+
+  <div style="position:relative; width:300px; height:300px; margin:0 auto;">
+  <img class="fragment" src="img/dirichlet1.png" style="position:absolute;top:0;left:0;" />
+  <img class="fragment" src="img/dirichlet2.png" style="position:absolute;top:0;left:0;" />
+  <img class="fragment" src="img/dirichlet3.png" style="position:absolute;top:0;left:0;" />
+  <img class="fragment" src="img/dirichlet4.png" style="position:absolute;top:0;left:0;" />
+  </div>
+
+* **$z_{d,n}|\theta_d$**: according to $\theta_d$, assign a topic $z_{d,n}$ for the $n^{th}$ word;
+
+      * $K=Topic 1$
+
+<aside class="notes">
+The higher value of $\alpha_i$, the greater “weight” of $X_i$ and the greater amount of the total “mass” is assigned to it (recall that in total it must be $x_1+⋯+x_k=1$).
+If all $\alpha_i$ are equal, the distribution is symmetric.
+If $\alpha_i<1$ it can be thought as anti-weight that pushes away $x_i$ toward extremes, while when it is high, it attracts $x_i$ toward some central value (central in the sense that all points are concentrated around it, not in the sense that it is symmetrically central).
+</aside>
+
+## Generative process (contd.)
+
+* **$w_{d,n}|z_{d,n},\beta,\theta$**: choose a term from that topic according to $\beta_k$
+
+    * $\beta_k$ ~ Dirichlet($\eta$)
+
+```{r eval=FALSE, include=FALSE}
+# Word-topic probabilities
+stmOut %>% tidy("beta") %>% filter(!is.na(topic)) -> posts.wtp
+# Document-topic probabilities
+stmOut %>% tidy("gamma") -> posts.dtp
+
+set.seed(35)
+# Label Topics
+label <- labelTopics(stmOut, n=40)
+terms <- as.data.frame(label$prob, stringsAsFactors = F)
+
+prob <- data.frame(words = t(terms[16,]),
+                   value = runif(40,min=0,max=1))
+
+ggsave(plot={
+  ggplot(prob, aes(X16,value, label=X16),
+       fill = "transparent") +
+  geom_text_repel(family = "xkcd",
+                  size = 4, seed=5) +
+  theme_xkcd() +
+  theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank(),
+        axis.title.y =element_blank(),
+        axis.text.y =element_blank(),
+        axis.ticks.y=element_blank()
+        )
+},
+file = "img/words1.png",
+width = 5,
+height = 4,
+dpi = 600
+)
+
+ggsave(plot={
+  ggplot(prob[-16,], aes(X16,value, label=X16),
+       fill = "transparent") +
+  geom_text_repel(family = "xkcd",
+                  size = 4, seed=5) +
+  geom_text_repel(data=prob[16,], color="red", 
+            family = "xkcd", size = 5) +
+  theme_xkcd() +
+  theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank(),
+        axis.title.y =element_blank(),
+        axis.text.y =element_blank(),
+        axis.ticks.y=element_blank()
+        )
+},
+file = "img/words2.png",
+width = 5,
+height = 4,
+dpi = 600
+)
+```
+
+<div style="position:relative; width:500px; height:400px; margin:0 auto;">
+  <img class="fragment" src="img/words1.png" style="position:absolute;top:0;left:0;" />
+  <img class="fragment" src="img/words2.png" style="position:absolute;top:0;left:0;" />
+</div>
+
+* **$N$**: repead this process for all $n$ word-positions in the document.
+
+* **$D$**: conduct this process for all $d$ documents in the corpus
+
+## Research Process
+
+<img class="fragment" src="img/research_strategy.png" width="1000"/>
+
+<aside class="notes">
+(1)We have knowledge about the world and want to answer a specific question: We know that newspapers are based on different business models.
+does that have an effect on the topics discussed in the newspaper?
+(2)We make assumptions and bring them together with our data to uncover patterns.
+(3)We use these patterns (posterior distributions) to predict a variable
+</aside>
+
+## Strucutral Topic Model (Roberts et. al. (2016))
+
+- Including covariates into a topic model:
+
+<aside class="notes">
+(1)to estimate the impact of document-level covariates on topic content and prevalence as part of the topic model itself.
+(2)We want to use estimates of $\theta_d$ as the dependent variable in an regression on covariates to test whether different types of documents have different content.
+(2)This is contradictory because documents are assumed to be generated by the same statistical process.
+</aside>
+
+  1. **Topic Prevalence**: Attributes that affect the likelihood of discussing topic $k$
+
+        News platform & the month the article was published.
+
+  2. **Topic Content**: Attributes that affect the likelihood of including term $w$ overall, and of including it within topic $k$
+
+        Not yet included.
+
+<div style="position:relative; width:850px; height:490px; margin:0 auto;">
+  <img class="fragment" src="img/stm1.png" style="position:absolute;top:0;left:0;" />
+  <img class="fragment" src="img/stm2.png" style="position:absolute;top:0;left:0;" />
+  <img class="fragment" src="img/stm3.png" style="position:absolute;top:0;left:0;" />
+  <img class="fragment" src="img/stm4.png" style="position:absolute;top:0;left:0;" />
+</div>
+
+<aside class="notes">
+(3)Diagram:
+$X$= Matrix of topic prevalence covariates, dimension: DxP
+$Y$= Matrix of topical content covariates, dimension: DxA
+$m$= marginal log-frequency of term $v$ (estimated from total counts)
+
+- The process for generating individual words is the same as for plain LDA conditional on the $\beta_k$ and $\theta_d$ terms.
+(3.1)Diagram: can be divided into three components
+(a)topic prevalence model: which controls how words are allocated to topics as a function of covariates
+(b)topical contnet model: which controls the frequency of terms in each topic as a function of covariates
+(c)core language (or observation) model, which combines these two sources of variation to produce the actual words in each document.
+</aside>
+
+## STM Priors
+
+<div style="position:relative; width:600px; height:350px; margin:0 auto;">
+  <img class="fragment" src="img/stm5.png" style="position:absolute;top:0;left:0;" />
+</div>
 
@@
 
-Posterior probability: $P(A|B)=\frac{P(B|A)P(A)}{P(B)}$
+Posterior probability:
 
-$p(\theta_{1:D},z_{1:D},\beta_{1:K}|w_{1:D}) = \frac{p(\theta_{1:D},\beta_{1:K},z_{1:D})(w_{1:D})}{p(w_{1:D})}$
+$$
+\begin{aligned}
+p(\eta,z,\kappa,\gamma,\Sigma|w,X,Y) \propto
+\displaystyle \prod_{d=1}^{D}(\eta_d|X_d\gamma,\Sigma) (\displaystyle \prod_{n=1}^{D}(z_{n,d}|\theta_d)*(w_n|\beta_{d,k=z_{d,n}}))) * \displaystyle \prod p(\kappa)\displaystyle \prod p(\Gamma)
+\end{aligned}
+$$
 
-  * **numerator**: joint distribution of all random variables (can be easily computed for any setting of hidden variables.)
-  * **denominator**: marginal probability of the observations (probability of seeing the observed corpus under any topic model.)
-
-- Then use posterior expectations to perform the task at hand: information retrieval, document similarity, exploration, and others.
+* The number of possible topic structures is exponentially large --> sum is intractable to compute.
+* Instead of obtaining a closed-form solution for the posterior distribution, we must approximate it.
 
@@
 A central research goal of modern probabilistic modeling is to develop efficient methods for approximating it.
-Topic modeling algorithms—like the algorithms used to create Figures 1 and 3—are often adaptations of general-purpose methods for approximating the posterior distribution.
+Topic modeling algorithms—like the algorithms are often adaptations of general-purpose methods for approximating the posterior distribution.
 First uncover the structure (calculate th posterior) - use the discovered distributions to perform task
@@
 
-## Research Process
+## Approximate Posterior
 
-<img class="fragment" src="img/research_strategy.png" width="1000"/>
+Central research goal of probabilistic modeling: develop efficient methods for approximating posterior.
+
+* Mean field variational methods (Blei et al., 2001, 2003)
+* Expectation propagation (Minka and Lafferty, 2002)
+* Collapsed Gibbs sampling (Griffiths and Steyvers, 2002)
+* Distributed samplung (Newsman et al., 2008; Ahmed et al., 2012)
+* Stochastic inference (Hoffman et al., 2010, 2013; Mimno et al., 2012)
+* Factorization inference (Arora et al., 2012; Anandkumar et al., 2012)
+* **Variational EM algorithm** (Wang and Blei 2013; Roberts et. al. (2016)
+* ...
 
 <aside class="notes">
-  1.
-We have knowledge about the world and want to answer a specific question: We know that newspapers are based on different business models.
-does that have an effect on the topics discussed in the newspaper?
-  2. We make assumptions and bring them together with our data to uncover patterns.
-  3. We use these patterns (posterior distributions) to predict a variable
+the answers the estimation procedure comes up with may depend on starting values of the parameters (e.g., the distribution over words for a particular topic).
 </aside>
 
-## Strucutral Topic Model
-- We want to use estimates of $\theta_d$ as the dependent variable in an regression on covariates to test whether different types of documents have different content.
+## Model Selection
 
-- This is contradictory because documents are assumed to be generated by the same statistical process.
+**Prior Specification:**
 
-- The structural topic model (STM) of Roberts et.
-al.
-(2016) explicitly introduces covariates into a topic model, and allows one to estimate the impact of document-level covariates on topic content and prevalence as part of the topic model itself.
+$\gamma_{p,k}$ ~ Normal$(0,\sigma^2_k)$
 
-## Topic Prevalence vs. Content
-- The process for generating individual words is the same as for plain LDA conditional on the $\beta_k$ and $\pi_d$ terms.
-
-- However both objects can depend on potentially different sets of document- level covariates. Each document has:
-    1. **Topic Prevalence**: Attributes that affect the likelihood of discussing topic $k$
-    2. **Topic Content**: Attributes that affect the likelihood of including term $v$ overall, and of including it within topic $k$
-
-- The generation of the $\beta_k$ and $\pi_k$ terms is via multinomial logistic regression, which breaks local conjugacy.
-
-## Model Selection
-- There are three parameters we need to make assumptions about: number of topics $K$ and priors $\alpha, \eta$:
-  - Priors don’t receive too much attention in literature: 
-    - Griffiths & Steyvers (2002) recommend $\eta = 200/V$ and $\alpha = 50/K$. 
-    - Smaller values will tend to generate more concentrated distributions. (See also Wallach et.al. (2009)).
-  - $K$ is clearer. Two potential goals:
-    1. Predict text well. Statistical criteria to select $K$.
-    2. Interpretability. General versus specific.
-
-## Approximate Posterior
-- Mean field variational methods (Blei et al., 2001, 2003)
-- Expectation propagation (Minka and Lafferty, 2002)
-- Collapsed Gibbs sampling (Griffiths and Steyvers, 2002)
-- Distributed samplung (Newsman et al., 2008; Ahmed et al., 2012)
-- Stochastic inference (Hoffman et al., 2010, 2013; Mimno et al., 2012)
-- Factorization inference (Arora et al., 2012; Anandkumar et al., 2012)
-- Amortized inference (Srivastava and Sutton, 2019)
-- ...
+$\sigma^2_k$ ~ Inverse-Gamma$(a,b)$
 
 <aside class="notes">
-  - We cannot obtain exact solutions for our posterior
-  - Instead of obtaining a closed-form solution for the posterior distribution, we must approximate it.
+The prior specification for the topic prevalence parameters is a zero mena Haussian distribution with shared variance parameter.
+$p$ indexes the covariates, $k$ indexes the topics and $a,b$ are fixed hyperparameters
 </aside>
 
-## Predicitve Distributions
+**Topic Selection:**
 
-$\beta_{k,v} = \frac{m_{k,v}+\eta}{\sum_{v=1}^V(m_{k,v}+\eta)}$
+$K=28$
 
-$\theta_{k,v} = \frac{n_{d,k}+\alpha}{\sum_{k=1}^K(n_{d,k}+\alpha)}$
-
-## Formalizing Interpretability
-- Chang et. al. (2009) propose an objective way of determining whether topics are indeed interpretable.
-- Two tests:
-  1. *Word intrusion*:
-      - Form set of words consisting of top five words from topic k + word with low probability in topic k. 
-      - Ask subjects to identify inserted word.
-  2. *Topic intrusion*: 
-      - Show subjects a snippet of a document + top three topics associated to it + randomly drawn other topic. 
-      - Ask to identify inserted topic.
+<aside class="notes">
+(2)Two potential goals:
+(2a)Predict text well. Statistical criteria to select $K$.
+(2b)Interpretability. General versus specific.
+</aside>
 
@@
 
-```{r Extract wtp and dtp, include=FALSE}
+```{r include=FALSE}
 # Word-topic probabilities
@@
 rm(prob, frex, lift, score)
+
+top_topics <-
+  posts.dtp %>% 
+  group_by(document) %>%
+  mutate(therank = rank(-gamma, ties.method = "random")) %>%
+  filter(therank %in% 1) %>%
+  select(- therank)
+
+# Add Topic to origian DF
+btw %>%
+  mutate(document = articleID) %>%
+  inner_join(.,top_topics, by="document") %>%
+  ## Combine with Topic label
+  left_join(., topicLabel %>%
+              select(topic_name, topic) %>%
+              mutate(topic = as.numeric(topic)), by="topic") -> btw
+
+topic_sample <- c(1,5,6,7,9,16,19,24)
 ```
@@
 
-<img src="img/topic_proportion.png" width="600">
+```{r echo=FALSE, fig.height=6.5}
+plot(stmOut, type = "summary", xlim = c(0,.16), n = 5, 
+     custom.labels = topicLabel$topic_name, 
+     family = "Roboto", main = "", text.cex = 1)
+```
+
+## Timeline
+```{r Data for topic trends chart, message=FALSE, warning=FALSE, include=FALSE}
+set.seed(7292)
+btw %>% 
+  filter(gamma>=0.5) %>%
+  mutate(date = as.POSIXct(date),
+         allocation = 1) %>%
+  mutate(post_period = 
+           date %>% with_tz("Europe/Paris") %>% 
+           floor_date("week")) %>%
+  # Summarise into tidy dataframe
+  group_by(post_period, topic, topic_name) %>% dplyr::summarise(articles = sum(allocation)) %>%
+  # Mark peaks 
+  group_by(topic_name) %>% dplyr::mutate(peak = ifelse(articles==max(articles),1,0)) -> chart_topic_trends.dt
+```
+
+```{r echo=FALSE, fig.width=10, message=FALSE, warning=FALSE}
+ggplot(chart_topic_trends.dt, 
+       aes(post_period, articles, color=topic_name)) +
+  geom_line() +
+  scale_color_manual(
+            values = rainbow(28) %>% 
+              adjustcolor(red.f = 0.6, green.f = 0.6, blue.f = 0.6)
+          ) +
+  geom_text_repel(data=subset(chart_topic_trends.dt,peak==1 & topic %in% topic_sample),
+            aes(post_period,articles,label=paste(topic,topic_name,sep=":")),
+            size=4) +
+      geom_vline(aes(xintercept=as.POSIXct("2017-09-23")),
+                 linetype = 2, color="grey20") +
+      geom_vline(aes(xintercept=as.POSIXct("2017-11-19")),
+                 linetype = 2, color="grey20") +
+  ylim(c(0,200)) +
+  labs(y="Number of Articles") +
+    theme(
+      legend.position   = "none",
+      plot.background   = element_rect("#fafafa", "#fafafa"),
+      plot.title        = element_text(size = 18),
+      plot.subtitle     = element_text(size = 8),
+      plot.caption      = element_text(size = 7),
+      panel.grid        = element_blank(),
+      panel.background  = element_rect("#fafafa"),
+      axis.title.x      = element_blank(),
+      axis.text.y       = element_text(size = 8)
+    )
+```
 
 ## Sample Articles
+
+```{r Document classification, echo=FALSE}
+set.seed(9272)
+
+posts_classification.sdt <-
+  btw %>%
+  filter(topic %in% topic_sample) %>%
+  mutate(topic_title = 
+           paste0("Topic ", formatC(topic, flag = "0", width = 2), 
+                  " - ", topic_name)) %>%
+  group_by(topic_name) %>% 
+  top_n(100, gamma) %>%
+  sample_n(3) %>%
+  arrange(topic)
+
+kable(posts_classification.sdt[1:12,c("topic_title","title")])
+```
+
+## Sample Articles (contd)
+
+```{r echo=FALSE}
+kable(posts_classification.sdt[13:24,c("topic_title","title")])
+```
+
+## Estimate Effect of Covariates
+
+Estimate the conditional expectation of topic prevalence for given document characteristics (lm on compositional data):
+
+$$
+\theta_d=\alpha+\beta_1 x_{site}+\beta_2x_{month}+\epsilon
+$$
+
+<div style="position:relative; width:500px; height:500px; margin:0 auto;">
+  <img class="fragment" src="img/estimate_effect1.png" style="position:absolute;top:0;left:0;" />
+  <img class="fragment" src="img/estimate_effect5.png" style="position:absolute;top:0;left:0;" />
+  <img class="fragment" src="img/estimate_effect6.png" style="position:absolute;top:0;left:0;" />
+  <img class="fragment" src="img/estimate_effect7.png" style="position:absolute;top:0;left:0;" />
+  <img class="fragment" src="img/estimate_effect9.png" style="position:absolute;top:0;left:0;" />
+  <img class="fragment" src="img/estimate_effect16.png" style="position:absolute;top:0;left:0;" />
+  <img class="fragment" src="img/estimate_effect19.png" style="position:absolute;top:0;left:0;" />
+  <img class="fragment" src="img/estimate_effect24.png" style="position:absolute;top:0;left:0;" />
+</div>
+
+<aside class="notes">
+The stm-package provides a function that uses the method of composition to incorporates uncertainty in the dependent variable, drawing a set of topic proportions from the variational posterior repeated times and compute the coefficients as the average over all results.
+</aside>
+
+# Whats next?
+
+## Whats next?
+
+1. **Estimate model, including the effect of covariates on topical content** How are topics discused within different newswires?
+
+2. **Relationship between topics** How topics are correlated differently for different newswires, indicating how topics are connected and framed differently in each newswire.

### 2017-12-12 phd_slides/phd-workshop.Rmd
final

@@
 ---
-title: "Whats inside the news?"
+title: "What is reported in the news?"
 author: Franziska Löw
-date: December 16, 2017
+date: December 12, 2017
 output: 
@@
 
-1. **Introduction**
+###1. Introduction
 
-2. **Methodology**
+###2. Data
 
-4. **First Results**
+###3. Methodology
 
-5. **Whats next**
+###4. First Results
+
+###5. Whats next?
 
@@
 - **Does the business model have an effect on the editorial content?**
-- **Methodology:**
-  1. Estimate a Structural Topic Model
-  2. Use posterior distribution to estimate the effect of document metadata.
+
+# Data
 
@@
 Online news articles about domestic politics from 01.06.2017 - 01.12.2017
+
+```{r echo=FALSE, fig.height=6, fig.width=8, message=FALSE, warning=FALSE}
+btw %>%
+  group_by(date) %>%
+  summarise(obs = n()) %>%
+  ggplot(aes(date, obs)) +
+  geom_line(color="blue") +
+  geom_vline(aes(xintercept=as.Date("2017-09-24")),
+             linetype = 2, color="grey40") +
+  geom_vline(aes(xintercept=as.Date("2017-11-20")),
+                 linetype = 2, color="grey40") +
+  labs(x="", y="Count") +
+  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
+  theme(
+      #legend.position   = "none",
+      plot.background   = element_rect("#fafafa", "#fafafa"),
+      plot.title        = element_text(size = 18),
+      plot.subtitle     = element_text(size = 8),
+      plot.caption      = element_text(size = 7),
+      #panel.grid        = element_blank(),
+      panel.background  = element_rect("#fafafa"),
+      axis.title.x      = element_blank(),
+      axis.text.y       = element_text(size = 8)
+    )
+```
 
@@
 - Each article has metadata: publisher (news platform) and the day it was published.
+
+## Research Process
+
+<img class="fragment" src="img/research_strategy.png" width="1000"/>
+
+<aside class="notes">
+(1)We have knowledge about the world and want to answer a specific question: We know that newspapers are based on different business models.
+does that have an effect on the topics discussed in the newspaper?
+(2)We make assumptions and bring them together with our data to uncover patterns.
+(3)We use these patterns (posterior distributions) to predict a variable
+</aside>
 
@@
 
-* Nodes are random variables; arrows indicate dependence
-* Plates indicate replicated variables:
   * $N =$ collection of words within a document.
   * $D =$ collection of documents within a corpus.
-
-* Shaded nodes are observed; unshaded nodes are hidden
   * observed: word in a document $w_{d,n}$
@@
 
-## LDA - joint distribution
-
 $$
 \begin{aligned}
-p(\beta_{1:K},\theta_{1:D},z_{1:D}, w_{1:D}) \propto
-\end{aligned}
-$$
-
-$$
-\begin{aligned}
-\displaystyle \prod_{i=1}^{K}p(\beta_i)\displaystyle \prod_{d=1}^{D}p(\theta_d)(\prod_{n=1}^Np(z_{d,n,}|\theta_d)p(w_{d,n}|\beta_{1:K},z_{d,n}))
+p(\beta,\theta,z|w) \propto
+\displaystyle \prod_{i=1}^{K}p(\beta_i)\displaystyle \prod_{d=1}^{D}p(\theta_d)(\prod_{n=1}^Np(z_{d,n,}|\theta_d)p(w_{d,n}|\beta_{d,k},z_{d,n}))
 \end{aligned}
@@
 
-* **$K$**: choose the number of topics
+* $K$: choose the number of topics
 
@@
 
-* **$\theta_d$**: for each document $d$, choose a distribution over topics;
+* $\theta_d$: for each document $d$, choose a distribution over topics;
 
@@
 
-* **$z_{d,n}|\theta_d$**: according to $\theta_d$, assign a topic $z_{d,n}$ for the $n^{th}$ word;
+* $z_{d,n}|\theta_d$: according to $\theta_d$, assign a topic $z_{d,n}$ for the $n^{th}$ word;
 
@@
 
-* **$w_{d,n}|z_{d,n},\beta,\theta$**: choose a term from that topic according to $\beta_k$
+* $w_{d,n}|z_{d,n},\beta,\theta$: choose a term from that topic according to $\beta_k$
 
@@
 
-* **$N$**: repead this process for all $n$ word-positions in the document.
+* $N$: repead this process for all $n$ word-positions in the document.
 
-* **$D$**: conduct this process for all $d$ documents in the corpus
+* $D$: conduct this process for all $d$ documents in the corpus
 
@@
 
-## STM Priors
-
-<div style="position:relative; width:600px; height:350px; margin:0 auto;">
-  <img class="fragment" src="img/stm5.png" style="position:absolute;top:0;left:0;" />
-</div>
-
 ## Bayesian inference
@@
 $$
-\begin{aligned}
-p(\eta,z,\kappa,\gamma,\Sigma|w,X,Y) \propto
-\displaystyle \prod_{d=1}^{D}(\eta_d|X_d\gamma,\Sigma) (\displaystyle \prod_{n=1}^{D}(z_{n,d}|\theta_d)*(w_n|\beta_{d,k=z_{d,n}}))) * \displaystyle \prod p(\kappa)\displaystyle \prod p(\Gamma)
-\end{aligned}
+p(\eta,z,\kappa,\gamma,\Sigma|w,X,Y)\propto (\displaystyle \prod^D_{d=1}(\eta_d|X_d,\gamma,\Sigma)( \prod^N_{n=1}(z_{n,d}|\theta_d)(w_n|\beta_{d,k=z_{d,n}}))) \prod p(\kappa)\prod p(\Gamma)
 $$
 
-* The number of possible topic structures is exponentially large --> sum is intractable to compute.
+* The number of possible topic structures is exponentially large
+    -> sum is intractable to compute.
 * Instead of obtaining a closed-form solution for the posterior distribution, we must approximate it.
@@
 * Factorization inference (Arora et al., 2012; Anandkumar et al., 2012)
-* **Variational EM algorithm** (Wang and Blei 2013; Roberts et. al. (2016)
+* **Variational EM algorithm** (Wang and Blei 2013; Roberts et. al. (2016))
 * ...
@@
 the answers the estimation procedure comes up with may depend on starting values of the parameters (e.g., the distribution over words for a particular topic).
-</aside>
-
-## Model Selection
-
-**Prior Specification:**
-
-$\gamma_{p,k}$ ~ Normal$(0,\sigma^2_k)$
-
-$\sigma^2_k$ ~ Inverse-Gamma$(a,b)$
-
-<aside class="notes">
-The prior specification for the topic prevalence parameters is a zero mena Haussian distribution with shared variance parameter.
-$p$ indexes the covariates, $k$ indexes the topics and $a,b$ are fixed hyperparameters
-</aside>
-
-**Topic Selection:**
-
-$K=28$
-
-<aside class="notes">
-(2)Two potential goals:
-(2a)Predict text well. Statistical criteria to select $K$.
-(2b)Interpretability. General versus specific.
 </aside>
@@
 ```{r echo=FALSE, fig.height=6.5}
-plot(stmOut, type = "summary", xlim = c(0,.16), n = 5, 
+plot(stmOut, type = "summary", xlim = c(0,.18), n = 5, 
      custom.labels = topicLabel$topic_name, 
@@
 
-2. **Relationship between topics** How topics are correlated differently for different newswires, indicating how topics are connected and framed differently in each newswire.
+2. **Sentiment analysis**
+
+3. **Relationship between topics** How topics are correlated differently for different newswires, indicating how topics are connected and framed differently in each newswire.
+
+# Thank you! Questions?

### 2017-12-14 paper/R/02_cleanAndCombine.Rmd
new sample

@@
 nov_22 <- read_csv("../data/eventbride/eventbride_nov_22.csv")
-nov_30 <- read_csv("../data/eventbride/eventbride_nov_30.csv")
+dec_16 <- read_csv("../data/eventbride/eventbride_dec_16.csv")
 ```
@@
 ```{r}
-btw1 <- bind_rows(list(okt,nov_03,nov_22,nov_30)) %>%
+df_full <- bind_rows(list(okt,nov_03,nov_22,dec_16)) %>%
   mutate(text = body,
@@
 
-btw1 <- bind_rows(df %>%
+df_full <- bind_rows(df %>%
                    mutate(date = as.Date(date)) %>%
                    select(date,title,text,site,url),
-                 btw1)
+                 df_full)
 ```
@@
 ```{r}
-keeps <- c("welt.de","spiegel.de","stern.de","focus.de","zeit.de","bild.de","tagesschau.de")
+keeps <- c("spiegel.de","focus.de","zeit.de","bild.de",
+           "tagesschau.de","deutschlandfunk.de")
 
-btw1 %>%
+df_full %>%
   mutate(title_text = paste(title, text, sep=" ")) %>%
-  filter(site %in% keeps) -> btw
+  filter(site %in% keeps) %>%
+  filter(date>=as.Date("2017-09-14")) -> btw
 ```
-
 ## select politic section
@@
 pat4 <- "\\w\\.de/politik/bundestagswahl"
-pat5 <- "tagesschau\\.de/inland"
+pat5 <- paste("cdu","csu","union","spd","fdp","afd","linkspartei","gruenen",
+              "merkel","schulz","nahles","gabriel","oezdemir","petry","wagenknecht","lindner",
+              "gauland","weidel","steinmeier","seehofer","maiziere","dreyer","althusmann",
+              "buergermeister", "fraktion","jamaika","groko","koalition","sondierung","btw","wahl",
+              "bundestag","bundewehr","bundesregierung","landtag","minister","kanzler",
+              "fluechtling","raf", "glyphosat","rundfunk",  sep="|")
 
 btw %>%
-  mutate(politics = ifelse(grepl(paste(pat1,pat2,pat3,pat4,pat5,
-                     sep="|"), url, perl = TRUE),1,0)) -> df_full
+  mutate(politics = ifelse(grepl(paste(pat1,pat2,pat3,pat4,
+                      sep="|"), url, perl = TRUE),1,0)) -> btw1
+
+btw1$politics <- ifelse(btw1$site=="deutschlandfunk.de"&grepl(pat5,btw1$url),1,btw1$politics)
+btw1$politics <- ifelse(btw1$site=="tagesschau.de"&grepl(pat5,btw1$url),1,btw1$politics)
 ```
@@
 ```{r}
-df_full %>%
-  filter(politics == 1) %>%
-  distinct(url, .keep_all = T) -> btw
+btw <- btw1 %>% filter(politics==1) %>%
+  filter(date>=as.Date("2017-09-14"))
+```
+
+```{r}
+p <- btw %>%
+  group_by(date, site) %>%
+  dplyr::summarise(obs = n()) %>%
+  ggplot(aes(date, obs, color = factor(site))) +
+  geom_line() +
+  #geom_vline(aes(xintercept=as.Date("2017-09-24")),
+  #           linetype = 2, color="grey40") +
+  #geom_vline(aes(xintercept=as.Date("2017-11-20")),
+  #               linetype = 2, color="grey40") +
+  #scale_color_manual(values = col) +
+  labs(x="", y="Count",color="") +
+  scale_x_date(breaks = date_breaks("1 day"), labels=date_format("%d.%m", tz="CET"))
+
+plotly::ggplotly(p)
 ```
@@
 btw %>%
-  filter(text_length > 200) %>%
+  filter(text_length > 120) %>%
+  arrange(desc(text_length)) %>%
+  distinct(url, .keep_all = TRUE) %>%
+
   # remove articles that contain daily overviews
-  filter(!grepl("News des Tages", title_text)) %>%
   filter(!grepl("Nachrichten am Morgen", title)) %>%
   filter(!startsWith(title,"News")) %>%
+
   # remove articles that only contain video 
   filter(!grepl("Video einbetten Nutzungsbedingungen Embedding Tagesschau", title_text)) %>%
+
   # remove english text
@@
   filter(!grepl("german",url)) %>%
+
   # remove text that mostly contain user comments
-  filter(!grepl("kommentar", title, ignore.case = TRUE)) %>%
   filter(!grepl("ticker", title, ignore.case = TRUE)) %>%
@@
   filter(!startsWith(text,"1.")) -> btw
-```
-
-```{r}
-btw %>%
-  filter(grepl("faktenfinder", title_text)) %>%
-  select(url, title_text)
 ```
@@
 ```{r}
-pat <- "Eine Kolumne von \\w{1,} \\w{1,}"
+pat <- "\\w{1,10}[^:]"
 btw %>%
@@
 ```{r}
-as.data.frame(str_match(btw$title_text, pat)) ->test
+btw_test <- btw
+
+as.data.frame(str_match(btw_test$title_text , pat)) ->test
+
 test %>%
@@
 
+  # Deutschlandfunk
+  x = gsub("Äußerungen unserer Gesprächspartner[^.]*", "", x, perl = TRUE)
+  x = gsub("im Gespräch mit \\w{1,}", "", x, ignore.case = TRUE)
+  x = gsub("Heinlein", "", x, ignore.case = TRUE)
+  x = gsub("Barenberg", "", x, ignore.case = TRUE)
+  x = gsub("Büüsker", "", x, ignore.case = TRUE)
+  x = gsub("Dobovisek", "", x, ignore.case = TRUE)
+  x = gsub("Schmidt-Mattern", "", x, ignore.case = TRUE)
+  x = gsub("Zagatta", "", x, ignore.case = TRUE)
+  x = gsub("Armbrüster", "", x, ignore.case = TRUE)
+  x = gsub("Münchenberg", "", x, ignore.case = TRUE)
+  x = gsub("Heckmann", "", x, ignore.case = TRUE)
+
   return(x)
@@
 ```{r}
-btw$text_cleaned<- removeWords(btw$text_cleaned, stopwords("german"))
+german_stopwords_full <- read.table("dict/german_stopwords_full.txt")
+
+btw$text_cleaned<- removeWords(btw$text_cleaned, german_stopwords_full$V1)
 ```
@@
 ```{r}
-mystopwords <- c("focus","online","spiegel", "stern", "de", "bild","bildplus", "zeit", "ersten", "tagesschau", "zeitmagazin","seitenanfang","ja","mal","heute","ich","sie","passwort","kommentar","wurde","ihr","der","im","artikel","mehr","ihren","foto","e","seien","comment","ticker","live","laif","uhr","videolänge","dass","mindestens","das","mail","die","schon","neuer abschnitt", "login", "loggen", "inaktiv","nwmi","wäre","viele","nwnoa","morgenkolumne","beim","dpa","video","quelle","afp","witters","fotogalerie","wurden","worden","wegen","sagt","immer","gibt","geht","spon","registrierter","als","spiegel","vielen","in","es","bitte","dank","unserer","nutzer","sei","beitrag","user","seit","zeichen","tba","datenschutzerklärung","premium","nutzungsbedingungen","nutzungsrechte","pflichtfelder","registrierung","anzeige","großbuchstaben","sonderzeichen","html","seitennavigation","fullscreen","statista","club","sagte","borenda","spreepicture","shopübersicht")
+mystopwords <- c("focus","online","spiegel", "stern", "de", "bild","bildplus", "zeit", "ersten", "tagesschau","müssen","sagen", "zeitmagazin","seitenanfang","ja","mal","heute","ich","sie","passwort","kommentar","wurde","ihr","der","im","artikel","mehr","ihren","foto","e","seien","comment","ticker","live","laif","uhr","videolänge","dass","mindestens","das","mail","die","schon","neuer abschnitt", "login", "loggen", "inaktiv","nwmi","wäre","viele","nwnoa","morgenkolumne","beim","dpa","video","quelle","afp","witters","fotogalerie","wurden","worden","wegen","sagt","immer","gibt","geht","spon","registrierter","als","spiegel","vielen","in","es","bitte","dank","unserer","nutzer","sei","beitrag","user","seit","zeichen","tba","datenschutzerklärung","premium","nutzungsbedingungen","nutzungsrechte","pflichtfelder","registrierung","anzeige","großbuchstaben","sonderzeichen","html","seitennavigation","fullscreen","statista","club","sagte","borenda","spreepicture","shopübersicht")
 
-mystopwords <- distinct(as.data.frame(mystopwords))
-
-btw$text_cleaned<- removeWords(btw$text_cleaned, mystopwords$mystopwords)
+btw$text_cleaned<- removeWords(btw$text_cleaned, mystopwords)
 ```
@@
   group_by(site) %>%
-  unnest_tokens(word, title) %>%
+  unnest_tokens(word, text_cleaned) %>%
   count(site, word, sort = TRUE)  %>%
@@
 
-btw$text_cleaned <- stem_text(btw$text_cleaned)
+btw$text_cleaned1 <- stem_text(btw$text_cleaned)
 ```
@@
   mutate(month = month(date),
+         week = week(date),
          articleID = as.numeric(rownames(btw)),
@@
 ```{r}
-save(btw, file="../output/btw_combined.Rda")
+save(btw, file="../output/btw_combined_small.Rda")
 ```

### 2017-12-14 paper/R/03_stm.Rmd
new sample

@@
 ## Preparation
+```{r}
+btw %>% mutate(week = week(date)) -> btw
+```
+
 ### Build Corpus
@@
 ```{r}
-k = 28 # Topics
+k = 15 # Topics
 
@@
            data=out$meta,
-           max.em.its = 75,
+           #max.em.its = 150,
            seed =8458159,

### 2017-12-14 paper/R/04_regression.Rmd
new sample

--- 2017-12-08 paper/R/04_regression.Rmd
@@
 #rm(list=ls())
-col <- brewer.pal(7,"Dark2")
+col <- brewer.pal(6,"Dark2")
 ```
@@
 ```{r caching, echo = FALSE}
-#load("../output/btw_combined.Rda")
-load("../output/models/STM 28 .Rda")
+load("../output/models/STM 15 .Rda")
 ```
@@
   group_by(date, site) %>%
-  summarise(obs = n()) %>%
+  dplyr::summarise(obs = n()) %>%
   ggplot(aes(date, obs, color = site)) +
@@
 # Add Topic to origian DF
+btw$articleID = as.numeric(rownames(btw))
+
 btw %>%
@@
 ## Topic Proportion
-```{r}
+```{r fig.height=7, fig.width=9}
+library(stm)
 png("../figs/topic_proportion.png")
-plot(stmOut, type = "summary", xlim = c(0,.16), n = 5, 
+plot(stmOut, type = "summary", xlim = c(0,.3), n = 5, 
      custom.labels = topicLabel$topic_name, 
-     family = "Roboto", main = "", text.cex = 0.7)
+     family = "Roboto", main = "", text.cex = 1)
 dev.off()
@@
   group_by(topic_name) %>% 
-  top_n(300, gamma) %>%
+  top_n(100, gamma) %>%
   sample_n(7) %>% 
@@
     posts_classification.sdt %>% 
-      ggplot(aes(x = 0, y = row, color = factor(topic, levels = 1:28))) +
-      facet_wrap(~topic_title, ncol = 4) +
+      ggplot(aes(x = 0, y = row, color = factor(topic, levels = 1:15))) +
+      facet_wrap(~topic_title, ncol = 3) +
       geom_text(
         aes(label = title),
-        size = 3, hjust = 0, family = "Roboto"
+        size = 2.8, hjust = 0, family = "Roboto"
       ) +
@@
 )
+```
+
+```{r}
+btw %>% filter(topic==8) %>%
+  filter(gamma>=0.5) %>%
+  select(url, gamma) %>% htmlTable::htmlTable(align="l")
+```
+
+```{r}
+label[1]
 ```
@@
 ```{r}
-prep <- estimateEffect(1:28 ~site + s(month),
+prep <- estimateEffect(1:15 ~site + s(month),
                        stmOut, meta=out$meta, uncertainty = "Global")
@@
 ```{r}
-for (i in 1:28){
+for (i in 1:15){
   png(paste0("../figs/estimate_effect",i,".png"))
@@
        main = paste0("Topic ",i,": ",topicLabel$topic_name[i]),
-       xlim = c(-.05,0.15))
+       xlim = c(-.05,0.2))
   dev.off()

### 2018-01-09 paper/R/02_cleanAndCombine.Rmd
step

--- 2017-12-08 paper/R/02_cleanAndCombine.Rmd
@@
 
-load("../output/news_cleaned.Rda")
+#load("../output/news_cleaned.Rda")
 okt <- read_csv("../data/eventbride/eventbride_okt_18.csv")
@@
 nov_22 <- read_csv("../data/eventbride/eventbride_nov_22.csv")
-nov_30 <- read_csv("../data/eventbride/eventbride_nov_30.csv")
+dec_16 <- read_csv("../data/eventbride/eventbride_dec_16.csv")
+jan_1 <- read_csv("../data/eventbride/eventbride_jan_1.csv")
 ```
@@
 ```{r}
-btw1 <- bind_rows(list(okt,nov_03,nov_22,nov_30)) %>%
+df_full <- bind_rows(list(okt,nov_03,nov_22,dec_16,jan_1)) %>%
   mutate(text = body,
@@
 
-btw1 <- bind_rows(df %>%
-                   mutate(date = as.Date(date)) %>%
-                   select(date,title,text,site,url),
-                 btw1)
+# df_full <- bind_rows(df %>%
+#                    mutate(date = as.Date(date)) %>%
+#                    select(date,title,text,site,url),
+#                  df_full)
 ```
@@
 ```{r}
-keeps <- c("welt.de","spiegel.de","stern.de","focus.de","zeit.de","bild.de","tagesschau.de")
+keeps <- c("spiegel.de", "focus.de", "zeit.de","bild.de",
+           "tagesschau.de","deutschlandfunk.de")
 
-btw1 %>%
+df <- df_full %>%
   mutate(title_text = paste(title, text, sep=" ")) %>%
-  filter(site %in% keeps) -> btw
+  filter(site %in% keeps) %>%
+  filter(date>=as.Date("2017-09-14"))
 ```
@@
 ```{r}
-pat1 <- "\\w\\.de/politik/deutschland"
-pat2 <- "\\w\\.de/politik/inland"
-pat3 <- "\\w\\.de/politik/wahl"
-pat4 <- "\\w\\.de/politik/bundestagswahl"
-pat5 <- "tagesschau\\.de/inland"
+# pat1 <- "\\w\\.de/politik/deutschland"
+# pat2 <- "\\w\\.de/politik/inland"
+# pat3 <- "\\w\\.de/politik/wahl"
+# pat4 <- "\\w\\.de/politik/bundestagswahl"
+# pat5 <- paste("cdu","csu","union","spd","fdp","afd","linkspartei","gruenen",
+#               "merkel","schulz","nahles","gabriel","oezdemir","petry","wagenknecht","lindner",
+#               "gauland","weidel","steinmeier","seehofer","maiziere","dreyer","althusmann",
+#               "buergermeister", "fraktion","jamaika","groko","koalition","sondierung","btw","wahl",
+#               "bundestag","bundewehr","bundesregierung","landtag","minister","kanzler",
+#               "fluechtling","raf","glyphosat","rundfunk",  sep="|")
+# 
+# btw %>%
+#   mutate(politics = ifelse(grepl(paste(pat1,pat2,pat3,pat4,
+#                       sep="|"), url, perl = TRUE),1,0)) -> btw1
+# 
+#  
+# btw1$politics <- ifelse(btw1$site=="deutschlandfunk.de"&grepl(pat5,btw1$url),1,btw1$politics)
+# btw1$politics <- ifelse(btw1$site=="tagesschau.de"&grepl(pat5,btw1$url),1,btw1$politics)
 
-btw %>%
-  mutate(politics = ifelse(grepl(paste(pat1,pat2,pat3,pat4,pat5,
-                     sep="|"), url, perl = TRUE),1,0)) -> df_full
+#........................
+pat <- paste("cdu","csu","union","spd","fdp","afd",
+             "linkspartei","die linke","die grünen","bündnis 90", sep="|")
+
+df %>%
+  mutate(politics = ifelse(grepl(pat, title_text, ignore.case = TRUE),1,0)) -> btw1
 ```
@@
 ```{r}
-df_full %>%
-  filter(politics == 1) %>%
-  distinct(url, .keep_all = T) -> btw
+btw1 %>%
+  #filter(politics==1) %>%
+  ggplot(aes(site, fill=factor(politics))) +
+  geom_bar(show.legend = FALSE, alpha=0.8)
+```
+
+```{r}
+btw <- btw1 %>% filter(politics==1)
+```
+
+```{r}
+btw %>%
+  group_by(date, site) %>%
+  summarize(obs = n()) %>%
+  ggplot(aes(date, obs, fill = factor(site))) +
+  geom_col(alpha=0.8) +
+  #geom_vline(aes(xintercept=as.Date("2017-09-24")),
+  #           linetype = 2, color="grey40") +
+  #geom_vline(aes(xintercept=as.Date("2017-11-20")),
+  #               linetype = 2, color="grey40") +
+  #scale_color_manual(values = col) +
+  labs(x="", y="Count",fill="") +
+  scale_x_date(breaks = date_breaks("1 week"), labels=date_format("%d.%m", tz="CET"))
 ```
@@
 ```{r}
-btw$text_length <- sapply(gregexpr("\\S+", btw$text), length)
+df$text_length <- sapply(gregexpr("\\S+", df$text), length)
 ```
@@
 ```{r}
-btw %>%
-  filter(text_length > 200) %>%
+btw <- df %>%
+  filter(text_length > 120) %>%
+  arrange(desc(text_length)) %>%
+  distinct(url, .keep_all = TRUE) %>%
+
   # remove articles that contain daily overviews
-  filter(!grepl("News des Tages", title_text)) %>%
   filter(!grepl("Nachrichten am Morgen", title)) %>%
+  filter(!grepl("elbvertiefung", url)) %>%
+  filter(!grepl("zeit-magazin", url)) %>%
+  filter(!grepl("s-magazin", url)) %>%
   filter(!startsWith(title,"News")) %>%
+
   # remove articles that only contain video 
   filter(!grepl("Video einbetten Nutzungsbedingungen Embedding Tagesschau", title_text)) %>%
+
   # remove english text
   filter(!grepl("bild-international", url)) %>%
+  filter(!grepl("spiegel.de/international", url)) %>%
   filter(!grepl("german",url)) %>%
+  filter(!grepl("arabisch",url)) %>%
+
   # remove text that mostly contain user comments
-  filter(!grepl("kommentar", title, ignore.case = TRUE)) %>%
   filter(!grepl("ticker", title, ignore.case = TRUE)) %>%
   filter(!grepl("stream", title, ignore.case = TRUE)) %>%
-  filter(!startsWith(text,"1.")) -> btw
+  filter(!startsWith(text,"1.")) 
 ```
@@
 ```{r}
-btw %>%
-  filter(grepl("faktenfinder", title_text)) %>%
-  select(url, title_text)
+save(btw, file="../output/btw_combined.Rda")
+
+rm(list=ls())
+load("../output/btw_combined.Rda")
 ```
@@
 ```{r}
-pat <- "Eine Kolumne von \\w{1,} \\w{1,}"
+pat <- "Newsletter[^\n]*"
 btw %>%
@@
 
+  # Deutschlandfunk
+  x = gsub("Äußerungen unserer Gesprächspartner[^.]*", "", x, perl = TRUE)
+  x = gsub("im Gespräch mit \\w{1,}", "", x, ignore.case = TRUE, perl=TRUE)
+  x = gsub("Heinlein", "", x, ignore.case = TRUE, perl=TRUE)
+  x = gsub("Barenberg", "", x, ignore.case = TRUE, perl=TRUE)
+  x = gsub("Büüsker", "", x, ignore.case = TRUE, perl=TRUE)
+  x = gsub("Dobovisek", "", x, ignore.case = TRUE, perl=TRUE)
+  x = gsub("Schmidt-Mattern", "", x, ignore.case = TRUE, perl=TRUE)
+  x = gsub("Zagatta", "", x, ignore.case = TRUE, perl=TRUE)
+  x = gsub("Armbrüster", "", x, ignore.case = TRUE, perl=TRUE)
+  x = gsub("Münchenberg", "", x, ignore.case = TRUE, perl=TRUE)
+  x = gsub("Heckmann", "", x, ignore.case = TRUE, perl=TRUE)
+  x = gsub("Kaess", "", x, ignore.case = TRUE, perl=TRUE)
+  x = gsub("Engels", "", x, ignore.case = TRUE, perl=TRUE)
+  x = gsub("Zurheide", "", x, ignore.case = TRUE, perl=TRUE)
+  x = gsub("Marc Müller", "", x, ignore.case = TRUE, perl=TRUE)
+
   return(x)
@@
 btw$text_cleaned <- clean.text(btw$title_text)
-```
 
-```{r}
 btw$text_cleaned <- gsub("[[:punct:]]", " ", btw$text_cleaned)
@@
 btw$text_cleaned <- tolower(btw$text_cleaned)
+
+## Remove stopwords
+# 1
+german_stopwords_full <- read.table("dict/german_stopwords_full.txt", stringsAsFactors = F)
+german_stopwords_full <- german_stopwords_full$V1
+
+# 2
+mystopwords <- c("focus","online","spiegel", "stern", "de", "bild","bildplus","n-tv.de", "zeit", "ersten", "tagesschau","müssen","sagen", "zeitmagazin","seitenanfang","ja","mal","heute","ich","sie","passwort","kommentar","wurde","ihr","der","im","artikel","mehr","ihren","foto","e","seien","comment","ticker","live","laif","uhr","videolänge","dass","mindestens","das","mail","die","schon","neuer abschnitt", "login", "loggen", "inaktiv","nwmi","wäre","viele","nwnoa","morgenkolumne","beim","dpa","video","quelle","afp","witters","fotogalerie","wurden","worden","wegen","sagt","immer","gibt","geht","spon","registrierter","als","spiegel","vielen","in","es","bitte","dank","unserer","nutzer","sei","beitrag","user","seit","zeichen","tba","datenschutzerklärung","premium","nutzungsbedingungen","nutzungsrechte","pflichtfelder","registrierung","anzeige","großbuchstaben","sonderzeichen","html","seitennavigation","fullscreen","statista","club","sagte","borenda","spreepicture","shopübersicht","herr","imago","dobovisek","barenberg","heinlein","armbrüster","kaess","münchenberg","büüsker","tsereteli","konietzny","klenkes","hauptstadtstudio","newsletter","premiumbereich","nachrichtenpodcast","karrierespiegel","ganslmeier","heißler","zerback","böddeker","frage","glaube","vorstellen","denken","beispiel","sozusagen","na","picture alliance")
+
+stopwords <- c(german_stopwords_full, mystopwords)
+stopwords <- unique(stopwords)
+
+# 3
+btw$text_cleaned<- removeWords(btw$text_cleaned, stopwords)
 ```
 
-## Remove Stopwords
+## month & document number
 ```{r}
-btw$text_cleaned<- removeWords(btw$text_cleaned, stopwords("german"))
+btw %>%
+  mutate(month = month(date),
+         week = week(date),
+         articleID = as.numeric(rownames(btw)),
+         site = ifelse(site=="bild.de","Bild.de",site),
+         site = ifelse(site=="focus.de","FOCUS ONLINE",site),
+         site = ifelse(site=="spiegel.de","SPIEGEL ONLINE",site),
+         site = ifelse(site=="zeit.de","ZEIT ONLINE",site),
+         site = ifelse(site=="deutschlandfunk.de","Deutschlandfunk.de",site),
+         site = ifelse(site=="tagesschau.de","Tagesschau.de",site)) -> btw
 ```
 
-### Remove customized stopwords
 ```{r}
-mystopwords <- c("focus","online","spiegel", "stern", "de", "bild","bildplus", "zeit", "ersten", "tagesschau", "zeitmagazin","seitenanfang","ja","mal","heute","ich","sie","passwort","kommentar","wurde","ihr","der","im","artikel","mehr","ihren","foto","e","seien","comment","ticker","live","laif","uhr","videolänge","dass","mindestens","das","mail","die","schon","neuer abschnitt", "login", "loggen", "inaktiv","nwmi","wäre","viele","nwnoa","morgenkolumne","beim","dpa","video","quelle","afp","witters","fotogalerie","wurden","worden","wegen","sagt","immer","gibt","geht","spon","registrierter","als","spiegel","vielen","in","es","bitte","dank","unserer","nutzer","sei","beitrag","user","seit","zeichen","tba","datenschutzerklärung","premium","nutzungsbedingungen","nutzungsrechte","pflichtfelder","registrierung","anzeige","großbuchstaben","sonderzeichen","html","seitennavigation","fullscreen","statista","club","sagte","borenda","spreepicture","shopübersicht")
-
-mystopwords <- distinct(as.data.frame(mystopwords))
-
-btw$text_cleaned<- removeWords(btw$text_cleaned, mystopwords$mystopwords)
+save(btw, file="../output/btw_combined.Rda")
 ```
@@
   group_by(site) %>%
-  unnest_tokens(word, title) %>%
-  count(site, word, sort = TRUE)  %>%
+  unnest_tokens(word, text_cleaned) %>%
+  dplyr::count(site, word, sort = TRUE)  %>%
   bind_tf_idf(word, site, n) %>%
-  arrange(desc(tf_idf))
+  dplyr::arrange(desc(tf_idf))
 
@@
 
-## month & document number
 ```{r}
-btw %>%
-  mutate(month = month(date),
-         articleID = as.numeric(rownames(btw)),
-         site = ifelse(site=="bild.de","Bild.de",site),
-         site = ifelse(site=="focus.de","FOCUS ONLINE",site),
-         site = ifelse(site=="spiegel.de","SPIEGEL ONLINE",site),
-         site = ifelse(site=="zeit.de","ZEIT ONLINE",site),
-         site = ifelse(site=="welt.de","DIE WELT",site)) -> btw
+btw %>% filter(grepl("Heckmann",text)) %>% select(text,text_cleaned) %>% sample_n(1) %>% htmlTable(align="l")
 ```
-
-```{r}
-save(btw, file="../output/btw_combined.Rda")
-```

### 2018-01-09 paper/R/03_stm.Rmd
step

--- 2017-12-08 paper/R/03_stm.Rmd
@@
 
-rm(list=ls())
+#rm(list=ls())
 # Functions
-source("func/topic-modelling-functions.R")
 ```
@@
 # Process data
-processed <- textProcessor(btw$text_cleaned, metadata = btw[,c("site","text_cleaned","month")],
+processed <- textProcessor(btw$text_cleaned, metadata = btw[,c("site","text_cleaned","week")],
                            wordLengths = c(2,Inf),
@@
 out <- prepDocuments(processed$documents, processed$vocab, processed$meta)
+
+save(btw, out, file="../output/btw_combined.Rda")
 ```
@@
 ```{r}
-k = 28 # Topics
+k = 50 # Topics
 
@@
            K=k,
-           prevalence = ~site+s(month),
+           prevalence = ~site+s(week),
            data=out$meta,
-           max.em.its = 75,
+           #max.em.its = 150,
            seed =8458159,

### 2018-01-09 paper/R/04_regression.Rmd
step

@@
 
-#rm(list=ls())
+rm(list=ls())
 col <- brewer.pal(6,"Dark2")
@@
 ```{r caching, echo = FALSE}
-load("../output/models/STM 15 .Rda")
-```
-
-load data "Unique User"
-```{r}
-## Daily (06-2017 - 12-2017)
-unique_user1 <- read_excel("../data/uniqueUser_1.xls")
-unique_user2 <- read_excel("../data/uniqueUser_2.xls")
-
-uu_df <- rbind(unique_user1,unique_user2) %>%
-  rename(uniqueUser = `Unique User Tag Mio.`,
-         site = Dachmarke,
-         date = Tag) %>%
-  select(date, site, uniqueUser)
-
-rm(unique_user1, unique_user2)
-```
-
-# Description of Data
-
-### Unique User 
-```{r}
-p <- uu_df %>%
-  filter(date > as.Date("2017-05-31")) %>%
-  ggplot(aes(date, uniqueUser, color=site)) +
-  geom_line() +
-  geom_vline(aes(xintercept=as.POSIXct("2017-09-24")),
-             linetype = 2, color="grey50") +
-  scale_color_manual(values = col[c(1,2,3,4,6,7)]) +
-  theme(
-      #legend.position   = "none",
-      legend.text       =  element_text(size=6),
-      plot.background   = element_rect("#fafafa", "#fafafa"),
-      panel.background  = element_rect("#fafafa"),
-      axis.title.x      = element_blank(),
-      axis.text.y       = element_text(size = 8)
-    ) +
-  labs(x="", y="", color="", title = "", 
-      caption = "
-  Source: AGOF (www.agof.de)
-      " )
-
-#ggplotly(p)
-ggsave(plot= p,
-filename = "../figs/uniqueUser.png", device = "png",
-width = 6, height = 4,
-        dpi = 600
-)
+load("../output/models/STM 20 .Rda")
 ```
@@
 
+# topicLabel <- as.data.frame(label$topics)
+# 
+# topicLabel <- topicLabel %>% 
+#   transmute(topic = rownames(.),
+#              topic_name = paste(V1,V2,V3,V4,V5, sep=","))
+
 prob <- as.data.frame(label$prob, stringsAsFactors = F)
@@
 rm(prob, frex, lift, score)
+```
+
+```{r}
+labelTopics(stmOut, 19, n=10)
 ```
@@
 png("../figs/topic_proportion.png")
-plot(stmOut, type = "summary", xlim = c(0,.3), n = 5, 
+plot(stmOut, type = "summary", xlim = c(0,.5), n = 5, 
      custom.labels = topicLabel$topic_name, 
@@
 
-```{r}
-btw %>% filter(topic==8) %>%
-  filter(gamma>=0.5) %>%
-  select(url, gamma) %>% htmlTable::htmlTable(align="l")
-```
-
-```{r}
-label[1]
-```
-
 ## Estimating the Effect of Covariates
@@
 ```{r}
-prep <- estimateEffect(1:15 ~site + s(month),
+prep <- estimateEffect(1:15 ~site + s(week),
                        stmOut, meta=out$meta, uncertainty = "Global")
@@
 for (i in 1:25){
-  plot(prep, "month", method = "continuous", topics = i,
+  plot(prep, "week", method = "continuous", topics = i,
        printlegend = F,
@@
 set.seed(7292)
-btw.reg %>% 
+btw %>% 
   mutate(date = as.POSIXct(date),
@@
   scale_color_manual(
-            values = rainbow(28) %>% 
+            values = rainbow(15) %>% 
               adjustcolor(red.f = 0.6, green.f = 0.6, blue.f = 0.6)

### 2018-01-09 paper/R/pageImpr.Rmd
step

@@
 ```
+
+```{r}
+p <- uu_df %>%
+  filter(date > as.Date("2017-05-31")) %>%
+  ggplot(aes(date, uniqueUser, color=site)) +
+  geom_line() +
+  geom_vline(aes(xintercept=as.POSIXct("2017-09-24")),
+             linetype = 2, color="grey50") +
+  scale_color_manual(values = col[c(1,2,3,4,6,7)]) +
+  theme(
+      #legend.position   = "none",
+      legend.text       =  element_text(size=6),
+      plot.background   = element_rect("#fafafa", "#fafafa"),
+      panel.background  = element_rect("#fafafa"),
+      axis.title.x      = element_blank(),
+      axis.text.y       = element_text(size = 8)
+    ) +
+  labs(x="", y="", color="", title = "", 
+      caption = "
+  Source: AGOF (www.agof.de)
+      " )
+
+#ggplotly(p)
+ggsave(plot= p,
+filename = "../figs/uniqueUser.png", device = "png",
+width = 6, height = 4,
+        dpi = 600
+)
+```

### 2018-01-09 paper/R/paper.Rmd
step

---
title: "Regression"
subtitle: ""
author: "Franziska Löw"
date: ""
output: 
  html_document:
    toc: true
    toc_float: true
    theme: "lumen"
    highlight: "tango"
    code_folding: show
    self_contained: true
---

```{r}
suppressPackageStartupMessages({
  library(dplyr)       # Data manipulation
  library(stringr)     # String manipulation
  library(lubridate)   # Date and time manipulation
  library(purrr)       # Functional programming
  library(tidyr)       # Reshaping
  library(magrittr)    # Advanced piping
  library(pushoverr)   # Pushover notifications
  library(doMC)        # Parallel Computing
  library(readr)       # Importing data
  library(tibble)      # Better data frames
  library(data.table)
  library(pscl)
  library(boot)
  library(stm)
  library(readxl)

  library(ggplot2)     # Static data visualization
  library(ggpmisc)
  library(ggiraph)
  library(RColorBrewer) 
  library(ggrepel)
  library(htmlwidgets)
  library(plotly)
  library(scales)      # Scales
  library(viridis)     # Viridis color scales

  library(tidytext)    # Tidy text mining
  library(stringdist)  # String distances
  library(proxy)       # Distance measures
})

# Theming
quartzFonts(
  Roboto =
    c("Roboto-Light",
      "Roboto-Bold",
      "Roboto-Regular",
      "Roboto-Thin")
)

theme_set(
  theme_bw(base_family = "Roboto", base_size = 8) +
    theme(
      plot.title = element_text(face = "bold", size = 14,
                                margin = margin(0, 0, 4, 0, "pt")),
      plot.subtitle = element_text(size = 12),
      plot.caption = element_text(size = 6, hjust = 0),
      axis.title = element_text(size = 10),
      panel.border = element_blank()
    )
)

rm(list=ls())
col <- brewer.pal(6,"Dark2")
```

# Load Data
```{r caching, echo = FALSE}
#load("../output/models/STM 80 .Rda")
load("../output/btw_combined.Rda")
```

### Distribution of articles
```{r message=FALSE, warning=FALSE}
ggsave({
  btw %>%
  ggplot(aes(site)) +
  geom_bar(fill=col, alpha= .8) +
  labs(x="", y="Count") +
  theme(
      legend.position   = "none",
      plot.background   = element_rect("#fafafa", "#fafafa"),
      plot.title        = element_text(size = 18),
      plot.subtitle     = element_text(size = 8),
      plot.caption      = element_text(size = 7),
      panel.background  = element_rect("#fafafa"),
      axis.title.x      = element_blank(),
      axis.text.y       = element_text(size = 8)
    )

},
filename = "../figs/bar.png", device = "png", 
width = 6, height = 4,
        dpi = 600)
```

```{r message=FALSE, warning=FALSE}
ggsave({
  btw %>%
  group_by(date, site) %>%
  dplyr::summarise(obs = n()) %>%
  ggplot(aes(date, obs, color = site)) +
  geom_line() +
  #geom_vline(aes(xintercept=as.Date("2017-09-24")),
  #           linetype = 2, color="grey40") +
  #geom_vline(aes(xintercept=as.Date("2017-11-20")),
  #               linetype = 2, color="grey40") +
  scale_color_manual(values = col) +
  labs(x="", y="Count",color="") +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
  theme(
      #legend.position   = "none",
      plot.background   = element_rect("#fafafa", "#fafafa"),
      plot.title        = element_text(size = 18),
      plot.subtitle     = element_text(size = 8),
      plot.caption      = element_text(size = 7),
      #panel.grid        = element_blank(),
      panel.background  = element_rect("#fafafa"),
      axis.title.x      = element_blank(),
      axis.text.y       = element_text(size = 8)
    )
},
filename = "../figs/timeline.png", device = "png",width = 7, height = 4,
dpi = 600
)

```

# Model Results
```{r Extract wtp and dtp}
# Word-topic probabilities
stmOut %>% tidy("beta") %>% filter(!is.na(topic)) -> posts.wtp
# Document-topic probabilities
stmOut %>% tidy("gamma") -> posts.dtp
```

## Topic Labeling
```{r Label Topics}
label <- labelTopics(stmOut, n=5)

# topicLabel <- as.data.frame(label$topics)
# 
# topicLabel <- topicLabel %>% 
#   transmute(topic = rownames(.),
#              topic_name = paste(V1,V2,V3,V4,V5, sep=","))

prob <- as.data.frame(label$prob, stringsAsFactors = F)
frex <- as.data.frame(label$frex, stringsAsFactors = F)
lift <- as.data.frame(label$lift, stringsAsFactors = F)
score <- as.data.frame(label$score, stringsAsFactors = F)

topicLabel <- prob %>%
  transmute(topic = rownames(.),
            topic_name = paste(prob$V1,prob$V2,prob$V3,score$V1,score$V2,score$V3, sep=","),
            prob = paste(prob$V1,prob$V2,prob$V3, sep=","),
            frex = paste(frex$V1,frex$V2,frex$V3, sep=","),
            lift = paste(lift$V1,lift$V2,lift$V3, sep=","),
            score = paste(score$V1,score$V2,score$V3, sep=","))

topicLabel$topic_name <- vapply(lapply(strsplit(topicLabel$topic_name, ","), unique), paste, character(1L), collapse = " ")
rm(prob, frex, lift, score)
```

```{r}
labelTopics(stmOut, 57, n=15)
```

```{r}
top_topics <-
  posts.dtp %>% 
  group_by(document) %>%
  mutate(therank = rank(-gamma, ties.method = "random")) %>%
  filter(therank %in% 1) %>%
  select(- therank)

# Add Topic to origian DF
btw$articleID = as.numeric(rownames(btw))

btw %>%
  mutate(document = articleID) %>%
  inner_join(.,top_topics, by="document") %>%
  ## Combine with Topic label
  left_join(., topicLabel %>%
              select(topic_name, topic) %>%
              mutate(topic = as.numeric(topic)), by="topic") -> btw
```

## Topic Proportion
```{r fig.height=12, fig.width=9}
#library(stm)
#png("../figs/topic_proportion.png")
plot(stmOut, type = "summary", xlim = c(0,.5), n = 5, 
     custom.labels = topicLabel$topic_name, 
     family = "Roboto", main = "", text.cex = 0.8)
#dev.off()
```

```{r}
btw %>% filter(grepl("zagatta", text_cleaned)) %>% select(url)
```

```{r}
keeps <- c(7,27,46,24,18,16,49,9,38,57,59,36,13)
```

## Sample Articles

```{r Document classification}
set.seed(9272)
posts_classification.sdt <-
  posts.dtp %>% 
  filter(topic %in% keeps) %>%
  group_by(articleID = document) %>% 
  summarise(topic = min(topic[gamma == max(gamma)]), gamma = max(gamma)) %>% 
  ungroup() %>%
  inner_join(btw %>% filter(topic %in% keeps) %>%
               select(title, title_text, articleID, topic_name, site),
              by = "articleID") %>%
  mutate(topic_title = 
           paste0("Topic ", formatC(topic, flag = "0", width = 2), 
                  " - ", topic_name)) %>%
  group_by(topic_name, site) %>% 
  top_n(50, gamma) %>%
  sample_n(3) %>%
  mutate(row = row_number()) %>% 
  ungroup() 
```

```{r}
posts_classification.sdt %>%
  select(site,topic_title,title) %>%
  htmlTable::htmlTable(align="l")
```

## Estimating the Effect of Covariates

### Difference in topic prevalence
The estimateEffect() function explores how prevalence of topics varies across documents according to document covariates (metadata). First, users must specify the variable that they wish to use for calculating an effect. If there are multiple variables specified in estimateEffect(), then all other variables are held at their sample median. These parameters include the expected proportion of a document that belongs to a topic as a function of a covariate, or a first difference type estimate, where topic prevalence for a particular topic is contrasted for two groups.

```{r}
prep <- estimateEffect(keeps ~site + s(week),
                       stmOut, meta=out$meta, uncertainty = "Global")
```

```{r}
summary(prep)
```

Expected difference in topic probability by news source (with 95% Confidence Intervals). 
parameter "covariate": String of the name of the main covariate of interest. Must be enclosed in quotes. All other covariates within the formula specified in estimateEffect will be kept at their median.
```{r}
for (i in keeps){

  png(paste0("../figs/estimate_effect",i,".png"))
  plot(prep, "site", method = "pointestimate", topics = i,
       labeltype = "custom", custom.labels = unique(prep$data$site),
       ylab = "", xlab = "Mean topic proportion in corpus",
       main = paste0("Topic ",i,": ",topicLabel$topic_name[i]),
       xlim = c(-.05,0.2))
  dev.off()
}

#plot(prep, "site", method = "pointestimate", topics = keeps[1])
```

```{r}
for (i in keeps){
  plot(prep, "week", method = "continuous", topics = i,
       printlegend = F,
       ylab = "", xlab = "Mean topic proportion in corpus",
       main = paste0("Topic ",i,": ",topicLabel$topic_name[i]))
}

```

```{r}
p<- posts.dtp %>%
  left_join(., btw %>% select(document, topic_name,
                              site, week),
            by="document")  %>%
  group_by(site, topic, topic_name, week) %>%
  summarize(gamma_mean = mean(gamma)) %>%
  #filter(month!=5) %>%
  ggplot(aes(x=week, y=gamma_mean, fill=factor(topic), text=topic_name)) +
  geom_col() +
  facet_wrap(~site) +
  #facet_grid(~site) +
  theme(legend.position = "none") +
  xlab("Proportion")

ggplotly(p)
```

What is the distribution of the gamma value?
```{r}
ggsave(plot={
  btw %>%
    filter(topic %in% keeps) %>%
  ggplot(aes(gamma)) +
  geom_density(fill="blue",alpha=.5,color="blue") 
},
filename = "../figs/gamma_dist.png",
       width = 8, height = 6, device = "png", dpi=600)
```

filter documents with low posterior
```{r}
btw.reg <- btw %>%
  filter(topic %in% keeps) %>%
  filter(gamma >= 0.5) %>%
  mutate(allocation = 1)
```

## Topic Timeline
```{r Data for topic trends chart, message=FALSE, warning=FALSE}
set.seed(7292)
btw.reg %>% 
  mutate(date = as.POSIXct(date),
         allocation = 1) %>%
  mutate(post_period = 
           date %>% with_tz("Europe/Paris") %>% 
           floor_date("week")) %>%
  # Summarise into tidy dataframe
  group_by(post_period, topic, topic_name) %>% dplyr::summarise(articles = sum(allocation)) %>%
  # Mark peaks 
  group_by(topic_name) %>% dplyr::mutate(peak = ifelse(articles==max(articles),1,0)) -> chart_topic_trends.dt
```

```{r message=FALSE, warning=FALSE}
ggsave(
  plot = {
    ggplot(chart_topic_trends.dt, 
       aes(post_period, articles, color=topic_name)) +
  geom_line() +
  scale_color_manual(
            values = rainbow(20) %>% 
              adjustcolor(red.f = 0.6, green.f = 0.6, blue.f = 0.6)
          ) +
  geom_text_repel(data=subset(chart_topic_trends.dt,peak==1),
            aes(post_period,articles,label=paste(topic,topic_name,sep=":")),
            size=2.8) +
      geom_vline(aes(xintercept=as.POSIXct("2017-09-23")),
                 linetype = 2, color="grey20") +
      geom_vline(aes(xintercept=as.POSIXct("2017-11-19")),
                 linetype = 2, color="grey20") +
  ylim(c(0,200)) +
    theme(
      legend.position   = "none",
      #plot.background   = element_rect("#fafafa", "#fafafa"),
      plot.title        = element_text(size = 18),
      plot.subtitle     = element_text(size = 8),
      plot.caption      = element_text(size = 7),
      panel.grid        = element_blank(),
      #panel.background  = element_rect("#fafafa"),
      axis.title.x      = element_blank(),
      axis.text.y       = element_text(size = 8)
    )
  },
  device = "png",
  filename = "../figs/topic-timeline.png",
  dpi = 600, height = 5, width = 8
)
```

### Topic Distribution by News Page

A common accusation leveled against traditional news media is the amount of bias in reporting various topics. We try to explore the topic distribution of news articles.

```{r Data for topic distribution chart}

set.seed(7292)
btw.reg %>% 
    mutate(document = articleID) %>%
  group_by(site, topic, topic_name) %>%
  summarise(
    articles = sum(allocation),
    sample_articles = 
      paste0(
        "<li>", sample(title, pmin(3, length(document))), "</li>",
        collapse = "<br>"
      )
  ) %>%
  ungroup() %>%
  group_by(site) %>% 
  mutate(perc_articles = articles/sum(articles)) %>% 
  ungroup() %>%
  mutate(
    tooltip_text = 
      paste0(
        "<b>", comma(round(articles, 0)), " (", percent(perc_articles), 
        ") </b> of articles from <b>", site, 
        "</b> fall under <b>", "Topic",topic,": ", topic_name, "</b><br><br>Sample Articles:<br><ul>",
        sample_articles, "</ul>"
      ) %>% str_replace_all("'", "")
  ) ->
  news_page_distribution.dt
```

```{r Topic distribution chart, eval = TRUE}
{
  news_page_distribution.dt %>% 
    ggplot(aes(x = site, y = perc_articles, fill = topic_name)) +
    geom_bar_interactive(
      aes(tooltip = tooltip_text),
      position = position_stack(), 
      stat = "identity", color = "darkgray"
    ) +
    scale_y_continuous(
      name = "Percent of Articles", 
      labels = percent,
      expand = c(0, 0)
    ) +
    theme(
      legend.position = "none",
      axis.title.y = element_blank(),
      legend.background = element_rect("#fafafa"),
      plot.background   = element_rect("#fafafa", "#fafafa"),
      plot.subtitle     = element_text(size = 8),
      plot.caption      = element_text(size = 7),
      plot.title        = element_text(size = 18)
    ) +
    coord_flip() +
    scale_fill_viridis(discrete = TRUE) +
    labs(
      title = ""
    )
} %>% 
  ggiraph(
    ggobj = .,
    width_svg = 12,
    height_svg = 8,
    width = 1,
    tooltip_extra_css = "
    font-family: Roboto; 
    background-color: #000; 
    color: #fff; font-size: 10px;
    padding: 5px;"
  ) -> chart_topic_distribution.wdgt

saveWidget(
  widget = chart_topic_distribution.wdgt,
  file = "../figs/04-topic-distribution-pages.html",
  selfcontained = FALSE,
  libdir = "../figs/js",
  background = "#fafafa"
)

chart_topic_distribution.wdgt

```

## Sentiment analysis
```{r}
library(sentimentr)
```

```{r}
# Load dictionaries (from: http://wortschatz.uni-leipzig.de/de/download)
neg_df <- read_tsv("dict/SentiWS_v1.8c_Negative.txt", col_names = FALSE)
pos_df <- read_tsv("dict/SentiWS_v1.8c_Positive.txt", col_names = FALSE)

sentiment_df <- bind_rows(neg_df,pos_df)
names(sentiment_df) <- c("Wort_POS", "polarity", "Inflektionen")

sentiment_df %>% 
  mutate(words = str_sub(Wort_POS, 1, regexpr("\\|", .$Wort_POS)-1),
         words = tolower(words)
         #POS = str_sub(Wort_POS, start = regexpr("\\|", .$Wort_POS)+1)
         ) %>%
  select(words, polarity) -> sentiment_df

sentiment_df <- rbind(sentiment_df, c("nicht",-0.8))

sentiment_df %>% mutate(polarity = as.numeric(polarity)) %>%
  as_key() -> sentiment_df
```

```{r}
btw.reg %>% 
  mutate(text_split = get_sentences(text)) %$%
  sentiment(text_split,
               polarity_dt = sentiment_df) -> btw_sentiment

btw_sentiment_doclevel <- btw_sentiment %>%
  group_by(element_id) %>%
  summarize(sentiment = mean(sentiment))

btw.reg <- left_join(btw.reg, btw_sentiment_doclevel %>%
                       mutate(document = element_id) %>%
                       select(document, sentiment),
                      by="document")
btw.reg %>%
  group_by(site) %>%
  mutate(ave_sentiment = mean(sentiment, na.rm = T)) -> plot_btw
```

```{r}
p1 <- plot_btw %>%
  ggplot(aes(sentiment, factor(site), color=topic_name, 
             text=paste(document,": ",title))) +
  geom_point(alpha=.5, shape=1) +
  xlim(c(-0.25,0.1)) +
  facet_wrap(~topic_name) +
  labs(y="") +
  theme(legend.position = "none")

ggplotly(p1)
```

```{r}
btw.reg %>% 
  filter(document==4) %>%
  mutate(text_split = get_sentences(text)) %$%
  sentiment_by(text_split,
               polarity_dt = sentiment_df) %>%
  sentimentr::highlight()
```

### Radar
```{r}
require(ggiraphExtra)
```

```{r}
btw.reg %>%
  group_by(site, topic_name) %>%
  summarize(sentiment = mean(sentiment, na.rm = T)) %>%
  spread(site, sentiment) %>%
  ungroup() %>%
  mutate(topic=factor(topic_name)) -> radar
```

```{r}
ggsave(plot={
  ggRadar(radar, aes(color=topic), rescale = FALSE,
        legend.position = "none") +
  facet_wrap(~topic, ncol = 4)
},
file="../figs/radar.png",
dpi=600,
height = 7,
width = 9
)
```

### 2018-01-09 paper/doc/doc2.tex
step

@@
 
-Social networks such as Facebook are becoming more and more important for online news services: an increasing number of their readers access the news pages via links in the networks.
-Users of Facebook, for example, can use their profile to share links to external websites - such as news portals - with their online friends.
-This has led to the development of social media becoming an important generator of traffic for content providers.
-In Germany, 94\% of online shared news articles in 2015 are distributed via Facebook, followed by Twitter with 3.5\% and Google+ with 2.3\% \citep{schiller_development_2016}.
+In Germany, the debate about the role of public media and their mission in a rapidly changing media world is a recurring theme.
+If the right to use digital media were to be withdrawn from the public media outlets, they would not only be deprived of the possibility of improved information provision.
+They also threatened to lose their competitiveness with commercial media.
+But it is precisely this competitiveness that is constitutionally guaranteed.
+On the other hand, there is the concern of commercial providers who are registering an ever-increasing number of digital services financed by fees.
+They complain about a bias in competition caused by public media offering online text-content because of their fee financing.
+The advertising-financed business model of the media houses is based on the premise that users visit their websites in order to achieve high advertising revenues.
 
-The advertising-financed business model of the media houses is based on the premise that users visit their websites in order to achieve high advertising revenues.
-For this reason, news agencies are particularly interested in finding out which topics are more likely shared on these platforms.
-\citet{schiller_development_2016} show, that social media users choose a certain site depending on the researched topic.
-FOCUS Online for example is targeted for articles from politics and business, while sports news is more likely to be shared from Bild.de.
+The fundamental question in this debate is whether the offer of public news on the internet is justified.
+They should only occur where there are clear deficits in private sector supply.
+A frequently cited argument is that only the public media make it possible to provide information that is free of self-interest.
+Due to their public mandate and financing, they can afford what private providers cannot or only to a limited extent because of their economic dependency: a journalistic and editorial self-observation of society in the public interest.
+Due to their constitutional determination, they are obliged to the diversity and representation of the political and social spectrum of opinion in its entire breadth, including minority positions.
 
-While these pre-defined resorts give an indication on the content of an article, multiple articles in the same resort probably don't cover the same topics.
-Especially if the articles originate from different news portals.
-Furthermore, articles can contain more than one topic.
-We use a structural topic model to reveal the underlying topics of a collection of articles, and how the articles exhibit them.
-We then estimate the effect of topic prevalence on the number of Facebook shares.
-We use a data set of online news articles about domestic politics dated from 01.06.2017 to 22.11.2017\footnote{German federal elections took place on 24th of September 2017.} from seven German content providers: Bild.de, Die Welt, Focus Online, Spiegel Online, Stern.de, Zeit Online and Tagesschau.de.
-They are all providers of online news, whereby Tagesschau.de is the only publicly funded service.
-The latter was also included in the study to verify whether the topics differ when the content is created on the basis of a different business model.
+In order to check whether there is a difference in content between public and private providers, we investigate online
+
+We use a data set of German online news articles about domestic politics to examine the differences in news content between public and private news provides.
+Your dataset contains articles dated from 01.06.2017 to 22.11.2017\footnote{German federal elections took place on 24th of September 2017.} from seven German content providers to analyze news reports about german elections, where we allow prevalence of topics to evolve over time (before and after the elections) and vary across newswire services.
+We then estimate the effect of news wire source on both topical prevalence (topic distribution) and topical content (word-topic distribution).
 
@@
 We use this approach to analyze online news about the german federal elections, where we allow prevalence of topics to vary across newswire services.
-We then estimate the effect of topical prevalence (the posterior document-topic distribution) on the number of Facebook shares.
+We then estimate the effect of topical prevalence (the posterior document-topic distribution) on the ownership (public or private).
 
-Figure \ref{fig_research_strat} gives an overview of the applied research strategy.
 Chapter \ref{ch_model} explains the generative process of the mixed membership model and the results of this process are presented in chapter \ref{ch_results}.
 Chapter \ref{ch_data} contains a description of the text data and how it was pre-processed in order to use it as input variable.
-Chapter \ref{ch_regression} describes how we regress the estimated probabilities of topic prevalence of a document on the times, this document was shared on Facebook.
-
-\begin{figure}[ht]
-	\centering
-	\includegraphics[width=0.95\textwidth]{../figs/research_strategy.pdf} 
-	\caption{Research Strategy}
-	\label{fig_research_strat}
-\end{figure}
+Chapter \ref{ch_regression} describes how we regress the estimated probabilities of topic prevalence of a document on its methadata.
 
@@
 Advertising can also have an effect on the recipients, which can be both negative and positive, depending on the quality of the advertising.
-Depending on the strength of the indirect network effects, private publisher maximize their revenue by balancing the demand from advertisers and subscribers using different business models \citep{evans_economics_2008}.\footnote{Public media such as Tagesschau.de do not depend on revenues from the advertising industry, which means that there is no two-way market structure.} Many traditional newspapers follow the subscription/advertising model, where the publisher charges both market sides: The audience pays a fee to obtain access to the content, and advertisers pay to obtain access to the viewers.
+Depending on the strength of the indirect network effects, private publisher maximize their revenue by balancing the demand from advertisers and subscribers using different business models \citep{evans_economics_2008}.
+Many traditional newspapers follow the subscription/advertising model, where the publisher charges both market sides: The audience pays a fee to obtain access to the content, and advertisers pay to obtain access to the viewers.
 Many online news agencies provide part of their editorial content for free and hide another, more exclusive part behind a paywall.
@@
 In fact, most advertising-financed online magazines earn their gross margin from advertising.\cite{evans_industrial_2005} In order to maximize their profits, these companies have an interest in attracting as many readers as possible.
-Facebook is an important traffic supplier for news sites: Over 487.000 news articles from TOP15\footnote{Bild.de, bunte, Chip, FAZ, Focus, Handelsblatt, Heise, N-TV, Spiegel, Sport1, Stern, Süddeutsche, Tagesschau, Welt, Zeit} media were shared 123.000.000 times on Facebook (94\%), Twitter(3.5\%) and Google+(2.3\%).\cite{schiller_development_2016} In addition to the quantity of the audience, the demographic characteristics of recipients also have an influence on the willingness to pay on the advertiser site.
+In addition to the quantity of the audience, the demographic characteristics of recipients also have an influence on the willingness to pay on the advertiser site.
 Online advertising makes it possible to target ads to particular consumers in real time.
-Facebook instant articles facilitates this targeting, as they make the public users profile data available to the publisher.
-However, not all topics are equally often distributed in social media.
-\citet{schiller_development_2016} show, that social media users choose a certain site depending on the researched topic.
-FOCUS Online for example is targeted for articles from politics and business, while sports news is more likely to be shared from Bild.de.
 
-While these pre-defined resorts give an indication on the content of an article, multiple articles in the same resort probably don't cover the same topics.
-Especially if the articles originate from different news portals.
-Furthermore, articles can contain more than one topic.
-We use a structural topic model to reveal the underlying topics of a collection of articles, and how the articles exhibit them.
-We then estimate the effect of topic prevalence on the number of Facebook shares.
-We use a data set of online news articles about domestic politics dated from 01.06.2017 to 22.11.2017\footnote{German federal elections took place on 24th of September 2017.} from seven German content providers: Bild.de, Die Welt, Focus Online, Spiegel Online, Stern.de, Zeit Online and Tagesschau.de.
-They are all providers of online news, whereby Tagesschau.de is the only publicly funded service.
-The latter was also included in the study to verify whether the topics differ when the content is created on the basis of a different business model.
+The two-sided market structure of the private news markets results in news platforms striving to choose their content in such a way that its reach is as large as possible in order to maximize profits from advertising revenues.
+\citep{steiner_program_1952} concluded, that profit-maximizing media owners may choose to offer the same content, i.e.
+content aligned with the tastes of the majority.
+\citep{gabszewicz_press_2001} study the problem of diversity of the political content of newspapers.
+They find that the maximum differentiation only prevails if the readers sufficiently value the political differentiation between the newspapers the advertising market is small enough.
+On the other hand, advertising may also have a positive impact on the media, as it enables publishers to report independently of political parties.
+\citet{ellman_what_2009} found that advertising increases the intensity of competition for readers and therefore raises accuracy of media coverage.
+
+Given the crucial role of the media in shaping opinion and promoting democracy, pluralism of opinion and accuracy of information is a major concern of public authorities.
+The public media in Germany was established in the post-war period and is still subject to three major main orders: (1)  In Germany, public media has the constitutional mandate to contribute to the formation of individual and public opinion, thus contributing to a well-functioning democratic society.
+In contrast to private media, public media do not operate on two-sided markets, but are paid out of public funds.
+This is intended to ensure their independence from advertiser revenue.
 
@@
 \end{figure}
-
-The two-sided market structure of news markets results in news platforms striving to choose their content in such a way that its reach is as large as possible in order to maximize profits from advertising revenues.
-This may lead to media-bias, as advertising may affect the ability and incentives of media to provide independent news.
-On the other hand, advertising may also have a positive impact on the media, as it enables publishers to report independently of political parties.
-\citet{ellman_what_2009} found that advertising increases the intensity of competition for readers and therefore raises accuracy of media coverage.
 

### 2018-01-09 paper/doc/doc_public_private.tex
step

--- 2017-10-18 paper/doc/doc.tex
@@
 
-Markt für Online-Texte.
-Presseverlage beklagen immer mehr eine Wettbewerbsverzerrung durch öffentlich-rechtliche Online-Angebote.
-"Wir erleben im Netz nach wie vor eine mit öffentlich-rechtlichen Geldern finanzierte Flut textbasierter Gratis-Angebote, nichts anderes als eine gebührenfinanzierte digitale Staatspresse, die den Wettbewerb verzerrt und uns Presseverlagen kaum Entfaltungsmöglichkeiten lässt" %(http://www.sz-online.de/nachrichten/ard-und-zdf-gebuehrenfinanzierte-staatspresse-3776123.html)
+Social networks such as Facebook are becoming more and more important for online news services: an increasing number of their readers access the news pages via links in the networks.
+Users of Facebook, for example, can use their profile to share links to external websites - such as news portals - with their online friends.
+This has led to the development of social media becoming an important generator of traffic for content providers.
+In Germany, 94\% of online shared news articles in 2015 are distributed via Facebook, followed by Twitter with 3.5\% and Google+ with 2.3\% \citep{schiller_development_2016}.
+
+The advertising-financed business model of the media houses is based on the premise that users visit their websites in order to achieve high advertising revenues.
+For this reason, news agencies are particularly interested in finding out which topics are more likely shared on these platforms.
+\citet{schiller_development_2016} show, that social media users choose a certain site depending on the researched topic.
+FOCUS Online for example is targeted for articles from politics and business, while sports news is more likely to be shared from Bild.de.
+
+While these pre-defined resorts give an indication on the content of an article, multiple articles in the same resort probably don't cover the same topics.
+Especially if the articles originate from different news portals.
+Furthermore, articles can contain more than one topic.
+We use a structural topic model to reveal the underlying topics of a collection of articles, and how the articles exhibit them.
+We then estimate the effect of topic prevalence on the number of Facebook shares.
+We use a data set of online news articles about domestic politics dated from 01.06.2017 to 22.11.2017\footnote{German federal elections took place on 24th of September 2017.} from seven German content providers: Bild.de, Die Welt, Focus Online, Spiegel Online, Stern.de, Zeit Online and Tagesschau.de.
+They are all providers of online news, whereby Tagesschau.de is the only publicly funded service.
+The latter was also included in the study to verify whether the topics differ when the content is created on the basis of a different business model.
 
@@
 % -----------------------
+
+Facebook is an important traffic supplier for news sites: Over 487.000 news articles from TOP15\footnote{Bild.de, bunte, Chip, FAZ, Focus, Handelsblatt, Heise, N-TV, Spiegel, Sport1, Stern, Süddeutsche, Tagesschau, Welt, Zeit} media were shared 123.000.000 times on Facebook (94\%), Twitter(3.5\%) and Google+(2.3\%).\cite{schiller_development_2016} In addition to the quantity of the audience, the demographic characteristics of recipients also have an influence on the willingness to pay on the advertiser site.
+Online advertising makes it possible to target ads to particular consumers in real time.
+Facebook instant articles facilitates this targeting, as they make the public users profile data available to the publisher.
+However, not all topics are equally often distributed in social media.
 

### 2018-01-19 paper/R/02_cleanAndCombine.Rmd
bla

--- 2017-12-08 paper/R/02_cleanAndCombine.Rmd
@@
 # load the packages
-libs <- c("tidytext","tidyr","readr","lubridate","tm","stm","RColorBrewer",
+libs <- c("tidytext","tidyr","readr","lubridate","tm","stm","RColorBrewer","sampling",
           "plyr","dplyr","class","knitr","data.table","parallel","SnowballC",
@@
 
-btw1 <- bind_rows(df %>%
+df_full <- bind_rows(df %>%
                    mutate(date = as.Date(date)) %>%
                    select(date,title,text,site,url),
-                 btw1)
+                 df_full)
+```
+
+## select stratified random sample
+```{r}
+public <- c("deutschlandfunk.de", "heute.de", "ndr.de", "swr.de", "tagesschau.de", "wdr.de", "zdf.de")
+
+df_full <- df_full %>% 
+  mutate(ownership = ifelse(site %in% public, "public", "private"),
+         month = month(date))
+
+df_full %>% 
+  #filter may2017 and january2018
+  filter(month>5) %>%
+  #calculate site totals by month
+  group_by(site, month) %>%
+  summarize(site_sum = n()) %>%
+  ungroup() %>%
+  #calculate month total
+  group_by(month) %>%
+  mutate(month_sum = sum(site_sum)) %>%
+  ungroup() %>%
+  #calculate share
+  mutate(share = 100*(site_sum/month_sum))-> totals_site
+
+df_full %>% 
+  #filter may2017 and january2018
+  filter(month>5) %>%
+  # calculate ownership totals by month
+  mutate(ownership = ifelse(site %in% public, "public", "private")) %>%
+  group_by(ownership, month) %>%
+  summarize(owner_sum = n()) %>%
+  #calculate month total
+  group_by(month) %>%
+  mutate(month_sum = sum(owner_sum)) %>%
+  ungroup() %>%
+  #calculate share
+  mutate(share = 100*(owner_sum/month_sum))-> totals_ownership
 ```
@@
 ```{r}
-keeps <- c("welt.de","spiegel.de","stern.de","focus.de","zeit.de","bild.de","tagesschau.de")
+keeps <- c("spiegel.de", "focus.de", "zeit.de","bild.de",
+           "tagesschau.de")
 
-btw1 %>%
+df <- df_full %>%
   mutate(title_text = paste(title, text, sep=" ")) %>%
-  filter(site %in% keeps) -> btw
+  filter(site %in% keeps) %>%
+  filter(date>=as.Date("2017-06-01")) %>%
+  filter(date< as.Date("2018-01-01"))
 ```
@@
 pat4 <- "\\w\\.de/politik/bundestagswahl"
-pat5 <- "tagesschau\\.de/inland"
+pat5 <- "tagesschau.de/inland"
 
-btw %>%
+df %>%
   mutate(politics = ifelse(grepl(paste(pat1,pat2,pat3,pat4,pat5,
-                     sep="|"), url, perl = TRUE),1,0)) -> df_full
+                      sep="|"), url, perl = TRUE),1,0)) -> df
+
+#........................
+# pat <- paste("cdu","csu","union","spd","fdp","afd",
+#              "linkspartei","die linke","die grünen","bündnis 90", sep="|")
+# 
+# df %>%
+#   mutate(politics = ifelse(grepl(pat, title_text, ignore.case = TRUE),1,0)) -> btw1
+
+#df %>% filter(site=="tagesschau.de") %>% select(url)
 ```
@@
 ```{r}
-df_full %>%
-  filter(politics == 1) %>%
-  distinct(url, .keep_all = T) -> btw
+df %>%
+  #filter(politics==1) %>%
+  ggplot(aes(site, fill=factor(politics))) +
+  geom_bar(show.legend = FALSE, alpha=0.8)
+```
+
+```{r}
+btw <- df %>% filter(politics==1)
+```
+
+```{r}
+btw %>%
+  group_by(date, site) %>%
+  dplyr::summarize(obs = n()) %>%
+  ggplot(aes(date, obs, color = factor(site))) +
+  geom_line() +
+  #geom_vline(aes(xintercept=as.Date("2017-09-24")),
+  #           linetype = 2, color="grey40") +
+  #geom_vline(aes(xintercept=as.Date("2017-11-20")),
+  #               linetype = 2, color="grey40") +
+  #scale_color_manual(values = col) +
+  labs(x="", y="Count",color="") +
+  scale_x_date(breaks = date_breaks("2 weeks"), labels=date_format("%d.%m", tz="CET"))
 ```
@@
 ```{r}
-btw %>%
-  filter(text_length > 200) %>%
+btw <- btw %>%
+  filter(text_length > 120) %>%
+  arrange(desc(text_length)) %>%
+  distinct(url, .keep_all = TRUE) %>%
+
   # remove articles that contain daily overviews
-  filter(!grepl("News des Tages", title_text)) %>%
   filter(!grepl("Nachrichten am Morgen", title)) %>%
+  filter(!grepl("elbvertiefung", url)) %>%
+  filter(!grepl("zeit-magazin", url)) %>%
+  filter(!grepl("s-magazin", url)) %>%
+  filter(!grepl("Der Morgen live", title)) %>%
+  filter(!grepl("Die Lage am", title)) %>%
   filter(!startsWith(title,"News")) %>%
+
   # remove articles that only contain video 
   filter(!grepl("Video einbetten Nutzungsbedingungen Embedding Tagesschau", title_text)) %>%
+  filter(!grepl("</div>", title_text)) %>%
+
   # remove english text
   filter(!grepl("bild-international", url)) %>%
+  filter(!grepl("spiegel.de/international", url)) %>%
   filter(!grepl("german",url)) %>%
+  filter(!grepl("arabisch",url)) %>%
+
   # remove text that mostly contain user comments
-  filter(!grepl("kommentar", title, ignore.case = TRUE)) %>%
   filter(!grepl("ticker", title, ignore.case = TRUE)) %>%
   filter(!grepl("stream", title, ignore.case = TRUE)) %>%
-  filter(!startsWith(text,"1.")) -> btw
+  filter(!startsWith(text,"1.")) %>%
+
+  # remove articles behind a pay-wall
+  filter(!grepl("SPIEGEL-Plus-Artikel", text)) %>%
+
+  # remove articles about the weater
+  filter(!grepl("wetter", url))
 ```
@@
 ```{r}
-pat <- "Eine Kolumne von \\w{1,} \\w{1,}"
+pat <- "Wahlprogramm"
 btw %>%
-  filter(grepl(pat, title_text, perl = TRUE, ignore.case = TRUE)) %>%
-  #filter(site=="tagesschau.de") %>%
-  #select(url, title_text) %>% 
-  #.[1,] %>%
-  #htmlTable::htmlTable()
-  group_by(site) %>%
-  tally(sort = TRUE)
+  filter(grepl(pat, title, perl = TRUE, ignore.case = TRUE)) %>%
+  select(title) 
+  #.[2,]
+  #group_by(site) %>%
+  #tally(sort = TRUE)
 ```
@@
 ```{r}
-as.data.frame(str_match(btw$title_text, pat)) ->test
+btw_test <- btw
+
+as.data.frame(str_match(btw_test$title_text , pat)) ->test
+
 test %>%
   filter(!is.na(test)) %>%
-  .[1:30,]
+  .[2,]
 ```
@@
   x = gsub('Aus unserem Netzwerk[^"]*', "", x, perl = TRUE)
+  x = gsub("</div>[^*]*", "", x, perl = TRUE)
 
@@
   x = gsub('Eine Kolumne von Jan Fleischhauer', "", x, perl = TRUE)
+  x = gsub("Wenig Zeit? Am Textende gibt's eine Zusammenfassung", "", x)
+  x = gsub("Twitter: @\\w{1,} folgen Mehr Artikel von \\w{1,} \\w{1,}", "", x, perl = TRUE)
 
@@
   x = gsub("Inhalt Seite", "", x)
+  x = gsub("\\w{1,} \\w{1,} zur Autorenseite", "", x, perl = TRUE)
   x = gsub('Seitennavig[^"]*',"", x, perl=TRUE)
@@
   x = gsub("auswählen", "", x, perl = TRUE)
-  x = gsub("Dieser Artikel wurde ausgedruckt unter der Adresse: www.tagesschau.de/inland/[^.]*", "", x, perl = TRUE)
+  x = gsub("Dieser Artikel wurde ausgedruckt unter der Adresse: [^\\s]*", "", x, perl = TRUE)
   x = gsub("faktenfinder.tagesschau.de", "", x, perl=TRUE)
+
+  # Deutschlandfunk
+  # x = gsub("Äußerungen unserer Gesprächspartner[^.]*", "", x, perl = TRUE)
+  # x = gsub("im Gespräch mit \\w{1,}", "", x, ignore.case = TRUE, perl=TRUE)
+  # x = gsub("Heinlein", "", x, ignore.case = TRUE, perl=TRUE)
+  # x = gsub("Barenberg", "", x, ignore.case = TRUE, perl=TRUE)
+  # x = gsub("Büüsker", "", x, ignore.case = TRUE, perl=TRUE)
+  # x = gsub("Dobovisek", "", x, ignore.case = TRUE, perl=TRUE)
+  # x = gsub("Schmidt-Mattern", "", x, ignore.case = TRUE, perl=TRUE)
+  # x = gsub("Zagatta", "", x, ignore.case = TRUE, perl=TRUE)
+  # x = gsub("Armbrüster", "", x, ignore.case = TRUE, perl=TRUE)
+  # x = gsub("Münchenberg", "", x, ignore.case = TRUE, perl=TRUE)
+  # x = gsub("Heckmann", "", x, ignore.case = TRUE, perl=TRUE)
+  # x = gsub("Kaess", "", x, ignore.case = TRUE, perl=TRUE)
+  # x = gsub("Engels", "", x, ignore.case = TRUE, perl=TRUE)
+  # x = gsub("Zurheide", "", x, ignore.case = TRUE, perl=TRUE)
+  # x = gsub("Marc Müller", "", x, ignore.case = TRUE, perl=TRUE)
 
@@
 btw$text_cleaned <- tolower(btw$text_cleaned)
+
+## Remove stopwords
+# 1
+german_stopwords_full <- read.table("dict/german_stopwords_full.txt", stringsAsFactors = F)
+german_stopwords_full <- german_stopwords_full$V1
+
+# 2
+mystopwords <- c("focus","online","spiegel", "stern", "de", "bild","bildplus","n-tv.de", "zeit", "ersten","ard", "tagesschau","müssen","sagen","faktenfinder", "zeitmagazin","seitenanfang","ja","mal","heute","ich","sie","passwort","kommentar","wurde","ihr","der","im","artikel","mehr","ihren","foto","e","seien","comment","ticker","live","laif","uhr","videolänge","dass","mindestens","das","mail","die","schon","neuer abschnitt", "login", "loggen", "inaktiv","nwmi","wäre","viele","nwnoa","morgenkolumne","beim","dpa","video","quelle","afp","witters","fotogalerie","wurden","worden","wegen","sagt","immer","gibt","geht","spon","registrierter","als","spiegel","vielen","in","es","bitte","dank","unserer","nutzer","sei","beitrag","user","seit","zeichen","tba","datenschutzerklärung","premium","nutzungsbedingungen","nutzungsrechte","pflichtfelder","registrierung","anzeige","großbuchstaben","sonderzeichen","html","seitennavigation","fullscreen","statista","club","sagte","borenda","spreepicture","shopübersicht","herr","imago","dobovisek","barenberg","heinlein","armbrüster","kaess","münchenberg","büüsker","tsereteli","konietzny","klenkes","hauptstadtstudio","newsletter","premiumbereich","nachrichtenpodcast","karrierespiegel","picture alliance","appnutzer","civey","abo")
+
+stopwords <- c(german_stopwords_full, mystopwords)
+stopwords <- unique(stopwords)
+
+# 3
+btw$text_cleaned<- removeWords(btw$text_cleaned, stopwords)
 ```
 
-## Remove Stopwords
+## month & document number
 ```{r}
-btw$text_cleaned<- removeWords(btw$text_cleaned, stopwords("german"))
+btw %>%
+  mutate(month = month(date),
+         week = week(date),
+         articleID = as.numeric(rownames(btw)),
+         site = ifelse(site=="bild.de","Bild.de",site),
+         site = ifelse(site=="focus.de","FOCUS ONLINE",site),
+         site = ifelse(site=="spiegel.de","SPIEGEL ONLINE",site),
+         site = ifelse(site=="zeit.de","ZEIT ONLINE",site),
+         site = ifelse(site=="tagesschau.de","Tagesschau.de",site)) -> btw
 ```
 
-### Remove customized stopwords
 ```{r}
-mystopwords <- c("focus","online","spiegel", "stern", "de", "bild","bildplus", "zeit", "ersten", "tagesschau", "zeitmagazin","seitenanfang","ja","mal","heute","ich","sie","passwort","kommentar","wurde","ihr","der","im","artikel","mehr","ihren","foto","e","seien","comment","ticker","live","laif","uhr","videolänge","dass","mindestens","das","mail","die","schon","neuer abschnitt", "login", "loggen", "inaktiv","nwmi","wäre","viele","nwnoa","morgenkolumne","beim","dpa","video","quelle","afp","witters","fotogalerie","wurden","worden","wegen","sagt","immer","gibt","geht","spon","registrierter","als","spiegel","vielen","in","es","bitte","dank","unserer","nutzer","sei","beitrag","user","seit","zeichen","tba","datenschutzerklärung","premium","nutzungsbedingungen","nutzungsrechte","pflichtfelder","registrierung","anzeige","großbuchstaben","sonderzeichen","html","seitennavigation","fullscreen","statista","club","sagte","borenda","spreepicture","shopübersicht")
+save(btw, file="../output/btw_combined.Rda")
+```
 
-mystopwords <- distinct(as.data.frame(mystopwords))
+## Stemming
+```{r }
+stem_text<- function(text, language = "porter", mc.cores = 1) {
+  # stem each word in a block of text
+  stem_string <- function(str, language) {
+    str <- strsplit(x = str, split = "\\s")
+    str <- wordStem(unlist(str), language = language)
+    str <- paste(str, collapse = " ")
+    return(str)
+  }
 
-btw$text_cleaned<- removeWords(btw$text_cleaned, mystopwords$mystopwords)
+  # stem each text block in turn
+  x <- mclapply(X = text, FUN = stem_string, language, mc.cores = mc.cores)
+
+  # return stemed text blocks
+  return(unlist(x))
+}
+
+btw$text_cleaned1 <- stem_text(btw$text_cleaned)
+```
+
+```{r}
+save(btw, file="../output/btw_combined.Rda")
 ```
@@
   group_by(site) %>%
-  unnest_tokens(word, title) %>%
-  count(site, word, sort = TRUE)  %>%
+  unnest_tokens(word, text_cleaned1) %>%
+  dplyr::count(site, word, sort = TRUE)  %>%
   bind_tf_idf(word, site, n) %>%
-  arrange(desc(tf_idf))
+  dplyr::arrange(desc(tf_idf))
 
@@
 
-## Stemming (not applied)
-```{r }
-stem_text<- function(text, language = "porter", mc.cores = 1) {
-  # stem each word in a block of text
-  stem_string <- function(str, language) {
-    str <- strsplit(x = str, split = "\\s")
-    str <- wordStem(unlist(str), language = language)
-    str <- paste(str, collapse = " ")
-    return(str)
-  }
+# Structural Topic Model
 
-  # stem each text block in turn
-  x <- mclapply(X = text, FUN = stem_string, language, mc.cores = mc.cores)
+## Preparation
+### Build Corpus
+```{r eval=FALSE, include=FALSE}
+# Process data
+processed1 <- textProcessor(btw$text_cleaned, metadata = btw[,c("site","text_cleaned","month")],
+                           wordLengths = c(2,Inf),
+                           lowercase = F,
+                           removestopwords = F,
+                           removenumbers = F,
+                           removepunctuation = F,
+                           stem = F)
+out1 <- prepDocuments(processed1$documents, processed1$vocab, processed1$meta)
 
-  # return stemed text blocks
-  return(unlist(x))
-}
+processed2 <- textProcessor(btw$text_cleaned1, metadata = btw[,c("site","text_cleaned1","month")],
+                           wordLengths = c(2,Inf),
+                           lowercase = F,
+                           removestopwords = F,
+                           removenumbers = F,
+                           removepunctuation = F,
+                           stem = F)
+out_stemmed <- prepDocuments(processed2$documents, processed2$vocab, processed2$meta)
 
-btw$text_cleaned <- stem_text(btw$text_cleaned)
+save(btw, out1, out_stemmed, file="../output/btw_combined.Rda")
 ```
 
-# Add new variables
-## FB Shares
+# FB Shares
 ```{r}
@@
 ```
-
-## month & document number
-```{r}
-btw %>%
-  mutate(month = month(date),
-         articleID = as.numeric(rownames(btw)),
-         site = ifelse(site=="bild.de","Bild.de",site),
-         site = ifelse(site=="focus.de","FOCUS ONLINE",site),
-         site = ifelse(site=="spiegel.de","SPIEGEL ONLINE",site),
-         site = ifelse(site=="zeit.de","ZEIT ONLINE",site),
-         site = ifelse(site=="welt.de","DIE WELT",site)) -> btw
-```
-
-```{r}
-save(btw, file="../output/btw_combined.Rda")
-```

### 2018-01-19 paper/R/03_stm.Rmd
bla

@@
   library(tidyr)       # Reshaping
-  library(magrittr)    # Advanced piping
   library(pushoverr)   # Pushover notifications
-  library(doMC)        # Parallel Computing
   library(readr)       # Importing data
@@
 
-  library(tidytext)    # Tidy text mining
-  library(tm)    # Tidy text mining
-  library(hunspell)    # Text processing
   library(stringdist)  # String distances
-  library(topicmodels) # Topic modelling
   library(stm)         # Sructural Topic Model
   library(proxy)       # Distance measures
-  library(SnowballC)   # Stemming
 })
@@
 # Process data
-processed <- textProcessor(btw$text_cleaned, metadata = btw[,c("site","text_cleaned","week")],
+processed <- textProcessor(btw$text_cleaned, metadata = btw[,c("site","text_cleaned","month","week")],
                            wordLengths = c(2,Inf),

### 2018-01-19 paper/R/paper.Rmd
bla

@@
 
-```{r}
-suppressPackageStartupMessages({
+```{r include=FALSE}
+library(ggplot2)     # Static data visualization
 library(dplyr)       # Data manipulation
@@
 library(pushoverr)   # Pushover notifications
-  library(doMC)        # Parallel Computing
 library(readr)       # Importing data
-  library(tibble)      # Better data frames
 library(data.table)
-  library(pscl)
-  library(boot)
 library(stm)
@@
 
-  library(ggplot2)     # Static data visualization
+library(igraph)
 library(ggpmisc)
@@
 library(ggrepel)
-  library(htmlwidgets)
-  library(plotly)
+#library(plotly)
 library(scales)      # Scales
@@
 library(proxy)       # Distance measures
-})
+
+library(htmlwidgets) # JS visuliaztions
+library(htmltools)   # Arbitrary html
 
@@
     theme(
-      plot.title = element_text(face = "bold", size = 14,
+      plot.title = element_text(size = 10,
                                 margin = margin(0, 0, 4, 0, "pt")),
       plot.subtitle = element_text(size = 12),
-      plot.caption = element_text(size = 6, hjust = 0),
-      axis.title = element_text(size = 10),
+      plot.caption = element_text(size = 6),
       panel.border = element_blank()
@@
 rm(list=ls())
-col <- brewer.pal(6,"Dark2")
+col <- brewer.pal(5,"Dark2")
 ```
 
-# Load Data
+# The online news market
+
+## Pageviews
+```{r}
+views1 <- read.csv("../data/alexa/Historical_Traffic_Trends__Pageviews_Percent_1.csv", comment.char="#")
+views2 <- read.csv("../data/alexa/Historical_Traffic_Trends__Pageviews_Percent_2.csv", comment.char="#")
+
+views <- left_join(views1, views2 %>% 
+                     select(-Metric), by = "Date") %>%
+  mutate(date = as.Date(Date, "%m/%d/%Y")) %>%
+  select(- c(Metric,Date)) %>%
+  gather(key="site", value="views", focus.de:tagesspiegel.de)
+```
+
+```{r}
+# keeps <- c("spiegel.de", "focus.de", "zeit.de","bild.de",
+#           "tagesschau.de")
+#drop <- c("stern.de","sueddeutsche.de")
+
+# reach <- reach %>% 
+#   mutate(date = as.Date(Date, "%m/%d/%Y")) %>%
+#   select(- c(Metric,Date)) %>%
+#   gather(key="site", value="reach", focus.de:n.tv.de) %>%
+#  filter(!site %in% drop) %>%
+#   mutate(site = ifelse(site=="bild.de","Bild.de",site),
+#        site = ifelse(site=="focus.de","FOCUS ONLINE",site),
+#        site = ifelse(site=="spiegel.de","SPIEGEL ONLINE",site),
+#        site = ifelse(site=="zeit.de","ZEIT ONLINE",site),
+#        site = ifelse(site=="tagesschau.de","Tagesschau.de",site),
+#        site = ifelse(site=="zdf.de","ZDF.de",site),
+#        site = ifelse(site=="welt.de","DIE WELT",site),
+#        site = ifelse(site=="n-tv.de","n-tv.de",site))
+
+```
+
+```{r}
+p1 <- views %>%
+  filter(date > as.POSIXct("2017-05-31")) %>%
+  ggplot(aes(date, views, color=site)) +
+  geom_line(show.legend = F) +
+  geom_text_repel(data = views[views$date==max(views$date), ],
+                  aes(date, views, label=site),
+                  size=2.8, show.legend = F, seed = 5) +
+  scale_x_date(limits = c(as.Date("2017-05-31"),as.Date("2018-02-15")),
+               breaks = date_breaks("1 month"), 
+               labels=date_format("%B %y", tz="CET")) +
+  theme(
+      #legend.position   = "none",
+      legend.text       =  element_text(size=6),
+      plot.background   = element_rect("#fafafa", "#fafafa"),
+      panel.background  = element_rect("#fafafa"),
+      axis.title.x      = element_blank(),
+      axis.text.y       = element_text(size = 8)
+    ) +
+  labs(x="", y="pageviews", color="", title = "", 
+      caption = "Source: Alexa Internet, Inc. (www.alexa.com)" )
+
+p1
+
+ggsave(plot= p1,
+filename = "../figs/reach.png", device = "png",
+width = 6, height = 4,
+        dpi = 600
+)
+```
+
+```{r}
+# calculate percentual change
+views$perc_change <- (views$views - lag(views$views, n=1)) / (views$views*100)
+
+p1 <- views %>% 
+  filter(date >= as.Date("2017-09-17") &
+                   date <= as.Date("2017-10-01")) %>%
+  ggplot(aes(date, perc_change, color=factor(site))) +
+  geom_line(show.legend = F) +
+  geom_text_repel(data = views[views$date=="2017-09-24", ],
+                  aes(date, perc_change, label=site),
+                  size=2.8, show.legend = F, seed = 5) +
+  #scale_color_manual(values = brewer.pal(8,"Dark2")) +
+  scale_x_date(breaks = date_breaks("1 day"), labels=date_format("%d.%m.", tz="CET")) +
+  labs(x="",y="% change", color="") +
+  theme(
+      legend.text       =  element_text(size=6),
+      plot.background   = element_rect("#fafafa", "#fafafa"),
+      panel.background  = element_rect("#fafafa"),
+      axis.title.x      = element_blank(),
+      axis.text.y       = element_text(size = 8)
+    )
+
+p1
+
+ggsave(plot= p1,
+filename = "../figs/perc_change.png", device = "png",
+width = 6, height = 4,
+        dpi = 600
+)
+```
+
+## Traffic source
+
+```{r}
+source1 <- read.csv("../data/alexa/Traffic_Sources_1.csv", 
+                    comment.char="#", stringsAsFactors = F)
+source2 <- read.csv("../data/alexa/Traffic_Sources_2.csv", 
+                    comment.char="#", stringsAsFactors = F)
+
+source <- left_join(source1, source2,
+                    by=c("Date","Metric")) %>%
+  select(- c(Date)) %>%
+  gather(key="site", value="traffic", 
+         focus.de:tagesspiegel.de)
+```
+
+```{r}
+p1 <- ggplot(source, aes(site, traffic, fill=Metric,
+                   label = round(traffic, digits = 2))) +
+  geom_col(alpha = 0.8) +
+  geom_text(size = 2, position = position_stack(vjust = 0.5)) +
+  labs(x = "", y = "Percentage of total traffic", 
+       caption = "Source: Alexa Internet, Inc. (www.alexa.com)") +
+  theme(axis.text.x = element_text(angle = 45, size = 7 ))
+
+p1
+
+ggsave(plot= p1,
+filename = "../figs/traffic_source.png", device = "png",
+width = 6, height = 4,
+        dpi = 600
+)
+```
+
+## Keywords
+```{r message=FALSE, warning=FALSE}
+setwd("../data/alexa/keywords/")
+filenames <- list.files(pattern = ".tsv$")
+
+# create an empty list that will serve as a container to receive the incoming files
+list.data<-list()
+
+# create a loop to read in your data
+for (i in 1:length(filenames)) {
+  list.data[[i]]<-read.delim(filenames[i], comment.char="#")
+}
+
+# Create DF
+keywords.df <- as.data.frame(list.data[1])
+
+for (i in 2:length(filenames)) {
+  keywords.df <- rbind(keywords.df, as.data.frame(list.data[i]))
+}
+```
+
+```{r}
+keepsite <- c("tagesschau.de", "spiegel.de", "zeit.de", "deutschlandfunk.de",
+              "zdf.de", "bild.de", "welt.de", "stern.de", "sueddeutsche.de", "focus.de")
+
+keywords.df <- keywords.df %>% 
+  filter(nchar(as.character(site))>1)
+#  filter(site %in% keepsite)
+
+unique(keywords.df$site)
+```
+
+### Search Traffic %
+```{r}
+p1 <- keywords.df %>%
+  arrange(desc(Percent_of_traffic)) %>%
+  group_by(site) %>%
+  top_n(10, Percent_of_traffic) %>%
+  ungroup() %>%
+  ggplot(aes(reorder(term, Percent_of_traffic), 
+             Percent_of_traffic, fill=site)) +
+  geom_col(show.legend = FALSE) +
+  theme_bw(base_family = "Roboto", base_size = 4) +
+  coord_flip() +
+  facet_wrap(~site, scales = "free") +
+  labs(x= "", y = "Search traffic %", 
+       title = "",
+       caption = "Source: Alexa Internet, Inc. (www.alexa.com)")
+
+p1
+
+ggsave(plot= p1,
+filename = "../figs/search_traffic.png", device = "png",
+width = 7, height = 4,
+        dpi = 600
+)
+```
+
+### Share of voice
+```{r}
+keyword1 <- c("nachrichten", "news", "bundestagswahl 2017",
+            "groko", "jamaika")
+
+keyword2 <- c("cdu","csu","spd","fdp","afd",
+           "die linke","die grünen")
+
+```
+
+```{r}
+p1 <- keywords.df %>%
+  filter(term %in% keyword1) %>%
+  ggplot(aes(site,
+             Share_of_voice, fill=term)) +
+  geom_col(show.legend = F) +
+  coord_flip() +
+  facet_grid(~term, scales = "free") +
+  labs(x= "", y = "Share of voice",
+       title = ""
+       )
+
+p1
+
+ggsave(plot= p1,
+filename = "../figs/keywords1.png", device = "png",
+width = 6, height = 4,
+        dpi = 600
+)
+```
+
+```{r}
+p1 <- keywords.df %>%
+  filter(term %in% keyword2) %>%
+  ggplot(aes(site,
+             Share_of_voice, fill=term)) +
+  geom_col(show.legend = F) +
+  coord_flip() +
+  facet_grid(~term) +
+  labs(x= "", y = "Share of voice",
+       caption = "
+  Source: Alexa Internet, Inc. (www.alexa.com)
+      ",
+       title = ""
+       )
+
+p1
+
+ggsave(plot= p1,
+filename = "../figs/keywords2.png", device = "png",
+width = 6, height = 4,
+        dpi = 600
+)
+```
+
+## Audience Network
+```{r}
+focus <- read.csv("../data/audience_network/Audience_Overlap_1_15_2018_focus.csv", header=FALSE, comment.char="#")
+spiegel <- read.csv("../data/audience_network/Audience_Overlap_1_15_2018_spiegel.csv", header=FALSE, comment.char="#")
+bild <- read.csv("../data/audience_network/Audience_Overlap_1_15_2018_bildde.csv", header=FALSE, comment.char="#")
+zeit <- read.csv("../data/audience_network/Audience_Overlap_1_15_2018_zeitde.csv", header=FALSE, comment.char="#")
+tagesschau <- read.csv("../data/audience_network/Audience_Overlap_1_15_2018_tagesschau.csv", header=FALSE, comment.char="#")
+
+zdf <-  read.csv("../data/audience_network/Audience_Overlap_1_15_2018_zdf.csv.crdownload.csv", header=FALSE, comment.char="#")
+#stern <- read.csv("../data/audience_network/Audience_Overlap_1_15_2018_stern.csv", header=FALSE, comment.char="#")
+welt <- read.csv("../data/audience_network/Audience_Overlap_1_15_2018 _welt.csv", header=FALSE, comment.char="#")
+```
+
+```{r}
+focus <- focus[-1,1:2] 
+colnames(focus) <- c("site","focus.de")
+
+spiegel <- spiegel[-1,1:2] 
+colnames(spiegel) <- c("site","spiegel.de")
+
+bild <- bild[-1,1:2] 
+colnames(bild) <- c("site","bild.de")
+
+zeit <- zeit[-1,1:2] 
+colnames(zeit) <- c("site","zeit.de")
+
+tagesschau <- tagesschau[-1,1:2] 
+colnames(tagesschau) <- c("site","tagesschau.de")
+
+zdf <- zdf[-1,1:2] 
+colnames(zdf) <- c("site","zdf.de")
+
+welt <- welt[-1,1:2] 
+colnames(welt) <- c("site","welt.de")
+```
+
+```{r}
+# combine dataframes
+network_df <- left_join(focus[1:80,], spiegel[1:80,], by="site") %>%
+  left_join(., bild[1:80,], by = "site") %>%
+  left_join(., zeit[1:80,], by = "site") %>%
+  left_join(., tagesschau[1:80,], by = "site") %>%
+  left_join(., zdf[1:80,], by = "site") %>%
+  left_join(., welt[1:80,], by = "site")
+
+network_df <- na.omit(network_df)
+
+melted <- network_df %>%
+    gather(key="seed", value="score", focus.de:welt.de) %>%
+  mutate(score = as.integer(score),
+         site = as.factor(site),
+         seed = as.factor(seed))
+```
+
+```{r}
+p1 <- ggplot(melted, aes(seed, site, fill=score)) +
+  geom_tile() +
+  scale_fill_gradient(low="gray95",high=col[3]) +
+  scale_x_discrete(labels=c("bilde.de" = "Bild.de", 
+                            "focus.de" = "FOCUS ONLINE", 
+                            "spiegel.de" = "SPIEGEL ONLINE",
+                            "tagesschau.de" = "Tagesschau.de", 
+                            "welt.de" ="DIE WELT",
+                            "zdf.de" = "ZDF.de",
+                            "zeit.de" = "ZEIT ONLINE")) +
+  labs(x="", y="",  caption = "
+  Source: Alexa Internet, Inc. (www.alexa.com)
+      ") +
+  theme(
+      legend.text       =  element_text(size=6),
+      plot.background   = element_rect("#fafafa", "#fafafa"),
+      panel.background  = element_rect("#fafafa"),
+      axis.title.x      = element_blank(),
+      axis.text.x = element_text(size=8, angle = 45),
+      axis.text.y       = element_text(size = 8)
+    )
+
+ggsave(plot= p1,
+filename = "../figs/audience.png", device = "png",
+width = 5, height = 6,
+        dpi = 600
+)
+
+p1
+```
+
+# Data
+
 ```{r caching, echo = FALSE}
-#load("../output/models/STM 80 .Rda")
 load("../output/btw_combined.Rda")
@@
 
-### Distribution of articles
+## Distribution of articles
 ```{r message=FALSE, warning=FALSE}
@@
   geom_bar(fill=col, alpha= .8) +
-  labs(x="", y="Count") +
+  labs(x="", y="Number of articles") +
   theme(
@@
 # Model Results
+
+```{r caching, echo = FALSE}
+#load("../output/models/STM 60 .Rda")
+```
+
 ```{r Extract wtp and dtp}
@@
 stmOut %>% tidy("gamma") -> posts.dtp
-```
 
-## Topic Labeling
-```{r Label Topics}
+##################
+# Topic Labeling #
+##################
 label <- labelTopics(stmOut, n=5)
-
-# topicLabel <- as.data.frame(label$topics)
-# 
-# topicLabel <- topicLabel %>% 
-#   transmute(topic = rownames(.),
-#              topic_name = paste(V1,V2,V3,V4,V5, sep=","))
 
@@
   transmute(topic = rownames(.),
-            topic_name = paste(prob$V1,prob$V2,prob$V3,score$V1,score$V2,score$V3, sep=","),
+            topic_name = paste(topic,": ",prob$V1,prob$V2,prob$V3,score$V1,score$V2,score$V3, sep=","),
             prob = paste(prob$V1,prob$V2,prob$V3, sep=","),
@@
 rm(prob, frex, lift, score)
-```
 
-```{r}
-labelTopics(stmOut, 57, n=15)
-```
+####################################################
+# Assign topic with highest gamma to each document #
+####################################################
 
-```{r}
 top_topics <-
@@
 
-# Add Topic to origian DF
-btw$articleID = as.numeric(rownames(btw))
-
 btw %>%
@@
               select(topic_name, topic) %>%
-              mutate(topic = as.numeric(topic)), by="topic") -> btw
+              mutate(topic = as.numeric(topic)), by="topic") %>%
+  filter(gamma >= 0.5) %>%
+  mutate(allocation = 1) -> btw
 ```
 
-## Topic Proportion
-```{r fig.height=12, fig.width=9}
-#library(stm)
-#png("../figs/topic_proportion.png")
-plot(stmOut, type = "summary", xlim = c(0,.5), n = 5, 
-     custom.labels = topicLabel$topic_name, 
-     family = "Roboto", main = "", text.cex = 0.8)
-#dev.off()
+After reviewing a sample of articles assigned to the respective topic, we assign a shorter name to the topics based on the most common words in order to improve readability and traceability.
+
+```{r}
+btw %>% group_by(topic, site) %>%
+  select(topic_name, title) %>% top_n(3) %>%
+  arrange(topic) %>%
+  htmlTable::htmlTable(align="l")
 ```
@@
 ```{r}
-btw %>% filter(grepl("zagatta", text_cleaned)) %>% select(url)
+topic_name <- c("1: A.Merkel & K.-T.z.Guttenberg","2: SPD (Schulz,Nahles)","3: Election in Niedersachsen","4: Election campaigns", 
+                "5: car industry, diesel", "6: exploratory talks CDU/SPD","7: exploratory talks Jamaika",
+                "8: people in GER, christmas speech Steinmeier", "9: CSU (Seehofer,Söder)", "10: Federal Election (various)",
+                "11: Schulz, TV-Duell", "12: G20 riots", "13: digital & telecommunication topics","14: regional politics", 
+                "15: text-processing failure", "16: Turkey (Erdoğan)", "17: Federal statistics", "18: various electoral districts", 
+                "19: SPD (Nahles, Geißler, Klingbeil,...)", "20: EU policies, refugee debate", "21: poll results", 
+                "22: FDP (C.Lindner)", "23: election campaign A.Merkel (riots finsterwalde)", "24: Armed Forces (v.d.Leyen)", 
+                "25: Twitter fail", "26: AfD internal party structures", "27: H.Maas, Facebook, social media", 
+                "28: SPD (Schwesig), women, sexism", "29: USA, D.Trump, UN-climate conference", "30: same-sex marriage vote", 
+                "31: DIE LINKE", "32: Muslims in GER, anti-Semitism", "33: S.Gabriel, G.Schröder, Russia", 
+                "34: AfD (Gauland, Höcke,...)", "35: BAMF, BND, BKA", "36: church, people", "37: political talkshows", 
+                "38: legal judgments (linksunten, insider trading, ...)", "39: Bundestag (AfD, Schäuble, Lammert)",
+                "40: refugees, deportation", "41: Terrorism in GER (NSA)", "42: refugee cap, family reunion", 
+                "43: general statistics", "44: AfD general", "45: RAF, Steinmeier", "46: Glyphosat, Schmidt, (green) policy",
+                "47: Terror attacks in GER (Breitscheidplatz)", "48: crime, healthcare statistics", "49: Helmut Kohl", "50: Muslims in GER", "51: SPD, Schulz", "52: Glyphosat scandal",
+                "53: Attack in Hamburg", "54: A.Merkel (pension policy)", "55: H.Kohl", "56: Election in Niedersachsen, various", 
+                "57: Terrorism, Rock am Ring", "58: Guttenberg, CSU", "59: CDU/SPD coalition", "60: statistics about crimes&terrorism")
+
+topic_name <- as.data.frame(topic_name) %>%
+  mutate(topic = seq(1:60))
+
+btw <- btw %>% select(- topic_name) %>%
+  left_join(., topic_name, by = "topic")
+
+btw %>% filter(topic==24 & site=="SPIEGEL ONLINE") %>% select(text_cleaned1) %>% .[2,]
 ```
 
+Figure \ref{fig_topic_proportion} displays the topics ordered by their expected frequency across the corpus.
+To assign a label to each topic, we used a combination of most frequent words in that topic and words with the highest "score", computed as the log frequency of the word in the topic divided by the log frequency of the word in other topics \citep{roberts_stm:_2016}.
+The most frequent topic (4) describes the exploratory talks between the CDU/CSU, FDP and Bündnis90/Die Grünen following the federal elections.
+This is followed by topic 32, which classifies articles that deal with the NSU trial and the main defendant Zschäpe.
+
 ```{r}
-keeps <- c(7,27,46,24,18,16,49,9,38,57,59,36,13)
+frequency <- as.data.frame(colMeans(stmOut$theta)) %>% 
+  mutate(frequency = colMeans(stmOut$theta),
+    topic=as.character(seq(1:40))) %>%
+  left_join(., topicLabel %>% select(topic, topic_name),
+            by="topic")
+
+ggsave(plot = {
+  ggplot(frequency, aes(x=reorder(topic_name, frequency), y=frequency)) + 
+    geom_col(fill=col[1], alpha=0.8) +
+    coord_flip() +
+    labs(x="", y="expected frequency") +
+    theme(axis.text = element_text(size=10))
+}, filename = "../figs/topic_proportion.png", device = "png",width = 8, height = 12,
+dpi = 600)
 ```
+
+![Topic Proportion](../figs/topic_proportion.png)
 
@@
   posts.dtp %>% 
-  filter(topic %in% keeps) %>%
+  #filter(topic %in% keeps) %>%
   group_by(articleID = document) %>% 
@@
   ungroup() %>%
-  inner_join(btw %>% filter(topic %in% keeps) %>%
+  inner_join(btw %>% 
+               #filter(topic %in% keeps) %>%
                select(title, title_text, articleID, topic_name, site),
@@
   group_by(topic_name, site) %>% 
-  top_n(50, gamma) %>%
-  sample_n(3) %>%
+  top_n(10, gamma) %>%
+  sample_n(3, replace = TRUE) %>%
   mutate(row = row_number()) %>% 
@@
 ```{r}
-prep <- estimateEffect(keeps ~site + s(week),
-                       stmOut, meta=out$meta, uncertainty = "Global")
+prep <- estimateEffect(1:40 ~site + s(month),
+                       stmOut, meta=out_stemmed$meta, uncertainty = "Global")
 ```
@@
 ```{r}
-for (i in keeps){
+for (i in 1:40){
 
@@
        ylab = "", xlab = "Mean topic proportion in corpus",
-       main = paste0("Topic ",i,": ",topicLabel$topic_name[i]),
+       main = paste0("Topic ",topicLabel$topic_name[i]),
        xlim = c(-.05,0.2))
@@
 ```{r}
-for (i in keeps){
-  plot(prep, "week", method = "continuous", topics = i,
-       printlegend = F,
-       ylab = "", xlab = "Mean topic proportion in corpus",
-       main = paste0("Topic ",i,": ",topicLabel$topic_name[i]))
-}
-
+# for (i in 1:40){
+#   plot(prep, "month", method = "continuous", topics = i,
+#        printlegend = F,
+#        ylab = "", xlab = "Mean topic proportion in corpus",
+#        main = paste0("Topic ",i,": ",topicLabel$topic_name[i]))
+# }
 ```
@@
   left_join(., btw %>% select(document, topic_name,
-                              site, week),
+                              site, month),
             by="document")  %>%
-  group_by(site, topic, topic_name, week) %>%
+  group_by(site, topic, topic_name, month) %>%
   summarize(gamma_mean = mean(gamma)) %>%
   #filter(month!=5) %>%
-  ggplot(aes(x=week, y=gamma_mean, fill=factor(topic), text=topic_name)) +
+  ggplot(aes(x=month, y=gamma_mean, fill=factor(topic), text=topic_name)) +
   geom_col() +
@@
   theme(legend.position = "none") +
-  xlab("Proportion")
+  xlab("Month")
 
@@
   btw %>%
-    filter(topic %in% keeps) %>%
+    #filter(topic %in% keeps) %>%
   ggplot(aes(gamma)) +
@@
 
-filter documents with low posterior
-```{r}
-btw.reg <- btw %>%
-  filter(topic %in% keeps) %>%
-  filter(gamma >= 0.5) %>%
-  mutate(allocation = 1)
-```
-
 ## Topic Timeline
@@
        aes(post_period, articles, color=topic_name)) +
-  geom_line() +
+  geom_line(show.legend = FALSE) +
   scale_color_manual(
-            values = rainbow(20) %>% 
+            values = rainbow(60) %>% 
               adjustcolor(red.f = 0.6, green.f = 0.6, blue.f = 0.6)
           ) +
-  geom_text_repel(data=subset(chart_topic_trends.dt,peak==1),
-            aes(post_period,articles,label=paste(topic,topic_name,sep=":")),
+      geom_text_repel(data= subset(chart_topic_trends.dt,peak==1 & articles >=25),
+            aes(post_period,articles,label=topic_name), vjust = -1, size = 2,
             size=2.8) +
@@
                  linetype = 2, color="grey20") +
-  ylim(c(0,200)) +
+  ylim(c(0,120)) +
     theme(
@@
 
-```{r Data for topic distribution chart}
+```{r}
+library(radarchart)
+```
 
-set.seed(7292)
-btw.reg %>% 
-    mutate(document = articleID) %>%
+```{r}
+btw %>% 
   group_by(site, topic, topic_name) %>%
-  summarise(
-    articles = sum(allocation),
-    sample_articles = 
-      paste0(
-        "<li>", sample(title, pmin(3, length(document))), "</li>",
-        collapse = "<br>"
-      )
-  ) %>%
+  summarise(articles = sum(allocation)) %>%
   ungroup() %>%
@@
   ungroup() %>%
-  mutate(
-    tooltip_text = 
-      paste0(
-        "<b>", comma(round(articles, 0)), " (", percent(perc_articles), 
-        ") </b> of articles from <b>", site, 
-        "</b> fall under <b>", "Topic",topic,": ", topic_name, "</b><br><br>Sample Articles:<br><ul>",
-        sample_articles, "</ul>"
-      ) %>% str_replace_all("'", "")
-  ) ->
-  news_page_distribution.dt
+  transmute(site=site,
+            perc_articles=perc_articles,
+            topic=topic_name) %>%
+  spread(key=site, value=perc_articles) %>%
+  ungroup() %>%
+  mutate(topic=factor(topic)) -> radar
 ```
 
-```{r Topic distribution chart, eval = TRUE}
-{
-  news_page_distribution.dt %>% 
-    ggplot(aes(x = site, y = perc_articles, fill = topic_name)) +
-    geom_bar_interactive(
-      aes(tooltip = tooltip_text),
-      position = position_stack(), 
-      stat = "identity", color = "darkgray"
-    ) +
-    scale_y_continuous(
-      name = "Percent of Articles", 
-      labels = percent,
-      expand = c(0, 0)
-    ) +
-    theme(
-      legend.position = "none",
-      axis.title.y = element_blank(),
-      legend.background = element_rect("#fafafa"),
-      plot.background   = element_rect("#fafafa", "#fafafa"),
-      plot.subtitle     = element_text(size = 8),
-      plot.caption      = element_text(size = 7),
-      plot.title        = element_text(size = 18)
-    ) +
-    coord_flip() +
-    scale_fill_viridis(discrete = TRUE) +
-    labs(
-      title = ""
-    )
-} %>% 
-  ggiraph(
-    ggobj = .,
-    width_svg = 12,
-    height_svg = 8,
-    width = 1,
-    tooltip_extra_css = "
-    font-family: Roboto; 
-    background-color: #000; 
-    color: #fff; font-size: 10px;
-    padding: 5px;"
-  ) -> chart_topic_distribution.wdgt
-
-saveWidget(
-  widget = chart_topic_distribution.wdgt,
-  file = "../figs/04-topic-distribution-pages.html",
-  selfcontained = FALSE,
-  libdir = "../figs/js",
-  background = "#fafafa"
-)
-
-chart_topic_distribution.wdgt
-
+```{r}
+chartJSRadar(scores = radar, labelSize = 9, maxScale = 0.1, 
+             showToolTipLabel = TRUE,
+             width = 8, height = 8)
 ```
@@
 ## Sentiment analysis
+
+```{r}
+sent <- c(
+  # positive Wörter
+  readLines("dict/SentiWS_v1.8c_Negative.txt",
+            encoding = "UTF-8"),
+  # negative Wörter
+  readLines("dict/SentiWS_v1.8c_Positive.txt",
+            encoding = "UTF-8")
+) %>% lapply(function(x) {
+  # Extrahieren der einzelnen Spalten
+  res <- strsplit(x, "\t", fixed = TRUE)[[1]]
+  return(data.frame(words = res[1], value = res[2],
+                    stringsAsFactors = FALSE))
+}) %>%
+  bind_rows %>% 
+  mutate(word = gsub("\\|.*", "", words) %>% tolower,
+         value = as.numeric(value)) %>% 
+  # manche Wörter kommen doppelt vor, hier nehmen wir den mittleren Wert
+  group_by(word) %>% summarise(value = mean(value)) %>% ungroup
+```
+
+```{r, message=FALSE, warning=FALSE, include=FALSE}
+# Tokenize text
+token <- btw %>%
+  unnest_tokens(word, text_cleaned1)
+
+# Combine with sentiment values
+sentDF <- left_join(token, sent, by="word") %>% 
+  mutate(sentiment = as.numeric(value)) %>% 
+  filter(!is.na(sentiment)) 
+```
+
+```{r fig.height=12}
+sentDF %>% group_by(topic_name, site) %>% 
+  summarize(sentiment = mean(sentiment)) %>%
+  ggplot(aes(topic_name, sentiment, fill=site)) +
+  geom_col(fill=col[3], alpha=0.8) +
+    facet_wrap(~site, ncol = 1) +
+    labs(x="", y="sentiment value") +
+    theme(axis.text.x = element_text(size=10, angle = 90))
+```
+
+### Radar plot
+```{r}
+sentDF %>% 
+  select(site, topic_name, sentiment) %>%
+  spread(key=site, value=sentiment) %>%
+  ungroup() -> radar
+```
+
+```{r}
+chartJSRadar(scores = radar, labelSize = 8, maxScale = 1000, showToolTipLabel = TRUE,
+             addDots = FALSE, showLegend = FALSE,
+             width = 8, height = 8)
+```
+
+### Using sentimentr
 ```{r}
@@
 btw.reg %>% 
-  filter(document==4) %>%
+  filter(document==372) %>%
   mutate(text_split = get_sentences(text)) %$%
@@
 
+```{r}
+btw.reg %>% 
+  filter(document==4) %>% select(text_cleaned)
+```
+
 ### Radar
+#### with ggiraphExtra
 ```{r}
@@
   summarize(sentiment = mean(sentiment, na.rm = T)) %>%
-  spread(site, sentiment) %>%
+  spread(topic_name, sentiment) -> radar
   ungroup() %>%
@@
 ggsave(plot={
-  ggRadar(radar, aes(color=topic), rescale = FALSE,
-        legend.position = "none") +
-  facet_wrap(~topic, ncol = 4)
+  ggRadar(radar, aes(color=site), rescale = FALSE,
+        legend.position = "none") 
+  facet_wrap(~topic)
 },
@@
 ```
+
+#### with radarchart
+
+```{r}
+btw.reg %>% 
+  group_by(site, topic, topic_name) %>%
+  summarise(sentiment = mean(sentiment, na.rm = TRUE)) %>%
+  ungroup() %>%
+  transmute(site=site,
+            sentiment=sentiment,
+            topic=paste(topic, topic_name, sep=": ")) %>%
+  spread(key=site, value=sentiment) %>%
+  ungroup() %>%
+  mutate(topic = factor(topic))-> radar
+```
+
+```{r}
+chartJSRadar(scores = radar, labelSize = 8, maxScale = 0.1, showToolTipLabel = TRUE,
+             addDots = FALSE, showLegend = FALSE,
+             width = 8, height = 8)
+```

### 2018-01-19 paper/doc/doc.tex
bla

@@
 \usepackage[toc,page]{appendix}
-\DeclareUnicodeCharacter{20AC}{\euro}
-\usepackage[backend=biber,
-			style=authoryear-comp,
-			isbn=false,
-			doi=false,
-			bibstyle=authoryear,
-			natbib,
-			]{biblatex}
+\usepackage{lscape}
+\usepackage{todonotes}
+\usepackage{booktabs}
+\usepackage{multirow}
+\usepackage{bm}
+\usepackage{eurosym}
+\usepackage{pdflscape}
+
+\addbibresource{Textmining.bib}
 
@@
 
-The debate about the role of public media and their mission in a rapidly changing media world is a recurring theme.
+In Germany, the debate about the role of public media and their mission in a rapidly changing media world is a recurring theme.
+By shifting media content to the Internet, the dual system, which has been shaping the German television and radio landscape since the introduction of private broadcasting in the early 1980s, is facing a radical change.
+Since 2000, public broadcasting has expanded its range of services, particularly in the digital media sector.
 If the right to use digital media were to be withdrawn from the public media outlets, they would not only be deprived of the possibility of improved information provision.
 They also threatened to lose their competitiveness with commercial media.
-But it is precisely this competitiveness that is constitutionally guaranteed.
 On the other hand, there is the concern of commercial providers who are registering an ever-increasing number of digital services financed by fees.
 They complain about a bias in competition caused by public media offering online text-content because of their fee financing.
-The regulator recognizes this inequality and has banned advertising and sponsorship in its online services.
+The advertising-financed business model of the media houses is based on the premise that users visit their websites in order to achieve high advertising revenues.
 
@@
 
-Markt für Online-Texte.
-Presseverlage beklagen immer mehr eine Wettbewerbsverzerrung durch öffentlich-rechtliche Online-Angebote.
-"Wir erleben im Netz nach wie vor eine mit öffentlich-rechtlichen Geldern finanzierte Flut textbasierter Gratis-Angebote, nichts anderes als eine gebührenfinanzierte digitale Staatspresse, die den Wettbewerb verzerrt und uns Presseverlagen kaum Entfaltungsmöglichkeiten lässt" %(http://www.sz-online.de/nachrichten/ard-und-zdf-gebuehrenfinanzierte-staatspresse-3776123.html)
+On the basis of these justifications, this paper examines whether public media offer different content than private providers.
+In other words, whether socially desired content that meets the (social) needs of society and is therefore politically desirable is not provided by the market of private news, but by public providers.
+In order to examine this, the online news content of public media is compared with the supply of private news providers.
 
-Wettbewerb im "Gemischten Oligopol": Die kostenlosen Nachrichtenangebote von ZDF.de oder tagesschau.de im Internet konkurrieren hier mit den Online Angeboten der klassischen Printmedien.
-Die beitragsfinanzierten Angebote behindern in der Tendenz Prozesse, durch die sich ein selbst tragendes, qualitativ hochwertiges Subskriptionssystem privatwirtschaftlicher Anbieter (spiegel.de, faz.net, welt.de, ...) entwickeln kann.
+We use a data set of German online news articles about domestic politics to examine the differences in news content between public and private news provides.
+Your dataset contains articles dated from 01.06.2017 to 31.12.2017\footnote{German federal elections took place on 24th of September 2017.} from seven German content providers to analyze news reports about german elections, where we allow prevalence of topics to evolve over time (before and after the elections) and vary across newswire services.
+We then estimate the effect of news wire source on both topical prevalence (topic distribution) and topical content (word-topic distribution).
 
-\begin{itemize}
-	\item Reserach Question
-	\begin{itemize}
-		\item Analyzing news reports about german elections, where we allow prevalence of topics to evolve over time (before and after the elections) and vary across newswire services.
-		\item Quantify the effect of news wire source on both topical prevalence (topic distribution) and topical content (word-topic distribution).
-	\end{itemize}
-	\item Method
-	\begin{itemize}
-		\item Topical content of documents, in which mixing weights are parameterized by observed covariates
-		\item Topic distribution word-topic distribution are specified as a simple generalized linear model on an arbitrary number of document-level covariates (news source, time of release).
-	\end{itemize}
-\end{itemize}
+Mapping raw text to one or more topics, without having prior knowledge on what those topics are, translates to an unsupervised classification problem on natural language.
+Topic models generate low-dimensional representations of data and can uncover interesting latent structure in large text datasets.
+They are popular tools for automatically identifying prominent themes in text.
+Within topic models the Latent Dirichlet Allocation (LDA) is a widely used technique, where each document (article) is viewed as a mixture of topics (represented by the document-topic distribution) and each topic is a mixture of unique terms, represented by the topic-term distribution \citep{blei_latent_2003}.
+\citet{roberts_model_2016} extents the base idea of LDA by developing a structural topic model (STM) that allows to incorporate external variables that effect both topical content and topical prevalence.
+We use this approach to analyze online news about the german domestic politics, where we allow prevalence of topics to vary across newswire services.
+We then estimate the effect of topical prevalence (the posterior document-topic distribution) on the ownership (public or private).
 
-Text as a data source is becoming increasingly popular in empirical economics, as the information encoded in text is a rich complement to conventional data (e.g.
-price, wage, votes, etc.) (\citet{grimmer_bayesian_2010}; \citet{grimmer_text_2013}; \citet{quinn_how_2010}; \citet{gentzkow_text_2017}; \citet{roberts_model_2016}).
-On interesting question is, how document metadata such as author or date influence its content.
-Depending on the characteristics of a corpus (a collection of documents), documents contain more than one topic, as well as terms most likely appear in multiple topics, thus the use of mixed-membership models \citep{airoldi_handbook_2014} - or topic model as they are often referred in the literature of text analysis \citep{blei_probabilistic_2012} - are a popular approach.
+The paper proceeds as follows: The next section (\ref{ch_onlinenews}) briefly explains the market for online news in Germany.
+We will examine the largest players on the market and use keyword analytics to investigate which providers are similar.
+Section \ref{ch_model} explains the generative process of the mixed membership model and the results of this process are presented in chapter \ref{ch_results}.
+Chapter \ref{ch_data} contains a description of the text data and how it was pre-processed in order to use it as input variable.
+Chapter \ref{ch_regression} describes how we regress the estimated probabilities of topic prevalence of a document on its metadata.
 
-Within these models the Latent Dirichlet Allocation (LDA hencefirth) is a widely used topic modelling technique, where each document is viewed as a mixture of topics (represented by the document-topic distribution) and each topic is a mixture of unique terms (represented by the topic-term distribution).
-To "learn" the topic prevalence and the topic-term distribution, collapsed Gibbs sampling\footnote{See Section \ref{section_gibbs} for a non-formal description of the Gibbs sampler} can be used.
-LDA makes a statistical assumption that all texts in the modeled corpus are generated by the same underlying process \citep{blei_latent_2003}.
-Thus, it is not ideally suited to examining differences in topical content that are affected by covariates such as author identity or time of writing.
+% ----------------------
+% the online news market
+% ----------------------
+\section{The online news market}\label{ch_onlinenews}
 
-\citet{roberts_model_2016} develop a structural topic model (STM) that allows to incorporate external variables that effect both topical content and topical prevalence.
-We use this approach to analyze online news about the german federal elections, where we allow prevalence of topics to change over time (before and after the elections) and vary across newswire services (private or public) to quantify the effect of news wire source on both topical prevalence and topical content.
+The market for media content in Germany is characterized by the coexistence of public and private broadcasters.
+By shifting media content to the Internet, the dual system, which has been shaping the German television and radio landscape since the introduction of private broadcasting in the early 1980s, is facing a radical change.
+Since 2000, public broadcasting has expanded its range of services, particularly in the digital media sector.
+In 2017, 22 own websites and 100 apps were operated by public broadcasters on which they offer their content.
+As a result, public broadcasting no longer only competes with private television and radio stations, but also enters the market for online news.
+In the following, we will briefly discuss the characteristics of the market for online news.
 
-\section{Related Literature}
+Private media outlets naturally appear as two-sided platforms, that allow interaction between two categories of consumers: audiences and advertisers.
+As the demand on both consumer-sides are linked via indirect network externalities, the market in which media outlets operate are referred to as two-sided or multi-sided markets.
+The theoretical literature on two-sided markets originates from the analysis of credit card markets \citep{rochet_platform_2003} and was later transferred to the concept of other industries, such as dating agencies, real estate agents, and internet “business-to-business” websites \citep{caillaud_chicken_2003}.
+The basic concept of two-sided markets was already discussed decades ago in several economic studies, especially on media markets \citep{corden_maximisation_1952}, \citep{gustafsson_circulation_1978}, \citep{blair_pricing_1993}.
+However, comprehensive analyses have only been carried out in the last ten years, starting with the works of \citet{rochet_platform_2003}, \citet{evans_empirical_2003} and \citet{armstrong_competition_2006}.
 
-% Quantitative approaches
-% -----------------------
+Advertising-supported media such as online newspapers are typical examples of two-sided markets where the newspaper can be conceived as platforms that allow interaction between audiences ("eyeballs") and advertisers.
+The newspaper creates (or buys) content to attract viewers which in turn attract advertisers who pay for readers' attention.\cite{evans_industrial_2005} The size and characteristics of the audience has a positive effect on the advertisers' willingness to pay, as advertisements are typically sold based on cost per viewer, often expressed in terms of the cost of reaching a thousand viewers (CPM).
+Advertising can also have an effect on the recipients, which can be both negative and positive, depending on the quality of the advertising.
+Depending on the strength of the indirect network effects, private publisher maximize their revenue by balancing the demand from advertisers and subscribers using different business models \citep{evans_economics_2008}.
+Many traditional newspapers follow the subscription/advertising model, where the publisher charges both market sides: The audience pays a fee to obtain access to the content, and advertisers pay to obtain access to the viewers.
+Many online news agencies provide part of their editorial content for free and hide another, more exclusive part behind a paywall.
+However, since the Internet has considerably simplified the possibilities for obtaining information and thus reduced the marginal utility of content, such a business model can only be efficient if the content is very exclusive.
+As a result, many publishers rely on a free-media model, in which the publishers do not charge viewers for access to the media at all, in order to attract as many eyeballs as possible to their platform, and thus exploit the indirect network effects on the advertising site.
+In fact, most advertising-financed online magazines earn their gross margin from advertising.\cite{evans_industrial_2005} In order to maximize their profits, these companies have an interest in attracting as many readers as possible.
+In addition to the quantity of the audience, the demographic characteristics of recipients also have an influence on the willingness to pay on the advertiser site.
+Online advertising makes it possible to target ads to particular consumers in real time.
 
-% Politics and Newspaper
+The two-sided market structure of the private news markets results in news platforms striving to choose their content in such a way that its reach is as large as possible in order to maximize profits from advertising revenues.
+\citep{steiner_program_1952} concluded, that profit-maximizing media owners may choose to offer the same content, i.e.
+content aligned with the tastes of the majority.
+\citep{gabszewicz_press_2001} study the problem of diversity of the political content of newspapers.
+They find that the maximum differentiation only prevails if the readers sufficiently value the political differentiation between the newspapers the advertising market is small enough.
+On the other hand, advertising may also have a positive impact on the media, as it enables publishers to report independently of political parties.
+\citet{ellman_what_2009} found that advertising increases the intensity of competition for readers and therefore raises accuracy of media coverage.
+
+Given the crucial role of the media in shaping opinion and promoting democracy, pluralism of opinion and accuracy of information is a major concern of public authorities.
+Public broadcasting in Germany originated in the post-war period and has always had the task of providing the entire population with independent media.
+This media offer is intended to guarantee diversity of opinion within the media landscape and to be economically and politically independent.
+The former is given by the fact that the public media are financed by compulsory fees.
+To take into account the distinct nature of digital media, the Interstate Broadcasting Agreement (Rundfunkstaatsvertrag) also regulates the scope for action of online services offered by public service broadcasting since 2007.
+Accordingly, public media are not allowed to distribute purchased content and must - depending on the category of content - set a time limit on its accessibility.
+In addition, there is a strict advertising ban and prohibition of regional reporting.
+
+However, given today's media landscape, the role of public media provider and its mandate is in discussion.
+The basic justification for a public media offer can be roughly divided into two categories: On the one hand, possible market failure and on the other hand, ensuring diversity.
+The former involves the pursuit of non-economic (e.
+g.
+democratic, social and cultural) objectives, as well as the provision of information that would not be made available by the market due to a lack of willingness to pay.
+Ensuring the diversity of media content is intended to counteract possible media bias.
+
+On the basis of these justifications, this paper examines whether imperfections in the market of online news exist.
+In other words, whether socially desired content that meets the (social) needs of society and is therefore politically desirable is not provided by the market.
+In order to examine this, the online news content of public media is compared with the supply of private news providers.
+In the event that there is no market failure in terms of information provision (the contents do not differ), the existence of public media could still be justified by the fact that socially relevant contents of private providers are systematically distorted and the existence of public offerings ensures the diversity of information and opinions transmitted.
+
+\subsection{Competitors}
+
+Figure \ref{fig_reach} shows the largest providers of online news in terms of daily pageviews.\footnote{The figure shows the estimated percentage of daily pageviews on the internet that occurred on a specific website.} It is striking that SPIEGEL ONLINE has the greatest reach over the entire course of time followed by Bild.de.
+Looking at the percentage change of pageviews on the election day, increase is highest for Tagesschau.de followed by Tagesspiegel.de, whereas Huffingtonpost.de and Bild.de have the lowest increase (see figure \ref{fig_change}).
+
+\begin{figure}[H]
+	\caption{}
+	\begin{center}
+		\begin{subfigure}[normla]{0.49\textwidth}
+			\includegraphics[width=\textwidth]{../figs/reach.png}
+			\caption{Percentage of daily pageviews}
+			\label{fig_reach}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.49\textwidth}
+			\includegraphics[width=\textwidth]{../figs/perc_change.png}
+			\caption{Percentage change of pageviews}
+			\label{fig_change}
+		\end{subfigure}
+	\end{center}
+\end{figure}
+
+Users can access a website either directly or through an intermediary, such as search engines or social media.
+As the figure \ref{fig_traffic} illustrates\footnote{The figure shows the percentage of total traffic by a source for the time period 18.12.2017-18.01.2017}, direct access\footnote{Direct traffic includes: Direct navigation (Someone types the website URL into a browser); Bookmarks (Clicks on a bookmark/favorite link in a browser); Email (Clicks on links in desktop email clients)} to a website is the main source of traffic for most news providers.
+In the case of Bild.de, the percentage is 85\%.
+Also n-tv.de (79\%), spiegel.de (76\%) and tagesschau.de (75\%) get most of their traffic via the direct route.
+Other providers are more reliant on intermediaries, mainly search engines.
+Focus.de, Deutschlandfunk.de, Handelsblatt.com, for example, obtain between 40\% and 45\% of its traffic via search engines.
+Thus, an important question is, which organic search keywords send traffic to a website.
+Figure \ref{fig_searchtraffic} displays the percentage of organic search referrals to a specific website that come from this keyword.\footnote{Percentage of organic search referrals in major search engines over the time span Jun-Dec 2017.} E.g., 0.78\% of all organic search referrals to handelsblatt.com come from the keyword "handelsblatt".
+It is not surprising that the provider's name is the keyword that generates the majority of traffic for most of the news pages.
+However, different topics as well as names of other providers are hidden among the top 10 keywords.
+
+\begin{figure}[H]
+	\caption{Traffic Sources}
+	\begin{center}
+		\includegraphics[width=0.8\textwidth]{../figs/traffic_source.png}
+		\label{fig_traffic}
+	\end{center}
+\end{figure}
+
+\begin{figure}[H]
+	\caption{Search traffic \%}
+	\begin{center}
+		\includegraphics[width=0.95\textwidth]{../figs/search_traffic.png}
+		\label{fig_searchtraffic}
+	\end{center}
+\end{figure}
+
+Assuming that each search query is in itself a market where providers compete for traffic, the share of search queries for a keyword that has led visitors to a news page is the market share of that provider.
+In this context, figures \ref{fig_keywords1} and \ref{fig_keywords2} show the market share of providers for different keywords.\footnote{The figures show the percentage of searches for a keyword that sent traffic to a website in major search engines over the time span Jun-Dec 2017.} Nearly 15\% of all search queries for the keyword "Bundestagswahl 2017" (federal elections 2017) were forwarded to welt.de.
+Focus.de, faz.net and spiegel.de obtained a market share of 7\% - 8\%.
+For the keyword "Groko" (grand coalition between CDU/CSU and SPD), SPIEGEL ONLINE was able to gain the largest market share (17\%) in the past six months, followed by DIE WELT (\%10), FOCUS ONLINE (8\%) and Bild.de (7.5\%).
+Figure \ref{fig_keywords2} shows the market share of news pages for the keyword search for a specific party.
+Contrary to figure \ref{fig_keywords1} , the x-axes in figure \ref{fig_keywords2} are scaled equally to show not only the market share of news sites depending on one party, but also for which party this provider has the largest market share.
+
+\begin{figure}[H]
+	\caption{Market share for different keywords}
+	\begin{center}
+		\begin{subfigure}[normla]{0.7\textwidth}
+			\includegraphics[width=\textwidth]{../figs/keywords1.png}
+			\caption{policy topics / general}
+			\label{fig_keywords1}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.7\textwidth}
+			\includegraphics[width=\textwidth]{../figs/keywords2.png}
+			\caption{political parties}
+			\label{fig_keywords2}
+		\end{subfigure}
+	\end{center}
+\end{figure}
+
+% -----
+% Data
+% -----
+\subsection{Dataset}\label{ch_data}
+
+We conduct our estimation on a sample of 7061 online news articles from five news provider about domestic politics\footnote{Bild.de, FOCUS ONLINE, SPIEGEL ONLINE, ZEIT ONLINE, Tagesschau.de} dated from 01.06.2017 to 31.12.2017.\footnote{German federal elections took place on 24th of September 2017.} We first extract all online articles using the the Webhose.io API.\footnote{For more information see https://docs.webhose.io/v1.0/docs/getting-started.
+The scraping code was written in Python and can be made available on request.} We then filtered all articles from the section "domestic policy" by checking the URL structure.
+
+Figure \ref{fig_distr1}\footnote{The vertical line indicate the date of the federal elections (24.09.2017).} shows the distribution of the number of articles from the respective news sources by date.
+There is a high peak around the federal elections on September, 24th.
+
+\begin{figure}[H]
+	\caption{Article distribution...}
+	\begin{center}
+		\begin{subfigure}[normla]{0.8\textwidth}
+			\includegraphics[width=\textwidth]{../figs/timeline.png}
+			\caption{...by date \& news source}
+			\label{fig_distr1}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.8\textwidth}
+			\includegraphics[width=\textwidth]{../figs/bar.png}
+			\caption{... by news source}
+			\label{fig_distr2}
+		\end{subfigure}
+	\end{center}
+\end{figure}
+
+% ------------------
+% Text Pre-Procesing
+% ------------------
+
+To use text as data and reduce the dimensionality, a common strategy is to pre-process the text by imposing some preliminary restrictions (stop-word removal, tokenization) based on the nature of the data (twitter text, newspaper articles, speeches, etc.) to reduce the number of language elements to consider \citep{gentzkow_text_2017}.
+An overview of how these steps were applied to our data set can be found in the next section.
+
+After pre-processing, each document $d$ is a finite list of terms.
+Each unique term in the corpus is indexed by some $v \in \lbrace 1,...,V \rbrace$ where $V$ is the number of unique terms.
+For each document $d \in \lbrace 1,...,D \rbrace$ we compute the number of occurrences of term $v$ in document $d$ to obtain the count $x_{d,v}$.
+The $D$ x $V$ matrix $\boldsymbol{X}$ of all such counts is called the document-term matrix.
+This representation is often referred to as the bag of words model, since the order in which words are used within a document is completely disregarded.
+
+A central task in text mining is to extract low-dimensional information from documents that are high-dimensional by nature \citep{bholat_text_2015}.
+This is related to the task of reducing the number of unique language elements in order to reduce the dimensionality of data (to avoid unnecessary computational complexity and overfitting) while at the same time keeping those words that reflect the content of a document.
+Any useful representation of text will throw away some information, the trick is to include the relevant information for our needs, and exclude the extraneous information.
+
+Intuitively the term frequency (tf) of a word is a measure of how important that word may be.
+There are words in a document, however, that occur many times but may not be important like articles, conjunctions, and so on.
+These terms, often called "stop words", are important to the grammatical structure of a text, but typically don't add any additional meaning and can therefore be neglected.
+We use a pre-defined stop word list from the Snowball stemmer project\footnote{http://svn.tartarus.org/snowball/trunk/website/algorithms/*/stop.txt} together with a customized list of stop-words that are redundant superfluous or distorting.
+We also remove punctuation character (e.g.
+., ,, !, ?, etc.) and all numbers from our corpus.
+
 % ----------------------
+% Structural topic Model
+% ----------------------
+\section{The structural topic model}\label{ch_model}
 
-In \citet{tetlock_giving_2007}, $c_i$ is a bag-of-words representation and the outcome of interest $v_i$ is the latent “sentiment” of Wall Street Journal columns, defined along a number of dimensions such as “positive,” “optimistic,” and so on.
-The author defines the function $f (\cdot)$ using a dictionary called the General Inquirer, which provides lists of words associated with each of these sentiment categories.2 The elements of $f(c_i)$ are defined to be the sum of the counts of words in each category.
+We use the structural topic model (STM) developed by \citet{roberts_model_2016} that allows us to incorporate document specific covariates (e.g.
+the author or date of a document).
+STM is a recent extension of the standard topic modeling technique, labeled as "latent Dirichlet allocation" (LDA), which refers to the Bayesian model in \citet{blei_latent_2003} that treats each word in a topic and each topic in a document as generated from a Dirichlet - distributed prior.\footnote{See also \citet{griffiths_probabilistic_2002}, \citet{griffiths_finding_2004} and \citet{hofmann_probabilistic_1999}.
+\citet{pritchard_inference_2000} introduced the same model in genetics for factorizing gene expression as a function of latent populations.} Topic models formalize the idea that documents are formed by hidden variables (topics) that generate correlations among observed terms.
+Since its introduction into text analysis, LDA has become hugely popular and especially useful in political science.\footnote{see \citet{blei_probabilistic_2012}, \citet{grimmer_text_2013} and \citet{wiedmann_text_2016} for an overview in social science and \citet{gentzkow_text_2017} give an overview of text mining applications in economics.} \citet{wiedmann_text_2016} use topic model methods in on large amounts of news articles from two german newspapers published between 1959 and 2011, to reveal how democratic demarcation was performed in Germany over the past six decades.
 
-% Topic Modeling / LDA
-% ---------------------------
+STM has been applied to multiple academic fields: \citet{roberts_structural_2014} uses STM to analyse open-ended responses from surveys and experiments, \citet{farrell_corporate_2016} applies the model to scientific texts on climate change, revealing links between corporate funding and the framing of scientific studies and \citet{mishler_using_2015} shows that "STM can be used to detect significant events such as the downing of Malaysia Air Flight 17" when applied to twitter data.
+Another study shows how STM can be used to explore the main international development topics of countries’ annual statements in the UN General Debate and examine the country-specific drivers of international development rhetoric \citep{baturo_what_2017}.
+\citet{mueller_reading_2016} uses newspaper text to predict armed conflicts in different regions.
+They use the estimated topic shares in linear fixed effects regression to forecast conflict out-of-sample.
 
-Topic modeling is a statistical and computational technique for discerning information about the contents of a large corpus of documents without reading or annotating the original texts.
-A topic model uncovers patterns of word co-occurrence across the corpus, yielding a set of word clusters, together with associated probabilities of occurrence, which constitute the topics.
+% Topic Modeling
+% --------------
+\subsection{Generative Process of STM}
 
-See \citep{taddy_estimation_2012} for a review of topic estimation techniques)
+The following description of the generative model of the STM is based on \citet{roberts_structural_2013} and \citet{roberts_stm:_2016}.
+The process of filling a word-position in a document begins with the generation of a document-specific topic-prevalence vector $d(\boldsymbol{\theta}_d)$ drawn from a logistic-normal distribution, where the parameters are a function of the covariate values:
 
-Since its introduction into text analysis, topic modeling has become hugely popular.8 (See \citet{blei_probabilistic_2012} for an overview.) The model has been especially useful in political science (e.g., \citep{grimmer_bayesian_2010}), where researchers have been successful in attaching political issues and beliefs to the estimated latent topics.
+\begin{align*}
+	\boldsymbol{\theta}_d|\boldsymbol{x}_{d\gamma},\boldsymbol{\Sigma} \sim \textrm{LogisticNormal}(\mu = \boldsymbol{x}_{d\gamma}\boldsymbol{\Sigma})
+\end{align*}
 
-Topic modeling is alternatively labeled as “latent Dirichlet allocation,” (LDA) which refers to the Bayesian model in \citet{blei_latent_2003} that treats each $\boldsymbol{v}_i$ and $\boldsymbol{\theta}_l$ as generated from a Dirichlet - distributed prior.
-The same model was independently introduced in genetics by \citet{pritchard_inference_2000} for factorizing gene expression as a function of latent populations; it has been similarly successful in that field.
+$\boldsymbol{x}_d\gamma$ lists the values of all metadata covariates for document $d$, where $\gamma$ relates these covariate values to the topic-prevalence.
+The structure of $\boldsymbol{\Sigma}$ implies the possibility of correlations across documents in the topic-prevalence vector which help enhance interpretation and prevent overfitting.
 
-The basic topic model has been generalized and extended in variety of ways.
-A prominent example is the dynamic topic model of \citet{blei_dynamic_2006}, which considers documents that are indexed by date (e.g., publication date for academic articles) and allows the topics, say $\boldsymbol{\Theta}_t$, to evolve smoothly in time.
+Given the document-specific distribution over topics, for each word in the document ($n \in \lbrace 1,...,N_d\rbrace$) is assigned to a specific topic $z_{dn}$ through the process
 
-% Structural topic models (STM)
-% ----------------------------
-A typical application of topic modeling in the social sciences first estimates LDA, then uses estimates of $\theta_d$ as the dependent variable in an regression on covariates to test whether different types of documents have different content.
+\begin{align*}
+	z_{dn}|\boldsymbol{\theta}_d \sim \textrm{Multinomial}(\boldsymbol{\theta}_d)
+\end{align*}
 
-This is contradictory because documents are assumed to be generated by a statistical process that we subsequently reject.
+where the $k^{th}$ element if $z_{dn}$ is unity and all other elements are zero when topic $k$ is chosen.
 
-The structural topic model (STM) of Roberts et.
-al.
-(2016) explicitly introduces covariates into a topic model, and allows one to estimate the impact of document-level covariates on topic content and prevalence as part of the topic model itself.
+Conditional in the topic chosen, a specific word, $w_{dn}$, is chosen from the overall corpus vocabulary $V$ to fill position $n$ in document $d$, using the following process:
 
-% ---------------------------------
-% Statistical Analysis of Text Data
-% ----------------------------------
-\section{Statistical Analysis of Text Data}
+\begin{align*}
+	w_{dn}|z_{dn},\beta_{dkv} \sim \textrm{Multinomial}(\beta_{dk1},...,\beta_{dkV}).
+\end{align*}
 
-Consider a collection of documents by $d \in \lbrace 1 ...
-D \rbrace$, each containing $n \in \lbrace 1 ...
-N_d \rbrace$ words.
-Primary observations consist of words $w_{d,n,}$ that are instances of unique terms from a vocabulary of terms, indexed by $v \in \lbrace 1 ...
-V \rbrace$.
+where the word probability $\beta_{dkv}$ is modeled as a function of the two parameters $m_v$ (indicating the importance of that word across all documents) and $\kappa_{kv}$ (indicating the importance of the word given the topic $k$).
+Transforming the sum of these coefficients into probabilities for use in a multinomial distribution via logistic transformation, one obtains:
 
-To use text as data and reduce the dimensionality, a common strategy is to (a) pre-process the text by imposing some preliminary restrictions (stop-word removal, tokenization) based on the nature of the data (twitter text, newspaper articles, speeches, etc.) and (b) to represent a document $d$ as a vector of word counts, $\boldsymbol{n}_d \in \boldsymbol{N}^V$.
-This representation is often referred to as the bag of words model, since the order in which words are used within a document is completely disregarded.
-Nowadays, the bag of words model is a common representation for most of statistic literature about text data analysis (\citet{blei_latent_2003}; \citet{erosheva_mixed-membership_2004}; \citet{griffiths_finding_2004}; \citet{genkin_large-scale_2007}).
+\begin{align*}
+	\beta_{dkv}|z_{dn}\propto\textrm{exp}(\boldsymbol{m}_v+\kappa_{kv})
+\end{align*}
 
-Term-Document matrices represent frequency distribution of unique terms in the documents.
-Any one document will contain only a subset of all unique terms, and the rows corresponding to unused terms will all be zero.The key task then becomes how to extract low-dimensional information from documents that are high-dimensional by nature.
-This is analogous to a situation in which a researcher has a database with thousands of covariates and is attempting to choose which subset of them, or which summary statistics, should be included in regression analysis.
-% The description of the data and how it was processed in order to reduce it to a manageable scale without losing significant information can be found in chapter ...
+% ----------------------
+% Model Selection
+% ----------------------
+\subsection{Model and parameter selection}
 
-\begin{enumerate}
-	\item Represent raw text $D$ as a numerical array $\boldsymbol{C}$.
+Topic models are usually imprecise as a number of assumptions have to be made that influence the performance of the classification task.
+Furthermore, multiple solutions exist for the optimization problem.
+The STM maximizes the posterior likelihood that the observed data were generated by the above data-generating process using an iterative approximation-based variational expectation-maximization algorithm\footnote{A technical description of this maximization process can be found in \citet{roberts_model_2016}} available in R's stm package \citep{roberts_stm:_2016}.
+Regularizing prior distributions are used for $\gamma$, $\kappa$ and $\Sigma$.
+Since an ex ante valuation of a model is hardly possible, we compute a variety of different models with different parameters and compare them with respect to the research problem \citep{gentzkow_text_2017}.
+To evaluate the accuracy of a model its perplexity can be computed.
+Similar to cross-validation (VC), different model specifications are compared to how well they do in predicting words within a document \citep{asuncion_smoothing_2012}, \citep{wallach_evaluation_2009}.
+However, \citet{chang_reading_2009} have proven with large user studies that optimal held out likelihood does not correspond to human perception of semantic coherence of topics.
+\cite{mimno_optimizing_2011} introduced a measure of coherence of a topic by observing co-occurences of the top $N$ terms of each topic on a document.
+Another strategy for selecting an appropriate model is to check for residual overdispersion of the variance of the multinomial within the data generating process of the model \citep{taddy_estimation_2012}.
+Other approaches can be found in \citet{airoldi_reconceptualizing_2010} and \citet{teh_hierarchical_2006}.
+However, cross-checking some subset of assigned topic distributions to evaluate whether the estimates align with the concept of interest \citep{gentzkow_text_2017}.
+We apply these manual audits together with numeric optimization based on the topic coherence measure suggested by \citet{mimno_optimizing_2011}.
 
-	\item Map $\boldsymbol{C}$ to predict values $\boldsymbol{\hat{V}}$ of unknown outcomes $\boldsymbol{V}$.
+This process revealed that a model with 25 topics best reflects the structure in the corpus.
+Furthermore, we use the source of each article (the media house) and the month it was published as covariates in the topic prevalence portion of the model.
+In other words, the probability distribution of topics depends on the editorial strategy of a media house as well as on the month the article was published.
+To address problems due to non-convexity, we rely on the spectral initialization approach advocated by \citet{roberts_navigating_2016}.
 
-	E.g.
-the variable of interest $\boldsymbol{V}$ is an indicator whether the email is spam.
-The prediction $\boldsymbol{\hat{V}}$ determines whether or not to send the email to a spam filter.
-Sometimes the attribute of interest is latent, such as the topics of a newspaper article.
-	\item Use $\boldsymbol{\hat{V}}$ in subsequent descriptive or causal analysis.
-\end{enumerate}
+% ----------------------
+% Model Results
+% ----------------------
+\subsection{Interpretation}
 
-Regarding 2, the methods to connect counts $\boldsymbol{c}_i$ to attributes $\boldsymbol{v}_i$ can be roughly divided into four categories \citep{gentzkow_text_2017}:
-\begin{enumerate}
-	\item Dictionary-based methods: 
-	No statistical inference.
-Simply specify $\boldsymbol{\hat{v}_i}=f(\boldsymbol{c}_i)$ for some unknown function $f(\cdot)$.
-Sometimes based on a specific dictionary of terms (\citet{tetlock_giving_2007}, \citet{baker_measuring_2015}).
-	\item Text regression methods:
-	Directly estimate the conditional outcome distribution $p(\boldsymbol{v}_i|\boldsymbol{c}_i)$.
-Intuition: If we want to predict $\boldsymbol{v_i}$ from $\boldsymbol{c}_i$, we would regress the observed values of the former ($\boldsymbol{V}^{train}$) on the corresponding latter ($\boldsymbol{C}^{train}$).
-High dimensionality of $\boldsymbol{c}_i$ ($p > n^{train}$) requires use of appropriate regression techniques to avoid overfitting (e.g.
-$L_1$ regularized linear or logistic regression)
-	\item Generative model of $p(\boldsymbol{c}_i|\boldsymbol{v}_i)$.
-	Intuition: In many cases the underlying causal relationship runs from outcomes to language rather than the other way around.
-E.g.
-Google searches about flu do not cause flu cases to occur, rather, people with flu are more likely to produce such searches.
-	\begin{enumerate}
-		\item Observed attributes (supervised methods):
-		Supervised machine learning starts with a researcher classifying observations to ‘train’ an algorithm under human ‘supervision’ – to ‘learn’ the correlation between the researcher’s ascribed classes and words characteristic of documents in those classes (Grimmer and Stewart (2013)).
-Fitting the model based on the observed training data $\boldsymbol{V}^{train}$, say $f_{\boldsymbol{\theta}}(\boldsymbol{c}_i;\boldsymbol{v}_i)$ for a vector of parameters $\boldsymbol{\theta}$, to this training set.
-The fitted model $f_{\hat{\boldsymbol{\theta}}}$ can be inverted in order to infer $\boldsymbol{v}_i$ for documents in the test set.
-		\item Latent attributes (unsupervised methods): The function relating $\boldsymbol{c}_i$ to $\boldsymbol{v}_i$ is unknown, as we cannot observe the true value of $v_i$.
-Principal component analysis (PCA), latent Dirichlet allocation (LDA, topic modeling, structural-topic modeling).
-Unsupervised machine learning involves taking unclassified observations and uncovering hidden patterns that structure them in some meaningful way.
-The outputs of algorithms for unsupervised machine learning can be used as inputs into econometric models for predicting some variable of interest, but this is a different approach from intentionally choosing the dimensions of content based on their predictive ability.
-	\end{enumerate}
-	\item Deep learning techniques: neural networks, distributed language models.
-\end{enumerate}
+Inference of mixed-membership models, such as the one applied in this paper, has been a thread of research in applied statistics in the past few years \citep{blei_latent_2003} \citep{erosheva_mixed-membership_2004} \citep{braun_variational_2010}.
+As the posterior can be highly dependent on the model definition, using multiple starting points and clever initialization are successful practices.
+The takeaway from empirical evaluations of the inference task of mixed-membership models is that the bayesian posterior as good frequentist properties \citep{wallach_evaluation_2009}.
+\citet{roberts_model_2016} use empirical evaluation, including a frequentist coverage analysis and compare the performance of their STM to a variety of alternatives in \citet{roberts_navigating_2016}.
 
-The goal of this paper is to find the latent topics within newspaper articles and how different types of media outlets (as well as the date?) influence the topic prevalence as well as the language to describe a topic (the word-topic distribution).
-We implement generative model (topic model).
-% A description of the generative process can be found in chapter ...
+A way to summerize the topics in an interpretable way is to use the most frequent terms within a topic \citep{chang_reading_2009}, but the exclusivity of words to topics is equally important for communicating content.
+\citep{bischof_summarizing_2012} consider the harmonic mean of the words's rank in terms of exclusivity and frequency as a summary for a word's contribution to a topic.
+It is important to take both of these properties into account, as frequent words are often simply functional words that are necessary to discuss a topic.
+While completely exclusive words can be so rare that their information content is too low.
+\citep{roberts_stm:_2016} refer to this as the FREX (FRequency and EXclusivity) metric.
 
-\section{Generative Process}
+\begin{align}
+	FREX_{k,\nu} = (\frac{\omega}{ECDF(\beta_{k,\nu}/\sum^K_{j=1}\beta_{j,\nu}}+\frac{1-\omega}{ECDF(\beta_{k,\nu}})^{-1},
+\end{align}
 
-In this unsupervised method, the words in a document are viewed as the realization of some stochastic process.
-The generative process is defined through a probability model for $p(\boldsymbol{c}_i|\boldsymbol{v}_i)$.
+with $\boldsymbol{B}$ denoted as the $KxV$ matrix of topic-conditional term probabilities.
+The first part of the equation calculates the frequency score  given by the empirical CDF of the word in it's topic distribution.
+Exclusivity is calculated by column-normalizing the beta matrix (thus representing the conditional probability of seeing the topic given the word).
+$\omega$ balances the influence of frequency and exclusivity and is set to $0.5$
 
-Each observation $\boldsymbol{c}_i$ is a conditionally independent draw from the vocabulary of possible tokens accodring to some document-specific token probability vector $\boldsymbol{q}_i=[q_{i1}...q_{ip}]'$.
-Conditioning on document length, $m_i=\sum_jc_{ij}$, this implies a multinomial distribution for the counts
+\section{Empirical Evaluation}
 
-\begin{equation}\label{eq_1}
-	\boldsymbol{c}_i \sim \boldsymbol{MN}(\boldsymbol{q}_i,m_i). 
-\end{equation}
+Figure \ref{fig_topic_proportion} displays the topics ordered by their expected frequency across the corpus.
+To assign a label to each topic, we used a combination of most frequent words in that topic and words with the highest "score", computed as the log frequency of the word in the topic divided by the log frequency of the word in other topics \citep{roberts_stm:_2016}.
+The most common topic (3) is a general topic full of words that are frequently used in policy news, and therefore is not very interpretable.
+However, the remaining labels seem to classify a certain topic.
 
-Under the basic model in \ref{eq_1}, a connection between text and attributes is defined through the link function $\boldsymbol{q}_i=q(\boldsymbol{v}_i)$.
+\begin{figure}[H]
+	\begin{center}
+	\includegraphics[width=0.8\textwidth,keepaspectratio]{../figs/topic_proportion.png}
+	\caption{Expected Topic Proportion}
+	\label{fig_topic_proportion}
+	\end{center}
+\end{figure}
 
-\begin{equation}\label{eq_2}
-	\boldsymbol{E} \bigg[\frac{\boldsymbol{c}_i}{m_i}\bigg]=\boldsymbol{q}_i =v_{i1}\boldsymbol{\theta}_1+v_{i2}\boldsymbol{\theta}_2+v_{ik}\boldsymbol{\theta}_k=\boldsymbol{\Theta v}_i
-\end{equation}
+%\begin{landscape}
+%\begin{figure}[H]
+%\centering
+%	\caption{Sample articles}
+%	\includegraphics[width=\linewidth,height=.9\textheight,keepaspectratio]{../figs/topic-classification-sample.png}	
+%	\label{fig_classification}
+%\end{figure}
+%\end{landscape}
 
-where attributes $v_{il}$ are referred as topic wights, restricting $v_{il}\geq 0$ and $\sum^k_{l=1}v_{il}=1$, and each topic $\boldsymbol{\theta}_l$ is a probability vector over possible tokens: $\theta_{lj}\geq 0$ and $\sum^p_{j=1}\theta_{il}=1$.
-Each $\boldsymbol{v}_i$ and $\boldsymbol{\theta}_l$ is generated from a Dirichlet-distributed prior.
+% ----------------------
+% Effect of covariates
+% ----------------------
+Since we included news source as a covariate in estimating topical prevalence part within the model, we can estimate the frequency a topic is discussed within a news corpus \citep{roberts_model_2016}.
+We estimate the conditional expectation of topic prevalence for given document characteristics.
+More specifically, we estimate a linear model, where the documents are observations, the dependent variable is the posterior probability of a topic and the covariates are the metadata of documents.
+The stm-package provides a function that uses the method of composition to incorporates uncertainty in the dependent variable, drawing a set of topic proportions from the variational posterior repeated times and compute the coefficients as the average over all results.
 
-Latent Dirichlet allocation (LDA) is a particularly popular method for fitting a topic model.
-It treats each document as a mixture of topics, and each topic as a mixture of words.
-This allows documents to “overlap” each other in terms of content, rather than being separated into discrete groups, in a way that mirrors typical use of natural language.
-Formally speaking, each document has its own probability distribution over topics.
-Then, for each word in each document, a topic assignment is made and then, conditional on the assignment, a word from the corresponding topic.
+Figure \ref{fig_estimateEffects_small} displays topics, where the most significant differences between the news sources are discernible.\footnote{An overview of all estimated topics can be found in the appendix \ref{fig_estimateEffects_full1} and \ref{fig_estimateEffects_full2}.} Topic 2, classifying articles about the diesel scandal, the glpyphosate decision and green policies, occur comparatively more often in tagesschau.de and bild.de, whereas tagesschau.de reports comparatively little about the riots during the G20 summit (topic 9).
+Topics 10 (about public (financial) statistics) and 13 (about the federal migration office (BAMF), asylum procedures and other issues related to refugees) also seems to be represented comparatively frequently in the tagesschau.de corpus, the latter topic is most often discussed in the DIE WELT corpus.
+However, topic 20 (the public debate between Die Grünen and FDP in the process of coalition negotiations) is represented significantly more often in the corpus of spiegel.de and bild.de.
+Topic 26, which classifies articles that deal with terrorism, mainly about the NSU trial and the main defendant Zschäpe as well es IS, is significantly more often present in the corpus of FOCUS ONLINE.
 
-Estimation of topic models make use of some alternating inference for $\boldsymbol{V|\Theta}$ and $\boldsymbol{\Theta|V}$.
+\begin{figure}[H]
+	\caption{Mean prevalence of topics within each news source corpus}
+	\begin{center}
+		\begin{subfigure}[normla]{0.3\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect2.png}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.3\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect9.png}
+		\end{subfigure}
+				\begin{subfigure}[normla]{0.3\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect11.png}
+		\end{subfigure}
+				\begin{subfigure}[normla]{0.3\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect13.png}
+		\end{subfigure}
+				\begin{subfigure}[normla]{0.3\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect20.png}
+		\end{subfigure}
+				\begin{subfigure}[normla]{0.3\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect26.png}
+		\end{subfigure}
+	\end{center}
+	\label{fig_estimateEffects_small}
+\end{figure}
 
-\begin{enumerate}
-	\item Expectation-maximization algorithm (EM)
-	Either maximize the likelihood implied by \ref{eq_1} and \ref{eq_2} or, after incorporating the usual Dirichlet priors on $\boldsymbol{v}_i$ and $\boldsymbol{\theta}_l$ \citep{taddy_estimation_2012} 
-	\item Target full posterior distribution $p(\boldsymbol{\Theta,V|c}_i})$
-\end{enumerate}
+Another interesting aspect is how the news sources discusses the different topics, that is, describe the same event with different vocabulary.
 
-Choice of number of topics $k$ is often fairly arbitrary.
-In practice it is very common to simply start with a number of topics on the order of ten, and then adjust the number of topics in whatever direction seems to improve interpretability.
-Whether this ad hoc procedure is problematic depends on the application.
-In many applications of topic models to date the goal is to provide an intuitive description of text rather than inference on some underlying “true” parameters; in these cases, the ad hoc selection of the number of topics may be reasonable.
+\section{Sentiment Analysis}
 
-Data-driven approaches: 
-\begin{enumerate}
-	\item \citet{taddy_estimation_2012} describes a model selection process for $k$ that is based upon Bayes factors.
-	\item \citet{airoldi_reconceptualizing_2010} provide a cross-validation (CV) scheme
-	\item \citet{teh_hierarchical_2006} use Bayesian nonparametric techniques that view $k$ as an unknown model parameter.
-\end{enumerate}
+commonly used lexical or “bag-ofwords” approach.
+In that approach, the researcher provides pre-defined dictionaries (lists) of words associated with a given emotion, such as negativity.
+The target text is then deconstructed into individual words (or tokens) and the frequencies of words contained in a given dictionary are then calculated.
+For example, Loughran and McDonald (2011) construct a dictionary of words that express negativity in financial contexts, which they then use to measure the negativity in company 10-K filings and relate that negativity to financial outcomes.
 
-\subsection{Structural Topic Model}
+The psychology literature demonstrates that any emotion can be parsimoniously defined by assigning it a score along two primary dimensions: valence (i.e., positive or negative) and arousal (i.e., activation and deactivation).
+For comparison purposes, we also examine three additional measures: “worried,” “satisfied,” and a lexical “negativity” measure.
 
-The process for generating individual words is the same as for plain LDA conditional on the $\beta_k$ and $\pi_d$ terms.
+% ----------------------
+% Appendix
+% ----------------------
+\section*{Appendix}
 
-However both objects can depend on potentially different sets of document-level covariates. Each document has:
-\begin{enumerate}
-	\item Topic Prevalence. Attributes $r_d$ that affect the likelihood of discussing topic $k$. how much of a document is associated with a topic
-	\item Topic Content. Attributes $r_d$ that affect the likelihood of discussing term $v$ overall, and of discussing it within topic $k$. the words used within a topic
-\end{enumerate}
+\begin{figure}[H]
+	\caption{Mean prevalence of topics within each news source corpus 1}
+	\begin{center}
+		\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect1.png}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect2.png}
+		\end{subfigure}
+				\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect3.png}
+		\end{subfigure}
+				\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect4.png}
+		\end{subfigure}
+				\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect5.png}
+		\end{subfigure}
+				\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect6.png}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect7.png}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect8.png}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect9.png}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect10.png}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect11.png}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect12.png}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect13.png}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect14.png}
+		\end{subfigure}
+	\end{center}
+	\label{fig_estimateEffects_full1}
+\end{figure}
 
-The generation of the $k$ and $d$ terms is via multinomial logistic regression, which breaks local conjugacy.
-
-The standard topic modeling technique, Latent Dirichlet Allocation (LDA), may have limited utility in the realm of social media.
-LDA makes a statistical assumption that all texts in the modeled corpus are generated by the same underlying process (Blei).
-Thus, it is not ideally suited to examining differences in topical content that are affected by external variables such as author identity or time of writing.
-
-Structural topic modeling (STM) is a recently introduced variant of LDA that is designed to address precisely this limitation .
-STM can represent the effect of external variables on both topical content and topical prevalence.
-The external variables can consist of any metadata that distinguishes one text from another, including variables relating to author identity (gender, age, political affiliation, etc.), textual genre (for example, news stories versus academic articles), and time of production.
-
-stmVigenette: "The goal of the Structural Topic Model is to allow researchers to discover topics and estimate their relationship to document metadata.
-Outputs of the model can be used to conduct hypothesis testing about these relationships."
-
-\subsubsection{Estimation of the STM}
-In STM, metadata can be entered in the topic model in two ways: topical prevalence and topical content.
-Metadata covariates for topical prevalence allow the observed metadata to affect the frequency with which a topic is discussed.
-Covariates in topical content allow the observed metadata to affect the word rate use within a given topic{that is, how a particular topic is discussed.
-
-We use the online magazine-type as a covariate in the topic prevalence portion of the model with the  data described above.
-Each document is modeled as a mixture of multiple topics.
-Topical prevalence captures how much each topic contributes to a document.
-Because different documents come from different sources, it is natural then to want to allow this prevalence to vary with metadata that we have about document sources.
-
-We will simply let prevalence be a function of the magazine variable, which is coded as either
-Spiegel Online or FOCUS Online and the variable day which is an integer measure of days running from 01-01-2017 to 31-07-2017.
-
-\subsection{Gibbs Sampler}\label{section_gibbs}
-
-Strategy for discovering topics  \cite{griffiths_finding_2004}
-\begin{itemize}
-	\item Considering the posterior distribution over the assignments of words to topics, $P(z|w)$. (and not explicitly representing $\phi$ or $\theta$ as parameters to be estimated)
-	\item Examine this posterior distribution to obtain $\phi$ or $\theta$
-\end{itemize}
-
-After making assumptions about the parameters (number of topics $K$, prior distributions $\alpha$ and $\beta$), the procedure of Gibbs sampling is as follows:
-
-\begin{enumerate}
-	\item Go through each document and randomly assign each word in the document to one of $K$ topics, based on the prior distributions.
-	\item For each document $d$, go through each word $w$ and compute:
-	\begin{enumerate}
-		\item The document-topic distribution $\theta = p(t|d)$
-		\item The topic-term distribution $\phi = p(w|t)$
-	\end{enumerate}
-	\item Reassign word $w$ a new topic $t^*$, where we choose topic $t^*$ with probability $p(t^*|d)*p(w|t^*)$
-\end{enumerate}
-
-On repeating the last step a large number of times, the algorithm reaches a steady state where topic assignments are pretty good.
-These posterior distributions $\theta$ and $\phi$ are then used to determine the topic mixtures of each document.
-
-\subsection{Validate accuracy}
-
-\begin{itemize}
-	\item Manual audits: cross checking some subset of the fitted values against the coding a human would produce by hand
-	\item Inspection of fitted parameters
-	\item Interpretation of fitted topics usually proceeds by ranking the tokens in each topic according to token probability.
-\end{itemize}
-
-Caution against the over-interpretation of unsupervised models: posterior distributions informing parameter estimates are highly multimodal, and multiple topic model runs can lead to multiple different interpretations.
-Add some supervision (\citet{airoldi_improving_2016}, \citet{gentzkow_text_2017})
+\begin{figure}[H]
+	\caption{Mean prevalence of topics within each news source corpus 2}
+	\begin{center}
+			\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect15.png}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect16.png}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect17.png}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect18.png}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect19.png}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect20.png}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect21.png}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect22.png}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect23.png}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect24.png}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect25.png}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect26.png}
+		\end{subfigure}
+				\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect26.png}
+		\end{subfigure}
+				\begin{subfigure}[normla]{0.2\textwidth}
+			\includegraphics[width=\textwidth]{../figs/estimate_effect28.png}
+		\end{subfigure}
+	\end{center}
+	\label{fig_estimateEffects_full2}
+\end{figure}
 

### 2018-01-19 paper/doc/doc_backup.tex
bla

--- 2018-01-09 paper/doc/doc_public_private.tex
@@
 % The description of the data and how it was processed in order to reduce it to a manageable scale without losing significant information can be found in chapter ...
+
+We used the URL of these articles, to check how many times they where shared on Facebook using the \textit{sharedcount} API.\footnote{http://docs.sharedcount.com/} The returned share count is the sum of (1) the number of likes of this URL, (2) the number of shares of this URL (including copy-pasting a link back to Facebook), (3) the number of likes and comments on stories on Facebook about this URL and (4) the number of inbox messages containing this URL as an attachment.\footnote{See https://developers.facebook.com/docs/graph-api for more information about the Facebook Graph API.}
 
@@
 
+% ----------------------
+% Regression
+% ----------------------
+\section{Causal relationship between topics and social media shares.}\label{ch_regression}
+
+%\begin{figure}[H]
+%\centering
+%	\caption{Sum of Facebook shares by topic}
+%	\includegraphics[width=\textwidth]{../figs/fb_shares_topics.png}	
+%	\label{fig_fb_shares_topic}
+%\end{figure}
+
+In order to answer the primary question of this paper, which topics are more often shared in social networks, we assign a single topic to each article.
+The examination of the topic probability distribution revealed that most documents are assigned a unique topic with a probability of 50\% and higher (see figure \ref{fig_gamma}), so that we can classify each document based on which topic has the highest probability.
+We keep only those documents, where the posterior probability of this topic is greater or equal than 0.5 which left us with 6565 documents.
+Figure \ref{fig_topic_timeline} shows the amount of articles to which a certain topic has been assigned over time.
+Some of the topics exhibit distinct peaks in the timeline.
+Topics 11 and 14 deal with the elections, although topic 11 tends to be more about incidents related to the AfD.
+This graph also illustrates the difference between topic 6 and 17, which have similar labels: topic 6 classifies articles before the negotiations for a "Jamaika" coalition failed, while topic 17 describes the articles written after failure.
+The highest peak can be found for topic 9, which classifies articles to the riots during the G20 summit.
+It becomes apparent that more articles deal with riots than with the political content of the summit (topic 8).
+
+The proportion of zeros in the independent variable (number of Facebook shares) is about 15\%.
+Figure \ref{fig_fb_shares} reveals that within the bin of 0-1 facebook shares, nearly all articles are published by stern.de.
+
+\begin{figure}[H]
+	\caption{}
+	\begin{center}
+		\begin{subfigure}[normla]{0.49\textwidth}
+			\includegraphics[width=\textwidth,keepaspectratio]{../figs/gamma_dist.png}
+			\caption{Density of Top-Topics posterior probability}
+			\label{fig_gamma}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.49\textwidth}
+			\includegraphics[width=\textwidth,keepaspectratio]{../figs/facebook_shares.png}
+			\caption{Grouped Facebook Shares}
+			\label{fig_fb_shares}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.9\textwidth}
+			\includegraphics[width=\textwidth,keepaspectratio]{../figs/topic-timeline.png}
+			\caption{Topic Timeline}
+			\label{fig_topic_timeline}
+		\end{subfigure}
+	\end{center}
+\end{figure}
+
+Model:
+
+\begin{align*}
+	log(FBshares) =\alpha+\beta_{topic}+\beta_{site}+\beta_{textlength}+\epsilon 
+\end{align*}
+
+\include{lm1}
+%
+%One way to model this type of situation is to assume that the data come from a mixture of two populations, one where the counts is always zero, and another where the count has a Poisson distribution with mean $\mu$.
+In this model zero counts can come from either population, while positive counts come only from the second one.
+%
+%The distribution of the outcome can then be modeled in terms of two parameters, $\pi$ the probability of 'always zero', and $\mu$, the mean number of publications for those not in the 'always zero' group.
+A natural way to introduce covariates is to model the logit of the probability $\pi$ of always zero and the log of the mean $\mu$ for those not in the always zero class.
+%
+%The two-part model relaxes the assumption that the zeros (whether or not the article is shared) and positives (how often it is shared) come from the same data generating process.
+The zero-inflated model lets the zeros occur in two different ways: as a realization of the binary process (z=0) and as a realization of the count process when the binary variable z=1.
+%
+%If the process generating the zeros is $f_1(.)$ and the process generating the positive responses is $f_2(.)$ then the two-part hurdle model is defined by the following probabilities. 
+%
+%\begin{align*}
+%	g(y)=\begin{cases}
+%		f_1(0) + 1(f_i(0))f_2(0) if y=0 \\
+%		(1-f_1(0))f_2(y) if y\geq 1
+%	\end{cases}
+%\end{align*}
+%
+%The model for the zero versus positive responses is a binary model with the specified distribution, but we usually estimate it with the probit/logit model.
+
 \end{document}

### 2018-01-19 wahlprogramme.Rmd
bla

--- 2017-11-09 paper/R/02_combine.Rmd
@@
 ---
-title: "Topic Modeling of News"
-author: "Franziska Löw"
-date: "`r format(Sys.Date())`"
-output: github_document
+title: "R Notebook"
+output: 
 ---
@@
 # Load and prepare Dataframes
-```{r}
+```{r message=FALSE}
 rm(list =ls())
 
-load("../output/news_cleaned.Rda")
-okt <- read_csv("../data/eventbride/eventbride_okt_18.csv")
-nov <- read_csv("../data/eventbride/eventbride_nov_03.csv")
+load("paper/output/news_cleaned.Rda")
 ```
 
-## Generate new variables 
+# Pre-Process Text
+## Artikel über Wahlprogramme
 ```{r}
-### Oktober ###
-# Extract site
-okt$site <- str_extract(okt$source, "(?<='uri': ')[A-z][^']*")
+pat <- c("Wahlprogramm")
 
-# number of Facebook shares
-okt$fb_shares <- str_extract(okt$shares, "(?<='facebook': )[0-9]*")
-okt$fb_shares <- ifelse(is.na(okt$fb_shares),0, okt$fb_shares)
-okt$fb_shares <- as.integer(okt$fb_shares)
-names(okt) <- gsub("body", "text", names(okt))
-
-### November ###
-# Extract site
-nov$site <- str_extract(nov$source, "(?<='uri': ')[A-z][^']*")
-
-# number of Facebook shares
-nov$fb_shares <- str_extract(nov$shares, "(?<='facebook': )[0-9]*")
-nov$fb_shares <- ifelse(is.na(nov$fb_shares),0, nov$fb_shares)
-nov$fb_shares <- as.integer(nov$fb_shares)
-names(nov) <- gsub("body", "text", names(nov))
-```
-
-## Reduce Dataframe
-```{r}
-keeps <- c( "welt.de","spiegel.de","stern.de","focus.de","zeit.de","bild.de" )
-keys <- paste(c("bundestagswahl","Koalition"), collapse = "|")
-
-df %>%
-  filter(site %in% keeps) %>%
-  filter(grepl(keys, text, ignore.case = TRUE)) -> btw1
-
-okt %>%
-  filter(isDuplicate == "False") %>%
-  filter(site %in% keeps) %>%
-  filter(grepl(keys, text, ignore.case = TRUE)) -> btw2
-
-nov %>%
-  filter(isDuplicate == "False") %>%
-  filter(site %in% keeps) %>%
-  filter(grepl(keys, text, ignore.case = TRUE)) -> btw3
-```
-
-## Combine Dataframes
-```{r}
-common_cols <- intersect(colnames(btw1), colnames(btw2))
-
-btw <- rbind(
-  btw1[, common_cols], 
-  btw2[, common_cols],
-  btw3[, common_cols]
-)
-
-```
-
-## Count number of terms in a string
-```{r}
-btw$text_length <- sapply(gregexpr("\\S+", btw$text), length)
+df <- df %>%
+  filter(grepl(pat, title))
 ```
@@
 ```{r}
-btw$title.text <- paste(btw$title, btw$text, sep = " ")
+df %>% select(title, site) %>% htmlTable::htmlTable(align="l")
 ```
-
-# Pre-Process Text
-
-## Filtering
-```{r}  
-btw %>%
-  group_by(title, site) %>%
-  ungroup() %>%
-  distinct(title,site, .keep_all = TRUE) -> btw
-```
-
-```{r}
-btw %>%
-  # remove articles that contain daily overviews
-  filter(!grepl("Elbvertiefung", title.text)) %>%
-  filter(!grepl("News des Tages", title.text)) %>%
-  # remove articles that dont contain text
-  filter(!grepl('</div>', title.text)) -> btw
-```
-
-```{r}
-pat <- 'Florian Gathmann[^\n]*'
-btw %>%
-  filter(grepl(pat, title.text, perl = TRUE, ignore.case = TRUE)) %>%
-  #select(text) %>%
-  #.[1,] %>%
-  #htmlTable::htmlTable()
-  group_by(site) %>%
-  tally(sort = TRUE)
-```
-
-```{r}
-as.data.frame(str_match(btw$title.text, pat)) ->test
-test %>%
-  filter(!is.na(test)) %>%
-  .[1:100,]
-```
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
-clean.text <- function(x)
-  {
-  # All
-  x = gsub("Getty Images", "", x)
-  x = gsub('Startseite[^\n]*', "", x, ignore.case = TRUE, perl = TRUE)
-
-  # Bild.de
-  x = gsub("Shopübersicht Top Gutscheine", "", x)
-  x = gsub('Politik Inland[^\n]*', "", x, perl = TRUE)
-
-  # welt.de
-  x = gsub('Quelle: N24[^\n]*', "", x, perl = TRUE)
-  x = gsub('infocom[^\n]*', "", x, perl = TRUE, ignore.case = TRUE)
-  x = gsub('Infografik[^\n]*', "", x, perl = TRUE, ignore.case = TRUE)
-  x = gsub('versuchen Sie es[^.]*', "", x, perl = TRUE, ignore.case = TRUE)
-  x = gsub('Video konnte nicht[^\n]*', "", x, perl = TRUE, ignore.case = TRUE)
-  x = gsub('Welt twitter', "", x, perl = TRUE, ignore.case = TRUE)
-
-  # FOCUS.de
-  x = gsub("FOCUS Online", "", x)
-  x = gsub('Wochit[^\n]*', "", x, perl = TRUE, ignore.case = TRUE)
-  x = gsub("Vielen Dank! Ihr Kommentar wurde abgeschickt.", "", x)
-  x = gsub('Im Interesse unserer User[^"]*', "", x, perl = TRUE)
-  x = gsub('Sie haben noch 800[^"]*', "", x, perl = TRUE)
-  x = gsub('Erzählen Sie auf FOCUS Online über Ihren Heimatort Teilen Sie Ihren Artikel und Ihr Foto', "", x, perl = TRUE)
-  x = gsub("Bericht schreiben", "", x)
-  x = gsub("Vielen Dank! Ihr Kommentar wurde abgeschickt.", "", x)
-  x = gsub("Hier können Sie selbst Artikel verfassen:","", x)
-  x = gsub("Live-Ticker", "", x)
-  x = gsub('Aus unserem Netzwerk[^"]*', "", x, perl = TRUE)
-
-  # Spiegel.de
-  x = gsub("7 mal 17", "", x)
-  x = gsub("Zur Startseite Diesen Artikel... Drucken Feedback Nutzungsrechte", "", x)
-  x = gsub('Liebe Leserin, lieber Leser,\num diesen[^"]*', "", x)
-  x = gsub('Liebe Leserin, lieber Leser, um diesen[^"]*', "", x)
-  x = gsub('ejf[^"]*', "", x)
-  x = gsub('tjf[^"]*', "", x)
-  x = gsub('Fotostrecke[^"]*', "", x, perl = TRUE, ignore.case = TRUE)
-  x = gsub('Florian Gathmann[^\n]*', "", x, perl = TRUE)
-
-  # Zeit.de
-  x = gsub("Inhalt Seite", "", x)
-  x = gsub('Seitennavig[^"]*',"", x, perl=TRUE)
-  x = gsub('Kartengeschichte[^"]*', "", x, perl = TRUE, ignore.case = TRUE)
-
-  # Stern.de
-  x = gsub('Fullscreen[^\n]*', "", x, perl = TRUE)
-
-  return(x)
-}
-
-# apply function to dataframe
-btw$text_cleaned <- clean.text(btw$title.text)
-```
-
-```{r}
-btw$text_cleaned <- gsub("[[:punct:]]", " ", btw$text_cleaned)
-btw$text_cleaned <- gsub("[[:cntrl:]]", " ", btw$text_cleaned)
-btw$text_cleaned <- gsub("[[:digit:]]", " ", btw$text_cleaned)
-btw$text_cleaned <- gsub("^[[:space:]]+", " ", btw$text_cleaned)
-btw$text_cleaned <- gsub("[[:space:]]+$", " ", btw$text_cleaned)
-btw$text_cleaned <- tolower(btw$text_cleaned)
-```
-
-## Remove Stopwords
-```{r}
-btw$text_cleaned<- removeWords(btw$text_cleaned, stopwords("german"))
-```
-
-### Remove customized stopwords
-```{r}
-mystopwords <- c("focus","online","spiegel", "stern", "handelsblatt", "de", "bild","bildplus", "zeit", "ersten", "tagesschau", "wdr", "ndr", "ich","sie","passwort","kommentar","wurde","ihr","der","im","artikel","mehr","ihren","foto","e","seien","comment", "uhr","videolänge","dass","mindestens","das","mail","die","schon","neuer abschnitt", "login", "loggen", "inaktiv", "nwmi", "nwnoa", "polizei","beim","dpa","video","quelle","afp","witters","fotogalerie","wurden","worden","wegen","sagt","immer","gibt","geht","spon", "registrierter","als","spiegel","vielen","in","es","bitte","dank","unserer","nutzer","sei","beitrag","user","seit","zeichen", "datenschutzerklärung","premium","nutzungsbedingungen","nutzungsrechte","pflichtfelder","registrierung","anzeige","großbuchstaben","sonderzeichen","html","seitennavigation","fullscreen","statista","club","sagte","borenda","spreepicture","shopübersicht")
-
-mystopwords <- distinct(as.data.frame(mystopwords))
-
-btw$text_cleaned<- removeWords(btw$text_cleaned, mystopwords$mystopwords)
-```
-
-## Stemming (not applied)
-```{r }
-stem_text<- function(text, language = "porter", mc.cores = 1) {
-  # stem each word in a block of text
-  stem_string <- function(str, language) {
-    str <- strsplit(x = str, split = "\\s")
-    str <- wordStem(unlist(str), language = language)
-    str <- paste(str, collapse = " ")
-    return(str)
-  }
-
-  # stem each text block in turn
-  x <- mclapply(X = text, FUN = stem_string, language, mc.cores = mc.cores)
-
-  # return stemed text blocks
-  return(unlist(x))
-}
-
-btw$text_cleaned <- stem_text(btw$text_cleaned)
-```
-
-```{r}
-load(file="../output/btw_combined.Rda")
-```
-
-# Extract FB Shares
-```{r}
-endpoint <- "https://api.sharedcount.com/?url="
-api1 <- "&apikey=24abe04472f42e5003938b0314844010d6425d37"
-api2 <- "&apikey=68d76247a02b3d39ff592aa5616ce9f73f182934"
-
-pattern <- 'share_count\\":[0-9]+'
-shares <- NULL
-
-for (i in (length(shares)+1):nrow(btw)){
-  page <- readLines(paste0(endpoint,btw$url[i],api2))
-  string <- str_extract(page, pattern)
-  shares <- append(shares, as.numeric(str_extract(string, "[0-9]+")))
-}
-```
-
-```{r}
-btw <- cbind(btw, shares)
-
-btw.reg %>%
-  filter(is.na(shares)) -> test
-```
-
-```{r}
-save(btw, file="../output/btw_combined.Rda")
-```

### 2018-01-21 paper/R/02_cleanAndCombine.Rmd
add Welt.de, user China.R skript. create backup

@@
 
-## select stratified random sample
-```{r}
-public <- c("deutschlandfunk.de", "heute.de", "ndr.de", "swr.de", "tagesschau.de", "wdr.de", "zdf.de")
-
-df_full <- df_full %>% 
-  mutate(ownership = ifelse(site %in% public, "public", "private"),
-         month = month(date))
-
-df_full %>% 
-  #filter may2017 and january2018
-  filter(month>5) %>%
-  #calculate site totals by month
-  group_by(site, month) %>%
-  summarize(site_sum = n()) %>%
-  ungroup() %>%
-  #calculate month total
-  group_by(month) %>%
-  mutate(month_sum = sum(site_sum)) %>%
-  ungroup() %>%
-  #calculate share
-  mutate(share = 100*(site_sum/month_sum))-> totals_site
-
-df_full %>% 
-  #filter may2017 and january2018
-  filter(month>5) %>%
-  # calculate ownership totals by month
-  mutate(ownership = ifelse(site %in% public, "public", "private")) %>%
-  group_by(ownership, month) %>%
-  summarize(owner_sum = n()) %>%
-  #calculate month total
-  group_by(month) %>%
-  mutate(month_sum = sum(owner_sum)) %>%
-  ungroup() %>%
-  #calculate share
-  mutate(share = 100*(owner_sum/month_sum))-> totals_ownership
-```
-
 # Pre-Process Text
@@
 ```{r}
+df_full %>%
+  mutate(month=month(date)) %>%
+  filter(month > 5) %>%
+  ggplot(aes(site, fill=factor(month))) +
+  geom_bar() +
+  labs(x="", y="") +
+  theme(axis.text.x = element_text(angle = 60))
+```
+
+```{r}
 keeps <- c("spiegel.de", "focus.de", "zeit.de","bild.de",
-           "tagesschau.de")
+           "tagesschau.de", "welt.de")
 
@@
 #   mutate(politics = ifelse(grepl(pat, title_text, ignore.case = TRUE),1,0)) -> btw1
-
-#df %>% filter(site=="tagesschau.de") %>% select(url)
-```
-
-```{r}
-df %>%
-  #filter(politics==1) %>%
-  ggplot(aes(site, fill=factor(politics))) +
-  geom_bar(show.legend = FALSE, alpha=0.8)
 ```
@@
 load("../output/btw_combined.Rda")
+```
+
+```{r}
+btw %>%
+  ggplot(aes(site)) +
+  geom_bar(show.legend = FALSE, alpha=0.8)
 ```
@@
          site = ifelse(site=="zeit.de","ZEIT ONLINE",site),
-         site = ifelse(site=="tagesschau.de","Tagesschau.de",site)) -> btw
+         site = ifelse(site=="tagesschau.de","Tagesschau.de",site),
+         site = ifelse(site=="welt.de","DIE WELT",site)) -> btw
 ```
@@
 # Process data
-processed1 <- textProcessor(btw$text_cleaned, metadata = btw[,c("site","text_cleaned","month")],
+
+### without stemming
+# processed1 <- textProcessor(btw$text_cleaned, metadata = btw[,c("site","text_cleaned","month")],
+#                            wordLengths = c(2,Inf),
+#                            lowercase = F,
+#                            removestopwords = F,
+#                            removenumbers = F,
+#                            removepunctuation = F,
+#                            stem = F)
+# out1 <- prepDocuments(processed1$documents, processed1$vocab, processed1$meta)
+###
+
+processed <- textProcessor(btw$text_cleaned1, metadata = btw[,c("site","text_cleaned1","month")],
                            wordLengths = c(2,Inf),
@@
                            stem = F)
-out1 <- prepDocuments(processed1$documents, processed1$vocab, processed1$meta)
+out <- prepDocuments(processed$documents, processed$vocab, processed$meta)
+out$meta$site <- as.factor(out$meta$site)
 
-processed2 <- textProcessor(btw$text_cleaned1, metadata = btw[,c("site","text_cleaned1","month")],
-                           wordLengths = c(2,Inf),
-                           lowercase = F,
-                           removestopwords = F,
-                           removenumbers = F,
-                           removepunctuation = F,
-                           stem = F)
-out_stemmed <- prepDocuments(processed2$documents, processed2$vocab, processed2$meta)
-
-save(btw, out1, out_stemmed, file="../output/btw_combined.Rda")
+save(btw, out, file="../output/btw_combined.Rda")
 ```

### 2018-01-21 paper/R/backup.Rmd
add Welt.de, user China.R skript. create backup

@@
 rm(list = ls())
-
-load("../output/news_btw.Rda")
-load("../output/news_btw2.Rda")
-```
-
-```{r}
-common_cols <- intersect(colnames(btw1), colnames(btw2))
-
-btw <- rbind(
-  btw1[, common_cols], 
-  btw2[, common_cols]
-)
-```
-
-## Remove Articles after 10.10.2017
-```{r}
-btw %>%
-  filter(date < as.Date("2017-10-10")) -> btw
-```
-
-## Generate new variables
-```{r}
-btw$video <- ifelse(grepl("video", btw$title, ignore.case = TRUE), 1,0)
-```
-
-## Save data
-```{r}
-save(btw, file="../output/btw_combined.Rda")
-```
-
-```{r}
-ggplot(btw, aes(site)) + 
-  geom_bar()
-```
-
-```{r}
-btw %>%
-  filter(site == "stern.de") %>%
-  arrange(desc(fb_shares)) %>%
-  select(title, fb_shares) %>%
-  .[1:100,]
-```
-
-```{r}
-ggplot(btw, aes(date, fill=site)) +
-  geom_bar()
 ```
@@
 
-### Text Length
-```{r}
-ggplot(btw, aes(x=as.factor(site), y=text_length)) +
-  stat_summary(fun.y="median", geom="bar", fill = "blue", alpha = .5) +
-  labs(title = "") +
-  labs(x="", y="Median Text Length") +
-  theme(axis.text.x = element_text(angle = 40, hjust = 1))
+## Sample Articles
+
+```{r Document classification}
+set.seed(9272)
+posts_classification.sdt <-
+  posts.dtp %>% 
+  #filter(topic %in% keeps) %>%
+  group_by(articleID = document) %>% 
+  summarise(topic = min(topic[gamma == max(gamma)]), gamma = max(gamma)) %>% 
+  ungroup() %>%
+  inner_join(btw %>% 
+               #filter(topic %in% keeps) %>%
+               select(title, title_text, articleID, topic_name, site),
+              by = "articleID") %>%
+  mutate(topic_title = 
+           paste0("Topic ", formatC(topic, flag = "0", width = 2), 
+                  " - ", topic_name)) %>%
+  group_by(topic_name, site) %>% 
+  top_n(10, gamma) %>%
+  sample_n(3, replace = TRUE) %>%
+  mutate(row = row_number()) %>% 
+  ungroup() 
 ```
 
-### Facebook Likes
 ```{r}
-ggplot(btw, aes(x=as.factor(site), y=fb_shares)) +
-  stat_summary(fun.y="median", geom="bar", fill = "blue", alpha = .5) +
-  labs(title = "") +
-  labs(x="", y="Median of Facebook Shares") +
-  theme(axis.text.x = element_text(angle = 40, hjust = 1))
+posts_classification.sdt %>%
+  select(site,topic_title,title) %>%
+  htmlTable::htmlTable(align="l")
 ```
+
+## Estimating the Effect of Covariates
+
+### Difference in topic prevalence
+The estimateEffect() function explores how prevalence of topics varies across documents according to document covariates (metadata).
+First, users must specify the variable that they wish to use for calculating an effect.
+If there are multiple variables specified in estimateEffect(), then all other variables are held at their sample median.
+These parameters include the expected proportion of a document that belongs to a topic as a function of a covariate, or a first difference type estimate, where topic prevalence for a particular topic is contrasted for two groups.
+
+```{r}
+effect <- estimateEffect(c(1:40) ~site+s(month), stmOut, 
+                         metadata = out$meta, uncertainty = "None")
+plot.estimateEffect(effect, "month", topics=c(33), method = "continuous", npoints=500)
+```
+
+```{r}
+summary(effect)
+```
+
+Expected difference in topic probability by news source (with 95% Confidence Intervals). 
+parameter "covariate": String of the name of the main covariate of interest.
+Must be enclosed in quotes.
+All other covariates within the formula specified in estimateEffect will be kept at their median.
+```{r}
+for (i in 1:40){
+
+  png(paste0("../figs/estimate_effect",i,".png"))
+  plot(prep, "site", method = "pointestimate", topics = i,
+       labeltype = "custom", custom.labels = unique(prep$data$site),
+       ylab = "", xlab = "Mean topic proportion in corpus",
+       main = paste0("Topic ",topicLabel$topic_name[i]),
+       xlim = c(-.05,0.2))
+  dev.off()
+}
+
+#plot(prep, "site", method = "pointestimate", topics = keeps[1])
+```
+
+```{r}
+# for (i in 1:40){
+#   plot(prep, "month", method = "continuous", topics = i,
+#        printlegend = F,
+#        ylab = "", xlab = "Mean topic proportion in corpus",
+#        main = paste0("Topic ",i,": ",topicLabel$topic_name[i]))
+# }
+```
+
+```{r}
+p<- posts.dtp %>%
+  left_join(., btw %>% select(document, topic_name,
+                              site, month),
+            by="document")  %>%
+  group_by(site, topic, topic_name, month) %>%
+  summarize(gamma_mean = mean(gamma)) %>%
+  #filter(month!=5) %>%
+  ggplot(aes(x=month, y=gamma_mean, fill=factor(topic), text=topic_name)) +
+  geom_col() +
+  facet_wrap(~site) +
+  #facet_grid(~site) +
+  theme(legend.position = "none") +
+  xlab("Month")
+
+ggplotly(p)
+```
+
+What is the distribution of the gamma value?
+```{r}
+ggsave(plot={
+  btw %>%
+    #filter(topic %in% keeps) %>%
+  ggplot(aes(gamma)) +
+  geom_density(fill="blue",alpha=.5,color="blue") 
+},
+filename = "../figs/gamma_dist.png",
+       width = 8, height = 6, device = "png", dpi=600)
+```
+
+## Topic Timeline
+```{r Data for topic trends chart, message=FALSE, warning=FALSE}
+set.seed(7292)
+btw %>% 
+  mutate(date = as.POSIXct(date),
+         allocation = 1) %>%
+  mutate(post_period = 
+           date %>% with_tz("Europe/Paris") %>% 
+           floor_date("week")) %>%
+  # Summarise into tidy dataframe
+  group_by(post_period, topic, topic_name) %>% dplyr::summarise(articles = sum(allocation)) %>%
+  # Mark peaks 
+  group_by(topic_name) %>% dplyr::mutate(peak = ifelse(articles==max(articles),1,0)) -> chart_topic_trends.dt
+```
+
+```{r message=FALSE, warning=FALSE}
+ggsave(
+  plot = {
+    ggplot(chart_topic_trends.dt, 
+       aes(post_period, articles, color=topic_name)) +
+  geom_line(show.legend = FALSE) +
+  scale_color_manual(
+            values = rainbow(60) %>% 
+              adjustcolor(red.f = 0.6, green.f = 0.6, blue.f = 0.6)
+          ) +
+      geom_text_repel(data= subset(chart_topic_trends.dt,peak==1 & articles >=25),
+            aes(post_period,articles,label=topic_name), vjust = -1, size = 2,
+            size=2.8) +
+      geom_vline(aes(xintercept=as.POSIXct("2017-09-23")),
+                 linetype = 2, color="grey20") +
+      geom_vline(aes(xintercept=as.POSIXct("2017-11-19")),
+                 linetype = 2, color="grey20") +
+  ylim(c(0,120)) +
+    theme(
+      legend.position = "none",
+      #plot.background   = element_rect("#fafafa", "#fafafa"),
+      plot.title        = element_text(size = 18),
+      plot.subtitle     = element_text(size = 8),
+      plot.caption      = element_text(size = 7),
+      panel.grid        = element_blank(),
+      #panel.background  = element_rect("#fafafa"),
+      axis.title.x      = element_blank(),
+      axis.text.y       = element_text(size = 8)
+    )
+  },
+  device = "png",
+  filename = "../figs/topic-timeline.png",
+  dpi = 600, height = 5, width = 8
+)
+```
+
+### Topic Distribution by News Page
+
+A common accusation leveled against traditional news media is the amount of bias in reporting various topics. We try to explore the topic distribution of news articles.
+
+```{r}
+library(radarchart)
+```
+
+```{r}
+btw %>% 
+  group_by(site, topic, topic_name) %>%
+  summarise(articles = sum(allocation)) %>%
+  ungroup() %>%
+  group_by(site) %>%
+  mutate(perc_articles = articles/sum(articles)) %>% 
+  ungroup() %>%
+  transmute(site=site,
+            perc_articles=perc_articles,
+            topic=topic_name) %>%
+  spread(key=site, value=perc_articles) %>%
+  ungroup() %>%
+  mutate(topic=factor(topic)) -> radar
+```
+
+```{r}
+chartJSRadar(scores = radar, labelSize = 9, maxScale = 0.1, 
+             showToolTipLabel = TRUE,
+             width = 8, height = 8)
+```
+
+## Sentiment analysis
+
+```{r}
+sent <- c(
+  # positive Wörter
+  readLines("dict/SentiWS_v1.8c_Negative.txt",
+            encoding = "UTF-8"),
+  # negative Wörter
+  readLines("dict/SentiWS_v1.8c_Positive.txt",
+            encoding = "UTF-8")
+) %>% lapply(function(x) {
+  # Extrahieren der einzelnen Spalten
+  res <- strsplit(x, "\t", fixed = TRUE)[[1]]
+  return(data.frame(words = res[1], value = res[2],
+                    stringsAsFactors = FALSE))
+}) %>%
+  bind_rows %>% 
+  mutate(word = gsub("\\|.*", "", words) %>% tolower,
+         value = as.numeric(value)) %>% 
+  # manche Wörter kommen doppelt vor, hier nehmen wir den mittleren Wert
+  group_by(word) %>% summarise(value = mean(value)) %>% ungroup
+```
+
+```{r, message=FALSE, warning=FALSE, include=FALSE}
+# Tokenize text
+token <- btw %>%
+  unnest_tokens(word, text_cleaned1)
+
+# Combine with sentiment values
+sentDF <- left_join(token, sent, by="word") %>% 
+  mutate(sentiment = as.numeric(value)) %>% 
+  filter(!is.na(sentiment)) 
+```
+
+```{r fig.height=12}
+sentDF %>% group_by(topic_name, site) %>% 
+  summarize(sentiment = mean(sentiment)) %>%
+  ggplot(aes(topic_name, sentiment, fill=site)) +
+  geom_col(fill=col[3], alpha=0.8) +
+    facet_wrap(~site, ncol = 1) +
+    labs(x="", y="sentiment value") +
+    theme(axis.text.x = element_text(size=10, angle = 90))
+```
+
+### Radar plot
+```{r}
+sentDF %>% 
+  select(site, topic_name, sentiment) %>%
+  spread(key=site, value=sentiment) %>%
+  ungroup() -> radar
+```
+
+```{r}
+chartJSRadar(scores = radar, labelSize = 8, maxScale = 1000, showToolTipLabel = TRUE,
+             addDots = FALSE, showLegend = FALSE,
+             width = 8, height = 8)
+```
+
+### Using sentimentr
+```{r}
+library(sentimentr)
+```
+
+```{r}
+# Load dictionaries (from: http://wortschatz.uni-leipzig.de/de/download)
+neg_df <- read_tsv("dict/SentiWS_v1.8c_Negative.txt", col_names = FALSE)
+pos_df <- read_tsv("dict/SentiWS_v1.8c_Positive.txt", col_names = FALSE)
+
+sentiment_df <- bind_rows(neg_df,pos_df)
+names(sentiment_df) <- c("Wort_POS", "polarity", "Inflektionen")
+
+sentiment_df %>% 
+  mutate(words = str_sub(Wort_POS, 1, regexpr("\\|", .$Wort_POS)-1),
+         words = tolower(words)
+         #POS = str_sub(Wort_POS, start = regexpr("\\|", .$Wort_POS)+1)
+         ) %>%
+  select(words, polarity) -> sentiment_df
+
+sentiment_df <- rbind(sentiment_df, c("nicht",-0.8))
+
+sentiment_df %>% mutate(polarity = as.numeric(polarity)) %>%
+  as_key() -> sentiment_df
+```
+
+```{r}
+btw.reg %>% 
+  mutate(text_split = get_sentences(text)) %$%
+  sentiment(text_split,
+               polarity_dt = sentiment_df) -> btw_sentiment
+
+btw_sentiment_doclevel <- btw_sentiment %>%
+  group_by(element_id) %>%
+  summarize(sentiment = mean(sentiment))
+
+btw.reg <- left_join(btw.reg, btw_sentiment_doclevel %>%
+                       mutate(document = element_id) %>%
+                       select(document, sentiment),
+                      by="document")
+btw.reg %>%
+  group_by(site) %>%
+  mutate(ave_sentiment = mean(sentiment, na.rm = T)) -> plot_btw
+```
+
+```{r}
+p1 <- plot_btw %>%
+  ggplot(aes(sentiment, factor(site), color=topic_name, 
+             text=paste(document,": ",title))) +
+  geom_point(alpha=.5, shape=1) +
+  xlim(c(-0.25,0.1)) +
+  facet_wrap(~topic_name) +
+  labs(y="") +
+  theme(legend.position = "none")
+
+ggplotly(p1)
+```
+
+```{r}
+btw.reg %>% 
+  filter(document==372) %>%
+  mutate(text_split = get_sentences(text)) %$%
+  sentiment_by(text_split,
+               polarity_dt = sentiment_df) %>%
+  sentimentr::highlight()
+```
+
+```{r}
+btw.reg %>% 
+  filter(document==4) %>% select(text_cleaned)
+```
+
+### Radar
+#### with ggiraphExtra
+```{r}
+require(ggiraphExtra)
+```
+
+```{r}
+btw.reg %>%
+  group_by(site, topic_name) %>%
+  summarize(sentiment = mean(sentiment, na.rm = T)) %>%
+  spread(topic_name, sentiment) -> radar
+  ungroup() %>%
+  mutate(topic=factor(topic_name)) -> radar
+```
+
+```{r}
+ggsave(plot={
+  ggRadar(radar, aes(color=site), rescale = FALSE,
+        legend.position = "none") 
+  facet_wrap(~topic)
+},
+file="../figs/radar.png",
+dpi=600,
+height = 7,
+width = 9
+)
+```
+
+#### with radarchart
+
+```{r}
+btw.reg %>% 
+  group_by(site, topic, topic_name) %>%
+  summarise(sentiment = mean(sentiment, na.rm = TRUE)) %>%
+  ungroup() %>%
+  transmute(site=site,
+            sentiment=sentiment,
+            topic=paste(topic, topic_name, sep=": ")) %>%
+  spread(key=site, value=sentiment) %>%
+  ungroup() %>%
+  mutate(topic = factor(topic))-> radar
+```
+
+```{r}
+chartJSRadar(scores = radar, labelSize = 8, maxScale = 0.1, showToolTipLabel = TRUE,
+             addDots = FALSE, showLegend = FALSE,
+             width = 8, height = 8)
+```

### 2018-01-21 paper/R/paper.Rmd
add Welt.de, user China.R skript. create backup

@@
 library(readxl)
+library(Matrix)
 
@@
 library(ggrepel)
-#library(plotly)
 library(scales)      # Scales
@@
 rm(list=ls())
-col <- brewer.pal(5,"Dark2")
+col <- brewer.pal(6,"Dark2")
 ```
 
-# The online news market
+# 1. The online news market
 
@@
 
-# Data
-
+# 2. Data 
 ```{r caching, echo = FALSE}
@@
 
-# Model Results
-
+# 3. Model Results
 ```{r caching, echo = FALSE}
-#load("../output/models/STM 60 .Rda")
+load("../output/models/STM_stemmed2 40 .Rda")
 ```
 
+## Label topics
+```{r}
+sagelabs <- sageLabels(stmOut, 100)
+```
+
+```{r}
+stmOut$settings$covariates$yvarlevels
+```
+
+### Label topics based on Bild.de
+
+After reviewing a sample of articles assigned to the respective topic, we assign a shorter name to the topics based on the most common words in order to improve readability and traceability.
+```{r}
+sagelabs$cov.betas[[1]]$problabels[,1:10]
+```
+
+```{r}
+topics <- matrix(c(1, "Great coalition", 2, "Merkel,election campaign", 3, "Jamaica coalition", 
+                   4, "Diesel scandal", 5, "Merkel chancellor", 6, "Seehover vs. Söder", 
+                   7, "Germany, EU, Jamaika", 8, "Merkel vs.Schulz", 9, "AfD election results", 
+                   10, "Steinmeier,Federal President", 11, "unclear (Schröder, Google)", 
+                   12, "Federal Election in social media", 13, "Climate policy", 14, "G20 Hamburg", 
+                   15, "error", 16, "Education, Pension policy", 17, "Reports on individuals",
+                   18, "Family reunion refugees", 19, "Polls federal election", 
+                   20, "AfD top candidates Weidel, Storch", 21, "M.Schwesig (SPD)",
+                   22, "elections in Niedersachsen", 23, "Böhmermann vs. Erdogan", 
+                   24, "political talkshows", 25, "German armed forces", 26, "W.Schäuble", 
+                   27, "C.Lindner FDP", 28, "Turkey, Russia", 29, "A.Merkel Youtube", 
+                   30, "H.Kohl obituary", 31, "AfD Gauland, Höcke", 32, "Asylum claims and deportation", 
+                   33, "EU policies", 34, "DIE LINKE", 35, "SPD", 36, "Islam and antisemitism in GER", 
+                   37, "AfD in parliament", 38, "Terror attacks (GER)  & police reports", 
+                   39, "Church", 40, "RAF"), ncol=2, byrow=T)
+```
+
+## Assign a topic to each document (choose by gamma)
 ```{r Extract wtp and dtp}
-# Word-topic probabilities
-stmOut %>% tidy("beta") %>% filter(!is.na(topic)) -> posts.wtp
 # Document-topic probabilities
-stmOut %>% tidy("gamma") -> posts.dtp
+stmOut %>% tidy("theta") -> theta
 
-##################
-# Topic Labeling #
-##################
-label <- labelTopics(stmOut, n=5)
-
-prob <- as.data.frame(label$prob, stringsAsFactors = F)
-frex <- as.data.frame(label$frex, stringsAsFactors = F)
-lift <- as.data.frame(label$lift, stringsAsFactors = F)
-score <- as.data.frame(label$score, stringsAsFactors = F)
-
-topicLabel <- prob %>%
-  transmute(topic = rownames(.),
-            topic_name = paste(topic,": ",prob$V1,prob$V2,prob$V3,score$V1,score$V2,score$V3, sep=","),
-            prob = paste(prob$V1,prob$V2,prob$V3, sep=","),
-            frex = paste(frex$V1,frex$V2,frex$V3, sep=","),
-            lift = paste(lift$V1,lift$V2,lift$V3, sep=","),
-            score = paste(score$V1,score$V2,score$V3, sep=","))
-
-topicLabel$topic_name <- vapply(lapply(strsplit(topicLabel$topic_name, ","), unique), paste, character(1L), collapse = " ")
-rm(prob, frex, lift, score)
-
-####################################################
-# Assign topic with highest gamma to each document #
-####################################################
-
-top_topics <-
-  posts.dtp %>% 
+top_topics <- theta %>% 
   group_by(document) %>%
   mutate(therank = rank(-gamma, ties.method = "random")) %>%
-  filter(therank %in% 1) %>%
+  filter(therank == 1) %>%
   select(- therank)
 
-btw %>%
+topics.df <- as.data.frame(topics) %>% transmute(topic = as.integer(V1),
+                                 topic_name = paste(topic, V2, sep=": "))
+
+btw.2 <- btw %>%
   mutate(document = articleID) %>%
@@
   ## Combine with Topic label
-  left_join(., topicLabel %>%
-              select(topic_name, topic) %>%
-              mutate(topic = as.numeric(topic)), by="topic") %>%
-  filter(gamma >= 0.5) %>%
-  mutate(allocation = 1) -> btw
+  left_join(., topics.df, by="topic") %>%
+  mutate(allocation = 1) 
 ```
 
-After reviewing a sample of articles assigned to the respective topic, we assign a shorter name to the topics based on the most common words in order to improve readability and traceability.
-
+### now we can inspect the unclear topics
 ```{r}
-btw %>% group_by(topic, site) %>%
-  select(topic_name, title) %>% top_n(3) %>%
-  arrange(topic) %>%
+btw %>% filter(topic==17) %>% select(title, gamma, url) %>%
   htmlTable::htmlTable(align="l")
@@
 
-```{r}
-topic_name <- c("1: A.Merkel & K.-T.z.Guttenberg","2: SPD (Schulz,Nahles)","3: Election in Niedersachsen","4: Election campaigns", 
-                "5: car industry, diesel", "6: exploratory talks CDU/SPD","7: exploratory talks Jamaika",
-                "8: people in GER, christmas speech Steinmeier", "9: CSU (Seehofer,Söder)", "10: Federal Election (various)",
-                "11: Schulz, TV-Duell", "12: G20 riots", "13: digital & telecommunication topics","14: regional politics", 
-                "15: text-processing failure", "16: Turkey (Erdoğan)", "17: Federal statistics", "18: various electoral districts", 
-                "19: SPD (Nahles, Geißler, Klingbeil,...)", "20: EU policies, refugee debate", "21: poll results", 
-                "22: FDP (C.Lindner)", "23: election campaign A.Merkel (riots finsterwalde)", "24: Armed Forces (v.d.Leyen)", 
-                "25: Twitter fail", "26: AfD internal party structures", "27: H.Maas, Facebook, social media", 
-                "28: SPD (Schwesig), women, sexism", "29: USA, D.Trump, UN-climate conference", "30: same-sex marriage vote", 
-                "31: DIE LINKE", "32: Muslims in GER, anti-Semitism", "33: S.Gabriel, G.Schröder, Russia", 
-                "34: AfD (Gauland, Höcke,...)", "35: BAMF, BND, BKA", "36: church, people", "37: political talkshows", 
-                "38: legal judgments (linksunten, insider trading, ...)", "39: Bundestag (AfD, Schäuble, Lammert)",
-                "40: refugees, deportation", "41: Terrorism in GER (NSA)", "42: refugee cap, family reunion", 
-                "43: general statistics", "44: AfD general", "45: RAF, Steinmeier", "46: Glyphosat, Schmidt, (green) policy",
-                "47: Terror attacks in GER (Breitscheidplatz)", "48: crime, healthcare statistics", "49: Helmut Kohl", "50: Muslims in GER", "51: SPD, Schulz", "52: Glyphosat scandal",
-                "53: Attack in Hamburg", "54: A.Merkel (pension policy)", "55: H.Kohl", "56: Election in Niedersachsen, various", 
-                "57: Terrorism, Rock am Ring", "58: Guttenberg, CSU", "59: CDU/SPD coalition", "60: statistics about crimes&terrorism")
+## Expected topic proportions
 
-topic_name <- as.data.frame(topic_name) %>%
-  mutate(topic = seq(1:60))
-
-btw <- btw %>% select(- topic_name) %>%
-  left_join(., topic_name, by = "topic")
-
-btw %>% filter(topic==24 & site=="SPIEGEL ONLINE") %>% select(text_cleaned1) %>% .[2,]
-```
-
-Figure \ref{fig_topic_proportion} displays the topics ordered by their expected frequency across the corpus.
-To assign a label to each topic, we used a combination of most frequent words in that topic and words with the highest "score", computed as the log frequency of the word in the topic divided by the log frequency of the word in other topics \citep{roberts_stm:_2016}.
-The most frequent topic (4) describes the exploratory talks between the CDU/CSU, FDP and Bündnis90/Die Grünen following the federal elections.
-This is followed by topic 32, which classifies articles that deal with the NSU trial and the main defendant Zschäpe.
-
+### in the overall corpus
 ```{r}
@@
   mutate(frequency = colMeans(stmOut$theta),
-    topic=as.character(seq(1:40))) %>%
-  left_join(., topicLabel %>% select(topic, topic_name),
-            by="topic")
+    topic=paste(topics[,1],topics[,2], sep=": "))
 
-ggsave(plot = {
-  ggplot(frequency, aes(x=reorder(topic_name, frequency), y=frequency)) + 
+p1 <- ggplot(frequency, aes(x=reorder(topic, frequency), y=frequency)) + 
     geom_col(fill=col[1], alpha=0.8) +
@@
     labs(x="", y="expected frequency") +
-    theme(axis.text = element_text(size=10))
-}, filename = "../figs/topic_proportion.png", device = "png",width = 8, height = 12,
-dpi = 600)
+    theme(axis.text = element_text(size=8),
+          axis.title = element_text(size=10))
+
+p1
+
+#ggsave(plot = p1, filename = "../figs/topic_proportion.png", device = "png",width = 8, height = 12,
+#dpi = 600)
 ```
 
-![Topic Proportion](../figs/topic_proportion.png)
+## by newspaper
+```{r}
+plotNewspaperHistogram <- function(topic){
+  tab <- tapply(stmOut$theta[,topic], stmOut$settings$covariates$betaindex, mean)
+  tab <- as.data.frame(tab) %>% 
+    mutate(site=stmOut$settings$covariates$yvarlevels)
 
-## Sample Articles
-
-```{r Document classification}
-set.seed(9272)
-posts_classification.sdt <-
-  posts.dtp %>% 
-  #filter(topic %in% keeps) %>%
-  group_by(articleID = document) %>% 
-  summarise(topic = min(topic[gamma == max(gamma)]), gamma = max(gamma)) %>% 
-  ungroup() %>%
-  inner_join(btw %>% 
-               #filter(topic %in% keeps) %>%
-               select(title, title_text, articleID, topic_name, site),
-              by = "articleID") %>%
-  mutate(topic_title = 
-           paste0("Topic ", formatC(topic, flag = "0", width = 2), 
-                  " - ", topic_name)) %>%
-  group_by(topic_name, site) %>% 
-  top_n(10, gamma) %>%
-  sample_n(3, replace = TRUE) %>%
-  mutate(row = row_number()) %>% 
-  ungroup() 
+  ggplot(data=tab, aes(x=site, y=tab)) +
+    geom_col(fill=col[3]) +
+    coord_flip() +
+    theme(axis.text = element_text(size=8),
+          axis.title = element_text(size=10)) +
+    labs(x="", y=paste("expected frequency of topic",topics.df[topic,2], sep=" ")) 
+}
 ```
@@
 ```{r}
-posts_classification.sdt %>%
-  select(site,topic_title,title) %>%
-  htmlTable::htmlTable(align="l")
+# Topic 3
+plotNewspaperHistogram(1)
 ```
 
-## Estimating the Effect of Covariates
+## Topic Correlation
+```{r}
+topicCorrelation <- function(ylevel) {
+  cormat <- cor(stmOut$theta[stmOut$settings$covariates$betaindex==ylevel,])
+  adjmat <- ifelse(cormat > .04,1,0)
 
-### Difference in topic prevalence
-The estimateEffect() function explores how prevalence of topics varies across documents according to document covariates (metadata).
-First, users must specify the variable that they wish to use for calculating an effect.
-If there are multiple variables specified in estimateEffect(), then all other variables are held at their sample median.
-These parameters include the expected proportion of a document that belongs to a topic as a function of a covariate, or a first difference type estimate, where topic prevalence for a particular topic is contrasted for two groups.
+  corr <- list()
+  corr$posadj <- adjmat
+  corr$poscor <- cormat*adjmat
+  corr$cor <- ifelse(abs(cormat)>.04,cormat,0)
 
-```{r}
-prep <- estimateEffect(1:40 ~site + s(month),
-                       stmOut, meta=out_stemmed$meta, uncertainty = "Global")
+  x <- corr$posadj[1:nrow(corr$posadj),1:nrow(corr$posadj)]
+
+  g<- graph.adjacency(x, mode="undirected", weighted=TRUE, diag=FALSE)
+
+  E(g)$size <- 1
+  E(g)$lty <- 2
+  E(g)$color <- "black"
+  V(g)$label <- topics[,2]
+  layout <- layout_nicely
+
+  plot.igraph(g, layout=layout_nicely, vertex.color="white", label.font = "Roboto",
+     vertex.frame.color="grey", vertex.size=1, vertex.label.cex=.6, edge.color="red",
+     edge.width=1, main=paste("Topic correlation", stmOut$settings$covariates$yvarlevels[ylevel]))
+}
 ```
@@
 ```{r}
-summary(prep)
+topicCorrelation(5)
 ```
 
-Expected difference in topic probability by news source (with 95% Confidence Intervals). 
-parameter "covariate": String of the name of the main covariate of interest.
-Must be enclosed in quotes.
-All other covariates within the formula specified in estimateEffect will be kept at their median.
+### Overlapping Correlation
 ```{r}
-for (i in 1:40){
+topicCorrCompare <- function(ylevel1, ylevel2) {
 
-  png(paste0("../figs/estimate_effect",i,".png"))
-  plot(prep, "site", method = "pointestimate", topics = i,
-       labeltype = "custom", custom.labels = unique(prep$data$site),
-       ylab = "", xlab = "Mean topic proportion in corpus",
-       main = paste0("Topic ",topicLabel$topic_name[i]),
-       xlim = c(-.05,0.2))
-  dev.off()
+  # find all edges between topics where they exhibit a positive correlation above 0.1
+  cormat <- cor(stmOut$theta[stmOut$settings$covariates$betaindex==ylevel1,])
+  adjmat <- ifelse(cormat > .1,1,0)
+
+  corr.1 <- list()
+  corr.1$posadj <- adjmat
+  corr.1$poscor <- cormat*adjmat
+  corr.1$cor <- ifelse(abs(cormat)>.04,cormat,0)
+
+  # Ylevel 2
+  cormat <- cor(stmOut$theta[stmOut$settings$covariates$betaindex==ylevel2,])
+  adjmat <- ifelse(cormat > .1,1,0)
+
+  corr.2 <- list()
+  corr.2$posadj <- adjmat
+  corr.2$poscor <- cormat*adjmat
+  corr.2$cor <- ifelse(abs(cormat)>.04,cormat,0)
+
+  # Prepare plot
+  g.1 <- graph.adjacency(corr.1$cor, mode="undirected", weighted = T, diag = F) 
+  g.2 <- graph.adjacency(corr.2$cor, mode = "undirected", weighted = T, diag = F)
+
+  inter.graph <- graph.intersection(g.1, g.2)
+  added.subgraph <- graph.difference(g.1, inter.graph)
+  subs.subgraph <- graph.difference(g.2, inter.graph)
+
+  # Styling
+  E(added.subgraph)$color <- col[1]
+  E(subs.subgraph)$color <- col[2]
+  E(inter.graph)$color <- col[3]
+
+  # Matrix
+  g.whole<-graph.union(inter.graph,added.subgraph,subs.subgraph)
+  V(g.whole)$color<-col[3]
+  E(g.whole)$color <- col[2]
+  E(g.whole)[1:length(E(inter.graph))]$color<-col[3]
+  E(g.whole)[(length(E(inter.graph))+1):(length(E(inter.graph))+length(E(added.subgraph)))]$color<-col[1]
+
+  inter.list <- get.edgelist(inter.graph)
+  list.1 <- get.edgelist(added.subgraph)
+  list.2 <- get.edgelist(subs.subgraph)
+
+  # Set Frame
+  cormat <- matrix(0, nrow=100, ncol=100)
+  for(i in 1:nrow(inter.list)){
+    cormat[inter.list[i,1], inter.list[i,2]] <- .5
+    cormat[inter.list[i,2], inter.list[i,1]] <- .5
     }
 
-#plot(prep, "site", method = "pointestimate", topics = keeps[1])
+  for(i in 1:nrow(list.1)){
+    cormat[list.1[i,1], list.1[i,2]] <- -1
+    cormat[list.1[i,2], list.1[i,1]] <- -1
+    }
+
+  for(i in 1:nrow(list.2)){
+    cormat[list.2[i,1], list.2[i,2]] <- 1
+    cormat[list.2[i,2], list.2[i,1]] <- 1
+    }
+
+  cormat <- cormat[as.numeric(topics[,1]),as.numeric(topics[,1])]
+  topics2 <- sapply(topics[,2], function (x) str_replace(x, "\n", ""))
+  rownames(cormat) <- colnames(cormat) <- topics.df$topic_name
+
+  only.1 <- apply(cormat,1, function (x) sum(x==1))
+  only.2 <- apply(cormat,1, function (x) sum(x==-1))
+  both <- apply(cormat,1, function (x) sum(x==.5))
+  all <- apply(cormat,1, function (x) sum(x!=0))
+  disagree <- only.1/all + only.2/all
+
+  disagreed <- order(disagree, decreasing=F)
+  list <- topics[disagreed,2]
+  disagreemat <- cormat[disagreed, disagreed]
+  rownames(disagreemat) <- topics2[disagreed]
+  colnames(disagreemat) <- topics2[disagreed]
+
+  corrplot(disagreemat, cl.pos="n", tl.col="black", tl.cex=.5)
+  legend(40,20, c(paste(stmOut$settings$covariates$yvarlevels[ylevel1]), paste(stmOut$settings$covariates$yvarlevels[ylevel2]), "Both", "None"),
+         col=c("darkred", "darkblue", "lightblue", "white"), 
+         pch=c(15,15,16,16), cex = 0.7, box.lty = 0)
+}
 ```
 
+Pairs of topics where an edge exists in both Newspaper, we denote with a light blue dot.
+Pairs of topics where Newspaper1, but not Newspaper2 have an edge between them, we denote with a red square, and those where Newspaper2, but not Newspaper1 have an edge between them we denote with a blue square.
+We then sort the matrix by topics that are similarly correlated with other topics in Newspaper1 and Newspaper2 to those that are not similarly correlated.
 ```{r}
-# for (i in 1:40){
-#   plot(prep, "month", method = "continuous", topics = i,
-#        printlegend = F,
-#        ylab = "", xlab = "Mean topic proportion in corpus",
-#        main = paste0("Topic ",i,": ",topicLabel$topic_name[i]))
-# }
+topicCorrCompare(3,5)
 ```
 
-```{r}
-p<- posts.dtp %>%
-  left_join(., btw %>% select(document, topic_name,
-                              site, month),
-            by="document")  %>%
-  group_by(site, topic, topic_name, month) %>%
-  summarize(gamma_mean = mean(gamma)) %>%
-  #filter(month!=5) %>%
-  ggplot(aes(x=month, y=gamma_mean, fill=factor(topic), text=topic_name)) +
-  geom_col() +
-  facet_wrap(~site) +
-  #facet_grid(~site) +
-  theme(legend.position = "none") +
-  xlab("Month")
-
-ggplotly(p)
-```
-
-What is the distribution of the gamma value?
-```{r}
-ggsave(plot={
-  btw %>%
-    #filter(topic %in% keeps) %>%
-  ggplot(aes(gamma)) +
-  geom_density(fill="blue",alpha=.5,color="blue") 
-},
-filename = "../figs/gamma_dist.png",
-       width = 8, height = 6, device = "png", dpi=600)
-```
-
-## Topic Timeline
-```{r Data for topic trends chart, message=FALSE, warning=FALSE}
-set.seed(7292)
-btw %>% 
-  mutate(date = as.POSIXct(date),
-         allocation = 1) %>%
-  mutate(post_period = 
-           date %>% with_tz("Europe/Paris") %>% 
-           floor_date("week")) %>%
-  # Summarise into tidy dataframe
-  group_by(post_period, topic, topic_name) %>% dplyr::summarise(articles = sum(allocation)) %>%
-  # Mark peaks 
-  group_by(topic_name) %>% dplyr::mutate(peak = ifelse(articles==max(articles),1,0)) -> chart_topic_trends.dt
-```
-
-```{r message=FALSE, warning=FALSE}
-ggsave(
-  plot = {
-    ggplot(chart_topic_trends.dt, 
-       aes(post_period, articles, color=topic_name)) +
-  geom_line(show.legend = FALSE) +
-  scale_color_manual(
-            values = rainbow(60) %>% 
-              adjustcolor(red.f = 0.6, green.f = 0.6, blue.f = 0.6)
-          ) +
-      geom_text_repel(data= subset(chart_topic_trends.dt,peak==1 & articles >=25),
-            aes(post_period,articles,label=topic_name), vjust = -1, size = 2,
-            size=2.8) +
-      geom_vline(aes(xintercept=as.POSIXct("2017-09-23")),
-                 linetype = 2, color="grey20") +
-      geom_vline(aes(xintercept=as.POSIXct("2017-11-19")),
-                 linetype = 2, color="grey20") +
-  ylim(c(0,120)) +
-    theme(
-      legend.position = "none",
-      #plot.background   = element_rect("#fafafa", "#fafafa"),
-      plot.title        = element_text(size = 18),
-      plot.subtitle     = element_text(size = 8),
-      plot.caption      = element_text(size = 7),
-      panel.grid        = element_blank(),
-      #panel.background  = element_rect("#fafafa"),
-      axis.title.x      = element_blank(),
-      axis.text.y       = element_text(size = 8)
-    )
-  },
-  device = "png",
-  filename = "../figs/topic-timeline.png",
-  dpi = 600, height = 5, width = 8
-)
-```
-
-### Topic Distribution by News Page
-
-A common accusation leveled against traditional news media is the amount of bias in reporting various topics. We try to explore the topic distribution of news articles.
-
-```{r}
-library(radarchart)
-```
-
-```{r}
-btw %>% 
-  group_by(site, topic, topic_name) %>%
-  summarise(articles = sum(allocation)) %>%
-  ungroup() %>%
-  group_by(site) %>%
-  mutate(perc_articles = articles/sum(articles)) %>% 
-  ungroup() %>%
-  transmute(site=site,
-            perc_articles=perc_articles,
-            topic=topic_name) %>%
-  spread(key=site, value=perc_articles) %>%
-  ungroup() %>%
-  mutate(topic=factor(topic)) -> radar
-```
-
-```{r}
-chartJSRadar(scores = radar, labelSize = 9, maxScale = 0.1, 
-             showToolTipLabel = TRUE,
-             width = 8, height = 8)
-```
-
-## Sentiment analysis
-
-```{r}
-sent <- c(
-  # positive Wörter
-  readLines("dict/SentiWS_v1.8c_Negative.txt",
-            encoding = "UTF-8"),
-  # negative Wörter
-  readLines("dict/SentiWS_v1.8c_Positive.txt",
-            encoding = "UTF-8")
-) %>% lapply(function(x) {
-  # Extrahieren der einzelnen Spalten
-  res <- strsplit(x, "\t", fixed = TRUE)[[1]]
-  return(data.frame(words = res[1], value = res[2],
-                    stringsAsFactors = FALSE))
-}) %>%
-  bind_rows %>% 
-  mutate(word = gsub("\\|.*", "", words) %>% tolower,
-         value = as.numeric(value)) %>% 
-  # manche Wörter kommen doppelt vor, hier nehmen wir den mittleren Wert
-  group_by(word) %>% summarise(value = mean(value)) %>% ungroup
-```
-
-```{r, message=FALSE, warning=FALSE, include=FALSE}
-# Tokenize text
-token <- btw %>%
-  unnest_tokens(word, text_cleaned1)
-
-# Combine with sentiment values
-sentDF <- left_join(token, sent, by="word") %>% 
-  mutate(sentiment = as.numeric(value)) %>% 
-  filter(!is.na(sentiment)) 
-```
-
-```{r fig.height=12}
-sentDF %>% group_by(topic_name, site) %>% 
-  summarize(sentiment = mean(sentiment)) %>%
-  ggplot(aes(topic_name, sentiment, fill=site)) +
-  geom_col(fill=col[3], alpha=0.8) +
-    facet_wrap(~site, ncol = 1) +
-    labs(x="", y="sentiment value") +
-    theme(axis.text.x = element_text(size=10, angle = 90))
-```
-
-### Radar plot
-```{r}
-sentDF %>% 
-  select(site, topic_name, sentiment) %>%
-  spread(key=site, value=sentiment) %>%
-  ungroup() -> radar
-```
-
-```{r}
-chartJSRadar(scores = radar, labelSize = 8, maxScale = 1000, showToolTipLabel = TRUE,
-             addDots = FALSE, showLegend = FALSE,
-             width = 8, height = 8)
-```
-
-### Using sentimentr
-```{r}
-library(sentimentr)
-```
-
-```{r}
-# Load dictionaries (from: http://wortschatz.uni-leipzig.de/de/download)
-neg_df <- read_tsv("dict/SentiWS_v1.8c_Negative.txt", col_names = FALSE)
-pos_df <- read_tsv("dict/SentiWS_v1.8c_Positive.txt", col_names = FALSE)
-
-sentiment_df <- bind_rows(neg_df,pos_df)
-names(sentiment_df) <- c("Wort_POS", "polarity", "Inflektionen")
-
-sentiment_df %>% 
-  mutate(words = str_sub(Wort_POS, 1, regexpr("\\|", .$Wort_POS)-1),
-         words = tolower(words)
-         #POS = str_sub(Wort_POS, start = regexpr("\\|", .$Wort_POS)+1)
-         ) %>%
-  select(words, polarity) -> sentiment_df
-
-sentiment_df <- rbind(sentiment_df, c("nicht",-0.8))
-
-sentiment_df %>% mutate(polarity = as.numeric(polarity)) %>%
-  as_key() -> sentiment_df
-```
-
-```{r}
-btw.reg %>% 
-  mutate(text_split = get_sentences(text)) %$%
-  sentiment(text_split,
-               polarity_dt = sentiment_df) -> btw_sentiment
-
-btw_sentiment_doclevel <- btw_sentiment %>%
-  group_by(element_id) %>%
-  summarize(sentiment = mean(sentiment))
-
-btw.reg <- left_join(btw.reg, btw_sentiment_doclevel %>%
-                       mutate(document = element_id) %>%
-                       select(document, sentiment),
-                      by="document")
-btw.reg %>%
-  group_by(site) %>%
-  mutate(ave_sentiment = mean(sentiment, na.rm = T)) -> plot_btw
-```
-
-```{r}
-p1 <- plot_btw %>%
-  ggplot(aes(sentiment, factor(site), color=topic_name, 
-             text=paste(document,": ",title))) +
-  geom_point(alpha=.5, shape=1) +
-  xlim(c(-0.25,0.1)) +
-  facet_wrap(~topic_name) +
-  labs(y="") +
-  theme(legend.position = "none")
-
-ggplotly(p1)
-```
-
-```{r}
-btw.reg %>% 
-  filter(document==372) %>%
-  mutate(text_split = get_sentences(text)) %$%
-  sentiment_by(text_split,
-               polarity_dt = sentiment_df) %>%
-  sentimentr::highlight()
-```
-
-```{r}
-btw.reg %>% 
-  filter(document==4) %>% select(text_cleaned)
-```
-
-### Radar
-#### with ggiraphExtra
-```{r}
-require(ggiraphExtra)
-```
-
-```{r}
-btw.reg %>%
-  group_by(site, topic_name) %>%
-  summarize(sentiment = mean(sentiment, na.rm = T)) %>%
-  spread(topic_name, sentiment) -> radar
-  ungroup() %>%
-  mutate(topic=factor(topic_name)) -> radar
-```
-
-```{r}
-ggsave(plot={
-  ggRadar(radar, aes(color=site), rescale = FALSE,
-        legend.position = "none") 
-  facet_wrap(~topic)
-},
-file="../figs/radar.png",
-dpi=600,
-height = 7,
-width = 9
-)
-```
-
-#### with radarchart
-
-```{r}
-btw.reg %>% 
-  group_by(site, topic, topic_name) %>%
-  summarise(sentiment = mean(sentiment, na.rm = TRUE)) %>%
-  ungroup() %>%
-  transmute(site=site,
-            sentiment=sentiment,
-            topic=paste(topic, topic_name, sep=": ")) %>%
-  spread(key=site, value=sentiment) %>%
-  ungroup() %>%
-  mutate(topic = factor(topic))-> radar
-```
-
-```{r}
-chartJSRadar(scores = radar, labelSize = 8, maxScale = 0.1, showToolTipLabel = TRUE,
-             addDots = FALSE, showLegend = FALSE,
-             width = 8, height = 8)
-```
+## How they talk about GroKo differently

### 2018-01-25 paper/R/backup.Rmd
jsd

@@
 rm(list = ls())
+```
+
+## Audience Network
+```{r}
+focus <- read.csv("../data/audience_network/Audience_Overlap_1_15_2018_focus.csv", header=FALSE, comment.char="#")
+spiegel <- read.csv("../data/audience_network/Audience_Overlap_1_15_2018_spiegel.csv", header=FALSE, comment.char="#")
+bild <- read.csv("../data/audience_network/Audience_Overlap_1_15_2018_bildde.csv", header=FALSE, comment.char="#")
+zeit <- read.csv("../data/audience_network/Audience_Overlap_1_15_2018_zeitde.csv", header=FALSE, comment.char="#")
+tagesschau <- read.csv("../data/audience_network/Audience_Overlap_1_15_2018_tagesschau.csv", header=FALSE, comment.char="#")
+
+zdf <-  read.csv("../data/audience_network/Audience_Overlap_1_15_2018_zdf.csv.crdownload.csv", header=FALSE, comment.char="#")
+#stern <- read.csv("../data/audience_network/Audience_Overlap_1_15_2018_stern.csv", header=FALSE, comment.char="#")
+welt <- read.csv("../data/audience_network/Audience_Overlap_1_15_2018 _welt.csv", header=FALSE, comment.char="#")
+```
+
+```{r}
+focus <- focus[-1,1:2] 
+colnames(focus) <- c("site","focus.de")
+
+spiegel <- spiegel[-1,1:2] 
+colnames(spiegel) <- c("site","spiegel.de")
+
+bild <- bild[-1,1:2] 
+colnames(bild) <- c("site","bild.de")
+
+zeit <- zeit[-1,1:2] 
+colnames(zeit) <- c("site","zeit.de")
+
+tagesschau <- tagesschau[-1,1:2] 
+colnames(tagesschau) <- c("site","tagesschau.de")
+
+zdf <- zdf[-1,1:2] 
+colnames(zdf) <- c("site","zdf.de")
+
+welt <- welt[-1,1:2] 
+colnames(welt) <- c("site","welt.de")
+```
+
+```{r}
+# combine dataframes
+network_df <- left_join(focus[1:80,], spiegel[1:80,], by="site") %>%
+  left_join(., bild[1:80,], by = "site") %>%
+  left_join(., zeit[1:80,], by = "site") %>%
+  left_join(., tagesschau[1:80,], by = "site") %>%
+  left_join(., zdf[1:80,], by = "site") %>%
+  left_join(., welt[1:80,], by = "site")
+
+network_df <- na.omit(network_df)
+
+melted <- network_df %>%
+    gather(key="seed", value="score", focus.de:welt.de) %>%
+  mutate(score = as.integer(score),
+         site = as.factor(site),
+         seed = as.factor(seed))
+```
+
+```{r}
+p1 <- ggplot(melted, aes(seed, site, fill=score)) +
+  geom_tile() +
+  scale_fill_gradient(low="gray95",high=col[3]) +
+  scale_x_discrete(labels=c("bilde.de" = "Bild.de", 
+                            "focus.de" = "FOCUS ONLINE", 
+                            "spiegel.de" = "SPIEGEL ONLINE",
+                            "tagesschau.de" = "Tagesschau.de", 
+                            "welt.de" ="DIE WELT",
+                            "zdf.de" = "ZDF.de",
+                            "zeit.de" = "ZEIT ONLINE")) +
+  labs(x="", y="",  caption = "
+  Source: Alexa Internet, Inc. (www.alexa.com)
+      ") +
+  theme(
+      legend.text       =  element_text(size=6),
+      plot.background   = element_rect("#fafafa", "#fafafa"),
+      panel.background  = element_rect("#fafafa"),
+      axis.title.x      = element_blank(),
+      axis.text.x = element_text(size=8, angle = 45),
+      axis.text.y       = element_text(size = 8)
+    )
+
+ggsave(plot= p1,
+filename = "../figs/audience.png", device = "png",
+width = 5, height = 6,
+        dpi = 600
+)
+
+p1
 ```

### 2018-01-25 paper/R/paper.Rmd
jsd

@@
 library(igraph)
+library(corrplot)
 library(ggpmisc)
@@
 library(proxy)       # Distance measures
-
-library(htmlwidgets) # JS visuliaztions
-library(htmltools)   # Arbitrary html
 
@@
       plot.caption = element_text(size = 6),
+      plot.background   = element_rect("#fafafa", "#fafafa"),
+      panel.background  = element_rect("#fafafa"),
       panel.border = element_blank()
@@
 col <- brewer.pal(6,"Dark2")
+source("func/functions.R")
 ```
@@
 #   gather(key="site", value="reach", focus.de:n.tv.de) %>%
-#  filter(!site %in% drop) %>%
-#   mutate(site = ifelse(site=="bild.de","Bild.de",site),
-#        site = ifelse(site=="focus.de","FOCUS ONLINE",site),
-#        site = ifelse(site=="spiegel.de","SPIEGEL ONLINE",site),
-#        site = ifelse(site=="zeit.de","ZEIT ONLINE",site),
-#        site = ifelse(site=="tagesschau.de","Tagesschau.de",site),
-#        site = ifelse(site=="zdf.de","ZDF.de",site),
-#        site = ifelse(site=="welt.de","DIE WELT",site),
-#        site = ifelse(site=="n-tv.de","n-tv.de",site))
+#  filter(!site %in% drop)
+
+views <- views %>%
+  mutate(site = ifelse(site=="bild.de","Bild.de",site),
+       site = ifelse(site=="focus.de","FOCUS ONLINE",site),
+       site = ifelse(site=="spiegel.de","SPIEGEL ONLINE",site),
+       site = ifelse(site=="zeit.de","ZEIT ONLINE",site),
+       site = ifelse(site=="tagesschau.de","Tagesschau.de",site),
+       site = ifelse(site=="zdf.de","ZDF.de",site),
+       site = ifelse(site=="welt.de","DIE WELT",site),
+       site = ifelse(site=="n-tv.de","n-tv.de",site))
 
@@
                   aes(date, views, label=site),
-                  size=2.8, show.legend = F, seed = 5) +
+                  size=2.8, show.legend = F, seed = 1) +
   scale_x_date(limits = c(as.Date("2017-05-31"),as.Date("2018-02-15")),
@@
       legend.text       =  element_text(size=6),
-      plot.background   = element_rect("#fafafa", "#fafafa"),
-      panel.background  = element_rect("#fafafa"),
-      axis.title.x      = element_blank(),
       axis.text.y       = element_text(size = 8)
@@
                   aes(date, perc_change, label=site),
-                  size=2.8, show.legend = F, seed = 5) +
+                  size=3, show.legend = F, seed = 5) +
   #scale_color_manual(values = brewer.pal(8,"Dark2")) +
@@
          focus.de:tagesspiegel.de)
+
+source <- source %>%
+  mutate(site = ifelse(site=="bild.de","Bild.de",site),
+       site = ifelse(site=="focus.de","FOCUS ONLINE",site),
+       site = ifelse(site=="spiegel.de","SPIEGEL ONLINE",site),
+       site = ifelse(site=="zeit.de","ZEIT ONLINE",site),
+       site = ifelse(site=="tagesschau.de","Tagesschau.de",site),
+       site = ifelse(site=="zdf.de","ZDF.de",site),
+       site = ifelse(site=="welt.de","DIE WELT",site),
+       site = ifelse(site=="n-tv.de","n-tv.de",site))
+
 ```
@@
        caption = "Source: Alexa Internet, Inc. (www.alexa.com)") +
-  theme(axis.text.x = element_text(angle = 45, size = 7 ))
+  theme(axis.text.x = element_text(angle = 45, size = 8 ))
 
@@
 ```{r}
-keepsite <- c("tagesschau.de", "spiegel.de", "zeit.de", "deutschlandfunk.de",
-              "zdf.de", "bild.de", "welt.de", "stern.de", "sueddeutsche.de", "focus.de")
+keepsite <- c("tagesschau.de", "spiegel.de", "zeit.de", 
+              "bild.de", "welt.de", "focus.de")
 
+keywords.df.reduced <- keywords.df %>% 
+  filter(nchar(as.character(site))>1) %>% filter(site %in% keepsite)
+```
+
+```{r}
 keywords.df <- keywords.df %>%
-  filter(nchar(as.character(site))>1)
-#  filter(site %in% keepsite)
-
-unique(keywords.df$site)
+  mutate(site = as.character(site)) %>%
+  mutate(site = ifelse(site=="bild.de","Bild.de",site),
+       site = ifelse(site=="focus.de","FOCUS ONLINE",site),
+       site = ifelse(site=="spiegel.de","SPIEGEL ONLINE",site),
+       site = ifelse(site=="zeit.de","ZEIT ONLINE",site),
+       site = ifelse(site=="tagesschau.de","Tagesschau.de",site),
+       site = ifelse(site=="deutschlandfunk.de","DLF",site),
+       site = ifelse(site=="zdf.de","ZDF.de",site),
+       site = ifelse(site=="welt.de","DIE WELT",site),
+       site = ifelse(site=="n-tv.de","n-tv.de",site))
 ```
@@
              Percent_of_traffic, fill=site)) +
-  geom_col(show.legend = FALSE) +
-  theme_bw(base_family = "Roboto", base_size = 4) +
+  geom_col(fill=col[1], show.legend = FALSE) +
+  theme_bw(base_family = "Roboto", base_size = 7) +
   coord_flip() +
@@
 filename = "../figs/search_traffic.png", device = "png",
-width = 7, height = 4,
+width = 9, height = 5,
         dpi = 600
@@
              Share_of_voice, fill=term)) +
-  geom_col(show.legend = F) +
+  geom_col(fill=col[3], show.legend = F) +
   coord_flip() +
@@
 
-## Audience Network
-```{r}
-focus <- read.csv("../data/audience_network/Audience_Overlap_1_15_2018_focus.csv", header=FALSE, comment.char="#")
-spiegel <- read.csv("../data/audience_network/Audience_Overlap_1_15_2018_spiegel.csv", header=FALSE, comment.char="#")
-bild <- read.csv("../data/audience_network/Audience_Overlap_1_15_2018_bildde.csv", header=FALSE, comment.char="#")
-zeit <- read.csv("../data/audience_network/Audience_Overlap_1_15_2018_zeitde.csv", header=FALSE, comment.char="#")
-tagesschau <- read.csv("../data/audience_network/Audience_Overlap_1_15_2018_tagesschau.csv", header=FALSE, comment.char="#")
-
-zdf <-  read.csv("../data/audience_network/Audience_Overlap_1_15_2018_zdf.csv.crdownload.csv", header=FALSE, comment.char="#")
-#stern <- read.csv("../data/audience_network/Audience_Overlap_1_15_2018_stern.csv", header=FALSE, comment.char="#")
-welt <- read.csv("../data/audience_network/Audience_Overlap_1_15_2018 _welt.csv", header=FALSE, comment.char="#")
-```
-
-```{r}
-focus <- focus[-1,1:2] 
-colnames(focus) <- c("site","focus.de")
-
-spiegel <- spiegel[-1,1:2] 
-colnames(spiegel) <- c("site","spiegel.de")
-
-bild <- bild[-1,1:2] 
-colnames(bild) <- c("site","bild.de")
-
-zeit <- zeit[-1,1:2] 
-colnames(zeit) <- c("site","zeit.de")
-
-tagesschau <- tagesschau[-1,1:2] 
-colnames(tagesschau) <- c("site","tagesschau.de")
-
-zdf <- zdf[-1,1:2] 
-colnames(zdf) <- c("site","zdf.de")
-
-welt <- welt[-1,1:2] 
-colnames(welt) <- c("site","welt.de")
-```
-
-```{r}
-# combine dataframes
-network_df <- left_join(focus[1:80,], spiegel[1:80,], by="site") %>%
-  left_join(., bild[1:80,], by = "site") %>%
-  left_join(., zeit[1:80,], by = "site") %>%
-  left_join(., tagesschau[1:80,], by = "site") %>%
-  left_join(., zdf[1:80,], by = "site") %>%
-  left_join(., welt[1:80,], by = "site")
-
-network_df <- na.omit(network_df)
-
-melted <- network_df %>%
-    gather(key="seed", value="score", focus.de:welt.de) %>%
-  mutate(score = as.integer(score),
-         site = as.factor(site),
-         seed = as.factor(seed))
-```
-
-```{r}
-p1 <- ggplot(melted, aes(seed, site, fill=score)) +
-  geom_tile() +
-  scale_fill_gradient(low="gray95",high=col[3]) +
-  scale_x_discrete(labels=c("bilde.de" = "Bild.de", 
-                            "focus.de" = "FOCUS ONLINE", 
-                            "spiegel.de" = "SPIEGEL ONLINE",
-                            "tagesschau.de" = "Tagesschau.de", 
-                            "welt.de" ="DIE WELT",
-                            "zdf.de" = "ZDF.de",
-                            "zeit.de" = "ZEIT ONLINE")) +
-  labs(x="", y="",  caption = "
-  Source: Alexa Internet, Inc. (www.alexa.com)
-      ") +
-  theme(
-      legend.text       =  element_text(size=6),
-      plot.background   = element_rect("#fafafa", "#fafafa"),
-      panel.background  = element_rect("#fafafa"),
-      axis.title.x      = element_blank(),
-      axis.text.x = element_text(size=8, angle = 45),
-      axis.text.y       = element_text(size = 8)
-    )
-
-ggsave(plot= p1,
-filename = "../figs/audience.png", device = "png",
-width = 5, height = 6,
-        dpi = 600
-)
-
-p1
-```
-
 # 2. Data 
@@
   ggplot(aes(site)) +
-  geom_bar(fill=col, alpha= .8) +
+  geom_bar(fill=col[1], alpha= .8) +
   labs(x="", y="Number of articles") +
   theme(
-      legend.position   = "none",
-      plot.background   = element_rect("#fafafa", "#fafafa"),
-      plot.title        = element_text(size = 18),
-      plot.subtitle     = element_text(size = 8),
-      plot.caption      = element_text(size = 7),
-      panel.background  = element_rect("#fafafa"),
-      axis.title.x      = element_blank(),
-      axis.text.y       = element_text(size = 8)
+      legend.position   = "none"
     )
@@
   btw %>%
-  group_by(date, site) %>%
+  group_by(date) %>%
   dplyr::summarise(obs = n()) %>%
-  ggplot(aes(date, obs, color = site)) +
-  geom_line() +
-  #geom_vline(aes(xintercept=as.Date("2017-09-24")),
-  #           linetype = 2, color="grey40") +
-  #geom_vline(aes(xintercept=as.Date("2017-11-20")),
-  #               linetype = 2, color="grey40") +
+  ggplot(aes(date, obs)) +
+  geom_line(color=col[3]) +
+  geom_vline(aes(xintercept=as.Date("2017-09-24")),
+             linetype = 2, color=col[2]) +
   scale_color_manual(values = col) +
-  labs(x="", y="Count",color="") +
+  labs(x="", y="number of articles",color="") +
   scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
   theme(
-      #legend.position   = "none",
-      plot.background   = element_rect("#fafafa", "#fafafa"),
-      plot.title        = element_text(size = 18),
-      plot.subtitle     = element_text(size = 8),
-      plot.caption      = element_text(size = 7),
-      #panel.grid        = element_blank(),
-      panel.background  = element_rect("#fafafa"),
+      legend.position   = "none",
       axis.title.x      = element_blank(),
-      axis.text.y       = element_text(size = 8)
+      axis.text       = element_text(size = 8)
     )
@@
 ```{r}
-sagelabs <- sageLabels(stmOut, 100)
+sagelabs <- sageLabels(stmOut, 25)
 ```
@@
 ```{r}
-sagelabs$cov.betas[[1]]$problabels[,1:10]
+sagelabs$cov.betas[[5]]$problabels[,1:10]
 ```
@@
 ```{r}
-topics <- matrix(c(1, "Great coalition", 2, "Merkel,election campaign", 3, "Jamaica coalition", 
-                   4, "Diesel scandal", 5, "Merkel chancellor", 6, "Seehover vs. Söder", 
-                   7, "Germany, EU, Jamaika", 8, "Merkel vs.Schulz", 9, "AfD election results", 
-                   10, "Steinmeier,Federal President", 11, "unclear (Schröder, Google)", 
+topics <- matrix(c(1, "Great coalition", 2, "Merkel vs. CSU", 3, "Jamaica coalition", 
+                   4, "Diesel scandal", 5, "Merkel as chancellor", 6, "Seehover vs. Söder", 
+                   7, "political trends after the election", 8, "Merkel vs.Schulz", 9, "AfD election results", 
+                   10, "Steinmeier,Federal President", 11, "IT themes (Data policy, Wifi, Telekom)", 
                    12, "Federal Election in social media", 13, "Climate policy", 14, "G20 Hamburg", 
-                   15, "error", 16, "Education, Pension policy", 17, "Reports on individuals",
-                   18, "Family reunion refugees", 19, "Polls federal election", 
+                   15, "error (text processing failure)", 16, "Education, Pension policy",
+                   17, "Reports on individuals", 18, "Family reunion refugees", 19, "Polls federal election", 
                    20, "AfD top candidates Weidel, Storch", 21, "M.Schwesig (SPD)",
-                   22, "elections in Niedersachsen", 23, "Böhmermann vs. Erdogan", 
-                   24, "political talkshows", 25, "German armed forces", 26, "W.Schäuble", 
-                   27, "C.Lindner FDP", 28, "Turkey, Russia", 29, "A.Merkel Youtube", 
+                   22, "elections in Niedersachsen", 23, "Court sentences (NSU, Böhmermann vs. Erdogan)", 
+                   24, "election capaigns & political talkshows", 25, "German armed forces", 26, "W.Schäuble", 
+                   27, "C.Lindner FDP", 28, "Turkey, Russia", 29, "railway problems (DBahn)", 
                    30, "H.Kohl obituary", 31, "AfD Gauland, Höcke", 32, "Asylum claims and deportation", 
@@
                    39, "Church", 40, "RAF"), ncol=2, byrow=T)
+
+topics.df <- as.data.frame(topics) %>%
+  transmute(topic_name = paste(V1, V2, sep=": "),
+         topic = 1:40) 
 ```
@@
   select(- therank)
-
-topics.df <- as.data.frame(topics) %>% transmute(topic = as.integer(V1),
-                                 topic_name = paste(topic, V2, sep=": "))
 
@@
     labs(x="", y="expected frequency") +
-    theme(axis.text = element_text(size=8),
+    theme(axis.text.x = element_text(size=8),
+          axis.text.y = element_text(size=11),
           axis.title = element_text(size=10))
@@
 
-#ggsave(plot = p1, filename = "../figs/topic_proportion.png", device = "png",width = 8, height = 12,
-#dpi = 600)
+ggsave(plot = p1, filename = "../figs/topic_proportion.png", device = "png",width = 8, height = 12,
+dpi = 600)
 ```
 
-## by newspaper
+### by newspaper
 ```{r}
@@
 
+### Difference in topic prevalence
+The estimateEffect() function explores how prevalence of topics varies across documents according to document covariates (metadata).
+First, users must specify the variable that they wish to use for calculating an effect.
+If there are multiple variables specified in estimateEffect(), then all other variables are held at their sample median.
+These parameters include the expected proportion of a document that belongs to a topic as a function of a covariate, or a first difference type estimate, where topic prevalence for a particular topic is contrasted for two groups.
+
+```{r}
+effect <- estimateEffect(c(1:40) ~site+s(month), stmOut, 
+                         metadata = out$meta, uncertainty = "None")
+#plot.estimateEffect(effect, "month", topics=c(33), method = "continuous", npoints=500)
+```
+
+```{r}
+summary(effect)
+```
+
+```{r}
+tables <- vector(mode="list", length = length(effect$topics))
+
+for (i in seq_along(effect$topics)) {
+  sims <- lapply(effect$parameters[[i]], function(x) stm:::rmvnorm(500, x$est, x$vcov))
+  sims <- do.call(rbind, sims)
+  est <- colMeans(sims)
+  se <- sqrt(apply(sims,2, stats::var))
+  tval <- est/se
+  rdf <- nrow(effect$data) - length(est)
+  p <- 2*stats::pt(abs(tval), rdf, lower.tail = FALSE)
+  topic <- i
+
+  coefficients <- cbind(topic, est, se, tval, p)
+  rownames(coefficients) <- attr(effect$parameters[[1]][[1]]$est, "names") 
+  colnames(coefficients) <- c("topic", "Estimate", "Std. Error", "t value", "p")
+  tables[[i]] <- coefficients
+}
+
+out <- list(call=effect$call, topics=effect$topics, tables=tables)
+```
+
+```{r}
+coeff <- as.data.frame(do.call(rbind,out$tables))
+
+coeff <- coeff %>% 
+  mutate(parameter = rownames(coeff),
+         parameter = gsub("site", "", parameter),
+         parameter = ifelse(parameter == "s(month)1", "1_July", parameter),
+         parameter = ifelse(parameter == "s(month)2", "2_August", parameter),
+         parameter = ifelse(parameter == "s(month)3", "3_September", parameter),
+         parameter = ifelse(parameter == "s(month)4", "4_October", parameter),
+         parameter = ifelse(parameter == "s(month)5", "5_November", parameter),
+         parameter = ifelse(parameter == "s(month)6", "6_December", parameter),
+         signifcant = ifelse(p <= 0.5,"yes","no")) %>%
+  left_join(., topics.df, by="topic")
+```
+
+```{r}
+sites <- c("(Intercept)", "DIE WELT", "FOCUS ONLINE","SPIEGEL ONLINE", "Tagesschau.de","ZEIT ONLINE")
+
+p1 <- coeff %>% filter(parameter %in% sites) %>%
+  ggplot(aes(x = reorder(topic_name,topic, decreasing=F), y = Estimate, fill=factor(signifcant))) +
+  geom_col() +
+  scale_fill_manual(values = col[c(2,1)]) +
+  coord_flip() +
+  facet_wrap(~parameter, ncol = 6) +
+  labs(x="", fill="significant at\nthe 5% level") +
+  theme(axis.text.x = element_text(angle=90))
+
+p1
+
+ggsave(plot = p1, filename = "../figs/estimates_site.png", device = "png",width = 9, height = 5,
+dpi = 600)
+```
+
+```{r}
+p1 <- coeff %>% filter(!parameter %in% sites) %>%
+  ggplot(aes(x = reorder(topic_name,topic, decreasing=F), y = Estimate, 
+             fill=factor(signifcant))) +
+  geom_col() +
+  scale_fill_manual(values = col[c(2,1)]) +
+  coord_flip() +
+  facet_wrap(~parameter, ncol = 6) +
+  labs(x="", fill="significant at\nthe 5% level") +
+  theme(axis.text.x = element_text(angle=90))
+
+p1
+
+ggsave(plot = p1, filename = "../figs/estimates_month.png", device = "png",width = 9, height = 5,
+dpi = 600)
+```
+
 ## Topic Correlation
 ```{r}
-topicCorrelation <- function(ylevel) {
-  cormat <- cor(stmOut$theta[stmOut$settings$covariates$betaindex==ylevel,])
-  adjmat <- ifelse(cormat > .04,1,0)
+## Create Dataframe with correlations
 
-  corr <- list()
-  corr$posadj <- adjmat
-  corr$poscor <- cormat*adjmat
-  corr$cor <- ifelse(abs(cormat)>.04,cormat,0)
+cor <- cor(stmOut$theta[stmOut$settings$covariates$betaindex==1,])
+colnames(cor) <- 1:40
 
-  x <- corr$posadj[1:nrow(corr$posadj),1:nrow(corr$posadj)]
+df <- as.data.frame(cor) %>% 
+  mutate(topic = 1:40) %>%
+  melt(., id="topic", value.name="corr") %>%
+  mutate(site = stmOut$settings$covariates$yvarlevels[1])
 
-  g<- graph.adjacency(x, mode="undirected", weighted=TRUE, diag=FALSE)
+for (i in 2:6) {
+  cor <- cor(stmOut$theta[stmOut$settings$covariates$betaindex==i,])
+  colnames(cor) <- 1:40
 
-  E(g)$size <- 1
-  E(g)$lty <- 2
-  E(g)$color <- "black"
-  V(g)$label <- topics[,2]
-  layout <- layout_nicely
+  df1 <- as.data.frame(cor) %>% 
+    mutate(topic = 1:40) %>%
+    melt(., id="topic", value.name="corr") %>%
+    mutate(site = stmOut$settings$covariates$yvarlevels[i])
 
-  plot.igraph(g, layout=layout_nicely, vertex.color="white", label.font = "Roboto",
-     vertex.frame.color="grey", vertex.size=1, vertex.label.cex=.6, edge.color="red",
-     edge.width=1, main=paste("Topic correlation", stmOut$settings$covariates$yvarlevels[ylevel]))
+  df <- rbind(df,df1)
 }
@@
 ```{r}
-topicCorrelation(5)
+df <- df %>% 
+  left_join(.,topics.df, by = "topic") %>%
+  mutate(topic1 = topic,
+         topic_name1 = topic_name,
+         topic = as.numeric(variable)) %>%
+  select(-topic_name) %>%
+  left_join(., topics.df, by="topic")
+```
+
+```{r}
+p1 <- df %>%
+  filter(corr>0.1 & corr < 1) %>%
+  ggplot(aes(reorder(topic_name1,topic1), topic_name, 
+             fill=corr)) +
+  geom_tile() +
+  facet_wrap(~site, ncol = 6) +
+  scale_fill_distiller(palette = "Spectral", trans = "reverse") + 
+  labs(x="", y="", fill="correlation") +
+  theme_bw(base_family = "Roboto", base_size = 10) +
+  theme(axis.text.x = element_text(angle=90, size = 6),
+        #plot.background = element_rect(fill = 'transparent', colour = 'transparent'),
+        strip.background = element_rect(fill = 'transparent', colour = 'transparent'),
+        axis.ticks = element_line(colour = 'transparent'))
+
+p1
+
+ggsave(plot = p1, filename = "../figs/topic_correlation.png", device = "png",width = 9, height = 5,
+dpi = 600)
 ```
@@
 ### Overlapping Correlation
-```{r}
-topicCorrCompare <- function(ylevel1, ylevel2) {
-
-  # find all edges between topics where they exhibit a positive correlation above 0.1
-  cormat <- cor(stmOut$theta[stmOut$settings$covariates$betaindex==ylevel1,])
-  adjmat <- ifelse(cormat > .1,1,0)
-
-  corr.1 <- list()
-  corr.1$posadj <- adjmat
-  corr.1$poscor <- cormat*adjmat
-  corr.1$cor <- ifelse(abs(cormat)>.04,cormat,0)
-
-  # Ylevel 2
-  cormat <- cor(stmOut$theta[stmOut$settings$covariates$betaindex==ylevel2,])
-  adjmat <- ifelse(cormat > .1,1,0)
-
-  corr.2 <- list()
-  corr.2$posadj <- adjmat
-  corr.2$poscor <- cormat*adjmat
-  corr.2$cor <- ifelse(abs(cormat)>.04,cormat,0)
-
-  # Prepare plot
-  g.1 <- graph.adjacency(corr.1$cor, mode="undirected", weighted = T, diag = F) 
-  g.2 <- graph.adjacency(corr.2$cor, mode = "undirected", weighted = T, diag = F)
-
-  inter.graph <- graph.intersection(g.1, g.2)
-  added.subgraph <- graph.difference(g.1, inter.graph)
-  subs.subgraph <- graph.difference(g.2, inter.graph)
-
-  # Styling
-  E(added.subgraph)$color <- col[1]
-  E(subs.subgraph)$color <- col[2]
-  E(inter.graph)$color <- col[3]
-
-  # Matrix
-  g.whole<-graph.union(inter.graph,added.subgraph,subs.subgraph)
-  V(g.whole)$color<-col[3]
-  E(g.whole)$color <- col[2]
-  E(g.whole)[1:length(E(inter.graph))]$color<-col[3]
-  E(g.whole)[(length(E(inter.graph))+1):(length(E(inter.graph))+length(E(added.subgraph)))]$color<-col[1]
-
-  inter.list <- get.edgelist(inter.graph)
-  list.1 <- get.edgelist(added.subgraph)
-  list.2 <- get.edgelist(subs.subgraph)
-
-  # Set Frame
-  cormat <- matrix(0, nrow=100, ncol=100)
-  for(i in 1:nrow(inter.list)){
-    cormat[inter.list[i,1], inter.list[i,2]] <- .5
-    cormat[inter.list[i,2], inter.list[i,1]] <- .5
-    }
-
-  for(i in 1:nrow(list.1)){
-    cormat[list.1[i,1], list.1[i,2]] <- -1
-    cormat[list.1[i,2], list.1[i,1]] <- -1
-    }
-
-  for(i in 1:nrow(list.2)){
-    cormat[list.2[i,1], list.2[i,2]] <- 1
-    cormat[list.2[i,2], list.2[i,1]] <- 1
-    }
-
-  cormat <- cormat[as.numeric(topics[,1]),as.numeric(topics[,1])]
-  topics2 <- sapply(topics[,2], function (x) str_replace(x, "\n", ""))
-  rownames(cormat) <- colnames(cormat) <- topics.df$topic_name
-
-  only.1 <- apply(cormat,1, function (x) sum(x==1))
-  only.2 <- apply(cormat,1, function (x) sum(x==-1))
-  both <- apply(cormat,1, function (x) sum(x==.5))
-  all <- apply(cormat,1, function (x) sum(x!=0))
-  disagree <- only.1/all + only.2/all
-
-  disagreed <- order(disagree, decreasing=F)
-  list <- topics[disagreed,2]
-  disagreemat <- cormat[disagreed, disagreed]
-  rownames(disagreemat) <- topics2[disagreed]
-  colnames(disagreemat) <- topics2[disagreed]
-
-  corrplot(disagreemat, cl.pos="n", tl.col="black", tl.cex=.5)
-  legend(40,20, c(paste(stmOut$settings$covariates$yvarlevels[ylevel1]), paste(stmOut$settings$covariates$yvarlevels[ylevel2]), "Both", "None"),
-         col=c("darkred", "darkblue", "lightblue", "white"), 
-         pch=c(15,15,16,16), cex = 0.7, box.lty = 0)
-}
-```
-
 Pairs of topics where an edge exists in both Newspaper, we denote with a light blue dot.
@@
 ```{r}
-topicCorrCompare(3,5)
+png("../figs/overlapping_correlation.png")
+topicCorrCompare(1,5)
+dev.off()
 ```
 
-## How they talk about GroKo differently
+### Distance metric
+
+Compute the Jensen Shannon divergence of the word-topic probability.
+The K-by-V (number of words in the vocabulary) matrix logbeta contains the natural log of the probability of seeing each word conditional on the topic.
+
+```{r}
+stmOut$settings$covariates$yvarlevels[1]
+```
+
+```{r}
+comb.matrix <- matrix(0, nrow= 36, ncol = 2)
+
+y <- 1
+for (i in 1:6) {
+  for (j in 1:6) {
+    comb.matrix[y,1] <- stmOut$settings$covariates$yvarlevels[i]
+    comb.matrix[y,2] <- stmOut$settings$covariates$yvarlevels[j]
+    y <- y+1
+  }
+}
+```
+
+```{r}
+# Create empty matrix
+kld.matrix <- matrix(0, nrow = nrow(comb.matrix), ncol = 40)
+names(kld.matrix) <- 1:40
+# Populate matrix with JSD Values
+
+x <- 1
+
+for (i in 1:6) {
+
+      print(paste("ylevel = ", i))
+    base <- exp(stmOut$beta$logbeta[[i]])
+    compare1 <- exp(stmOut$beta$logbeta[[1]])
+    compare2 <- exp(stmOut$beta$logbeta[[2]])
+    compare3 <- exp(stmOut$beta$logbeta[[3]])
+    compare4 <- exp(stmOut$beta$logbeta[[4]])
+    compare5 <- exp(stmOut$beta$logbeta[[5]])
+    compare6 <- exp(stmOut$beta$logbeta[[6]])
+
+  for (j in 1:40) {
+
+    print(paste("topic = ", j))
+    kld.matrix[x,j] <- JSD(base[j,],compare1[j,])
+    kld.matrix[x+1,j] <- JSD(base[j,],compare2[j,])
+    kld.matrix[x+2,j] <- JSD(base[j,],compare3[j,])
+    kld.matrix[x+3,j] <- JSD(base[j,],compare4[j,])
+    kld.matrix[x+4,j] <- JSD(base[j,],compare5[j,])
+    kld.matrix[x+5,j] <- JSD(base[j,],compare6[j,])
+
+  }
+    x <- x+6
+}
+
+```
+
+```{r}
+## Create DF
+kld.df <- as.data.frame(kld.matrix) 
+colnames(kld.df) <- 1:40
+
+kld.df <- kld.df %>% mutate(News1 = comb.matrix[,1],
+         News2 = comb.matrix[,2]) %>%
+  melt(.,id=c("News1","News2"), value.name="JSD",
+       variable.name = "topic") %>%
+  mutate(topic = as.integer(topic)) %>%
+  left_join(., topics.df, by="topic")
+```
+
+```{r}
+cols <- rev(brewer.pal(11, 'RdYlBu'))
+
+p1 <- kld.df %>%
+  filter(!topic %in% c("11","15")) %>%
+  filter(News1!=News2) %>%
+  ggplot(aes(News2, factor(topic_name), fill = JSD)) + 
+  geom_tile() + 
+  facet_grid(~News1) + 
+  scale_fill_gradientn(colours = cols) +
+  labs(x="", y="") +
+  theme_bw(base_family = "Roboto", base_size = 11) +
+  theme(axis.text.x = element_text(angle=90),
+        plot.background = element_rect(fill = 'transparent', colour = 'transparent'),
+        strip.background = element_rect(fill = 'transparent', colour = 'transparent'),
+        axis.ticks = element_line(colour = 'transparent'))
+
+p1
+
+ggsave(plot = p1, filename = "../figs/jsd.png", device = "png",width = 10, height = 8,
+dpi = 600)
+```

### 2018-01-25 paper/doc/structure.tex
jsd

--- 2018-01-19 paper/doc/doc.tex
@@
 Since 2000, public broadcasting has expanded its range of services, particularly in the digital media sector.
-If the right to use digital media were to be withdrawn from the public media outlets, they would not only be deprived of the possibility of improved information provision.
+If the right to produce digital media content were to be withdrawn from the public media outlets, they would not only be deprived of the possibility of improved information provision.
 They also threatened to lose their competitiveness with commercial media.
@@
 
-The fundamental question in this debate is whether the offer of public news on the internet is justified.
+One fundamental question in this debate is whether the offer of public news on the internet is justified.
 They should only occur where there are clear deficits in private sector supply.
@@
 On the basis of these justifications, this paper examines whether public media offer different content than private providers.
-In other words, whether socially desired content that meets the (social) needs of society and is therefore politically desirable is not provided by the market of private news, but by public providers.
 In order to examine this, the online news content of public media is compared with the supply of private news providers.
 
-We use a data set of German online news articles about domestic politics to examine the differences in news content between public and private news provides.
-Your dataset contains articles dated from 01.06.2017 to 31.12.2017\footnote{German federal elections took place on 24th of September 2017.} from seven German content providers to analyze news reports about german elections, where we allow prevalence of topics to evolve over time (before and after the elections) and vary across newswire services.
-We then estimate the effect of news wire source on both topical prevalence (topic distribution) and topical content (word-topic distribution).
+We use a data set of German online news articles about domestic politics dated from 01.06.2017 to 31.12.2017\footnote{German federal elections took place on 24th of September 2017.} from six German content providers.
 
-Mapping raw text to one or more topics, without having prior knowledge on what those topics are, translates to an unsupervised classification problem on natural language.
-Topic models generate low-dimensional representations of data and can uncover interesting latent structure in large text datasets.
-They are popular tools for automatically identifying prominent themes in text.
-Within topic models the Latent Dirichlet Allocation (LDA) is a widely used technique, where each document (article) is viewed as a mixture of topics (represented by the document-topic distribution) and each topic is a mixture of unique terms, represented by the topic-term distribution \citep{blei_latent_2003}.
-\citet{roberts_model_2016} extents the base idea of LDA by developing a structural topic model (STM) that allows to incorporate external variables that effect both topical content and topical prevalence.
-We use this approach to analyze online news about the german domestic politics, where we allow prevalence of topics to vary across newswire services.
-We then estimate the effect of topical prevalence (the posterior document-topic distribution) on the ownership (public or private).
+The research strategy is as follows:
 
-The paper proceeds as follows: The next section (\ref{ch_onlinenews}) briefly explains the market for online news in Germany.
-We will examine the largest players on the market and use keyword analytics to investigate which providers are similar.
-Section \ref{ch_model} explains the generative process of the mixed membership model and the results of this process are presented in chapter \ref{ch_results}.
-Chapter \ref{ch_data} contains a description of the text data and how it was pre-processed in order to use it as input variable.
-Chapter \ref{ch_regression} describes how we regress the estimated probabilities of topic prevalence of a document on its metadata.
+\begin{enumerate}
+	\item \textbf{Discovering Topics} Discover latent topics in the corpus using structural topic modeling (STM)\citep{roberts_model_2016} An extension of latent dirichlet allocation (LDA) \citep{blei_latent_2003}).
+The STM approach models (a) topics as multinomial distributions of words and (b) documents as multinomial distributions of topics, allowing to incorporate external variables that effect both (a) topical content and (b) topical prevalence.
+To explore the results, we label each topic by looking at most frequent words and most representative articles across all news providers.
+(Section \ref{ch_model})
+
+	\item \textbf{Measuring Similarity of news content} Different approaches to examine the similarities / differences of content between the news provider:
+	\begin{enumerate}
+		\item \textbf{Differences in topic prevalence:} As we allow prevalence of topics to evolve over time (by month) and vary across newswire services, we can use the posterior topic-probability of document $d$, to estimate the conditional expectation of topic prevalence $\theta_d$ for given document characteristics (lm on compositional data) \citep{roberts_model_2016}.
+		\begin{align*}
+			\theta_d=\alpha+\beta_1x_{site}+\beta_2x_{month}+\epsilon
+		\end{align*}
+
+		\item \textbf{Topic correlation} How are topics linked and framed differently across news wires?
+Find all edges between topics where they exhibit a positive correlation above 0.1 \citep{roberts_model_2016}.
+
+		\item \textbf{Differences in word-topic distributions} From the STM we get a $K$x$V$ matrix (where $K=$ number of topics and $V=$ vocabulary) of the whole corpus that contains the probability of seeing each word of the vocabulary $V$ within topic $k$ conditional on the news provider.
+That is, for each news provider we get a respective $K$x$V$ matrix.
+We then use each row (corresponding to each topic) to calculate the similarity of the word-topic distribution between the news provider using the square root of the Jensen-Shannon (JS) Divergence.
+
+		Previous topic modeling research try to measure the similarity between topics, comparing the word-topic-distribution between the topics (most of the research uses LDA without metadata, so the word-topic-distribution is the same within the whole corpus).
+cosine similarity \citep{he_detecting_2009}, \citep{ramage_labeled_2009}, Kullback-Leibler (KL) \citep{newman_distributed_2009}, \citep{wang_mining_2009} and the average Log Odds Ratio \citep{chaney_visualizing_2012} are frequently used metrics to compare word probability distributions.
+\citet{kim_topic_2011} compare six popular similarity metrics in terms of log likelihood of data, concluding that Jensen-Shannon Divergence (the symmetric variation of KL divergence) is best in terms of performance and generality.
+
+		\end{enumerate}
+
+\end{enumerate}
 
@@
 
-\subsection{Competitors}
+\subsection{Competitor analysis}
 
 Figure \ref{fig_reach} shows the largest providers of online news in terms of daily pageviews.\footnote{The figure shows the estimated percentage of daily pageviews on the internet that occurred on a specific website.} It is striking that SPIEGEL ONLINE has the greatest reach over the entire course of time followed by Bild.de.
-Looking at the percentage change of pageviews on the election day, increase is highest for Tagesschau.de followed by Tagesspiegel.de, whereas Huffingtonpost.de and Bild.de have the lowest increase (see figure \ref{fig_change}).
 
@@
 	\begin{center}
-		\begin{subfigure}[normla]{0.49\textwidth}
+		\begin{subfigure}[normla]{0.8\textwidth}
 			\includegraphics[width=\textwidth]{../figs/reach.png}
@@
 			\label{fig_reach}
-		\end{subfigure}
-		\begin{subfigure}[normla]{0.49\textwidth}
-			\includegraphics[width=\textwidth]{../figs/perc_change.png}
-			\caption{Percentage change of pageviews}
-			\label{fig_change}
 		\end{subfigure}
@@
 	\begin{center}
-		\includegraphics[width=0.8\textwidth]{../figs/traffic_source.png}
+		\includegraphics[width=0.6\textwidth]{../figs/traffic_source.png}
 		\label{fig_traffic}
@@
 	\begin{center}
-		\includegraphics[width=0.95\textwidth]{../figs/search_traffic.png}
+		\includegraphics[width=0.8\textwidth]{../figs/search_traffic.png}
 		\label{fig_searchtraffic}
@@
 Assuming that each search query is in itself a market where providers compete for traffic, the share of search queries for a keyword that has led visitors to a news page is the market share of that provider.
-In this context, figures \ref{fig_keywords1} and \ref{fig_keywords2} show the market share of providers for different keywords.\footnote{The figures show the percentage of searches for a keyword that sent traffic to a website in major search engines over the time span Jun-Dec 2017.} Nearly 15\% of all search queries for the keyword "Bundestagswahl 2017" (federal elections 2017) were forwarded to welt.de.
-Focus.de, faz.net and spiegel.de obtained a market share of 7\% - 8\%.
+In this context, figures \ref{fig_keywords1} and \ref{fig_keywords2} show the market share of providers for different keywords.\footnote{The figures show the percentage of searches for a keyword that sent traffic to a website in major search engines over the time span Jun-Dec 2017.} Nearly 15\% of all search queries for the keyword "Bundestagswahl 2017" (federal elections 2017) were forwarded to DIE WELT.
+FOCUS ONLINE, faz.net and SPIEGEL ONLINE obtained a market share of 7\% - 8\%.
 For the keyword "Groko" (grand coalition between CDU/CSU and SPD), SPIEGEL ONLINE was able to gain the largest market share (17\%) in the past six months, followed by DIE WELT (\%10), FOCUS ONLINE (8\%) and Bild.de (7.5\%).
 Figure \ref{fig_keywords2} shows the market share of news pages for the keyword search for a specific party.
-Contrary to figure \ref{fig_keywords1} , the x-axes in figure \ref{fig_keywords2} are scaled equally to show not only the market share of news sites depending on one party, but also for which party this provider has the largest market share.
+
+Contrary to figure \ref{fig_keywords1} , the x-axes in figure \ref{fig_keywords2} are scaled equally to show not only the market share of news sites for a specific party-keyword, but also for which party this provider has the largest market share.
+For example, we can see that the market share of sueddeutsche.de is largest for the keyword "Die Grünen".
+However, the biggest market share among the listed news providers for this keyword has Zeit.de.
+The largest market share for the keyword "AfD" can be found at DIE WELT, followed by SPIEGEL ONLINE.
+The proportion of public news providers is comparatively low for all keywords.
 
 \begin{figure}[H]
-	\caption{Market share for different keywords}
 	\begin{center}
-		\begin{subfigure}[normla]{0.7\textwidth}
-			\includegraphics[width=\textwidth]{../figs/keywords1.png}
-			\caption{policy topics / general}
+			\includegraphics[width=.8\textwidth]{../figs/keywords1.png}
+			\caption{Keyword market share for policy topics / general}
 			\label{fig_keywords1}
-		\end{subfigure}
-		\begin{subfigure}[normla]{0.7\textwidth}
-			\includegraphics[width=\textwidth]{../figs/keywords2.png}
-			\caption{political parties}
+	\end{center}
+\end{figure}
+
+\begin{figure}[H]
+	\begin{center}
+			\includegraphics[width=.8\textwidth]{../figs/keywords2.png}
+			\caption{Keyword market share for party-keywords}
 			\label{fig_keywords2}
-		\end{subfigure}
 	\end{center}
@@
 
-We conduct our estimation on a sample of 7061 online news articles from five news provider about domestic politics\footnote{Bild.de, FOCUS ONLINE, SPIEGEL ONLINE, ZEIT ONLINE, Tagesschau.de} dated from 01.06.2017 to 31.12.2017.\footnote{German federal elections took place on 24th of September 2017.} We first extract all online articles using the the Webhose.io API.\footnote{For more information see https://docs.webhose.io/v1.0/docs/getting-started.
+We conduct our estimation on a sample of 9393 online news articles from six news provider about domestic politics\footnote{Bild.de, DIE WELT, FOCUS ONLINE, SPIEGEL ONLINE, ZEIT ONLINE, Tagesschau.de}, of which only Tagesschau.de belongs to the group of public provider.
+The reason for this is that the content of Tagesschau.de is most similar to that of the private providers.
+ZDF.de offers predominantly video content and DLF website mainly offers audio content in the form of interviews.
+The articles are dated from 01.06.2017 to 31.12.2017.\footnote{German federal elections took place on 24th of September 2017.} We first extract all online articles using the the Webhose.io API.\footnote{For more information see https://docs.webhose.io/v1.0/docs/getting-started.
 The scraping code was written in Python and can be made available on request.} We then filtered all articles from the section "domestic policy" by checking the URL structure.
 
-Figure \ref{fig_distr1}\footnote{The vertical line indicate the date of the federal elections (24.09.2017).} shows the distribution of the number of articles from the respective news sources by date.
-There is a high peak around the federal elections on September, 24th.
+Figure \ref{fig_distr1} shows the distribution of the number of articles from the respective news sources by date. There is a high peak around the federal elections on September, 24th.
 
@@
 	\begin{center}
-		\begin{subfigure}[normla]{0.8\textwidth}
+		\begin{subfigure}[normla]{0.49\textwidth}
 			\includegraphics[width=\textwidth]{../figs/timeline.png}
-			\caption{...by date \& news source}
+			\caption{...by date}
 			\label{fig_distr1}
 		\end{subfigure}
-		\begin{subfigure}[normla]{0.8\textwidth}
+		\begin{subfigure}[normla]{0.49\textwidth}
 			\includegraphics[width=\textwidth]{../figs/bar.png}
@@
 
-This process revealed that a model with 25 topics best reflects the structure in the corpus.
-Furthermore, we use the source of each article (the media house) and the month it was published as covariates in the topic prevalence portion of the model.
+This process revealed that a model with 40 topics best reflects the structure in the corpus.
+Furthermore, we use the source of each article (the media house) and the month it was published as covariates in the topic prevalence.
 In other words, the probability distribution of topics depends on the editorial strategy of a media house as well as on the month the article was published.
+We also include news agency as a covariate affecting topical content to estimate how topics are discussed in different ways by different news agencies.
 To address problems due to non-convexity, we rely on the spectral initialization approach advocated by \citet{roberts_navigating_2016}.
@@
 % ----------------------
-\subsection{Interpretation}
+\section{Empirical Evaluation}
 
@@
 
-A way to summerize the topics in an interpretable way is to use the most frequent terms within a topic \citep{chang_reading_2009}, but the exclusivity of words to topics is equally important for communicating content.
-\citep{bischof_summarizing_2012} consider the harmonic mean of the words's rank in terms of exclusivity and frequency as a summary for a word's contribution to a topic.
-It is important to take both of these properties into account, as frequent words are often simply functional words that are necessary to discuss a topic.
-While completely exclusive words can be so rare that their information content is too low.
-\citep{roberts_stm:_2016} refer to this as the FREX (FRequency and EXclusivity) metric.
-
-\begin{align}
-	FREX_{k,\nu} = (\frac{\omega}{ECDF(\beta_{k,\nu}/\sum^K_{j=1}\beta_{j,\nu}}+\frac{1-\omega}{ECDF(\beta_{k,\nu}})^{-1},
-\end{align}
-
-with $\boldsymbol{B}$ denoted as the $KxV$ matrix of topic-conditional term probabilities.
-The first part of the equation calculates the frequency score  given by the empirical CDF of the word in it's topic distribution.
-Exclusivity is calculated by column-normalizing the beta matrix (thus representing the conditional probability of seeing the topic given the word).
-$\omega$ balances the influence of frequency and exclusivity and is set to $0.5$
-
-\section{Empirical Evaluation}
-
 Figure \ref{fig_topic_proportion} displays the topics ordered by their expected frequency across the corpus.
-To assign a label to each topic, we used a combination of most frequent words in that topic and words with the highest "score", computed as the log frequency of the word in the topic divided by the log frequency of the word in other topics \citep{roberts_stm:_2016}.
-The most common topic (3) is a general topic full of words that are frequently used in policy news, and therefore is not very interpretable.
-However, the remaining labels seem to classify a certain topic.
+To assign a label to each topic, we looked at the most frequent words in that topic and the most representative articles \citep{roberts_model_2016}.
 
@@
 
-%\begin{landscape}
-%\begin{figure}[H]
-%\centering
-%	\caption{Sample articles}
-%	\includegraphics[width=\linewidth,height=.9\textheight,keepaspectratio]{../figs/topic-classification-sample.png}	
-%	\label{fig_classification}
-%\end{figure}
-%\end{landscape}
-
 % ----------------------
@@
 % ----------------------
+\subsection{Differences in topic prevalence}
 Since we included news source as a covariate in estimating topical prevalence part within the model, we can estimate the frequency a topic is discussed within a news corpus \citep{roberts_model_2016}.
 We estimate the conditional expectation of topic prevalence for given document characteristics.
-More specifically, we estimate a linear model, where the documents are observations, the dependent variable is the posterior probability of a topic and the covariates are the metadata of documents.
-The stm-package provides a function that uses the method of composition to incorporates uncertainty in the dependent variable, drawing a set of topic proportions from the variational posterior repeated times and compute the coefficients as the average over all results.
+More specifically, we estimate a linear model, where the documents are observations, the dependent variable is the posterior probability of a topic and the covariates are the metadata of documents (see equation \ref{eq_1}).
+The stm-package provides a function that uses the method of composition to incorporates uncertainty in the dependent variable, drawing a set of topic proportions from the variational posterior repeated times and compute the coefficients as the average over all results \citep{roberts_stm:_2016}.
 
-Figure \ref{fig_estimateEffects_small} displays topics, where the most significant differences between the news sources are discernible.\footnote{An overview of all estimated topics can be found in the appendix \ref{fig_estimateEffects_full1} and \ref{fig_estimateEffects_full2}.} Topic 2, classifying articles about the diesel scandal, the glpyphosate decision and green policies, occur comparatively more often in tagesschau.de and bild.de, whereas tagesschau.de reports comparatively little about the riots during the G20 summit (topic 9).
-Topics 10 (about public (financial) statistics) and 13 (about the federal migration office (BAMF), asylum procedures and other issues related to refugees) also seems to be represented comparatively frequently in the tagesschau.de corpus, the latter topic is most often discussed in the DIE WELT corpus.
-However, topic 20 (the public debate between Die Grünen and FDP in the process of coalition negotiations) is represented significantly more often in the corpus of spiegel.de and bild.de.
-Topic 26, which classifies articles that deal with terrorism, mainly about the NSU trial and the main defendant Zschäpe as well es IS, is significantly more often present in the corpus of FOCUS ONLINE.
+\begin{align}\label{eq_1}
+	\theta_d=\alpha+\beta_1x_{site}+\beta_2x_{month}+\epsilon
+\end{align}
+
+Figures \ref{fig_estimateEffects1} and \ref{fig_estimateEffects2} display the regression results.
 
 \begin{figure}[H]
-	\caption{Mean prevalence of topics within each news source corpus}
+	\caption{Regression results 1}
 		\begin{center}
-		\begin{subfigure}[normla]{0.3\textwidth}
-			\includegraphics[width=\textwidth]{../figs/estimate_effect2.png}
-		\end{subfigure}
-		\begin{subfigure}[normla]{0.3\textwidth}
-			\includegraphics[width=\textwidth]{../figs/estimate_effect9.png}
-		\end{subfigure}
-				\begin{subfigure}[normla]{0.3\textwidth}
-			\includegraphics[width=\textwidth]{../figs/estimate_effect11.png}
-		\end{subfigure}
-				\begin{subfigure}[normla]{0.3\textwidth}
-			\includegraphics[width=\textwidth]{../figs/estimate_effect13.png}
-		\end{subfigure}
-				\begin{subfigure}[normla]{0.3\textwidth}
-			\includegraphics[width=\textwidth]{../figs/estimate_effect20.png}
-		\end{subfigure}
-				\begin{subfigure}[normla]{0.3\textwidth}
-			\includegraphics[width=\textwidth]{../figs/estimate_effect26.png}
-		\end{subfigure}
+			\includegraphics[width=0.9\textwidth,keepaspectratio]{../figs/estimates_site.png}
 		\end{center}
-	\label{fig_estimateEffects_small}
+	\label{fig_estimateEffects1}
 \end{figure}
 
-Another interesting aspect is how the news sources discusses the different topics, that is, describe the same event with different vocabulary.
+\begin{figure}[H]
+	\caption{Regression results 2}
+		\begin{center}
+			\includegraphics[width=0.9\textwidth,keepaspectratio]{../figs/estimates_month.png}
+		\end{center}
+	\label{fig_estimateEffects2}
+\end{figure}
 
-\section{Sentiment Analysis}
+\subsection{Topic correlations}
 
-commonly used lexical or “bag-ofwords” approach.
-In that approach, the researcher provides pre-defined dictionaries (lists) of words associated with a given emotion, such as negativity.
-The target text is then deconstructed into individual words (or tokens) and the frequencies of words contained in a given dictionary are then calculated.
-For example, Loughran and McDonald (2011) construct a dictionary of words that express negativity in financial contexts, which they then use to measure the negativity in company 10-K filings and relate that negativity to financial outcomes.
+Next, we examine how topics are correlated differently for different news wires, indicating how topics are connected and framed differently in each newswire.
+In Figure \ref{fig_topic_correlations}, we find all edges between topics where they exhibit a positive correlation above 0.1 \citep{roberts_model_2016}.
 
-The psychology literature demonstrates that any emotion can be parsimoniously defined by assigning it a score along two primary dimensions: valence (i.e., positive or negative) and arousal (i.e., activation and deactivation).
-For comparison purposes, we also examine three additional measures: “worried,” “satisfied,” and a lexical “negativity” measure.
+\begin{figure}[H]
+	\caption{Topic Correlation}
+		\begin{center}
+			\includegraphics[width=0.9\textwidth,keepaspectratio]{../figs/topic_correlation.png}
+		\end{center}
+	\label{fig_topic_correlations}
+\end{figure}
+
+\subsection{Differences in word-topic distributions}
+
+From the STM model we get a $KxV$ matrix (where $K=$number of topics and $V=$vocabulary) of the whole corpus that contains the probability of seeing each word of the vocabulary $V$ within topic $k$ conditional on the news provider.
+That is, for every news provider we get a $KxV$ matrix.
+We use each row (corresponding to each topic) to calculate the similarity of the word-topic distribution between the news provider using the square root of the Jensen-Shannon (JS) Divergence.
+
+A low JSD value indicates stronger similarities.
+
+\begin{figure}[H]
+	\begin{center}
+	\includegraphics[width=\textwidth,keepaspectratio]{../figs/jsd.png}
+	\caption{Jensen-Shannon (JS) Divergence of word-topic probability}
+	\label{fig_jsd}
+	\end{center}
+\end{figure}
 
@@
 
-\begin{figure}[H]
-	\caption{Mean prevalence of topics within each news source corpus 1}
-	\begin{center}
-		\begin{subfigure}[normla]{0.2\textwidth}
-			\includegraphics[width=\textwidth]{../figs/estimate_effect1.png}
-		\end{subfigure}
-		\begin{subfigure}[normla]{0.2\textwidth}
-			\includegraphics[width=\textwidth]{../figs/estimate_effect2.png}
-		\end{subfigure}
-				\begin{subfigure}[normla]{0.2\textwidth}
-			\includegraphics[width=\textwidth]{../figs/estimate_effect3.png}
-		\end{subfigure}
-				\begin{subfigure}[normla]{0.2\textwidth}
-			\includegraphics[width=\textwidth]{../figs/estimate_effect4.png}
-		\end{subfigure}
-				\begin{subfigure}[normla]{0.2\textwidth}
-			\includegraphics[width=\textwidth]{../figs/estimate_effect5.png}
-		\end{subfigure}
-				\begin{subfigure}[normla]{0.2\textwidth}
-			\includegraphics[width=\textwidth]{../figs/estimate_effect6.png}
-		\end{subfigure}
-		\begin{subfigure}[normla]{0.2\textwidth}
-			\includegraphics[width=\textwidth]{../figs/estimate_effect7.png}
-		\end{subfigure}
-		\begin{subfigure}[normla]{0.2\textwidth}
-			\includegraphics[width=\textwidth]{../figs/estimate_effect8.png}
-		\end{subfigure}
-		\begin{subfigure}[normla]{0.2\textwidth}
-			\includegraphics[width=\textwidth]{../figs/estimate_effect9.png}
-		\end{subfigure}
-		\begin{subfigure}[normla]{0.2\textwidth}
-			\includegraphics[width=\textwidth]{../figs/estimate_effect10.png}
-		\end{subfigure}
-		\begin{subfigure}[normla]{0.2\textwidth}
-			\includegraphics[width=\textwidth]{../figs/estimate_effect11.png}
-		\end{subfigure}
-		\begin{subfigure}[normla]{0.2\textwidth}
-			\includegraphics[width=\textwidth]{../figs/estimate_effect12.png}
-		\end{subfigure}
-		\begin{subfigure}[normla]{0.2\textwidth}
-			\includegraphics[width=\textwidth]{../figs/estimate_effect13.png}
-		\end{subfigure}
-		\begin{subfigure}[normla]{0.2\textwidth}
-			\includegraphics[width=\textwidth]{../figs/estimate_effect14.png}
-		\end{subfigure}
-	\end{center}
-	\label{fig_estimateEffects_full1}
-\end{figure}
-
-\begin{figure}[H]
-	\caption{Mean prevalence of topics within each news source corpus 2}
-	\begin{center}
-			\begin{subfigure}[normla]{0.2\textwidth}
-			\includegraphics[width=\textwidth]{../figs/estimate_effect15.png}
-		\end{subfigure}
-		\begin{subfigure}[normla]{0.2\textwidth}
-			\includegraphics[width=\textwidth]{../figs/estimate_effect16.png}
-		\end{subfigure}
-		\begin{subfigure}[normla]{0.2\textwidth}
-			\includegraphics[width=\textwidth]{../figs/estimate_effect17.png}
-		\end{subfigure}
-		\begin{subfigure}[normla]{0.2\textwidth}
-			\includegraphics[width=\textwidth]{../figs/estimate_effect18.png}
-		\end{subfigure}
-		\begin{subfigure}[normla]{0.2\textwidth}
-			\includegraphics[width=\textwidth]{../figs/estimate_effect19.png}
-		\end{subfigure}
-		\begin{subfigure}[normla]{0.2\textwidth}
-			\includegraphics[width=\textwidth]{../figs/estimate_effect20.png}
-		\end{subfigure}
-		\begin{subfigure}[normla]{0.2\textwidth}
-			\includegraphics[width=\textwidth]{../figs/estimate_effect21.png}
-		\end{subfigure}
-		\begin{subfigure}[normla]{0.2\textwidth}
-			\includegraphics[width=\textwidth]{../figs/estimate_effect22.png}
-		\end{subfigure}
-		\begin{subfigure}[normla]{0.2\textwidth}
-			\includegraphics[width=\textwidth]{../figs/estimate_effect23.png}
-		\end{subfigure}
-		\begin{subfigure}[normla]{0.2\textwidth}
-			\includegraphics[width=\textwidth]{../figs/estimate_effect24.png}
-		\end{subfigure}
-		\begin{subfigure}[normla]{0.2\textwidth}
-			\includegraphics[width=\textwidth]{../figs/estimate_effect25.png}
-		\end{subfigure}
-		\begin{subfigure}[normla]{0.2\textwidth}
-			\includegraphics[width=\textwidth]{../figs/estimate_effect26.png}
-		\end{subfigure}
-				\begin{subfigure}[normla]{0.2\textwidth}
-			\includegraphics[width=\textwidth]{../figs/estimate_effect26.png}
-		\end{subfigure}
-				\begin{subfigure}[normla]{0.2\textwidth}
-			\includegraphics[width=\textwidth]{../figs/estimate_effect28.png}
-		\end{subfigure}
-	\end{center}
-	\label{fig_estimateEffects_full2}
-\end{figure}
-
 \end{document}

### 2018-01-25 paper/R/func/functions.R

@@ -1,23 +1,3 @@
-AddAdjustBox <- function(sg.table){
-  after.location <- grep(" \\\\label\\{t_*", sg.table)
-  sg.table <- append(sg.table,
-                     "\\begin{adjustbox}{totalheight=\\textheight-2\\baselineskip}",
-                     after = after.location)
-  after.location <- grep("\\\\end\\{tabular\\}", sg.table)
-  sg.table <- append(sg.table, "\\end{adjustbox}", after = after.location)
-  return(sg.table)
-}
-
-AddResizeBox <- function(sg.table){
-  after.location <- grep(" \\\\label\\{t_*", sg.table)
-  sg.table <- append(sg.table,
-                     "\\resizebox{\\textwidth}{!}{",
-                     after = after.location)
-  after.location <- grep("\\\\end\\{tabular\\}", sg.table)
-  sg.table <- append(sg.table, "}", after = after.location)
-  return(sg.table)
-}
-
 Mode = function(x){ 
   ta = table(x)
   tam = max(ta)
@@ -29,4 +9,112 @@ Mode = function(x){
   else
     mod = names(ta)[ta == tam]
   return(mod)
+}
+
+##################################
+## Topic correlation within Ylevel
+##################################
+topicCorrelation <- function(ylevel) {
+  cormat <- cor(stmOut$theta[stmOut$settings$covariates$betaindex==ylevel,])
+  adjmat <- ifelse(cormat > .05,1,0)
+  
+  corr <- list()
+  corr$posadj <- adjmat
+  corr$poscor <- cormat*adjmat
+  corr$cor <- ifelse(abs(cormat)>.05,cormat,0)
+  
+  x <- corr$posadj[1:nrow(corr$posadj),1:nrow(corr$posadj)]
+  
+  g<- graph.adjacency(x, mode="undirected", weighted=TRUE, diag=FALSE)
+  
+  E(g)$size <- 1
+  E(g)$lty <- 2
+  E(g)$color <- "black"
+  V(g)$label <- topics[,2]
+  layout <- layout_nicely
+  
+  plot.igraph(g, layout=layout_nicely, vertex.color="white", label.font = "Roboto",
+              vertex.frame.color="grey", vertex.size=1, vertex.label.cex=.7, edge.color="red",
+              edge.width=1, main=paste("Topic correlation", stmOut$settings$covariates$yvarlevels[ylevel]))
+}
+
[…]

### 2018-01-30 paper/R/02_cleanAndCombine.Rmd
add ownership covariates

@@
 ## Preparation
+```{r}
+btw <- btw %>% 
+  mutate(ownership = ifelse(site == "Tagesschau.de", "public", "private"))
+```
+
 ### Build Corpus
@@
 ### without stemming
-# processed1 <- textProcessor(btw$text_cleaned, metadata = btw[,c("site","text_cleaned","month")],
+processed1 <- textProcessor(btw$text_cleaned1, metadata = btw[,c("ownership","text_cleaned1","month")],
+                           wordLengths = c(2,Inf),
+                           lowercase = F,
+                           removestopwords = F,
+                           removenumbers = F,
+                           removepunctuation = F,
+                           stem = F)
+out_ownership <- prepDocuments(processed1$documents, processed1$vocab, processed1$meta)
+out_ownership$meta$ownership <- as.factor(out_ownership$meta$ownership)
+###
+
+# processed <- textProcessor(btw$text_cleaned1, metadata = btw[,c("site","text_cleaned1","month")],
 #                            wordLengths = c(2,Inf),
@@
 #                            stem = F)
-# out1 <- prepDocuments(processed1$documents, processed1$vocab, processed1$meta)
-###
+# out <- prepDocuments(processed$documents, processed$vocab, processed$meta)
+# out$meta$site <- as.factor(out$meta$site)
 
-processed <- textProcessor(btw$text_cleaned1, metadata = btw[,c("site","text_cleaned1","month")],
-                           wordLengths = c(2,Inf),
-                           lowercase = F,
-                           removestopwords = F,
-                           removenumbers = F,
-                           removepunctuation = F,
-                           stem = F)
-out <- prepDocuments(processed$documents, processed$vocab, processed$meta)
-out$meta$site <- as.factor(out$meta$site)
-
-save(btw, out, file="../output/btw_combined.Rda")
+save(btw, out_ownership, file="../output/btw_comb_ownership.Rda")
 ```

### 2018-01-30 paper/R/paper.Rmd
add ownership covariates

@@
 library(corrplot)
+library(patchwork)
 library(ggpmisc)
@@
 
-p1
-
 ggsave(plot = p1, filename = "../figs/topic_proportion.png", device = "png",width = 8, height = 12,
@@
 ```{r}
-# Topic 3
+# Topic 1
 plotNewspaperHistogram(1)
+```
+
+### by ownership
+plots the expected proportion of topic use in public media minus the expected proportion of topic use in private media. Thus topics more associated with public media appear to the right of zero.
+
+```{r}
+freq <- tapply(stmOut$theta[,1], stmOut$settings$covariates$betaindex, mean)
+freq <- as.data.frame(freq) %>% 
+    mutate(site=stmOut$settings$covariates$yvarlevels,
+           topic = 1)
+
+for(i in 2:40) {
+  freq1 <- tapply(stmOut$theta[,i], stmOut$settings$covariates$betaindex, mean)
+  freq1 <- as.data.frame(freq1) %>% 
+    transmute(site=stmOut$settings$covariates$yvarlevels,
+           topic = i,
+           freq = freq1)
+
+  freq <- rbind(freq, freq1)
+}
+
+freq <- freq %>%
+  mutate(ownership = ifelse(site == "Tagesschau.de", "public", "private")) %>%
+  group_by(topic, ownership) %>%
+  summarise(freq_mean = mean(freq)) %>%
+  spread(ownership, freq_mean) %>%
+  mutate(freq_diff = public - private) %>%
+  mutate(value = ifelse(freq_diff>=0, 1,0)) %>%
+  left_join(., topics.df, by = "topic")
+```
+
+```{r}
+p1 <- ggplot(freq, aes(reorder(topic_name, freq_diff), freq_diff,
+                 fill = factor(value))) +
+  geom_col(show.legend = F) +
+  scale_fill_manual(values = col[c(1,3)]) +
+  coord_flip() +
+  theme(axis.text.x = element_text(size=8),
+          axis.text.y = element_text(size=11),
+          axis.title = element_text(size=10)) +
+    labs(x="", y="difference in expected frequency (public-private)")
+
+p1
+
+ggsave(plot = p1, filename = "../figs/topic_proportion_diff.png", device = "png",width = 8, height = 12,
+dpi = 600)
 ```
@@
 ```{r}
-summary(effect)
+save.image("stm_newsdata.RData")
 ```
@@
 ### Distance metric
+Compute different metrices and compare them.
 

### 2018-01-30 paper/doc/structure.tex
work on technical part

@@
 They use the estimated topic shares in linear fixed effects regression to forecast conflict out-of-sample.
+In order to demonstrate multi-modality of topic-models\footnote{That is, the solution of topic-models can be sensitive to the starting values as the function to be optimized has multiple modes.} can be mitigated, \citep{roberts_navigating_2016} use STM to examine the role of partisanship in topical coverage using a corpus of 13,246 posts that were written for 6 political blogs during the course of the 2008 U.S.
+presidential election.
+With the aim of revealing the effect of partisan membership on topic prevalence, each blog is assigned to be either liberal or conservative.
+To explore the differences between the two, they look at the expected proportion of topic and examine the posts most associated with a respective topic.
+This approach is similar to \citet{roberts_model_2016}.
+They also use different measures of distance between the topic-word distributions of the same topic within different models.
+In section \ref{ch_similarity}, we apply a similar approach to measure similarity between the same topic for different covariate levels.
+
+The outline of this chapter is as follows. In Section \ref{ch_generativeProcess} we describe the generative process of the Structural Topic Model (STM).
 
@@
 % --------------
-\subsection{Generative Process of STM}
+\subsection{Generative Process of STM}\label{ch_generativeProcess}
 
-The following description of the generative model of the STM is based on \citet{roberts_structural_2013} and \citet{roberts_stm:_2016}.
-The process of filling a word-position in a document begins with the generation of a document-specific topic-prevalence vector $d(\boldsymbol{\theta}_d)$ drawn from a logistic-normal distribution, where the parameters are a function of the covariate values:
+As mentioned above, the STM allows to incorporate observed document metadata which is able to affect either topical prevalence and topical content.
+The following description of the generative model - the process of filling a word-position in a document - of the STM is based on \citet{roberts_structural_2013} and \citet{roberts_stm:_2016}.
+For each document $d$ and a given number of topics $K$, a document-specific topic-prevalence vector $d(\boldsymbol{\theta}_d)$ is drawn from a logistic-normal distribution, where the parameters are a function of the covariate values:
 
@@
 $\boldsymbol{x}_d\gamma$ lists the values of all metadata covariates for document $d$, where $\gamma$ relates these covariate values to the topic-prevalence.
-The structure of $\boldsymbol{\Sigma}$ implies the possibility of correlations across documents in the topic-prevalence vector which help enhance interpretation and prevent overfitting.
+The structure of $\boldsymbol{\Sigma}$ implies the possibility of correlations across documents in the topic-prevalence vector.
 
-Given the document-specific distribution over topics, for each word in the document ($n \in \lbrace 1,...,N_d\rbrace$) is assigned to a specific topic $z_{dn}$ through the process
+According to $\theta$, a specific topic $z_{dn}$ is assigned for the $n^{th}$ word-position in the document through the process
 
 \begin{align*}
-	z_{dn}|\boldsymbol{\theta}_d \sim \textrm{Multinomial}(\boldsymbol{\theta}_d)
+	z_{dn}|\boldsymbol{\theta}_d \sim \textrm{Multinomial}(\boldsymbol{\theta}_d).
 \end{align*}
 
-where the $k^{th}$ element if $z_{dn}$ is unity and all other elements are zero when topic $k$ is chosen.
-
-Conditional in the topic chosen, a specific word, $w_{dn}$, is chosen from the overall corpus vocabulary $V$ to fill position $n$ in document $d$, using the following process:
+Conditional in the topic chosen, a specific word, $w_{dn}$, is chosen from the overall corpus vocabulary $V$, using the following process:
 
 \begin{align*}
-	w_{dn}|z_{dn},\beta_{dkv} \sim \textrm{Multinomial}(\beta_{dk1},...,\beta_{dkV}).
+	w_{dn}|z_{dn},\beta_{dkv} \sim \textrm{Multinomial}(\beta_{dk1},...,\beta_{dkV}),
 \end{align*}
 
-where the word probability $\beta_{dkv}$ is modeled as a function of the two parameters $m_v$ (indicating the importance of that word across all documents) and $\kappa_{kv}$ (indicating the importance of the word given the topic $k$).
-Transforming the sum of these coefficients into probabilities for use in a multinomial distribution via logistic transformation, one obtains:
+where the word probability $\beta_{dkv}$ is parameterized in terms of log-transformed rate deviations from the rates of a corpus-wide background distribution $m_v$.
+The log-transformed rate deviations can then be specified by a collection of parameters $\lbrace \boldsymbol{\kappa} \rbrace$, where $\kappa^{(t)}$ is a $K$-by-$V$ matrix containing the log-transformed rate deviations for each topic $k$ and term $v$, over the baseline log-transformed rate for term $v$.
+This matrix is the same for all $A$ levels of covariates.
+To put it differently, $\kappa^{(t)}$ indicates the importance of the term $v$ given topic $k$ regardless of the covariates.
+Similarly, $\kappa^{(c)}$ is a $A$-by-$V$ matrix, indicating the importance of the term $v$ given the covariate level $k$ regardless of the topic.
+Finally, $\kappa^{(i)}$ is a $A$-by-$K$-by-$V$ matrix, collecting the covariate-topic effects.
 
 \begin{align*}
-	\beta_{dkv}|z_{dn}\propto\textrm{exp}(\boldsymbol{m}_v+\kappa_{kv})
+	\beta_{dkv}|z_{dn}=\frac{\textrm{exp}(m_v+\kappa^{(t)}_{kv},\kappa^{(c)}_{y_dv}+\kappa^{(i)}_{y_dkv})}{\sum_v \textrm{exp}(m_v+\kappa^{(t)}_{kv},\kappa^{(c)}_{y_dv}+\kappa^{(i)}_{y_dkv})}
 \end{align*}
@@
 
-Topic models are usually imprecise as a number of assumptions have to be made that influence the performance of the classification task.
-Furthermore, multiple solutions exist for the optimization problem.
 The STM maximizes the posterior likelihood that the observed data were generated by the above data-generating process using an iterative approximation-based variational expectation-maximization algorithm\footnote{A technical description of this maximization process can be found in \citet{roberts_model_2016}} available in R's stm package \citep{roberts_stm:_2016}.
 Regularizing prior distributions are used for $\gamma$, $\kappa$ and $\Sigma$.
-Since an ex ante valuation of a model is hardly possible, we compute a variety of different models with different parameters and compare them with respect to the research problem \citep{gentzkow_text_2017}.
+Topic models are usually imprecise as the function we are optimizing has multiple modes, such that the model results can be sensitive to the starting values.
+Since an ex ante valuation of a model is hardly possible, we compute a variety of different models and compare their posterior probability.
+This enables us to check how substantively different results are for different model solution \citep{roberts_navigating_2016}.
+
+them with respect to the research problem \citep{gentzkow_text_2017}.
 To evaluate the accuracy of a model its perplexity can be computed.
@@
 
+\todo{Inspect model with ownership covariates}
+\todo{Inspect model with different topic-numbers}
+
 Inference of mixed-membership models, such as the one applied in this paper, has been a thread of research in applied statistics in the past few years \citep{blei_latent_2003} \citep{erosheva_mixed-membership_2004} \citep{braun_variational_2010}.
@@
 
+From the STM we get two matrices of parameters: $\beta$ is a row-normalized $K$-by-$V$ matrix of topic-word distributions, where the entry $\beta_{k,v}$ can be interpreted as the probability of observing the $v$-th word in topic $k$.
+Similarly $\theta$ is a row-normalized $D$-by-$K$ matrix of topic-word distributions, where the entry $\theta_{d,k}$ can be interpreted as the proportion of words in document $d$ which arise from topic $k$.
+In this section we will use the $\theta$ and $\beta$ matrices to analyze the model results.
+
 Figure \ref{fig_topic_proportion} displays the topics ordered by their expected frequency across the corpus.
@@
 
+Figure \ref{fig_topic_proportion_diff} plots the expected proportion of topic use in public media minus the expected proportion of topic use in private media.
+Thus topics more associated with public media appear to the right of zero.
+
 \begin{figure}[H]
 	\begin{center}
-	\includegraphics[width=0.8\textwidth,keepaspectratio]{../figs/topic_proportion.png}
-	\caption{Expected Topic Proportion}
+	\caption{Expected topic proportion}
+	\begin{subfigure}[normla]{0.4\textwidth}
+		\includegraphics[width=\textwidth,keepaspectratio]{../figs/topic_proportion.png}
+		\caption{Entire corpus}
 		\label{fig_topic_proportion}
+	\end{subfigure}
+
+	\begin{subfigure}[normla]{0.4\textwidth}
+		\includegraphics[width=\textwidth,keepaspectratio]{../figs/topic_proportion_diff.png}
+		\caption{Differences}
+		\label{fig_topic_proportion_diff}
+	\end{subfigure}
 \end{center}
@@
 
-\subsection{Differences in word-topic distributions}
+\subsection{Differences in word-topic distributions}\label{ch_similarity}
+
+\todo{Compare different metrices}
+L1 distance, cosine similarity metric (essentially the dot product rescaled by the L2 norm of the vectors).
 

### 2018-02-01 paper/R/03_marektDescription.Rmd
new

--- 2018-01-25 paper/R/paper.Rmd
@@
 library(corrplot)
+library(patchwork)
 library(ggpmisc)
+library(ggraph)
 library(ggiraph)
+library(tidygraph)
 library(RColorBrewer) 
@@
 ```
-
-# 2. Data 
-```{r caching, echo = FALSE}
-load("../output/btw_combined.Rda")
-```
-
-## Distribution of articles
-```{r message=FALSE, warning=FALSE}
-ggsave({
-  btw %>%
-  ggplot(aes(site)) +
-  geom_bar(fill=col[1], alpha= .8) +
-  labs(x="", y="Number of articles") +
-  theme(
-      legend.position   = "none"
-    )
-
-},
-filename = "../figs/bar.png", device = "png", 
-width = 6, height = 4,
-        dpi = 600)
-```
-
-```{r message=FALSE, warning=FALSE}
-ggsave({
-  btw %>%
-  group_by(date) %>%
-  dplyr::summarise(obs = n()) %>%
-  ggplot(aes(date, obs)) +
-  geom_line(color=col[3]) +
-  geom_vline(aes(xintercept=as.Date("2017-09-24")),
-             linetype = 2, color=col[2]) +
-  scale_color_manual(values = col) +
-  labs(x="", y="number of articles",color="") +
-  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
-  theme(
-      legend.position   = "none",
-      axis.title.x      = element_blank(),
-      axis.text       = element_text(size = 8)
-    )
-},
-filename = "../figs/timeline.png", device = "png",width = 7, height = 4,
-dpi = 600
-)
-
-```
-
-# 3. Model Results
-```{r caching, echo = FALSE}
-load("../output/models/STM_stemmed2 40 .Rda")
-```
-
-## Label topics
-```{r}
-sagelabs <- sageLabels(stmOut, 25)
-```
-
-```{r}
-stmOut$settings$covariates$yvarlevels
-```
-
-### Label topics based on Bild.de
-
-After reviewing a sample of articles assigned to the respective topic, we assign a shorter name to the topics based on the most common words in order to improve readability and traceability.
-```{r}
-sagelabs$cov.betas[[5]]$problabels[,1:10]
-```
-
-```{r}
-topics <- matrix(c(1, "Great coalition", 2, "Merkel vs. CSU", 3, "Jamaica coalition", 
-                   4, "Diesel scandal", 5, "Merkel as chancellor", 6, "Seehover vs. Söder", 
-                   7, "political trends after the election", 8, "Merkel vs.Schulz", 9, "AfD election results", 
-                   10, "Steinmeier,Federal President", 11, "IT themes (Data policy, Wifi, Telekom)", 
-                   12, "Federal Election in social media", 13, "Climate policy", 14, "G20 Hamburg", 
-                   15, "error (text processing failure)", 16, "Education, Pension policy",
-                   17, "Reports on individuals", 18, "Family reunion refugees", 19, "Polls federal election", 
-                   20, "AfD top candidates Weidel, Storch", 21, "M.Schwesig (SPD)",
-                   22, "elections in Niedersachsen", 23, "Court sentences (NSU, Böhmermann vs. Erdogan)", 
-                   24, "election capaigns & political talkshows", 25, "German armed forces", 26, "W.Schäuble", 
-                   27, "C.Lindner FDP", 28, "Turkey, Russia", 29, "railway problems (DBahn)", 
-                   30, "H.Kohl obituary", 31, "AfD Gauland, Höcke", 32, "Asylum claims and deportation", 
-                   33, "EU policies", 34, "DIE LINKE", 35, "SPD", 36, "Islam and antisemitism in GER", 
-                   37, "AfD in parliament", 38, "Terror attacks (GER)  & police reports", 
-                   39, "Church", 40, "RAF"), ncol=2, byrow=T)
-
-topics.df <- as.data.frame(topics) %>%
-  transmute(topic_name = paste(V1, V2, sep=": "),
-         topic = 1:40) 
-```
-
-## Assign a topic to each document (choose by gamma)
-```{r Extract wtp and dtp}
-# Document-topic probabilities
-stmOut %>% tidy("theta") -> theta
-
-top_topics <- theta %>% 
-  group_by(document) %>%
-  mutate(therank = rank(-gamma, ties.method = "random")) %>%
-  filter(therank == 1) %>%
-  select(- therank)
-
-btw.2 <- btw %>%
-  mutate(document = articleID) %>%
-  inner_join(.,top_topics, by="document") %>%
-  ## Combine with Topic label
-  left_join(., topics.df, by="topic") %>%
-  mutate(allocation = 1) 
-```
-
-### now we can inspect the unclear topics
-```{r}
-btw %>% filter(topic==17) %>% select(title, gamma, url) %>%
-  htmlTable::htmlTable(align="l")
-```
-
-## Expected topic proportions
-
-### in the overall corpus
-```{r}
-frequency <- as.data.frame(colMeans(stmOut$theta)) %>% 
-  mutate(frequency = colMeans(stmOut$theta),
-    topic=paste(topics[,1],topics[,2], sep=": "))
-
-p1 <- ggplot(frequency, aes(x=reorder(topic, frequency), y=frequency)) + 
-    geom_col(fill=col[1], alpha=0.8) +
-    coord_flip() +
-    labs(x="", y="expected frequency") +
-    theme(axis.text.x = element_text(size=8),
-          axis.text.y = element_text(size=11),
-          axis.title = element_text(size=10))
-
-p1
-
-ggsave(plot = p1, filename = "../figs/topic_proportion.png", device = "png",width = 8, height = 12,
-dpi = 600)
-```
-
-### by newspaper
-```{r}
-plotNewspaperHistogram <- function(topic){
-  tab <- tapply(stmOut$theta[,topic], stmOut$settings$covariates$betaindex, mean)
-  tab <- as.data.frame(tab) %>% 
-    mutate(site=stmOut$settings$covariates$yvarlevels)
-
-  ggplot(data=tab, aes(x=site, y=tab)) +
-    geom_col(fill=col[3]) +
-    coord_flip() +
-    theme(axis.text = element_text(size=8),
-          axis.title = element_text(size=10)) +
-    labs(x="", y=paste("expected frequency of topic",topics.df[topic,2], sep=" ")) 
-}
-```
-
-```{r}
-# Topic 3
-plotNewspaperHistogram(1)
-```
-
-### Difference in topic prevalence
-The estimateEffect() function explores how prevalence of topics varies across documents according to document covariates (metadata).
-First, users must specify the variable that they wish to use for calculating an effect.
-If there are multiple variables specified in estimateEffect(), then all other variables are held at their sample median.
-These parameters include the expected proportion of a document that belongs to a topic as a function of a covariate, or a first difference type estimate, where topic prevalence for a particular topic is contrasted for two groups.
-
-```{r}
-effect <- estimateEffect(c(1:40) ~site+s(month), stmOut, 
-                         metadata = out$meta, uncertainty = "None")
-#plot.estimateEffect(effect, "month", topics=c(33), method = "continuous", npoints=500)
-```
-
-```{r}
-summary(effect)
-```
-
-```{r}
-tables <- vector(mode="list", length = length(effect$topics))
-
-for (i in seq_along(effect$topics)) {
-  sims <- lapply(effect$parameters[[i]], function(x) stm:::rmvnorm(500, x$est, x$vcov))
-  sims <- do.call(rbind, sims)
-  est <- colMeans(sims)
-  se <- sqrt(apply(sims,2, stats::var))
-  tval <- est/se
-  rdf <- nrow(effect$data) - length(est)
-  p <- 2*stats::pt(abs(tval), rdf, lower.tail = FALSE)
-  topic <- i
-
-  coefficients <- cbind(topic, est, se, tval, p)
-  rownames(coefficients) <- attr(effect$parameters[[1]][[1]]$est, "names") 
-  colnames(coefficients) <- c("topic", "Estimate", "Std. Error", "t value", "p")
-  tables[[i]] <- coefficients
-}
-
-out <- list(call=effect$call, topics=effect$topics, tables=tables)
-```
-
-```{r}
-coeff <- as.data.frame(do.call(rbind,out$tables))
-
-coeff <- coeff %>% 
-  mutate(parameter = rownames(coeff),
-         parameter = gsub("site", "", parameter),
-         parameter = ifelse(parameter == "s(month)1", "1_July", parameter),
-         parameter = ifelse(parameter == "s(month)2", "2_August", parameter),
-         parameter = ifelse(parameter == "s(month)3", "3_September", parameter),
-         parameter = ifelse(parameter == "s(month)4", "4_October", parameter),
-         parameter = ifelse(parameter == "s(month)5", "5_November", parameter),
-         parameter = ifelse(parameter == "s(month)6", "6_December", parameter),
-         signifcant = ifelse(p <= 0.5,"yes","no")) %>%
-  left_join(., topics.df, by="topic")
-```
-
-```{r}
-sites <- c("(Intercept)", "DIE WELT", "FOCUS ONLINE","SPIEGEL ONLINE", "Tagesschau.de","ZEIT ONLINE")
-
-p1 <- coeff %>% filter(parameter %in% sites) %>%
-  ggplot(aes(x = reorder(topic_name,topic, decreasing=F), y = Estimate, fill=factor(signifcant))) +
-  geom_col() +
-  scale_fill_manual(values = col[c(2,1)]) +
-  coord_flip() +
-  facet_wrap(~parameter, ncol = 6) +
-  labs(x="", fill="significant at\nthe 5% level") +
-  theme(axis.text.x = element_text(angle=90))
-
-p1
-
-ggsave(plot = p1, filename = "../figs/estimates_site.png", device = "png",width = 9, height = 5,
-dpi = 600)
-```
-
-```{r}
-p1 <- coeff %>% filter(!parameter %in% sites) %>%
-  ggplot(aes(x = reorder(topic_name,topic, decreasing=F), y = Estimate, 
-             fill=factor(signifcant))) +
-  geom_col() +
-  scale_fill_manual(values = col[c(2,1)]) +
-  coord_flip() +
-  facet_wrap(~parameter, ncol = 6) +
-  labs(x="", fill="significant at\nthe 5% level") +
-  theme(axis.text.x = element_text(angle=90))
-
-p1
-
-ggsave(plot = p1, filename = "../figs/estimates_month.png", device = "png",width = 9, height = 5,
-dpi = 600)
-```
-
-## Topic Correlation
-```{r}
-## Create Dataframe with correlations
-
-cor <- cor(stmOut$theta[stmOut$settings$covariates$betaindex==1,])
-colnames(cor) <- 1:40
-
-df <- as.data.frame(cor) %>% 
-  mutate(topic = 1:40) %>%
-  melt(., id="topic", value.name="corr") %>%
-  mutate(site = stmOut$settings$covariates$yvarlevels[1])
-
-for (i in 2:6) {
-  cor <- cor(stmOut$theta[stmOut$settings$covariates$betaindex==i,])
-  colnames(cor) <- 1:40
-
-  df1 <- as.data.frame(cor) %>% 
-    mutate(topic = 1:40) %>%
-    melt(., id="topic", value.name="corr") %>%
-    mutate(site = stmOut$settings$covariates$yvarlevels[i])
-
-  df <- rbind(df,df1)
-}
-```
-
-```{r}
-df <- df %>% 
-  left_join(.,topics.df, by = "topic") %>%
-  mutate(topic1 = topic,
-         topic_name1 = topic_name,
-         topic = as.numeric(variable)) %>%
-  select(-topic_name) %>%
-  left_join(., topics.df, by="topic")
-```
-
-```{r}
-p1 <- df %>%
-  filter(corr>0.1 & corr < 1) %>%
-  ggplot(aes(reorder(topic_name1,topic1), topic_name, 
-             fill=corr)) +
-  geom_tile() +
-  facet_wrap(~site, ncol = 6) +
-  scale_fill_distiller(palette = "Spectral", trans = "reverse") + 
-  labs(x="", y="", fill="correlation") +
-  theme_bw(base_family = "Roboto", base_size = 10) +
-  theme(axis.text.x = element_text(angle=90, size = 6),
-        #plot.background = element_rect(fill = 'transparent', colour = 'transparent'),
-        strip.background = element_rect(fill = 'transparent', colour = 'transparent'),
-        axis.ticks = element_line(colour = 'transparent'))
-
-p1
-
-ggsave(plot = p1, filename = "../figs/topic_correlation.png", device = "png",width = 9, height = 5,
-dpi = 600)
-```
-
-### Overlapping Correlation
-Pairs of topics where an edge exists in both Newspaper, we denote with a light blue dot.
-Pairs of topics where Newspaper1, but not Newspaper2 have an edge between them, we denote with a red square, and those where Newspaper2, but not Newspaper1 have an edge between them we denote with a blue square.
-We then sort the matrix by topics that are similarly correlated with other topics in Newspaper1 and Newspaper2 to those that are not similarly correlated.
-```{r}
-png("../figs/overlapping_correlation.png")
-topicCorrCompare(1,5)
-dev.off()
-```
-
-### Distance metric
-
-Compute the Jensen Shannon divergence of the word-topic probability.
-The K-by-V (number of words in the vocabulary) matrix logbeta contains the natural log of the probability of seeing each word conditional on the topic.
-
-```{r}
-stmOut$settings$covariates$yvarlevels[1]
-```
-
-```{r}
-comb.matrix <- matrix(0, nrow= 36, ncol = 2)
-
-y <- 1
-for (i in 1:6) {
-  for (j in 1:6) {
-    comb.matrix[y,1] <- stmOut$settings$covariates$yvarlevels[i]
-    comb.matrix[y,2] <- stmOut$settings$covariates$yvarlevels[j]
-    y <- y+1
-  }
-}
-```
-
-```{r}
-# Create empty matrix
-kld.matrix <- matrix(0, nrow = nrow(comb.matrix), ncol = 40)
-names(kld.matrix) <- 1:40
-# Populate matrix with JSD Values
-
-x <- 1
-
-for (i in 1:6) {
-
-      print(paste("ylevel = ", i))
-    base <- exp(stmOut$beta$logbeta[[i]])
-    compare1 <- exp(stmOut$beta$logbeta[[1]])
-    compare2 <- exp(stmOut$beta$logbeta[[2]])
-    compare3 <- exp(stmOut$beta$logbeta[[3]])
-    compare4 <- exp(stmOut$beta$logbeta[[4]])
-    compare5 <- exp(stmOut$beta$logbeta[[5]])
-    compare6 <- exp(stmOut$beta$logbeta[[6]])
-
-  for (j in 1:40) {
-
-    print(paste("topic = ", j))
-    kld.matrix[x,j] <- JSD(base[j,],compare1[j,])
-    kld.matrix[x+1,j] <- JSD(base[j,],compare2[j,])
-    kld.matrix[x+2,j] <- JSD(base[j,],compare3[j,])
-    kld.matrix[x+3,j] <- JSD(base[j,],compare4[j,])
-    kld.matrix[x+4,j] <- JSD(base[j,],compare5[j,])
-    kld.matrix[x+5,j] <- JSD(base[j,],compare6[j,])
-
-  }
-    x <- x+6
-}
-
-```
-
-```{r}
-## Create DF
-kld.df <- as.data.frame(kld.matrix) 
-colnames(kld.df) <- 1:40
-
-kld.df <- kld.df %>% mutate(News1 = comb.matrix[,1],
-         News2 = comb.matrix[,2]) %>%
-  melt(.,id=c("News1","News2"), value.name="JSD",
-       variable.name = "topic") %>%
-  mutate(topic = as.integer(topic)) %>%
-  left_join(., topics.df, by="topic")
-```
-
-```{r}
-cols <- rev(brewer.pal(11, 'RdYlBu'))
-
-p1 <- kld.df %>%
-  filter(!topic %in% c("11","15")) %>%
-  filter(News1!=News2) %>%
-  ggplot(aes(News2, factor(topic_name), fill = JSD)) + 
-  geom_tile() + 
-  facet_grid(~News1) + 
-  scale_fill_gradientn(colours = cols) +
-  labs(x="", y="") +
-  theme_bw(base_family = "Roboto", base_size = 11) +
-  theme(axis.text.x = element_text(angle=90),
-        plot.background = element_rect(fill = 'transparent', colour = 'transparent'),
-        strip.background = element_rect(fill = 'transparent', colour = 'transparent'),
-        axis.ticks = element_line(colour = 'transparent'))
-
-p1
-
-ggsave(plot = p1, filename = "../figs/jsd.png", device = "png",width = 10, height = 8,
-dpi = 600)
-```

### 2018-02-01 paper/R/04_Modelresults.Rmd
new

--- 2018-01-25 paper/R/paper.Rmd
@@
 
-# 1. The online news market
-
-## Pageviews
-```{r}
-views1 <- read.csv("../data/alexa/Historical_Traffic_Trends__Pageviews_Percent_1.csv", comment.char="#")
-views2 <- read.csv("../data/alexa/Historical_Traffic_Trends__Pageviews_Percent_2.csv", comment.char="#")
-
-views <- left_join(views1, views2 %>% 
-                     select(-Metric), by = "Date") %>%
-  mutate(date = as.Date(Date, "%m/%d/%Y")) %>%
-  select(- c(Metric,Date)) %>%
-  gather(key="site", value="views", focus.de:tagesspiegel.de)
-```
-
-```{r}
-# keeps <- c("spiegel.de", "focus.de", "zeit.de","bild.de",
-#           "tagesschau.de")
-#drop <- c("stern.de","sueddeutsche.de")
-
-# reach <- reach %>%
-#   mutate(date = as.Date(Date, "%m/%d/%Y")) %>%
-#   select(- c(Metric,Date)) %>%
-#   gather(key="site", value="reach", focus.de:n.tv.de) %>%
-#  filter(!site %in% drop)
-
-views <- views %>%
-  mutate(site = ifelse(site=="bild.de","Bild.de",site),
-       site = ifelse(site=="focus.de","FOCUS ONLINE",site),
-       site = ifelse(site=="spiegel.de","SPIEGEL ONLINE",site),
-       site = ifelse(site=="zeit.de","ZEIT ONLINE",site),
-       site = ifelse(site=="tagesschau.de","Tagesschau.de",site),
-       site = ifelse(site=="zdf.de","ZDF.de",site),
-       site = ifelse(site=="welt.de","DIE WELT",site),
-       site = ifelse(site=="n-tv.de","n-tv.de",site))
-
-```
-
-```{r}
-p1 <- views %>%
-  filter(date > as.POSIXct("2017-05-31")) %>%
-  ggplot(aes(date, views, color=site)) +
-  geom_line(show.legend = F) +
-  geom_text_repel(data = views[views$date==max(views$date), ],
-                  aes(date, views, label=site),
-                  size=2.8, show.legend = F, seed = 1) +
-  scale_x_date(limits = c(as.Date("2017-05-31"),as.Date("2018-02-15")),
-               breaks = date_breaks("1 month"), 
-               labels=date_format("%B %y", tz="CET")) +
-  theme(
-      #legend.position   = "none",
-      legend.text       =  element_text(size=6),
-      axis.text.y       = element_text(size = 8)
-    ) +
-  labs(x="", y="pageviews", color="", title = "", 
-      caption = "Source: Alexa Internet, Inc. (www.alexa.com)" )
-
-p1
-
-ggsave(plot= p1,
-filename = "../figs/reach.png", device = "png",
-width = 6, height = 4,
-        dpi = 600
-)
-```
-
-```{r}
-# calculate percentual change
-views$perc_change <- (views$views - lag(views$views, n=1)) / (views$views*100)
-
-p1 <- views %>% 
-  filter(date >= as.Date("2017-09-17") &
-                   date <= as.Date("2017-10-01")) %>%
-  ggplot(aes(date, perc_change, color=factor(site))) +
-  geom_line(show.legend = F) +
-  geom_text_repel(data = views[views$date=="2017-09-24", ],
-                  aes(date, perc_change, label=site),
-                  size=3, show.legend = F, seed = 5) +
-  #scale_color_manual(values = brewer.pal(8,"Dark2")) +
-  scale_x_date(breaks = date_breaks("1 day"), labels=date_format("%d.%m.", tz="CET")) +
-  labs(x="",y="% change", color="") +
-  theme(
-      legend.text       =  element_text(size=6),
-      axis.text.y       = element_text(size = 8)
-    )
-
-p1
-
-ggsave(plot= p1,
-filename = "../figs/perc_change.png", device = "png",
-width = 6, height = 4,
-        dpi = 600
-)
-```
-
-## Traffic source
-
-```{r}
-source1 <- read.csv("../data/alexa/Traffic_Sources_1.csv", 
-                    comment.char="#", stringsAsFactors = F)
-source2 <- read.csv("../data/alexa/Traffic_Sources_2.csv", 
-                    comment.char="#", stringsAsFactors = F)
-
-source <- left_join(source1, source2,
-                    by=c("Date","Metric")) %>%
-  select(- c(Date)) %>%
-  gather(key="site", value="traffic", 
-         focus.de:tagesspiegel.de)
-
-source <- source %>%
-  mutate(site = ifelse(site=="bild.de","Bild.de",site),
-       site = ifelse(site=="focus.de","FOCUS ONLINE",site),
-       site = ifelse(site=="spiegel.de","SPIEGEL ONLINE",site),
-       site = ifelse(site=="zeit.de","ZEIT ONLINE",site),
-       site = ifelse(site=="tagesschau.de","Tagesschau.de",site),
-       site = ifelse(site=="zdf.de","ZDF.de",site),
-       site = ifelse(site=="welt.de","DIE WELT",site),
-       site = ifelse(site=="n-tv.de","n-tv.de",site))
-
-```
-
-```{r}
-p1 <- ggplot(source, aes(site, traffic, fill=Metric,
-                   label = round(traffic, digits = 2))) +
-  geom_col(alpha = 0.8) +
-  geom_text(size = 2, position = position_stack(vjust = 0.5)) +
-  labs(x = "", y = "Percentage of total traffic", 
-       caption = "Source: Alexa Internet, Inc. (www.alexa.com)") +
-  theme(axis.text.x = element_text(angle = 45, size = 8 ))
-
-p1
-
-ggsave(plot= p1,
-filename = "../figs/traffic_source.png", device = "png",
-width = 6, height = 4,
-        dpi = 600
-)
-```
-
-## Keywords
-```{r message=FALSE, warning=FALSE}
-setwd("../data/alexa/keywords/")
-filenames <- list.files(pattern = ".tsv$")
-
-# create an empty list that will serve as a container to receive the incoming files
-list.data<-list()
-
-# create a loop to read in your data
-for (i in 1:length(filenames)) {
-  list.data[[i]]<-read.delim(filenames[i], comment.char="#")
-}
-
-# Create DF
-keywords.df <- as.data.frame(list.data[1])
-
-for (i in 2:length(filenames)) {
-  keywords.df <- rbind(keywords.df, as.data.frame(list.data[i]))
-}
-```
-
-```{r}
-keepsite <- c("tagesschau.de", "spiegel.de", "zeit.de", 
-              "bild.de", "welt.de", "focus.de")
-
-keywords.df.reduced <- keywords.df %>% 
-  filter(nchar(as.character(site))>1) %>% filter(site %in% keepsite)
-```
-
-```{r}
-keywords.df <- keywords.df %>%
-  mutate(site = as.character(site)) %>%
-  mutate(site = ifelse(site=="bild.de","Bild.de",site),
-       site = ifelse(site=="focus.de","FOCUS ONLINE",site),
-       site = ifelse(site=="spiegel.de","SPIEGEL ONLINE",site),
-       site = ifelse(site=="zeit.de","ZEIT ONLINE",site),
-       site = ifelse(site=="tagesschau.de","Tagesschau.de",site),
-       site = ifelse(site=="deutschlandfunk.de","DLF",site),
-       site = ifelse(site=="zdf.de","ZDF.de",site),
-       site = ifelse(site=="welt.de","DIE WELT",site),
-       site = ifelse(site=="n-tv.de","n-tv.de",site))
-```
-
-### Search Traffic %
-```{r}
-p1 <- keywords.df %>%
-  arrange(desc(Percent_of_traffic)) %>%
-  group_by(site) %>%
-  top_n(10, Percent_of_traffic) %>%
-  ungroup() %>%
-  ggplot(aes(reorder(term, Percent_of_traffic), 
-             Percent_of_traffic, fill=site)) +
-  geom_col(fill=col[1], show.legend = FALSE) +
-  theme_bw(base_family = "Roboto", base_size = 7) +
-  coord_flip() +
-  facet_wrap(~site, scales = "free") +
-  labs(x= "", y = "Search traffic %", 
-       title = "",
-       caption = "Source: Alexa Internet, Inc. (www.alexa.com)")
-
-p1
-
-ggsave(plot= p1,
-filename = "../figs/search_traffic.png", device = "png",
-width = 9, height = 5,
-        dpi = 600
-)
-```
-
-### Share of voice
-```{r}
-keyword1 <- c("nachrichten", "news", "bundestagswahl 2017",
-            "groko", "jamaika")
-
-keyword2 <- c("cdu","csu","spd","fdp","afd",
-           "die linke","die grünen")
-
-```
-
-```{r}
-p1 <- keywords.df %>%
-  filter(term %in% keyword1) %>%
-  ggplot(aes(site,
-             Share_of_voice, fill=term)) +
-  geom_col(fill=col[3], show.legend = F) +
-  coord_flip() +
-  facet_grid(~term, scales = "free") +
-  labs(x= "", y = "Share of voice",
-       title = ""
-       )
-
-p1
-
-ggsave(plot= p1,
-filename = "../figs/keywords1.png", device = "png",
-width = 6, height = 4,
-        dpi = 600
-)
-```
-
-```{r}
-p1 <- keywords.df %>%
-  filter(term %in% keyword2) %>%
-  ggplot(aes(site,
-             Share_of_voice, fill=term)) +
-  geom_col(fill=col[3], show.legend = F) +
-  coord_flip() +
-  facet_grid(~term) +
-  labs(x= "", y = "Share of voice",
-       caption = "
-  Source: Alexa Internet, Inc. (www.alexa.com)
-      ",
-       title = ""
-       )
-
-p1
-
-ggsave(plot= p1,
-filename = "../figs/keywords2.png", device = "png",
-width = 6, height = 4,
-        dpi = 600
-)
-```
-
 # 2. Data 
 ```{r caching, echo = FALSE}
-load("../output/btw_combined.Rda")
+#load("../output/btw_combined.Rda")
+load("../output/btw_comb_ownership.Rda")
 ```
@@
   btw %>%
-  ggplot(aes(site)) +
+  ggplot(aes(ownership)) +
   geom_bar(fill=col[1], alpha= .8) +
@@
 ```{r caching, echo = FALSE}
-load("../output/models/STM_stemmed2 40 .Rda")
+#load("../output/models/STM_stemmed2 40 .Rda")
+load("../output/models/STM_ownership 40 .Rda")
+out <- out_ownership
 ```
@@
 ```{r}
-sagelabs$cov.betas[[5]]$problabels[,1:10]
+sagelabs$cov.betas[[1]]$problabels[,1:6]
 ```
@@
 ```{r}
-topics <- matrix(c(1, "Great coalition", 2, "Merkel vs. CSU", 3, "Jamaica coalition", 
-                   4, "Diesel scandal", 5, "Merkel as chancellor", 6, "Seehover vs. Söder", 
-                   7, "political trends after the election", 8, "Merkel vs.Schulz", 9, "AfD election results", 
-                   10, "Steinmeier,Federal President", 11, "IT themes (Data policy, Wifi, Telekom)", 
-                   12, "Federal Election in social media", 13, "Climate policy", 14, "G20 Hamburg", 
-                   15, "error (text processing failure)", 16, "Education, Pension policy",
-                   17, "Reports on individuals", 18, "Family reunion refugees", 19, "Polls federal election", 
-                   20, "AfD top candidates Weidel, Storch", 21, "M.Schwesig (SPD)",
-                   22, "elections in Niedersachsen", 23, "Court sentences (NSU, Böhmermann vs. Erdogan)", 
-                   24, "election capaigns & political talkshows", 25, "German armed forces", 26, "W.Schäuble", 
-                   27, "C.Lindner FDP", 28, "Turkey, Russia", 29, "railway problems (DBahn)", 
-                   30, "H.Kohl obituary", 31, "AfD Gauland, Höcke", 32, "Asylum claims and deportation", 
-                   33, "EU policies", 34, "DIE LINKE", 35, "SPD", 36, "Islam and antisemitism in GER", 
-                   37, "AfD in parliament", 38, "Terror attacks (GER)  & police reports", 
-                   39, "Church", 40, "RAF"), ncol=2, byrow=T)
+topics <- matrix(c(1, "Great coalition", 2, "A.Merkel, CSU, Guttenberg", 3, "Jamaica coalition",
+                   4, "Diesel scandal", 5, "A.Merkel, glyphosat scandal", 6, "Seehover vs. Söder",
+                   7, "political trends after the election", 8, "Merkel vs.Schulz", 9, "Trends in electoral districts", 
+                   10, "Steinmeier, Federal President", 11, "G.Schröder & IT themes (Data policy, Wifi, Telekom)", 
+                   12, "Federal Election trends", 13, "Climate policy", 14, "G20 Hamburg", 
+                   15, "error (text processing failure)", 16, "Federal budget statistics", 
+                   17, "Reports on individuals (Berlin)", 18, "Family reunion refugees", 
+                   19, "Polls federal election", 20, "AfD, Weidel in social media", 
+                   21, "Women empowerment, M.Schwesig (SPD)", 22, "elections in Niedersachsen", 
+                   23, "Court sentences, NSU trial", 24, "election capaigns & political talkshows", 
+                   25, "German armed forces", 26, "Issues in the Bundestag", 27, "C.Lindner FDP", 
+                   28, "Turkey, Russia", 29, "railway problems (DBahn)", 30, "H.Kohl obituary", 
+                   31, "AfD Gauland, Höcke", 32, "Asylum claims and deportation", 33, "EU policies", 
+                   34, "DIE LINKE", 35, "SPD", 36, "Islam and antisemitism in GER", 37, "AfD in parliament", 
+                   38, "Terror attacks (GER)  & police reports", 39, "Church", 40, "RAF"), ncol=2, byrow=T)
 
@@
 ```{r}
-btw %>% filter(topic==17) %>% select(title, gamma, url) %>%
+btw.2 %>% filter(topic==11) %>% select(title, gamma, url) %>%
   htmlTable::htmlTable(align="l")
@@
 
-## Expected topic proportions
+## 3.1. Topic proportions
 
@@
 ```{r}
-plotNewspaperHistogram <- function(topic){
-  tab <- tapply(stmOut$theta[,topic], stmOut$settings$covariates$betaindex, mean)
-  tab <- as.data.frame(tab) %>% 
-    mutate(site=stmOut$settings$covariates$yvarlevels)
+# Topic 1
+plotNewspaperHistogram(2)
+```
 
-  ggplot(data=tab, aes(x=site, y=tab)) +
-    geom_col(fill=col[3]) +
-    coord_flip() +
-    theme(axis.text = element_text(size=8),
-          axis.title = element_text(size=10)) +
-    labs(x="", y=paste("expected frequency of topic",topics.df[topic,2], sep=" ")) 
+### by ownership
+plots the expected proportion of topic use in public media minus the expected proportion of topic use in private media. Thus topics more associated with public media appear to the right of zero.
+
+```{r}
+freq <- tapply(stmOut$theta[,1], stmOut$settings$covariates$betaindex, mean)
+freq <- as.data.frame(freq) %>% 
+    mutate(ownership=stmOut$settings$covariates$yvarlevels,
+           topic = 1)
+
+for(i in 2:40) {
+  freq1 <- tapply(stmOut$theta[,i], stmOut$settings$covariates$betaindex, mean)
+  freq1 <- as.data.frame(freq1) %>% 
+    transmute(ownership=stmOut$settings$covariates$yvarlevels,
+           topic = i,
+           freq = freq1)
+
+  freq <- rbind(freq, freq1)
 }
+
+freq <- freq %>%
+  #mutate(ownership = ifelse(site == "Tagesschau.de", "public", "private")) %>%
+  group_by(topic, ownership) %>%
+  summarise(freq_mean = mean(freq)) %>%
+  spread(ownership, freq_mean) %>%
+  mutate(freq_diff = public - private) %>%
+  mutate(value = ifelse(freq_diff>=0, 1,0)) %>%
+  left_join(., topics.df, by = "topic")
 ```
@@
 ```{r}
-# Topic 3
-plotNewspaperHistogram(1)
+p1 <- ggplot(freq, aes(reorder(topic_name, freq_diff), freq_diff,
+                 fill = factor(value))) +
+  geom_col(show.legend = F) +
+  scale_fill_manual(values = col[c(1,3)]) +
+  coord_flip() +
+  theme(axis.text.x = element_text(size=8),
+          axis.text.y = element_text(size=11),
+          axis.title = element_text(size=10)) +
+    labs(x="", y="difference in expected frequency (public-private)")
+
+p1
+
+ggsave(plot = p1, filename = "../figs/topic_proportion_diff.png", device = "png",width = 8, height = 12,
+dpi = 600)
 ```
 
-### Difference in topic prevalence
+## 3.2. Difference in topic prevalence
 The estimateEffect() function explores how prevalence of topics varies across documents according to document covariates (metadata).
@@
 ```{r}
-effect <- estimateEffect(c(1:40) ~site+s(month), stmOut, 
-                         metadata = out$meta, uncertainty = "None")
-#plot.estimateEffect(effect, "month", topics=c(33), method = "continuous", npoints=500)
-```
+# effect <- estimateEffect(c(1:40) ~site+s(month), stmOut, 
+#                          metadata = out$meta, uncertainty = "None")
 
-```{r}
-summary(effect)
+effect <- estimateEffect(c(1:40) ~ownership+s(month), stmOut, 
+                         metadata = out_ownership$meta, uncertainty = "None")
+#save(out_ownership,stmOut, effect, file = "stm_newsdata.RData")
 ```
@@
 
-out <- list(call=effect$call, topics=effect$topics, tables=tables)
+out1 <- list(call=effect$call, topics=effect$topics, tables=tables)
 ```
@@
 ```{r}
-coeff <- as.data.frame(do.call(rbind,out$tables))
+coeff <- as.data.frame(do.call(rbind,out1$tables))
 
@@
   mutate(parameter = rownames(coeff),
-         parameter = gsub("site", "", parameter),
+         parameter = gsub("ownership", "", parameter),
          parameter = ifelse(parameter == "s(month)1", "1_July", parameter),
@@
 ```{r}
-sites <- c("(Intercept)", "DIE WELT", "FOCUS ONLINE","SPIEGEL ONLINE", "Tagesschau.de","ZEIT ONLINE")
-
+#sites <- c("(Intercept)", "DIE WELT", "FOCUS ONLINE","SPIEGEL ONLINE", "Tagesschau.de","ZEIT ONLINE")
+sites <- c("(Intercept)", "public", "private")
 p1 <- coeff %>% filter(parameter %in% sites) %>%
@@
 
-ggsave(plot = p1, filename = "../figs/estimates_site.png", device = "png",width = 9, height = 5,
-dpi = 600)
+# ggsave(plot = p1, filename = "../figs/estimates_site.png", device = "png",width = 9, height = 5,
+# dpi = 600)
 ```
@@
 
-ggsave(plot = p1, filename = "../figs/estimates_month.png", device = "png",width = 9, height = 5,
-dpi = 600)
+# ggsave(plot = p1, filename = "../figs/estimates_month.png", device = "png",width = 9, height = 5,
+# dpi = 600)
 ```
 
-## Topic Correlation
+## 3.3 Topic Correlation
 ```{r}
 ## Create Dataframe with correlations
-
 cor <- cor(stmOut$theta[stmOut$settings$covariates$betaindex==1,])
@@
 
-for (i in 2:6) {
+for (i in 2:2) {
   cor <- cor(stmOut$theta[stmOut$settings$covariates$betaindex==i,])
@@
   facet_wrap(~site, ncol = 6) +
-  scale_fill_distiller(palette = "Spectral", trans = "reverse") + 
+  #scale_fill_distiller(palette = "Spectral", trans = "reverse") + 
   labs(x="", y="", fill="correlation") +
@@
 
-ggsave(plot = p1, filename = "../figs/topic_correlation.png", device = "png",width = 9, height = 5,
-dpi = 600)
+# ggsave(plot = p1, filename = "../figs/topic_correlation.png", device = "png",width = 9, height = 5,
+# dpi = 600)
+```
+
+### Network graph
+```{r}
+i <- 1
+cormat <- cor(stmOut$theta[stmOut$settings$covariates$betaindex==i,])
+cormat <- ifelse(cormat >=0.05, cor, 0)
+# 
+g <- igraph::simplify(igraph::graph.adjacency(cormat, mode = "undirected", weight=TRUE))
+igraph::V(g)$name <- topics.df$topic_name
+igraph::V(g)$props <- colMeans(stmOut$theta)
+
+p1 <- topicCorrNetwork(g, stmOut$settings$covariates$yvarlevels[i])
+# 
+ggsave(
+      paste0("../figs/corrplot",i,".png"),
+      p1,
+      dpi = 300,
+      width = 9,
+      height = 6
+    )
 ```
@@
 
-### Distance metric
+## 3.4 Distance metric
+Compute different metrices and compare them.
 
@@
 ```{r}
-stmOut$settings$covariates$yvarlevels[1]
+k <- stmOut$settings$dim$K
+y <- length(stmOut$settings$covariates$yvarlevels)
 ```
@@
 ```{r}
-comb.matrix <- matrix(0, nrow= 36, ncol = 2)
+## Find all combinations of ylevel
+comb.matrix <- matrix(0, 
+                      nrow= y^2, 
+                      ncol = 2)
 
-y <- 1
-for (i in 1:6) {
-  for (j in 1:6) {
-    comb.matrix[y,1] <- stmOut$settings$covariates$yvarlevels[i]
-    comb.matrix[y,2] <- stmOut$settings$covariates$yvarlevels[j]
-    y <- y+1
+z <- 1
+for (i in 1:y) {
+  for (j in 1:y) {
+    comb.matrix[z,1] <- stmOut$settings$covariates$yvarlevels[i]
+    comb.matrix[z,2] <- stmOut$settings$covariates$yvarlevels[j]
+    z <- z+1
   }
@@
 
+### Calculate KLD
 ```{r}
 # Create empty matrix
-kld.matrix <- matrix(0, nrow = nrow(comb.matrix), ncol = 40)
-names(kld.matrix) <- 1:40
+kld.matrix <- matrix(0, nrow = nrow(comb.matrix), ncol = k)
+names(kld.matrix) <- 1:k
+
 # Populate matrix with JSD Values
+x <- 1
+for (i in 1:y) {
 
-x <- 1
-
-for (i in 1:6) {
-
-      print(paste("ylevel = ", i))
+    #print(paste("ylevel = ", i))
     base <- exp(stmOut$beta$logbeta[[i]])
@@
     compare2 <- exp(stmOut$beta$logbeta[[2]])
-    compare3 <- exp(stmOut$beta$logbeta[[3]])
-    compare4 <- exp(stmOut$beta$logbeta[[4]])
-    compare5 <- exp(stmOut$beta$logbeta[[5]])
-    compare6 <- exp(stmOut$beta$logbeta[[6]])
+    # compare3 <- exp(stmOut$beta$logbeta[[3]])
+    # compare4 <- exp(stmOut$beta$logbeta[[4]])
+    # compare5 <- exp(stmOut$beta$logbeta[[5]])
+    # compare6 <- exp(stmOut$beta$logbeta[[6]])
 
-  for (j in 1:40) {
+  for (j in 1:k) {
 
-    print(paste("topic = ", j))
-    kld.matrix[x,j] <- JSD(base[j,],compare1[j,])
-    kld.matrix[x+1,j] <- JSD(base[j,],compare2[j,])
-    kld.matrix[x+2,j] <- JSD(base[j,],compare3[j,])
-    kld.matrix[x+3,j] <- JSD(base[j,],compare4[j,])
-    kld.matrix[x+4,j] <- JSD(base[j,],compare5[j,])
-    kld.matrix[x+5,j] <- JSD(base[j,],compare6[j,])
+    #print(paste("topic = ", j))
+    kld.matrix[x,j] <- KLD(base[j,],compare1[j,])
+    kld.matrix[x+1,j] <- KLD(base[j,],compare2[j,])
+    # kld.matrix[x+2,j] <- JSD(base[j,],compare3[j,])
+    # kld.matrix[x+3,j] <- JSD(base[j,],compare4[j,])
+    # kld.matrix[x+4,j] <- JSD(base[j,],compare5[j,])
+    # kld.matrix[x+5,j] <- JSD(base[j,],compare6[j,])
 
   }
-    x <- x+6
+    x <- x+y
 }
-
 ```
@@
 kld.df <- as.data.frame(kld.matrix) 
-colnames(kld.df) <- 1:40
+colnames(kld.df) <- 1:k
 
@@
          News2 = comb.matrix[,2]) %>%
-  melt(.,id=c("News1","News2"), value.name="JSD",
+  melt(.,id=c("News1","News2"), value.name="KLD",
        variable.name = "topic") %>%
@@
 
+### Calculate JSD
+```{r}
+# Create empty matrix
+jsd.matrix <- matrix(0, nrow = nrow(comb.matrix), ncol = k)
+names(jsd.matrix) <- 1:k
+
+# Populate matrix with JSD Values
+x <- 1
+for (i in 1:y) {
+
+    #print(paste("ylevel = ", i))
+    base <- exp(stmOut$beta$logbeta[[i]])
+    compare1 <- exp(stmOut$beta$logbeta[[1]])
+    compare2 <- exp(stmOut$beta$logbeta[[2]])
+    # compare3 <- exp(stmOut$beta$logbeta[[3]])
+    # compare4 <- exp(stmOut$beta$logbeta[[4]])
+    # compare5 <- exp(stmOut$beta$logbeta[[5]])
+    # compare6 <- exp(stmOut$beta$logbeta[[6]])
+
+  for (j in 1:k) {
+
+    #print(paste("topic = ", j))
+    jsd.matrix[x,j] <- JSD(base[j,],compare1[j,])
+    jsd.matrix[x+1,j] <- JSD(base[j,],compare2[j,])
+    # kld.matrix[x+2,j] <- JSD(base[j,],compare3[j,])
+    # kld.matrix[x+3,j] <- JSD(base[j,],compare4[j,])
+    # kld.matrix[x+4,j] <- JSD(base[j,],compare5[j,])
+    # kld.matrix[x+5,j] <- JSD(base[j,],compare6[j,])
+
+  }
+    x <- x+y
+}
+```
+
+```{r}
+## Create DF
+jsd.df <- as.data.frame(jsd.matrix) 
+colnames(jsd.df) <- 1:k
+
+distance.df <- jsd.df %>% mutate(News1 = comb.matrix[,1],
+         News2 = comb.matrix[,2]) %>% 
+  melt(.,id=c("News1","News2"), value.name="JSD",
+       variable.name = "topic") %>%
+  mutate(topic = as.integer(topic)) %>%
+  left_join(., kld.df, by=c("News1","News2","topic")) 
+```
+
+### Plot 
 ```{r}
@@
 
-p1 <- kld.df %>%
+p1 <- distance.df %>%
   filter(!topic %in% c("11","15")) %>%
   filter(News1!=News2) %>%
-  ggplot(aes(News2, factor(topic_name), fill = JSD)) + 
+  ggplot(aes(News1, reorder(factor(topic_name),JSD), fill = KLD)) + 
   geom_tile() +
-  facet_grid(~News1) + 
+  #facet_wrap(~variable) + 
   scale_fill_gradientn(colours = cols) +
@@
   theme_bw(base_family = "Roboto", base_size = 11) +
-  theme(axis.text.x = element_text(angle=90),
+  theme(axis.text.y = element_blank(),
+        legend.position = "top",
+    #axis.text.x = element_text(angle=90),
         plot.background = element_rect(fill = 'transparent', colour = 'transparent'),
@@
 
-p1
+p2 <- distance.df %>%
+  filter(!topic %in% c("11","15")) %>%
+  filter(News1!=News2) %>%
+  filter(News1=="private") %>%
+  ggplot(aes(News1, reorder(factor(topic_name),JSD), fill = JSD)) + 
+  geom_tile() +
+  #facet_wrap(~variable) + 
+  scale_fill_gradientn(colours = cols) +
+  labs(x="", y="") +
+  theme_bw(base_family = "Roboto", base_size = 11) +
+  theme(axis.text.x = element_blank(),
+        legend.position = "top",
+    #axis.text.x = element_text(angle=90),
+        plot.background = element_rect(fill = 'transparent', colour = 'transparent'),
+        strip.background = element_rect(fill = 'transparent', colour = 'transparent'),
+        axis.ticks = element_line(colour = 'transparent'))
 
-ggsave(plot = p1, filename = "../figs/jsd.png", device = "png",width = 10, height = 8,
+p2+p1
+
+ggsave(filename = "../figs/distance.png", device = "png",width = 10, height = 8,
 dpi = 600)

### 2018-02-01 paper/doc/structure.tex
new

@@
 
+\todo{Separate by ownership and explain why article distribution represents real-world.}
+
 \begin{figure}[H]
@@
 
-The outline of this chapter is as follows. In Section \ref{ch_generativeProcess} we describe the generative process of the Structural Topic Model (STM).
-
 % Topic Modeling
@@
 
+The STM maximizes the posterior likelihood that the observed data were generated by the above data-generating process using an iterative approximation-based variational expectation-maximization algorithm\footnote{A technical description of this maximization process can be found in \citet{roberts_model_2016}} available in R's stm package \citep{roberts_stm:_2016}.
+The process gives us two posterior distribution parameter: (1) $\beta$ is a $K$-by-$V$ matrix (where $K=$ number of topics and $V=$ vocabulary), where the entry $\beta_{kv}$ can be interpreted as the probability of observing the $v$-th word in topic $k$.
+As we let covariate levels (the news provider) effect the word-distribution of a topic, we will get as many $\beta$ matrices as news provider.
+(2) $\theta$ is a $D$-by-$V$ matrix of the document-topic distributions, where the entry $\theta_{dk}$ can be interpreted as the proportion of words in document $d$ which arise from topic $k$, or rather as the probability that document $d$ deals about topic $k$.
+We will use these probability distributions to compare the content of public and private news provider in Section \ref{ch_empirical}.
+
 % ----------------------
@@
 
-The STM maximizes the posterior likelihood that the observed data were generated by the above data-generating process using an iterative approximation-based variational expectation-maximization algorithm\footnote{A technical description of this maximization process can be found in \citet{roberts_model_2016}} available in R's stm package \citep{roberts_stm:_2016}.
-Regularizing prior distributions are used for $\gamma$, $\kappa$ and $\Sigma$.
+Inference of mixed-membership models, such as the one applied in this paper, has been a thread of research in applied statistics in the past few years \citep{blei_latent_2003} \citep{erosheva_mixed-membership_2004} \citep{braun_variational_2010}.
 Topic models are usually imprecise as the function we are optimizing has multiple modes, such that the model results can be sensitive to the starting values.
@@
 This enables us to check how substantively different results are for different model solution \citep{roberts_navigating_2016}.
-
-them with respect to the research problem \citep{gentzkow_text_2017}.
-To evaluate the accuracy of a model its perplexity can be computed.
-Similar to cross-validation (VC), different model specifications are compared to how well they do in predicting words within a document \citep{asuncion_smoothing_2012}, \citep{wallach_evaluation_2009}.
-However, \citet{chang_reading_2009} have proven with large user studies that optimal held out likelihood does not correspond to human perception of semantic coherence of topics.
-\cite{mimno_optimizing_2011} introduced a measure of coherence of a topic by observing co-occurences of the top $N$ terms of each topic on a document.
-Another strategy for selecting an appropriate model is to check for residual overdispersion of the variance of the multinomial within the data generating process of the model \citep{taddy_estimation_2012}.
-Other approaches can be found in \citet{airoldi_reconceptualizing_2010} and \citet{teh_hierarchical_2006}.
-However, cross-checking some subset of assigned topic distributions to evaluate whether the estimates align with the concept of interest \citep{gentzkow_text_2017}.
+We then cross-checked some subset of assigned topic distributions to evaluate whether the estimates align with the concept of interest \citep{gentzkow_text_2017}.
 We apply these manual audits together with numeric optimization based on the topic coherence measure suggested by \citet{mimno_optimizing_2011}.
@@
 % ----------------------
-\section{Empirical Evaluation}
-
-\todo{Inspect model with ownership covariates}
-\todo{Inspect model with different topic-numbers}
-
-Inference of mixed-membership models, such as the one applied in this paper, has been a thread of research in applied statistics in the past few years \citep{blei_latent_2003} \citep{erosheva_mixed-membership_2004} \citep{braun_variational_2010}.
-As the posterior can be highly dependent on the model definition, using multiple starting points and clever initialization are successful practices.
-The takeaway from empirical evaluations of the inference task of mixed-membership models is that the bayesian posterior as good frequentist properties \citep{wallach_evaluation_2009}.
-\citet{roberts_model_2016} use empirical evaluation, including a frequentist coverage analysis and compare the performance of their STM to a variety of alternatives in \citet{roberts_navigating_2016}.
-
-From the STM we get two matrices of parameters: $\beta$ is a row-normalized $K$-by-$V$ matrix of topic-word distributions, where the entry $\beta_{k,v}$ can be interpreted as the probability of observing the $v$-th word in topic $k$.
-Similarly $\theta$ is a row-normalized $D$-by-$K$ matrix of topic-word distributions, where the entry $\theta_{d,k}$ can be interpreted as the proportion of words in document $d$ which arise from topic $k$.
-In this section we will use the $\theta$ and $\beta$ matrices to analyze the model results.
+\section{Empirical Evaluation}\label{ch_empirical}
 
@@
 To assign a label to each topic, we looked at the most frequent words in that topic and the most representative articles \citep{roberts_model_2016}.
-
 Figure \ref{fig_topic_proportion_diff} plots the expected proportion of topic use in public media minus the expected proportion of topic use in private media.
@@
 % ----------------------
+We use various approaches to investigate the differences between news provider content: (1) First, we use the document-topic probability $\theta$, to estimate the conditional expectation of topic prevalence for given document characteristics.
+(2) Next, we find all edges between topics where they exhibit a positive correlation of $\theta$ above 0.1 to examine how topics are correlated differently for different news wires, indicating how topics are connected and framed differently in each newswire.
+Approaches (1) and (2) have been used in \citep{roberts_model_2016} \todo{Noch 1,2,3 studien angeben ,die das gemacht haben.} However, we extend the analysis by (3) calculaing the similarity of the word-topic distribution $\beta$ between the news provider using different distance metrices, to identify which topics are discussed similar and differently.
+
 \subsection{Differences in topic prevalence}
@@
 		\begin{center}
-			\includegraphics[width=0.9\textwidth,keepaspectratio]{../figs/topic_correlation.png}
+		\begin{subfigure}{.7\textwidth}
+			\includegraphics[width=\textwidth]{../figs/corrplot1.png}	
+			\subcaption{Private news provider}
+		\end{subfigure}
+		\begin{subfigure}{.7\textwidth}
+			\includegraphics[width=\textwidth]{../figs/corrplot2}
+			\caption{Public news provider}	
+		\end{subfigure}
 		\end{center}
@@
 \subsection{Differences in word-topic distributions}\label{ch_similarity}
+
+for each news provider we get a respective $\beta$, $K$x$V$ matrix.
+We then use each row (corresponding to each topic) to calculate the similarity of the word-topic distribution between the news provider using the square root of the Jensen-Shannon (JS) Divergence.
 
@@
 	\begin{center}
-	\includegraphics[width=\textwidth,keepaspectratio]{../figs/jsd.png}
-	\caption{Jensen-Shannon (JS) Divergence of word-topic probability}
-	\label{fig_jsd}
+		\includegraphics[width=0.8\textwidth,keepaspectratio]{../figs/distance}
+		\caption{Similarity measures of word-topic probabilities}
 	\end{center}

### 2018-02-01 paper/R/func/functions.R

@@ -11,6 +11,22 @@ Mode = function(x){
   return(mod)
 }
 
+#############################
+## Topic proportion by Ylevel
+#############################
+plotNewspaperHistogram <- function(topic){
+  tab <- tapply(stmOut$theta[,topic], stmOut$settings$covariates$betaindex, mean)
+  tab <- as.data.frame(tab) %>% 
+    mutate(site=stmOut$settings$covariates$yvarlevels)
+  
+  ggplot(data=tab, aes(x=site, y=tab)) +
+    geom_col(fill=col[3]) +
+    coord_flip() +
+    theme(axis.text = element_text(size=8),
+          axis.title = element_text(size=10)) +
+    labs(x="", y=paste("expected frequency of topic",topics.df[topic,2], sep=" ")) 
+}
+
 ##################################
 ## Topic correlation within Ylevel
 ##################################
@@ -36,6 +52,46 @@ topicCorrelation <- function(ylevel) {
   plot.igraph(g, layout=layout_nicely, vertex.color="white", label.font = "Roboto",
               vertex.frame.color="grey", vertex.size=1, vertex.label.cex=.7, edge.color="red",
               edge.width=1, main=paste("Topic correlation", stmOut$settings$covariates$yvarlevels[ylevel]))
+}
+
+##################################
+## Topic correlation Network
+##################################
+topicCorrNetwork <- function(g, title) {
+  
+  toplot <- tidygraph::as_tbl_graph(g) %>%
+    mutate(degree = tidygraph::centrality_degree(loops = FALSE)) %>%
+    tidygraph::activate(edges) %>%
+    filter(!tidygraph::edge_is_loop()) %>%
+    mutate(weight = round(weight, 2),
+           edge_label = '')
+  
+  plot <- toplot %>% ggraph(layout = 'fr') +
+    geom_edge_link(
+      aes(edge_width = weight, label =  edge_label),
+      label_colour = '#fc8d62',
+      edge_colour = '#377eb8',
+      alpha = 0.5,
+      label_size = 0.5,
+      angle_calc = 'along'
+      #label_dodge = unit(3, "mm")
+    ) +
+    geom_node_point(size = 2, colour = 'black')  +
+    geom_node_label(
+      aes(label = name),
+      size = 2,
+      colour = 'black',
+      repel = TRUE,
+      alpha = 0.85
+    ) +
+    theme_graph() +
+    #scale_size(range = c(1, 3), labels = scales::percent) +
[…]

### 2018-02-02 paper/R/04_Modelresults.Rmd
add l1norm, cosine similarity

@@
 ```{r}
-sagelabs$cov.betas[[1]]$problabels[,1:6]
+sagelabs$cov.betas[[2]]$problabels[,1:6]
 ```
@@
 k <- stmOut$settings$dim$K
-y <- length(stmOut$settings$covariates$yvarlevels)
+p <- length(stmOut$settings$covariates$yvarlevels)
 ```
@@
 comb.matrix <- matrix(0, 
-                      nrow= y^2, 
+                      nrow= p^2, 
                       ncol = 2)
@@
 z <- 1
-for (i in 1:y) {
-  for (j in 1:y) {
+for (i in 1:p) {
+  for (j in 1:p) {
     comb.matrix[z,1] <- stmOut$settings$covariates$yvarlevels[i]
@@
 }
+```
+
+### Calculate L1 Norm
+```{r}
+# Create empty matrix
+l1.matrix <- matrix(0, nrow = nrow(comb.matrix), ncol = k)
+names(l1.matrix) <- 1:k
+
+# Populate matrix with JSD Values
+z <- 1
+for (i in 1:p) {
+
+    #print(paste("ylevel = ", i))
+    base <- exp(stmOut$beta$logbeta[[i]])
+    compare1 <- exp(stmOut$beta$logbeta[[1]])
+    compare2 <- exp(stmOut$beta$logbeta[[2]])
+
+  for (j in 1:k) {
+
+    #print(paste("topic = ", j))
+    l1.matrix[z,j] <- sum(abs(base[j,]-compare1[j,]))
+    l1.matrix[z+1,j] <- sum(abs(base[j,]-compare2[j,]))
+
+  }
+    z <- z+p
+}
+
+```
+
+```{r}
+## Create DF
+l1.df <- as.data.frame(l1.matrix) 
+colnames(l1.df) <- 1:k
+
+l1.df <- l1.df %>% 
+  mutate(News1 = comb.matrix[,1],
+         News2 = comb.matrix[,2]) %>%
+  melt(.,id=c("News1","News2"), value.name="L1Norm",
+       variable.name = "topic") %>%
+  mutate(topic = as.integer(topic)) %>%
+  left_join(., topics.df, by="topic")
+```
+
+### Calculate Cosine Similarity
+```{r}
+# Create empty matrix
+cosine.matrix <- matrix(0, nrow = nrow(comb.matrix), ncol = k)
+names(cosine.matrix) <- 1:k
+
+# Populate matrix with JSD Values
+z <- 1
+for (i in 1:p) {
+
+    #print(paste("ylevel = ", i))
+    base <- exp(stmOut$beta$logbeta[[i]])
+    compare1 <- exp(stmOut$beta$logbeta[[1]])
+    compare2 <- exp(stmOut$beta$logbeta[[2]])
+
+  for (j in 1:k) {
+
+    #print(paste("topic = ", j))
+    cosine.matrix[z,j] <- CosSim(base[j,],compare1[j,])
+    cosine.matrix[z+1,j] <- CosSim(base[j,],compare2[j,])
+
+  }
+    z <- z+p
+}
+
+```
+
+```{r}
+## Create DF
+cosine.df <- as.data.frame(cosine.matrix) 
+colnames(cosine.df) <- 1:k
+
+cosine.df <- cosine.df %>% 
+  mutate(News1 = comb.matrix[,1],
+         News2 = comb.matrix[,2]) %>%
+  melt(.,id=c("News1","News2"), value.name="CosineSimilarity",
+       variable.name = "topic") %>%
+  mutate(topic = as.integer(topic)) %>%
+  left_join(., l1.df, by=c("News1","News2","topic"))
 ```
@@
 # Populate matrix with JSD Values
-x <- 1
-for (i in 1:y) {
+z <- 1
+for (i in 1:p) {
 
@@
     compare2 <- exp(stmOut$beta$logbeta[[2]])
-    # compare3 <- exp(stmOut$beta$logbeta[[3]])
-    # compare4 <- exp(stmOut$beta$logbeta[[4]])
-    # compare5 <- exp(stmOut$beta$logbeta[[5]])
-    # compare6 <- exp(stmOut$beta$logbeta[[6]])
 
@@
     #print(paste("topic = ", j))
-    kld.matrix[x,j] <- KLD(base[j,],compare1[j,])
-    kld.matrix[x+1,j] <- KLD(base[j,],compare2[j,])
-    # kld.matrix[x+2,j] <- JSD(base[j,],compare3[j,])
-    # kld.matrix[x+3,j] <- JSD(base[j,],compare4[j,])
-    # kld.matrix[x+4,j] <- JSD(base[j,],compare5[j,])
-    # kld.matrix[x+5,j] <- JSD(base[j,],compare6[j,])
+    kld.matrix[z,j] <- KLD(base[j,],compare1[j,])
+    kld.matrix[z+1,j] <- KLD(base[j,],compare2[j,])
 
   }
-    x <- x+y
+    z <- z+p
 }
@@
   mutate(topic = as.integer(topic)) %>%
-  left_join(., topics.df, by="topic")
+  left_join(., cosine.df, by=c("News1","News2","topic"))
 ```
@@
     #print(paste("topic = ", j))
-    jsd.matrix[x,j] <- JSD(base[j,],compare1[j,])
-    jsd.matrix[x+1,j] <- JSD(base[j,],compare2[j,])
-    # kld.matrix[x+2,j] <- JSD(base[j,],compare3[j,])
-    # kld.matrix[x+3,j] <- JSD(base[j,],compare4[j,])
-    # kld.matrix[x+4,j] <- JSD(base[j,],compare5[j,])
-    # kld.matrix[x+5,j] <- JSD(base[j,],compare6[j,])
+    jsd.matrix[z,j] <- JSD(base[j,],compare1[j,])
+    jsd.matrix[z+1,j] <- JSD(base[j,],compare2[j,])
 
   }
-    x <- x+y
+    z <- z+p
 }
@@
   left_join(., kld.df, by=c("News1","News2","topic"))
+
+rm(l1.df, jsd.df, cosine.df, kld.df)
 ```
@@
   filter(News1!=News2) %>%
-  ggplot(aes(News1, reorder(factor(topic_name),JSD), fill = KLD)) + 
+  filter(News1=="private") %>%
+  ggplot(aes(News1, reorder(factor(topic_name),JSD), fill = JSD)) + 
   geom_tile() +
-  #facet_wrap(~variable) + 
   scale_fill_gradientn(colours = cols) +
@@
   theme_bw(base_family = "Roboto", base_size = 11) +
-  theme(axis.text.y = element_blank(),
+  theme(axis.text.x = element_blank(),
         legend.position = "top",
-    #axis.text.x = element_text(angle=90),
         plot.background = element_rect(fill = 'transparent', colour = 'transparent'),
@@
   filter(News1!=News2) %>%
-  filter(News1=="private") %>%
-  ggplot(aes(News1, reorder(factor(topic_name),JSD), fill = JSD)) + 
+  ggplot(aes(News1, reorder(factor(topic_name),JSD), fill = KLD)) + 
   geom_tile() +
-  #facet_wrap(~variable) + 
   scale_fill_gradientn(colours = cols) +
@@
   theme_bw(base_family = "Roboto", base_size = 11) +
-  theme(axis.text.x = element_blank(),
+  theme(axis.text.y = element_blank(),
         legend.position = "top",
-    #axis.text.x = element_text(angle=90),
         plot.background = element_rect(fill = 'transparent', colour = 'transparent'),
@@
 
-p2+p1
+p3 <- distance.df %>%
+  filter(!topic %in% c("11","15")) %>%
+  filter(News1!=News2) %>%
+  filter(News1=="private") %>%
+  ggplot(aes(News1, reorder(factor(topic_name),JSD), 
+             fill = CosineSimilarity)) + 
+  geom_tile() +
+  scale_fill_gradientn(colours = cols) +
+  labs(x="", y="") +
+  theme_bw(base_family = "Roboto", base_size = 11) +
+  theme(axis.text = element_blank(),
+        legend.position = "top",
+        plot.background = element_rect(fill = 'transparent', colour = 'transparent'),
+        strip.background = element_rect(fill = 'transparent', colour = 'transparent'),
+        axis.ticks = element_line(colour = 'transparent'))
 
-ggsave(filename = "../figs/distance.png", device = "png",width = 10, height = 8,
+p4 <- distance.df %>%
+  filter(!topic %in% c("11","15")) %>%
+  filter(News1!=News2) %>%
+  filter(News1=="private") %>%
+  ggplot(aes(News1, reorder(factor(topic_name),JSD), 
+             fill = L1Norm)) + 
+  geom_tile() +
+  scale_fill_gradientn(colours = cols) +
+  labs(x="", y="") +
+  theme_bw(base_family = "Roboto", base_size = 11) +
+  theme(axis.text = element_blank(),
+        legend.position = "top",
+        plot.background = element_rect(fill = 'transparent', colour = 'transparent'),
+        strip.background = element_rect(fill = 'transparent', colour = 'transparent'),
+        axis.ticks = element_line(colour = 'transparent'))
+
+(p1 | p2 | p3 | p4 )
+
+ggsave(filename = "../figs/distance.png", device = "png",width = 12, height = 8,
 dpi = 600)

### 2018-02-02 paper/doc/structure.tex
add l1norm, cosine similarity

@@
 
+\subsection{Similar Research}
+
+M.Paul (Cross-Collection Topic Models: Automatically Comparing and Contrasting Text): compares editorial differences between media sources, using cross-collection latent Dirichlet allocation (ccLDA), an LDA-based approach that incorporates differences in document metadata.
+They use a dataset of 623 news articles from August 2008 from two American media outlets - msnbc.com and foxnews.com - to analyse how they discuss topics differently.
+Comparing the top words of the word-topic distribution, they find some content differences between the two.
+
 % ----------------------
@@
 To put it differently, $\kappa^{(t)}$ indicates the importance of the term $v$ given topic $k$ regardless of the covariates.
-Similarly, $\kappa^{(c)}$ is a $A$-by-$V$ matrix, indicating the importance of the term $v$ given the covariate level $k$ regardless of the topic.
+Similarly, $\kappa^{(c)}$ is a $A$-by-$V$ matrix, indicating the importance of the term $v$ given the covariate level $c$ regardless of the topic.
 Finally, $\kappa^{(i)}$ is a $A$-by-$K$-by-$V$ matrix, collecting the covariate-topic effects.
@@
 The STM maximizes the posterior likelihood that the observed data were generated by the above data-generating process using an iterative approximation-based variational expectation-maximization algorithm\footnote{A technical description of this maximization process can be found in \citet{roberts_model_2016}} available in R's stm package \citep{roberts_stm:_2016}.
-The process gives us two posterior distribution parameter: (1) $\beta$ is a $K$-by-$V$ matrix (where $K=$ number of topics and $V=$ vocabulary), where the entry $\beta_{kv}$ can be interpreted as the probability of observing the $v$-th word in topic $k$.
-As we let covariate levels (the news provider) effect the word-distribution of a topic, we will get as many $\beta$ matrices as news provider.
+The process gives us two posterior distribution parameter: (1) $\beta$ is a $K$-by-$V$ matrix (where $K=$ number of topics and $V=$ vocabulary), where the entry $\beta_{kvc}$ can be interpreted as the probability of observing the $v$-th word in topic $k$ for the covariate level $c$.
 (2) $\theta$ is a $D$-by-$V$ matrix of the document-topic distributions, where the entry $\theta_{dk}$ can be interpreted as the proportion of words in document $d$ which arise from topic $k$, or rather as the probability that document $d$ deals about topic $k$.
@@
 This process revealed that a model with 40 topics best reflects the structure in the corpus.
-Furthermore, we use the source of each article (the media house) and the month it was published as covariates in the topic prevalence.
-In other words, the probability distribution of topics depends on the editorial strategy of a media house as well as on the month the article was published.
-We also include news agency as a covariate affecting topical content to estimate how topics are discussed in different ways by different news agencies.
+Furthermore, we use the ownership of the news provider of each article (public or private) and the month it was published as covariates in the topic prevalence.
+In other words, the probability distribution of topics depends on the business-model of a media house as well as on the month the article was published.
+We also include ownership as a covariate affecting topical content to estimate how topics are discussed in different ways by different news agencies.
 To address problems due to non-convexity, we rely on the spectral initialization approach advocated by \citet{roberts_navigating_2016}.
@@
 \section{Empirical Evaluation}\label{ch_empirical}
+
+In this section we summarize the results of the STM and apply different measures to analyze the content differences between public and private ownership.
 
@@
 Approaches (1) and (2) have been used in \citep{roberts_model_2016} \todo{Noch 1,2,3 studien angeben ,die das gemacht haben.} However, we extend the analysis by (3) calculaing the similarity of the word-topic distribution $\beta$ between the news provider using different distance metrices, to identify which topics are discussed similar and differently.
+
+\citep{roberts_navigating_2016}: Poliblog corpus to examine the role of partisanship in topical coverage.
 
@@
 
-for each news provider we get a respective $\beta$, $K$x$V$ matrix.
-We then use each row (corresponding to each topic) to calculate the similarity of the word-topic distribution between the news provider using the square root of the Jensen-Shannon (JS) Divergence.
+Since the word distribution of a topic is a simple mapping of text in space, we can use their word distribution $\beta$ to compute the similarity.
+More precisely, we get a respective $\beta$, $K$x$V$ matrix for each covariate level.
+We use each row (corresponding to each topic) to calculate the similarity of the word-topic distribution between the news provider using the square root of the Jensen-Shannon (JS) Divergence.
+Jensen-Shannon Divergence is a positive definite measure, satisfying the following conditions: $D_{js}(a,b) \geq 0$, $D_{js}(a,b)=0$ iff $(a=b)$.
+It is also symmetric: $D_{js}(a,b)=D_{js}(b,a)$.
+Let $p(x)$ and $q(x)$ be two probability density functions, the Jensen-Shannon distance $D_{js}(p,q)$ between this two distributions is defined as:
 
-\todo{Compare different metrices}
-L1 distance, cosine similarity metric (essentially the dot product rescaled by the L2 norm of the vectors).
+\begin{align*}
+	D_{js}(p,q)=\frac{1}{2}D_{KL}(p,\frac{p+q}{2})+\frac{1}{2}D_{KL}(q,\frac{p+q}{2})
+\end{align*}
 
-From the STM model we get a $KxV$ matrix (where $K=$number of topics and $V=$vocabulary) of the whole corpus that contains the probability of seeing each word of the vocabulary $V$ within topic $k$ conditional on the news provider.
-That is, for every news provider we get a $KxV$ matrix.
-We use each row (corresponding to each topic) to calculate the similarity of the word-topic distribution between the news provider using the square root of the Jensen-Shannon (JS) Divergence.
+where $D_{KL}$ is the Kullback-Leibler divergence between $p$ and $q$ defined as:
 
-A low JSD value indicates stronger similarities.
+\begin{align*}
+	D_{KL}(p,q)=\sum_{i=1}^T p_i ln \frac{p_i}{q_i}
+\end{align*}
+
+So $D_{js} \to 0$ indicates stronger similarities.
+Since $D_{js}$ does not satisfy the triangular inequality condition $D_{js}(a,c)\leq D_{js}(a,c)+D_{js}(b,c)$, the JSD is not considered to be a real metric.
+However, we can use the square root of JSD as a real distance metric \citep{endres_new_2003}.
+We will compare this metric with a set of other similarity measures recently used in the literature to measure the difference between word-topic distributions.
+
+\citep{roberts_navigating_2016}: They use the $L_1$ norm of the word-topic distributions to compare topics from different models.
+The $L_1$ norm is the sum of the absolute value of the difference between two vectors.
+Its defined as
+
+\begin{align*}
+	L_1=\sum_v |\beta_{kvi}-\beta_{kvj}|
+\end{align*}
+
+where $i$ and $j$ indicate different covariate levels.
+This measure has a range of $[0,2]$, where $ L_1 \rightarrow 0$ indicates strong similarities.
+They compare this measure with a cosine similarity metric, which is essentially the dot product rescaled by the $L_2$ norm of the vectors and is defined as
+
+\begin{align*}
+	\text{cos}(\theta)=\frac{\sum^d_{v=1}\beta_{kvi}\beta{kvj}}{\sqrt{\sum^d_{v=1}\beta_{kvi}^2}\sum^d_{v=1}\beta_{kvj}^2}
+\end{align*}
+
+Again, $i, j$ indicate different covariate levels. However, different to the above mentioned metrics the cosine similarity has a range of $[0,1]$ and $cos(\theta) \to 0$ indicate less similarity.
+
+Figure \ref{fig_distance} displays the different distance measures
 
@@
 		\caption{Similarity measures of word-topic probabilities}
+		\label{fig_distance}
 	\end{center}
 \end{figure}
+
+\todo{check topics that are most different}
 

### 2018-02-02 paper/R/func/functions.R

@@ -163,14 +163,23 @@ topicCorrCompare <- function(ylevel1, ylevel2) {
          pch=c(15,15,16,16), cex = 0.7, box.lty = 0)
 }
 
-##################################
-## Jensen-Shannon divergence (JSD)
-##################################
+####################
+## Distance Measures
+####################
 
+# Cosine Similarity
+CosSim <- function(x,y) {
+  
+  sum(x * y) / (sqrt(sum(x*x)) * sqrt(sum(y*y)))
+  
+}
+
+# Jensen Shanon Divergence
 JSD<- function(x,y) {
   sqrt(0.5 * KLD(x, (x+y)/2) + 0.5 * KLD(y, (x+y)/2))
 }
 
+# Kullback Leibler Divergence
 KLD <- function(x,y) {
   sum(x * log(x/y))
 }

### 2018-02-06 paper/R/04_Modelresults.Rmd
small corrections

@@
 },
-filename = "../figs/timeline.png", device = "png",width = 7, height = 4,
+filename = "../figs/timeline.png", device = "png",width = 6, height = 4,
 dpi = 600

### 2018-02-06 paper/doc/structure.tex
small corrections

@@
 Since 2000, public broadcasting has expanded its range of services, particularly in the digital media sector.
-If the right to produce digital media content were to be withdrawn from the public media outlets, they would not only be deprived of the possibility of improved information provision.
-They also threatened to lose their competitiveness with commercial media.
-On the other hand, there is the concern of commercial providers who are registering an ever-increasing number of digital services financed by fees.
+There is the concern of commercial providers who are registering an ever-increasing number of digital services financed by fees.
 They complain about a bias in competition caused by public media offering online text-content because of their fee financing.
 The advertising-financed business model of the media houses is based on the premise that users visit their websites in order to achieve high advertising revenues.
+However, if the right to produce digital media content were to be withdrawn from the public media outlets, they would not only be deprived of the possibility of improved information provision.
+They also threatened to lose their competitiveness with commercial media.
 
@@
 The STM approach models (a) topics as multinomial distributions of words and (b) documents as multinomial distributions of topics, allowing to incorporate external variables that effect both (a) topical content and (b) topical prevalence.
+We will include the business model (public or private) as a control for both the topical content and the topical prevalence.
+Additional, we include the month an article was published as a control for the topical prevalence.
 To explore the results, we label each topic by looking at most frequent words and most representative articles across all news providers.
@@
 	\begin{enumerate}
-		\item \textbf{Differences in topic prevalence:} As we allow prevalence of topics to evolve over time (by month) and vary across newswire services, we can use the posterior topic-probability of document $d$, to estimate the conditional expectation of topic prevalence $\theta_d$ for given document characteristics (lm on compositional data) \citep{roberts_model_2016}.
+		\item \textbf{Differences in topic prevalence:} As we allow prevalence of topics to evolve over time (by month) and vary across business models, we can use the posterior topic-probability of document $d$, to estimate the conditional expectation of topic prevalence $\theta_d$ for given document characteristics (lm on compositional data) \citep{roberts_model_2016}.
 		\begin{align*}
@@
 
-		\item \textbf{Topic correlation} How are topics linked and framed differently across news wires?
-Find all edges between topics where they exhibit a positive correlation above 0.1 \citep{roberts_model_2016}.
+		\item \textbf{Topic correlation} To get an idea of how topics are linked and framed differently across news wires, we find all edges between topics where they exhibit a positive correlation above 0.1 \citep{roberts_model_2016}.
 
-		\item \textbf{Differences in word-topic distributions} From the STM we get a $K$x$V$ matrix (where $K=$ number of topics and $V=$ vocabulary) of the whole corpus that contains the probability of seeing each word of the vocabulary $V$ within topic $k$ conditional on the news provider.
-That is, for each news provider we get a respective $K$x$V$ matrix.
+		\item \textbf{Differences in word-topic distributions} From the STM we get $\beta_{kv}$ - a $K$x$V$ matrix (where $K=$ number of topics and $V=$ vocabulary) of the whole corpus that contains the probability of seeing each word of the vocabulary $V$ within topic $k$ conditional on the business model (we get two different $\beta_{kv}$ for each topic $k$, as we have two specifications of the business model covariate: public and private).
 We then use each row (corresponding to each topic) to calculate the similarity of the word-topic distribution between the news provider using the square root of the Jensen-Shannon (JS) Divergence.
+We also compare this distance metric with three other measures of the similarity of distributions.
 
@@
 As a result, public broadcasting no longer only competes with private television and radio stations, but also enters the market for online news.
-In the following, we will briefly discuss the characteristics of the market for online news.
+In the following, we will briefly discuss the characteristics of the market for online news in Germany.
 
@@
 Advertising-supported media such as online newspapers are typical examples of two-sided markets where the newspaper can be conceived as platforms that allow interaction between audiences ("eyeballs") and advertisers.
-The newspaper creates (or buys) content to attract viewers which in turn attract advertisers who pay for readers' attention.\cite{evans_industrial_2005} The size and characteristics of the audience has a positive effect on the advertisers' willingness to pay, as advertisements are typically sold based on cost per viewer, often expressed in terms of the cost of reaching a thousand viewers (CPM).
+The newspaper creates (or buys) content to attract viewers which in turn attract advertisers who pay for readers' attention \citep{evans_industrial_2005}.
+The size and characteristics of the audience has a positive effect on the advertisers' willingness to pay, as advertisements are typically sold based on cost per viewer, often expressed in terms of the cost of reaching a thousand viewers (CPM).
 Advertising can also have an effect on the recipients, which can be both negative and positive, depending on the quality of the advertising.
@@
 As a result, many publishers rely on a free-media model, in which the publishers do not charge viewers for access to the media at all, in order to attract as many eyeballs as possible to their platform, and thus exploit the indirect network effects on the advertising site.
-In fact, most advertising-financed online magazines earn their gross margin from advertising.\cite{evans_industrial_2005} In order to maximize their profits, these companies have an interest in attracting as many readers as possible.
+In fact, most advertising-financed online magazines earn their gross margin from advertising \citep{evans_industrial_2005}.
+In order to maximize their profits, these companies have an interest in attracting as many readers as possible.
 In addition to the quantity of the audience, the demographic characteristics of recipients also have an influence on the willingness to pay on the advertiser site.
@@
 In other words, whether socially desired content that meets the (social) needs of society and is therefore politically desirable is not provided by the market.
-In order to examine this, the online news content of public media is compared with the supply of private news providers.
+In order to examine this, the online news content of public media is compared with the supply of private news providers, by comparing the topic prevalence between them.
 In the event that there is no market failure in terms of information provision (the contents do not differ), the existence of public media could still be justified by the fact that socially relevant contents of private providers are systematically distorted and the existence of public offerings ensures the diversity of information and opinions transmitted.
+We try to examine this part by analyzing how the topics are discussed differently for public and private news provider.
+For this purpose, we calculate the divergence of the word probabilities of a topic.
 
@@
 
+The following analysis of the online news market includes the largest suppliers of online news.
 Figure \ref{fig_reach} shows the largest providers of online news in terms of daily pageviews.\footnote{The figure shows the estimated percentage of daily pageviews on the internet that occurred on a specific website.} It is striking that SPIEGEL ONLINE has the greatest reach over the entire course of time followed by Bild.de.
+Public websites like Deutschlandfunk.de or Tagesschau.de have a rather small share in that market.
 
 \begin{figure}[H]
-	\caption{}
-	\begin{center}
-		\begin{subfigure}[normla]{0.8\textwidth}
-			\includegraphics[width=\textwidth]{../figs/reach.png}
+			\includegraphics[width=0.8\textwidth]{../figs/reach.png}
 			\caption{Percentage of daily pageviews}
 			\label{fig_reach}
-		\end{subfigure}
-	\end{center}
 \end{figure}
 
-Users can access a website either directly or through an intermediary, such as search engines or social media.
-As the figure \ref{fig_traffic} illustrates\footnote{The figure shows the percentage of total traffic by a source for the time period 18.12.2017-18.01.2017}, direct access\footnote{Direct traffic includes: Direct navigation (Someone types the website URL into a browser); Bookmarks (Clicks on a bookmark/favorite link in a browser); Email (Clicks on links in desktop email clients)} to a website is the main source of traffic for most news providers.
+Users can access a news website either directly or through an intermediary, such as search engines or social media.
+As the Figure \ref{fig_traffic} illustrates\footnote{The figure shows the percentage of total traffic by a source for the time period 18.12.2017-18.01.2017}, direct access\footnote{Direct traffic includes: Direct navigation (Someone types the website URL into a browser); Bookmarks (Clicks on a bookmark/favorite link in a browser); Email (Clicks on links in desktop email clients)} to a website is the main source of traffic for most news providers.
 In the case of Bild.de, the percentage is 85\%.
-Also n-tv.de (79\%), spiegel.de (76\%) and tagesschau.de (75\%) get most of their traffic via the direct route.
+Also n-tv.de (79\%), SPIEGEL ONLINE (76\%) and Tagesschau.de (75\%) get most of their traffic via the direct route.
 Other providers are more reliant on intermediaries, mainly search engines.
-Focus.de, Deutschlandfunk.de, Handelsblatt.com, for example, obtain between 40\% and 45\% of its traffic via search engines.
+FOCUS ONLINE, DLF and Handelsblatt.com, for example, obtain between 40\% and 45\% of its traffic via search engines.
 Thus, an important question is, which organic search keywords send traffic to a website.
-Figure \ref{fig_searchtraffic} displays the percentage of organic search referrals to a specific website that come from this keyword.\footnote{Percentage of organic search referrals in major search engines over the time span Jun-Dec 2017.} E.g., 0.78\% of all organic search referrals to handelsblatt.com come from the keyword "handelsblatt".
+Figure \ref{fig_searchtraffic} displays the percentage of organic search referrals to a specific website that come from this keyword.\footnote{Percentage of organic search referrals in major search engines over the time span Jun-Dec 2017.} E.g., 0.78\% of all organic search referrals to Handelsblatt.com come from the keyword "handelsblatt".
 It is not surprising that the provider's name is the keyword that generates the majority of traffic for most of the news pages.
@@
 	\begin{center}
-		\includegraphics[width=0.6\textwidth]{../figs/traffic_source.png}
+		\includegraphics[width=0.8\textwidth]{../figs/traffic_source.png}
 		\label{fig_traffic}
@@
 We conduct our estimation on a sample of 9393 online news articles from six news provider about domestic politics\footnote{Bild.de, DIE WELT, FOCUS ONLINE, SPIEGEL ONLINE, ZEIT ONLINE, Tagesschau.de}, of which only Tagesschau.de belongs to the group of public provider.
-The reason for this is that the content of Tagesschau.de is most similar to that of the private providers.
-ZDF.de offers predominantly video content and DLF website mainly offers audio content in the form of interviews.
+The reason for this is that the content structure of Tagesschau.de is most similar to that of the private providers.
+ZDF.de offers predominantly video content and DLF website mainly offers audio content in the form of interviews, which makes it hard to include in the model0 However, as we only include some of the above mentioned private suppliers, the proportions between private and public market participants are maintained, thus minimizing possible bias.
 The articles are dated from 01.06.2017 to 31.12.2017.\footnote{German federal elections took place on 24th of September 2017.} We first extract all online articles using the the Webhose.io API.\footnote{For more information see https://docs.webhose.io/v1.0/docs/getting-started.
@@
 Figure \ref{fig_distr1} shows the distribution of the number of articles from the respective news sources by date. There is a high peak around the federal elections on September, 24th.
-
-\todo{Separate by ownership and explain why article distribution represents real-world.}
 
@@
 
+A central task in text mining is to extract low-dimensional information from documents that are high-dimensional by nature \citep{bholat_text_2015}.
+This is related to the task of reducing the number of unique language elements in order to reduce the dimensionality of data (to avoid unnecessary computational complexity and overfitting) while at the same time keeping those words that reflect the content of a document.
+Any useful representation of text will throw away some information, the trick is to include the relevant information for our needs, and exclude the extraneous information.
 To use text as data and reduce the dimensionality, a common strategy is to pre-process the text by imposing some preliminary restrictions (stop-word removal, tokenization) based on the nature of the data (twitter text, newspaper articles, speeches, etc.) to reduce the number of language elements to consider \citep{gentzkow_text_2017}.
-An overview of how these steps were applied to our data set can be found in the next section.
+Intuitively the term frequency (tf) of a word is a measure of how important that word may be.
+There are words in a document, however, that occur many times but may not be important like articles, conjunctions, and so on.
+These terms, often called "stop words", are important to the grammatical structure of a text, but typically don't add any additional meaning and can therefore be neglected.
+We use a pre-defined stop word list from the Snowball stemmer project\footnote{http://svn.tartarus.org/snowball/trunk/website/algorithms/*/stop.txt} together with a customized list of stop-words that are redundant superfluous or distorting.
+We also remove punctuation character (e.g.
+., ,, !, ?, etc.) and all numbers from our corpus.
+After completing this steps we were left with 55.235 unique terms in our vocabulary.
 
@@
 This representation is often referred to as the bag of words model, since the order in which words are used within a document is completely disregarded.
-
-A central task in text mining is to extract low-dimensional information from documents that are high-dimensional by nature \citep{bholat_text_2015}.
-This is related to the task of reducing the number of unique language elements in order to reduce the dimensionality of data (to avoid unnecessary computational complexity and overfitting) while at the same time keeping those words that reflect the content of a document.
-Any useful representation of text will throw away some information, the trick is to include the relevant information for our needs, and exclude the extraneous information.
-
-Intuitively the term frequency (tf) of a word is a measure of how important that word may be.
-There are words in a document, however, that occur many times but may not be important like articles, conjunctions, and so on.
-These terms, often called "stop words", are important to the grammatical structure of a text, but typically don't add any additional meaning and can therefore be neglected.
-We use a pre-defined stop word list from the Snowball stemmer project\footnote{http://svn.tartarus.org/snowball/trunk/website/algorithms/*/stop.txt} together with a customized list of stop-words that are redundant superfluous or distorting.
-We also remove punctuation character (e.g.
-., ,, !, ?, etc.) and all numbers from our corpus.
-
-\subsection{Similar Research}
-
-M.Paul (Cross-Collection Topic Models: Automatically Comparing and Contrasting Text): compares editorial differences between media sources, using cross-collection latent Dirichlet allocation (ccLDA), an LDA-based approach that incorporates differences in document metadata.
-They use a dataset of 623 news articles from August 2008 from two American media outlets - msnbc.com and foxnews.com - to analyse how they discuss topics differently.
-Comparing the top words of the word-topic distribution, they find some content differences between the two.
 
@@
 Since its introduction into text analysis, LDA has become hugely popular and especially useful in political science.\footnote{see \citet{blei_probabilistic_2012}, \citet{grimmer_text_2013} and \citet{wiedmann_text_2016} for an overview in social science and \citet{gentzkow_text_2017} give an overview of text mining applications in economics.} \citet{wiedmann_text_2016} use topic model methods in on large amounts of news articles from two german newspapers published between 1959 and 2011, to reveal how democratic demarcation was performed in Germany over the past six decades.
+\citet{paul_cross-collection_2017} compares editorial differences between media sources, using cross-collection latent Dirichlet allocation (ccLDA), an LDA-based approach that incorporates differences in document metadata.
+They use a dataset of 623 news articles from August 2008 from two American media outlets - msnbc.com and foxnews.com - to analyse how they discuss topics differently.
+Comparing the top words of the word-topic distribution, they find some content differences between the two.
 
@@
 They use the estimated topic shares in linear fixed effects regression to forecast conflict out-of-sample.
-In order to demonstrate multi-modality of topic-models\footnote{That is, the solution of topic-models can be sensitive to the starting values as the function to be optimized has multiple modes.} can be mitigated, \citep{roberts_navigating_2016} use STM to examine the role of partisanship in topical coverage using a corpus of 13,246 posts that were written for 6 political blogs during the course of the 2008 U.S.
+In order to demonstrate multi-modality of topic-models\footnote{That is, the solution of topic-models can be sensitive to the starting values as the function to be optimized has multiple modes.} can be mitigated, \citet{roberts_navigating_2016} use STM to examine the role of partisanship in topical coverage using a corpus of 13,246 posts that were written for 6 political blogs during the course of the 2008 U.S.
 presidential election.
@@
 Topic models are usually imprecise as the function we are optimizing has multiple modes, such that the model results can be sensitive to the starting values.
-Since an ex ante valuation of a model is hardly possible, we compute a variety of different models and compare their posterior probability.
-This enables us to check how substantively different results are for different model solution \citep{roberts_navigating_2016}.
-We then cross-checked some subset of assigned topic distributions to evaluate whether the estimates align with the concept of interest \citep{gentzkow_text_2017}.
-We apply these manual audits together with numeric optimization based on the topic coherence measure suggested by \citet{mimno_optimizing_2011}.
+Since an ex ante valuation of a model is hardly possible, I compute a variety of different models and compare their posterior probability.
+This enables me to check how substantively different results are for different model solution \citep{roberts_navigating_2016}.
+I then cross-checked some subset of assigned topic distributions to evaluate whether the estimates align with the concept of interest \citep{gentzkow_text_2017}.
+I apply these manual audits together with numeric optimization based on the topic coherence measure suggested by \citet{mimno_optimizing_2011}.
 
@@
 Furthermore, we use the ownership of the news provider of each article (public or private) and the month it was published as covariates in the topic prevalence.
-In other words, the probability distribution of topics depends on the business-model of a media house as well as on the month the article was published.
+In other words, the probability distribution of topics depends on the business-model as well as on the month the article was published.
 We also include ownership as a covariate affecting topical content to estimate how topics are discussed in different ways by different news agencies.
@@
 
-In this section we summarize the results of the STM and apply different measures to analyze the content differences between public and private ownership.
+In this section I summarize the results of the STM and apply different measures to analyze the content differences between public and private ownership.
+We use various approaches to investigate the differences between news provider content: (1) To address the question whether market imperfections exist in that sense, that some topics are not covered by private but by public news provider, I use the document-topic probability $\theta$, to estimate the conditional expectation of topic prevalence for given document characteristics.
+(2) Next, I find all edges between topics where they exhibit a positive correlation of $\theta$ above 0.1 to examine how topics are correlated differently for different covariate levels, indicating how topics are connected and framed differently between private and public media.
+Approaches (1) and (2) have been used in \citep{roberts_model_2016}.
+However, we extend the analysis by (3) calculating the similarity of the word-topic distribution $\beta$ between the news provider using different distance measures, to identify which topics are discussed similar or differently.
+This process also helps us to understand whether the supply of public media
 
-Figure \ref{fig_topic_proportion} displays the topics ordered by their expected frequency across the corpus.
+Figure \ref{fig_topic_proportion} displays the topics ordered by their expected frequency across the corpus (left side of the Figure) and the expected proportion of a topic in public media minus the expected proportion of topic use in private media (right side of the Figure).
+Thus topics more associated with public media appear to the right of zero.
 To assign a label to each topic, we looked at the most frequent words in that topic and the most representative articles \citep{roberts_model_2016}.
-Figure \ref{fig_topic_proportion_diff} plots the expected proportion of topic use in public media minus the expected proportion of topic use in private media.
-Thus topics more associated with public media appear to the right of zero.
 
@@
 	\caption{Expected topic proportion}
-	\begin{subfigure}[normla]{0.4\textwidth}
 		\includegraphics[width=\textwidth,keepaspectratio]{../figs/topic_proportion.png}
-		\caption{Entire corpus}
+		\caption{Expected topic proportions}
 		\label{fig_topic_proportion}
-	\end{subfigure}
-
-	\begin{subfigure}[normla]{0.4\textwidth}
-		\includegraphics[width=\textwidth,keepaspectratio]{../figs/topic_proportion_diff.png}
-		\caption{Differences}
-		\label{fig_topic_proportion_diff}
-	\end{subfigure}
 \end{center}
@@
 
-% ----------------------
-% Effect of covariates
-% ----------------------
-We use various approaches to investigate the differences between news provider content: (1) First, we use the document-topic probability $\theta$, to estimate the conditional expectation of topic prevalence for given document characteristics.
-(2) Next, we find all edges between topics where they exhibit a positive correlation of $\theta$ above 0.1 to examine how topics are correlated differently for different news wires, indicating how topics are connected and framed differently in each newswire.
-Approaches (1) and (2) have been used in \citep{roberts_model_2016} \todo{Noch 1,2,3 studien angeben ,die das gemacht haben.} However, we extend the analysis by (3) calculaing the similarity of the word-topic distribution $\beta$ between the news provider using different distance metrices, to identify which topics are discussed similar and differently.
-
-\citep{roberts_navigating_2016}: Poliblog corpus to examine the role of partisanship in topical coverage.
+\textcolor{red}{AUSWERTUNG}
 
@@
 More specifically, we estimate a linear model, where the documents are observations, the dependent variable is the posterior probability of a topic and the covariates are the metadata of documents (see equation \ref{eq_1}).
-The stm-package provides a function that uses the method of composition to incorporates uncertainty in the dependent variable, drawing a set of topic proportions from the variational posterior repeated times and compute the coefficients as the average over all results \citep{roberts_stm:_2016}.
+The stm-package provides a function that uses the method of composition to incorporate uncertainty in the dependent variable, drawing a set of topic proportions from the variational posterior repeated times and compute the coefficients as the average over all results \citep{roberts_stm:_2016}.
 
@@
 
-Figures \ref{fig_estimateEffects1} and \ref{fig_estimateEffects2} display the regression results.
+Figure \ref{fig_estimateEffects} display the regression results for private vs.
+public.
+As we also control for the month, the intercept gives the mean of private news suppliers in June 2017.\footnote{Table of regression results can be found in appendix.}
 
 \begin{figure}[H]
-	\caption{Regression results 1}
+	\caption{Regression results}
 		\begin{center}
@@
 		\end{center}
-	\label{fig_estimateEffects1}
+	\label{fig_estimateEffects}
 \end{figure}
 
-\begin{figure}[H]
-	\caption{Regression results 2}
-		\begin{center}
-			\includegraphics[width=0.9\textwidth,keepaspectratio]{../figs/estimates_month.png}
-		\end{center}
-	\label{fig_estimateEffects2}
-\end{figure}
+\textcolor{red}{AUSWERTUNG}
 
@@
 
+\textcolor{red}{AUSWERTUNG}
+
 \subsection{Differences in word-topic distributions}\label{ch_similarity}
 
-Since the word distribution of a topic is a simple mapping of text in space, we can use their word distribution $\beta$ to compute the similarity.
-More precisely, we get a respective $\beta$, $K$x$V$ matrix for each covariate level.
-We use each row (corresponding to each topic) to calculate the similarity of the word-topic distribution between the news provider using the square root of the Jensen-Shannon (JS) Divergence.
-Jensen-Shannon Divergence is a positive definite measure, satisfying the following conditions: $D_{js}(a,b) \geq 0$, $D_{js}(a,b)=0$ iff $(a=b)$.
-It is also symmetric: $D_{js}(a,b)=D_{js}(b,a)$.
-Let $p(x)$ and $q(x)$ be two probability density functions, the Jensen-Shannon distance $D_{js}(p,q)$ between this two distributions is defined as:
+Since a topic is a multinomial distribution over the vocabulary, where $\beta_{kvi}$ indicates the probability of observing word $v$ in topic $k$ for covariate level $i$, we can analyze how similar a topic $k$ is for different levels of covariates.
+More precisely, we can calculate the similarity between $\beta_{kvi}$ and $\beta_{kvj}$.
+I use each row of that matrix (corresponding to each topic) to calculate the similarity of the word-topic distribution between the public and private media using the square root of the Jensen-Shannon (JS) Divergence.
+I will compare this metric with a set of other similarity measures recently used in the literature to measure the difference between word-topic distributions: The Kullback-Leibler (KL) divergence (\citet{newman_distributed_2009}, \citet{wang_mining_2009}), the cosine similarity (\citet{he_detecting_2009}, \citet{ramage_labeled_2009}) and the difference of the $L1$ norm of the vectors \citep{roberts_navigating_2016}.
+I will briefly explain these measures before I proceed to the results.
+
+Essentially, what we're looking at with the KL divergence is the expectation of the log difference between probabilities $a$ and $b$. It can be defined as:
 
 \begin{align*}
-	D_{js}(p,q)=\frac{1}{2}D_{KL}(p,\frac{p+q}{2})+\frac{1}{2}D_{KL}(q,\frac{p+q}{2})
+	D_{KL}(a,b)=\sum_{i=1}^T a_i \text{ln} \frac{a_i}{b_i}
 \end{align*}
 
-where $D_{KL}$ is the Kullback-Leibler divergence between $p$ and $q$ defined as:
+So $D_{kl} \to 0$ indicates stronger similarities. However, since the KL divergence is not symmetric, it cannot be used to measure the distance between two distributions, but as a divergence measure.
+
+The Jensen-Shannon Divergence is a positive definite measure, satisfying the following conditions: $D_{js}(a,b) \geq 0$, $D_{js}(a,b)=0$ iff $(a=b)$.
+It is also symmetric: $D_{js}(a,b)=D_{js}(b,a)$.
+The Jensen-Shannon distance $D_{js}(a,b)$ between this two distributions is defined as:
 
 \begin{align*}
-	D_{KL}(p,q)=\sum_{i=1}^T p_i ln \frac{p_i}{q_i}
+	D_{js}(a,b)=\frac{1}{2}D_{KL}(a,\frac{a+b}{2})+\frac{1}{2}D_{KL}(b,\frac{a+b}{2})
 \end{align*}
 
-So $D_{js} \to 0$ indicates stronger similarities.
-Since $D_{js}$ does not satisfy the triangular inequality condition $D_{js}(a,c)\leq D_{js}(a,c)+D_{js}(b,c)$, the JSD is not considered to be a real metric.
+where $D_{KL}$ is the Kullback-Leibler divergence.
+Since $D_{js}$ does not satisfy the triangular inequality condition $D_{js}(a,c)\leq D_{js}(a,c)+D_{js}(b,c)$, the JSD is not considered to be a real distance metric.
 However, we can use the square root of JSD as a real distance metric \citep{endres_new_2003}.
-We will compare this metric with a set of other similarity measures recently used in the literature to measure the difference between word-topic distributions.
 
-\citep{roberts_navigating_2016}: They use the $L_1$ norm of the word-topic distributions to compare topics from different models.
+\citep{roberts_navigating_2016} use the $L_1$ norm of the word-topic distributions to compare topics from different models.
 The $L_1$ norm is the sum of the absolute value of the difference between two vectors.
@@
 \begin{align*}
-	L_1=\sum_v |\beta_{kvi}-\beta_{kvj}|
+	L_1=\sum_{i=1} |a_i-b_i|
 \end{align*}
 
-where $i$ and $j$ indicate different covariate levels.
-This measure has a range of $[0,2]$, where $ L_1 \rightarrow 0$ indicates strong similarities.
-They compare this measure with a cosine similarity metric, which is essentially the dot product rescaled by the $L_2$ norm of the vectors and is defined as
+his measure has a range of $[0,2]$, where $ L_1 \to 0$ indicates strong similarities.
+They compare this measure with a cosine similarity metric, which is essentially the dot product rescaled by the $L_2$ norm of the vectors and is defined as.
 
 \begin{align*}
-	\text{cos}(\theta)=\frac{\sum^d_{v=1}\beta_{kvi}\beta{kvj}}{\sqrt{\sum^d_{v=1}\beta_{kvi}^2}\sum^d_{v=1}\beta_{kvj}^2}
+	\text{cos}(\theta)=\frac{\sum_{i=1}a_i b_i}{\sqrt{\sum_{i=1}a_i^2}\sum_{i=1}b_i^2}
 \end{align*}
 
-Again, $i, j$ indicate different covariate levels. However, different to the above mentioned metrics the cosine similarity has a range of $[0,1]$ and $cos(\theta) \to 0$ indicate less similarity.
+However, different to the above mentioned metrics the cosine similarity has a range of $[0,1]$ and $cos(\theta) \to 0$ indicate less similarity.
 
@@
 
-\todo{check topics that are most different}
+\textcolor{red}{AUSWERTUNG}
 

### 2018-02-06 paper/R/04_Modelresults.Rmd
minor changes

@@
 
-ggsave(plot = p1, filename = "../figs/topic_proportion.png", device = "png",width = 8, height = 12,
-dpi = 600)
+#ggsave(plot = p1, filename = "../figs/topic_proportion.png", device = "png",width = 8, height = 12,
+#dpi = 600)
 ```
@@
   mutate(value = ifelse(freq_diff>=0, 1,0)) %>%
-  left_join(., topics.df, by = "topic")
+  left_join(., topics.df, by = "topic") %>%
+  left_join(., frequency %>% mutate(topic_name = topic) %>%
+              select(-topic),
+            by = "topic_name")
 ```
@@
 ```{r}
-p1 <- ggplot(freq, aes(reorder(topic_name, freq_diff), freq_diff,
+p2 <- ggplot(freq, aes(reorder(topic_name,frequency), freq_diff,
                  fill = factor(value))) +
@@
   coord_flip() +
-  theme(axis.text.x = element_text(size=8),
-          axis.text.y = element_text(size=11),
+  theme(axis.text.y = element_blank(),
+          #axis.text.y = element_text(size=11),
           axis.title = element_text(size=10)) +
@@
 
-p1
+p1 + p2
 
-ggsave(plot = p1, filename = "../figs/topic_proportion_diff.png", device = "png",width = 8, height = 12,
+ggsave(filename = "../figs/topic_proportion.png", device = "png",width = 12, height = 10,
 dpi = 600)
@@
 
-# ggsave(plot = p1, filename = "../figs/estimates_site.png", device = "png",width = 9, height = 5,
-# dpi = 600)
+ggsave(plot = p1, filename = "../figs/estimates_site.png", device = "png",width = 9, height = 7,
+dpi = 600)
 ```
@@
 
-# ggsave(plot = p1, filename = "../figs/estimates_month.png", device = "png",width = 9, height = 5,
-# dpi = 600)
+ggsave(plot = p1, filename = "../figs/estimates_month.png", device = "png",width = 9, height = 7,
+dpi = 600)
 ```

### 2018-02-08 paper/R/03_marektDescription.Rmd
change labels

@@
 col <- brewer.pal(6,"Dark2")
-source("func/functions.R")
 ```
@@
        site = ifelse(site=="welt.de","DIE WELT",site),
-       site = ifelse(site=="n-tv.de","n-tv.de",site))
+       site = ifelse(site=="n-tv.de","n-tv.de",site),
+       site = ifelse(site=="deutschlandfunk.de", "DLF", site))
 
+keepsite <- c("Tagesschau.de", "SPIEGEL ONLINE", "ZEIT ONLINE", 
+              "Bild.de", "DIE WELT", "FOCUS ONLINE")
 ```
@@
   ggplot(aes(date, views, color=site)) +
-  geom_line(show.legend = F) +
-  geom_text_repel(data = views[views$date==max(views$date), ],
-                  aes(date, views, label=site),
-                  size=2.8, show.legend = F, seed = 1) +
-  scale_x_date(limits = c(as.Date("2017-05-31"),as.Date("2018-02-15")),
+  geom_line() +
+  geom_text(data = views[views$date==max(views$date) &
+                                 views$site %in% keepsite , ],
+                  aes((date+3), views, label=site), hjust=0.1,
+                  size=2.5, show.legend = F, check_overlap = T) +
+  scale_x_date(limits = c(as.Date("2017-05-31"),as.Date("2018-02-16")),
                breaks = date_breaks("1 month"), 
@@
   theme(
-      #legend.position   = "none",
+      legend.position   = "right",
       legend.text       =  element_text(size=6),

### 2018-02-08 paper/doc/structure.tex
comments melissa

@@
 
-In Germany, the debate about the role of public media and their mission in a rapidly changing media world is a recurring theme.
+In Germany, the debate about the role of public media and their mission in a rapidly changing media world is a frequently discussed topic.
 By shifting media content to the Internet, the dual system, which has been shaping the German television and radio landscape since the introduction of private broadcasting in the early 1980s, is facing a radical change.
@@
 
-On the basis of these justifications, this paper examines whether public media offer different content than private providers.
+On the basis of these justifications, this paper examines whether imperfections in the market of online news exist.
+In other words, whether socially desired content that meets the (social) needs of society - and is therefore politically desirable - is not, or very poorly provided by the market.
 In order to examine this, the online news content of public media is compared with the supply of private news providers.
-
-We use a data set of German online news articles about domestic politics dated from 01.06.2017 to 31.12.2017\footnote{German federal elections took place on 24th of September 2017.} from six German content providers.
+More specifically, I use a data set of German online news articles about domestic politics dated from 01.06.2017 to 31.12.2017\footnote{German federal elections took place on 24th of September 2017.} from six German content providers.
+In the event that there is no market failure in terms of information provision (the prevalence of topics do not differ), the existence of public media could still be justified by the fact that socially relevant contents of private providers are systematically distorted and the existence of public offerings ensures the diversity of information and opinions transmitted.
+In order to examine this bias, I analyze how the topics are discussed differently in public and private news.
 
@@
 \begin{enumerate}
-	\item \textbf{Discovering Topics} Discover latent topics in the corpus using structural topic modeling (STM)\citep{roberts_model_2016} An extension of latent dirichlet allocation (LDA) \citep{blei_latent_2003}).
-The STM approach models (a) topics as multinomial distributions of words and (b) documents as multinomial distributions of topics, allowing to incorporate external variables that effect both (a) topical content and (b) topical prevalence.
-We will include the business model (public or private) as a control for both the topical content and the topical prevalence.
-Additional, we include the month an article was published as a control for the topical prevalence.
-To explore the results, we label each topic by looking at most frequent words and most representative articles across all news providers.
-(Section \ref{ch_model})
+	\item \textbf{Discovering Topics (Section \ref{ch_model})} To discover the latent topics in the corpus, the structural topic modeling (STM) developed by \citet{roberts_model_2016} is applied.
+The STM is an unsupervised machine learning approach that models topics as multinomial distributions of words and documents as multinomial distributions of topics, allowing to incorporate external variables that effect both, topical content and topical prevalence.
+I will include the business model (public or private) as a control for both the topical content and the topical prevalence.
+Additional, the month an article was published is included as a control for the topical prevalence.
+The result of the generative process of STM are the posterior distributions for topic prevalence and topical content, which can then be used to measure the similarity between private and public news providers in the further course of the paper: (1) $\beta$ is a $K$-by-$V$ matrix (where $K=$ number of topics and $V=$ vocabulary), where the entry $\beta_{kvc}$ can be interpreted as the probability of observing the $v$-th word in topic $k$ for the covariate level $c$.
+(2) $\theta$ is a $D$-by-$V$ matrix of the document-topic distributions, where the entry $\theta_{dk}$ can be interpreted as the proportion of words in document $d$ which arise from topic $k$, or rather as the probability that document $d$ deals about topic $k$.
 
-	\item \textbf{Measuring Similarity of news content} Different approaches to examine the similarities / differences of content between the news provider:
+	\item \textbf{Measuring Similarity of news content} Different approaches are used to examine similarities and/or differences of content between the news provider:
 	\begin{enumerate}
-		\item \textbf{Differences in topic prevalence:} As we allow prevalence of topics to evolve over time (by month) and vary across business models, we can use the posterior topic-probability of document $d$, to estimate the conditional expectation of topic prevalence $\theta_d$ for given document characteristics (lm on compositional data) \citep{roberts_model_2016}.
-		\begin{align*}
-			\theta_d=\alpha+\beta_1x_{site}+\beta_2x_{month}+\epsilon
-		\end{align*}
+		\item\label{item_1}\textbf{Differences in topic prevalence:} As I allow prevalence of topics to evolve over time (by month) and vary across business models, the posterior topic-probability $\theta_{dk}$ of document can be used to estimate the conditional expectation of topic prevalence for given document characteristics.
 
-		\item \textbf{Topic correlation} To get an idea of how topics are linked and framed differently across news wires, we find all edges between topics where they exhibit a positive correlation above 0.1 \citep{roberts_model_2016}.
+		\item\label{item_2} \textbf{Topic correlation} To get an idea of how topics are linked and framed differently across news wires, the correlation of the posterior probability of topics $\theta_{dk}$ is calculated.
 
-		\item \textbf{Differences in word-topic distributions} From the STM we get $\beta_{kv}$ - a $K$x$V$ matrix (where $K=$ number of topics and $V=$ vocabulary) of the whole corpus that contains the probability of seeing each word of the vocabulary $V$ within topic $k$ conditional on the business model (we get two different $\beta_{kv}$ for each topic $k$, as we have two specifications of the business model covariate: public and private).
-We then use each row (corresponding to each topic) to calculate the similarity of the word-topic distribution between the news provider using the square root of the Jensen-Shannon (JS) Divergence.
-We also compare this distance metric with three other measures of the similarity of distributions.
-
-		Previous topic modeling research try to measure the similarity between topics, comparing the word-topic-distribution between the topics (most of the research uses LDA without metadata, so the word-topic-distribution is the same within the whole corpus).
-cosine similarity \citep{he_detecting_2009}, \citep{ramage_labeled_2009}, Kullback-Leibler (KL) \citep{newman_distributed_2009}, \citep{wang_mining_2009} and the average Log Odds Ratio \citep{chaney_visualizing_2012} are frequently used metrics to compare word probability distributions.
-\citet{kim_topic_2011} compare six popular similarity metrics in terms of log likelihood of data, concluding that Jensen-Shannon Divergence (the symmetric variation of KL divergence) is best in terms of performance and generality.
+		\item\label{item_3} \textbf{Differences in word-topic distributions} As each row of $\beta_{kvc}$ corresponds to the word-distribution of a respective topic for the covariate level $c$, it can be used to calculate the similarity of the word-topic distribution between the news provider using established similarity measures.
 
@@
 \end{enumerate}
+
+Approaches \ref{item_1} and \ref{item_2} have been used in \citet{roberts_model_2016}, among others, to examine differences in the content of news providers.
+However, I extend the analysis by calculating the similarity of the word-topic distribution between the news provider, to identify which topics are discussed similar or differently (\ref{item_3}).
+In addition, this approach is applied to a new dataset covering recent political trends in Germany.
+
+The remaining course of the paper is as follows: In Section \ref{ch_onlinenews} I briefly discuss the characteristics of the market for online news in Germany.
+The data used to conduct the model is described in Section \ref{ch_data}.
+Section \ref{ch_model} explains the generative process of the structural topic model as well as the selected parameters to run the model.
+The results are the evaluated in Section \ref{ch_empirical}.
 
@@
 As a result, public broadcasting no longer only competes with private television and radio stations, but also enters the market for online news.
-In the following, we will briefly discuss the characteristics of the market for online news in Germany.
+In the following, the characteristics of the market for online news in Germany are briefly described.
 
@@
 The size and characteristics of the audience has a positive effect on the advertisers' willingness to pay, as advertisements are typically sold based on cost per viewer, often expressed in terms of the cost of reaching a thousand viewers (CPM).
-Advertising can also have an effect on the recipients, which can be both negative and positive, depending on the quality of the advertising.
-Depending on the strength of the indirect network effects, private publisher maximize their revenue by balancing the demand from advertisers and subscribers using different business models \citep{evans_economics_2008}.
+Advertising can also have an effect on the recipients, which can be either negative or positive, depending on the quality of the advertising.
+Based on the strength of the indirect network effects, private publishers maximize their revenue by balancing the demand from advertisers and subscribers using different business models \citep{evans_economics_2008}.
 Many traditional newspapers follow the subscription/advertising model, where the publisher charges both market sides: The audience pays a fee to obtain access to the content, and advertisers pay to obtain access to the viewers.
@@
 However, since the Internet has considerably simplified the possibilities for obtaining information and thus reduced the marginal utility of content, such a business model can only be efficient if the content is very exclusive.
-As a result, many publishers rely on a free-media model, in which the publishers do not charge viewers for access to the media at all, in order to attract as many eyeballs as possible to their platform, and thus exploit the indirect network effects on the advertising site.
+As a result, many publishers rely on a free-media model, in which the publishers do not charge viewers for access to the media at all, in order to attract as many eyeballs as possible to their platform, and thus, exploit the indirect network effects on the advertising site.
 In fact, most advertising-financed online magazines earn their gross margin from advertising \citep{evans_industrial_2005}.
@@
 
-The two-sided market structure of the private news markets results in news platforms striving to choose their content in such a way that its reach is as large as possible in order to maximize profits from advertising revenues.
-\citep{steiner_program_1952} concluded, that profit-maximizing media owners may choose to offer the same content, i.e.
+The two-sided market structure of the private news market results in news platforms striving to choose their content in such a way that its reach is as large as possible in order to maximize profits from advertising revenues.
+\citet{steiner_program_1952} concluded, that profit-maximizing media owners may choose to offer the same content, i.e.
 content aligned with the tastes of the majority.
@@
 On the other hand, advertising may also have a positive impact on the media, as it enables publishers to report independently of political parties.
-\citet{ellman_what_2009} found that advertising increases the intensity of competition for readers and therefore raises accuracy of media coverage.
+\citet{ellman_what_2009} analyze a theoretical framework of a two-sided market for newspaper, where readers value accuracy and advertisers value advert-receptive readers.
+They found that advertising increases the intensity of competition for readers and therefore raises accuracy of media coverage.
+However, in the monopolistic case, newspapers under-report news that sufficiently reduces advertiser profits.
 
@@
 
-However, given today's media landscape, the role of public media provider and its mandate is in discussion.
+However, given today's media landscape, the role of public media provider and its mandate is questioned.
 The basic justification for a public media offer can be roughly divided into two categories: On the one hand, possible market failure and on the other hand, ensuring diversity.
@@
 
-On the basis of these justifications, this paper examines whether imperfections in the market of online news exist.
-In other words, whether socially desired content that meets the (social) needs of society and is therefore politically desirable is not provided by the market.
-In order to examine this, the online news content of public media is compared with the supply of private news providers, by comparing the topic prevalence between them.
-In the event that there is no market failure in terms of information provision (the contents do not differ), the existence of public media could still be justified by the fact that socially relevant contents of private providers are systematically distorted and the existence of public offerings ensures the diversity of information and opinions transmitted.
-We try to examine this part by analyzing how the topics are discussed differently for public and private news provider.
-For this purpose, we calculate the divergence of the word probabilities of a topic.
+As stated above, this paper examines whether imperfections in the market of online news exist, by comparing the topic prevalence between public and private online news with the supply of private news providers.
+In the event that there is no market failure in terms of information provision, the existence of public media could still be justified by the fact that socially relevant contents of private providers are systematically distorted and the existence of public offerings ensures the diversity of information and opinions transmitted.
+In order to examine this bias, the divergence of word-topic probabilities is calculated to analyze how the topics are discussed differently.
 
-\subsection{Competitor analysis}
+% -----
+% Data
+% -----
+\section{Dataset and data preparation}\label{ch_data}
 
-The following analysis of the online news market includes the largest suppliers of online news.
 Figure \ref{fig_reach} shows the largest providers of online news in terms of daily pageviews.\footnote{The figure shows the estimated percentage of daily pageviews on the internet that occurred on a specific website.} It is striking that SPIEGEL ONLINE has the greatest reach over the entire course of time followed by Bild.de.
@@
 \begin{figure}[H]
-			\includegraphics[width=0.8\textwidth]{../figs/reach.png}
 	\caption{Percentage of daily pageviews}
+	\includegraphics[width=\textwidth]{../figs/reach.png}
 	\label{fig_reach}
@@
 
-Users can access a news website either directly or through an intermediary, such as search engines or social media.
-As the Figure \ref{fig_traffic} illustrates\footnote{The figure shows the percentage of total traffic by a source for the time period 18.12.2017-18.01.2017}, direct access\footnote{Direct traffic includes: Direct navigation (Someone types the website URL into a browser); Bookmarks (Clicks on a bookmark/favorite link in a browser); Email (Clicks on links in desktop email clients)} to a website is the main source of traffic for most news providers.
-In the case of Bild.de, the percentage is 85\%.
-Also n-tv.de (79\%), SPIEGEL ONLINE (76\%) and Tagesschau.de (75\%) get most of their traffic via the direct route.
-Other providers are more reliant on intermediaries, mainly search engines.
-FOCUS ONLINE, DLF and Handelsblatt.com, for example, obtain between 40\% and 45\% of its traffic via search engines.
-Thus, an important question is, which organic search keywords send traffic to a website.
-Figure \ref{fig_searchtraffic} displays the percentage of organic search referrals to a specific website that come from this keyword.\footnote{Percentage of organic search referrals in major search engines over the time span Jun-Dec 2017.} E.g., 0.78\% of all organic search referrals to Handelsblatt.com come from the keyword "handelsblatt".
-It is not surprising that the provider's name is the keyword that generates the majority of traffic for most of the news pages.
-However, different topics as well as names of other providers are hidden among the top 10 keywords.
-
-\begin{figure}[H]
-	\caption{Traffic Sources}
-	\begin{center}
-		\includegraphics[width=0.8\textwidth]{../figs/traffic_source.png}
-		\label{fig_traffic}
-	\end{center}
-\end{figure}
-
-\begin{figure}[H]
-	\caption{Search traffic \%}
-	\begin{center}
-		\includegraphics[width=0.8\textwidth]{../figs/search_traffic.png}
-		\label{fig_searchtraffic}
-	\end{center}
-\end{figure}
-
-Assuming that each search query is in itself a market where providers compete for traffic, the share of search queries for a keyword that has led visitors to a news page is the market share of that provider.
-In this context, figures \ref{fig_keywords1} and \ref{fig_keywords2} show the market share of providers for different keywords.\footnote{The figures show the percentage of searches for a keyword that sent traffic to a website in major search engines over the time span Jun-Dec 2017.} Nearly 15\% of all search queries for the keyword "Bundestagswahl 2017" (federal elections 2017) were forwarded to DIE WELT.
-FOCUS ONLINE, faz.net and SPIEGEL ONLINE obtained a market share of 7\% - 8\%.
-For the keyword "Groko" (grand coalition between CDU/CSU and SPD), SPIEGEL ONLINE was able to gain the largest market share (17\%) in the past six months, followed by DIE WELT (\%10), FOCUS ONLINE (8\%) and Bild.de (7.5\%).
-Figure \ref{fig_keywords2} shows the market share of news pages for the keyword search for a specific party.
-
-Contrary to figure \ref{fig_keywords1} , the x-axes in figure \ref{fig_keywords2} are scaled equally to show not only the market share of news sites for a specific party-keyword, but also for which party this provider has the largest market share.
-For example, we can see that the market share of sueddeutsche.de is largest for the keyword "Die Grünen".
-However, the biggest market share among the listed news providers for this keyword has Zeit.de.
-The largest market share for the keyword "AfD" can be found at DIE WELT, followed by SPIEGEL ONLINE.
-The proportion of public news providers is comparatively low for all keywords.
-
-\begin{figure}[H]
-	\begin{center}
-			\includegraphics[width=.8\textwidth]{../figs/keywords1.png}
-			\caption{Keyword market share for policy topics / general}
-			\label{fig_keywords1}
-	\end{center}
-\end{figure}
-
-\begin{figure}[H]
-	\begin{center}
-			\includegraphics[width=.8\textwidth]{../figs/keywords2.png}
-			\caption{Keyword market share for party-keywords}
-			\label{fig_keywords2}
-	\end{center}
-\end{figure}
-
-% -----
-% Data
-% -----
-\subsection{Dataset}\label{ch_data}
-
-We conduct our estimation on a sample of 9393 online news articles from six news provider about domestic politics\footnote{Bild.de, DIE WELT, FOCUS ONLINE, SPIEGEL ONLINE, ZEIT ONLINE, Tagesschau.de}, of which only Tagesschau.de belongs to the group of public provider.
+I conduct the estimation on a sample of 9,393 online news articles from six news provider about domestic politics\footnote{Bild.de, DIE WELT, FOCUS ONLINE, SPIEGEL ONLINE, ZEIT ONLINE, Tagesschau.de}, of which only Tagesschau.de belongs to the group of public provider.
 The reason for this is that the content structure of Tagesschau.de is most similar to that of the private providers.
-ZDF.de offers predominantly video content and DLF website mainly offers audio content in the form of interviews, which makes it hard to include in the model0 However, as we only include some of the above mentioned private suppliers, the proportions between private and public market participants are maintained, thus minimizing possible bias.
-The articles are dated from 01.06.2017 to 31.12.2017.\footnote{German federal elections took place on 24th of September 2017.} We first extract all online articles using the the Webhose.io API.\footnote{For more information see https://docs.webhose.io/v1.0/docs/getting-started.
-The scraping code was written in Python and can be made available on request.} We then filtered all articles from the section "domestic policy" by checking the URL structure.
+ZDF.de offers predominantly video content and DLF website mainly offers audio content in the form of interviews, which makes it hard to include it in the model.
+However, as only a part of the private suppliers are included to maintain the proportions between private and public market participants are maintained, thus minimizing possible bias.
+The articles are dated from 01.06.2017 to 31.12.2017.\footnote{German federal elections took place on 24th of September 2017.} I first extract all online articles using the the Webhose.io API.\footnote{For more information see https://docs.webhose.io/v1.0/docs/getting-started.
+The scraping code was written in Python and can be made available on request.} Then all articles from the section "domestic policy" are filtered by checking the URL structure.
 
@@
 Any useful representation of text will throw away some information, the trick is to include the relevant information for our needs, and exclude the extraneous information.
-To use text as data and reduce the dimensionality, a common strategy is to pre-process the text by imposing some preliminary restrictions (stop-word removal, tokenization) based on the nature of the data (twitter text, newspaper articles, speeches, etc.) to reduce the number of language elements to consider \citep{gentzkow_text_2017}.
+A common strategy to use text as data and reduce the dimensionality, is to pre-process the text by imposing some preliminary restrictions (stop-word removal, tokenization) based on the nature of the data (twitter text, newspaper articles, speeches, etc.) to reduce the number of language elements \citep{gentzkow_text_2017}.
 Intuitively the term frequency (tf) of a word is a measure of how important that word may be.
@@
 
-We use the structural topic model (STM) developed by \citet{roberts_model_2016} that allows us to incorporate document specific covariates (e.g.
+The structural topic model (STM) developed by \citet{roberts_model_2016} allows to incorporate document specific covariates (e.g.
 the author or date of a document).
@@
 \citet{pritchard_inference_2000} introduced the same model in genetics for factorizing gene expression as a function of latent populations.} Topic models formalize the idea that documents are formed by hidden variables (topics) that generate correlations among observed terms.
-Since its introduction into text analysis, LDA has become hugely popular and especially useful in political science.\footnote{see \citet{blei_probabilistic_2012}, \citet{grimmer_text_2013} and \citet{wiedmann_text_2016} for an overview in social science and \citet{gentzkow_text_2017} give an overview of text mining applications in economics.} \citet{wiedmann_text_2016} use topic model methods in on large amounts of news articles from two german newspapers published between 1959 and 2011, to reveal how democratic demarcation was performed in Germany over the past six decades.
+Since its introduction into text analysis, LDA has become hugely popular and especially useful in political science.\footnote{see \citet{blei_probabilistic_2012}, \citet{grimmer_text_2013} and \citet{wiedmann_text_2016} for an overview in social science and \citet{gentzkow_text_2017} give an overview of text mining applications in economics.} \citet{wiedmann_text_2016} uses topic model methods on large amounts of news articles from two german newspapers published between 1959 and 2011, to reveal how democratic demarcation was performed in Germany over the past six decades.
 \citet{paul_cross-collection_2017} compares editorial differences between media sources, using cross-collection latent Dirichlet allocation (ccLDA), an LDA-based approach that incorporates differences in document metadata.
-They use a dataset of 623 news articles from August 2008 from two American media outlets - msnbc.com and foxnews.com - to analyse how they discuss topics differently.
-Comparing the top words of the word-topic distribution, they find some content differences between the two.
+They use a dataset of 623 news articles from August 2008 from two American media outlets - msnbc.com and foxnews.com - to compare how they discuss topics.
+Reviewing the top words of the word-topic distribution, they find some content differences between the two.
 
-STM has been applied to multiple academic fields: \citet{roberts_structural_2014} uses STM to analyse open-ended responses from surveys and experiments, \citet{farrell_corporate_2016} applies the model to scientific texts on climate change, revealing links between corporate funding and the framing of scientific studies and \citet{mishler_using_2015} shows that "STM can be used to detect significant events such as the downing of Malaysia Air Flight 17" when applied to twitter data.
+STM has been applied to multiple academic fields: \citet{roberts_structural_2014} uses STM to analyse open-ended responses from surveys and experiments, \citet{farrell_corporate_2016} applies the model to scientific texts on climate change, revealing links between corporate funding and the framing of scientific studies.
+\citet{mishler_using_2015} show that "STM can be used to detect significant events such as the downing of Malaysia Air Flight 17" when applied to twitter data.
 Another study shows how STM can be used to explore the main international development topics of countries’ annual statements in the UN General Debate and examine the country-specific drivers of international development rhetoric \citep{baturo_what_2017}.
-\citet{mueller_reading_2016} uses newspaper text to predict armed conflicts in different regions.
+\citet{mueller_reading_2016} use newspaper text to predict armed conflicts in different regions.
 They use the estimated topic shares in linear fixed effects regression to forecast conflict out-of-sample.
-In order to demonstrate multi-modality of topic-models\footnote{That is, the solution of topic-models can be sensitive to the starting values as the function to be optimized has multiple modes.} can be mitigated, \citet{roberts_navigating_2016} use STM to examine the role of partisanship in topical coverage using a corpus of 13,246 posts that were written for 6 political blogs during the course of the 2008 U.S.
+\citet{roberts_navigating_2016} use STM to examine the role of partisanship in topical coverage using a corpus of 13,246 posts that were written for 6 political blogs during the course of the 2008 U.S.
 presidential election.
@@
 They also use different measures of distance between the topic-word distributions of the same topic within different models.
-In section \ref{ch_similarity}, we apply a similar approach to measure similarity between the same topic for different covariate levels.
+In section \ref{ch_similarity} a similar approach is applied to measure similarity between the same topic for different covariate levels.
 
@@
 
-As mentioned above, the STM allows to incorporate observed document metadata which is able to affect either topical prevalence and topical content.
+As mentioned above, the STM allows to incorporate observed document metadata which is able to affect both topical prevalence and topical content.
 The following description of the generative model - the process of filling a word-position in a document - of the STM is based on \citet{roberts_structural_2013} and \citet{roberts_stm:_2016}.
@@
 
-\begin{align*}
-	\boldsymbol{\theta}_d|\boldsymbol{x}_{d\gamma},\boldsymbol{\Sigma} \sim \textrm{LogisticNormal}(\mu = \boldsymbol{x}_{d\gamma}\boldsymbol{\Sigma})
-\end{align*}
+\begin{equation}
+	\boldsymbol{\theta}_d|\boldsymbol{x}_{d\gamma},\boldsymbol{\Sigma} \sim \textrm{LogisticNormal}(\mu = \boldsymbol{x}_{d\gamma}\boldsymbol{\Sigma}).
+\end{equation}
 
@@
 
-According to $\theta$, a specific topic $z_{dn}$ is assigned for the $n^{th}$ word-position in the document through the process
+According to $\theta$, a specific topic $z_{dn}$ is assigned for the $n^{th}$ word-position in the document through the process:
 
-\begin{align*}
+\begin{equation}
 	z_{dn}|\boldsymbol{\theta}_d \sim \textrm{Multinomial}(\boldsymbol{\theta}_d).
-\end{align*}
+\end{equation}
 
@@
 
-\begin{align*}
+\begin{equation}
 	w_{dn}|z_{dn},\beta_{dkv} \sim \textrm{Multinomial}(\beta_{dk1},...,\beta_{dkV}),
-\end{align*}
+\end{equation}
 
@@
 Similarly, $\kappa^{(c)}$ is a $A$-by-$V$ matrix, indicating the importance of the term $v$ given the covariate level $c$ regardless of the topic.
-Finally, $\kappa^{(i)}$ is a $A$-by-$K$-by-$V$ matrix, collecting the covariate-topic effects.
+Finally, $\kappa^{(i)}$ is a $A$-by-$K$-by-$V$ matrix, collecting the covariate-topic effects:
 
-\begin{align*}
-	\beta_{dkv}|z_{dn}=\frac{\textrm{exp}(m_v+\kappa^{(t)}_{kv},\kappa^{(c)}_{y_dv}+\kappa^{(i)}_{y_dkv})}{\sum_v \textrm{exp}(m_v+\kappa^{(t)}_{kv},\kappa^{(c)}_{y_dv}+\kappa^{(i)}_{y_dkv})}
-\end{align*}
+\begin{equation}
+	\beta_{dkv}|z_{dn}=\frac{\textrm{exp}(m_v+\kappa^{(t)}_{kv},\kappa^{(c)}_{y_dv}+\kappa^{(i)}_{y_dkv})}{\sum_v \textrm{exp}(m_v+\kappa^{(t)}_{kv},\kappa^{(c)}_{y_dv}+\kappa^{(i)}_{y_dkv})}.
+\end{equation}
 
@@
 (2) $\theta$ is a $D$-by-$V$ matrix of the document-topic distributions, where the entry $\theta_{dk}$ can be interpreted as the proportion of words in document $d$ which arise from topic $k$, or rather as the probability that document $d$ deals about topic $k$.
-We will use these probability distributions to compare the content of public and private news provider in Section \ref{ch_empirical}.
+These probability distributions are used to compare the content of public and private news providers in section \ref{ch_empirical}.
 
@@
 Inference of mixed-membership models, such as the one applied in this paper, has been a thread of research in applied statistics in the past few years \citep{blei_latent_2003} \citep{erosheva_mixed-membership_2004} \citep{braun_variational_2010}.
-Topic models are usually imprecise as the function we are optimizing has multiple modes, such that the model results can be sensitive to the starting values.
+Topic models are usually imprecise as the function to be optimized has multiple modes, such that the model results can be sensitive to the starting values.
 Since an ex ante valuation of a model is hardly possible, I compute a variety of different models and compare their posterior probability.
-This enables me to check how substantively different results are for different model solution \citep{roberts_navigating_2016}.
+This enables me to check how results vary for different model solution \citep{roberts_navigating_2016}.
 I then cross-checked some subset of assigned topic distributions to evaluate whether the estimates align with the concept of interest \citep{gentzkow_text_2017}.
-I apply these manual audits together with numeric optimization based on the topic coherence measure suggested by \citet{mimno_optimizing_2011}.
+These manual audits are applied together with numeric optimization based on the topic coherence measure suggested by \citet{mimno_optimizing_2011}.
 
 This process revealed that a model with 40 topics best reflects the structure in the corpus.
-Furthermore, we use the ownership of the news provider of each article (public or private) and the month it was published as covariates in the topic prevalence.
+Furthermore, the ownership of the news provider of each article (public or private) and the month it was published are used as covariates in the topic prevalence.
 In other words, the probability distribution of topics depends on the business-model as well as on the month the article was published.
-We also include ownership as a covariate affecting topical content to estimate how topics are discussed in different ways by different news agencies.
+The ownership is also included as a covariate affecting topical content, following the assumption that the same topic is discussed in different ways in private and public media respectively.
 To address problems due to non-convexity, we rely on the spectral initialization approach advocated by \citet{roberts_navigating_2016}.
@@
 
-In this section I summarize the results of the STM and apply different measures to analyze the content differences between public and private ownership.
-We use various approaches to investigate the differences between news provider content: (1) To address the question whether market imperfections exist in that sense, that some topics are not covered by private but by public news provider, I use the document-topic probability $\theta$, to estimate the conditional expectation of topic prevalence for given document characteristics.
+This section summarizes the results of the STM.
+Subsequently different measures to analyze the content differences between public and private ownership are applied according to the following approaches: (1) To address the question whether market imperfections exist in that sense, that some topics are not covered by private but by public news provider, I use the document-topic probability $\theta$, to estimate the conditional expectation of topic prevalence for given document characteristics.
 (2) Next, I find all edges between topics where they exhibit a positive correlation of $\theta$ above 0.1 to examine how topics are correlated differently for different covariate levels, indicating how topics are connected and framed differently between private and public media.
 Approaches (1) and (2) have been used in \citep{roberts_model_2016}.
-However, we extend the analysis by (3) calculating the similarity of the word-topic distribution $\beta$ between the news provider using different distance measures, to identify which topics are discussed similar or differently.
-This process also helps us to understand whether the supply of public media
+However, we extend the analysis by (3) calculating the similarity of the word-topic distribution $\beta$ between the news provider using various distance measures, to identify which topics are discussed similar or differently.
 
@@
 		\includegraphics[width=\textwidth,keepaspectratio]{../figs/topic_proportion.png}
-		\caption{Expected topic proportions}
 		\label{fig_topic_proportion}
@@
 \subsection{Differences in topic prevalence}
-Since we included news source as a covariate in estimating topical prevalence part within the model, we can estimate the frequency a topic is discussed within a news corpus \citep{roberts_model_2016}.
-We estimate the conditional expectation of topic prevalence for given document characteristics.
-More specifically, we estimate a linear model, where the documents are observations, the dependent variable is the posterior probability of a topic and the covariates are the metadata of documents (see equation \ref{eq_1}).
+Since news source is included as a covariate in estimating topical prevalence part within the model, the frequency a topic is discussed within a news corpus can be calculated \citep{roberts_model_2016}.
+I estimate the conditional expectation of topic prevalence for given document characteristics.
+More specifically, I estimate a linear model, where the documents are observations, the dependent variable is the posterior probability of a topic and the covariates are the metadata of documents (see equation \ref{eq_1}).
 The stm-package provides a function that uses the method of composition to incorporate uncertainty in the dependent variable, drawing a set of topic proportions from the variational posterior repeated times and compute the coefficients as the average over all results \citep{roberts_stm:_2016}.
 
-\begin{align}\label{eq_1}
+\begin{equation}\label{eq_1}
 	\theta_d=\alpha+\beta_1x_{site}+\beta_2x_{month}+\epsilon
-\end{align}
+\end{equation}
 
-Figure \ref{fig_estimateEffects} display the regression results for private vs.
+Figure \ref{fig_estimateEffects} displays the regression results for private vs.
 public.
-As we also control for the month, the intercept gives the mean of private news suppliers in June 2017.\footnote{Table of regression results can be found in appendix.}
+As the month an articles was published is included in the regression, the intercept indicates the mean of private news suppliers in June 2017.\footnote{Table of regression results can be found in appendix.}
 
@@
 
-Next, we examine how topics are correlated differently for different news wires, indicating how topics are connected and framed differently in each newswire.
-In Figure \ref{fig_topic_correlations}, we find all edges between topics where they exhibit a positive correlation above 0.1 \citep{roberts_model_2016}.
+Next, the topic correlation is calculated, indicating how topics are connected and framed in public and private media.
+In Figure \ref{fig_topic_correlations}, indicates all edges between topics where they exhibit a positive correlation above 0.1 \citep{roberts_model_2016}.
 
@@
 
+Previous topic modeling research try to measure the similarity between topics, comparing the word-topic-distribution between the topics (most of the research uses LDA without metadata, so the word-topic-distribution is the same within the whole corpus).
+cosine similarity \citep{he_detecting_2009}, \citep{ramage_labeled_2009}, Kullback-Leibler (KL) \citep{newman_distributed_2009}, \citep{wang_mining_2009} and the average Log Odds Ratio \citep{chaney_visualizing_2012} are frequently used metrics to compare word probability distributions.
+\citet{kim_topic_2011} compare six popular similarity metrics in terms of log likelihood of data, concluding that Jensen-Shannon Divergence (the symmetric variation of KL divergence) is best in terms of performance and generality.
+
 Since a topic is a multinomial distribution over the vocabulary, where $\beta_{kvi}$ indicates the probability of observing word $v$ in topic $k$ for covariate level $i$, we can analyze how similar a topic $k$ is for different levels of covariates.
@@
 I will compare this metric with a set of other similarity measures recently used in the literature to measure the difference between word-topic distributions: The Kullback-Leibler (KL) divergence (\citet{newman_distributed_2009}, \citet{wang_mining_2009}), the cosine similarity (\citet{he_detecting_2009}, \citet{ramage_labeled_2009}) and the difference of the $L1$ norm of the vectors \citep{roberts_navigating_2016}.
-I will briefly explain these measures before I proceed to the results.
+Before the results are presented, I will briefly explain these measures before I proceed to the results.
 
-Essentially, what we're looking at with the KL divergence is the expectation of the log difference between probabilities $a$ and $b$. It can be defined as:
+Essentially, the KL divergence is the expectation of the log difference between probabilities $a$ and $b$. It can be defined as:
 
 \begin{align*}
-	D_{KL}(a,b)=\sum_{i=1}^T a_i \text{ln} \frac{a_i}{b_i}
+	D_{KL}(a,b)=\sum_{i=1}^T a_i \text{ln} \frac{a_i}{b_i},
 \end{align*}
 
-So $D_{kl} \to 0$ indicates stronger similarities. However, since the KL divergence is not symmetric, it cannot be used to measure the distance between two distributions, but as a divergence measure.
+where $D_{kl} \to 0$ indicates stronger similarities.
+However, since the KL divergence is not symmetric, it cannot be used to measure the distance between two distributions, but as a divergence measure.
 
@@
 It is also symmetric: $D_{js}(a,b)=D_{js}(b,a)$.
-The Jensen-Shannon distance $D_{js}(a,b)$ between this two distributions is defined as:
+The Jensen-Shannon distance $D_{js}(a,b)$ between the two distributions is defined as:
 
@@
 
-\citep{roberts_navigating_2016} use the $L_1$ norm of the word-topic distributions to compare topics from different models.
+\citet{roberts_navigating_2016} use the $L_1$ norm of the word-topic distributions to compare topics from different models.
 The $L_1$ norm is the sum of the absolute value of the difference between two vectors.
@@
 
-his measure has a range of $[0,2]$, where $ L_1 \to 0$ indicates strong similarities.
-They compare this measure with a cosine similarity metric, which is essentially the dot product rescaled by the $L_2$ norm of the vectors and is defined as.
+this measure has a range of $[0,2]$, where $ L_1 \to 0$ indicates strong similarities.
+\citet{roberts_navigating_2016} compare this measure with a cosine similarity metric, which is essentially the dot product rescaled by the $L_2$ norm of the vectors and is defined as.
 
@@
 	\begin{center}
-		\includegraphics[width=0.8\textwidth,keepaspectratio]{../figs/distance}
 		\caption{Similarity measures of word-topic probabilities}
+		\includegraphics[width=\textwidth,keepaspectratio]{../figs/distance}
 		\label{fig_distance}

### 2018-02-08 paper/R/02_cleanAndCombine.Rmd
delete articles about DB

@@
   # remove articles about the weater
-  filter(!grepl("wetter", url))
+  filter(!grepl("wetter", url)) %>%
+  filter(!grepl("Deutsche Bahn", text) | site!="Tagesschau.de")
 ```
@@
 btw <- btw %>% 
-  mutate(ownership = ifelse(site == "Tagesschau.de", "public", "private"))
+  #mutate(ownership = ifelse(site == "Tagesschau.de", "public", "private")) %>%
+  filter(!grepl("Deutsche Bahn", text) | site!="Tagesschau.de")
 ```
@@
 ### without stemming
-processed1 <- textProcessor(btw$text_cleaned1, metadata = btw[,c("ownership","text_cleaned1","month")],
+processed <- textProcessor(btw$text_cleaned1, metadata = btw[,c("ownership","text_cleaned1","month")],
                            wordLengths = c(2,Inf),
@@
                            stem = F)
-out_ownership <- prepDocuments(processed1$documents, processed1$vocab, processed1$meta)
-out_ownership$meta$ownership <- as.factor(out_ownership$meta$ownership)
+out <- prepDocuments(processed$documents, processed$vocab, processed$meta)
+out$meta$ownership <- as.factor(out$meta$ownership)
 ###
@@
 
-save(btw, out_ownership, file="../output/btw_comb_ownership.Rda")
+save(btw, out, file="../output/btw_comb.Rda")
 ```

### 2018-02-08 paper/R/02_cleanAndCombine.Rmd
more filtering

@@
   filter(!grepl("wetter", url)) %>%
-  filter(!grepl("Deutsche Bahn", text) | site!="Tagesschau.de")
+  filter(!grepl("sturm", url) |
+           site != "Tagesschau.de") %>%
+  filter(!grepl("Deutsche Bahn", text) | 
+           site!="Tagesschau.de") %>%
+  filter(!grepl("bahnstrecke", text) | 
+           site!="Tagesschau.de")
 ```
@@
 btw <- btw %>% 
-  #mutate(ownership = ifelse(site == "Tagesschau.de", "public", "private")) %>%
-  filter(!grepl("Deutsche Bahn", text) | site!="Tagesschau.de")
+  #mutate(ownership = ifelse(site == "Tagesschau.de", "public", "private"))
+  filter(!grepl("sturm", url) |
+           site != "Tagesschau.de") %>%
+  filter(!grepl("Deutsche Bahn", text) | 
+           site!="Tagesschau.de") %>%
+  filter(!grepl("bahnstrecke", text) | 
+           site!="Tagesschau.de")
 ```

### 2018-02-08 paper/R/04_Modelresults.Rmd
more filtering

@@
 #load("../output/btw_combined.Rda")
-load("../output/btw_comb_ownership.Rda")
+load("../output/btw_comb.Rda")
 ```
@@
 ```{r caching, echo = FALSE}
-#load("../output/models/STM_stemmed2 40 .Rda")
 load("../output/models/STM_ownership 40 .Rda")
-out <- out_ownership
 ```
@@
 ```{r}
-sagelabs$cov.betas[[2]]$problabels[,1:6]
+sagelabs$cov.betas[[2]]$problabels[,1:5]
 ```
@@
                    4, "Diesel scandal", 5, "A.Merkel, glyphosat scandal", 6, "Seehover vs. Söder", 
-                   7, "political trends after the election", 8, "Merkel vs.Schulz", 9, "Trends in electoral districts", 
-                   10, "Steinmeier, Federal President", 11, "G.Schröder & IT themes (Data policy, Wifi, Telekom)", 
-                   12, "Federal Election trends", 13, "Climate policy", 14, "G20 Hamburg", 
-                   15, "error (text processing failure)", 16, "Federal budget statistics", 
-                   17, "Reports on individuals (Berlin)", 18, "Family reunion refugees", 
-                   19, "Polls federal election", 20, "AfD, Weidel in social media", 
+                   7, "political trends after the election", 8, "Merkel vs.Schulz", 
+                   9, "Trends in electoral districts", 10, "Steinmeier, Federal President", 
+                   11, "G.Schröder & IT themes (Data policy, Wifi, Telekom)", 
+                   12, "Federal Election trends", 13, "Climate policy, Die Grünen", 14, "G20 Hamburg", 
+                   15, "error (text processing failure)", 16, "Police academy (Berlin), AfD", 
+                   17, "Federal budget statistics", 18, "Family reunion refugees", 
+                   19, "Polls federal election", 20, "AfD in social media", 
                    21, "Women empowerment, M.Schwesig (SPD)", 22, "elections in Niedersachsen", 
-                   23, "Court sentences, NSU trial", 24, "election capaigns & political talkshows", 
+                   23, "Court sentences, NSU trial", 24, "election campaigns & political talkshows", 
                    25, "German armed forces", 26, "Issues in the Bundestag", 27, "C.Lindner FDP", 
-                   28, "Turkey, Russia", 29, "railway problems (DBahn)", 30, "H.Kohl obituary", 
-                   31, "AfD Gauland, Höcke", 32, "Asylum claims and deportation", 33, "EU policies", 
-                   34, "DIE LINKE", 35, "SPD", 36, "Islam and antisemitism in GER", 37, "AfD in parliament", 
-                   38, "Terror attacks (GER)  & police reports", 39, "Church", 40, "RAF"), ncol=2, byrow=T)
+                   28, "Turkey, Russia", 29, "A.Merkel in east GER", 30, "H.Kohl obituary", 
+                   31, "AfD (Petri, Gauland, Höcke)", 32, "Asylum claims and deportation", 
+                   33, "EU policies", 34, "DIE LINKE", 35, "SPD", 36, "Islam and antisemitism in GER", 
+                   37, "AfD in parliament", 38, "Church", 39, "Terror attacks (GER)  & police reports", 
+                   40, "DHL package attack (Potsdam)"), ncol=2, byrow=T)
 
@@
   group_by(document) %>%
-  mutate(therank = rank(-gamma, ties.method = "random")) %>%
+  mutate(therank = rank(-gamma)) %>%
   filter(therank == 1) %>%
@@
   mutate(document = articleID) %>%
-  inner_join(.,top_topics, by="document") %>%
+  merge(.,top_topics, by="document") %>%
   ## Combine with Topic label
-  left_join(., topics.df, by="topic") %>%
+  merge(., topics.df, by="topic") %>%
   mutate(allocation = 1) 
@@
 ```{r}
-btw.2 %>% filter(topic==11) %>% select(title, gamma, url) %>%
+btw.2 %>% filter(topic==17) %>% select(title, gamma, site) %>%
+  arrange(desc(gamma)) %>%
   htmlTable::htmlTable(align="l")
@@
 effect <- estimateEffect(c(1:40) ~ownership+s(month), stmOut, 
-                         metadata = out_ownership$meta, uncertainty = "None")
+                         metadata = out$meta, uncertainty = "None")
 #save(out_ownership,stmOut, effect, file = "stm_newsdata.RData")
@@
 p1 <- df %>%
-  filter(corr>0.1 & corr < 1) %>%
+  filter(corr>0.05 & corr < 1) %>%
   ggplot(aes(reorder(topic_name1,topic1), topic_name, 
@@
 ```
+
+Take a closer look to those topics that are discussed most different.
+
+```{r}
+plotQuote(c(paste(sagelabs$cov.betas[[1]]$problabels[29,], collapse="\n"),
+            paste(sagelabs$cov.betas[[2]]$problabels[29,], collapse="\n")))
+```
+
+```{r}
+btw.2 %>%
+  filter(grepl("sturm", url) &
+           site == "Tagesschau.de") %>%
+  select(title, site)
+```

### 2018-02-11 paper/R/04_Modelresults.Rmd
30 topics

@@
 ```{r caching, echo = FALSE}
-load("../output/models/STM_ownership 40 .Rda")
+load("../output/models/STM_ownership 30 .Rda")
+k <- stmOut$settings$dim$K
 ```
@@
 ```{r}
-sagelabs$cov.betas[[2]]$problabels[,1:5]
+sagelabs$cov.betas[[1]]$problabels[,1:5]
 ```
@@
 ```{r}
-topics <- matrix(c(1, "Great coalition", 2, "A.Merkel, CSU, Guttenberg", 3, "Jamaica coalition", 
-                   4, "Diesel scandal", 5, "A.Merkel, glyphosat scandal", 6, "Seehover vs. Söder", 
-                   7, "political trends after the election", 8, "Merkel vs.Schulz", 
+topics <- matrix(c(1, "Great coalition", 2, "A.Merkel, CSU, Guttenberg", 3, "Coalition talks (Jamaica, Niedersachsen)", 
+                   4, "Diesel scandal", 5, "A.Merkel, glyphosat scandal", 6, "DIE LINKE", 
+                   7, "Islam and antisemitism in GER", 8, "Merkel vs.Schulz", 
                    9, "Trends in electoral districts", 10, "Steinmeier, Federal President", 
                    11, "G.Schröder & IT themes (Data policy, Wifi, Telekom)", 
-                   12, "Federal Election trends", 13, "Climate policy, Die Grünen", 14, "G20 Hamburg", 
-                   15, "error (text processing failure)", 16, "Police academy (Berlin), AfD", 
-                   17, "Federal budget statistics", 18, "Family reunion refugees", 
+                   12, "Federal Election trends", 13, "EU policies", 14, "G20 Hamburg", 
+                   15, "error (text processing failure)", 16, "Refugees, asylum claims", 
+                   17, "Budget statistics, social welfare", 18, "Jamaica Coalition talks", 
                    19, "Polls federal election", 20, "AfD in social media", 
-                   21, "Women empowerment, M.Schwesig (SPD)", 22, "elections in Niedersachsen", 
-                   23, "Court sentences, NSU trial", 24, "election campaigns & political talkshows", 
+                   21, "Women empowerment, M.Schwesig (SPD)", 22, "AfD (Petri, Gauland, Höcke)", 
+                   23, "Terror attack Berlin (Amri)", 24, "election campaigns & political talkshows", 
                    25, "German armed forces", 26, "Issues in the Bundestag", 27, "C.Lindner FDP", 
-                   28, "Turkey, Russia", 29, "A.Merkel in east GER", 30, "H.Kohl obituary", 
-                   31, "AfD (Petri, Gauland, Höcke)", 32, "Asylum claims and deportation", 
-                   33, "EU policies", 34, "DIE LINKE", 35, "SPD", 36, "Islam and antisemitism in GER", 
-                   37, "AfD in parliament", 38, "Church", 39, "Terror attacks (GER)  & police reports", 
-                   40, "DHL package attack (Potsdam)"), ncol=2, byrow=T)
+                   28, "Turkey, Russia", 29, "Terror attacks (GER)  & police reports", 30, "H.Kohl obituary"), ncol=2, byrow=T)
+
+# topics <- matrix(c(1, "Great coalition", 2, "A.Merkel, CSU, Guttenberg", 3, "Jamaica coalition", 
+#                    4, "Diesel scandal", 5, "A.Merkel, glyphosat scandal", 6, "Seehover vs. Söder", 
+#                    7, "political trends after the election", 8, "Merkel vs.Schulz", 
+#                    9, "Trends in electoral districts", 10, "Steinmeier, Federal President", 
+#                    11, "G.Schröder & IT themes (Data policy, Wifi, Telekom)", 
+#                    12, "Federal Election trends", 13, "Climate policy, Die Grünen", 14, "G20 Hamburg", 
+#                    15, "error (text processing failure)", 16, "Police academy (Berlin), AfD", 
+#                    17, "Federal budget statistics", 18, "Family reunion refugees", 
+#                    19, "Polls federal election", 20, "AfD in social media", 
+#                    21, "Women empowerment, M.Schwesig (SPD)", 22, "elections in Niedersachsen", 
+#                    23, "Court sentences, NSU trial", 24, "election campaigns & political talkshows", 
+#                    25, "German armed forces", 26, "Issues in the Bundestag", 27, "C.Lindner FDP", 
+#                    28, "Turkey, Russia", 29, "A.Merkel in east GER", 30, "H.Kohl obituary", 
+#                    31, "AfD (Petri, Gauland, Höcke)", 32, "Asylum claims and deportation", 
+#                    33, "EU policies", 34, "DIE LINKE", 35, "SPD", 36, "Islam and antisemitism in GER", 
+#                    37, "AfD in parliament", 38, "Church", 39, "Terror attacks (GER)  & police reports", 
+#                    40, "DHL package attack (Potsdam)"), ncol=2, byrow=T)
 
@@
   transmute(topic_name = paste(V1, V2, sep=": "),
-         topic = 1:40) 
+         topic = 1:k) 
 ```
@@
 
-for(i in 2:40) {
+for(i in 2:k) {
   freq1 <- tapply(stmOut$theta[,i], stmOut$settings$covariates$betaindex, mean)
@@
 
-ggsave(filename = "../figs/topic_proportion.png", device = "png",width = 12, height = 10,
-dpi = 600)
+# ggsave(filename = "../figs/topic_proportion.png", device = "png",width = 12, height = 10,
+# dpi = 600)
 ```
@@
 ```{r}
-# effect <- estimateEffect(c(1:40) ~site+s(month), stmOut, 
-#                          metadata = out$meta, uncertainty = "None")
-
-effect <- estimateEffect(c(1:40) ~ownership+s(month), stmOut, 
+effect <- estimateEffect(c(1:k) ~ownership+s(month), stmOut, 
                          metadata = out$meta, uncertainty = "None")
@@
 
-ggsave(plot = p1, filename = "../figs/estimates_site.png", device = "png",width = 9, height = 7,
-dpi = 600)
+# ggsave(plot = p1, filename = "../figs/estimates_site.png", device = "png",width = 9, height = 7,
+# dpi = 600)
 ```
@@
 cor <- cor(stmOut$theta[stmOut$settings$covariates$betaindex==1,])
-colnames(cor) <- 1:40
+colnames(cor) <- 1:k
 
 df <- as.data.frame(cor) %>% 
-  mutate(topic = 1:40) %>%
+  mutate(topic = 1:k) %>%
   melt(., id="topic", value.name="corr") %>%
@@
   cor <- cor(stmOut$theta[stmOut$settings$covariates$betaindex==i,])
-  colnames(cor) <- 1:40
+  colnames(cor) <- 1:k
 
   df1 <- as.data.frame(cor) %>%
-    mutate(topic = 1:40) %>%
+    mutate(topic = 1:k) %>%
     melt(., id="topic", value.name="corr") %>%
@@
 ```{r}
-plotQuote(c(paste(sagelabs$cov.betas[[1]]$problabels[29,], collapse="\n"),
-            paste(sagelabs$cov.betas[[2]]$problabels[29,], collapse="\n")))
+plotQuote(c(paste(sagelabs$cov.betas[[1]]$problabels[27,], collapse="\n"),
+            paste(sagelabs$cov.betas[[2]]$problabels[27,], collapse="\n")))
 ```

### 2018-02-13 paper/R/02_cleanAndCombine.Rmd
new file structure

@@
 load("../output/news_cleaned.Rda")
-okt <- read_csv("../data/eventbride/eventbride_okt_18.csv")
-nov_03 <- read_csv("../data/eventbride/eventbride_nov_03.csv")
-nov_22 <- read_csv("../data/eventbride/eventbride_nov_22.csv")
-dec_16 <- read_csv("../data/eventbride/eventbride_dec_16.csv")
-jan_1 <- read_csv("../data/eventbride/eventbride_jan_1.csv")
+okt <- read_csv("../data/eventregistry/eventbride_17_10_18.csv")
+nov_03 <- read_csv("../data/eventregistry/eventbride_17_11_03.csv")
+nov_22 <- read_csv("../data/eventregistry/eventbride_17_11_22.csv")
+nov_30 <- read_csv("../data/eventregistry/eventbride_17_11_30.csv")
+dec_16 <- read_csv("../data/eventregistry/eventbride_17_12_16.csv")
+jan_1 <- read_csv("../data/eventregistry/eventbride_18_01_1.csv")
 ```
@@
 ```{r}
-df_full <- bind_rows(list(okt,nov_03,nov_22,dec_16,jan_1)) %>%
+df_full <- bind_rows(list(okt,nov_03,nov_22,nov_30,dec_16,jan_1)) %>%
   mutate(text = body,
@@
 ```{r}
-keeps <- c("spiegel.de", "focus.de", "zeit.de","bild.de",
-           "tagesschau.de", "welt.de")
+keeps <- c("bild.de","focus.de", "zeit.de","spiegel.de", "stern.de",
+           "tagesschau.de", "welt.de", "zeit.de")
 
 df <- df_full %>%
-  mutate(title_text = paste(title, text, sep=" ")) %>%
   filter(site %in% keeps) %>%
   filter(date>=as.Date("2017-06-01")) %>%
-  filter(date< as.Date("2018-01-01"))
+  filter(date< as.Date("2018-01-01")) %>%
+  mutate(title_text = paste(title, text, sep=" "))
 ```
@@
 ```{r}
-pat1 <- "\\w\\.de/politik/deutschland"
-pat2 <- "\\w\\.de/politik/inland"
-pat3 <- "\\w\\.de/politik/wahl"
-pat4 <- "\\w\\.de/politik/bundestagswahl"
-pat5 <- "tagesschau.de/inland"
+# pat1 <- "\\w\\.de/politik/deutschland"
+# pat2 <- "\\w\\.de/politik/inland"
+# pat3 <- "\\w\\.de/politik/wahl"
+# pat4 <- "\\w\\.de/politik/bundestagswahl"
+# pat5 <- "tagesschau.de/inland"
+# 
+# df %>%
+#   mutate(politics = ifelse(grepl(paste(pat1,pat2,pat3,pat4,pat5,
+#                       sep="|"), url, perl = TRUE),1,0)) -> df
+
+#........................
+pat <- paste("cdu","csu","union","spd","fdp","afd",
+             "linkspartei","die linke","die grünen","bündnis 90", sep="|")
 
 df %>%
-  mutate(politics = ifelse(grepl(paste(pat1,pat2,pat3,pat4,pat5,
-                      sep="|"), url, perl = TRUE),1,0)) -> df
-
-#........................
-# pat <- paste("cdu","csu","union","spd","fdp","afd",
-#              "linkspartei","die linke","die grünen","bündnis 90", sep="|")
-# 
-# df %>%
-#   mutate(politics = ifelse(grepl(pat, title_text, ignore.case = TRUE),1,0)) -> btw1
+  mutate(politics = ifelse(grepl(pat, title_text, ignore.case = TRUE),1,0)) -> df
 ```

### 2018-02-13 paper/R/04_Modelresults.Rmd
new file structure

@@
   btw %>%
-  ggplot(aes(ownership)) +
+  ggplot(aes(site)) +
   geom_bar(fill=col[1], alpha= .8) +
@@
 # 3. Model Results
-```{r caching, echo = FALSE}
-load("../output/models/STM_ownership 30 .Rda")
+```{r echo = FALSE}
+load("../output/models/STM_ownership 40 .Rda")
 k <- stmOut$settings$dim$K
@@
 ```{r}
-topics <- matrix(c(1, "Great coalition", 2, "A.Merkel, CSU, Guttenberg", 3, "Coalition talks (Jamaica, Niedersachsen)", 
-                   4, "Diesel scandal", 5, "A.Merkel, glyphosat scandal", 6, "DIE LINKE", 
-                   7, "Islam and antisemitism in GER", 8, "Merkel vs.Schulz", 
+topics <- matrix(c(1, "Great coalition", 2, "A.Merkel, CSU, Guttenberg", 3, "Jamaica coalition",
+                   4, "Diesel scandal", 5, "A.Merkel, glyphosat scandal", 6, "Seehover vs. Söder",
+                   7, "political trends in GER", 8, "Merkel vs.Schulz",
                    9, "Trends in electoral districts", 10, "Steinmeier, Federal President",
                    11, "G.Schröder & IT themes (Data policy, Wifi, Telekom)",
-                   12, "Federal Election trends", 13, "EU policies", 14, "G20 Hamburg", 
-                   15, "error (text processing failure)", 16, "Refugees, asylum claims", 
-                   17, "Budget statistics, social welfare", 18, "Jamaica Coalition talks", 
-                   19, "Polls federal election", 20, "AfD in social media", 
-                   21, "Women empowerment, M.Schwesig (SPD)", 22, "AfD (Petri, Gauland, Höcke)", 
-                   23, "Terror attack Berlin (Amri)", 24, "election campaigns & political talkshows", 
-                   25, "German armed forces", 26, "Issues in the Bundestag", 27, "C.Lindner FDP", 
-                   28, "Turkey, Russia", 29, "Terror attacks (GER)  & police reports", 30, "H.Kohl obituary"), ncol=2, byrow=T)
+                   12, "Federal Election trends", 13, "Climate policy, Die Grünen", 14, "G20 Hamburg",
+                   15, "error (text processing failure)", 16, "Public authorities (police, BKA)",
+                   17, "Federal budget statistics", 18, "Family reunion refugees",
+                   19, "Election Polls", 20, "AfD in social media", 21, "(Sexual) assaults, Gender Debate, M.Schwesig", 
+                   22, "elections in Niedersachsen", 23, "Court judgements (on terror attacks, NSU)", 
+                   24, "election campaigns & political talkshows", 25, "German armed forces",
+                   26, "Issues in the Bundestag", 27, "C.Lindner FDP", 28, "Diplomatic relations w Turkey & Russia", 
+                   29, "A.Merkel in east GER", 30, "H.Kohl obituary", 31, "AfD (Petri, Gauland, Höcke)", 
+                   32, "Refugees (in GER)", 33, "EU policies", 34, "DIE LINKE", 35, "SPD", 
+                   36, "Islam and antisemitism in GER", 37, "AfD in parliament", 38, "Church", 
+                   39, "Terror attack in Berlin (Amri)", 40, "DHL package attack (Potsdam)"), ncol=2, byrow=T)
 
-# topics <- matrix(c(1, "Great coalition", 2, "A.Merkel, CSU, Guttenberg", 3, "Jamaica coalition", 
-#                    4, "Diesel scandal", 5, "A.Merkel, glyphosat scandal", 6, "Seehover vs. Söder", 
-#                    7, "political trends after the election", 8, "Merkel vs.Schulz", 
+# topics <- matrix(c(1, "Great coalition", 2, "A.Merkel, CSU, Guttenberg", 3, "Coalition talks (Jamaica, Niedersachsen)",
+#                    4, "Diesel scandal", 5, "A.Merkel, glyphosat scandal", 6, "DIE LINKE", 
+#                    7, "Islam and antisemitism in GER", 8, "Merkel vs.Schulz", 
 #                    9, "Trends in electoral districts", 10, "Steinmeier, Federal President", 
 #                    11, "G.Schröder & IT themes (Data policy, Wifi, Telekom)", 
-#                    12, "Federal Election trends", 13, "Climate policy, Die Grünen", 14, "G20 Hamburg", 
-#                    15, "error (text processing failure)", 16, "Police academy (Berlin), AfD", 
-#                    17, "Federal budget statistics", 18, "Family reunion refugees", 
+#                    12, "Federal Election trends", 13, "EU policies", 14, "G20 Hamburg", 
+#                    15, "error (text processing failure)", 16, "Refugees in GER", 
+#                    17, "Budget statistics, social welfare", 18, "Jamaica Coalition talks", 
 #                    19, "Polls federal election", 20, "AfD in social media", 
-#                    21, "Women empowerment, M.Schwesig (SPD)", 22, "elections in Niedersachsen", 
-#                    23, "Court sentences, NSU trial", 24, "election campaigns & political talkshows", 
+#                    21, "Women empowerment, M.Schwesig (SPD)", 22, "AfD (Petri, Gauland, Höcke)", 
+#                    23, "Court judgements on terrorist attacks", 24, "election campaigns & political talkshows", 
 #                    25, "German armed forces", 26, "Issues in the Bundestag", 27, "C.Lindner FDP", 
-#                    28, "Turkey, Russia", 29, "A.Merkel in east GER", 30, "H.Kohl obituary", 
-#                    31, "AfD (Petri, Gauland, Höcke)", 32, "Asylum claims and deportation", 
-#                    33, "EU policies", 34, "DIE LINKE", 35, "SPD", 36, "Islam and antisemitism in GER", 
-#                    37, "AfD in parliament", 38, "Church", 39, "Terror attacks (GER)  & police reports", 
-#                    40, "DHL package attack (Potsdam)"), ncol=2, byrow=T)
+#                    28, "Turkey, Russia", 29, "Terror attacks (GER)  & police reports", 30, "H.Kohl obituary"), ncol=2, byrow=T)
 
@@
 ```{r}
-btw.2 %>% filter(topic==17) %>% select(title, gamma, site) %>%
+btw.2 %>% filter(topic==16) %>% select(title, gamma, site) %>%
   arrange(desc(gamma)) %>%
@@
 
-### in the overall corpus
-```{r}
-frequency <- as.data.frame(colMeans(stmOut$theta)) %>% 
-  mutate(frequency = colMeans(stmOut$theta),
-    topic=paste(topics[,1],topics[,2], sep=": "))
-
-p1 <- ggplot(frequency, aes(x=reorder(topic, frequency), y=frequency)) + 
-    geom_col(fill=col[1], alpha=0.8) +
-    coord_flip() +
-    labs(x="", y="expected frequency") +
-    theme(axis.text.x = element_text(size=8),
-          axis.text.y = element_text(size=11),
-          axis.title = element_text(size=10))
-
-#ggsave(plot = p1, filename = "../figs/topic_proportion.png", device = "png",width = 8, height = 12,
-#dpi = 600)
-```
-
-### by newspaper
-```{r}
-# Topic 1
-plotNewspaperHistogram(2)
-```
-
-### by ownership
-plots the expected proportion of topic use in public media minus the expected proportion of topic use in private media. Thus topics more associated with public media appear to the right of zero.
-
+Create a Df that contains the columns means of theta (per topic and covariate level)
 ```{r}
@@
 }
+```
 
-freq <- freq %>%
-  #mutate(ownership = ifelse(site == "Tagesschau.de", "public", "private")) %>%
+### in the overall corpus
+
+```{r}
+frequency <- as.data.frame(colMeans(stmOut$theta)) %>% 
+  mutate(frequency = colMeans(stmOut$theta),
+    topic=paste(topics[,1],topics[,2], sep=": "))
+
+p1 <- ggplot(frequency, aes(x=reorder(topic, frequency), y=frequency)) + 
+    geom_col(fill=col[1], alpha=0.8) +
+    coord_flip() +
+    labs(x="", y="expected frequency") +
+    theme(axis.text.x = element_text(size=8),
+          axis.text.y = element_text(size=11),
+          axis.title = element_text(size=10))
+```
+
+Alternatively we can show the expected frequency separated by ownership:
+
+```{r}
+freq %>% left_join(., topics.df, by = "topic") %>%
+  ggplot(aes(reorder(topic_name,freq), freq, fill=factor(ownership))) +
+  geom_col() +
+  scale_fill_manual(values = col[c(1,3)]) +
+  coord_flip() +
+  theme(#axis.text.y = element_blank(),
+          axis.text.y = element_text(size=9),
+          axis.title = element_text(size=10)) +
+    labs(x="", y="Expected frequency") 
+```
+
+### by ownership
+```{r}
+plotNewspaperHistogram(2)
+```
+
+plots the expected proportion of topic use in public media minus the expected proportion of topic use in private media. Thus topics more associated with public media appear to the right of zero.
+
+```{r}
+freq1 <- freq %>%
   group_by(topic, ownership) %>%
@@
             by = "topic_name")
-```
 
-```{r}
-p2 <- ggplot(freq, aes(reorder(topic_name,frequency), freq_diff,
+p2 <- ggplot(freq1, aes(reorder(topic_name,frequency), freq_diff,
                  fill = factor(value))) +
@@
 
-# ggsave(filename = "../figs/topic_proportion.png", device = "png",width = 12, height = 10,
-# dpi = 600)
+ggsave(filename = "../figs/topic_proportion.png", device = "png",width = 12, height = 10,
+dpi = 600)
+```
+
+```{r fig.height=6}
+plotQuote(c(paste(sagelabs$cov.betas[[1]]$problabels[7,], collapse="\n"),
+            paste(sagelabs$cov.betas[[2]]$problabels[7,], collapse="\n")))
 ```
@@
                          metadata = out$meta, uncertainty = "None")
-#save(out_ownership,stmOut, effect, file = "stm_newsdata.RData")
 ```
@@
 sites <- c("(Intercept)", "public", "private")
-p1 <- coeff %>% filter(parameter %in% sites) %>%
+p1 <- coeff %>% 
+  #filter(parameter %in% sites) %>%
   ggplot(aes(x = reorder(topic_name,topic, decreasing=F), y = Estimate, fill=factor(signifcant))) +
@@
   scale_fill_manual(values = col[c(2,1)]) +
+  scale_x_discrete(position = "top") +
   coord_flip() +
-  facet_wrap(~parameter, ncol = 6) +
-  labs(x="", fill="significant at\nthe 5% level") +
-  theme(axis.text.x = element_text(angle=90))
+  facet_wrap(~parameter, ncol = 8, scales = "free_x") +
+  labs(x="", fill="significant at the 5% level") +
+  theme(legend.position = "top", 
+        axis.text.y = element_text(size=9),
+        axis.text.x = element_text(angle=90))
 
@@
 
-# ggsave(plot = p1, filename = "../figs/estimates_site.png", device = "png",width = 9, height = 7,
-# dpi = 600)
-```
-
-```{r}
-p1 <- coeff %>% filter(!parameter %in% sites) %>%
-  ggplot(aes(x = reorder(topic_name,topic, decreasing=F), y = Estimate, 
-             fill=factor(signifcant))) +
-  geom_col() +
-  scale_fill_manual(values = col[c(2,1)]) +
-  coord_flip() +
-  facet_wrap(~parameter, ncol = 6) +
-  labs(x="", fill="significant at\nthe 5% level") +
-  theme(axis.text.x = element_text(angle=90))
-
-p1
-
-ggsave(plot = p1, filename = "../figs/estimates_month.png", device = "png",width = 9, height = 7,
+ggsave(plot = p1, filename = "../figs/estimates.png", device = "png",width = 10, height = 7,
 dpi = 600)
@@
 
+## 3.5 Plotquote
 Take a closer look to those topics that are discussed most different.
 
-```{r}
-plotQuote(c(paste(sagelabs$cov.betas[[1]]$problabels[27,], collapse="\n"),
-            paste(sagelabs$cov.betas[[2]]$problabels[27,], collapse="\n")))
+```{r fig.height=6}
+plotQuote(c(paste(sagelabs$cov.betas[[1]]$problabels[23,], collapse="\n"),
+            paste(sagelabs$cov.betas[[2]]$problabels[23,], collapse="\n")))
 ```
-
-```{r}
-btw.2 %>%
-  filter(grepl("sturm", url) &
-           site == "Tagesschau.de") %>%
-  select(title, site)
-```

### 2018-02-13 paper/R/02_cleanAndCombine.Rmd
ownership to site

@@
 ### without stemming
-processed <- textProcessor(btw$text_cleaned1, metadata = btw[,c("ownership","text_cleaned1","month")],
+processed <- textProcessor(btw$text_cleaned1, metadata = btw[,c("site","text_cleaned1","month")],
                            wordLengths = c(2,Inf),
@@
 out <- prepDocuments(processed$documents, processed$vocab, processed$meta)
-out$meta$ownership <- as.factor(out$meta$ownership)
-###
+out$meta$site <- as.factor(out$meta$site)
 
-# processed <- textProcessor(btw$text_cleaned1, metadata = btw[,c("site","text_cleaned1","month")],
-#                            wordLengths = c(2,Inf),
-#                            lowercase = F,
-#                            removestopwords = F,
-#                            removenumbers = F,
-#                            removepunctuation = F,
-#                            stem = F)
-# out <- prepDocuments(processed$documents, processed$vocab, processed$meta)
-# out$meta$site <- as.factor(out$meta$site)
-
-save(btw, out, file="../output/btw_comb.Rda")
+save(btw, out, file="../output/btw_out.Rda")
 ```

### 2018-02-15 paper/R/04_Modelresults.Rmd
add gesis data

@@
 ---
-title: "Regression"
+title: "Model Results"
 subtitle: ""

### 2018-02-15 paper/doc/structure.tex
add gesis data

@@
 This section summarizes the results of the STM.
-Subsequently different measures to analyze the content differences between public and private ownership are applied according to the following approaches: (1) To address the question whether market imperfections exist in that sense, that some topics are not covered by private but by public news provider, I use the document-topic probability $\theta$, to estimate the conditional expectation of topic prevalence for given document characteristics.
-(2) Next, I find all edges between topics where they exhibit a positive correlation of $\theta$ above 0.1 to examine how topics are correlated differently for different covariate levels, indicating how topics are connected and framed differently between private and public media.
+Subsequently different measures to analyze the content differences between public and private ownership are applied according to the following approaches: (1) To address the question whether market imperfections exist in that sense, that some topics are not covered by private but by public news provider, I use the document-topic probability $\theta$, to estimate the conditional expectation of topic prevalence for given document characteristics (See section \ref{subsectiona_topicprevalence}).
+(2) Next, I find all edges between topics where they exhibit a positive correlation of $\theta$ above 0.1 to examine how topics are correlated differently for different covariate levels, indicating how topics are connected and framed differently between private and public media (see section \ref{subsection_topiccorrelation}).
 Approaches (1) and (2) have been used in \citep{roberts_model_2016}.
-However, we extend the analysis by (3) calculating the similarity of the word-topic distribution $\beta$ between the news provider using various distance measures, to identify which topics are discussed similar or differently.
+However, we extend the analysis by (3) calculating the similarity of the word-topic distribution $\beta$ between the news provider using various distance measures, to identify which topics are discussed similar or differently (see section \ref{subsection_similarity}).
 
-Figure \ref{fig_topic_proportion} displays the topics ordered by their expected frequency across the corpus (left side of the Figure) and the expected proportion of a topic in public media minus the expected proportion of topic use in private media (right side of the Figure).
+In order to get an initial overview of the results, Figure \ref{fig_topic_proportion} displays the topics ordered by their expected frequency across the corpus (left side of the Figure) and the expected proportion of a topic in public media minus the expected proportion of topic use in private media (right side of the Figure).
 Thus topics more associated with public media appear to the right of zero.
-To assign a label to each topic, we looked at the most frequent words in that topic and the most representative articles \citep{roberts_model_2016}.
+To assign a label to each topic, I looked at the most frequent words in that topic and the most representative articles \citep{roberts_model_2016}.
+
+It becomes apparent that the topic (topic 3) about the coalition talks between the so-called Jamaica parties (CDU/CSU, FDP and Bündnis 90/Die Grünen) is the topic with the highest expected frequency in the whole corpus, followed by the topics about refugees in Germany (topic 32) and the coalition talks between CDU/CSU and SPD (topic 1), that began shortly after the failure of the Jamaican coalition.
+Particularly in the latter case, there is no discernible difference between private and public providers, while topic 3 and 32 are more likely to be seen in public news.
+The biggest difference can be seen in Topic 23, which covers court proceedings, especially in relation to the NSU case.
+Private providers seem to be less likely to report on this topic, as it is of less likelihood of observing this topic in the corpus of private news.
+Topic 7, which deals with political trends in Germany, seems to be discussed more often in private than in public news.
 
@@
 
-\textcolor{red}{AUSWERTUNG}
+\subsection{Differences in topic prevalence}\label{subsectiona_topicprevalence}
 
-\subsection{Differences in topic prevalence}
-Since news source is included as a covariate in estimating topical prevalence part within the model, the frequency a topic is discussed within a news corpus can be calculated \citep{roberts_model_2016}.
-I estimate the conditional expectation of topic prevalence for given document characteristics.
+To identify which of these differences is significant, the conditional expectation of topic prevalence for given document characteristics can be estimated \citep{roberts_model_2016}.
 More specifically, I estimate a linear model, where the documents are observations, the dependent variable is the posterior probability of a topic and the covariates are the metadata of documents (see equation \ref{eq_1}).
@@
 \begin{equation}\label{eq_1}
-	\theta_d=\alpha+\beta_1x_{site}+\beta_2x_{month}+\epsilon
+	\theta_d=\alpha+\beta_1x_{ownership}+\beta_2x_{month}+\epsilon
 \end{equation}
 
-Figure \ref{fig_estimateEffects} displays the regression results for private vs.
-public.
-As the month an articles was published is included in the regression, the intercept indicates the mean of private news suppliers in June 2017.\footnote{Table of regression results can be found in appendix.}
+Figure \ref{fig_estimateEffects} displays the regression results for private vs. public.
 
@@
 		\begin{center}
-			\includegraphics[width=0.9\textwidth,keepaspectratio]{../figs/estimates_site.png}
+			\includegraphics[width=0.9\textwidth,keepaspectratio]{../figs/estimates.png}
 		\end{center}
@@
 
-\subsection{Topic correlations}
+\subsection{Topic correlations}\label{subsection_topiccorrelation}
 
@@
 
-\subsection{Differences in word-topic distributions}\label{ch_similarity}
+\subsection{Differences in word-topic distributions}\label{subsection_similarity}
 

### 2018-02-16 paper/R/04_Modelresults.Rmd
from ownership to site

--- 2018-02-13 paper/R/04_Modelresults.Rmd
@@
   html_document:
-    toc: true
-    toc_float: true
     theme: "lumen"
@@
 ```{r caching, echo = FALSE}
-#load("../output/btw_combined.Rda")
-load("../output/btw_comb.Rda")
+load("../output/btw_out.Rda")
 ```
@@
 ```{r echo = FALSE}
-load("../output/models/STM_ownership 40 .Rda")
+load("../output/models/STM 35 .Rda")
 k <- stmOut$settings$dim$K
@@
 ```{r}
-topics <- matrix(c(1, "Great coalition", 2, "A.Merkel, CSU, Guttenberg", 3, "Jamaica coalition",
-                   4, "Diesel scandal", 5, "A.Merkel, glyphosat scandal", 6, "Seehover vs. Söder",
-                   7, "political trends in GER", 8, "Merkel vs.Schulz",
-                   9, "Trends in electoral districts", 10, "Steinmeier, Federal President",
-                   11, "G.Schröder & IT themes (Data policy, Wifi, Telekom)",
-                   12, "Federal Election trends", 13, "Climate policy, Die Grünen", 14, "G20 Hamburg",
-                   15, "error (text processing failure)", 16, "Public authorities (police, BKA)",
-                   17, "Federal budget statistics", 18, "Family reunion refugees",
-                   19, "Election Polls", 20, "AfD in social media", 21, "(Sexual) assaults, Gender Debate, M.Schwesig", 
-                   22, "elections in Niedersachsen", 23, "Court judgements (on terror attacks, NSU)", 
-                   24, "election campaigns & political talkshows", 25, "German armed forces",
-                   26, "Issues in the Bundestag", 27, "C.Lindner FDP", 28, "Diplomatic relations w Turkey & Russia", 
-                   29, "A.Merkel in east GER", 30, "H.Kohl obituary", 31, "AfD (Petri, Gauland, Höcke)", 
-                   32, "Refugees (in GER)", 33, "EU policies", 34, "DIE LINKE", 35, "SPD", 
-                   36, "Islam and antisemitism in GER", 37, "AfD in parliament", 38, "Church", 
-                   39, "Terror attack in Berlin (Amri)", 40, "DHL package attack (Potsdam)"), ncol=2, byrow=T)
-
-# topics <- matrix(c(1, "Great coalition", 2, "A.Merkel, CSU, Guttenberg", 3, "Coalition talks (Jamaica, Niedersachsen)",
-#                    4, "Diesel scandal", 5, "A.Merkel, glyphosat scandal", 6, "DIE LINKE", 
-#                    7, "Islam and antisemitism in GER", 8, "Merkel vs.Schulz", 
-#                    9, "Trends in electoral districts", 10, "Steinmeier, Federal President", 
-#                    11, "G.Schröder & IT themes (Data policy, Wifi, Telekom)", 
-#                    12, "Federal Election trends", 13, "EU policies", 14, "G20 Hamburg", 
-#                    15, "error (text processing failure)", 16, "Refugees in GER", 
-#                    17, "Budget statistics, social welfare", 18, "Jamaica Coalition talks", 
-#                    19, "Polls federal election", 20, "AfD in social media", 
-#                    21, "Women empowerment, M.Schwesig (SPD)", 22, "AfD (Petri, Gauland, Höcke)", 
-#                    23, "Court judgements on terrorist attacks", 24, "election campaigns & political talkshows", 
-#                    25, "German armed forces", 26, "Issues in the Bundestag", 27, "C.Lindner FDP", 
-#                    28, "Turkey, Russia", 29, "Terror attacks (GER)  & police reports", 30, "H.Kohl obituary"), ncol=2, byrow=T)
+topics <- matrix(c(1, "SPD, M.Schulz", 2, "A.Merkel vs. Schulz", 3, "Jamaica coalition", 4, "Diesel scandal", 
+                   5, "H.Kohl", 6, "Federal Elections", 7, "EU policies, refugees", 8, "Political trends in GER", 
+                   9, "AfD in Parliament", 10, "A.Merkel", 11, "Deportation, radicalization, refugees", 
+                   12, "Christian, Berlin, Bruch", 13, "Climate policy, Die Grünen", 14, "Seehofer vs. Söder", 
+                   15, "D.Trump", 16, "Great coalition", 17, "CDU/CSU", 18, "Elections in Niedersachen", 
+                   19, "Budget statistics, Welfare policy", 20, "AfD in social media", 21, "DIE LINKE", 
+                   22, "German armed forces, Mali", 23, "Nuclear Waste, Weather reports", 
+                   24, "Innenministerium, Verfassungsschutz", 
+                   25, "Terror attack (Amri)", 26, "G20 in Hamburg", 27, "Spahn (CDU)", 
+                   28, "Steinmeier", 29, "German armed forces", 30, "AfD", 31, "Women empowerment", 
+                   32, "Diplomatic relations w Turkey, Russia", 33, "Election polls", 34, "Votings in parliament", 
+                   35, "F.Petri, Staatsanwaldschaft"), ncol=2, byrow=T)
 
@@
 ```{r}
-btw.2 %>% filter(topic==16) %>% select(title, gamma, site) %>%
+btw.2 %>% filter(topic==23) %>% select(title, gamma, url) %>%
   arrange(desc(gamma)) %>%
@@
 ## 3.1. Topic proportions
-
-Create a Df that contains the columns means of theta (per topic and covariate level)
-```{r}
-freq <- tapply(stmOut$theta[,1], stmOut$settings$covariates$betaindex, mean)
-freq <- as.data.frame(freq) %>% 
-    mutate(ownership=stmOut$settings$covariates$yvarlevels,
-           topic = 1)
-
-for(i in 2:k) {
-  freq1 <- tapply(stmOut$theta[,i], stmOut$settings$covariates$betaindex, mean)
-  freq1 <- as.data.frame(freq1) %>% 
-    transmute(ownership=stmOut$settings$covariates$yvarlevels,
-           topic = i,
-           freq = freq1)
-
-  freq <- rbind(freq, freq1)
-}
-```
 
@@
           axis.title = element_text(size=10))
+
+p1
 ```
@@
 
-### by ownership
+### by site
 ```{r}
-plotNewspaperHistogram(2)
+plotNewspaperHistogram(11)
+```
+
+Create a Df that contains the columns means of theta (per topic and covariate level)
+```{r}
+freq <- tapply(stmOut$theta[,1], stmOut$settings$covariates$betaindex, mean)
+freq <- as.data.frame(freq) %>% 
+    mutate(site=stmOut$settings$covariates$yvarlevels,
+           topic = 1)
+
+for(i in 2:k) {
+  freq1 <- tapply(stmOut$theta[,i], stmOut$settings$covariates$betaindex, mean)
+  freq1 <- as.data.frame(freq1) %>% 
+    transmute(site=stmOut$settings$covariates$yvarlevels,
+           topic = i,
+           freq = freq1)
+
+  freq <- rbind(freq, freq1)
+}
+
+freq <- freq %>%
+  left_join(., topics.df, by = "topic") %>%
+  mutate(topic = topic_name) %>%
+  left_join(., frequency %>% select(topic, frequency),
+            by = "topic")
 ```
@@
 ```{r}
-freq1 <- freq %>%
-  group_by(topic, ownership) %>%
-  summarise(freq_mean = mean(freq)) %>%
-  spread(ownership, freq_mean) %>%
-  mutate(freq_diff = public - private) %>%
-  mutate(value = ifelse(freq_diff>=0, 1,0)) %>%
-  left_join(., topics.df, by = "topic") %>%
-  left_join(., frequency %>% mutate(topic_name = topic) %>%
-              select(-topic),
-            by = "topic_name")
-
-p2 <- ggplot(freq1, aes(reorder(topic_name,frequency), freq_diff,
-                 fill = factor(value))) +
-  geom_col(show.legend = F) +
-  scale_fill_manual(values = col[c(1,3)]) +
+ggplot(freq, aes(reorder(topic_name,frequency), freq)) +
+  geom_col(fill = col[1]) +
+  #scale_fill_manual(values = col[1]) +
   coord_flip() +
+  facet_wrap(~site, ncol = 7)
   theme(axis.text.y = element_blank(),
@@
 
-p1 + p2
+p2
 
-ggsave(filename = "../figs/topic_proportion.png", device = "png",width = 12, height = 10,
-dpi = 600)
+# ggsave(filename = "../figs/topic_proportion.png", device = "png",width = 12, height = 10,
+# dpi = 600)
 ```
 
-```{r fig.height=6}
-plotQuote(c(paste(sagelabs$cov.betas[[1]]$problabels[7,], collapse="\n"),
-            paste(sagelabs$cov.betas[[2]]$problabels[7,], collapse="\n")))
+```{r fig.height=11, fig.width=5}
+topic <- 11
+
+plotQuote(c(paste(sagelabs$cov.betas[[1]]$problabels[topic,], collapse="\n"),
+            paste(sagelabs$cov.betas[[2]]$problabels[topic,], collapse="\n"),
+            paste(sagelabs$cov.betas[[3]]$problabels[topic,], collapse="\n"),
+            paste(sagelabs$cov.betas[[4]]$problabels[topic,], collapse="\n"),
+            paste(sagelabs$cov.betas[[5]]$problabels[topic,], collapse="\n"),
+            paste(sagelabs$cov.betas[[6]]$problabels[topic,], collapse="\n"),
+            paste(sagelabs$cov.betas[[7]]$problabels[topic,], collapse="\n")))
 ```
@@
 ```{r}
-effect <- estimateEffect(c(1:k) ~ownership+s(month), stmOut, 
+effect <- estimateEffect(c(1:k) ~site+s(month), stmOut, 
                          metadata = out$meta, uncertainty = "None")
@@
   mutate(parameter = rownames(coeff),
-         parameter = gsub("ownership", "", parameter),
+         parameter = gsub("site", "", parameter),
          parameter = ifelse(parameter == "s(month)1", "1_July", parameter),
@@
 ```{r}
-#sites <- c("(Intercept)", "DIE WELT", "FOCUS ONLINE","SPIEGEL ONLINE", "Tagesschau.de","ZEIT ONLINE")
-sites <- c("(Intercept)", "public", "private")
+
 p1 <- coeff %>% 
-  #filter(parameter %in% sites) %>%
+  filter(parameter %in% stmOut$settings$covariates$yvarlevels) %>%
   ggplot(aes(x = reorder(topic_name,topic, decreasing=F), y = Estimate, fill=factor(signifcant))) +
@@
 
-ggsave(plot = p1, filename = "../figs/estimates.png", device = "png",width = 10, height = 7,
-dpi = 600)
-```
-
-## 3.3 Topic Correlation
-```{r}
-## Create Dataframe with correlations
-cor <- cor(stmOut$theta[stmOut$settings$covariates$betaindex==1,])
-colnames(cor) <- 1:k
-
-df <- as.data.frame(cor) %>% 
-  mutate(topic = 1:k) %>%
-  melt(., id="topic", value.name="corr") %>%
-  mutate(site = stmOut$settings$covariates$yvarlevels[1])
-
-for (i in 2:2) {
-  cor <- cor(stmOut$theta[stmOut$settings$covariates$betaindex==i,])
-  colnames(cor) <- 1:k
-
-  df1 <- as.data.frame(cor) %>%
-    mutate(topic = 1:k) %>%
-    melt(., id="topic", value.name="corr") %>%
-    mutate(site = stmOut$settings$covariates$yvarlevels[i])
-
-  df <- rbind(df,df1)
-}
-```
-
-```{r}
-df <- df %>% 
-  left_join(.,topics.df, by = "topic") %>%
-  mutate(topic1 = topic,
-         topic_name1 = topic_name,
-         topic = as.numeric(variable)) %>%
-  select(-topic_name) %>%
-  left_join(., topics.df, by="topic")
-```
-
-```{r}
-p1 <- df %>%
-  filter(corr>0.05 & corr < 1) %>%
-  ggplot(aes(reorder(topic_name1,topic1), topic_name, 
-             fill=corr)) +
-  geom_tile() +
-  facet_wrap(~site, ncol = 6) +
-  #scale_fill_distiller(palette = "Spectral", trans = "reverse") + 
-  labs(x="", y="", fill="correlation") +
-  theme_bw(base_family = "Roboto", base_size = 10) +
-  theme(axis.text.x = element_text(angle=90, size = 6),
-        #plot.background = element_rect(fill = 'transparent', colour = 'transparent'),
-        strip.background = element_rect(fill = 'transparent', colour = 'transparent'),
-        axis.ticks = element_line(colour = 'transparent'))
-
-p1
-
-# ggsave(plot = p1, filename = "../figs/topic_correlation.png", device = "png",width = 9, height = 5,
+# ggsave(plot = p1, filename = "../figs/estimates.png", device = "png",width = 10, height = 7,
 # dpi = 600)
-```
-
-### Network graph
-```{r}
-i <- 1
-cormat <- cor(stmOut$theta[stmOut$settings$covariates$betaindex==i,])
-cormat <- ifelse(cormat >=0.05, cor, 0)
-# 
-g <- igraph::simplify(igraph::graph.adjacency(cormat, mode = "undirected", weight=TRUE))
-igraph::V(g)$name <- topics.df$topic_name
-igraph::V(g)$props <- colMeans(stmOut$theta)
-
-p1 <- topicCorrNetwork(g, stmOut$settings$covariates$yvarlevels[i])
-# 
-ggsave(
-      paste0("../figs/corrplot",i,".png"),
-      p1,
-      dpi = 300,
-      width = 9,
-      height = 6
-    )
-```
-
-### Overlapping Correlation
-Pairs of topics where an edge exists in both Newspaper, we denote with a light blue dot.
-Pairs of topics where Newspaper1, but not Newspaper2 have an edge between them, we denote with a red square, and those where Newspaper2, but not Newspaper1 have an edge between them we denote with a blue square.
-We then sort the matrix by topics that are similarly correlated with other topics in Newspaper1 and Newspaper2 to those that are not similarly correlated.
-```{r}
-png("../figs/overlapping_correlation.png")
-topicCorrCompare(1,5)
-dev.off()
 ```

### 2018-02-16 paper/R/backup.Rmd
from ownership to site

@@
 
+## 3.3 Topic Correlation
+```{r}
+## Create Dataframe with correlations
+cor <- cor(stmOut$theta[stmOut$settings$covariates$betaindex==1,])
+colnames(cor) <- 1:k
+
+df <- as.data.frame(cor) %>% 
+  mutate(topic = 1:k) %>%
+  melt(., id="topic", value.name="corr") %>%
+  mutate(site = stmOut$settings$covariates$yvarlevels[1])
+
+for (i in 2:2) {
+  cor <- cor(stmOut$theta[stmOut$settings$covariates$betaindex==i,])
+  colnames(cor) <- 1:k
+
+  df1 <- as.data.frame(cor) %>%
+    mutate(topic = 1:k) %>%
+    melt(., id="topic", value.name="corr") %>%
+    mutate(site = stmOut$settings$covariates$yvarlevels[i])
+
+  df <- rbind(df,df1)
+}
+```
+
+```{r}
+df <- df %>% 
+  left_join(.,topics.df, by = "topic") %>%
+  mutate(topic1 = topic,
+         topic_name1 = topic_name,
+         topic = as.numeric(variable)) %>%
+  select(-topic_name) %>%
+  left_join(., topics.df, by="topic")
+```
+
+```{r}
+p1 <- df %>%
+  filter(corr>0.05 & corr < 1) %>%
+  ggplot(aes(reorder(topic_name1,topic1), topic_name, 
+             fill=corr)) +
+  geom_tile() +
+  facet_wrap(~site, ncol = 6) +
+  #scale_fill_distiller(palette = "Spectral", trans = "reverse") + 
+  labs(x="", y="", fill="correlation") +
+  theme_bw(base_family = "Roboto", base_size = 10) +
+  theme(axis.text.x = element_text(angle=90, size = 6),
+        #plot.background = element_rect(fill = 'transparent', colour = 'transparent'),
+        strip.background = element_rect(fill = 'transparent', colour = 'transparent'),
+        axis.ticks = element_line(colour = 'transparent'))
+
+p1
+
+# ggsave(plot = p1, filename = "../figs/topic_correlation.png", device = "png",width = 9, height = 5,
+# dpi = 600)
+```
+
+### Network graph
+```{r}
+i <- 1
+cormat <- cor(stmOut$theta[stmOut$settings$covariates$betaindex==i,])
+cormat <- ifelse(cormat >=0.05, cor, 0)
+# 
+g <- igraph::simplify(igraph::graph.adjacency(cormat, mode = "undirected", weight=TRUE))
+igraph::V(g)$name <- topics.df$topic_name
+igraph::V(g)$props <- colMeans(stmOut$theta)
+
+p1 <- topicCorrNetwork(g, stmOut$settings$covariates$yvarlevels[i])
+# 
+ggsave(
+      paste0("../figs/corrplot",i,".png"),
+      p1,
+      dpi = 300,
+      width = 9,
+      height = 6
+    )
+```
+
+### Overlapping Correlation
+Pairs of topics where an edge exists in both Newspaper, we denote with a light blue dot.
+Pairs of topics where Newspaper1, but not Newspaper2 have an edge between them, we denote with a red square, and those where Newspaper2, but not Newspaper1 have an edge between them we denote with a blue square.
+We then sort the matrix by topics that are similarly correlated with other topics in Newspaper1 and Newspaper2 to those that are not similarly correlated.
+```{r}
+png("../figs/overlapping_correlation.png")
+topicCorrCompare(1,5)
+dev.off()
+```
+
 ## Sentiment analysis

### 2018-02-16 paper/R/02_cleanAndCombine.Rmd
add sentiemtn analysis

@@
 ```{r}
-# pat1 <- "\\w\\.de/politik/deutschland"
-# pat2 <- "\\w\\.de/politik/inland"
-# pat3 <- "\\w\\.de/politik/wahl"
-# pat4 <- "\\w\\.de/politik/bundestagswahl"
-# pat5 <- "tagesschau.de/inland"
+pat1 <- "\\w\\.de/politik/deutschland"
+pat2 <- "\\w\\.de/politik/inland"
+pat3 <- "\\w\\.de/politik/wahl"
+pat4 <- "\\w\\.de/politik/bundestagswahl"
+pat5 <- "tagesschau.de/inland"
+
+df %>%
+  mutate(politics = ifelse(grepl(paste(pat1,pat2,pat3,pat4,pat5,
+                      sep="|"), url, perl = TRUE),1,0)) -> df
+
+#........................
+# pat <- paste("cdu","csu","union","spd","fdp","afd",
+#              "linkspartei","die linke","die grünen","bündnis 90", sep="|")
 # 
 # df %>%
-#   mutate(politics = ifelse(grepl(paste(pat1,pat2,pat3,pat4,pat5,
-#                       sep="|"), url, perl = TRUE),1,0)) -> df
+#   mutate(politics = ifelse(grepl(pat, title_text, ignore.case = TRUE),1,0)) -> df
 
-#........................
-pat <- paste("cdu","csu","union","spd","fdp","afd",
-             "linkspartei","die linke","die grünen","bündnis 90", sep="|")
-
-df %>%
-  mutate(politics = ifelse(grepl(pat, title_text, ignore.case = TRUE),1,0)) -> df
-```
-
-```{r}
 btw <- df %>% filter(politics==1)
-```
-
-```{r}
-btw %>%
-  group_by(date, site) %>%
-  dplyr::summarize(obs = n()) %>%
-  ggplot(aes(date, obs, color = factor(site))) +
-  geom_line() +
-  #geom_vline(aes(xintercept=as.Date("2017-09-24")),
-  #           linetype = 2, color="grey40") +
-  #geom_vline(aes(xintercept=as.Date("2017-11-20")),
-  #               linetype = 2, color="grey40") +
-  #scale_color_manual(values = col) +
-  labs(x="", y="Count",color="") +
-  scale_x_date(breaks = date_breaks("2 weeks"), labels=date_format("%d.%m", tz="CET"))
 ```
@@
 ## Preparation
-```{r}
-btw <- btw %>% 
-  #mutate(ownership = ifelse(site == "Tagesschau.de", "public", "private"))
-  filter(!grepl("sturm", url) |
-           site != "Tagesschau.de") %>%
-  filter(!grepl("Deutsche Bahn", text) | 
-           site!="Tagesschau.de") %>%
-  filter(!grepl("bahnstrecke", text) | 
-           site!="Tagesschau.de")
-```
 

### 2018-02-16 paper/R/04_Modelresults.Rmd
add sentiemtn analysis

@@
 ```{r}
-sagelabs <- sageLabels(stmOut, 25)
+sagelabs <- sageLabels(stmOut, 20)
 ```
@@
 
-## 3.5 Plotquote
-Take a closer look to those topics that are discussed most different.
+## Sentiment analysis
 
-```{r fig.height=6}
-plotQuote(c(paste(sagelabs$cov.betas[[1]]$problabels[23,], collapse="\n"),
-            paste(sagelabs$cov.betas[[2]]$problabels[23,], collapse="\n")))
+```{r}
+sent <- c(
+  # positive Wörter
+  readLines("dict/SentiWS_v1.8c_Negative.txt",
+            encoding = "UTF-8"),
+  # negative Wörter
+  readLines("dict/SentiWS_v1.8c_Positive.txt",
+            encoding = "UTF-8")
+) %>% lapply(function(x) {
+  # Extrahieren der einzelnen Spalten
+  res <- strsplit(x, "\t", fixed = TRUE)[[1]]
+  return(data.frame(words = res[1], value = res[2],
+                    stringsAsFactors = FALSE))
+}) %>%
+  bind_rows %>% 
+  mutate(word = gsub("\\|.*", "", words) %>% tolower,
+         value = as.numeric(value)) %>% 
+  # manche Wörter kommen doppelt vor, hier nehmen wir den mittleren Wert
+  group_by(word) %>% summarise(value = mean(value)) %>% ungroup
 ```
+
+Apply the dictionary on the artciles
+
+```{r, message=FALSE, warning=FALSE, include=FALSE}
+# Tokenize text
+token <- btw.2 %>%
+  unnest_tokens(word, text)
+
+# Combine with sentiment values
+sentDF <- left_join(token, sent, by="word") %>% 
+  mutate(sentiment = as.numeric(value)) %>% 
+  filter(!is.na(sentiment)) 
+```
+
+Calculate the number of total articles to weight the senitiment value.
+
+```{r}
+sentDF.red <- sentDF %>%
+
+  # Count number of articles by medium
+  group_by(site) %>% 
+  add_tally() %>%
+  ungroup() %>%
+  mutate(totalcount = n) %>%
+  select(-n) %>%
+
+  # count number of articles by medium and topic
+  group_by(site, topic_name) %>%
+  add_tally() %>%
+  ungroup() %>%
+  mutate(count = n) %>%
+  mutate(weight = count/totalcount) %>%
+
+  # calculate weight and weighted sentiment score
+  group_by(site, topic_name) %>%
+  summarize(sent_value = mean(sentiment),
+            weight = mean(weight)) %>%
+  mutate(weighted = sent_value*weight)
+```
+
+### Plot Sentiment
+
+Unweighted
+```{r fig.height=12}
+sentDF.red %>%
+  ggplot(aes(topic_name, sent_value)) +
+  geom_col(fill=col[3], alpha=0.8) +
+  coord_flip() +
+  facet_wrap(~site, ncol = 7) +
+  labs(x="", y="sentiment value") +
+  theme(axis.text.x = element_text(size=10, angle = 90))
+
+ggsave(filename = "../figs/sentiment.png", device = "png",width = 12, height = 8,
+dpi = 600)
+```
+
+weighted
+```{r fig.height=12}
+sentDF.red %>%
+  ggplot(aes(topic_name, weighted)) +
+  geom_col(fill=col[3], alpha=0.8) +
+  coord_flip() +
+  facet_wrap(~site, ncol = 7) +
+  labs(x="", y="sentiment value") +
+  theme(axis.text.x = element_text(size=10, angle = 90))
+
+ggsave(filename = "../figs/sent_weighted.png", device = "png",width = 12, height = 8,
+dpi = 600)
+```
+
+### Radar plot
+```{r}
+library(radarchart)
+```
+
+```{r}
+sentDF.red %>% 
+  select(site, topic_name, sent_value) %>%
+  spread(key=site, value=sent_value) %>%
+  ungroup() -> radar
+```
+
+```{r}
+chartJSRadar(scores = radar, labelSize = 8, 
+             scaleStartValue = -0.15,
+             maxScale = 0, 
+             showToolTipLabel = TRUE,
+             width = 8, height = 8)
+```

### 2018-02-18 paper/R/04_Modelresults.Rmd
new model results (k=35)

--- 2018-02-16 paper/R/04_Modelresults.Rmd
@@
 ---
-title: "Model Results"
+title: "Whats reported in the news?"
 subtitle: ""
@@
 theme_set(
-  theme_bw(base_family = "Roboto", base_size = 8) +
+  theme_bw(base_family = "Roboto", base_size = 10) +
     theme(
-      plot.title = element_text(size = 10,
+      plot.title = element_text(size = 12,
                                 margin = margin(0, 0, 4, 0, "pt")),
@@
 
-# 2. Data 
 ```{r caching, echo = FALSE}
@@
 
+I conduct a STM (Strucutral Topic Molde) estimation on a sample of 11,919 online news articles from seven news provider about domestic politics: Bild.de, DIE WELT, FOCUS ONLINE, SPIEGEL ONLINE, Stern.de, ZEIT ONLINE, Tagesschau.de.
+The articles are dated from 01.06.2017 to 31.12.2017 (German federal elections took place on 24th of September 2017.).
+I first extract all online articles using the the [Eventregistry API](http://eventregistry.org/documentation).
+Then all articles from the section "domestic policy" are filtered by checking the URL structure.
+
+To discover the latent topics in the corpus, the structural topic modeling (STM) developed by [Roberts (2016)](https://scholar.princeton.edu/sites/default/files/bstewart/files/a_model_of_text_for_experimentation_in_the_social_sciences.pdf) is applied.
+The STM is an unsupervised machine learning approach that models topics as multinomial distributions of words and documents as multinomial distributions of topics, allowing to incorporate external variables that effect both, topical content and topical prevalence.
+I will included the news provider as a control for both the topical content and the topical prevalence.
+Additional, the month an article was published is included as a control for the topical prevalence.
+The number of topics is set to 35.
+
 ## Distribution of articles
+
+The Figures below show the distribution of the number of articles from the respective news sources by date. There is a high peak around the federal elections on September, 24th.
+
 ```{r message=FALSE, warning=FALSE}
@@
 
+![plot1](../figs/bar.png)
 ```{r message=FALSE, warning=FALSE}
@@
 
-# 3. Model Results
+![plot1](../figs/timeline.png)
+
+# 2. Model Results
+
 ```{r echo = FALSE}
@@
 ## Label topics
-```{r}
-sagelabs <- sageLabels(stmOut, 25)
-```
+
+In order to improve readability and traceability, I assign a shorter name to the topics based on the most common words.
 
 ```{r}
-stmOut$settings$covariates$yvarlevels
-```
+sagelabs <- sageLabels(stmOut, 20)
 
-### Label topics based on Bild.de
-
-After reviewing a sample of articles assigned to the respective topic, we assign a shorter name to the topics based on the most common words in order to improve readability and traceability.
-```{r}
-sagelabs$cov.betas[[1]]$problabels[,1:5]
+sagelabs$cov.betas[[2]]$problabels[,1:4]
 ```
@@
 topics <- matrix(c(1, "SPD, M.Schulz", 2, "A.Merkel vs. Schulz", 3, "Jamaica coalition", 4, "Diesel scandal", 
-                   5, "H.Kohl", 6, "Federal Elections", 7, "EU policies, refugees", 8, "Political trends in GER", 
-                   9, "AfD in Parliament", 10, "A.Merkel", 11, "Deportation, radicalization, refugees", 
-                   12, "Christian, Berlin, Bruch", 13, "Climate policy, Die Grünen", 14, "Seehofer vs. Söder", 
-                   15, "D.Trump", 16, "Great coalition", 17, "CDU/CSU", 18, "Elections in Niedersachen", 
-                   19, "Budget statistics, Welfare policy", 20, "AfD in social media", 21, "DIE LINKE", 
-                   22, "German armed forces, Mali", 23, "Nuclear Waste, Weather reports", 
-                   24, "Innenministerium, Verfassungsschutz", 
-                   25, "Terror attack (Amri)", 26, "G20 in Hamburg", 27, "Spahn (CDU)", 
-                   28, "Steinmeier", 29, "German armed forces", 30, "AfD", 31, "Women empowerment", 
-                   32, "Diplomatic relations w Turkey, Russia", 33, "Election polls", 34, "Votings in parliament", 
-                   35, "F.Petri, Staatsanwaldschaft"), ncol=2, byrow=T)
+                   5, "H.Kohl", 6, "A.Merkel", 7, "Federal Election results", 8, "CSU, Seehofer, Söder", 
+                   9, "Deportation, radicalization, refugees", 10, "Parliament (Bundestag)", 
+                   11, "DIE LINKE, W.Schäuble", 12, "Refugees in GER", 13, "G.Schröder, IT Topics", 
+                   14, "B90/Die Grüne", 
+                   15, "D.Trump, antisemitism", 16, "Great coalition", 17, "AfD, in social media", 
+                   18, "Budget statistics, Welfare policy", 
+                   19, "Rubbish", 20, "Verfassungsschutz, Terror attacks", 21, "German armed forces, Drones, Mali", 
+                   22, "EU policies, Weather", 23, "Elections in Niedersachsen", 24, "CDU, social media", 
+                   25, "Political talkshows", 26, "Bundestag, Steinmeier, Maas", 
+                   27, "Surveys, public statistics", 28, "Election polls", 
+                   29, "AfD", 30, "Court sentences, NSU trial", 31, "German armed forces, v.d.Leyen", 
+                   32, "G20 in Hamburg", 33, "Diplomatic relations w Turkey, Russia", 
+                   34, "Terror attacks, polics reports", 35, "CDU/CSU H.Seehofer, Obergrenze"), ncol=2, byrow=T)
 
@@
 
-## Assign a topic to each document (choose by gamma)
+Next, we can assign a topic to each document (topic with highest postertior gamma)
+
 ```{r Extract wtp and dtp}
@@
 
-### now we can inspect the unclear topics
+##### How is the top-gamma value distributed among the corpus?
+
 ```{r}
-btw.2 %>% filter(topic==23) %>% select(title, gamma, url) %>%
+btw.2 %>%
+  ggplot(aes(gamma)) +
+  geom_density(color = col[3],
+               fill = col[3], alpha=.7) +
+  labs(x="Distribution of gamma value")
+```
+
+#### Inspect the unclear topics
+```{r}
+btw.2 %>% filter(topic==13) %>% select(title, gamma, url) %>%
   arrange(desc(gamma)) %>%
+  top_n(10) %>%
   htmlTable::htmlTable(align="l")
+```
+
+```{r}
+btw.2 %>% filter(topic==10) %>% select(title, gamma, url) %>%
+  arrange(desc(gamma)) %>%
+  top_n(10) %>%
+  htmlTable::htmlTable(align="l")
+```
+
+The plotQuote function allows to inspect die most common words of a topic for each covariate. Here I check for topic 3 (Jamaica coalition)
+
+```{r fig.height=11, fig.width=5}
+topic <- 3
+
+plotQuote(c(paste(sagelabs$cov.betas[[1]]$problabels[topic,], collapse="\n"),
+            paste(sagelabs$cov.betas[[2]]$problabels[topic,], collapse="\n"),
+            paste(sagelabs$cov.betas[[3]]$problabels[topic,], collapse="\n"),
+            paste(sagelabs$cov.betas[[4]]$problabels[topic,], collapse="\n"),
+            paste(sagelabs$cov.betas[[5]]$problabels[topic,], collapse="\n"),
+            paste(sagelabs$cov.betas[[6]]$problabels[topic,], collapse="\n"),
+            paste(sagelabs$cov.betas[[7]]$problabels[topic,], collapse="\n")))
 ```
@@
 
-### in the overall corpus
+In order to get an initial overview of the results, Figure \ref{fig_topic_proportion} displays the topics ordered by their expected frequency across the corpus (left side of the Figure) and the expected proportion of a topic in public media minus the expected proportion of topic use in private media (right side of the Figure).
+Thus topics more associated with public media appear to the right of zero.
+To assign a label to each topic, I looked at the most frequent words in that topic and the most representative articles
+
+##### Here, I create a Dataframe that contains the columns means of theta (per topic and covariate level)
 
@@
 
-p1 <- ggplot(frequency, aes(x=reorder(topic, frequency), y=frequency)) + 
-    geom_col(fill=col[1], alpha=0.8) +
-    coord_flip() +
-    labs(x="", y="expected frequency") +
-    theme(axis.text.x = element_text(size=8),
-          axis.text.y = element_text(size=11),
-          axis.title = element_text(size=10))
-
-p1
-```
-
-Alternatively we can show the expected frequency separated by ownership:
-
-```{r}
-freq %>% left_join(., topics.df, by = "topic") %>%
-  ggplot(aes(reorder(topic_name,freq), freq, fill=factor(ownership))) +
-  geom_col() +
-  scale_fill_manual(values = col[c(1,3)]) +
-  coord_flip() +
-  theme(#axis.text.y = element_blank(),
-          axis.text.y = element_text(size=9),
-          axis.title = element_text(size=10)) +
-    labs(x="", y="Expected frequency") 
-```
-
-### by site
-```{r}
-plotNewspaperHistogram(11)
-```
-
-Create a Df that contains the columns means of theta (per topic and covariate level)
-```{r}
 freq <- tapply(stmOut$theta[,1], stmOut$settings$covariates$betaindex, mean)
@@
 
-plots the expected proportion of topic use in public media minus the expected proportion of topic use in private media. Thus topics more associated with public media appear to the right of zero.
+#### Next, we can plot the expected proportion of topic use in the overall corpus vs. the expected proportion of topic use for each medium.
 
-```{r}
-ggplot(freq, aes(reorder(topic_name,frequency), freq)) +
-  geom_col(fill = col[1]) +
+```{r fig.height=6}
+p1 <- ggplot(frequency, aes(x=reorder(topic, frequency), y=frequency)) + 
+    geom_col(fill=col[1], alpha=0.8) +
+    coord_flip() +
+    labs(x="", y="expected frequency") +
+    theme(axis.text.x = element_text(size=8),
+          axis.text.y = element_text(size=11),
+          axis.title = element_text(size=10))
+
+p1
+```
+
+```{r fig.width=12}
+p2 <- ggplot(freq, aes(reorder(topic_name,frequency), freq)) +
+  geom_col(fill = col[3]) +
   #scale_fill_manual(values = col[1]) +
   coord_flip() +
-  facet_wrap(~site, ncol = 7)
-  theme(axis.text.y = element_blank(),
-          #axis.text.y = element_text(size=11),
+  facet_wrap(~site, ncol = 7) +
+  theme(
+    #axis.text.y = element_blank(),
+          axis.text.y = element_text(size=11),
           axis.title = element_text(size=10)) +
-    labs(x="", y="difference in expected frequency (public-private)")
+    labs(x="", y="expected frequency")
 
 p2 
-
-# ggsave(filename = "../figs/topic_proportion.png", device = "png",width = 12, height = 10,
-# dpi = 600)
-```
-
-```{r fig.height=11, fig.width=5}
-topic <- 11
-
-plotQuote(c(paste(sagelabs$cov.betas[[1]]$problabels[topic,], collapse="\n"),
-            paste(sagelabs$cov.betas[[2]]$problabels[topic,], collapse="\n"),
-            paste(sagelabs$cov.betas[[3]]$problabels[topic,], collapse="\n"),
-            paste(sagelabs$cov.betas[[4]]$problabels[topic,], collapse="\n"),
-            paste(sagelabs$cov.betas[[5]]$problabels[topic,], collapse="\n"),
-            paste(sagelabs$cov.betas[[6]]$problabels[topic,], collapse="\n"),
-            paste(sagelabs$cov.betas[[7]]$problabels[topic,], collapse="\n")))
 ```
@@
 ## 3.2. Difference in topic prevalence
-The estimateEffect() function explores how prevalence of topics varies across documents according to document covariates (metadata).
-First, users must specify the variable that they wish to use for calculating an effect.
-If there are multiple variables specified in estimateEffect(), then all other variables are held at their sample median.
-These parameters include the expected proportion of a document that belongs to a topic as a function of a covariate, or a first difference type estimate, where topic prevalence for a particular topic is contrasted for two groups.
+
+To identify which of these differences is significant, the conditional expectation of topic prevalence for given document characteristics can be estimated.
+More specifically, I estimate a linear model, where the documents are observations, the dependent variable is the posterior probability of a topic and the covariates are the metadata of documents (see equation below).
+
+$$
+\theta_d=\alpha+\beta_1x_{ownership}+\beta_2x_{month}+\epsilon
+$$
+
+The estimateEffect() uses the method of composition to incorporate uncertainty in the dependent variable, drawing a set of topic proportions from the variational posterior repeated times and compute the coefficients as the average over all results.
 
@@
 ```
+
+Here, I create a dataframe that contains the results of the estimation.
 
@@
 out1 <- list(call=effect$call, topics=effect$topics, tables=tables)
-```
 
-```{r}
 coeff <- as.data.frame(do.call(rbind,out1$tables))
@@
 
-```{r}
+The following figure shows the regression results for each news page. The coefficients indicate the deviation from the base value of Bild.de.
 
+```{r fig.height=8, fig.width=12}
 p1 <- coeff %>% 
@@
 
-# ggsave(plot = p1, filename = "../figs/estimates.png", device = "png",width = 10, height = 7,
-# dpi = 600)
+ggsave(plot = p1, filename = "../figs/estimates.png", device = "png",width = 10, height = 7,
+dpi = 600)
 ```
 
-## 3.4 Distance metric
-Compute different metrices and compare them.
+## Sentiment analysis
 
-Compute the Jensen Shannon divergence of the word-topic probability.
-The K-by-V (number of words in the vocabulary) matrix logbeta contains the natural log of the probability of seeing each word conditional on the topic.
+The idea of Sentiment analysis is to determine the attitude of a writer through online text data toward certain topic or the overall tonality of a document.
+
+Lexical or “bag-ofwords” approaches are commonly used.
+In that approach, the researcher provides pre-defined dictionaries (lists) of words associated with a given emotion, such as negativity.
+The target text is then deconstructed into individual words (or tokens) and the frequencies of words contained in a given dictionary are then calculated.
+
+#### 1. Load sentiment dictionary.
+
+[SentimentWortschatz](http://wortschatz.uni-leipzig.de/de/download), or SentiWS for short, is a publicly available German-language resource for sentiment analysis, opinion mining etc.
+It lists positive and negative polarity bearing words weighted within the interval of [-1; 1] plus their part of speech tag, and if applicable, their inflections.
+The current version of SentiWS (v1.8b) contains 1,650 positive and 1,818 negative words, which sum up to 15,649 positive and 15,632 negative word forms incl.
+their inflections, respectively.
+It not only contains adjectives and adverbs explicitly expressing a sentiment, but also nouns and verbs implicitly containing one.
 
 ```{r}
-k <- stmOut$settings$dim$K
-p <- length(stmOut$settings$covariates$yvarlevels)
+sent <- c(
+  # positive Wörter
+  readLines("dict/SentiWS_v1.8c_Negative.txt",
+            encoding = "UTF-8"),
+  # negative Wörter
+  readLines("dict/SentiWS_v1.8c_Positive.txt",
+            encoding = "UTF-8")
+) %>% lapply(function(x) {
+  # Extrahieren der einzelnen Spalten
+  res <- strsplit(x, "\t", fixed = TRUE)[[1]]
+  return(data.frame(words = res[1], value = res[2],
+                    stringsAsFactors = FALSE))
+}) %>%
+  bind_rows %>% 
+  mutate(word = gsub("\\|.*", "", words) %>% tolower,
+         value = as.numeric(value)) %>% 
+  # manche Wörter kommen doppelt vor, hier nehmen wir den mittleren Wert
+  group_by(word) %>% summarise(value = mean(value)) %>% ungroup
+```
+
+#### 2. Apply the dictionary on the artciles.
+
+We now take each word in each article and assign a sentiment value for that word. I only use articles that have been assigned a topic with a probability of over 90% (gamma > 0.9).
+
+```{r, message=FALSE, warning=FALSE, include=FALSE}
+# Tokenize text
+token <- btw.2 %>%
+  filter(gamma >= 0.9) %>%
+  filter(topic != 19) %>%
+  unnest_tokens(word, text)
+
+# Combine with sentiment values
+sentDF <- left_join(token, sent, by="word") %>% 
+  mutate(sentiment = as.numeric(value)) %>% 
+  filter(!is.na(sentiment)) 
+```
+
+#### 3. Calculate sentiment value
+
+calculate weight:
+
+$$
+\text{weight} = \frac{\text{Total Articles, by site & topic}}{\text{Total Articles, by site}}
+$$
+
+```{r}
+# Calculate weight
+btw.2 <- btw.2 %>%
+
+  # how many articles per site & topic?
+  group_by(site, topic) %>%
+  add_tally() %>%
+  ungroup() %>%
+  mutate(count = n) %>%
+  select(-n) %>%
+
+  # how many articles per site?
+  group_by(site) %>%
+  add_tally() %>%
+  ungroup() %>%
+  mutate(totalcount = n) %>%
+  select(-n) %>%
+
+  # calculate weight
+  mutate(weight = count/totalcount)
+```
+
+Group by article ID and calculate the mean sentiment value of each article.
+
+```{r}
+sentDF.red <- sentDF %>%
+
+  # calculate weight and weighted sentiment score
+  group_by(articleID) %>%
+  summarise(sent_value = mean(sentiment)) %>%
+
+  # leftjoin with btw
+  left_join(., btw.2 %>% select(articleID, topic, topic_name,
+                                title, url, site, gamma, weight),
+            by="articleID") %>%
+  mutate(weighted = sent_value*weight)
+```
+
+### Plot Sentiment
+
+#### 1. by topic
+```{r fig.height=10, fig.width=12}
+p1 <- sentDF.red %>%
+  group_by(topic_name, topic) %>%
+  summarise(sent_value = mean(sent_value)) %>%
+  ggplot(aes(reorder(topic_name, sent_value), sent_value)) +
+  geom_col(fill=col[3], alpha=0.8) +
+  coord_flip() +
+  labs(x="", y="sentiment value (unweighted)",
+       title = "sentiment value (unweighted)") +
+  theme(
+        axis.text.y = element_text(size = 10))
+
+p2 <- sentDF.red %>%
+  group_by(topic_name, topic) %>%
+  summarise(weighted = mean(weighted),
+            sent_value = mean(sent_value)) %>%
+  ggplot(aes(reorder(topic_name, sent_value), weighted)) +
+  geom_col(fill=col[1], alpha=0.8) +
+  coord_flip() +
+  labs(x="", y="sentiment value (weighted)",
+       title = "sentiment value (weighted)") +
+  theme(
+        axis.text.y = element_blank())
+
+p1 + p2
+```
+
+#### 2.by site
+
+```{r fig.width=12}
+p1 <- sentDF.red %>%
+  group_by(site) %>%
+  summarise(sent_value = mean(sent_value)) %>%
+  ggplot(aes(reorder(site, sent_value), sent_value)) +
+  geom_col(fill=col[3], alpha=0.8) +
+  coord_flip() +
+  labs(x="", y="sentiment value (unweighted)",
+       title = "sentiment value (unweighted)") +
+  theme(
+        axis.text.y = element_text(size = 10))
+
+p2 <- sentDF.red %>%
+  group_by(site) %>%
+  summarise(weighted = mean(weighted),
+            sent_value = mean(sent_value)) %>%
+  ggplot(aes(reorder(site, sent_value), weighted)) +
+  geom_col(fill=col[1], alpha=0.8) +
+  coord_flip() +
+  labs(x="", y="sentiment value (weighted)",
+       title = "sentiment value (weighted)") +
+  theme(
+        axis.text.y = element_blank())
+
+p1 + p2
+```
+
+#### 3. By site and topic
+
+```{r fig.height=10, fig.width=12}
+sentDF.red %>%
+  group_by(site, topic_name, topic) %>%
+  summarise(sent_value = mean(sent_value)) %>%
+  ggplot(aes(reorder(topic_name, topic), sent_value)) +
+  geom_col(fill=col[3], alpha=0.8) +
+  coord_flip() +
+  facet_wrap(~site, ncol = 7) +
+  labs(x="", y="sentiment value (unweighted)",
+       title = "sentiment value (unweighted)") +
+  theme(axis.text.y = element_text(size=12))
+
+ggsave(filename = "../figs/sent_weighted.png", device = "png",width = 12, height = 8,
+dpi = 600)
+```
+
+```{r fig.height=10, fig.width=12}
+sentDF.red %>%
+  group_by(site, topic_name, topic) %>%
+  summarise(weighted = mean(weighted)) %>%
+  ggplot(aes(reorder(topic_name, topic), weighted)) +
+  geom_col(fill=col[1], alpha=0.8) +
+  coord_flip() +
+  facet_wrap(~site, ncol = 7) +
+  labs(x="", y="sentiment value (weighted)",
+       title = "sentiment value (weighted)") +
+  theme(axis.text.y = element_text(size=12))
+```
+
+### Radar plot
+
+```{r}
+library(radarchart)
+```
+
+Select topics to be analyzed:
+
+1: "SPD, M.Schulz"
+2: "A.Merkel vs. Schulz"
+3: "Jamaica coalition"
+6: "A.Merkel"
+8: "CSU, Seehofer, Söder"
+14: "B90/Die Grüne"
+16: "Great coalition"
+17: "AfD, in social media",
+24: "CDU, social media"
+29: "AfD"
+
+```{r}
+keep <- c(1,2,3,6,8,14,16,17,24,29)
+```
+
+#### Unweighted
+```{r}
+sentDF.red %>% 
+  filter(topic %in% keep) %>%
+  group_by(site, topic_name) %>%
+  summarise(sent_value = mean(sent_value)) %>%
+  spread(key=site, value=sent_value) %>%
+  ungroup() -> radar
 ```
@@
 ```{r}
-## Find all combinations of ylevel
-comb.matrix <- matrix(0, 
-                      nrow= p^2, 
-                      ncol = 2)
-
-z <- 1
-for (i in 1:p) {
-  for (j in 1:p) {
-    comb.matrix[z,1] <- stmOut$settings$covariates$yvarlevels[i]
-    comb.matrix[z,2] <- stmOut$settings$covariates$yvarlevels[j]
-    z <- z+1
-  }
-}
+chartJSRadar(scores = radar, labelSize = 8, 
+             scaleStartValue = -0.2,
+             maxScale = 0.1, 
+             showToolTipLabel = TRUE,
+             width = 8, height = 8)
 ```
 
-### Calculate L1 Norm
+#### Weighted
 ```{r}
-# Create empty matrix
-l1.matrix <- matrix(0, nrow = nrow(comb.matrix), ncol = k)
-names(l1.matrix) <- 1:k
-
-# Populate matrix with JSD Values
-z <- 1
-for (i in 1:p) {
-
-    #print(paste("ylevel = ", i))
-    base <- exp(stmOut$beta$logbeta[[i]])
-    compare1 <- exp(stmOut$beta$logbeta[[1]])
-    compare2 <- exp(stmOut$beta$logbeta[[2]])
-
-  for (j in 1:k) {
-
-    #print(paste("topic = ", j))
-    l1.matrix[z,j] <- sum(abs(base[j,]-compare1[j,]))
-    l1.matrix[z+1,j] <- sum(abs(base[j,]-compare2[j,]))
-
-  }
-    z <- z+p
-}
-
+sentDF.red %>% 
+  filter(topic %in% keep) %>%
+  group_by(site, topic_name) %>%
+  summarise(weighted = mean(weighted)) %>%
+  spread(key=site, value=weighted) %>%
+  ungroup() -> radar
 ```
@@
 ```{r}
-## Create DF
-l1.df <- as.data.frame(l1.matrix) 
-colnames(l1.df) <- 1:k
-
-l1.df <- l1.df %>% 
-  mutate(News1 = comb.matrix[,1],
-         News2 = comb.matrix[,2]) %>%
-  melt(.,id=c("News1","News2"), value.name="L1Norm",
-       variable.name = "topic") %>%
-  mutate(topic = as.integer(topic)) %>%
-  left_join(., topics.df, by="topic")
+chartJSRadar(scores = radar, labelSize = 8, 
+             scaleStartValue = -0.005,
+             maxScale = 0.002, 
+             showToolTipLabel = TRUE,
+             width = 8, height = 8)
 ```
-
-### Calculate Cosine Similarity
-```{r}
-# Create empty matrix
-cosine.matrix <- matrix(0, nrow = nrow(comb.matrix), ncol = k)
-names(cosine.matrix) <- 1:k
-
-# Populate matrix with JSD Values
-z <- 1
-for (i in 1:p) {
-
-    #print(paste("ylevel = ", i))
-    base <- exp(stmOut$beta$logbeta[[i]])
-    compare1 <- exp(stmOut$beta$logbeta[[1]])
-    compare2 <- exp(stmOut$beta$logbeta[[2]])
-
-  for (j in 1:k) {
-
-    #print(paste("topic = ", j))
-    cosine.matrix[z,j] <- CosSim(base[j,],compare1[j,])
-    cosine.matrix[z+1,j] <- CosSim(base[j,],compare2[j,])
-
-  }
-    z <- z+p
-}
-
-```
-
-```{r}
-## Create DF
-cosine.df <- as.data.frame(cosine.matrix) 
-colnames(cosine.df) <- 1:k
-
-cosine.df <- cosine.df %>% 
-  mutate(News1 = comb.matrix[,1],
-         News2 = comb.matrix[,2]) %>%
-  melt(.,id=c("News1","News2"), value.name="CosineSimilarity",
-       variable.name = "topic") %>%
-  mutate(topic = as.integer(topic)) %>%
-  left_join(., l1.df, by=c("News1","News2","topic"))
-```
-
-### Calculate KLD
-```{r}
-# Create empty matrix
-kld.matrix <- matrix(0, nrow = nrow(comb.matrix), ncol = k)
-names(kld.matrix) <- 1:k
-
-# Populate matrix with JSD Values
-z <- 1
-for (i in 1:p) {
-
-    #print(paste("ylevel = ", i))
-    base <- exp(stmOut$beta$logbeta[[i]])
-    compare1 <- exp(stmOut$beta$logbeta[[1]])
-    compare2 <- exp(stmOut$beta$logbeta[[2]])
-
-  for (j in 1:k) {
-
-    #print(paste("topic = ", j))
-    kld.matrix[z,j] <- KLD(base[j,],compare1[j,])
-    kld.matrix[z+1,j] <- KLD(base[j,],compare2[j,])
-
-  }
-    z <- z+p
-}
-```
-
-```{r}
-## Create DF
-kld.df <- as.data.frame(kld.matrix) 
-colnames(kld.df) <- 1:k
-
-kld.df <- kld.df %>% mutate(News1 = comb.matrix[,1],
-         News2 = comb.matrix[,2]) %>%
-  melt(.,id=c("News1","News2"), value.name="KLD",
-       variable.name = "topic") %>%
-  mutate(topic = as.integer(topic)) %>%
-  left_join(., cosine.df, by=c("News1","News2","topic"))
-```
-
-### Calculate JSD
-```{r}
-# Create empty matrix
-jsd.matrix <- matrix(0, nrow = nrow(comb.matrix), ncol = k)
-names(jsd.matrix) <- 1:k
-
-# Populate matrix with JSD Values
-z <- 1
-for (i in 1:p) {
-
-    #print(paste("ylevel = ", i))
-    base <- exp(stmOut$beta$logbeta[[i]])
-    compare1 <- exp(stmOut$beta$logbeta[[1]])
-    compare2 <- exp(stmOut$beta$logbeta[[2]])
-
-  for (j in 1:k) {
-
-    #print(paste("topic = ", j))
-    jsd.matrix[z,j] <- JSD(base[j,],compare1[j,])
-    jsd.matrix[z+1,j] <- JSD(base[j,],compare2[j,])
-
-  }
-    z <- z+p
-}
-```
-
-```{r}
-## Create DF
-jsd.df <- as.data.frame(jsd.matrix) 
-colnames(jsd.df) <- 1:k
-
-distance.df <- jsd.df %>% mutate(News1 = comb.matrix[,1],
-         News2 = comb.matrix[,2]) %>% 
-  melt(.,id=c("News1","News2"), value.name="JSD",
-       variable.name = "topic") %>%
-  mutate(topic = as.integer(topic)) %>%
-  left_join(., kld.df, by=c("News1","News2","topic"))
-
-rm(l1.df, jsd.df, cosine.df, kld.df)
-```
-
-### Plot 
-```{r}
-cols <- rev(brewer.pal(11, 'RdYlBu'))
-
-p1 <- distance.df %>%
-  filter(!topic %in% c("11","15")) %>%
-  filter(News1!=News2) %>%
-  filter(News1=="private") %>%
-  ggplot(aes(News1, reorder(factor(topic_name),JSD), fill = JSD)) + 
-  geom_tile() +
-  scale_fill_gradientn(colours = cols) +
-  labs(x="", y="") +
-  theme_bw(base_family = "Roboto", base_size = 11) +
-  theme(axis.text.x = element_blank(),
-        legend.position = "top",
-        plot.background = element_rect(fill = 'transparent', colour = 'transparent'),
-        strip.background = element_rect(fill = 'transparent', colour = 'transparent'),
-        axis.ticks = element_line(colour = 'transparent'))
-
-p2 <- distance.df %>%
-  filter(!topic %in% c("11","15")) %>%
-  filter(News1!=News2) %>%
-  ggplot(aes(News1, reorder(factor(topic_name),JSD), fill = KLD)) + 
-  geom_tile() +
-  scale_fill_gradientn(colours = cols) +
-  labs(x="", y="") +
-  theme_bw(base_family = "Roboto", base_size = 11) +
-  theme(axis.text.y = element_blank(),
-        legend.position = "top",
-        plot.background = element_rect(fill = 'transparent', colour = 'transparent'),
-        strip.background = element_rect(fill = 'transparent', colour = 'transparent'),
-        axis.ticks = element_line(colour = 'transparent'))
-
-p3 <- distance.df %>%
-  filter(!topic %in% c("11","15")) %>%
-  filter(News1!=News2) %>%
-  filter(News1=="private") %>%
-  ggplot(aes(News1, reorder(factor(topic_name),JSD), 
-             fill = CosineSimilarity)) + 
-  geom_tile() +
-  scale_fill_gradientn(colours = cols) +
-  labs(x="", y="") +
-  theme_bw(base_family = "Roboto", base_size = 11) +
-  theme(axis.text = element_blank(),
-        legend.position = "top",
-        plot.background = element_rect(fill = 'transparent', colour = 'transparent'),
-        strip.background = element_rect(fill = 'transparent', colour = 'transparent'),
-        axis.ticks = element_line(colour = 'transparent'))
-
-p4 <- distance.df %>%
-  filter(!topic %in% c("11","15")) %>%
-  filter(News1!=News2) %>%
-  filter(News1=="private") %>%
-  ggplot(aes(News1, reorder(factor(topic_name),JSD), 
-             fill = L1Norm)) + 
-  geom_tile() +
-  scale_fill_gradientn(colours = cols) +
-  labs(x="", y="") +
-  theme_bw(base_family = "Roboto", base_size = 11) +
-  theme(axis.text = element_blank(),
-        legend.position = "top",
-        plot.background = element_rect(fill = 'transparent', colour = 'transparent'),
-        strip.background = element_rect(fill = 'transparent', colour = 'transparent'),
-        axis.ticks = element_line(colour = 'transparent'))
-
-(p1 | p2 | p3 | p4 )
-
-ggsave(filename = "../figs/distance.png", device = "png",width = 12, height = 8,
-dpi = 600)
-```
-
-## 3.5 Plotquote
-Take a closer look to those topics that are discussed most different.
-
-```{r fig.height=6}
-plotQuote(c(paste(sagelabs$cov.betas[[1]]$problabels[23,], collapse="\n"),
-            paste(sagelabs$cov.betas[[2]]$problabels[23,], collapse="\n")))
-```

### 2018-02-20 paper/R/04_Modelresults.Rmd
inspect k=40

@@
 ```{r echo = FALSE}
-load("../output/models/STM 35 .Rda")
+load("../output/models/STM 40 .Rda")
 k <- stmOut$settings$dim$K
@@
 
-sagelabs$cov.betas[[2]]$problabels[,1:4]
+sagelabs$cov.betas[[3]]$problabels[,1:5]
 ```
@@
 ```{r}
-topics <- matrix(c(1, "SPD, M.Schulz", 2, "A.Merkel vs. Schulz", 3, "Jamaica coalition", 4, "Diesel scandal", 
+topics <- matrix(c(1, "SPD, M.Schulz", 2, "A.Merkel vs. Schulz", 3, "B90/Die Grüne, coalition talks", 4, "EU policies", 
                    5, "H.Kohl", 6, "A.Merkel", 7, "Federal Election results", 8, "CSU, Seehofer, Söder", 
-                   9, "Deportation, radicalization, refugees", 10, "Parliament (Bundestag)", 
-                   11, "DIE LINKE, W.Schäuble", 12, "Refugees in GER", 13, "G.Schröder, IT Topics", 
-                   14, "B90/Die Grüne", 
-                   15, "D.Trump, antisemitism", 16, "Great coalition", 17, "AfD, in social media", 
-                   18, "Budget statistics, Welfare policy", 
-                   19, "Rubbish", 20, "Verfassungsschutz, Terror attacks", 21, "German armed forces, Drones, Mali", 
-                   22, "EU policies, Weather", 23, "Elections in Niedersachsen", 24, "CDU, social media", 
-                   25, "Political talkshows", 26, "Bundestag, Steinmeier, Maas", 
+                   9, "Welt, Deutschland, Menschen", 10, "Parliament (Bundestag)", 
+                   11, "W.Schäuble", 12, "Refugees in GER", 13, "G.Schröder, IT Topics", 
+                   14, "B90/Die Grüne, climate/refugee policy", 
+                   15, "D.Trump, Israel", 16, "Great coalition", 17, "AfD, in media", 
+                   18, "Jamaica coalition", 
+                   19, "Rubbish", 20, "Terror attack Amri", 21, "German armed forces, Mali, Helicopter", 
+                   22, "Muslim, Ditib", 23, "Elections in Niedersachsen", 24, "CDU, Twitter, Saxony", 
+                   25, "Europa", 26, "Bundestag, Laws", 
                    27, "Surveys, public statistics", 28, "Election polls", 
@@
                    32, "G20 in Hamburg", 33, "Diplomatic relations w Turkey, Russia", 
-                   34, "Terror attacks, polics reports", 35, "CDU/CSU H.Seehofer, Obergrenze"), ncol=2, byrow=T)
+                   34, "Left- & Right-wing Terror", 35, "CDU/CSU H.Seehofer, Obergrenze",
+                   36, "Church", 37, "Car industry, Stuttgart", 38, "AfD, F.Petry", 39, "Statistics, welfare policy",
+                   40, "J.Spahn"), ncol=2, byrow=T)
+
+# topics <- matrix(c(1, "SPD, M.Schulz", 2, "A.Merkel vs. Schulz", 3, "Jamaica coalition", 4, "Diesel scandal", 
+#                    5, "H.Kohl", 6, "A.Merkel", 7, "Federal Election results", 8, "CSU, Seehofer, Söder", 
+#                    9, "Deportation, radicalization, refugees", 10, "Parliament (Bundestag)", 
+#                    11, "DIE LINKE, W.Schäuble", 12, "Refugees in GER", 13, "G.Schröder, IT Topics", 
+#                    14, "B90/Die Grüne", 
+#                    15, "D.Trump, antisemitism", 16, "Great coalition", 17, "AfD, in social media", 
+#                    18, "Budget statistics, Welfare policy", 
+#                    19, "Rubbish", 20, "Verfassungsschutz, Terror attacks", 21, "German armed forces, Drones, Mali", 
+#                    22, "EU policies, Weather", 23, "Elections in Niedersachsen", 24, "CDU, social media", 
+#                    25, "Political talkshows", 26, "Bundestag, Steinmeier, Maas", 
+#                    27, "Surveys, public statistics", 28, "Election polls", 
+#                    29, "AfD", 30, "Court sentences, NSU trial", 31, "German armed forces, v.d.Leyen", 
+#                    32, "G20 in Hamburg", 33, "Diplomatic relations w Turkey, Russia", 
+#                    34, "Terror attacks, polics reports", 35, "CDU/CSU H.Seehofer, Obergrenze"), ncol=2, byrow=T)
 
@@
 ```{r fig.height=11, fig.width=5}
-topic <- 3
+topic <- 12
 
@@
 
+```{r}
+sentDF.red %>% group_by(topic_name) %>%
+  top_n(5, gamma) %>%
+  select(topic_name, gamma, title) %>%
+  htmlTable::htmlTable(align="l")
+```
+
 ### Plot Sentiment
@@
 
-```{r}
-library(radarchart)
+```{r message=FALSE, warning=FALSE}
+require(ggiraph)
+require(ggiraphExtra)
 ```
@@
 
+1, "SPD, M.Schulz"
+2, "A.Merkel vs. Schulz"
+3, "B90/Die Grüne, coalition talks"
+4, "EU policies"
+5, "H.Kohl", 
+6, "A.Merkel", 
+8, "CSU, Seehofer, Söder",
+12, "Refugees in GER"
+14, "B90/Die Grüne, climate/refugee policy",
+16, "Great coalition", 
+17, "AfD, in media", 
+18, "Jamaica coalition",
+29, "AfD",
+33, "Diplomatic relations w Turkey, Russia",
+35, "CDU/CSU H.Seehofer, Obergrenze",
+38, "AfD, F.Petry")
+
 ```{r}
-keep <- c(1,2,3,6,8,14,16,17,24,29)
+#keep <- c(1,2,3,6,8,14,16,17,24,29)
+
+keep <- c(1,3,4,5,6,8,14,16,17,18,29,33,35,38)
 ```
@@
   summarise(sent_value = mean(sent_value)) %>%
-  spread(key=site, value=sent_value) %>%
+  spread(key=topic_name, value=sent_value) %>%
   ungroup() -> radar
-```
 
-```{r}
-chartJSRadar(scores = radar, labelSize = 8, 
-             scaleStartValue = -0.2,
-             maxScale = 0.1, 
-             showToolTipLabel = TRUE,
-             width = 8, height = 8)
+radar %>%
+  ggRadar(aes(color=site), rescale = F,
+          alpha = 0, legend.position = "right") +
+  labs(title = "")
 ```
@@
   summarise(weighted = mean(weighted)) %>%
-  spread(key=site, value=weighted) %>%
+  spread(key=topic_name, value=weighted) %>%
   ungroup() -> radar
+
+radar %>%
+  ggRadar(aes(color=site), rescale = F,
+          alpha = 0, legend.position = "right") +
+  labs(title = "")
 ```
-
-```{r}
-chartJSRadar(scores = radar, labelSize = 8, 
-             scaleStartValue = -0.005,
-             maxScale = 0.002, 
-             showToolTipLabel = TRUE,
-             width = 8, height = 8)
-```

### 2018-02-21 paper/docs/04_Modelresults.Rmd
k=40

--- 2018-02-20 paper/R/04_Modelresults.Rmd
@@
 
-I conduct a STM (Strucutral Topic Molde) estimation on a sample of 11,919 online news articles from seven news provider about domestic politics: Bild.de, DIE WELT, FOCUS ONLINE, SPIEGEL ONLINE, Stern.de, ZEIT ONLINE, Tagesschau.de.
+I conduct a STM (Strucutral Topic Model) estimation on a sample of 11,919 online news articles from seven news provider about domestic politics: Bild.de, DIE WELT, FOCUS ONLINE, SPIEGEL ONLINE, Stern.de, ZEIT ONLINE, Tagesschau.de.
 The articles are dated from 01.06.2017 to 31.12.2017 (German federal elections took place on 24th of September 2017.).
@@
 
-sagelabs$cov.betas[[3]]$problabels[,1:5]
+sagelabs$cov.betas[[3]]$problabels[,1:6]
 ```
@@
 ```{r}
-topics <- matrix(c(1, "SPD, M.Schulz", 2, "A.Merkel vs. Schulz", 3, "B90/Die Grüne, coalition talks", 4, "EU policies", 
-                   5, "H.Kohl", 6, "A.Merkel", 7, "Federal Election results", 8, "CSU, Seehofer, Söder", 
-                   9, "Welt, Deutschland, Menschen", 10, "Parliament (Bundestag)", 
-                   11, "W.Schäuble", 12, "Refugees in GER", 13, "G.Schröder, IT Topics", 
-                   14, "B90/Die Grüne, climate/refugee policy", 
-                   15, "D.Trump, Israel", 16, "Great coalition", 17, "AfD, in media", 
-                   18, "Jamaica coalition", 
-                   19, "Rubbish", 20, "Terror attack Amri", 21, "German armed forces, Mali, Helicopter", 
-                   22, "Muslim, Ditib", 23, "Elections in Niedersachsen", 24, "CDU, Twitter, Saxony", 
-                   25, "Europa", 26, "Bundestag, Laws", 
-                   27, "Surveys, public statistics", 28, "Election polls", 
-                   29, "AfD", 30, "Court sentences, NSU trial", 31, "German armed forces, v.d.Leyen", 
+topics <- matrix(c(1, "SPD, M.Schulz", 2, "A.Merkel vs. Schulz", 3, "B90/Die Grüne, coalition talks", 
+                   4, "EU topics: Diesel, Glyphosat, toll", 5, "H.Kohl", 6, "A.Merkel", 7, "Federal Election results",
+                   8, "Party congress (CSU and DIE LINKE)", 9, "General societal issues", 
+                   10, "Information on Federal elections (e.g. Wahlomat, election programmes)",  
+                   11, "W.Schäuble, F.Steinmeier", 12, "Refugees in GER", 13, "Auffangbecken ('Find us on Twitter')",
+                   14, "B90/Die Grüne, climate/refugee policy", 15, "D.Trump, Israel, G20", 
+                   16, "Great coalition, minority government", 17, "AfD, in media", 18, "Jamaica coalition", 
+                   19, "Rubbish", 20, "Mix (Amri, Berlin, Court)", 21, "German armed forces, Mali, Helicopter", 
+                   22, "Mix (Ditib, Weather, DB)", 23, "Elections in Niedersachsen", 24, "CDU, regional politics (Saxony)", 
+                   25, "Mix (Europa, political talkshows)", 26, "Votes in the Bundestag", 
+                   27, "Mix, Surveys, public statistics", 28, "Election polls", 
+                   29, "AfD in parliament", 30, "Mix: Sexism, Court sentences, NSU trial", 31, "German armed forces, v.d.Leyen", 
                    32, "G20 in Hamburg", 33, "Diplomatic relations w Turkey, Russia", 
-                   34, "Left- & Right-wing Terror", 35, "CDU/CSU H.Seehofer, Obergrenze",
-                   36, "Church", 37, "Car industry, Stuttgart", 38, "AfD, F.Petry", 39, "Statistics, welfare policy",
+                   34, "Terror in GER, Left- & Right-wing", 35, "CDU/CSU H.Seehofer, Obergrenze",
+                   36, "Church, Family", 37, "Car industry, Stuttgart (Mix)", 38, "AfD, F.Petry", 39, "Statistics, welfare policy",
                    40, "J.Spahn"), ncol=2, byrow=T)
@@
 ```{r fig.height=11, fig.width=5}
-topic <- 12
+topic <- 40
 
@@
 
-In order to get an initial overview of the results, Figure \ref{fig_topic_proportion} displays the topics ordered by their expected frequency across the corpus (left side of the Figure) and the expected proportion of a topic in public media minus the expected proportion of topic use in private media (right side of the Figure).
+In order to get an initial overview of the results, the figure below displays the topics ordered by their expected frequency across the corpus (left side of the Figure) and the expected proportion of a topic in public media minus the expected proportion of topic use in private media (right side of the Figure).
 Thus topics more associated with public media appear to the right of zero.
-To assign a label to each topic, I looked at the most frequent words in that topic and the most representative articles
+To assign a label to each topic, I looked at the most frequent words in that topic and the most representative articles.
+
+Keep only those articles, that are clear
+
+```{r}
+keep <- c(1,2,3,4,5,6,7,12,14,15,16,17,18,21,23,24,28,29,31,32,33,34,35,38,40)
+```
 
@@
   mutate(frequency = colMeans(stmOut$theta),
-    topic=paste(topics[,1],topics[,2], sep=": "))
+         topic = topics[,1],
+         topic_name=paste(topics[,1],topics[,2], 
+                          sep=": ")) %>%
+  filter(topic %in% keep)
 
@@
   left_join(., topics.df, by = "topic") %>%
+  filter(topic %in% keep) %>%
   mutate(topic = topic_name) %>%
@@
 ```{r fig.height=6}
-p1 <- ggplot(frequency, aes(x=reorder(topic, frequency), y=frequency)) + 
+p1 <- ggplot(frequency, aes(x=reorder(topic_name, frequency), y=frequency)) + 
     geom_col(fill=col[1], alpha=0.8) +
@@
 p1 <- coeff %>% 
+  filter(topic %in% keep) %>%
   filter(parameter %in% stmOut$settings$covariates$yvarlevels) %>%
@@
   filter(gamma >= 0.9) %>%
-  filter(topic != 19) %>%
+  filter(topic %in% keep) %>%
   unnest_tokens(word, text)

### 2018-02-21 paper/docs/backup.Rmd
k=40

--- 2018-02-16 paper/R/backup.Rmd
@@
 ```
+
+## 3.4 Distance metric
+Compute different metrices and compare them.
+
+Compute the Jensen Shannon divergence of the word-topic probability.
+The K-by-V (number of words in the vocabulary) matrix logbeta contains the natural log of the probability of seeing each word conditional on the topic.
+
+```{r}
+k <- stmOut$settings$dim$K
+p <- length(stmOut$settings$covariates$yvarlevels)
+```
+
+```{r}
+## Find all combinations of ylevel
+comb.matrix <- matrix(0, 
+                      nrow= p^2, 
+                      ncol = 2)
+
+z <- 1
+for (i in 1:p) {
+  for (j in 1:p) {
+    comb.matrix[z,1] <- stmOut$settings$covariates$yvarlevels[i]
+    comb.matrix[z,2] <- stmOut$settings$covariates$yvarlevels[j]
+    z <- z+1
+  }
+}
+```
+
+### Calculate L1 Norm
+```{r}
+# Create empty matrix
+l1.matrix <- matrix(0, nrow = nrow(comb.matrix), ncol = k)
+names(l1.matrix) <- 1:k
+
+# Populate matrix with JSD Values
+z <- 1
+for (i in 1:p) {
+
+    #print(paste("ylevel = ", i))
+    base <- exp(stmOut$beta$logbeta[[i]])
+    compare1 <- exp(stmOut$beta$logbeta[[1]])
+    compare2 <- exp(stmOut$beta$logbeta[[2]])
+
+  for (j in 1:k) {
+
+    #print(paste("topic = ", j))
+    l1.matrix[z,j] <- sum(abs(base[j,]-compare1[j,]))
+    l1.matrix[z+1,j] <- sum(abs(base[j,]-compare2[j,]))
+
+  }
+    z <- z+p
+}
+
+```
+
+```{r}
+## Create DF
+l1.df <- as.data.frame(l1.matrix) 
+colnames(l1.df) <- 1:k
+
+l1.df <- l1.df %>% 
+  mutate(News1 = comb.matrix[,1],
+         News2 = comb.matrix[,2]) %>%
+  melt(.,id=c("News1","News2"), value.name="L1Norm",
+       variable.name = "topic") %>%
+  mutate(topic = as.integer(topic)) %>%
+  left_join(., topics.df, by="topic")
+```
+
+### Calculate Cosine Similarity
+```{r}
+# Create empty matrix
+cosine.matrix <- matrix(0, nrow = nrow(comb.matrix), ncol = k)
+names(cosine.matrix) <- 1:k
+
+# Populate matrix with JSD Values
+z <- 1
+for (i in 1:p) {
+
+    #print(paste("ylevel = ", i))
+    base <- exp(stmOut$beta$logbeta[[i]])
+    compare1 <- exp(stmOut$beta$logbeta[[1]])
+    compare2 <- exp(stmOut$beta$logbeta[[2]])
+
+  for (j in 1:k) {
+
+    #print(paste("topic = ", j))
+    cosine.matrix[z,j] <- CosSim(base[j,],compare1[j,])
+    cosine.matrix[z+1,j] <- CosSim(base[j,],compare2[j,])
+
+  }
+    z <- z+p
+}
+
+```
+
+```{r}
+## Create DF
+cosine.df <- as.data.frame(cosine.matrix) 
+colnames(cosine.df) <- 1:k
+
+cosine.df <- cosine.df %>% 
+  mutate(News1 = comb.matrix[,1],
+         News2 = comb.matrix[,2]) %>%
+  melt(.,id=c("News1","News2"), value.name="CosineSimilarity",
+       variable.name = "topic") %>%
+  mutate(topic = as.integer(topic)) %>%
+  left_join(., l1.df, by=c("News1","News2","topic"))
+```
+
+### Calculate KLD
+```{r}
+# Create empty matrix
+kld.matrix <- matrix(0, nrow = nrow(comb.matrix), ncol = k)
+names(kld.matrix) <- 1:k
+
+# Populate matrix with JSD Values
+z <- 1
+for (i in 1:p) {
+
+    #print(paste("ylevel = ", i))
+    base <- exp(stmOut$beta$logbeta[[i]])
+    compare1 <- exp(stmOut$beta$logbeta[[1]])
+    compare2 <- exp(stmOut$beta$logbeta[[2]])
+
+  for (j in 1:k) {
+
+    #print(paste("topic = ", j))
+    kld.matrix[z,j] <- KLD(base[j,],compare1[j,])
+    kld.matrix[z+1,j] <- KLD(base[j,],compare2[j,])
+
+  }
+    z <- z+p
+}
+```
+
+```{r}
+## Create DF
+kld.df <- as.data.frame(kld.matrix) 
+colnames(kld.df) <- 1:k
+
+kld.df <- kld.df %>% mutate(News1 = comb.matrix[,1],
+         News2 = comb.matrix[,2]) %>%
+  melt(.,id=c("News1","News2"), value.name="KLD",
+       variable.name = "topic") %>%
+  mutate(topic = as.integer(topic)) %>%
+  left_join(., cosine.df, by=c("News1","News2","topic"))
+```
+
+### Calculate JSD
+```{r}
+# Create empty matrix
+jsd.matrix <- matrix(0, nrow = nrow(comb.matrix), ncol = k)
+names(jsd.matrix) <- 1:k
+
+# Populate matrix with JSD Values
+z <- 1
+for (i in 1:p) {
+
+    #print(paste("ylevel = ", i))
+    base <- exp(stmOut$beta$logbeta[[i]])
+    compare1 <- exp(stmOut$beta$logbeta[[1]])
+    compare2 <- exp(stmOut$beta$logbeta[[2]])
+
+  for (j in 1:k) {
+
+    #print(paste("topic = ", j))
+    jsd.matrix[z,j] <- JSD(base[j,],compare1[j,])
+    jsd.matrix[z+1,j] <- JSD(base[j,],compare2[j,])
+
+  }
+    z <- z+p
+}
+```
+
+```{r}
+## Create DF
+jsd.df <- as.data.frame(jsd.matrix) 
+colnames(jsd.df) <- 1:k
+
+distance.df <- jsd.df %>% mutate(News1 = comb.matrix[,1],
+         News2 = comb.matrix[,2]) %>% 
+  melt(.,id=c("News1","News2"), value.name="JSD",
+       variable.name = "topic") %>%
+  mutate(topic = as.integer(topic)) %>%
+  left_join(., kld.df, by=c("News1","News2","topic"))
+
+rm(l1.df, jsd.df, cosine.df, kld.df)
+```
+
+### Plot 
+```{r}
+cols <- rev(brewer.pal(11, 'RdYlBu'))
+
+p1 <- distance.df %>%
+  filter(!topic %in% c("11","15")) %>%
+  filter(News1!=News2) %>%
+  filter(News1=="private") %>%
+  ggplot(aes(News1, reorder(factor(topic_name),JSD), fill = JSD)) + 
+  geom_tile() +
+  scale_fill_gradientn(colours = cols) +
+  labs(x="", y="") +
+  theme_bw(base_family = "Roboto", base_size = 11) +
+  theme(axis.text.x = element_blank(),
+        legend.position = "top",
+        plot.background = element_rect(fill = 'transparent', colour = 'transparent'),
+        strip.background = element_rect(fill = 'transparent', colour = 'transparent'),
+        axis.ticks = element_line(colour = 'transparent'))
+
+p2 <- distance.df %>%
+  filter(!topic %in% c("11","15")) %>%
+  filter(News1!=News2) %>%
+  ggplot(aes(News1, reorder(factor(topic_name),JSD), fill = KLD)) + 
+  geom_tile() +
+  scale_fill_gradientn(colours = cols) +
+  labs(x="", y="") +
+  theme_bw(base_family = "Roboto", base_size = 11) +
+  theme(axis.text.y = element_blank(),
+        legend.position = "top",
+        plot.background = element_rect(fill = 'transparent', colour = 'transparent'),
+        strip.background = element_rect(fill = 'transparent', colour = 'transparent'),
+        axis.ticks = element_line(colour = 'transparent'))
+
+p3 <- distance.df %>%
+  filter(!topic %in% c("11","15")) %>%
+  filter(News1!=News2) %>%
+  filter(News1=="private") %>%
+  ggplot(aes(News1, reorder(factor(topic_name),JSD), 
+             fill = CosineSimilarity)) + 
+  geom_tile() +
+  scale_fill_gradientn(colours = cols) +
+  labs(x="", y="") +
+  theme_bw(base_family = "Roboto", base_size = 11) +
+  theme(axis.text = element_blank(),
+        legend.position = "top",
+        plot.background = element_rect(fill = 'transparent', colour = 'transparent'),
+        strip.background = element_rect(fill = 'transparent', colour = 'transparent'),
+        axis.ticks = element_line(colour = 'transparent'))
+
+p4 <- distance.df %>%
+  filter(!topic %in% c("11","15")) %>%
+  filter(News1!=News2) %>%
+  filter(News1=="private") %>%
+  ggplot(aes(News1, reorder(factor(topic_name),JSD), 
+             fill = L1Norm)) + 
+  geom_tile() +
+  scale_fill_gradientn(colours = cols) +
+  labs(x="", y="") +
+  theme_bw(base_family = "Roboto", base_size = 11) +
+  theme(axis.text = element_blank(),
+        legend.position = "top",
+        plot.background = element_rect(fill = 'transparent', colour = 'transparent'),
+        strip.background = element_rect(fill = 'transparent', colour = 'transparent'),
+        axis.ticks = element_line(colour = 'transparent'))
+
+(p1 | p2 | p3 | p4 )
+
+ggsave(filename = "../figs/distance.png", device = "png",width = 12, height = 8,
+dpi = 600)
+```

### 2018-02-21 paper/writing/doc.tex
k=40

--- 2018-01-19 paper/doc/doc.tex
@@
 % ----------------------
-\subsection{Interpretation}
+\subsection{Empirical Evaluation}
 
@@
 \citet{roberts_model_2016} use empirical evaluation, including a frequentist coverage analysis and compare the performance of their STM to a variety of alternatives in \citet{roberts_navigating_2016}.
-
-A way to summerize the topics in an interpretable way is to use the most frequent terms within a topic \citep{chang_reading_2009}, but the exclusivity of words to topics is equally important for communicating content.
-\citep{bischof_summarizing_2012} consider the harmonic mean of the words's rank in terms of exclusivity and frequency as a summary for a word's contribution to a topic.
-It is important to take both of these properties into account, as frequent words are often simply functional words that are necessary to discuss a topic.
-While completely exclusive words can be so rare that their information content is too low.
-\citep{roberts_stm:_2016} refer to this as the FREX (FRequency and EXclusivity) metric.
-
-\begin{align}
-	FREX_{k,\nu} = (\frac{\omega}{ECDF(\beta_{k,\nu}/\sum^K_{j=1}\beta_{j,\nu}}+\frac{1-\omega}{ECDF(\beta_{k,\nu}})^{-1},
-\end{align}
-
-with $\boldsymbol{B}$ denoted as the $KxV$ matrix of topic-conditional term probabilities.
-The first part of the equation calculates the frequency score  given by the empirical CDF of the word in it's topic distribution.
-Exclusivity is calculated by column-normalizing the beta matrix (thus representing the conditional probability of seeing the topic given the word).
-$\omega$ balances the influence of frequency and exclusivity and is set to $0.5$
-
-\section{Empirical Evaluation}
 
@@
 \end{figure}
-
-%\begin{landscape}
-%\begin{figure}[H]
-%\centering
-%	\caption{Sample articles}
-%	\includegraphics[width=\linewidth,height=.9\textheight,keepaspectratio]{../figs/topic-classification-sample.png}	
-%	\label{fig_classification}
-%\end{figure}
-%\end{landscape}
 
@@
 
-\section{Sentiment Analysis}
+\section{Distance Metric}
+
+Since the topic distribution of a text is a simple mapping of text space, similarity of two texts can be measured by computing the topic distribution.
+KL distance is the measurement of “difference” between two probabilities.
+
+We use a probability distribution distance metric related to Jensen-Shannon divergence (JSD) to compare the word-topic distribution.
+Jensen-Shannon Divergence is a positive definite measure, satisfying the following conditions: $D_{js}(a,b) \geq 0$, $D_{js}(a,b)=0$ iff $(a=b)$.
+It is also symmetric: $D_{js}(a,b)=D_{js}(b,a)$.
+Let $p(x)$ and $q(x)$ be two probability density functions, the Jensen-Shannon distance $D_{js}(p,q)$ between this two distributions is defined as:
+
+\begin{align*}
+	D_{js}(p,q)=\frac{1}{2}D_{KL}(p,\frac{p+q}{2})+\frac{1}{2}D_{KL}(q,\frac{p+q}{2})
+\end{align*}
+
+where $D_{KL}$ is the Kullback-Leibler divergence between $p$ and $q$ defined as:
+
+\begin{align*}
+	D_{KL}(p,q)=\sum_{i=1}^T p_i ln \frac{p_i}{q_i}
+\end{align*}
+
+Since $D_{js}$ does not satisfy the triangular inequality condition $D_{js}(a,c)\leq D_{js}(a,c)+D_{js}(b,c)$, the JSD is not considered to be a real metric.
+On the other hand, the square root of JSD is a real distance metric \citep{endres_new_2003}.
+This is the reason why we use the square root and not JSD itself.
+
+\section{Sentiment analysis}
+
+The idea of Sentiment analysis is to determine the attitude of a writer through online text data toward certain topic or the overall tonality of a document.
 

### 2018-02-21 paper/writing/doc_backup.tex
k=40

--- 2018-01-19 paper/doc/doc_backup.tex
@@
 We use this approach to analyze online news about the german federal elections, where we allow prevalence of topics to change over time (before and after the elections) and vary across newswire services (private or public) to quantify the effect of news wire source on both topical prevalence and topical content.
+
+\section{Competitor Analysis}
+\subsection{Competitor analysis}
+
+Users can access a news website either directly or through an intermediary, such as search engines or social media.
+As Figure \ref{fig_traffic} illustrates\footnote{The figure shows the percentage of total traffic by source for the time period 18.12.2017-18.01.2017}, direct access\footnote{Direct traffic includes: Direct navigation (Someone types the website URL into a browser); Bookmarks (Clicks on a bookmark/favorite link in a browser); Email (Clicks on links in desktop email clients)} to a website is the main source of traffic for most news providers.
+In the case of Bild.de, the percentage is 85\%.
+Also n-tv.de (79\%), SPIEGEL ONLINE (76\%) and Tagesschau.de (75\%) get most of their traffic via the direct route.
+Other providers are more reliant on intermediaries, mainly search engines.
+FOCUS ONLINE, DLF and Handelsblatt.com, for example, obtain between 40\% and 45\% of its traffic via search engines.
+Thus, an important question is, which organic search keywords send traffic to a website.
+Figure \ref{fig_searchtraffic} displays the percentage of organic search referrals to a specific website that come from this keyword.\footnote{Percentage of organic search referrals in major search engines over the time span Jun-Dec 2017.} E.g., 0.78\% of all organic search referrals to Handelsblatt.com come from the keyword "handelsblatt".
+It is not surprising that the provider's name is the keyword that generates the majority of traffic for most of the news pages.
+However, different topics as well as names of other providers are hidden among the top 10 keywords.
+
+\begin{figure}[H]
+	\caption{Traffic Sources}
+	\begin{center}
+		\includegraphics[width=0.8\textwidth]{../figs/traffic_source.png}
+		\label{fig_traffic}
+	\end{center}
+\end{figure}
+
+\begin{figure}[H]
+	\caption{Search traffic \%}
+	\begin{center}
+		\includegraphics[width=0.8\textwidth]{../figs/search_traffic.png}
+		\label{fig_searchtraffic}
+	\end{center}
+\end{figure}
+
+Assuming that each search query is in itself a market where providers compete for traffic, the share of search queries for a keyword that has led visitors to a news page is the market share of that provider.
+In this context, figures \ref{fig_keywords1} and \ref{fig_keywords2} show the market share of providers for different keywords.\footnote{The figures show the percentage of searches for a keyword that sent traffic to a website in major search engines over the time span Jun-Dec 2017.} Nearly 15\% of all search queries for the keyword "Bundestagswahl 2017" (federal elections 2017) were forwarded to DIE WELT.
+FOCUS ONLINE, faz.net and SPIEGEL ONLINE obtained a market share of 7\% - 8\%.
+For the keyword "Groko" (grand coalition between CDU/CSU and SPD), SPIEGEL ONLINE was able to gain the largest market share (17\%) in the past six months, followed by DIE WELT (\%10), FOCUS ONLINE (8\%) and Bild.de (7.5\%).
+Figure \ref{fig_keywords2} shows the market share of news pages for the keyword search for a specific party.
+
+Contrary to figure \ref{fig_keywords1} , the x-axes in figure \ref{fig_keywords2} are scaled equally to show not only the market share of news sites for a specific party-keyword, but also for which party this provider has the largest market share.
+For example, we can see that the market share of sueddeutsche.de is largest for the keyword "Die Grünen".
+However, the biggest market share among the listed news providers for this keyword has Zeit.de.
+The largest market share for the keyword "AfD" can be found at DIE WELT, followed by SPIEGEL ONLINE.
+The proportion of public news providers is comparatively low for all keywords.
+
+\begin{figure}[H]
+	\begin{center}
+			\includegraphics[width=.8\textwidth]{../figs/keywords1.png}
+			\caption{Keyword market share for policy topics / general}
+			\label{fig_keywords1}
+	\end{center}
+\end{figure}
+
+\begin{figure}[H]
+	\begin{center}
+			\includegraphics[width=.8\textwidth]{../figs/keywords2.png}
+			\caption{Keyword market share for party-keywords}
+			\label{fig_keywords2}
+	\end{center}
+\end{figure}
 

### 2018-02-21 paper/R/func/functions.R

@@ -1,185 +1,0 @@
-Mode = function(x){ 
-  ta = table(x)
-  tam = max(ta)
-  if (all(ta == tam))
-    mod = NA
-  else
-    if(is.numeric(x))
-      mod = as.numeric(names(ta)[ta == tam])
-  else
-    mod = names(ta)[ta == tam]
-  return(mod)
-}
-
-#############################
-## Topic proportion by Ylevel
-#############################
-plotNewspaperHistogram <- function(topic){
-  tab <- tapply(stmOut$theta[,topic], stmOut$settings$covariates$betaindex, mean)
-  tab <- as.data.frame(tab) %>% 
-    mutate(site=stmOut$settings$covariates$yvarlevels)
-  
-  ggplot(data=tab, aes(x=site, y=tab)) +
-    geom_col(fill=col[3]) +
-    coord_flip() +
-    theme(axis.text = element_text(size=8),
-          axis.title = element_text(size=10)) +
-    labs(x="", y=paste("expected frequency of topic",topics.df[topic,2], sep=" ")) 
-}
-
-##################################
-## Topic correlation within Ylevel
-##################################
-topicCorrelation <- function(ylevel) {
-  cormat <- cor(stmOut$theta[stmOut$settings$covariates$betaindex==ylevel,])
-  adjmat <- ifelse(cormat > .05,1,0)
-  
-  corr <- list()
-  corr$posadj <- adjmat
-  corr$poscor <- cormat*adjmat
-  corr$cor <- ifelse(abs(cormat)>.05,cormat,0)
-  
-  x <- corr$posadj[1:nrow(corr$posadj),1:nrow(corr$posadj)]
-  
-  g<- graph.adjacency(x, mode="undirected", weighted=TRUE, diag=FALSE)
-  
-  E(g)$size <- 1
-  E(g)$lty <- 2
-  E(g)$color <- "black"
-  V(g)$label <- topics[,2]
-  layout <- layout_nicely
-  
-  plot.igraph(g, layout=layout_nicely, vertex.color="white", label.font = "Roboto",
-              vertex.frame.color="grey", vertex.size=1, vertex.label.cex=.7, edge.color="red",
-              edge.width=1, main=paste("Topic correlation", stmOut$settings$covariates$yvarlevels[ylevel]))
-}
-
-##################################
-## Topic correlation Network
-##################################
[…]

### 2018-02-21 paper/R/func/topic-modelling-functions.R

@@ -1,66 +1,0 @@
-# Topic Modelling Functions
-
-# This section contains functions that assist with topic modelling.
-
-computeJensenShannonPCA <- function(wtp) {
-  # Adapted from https://github.com/cpsievert/LDAvis/blob/master/R/createJSON.R
-  # 
-  # Returns coordinates for plotting topics with Jensen Shannon distance as 
-  # the distance measure, projected down to 2 dimensions using principal 
-  # coordinates analysis.
-  #
-  # Args:    wtp:  word-topic probability matrix
-  # Returns: data frame containing the x-y location of each topic 
-  
-  jensenShannon <- function(x, y) {
-    c = .000000001
-    x = x + c
-    y = y + c
-    m <- 0.5 * (x + y)
-    0.5 * sum(x * log(x/m)) + 0.5 * sum(y * log(y/m))
-  }
-  
-  wtp %>% 
-    spread(term, beta) %>% 
-    { .[, 2:ncol(.)] } %>%
-    dist(x = ., method = jensenShannon) %>% 
-    cmdscale(k = 2) %>% {
-      data.frame(
-        topic = 1:n_distinct(wtp$topic),
-        x = .[, 1],
-        y = .[, 2]
-      )
-    }
-}
-
-computeJensenShannonPCA2 <- function(dtp) {
-  # Adapted from https://github.com/cpsievert/LDAvis/blob/master/R/createJSON.R
-  # 
-  # Returns coordinates for plotting topics with Jensen Shannon distance as 
-  # the distance measure, projected down to 2 dimensions using principal 
-  # coordinates analysis.
-  #
-  # Args:    dtp:  document-topic probability matrix
-  # Returns: data frame containing the x-y location of each topic 
-  
-  jensenShannon <- function(x, y) {
-    c = .000000001
-    x = x + c
-    y = y + c
-    m <- 0.5 * (x + y)
-    0.5 * sum(x * log(x / m)) + 0.5 * sum(y * log(y / m))
-  }
-  
-  dtp %>% 
-    { .[, 2:ncol(.)] } %>%
-    dist(x = ., method = jensenShannon) %>% 
-    cmdscale(k = 2) %>% {
-      data.frame(
-        document = unique(dtp$document),
-        x = .[, 1],
-        y = .[, 2]
-      )
-    }
-}
-
-

### 2018-02-21 paper/docs/func/functions.R

@@ -1,0 +1,185 @@
+Mode = function(x){ 
+  ta = table(x)
+  tam = max(ta)
+  if (all(ta == tam))
+    mod = NA
+  else
+    if(is.numeric(x))
+      mod = as.numeric(names(ta)[ta == tam])
+  else
+    mod = names(ta)[ta == tam]
+  return(mod)
+}
+
+#############################
+## Topic proportion by Ylevel
+#############################
+plotNewspaperHistogram <- function(topic){
+  tab <- tapply(stmOut$theta[,topic], stmOut$settings$covariates$betaindex, mean)
+  tab <- as.data.frame(tab) %>% 
+    mutate(site=stmOut$settings$covariates$yvarlevels)
+  
+  ggplot(data=tab, aes(x=site, y=tab)) +
+    geom_col(fill=col[3]) +
+    coord_flip() +
+    theme(axis.text = element_text(size=8),
+          axis.title = element_text(size=10)) +
+    labs(x="", y=paste("expected frequency of topic",topics.df[topic,2], sep=" ")) 
+}
+
+##################################
+## Topic correlation within Ylevel
+##################################
+topicCorrelation <- function(ylevel) {
+  cormat <- cor(stmOut$theta[stmOut$settings$covariates$betaindex==ylevel,])
+  adjmat <- ifelse(cormat > .05,1,0)
+  
+  corr <- list()
+  corr$posadj <- adjmat
+  corr$poscor <- cormat*adjmat
+  corr$cor <- ifelse(abs(cormat)>.05,cormat,0)
+  
+  x <- corr$posadj[1:nrow(corr$posadj),1:nrow(corr$posadj)]
+  
+  g<- graph.adjacency(x, mode="undirected", weighted=TRUE, diag=FALSE)
+  
+  E(g)$size <- 1
+  E(g)$lty <- 2
+  E(g)$color <- "black"
+  V(g)$label <- topics[,2]
+  layout <- layout_nicely
+  
+  plot.igraph(g, layout=layout_nicely, vertex.color="white", label.font = "Roboto",
+              vertex.frame.color="grey", vertex.size=1, vertex.label.cex=.7, edge.color="red",
+              edge.width=1, main=paste("Topic correlation", stmOut$settings$covariates$yvarlevels[ylevel]))
+}
+
+##################################
+## Topic correlation Network
+##################################
[…]

### 2018-02-21 paper/docs/04_Modelresults.Rmd
k=40

@@
 ```{r echo = FALSE}
-load("../output/models/STM 40 .Rda")
+load("../output/models/STM 45 .Rda")
 k <- stmOut$settings$dim$K
@@
                    27, "Mix, Surveys, public statistics", 28, "Election polls", 
-                   29, "AfD in parliament", 30, "Mix: Sexism, Court sentences, NSU trial", 31, "German armed forces, v.d.Leyen", 
+                   29, "AfD in parliament", 30, "Mix: Sexism, Court sentences, NSU trial", 
+                   31, "German armed forces, v.d.Leyen", 
                    32, "G20 in Hamburg", 33, "Diplomatic relations w Turkey, Russia", 
                    34, "Terror in GER, Left- & Right-wing", 35, "CDU/CSU H.Seehofer, Obergrenze",
-                   36, "Church, Family", 37, "Car industry, Stuttgart (Mix)", 38, "AfD, F.Petry", 39, "Statistics, welfare policy",
+                   36, "Church, Family", 37, "Car industry, Stuttgart (Mix)", 38, "AfD, F.Petry", 
+                   39, "Statistics, welfare policy",
                    40, "J.Spahn"), ncol=2, byrow=T)
@@
          topic = 1:k) 
+```
+
+The plotQuote function allows to inspect die most common words of a topic for each covariate.
+
+```{r fig.height=11, fig.width=5}
+topic <- 40
+
+plotQuote(c(paste(sagelabs$cov.betas[[1]]$problabels[topic,], collapse="\n"),
+            paste(sagelabs$cov.betas[[2]]$problabels[topic,], collapse="\n"),
+            paste(sagelabs$cov.betas[[3]]$problabels[topic,], collapse="\n"),
+            paste(sagelabs$cov.betas[[4]]$problabels[topic,], collapse="\n"),
+            paste(sagelabs$cov.betas[[5]]$problabels[topic,], collapse="\n"),
+            paste(sagelabs$cov.betas[[6]]$problabels[topic,], collapse="\n"),
+            paste(sagelabs$cov.betas[[7]]$problabels[topic,], collapse="\n")))
 ```
@@
   htmlTable::htmlTable(align="l")
-```
-
-The plotQuote function allows to inspect die most common words of a topic for each covariate. Here I check for topic 3 (Jamaica coalition)
-
-```{r fig.height=11, fig.width=5}
-topic <- 40
-
-plotQuote(c(paste(sagelabs$cov.betas[[1]]$problabels[topic,], collapse="\n"),
-            paste(sagelabs$cov.betas[[2]]$problabels[topic,], collapse="\n"),
-            paste(sagelabs$cov.betas[[3]]$problabels[topic,], collapse="\n"),
-            paste(sagelabs$cov.betas[[4]]$problabels[topic,], collapse="\n"),
-            paste(sagelabs$cov.betas[[5]]$problabels[topic,], collapse="\n"),
-            paste(sagelabs$cov.betas[[6]]$problabels[topic,], collapse="\n"),
-            paste(sagelabs$cov.betas[[7]]$problabels[topic,], collapse="\n")))
 ```
@@
 
-```{r fig.width=12}
+```{r fig.height=8, fig.width=12}
 p2 <- ggplot(freq, aes(reorder(topic_name,frequency), freq)) +
@@
 
-ggsave(plot = p1, filename = "../figs/estimates.png", device = "png",width = 10, height = 7,
-dpi = 600)
+# ggsave(plot = p1, filename = "../figs/estimates.png", device = "png",width = 10, height = 7,
+# dpi = 600)
 ```
@@
 token <- btw.2 %>%
-  filter(gamma >= 0.9) %>%
+  filter(gamma >= 0.75) %>%
   filter(topic %in% keep) %>%
@@
 sentDF <- left_join(token, sent, by="word") %>% 
-  mutate(sentiment = as.numeric(value)) %>% 
-  filter(!is.na(sentiment)) 
+  mutate(value = as.numeric(value)) %>% 
+  filter(!is.na(value)) %>%
+  mutate(polarity = ifelse(value < 0, "negative", "positive"))
 ```
 
-#### 3. Calculate sentiment value
+#### 3. Calculate sentiment value by document
+
+calculate sentiment value of document $d$:
+
+$$
+\text{Sentiment}_d = \frac{|\text{Sum of positive tokens}_d| - |\text{Sum of negative tokens}_d|}{\text{Number ot tokens}_d}
+$$
+
+```{r}
+sentDF.values <- sentDF %>%
+  select(document, word, value, polarity) %>%
+  mutate(id = row_number()) %>%
+  spread(polarity, value) %>%
+  group_by(document) %>%
+
+  # calculate sum of positive and negative values
+  summarise(sum_positive = sum(positive, na.rm = T),
+            sum_negative = sum(negative, na.rm = T)) %>%
+  ungroup() %>%
+  # calculate diff
+  mutate(sent_diff = abs(sum_positive) - abs(sum_negative)) %>%
+  # combine with dataframe
+  left_join(., btw.2 %>% filter(topic %in% keep), 
+            by = "document") %>%
+  # calculate sentiment
+  mutate(sentiment = sent_diff / text_length)
+```
+
+#### 4. Inspect sentiment value
+
+```{r fig.width=8, fig.height=12}
+p <- sentDF.values %>%
+  group_by(topic_name, date, site) %>%
+  summarise(sentiment = mean(sentiment, na.rm=T))
+
+p %>%
+  filter(grepl("Merkel", topic_name)) %>%
+  ggplot(aes(date, sentiment,
+              fill = factor(topic_name))) +
+  geom_col() +
+  geom_hline(yintercept = 0, linetype = 2,
+             color = "black") +
+  facet_wrap(~site, ncol = 1) +
+  labs(x="", y="", fill="") +
+  theme(legend.position = "right")
+```
 

### 2018-02-21 paper/docs/04_Modelresults_35.Rmd
k=40

--- 2018-02-21 paper/docs/04_Modelresults.Rmd
@@
     theme(
-      plot.title = element_text(size = 12,
+      plot.title = element_text(size = 14,
                                 margin = margin(0, 0, 4, 0, "pt")),
-      plot.subtitle = element_text(size = 12),
+      plot.subtitle = element_text(size = 8),
       plot.caption = element_text(size = 6),
@@
 ```{r echo = FALSE}
-load("../output/models/STM 40 .Rda")
+load("../output/models/STM 35 .Rda")
 k <- stmOut$settings$dim$K
+sagelabs <- sageLabels(stmOut, 20)
 ```
@@
 In order to improve readability and traceability, I assign a shorter name to the topics based on the most common words.
+The plotQuote function allows to inspect die most common words of a topic for each covariate.
 
-```{r}
-sagelabs <- sageLabels(stmOut, 20)
+```{r eval=FALSE, fig.height=12, fig.width=5, include=FALSE}
+topic <- 45
 
-sagelabs$cov.betas[[3]]$problabels[,1:6]
+plotQuote(c(paste(sagelabs$cov.betas[[1]]$problabels[topic,], collapse="\n"),
+            paste(sagelabs$cov.betas[[2]]$problabels[topic,], collapse="\n"),
+            paste(sagelabs$cov.betas[[3]]$problabels[topic,], collapse="\n"),
+            paste(sagelabs$cov.betas[[4]]$problabels[topic,], collapse="\n"),
+            paste(sagelabs$cov.betas[[5]]$problabels[topic,], collapse="\n"),
+            paste(sagelabs$cov.betas[[6]]$problabels[topic,], collapse="\n"),
+            paste(sagelabs$cov.betas[[7]]$problabels[topic,], collapse="\n")))
 ```
@@
 ```{r}
-topics <- matrix(c(1, "SPD, M.Schulz", 2, "A.Merkel vs. Schulz", 3, "B90/Die Grüne, coalition talks", 
-                   4, "EU topics: Diesel, Glyphosat, toll", 5, "H.Kohl", 6, "A.Merkel", 7, "Federal Election results",
-                   8, "Party congress (CSU and DIE LINKE)", 9, "General societal issues", 
-                   10, "Information on Federal elections (e.g. Wahlomat, election programmes)",  
-                   11, "W.Schäuble, F.Steinmeier", 12, "Refugees in GER", 13, "Auffangbecken ('Find us on Twitter')",
-                   14, "B90/Die Grüne, climate/refugee policy", 15, "D.Trump, Israel, G20", 
-                   16, "Great coalition, minority government", 17, "AfD, in media", 18, "Jamaica coalition", 
-                   19, "Rubbish", 20, "Mix (Amri, Berlin, Court)", 21, "German armed forces, Mali, Helicopter", 
-                   22, "Mix (Ditib, Weather, DB)", 23, "Elections in Niedersachsen", 24, "CDU, regional politics (Saxony)", 
-                   25, "Mix (Europa, political talkshows)", 26, "Votes in the Bundestag", 
-                   27, "Mix, Surveys, public statistics", 28, "Election polls", 
-                   29, "AfD in parliament", 30, "Mix: Sexism, Court sentences, NSU trial", 31, "German armed forces, v.d.Leyen", 
-                   32, "G20 in Hamburg", 33, "Diplomatic relations w Turkey, Russia", 
-                   34, "Terror in GER, Left- & Right-wing", 35, "CDU/CSU H.Seehofer, Obergrenze",
-                   36, "Church, Family", 37, "Car industry, Stuttgart (Mix)", 38, "AfD, F.Petry", 39, "Statistics, welfare policy",
-                   40, "J.Spahn"), ncol=2, byrow=T)
-
-# topics <- matrix(c(1, "SPD, M.Schulz", 2, "A.Merkel vs. Schulz", 3, "Jamaica coalition", 4, "Diesel scandal", 
-#                    5, "H.Kohl", 6, "A.Merkel", 7, "Federal Election results", 8, "CSU, Seehofer, Söder", 
-#                    9, "Deportation, radicalization, refugees", 10, "Parliament (Bundestag)", 
-#                    11, "DIE LINKE, W.Schäuble", 12, "Refugees in GER", 13, "G.Schröder, IT Topics", 
-#                    14, "B90/Die Grüne", 
-#                    15, "D.Trump, antisemitism", 16, "Great coalition", 17, "AfD, in social media", 
-#                    18, "Budget statistics, Welfare policy", 
-#                    19, "Rubbish", 20, "Verfassungsschutz, Terror attacks", 21, "German armed forces, Drones, Mali", 
-#                    22, "EU policies, Weather", 23, "Elections in Niedersachsen", 24, "CDU, social media", 
-#                    25, "Political talkshows", 26, "Bundestag, Steinmeier, Maas", 
-#                    27, "Surveys, public statistics", 28, "Election polls", 
-#                    29, "AfD", 30, "Court sentences, NSU trial", 31, "German armed forces, v.d.Leyen", 
-#                    32, "G20 in Hamburg", 33, "Diplomatic relations w Turkey, Russia", 
-#                    34, "Terror attacks, polics reports", 35, "CDU/CSU H.Seehofer, Obergrenze"), ncol=2, byrow=T)
+topics <- matrix(c(1, "SPD, M.Schulz", 2, "A.Merkel vs.
+Schulz", 3, "Jamaica coalition", 4, "Diesel scandal", 5, "H.Kohl", 6, "Federal Elections", 7, "EU policies, refugees", 8, "Political trends in GER", 9, "AfD in Parliament", 10, "A.Merkel", 11, "Hamburg G20", 12, "Christian, Berlin, Bruch", 13, "Climate policy, Die Grünen", 14, "Seehofer vs.
+Söder", 15, "D.Trump", 16, "Great coalition", 17, "CDU/CSU", 18, "Elections in Niedersachen", 19, "Budget statistics, Welfare policy", 20, "AfD in social media", 21, "DIE LINKE", 22, "German armed forces, Mali", 23, "Weather, Bahn", 24, "Innenministerium, Verfassungsschutz", 25, "Terror attack (Amri)", 26, "G20 in Hamburg", 27, "Spahn (CDU)", 28, "Steinmeier", 29, "German armed forces", 30, "AfD", 31, "Women empowerment", 32, "Diplomatic relations w Turkey, Russia", 33, "Election polls", 34, "Votings in parliament", 35, "F.Petri, Staatsanwaldschaft"), ncol=2, byrow=T)
 
@@
 #### Inspect the unclear topics
-```{r}
+```{r eval=FALSE, include=FALSE}
 btw.2 %>% filter(topic==13) %>% select(title, gamma, url) %>%
@@
   htmlTable::htmlTable(align="l")
-```
-
-```{r}
-btw.2 %>% filter(topic==10) %>% select(title, gamma, url) %>%
-  arrange(desc(gamma)) %>%
-  top_n(10) %>%
-  htmlTable::htmlTable(align="l")
-```
-
-The plotQuote function allows to inspect die most common words of a topic for each covariate. Here I check for topic 3 (Jamaica coalition)
-
-```{r fig.height=11, fig.width=5}
-topic <- 40
-
-plotQuote(c(paste(sagelabs$cov.betas[[1]]$problabels[topic,], collapse="\n"),
-            paste(sagelabs$cov.betas[[2]]$problabels[topic,], collapse="\n"),
-            paste(sagelabs$cov.betas[[3]]$problabels[topic,], collapse="\n"),
-            paste(sagelabs$cov.betas[[4]]$problabels[topic,], collapse="\n"),
-            paste(sagelabs$cov.betas[[5]]$problabels[topic,], collapse="\n"),
-            paste(sagelabs$cov.betas[[6]]$problabels[topic,], collapse="\n"),
-            paste(sagelabs$cov.betas[[7]]$problabels[topic,], collapse="\n")))
 ```
@@
 
-Keep only those articles, that are clear
+Keep only those articles, that are clear & interessting to analyse.
 
 ```{r}
-keep <- c(1,2,3,4,5,6,7,12,14,15,16,17,18,21,23,24,28,29,31,32,33,34,35,38,40)
+keep <- c(1,2,6,8,14,16,17,18,24,29,31,35,38,40,41,43)
 ```
@@
   left_join(., topics.df, by = "topic") %>%
-  filter(topic %in% keep) %>%
+  #filter(topic %in% keep) %>%
   mutate(topic = topic_name) %>%
@@
 
-```{r fig.width=12}
+```{r fig.height=8, fig.width=12}
 p2 <- ggplot(freq, aes(reorder(topic_name,frequency), freq)) +
   geom_col(fill = col[3]) +
-  #scale_fill_manual(values = col[1]) +
   coord_flip() +
@@
 
-The following figure shows the regression results for each news page. The coefficients indicate the deviation from the base value of Bild.de.
+The following figure shows the regression results for each news page. The coefficients indicate the deviation from the base value of Bild.de (keeping the month equal).
 
@@
 
-ggsave(plot = p1, filename = "../figs/estimates.png", device = "png",width = 10, height = 7,
-dpi = 600)
+# ggsave(plot = p1, filename = "../figs/estimates.png", device = "png",width = 10, height = 7,
+# dpi = 600)
+```
+
+The following figure shows the regression results for each month. The coefficients indicate the deviation from the base value of June 2017 (keeping the news source).
+
+```{r fig.height=8, fig.width=12}
+p1 <- coeff %>% 
+  filter(topic %in% keep) %>%
+  filter(!parameter %in% stmOut$settings$covariates$yvarlevels) %>%
+  filter(parameter != "(Intercept)") %>%
+  ggplot(aes(x = reorder(topic_name,topic, decreasing=F), y = Estimate, fill=factor(signifcant))) +
+  geom_col() +
+  scale_fill_manual(values = col[c(2,1)]) +
+  scale_x_discrete(position = "top") +
+  coord_flip() +
+  facet_wrap(~parameter, ncol = 8, scales = "free_x") +
+  labs(x="", fill="significant at the 5% level") +
+  theme(legend.position = "top", 
+        axis.text.y = element_text(size=9),
+        axis.text.x = element_text(angle=90))
+
+p1
 ```
@@
 ```{r, message=FALSE, warning=FALSE, include=FALSE}
+df <- btw.2 %>%
+  filter(gamma >= 0.75) %>%
+  filter(topic %in% keep)
+
 # Tokenize text
-token <- btw.2 %>%
-  filter(gamma >= 0.9) %>%
-  filter(topic %in% keep) %>%
+token <- df %>%
   unnest_tokens(word, text)
@@
 sentDF <- left_join(token, sent, by="word") %>% 
-  mutate(sentiment = as.numeric(value)) %>% 
-  filter(!is.na(sentiment)) 
+  mutate(value = as.numeric(value)) %>% 
+  #filter(!is.na(value)) %>%
+  mutate(polarity = ifelse(value < 0, "negative", "NA"),
+         polarity = ifelse(value > 0, "positive", polarity))
 ```
 
-#### 3. Calculate sentiment value
+#### 3. Calculate sentiment value by document
 
-calculate weight:
+calculate sentiment value of document $d$:
 
 $$
-\text{weight} = \frac{\text{Total Articles, by site & topic}}{\text{Total Articles, by site}}
+\text{Sentiment}_d = \frac{|\text{Sum of positive tokens}_d| - |\text{Sum of negative tokens}_d|}{\text{Number ot tokens}_d}
 $$
@@
 ```{r}
-# Calculate weight
-btw.2 <- btw.2 %>%
+sentDF.values <- sentDF %>%
+  select(document, word, value, polarity) %>%
+  mutate(id = row_number()) %>%
+  spread(polarity, value) %>%
+  group_by(document) %>%
 
-  # how many articles per site & topic?
-  group_by(site, topic) %>%
-  add_tally() %>%
-  ungroup() %>%
-  mutate(count = n) %>%
-  select(-n) %>%
+  # calculate sum of positive and negative values
+  summarise(sum_positive = sum(positive, na.rm = T),
+            sum_negative = sum(negative, na.rm = T)) %>%
 
-  # how many articles per site?
-  group_by(site) %>%
-  add_tally() %>%
-  ungroup() %>%
-  mutate(totalcount = n) %>%
-  select(-n) %>%
+  # calculate diff
+  mutate(sent_diff = abs(sum_positive) - abs(sum_negative)) %>%
 
-  # calculate weight
-  mutate(weight = count/totalcount)
-```
-
-Group by article ID and calculate the mean sentiment value of each article.
-
-```{r}
-sentDF.red <- sentDF %>%
-
-  # calculate weight and weighted sentiment score
-  group_by(articleID) %>%
-  summarise(sent_value = mean(sentiment)) %>%
-
-  # leftjoin with btw
-  left_join(., btw.2 %>% select(articleID, topic, topic_name,
-                                title, url, site, gamma, weight),
-            by="articleID") %>%
-  mutate(weighted = sent_value*weight)
-```
-
-```{r}
-sentDF.red %>% group_by(topic_name) %>%
-  top_n(5, gamma) %>%
-  select(topic_name, gamma, title) %>%
-  htmlTable::htmlTable(align="l")
+  # combine with dataframe
+  left_join(., df, 
+            by = "document") %>%
+  # calculate sentiment
+  mutate(sentiment = sent_diff / text_length)
 ```
@@
 #### 1. by topic
-```{r fig.height=10, fig.width=12}
-p1 <- sentDF.red %>%
-  group_by(topic_name, topic) %>%
-  summarise(sent_value = mean(sent_value)) %>%
-  ggplot(aes(reorder(topic_name, sent_value), sent_value)) +
-  geom_col(fill=col[3], alpha=0.8) +
+```{r fig.height=8, fig.width=6}
+
+p <- sentDF.values %>%
+  group_by(topic_name) %>%
+  summarise(sentiment = mean(sentiment, na.rm=T),
+            obs = n())
+
+ggplot(p, aes(reorder(topic_name, sentiment), 
+              sentiment)) +
+  geom_col(aes(fill=p$obs)) +
+  geom_hline(yintercept = 0, linetype = 2,
+             color = "black") +
   coord_flip() +
-  labs(x="", y="sentiment value (unweighted)",
-       title = "sentiment value (unweighted)") +
-  theme(
-        axis.text.y = element_text(size = 10))
-
-p2 <- sentDF.red %>%
-  group_by(topic_name, topic) %>%
-  summarise(weighted = mean(weighted),
-            sent_value = mean(sent_value)) %>%
-  ggplot(aes(reorder(topic_name, sent_value), weighted)) +
-  geom_col(fill=col[1], alpha=0.8) +
-  coord_flip() +
-  labs(x="", y="sentiment value (weighted)",
-       title = "sentiment value (weighted)") +
-  theme(
-        axis.text.y = element_blank())
-
-p1 + p2
+  labs(x="", y="",
+       title = "Grouped Sentiment value",
+       fill = "Number of\nObservations") +
+  theme(axis.text.y = element_text(size = 10))
 ```
@@
 
-```{r fig.width=12}
-p1 <- sentDF.red %>%
+```{r}
+p <- sentDF.values %>%
   group_by(site) %>%
-  summarise(sent_value = mean(sent_value)) %>%
-  ggplot(aes(reorder(site, sent_value), sent_value)) +
-  geom_col(fill=col[3], alpha=0.8) +
+  summarise(sentiment = mean(sentiment, na.rm=T),
+            obs = n())
+
+ggplot(p, aes(reorder(site, sentiment), 
+              sentiment)) +
+  geom_col(aes(fill=p$obs)) +
+  geom_hline(yintercept = 0, linetype = 2,
+             color = "black") +
   coord_flip() +
-  labs(x="", y="sentiment value (unweighted)",
-       title = "sentiment value (unweighted)") +
-  theme(
-        axis.text.y = element_text(size = 10))
-
-p2 <- sentDF.red %>%
-  group_by(site) %>%
-  summarise(weighted = mean(weighted),
-            sent_value = mean(sent_value)) %>%
-  ggplot(aes(reorder(site, sent_value), weighted)) +
-  geom_col(fill=col[1], alpha=0.8) +
-  coord_flip() +
-  labs(x="", y="sentiment value (weighted)",
-       title = "sentiment value (weighted)") +
-  theme(
-        axis.text.y = element_blank())
-
-p1 + p2
+  labs(x="", y="",
+       title = "Grouped Sentiment value",
+       fill = "Number of\nObservations") +
+  theme(axis.text.y = element_text(size = 10))
 ```
@@
 
-```{r fig.height=10, fig.width=12}
-sentDF.red %>%
+```{r fig.height=8, fig.width=12}
+p <- sentDF.values %>%
   group_by(site, topic_name, topic) %>%
-  summarise(sent_value = mean(sent_value)) %>%
-  ggplot(aes(reorder(topic_name, topic), sent_value)) +
-  geom_col(fill=col[3], alpha=0.8) +
+  summarise(sentiment = mean(sentiment, na.rm=T),
+            obs = n())
+
+ggplot(p, 
+       aes(reorder(topic_name, topic), 
+           sentiment)) +
+  geom_col(aes(fill=p$obs)) +
+  geom_hline(yintercept = 0, linetype = 2,
+             color = "black") +
   coord_flip() +
   facet_wrap(~site, ncol = 7) +
-  labs(x="", y="sentiment value (unweighted)",
-       title = "sentiment value (unweighted)") +
-  theme(axis.text.y = element_text(size=12))
-
-ggsave(filename = "../figs/sent_weighted.png", device = "png",width = 12, height = 8,
-dpi = 600)
-```
-
-```{r fig.height=10, fig.width=12}
-sentDF.red %>%
-  group_by(site, topic_name, topic) %>%
-  summarise(weighted = mean(weighted)) %>%
-  ggplot(aes(reorder(topic_name, topic), weighted)) +
-  geom_col(fill=col[1], alpha=0.8) +
-  coord_flip() +
-  facet_wrap(~site, ncol = 7) +
-  labs(x="", y="sentiment value (weighted)",
-       title = "sentiment value (weighted)") +
+  labs(x="", y="", fill= "Number of\nObservations",
+       title = "Sentiment value") +
   theme(axis.text.y = element_text(size=12))
@@
 
-Select topics to be analyzed:
-
-1: "SPD, M.Schulz"
-2: "A.Merkel vs. Schulz"
-3: "Jamaica coalition"
-6: "A.Merkel"
-8: "CSU, Seehofer, Söder"
-14: "B90/Die Grüne"
-16: "Great coalition"
-17: "AfD, in social media",
-24: "CDU, social media"
-29: "AfD"
-
-1, "SPD, M.Schulz"
-2, "A.Merkel vs. Schulz"
-3, "B90/Die Grüne, coalition talks"
-4, "EU policies"
-5, "H.Kohl", 
-6, "A.Merkel", 
-8, "CSU, Seehofer, Söder",
-12, "Refugees in GER"
-14, "B90/Die Grüne, climate/refugee policy",
-16, "Great coalition", 
-17, "AfD, in media", 
-18, "Jamaica coalition",
-29, "AfD",
-33, "Diplomatic relations w Turkey, Russia",
-35, "CDU/CSU H.Seehofer, Obergrenze",
-38, "AfD, F.Petry")
-
 ```{r}
-#keep <- c(1,2,3,6,8,14,16,17,24,29)
-
-keep <- c(1,3,4,5,6,8,14,16,17,18,29,33,35,38)
-```
-
-#### Unweighted
-```{r}
-sentDF.red %>% 
-  filter(topic %in% keep) %>%
+sentDF.values %>%
   group_by(site, topic_name) %>%
-  summarise(sent_value = mean(sent_value)) %>%
-  spread(key=topic_name, value=sent_value) %>%
-  ungroup() -> radar
+  summarise(sentiment = mean(sentiment, na.rm=T)) %>%
+  spread(key=topic_name, value=sentiment) -> radar
 
 radar %>%
-  ggRadar(aes(color=site), rescale = F,
+  ggRadar(aes(color=site), 
+          rescale = F,
           alpha = 0, legend.position = "right") +
@@
 
-#### Weighted
 ```{r}
-sentDF.red %>% 
-  filter(topic %in% keep) %>%
-  group_by(site, topic_name) %>%
-  summarise(weighted = mean(weighted)) %>%
-  spread(key=topic_name, value=weighted) %>%
-  ungroup() -> radar
+for (i in stmOut$settings$covariates$yvarlevels) {
 
-radar %>%
-  ggRadar(aes(color=site), rescale = F,
+  p <-radar %>%
+    filter(site == i) %>%
+    ggRadar(rescale = F,
             alpha = 0, legend.position = "right") +
-  labs(title = "")
+    labs(title = i)
+
+  ggsave(p, filename = paste0("../figs/radarchart_",i,k,".png"), 
+         device = "png", dpi = 600)
+
+}
+
 ```
+
+<img src="../figs/radarchart_Bild.de45.png", width = "45%">
+<img src="../figs/radarchart_DIE WELT45.png", width = "45%">
+<img src="../figs/radarchart_FOCUS ONLINE45.png", width = "45%">
+<img src="../figs/radarchart_SPIEGEL ONLINE45.png", width = "45%">
+<img src="../figs/radarchart_stern.de45.png", width = "45%">
+<img src="../figs/radarchart_Tagesschau.de45.png", width = "45%">
+<img src="../figs/radarchart_ZEIT ONLINE45.png", width = "45%">

### 2018-02-21 paper/docs/04_Modelresults_40.Rmd
k=40

--- 2018-02-21 paper/docs/04_Modelresults_35.Rmd
@@
 ```{r}
-topics <- matrix(c(1, "SPD, M.Schulz", 2, "A.Merkel vs.
-Schulz", 3, "Jamaica coalition", 4, "Diesel scandal", 5, "H.Kohl", 6, "Federal Elections", 7, "EU policies, refugees", 8, "Political trends in GER", 9, "AfD in Parliament", 10, "A.Merkel", 11, "Hamburg G20", 12, "Christian, Berlin, Bruch", 13, "Climate policy, Die Grünen", 14, "Seehofer vs.
-Söder", 15, "D.Trump", 16, "Great coalition", 17, "CDU/CSU", 18, "Elections in Niedersachen", 19, "Budget statistics, Welfare policy", 20, "AfD in social media", 21, "DIE LINKE", 22, "German armed forces, Mali", 23, "Weather, Bahn", 24, "Innenministerium, Verfassungsschutz", 25, "Terror attack (Amri)", 26, "G20 in Hamburg", 27, "Spahn (CDU)", 28, "Steinmeier", 29, "German armed forces", 30, "AfD", 31, "Women empowerment", 32, "Diplomatic relations w Turkey, Russia", 33, "Election polls", 34, "Votings in parliament", 35, "F.Petri, Staatsanwaldschaft"), ncol=2, byrow=T)
+topics <- matrix(c(1, "SPD, M.Schulz", 2, "A.Merkel vs. Schulz", 3, "B90/Die Grüne, coalition talks",
+4, "EU topics: Diesel, Glyphosat, toll", 5, "H.Kohl", 6, "A.Merkel",
+7, "Federal Election results", 8, "Party congress (CSU and DIE LINKE)",
+9, "General societal issues", 10, "Information on Federal elections (e.g. Wahlomat, election programmes)",
+11, "W.Schäuble, F.Steinmeier", 12, "Refugees in GER", 13, "Auffangbecken ('Find us on Twitter')", 14, "B90/Die Grüne, climate/refugee policy", 15, "D.Trump, Israel, G20", 16, "Great coalition, minority government", 17, "AfD, in media",
+                   18, "Jamaica coalition",
+                   19, "Rubbish", 20, "Mix (Amri, Berlin, Court)", 21, "German armed forces, Mali, Helicopter",
+                   22, "Mix (Ditib, Weather, DB)", 23, "Elections in Niedersachsen", 24, "CDU, regional politics (Saxony)",
+                   25, "Mix (Europa, political talkshows)", 26, "Votes in the Bundestag",
+                   27, "Mix, Surveys, public statistics", 28, "Election polls",
+                   29, "AfD in parliament", 30, "Mix: Sexism, Court sentences, NSU trial", 31, "German armed forces, v.d.Leyen",
+                   32, "G20 in Hamburg", 33, "Diplomatic relations w Turkey, Russia",
+                   34, "Terror in GER, Left- & Right-wing", 35, "CDU/CSU H.Seehofer, Obergrenze",
+                   36, "Church, Family", 37, "Car industry, Stuttgart (Mix)", 38, "AfD, F.Petry", 39, "Statistics, welfare policy",
+                   40, "J.Spahn"), ncol=2, byrow=T)
 

### 2018-02-21 paper/docs/04_Modelresults_45.Rmd
k=40

--- 2018-02-21 paper/docs/04_Modelresults_35.Rmd
@@
 ```{r echo = FALSE}
-load("../output/models/STM 35 .Rda")
+load("../output/models/STM 45 .Rda")
 k <- stmOut$settings$dim$K
@@
 ```{r}
-topics <- matrix(c(1, "SPD, M.Schulz", 2, "A.Merkel vs.
-Schulz", 3, "Jamaica coalition", 4, "Diesel scandal", 5, "H.Kohl", 6, "Federal Elections", 7, "EU policies, refugees", 8, "Political trends in GER", 9, "AfD in Parliament", 10, "A.Merkel", 11, "Hamburg G20", 12, "Christian, Berlin, Bruch", 13, "Climate policy, Die Grünen", 14, "Seehofer vs.
-Söder", 15, "D.Trump", 16, "Great coalition", 17, "CDU/CSU", 18, "Elections in Niedersachen", 19, "Budget statistics, Welfare policy", 20, "AfD in social media", 21, "DIE LINKE", 22, "German armed forces, Mali", 23, "Weather, Bahn", 24, "Innenministerium, Verfassungsschutz", 25, "Terror attack (Amri)", 26, "G20 in Hamburg", 27, "Spahn (CDU)", 28, "Steinmeier", 29, "German armed forces", 30, "AfD", 31, "Women empowerment", 32, "Diplomatic relations w Turkey, Russia", 33, "Election polls", 34, "Votings in parliament", 35, "F.Petri, Staatsanwaldschaft"), ncol=2, byrow=T)
+topics <- matrix(c(1, "SPD, M.Schulz", 2, "A.Merkel vs. Schulz", 3, "Jamaica, fail of coalition talks, reelections",
+                   4, "EU topics: Diesel, Glyphosat, toll", 5, "H.Kohl", 6, "A.Merkel",
+                   7, "Federal Election results", 8, "Party congress CSU",
+                   9, "Mix: political trends, Macron (FR), EU", 
+                   10, "Information on Federal elections (e.g. Wahlomat, election programmes)", 
+                   11, "politics & democracy in GER", 12, "Refugees in GER", 13, "Auffangbecken ('Find us on Twitter')", 
+                   14, "B90/Die Grüne, climate/refugee policy", 15, "D.Trump, Israel, G20", 
+                   16, "Great coalition, minority government", 17, "AfD, in media", 18, "Jamaica coalition talks", 
+                   19, "Rubbish", 20, "Mix (Amri, Schmähgedicht Böhmermann)", 21, "German armed forces, Aviation", 
+                   22, "Mix (Ditib, Weather, DB)", 23, "Elections in Niedersachsen", 24, "CDU", 
+                   25, "Mix (Europa, political talkshows)", 26, "Votes in the Bundestag", 
+                   27, "Mix, Surveys, public statistics", 
+                   28, "Election polls", 29, "AfD, Gauland", 30, "Sexism, abuse of women & children", 
+                   31, "German armed forces, v.d.Leyen", 32, "G20 in Hamburg",
+                   33, "Diplomatic relations w Turkey, Russia", 
+                   34, "Terror in GER, Left- & Right-wing", 35, "CDU/CSU H.Seehofer, refugee cap",
+                   36, "Mix: A.Merkel in Saxony, Weather", 37, "Car industry, Stuttgart, Mix", 38, "AfD, F.Petry", 
+                   39, "Statistics, welfare policy", 40, "Jamaica", 41, "AfD, Höcke", 42, "Religion (Muslim, Christ)", 
+                   43, "AfD Fraktion im Bundestag", 44, "Ermittlungen Bundesanwaltshaft (NSU, Franco, Terror)", 
+                   45, "Berlin capital"), ncol=2, byrow=T)
 

### 2018-02-21 paper/writing/structure.tex
k=40

--- 2018-02-15 paper/doc/structure.tex
@@
 
-\textcolor{red}{AUSWERTUNG}
+\subsection{Sentiment Analysis}
+
+The idea of Sentiment analysis is to determine the attitude of a writer through online text data toward certain topic or the overall tonality of a document.
+
+commonly used lexical or “bag-ofwords” approach.
+In that approach, the researcher provides pre-defined dictionaries (lists) of words associated with a given emotion, such as negativity.
+The target text is then deconstructed into individual words (or tokens) and the frequencies of words contained in a given dictionary are then calculated.
+For example, Loughran and McDonald (2011) construct a dictionary of words that express negativity in financial contexts, which they then use to measure the negativity in company 10-K filings and relate that negativity to financial outcomes.
+
+The psychology literature demonstrates that any emotion can be parsimoniously defined by assigning it a score along two primary dimensions: valence (i.e., positive or negative) and arousal (i.e., activation and deactivation).
+For comparison purposes, we also examine three additional measures: “worried,” “satisfied,” and a lexical “negativity” measure.
+
+In financial market research: 
+\citep{nyman_news_2018}: This paper applies algorithmic analysis to large amounts of financial market text-based data to assess how narratives and sentiment play a role in driving developments in the financial system.
+For the summary statistic of a collection of texts T, we count the number of occurrences of excitement words and anxiety words and then scale these numbers by the total text size as measured by the number of characters:
+
+\begin{equation}
+	\text{Sentiment}[T]=\frac{|\text{Excitement}|-|\text{Anxiety}|}{\text{size}[T]}
+\end{equation}
+
+Simplicity of this method also allows for an easier assessment of the robustness of the methodology: The apply a bootstrap technique to compute 95\% confidence intervals around the summary statistic.
+We sample new weights for each word in each dictionary (so that the sum of weights equals the size of the dictionary) and re-compute the statistic.
+Repeating the procedure gives a distribution from which to extract the confidence intervals.
+This technique gives us increased confidence that the meaning of individual words in our two lists does not change over time.
+Obviously, one can also imagine other methods of extracting confidence levels, e.g., to sample with replacement from the collection of texts.
 

### 2018-03-05 paper/docs/04_Modelresults_35.Rmd
add poll data

@@
 ```{r eval=FALSE, fig.height=12, fig.width=5, include=FALSE}
-topic <- 45
+topic <- 35
 
@@
 topics <- matrix(c(1, "SPD, M.Schulz", 2, "A.Merkel vs.
-Schulz", 3, "Jamaica coalition", 4, "Diesel scandal", 5, "H.Kohl", 6, "Federal Elections", 7, "EU policies, refugees", 8, "Political trends in GER", 9, "AfD in Parliament", 10, "A.Merkel", 11, "Hamburg G20", 12, "Christian, Berlin, Bruch", 13, "Climate policy, Die Grünen", 14, "Seehofer vs.
-Söder", 15, "D.Trump", 16, "Great coalition", 17, "CDU/CSU", 18, "Elections in Niedersachen", 19, "Budget statistics, Welfare policy", 20, "AfD in social media", 21, "DIE LINKE", 22, "German armed forces, Mali", 23, "Weather, Bahn", 24, "Innenministerium, Verfassungsschutz", 25, "Terror attack (Amri)", 26, "G20 in Hamburg", 27, "Spahn (CDU)", 28, "Steinmeier", 29, "German armed forces", 30, "AfD", 31, "Women empowerment", 32, "Diplomatic relations w Turkey, Russia", 33, "Election polls", 34, "Votings in parliament", 35, "F.Petri, Staatsanwaldschaft"), ncol=2, byrow=T)
+Schulz", 3, "Jamaica coalition", 4, "Diesel scandal", 5, "H.Kohl", 6, "A.Merkel", 7, "Federal Election Results", 8, "Seehover vs.
+Söder, CSU", 9, "EU policies, refugee policy", 10, "German Parliament, parliamentarians", 11, "Mix: DIE LINKE, W.Schäuble", 12, "Refugees, deportation", 13, "Mix: Schröder, IT Topics", 14, "B90/Die Grünen", 15, "USA, Russia, Israel", 16, "Great coalition", 17, "A.Weidel (AfD)", 18, "Budget statistics, Welfare policy", 19, "Process Error", 20, "Federal Constitutional Court, Ministry of the Interior", 21, "German armed forces, Mali", 22, "Mix: Weather, DB, nuclear transport, ...", 23, "Elections in Niedersachsen", 24, "CDU / CSU", 25, "Mix: political talkshows, Berxit, Macron", 26, "Mix: F.-W.Steinmeier, Constitution, H.Maas", 27, "public statistics", 28, "Election polls", 29, "F.Petry, Gauland (AfD)", 30, "Mix: NSU, sexism", 31, "German armed forces, V.d.Leyen", 32, "G20 in Hamburg", 33, "Turkey, S.Gabriel", 34, "police reports, terror (left-, right-wing, IS)", 35, "Seehofer, refugee cap"), ncol=2, byrow=T)
 
@@
 
-Keep only those articles, that are clear & interessting to analyse.
-
 ```{r}
-keep <- c(1,2,6,8,14,16,17,18,24,29,31,35,38,40,41,43)
+keep <- seq(1:k)
 ```
@@
 p2 
+```
+
+Keep only those articles, that are clear & interessting to analyse.
+
+```{r}
+keep <- c(1,16,24,29,3,6,8)
 ```
@@
 df <- btw.2 %>%
-  filter(gamma >= 0.75) %>%
+  filter(gamma >= 0.8) %>%
   filter(topic %in% keep)
@@
 ```{r fig.height=8, fig.width=6}
-
 p <- sentDF.values %>%
@@
 ggplot(p, aes(reorder(topic_name, sentiment), 
-              sentiment)) +
-  geom_col(aes(fill=p$obs)) +
+              sentiment,
+              label = obs)) +
+  geom_col(fill = col[1], alpha = 0.7) +
+  geom_text() +
   geom_hline(yintercept = 0, linetype = 2,
@@
 ggplot(p, aes(reorder(site, sentiment), 
-              sentiment)) +
-  geom_col(aes(fill=p$obs)) +
+              sentiment,
+              label = obs)) +
+  geom_col(fill = col[3], alpha = 0.7) +
+  geom_text() +
   geom_hline(yintercept = 0, linetype = 2,
@@
        aes(reorder(topic_name, topic), 
-           sentiment)) +
-  geom_col(aes(fill=p$obs)) +
+           sentiment, label = obs)) +
+  geom_col(fill=col[1], alpha = 0.7) +
+  geom_text() +
   geom_hline(yintercept = 0, linetype = 2,
@@
   theme(axis.text.y = element_text(size=12))
+```
+
+```{r}
+sentDF.values %>%
+  filter(topic == 6) %>%
+  select(title, sentiment, site) %>%
+  htmlTable::htmlTable(align = "l")
 ```
@@
 
-<img src="../figs/radarchart_Bild.de45.png", width = "45%">
-<img src="../figs/radarchart_DIE WELT45.png", width = "45%">
-<img src="../figs/radarchart_FOCUS ONLINE45.png", width = "45%">
-<img src="../figs/radarchart_SPIEGEL ONLINE45.png", width = "45%">
-<img src="../figs/radarchart_stern.de45.png", width = "45%">
-<img src="../figs/radarchart_Tagesschau.de45.png", width = "45%">
-<img src="../figs/radarchart_ZEIT ONLINE45.png", width = "45%">
+<img src="../figs/radarchart_Bild.de35.png", width = "49%">
+<img src="../figs/radarchart_DIE WELT35.png", width = "49%">
+<img src="../figs/radarchart_FOCUS ONLINE35.png", width = "49%">
+<img src="../figs/radarchart_SPIEGEL ONLINE35.png", width = "49%">
+<img src="../figs/radarchart_stern.de35.png", width = "49%">
+<img src="../figs/radarchart_Tagesschau.de35.png", width = "49%">
+<img src="../figs/radarchart_ZEIT ONLINE35.png", width = "49%">
+
+### Compare with polls
+```{r eval=FALSE, include=FALSE}
+load("../output/polls.Rda")
+```
+
+Define Functions
+
+```{r eval=FALSE, include=FALSE}
+calculate_month = function(month, year) {
+  date <- ymd(paste(year, 1, 1, sep="-"))
+  month(date) = month
+  return(date)
+}
+
+normalize_data <- function(x) {
+  y <- (x - min(x, na.rm = T)) / (max(x, na.rm = T) - min(x, na.rm = T))
+  return(y)
+}
+```
+
+Prepare Dataframes
+
+```{r eval=FALSE, include=FALSE}
+polls <- table_long %>%
+  mutate(month=month(Datum),
+         year = year(Datum),
+         yearmonth = calculate_month(month,year),
+         val_norm = normalize_data(value)) %>%
+  group_by(yearmonth,party) %>%
+  summarise(mean_val = mean(value, na.rm=T),
+            mean_val_norm = mean(val_norm)) %>%
+  ungroup() %>%
+  filter(mean_val != "NaN") %>%
+  select(party, yearmonth, mean_val_norm) %>%
+  spread(party, mean_val_norm)
+```
+
+```{r eval=FALSE, include=FALSE}
+sentDF.values %>%
+  mutate(year = year(date),
+         month = month(date),
+         yearmonth = calculate_month(month,year),
+         sentiment_norm = normalize_data(sentiment)) %>%
+  group_by(yearmonth, topic_name, topic, site) %>%
+  summarise(mean_sent = mean(sentiment, na.rm=T),
+            mean_sent_norm = mean(sentiment_norm, na.rm = T)) %>%
+  ungroup() %>%
+  left_join(polls, by="yearmonth") -> p
+```
+
+Plot
+
+```{r eval=FALSE, include=FALSE}
+for (i in unique(p$site)) {
+
+  p1 <- p %>%
+  filter(site == i) %>%
+  ggplot(aes(yearmonth, mean_sent_norm,
+               group = site)) +
+  geom_point(show.legend = F, color = col[1]) + 
+  geom_line(color = col[1]) +
+
+  scale_y_continuous(limits = c(0,1)) +
+  scale_x_date(breaks = date_breaks("1 month"), 
+               labels = date_format("%b", tz = "CET")) +
+  # AfD
+  geom_point(aes(yearmonth, AfD), size= 0.5,
+             color = "deepskyblue") +
+  geom_line(aes(yearmonth, AfD), color = "deepskyblue") +
+
+  # CDU/CSU
+  geom_point(aes(yearmonth, Union), size= 0.5,
+             color = "black") +
+  geom_line(aes(yearmonth, Union),
+             color = "black") +
+
+  # SPD
+  geom_point(aes(yearmonth, SPD), size= 0.5,
+             color = "red") +
+  geom_line(aes(yearmonth, SPD),
+             color = "red") +
+
+  # Grüne
+  geom_point(aes(yearmonth, Grüne), size= 0.5,
+             color = "limegreen") +
+  geom_line(aes(yearmonth, Grüne),
+             color = "limegreen") +
+
+  # DIE LINKE
+  geom_point(aes(yearmonth, Linke), size= 0.5,
+             color = "deeppink") +
+  geom_line(aes(yearmonth, Linke),
+             color = "deeppink") +
+
+  # 
+  labs(x="", y="", title=paste(i)) +
+    theme(axis.text = element_text(size = 6)) +
+  facet_grid(topic_name ~.)
+
+  ggsave(p1, file=paste0("../figs/polls_",i,".png"),
+         width = 4, height = 10)
+
+}
+```
+
+<!-- <img src="../figs/polls_Bild.de.png", width = "49%"> -->
+<!-- <img src="../figs/polls_DIE WELT.png", width = "49%"> -->
+<!-- <img src="../figs/polls_FOCUS ONLINE.png", width = "49%"> -->
+<!-- <img src="../figs/polls_SPIEGEL ONLINE.png", width = "49%"> -->
+<!-- <img src="../figs/polls_stern.de.png", width = "49%"> -->
+<!-- <img src="../figs/polls_Tagesschau.de.png", width = "49%"> -->
+<!-- <img src="../figs/polls_ZEIT ONLINE.png", width = "49%"> -->

### 2018-03-05 paper/docs/func/functions.R

@@ -183,3 +183,12 @@ JSD<- function(x,y) {
 KLD <- function(x,y) {
   sum(x * log(x/y))
 }
+
+#####################
+## Standartization ##
+#####################
+
+normalize_data <- function(x) {
+  y <- (x - min(x)) / (max(x) - min(x))
+  return(y)
+}

### 2018-03-08 paper/writing/doc_backup.tex
add sentimentR

@@
 
+% ---- Facebook ---- 
 Social networks such as Facebook are becoming more and more important for online news services: an increasing number of their readers access the news pages via links in the networks.
@@
 
-Text as a data source is becoming increasingly popular in empirical economics, as the information encoded in text is a rich complement to conventional data (e.g.
-price, wage, votes, etc.) (\citet{grimmer_bayesian_2010}; \citet{grimmer_text_2013}; \citet{quinn_how_2010}; \citet{gentzkow_text_2017}; \citet{roberts_model_2016}).
-On interesting question is, how document metadata such as author or date influence its content.
-Depending on the characteristics of a corpus (a collection of documents), documents contain more than one topic, as well as terms most likely appear in multiple topics, thus the use of mixed-membership models \citep{airoldi_handbook_2014} - or topic model as they are often referred in the literature of text analysis \citep{blei_probabilistic_2012} - are a popular approach.
+% ---- public vs. private media ---- %
+In Germany, the debate about the role of public media and their mission in a rapidly changing media world is a frequently discussed topic.
+By shifting media content to the Internet, the dual system, which has been shaping the German television and radio landscape since the introduction of private broadcasting in the early 1980s, is facing a radical change.
+Since 2000, public broadcasting has expanded its range of services, particularly in the digital media sector.
+There is the concern of commercial providers who are registering an ever-increasing number of digital services financed by fees.
+They complain about a bias in competition caused by public media offering online text-content because of their fee financing.
+The advertising-financed business model of the media houses is based on the premise that users visit their websites in order to achieve high advertising revenues.
+However, if the right to produce digital media content were to be withdrawn from the public media outlets, they would not only be deprived of the possibility of improved information provision.
+They also threatened to lose their competitiveness with commercial media.
 
-Within these models the Latent Dirichlet Allocation (LDA hencefirth) is a widely used topic modelling technique, where each document is viewed as a mixture of topics (represented by the document-topic distribution) and each topic is a mixture of unique terms (represented by the topic-term distribution).
-To "learn" the topic prevalence and the topic-term distribution, collapsed Gibbs sampling\footnote{See Section \ref{section_gibbs} for a non-formal description of the Gibbs sampler} can be used.
-LDA makes a statistical assumption that all texts in the modeled corpus are generated by the same underlying process \citep{blei_latent_2003}.
-Thus, it is not ideally suited to examining differences in topical content that are affected by covariates such as author identity or time of writing.
+One fundamental question in this debate is whether the offer of public news on the internet is justified.
+They should only occur where there are clear deficits in private sector supply.
+A frequently cited argument is that only the public media make it possible to provide information that is free of self-interest.
+Due to their public mandate and financing, they can afford what private providers cannot or only to a limited extent because of their economic dependency: a journalistic and editorial self-observation of society in the public interest.
+Due to their constitutional determination, they are obliged to the diversity and representation of the political and social spectrum of opinion in its entire breadth, including minority positions.
 
-\citet{roberts_model_2016} develop a structural topic model (STM) that allows to incorporate external variables that effect both topical content and topical prevalence.
-We use this approach to analyze online news about the german federal elections, where we allow prevalence of topics to change over time (before and after the elections) and vary across newswire services (private or public) to quantify the effect of news wire source on both topical prevalence and topical content.
+On the basis of these justifications, this paper examines whether imperfections in the market of online news exist.
+In other words, whether socially desired content that meets the (social) needs of society - and is therefore politically desirable - is not, or very poorly provided by the market.
+In order to examine this, the online news content of public media is compared with the supply of private news providers.
+More specifically, I use a data set of German online news articles about domestic politics dated from 01.06.2017 to 31.12.2017\footnote{German federal elections took place on 24th of September 2017.} from six German news content providers.
+In the event that there is no market failure in terms of information provision (the prevalence of topics do not differ), the existence of public media could still be justified by the fact that socially relevant contents of private providers are systematically distorted and the existence of public offerings ensures the diversity of information and opinions transmitted.
+In order to examine this bias, I analyze how the topics are discussed differently in public and private news.
 

### 2018-03-08 paper/writing/structure.tex
add sentimentR

--- 2018-02-15 paper/doc/structure.tex
@@
 
-In Germany, the debate about the role of public media and their mission in a rapidly changing media world is a frequently discussed topic.
-By shifting media content to the Internet, the dual system, which has been shaping the German television and radio landscape since the introduction of private broadcasting in the early 1980s, is facing a radical change.
-Since 2000, public broadcasting has expanded its range of services, particularly in the digital media sector.
-There is the concern of commercial providers who are registering an ever-increasing number of digital services financed by fees.
-They complain about a bias in competition caused by public media offering online text-content because of their fee financing.
-The advertising-financed business model of the media houses is based on the premise that users visit their websites in order to achieve high advertising revenues.
-However, if the right to produce digital media content were to be withdrawn from the public media outlets, they would not only be deprived of the possibility of improved information provision.
-They also threatened to lose their competitiveness with commercial media.
+Pluralism is an essential principle of democratic societies.
+An important pillar of this principle is an opinion-forming process that incorporates as many different perspectives as possible.
+For the process of forming opinions, information conveyed by the media, in particular the mass media of journalism, plays a decisive role.
+They create the preconditions for making the social and cultural diversity of modern societies visible and manageable.
+Securing the diversity of opinion-forming processes and preventing concentration processes in the media sector is an essential prerequisite for a functioning democracy.
 
-One fundamental question in this debate is whether the offer of public news on the internet is justified.
-They should only occur where there are clear deficits in private sector supply.
-A frequently cited argument is that only the public media make it possible to provide information that is free of self-interest.
-Due to their public mandate and financing, they can afford what private providers cannot or only to a limited extent because of their economic dependency: a journalistic and editorial self-observation of society in the public interest.
-Due to their constitutional determination, they are obliged to the diversity and representation of the political and social spectrum of opinion in its entire breadth, including minority positions.
+The new developments in digital media provide new opportunities and challenges for content creators, the public and politicians.
+The provision of information through the Internet is both faster and much cheaper compared to a time when information was mainly distributed through traditional media (TV, newspaper).
+The speed and (low)cost of information distribution could contribute to an informed electorate.
+On the other hand, this change also means that the incentive for media to produce primary information declines since the Internet has reduced the marginal utility of content.
+A study of French news websites from 2013 shows that only 38 percent of the online articles contained original content, with the remainder being copies of those originals \citep{cage_information_2017}.
 
-On the basis of these justifications, this paper examines whether imperfections in the market of online news exist.
-In other words, whether socially desired content that meets the (social) needs of society - and is therefore politically desirable - is not, or very poorly provided by the market.
-In order to examine this, the online news content of public media is compared with the supply of private news providers.
-More specifically, I use a data set of German online news articles about domestic politics dated from 01.06.2017 to 31.12.2017\footnote{German federal elections took place on 24th of September 2017.} from six German content providers.
-In the event that there is no market failure in terms of information provision (the prevalence of topics do not differ), the existence of public media could still be justified by the fact that socially relevant contents of private providers are systematically distorted and the existence of public offerings ensures the diversity of information and opinions transmitted.
-In order to examine this bias, I analyze how the topics are discussed differently in public and private news.
+- More information available, more pluralism? 
+ Pluralism and diversely sourced media are on the decline, whereas concentration of media ownership and consolidation are increasing.
+
+More specifically, I use a data set of German online news articles about domestic politics dated from 01.06.2017 to 31.12.2017\footnote{German federal elections took place on 24th of September 2017.} from six German news content providers.
+I analyze how the topics are discussed differently in public and private news.
 
@@
 
-\textcolor{red}{AUSWERTUNG}
+\subsection{Sentiment Analysis}
+
+Once we identifying the topics of interest, we use only these documents in which the posterior probability of topic $k$ is above the threshold of $0.75$, to apply a dictionary method with the aim to measure the tone of a document.
+To conduct such an analysis, a lists of words (dictionary) associated with a given emotion, such as negativity is pre-defined by the analyst.
+The target text is then deconstructed into individual words and the frequencies of words contained in a given dictionary are then calculated.
+Such lexical or “bag-of-words” approaches are widely presented in the finance literature to  determine  the  effect  of  central  banks’  monetary  policy  communications on asset prices and real variables (\citet{nyman_news_2018} \citep{tetlock_giving_2007}, \citep{tetlock_more_2008}).
+\citet{hansen_shocking_2016} use a similar approach to measure "the two Ts" (Topic and tone).
+They explore the effects of FOMC statements on both market and real economic variables.
+To understand the multi-dimensional information a statement is transmitting, they apply LDA on a corpus of 142 FOMC decision statements split into sentences (topic).
+They then measure how the central bank is talking about that topic, using a dictionary approach (tone).
+To calculate their score, they subtract the negative words from the positive words und divide this by the number of total words of the statement.
+A similar score is used by \citet{nyman_news_2018}, who measure the effect of narratives and sentiment of financial market text-based data on developments in the financial system.
+They count the number of occurrences of excitement words and anxiety words and then scale these numbers by the total text size as measured by the number of characters.
+
+To measure the tone of a document, we use a dictionary that lists words associated with positive and negative polarity weighted within the interval of $[-1; 1]$.
+SentimentWortschatz\footnote{SentiWS for short.
+available here: http://wortschatz.uni-leipzig.de/de/download}, is a publicly available German-language resource for sentiment analysis, opinion mining etc.
+The current version of SentiWS (v1.8b) contains 1,650 positive and 1,818 negative words, which sum up to 15,649 positive and 15,632 negative word forms incl.
+their inflections, respectively.
+The sentiment score for each document $d$ is calculated as follows:
+
+\begin{equation}
+	\text{SentScore}_d = \frac{|\text{positive}_d| - |\text{negative}_d|}{|\text{TotalWords}_d|}
+\end{equation}
 

### 2018-03-12 paper/docs/04_Modelresults_50.Rmd
add 50k model

--- 2018-03-05 paper/docs/04_Modelresults_35.Rmd
@@
 library(scales)      # Scales
-library(viridis)     # Viridis color scales
 
@@
 rm(list=ls())
-col <- brewer.pal(6,"Dark2")
+col <- rcartocolor::carto_pal(12, "Bold")
 source("func/functions.R")
@@
 ```{r caching, echo = FALSE}
-load("../output/btw_out.Rda")
+load("../output/btw_out2.Rda")
 ```
 
-I conduct a STM (Strucutral Topic Model) estimation on a sample of 11,919 online news articles from seven news provider about domestic politics: Bild.de, DIE WELT, FOCUS ONLINE, SPIEGEL ONLINE, Stern.de, ZEIT ONLINE, Tagesschau.de.
+I conduct a STM (Strucutral Topic Model) estimation on a sample of 14,936 online news articles from seven news provider about domestic politics: Bild.de, DIE WELT, FOCUS ONLINE, SPIEGEL ONLINE, Stern.de, ZEIT ONLINE, Tagesschau.de.
 The articles are dated from 01.06.2017 to 31.12.2017 (German federal elections took place on 24th of September 2017.).
@@
   ggplot(aes(site)) +
-  geom_bar(fill=col[1], alpha= .8) +
+  geom_bar(fill=col[8], alpha = 0.8) +
   labs(x="", y="Number of articles") +
@@
   geom_vline(aes(xintercept=as.Date("2017-09-24")),
-             linetype = 2, color=col[2]) +
+             linetype = 2, color=col[5]) +
   scale_color_manual(values = col) +
@@
 ```{r echo = FALSE}
-load("../output/models/STM 35 .Rda")
+load("../output/models/STM 50 .Rda")
 k <- stmOut$settings$dim$K
@@
 
-```{r eval=FALSE, fig.height=12, fig.width=5, include=FALSE}
-topic <- 35
+```{r eval=FALSE, fig.height=12, fig.width=5}
+topic <- 50
 
@@
 ```{r}
-topics <- matrix(c(1, "SPD, M.Schulz", 2, "A.Merkel vs.
-Schulz", 3, "Jamaica coalition", 4, "Diesel scandal", 5, "H.Kohl", 6, "A.Merkel", 7, "Federal Election Results", 8, "Seehover vs.
-Söder, CSU", 9, "EU policies, refugee policy", 10, "German Parliament, parliamentarians", 11, "Mix: DIE LINKE, W.Schäuble", 12, "Refugees, deportation", 13, "Mix: Schröder, IT Topics", 14, "B90/Die Grünen", 15, "USA, Russia, Israel", 16, "Great coalition", 17, "A.Weidel (AfD)", 18, "Budget statistics, Welfare policy", 19, "Process Error", 20, "Federal Constitutional Court, Ministry of the Interior", 21, "German armed forces, Mali", 22, "Mix: Weather, DB, nuclear transport, ...", 23, "Elections in Niedersachsen", 24, "CDU / CSU", 25, "Mix: political talkshows, Berxit, Macron", 26, "Mix: F.-W.Steinmeier, Constitution, H.Maas", 27, "public statistics", 28, "Election polls", 29, "F.Petry, Gauland (AfD)", 30, "Mix: NSU, sexism", 31, "German armed forces, V.d.Leyen", 32, "G20 in Hamburg", 33, "Turkey, S.Gabriel", 34, "police reports, terror (left-, right-wing, IS)", 35, "Seehofer, refugee cap"), ncol=2, byrow=T)
+topics <- matrix(c(1, "SPD, M.Schulz", 2, "B90/ Die Grüne", 3, "Mix: Akhanli, Guttenberg, Bayern", 4, "Great Coalition debates", 5, "Diesel scandal", 6, "H.Kohl", 7, "Federal Election results", 8, "Europa, Macron, Schäuble", 9, "Mix: political trends, twitter", 10, "Merkel vs.
+Schulz", 11, "politics & democracy in GER", 12, "Deportation of criminal Refugees", 13, "A.Merkel", 14, "Text processing fail", 15, "Israel, antisemitism, D.Trump", 16, "Mix: political talkshows, Refugees", 17, "Decision about GroKo in the SPD", 18, "Election in Niedersachsen", 19, "N.Lammert", 20, "AfD", 21, "German armed forces, v.d.Leyen", 22, "SPD, stuffing debates", 23, "CSU, Söder vs.
+Seehover, refugee cap", 24, "Bundespräsident F.-W.Steinmeier", 25, "Election polls", 26, "Reelections after Jamaica failure", 27, "Jamaica caolition talks", 28, "G20 in Hamburg", 29, "Federal Constitutional Court, Ministry of the Interior", 30, "F.Petri, AfD", 31, "D.Trump, Russia", 32, "Gauland, Weidel, AfD", 33, "German armed forces, Mali", 34, "Mix: Children, Education, Women", 35, "Left- rightwing Terror, police reports", 36, "Mix: people, Germany, democracy", 37, "AfD in parliament", 38, "EU policies", 39, "Mix: Terror attacks", 40, "Mix: Metoo, SPD", 41, "Terror attack Berlin (Amri)", 42, "Refugee family reunion", 43, "Mix: studies", 44, "Federal Constitutional Court (NSU, Franco, Terror)", 45, "Mix: minister of the interior, environment", 46, "CDU, Spahn", 47, "Church", 48, "public budget statistics, Education and Healthcare", 49, "Turkey", 50, "Höcke, Holocaust"), ncol=2, byrow=T)
 
@@
 
-Next, we can assign a topic to each document (topic with highest postertior gamma)
+## Posterior distribution (gamma)
+
+The theta Matrix is a DxK Matrix that gives us a probability for each topic (K) and each document (D)
 
@@
 stmOut %>% tidy("theta") -> theta
+```
 
+The probability of each topic for documents 1-5 can be plotted as:
+
+```{r}
+theta %>%
+  filter(document < 6) %>%
+  ggplot(aes(factor(topic), gamma, 
+             fill = factor(document))) +
+  geom_col(position = "dodge") +
+  scale_fill_manual(values = col,
+                    guide = guide_legend(
+                      nrow = 1
+                    )) +
+  labs(x = "Topic", fill = "Document",
+       title = "Gamma distribution of documents 1-5") +
+  theme(legend.position = "bottom") 
+```
+
+As you can see, only document 2 cannot be assigned to any topic with a high probability. In the case of the other documents, it is highly likely that it belongs to a particular topic.
+
+To get a better understanding of the distribution of the "highest gamma", we assign a topic to each document (topic with highest postertior distribution).
+
+```{r}
 top_topics <- theta %>% 
@@
 
-##### How is the top-gamma value distributed among the corpus?
-
 ```{r}
-btw.2 %>%
-  ggplot(aes(gamma)) +
-  geom_density(color = col[3],
-               fill = col[3], alpha=.7) +
-  labs(x="Distribution of gamma value")
+ggplot(btw.2, aes(gamma)) +
+  geom_density(fill=col[3], alpha = 0.8,
+               color = col[3]) +
+  labs(title = "Density Plot / Posterior distribution",
+       y = "Theta")
 ```
 
-#### Inspect the unclear topics
 ```{r eval=FALSE, include=FALSE}
+# Inspect the unclear topics
 btw.2 %>% filter(topic==13) %>% select(title, gamma, url) %>%
@@
 
-```{r fig.height=6}
+```{r fig.height=8, fig.width=6}
 p1 <- ggplot(frequency, aes(x=reorder(topic_name, frequency), y=frequency)) + 
@@
 ```{r fig.height=8, fig.width=12}
-p2 <- ggplot(freq, aes(reorder(topic_name,frequency), freq)) +
+p2 <- freq %>%
+  mutate(topic =  as.numeric(gsub(":.*$","",topic))) %>% 
+  ggplot(aes(reorder(topic_name,topic), freq)) +
   geom_col(fill = col[3]) +
@@
 ```{r}
-keep <- c(1,16,24,29,3,6,8)
+keep <- c(1,2,4,10,13,17,20,22,26,27,37,46)
 ```
@@
 ```{r}
-effect <- estimateEffect(c(1:k) ~site+s(month), stmOut, 
+effect <- estimateEffect(c(1:k) ~site, stmOut, 
                          metadata = out$meta, uncertainty = "None")
@@
          parameter = gsub("site", "", parameter),
-         parameter = ifelse(parameter == "s(month)1", "1_July", parameter),
-         parameter = ifelse(parameter == "s(month)2", "2_August", parameter),
-         parameter = ifelse(parameter == "s(month)3", "3_September", parameter),
-         parameter = ifelse(parameter == "s(month)4", "4_October", parameter),
-         parameter = ifelse(parameter == "s(month)5", "5_November", parameter),
-         parameter = ifelse(parameter == "s(month)6", "6_December", parameter),
          signifcant = ifelse(p <= 0.5,"yes","no")) %>%
@@
 
-```{r fig.height=8, fig.width=12}
+```{r fig.height=4, fig.width=10}
 p1 <- coeff %>% 
@@
 # dpi = 600)
-```
-
-The following figure shows the regression results for each month. The coefficients indicate the deviation from the base value of June 2017 (keeping the news source).
-
-```{r fig.height=8, fig.width=12}
-p1 <- coeff %>% 
-  filter(topic %in% keep) %>%
-  filter(!parameter %in% stmOut$settings$covariates$yvarlevels) %>%
-  filter(parameter != "(Intercept)") %>%
-  ggplot(aes(x = reorder(topic_name,topic, decreasing=F), y = Estimate, fill=factor(signifcant))) +
-  geom_col() +
-  scale_fill_manual(values = col[c(2,1)]) +
-  scale_x_discrete(position = "top") +
-  coord_flip() +
-  facet_wrap(~parameter, ncol = 8, scales = "free_x") +
-  labs(x="", fill="significant at the 5% level") +
-  theme(legend.position = "top", 
-        axis.text.y = element_text(size=9),
-        axis.text.x = element_text(angle=90))
-
-p1
 ```
@@
   group_by(word) %>% summarise(value = mean(value)) %>% ungroup
+
+# sent %>% 
+#   dplyr::top_n(10, desc(value)) %>%
+#   htmlTable::htmlTable()
 ```
@@
 df <- btw.2 %>%
-  filter(gamma >= 0.8) %>%
+  filter(gamma >= 0.85) %>%
   filter(topic %in% keep)
@@
   #filter(!is.na(value)) %>%
-  mutate(polarity = ifelse(value < 0, "negative", "NA"),
-         polarity = ifelse(value > 0, "positive", polarity))
+  mutate(negative = ifelse(value < 0, value, NA),
+         positive = ifelse(value > 0, value, NA),
+         negative_d = ifelse(value < 0, 1, 0),
+         positive_d = ifelse(value > 0, 1, 0)) 
+```
+
+##### Check the analysis for a set of example documents.
+
+```{r}
+sentDF %>% filter(document == unique(sentDF$document)[1]) %>%
+  select(title, word, value, site) %>%
+  htmlTable::htmlTable(align = "l")
 ```
@@
 
-calculate sentiment value of document $d$:
+We apply two different measurements:
+
+  1.
+**Weighted** calculates the score based on the weighted values for a word.
+As explained above, the dictionary places the words on an interval of -1 and 1.
+The score is then calculated from the sum of the words in a document (which can be assigned to a word from the dictionary) divided by the total number of words in that document.
 
 $$
-\text{Sentiment}_d = \frac{|\text{Sum of positive tokens}_d| - |\text{Sum of negative tokens}_d|}{\text{Number ot tokens}_d}
+\text{Weighted}_d = \frac{|\text{positive polarity score}_d| - |\text{negative polarity score}_d|}{\text{Total Words}_d}
+$$
+
+  2.
+**Count** calculates the score as the difference of positive and negative words (dummy) divided divided by the total number of words in that document.
+This value therefore only reflects the relation between positive and negative words, without considering the weighting of these words.
+
+$$
+\text{Count}_d = \frac{\text{Sum of positive Words}_d - \text{Sum of negative Words}_d}{\text{Total Words}_d}
 $$
@@
 sentDF.values <- sentDF %>%
-  select(document, word, value, polarity) %>%
-  mutate(id = row_number()) %>%
-  spread(polarity, value) %>%
+  select(document, word, value, 
+         negative, positive,
+         negative_d, positive_d) %>%
   group_by(document) %>%
@@
   summarise(sum_positive = sum(positive, na.rm = T),
-            sum_negative = sum(negative, na.rm = T)) %>%
+            sum_negative = sum(negative, na.rm = T),
+            sum_positive_d = sum(positive_d, na.rm = T),
+            sum_negative_d = sum(negative_d, na.rm = T)) %>%
 
   # calculate diff
-  mutate(sent_diff = abs(sum_positive) - abs(sum_negative)) %>%
+  mutate(sent_diff = sum_positive + sum_negative,
+         sent_diff_d = sum_positive_d - sum_negative_d) %>%
 
@@
   # calculate sentiment
-  mutate(sentiment = sent_diff / text_length)
+  mutate(sentiment_d = sent_diff_d / text_length,
+         sentiment = sent_diff / text_length)
 ```
 
-### Plot Sentiment
+#### 4. Plot Sentiment
 
-#### 1. by topic
-```{r fig.height=8, fig.width=6}
+##### 4.1. by topic
+```{r fig.height=4, fig.width=7}
 p <- sentDF.values %>%
   group_by(topic_name) %>%
-  summarise(sentiment = mean(sentiment, na.rm=T),
+  summarise(sentiment_d = mean(sentiment_d, na.rm=T),
+            sentiment = mean(sentiment, na.rm=T),
             obs = n())
 
-ggplot(p, aes(reorder(topic_name, sentiment), 
+## weighted ##
+p1 <- ggplot(p, aes(reorder(topic_name, sentiment), 
               sentiment,
@@
   geom_col(fill = col[1], alpha = 0.7) +
-  geom_text() +
+  #geom_text() +
   geom_hline(yintercept = 0, linetype = 2,
@@
   labs(x="", y="",
-       title = "Grouped Sentiment value",
-       fill = "Number of\nObservations") +
-  theme(axis.text.y = element_text(size = 10))
-```
+       title = "Weighted") +
+  theme(axis.text.y = element_text(size = 8))
 
-#### 2.by site
-
-```{r}
-p <- sentDF.values %>%
-  group_by(site) %>%
-  summarise(sentiment = mean(sentiment, na.rm=T),
-            obs = n())
-
-ggplot(p, aes(reorder(site, sentiment), 
-              sentiment,
+## unweighted ##
+p2 <- ggplot(p, aes(reorder(topic_name, sentiment), 
+              sentiment_d,
               label = obs)) +
-  geom_col(fill = col[3], alpha = 0.7) +
-  geom_text() +
+  geom_col(fill = col[4], alpha = 0.7) +
+  #geom_text() +
   geom_hline(yintercept = 0, linetype = 2,
@@
   labs(x="", y="",
-       title = "Grouped Sentiment value",
-       fill = "Number of\nObservations") +
-  theme(axis.text.y = element_text(size = 10))
+       title = "Count") +
+  theme(axis.text.y = element_blank(),
+        axis.ticks.y = element_blank())
+
+p1 + p2
 ```
 
-#### 3. By site and topic
+##### 4.2. by site
+
+```{r fig.height=4, fig.width=7}
+p <- sentDF.values %>%
+  group_by(site) %>%
+  summarise(sentiment_d = mean(sentiment_d, na.rm=T),
+            sentiment = mean(sentiment, na.rm=T),
+            obs = n())
+
+## weighted ##
+p1 <- ggplot(p, aes(reorder(site, sentiment), 
+              sentiment,
+              label = obs)) +
+  geom_col(fill = col[1], alpha = 0.7) +
+  #geom_text() +
+  geom_hline(yintercept = 0, linetype = 2,
+             color = "black") +
+  coord_flip() +
+  labs(x="", y="",
+       title = "Weighted") +
+  theme(axis.text.y = element_text(size = 8))
+
+## unweighted ##
+p2 <- ggplot(p, aes(reorder(site, sentiment), 
+              sentiment_d,
+              label = obs)) +
+  geom_col(fill = col[4], alpha = 0.7) +
+  #geom_text() +
+  geom_hline(yintercept = 0, linetype = 2,
+             color = "black") +
+  coord_flip() +
+  labs(x="", y="",
+       title = "Count") +
+  theme(axis.text.y = element_blank(),
+        axis.ticks.y = element_blank())
+
+p1 + p2
+```
+
+##### 4.3. By site and topic
 
@@
   summarise(sentiment = mean(sentiment, na.rm=T),
+            sentiment_d = mean(sentiment_d, na.rm=T),
             obs = n())
 
-ggplot(p, 
+p1 <- ggplot(p, 
        aes(reorder(topic_name, topic), 
@@
   geom_col(fill=col[1], alpha = 0.7) +
-  geom_text() +
+  #geom_text() +
   geom_hline(yintercept = 0, linetype = 2,
@@
   facet_wrap(~site, ncol = 7) +
-  labs(x="", y="", fill= "Number of\nObservations",
-       title = "Sentiment value") +
-  theme(axis.text.y = element_text(size=12))
+  labs(x="", y="",
+       title = "Weighted") +
+  theme(axis.text.y = element_text(size=8))
+
+p2 <- ggplot(p, 
+       aes(reorder(topic_name, topic), 
+           sentiment_d, label = obs)) +
+  geom_col(fill=col[4], alpha = 0.7) +
+  #geom_text() +
+  geom_hline(yintercept = 0, linetype = 2,
+             color = "black") +
+  coord_flip() +
+  facet_wrap(~site, ncol = 7) +
+  labs(x="", y="",
+       title = "Count") +
+  theme(axis.text.y = element_text(size=8))
+
+p1 + p2 + plot_layout(ncol = 1)
 ```
 
-```{r}
-sentDF.values %>%
-  filter(topic == 6) %>%
-  select(title, sentiment, site) %>%
-  htmlTable::htmlTable(align = "l")
-```
-
-### Radar plot
+##### 4.4. Radar plot
 
@@
           alpha = 0, legend.position = "right") +
-  labs(title = "")
+  labs(title = "Weighted")
+```
+
+```{r eval=FALSE, include=FALSE}
+for (i in stmOut$settings$covariates$yvarlevels) {
+
+  p <-radar %>%
+    filter(site == i) %>%
+    ggRadar(rescale = F,
+            alpha = 0, legend.position = "right") +
+    labs(title = i)
+
+  ggsave(p, filename = paste0("../figs/radarchartWeighted_",i,k,".png"), 
+         device = "png", dpi = 600)
+
+}
 ```
@@
 ```{r}
+sentDF.values %>%
+  group_by(site, topic_name) %>%
+  summarise(sentiment = mean(sentiment_d, na.rm=T)) %>%
+  spread(key=topic_name, value=sentiment) -> radar
+
+radar %>%
+  ggRadar(aes(color=site), 
+          rescale = F,
+          alpha = 0, legend.position = "right") +
+  labs(title = "Count")
+```
+
+```{r eval=FALSE, include=FALSE}
 for (i in stmOut$settings$covariates$yvarlevels) {
@@
 }
+```
 
-```
+###### Weighted
+
+<img src="../figs/radarchartWeighted_Bild.de35.png", width = "49%">
+<img src="../figs/radarchartWeighted_DIE WELT35.png", width = "49%">
+<img src="../figs/radarchartWeighted_FOCUS ONLINE35.png", width = "49%">
+<img src="../figs/radarchartWeighted_SPIEGEL ONLINE35.png", width = "49%">
+<img src="../figs/radarchartWeighted_stern.de35.png", width = "49%">
+<img src="../figs/radarchartWeighted_Tagesschau.de35.png", width = "49%">
+<img src="../figs/radarchartWeighted_ZEIT ONLINE35.png", width = "49%">
+
+###### Count
 
@@
 
-### Compare with polls
+### 5. SenitmantR
+
+```{r}
+pacman::p_load(sentimentr)
+```
+
+```{r}
+sent %>%
+  mutate(polarity = value) %>%
+  as_key() -> sentiment_df
+```
+
+#### Output
+
+We may wish to see the output from sentiment_by line by line with positive/negative sentences highlighted.
+The highlight function wraps a sentiment_by output to produces a highlighted HTML file (positive = green; negative = pink).
+Here we look at a random article for each site.
+
+```{r}
+df %>% 
+  mutate(text_split = get_sentences(text)) %$%
+  sentiment(text_split,
+               polarity_dt = sentiment_df) -> df_sent
+
+df %>% 
+  group_by(site) %>%
+  sample_n(1) %>%
+  mutate(text_split = get_sentences(title_text)) %$%
+  sentiment_by(text_split, site,
+               polarity_dt = sentiment_df) %>%
+  sentimentr::highlight()
+```
+
+[Polarity](polarity.html)
+
+<!-- ### 5. Compare with polls -->
+
 ```{r eval=FALSE, include=FALSE}
 load("../output/polls.Rda")
+
+htmlTable::htmlTable(table[1:10,], align = "l")
 ```
 
-Define Functions
+<!-- Define Functions  -->
 
@@
 
-Prepare Dataframes
+<!-- Prepare Dataframes -->
 
@@
 
-Plot
+<!-- Plot  -->
 

### 2018-03-12 paper/docs/04_Modelresults_50.Rmd
its getting better...

@@
 
-# 2. Model Results
+# Model Results
 
@@
 
-## Label topics
+## 1. Topic
+
+### 1.1. Label topics
 
@@
 
-```{r eval=FALSE, fig.height=12, fig.width=5}
-topic <- 50
+```{r eval=FALSE, fig.height=8, fig.width=4}
+topic <- 1
 
-plotQuote(c(paste(sagelabs$cov.betas[[1]]$problabels[topic,], collapse="\n"),
-            paste(sagelabs$cov.betas[[2]]$problabels[topic,], collapse="\n"),
-            paste(sagelabs$cov.betas[[3]]$problabels[topic,], collapse="\n"),
-            paste(sagelabs$cov.betas[[4]]$problabels[topic,], collapse="\n"),
-            paste(sagelabs$cov.betas[[5]]$problabels[topic,], collapse="\n"),
-            paste(sagelabs$cov.betas[[6]]$problabels[topic,], collapse="\n"),
-            paste(sagelabs$cov.betas[[7]]$problabels[topic,], collapse="\n")))
+plotQuote(c(paste(sagelabs$covnames[1],":", 
+                  paste(sagelabs$cov.betas[[1]]$problabels[topic,], collapse="\n")),
+            paste(sagelabs$covnames[2],":",
+                  paste(sagelabs$cov.betas[[2]]$problabels[topic,], collapse="\n")),
+            paste(sagelabs$covnames[3],":", 
+                  paste(sagelabs$cov.betas[[3]]$problabels[topic,], collapse="\n")),
+            paste(sagelabs$covnames[4],":", 
+                  paste(sagelabs$cov.betas[[4]]$problabels[topic,], collapse="\n")),
+            paste(sagelabs$covnames[5],":", 
+                  paste(sagelabs$cov.betas[[5]]$problabels[topic,], collapse="\n")),
+            paste(sagelabs$covnames[6],":",
+                  paste(sagelabs$cov.betas[[6]]$problabels[topic,], collapse="\n")),
+            paste(sagelabs$covnames[7],":",
+                  paste(sagelabs$cov.betas[[7]]$problabels[topic,], collapse="\n"))),
+          text.cex = 0.8, width = 40,
+          main = paste(topics.df$topic_name[topics.df$topic==topic])
+          )
 ```
@@
 ```{r}
-topics <- matrix(c(1, "SPD, M.Schulz", 2, "B90/ Die Grüne", 3, "Mix: Akhanli, Guttenberg, Bayern", 4, "Great Coalition debates", 5, "Diesel scandal", 6, "H.Kohl", 7, "Federal Election results", 8, "Europa, Macron, Schäuble", 9, "Mix: political trends, twitter", 10, "Merkel vs.
-Schulz", 11, "politics & democracy in GER", 12, "Deportation of criminal Refugees", 13, "A.Merkel", 14, "Text processing fail", 15, "Israel, antisemitism, D.Trump", 16, "Mix: political talkshows, Refugees", 17, "Decision about GroKo in the SPD", 18, "Election in Niedersachsen", 19, "N.Lammert", 20, "AfD", 21, "German armed forces, v.d.Leyen", 22, "SPD, stuffing debates", 23, "CSU, Söder vs.
-Seehover, refugee cap", 24, "Bundespräsident F.-W.Steinmeier", 25, "Election polls", 26, "Reelections after Jamaica failure", 27, "Jamaica caolition talks", 28, "G20 in Hamburg", 29, "Federal Constitutional Court, Ministry of the Interior", 30, "F.Petri, AfD", 31, "D.Trump, Russia", 32, "Gauland, Weidel, AfD", 33, "German armed forces, Mali", 34, "Mix: Children, Education, Women", 35, "Left- rightwing Terror, police reports", 36, "Mix: people, Germany, democracy", 37, "AfD in parliament", 38, "EU policies", 39, "Mix: Terror attacks", 40, "Mix: Metoo, SPD", 41, "Terror attack Berlin (Amri)", 42, "Refugee family reunion", 43, "Mix: studies", 44, "Federal Constitutional Court (NSU, Franco, Terror)", 45, "Mix: minister of the interior, environment", 46, "CDU, Spahn", 47, "Church", 48, "public budget statistics, Education and Healthcare", 49, "Turkey", 50, "Höcke, Holocaust"), ncol=2, byrow=T)
+topics <- matrix(c(1, "SPD", 2, "B90/ Die Grüne & DIE LINKE", 3, "Mix: Akhanli, Guttenberg, Bayern", 4, "Great Coalition debates", 5, "Diesel scandal", 6, "H.Kohl", 7, "Federal Election results", 8, "Europa, Macron, Schäuble", 9, "Mix: political trends, twitter", 10, "Merkel vs.
+Schulz", 11, "politics & democracy in GER", 12, "Deportation of criminal Refugees", 13, "A.Merkel", 14, "Text processing fail", 15, "Israel, antisemitism, D.Trump", 16, "Mix: political talkshows, Refugees", 17, "Intra-party vote (SPD) about the coalition w CDU/CSU", 18, "Election in Niedersachsen", 19, "R.Lammert", 20, "AfD, Right-wing extremist tendencies", 21, "German armed forces, v.d.Leyen", 22, "SPD, stuffing debates", 23, "CSU, Söder vs.
+Seehover, refugee cap", 24, "Bundespräsident F.-W.Steinmeier", 25, "Election polls", 26, "Reelections vs.
+Great Coalition after Jamaica failure", 27, "Jamaica caolition talks", 28, "G20 in Hamburg", 29, "Federal Constitutional Court, Ministry of the Interior", 30, "F.Petri, AfD", 31, "D.Trump, Russia", 32, "Gauland, Weidel, AfD", 33, "German armed forces, Mali", 34, "Mix: Children, Education, Women", 35, "Left- rightwing Terror, police reports", 36, "Mix: people, Germany, democracy", 37, "AfD in parliament", 38, "EU policies", 39, "Mix: Terror attacks", 40, "Mix: Metoo, SPD", 41, "Terror attack Berlin (Amri)", 42, "Refugee family reunion", 43, "Mix: studies", 44, "Federal Constitutional Court (NSU, Franco, Terror)", 45, "Mix: minister of the interior, environment", 46, "CDU, Spahn", 47, "Church", 48, "public (budget) statistics, Education/ Healthcare/ Digital policies", 49, "Turkey", 50, "Höcke, Holocaust"), ncol=2, byrow=T)
 
@@
 
-## Posterior distribution (gamma)
+### 1.2. Posterior distribution (gamma)
 
@@
 ```
-
-The probability of each topic for documents 1-5 can be plotted as:
-
-```{r}
-theta %>%
-  filter(document < 6) %>%
-  ggplot(aes(factor(topic), gamma, 
-             fill = factor(document))) +
-  geom_col(position = "dodge") +
-  scale_fill_manual(values = col,
-                    guide = guide_legend(
-                      nrow = 1
-                    )) +
-  labs(x = "Topic", fill = "Document",
-       title = "Gamma distribution of documents 1-5") +
-  theme(legend.position = "bottom") 
-```
-
-As you can see, only document 2 cannot be assigned to any topic with a high probability. In the case of the other documents, it is highly likely that it belongs to a particular topic.
 
@@
 
-## 3.1. Topic proportions
+### 1.3 Topic proportions
 
@@
 
-```{r fig.height=8, fig.width=6}
+```{r fig.height=8, fig.width=8}
 p1 <- ggplot(frequency, aes(x=reorder(topic_name, frequency), y=frequency)) + 
@@
 
-Keep only those articles, that are clear & interessting to analyse.
+```{r eval=FALSE, include=FALSE}
+btw.2 %>% filter(topic == 46) %>%
+  filter(!grepl("Geißler", title)) %>%
+  select(title, url, site) %>%
+  htmlTable::htmlTable(align = "l")
+```
+
+We will conduct our further analysis on 15 selected topics which relate to political parties.
 
 ```{r}
-keep <- c(1,2,4,10,13,17,20,22,26,27,37,46)
+keep <- c(1,2,4,10,13,17,20,22,23,26,27,30,32,37,46)
 ```
 
-## 3.2. Difference in topic prevalence
+### 1.4. Difference in topic prevalence
 
@@
 
-## Sentiment analysis
+## 2. Tone
+
+### 2.1. Plotquote
+
+The plotQuote function allows to inspect die most common words of a topic for each covariate.
+
+```{r eval=FALSE, fig.height=8, fig.width=4}
+for (topic in keep) {
+
+  png(filename = paste0("../figs/plotquote",topic,".png"), width = 300,
+      height = 700)
+
+  plotQuote(c(paste(sagelabs$covnames[1],":", 
+                  paste(sagelabs$cov.betas[[1]]$problabels[topic,], collapse="\n")),
+            paste(sagelabs$covnames[2],":",
+                  paste(sagelabs$cov.betas[[2]]$problabels[topic,], collapse="\n")),
+            paste(sagelabs$covnames[3],":", 
+                  paste(sagelabs$cov.betas[[3]]$problabels[topic,], collapse="\n")),
+            paste(sagelabs$covnames[4],":", 
+                  paste(sagelabs$cov.betas[[4]]$problabels[topic,], collapse="\n")),
+            paste(sagelabs$covnames[5],":", 
+                  paste(sagelabs$cov.betas[[5]]$problabels[topic,], collapse="\n")),
+            paste(sagelabs$covnames[6],":",
+                  paste(sagelabs$cov.betas[[6]]$problabels[topic,], collapse="\n")),
+            paste(sagelabs$covnames[7],":",
+                  paste(sagelabs$cov.betas[[7]]$problabels[topic,], collapse="\n"))),
+          text.cex = 0.8, width = 40,
+          main = paste(topics.df$topic_name[topics.df$topic==topic])
+          )
+  dev.off()
+}
+```
+
+<img src="../figs/plotquote1.png", width = "30%">
+<img src="../figs/plotquote2.png", width = "30%">
+<img src="../figs/plotquote4.png", width = "30%">
+<img src="../figs/plotquote10.png", width = "30%">
+<img src="../figs/plotquote13.png", width = "30%">
+<img src="../figs/plotquote17.png", width = "30%">
+<img src="../figs/plotquote20.png", width = "30%">
+<img src="../figs/plotquote22.png", width = "30%">
+<img src="../figs/plotquote23.png", width = "30%">
+<img src="../figs/plotquote26.png", width = "30%">
+<img src="../figs/plotquote27.png", width = "30%">
+<img src="../figs/plotquote30.png", width = "30%">
+<img src="../figs/plotquote32.png", width = "30%">
+<img src="../figs/plotquote37.png", width = "30%">
+<img src="../figs/plotquote46.png", width = "30%">
+
+### 2.2. Sentiment analysis
 
@@
 
-#### 1. Load sentiment dictionary.
+#### 2.2.1. Load sentiment dictionary.
 
@@
   group_by(word) %>% summarise(value = mean(value)) %>% ungroup
-
-# sent %>% 
-#   dplyr::top_n(10, desc(value)) %>%
-#   htmlTable::htmlTable()
 ```
 
-#### 2. Apply the dictionary on the artciles.
+#### 2.2.2. Apply the dictionary on the artciles.
 
-We now take each word in each article and assign a sentiment value for that word. I only use articles that have been assigned a topic with a probability of over 90% (gamma > 0.9).
+To carry out the sentiment analysis we filter some documents from the corpus:
+
+  1. Articles that have been assigned a topic with a probability of over 75% (gamma > 0.75).
+  2. Articles assigned to one of the above mentioned topics.
+  3. Some manual cleanups
+
+After applying these filters, we still have about 2500 articles left to conduct the sentiment analysis. We now take each word in each article and assign a sentiment value for that word.
 
@@
 df <- btw.2 %>%
-  filter(gamma >= 0.85) %>%
-  filter(topic %in% keep)
+  filter(gamma >= 0.75) %>%
+  distinct(title, .keep_all = T) %>%
+  filter(topic %in% keep) %>%
+  # Filter documents about the death of H.Geißler
+  filter(!grepl("Geißler", title)) %>%
+  # Filter outliner article (wrong topic assignment)
+  filter(document != 9725) %>%
+  filter(!grepl("Thermilindner", title, ignore.case = T))
 
@@
 
-##### Check the analysis for a set of example documents.
+#### 2.2.3. Check the analysis for a set of example documents.
 
@@
 
-#### 3. Calculate sentiment value by document
+#### 2.2.4. Calculate sentiment value by document
 
-We apply two different measurements:
-
-  1.
-**Weighted** calculates the score based on the weighted values for a word.
-As explained above, the dictionary places the words on an interval of -1 and 1.
+The sentiment score is calculated based on the weighted polarity values for a word, defined on an interval between -1 and 1.
 The score is then calculated from the sum of the words in a document (which can be assigned to a word from the dictionary) divided by the total number of words in that document.
@@
 \text{Weighted}_d = \frac{|\text{positive polarity score}_d| - |\text{negative polarity score}_d|}{\text{Total Words}_d}
-$$
-
-  2.
-**Count** calculates the score as the difference of positive and negative words (dummy) divided divided by the total number of words in that document.
-This value therefore only reflects the relation between positive and negative words, without considering the weighting of these words.
-
-$$
-\text{Count}_d = \frac{\text{Sum of positive Words}_d - \text{Sum of negative Words}_d}{\text{Total Words}_d}
 $$
@@
   mutate(sentiment_d = sent_diff_d / text_length,
-         sentiment = sent_diff / text_length)
+         sentiment = sent_diff / text_length) %>%
+
+  # generate week
+  mutate(week = week(date),
+         month = as.character(month)) %>%
+  mutate(week = paste(month,week, sep = "-"))
 ```
 
-#### 4. Plot Sentiment
+#### 2.2.5. Plot Sentiment Score
 
-##### 4.1. by topic
-```{r fig.height=4, fig.width=7}
+The following figure shows the results of the analysis for each topic on a monthly basis, aggregated on all newspaper.
+Some conclusions can be drawn from this illustration.
+First of all, it is clear that topics concerning the AfD (20, 30, 32, 37) are discussed in a negative way over the entire period, with an exepction for topic 30, dealing with Frauk Petry and the AfD.
+The topic that is discussed most negatively is that of the right-wing extremist tendencies within the AfD.
+Another striking result is that the sentiment score of topics topics that deal with the SPD alone (1, 22) is diminishing in the course of time.
+The topic, which contains the CDU in isolation (46), is rather zigzagging, with a high peak in November 2017 and a low peak in January 2018, but there is only one observation this month, which is an article about Peter Tauber's illness.
+
+Concerning the issues that discuss possible coalitions, it is evident that there was a month in which the Jamaican coalition was positively discussed (topic 27): October 2017, when coalition talks were in full swing.
+With the failure of the negotiations, the sentiment value of the articles also decreases, while the number of articles dealing with this topic increases sharply in the short term (to 210 articles) and decreases significantly in the following months.
+It is striking that precisely at this time (December 2017), both the observations, as well as the sentiment value of the articles that report on the grand coalition increase (topic 4).
+
+##### By Month & Topic
+```{r fig.height=10, fig.width=12}
 p <- sentDF.values %>%
-  group_by(topic_name) %>%
-  summarise(sentiment_d = mean(sentiment_d, na.rm=T),
-            sentiment = mean(sentiment, na.rm=T),
-            obs = n())
+  group_by(month, topic_name, topic) %>%
+  summarise(sentiment = mean(sentiment, na.rm=T),
+            sentiment_d = mean(sentiment_d, na.rm=T),
+            obs = n()) %>%
+  ungroup()
 
-## weighted ##
-p1 <- ggplot(p, aes(reorder(topic_name, sentiment), 
-              sentiment,
+p1 <- ggplot(p, 
+       aes(month, sentiment, 
+           group = topic_name,
            label = obs)) +
+  facet_wrap(~topic_name, nrow = 3) +
   geom_col(fill = col[1], alpha = 0.7) +
-  #geom_text() +
+ geom_line(color = col[2], size = 1) +
+  geom_text() +
   geom_hline(yintercept = 0, linetype = 2,
              color = "black") +
-  coord_flip() +
   labs(x="", y="",
-       title = "Weighted") +
-  theme(axis.text.y = element_text(size = 8))
+       title = "Monthly Sentiment Score") +
+  theme(axis.text.y = element_text(size=8),
+        axis.text.x = element_text(angle = 90, size = 6))
 
-## unweighted ##
-p2 <- ggplot(p, aes(reorder(topic_name, sentiment), 
-              sentiment_d,
-              label = obs)) +
-  geom_col(fill = col[4], alpha = 0.7) +
-  #geom_text() +
-  geom_hline(yintercept = 0, linetype = 2,
-             color = "black") +
-  coord_flip() +
-  labs(x="", y="",
-       title = "Count") +
-  theme(axis.text.y = element_blank(),
-        axis.ticks.y = element_blank())
-
-p1 + p2
+p1
 ```
 
-##### 4.2. by site
+##### By Site and Topic
 
-```{r fig.height=4, fig.width=7}
-p <- sentDF.values %>%
-  group_by(site) %>%
-  summarise(sentiment_d = mean(sentiment_d, na.rm=T),
-            sentiment = mean(sentiment, na.rm=T),
-            obs = n())
-
-## weighted ##
-p1 <- ggplot(p, aes(reorder(site, sentiment), 
-              sentiment,
-              label = obs)) +
-  geom_col(fill = col[1], alpha = 0.7) +
-  #geom_text() +
-  geom_hline(yintercept = 0, linetype = 2,
-             color = "black") +
-  coord_flip() +
-  labs(x="", y="",
-       title = "Weighted") +
-  theme(axis.text.y = element_text(size = 8))
-
-## unweighted ##
-p2 <- ggplot(p, aes(reorder(site, sentiment), 
-              sentiment_d,
-              label = obs)) +
-  geom_col(fill = col[4], alpha = 0.7) +
-  #geom_text() +
-  geom_hline(yintercept = 0, linetype = 2,
-             color = "black") +
-  coord_flip() +
-  labs(x="", y="",
-       title = "Count") +
-  theme(axis.text.y = element_blank(),
-        axis.ticks.y = element_blank())
-
-p1 + p2
-```
-
-##### 4.3. By site and topic
-
-```{r fig.height=8, fig.width=12}
+```{r fig.height=5, fig.width=10}
 p <- sentDF.values %>%
@@
            sentiment, label = obs)) +
-  geom_col(fill=col[1], alpha = 0.7) +
-  #geom_text() +
+  geom_col(fill=col[2], alpha = 0.7) +
+  geom_text(size = 2.5) +
   geom_hline(yintercept = 0, linetype = 2,
@@
   labs(x="", y="",
-       title = "Weighted") +
-  theme(axis.text.y = element_text(size=8))
+       title = "Sentiment Score") +
+  theme(axis.text.y = element_text(size=8),
+        axis.text.x = element_text(angle = 90))
 
-p2 <- ggplot(p, 
-       aes(reorder(topic_name, topic), 
-           sentiment_d, label = obs)) +
-  geom_col(fill=col[4], alpha = 0.7) +
-  #geom_text() +
-  geom_hline(yintercept = 0, linetype = 2,
-             color = "black") +
-  coord_flip() +
-  facet_wrap(~site, ncol = 7) +
-  labs(x="", y="",
-       title = "Count") +
-  theme(axis.text.y = element_text(size=8))
-
-p1 + p2 + plot_layout(ncol = 1)
+p1
 ```
 
-##### 4.4. Radar plot
+##### Radar plot
 
@@
 
-```{r}
+```{r fig.height=10, fig.width=10}
 sentDF.values %>%
@@
           alpha = 0, legend.position = "right") +
-  labs(title = "Weighted")
+  labs(title = "Sentiment score Jun 2017-March 2018") +
+  guides(col = guide_legend(nrow = 1)) +
+  theme(legend.position = "bottom")
 ```
@@
 ```{r eval=FALSE, include=FALSE}
-for (i in stmOut$settings$covariates$yvarlevels) {
+for (i in unique(sentDF.values$month)) {
+
+  sentDF.values %>%
+  filter(month == i) %>%
+  group_by(site, topic_name) %>%
+  summarise(sentiment = mean(sentiment, na.rm=T)) %>%
+  spread(key=topic_name, value=sentiment) -> radar
 
   p <-radar %>%
-    filter(site == i) %>%
-    ggRadar(rescale = F,
+    ggRadar(aes(color=site), 
+          rescale = F,
           alpha = 0, legend.position = "right") +
-    labs(title = i)
+  labs(title = paste("Sentiment Score", i))
 
-  ggsave(p, filename = paste0("../figs/radarchartWeighted_",i,k,".png"), 
+  ggsave(p, filename = paste0("../figs/radarchart_",i,".png"), 
          device = "png", dpi = 600)
@@
 
-```{r}
-sentDF.values %>%
-  group_by(site, topic_name) %>%
-  summarise(sentiment = mean(sentiment_d, na.rm=T)) %>%
-  spread(key=topic_name, value=sentiment) -> radar
-
-radar %>%
-  ggRadar(aes(color=site), 
-          rescale = F,
-          alpha = 0, legend.position = "right") +
-  labs(title = "Count")
-```
-
-```{r eval=FALSE, include=FALSE}
-for (i in stmOut$settings$covariates$yvarlevels) {
-
-  p <-radar %>%
-    filter(site == i) %>%
-    ggRadar(rescale = F,
-            alpha = 0, legend.position = "right") +
-    labs(title = i)
-
-  ggsave(p, filename = paste0("../figs/radarchart_",i,k,".png"), 
-         device = "png", dpi = 600)
-
-}
-```
-
-###### Weighted
-
-<img src="../figs/radarchartWeighted_Bild.de35.png", width = "49%">
-<img src="../figs/radarchartWeighted_DIE WELT35.png", width = "49%">
-<img src="../figs/radarchartWeighted_FOCUS ONLINE35.png", width = "49%">
-<img src="../figs/radarchartWeighted_SPIEGEL ONLINE35.png", width = "49%">
-<img src="../figs/radarchartWeighted_stern.de35.png", width = "49%">
-<img src="../figs/radarchartWeighted_Tagesschau.de35.png", width = "49%">
-<img src="../figs/radarchartWeighted_ZEIT ONLINE35.png", width = "49%">
-
-###### Count
-
-<img src="../figs/radarchart_Bild.de35.png", width = "49%">
-<img src="../figs/radarchart_DIE WELT35.png", width = "49%">
-<img src="../figs/radarchart_FOCUS ONLINE35.png", width = "49%">
-<img src="../figs/radarchart_SPIEGEL ONLINE35.png", width = "49%">
-<img src="../figs/radarchart_stern.de35.png", width = "49%">
-<img src="../figs/radarchart_Tagesschau.de35.png", width = "49%">
-<img src="../figs/radarchart_ZEIT ONLINE35.png", width = "49%">
-
-### 5. SenitmantR
-
-```{r}
-pacman::p_load(sentimentr)
-```
-
-```{r}
-sent %>%
-  mutate(polarity = value) %>%
-  as_key() -> sentiment_df
-```
-
-#### Output
-
-We may wish to see the output from sentiment_by line by line with positive/negative sentences highlighted.
-The highlight function wraps a sentiment_by output to produces a highlighted HTML file (positive = green; negative = pink).
-Here we look at a random article for each site.
-
-```{r}
-df %>% 
-  mutate(text_split = get_sentences(text)) %$%
-  sentiment(text_split,
-               polarity_dt = sentiment_df) -> df_sent
-
-df %>% 
-  group_by(site) %>%
-  sample_n(1) %>%
-  mutate(text_split = get_sentences(title_text)) %$%
-  sentiment_by(text_split, site,
-               polarity_dt = sentiment_df) %>%
-  sentimentr::highlight()
-```
-
-[Polarity](polarity.html)
+<!-- <img src="../figs/radarchart_2017-06.png", width = "49%"> -->
+<!-- <img src="../figs/radarchart_2017-07.png", width = "49%"> -->
+<!-- <img src="../figs/radarchart_2017-09.png", width = "49%"> -->
+<!-- <img src="../figs/radarchart_2017-10.png", width = "49%"> -->
+<!-- <img src="../figs/radarchart_2017-11.png", width = "49%"> -->
+<!-- <img src="../figs/radarchart_2017-12.png", width = "49%"> -->
+<!-- <img src="../figs/radarchart_2018-01.png", width = "49%"> -->
+<!-- <img src="../figs/radarchart_2018-02.png", width = "49%"> -->
 

### 2018-03-12 paper/writing/doc_backup.tex
its getting better...

@@
 \end{itemize}
+
+\begin{enumerate}
+	\item \textbf{Discovering Topics (Section \ref{ch_model})} To discover the latent topics in the corpus, the structural topic modeling (STM) developed by \citet{roberts_model_2016} is applied.
+The STM is an unsupervised machine learning approach that models topics as multinomial distributions of words and documents as multinomial distributions of topics, allowing to incorporate external variables that effect both, topical content and topical prevalence.
+I estimate a model, where the newswire service is included as a control for both the topical content and the topical prevalence.
+The result of the generative process of STM are the posterior distributions for topic prevalence and topical content, which can then be used to measure the similarity between private and public news providers in the further course of the paper: (1) $\beta$ is a $K$-by-$V$ matrix (where $K=$ number of topics and $V=$ vocabulary), where the entry $\beta_{kvc}$ can be interpreted as the probability of observing the $v$-th word in topic $k$ for the covariate level $c$.
+(2) $\theta$ is a $D$-by-$V$ matrix of the document-topic distributions, where the entry $\theta_{dk}$ can be interpreted as the proportion of words in document $d$ which arise from topic $k$, or rather as the probability that document $d$ deals about topic $k$.
+
+	\item \textbf{Measuring Similarity of news content} Different approaches are used to examine similarities and/or differences of content between the news provider:
+	\begin{enumerate}
+		\item\label{item_1}\textbf{Differences in topic prevalence:} As I allow prevalence of topics to evolve over time (by month) and vary across business models, the posterior topic-probability $\theta_{dk}$ of document can be used to estimate the conditional expectation of topic prevalence for given document characteristics.
+
+		\item\label{item_2} \textbf{Topic correlation} To get an idea of how topics are linked and framed differently across news wires, the correlation of the posterior probability of topics $\theta_{dk}$ is calculated.
+
+		\item\label{item_3} \textbf{Differences in word-topic distributions} As each row of $\beta_{kvc}$ corresponds to the word-distribution of a respective topic for the covariate level $c$, it can be used to calculate the similarity of the word-topic distribution between the news provider using established similarity measures.
+
+		\end{enumerate}
+
+\end{enumerate}
 

### 2018-03-12 paper/writing/structure.tex
its getting better...

@@
 
-- More information available, more pluralism? 
- Pluralism and diversely sourced media are on the decline, whereas concentration of media ownership and consolidation are increasing.
+At the same time, the number of people who find out about current news on the Internet is also increasing.
+According to a study on the media coverage of the German-speaking population, nearly 40\% of respondents used the internet at least once a week in 2017 to inform themselves about the current news compared to 34\% in 2016 \citep{vuma_arbeitsgemeinschaft_verbrauchs-_und_medienanalyse_verbrauchs-_2017}.
 
-More specifically, I use a data set of German online news articles about domestic politics dated from 01.06.2017 to 31.12.2017\footnote{German federal elections took place on 24th of September 2017.} from six German news content providers.
-I analyze how the topics are discussed differently in public and private news.
-
-The research strategy is as follows:
+This paper examines to what extent the content of different online news resembles each other.
+More specifically, I use a data set of German online news articles about domestic politics dated from 01.06.2017 to 31.12.2017\footnote{German federal elections took place on 24th of September 2017.} from seven German news content providers.
+The final step is to check whether the tonality of reporting is reflected in the polls.
+The empirical strategy follows a novel approach combining "the two Ts": Topic and Tone \citep{hansen_shocking_2016}.
+That is, first the topics covered in the articles are identified, to find out how these topics are discussed (tone).
+More precisely, the research strategy is as follows:
 
@@
 The STM is an unsupervised machine learning approach that models topics as multinomial distributions of words and documents as multinomial distributions of topics, allowing to incorporate external variables that effect both, topical content and topical prevalence.
-I will include the business model (public or private) as a control for both the topical content and the topical prevalence.
-Additional, the month an article was published is included as a control for the topical prevalence.
-The result of the generative process of STM are the posterior distributions for topic prevalence and topical content, which can then be used to measure the similarity between private and public news providers in the further course of the paper: (1) $\beta$ is a $K$-by-$V$ matrix (where $K=$ number of topics and $V=$ vocabulary), where the entry $\beta_{kvc}$ can be interpreted as the probability of observing the $v$-th word in topic $k$ for the covariate level $c$.
+I estimate a model, where the newswire service is included as a control for both the topical content and the topical prevalence.
+The result of the generative process of STM are the posterior distributions for topic prevalence and topical content, which can then be used to measure the similarity between the news providers in the further course of the paper: (1) $\beta$ is a $K$-by-$V$ matrix (where $K=$ number of topics and $V=$ vocabulary) containing the probability distribution for topic $k$ over the words in the predefined vocabulary.
 (2) $\theta$ is a $D$-by-$V$ matrix of the document-topic distributions, where the entry $\theta_{dk}$ can be interpreted as the proportion of words in document $d$ which arise from topic $k$, or rather as the probability that document $d$ deals about topic $k$.
+As the prevalence of topics are allowed to vary across news wires, the posterior topic-probability $\theta_{dk}$ of an article (document) can be used to estimate the conditional expectation of topic prevalence for given article characteristics.
 
-	\item \textbf{Measuring Similarity of news content} Different approaches are used to examine similarities and/or differences of content between the news provider:
-	\begin{enumerate}
-		\item\label{item_1}\textbf{Differences in topic prevalence:} As I allow prevalence of topics to evolve over time (by month) and vary across business models, the posterior topic-probability $\theta_{dk}$ of document can be used to estimate the conditional expectation of topic prevalence for given document characteristics.
-
-		\item\label{item_2} \textbf{Topic correlation} To get an idea of how topics are linked and framed differently across news wires, the correlation of the posterior probability of topics $\theta_{dk}$ is calculated.
-
-		\item\label{item_3} \textbf{Differences in word-topic distributions} As each row of $\beta_{kvc}$ corresponds to the word-distribution of a respective topic for the covariate level $c$, it can be used to calculate the similarity of the word-topic distribution between the news provider using established similarity measures.
+	\item \textbf{Measuring Tone} After assigning a topic to each article (document), a dictionary-based sentiment analysis is conducted to estimate how topics are discussed differently by different news wires.
 
@@
 
-\end{enumerate}
+Approach \ref{item_1} has been used in \citet{roberts_model_2016}, among others, to examine differences in the content of news providers.
+However, I extend the analysis by comparing the sentiment score for a given topic between the news provider, to identify which topics are discussed similar or differently (\ref{item_2}).
+\citet{hansen_shocking_2016} applied a similar approach to a dataset of 142 FOMC decision statements to measure the effect of those statements on macroeconomic variables.
 
-Approaches \ref{item_1} and \ref{item_2} have been used in \citet{roberts_model_2016}, among others, to examine differences in the content of news providers.
-However, I extend the analysis by calculating the similarity of the word-topic distribution between the news provider, to identify which topics are discussed similar or differently (\ref{item_3}).
-In addition, this approach is applied to a new dataset covering recent political trends in Germany.
-
-The remaining course of the paper is as follows: In Section \ref{ch_onlinenews} I briefly discuss the characteristics of the market for online news in Germany.
+The remaining course of the paper is as follows: In Section \ref{ch_onlinenews} the characteristics of the market for online news in Germany are outlined.
 The data used to conduct the model is described in Section \ref{ch_data}.
 Section \ref{ch_model} explains the generative process of the structural topic model as well as the selected parameters to run the model.
-The results are the evaluated in Section \ref{ch_empirical}.
+The results of the STM, as well as the sentiment analysis are the evaluated in Section \ref{ch_empirical}.
 
@@
 
-I conduct the estimation on a sample of 9,393 online news articles from six news provider about domestic politics\footnote{Bild.de, DIE WELT, FOCUS ONLINE, SPIEGEL ONLINE, ZEIT ONLINE, Tagesschau.de}, of which only Tagesschau.de belongs to the group of public provider.
+I conduct the estimation on a sample of 14,937 online news articles from six news provider about domestic politics\footnote{Bild.de, DIE WELT, FOCUS ONLINE, SPIEGEL ONLINE, Stern.de, ZEIT ONLINE, Tagesschau.de}, of which only Tagesschau.de belongs to the group of public provider.
 The reason for this is that the content structure of Tagesschau.de is most similar to that of the private providers.
 ZDF.de offers predominantly video content and DLF website mainly offers audio content in the form of interviews, which makes it hard to include it in the model.
-However, as only a part of the private suppliers are included to maintain the proportions between private and public market participants are maintained, thus minimizing possible bias.
-The articles are dated from 01.06.2017 to 31.12.2017.\footnote{German federal elections took place on 24th of September 2017.} I first extract all online articles using the the Webhose.io API.\footnote{For more information see https://docs.webhose.io/v1.0/docs/getting-started.
+The articles are dated from 01.06.2017 to 01.03.2018.\footnote{German federal elections took place on 24th of September 2017.} I first extract all online articles using the the Webhose.io API.\footnote{For more information see https://docs.webhose.io/v1.0/docs/getting-started.
 The scraping code was written in Python and can be made available on request.} Then all articles from the section "domestic policy" are filtered by checking the URL structure.

### 2018-03-13 paper/docs/04_Modelresults_50.Rmd
combine with polls

@@
 topics <- matrix(c(1, "SPD", 2, "B90/ Die Grüne & DIE LINKE", 3, "Mix: Akhanli, Guttenberg, Bayern", 4, "Great Coalition debates", 5, "Diesel scandal", 6, "H.Kohl", 7, "Federal Election results", 8, "Europa, Macron, Schäuble", 9, "Mix: political trends, twitter", 10, "Merkel vs.
-Schulz", 11, "politics & democracy in GER", 12, "Deportation of criminal Refugees", 13, "A.Merkel", 14, "Text processing fail", 15, "Israel, antisemitism, D.Trump", 16, "Mix: political talkshows, Refugees", 17, "Intra-party vote (SPD) about the coalition w CDU/CSU", 18, "Election in Niedersachsen", 19, "R.Lammert", 20, "AfD, Right-wing extremist tendencies", 21, "German armed forces, v.d.Leyen", 22, "SPD, stuffing debates", 23, "CSU, Söder vs.
-Seehover, refugee cap", 24, "Bundespräsident F.-W.Steinmeier", 25, "Election polls", 26, "Reelections vs.
-Great Coalition after Jamaica failure", 27, "Jamaica caolition talks", 28, "G20 in Hamburg", 29, "Federal Constitutional Court, Ministry of the Interior", 30, "F.Petri, AfD", 31, "D.Trump, Russia", 32, "Gauland, Weidel, AfD", 33, "German armed forces, Mali", 34, "Mix: Children, Education, Women", 35, "Left- rightwing Terror, police reports", 36, "Mix: people, Germany, democracy", 37, "AfD in parliament", 38, "EU policies", 39, "Mix: Terror attacks", 40, "Mix: Metoo, SPD", 41, "Terror attack Berlin (Amri)", 42, "Refugee family reunion", 43, "Mix: studies", 44, "Federal Constitutional Court (NSU, Franco, Terror)", 45, "Mix: minister of the interior, environment", 46, "CDU, Spahn", 47, "Church", 48, "public (budget) statistics, Education/ Healthcare/ Digital policies", 49, "Turkey", 50, "Höcke, Holocaust"), ncol=2, byrow=T)
+Schulz", 11, "politics & democracy in GER", 12, "Deportation of criminal Refugees", 13, "A.Merkel", 14, "Text processing fail", 15, "Israel, antisemitism, D.Trump", 16, "Mix: political talkshows, Refugees", 17, "Votes within SPD", 18, "Election in Niedersachsen", 19, "R.Lammert", 20, "AfD, Right-wing extremist tendencies", 21, "German armed forces, v.d.Leyen", 22, "SPD, stuffing debates", 23, "CSU, Söder vs.
+Seehover, refugee cap", 24, "Bundespräsident F.-W.Steinmeier", 25, "Election polls", 26, "Jamaica failure", 27, "Jamaica Coalition debates", 28, "G20 in Hamburg", 29, "Federal Constitutional Court, Ministry of the Interior", 30, "F.Petri, AfD", 31, "D.Trump, Russia", 32, "Gauland, Weidel, AfD", 33, "German armed forces, Mali", 34, "Mix: Children, Education, Women", 35, "Left- rightwing Terror, police reports", 36, "Mix: people, Germany, democracy", 37, "AfD in parliament", 38, "EU policies", 39, "Mix: Terror attacks", 40, "Mix: Metoo, SPD", 41, "Terror attack Berlin (Amri)", 42, "Refugee family reunion", 43, "Mix: studies", 44, "Federal Constitutional Court (NSU, Franco, Terror)", 45, "Mix: minister of the interior, environment", 46, "CDU, J.Spahn, Tauber (Disease)", 47, "Church", 48, "public (budget) statistics, Education/ Healthcare/ Digital policies", 49, "Turkey", 50, "Höcke, Holocaust"), ncol=2, byrow=T)
 
@@
 
-# ggsave(plot = p1, filename = "../figs/estimates.png", device = "png",width = 10, height = 7,
-# dpi = 600)
+ggsave(plot = p1, filename = "../figs/estimates.png", device = "png",width = 10, height = 7,
+dpi = 600)
 ```
@@
 ```{r}
-sentDF %>% filter(document == unique(sentDF$document)[1]) %>%
+sentDF %>% filter(document == unique(sentDF$document)[2]) %>%
   select(title, word, value, site) %>%
@@
 $$
-
 ```{r}
@@
 
-  # generate week
+  # generate month & week
   mutate(week = week(date),
-         month = as.character(month)) %>%
-  mutate(week = paste(month,week, sep = "-"))
+         month = month(date),
+         year = year(date),
+         yearmonth = calculate_month(month,year),
+         yearweek = calculate_week(week, year)) 
 ```
@@
 #### 2.2.5. Plot Sentiment Score
+```{r}
+btw.2 %>% 
+  mutate(yearmonth = calculate_month(month(date), year(date))) %>%
+  group_by(yearmonth) %>%
+  summarise(total_obs = n()) -> tally_month
+
+btw.2 %>%
+  group_by(site) %>%
+  summarise(total_obs = n()) -> tally_site
+
+btw.2 %>% 
+  mutate(yearmonth = calculate_month(month(date),year(date))) %>%
+  group_by(yearmonth, site) %>%
+  summarise(total_obs = n()) -> tally_month_site
+```
 
 The following figure shows the results of the analysis for each topic on a monthly basis, aggregated on all newspaper.
+Each sentiment value is weighted by the relative share of the topic in the overall reporting of that month.
+
+$$
+\text{w} = \frac{\text{# of obs per month & topic}}{\text{# of obs per month}}
+$$
+
+$$
+\text{weighted sentiment} = \text{sentiment} * \text{w}
+$$
+
 Some conclusions can be drawn from this illustration.
@@
 ##### By Month & Topic
-```{r fig.height=10, fig.width=12}
+```{r fig.height=12, fig.width=10}
 p <- sentDF.values %>%
-  group_by(month, topic_name, topic) %>%
+  group_by(yearmonth, topic_name, topic) %>%
   summarise(sentiment = mean(sentiment, na.rm=T),
-            sentiment_d = mean(sentiment_d, na.rm=T),
             obs = n()) %>%
-  ungroup()
+  left_join(., tally_month, by = "yearmonth") %>%
+  mutate(w = obs / total_obs,
+         sentiment_w = sentiment * w)
 
 p1 <- ggplot(p, 
-       aes(month, sentiment, 
+       aes(yearmonth, sentiment, 
            group = topic_name,
@@
   geom_col(fill = col[1], alpha = 0.7) +
- geom_line(color = col[2], size = 1) +
-  geom_text() +
+ geom_line(color = col[2], size = 0.8) +
+  #geom_text() +
   geom_hline(yintercept = 0, linetype = 2,
@@
   labs(x="", y="",
-       title = "Monthly Sentiment Score") +
+       title = "Monthly Sentiment Score",
+       subtitle = "unweighted") +
   theme(axis.text.y = element_text(size=8),
-        axis.text.x = element_text(angle = 90, size = 6))
+        axis.text.x = element_text(size = 10))
 
-p1
+p2 <- ggplot(p, 
+       aes(yearmonth, sentiment_w, 
+           group = topic_name,
+           label = obs)) +
+  facet_wrap(~topic_name, nrow = 3) +
+  geom_col(fill = col[2], alpha = 0.7) +
+ geom_line(color = col[1], size = 0.8) +
+  #geom_text() +
+  geom_hline(yintercept = 0, linetype = 2,
+             color = "black") +
+  labs(x="", y="",
+       title = "",
+       subtitle = "weighted") +
+  theme(axis.text.y = element_text(size=8),
+        axis.text.x = element_text(size = 10))
+
+p1 + p2 + plot_layout(ncol = 1)
 ```
@@
 
-```{r fig.height=5, fig.width=10}
+The following figure shows the results of the analysis for each topic and each newspaper, aggregated over time.
+Each sentiment value is weighted by the relative share of the topic in the overall political news coverage of that online newspaper.
+
+$$
+\text{w} = \frac{\text{# of obs per newspaper & topic}}{\text{# of obs per newspaper}}
+$$
+
+$$
+\text{weighted sentiment} = \text{sentiment} * \text{w}
+$$
+
+```{r fig.height=12, fig.width=10}
 p <- sentDF.values %>%
@@
   summarise(sentiment = mean(sentiment, na.rm=T),
-            sentiment_d = mean(sentiment_d, na.rm=T),
-            obs = n())
+            obs = n()) %>%
+  left_join(., tally_site, by = "site") %>%
+  mutate(w = obs/total_obs,
+         sentiment_w = sentiment * w)
 
@@
        aes(reorder(topic_name, topic), 
-           sentiment, label = obs)) +
+           sentiment, 
+           group = site,
+           label = obs)) +
   geom_col(fill=col[2], alpha = 0.7) +
-  geom_text(size = 2.5) +
+  #geom_line(color = col[1], size = 0.8) +
+  #geom_text(size = 2.5) +
   geom_hline(yintercept = 0, linetype = 2,
@@
   labs(x="", y="",
-       title = "Sentiment Score") +
-  theme(axis.text.y = element_text(size=8),
-        axis.text.x = element_text(angle = 90))
+       title = "Sentiment Score",
+       subtitle = "unweighted") +
+  theme(axis.text.y = element_text(size = 10),
+        axis.text.x = element_text(size=6))
 
-p1
+p2 <- ggplot(p, 
+       aes(reorder(topic_name, topic), 
+           sentiment_w, 
+           group = site,
+           label = obs)) +
+  geom_col(fill=col[1], alpha = 0.7) +
+  #geom_line(color = col[2], size = 0.8) +
+  #geom_text(size = 2.5) +
+  geom_hline(yintercept = 0, linetype = 2,
+             color = "black") +
+  coord_flip() +
+  facet_wrap(~site, ncol = 7) +
+  labs(x="", y="",
+       title = "",
+       subtitle = "weighted") +
+  theme(axis.text.y = element_text(size = 10),
+        axis.text.x = element_text(size=6))
+
+p1 + p2 + plot_layout(ncol = 1)
 ```
@@
           alpha = 0, legend.position = "right") +
-  labs(title = "Sentiment score Jun 2017-March 2018") +
+  labs(title = "Sentiment score Jun 2017-March 2018",
+       subtitle = "unweighted") +
+  guides(col = guide_legend(nrow = 1)) +
+  theme(legend.position = "bottom")
+```
+
+```{r fig.height=10, fig.width=10}
+sentDF.values %>%
+  group_by(site, topic_name) %>%
+  summarise(sentiment = mean(sentiment, na.rm=T),
+            obs = n()) %>%
+  left_join(., tally_site, by = "site") %>%
+  mutate(w = obs/total_obs,
+         sentiment_w = sentiment * w) %>%
+  select(site, topic_name, sentiment_w) %>%
+  spread(key=topic_name, value=sentiment_w) -> radar
+
+radar %>%
+  ggRadar(aes(color=site), 
+          rescale = F,
+          alpha = 0, legend.position = "right") +
+  labs(title = "Sentiment score Jun 2017-March 2018",
+       subtitle = "weighted") +
   guides(col = guide_legend(nrow = 1)) +
@@
 
-<!-- ### 5. Compare with polls -->
+## 3. Compare with polls
 
-```{r eval=FALSE, include=FALSE}
+```{r}
 load("../output/polls.Rda")
@@
 
-<!-- Define Functions  -->
+Prepare Dataframes
 
-```{r eval=FALSE, include=FALSE}
-calculate_month = function(month, year) {
-  date <- ymd(paste(year, 1, 1, sep="-"))
-  month(date) = month
-  return(date)
-}
-
-normalize_data <- function(x) {
-  y <- (x - min(x, na.rm = T)) / (max(x, na.rm = T) - min(x, na.rm = T))
-  return(y)
-}
-```
-
-<!-- Prepare Dataframes -->
-
-```{r eval=FALSE, include=FALSE}
+```{r}
 polls <- table_long %>%
@@
          year = year(Datum),
-         yearmonth = calculate_month(month,year),
-         val_norm = normalize_data(value)) %>%
+         yearmonth = calculate_month(month,year)) %>%
   group_by(yearmonth,party) %>%
-  summarise(mean_val = mean(value, na.rm=T),
-            mean_val_norm = mean(val_norm)) %>%
+  summarise(mean_val = mean(value, na.rm=T)) %>%
   ungroup() %>%
   filter(mean_val != "NaN") %>%
-  select(party, yearmonth, mean_val_norm) %>%
-  spread(party, mean_val_norm)
+  select(party, yearmonth, mean_val) %>%
+  spread(party, mean_val)
 ```
 
-```{r eval=FALSE, include=FALSE}
-sentDF.values %>%
-  mutate(year = year(date),
-         month = month(date),
-         yearmonth = calculate_month(month,year),
-         sentiment_norm = normalize_data(sentiment)) %>%
+#### CDU
+
+```{r fig.height=12, fig.width=10}
+polls.red <- polls %>%
+  filter(yearmonth > as.Date("2017-05-01")) %>%
+  mutate(Union = normalize_data(Union))
+
+topics.red <- sentDF.values %>%
+  filter(grepl(paste("CDU","CSU","coalition", sep="|"), 
+               topic_name, ignore.case = T))
+
+### plot by time
+p <-topics.red %>%
+  group_by(yearmonth, topic_name, topic) %>%
+  summarise(sentiment = mean(sentiment, na.rm=T),
+            obs = n()) %>%
+  ungroup() %>%
+  left_join(., tally_month, by="yearmonth") %>%
+  mutate(w = obs / total_obs,
+         sentiment_w = sentiment * w,
+         sentiment_n = normalize_data(sentiment_w))
+
+### Plot 1  
+p1 <- ggplot() +
+  geom_col(data=p, aes(yearmonth, sentiment_n, 
+             group = topic_name,
+             fill = topic_name),
+           position = "dodge", 
+           alpha = 0.8) +
+  scale_fill_manual(values = col) +
+  guides(fill = guide_legend(ncol=3)) +
+
+  # Add poll line
+  geom_line(data = polls.red, 
+            aes(yearmonth, Union),
+            color = "black",
+            size = 1) +
+  labs(y="", x="", fill="",
+       title = "Sentiment & Poll Values",
+       subtitle = "Both scores are normalized") +
+  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
+  theme(legend.position = "bottom")
+
+### plot by time and site
+p <- topics.red %>%
   group_by(yearmonth, topic_name, topic, site) %>%
-  summarise(mean_sent = mean(sentiment, na.rm=T),
-            mean_sent_norm = mean(sentiment_norm, na.rm = T)) %>%
+  summarise(sentiment = mean(sentiment, na.rm=T),
+            obs = n()) %>%
   ungroup() %>%
-  left_join(polls, by="yearmonth") -> p
+  left_join(., tally_month_site, by=c("yearmonth","site")) %>%
+  mutate(w = obs / total_obs,
+         sentiment_w = sentiment * w,
+         sentiment_n = normalize_data(sentiment_w))
+
+### Plot 2
+p2 <- ggplot() +
+  geom_col(data = p,
+           aes(yearmonth, sentiment_n, 
+             group = topic_name,
+             fill = topic_name),
+           alpha = 0.8,
+           position = "dodge") +
+  scale_fill_manual(values = col) +
+  facet_wrap(~site, ncol = 2) +
+   # Add poll line
+  geom_line(data = polls.red, 
+            aes(yearmonth, Union),
+            color = "black",
+            size = 1) +
+  labs(y="", x="", fill="") +
+  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
+  theme(legend.position = "none",
+        axis.text.x = element_text(angle = 90))
+
+p1 + p2 + plot_layout(ncol = 1, heights = c(1,4))
 ```
 
-<!-- Plot  -->
+#### SPD
+```{r fig.height=12, fig.width=10}
+polls.red <- polls %>%
+  filter(yearmonth > as.Date("2017-05-01")) %>%
+  mutate(SPD = normalize_data(SPD))
 
-```{r eval=FALSE, include=FALSE}
-for (i in unique(p$site)) {
+topics.red <- sentDF.values %>%
+  filter(grepl(paste("SPD", sep="|"), topic_name, ignore.case = T))
 
-  p1 <- p %>%
-  filter(site == i) %>%
-  ggplot(aes(yearmonth, mean_sent_norm,
-               group = site)) +
-  geom_point(show.legend = F, color = col[1]) + 
-  geom_line(color = col[1]) +
+### plot by time
+p <-topics.red %>%
+  group_by(yearmonth, topic_name, topic) %>%
+  summarise(sentiment = mean(sentiment, na.rm=T),
+            obs = n()) %>%
+  ungroup() %>%
+  left_join(., tally_month, by="yearmonth") %>%
+  mutate(w = obs / total_obs,
+         sentiment_w = sentiment * w,
+         sentiment_n = normalize_data(sentiment_w))
 
-  scale_y_continuous(limits = c(0,1)) +
-  scale_x_date(breaks = date_breaks("1 month"), 
-               labels = date_format("%b", tz = "CET")) +
-  # AfD
-  geom_point(aes(yearmonth, AfD), size= 0.5,
-             color = "deepskyblue") +
-  geom_line(aes(yearmonth, AfD), color = "deepskyblue") +
+### Plot 1  
+p1 <- ggplot() +
+  geom_col(data=p, aes(yearmonth, sentiment_n, 
+             group = topic_name,
+             fill = topic_name),
+           position = "dodge", 
+           alpha = 0.8) +
+  scale_fill_manual(values = col) +
+  guides(fill = guide_legend(ncol=3)) +
 
-  # CDU/CSU
-  geom_point(aes(yearmonth, Union), size= 0.5,
-             color = "black") +
-  geom_line(aes(yearmonth, Union),
-             color = "black") +
+  # Add poll line
+  geom_line(data = polls.red, 
+            aes(yearmonth, SPD),
+            color = "red",
+            size = 1) +
+  labs(y="", x="", fill="",
+       title = "Sentiment & Poll Values",
+       subtitle = "Both scores are normalized") +
+  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
+  theme(legend.position = "bottom")
 
-  # SPD
-  geom_point(aes(yearmonth, SPD), size= 0.5,
-             color = "red") +
-  geom_line(aes(yearmonth, SPD),
-             color = "red") +
+### plot by time and site
+p <- topics.red %>%
+  group_by(yearmonth, topic_name, topic, site) %>%
+  summarise(sentiment = mean(sentiment, na.rm=T),
+            obs = n()) %>%
+  ungroup() %>%
+  left_join(., tally_month_site, by=c("yearmonth","site")) %>%
+  mutate(w = obs / total_obs,
+         sentiment_w = sentiment * w,
+         sentiment_n = normalize_data(sentiment_w))
 
-  # Grüne
-  geom_point(aes(yearmonth, Grüne), size= 0.5,
-             color = "limegreen") +
-  geom_line(aes(yearmonth, Grüne),
-             color = "limegreen") +
+### Plot 2
+p2 <- ggplot() +
+  geom_col(data = p,
+           aes(yearmonth, sentiment_n, 
+             group = topic_name,
+             fill = topic_name),
+           alpha = 0.8,
+           position = "dodge") +
+  scale_fill_manual(values = col) +
+  facet_wrap(~site, ncol = 2) +
+   # Add poll line
+  geom_line(data = polls.red, 
+            aes(yearmonth, SPD),
+            color = "red",
+            size = 1) +
+  labs(y="", x="", fill="") +
+  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
+  theme(legend.position = "none",
+        axis.text.x = element_text(angle = 90))
 
-  # DIE LINKE
-  geom_point(aes(yearmonth, Linke), size= 0.5,
-             color = "deeppink") +
-  geom_line(aes(yearmonth, Linke),
-             color = "deeppink") +
-
-  # 
-  labs(x="", y="", title=paste(i)) +
-    theme(axis.text = element_text(size = 6)) +
-  facet_grid(topic_name ~.)
-
-  ggsave(p1, file=paste0("../figs/polls_",i,".png"),
-         width = 4, height = 10)
-
-}
+p1 + p2 + plot_layout(ncol = 1, heights = c(1,4))
 ```
 
-<!-- <img src="../figs/polls_Bild.de.png", width = "49%"> -->
-<!-- <img src="../figs/polls_DIE WELT.png", width = "49%"> -->
-<!-- <img src="../figs/polls_FOCUS ONLINE.png", width = "49%"> -->
-<!-- <img src="../figs/polls_SPIEGEL ONLINE.png", width = "49%"> -->
-<!-- <img src="../figs/polls_stern.de.png", width = "49%"> -->
-<!-- <img src="../figs/polls_Tagesschau.de.png", width = "49%"> -->
-<!-- <img src="../figs/polls_ZEIT ONLINE.png", width = "49%"> -->
+#### FDP
+
+```{r fig.height=12, fig.width=10}
+polls.red <- polls %>%
+  filter(yearmonth > as.Date("2017-05-01")) %>%
+  mutate(FDP = normalize_data(FDP))
+
+topics.red <- sentDF.values %>%
+  filter(grepl(paste("Jamaica", sep="|"), 
+               topic_name, ignore.case = T))
+
+### plot by time
+p <-topics.red %>%
+  group_by(yearmonth, topic_name, topic) %>%
+  summarise(sentiment = mean(sentiment, na.rm=T),
+            obs = n()) %>%
+  ungroup() %>%
+  left_join(., tally_month, by="yearmonth") %>%
+  mutate(w = obs / total_obs,
+         sentiment_w = sentiment * w,
+         sentiment_n = normalize_data(sentiment_w))
+
+### Plot 1  
+p1 <- ggplot() +
+  geom_col(data=p, aes(yearmonth, sentiment_n, 
+             group = topic_name,
+             fill = topic_name),
+           position = "dodge", 
+           alpha = 0.8) +
+  scale_fill_manual(values = col) +
+  guides(fill = guide_legend(ncol=3)) +
+
+  # Add poll line (FDP)
+  geom_line(data = polls.red, 
+            aes(yearmonth, FDP),
+            color = col[4],
+            size = 1) +
+  labs(y="", x="", fill="",
+       title = "Sentiment & Poll Values",
+       subtitle = "Both scores are normalized") +
+  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
+  theme(legend.position = "bottom")
+
+### plot by time and site
+p <- topics.red %>%
+  group_by(yearmonth, topic_name, topic, site) %>%
+  summarise(sentiment = mean(sentiment, na.rm=T),
+            obs = n()) %>%
+  ungroup() %>%
+  left_join(., tally_month_site, by=c("yearmonth","site")) %>%
+  mutate(w = obs / total_obs,
+         sentiment_w = sentiment * w,
+         sentiment_n = normalize_data(sentiment_w))
+
+### Plot 2
+p2 <- ggplot() +
+  geom_col(data = p,
+           aes(yearmonth, sentiment_n, 
+             group = topic_name,
+             fill = topic_name),
+           alpha = 0.8,
+           position = "dodge") +
+  scale_fill_manual(values = col) +
+  facet_wrap(~site, ncol = 2) +
+    # Add poll line (FDP)
+  geom_line(data = polls.red, 
+            aes(yearmonth, FDP),
+            color = col[4],
+            size = 1) +
+  labs(y="", x="", fill="") +
+  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
+  theme(legend.position = "none",
+        axis.text.x = element_text(angle = 90))
+
+p1 + p2 + plot_layout(ncol = 1, heights = c(1,4))
+```
+
+#### B90 / Die Grüne
+
+```{r fig.height=12, fig.width=10}
+polls.red <- polls %>%
+  filter(yearmonth > as.Date("2017-05-01")) %>%
+  mutate(Grüne = normalize_data(Grüne))
+
+topics.red <- sentDF.values %>%
+  filter(grepl(paste("Jamaica","Grüne", sep="|"), 
+               topic_name, ignore.case = T))
+
+### plot by time
+p <-topics.red %>%
+  group_by(yearmonth, topic_name, topic) %>%
+  summarise(sentiment = mean(sentiment, na.rm=T),
+            obs = n()) %>%
+  ungroup() %>%
+  left_join(., tally_month, by="yearmonth") %>%
+  mutate(w = obs / total_obs,
+         sentiment_w = sentiment * w,
+         sentiment_n = normalize_data(sentiment_w))
+
+### Plot 1  
+p1 <- ggplot() +
+  geom_col(data=p, aes(yearmonth, sentiment_n, 
+             group = topic_name,
+             fill = topic_name),
+           position = "dodge", 
+           alpha = 0.8) +
+  scale_fill_manual(values = col) +
+  guides(fill = guide_legend(ncol=3)) +
+
+    # Add poll line (Grüne)
+  geom_line(data = polls.red, 
+            aes(yearmonth, Grüne),
+            color = "limegreen",
+            size = 1) +
+  labs(y="", x="", fill="",
+       title = "Sentiment & Poll Values",
+       subtitle = "Both scores are normalized") +
+  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
+  theme(legend.position = "bottom")
+
+### plot by time and site
+p <- topics.red %>%
+  group_by(yearmonth, topic_name, topic, site) %>%
+  summarise(sentiment = mean(sentiment, na.rm=T),
+            obs = n()) %>%
+  ungroup() %>%
+  left_join(., tally_month_site, by=c("yearmonth","site")) %>%
+  mutate(w = obs / total_obs,
+         sentiment_w = sentiment * w,
+         sentiment_n = normalize_data(sentiment_w))
+
+### Plot 2
+p2 <- ggplot() +
+  geom_col(data = p,
+           aes(yearmonth, sentiment_n, 
+             group = topic_name,
+             fill = topic_name),
+           alpha = 0.8,
+           position = "dodge") +
+  scale_fill_manual(values = col) +
+  facet_wrap(~site, ncol = 2) +
+
+    # Add poll line (Grüne)
+  geom_line(data = polls.red, 
+            aes(yearmonth, Grüne),
+            color = "limegreen",
+            size = 1) +
+  labs(y="", x="", fill="") +
+  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
+  theme(legend.position = "none",
+        axis.text.x = element_text(angle = 90))
+
+p1 + p2 + plot_layout(ncol = 1, heights = c(1,4))
+```
+
+#### AfD
+
+```{r fig.height=12, fig.width=10}
+polls.red <- polls %>%
+  filter(yearmonth > as.Date("2017-05-01")) %>%
+  mutate(AfD = normalize_data(AfD))
+
+topics.red <- sentDF.values %>%
+  filter(grepl(paste("AfD", sep="|"), 
+               topic_name, ignore.case = T))
+
+### plot by time
+p <-topics.red %>%
+  group_by(yearmonth, topic_name, topic) %>%
+  summarise(sentiment = mean(sentiment, na.rm=T),
+            obs = n()) %>%
+  ungroup() %>%
+  left_join(., tally_month, by="yearmonth") %>%
+  mutate(w = obs / total_obs,
+         sentiment_w = sentiment * w,
+         sentiment_n = normalize_data(sentiment_w))
+
+### Plot 1  
+p1 <- ggplot() +
+  geom_col(data=p, aes(yearmonth, sentiment_n, 
+             group = topic_name,
+             fill = topic_name),
+           position = "dodge", 
+           alpha = 0.8) +
+  scale_fill_manual(values = col) +
+  guides(fill = guide_legend(ncol=3)) +
+
+    # Add poll line (AfD)
+  geom_line(data = polls.red, 
+            aes(yearmonth, AfD),
+            color = "skyblue",
+            size = 1) +
+  labs(y="", x="", fill="",
+       title = "Sentiment & Poll Values",
+       subtitle = "Both scores are normalized") +
+  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
+  theme(legend.position = "bottom")
+
+### plot by time and site
+p <- topics.red %>%
+  group_by(yearmonth, topic_name, topic, site) %>%
+  summarise(sentiment = mean(sentiment, na.rm=T),
+            obs = n()) %>%
+  ungroup() %>%
+  left_join(., tally_month_site, by=c("yearmonth","site")) %>%
+  mutate(w = obs / total_obs,
+         sentiment_w = sentiment * w,
+         sentiment_n = normalize_data(sentiment_w))
+
+### Plot 2
+p2 <- ggplot() +
+  geom_col(data = p,
+           aes(yearmonth, sentiment_n, 
+             group = topic_name,
+             fill = topic_name),
+           alpha = 0.8,
+           position = "dodge") +
+  scale_fill_manual(values = col) +
+  facet_wrap(~site, ncol = 2) +
+
+    # Add poll line (AfD)
+  geom_line(data = polls.red, 
+            aes(yearmonth, AfD),
+            color = "skyblue",
+            size = 1) +
+  labs(y="", x="", fill="") +
+  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
+  theme(legend.position = "none",
+        axis.text.x = element_text(angle = 90))
+
+p1 + p2 + plot_layout(ncol = 1, heights = c(1,4))
+```

### 2018-03-13 paper/docs/func/functions.R

@@ -189,6 +189,22 @@ KLD <- function(x,y) {
 #####################
 
 normalize_data <- function(x) {
-  y <- (x - min(x)) / (max(x) - min(x))
+  y <- (x - min(x, na.rm = T)) / (max(x, na.rm = T) - min(x, na.rm = T))
   return(y)
+}
+
+###########
+## Dates ##
+###########
+
+calculate_month = function(month, year) {
+  date <- ymd(paste(year, 1, 1, sep="-"))
+  month(date) = month
+  return(date)
+}
+
+calculate_week = function(week, year) {
+  date <- ymd(paste(year, 1, 1, sep="-"))
+  week(date) = week
+  return(date)
 }

### 2018-03-13 paper/docs/04_Modelresults_50.Rmd
add correlation

@@
 ```{r eval=FALSE, fig.height=8, fig.width=4}
-topic <- 1
+topic <- 2
 
@@
                   paste(sagelabs$cov.betas[[7]]$problabels[topic,], collapse="\n"))),
-          text.cex = 0.8, width = 40,
-          main = paste(topics.df$topic_name[topics.df$topic==topic])
+          text.cex = 0.8, width = 40
           )
@@
 
-```{r}
+We use the data from the "Sonntagsumfrage" (Sunday survey) from [infratest dimap](https://www.infratest-dimap.de/umfragen-analysen/bundesweit/sonntagsfrage/).
+The institution regularly asks at least 1000 German citizens the question: "Which party would you choose if federal elections take place next Sunday?" The survey thus measures the current election tendencies and therefore reflects an intermediate state in the opinion-forming process of the electoral population.
+
+The comparison with the sentiment value of individual topics is intended to show whether there is a correlation between the current tendency to vote and the type of reporting.
+For this purpose, the monthly average of both time series is calculated and rescaled to an interval between 0 and 1.
+
+The analysis in this section is done in two steps: First, the standardised time series are compared graphically. In the second step, the cross-correlation between two time series is calculated.
+
+###### Normalization
+
+$$
+z_i = \frac{x_i-\text{min}(x)}{\text{max}(x)-\text{min}(x)}
+$$
+where $x = (x_1,...,x_n)$ and $z_i$ is the $i^{th}$ normalized data.
+
+```{r}
+# Import and prepare survey data
 load("../output/polls.Rda")
 
-htmlTable::htmlTable(table[1:10,], align = "l")
-```
-
-Prepare Dataframes
-
-```{r}
 polls <- table_long %>%
@@
 
-#### CDU
-
 ```{r fig.height=12, fig.width=10}
@@
   filter(yearmonth > as.Date("2017-05-01")) %>%
-  mutate(Union = normalize_data(Union))
-
-topics.red <- sentDF.values %>%
-  filter(grepl(paste("CDU","CSU","coalition", sep="|"), 
-               topic_name, ignore.case = T))
-
-### plot by time
-p <-topics.red %>%
+  transmute(Union = normalize_data(Union),
+         SPD = normalize_data(SPD),
+         Grüne = normalize_data(Grüne),
+         FDP = normalize_data(FDP),
+         AfD = normalize_data(AfD),
+         yearmonth = yearmonth)
+
+# topics.red <- sentDF.values %>%
+#   filter(grepl(paste("CDU","CSU","coalition", sep="|"), 
+#                topic_name, ignore.case = T))
+### by time
+group1 <- sentDF.values %>%
   group_by(yearmonth, topic_name, topic) %>%
@@
 
+### by time and site
+group2 <- sentDF.values %>%
+  group_by(yearmonth, topic_name, topic, site) %>%
+  summarise(sentiment = mean(sentiment, na.rm=T),
+            obs = n()) %>%
+  ungroup() %>%
+  left_join(., tally_month_site, by=c("yearmonth","site")) %>%
+  mutate(w = obs / total_obs,
+         sentiment_w = sentiment * w,
+         sentiment_n = normalize_data(sentiment_w))
+```
+
+```{r fig.height=5, fig.width=10}
+ggplot(group1, aes(yearmonth, 
+                   sentiment_n, 
+                   group = topic_name,
+                   color = topic_name)) +
+  geom_line(show.legend = F) +
+  facet_wrap(~topic_name, nrow = 3) +
+  labs(x="", y="", title="Sentiment Score")
+```
+
+```{r}
+polls.red %>%
+  gather(key = party, value = poll, Union:AfD) %>%
+  ggplot(aes(yearmonth, poll, color = party)) +
+  geom_line() +
+  labs(x="", y="", title = "Survey Value", color = "")
+```
+
+#### 3.1. Cross-Correlation
+```{r}
+group1 %>%
+  select(yearmonth, topic_name, sentiment_n) %>%
+  spread(topic_name, sentiment_n) %>%
+  select(- yearmonth) -> corr1
+
+polls.red %>% select(- yearmonth) -> corr2
+
+corr <- expand.grid(names(corr1), names(corr2))
+corr$correlation <- NA
+```
+
+```{r}
+x <- 1
+
+for (corr1Id in 1:ncol(corr2)) {
+  c1 = corr2[,corr1Id]
+  #print(names(corr2[,corr1Id]))
+  for(corr2Id in 1:ncol(corr1)) {
+    c2 = corr1[,corr2Id]
+    #print(names(corr1[,corr2Id]))
+    correlation = ccf(c1, c2, lag.max = 0,
+                      na.action = na.contiguous, plot=F)
+    corr[x,3] <- correlation$acf[1]
+
+    x<- x+1
+  }
+}
+```
+
+```{r}
+ggplot(corr, aes(Var2, Var1,
+                 fill = correlation,
+                 label = round(correlation,2))) +
+  geom_tile(color="white") +
+  geom_text(size = 3, color = col[5]) +
+  viridis::scale_fill_viridis() +
+  labs(x="", y="", title = "Cross Correlation of Polls vs. Sentiment Value")
+```
+
+#### 3.2. Graphical analysis
+
+##### 3.2.1. CDU
+```{r fig.height=10, fig.width=12}
 ### Plot 1  
+plot1 <- group1 %>%
+  filter(grepl(paste("CDU","CSU",sep="|"), topic_name))
+
 p1 <- ggplot() +
-  geom_col(data=p, aes(yearmonth, sentiment_n, 
+  geom_col(data=plot1, aes(yearmonth, sentiment_n, 
              group = topic_name,
@@
   scale_fill_manual(values = col) +
+    geom_line(data=plot1, aes(yearmonth, sentiment_n, 
+             group = topic_name,
+             color = topic_name),
+             show.legend = F) +
+  scale_color_manual(values = col) +
   guides(fill = guide_legend(ncol=3)) +
-
   # Add poll line
@@
 
-### plot by time and site
-p <- topics.red %>%
-  group_by(yearmonth, topic_name, topic, site) %>%
-  summarise(sentiment = mean(sentiment, na.rm=T),
-            obs = n()) %>%
-  ungroup() %>%
-  left_join(., tally_month_site, by=c("yearmonth","site")) %>%
-  mutate(w = obs / total_obs,
-         sentiment_w = sentiment * w,
-         sentiment_n = normalize_data(sentiment_w))
-
 ### Plot 2
+plot2 <- group2 %>%
+  filter(grepl(paste("CDU","CSU",sep="|"), topic_name))
+
 p2 <- ggplot() +
-  geom_col(data = p,
+  geom_col(data = plot2,
            aes(yearmonth, sentiment_n, 
@@
     scale_fill_manual(values = col) +
+    scale_color_manual(values = col) +
+  geom_line(data = plot2,
+            aes(yearmonth, sentiment_n,
+                group = topic_name,
+                color = topic_name),
+            show.legend = F) +
   facet_wrap(~site, ncol = 2) +
@@
 ```{r fig.height=12, fig.width=10}
-polls.red <- polls %>%
-  filter(yearmonth > as.Date("2017-05-01")) %>%
-  mutate(SPD = normalize_data(SPD))
-
-topics.red <- sentDF.values %>%
+plot1 <- group1 %>%
   filter(grepl(paste("SPD", sep="|"), topic_name, ignore.case = T))
-
-### plot by time
-p <-topics.red %>%
-  group_by(yearmonth, topic_name, topic) %>%
-  summarise(sentiment = mean(sentiment, na.rm=T),
-            obs = n()) %>%
-  ungroup() %>%
-  left_join(., tally_month, by="yearmonth") %>%
-  mutate(w = obs / total_obs,
-         sentiment_w = sentiment * w,
-         sentiment_n = normalize_data(sentiment_w))
 
@@
 p1 <- ggplot() +
-  geom_col(data=p, aes(yearmonth, sentiment_n, 
+  geom_col(data=plot1, aes(yearmonth, sentiment_n, 
              group = topic_name,
@@
   guides(fill = guide_legend(ncol=3)) +
-
+   geom_line(data=plot1, aes(yearmonth, sentiment_n, 
+             group = topic_name,
+             color = topic_name),
+             show.legend = F) +
+  scale_color_manual(values = col) +
   # Add poll line
@@
 ### plot by time and site
-p <- topics.red %>%
-  group_by(yearmonth, topic_name, topic, site) %>%
-  summarise(sentiment = mean(sentiment, na.rm=T),
-            obs = n()) %>%
-  ungroup() %>%
-  left_join(., tally_month_site, by=c("yearmonth","site")) %>%
-  mutate(w = obs / total_obs,
-         sentiment_w = sentiment * w,
-         sentiment_n = normalize_data(sentiment_w))
+plot2 <- group2 %>%
+  filter(grepl(paste("SPD", sep="|"), topic_name, ignore.case = T))
 
@@
 p2 <- ggplot() +
-  geom_col(data = p,
+  geom_col(data = plot2,
            aes(yearmonth, sentiment_n, 
@@
   facet_wrap(~site, ncol = 2) +
+     geom_line(data=plot2, aes(yearmonth, sentiment_n, 
+             group = topic_name,
+             color = topic_name),
+             show.legend = F) +
+  scale_color_manual(values = col) +
    # Add poll line
@@
 ```
-
-#### FDP
-
-```{r fig.height=12, fig.width=10}
-polls.red <- polls %>%
-  filter(yearmonth > as.Date("2017-05-01")) %>%
-  mutate(FDP = normalize_data(FDP))
-
-topics.red <- sentDF.values %>%
-  filter(grepl(paste("Jamaica", sep="|"), 
-               topic_name, ignore.case = T))
-
-### plot by time
-p <-topics.red %>%
-  group_by(yearmonth, topic_name, topic) %>%
-  summarise(sentiment = mean(sentiment, na.rm=T),
-            obs = n()) %>%
-  ungroup() %>%
-  left_join(., tally_month, by="yearmonth") %>%
-  mutate(w = obs / total_obs,
-         sentiment_w = sentiment * w,
-         sentiment_n = normalize_data(sentiment_w))
-
-### Plot 1  
-p1 <- ggplot() +
-  geom_col(data=p, aes(yearmonth, sentiment_n, 
-             group = topic_name,
-             fill = topic_name),
-           position = "dodge", 
-           alpha = 0.8) +
-  scale_fill_manual(values = col) +
-  guides(fill = guide_legend(ncol=3)) +
-
-  # Add poll line (FDP)
-  geom_line(data = polls.red, 
-            aes(yearmonth, FDP),
-            color = col[4],
-            size = 1) +
-  labs(y="", x="", fill="",
-       title = "Sentiment & Poll Values",
-       subtitle = "Both scores are normalized") +
-  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
-  theme(legend.position = "bottom")
-
-### plot by time and site
-p <- topics.red %>%
-  group_by(yearmonth, topic_name, topic, site) %>%
-  summarise(sentiment = mean(sentiment, na.rm=T),
-            obs = n()) %>%
-  ungroup() %>%
-  left_join(., tally_month_site, by=c("yearmonth","site")) %>%
-  mutate(w = obs / total_obs,
-         sentiment_w = sentiment * w,
-         sentiment_n = normalize_data(sentiment_w))
-
-### Plot 2
-p2 <- ggplot() +
-  geom_col(data = p,
-           aes(yearmonth, sentiment_n, 
-             group = topic_name,
-             fill = topic_name),
-           alpha = 0.8,
-           position = "dodge") +
-  scale_fill_manual(values = col) +
-  facet_wrap(~site, ncol = 2) +
-    # Add poll line (FDP)
-  geom_line(data = polls.red, 
-            aes(yearmonth, FDP),
-            color = col[4],
-            size = 1) +
-  labs(y="", x="", fill="") +
-  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
-  theme(legend.position = "none",
-        axis.text.x = element_text(angle = 90))
-
-p1 + p2 + plot_layout(ncol = 1, heights = c(1,4))
-```
-
-#### B90 / Die Grüne
-
-```{r fig.height=12, fig.width=10}
-polls.red <- polls %>%
-  filter(yearmonth > as.Date("2017-05-01")) %>%
-  mutate(Grüne = normalize_data(Grüne))
-
-topics.red <- sentDF.values %>%
-  filter(grepl(paste("Jamaica","Grüne", sep="|"), 
-               topic_name, ignore.case = T))
-
-### plot by time
-p <-topics.red %>%
-  group_by(yearmonth, topic_name, topic) %>%
-  summarise(sentiment = mean(sentiment, na.rm=T),
-            obs = n()) %>%
-  ungroup() %>%
-  left_join(., tally_month, by="yearmonth") %>%
-  mutate(w = obs / total_obs,
-         sentiment_w = sentiment * w,
-         sentiment_n = normalize_data(sentiment_w))
-
-### Plot 1  
-p1 <- ggplot() +
-  geom_col(data=p, aes(yearmonth, sentiment_n, 
-             group = topic_name,
-             fill = topic_name),
-           position = "dodge", 
-           alpha = 0.8) +
-  scale_fill_manual(values = col) +
-  guides(fill = guide_legend(ncol=3)) +
-
-    # Add poll line (Grüne)
-  geom_line(data = polls.red, 
-            aes(yearmonth, Grüne),
-            color = "limegreen",
-            size = 1) +
-  labs(y="", x="", fill="",
-       title = "Sentiment & Poll Values",
-       subtitle = "Both scores are normalized") +
-  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
-  theme(legend.position = "bottom")
-
-### plot by time and site
-p <- topics.red %>%
-  group_by(yearmonth, topic_name, topic, site) %>%
-  summarise(sentiment = mean(sentiment, na.rm=T),
-            obs = n()) %>%
-  ungroup() %>%
-  left_join(., tally_month_site, by=c("yearmonth","site")) %>%
-  mutate(w = obs / total_obs,
-         sentiment_w = sentiment * w,
-         sentiment_n = normalize_data(sentiment_w))
-
-### Plot 2
-p2 <- ggplot() +
-  geom_col(data = p,
-           aes(yearmonth, sentiment_n, 
-             group = topic_name,
-             fill = topic_name),
-           alpha = 0.8,
-           position = "dodge") +
-  scale_fill_manual(values = col) +
-  facet_wrap(~site, ncol = 2) +
-
-    # Add poll line (Grüne)
-  geom_line(data = polls.red, 
-            aes(yearmonth, Grüne),
-            color = "limegreen",
-            size = 1) +
-  labs(y="", x="", fill="") +
-  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
-  theme(legend.position = "none",
-        axis.text.x = element_text(angle = 90))
-
-p1 + p2 + plot_layout(ncol = 1, heights = c(1,4))
-```
-
-#### AfD
-
-```{r fig.height=12, fig.width=10}
-polls.red <- polls %>%
-  filter(yearmonth > as.Date("2017-05-01")) %>%
-  mutate(AfD = normalize_data(AfD))
-
-topics.red <- sentDF.values %>%
-  filter(grepl(paste("AfD", sep="|"), 
-               topic_name, ignore.case = T))
-
-### plot by time
-p <-topics.red %>%
-  group_by(yearmonth, topic_name, topic) %>%
-  summarise(sentiment = mean(sentiment, na.rm=T),
-            obs = n()) %>%
-  ungroup() %>%
-  left_join(., tally_month, by="yearmonth") %>%
-  mutate(w = obs / total_obs,
-         sentiment_w = sentiment * w,
-         sentiment_n = normalize_data(sentiment_w))
-
-### Plot 1  
-p1 <- ggplot() +
-  geom_col(data=p, aes(yearmonth, sentiment_n, 
-             group = topic_name,
-             fill = topic_name),
-           position = "dodge", 
-           alpha = 0.8) +
-  scale_fill_manual(values = col) +
-  guides(fill = guide_legend(ncol=3)) +
-
-    # Add poll line (AfD)
-  geom_line(data = polls.red, 
-            aes(yearmonth, AfD),
-            color = "skyblue",
-            size = 1) +
-  labs(y="", x="", fill="",
-       title = "Sentiment & Poll Values",
-       subtitle = "Both scores are normalized") +
-  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
-  theme(legend.position = "bottom")
-
-### plot by time and site
-p <- topics.red %>%
-  group_by(yearmonth, topic_name, topic, site) %>%
-  summarise(sentiment = mean(sentiment, na.rm=T),
-            obs = n()) %>%
-  ungroup() %>%
-  left_join(., tally_month_site, by=c("yearmonth","site")) %>%
-  mutate(w = obs / total_obs,
-         sentiment_w = sentiment * w,
-         sentiment_n = normalize_data(sentiment_w))
-
-### Plot 2
-p2 <- ggplot() +
-  geom_col(data = p,
-           aes(yearmonth, sentiment_n, 
-             group = topic_name,
-             fill = topic_name),
-           alpha = 0.8,
-           position = "dodge") +
-  scale_fill_manual(values = col) +
-  facet_wrap(~site, ncol = 2) +
-
-    # Add poll line (AfD)
-  geom_line(data = polls.red, 
-            aes(yearmonth, AfD),
-            color = "skyblue",
-            size = 1) +
-  labs(y="", x="", fill="") +
-  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
-  theme(legend.position = "none",
-        axis.text.x = element_text(angle = 90))
-
-p1 + p2 + plot_layout(ncol = 1, heights = c(1,4))
-```

### 2018-03-13 paper/docs/04_Modelresults_50.Rmd
change topic names

@@
 ```{r}
-topics <- matrix(c(1, "SPD", 2, "B90/ Die Grüne & DIE LINKE", 3, "Mix: Akhanli, Guttenberg, Bayern", 4, "Great Coalition debates", 5, "Diesel scandal", 6, "H.Kohl", 7, "Federal Election results", 8, "Europa, Macron, Schäuble", 9, "Mix: political trends, twitter", 10, "Merkel vs.
-Schulz", 11, "politics & democracy in GER", 12, "Deportation of criminal Refugees", 13, "A.Merkel", 14, "Text processing fail", 15, "Israel, antisemitism, D.Trump", 16, "Mix: political talkshows, Refugees", 17, "Votes within SPD", 18, "Election in Niedersachsen", 19, "R.Lammert", 20, "AfD, Right-wing extremist tendencies", 21, "German armed forces, v.d.Leyen", 22, "SPD, stuffing debates", 23, "CSU, Söder vs.
-Seehover, refugee cap", 24, "Bundespräsident F.-W.Steinmeier", 25, "Election polls", 26, "Jamaica failure", 27, "Jamaica Coalition debates", 28, "G20 in Hamburg", 29, "Federal Constitutional Court, Ministry of the Interior", 30, "F.Petri, AfD", 31, "D.Trump, Russia", 32, "Gauland, Weidel, AfD", 33, "German armed forces, Mali", 34, "Mix: Children, Education, Women", 35, "Left- rightwing Terror, police reports", 36, "Mix: people, Germany, democracy", 37, "AfD in parliament", 38, "EU policies", 39, "Mix: Terror attacks", 40, "Mix: Metoo, SPD", 41, "Terror attack Berlin (Amri)", 42, "Refugee family reunion", 43, "Mix: studies", 44, "Federal Constitutional Court (NSU, Franco, Terror)", 45, "Mix: minister of the interior, environment", 46, "CDU, J.Spahn, Tauber (Disease)", 47, "Church", 48, "public (budget) statistics, Education/ Healthcare/ Digital policies", 49, "Turkey", 50, "Höcke, Holocaust"), ncol=2, byrow=T)
+topics <- matrix(c(1, "SPD, mainly M.Schulz", 2, "B90/ Die Grüne & DIE LINKE", 3, "Mix: Akhanli, Guttenberg, Bayern", 4, "Great Coalition debates", 5, "Diesel scandal", 6, "H.Kohl", 7, "Federal Election results", 8, "Europa, Macron, Schäuble", 9, "Mix: political trends, twitter", 10, "M.Schulz, mainly vs.
+A.Merkel", 11, "politics & democracy in GER", 12, "Deportation of criminal Refugees", 13, "A.Merkel, mainly election campaign", 14, "Text processing fail", 15, "Israel, antisemitism, D.Trump", 16, "Mix: political talkshows, Refugees", 17, "Debates within SPD", 18, "Election in Niedersachsen", 19, "N.Lammert", 20, "AfD, mainly right-wing radicalism", 21, "German armed forces, v.d.Leyen", 22, "SPD, mainly stuffing debates", 23, "CSU, mainly Söder & Seehover", 24, "Bundespräsident F.-W.Steinmeier", 25, "Election polls", 26, "Jamaica fail, Reelections or GroKo?", 27, "Jamaica Coalition debates", 28, "G20 in Hamburg", 29, "Federal Constitutional Court, Ministry of the Interior", 30, "AfD, mainly F.Petry & Meuthen", 31, "D.Trump, Russia", 32, "AfD, mainly Gauland & Weidel", 33, "German armed forces, Mali", 34, "Mix: Children, Education, Women", 35, "Left- rightwing Terror, police reports", 36, "Mix: people, Germany, democracy", 37, "AfD & DIE LINKE in parliament", 38, "EU policies", 39, "Mix: Terror attacks", 40, "Mix: Metoo, SPD", 41, "Terror attack Berlin (Amri)", 42, "Refugee family reunion", 43, "Mix: studies", 44, "Federal Constitutional Court (NSU, Franco, Terror)", 45, "Mix: minister of the interior, environment", 46, "CDU", 47, "Church", 48, "public (budget) statistics, Education/ Healthcare/ Digital policies", 49, "Turkey", 50, "Höcke, Holocaust"), ncol=2, byrow=T)
 
@@
 ```{r eval=FALSE, include=FALSE}
-# Inspect the unclear topics
-btw.2 %>% filter(topic==13) %>% select(title, gamma, url) %>%
+# Inspect some topics
+btw.2 %>% filter(topic==37) %>% 
+  select(title, gamma, site) %>%
   arrange(desc(gamma)) %>%
-  top_n(10) %>%
   htmlTable::htmlTable(align="l")
@@
 df <- btw.2 %>%
-  filter(gamma >= 0.75) %>%
+  filter(gamma >= 0.3) %>%
   distinct(title, .keep_all = T) %>%
@@
 btw.2 %>% 
+  mutate(yearweek = calculate_week(week(date), year(date))) %>%
+  group_by(yearweek) %>%
+  summarise(total_obs = n()) -> tally_week
+
+btw.2 %>%
   group_by(site) %>%
@@
   summarise(total_obs = n()) -> tally_month_site
+
+btw.2 %>% 
+  mutate(yearweek = calculate_week(week(date), year(date))) %>%
+  group_by(yearweek, site) %>%
+  summarise(total_obs = n()) -> tally_week_site
 ```
@@
 polls <- table_long %>%
-  mutate(month=month(Datum),
-         year = year(Datum),
-         yearmonth = calculate_month(month,year)) %>%
+  mutate(yearmonth = calculate_month(month(Datum),year(Datum)),
+         yearweek = calculate_week(week(Datum), year(Datum)))
+
+## Monthly
+polls_monthly <- polls %>%
   group_by(yearmonth,party) %>%
@@
   select(party, yearmonth, mean_val) %>%
-  spread(party, mean_val)
-```
-
-```{r fig.height=12, fig.width=10}
-polls.red <- polls %>%
+  spread(party, mean_val) %>%
   filter(yearmonth > as.Date("2017-05-01")) %>%
@@
 
-# topics.red <- sentDF.values %>%
-#   filter(grepl(paste("CDU","CSU","coalition", sep="|"), 
-#                topic_name, ignore.case = T))
+polls_monthly %>%
+  gather(key = party, value = poll, Union:AfD) %>%
+  ggplot(aes(yearmonth, poll, color = party)) +
+  geom_line() +
+  scale_color_manual(values = c("skyblue", "gold", "limegreen", "red", "black")) +
+  labs(x="", y="", title = "Survey Value", 
+       subtitle = "weekly", color = "") +
+  geom_vline(xintercept = as.Date("2017-09-24"), 
+             linetype = 2, color = col[3]) +
+  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET"))
+```
+
+```{r fig.height=12, fig.width=10}
 ### by time
@@
 
-```{r fig.height=5, fig.width=10}
-ggplot(group1, aes(yearmonth, 
-                   sentiment_n, 
-                   group = topic_name,
-                   color = topic_name)) +
-  geom_line(show.legend = F) +
-  facet_wrap(~topic_name, nrow = 3) +
-  labs(x="", y="", title="Sentiment Score")
-```
-
-```{r}
-polls.red %>%
-  gather(key = party, value = poll, Union:AfD) %>%
-  ggplot(aes(yearmonth, poll, color = party)) +
-  geom_line() +
-  labs(x="", y="", title = "Survey Value", color = "")
-```
-
 #### 3.1. Cross-Correlation
@@
   select(yearmonth, topic_name, sentiment_n) %>%
-  spread(topic_name, sentiment_n) %>%
-  select(- yearmonth) -> corr1
-
-polls.red %>% select(- yearmonth) -> corr2
+  spread(topic_name, sentiment_n)  -> corr1
+
+polls_monthly %>% select(- yearmonth) -> corr2
 
@@
   # Add poll line
-  geom_line(data = polls.red, 
+  geom_line(data = polls_monthly, 
             aes(yearmonth, Union),
@@
    # Add poll line
-  geom_line(data = polls.red, 
+  geom_line(data = polls_monthly, 
             aes(yearmonth, Union),
@@
   # Add poll line
-  geom_line(data = polls.red, 
+  geom_line(data = polls_monthly, 
             aes(yearmonth, SPD),
@@
    # Add poll line
-  geom_line(data = polls.red, 
+  geom_line(data = polls_monthly, 
             aes(yearmonth, SPD),

### 2018-03-14 paper/docs/04_Modelresults_50.Rmd
some cleaning

@@
 ```{r}
-topics <- matrix(c(1, "SPD, mainly M.Schulz", 2, "B90/ Die Grüne & DIE LINKE", 3, "Mix: Akhanli, Guttenberg, Bayern", 4, "Great Coalition debates", 5, "Diesel scandal", 6, "H.Kohl", 7, "Federal Election results", 8, "Europa, Macron, Schäuble", 9, "Mix: political trends, twitter", 10, "M.Schulz, mainly vs.
+topics <- matrix(c(1, "SPD, mainly M.Schulz", 2, "B90/ Die Grünen, mainly personell debates", 3, "Mix: Akhanli, Guttenberg, Bayern", 4, "Great Coalition debates", 5, "Diesel scandal", 6, "H.Kohl", 7, "Federal Election results", 8, "Europa, Macron, Schäuble", 9, "Mix: political trends, twitter", 10, "M.Schulz, mainly vs.
 A.Merkel", 11, "politics & democracy in GER", 12, "Deportation of criminal Refugees", 13, "A.Merkel, mainly election campaign", 14, "Text processing fail", 15, "Israel, antisemitism, D.Trump", 16, "Mix: political talkshows, Refugees", 17, "Debates within SPD", 18, "Election in Niedersachsen", 19, "N.Lammert", 20, "AfD, mainly right-wing radicalism", 21, "German armed forces, v.d.Leyen", 22, "SPD, mainly stuffing debates", 23, "CSU, mainly Söder & Seehover", 24, "Bundespräsident F.-W.Steinmeier", 25, "Election polls", 26, "Jamaica fail, Reelections or GroKo?", 27, "Jamaica Coalition debates", 28, "G20 in Hamburg", 29, "Federal Constitutional Court, Ministry of the Interior", 30, "AfD, mainly F.Petry & Meuthen", 31, "D.Trump, Russia", 32, "AfD, mainly Gauland & Weidel", 33, "German armed forces, Mali", 34, "Mix: Children, Education, Women", 35, "Left- rightwing Terror, police reports", 36, "Mix: people, Germany, democracy", 37, "AfD & DIE LINKE in parliament", 38, "EU policies", 39, "Mix: Terror attacks", 40, "Mix: Metoo, SPD", 41, "Terror attack Berlin (Amri)", 42, "Refugee family reunion", 43, "Mix: studies", 44, "Federal Constitutional Court (NSU, Franco, Terror)", 45, "Mix: minister of the interior, environment", 46, "CDU", 47, "Church", 48, "public (budget) statistics, Education/ Healthcare/ Digital policies", 49, "Turkey", 50, "Höcke, Holocaust"), ncol=2, byrow=T)
@@
 # Inspect some topics
-btw.2 %>% filter(topic==37) %>% 
+btw.2 %>% filter(topic==2) %>% 
   select(title, gamma, site) %>%
@@
 
-```{r fig.height=8, fig.width=8}
-p1 <- ggplot(frequency, aes(x=reorder(topic_name, frequency), y=frequency)) + 
-    geom_col(fill=col[1], alpha=0.8) +
+```{r fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
+p <- ggplot(frequency, aes(x=reorder(topic_name, frequency), y=frequency)) + 
+    geom_col(fill=col[2], alpha=0.8) +
     coord_flip() +
@@
     theme(axis.text.x = element_text(size=8),
-          axis.text.y = element_text(size=11),
+          axis.text.y = element_text(size=9),
           axis.title = element_text(size=10))
 
-p1
-```
-
-```{r fig.height=8, fig.width=12}
-p2 <- freq %>%
+ggsave(filename = "../figs/topic_proportion.png")
+```
+
+![Topic Proportion](../figs/topic_proportion.png)
+
+```{r fig.height=8, fig.width=12, message=FALSE, warning=FALSE}
+p <- freq %>%
   mutate(topic =  as.numeric(gsub(":.*$","",topic))) %>% 
@@
 
-p2 
-```
+ggsave(filename = "../figs/topic_proportion2.png")
+```
+
+![Topic Proportion](../figs/topic_proportion2.png)
 
@@
   ggplot(aes(x = reorder(topic_name,topic, decreasing=F), y = Estimate, fill=factor(signifcant))) +
-  geom_col() +
+  geom_col(alpha = 0.8) +
   scale_fill_manual(values = col[c(2,1)]) +
@@
 
-```{r}
+```{r eval=FALSE, include=FALSE}
 sentDF %>% filter(document == unique(sentDF$document)[2]) %>%
@@
 $$
-\text{Weighted}_d = \frac{|\text{positive polarity score}_d| - |\text{negative polarity score}_d|}{\text{Total Words}_d}
+\text{SentScore}_d = \frac{|\text{positive polarity score}_d| - |\text{negative polarity score}_d|}{\text{Total Words}_d}
 $$
@@
 btw.2 %>%
-  mutate(yearweek = calculate_week(week(date), year(date))) %>%
-  group_by(yearweek) %>%
-  summarise(total_obs = n()) -> tally_week
-
-btw.2 %>%
   group_by(site) %>%
@@
 
-btw.2 %>% 
-  mutate(yearweek = calculate_week(week(date), year(date))) %>%
-  group_by(yearweek, site) %>%
-  summarise(total_obs = n()) -> tally_week_site
 ```
@@
 $$
-\text{w} = \frac{\text{# of obs per month & topic}}{\text{# of obs per month}}
+\text{w} = \frac{\text{# of documents per month & topic}}{\text{# of documents per month}}
 $$
@@
 Some conclusions can be drawn from this illustration.
-First of all, it is clear that topics concerning the AfD (20, 30, 32, 37) are discussed in a negative way over the entire period, with an exepction for topic 30, dealing with Frauk Petry and the AfD.
-The topic that is discussed most negatively is that of the right-wing extremist tendencies within the AfD.
-Another striking result is that the sentiment score of topics topics that deal with the SPD alone (1, 22) is diminishing in the course of time.
-The topic, which contains the CDU in isolation (46), is rather zigzagging, with a high peak in November 2017 and a low peak in January 2018, but there is only one observation this month, which is an article about Peter Tauber's illness.
-
-Concerning the issues that discuss possible coalitions, it is evident that there was a month in which the Jamaican coalition was positively discussed (topic 27): October 2017, when coalition talks were in full swing.
-With the failure of the negotiations, the sentiment value of the articles also decreases, while the number of articles dealing with this topic increases sharply in the short term (to 210 articles) and decreases significantly in the following months.
-It is striking that precisely at this time (December 2017), both the observations, as well as the sentiment value of the articles that report on the grand coalition increase (topic 4).
+First of all, it can be seen that, on average, all topics are discussed almost exclusively negatively.
+An exception is topic 27 concerning the Jaimiaca coalition negotiations, which shows a positive sentiment value for a short period of time (October 2017).
+In the following month (November 2017), after it became clear that there would be no coalition between the CDU/CSU, FDP and Die Grünen, the value of this topic as well as that of topic 26 drops rapidly.
+
+Concerning the issues that discuss the great coaltion between CDU/CSU and SPD, it is evident that the overall tone is in which this topic is discussed is generally decreasing from November 2017 to January 2018, but in the following February, the sentiment value of this topic rises.
+However, the sentiment score of topics that deal with the SPD alone (1, 17, 22) is diminishing in the course of time, with topic 17 recording the largest decline.
+The topic, which contains the CDU in isolation (46), is rather zigzagging, with a low peak in October 2017.
 
 ##### By Month & Topic
-```{r fig.height=12, fig.width=10}
+```{r eval=FALSE, include=FALSE}
 p <- sentDF.values %>%
@@
              color = "black") +
-  labs(x="", y="",
+  labs(x="", y="Sentiment Score (weighted)",
         title = "",
-       subtitle = "weighted") +
+       subtitle = "") +
+  scale_x_date(breaks = date_breaks("1 month"), 
+               labels = date_format("%B", tz ="CET")) +
   theme(axis.text.y = element_text(size=8),
-        axis.text.x = element_text(size = 10))
-
-p1 + p2 + plot_layout(ncol = 1)
-```
+        axis.text.x = element_text(size = 8, angle = 90))
+
+ggsave(filename = "../figs/sentscore_monthly.png", plot = p2, width = 12)
+```
+
+![Monthly Sentiment Score](../figs/sentscore_monthly.png)
 
@@
 
-```{r fig.height=12, fig.width=10}
+```{r eval=FALSE, fig.height=12, fig.width=10, include=FALSE}
 p <- sentDF.values %>%
@@
   facet_wrap(~site, ncol = 7) +
-  labs(x="", y="",
+  labs(x="", y="Sentiment Score (weighted)",
        title = "",
-       subtitle = "weighted") +
+       subtitle = "") +
   theme(axis.text.y = element_text(size = 10),
-        axis.text.x = element_text(size=6))
-
-p1 + p2 + plot_layout(ncol = 1)
-```
+        axis.text.x = element_text(size=6, angle = 90))
+
+ggsave(filename = "../figs/sentscore_site.png", plot = p2, width = 12)
+```
+
+![Sentiment Score by Newssite](../figs/sentscore_site.png)
 
@@
 
-```{r fig.height=10, fig.width=10}
+```{r eval=FALSE, fig.height=10, fig.width=10, include=FALSE}
 sentDF.values %>%
@@
 
-radar %>%
+p <- radar %>%
   ggRadar(aes(color=site), 
@@
           alpha = 0, legend.position = "right") +
-  labs(title = "Sentiment score Jun 2017-March 2018",
+  labs(title = "Sentiment scores Jun 2017-March 2018",
        subtitle = "weighted") +
@@
   theme(legend.position = "bottom")
-```
+
+ggsave(filename = "../figs/sentscore_radar.png", plot = p, width = 12)
+```
+
+![Radarplot Sentiment Score](../figs/sentscore_radar.png)
 

### 2018-03-14 paper/writing/doc_backup.tex
some cleaning

@@
 In order to examine this bias, I analyze how the topics are discussed differently in public and private news.
+
+As stated above, this paper examines whether imperfections in the market of online news exist, by comparing the topic prevalence between public and private online news with the supply of private news providers.
+In the event that there is no market failure in terms of information provision, the existence of public media could still be justified by the fact that socially relevant contents of private providers are systematically distorted and the existence of public offerings ensures the diversity of information and opinions transmitted.
+In order to examine this bias, the divergence of word-topic probabilities is calculated to analyze how the topics are discussed differently.
 
@@
 % ----------------------
+% Model Results
+% ----------------------
+\section{Empirical Evaluation}\label{ch_empirical}
+
+This section summarizes the results of the STM.
+Subsequently different measures to analyze the content differences between public and private ownership are applied according to the following approaches: (1) To address the question whether market imperfections exist in that sense, that some topics are not covered by private but by public news provider, I use the document-topic probability $\theta$, to estimate the conditional expectation of topic prevalence for given document characteristics (See section \ref{subsectiona_topicprevalence}).
+(2) Next, I find all edges between topics where they exhibit a positive correlation of $\theta$ above 0.1 to examine how topics are correlated differently for different covariate levels, indicating how topics are connected and framed differently between private and public media (see section \ref{subsection_topiccorrelation}).
+Approaches (1) and (2) have been used in \citep{roberts_model_2016}.
+However, we extend the analysis by (3) calculating the similarity of the word-topic distribution $\beta$ between the news provider using various distance measures, to identify which topics are discussed similar or differently (see section \ref{subsection_similarity}).
+
+\subsection{Topic correlations}\label{subsection_topiccorrelation}
+
+Next, the topic correlation is calculated, indicating how topics are connected and framed in public and private media.
+In Figure \ref{fig_topic_correlations}, indicates all edges between topics where they exhibit a positive correlation above 0.1 \citep{roberts_model_2016}.
+
+\begin{figure}[H]
+	\caption{Topic Correlation}
+		\begin{center}
+		\begin{subfigure}{.7\textwidth}
+			\includegraphics[width=\textwidth]{../figs/corrplot1.png}	
+			\subcaption{Private news provider}
+		\end{subfigure}
+		\begin{subfigure}{.7\textwidth}
+			\includegraphics[width=\textwidth]{../figs/corrplot2}
+			\caption{Public news provider}	
+		\end{subfigure}
+		\end{center}
+	\label{fig_topic_correlations}
+\end{figure}
+
+\textcolor{red}{AUSWERTUNG}
+
+\subsection{Differences in word-topic distributions}\label{subsection_similarity}
+
+Previous topic modeling research try to measure the similarity between topics, comparing the word-topic-distribution between the topics (most of the research uses LDA without metadata, so the word-topic-distribution is the same within the whole corpus).
+cosine similarity \citep{he_detecting_2009}, \citep{ramage_labeled_2009}, Kullback-Leibler (KL) \citep{newman_distributed_2009}, \citep{wang_mining_2009} and the average Log Odds Ratio \citep{chaney_visualizing_2012} are frequently used metrics to compare word probability distributions.
+\citet{kim_topic_2011} compare six popular similarity metrics in terms of log likelihood of data, concluding that Jensen-Shannon Divergence (the symmetric variation of KL divergence) is best in terms of performance and generality.
+
+Since a topic is a multinomial distribution over the vocabulary, where $\beta_{kvi}$ indicates the probability of observing word $v$ in topic $k$ for covariate level $i$, we can analyze how similar a topic $k$ is for different levels of covariates.
+More precisely, we can calculate the similarity between $\beta_{kvi}$ and $\beta_{kvj}$.
+I use each row of that matrix (corresponding to each topic) to calculate the similarity of the word-topic distribution between the public and private media using the square root of the Jensen-Shannon (JS) Divergence.
+I will compare this metric with a set of other similarity measures recently used in the literature to measure the difference between word-topic distributions: The Kullback-Leibler (KL) divergence (\citet{newman_distributed_2009}, \citet{wang_mining_2009}), the cosine similarity (\citet{he_detecting_2009}, \citet{ramage_labeled_2009}) and the difference of the $L1$ norm of the vectors \citep{roberts_navigating_2016}.
+Before the results are presented, I will briefly explain these measures before I proceed to the results.
+
+Essentially, the KL divergence is the expectation of the log difference between probabilities $a$ and $b$. It can be defined as:
+
+\begin{align*}
+	D_{KL}(a,b)=\sum_{i=1}^T a_i \text{ln} \frac{a_i}{b_i},
+\end{align*}
+
+where $D_{kl} \to 0$ indicates stronger similarities.
+However, since the KL divergence is not symmetric, it cannot be used to measure the distance between two distributions, but as a divergence measure.
+
+The Jensen-Shannon Divergence is a positive definite measure, satisfying the following conditions: $D_{js}(a,b) \geq 0$, $D_{js}(a,b)=0$ iff $(a=b)$.
+It is also symmetric: $D_{js}(a,b)=D_{js}(b,a)$.
+The Jensen-Shannon distance $D_{js}(a,b)$ between the two distributions is defined as:
+
+\begin{align*}
+	D_{js}(a,b)=\frac{1}{2}D_{KL}(a,\frac{a+b}{2})+\frac{1}{2}D_{KL}(b,\frac{a+b}{2})
+\end{align*}
+
+where $D_{KL}$ is the Kullback-Leibler divergence.
+Since $D_{js}$ does not satisfy the triangular inequality condition $D_{js}(a,c)\leq D_{js}(a,c)+D_{js}(b,c)$, the JSD is not considered to be a real distance metric.
+However, we can use the square root of JSD as a real distance metric \citep{endres_new_2003}.
+
+\citet{roberts_navigating_2016} use the $L_1$ norm of the word-topic distributions to compare topics from different models.
+The $L_1$ norm is the sum of the absolute value of the difference between two vectors.
+Its defined as
+
+\begin{align*}
+	L_1=\sum_{i=1} |a_i-b_i|
+\end{align*}
+
+this measure has a range of $[0,2]$, where $ L_1 \to 0$ indicates strong similarities.
+\citet{roberts_navigating_2016} compare this measure with a cosine similarity metric, which is essentially the dot product rescaled by the $L_2$ norm of the vectors and is defined as.
+
+\begin{align*}
+	\text{cos}(\theta)=\frac{\sum_{i=1}a_i b_i}{\sqrt{\sum_{i=1}a_i^2}\sum_{i=1}b_i^2}
+\end{align*}
+
+However, different to the above mentioned metrics the cosine similarity has a range of $[0,1]$ and $cos(\theta) \to 0$ indicate less similarity.
+
+Figure \ref{fig_distance} displays the different distance measures
+
+\begin{figure}[H]
+	\begin{center}
+		\caption{Similarity measures of word-topic probabilities}
+		\includegraphics[width=\textwidth,keepaspectratio]{../figs/distance}
+		\label{fig_distance}
+	\end{center}
+\end{figure}
+
+% ----------------------
 % Regression
@@
 \include{lm1}
-%
-%One way to model this type of situation is to assume that the data come from a mixture of two populations, one where the counts is always zero, and another where the count has a Poisson distribution with mean $\mu$.
-In this model zero counts can come from either population, while positive counts come only from the second one.
-%
-%The distribution of the outcome can then be modeled in terms of two parameters, $\pi$ the probability of 'always zero', and $\mu$, the mean number of publications for those not in the 'always zero' group.
-A natural way to introduce covariates is to model the logit of the probability $\pi$ of always zero and the log of the mean $\mu$ for those not in the always zero class.
-%
-%The two-part model relaxes the assumption that the zeros (whether or not the article is shared) and positives (how often it is shared) come from the same data generating process.
-The zero-inflated model lets the zeros occur in two different ways: as a realization of the binary process (z=0) and as a realization of the count process when the binary variable z=1.
-%
-%If the process generating the zeros is $f_1(.)$ and the process generating the positive responses is $f_2(.)$ then the two-part hurdle model is defined by the following probabilities. 
-%
-%\begin{align*}
-%	g(y)=\begin{cases}
-%		f_1(0) + 1(f_i(0))f_2(0) if y=0 \\
-%		(1-f_1(0))f_2(y) if y\geq 1
-%	\end{cases}
-%\end{align*}
-%
-%The model for the zero versus positive responses is a binary model with the specified distribution, but we usually estimate it with the probit/logit model.
 

### 2018-03-14 paper/writing/structure.tex
some cleaning

@@
 
-The new developments in digital media provide new opportunities and challenges for content creators, the public and politicians.
-The provision of information through the Internet is both faster and much cheaper compared to a time when information was mainly distributed through traditional media (TV, newspaper).
-The speed and (low)cost of information distribution could contribute to an informed electorate.
-On the other hand, this change also means that the incentive for media to produce primary information declines since the Internet has reduced the marginal utility of content.
+Media outlets (TV, Radio, Newspaper) usually operate in two-sided markets, where they serve two customer groups (content consumer and advertiser) that are connected via indirect network effects.
+The new developments in digital media provide new opportunities and challenges for media outlets.
+The costs of providing and disseminating information have been reduced and the speed of information exchange has increased enormously.
+At first glance, these developments seem to have a positive effect on the provision of information.
+However, it also means that the incentive for media to produce primary information declines since the Internet has reduced the marginal utility of content.
 A study of French news websites from 2013 shows that only 38 percent of the online articles contained original content, with the remainder being copies of those originals \citep{cage_information_2017}.
+At the same time, the number of people who find out about current news on the Internet is increasing.
+According to a study on the media coverage of the German-speaking population, nearly 40\% of respondents used the internet at least once a week in 2017 to inform themselves about the current news compared to 34\% in 2016 \citep{vuma_arbeitsgemeinschaft_verbrauchs-_und_medienanalyse_verbrauchs-_2017}.
+Recognizing the importance of media pluralism, the European Commission has endorsed several initiatives to discuss and promote media diversity in the European Union \citep{_media_2014}.
 
-At the same time, the number of people who find out about current news on the Internet is also increasing.
-According to a study on the media coverage of the German-speaking population, nearly 40\% of respondents used the internet at least once a week in 2017 to inform themselves about the current news compared to 34\% in 2016 \citep{vuma_arbeitsgemeinschaft_verbrauchs-_und_medienanalyse_verbrauchs-_2017}.
-
-This paper examines to what extent the content of different online news resembles each other.
-More specifically, I use a data set of German online news articles about domestic politics dated from 01.06.2017 to 31.12.2017\footnote{German federal elections took place on 24th of September 2017.} from seven German news content providers.
-The final step is to check whether the tonality of reporting is reflected in the polls.
+This paper examines the media pluralism in the market for German-language online news.
+More specifically, I use a data set of German online news articles about domestic politics dated from 01.06.2017 to 01.03.2018 from seven German news content providers.
+German federal elections took place on 24th of September 2017 and the formation of the government has taken up a period of about five month.
+The articles considered here thus inform their readers both about the election promises of the parties (before the election) and about the coalition talks (after the election).
+They thus make an important contribution to the public's opinion-forming process.
 The empirical strategy follows a novel approach combining "the two Ts": Topic and Tone \citep{hansen_shocking_2016}.
 That is, first the topics covered in the articles are identified, to find out how these topics are discussed (tone).
+The final step is to check whether the tonality of reporting is reflected in the survey results on voting preferences.
 More precisely, the research strategy is as follows:
@@
 \begin{enumerate}
-	\item \textbf{Discovering Topics (Section \ref{ch_model})} To discover the latent topics in the corpus, the structural topic modeling (STM) developed by \citet{roberts_model_2016} is applied.
+	\item\label{item_1} \textbf{Discovering Topics (Section \ref{ch_model})} To discover the latent topics in the corpus, the structural topic modeling (STM) developed by \citet{roberts_model_2016} is applied.
 The STM is an unsupervised machine learning approach that models topics as multinomial distributions of words and documents as multinomial distributions of topics, allowing to incorporate external variables that effect both, topical content and topical prevalence.
@@
 As the prevalence of topics are allowed to vary across news wires, the posterior topic-probability $\theta_{dk}$ of an article (document) can be used to estimate the conditional expectation of topic prevalence for given article characteristics.
-
-	\item \textbf{Measuring Tone} After assigning a topic to each article (document), a dictionary-based sentiment analysis is conducted to estimate how topics are discussed differently by different news wires.
+	\item\label{item_2} \textbf{Measuring Tone} After assigning a topic to each article (document), a dictionary-based sentiment analysis is conducted to estimate how topics are discussed differently by different news wires.
+	\item\label{item_3} \textbf{Comparing with polls} In order to check whether the transmitted content from the online media is reflected in the voting preferences, we compare the values from \ref{item_2} with the survey values of the Sunday survey ("Sonntagsumfrage") graphically and mathematically.
+The latter is done by means of correlations.
+Therefore, no causal relationships are calculated.
 
@@
 \citet{hansen_shocking_2016} applied a similar approach to a dataset of 142 FOMC decision statements to measure the effect of those statements on macroeconomic variables.
+An additional extension is the comparison with current poll values (\ref{item_3}).
 
@@
 Section \ref{ch_model} explains the generative process of the structural topic model as well as the selected parameters to run the model.
-The results of the STM, as well as the sentiment analysis are the evaluated in Section \ref{ch_empirical}.
+The empirical analysis containing the above mentioned steps is conducted in Section \ref{ch_empirical}.
 
@@
 Many online news agencies provide part of their editorial content for free and hide another, more exclusive part behind a paywall.
-However, since the Internet has considerably simplified the possibilities for obtaining information and thus reduced the marginal utility of content, such a business model can only be efficient if the content is very exclusive.
+However, since the Internet has considerably simplified the possibilities for obtaining information and thus reduced the marginal utility of content, such a business model can only be efficient if the content behind the paywall is very exclusive.
 As a result, many publishers rely on a free-media model, in which the publishers do not charge viewers for access to the media at all, in order to attract as many eyeballs as possible to their platform, and thus, exploit the indirect network effects on the advertising site.
-In fact, most advertising-financed online magazines earn their gross margin from advertising \citep{evans_industrial_2005}.
+In fact, most advertising-financed online magazines earn a large part of their gross margin from advertising \citep{evans_industrial_2005}.
 In order to maximize their profits, these companies have an interest in attracting as many readers as possible.
@@
 Ensuring the diversity of media content is intended to counteract possible media bias.
-
-As stated above, this paper examines whether imperfections in the market of online news exist, by comparing the topic prevalence between public and private online news with the supply of private news providers.
-In the event that there is no market failure in terms of information provision, the existence of public media could still be justified by the fact that socially relevant contents of private providers are systematically distorted and the existence of public offerings ensures the diversity of information and opinions transmitted.
-In order to examine this bias, the divergence of word-topic probabilities is calculated to analyze how the topics are discussed differently.
+As stated above, this paper examines content diversity in the market of online news, by comparing the topic prevalence between the news providers.
 
@@
 
-This process revealed that a model with 40 topics best reflects the structure in the corpus.
-Furthermore, the ownership of the news provider of each article (public or private) and the month it was published are used as covariates in the topic prevalence.
-In other words, the probability distribution of topics depends on the business-model as well as on the month the article was published.
-The ownership is also included as a covariate affecting topical content, following the assumption that the same topic is discussed in different ways in private and public media respectively.
+This process revealed that a model with 50 topics best reflects the structure in the corpus.
+Furthermore, the publisher of the article is used as covariates in the topic prevalence and topical content.
+In other words, the corresponding newswire of an article influences the probability distribution of topics and how the topics are discussed.
 To address problems due to non-convexity, we rely on the spectral initialization approach advocated by \citet{roberts_navigating_2016}.
@@
 This section summarizes the results of the STM.
-Subsequently different measures to analyze the content differences between public and private ownership are applied according to the following approaches: (1) To address the question whether market imperfections exist in that sense, that some topics are not covered by private but by public news provider, I use the document-topic probability $\theta$, to estimate the conditional expectation of topic prevalence for given document characteristics (See section \ref{subsectiona_topicprevalence}).
-(2) Next, I find all edges between topics where they exhibit a positive correlation of $\theta$ above 0.1 to examine how topics are correlated differently for different covariate levels, indicating how topics are connected and framed differently between private and public media (see section \ref{subsection_topiccorrelation}).
-Approaches (1) and (2) have been used in \citep{roberts_model_2016}.
-However, we extend the analysis by (3) calculating the similarity of the word-topic distribution $\beta$ between the news provider using various distance measures, to identify which topics are discussed similar or differently (see section \ref{subsection_similarity}).
+Subsequently "the two T's" (Topic and Tone) of the corpus are analyzed according to the following approaches: (1) The document-topic probability $\theta$ is used, to estimate the conditional expectation of topic prevalence for given document characteristics (See section \ref{subsection_topic}).
+A set of topics is selected, that most distinctly discuss a particular party (or a topic related to a party).
+(2) Articles that are assigned to the selected topics with the highest probability are then used to conduct a dictionary-based analysis (see section \ref{subsection_tone}).
+
+\subsection{Topic}\label{subsection_topic}
 
@@
 
-It becomes apparent that the topic (topic 3) about the coalition talks between the so-called Jamaica parties (CDU/CSU, FDP and Bündnis 90/Die Grünen) is the topic with the highest expected frequency in the whole corpus, followed by the topics about refugees in Germany (topic 32) and the coalition talks between CDU/CSU and SPD (topic 1), that began shortly after the failure of the Jamaican coalition.
-Particularly in the latter case, there is no discernible difference between private and public providers, while topic 3 and 32 are more likely to be seen in public news.
-The biggest difference can be seen in Topic 23, which covers court proceedings, especially in relation to the NSU case.
-Private providers seem to be less likely to report on this topic, as it is of less likelihood of observing this topic in the corpus of private news.
-Topic 7, which deals with political trends in Germany, seems to be discussed more often in private than in public news.
+It becomes apparent that the topic (topic 4) about the coalition talks between CDU/CSU and SPD - the "Great coalition" or "GroKo" (from the German word Große Koalition) - is the topic with the highest expected frequency in the whole corpus, followed by the topic about the so-called Jamaica parties (CDU/CSU, FDP and Bündnis 90/Die Grünen), which was the first alternative to be negotiated directly after the elections.
+The Figure also shows, that topics related to refugees in Germany (topics 12 and 42) are quite frequent within the corpus.
+We will select the following topics from the whole set (topic are ordered regarding their overall corpus frequency):
+
+\begin{enumerate}
+	\item Topic 4: Covering the debates about the great coalition talks, mainly after the failure of the Jamaica coalition talks. 
+	\item Topic 27: Covering the Jamaica coalition talks, mainly focusing on the smaller players Bündnis 90/Die Grünen and FDP.
+	\item Topic 23: About issues regarding the CSU, mainly about the competition between Horst Seehofer and Markus Söder and the negotiations with the CDU.
+	\item Topic 37: Covering debates of AfD and DIE LINKE in the parliament (Deutscher Bundestag).
+	\item Topic 17: Covering votes within the SPD, mainly regarding the vote about a possible coalition with CDU/CSU ("GroKo")
+	\item Topic 26: Discussing the failure of the Jamaica coalition talks and the two possible alternatives: Reelections or a great coalition.
+	\item Topic 13: About Angela Merkel, mainly right before the election.
+	\item Topic 1: About the SPD, mainly about the election campaign and Martin Schulz as candidate for the chancellor.
+	\item Topic 32: About the AfD, mainly about Alice Weidel and Alexander Gauland, voted as parliamentary party leaders after the resignation of Frauke Petry.
+	\item Topic 30: About the AfD, mainly about the resignation of Frauke Petry and Jörg Meuthen.
+	\item Topic 2: About Bündnis 90/Die Grünen, mainly covering issues regarding the party's personell debates.
+	\item Topic 22: About SPD, mainly covering issues regarding the party's personell debates
+	\item Topic 20: About the AfD, mainly about their relation to right-wing extremist groups.
+	\item Topic 46: Covering issues regarding the CDU.
+\end{enumerate}
 
@@
 
-\subsection{Differences in topic prevalence}\label{subsectiona_topicprevalence}
-
-To identify which of these differences is significant, the conditional expectation of topic prevalence for given document characteristics can be estimated \citep{roberts_model_2016}.
+Next, the differences of topic prevalence for given document characteristics can be estimated \citep{roberts_model_2016}.
 More specifically, I estimate a linear model, where the documents are observations, the dependent variable is the posterior probability of a topic and the covariates are the metadata of documents (see equation \ref{eq_1}).
@@
 \begin{equation}\label{eq_1}
-	\theta_d=\alpha+\beta_1x_{ownership}+\beta_2x_{month}+\epsilon
+	\theta_d=\alpha+\beta x_{ownership}+\epsilon
 \end{equation}
 
-Figure \ref{fig_estimateEffects} displays the regression results for private vs. public.
+Figure \ref{fig_estimateEffects} shows the regression results for the above selected topics. The coefficients indicate the deviation from the base value of Bild.de.
 
@@
 
-\subsection{Topic correlations}\label{subsection_topiccorrelation}
+\subsection{Tone}\label{subsection_tone}
 
-Next, the topic correlation is calculated, indicating how topics are connected and framed in public and private media.
-In Figure \ref{fig_topic_correlations}, indicates all edges between topics where they exhibit a positive correlation above 0.1 \citep{roberts_model_2016}.
+Once we identifying the topics of interest, we use only these documents that are assigned to one of the topics with the highest probability.
+A dictionary-based method is then applied on the remaining 5611 documents with the aim to measure the tone (or sentiment) of a document.
+The idea of a sentiment analysis is to determine the attitude of a writer toward the overall tonality of a document.
+To conduct such an analysis, a lists of words (dictionary) associated with a given emotion, such as negativity is pre-defined by the analyst.
+The document is then deconstructed into individual words and the frequencies of words contained in a given dictionary are then calculated.
 
-\begin{figure}[H]
-	\caption{Topic Correlation}
-		\begin{center}
-		\begin{subfigure}{.7\textwidth}
-			\includegraphics[width=\textwidth]{../figs/corrplot1.png}	
-			\subcaption{Private news provider}
-		\end{subfigure}
-		\begin{subfigure}{.7\textwidth}
-			\includegraphics[width=\textwidth]{../figs/corrplot2}
-			\caption{Public news provider}	
-		\end{subfigure}
-		\end{center}
-	\label{fig_topic_correlations}
-\end{figure}
-
-\textcolor{red}{AUSWERTUNG}
-
-\subsection{Differences in word-topic distributions}\label{subsection_similarity}
-
-Previous topic modeling research try to measure the similarity between topics, comparing the word-topic-distribution between the topics (most of the research uses LDA without metadata, so the word-topic-distribution is the same within the whole corpus).
-cosine similarity \citep{he_detecting_2009}, \citep{ramage_labeled_2009}, Kullback-Leibler (KL) \citep{newman_distributed_2009}, \citep{wang_mining_2009} and the average Log Odds Ratio \citep{chaney_visualizing_2012} are frequently used metrics to compare word probability distributions.
-\citet{kim_topic_2011} compare six popular similarity metrics in terms of log likelihood of data, concluding that Jensen-Shannon Divergence (the symmetric variation of KL divergence) is best in terms of performance and generality.
-
-Since a topic is a multinomial distribution over the vocabulary, where $\beta_{kvi}$ indicates the probability of observing word $v$ in topic $k$ for covariate level $i$, we can analyze how similar a topic $k$ is for different levels of covariates.
-More precisely, we can calculate the similarity between $\beta_{kvi}$ and $\beta_{kvj}$.
-I use each row of that matrix (corresponding to each topic) to calculate the similarity of the word-topic distribution between the public and private media using the square root of the Jensen-Shannon (JS) Divergence.
-I will compare this metric with a set of other similarity measures recently used in the literature to measure the difference between word-topic distributions: The Kullback-Leibler (KL) divergence (\citet{newman_distributed_2009}, \citet{wang_mining_2009}), the cosine similarity (\citet{he_detecting_2009}, \citet{ramage_labeled_2009}) and the difference of the $L1$ norm of the vectors \citep{roberts_navigating_2016}.
-Before the results are presented, I will briefly explain these measures before I proceed to the results.
-
-Essentially, the KL divergence is the expectation of the log difference between probabilities $a$ and $b$. It can be defined as:
-
-\begin{align*}
-	D_{KL}(a,b)=\sum_{i=1}^T a_i \text{ln} \frac{a_i}{b_i},
-\end{align*}
-
-where $D_{kl} \to 0$ indicates stronger similarities.
-However, since the KL divergence is not symmetric, it cannot be used to measure the distance between two distributions, but as a divergence measure.
-
-The Jensen-Shannon Divergence is a positive definite measure, satisfying the following conditions: $D_{js}(a,b) \geq 0$, $D_{js}(a,b)=0$ iff $(a=b)$.
-It is also symmetric: $D_{js}(a,b)=D_{js}(b,a)$.
-The Jensen-Shannon distance $D_{js}(a,b)$ between the two distributions is defined as:
-
-\begin{align*}
-	D_{js}(a,b)=\frac{1}{2}D_{KL}(a,\frac{a+b}{2})+\frac{1}{2}D_{KL}(b,\frac{a+b}{2})
-\end{align*}
-
-where $D_{KL}$ is the Kullback-Leibler divergence.
-Since $D_{js}$ does not satisfy the triangular inequality condition $D_{js}(a,c)\leq D_{js}(a,c)+D_{js}(b,c)$, the JSD is not considered to be a real distance metric.
-However, we can use the square root of JSD as a real distance metric \citep{endres_new_2003}.
-
-\citet{roberts_navigating_2016} use the $L_1$ norm of the word-topic distributions to compare topics from different models.
-The $L_1$ norm is the sum of the absolute value of the difference between two vectors.
-Its defined as
-
-\begin{align*}
-	L_1=\sum_{i=1} |a_i-b_i|
-\end{align*}
-
-this measure has a range of $[0,2]$, where $ L_1 \to 0$ indicates strong similarities.
-\citet{roberts_navigating_2016} compare this measure with a cosine similarity metric, which is essentially the dot product rescaled by the $L_2$ norm of the vectors and is defined as.
-
-\begin{align*}
-	\text{cos}(\theta)=\frac{\sum_{i=1}a_i b_i}{\sqrt{\sum_{i=1}a_i^2}\sum_{i=1}b_i^2}
-\end{align*}
-
-However, different to the above mentioned metrics the cosine similarity has a range of $[0,1]$ and $cos(\theta) \to 0$ indicate less similarity.
-
-Figure \ref{fig_distance} displays the different distance measures
-
-\begin{figure}[H]
-	\begin{center}
-		\caption{Similarity measures of word-topic probabilities}
-		\includegraphics[width=\textwidth,keepaspectratio]{../figs/distance}
-		\label{fig_distance}
-	\end{center}
-\end{figure}
-
-\subsection{Sentiment Analysis}
-
-Once we identifying the topics of interest, we use only these documents in which the posterior probability of topic $k$ is above the threshold of $0.75$, to apply a dictionary method with the aim to measure the tone of a document.
-To conduct such an analysis, a lists of words (dictionary) associated with a given emotion, such as negativity is pre-defined by the analyst.
-The target text is then deconstructed into individual words and the frequencies of words contained in a given dictionary are then calculated.
 Such lexical or “bag-of-words” approaches are widely presented in the finance literature to  determine  the  effect  of  central  banks’  monetary  policy  communications on asset prices and real variables (\citet{nyman_news_2018} \citep{tetlock_giving_2007}, \citep{tetlock_more_2008}).
@@
 
-To measure the tone of a document, we use a dictionary that lists words associated with positive and negative polarity weighted within the interval of $[-1; 1]$.
+The present paper uses a dictionary that lists words associated with positive and negative polarity weighted within the interval of $[-1; 1]$.
 SentimentWortschatz\footnote{SentiWS for short.
@@
 their inflections, respectively.
-The sentiment score for each document $d$ is calculated as follows:
+The sentiment score for each document $d$ is calculated  based on the weighted polarity values for a word, defined on an interval between -1 and 1.
+The score is then calculated from the sum of the words in a document (which can be assigned to a word from the dictionary) divided by the total number of words in that document:
 
 \begin{equation}
-	\text{SentScore}_d = \frac{|\text{positive}_d| - |\text{negative}_d|}{|\text{TotalWords}_d|}
+	\text{SentScore}_d = \frac{|\text{positive polarity score}_d| - |\text{negative polarity score}_d|}{|\text{TotalWords}_d|}
 \end{equation}
+
+The following figure shows the results of the analysis for each topic on a monthly basis, aggregated on all newspaper.
+Each sentiment value is weighted by the relative share of the topic in the overall reporting of that month.
+
+Some conclusions can be drawn from this illustration.
+First of all, it can be seen that, on average, all topics are discussed almost exclusively negatively.
+An exception is topic 27 concerning the Jaimiaca coalition negotiations, which shows a positive sentiment value for a short period of time (October 2017).
+In the following month (November 2017), after it became clear that there would be no coalition between the CDU/CSU, FDP and Die Grünen, the value of this topic as well as that of topic 26 drops rapidly.
+
+Concerning the issues that discuss the great coaltion between CDU/CSU and SPD, it is evident that the overall tone is in which this topic is discussed is generally decreasing from November 2017 to January 2018, but in the following February, the sentiment value of this topic rises.
+However, the sentiment score of topics that deal with the SPD alone (1, 17, 22) is diminishing in the course of time, with topic 17 recording the largest decline.
+The topic, which contains the CDU in isolation (46), is rather zigzagging, with a low peak in October 2017.
+
+\begin{figure}[H]
+	\caption{Monthly Sentiment Score}
+		\begin{center}
+			\includegraphics[width=0.9\textwidth,keepaspectratio]{../figs/sentscore_monthly.png}
+		\end{center}
+	\label{fig_sentscore_monthly}
+\end{figure}
+
+\begin{figure}[H]
+	\caption{Sentiment Score by news wire}
+		\begin{center}
+			\includegraphics[width=0.9\textwidth,keepaspectratio]{../figs/sentscore_site.png}
+		\end{center}
+	\label{fig_sentscore_site}
+\end{figure}
+
+\begin{figure}[H]
+	\caption{Sentiment Score Radarplot}
+		\begin{center}
+			\includegraphics[width=0.9\textwidth,keepaspectratio]{../figs/sentscore_radar.png}
+		\end{center}
+	\label{fig_sentscore_radar}
+\end{figure}
 

### 2018-03-14 paper/docs/04_Modelresults_50.Rmd
some more writing

@@
 
-  1. Articles that have been assigned a topic with a probability of over 75% (gamma > 0.75).
+  1. Articles that have been assigned a topic with a probability of over 30% (gamma > 0.3).
   2. Articles assigned to one of the above mentioned topics.
@@
 
-```{r eval=FALSE, fig.height=10, fig.width=10, include=FALSE}
+```{r eval=FALSE, include=FALSE}
 sentDF.values %>%
@@
           rescale = F,
-          alpha = 0, legend.position = "right") +
+          alpha = 0) +
   labs(title = "Sentiment scores Jun 2017-March 2018",
@@
   guides(col = guide_legend(nrow = 1)) +
-  theme(legend.position = "bottom")
-
-ggsave(filename = "../figs/sentscore_radar.png", plot = p, width = 12)
+  theme(legend.position = "bottom",
+        axis.text = element_text(size = 8))
+
+ggsave(filename = "../figs/sentscore_radar.png", 
+       plot = p)
 ```

### 2018-03-14 paper/writing/structure.tex
some more writing

@@
 \begin{enumerate}
-	\item\label{item_1} \textbf{Discovering Topics (Section \ref{ch_model})} To discover the latent topics in the corpus, the structural topic modeling (STM) developed by \citet{roberts_model_2016} is applied.
+	\item\label{item_1} \textbf{Discovering Topics (Section \ref{subsection_topic})} To discover the latent topics in the corpus, the structural topic modeling (STM) developed by \citet{roberts_model_2016} is applied.
 The STM is an unsupervised machine learning approach that models topics as multinomial distributions of words and documents as multinomial distributions of topics, allowing to incorporate external variables that effect both, topical content and topical prevalence.
@@
 As the prevalence of topics are allowed to vary across news wires, the posterior topic-probability $\theta_{dk}$ of an article (document) can be used to estimate the conditional expectation of topic prevalence for given article characteristics.
-	\item\label{item_2} \textbf{Measuring Tone} After assigning a topic to each article (document), a dictionary-based sentiment analysis is conducted to estimate how topics are discussed differently by different news wires.
+	\item\label{item_2} \textbf{Measuring Tone (Section \ref{subsection_tone}) After assigning a topic to each article (document), a dictionary-based sentiment analysis is conducted to estimate how topics are discussed differently by different news wires.
 	\item\label{item_3} \textbf{Comparing with polls} In order to check whether the transmitted content from the online media is reflected in the voting preferences, we compare the values from \ref{item_2} with the survey values of the Sunday survey ("Sonntagsumfrage") graphically and mathematically.
@@
 		\begin{center}
-			\includegraphics[width=0.9\textwidth,keepaspectratio]{../figs/estimates.png}
+			\includegraphics[width=\textwidth,keepaspectratio]{../figs/estimates.png}
 		\end{center}
@@
 First of all, it can be seen that, on average, all topics are discussed almost exclusively negatively.
-An exception is topic 27 concerning the Jaimiaca coalition negotiations, which shows a positive sentiment value for a short period of time (October 2017).
+An exception is topic 27 concerning the Jaimaica coalition negotiations, which shows a positive sentiment value for a short period of time (October 2017).
 In the following month (November 2017), after it became clear that there would be no coalition between the CDU/CSU, FDP and Die Grünen, the value of this topic as well as that of topic 26 drops rapidly.
 
-Concerning the issues that discuss the great coaltion between CDU/CSU and SPD, it is evident that the overall tone is in which this topic is discussed is generally decreasing from November 2017 to January 2018, but in the following February, the sentiment value of this topic rises.
+Concerning the issues that discuss the great coalition between CDU/CSU and SPD, it is evident that the overall tone is in which this topic is discussed is generally decreasing from November 2017 to January 2018, but in the following February, the sentiment value of this topic rises.
 However, the sentiment score of topics that deal with the SPD alone (1, 17, 22) is diminishing in the course of time, with topic 17 recording the largest decline.
 The topic, which contains the CDU in isolation (46), is rather zigzagging, with a low peak in October 2017.
+
+If aggregated by news provider, some differences between the sites are discernible (Figure \ref{fig_sentscore_site}).
+To begin with, it should be noted that on average all topics are discussed negatively by all news providers, except topic 22, which mainly covers the personnel debates of the SPD and has a positive value at Tagesschau.de.
+One striking feature is the way in which the Jamaica negotiations are reported.
+Although all providers discuss this topic in a negative light, Bild.de reports this topic particularly negative.
+The same applies to the reports on the grand coalition, where the value of ZEIT ONLINE is the most negative.
+A good overview of how differently the topics are discussed by the providers is also shown in Figure \ref{fig_sentscore_radar}.
+This also clearly shows that the sentiment value of the media differs most notably with regard to topic 27 and topic 4, i.
+e.
+the topics on which the coalition negotiations are reported.
+Furthermore, it becomes evident that the negative sentiment value of FOCUS ONLINE regarding topic 17 is high in relation to the other media.
+FOCUS ONLINE thus reports comparatively more negatively on the debates within the SPD.
+This includes in particular the vote on a possible coalition with CDU/CSU.
+For topic 1, which also deals with the SPD, the value of FOCUS ONLINE is rather negative, only undercut by Bild.de.
 
@@
 		\begin{center}
-			\includegraphics[width=0.9\textwidth,keepaspectratio]{../figs/sentscore_monthly.png}
+			\includegraphics[width=\textwidth,keepaspectratio]{../figs/sentscore_monthly.png}
 		\end{center}
@@
 	\begin{center}
-			\includegraphics[width=0.9\textwidth,keepaspectratio]{../figs/sentscore_site.png}
+		\begin{subfigure}[normla]{\textwidth}
+			\includegraphics[width=\textwidth,keepaspectratio]{../figs/sentscore_site.png}
+			\label{fig_sentscore_site}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.7\textwidth}
+			\includegraphics[width=\textwidth,keepaspectratio]{../figs/sentscore_radar.png}
+			\label{fig_sentscore_radar}
+		\end{subfigure}
 		\end{center}
-	\label{fig_sentscore_site}
-\end{figure}
-
-\begin{figure}[H]
-	\caption{Sentiment Score Radarplot}
-		\begin{center}
-			\includegraphics[width=0.9\textwidth,keepaspectratio]{../figs/sentscore_radar.png}
-		\end{center}
-	\label{fig_sentscore_radar}
 \end{figure}

### 2018-03-14 paper/writing/structure.tex
more on writing

@@
 As the prevalence of topics are allowed to vary across news wires, the posterior topic-probability $\theta_{dk}$ of an article (document) can be used to estimate the conditional expectation of topic prevalence for given article characteristics.
-	\item\label{item_2} \textbf{Measuring Tone (Section \ref{subsection_tone}) After assigning a topic to each article (document), a dictionary-based sentiment analysis is conducted to estimate how topics are discussed differently by different news wires.
+	\item\label{item_2} \textbf{Measuring Tone (Section \ref{subsection_tone})} After assigning a topic to each article (document), a dictionary-based sentiment analysis is conducted to estimate how topics are discussed differently by different news wires.
 	\item\label{item_3} \textbf{Comparing with polls} In order to check whether the transmitted content from the online media is reflected in the voting preferences, we compare the values from \ref{item_2} with the survey values of the Sunday survey ("Sonntagsumfrage") graphically and mathematically.
@@
 
-Figure \ref{fig_estimateEffects} shows the regression results for the above selected topics. The coefficients indicate the deviation from the base value of Bild.de.
+Figure \ref{fig_estimateEffects} shows the regression results for the above selected topics.
+The coefficients indicate the deviation from the base value of Bild.de.
+Starting from above it becomes apparent that the topic prevalence of topic 46 (regarding the CDU) is significantly less for Tagesschau.de and Stern.de.
+The other media do not show any significant difference to Bild.de for this topic.
+The opposite is true for topic 37: With the exception of Stern.de and DIE WELT, topic prevalence for this topic is significantly higher for all media than for Bild.de.
+With the following two topics on AfD it is striking that the topic prevalence at Tagesschau.de is significantly lower compared to Bild.de.
+The topics concerning the Jamaican coalition (topic 27) and the failure (topic 26) seem to be discussed most likely at Bild.de.
+The case is different for the CSU issue (Topic 23), where SPIEGEL ONLINE has the highest probability.
+The same applies to the topic related to the personnel debates of the SPD (22).
+However, Bild.de has the highest topic prevalence for the topic related to votes within the SPD, especially the vote on the grand coalition.
+The same applies to the topic regarding the SPD in general and Martin Schulz in particular (1).
+Overall, topics concerning the SPD seem to be more frequent at Bild.de than in the other media.
+Moreover, the distribution of topics at FOCUS ONLINE seems to be the most similar to that of Bild.de, while the biggest differences exist between Bild.de and Tagesschau.de.
 
@@
 
-\textcolor{red}{AUSWERTUNG}
-
 \subsection{Tone}\label{subsection_tone}
 
-Once we identifying the topics of interest, we use only these documents that are assigned to one of the topics with the highest probability.
+The sentiment analysis is conducted with those documents that are assigned to one of the above selected topics with the highest probability.
 A dictionary-based method is then applied on the remaining 5611 documents with the aim to measure the tone (or sentiment) of a document.

### 2018-03-14 paper/docs/04_Modelresults_50.Rmd
update

@@
 ```{r}
-topics <- matrix(c(1, "SPD, mainly M.Schulz", 2, "B90/ Die Grünen, mainly personell debates", 3, "Mix: Akhanli, Guttenberg, Bayern", 4, "Great Coalition debates", 5, "Diesel scandal", 6, "H.Kohl", 7, "Federal Election results", 8, "Europa, Macron, Schäuble", 9, "Mix: political trends, twitter", 10, "M.Schulz, mainly vs.
-A.Merkel", 11, "politics & democracy in GER", 12, "Deportation of criminal Refugees", 13, "A.Merkel, mainly election campaign", 14, "Text processing fail", 15, "Israel, antisemitism, D.Trump", 16, "Mix: political talkshows, Refugees", 17, "Debates within SPD", 18, "Election in Niedersachsen", 19, "N.Lammert", 20, "AfD, mainly right-wing radicalism", 21, "German armed forces, v.d.Leyen", 22, "SPD, mainly stuffing debates", 23, "CSU, mainly Söder & Seehover", 24, "Bundespräsident F.-W.Steinmeier", 25, "Election polls", 26, "Jamaica fail, Reelections or GroKo?", 27, "Jamaica Coalition debates", 28, "G20 in Hamburg", 29, "Federal Constitutional Court, Ministry of the Interior", 30, "AfD, mainly F.Petry & Meuthen", 31, "D.Trump, Russia", 32, "AfD, mainly Gauland & Weidel", 33, "German armed forces, Mali", 34, "Mix: Children, Education, Women", 35, "Left- rightwing Terror, police reports", 36, "Mix: people, Germany, democracy", 37, "AfD & DIE LINKE in parliament", 38, "EU policies", 39, "Mix: Terror attacks", 40, "Mix: Metoo, SPD", 41, "Terror attack Berlin (Amri)", 42, "Refugee family reunion", 43, "Mix: studies", 44, "Federal Constitutional Court (NSU, Franco, Terror)", 45, "Mix: minister of the interior, environment", 46, "CDU", 47, "Church", 48, "public (budget) statistics, Education/ Healthcare/ Digital policies", 49, "Turkey", 50, "Höcke, Holocaust"), ncol=2, byrow=T)
+topics <- matrix(c(1, "SPD, M.Schulz", 2, "B90/ Die Grünen", 3, "Mix: Akhanli, Guttenberg, Bayern", 4, "Great Coalition debates", 5, "Diesel scandal", 6, "H.Kohl", 7, "Federal Election results", 8, "Europa, Macron, Schäuble", 9, "Mix: political trends, twitter", 10, "M.Schulz, vs.
+A.Merkel", 11, "politics & democracy in GER", 12, "Deportation of criminal Refugees", 13, "A.Merkel, election campaign", 14, "Text processing fail", 15, "Israel, antisemitism, D.Trump", 16, "Mix: political talkshows, Refugees", 17, "Debates within SPD", 18, "Election in Niedersachsen", 19, "N.Lammert", 20, "AfD, right-wing radicalism", 21, "German armed forces, v.d.Leyen", 22, "SPD, stuffing debates", 23, "CSU, Söder & Seehover", 24, "Bundespräsident F.-W.Steinmeier", 25, "Election polls", 26, "Jamaica fail, Reelections or GroKo?", 27, "Jamaica Coalition debates", 28, "G20 in Hamburg", 29, "Federal Constitutional Court, Ministry of the Interior", 30, "AfD, F.Petry & Meuthen", 31, "D.Trump, Russia", 32, "AfD, Gauland & Weidel", 33, "German armed forces, Mali", 34, "Mix: Children, Education, Women", 35, "Left- rightwing Terror, police reports", 36, "Mix: people, Germany, democracy", 37, "AfD & DIE LINKE in parliament", 38, "EU policies", 39, "Mix: Terror attacks", 40, "Mix: Metoo, SPD", 41, "Terror attack Berlin (Amri)", 42, "Refugee family reunion", 43, "Mix: studies", 44, "Federal Constitutional Court (NSU, Franco, Terror)", 45, "Mix: minister of the interior, environment", 46, "CDU", 47, "Church", 48, "public (budget) statistics, Education/ Healthcare/ Digital policies", 49, "Turkey", 50, "Höcke, Holocaust"), ncol=2, byrow=T)
 
@@
 
-```{r fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
+```{r message=FALSE, warning=FALSE}
 p <- ggplot(frequency, aes(x=reorder(topic_name, frequency), y=frequency)) + 
-    geom_col(fill=col[2], alpha=0.8) +
+    geom_col(fill=col[3], alpha=0.8) +
     coord_flip() +
@@
 
-ggsave(filename = "../figs/topic_proportion.png")
+ggsave(filename = "../figs/topic_proportion.png", height = 10)
 ```
@@
   geom_col(alpha = 0.8) +
-  scale_fill_manual(values = col[c(2,1)]) +
+  scale_fill_manual(values = col[c(5,3)]) +
   scale_x_discrete(position = "top") +
+  geom_hline(yintercept = 0, linetype = 2,
+             color = "black") +
   coord_flip() +
@@
 
-p1
-
-ggsave(plot = p1, filename = "../figs/estimates.png", device = "png",width = 10, height = 7,
+ggsave(plot = p1, filename = "../figs/estimates.png", device = "png",width = 8, height = 5,
 dpi = 600)
@@
 $$
-```{r}
+```{r message=FALSE, warning=FALSE}
 sentDF.values <- sentDF %>%
@@
 p1 <- ggplot(p, 
-       aes(yearmonth, sentiment, 
-           group = topic_name,
-           label = obs)) +
-  facet_wrap(~topic_name, nrow = 3) +
-  geom_col(fill = col[1], alpha = 0.7) +
- geom_line(color = col[2], size = 0.8) +
-  #geom_text() +
-  geom_hline(yintercept = 0, linetype = 2,
-             color = "black") +
-  labs(x="", y="",
-       title = "Monthly Sentiment Score",
-       subtitle = "unweighted") +
-  theme(axis.text.y = element_text(size=8),
-        axis.text.x = element_text(size = 10))
-
-p2 <- ggplot(p, 
        aes(yearmonth, sentiment_w, 
@@
   facet_wrap(~topic_name, nrow = 3) +
-  geom_col(fill = col[2], alpha = 0.7) +
- geom_line(color = col[1], size = 0.8) +
+  geom_col(fill = col[3], alpha = 0.8) +
+ geom_line(color = col[5], size = 0.6) +
   #geom_text() +
@@
 
-ggsave(filename = "../figs/sentscore_monthly.png", plot = p2, width = 12)
+ggsave(filename = "../figs/sentscore_monthly.png", plot = p1,  width = 9,
+       height = 5)
 ```
@@
 
-```{r eval=FALSE, fig.height=12, fig.width=10, include=FALSE}
+```{r eval=FALSE, include=FALSE}
 p <- sentDF.values %>%
@@
        aes(reorder(topic_name, topic), 
-           sentiment, 
-           group = site,
-           label = obs)) +
-  geom_col(fill=col[2], alpha = 0.7) +
-  #geom_line(color = col[1], size = 0.8) +
-  #geom_text(size = 2.5) +
-  geom_hline(yintercept = 0, linetype = 2,
-             color = "black") +
-  coord_flip() +
-  facet_wrap(~site, ncol = 7) +
-  labs(x="", y="",
-       title = "Sentiment Score",
-       subtitle = "unweighted") +
-  theme(axis.text.y = element_text(size = 10),
-        axis.text.x = element_text(size=6))
-
-p2 <- ggplot(p, 
-       aes(reorder(topic_name, topic), 
            sentiment_w, 
@@
            label = obs)) +
-  geom_col(fill=col[1], alpha = 0.7) +
+  geom_col(fill=col[3], alpha = 0.8) +
   #geom_line(color = col[2], size = 0.8) +
-  #geom_text(size = 2.5) +
+  geom_text(size = 2) +
   geom_hline(yintercept = 0, linetype = 2,
@@
        subtitle = "") +
-  theme(axis.text.y = element_text(size = 10),
+  theme(axis.text.y = element_text(size =8),
         axis.text.x = element_text(size=6, angle = 90))
 
-ggsave(filename = "../figs/sentscore_site.png", plot = p2, width = 12)
+ggsave(filename = "../figs/sentscore_site.png", plot = p1, width = 9,
+       height = 5)
 ```

### 2018-03-16 paper/docs/04_Modelresults_50.Rmd
add crosscorrelation

@@
       plot.caption = element_text(size = 6),
-      plot.background   = element_rect("#fafafa", "#fafafa"),
-      panel.background  = element_rect("#fafafa"),
       panel.border = element_blank()
@@
 load("../output/btw_out2.Rda")
+
+btw <- btw %>%
+  mutate(site = ifelse(site == "welt.de", "DIE WELT", site),
+         site = ifelse(site == "zeit.de", "ZEIT ONLINE", site),
+         site = ifelse(site == "focus.de", "FOCUS ONLINE", site),
+         site = ifelse(site == "spiegel.de", "SPIEGEL ONLINE", site),
+         site = ifelse(site == "tagesschau.de", "Tagesschau.de", site))
 ```
@@
 $$
-\theta_d=\alpha+\beta_1x_{ownership}+\beta_2x_{month}+\epsilon
+\theta_d=\alpha+\beta x_{ownership}+\epsilon
 $$
@@
 ```
+
+![Estimates](../figs/estimates.png)
 
@@
 ## Monthly
+# polls_monthly <- polls %>%
+#   group_by(yearmonth,party) %>%
+#   summarise(mean_val = mean(value, na.rm=T)) %>%
+#   ungroup() %>%
+#   filter(!party %in% c("Piraten", "Sonstige")) %>%
+#   filter(mean_val != "NaN") %>%
+#   mutate(mean_val = normalize_data(mean_val)) %>%
+#   select(party, yearmonth, mean_val) %>%
+#   spread(party, mean_val) %>%
+#   filter(yearmonth > as.Date("2017-05-01"))
+
 polls_monthly <- polls %>%
@@
   ungroup() %>%
+  filter(!party %in% c("Piraten", "Sonstige")) %>%
   filter(mean_val != "NaN") %>%
@@
   filter(yearmonth > as.Date("2017-05-01")) %>%
-  transmute(Union = normalize_data(Union),
+  filter(yearmonth < as.Date("2018-03-01")) %>%
+  mutate(AfD = normalize_data(AfD),
+         FDP = normalize_data(FDP),
+         Grüne = normalize_data(Grüne),
+         Linke = normalize_data(Linke),
          SPD = normalize_data(SPD),
-         Grüne = normalize_data(Grüne),
-         FDP = normalize_data(FDP),
-         AfD = normalize_data(AfD),
-         yearmonth = yearmonth)
+         Union = normalize_data(Union))
 
 polls_monthly %>%
-  gather(key = party, value = poll, Union:AfD) %>%
+  gather(key = party, value = poll, AfD:Union) %>%
   ggplot(aes(yearmonth, poll, color = party)) +
   geom_line() +
-  scale_color_manual(values = c("skyblue", "gold", "limegreen", "red", "black")) +
+  scale_color_manual(values =  c("deepskyblue", "gold", "limegreen", "deeppink", "red", "black")) +
   labs(x="", y="", title = "Survey Value", 
@@
              linetype = 2, color = col[3]) +
-  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET"))
-```
-
+  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%b", tz="CET")) +
+    theme(axis.text.x = element_text(size = 10))
+```
+
+Normalize topic-sentiment value
+
+A)
 ```{r fig.height=12, fig.width=10}
+### by time
+# group1 <- sentDF.values %>%
+#   group_by(yearmonth, topic_name, topic) %>%
+#   summarise(sentiment = mean(sentiment, na.rm=T),
+#             obs = n()) %>%
+#   ungroup() %>%
+#   left_join(., tally_month, by="yearmonth") %>%
+#   mutate(w = obs / total_obs,
+#          sentiment_w = sentiment * w,
+#          sentiment_n = normalize_data(sentiment_w))
+
+### by time and site
+# group2 <- sentDF.values %>%
+#   group_by(yearmonth, topic_name, topic, site) %>%
+#   summarise(sentiment = mean(sentiment, na.rm=T),
+#             obs = n()) %>%
+#   ungroup() %>%
+#   left_join(., tally_month_site, by=c("yearmonth","site")) %>%
+#   mutate(w = obs / total_obs,
+#          sentiment_w = sentiment * w,
+#          sentiment_n = normalize_data(sentiment_w))
+```
+
+B)
+```{r}
 ### by time
@@
   mutate(w = obs / total_obs,
-         sentiment_w = sentiment * w,
-         sentiment_n = normalize_data(sentiment_w))
+         sentiment_w = sentiment * w)
+
+group1 <- group1 %>%
+  select(yearmonth, topic, sentiment_w) %>%
+  spread(topic, sentiment_w) %>%
+  lapply(normalize_data) %>%
+  as.data.frame() %>%
+  gather(topic, sentiment_n, -yearmonth) %>%
+  mutate(topic = as.numeric(gsub("X","", topic))) %>%
+  merge(., group1, by = c("topic", "yearmonth"))
 
@@
   mutate(w = obs / total_obs,
-         sentiment_w = sentiment * w,
-         sentiment_n = normalize_data(sentiment_w))
+         sentiment_w = sentiment * w)
+
+group2 <- group2 %>%
+  select(yearmonth, topic, site, sentiment_w) %>%
+  spread(topic, sentiment_w) %>%
+  lapply(normalize_data) %>%
+  as.data.frame() %>%
+  gather(topic, sentiment_n, -yearmonth, -site) %>%
+  mutate(topic = as.numeric(gsub("X","", topic))) %>%
+  merge(., group2, by = c("topic", "yearmonth","site"))
 ```
@@
 #### 3.1. Cross-Correlation
-```{r}
-group1 %>%
-  select(yearmonth, topic_name, sentiment_n) %>%
-  spread(topic_name, sentiment_n)  -> corr1
-
-polls_monthly %>% select(- yearmonth) -> corr2
-
+
+```{r}
+plot_ccf <- function(corr1, corr2, ...){
+
+  # Create empty matrix
   corr <- expand.grid(names(corr1), names(corr2))
   corr$correlation <- NA
-```
-
-```{r}
+
   x <- 1
@@
     #print(names(corr2[,corr1Id]))
+
     for(corr2Id in 1:ncol(corr1)) {
@@
   }
-```
-
-```{r}
+
+      ### Plot Corr ##
       ggplot(corr, aes(Var2, Var1,
@@
                  label = round(correlation,2))) +
-  geom_tile(color="white") +
-  geom_text(size = 3, color = col[5]) +
-  viridis::scale_fill_viridis() +
-  labs(x="", y="", title = "Cross Correlation of Polls vs. Sentiment Value")
-```
+        geom_tile(color="white", ...) +
+        geom_text(size = 3.5, color = col[5]) +
+        viridis::scale_fill_viridis(limits=c(-1, 1)) +
+        labs(x="", y="", fill="",
+             title = "Cross-Correlation / Polls vs. Sentiment Value",
+             ...)
+}
+```
+
+##### 3.1.1. Overall
+```{r fig.height=6, fig.width=8}
+group1 %>%
+  select(yearmonth, topic_name, sentiment_n) %>%
+  spread(topic_name, sentiment_n) %>%
+  select(- yearmonth) -> corr1
+
+polls_monthly %>% select(- yearmonth) -> corr2
+
+plot_ccf(corr1, corr2)
+```
+
+##### 3.1.2. By Media
+```{r eval=FALSE, include=FALSE}
+for (i in unique(group2$site)) {
+
+  group2 %>%
+  filter(site == i) %>%
+  select(yearmonth, topic_name, sentiment_n) %>%
+  spread(topic_name, sentiment_n) %>%
+  select(- yearmonth) -> corr1
+
+  p <- plot_ccf(corr1, corr2,
+                show.legend = F,
+                subtitle = paste(i)
+                )
+
+  ggsave(filename = paste0("../figs/corrplot_",i,".png"),
+         height = 5)
+}
+
+```
+
+<img src="../figs/corrplot_Bild.de.png", width = "49%">
+<img src="../figs/corrplot_DIE WELT.png", width = "49%">
+<img src="../figs/corrplot_FOCUS ONLINE.png", width = "49%">
+<img src="../figs/corrplot_SPIEGEL ONLINE.png", width = "49%">
+<img src="../figs/corrplot_stern.de.png", width = "49%">
+<img src="../figs/corrplot_Tagesschau.de.png", width = "49%">
+<img src="../figs/corrplot_ZEIT ONLINE.png", width = "49%">
 
@@
 
-##### 3.2.1. CDU
-```{r fig.height=10, fig.width=12}
+```{r}
+plot_Poll_Sent <- function(filters, party_str, color_str) {
+
   ### Plot 1  
   plot1 <- group1 %>%
-  filter(grepl(paste("CDU","CSU",sep="|"), topic_name))
+    filter(grepl(filters, topic_name))
 
@@
              position = "dodge",
-           alpha = 0.8) +
+             alpha = 0.5) +
     scale_fill_manual(values = col) +
-    geom_line(data=plot1, aes(yearmonth, sentiment_n, 
+
+    geom_line(data=plot1, aes(yearmonth, 
+                              sentiment_n,
                               group = topic_name,
@@
     guides(fill = guide_legend(ncol=3)) +
+
     # Add poll line
     geom_line(data = polls_monthly,
-            aes(yearmonth, Union),
-            color = "black",
-            size = 1) +
+              aes_string("yearmonth", party_str),
+              color = color_str,
+                            size = 0.9,
+              linetype = 2) +
     labs(y="", x="", fill="",
          title = "Sentiment & Poll Values",
-       subtitle = "Both scores are normalized") +
-  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
+         subtitle = party_str,
+         caption = "Both scores are normalized") +
+    scale_x_date(breaks = date_breaks("1 month"), 
+                 labels=date_format("%B", tz="CET")) +
     theme(legend.position = "bottom")
@@
   plot2 <- group2 %>%
-  filter(grepl(paste("CDU","CSU",sep="|"), topic_name))
+    filter(grepl(filters, topic_name))
 
@@
                  fill = topic_name),
-           alpha = 0.8,
+             alpha = 0.5,
              position = "dodge") +
@@
     scale_color_manual(values = col) +
+
     geom_line(data = plot2,
@@
     facet_wrap(~site, ncol = 2) +
+
     # Add poll line
     geom_line(data = polls_monthly, 
-            aes(yearmonth, Union),
-            color = "black",
-            size = 1) +
+              aes_string("yearmonth", party_str),
+              color = color_str,
+              size = 0.9,
+              linetype = 2) +
     labs(y="", x="", fill="") +
-  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
+    scale_x_date(breaks = date_breaks("1 month"), 
+                 labels=date_format("%B", tz="CET")) +
     theme(legend.position = "none",
@@
   p1 + p2 + plot_layout(ncol = 1, heights = c(1,4))
+
+}
+```
+
+##### 3.2.1. CDU
+```{r fig.height=12, fig.width=10}
+filters <- paste("CDU","CSU","Great Coalition", sep="|")
+
+### Plot 1  
+plot_Poll_Sent(filters, "Union", "black")
 ```
@@
 ```{r fig.height=12, fig.width=10}
-plot1 <- group1 %>%
-  filter(grepl(paste("SPD", sep="|"), topic_name, ignore.case = T))
-
-### Plot 1  
-p1 <- ggplot() +
-  geom_col(data=plot1, aes(yearmonth, sentiment_n, 
-             group = topic_name,
-             fill = topic_name),
-           position = "dodge", 
-           alpha = 0.8) +
-  scale_fill_manual(values = col) +
-  guides(fill = guide_legend(ncol=3)) +
-   geom_line(data=plot1, aes(yearmonth, sentiment_n, 
-             group = topic_name,
-             color = topic_name),
-             show.legend = F) +
-  scale_color_manual(values = col) +
-  # Add poll line
-  geom_line(data = polls_monthly, 
-            aes(yearmonth, SPD),
-            color = "red",
-            size = 1) +
-  labs(y="", x="", fill="",
-       title = "Sentiment & Poll Values",
-       subtitle = "Both scores are normalized") +
-  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
-  theme(legend.position = "bottom")
-
-### plot by time and site
-plot2 <- group2 %>%
-  filter(grepl(paste("SPD", sep="|"), topic_name, ignore.case = T))
-
-### Plot 2
-p2 <- ggplot() +
-  geom_col(data = plot2,
-           aes(yearmonth, sentiment_n, 
-             group = topic_name,
-             fill = topic_name),
-           alpha = 0.8,
-           position = "dodge") +
-  scale_fill_manual(values = col) +
-  facet_wrap(~site, ncol = 2) +
-     geom_line(data=plot2, aes(yearmonth, sentiment_n, 
-             group = topic_name,
-             color = topic_name),
-             show.legend = F) +
-  scale_color_manual(values = col) +
-   # Add poll line
-  geom_line(data = polls_monthly, 
-            aes(yearmonth, SPD),
-            color = "red",
-            size = 1) +
-  labs(y="", x="", fill="") +
-  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
-  theme(legend.position = "none",
-        axis.text.x = element_text(angle = 90))
-
-p1 + p2 + plot_layout(ncol = 1, heights = c(1,4))
-```
+filters <- paste("SPD","Great Coalition", sep="|")
+
+plot_Poll_Sent(filters, "SPD", "black")
+```
+
+##### 3.2.3. AfD
+```{r fig.height=12, fig.width=10}
+filters <- paste("AfD", sep="|")
+
+plot_Poll_Sent(filters, "AfD", "black")
+```
+
+#### FDP
+```{r fig.height=12, fig.width=10}
+filters <- paste("Jamaica", sep="|")
+
+plot_Poll_Sent(filters, "FDP", "black")
+```
+
+#### Grüne
+```{r fig.height=12, fig.width=10}
+filters <- paste("Grüne","Jamaica", sep="|")
+
+plot_Poll_Sent(filters, "Grüne", "black")
+```

### 2018-03-16 paper/writing/structure.tex
add crosscorrelation

@@
 First of all, it can be seen that, on average, all topics are discussed almost exclusively negatively.
-An exception is topic 27 concerning the Jaimaica coalition negotiations, which shows a positive sentiment value for a short period of time (October 2017).
-In the following month (November 2017), after it became clear that there would be no coalition between the CDU/CSU, FDP and Die Grünen, the value of this topic as well as that of topic 26 drops rapidly.
+An exception is topic 27 concerning the Jamaica coalition negotiations, which shows a positive sentiment value for a short period of time (October 2017).
+In the following month (November 2017), after it became clear that there would be no coalition between the CDU/CSU, FDP and Die Grünen, the value of this topic as well as that of topic 26 drops rapidly, but then rises again in February.
+Concerning the issues that discuss the great coalition between CDU/CSU and SPD, it is evident that the overall tone is in which this topic is discussed is generally decreasing from November 2017 to January 2018, but in the following February, the sentiment value of this topic rises.
+However, the sentiment score of topics that deal with the SPD (1, 17, 22) is diminishing in the course of time, with topic 17 recording the largest decline.
+For the other parties the process is rather zigzag-like.
 
-Concerning the issues that discuss the great coalition between CDU/CSU and SPD, it is evident that the overall tone is in which this topic is discussed is generally decreasing from November 2017 to January 2018, but in the following February, the sentiment value of this topic rises.
-However, the sentiment score of topics that deal with the SPD alone (1, 17, 22) is diminishing in the course of time, with topic 17 recording the largest decline.
-The topic, which contains the CDU in isolation (46), is rather zigzagging, with a low peak in October 2017.
+\begin{figure}[H]
+	\caption{Monthly Sentiment Score}
+		\begin{center}
+			\includegraphics[width=\textwidth,keepaspectratio]{../figs/sentscore_monthly.png}
+		\end{center}
+	\label{fig_sentscore_monthly}
+\end{figure}
 
@@
 For topic 1, which also deals with the SPD, the value of FOCUS ONLINE is rather negative, only undercut by Bild.de.
-
-\begin{figure}[H]
-	\caption{Monthly Sentiment Score}
-		\begin{center}
-			\includegraphics[width=\textwidth,keepaspectratio]{../figs/sentscore_monthly.png}
-		\end{center}
-	\label{fig_sentscore_monthly}
-\end{figure}
 

### 2018-03-16 paper/docs/func/functions.R

@@ -189,8 +189,13 @@ KLD <- function(x,y) {
 #####################
 
 normalize_data <- function(x) {
-  y <- (x - min(x, na.rm = T)) / (max(x, na.rm = T) - min(x, na.rm = T))
-  return(y)
+  if (is.numeric(x)) {
+    y <- (x - min(x, na.rm = T)) / (max(x, na.rm = T) - min(x, na.rm = T))
+    return(y)
+  } else {
+    return(x)
+  }
+
 }
 
 ###########

### 2018-03-16 paper/docs/04_Modelresults_50.Rmd
more writign

@@
 
-ggsave(filename = "../figs/topic_proportion.png", height = 10)
+ggsave(filename = "../figs/topic_proportion.png", height = 8)
 ```
@@
        title = "",
-       subtitle = "") +
+       subtitle = "Numbers indicate the ") +
   theme(axis.text.y = element_text(size =8),
-        axis.text.x = element_text(size=6, angle = 90))
+        axis.text.x = element_text(size=6, angle = 90),
+        axis.title.x = element_text(size = 8))
 

### 2018-03-16 paper/writing/structure.tex
more writign

@@
 
-If aggregated by news provider, some differences between the sites are discernible (Figure \ref{fig_sentscore_site}).
-To begin with, it should be noted that on average all topics are discussed negatively by all news providers, except topic 22, which mainly covers the personnel debates of the SPD and has a positive value at Tagesschau.de.
-One striking feature is the way in which the Jamaica negotiations are reported.
-Although all providers discuss this topic in a negative light, Bild.de reports this topic particularly negative.
+If aggregated by news provider, some differences between the sites are discernible (Figure \ref{fig_sentscore_site}\footnote{The numbers reflect the number of observations.}).
+To begin with, it can be noted that on average all topics are discussed negatively by all news providers, except topic 22, which mainly covers the personnel debates of the SPD and has a positive value at Tagesschau.de.
+One striking feature is the way in which the Jamaica negotiations and their failure are reported (topics 27 and 26).
+Although all providers discuss this topics in a negative light, Bild.de reports them particularly negative.
 The same applies to the reports on the grand coalition, where the value of ZEIT ONLINE is the most negative.
-A good overview of how differently the topics are discussed by the providers is also shown in Figure \ref{fig_sentscore_radar}.
-This also clearly shows that the sentiment value of the media differs most notably with regard to topic 27 and topic 4, i.
+
+Barplot um die Topic-Tendenzen innerhalb eines Mediums zu betrachten, Radarplot um die Unterschiede besser dazustellen.
+Barplot: 
+- Insgesamt alle Themen negativ (bis auf topic 23 bei tagesschau.de). 
+- Bei Bild.de sind die Themen, die die Koalitionsverhandlungen (26,27,4) und die SPD (1,17) am stärksten negativ. Auch die Themen bezüglich der AfD (20,30,32,37) werden stärker negativ besprochen.
+- WELT ONLINE: Zwei Themen bezüglich der AfD (32,20) am stärksten negativ, sowie die Topics bzgl. der Jamaika Koalition (27) und der Großen Koalition (4).
+- FOCUS ONLINE sind es vor allem Themen, die die SPD betreffen (27, 17, 4, 1), die einen negativen Sentiment Wert haben. Auch topic 32 und 37 sind vergleichsweise stark negativ.
+- Bei SPIEGEL ONLINE ist zunächst auffällig, dass hier der Unterschied des Sentiment Wertes zwischen den einzelnen Themen weniger stark ist.
+Dabei stechen die Themen 13, als vergleichsweise weniger negativ heraus (allerdings sind diese Themen auch bei den anderen Medien die, die am wenigsten negativ besprochen werden.)
+- Auch bei stern.de ist der Unterschied des Sentiment Wertes weniger groß und insgesamt weniger stark negativ.
+Am positivsten (bzw.
+am wenigsten negativ) schneidet das Theme zur CDU (46) und zu Martin Schulz (10).
+- Tagesschau.de ist bei den meisten Themen am wenigsten negativ , bzw.
+sogar einmal positiv.
+Dies trifft allerdings nicht auf topic 23 (CSU) zu, wo tagesschau.de im Vergleich zu den anderen Medien am stärksten negativ ist.
+- Wie schon bei Bild.de, schneiden die Themen in Bezug auf die Koalitionsverhandlungen (27 und 4) auch bei ZEIT ONLINE eher schlecht ab.
+Allerdings sind die Themen rund um die AfD (30, 32,37 und 20) noch negativer als bei Bild.de.
+
+\begin{figure}[H]
+	\caption{Sentiment Score by news wire}
+	\begin{center}
+			\includegraphics[width=\textwidth,keepaspectratio]{../figs/sentscore_site.png}
+			\label{fig_sentscore_site}
+	\end{center}
+\end{figure}
+
+A good overview of how differently the topics are discussed by the providers is shown in Figure \ref{fig_sentscore_radar}.
+It gets evident that the sentiment value of the media differs most notably with regard to topic 27 and topic 4, i.
 e.
 the topics on which the coalition negotiations are reported.
+With regard to the Jamaica coalition, Bild.de reports the most and tagesschau.de the least negative.
+The reporting of ZEIT ONLINE concerning the grand coalition is the one with the most negative sentiment value and again Tagesschau.de, together with stern.de, the one with the value which is least negative.
 Furthermore, it becomes evident that the negative sentiment value of FOCUS ONLINE regarding topic 17 is high in relation to the other media.
@@
 For topic 1, which also deals with the SPD, the value of FOCUS ONLINE is rather negative, only undercut by Bild.de.
+Topics related to AfD do not show striking differences.
 
@@
 	\begin{center}
-		\begin{subfigure}[normla]{\textwidth}
-			\includegraphics[width=\textwidth,keepaspectratio]{../figs/sentscore_site.png}
-			\label{fig_sentscore_site}
-		\end{subfigure}
-		\begin{subfigure}[normla]{0.7\textwidth}
 			\includegraphics[width=\textwidth,keepaspectratio]{../figs/sentscore_radar.png}
 			\label{fig_sentscore_radar}
-		\end{subfigure}
 	\end{center}
 \end{figure}
+
+After the above figures have been analyzed, the following points can be summarized: (a) The sentiment value of the SPD is decreasing over time, especially in regard to internal votes.
+(b) The topics relating to the coalition talks on Jamaica (26, 27) and the grand coalition (4) are discussed rather critically, but they also show the greatest differences within the media.
+In contrast, the tonality of the topics in relation to the AfD shows rather small differences.
+(c) Overall, the sentiment value at Tagesschau.de is the least negative and only shows a comparatively strong negative value at topic 23, concerning the CSU.
 

### 2018-03-19 paper/docs/04_Modelresults_50.Rmd
change styling of figures

@@
 
-ggsave(plot = p1, filename = "../figs/estimates.png", device = "png",width = 8, height = 5,
+ggsave(plot = p1, filename = "../figs/estimates.png", device = "png",width = 8, height = 6,
 dpi = 600)
@@
 
-The comparison with the sentiment value of individual topics is intended to show whether there is a correlation between the current tendency to vote and the type of reporting.
-For this purpose, the monthly average of both time series is calculated and rescaled to an interval between 0 and 1.
-
-The analysis in this section is done in two steps: First, the standardised time series are compared graphically. In the second step, the cross-correlation between two time series is calculated.
-
-###### Normalization
-
-$$
-z_i = \frac{x_i-\text{min}(x)}{\text{max}(x)-\text{min}(x)}
-$$
-where $x = (x_1,...,x_n)$ and $z_i$ is the $i^{th}$ normalized data.
-
 ```{r}
@@
          yearweek = calculate_week(week(Datum), year(Datum))) 
-
-## Monthly
-# polls_monthly <- polls %>%
-#   group_by(yearmonth,party) %>%
-#   summarise(mean_val = mean(value, na.rm=T)) %>%
-#   ungroup() %>%
-#   filter(!party %in% c("Piraten", "Sonstige")) %>%
-#   filter(mean_val != "NaN") %>%
-#   mutate(mean_val = normalize_data(mean_val)) %>%
-#   select(party, yearmonth, mean_val) %>%
-#   spread(party, mean_val) %>%
-#   filter(yearmonth > as.Date("2017-05-01"))
-
+```
+
+```{r include=FALSE}
+p <- polls %>%
+  filter(yearmonth > as.Date("2017-01-01")) %>%
+  filter(!party %in% c("Piraten", "Sonstige")) %>%
+  ggplot(aes(Datum, value, 
+             group = party,
+             color = party)) +
+  geom_line() +
+  scale_color_manual(values =  c("deepskyblue", "gold", "limegreen", "deeppink", "red", "black")) +
+  scale_x_date(breaks = date_breaks("1 month"), 
+               labels=date_format("%b", tz="CET")) +
+    geom_vline(xintercept = as.Date("2017-09-24"), 
+             linetype = 2, color = col[3]) +
+  labs(x="", y="", color="",
+       title = "",
+       caption = "source: infratest dimap") +
+    guides(color = guide_legend(nrow = 1,
+                                label.theme = element_text(size = 6,
+                                                           angle=0))) +
+  theme(axis.text = element_text(size=6),
+        legend.position = "bottom")
+
+ggsave(filename = "../figs/polls.png", plot = p, width = 6, height = 4, dpi = 600)
+```
+
+![Poll Results](../figs/polls.png)
+###### Normalization 
+The comparison with the sentiment value of individual topics is intended to show whether there is a correlation between the current tendency to vote and the type of reporting.
+For this purpose, the monthly average of both time series is calculated and rescaled to an interval between 0 and 1.
+
+The analysis in this section is done in two steps: First, the standardised time series are compared graphically. In the second step, the cross-correlation between two time series is calculated.
+
+$$
+z_i = \frac{x_i-\text{min}(x)}{\text{max}(x)-\text{min}(x)}
+$$
+where $x = (x_1,...,x_n)$ and $z_i$ is the $i^{th}$ normalized data.
+
+```{r}
 polls_monthly <- polls %>%
@@
 
-B)
+B) Normalize each time series by its own.
+
 ```{r}
@@
         labs(x="", y="", fill="",
-             title = "Cross-Correlation / Polls vs. Sentiment Value",
+             title = "",
              ...)
@@
 
-plot_ccf(corr1, corr2)
-```
-
+p <- plot_ccf(corr1, corr2, alpha = 0.8,
+              subtitle = "Election polls vs. topic sentiment value (monthly)")
+
+ggsave(filename = "../figs/ccf.png", plot = p,
+       height = 6, width = 8)
+```
+
+![Cross-correlation](../figs/ccf.png)
 ##### 3.1.2. By Media
@@
   p1 <- ggplot() +
-    geom_col(data=plot1, aes(yearmonth, sentiment_n,
-                             group = topic_name,
-                             fill = topic_name),
-             position = "dodge",
-             alpha = 0.5) +
-    scale_fill_manual(values = col) +
+    # geom_col(data=plot1, aes(yearmonth, sentiment_n,
+    #                          group = topic_name,
+    #                          fill = topic_name),
+    #          position = "dodge",
+    #          alpha = 0.5) +
+    # scale_fill_manual(values = col) +
 
@@
               show.legend = F) +
-    scale_color_manual(values = col) +
+    #scale_color_manual(values = col) +
     guides(fill = guide_legend(ncol=3)) +
@@
   p2 <- ggplot() +
-    geom_col(data = plot2,
-             aes(yearmonth, sentiment_n, 
-                 group = topic_name,
-                 fill = topic_name),
-             alpha = 0.5,
-             position = "dodge") +
-    scale_fill_manual(values = col) +
-    scale_color_manual(values = col) +
+    # geom_col(data = plot2,
+    #          aes(yearmonth, sentiment_n, 
+    #              group = topic_name,
+    #              fill = topic_name),
+    #          alpha = 0.5,
+    #          position = "dodge") +
+    # scale_fill_manual(values = col) +
+    # scale_color_manual(values = col) +
 
@@
 ```{r fig.height=12, fig.width=10}
-filters <- paste("CDU","CSU","Great Coalition", sep="|")
+filters <- paste(":", sep="|")
 

### 2018-03-19 paper/docs/04_Modelresults_50.Rmd
finish that writing!

@@
   theme(
+    axis.text = element_text(size = 6),
       legend.position   = "none"
@@
 ggsave(filename = "../figs/ccf.png", plot = p,
-       height = 6, width = 8)
+       height = 6, width = 8, dpi = 600)
 ```

### 2018-03-19 paper/writing/structure.tex
finish that writing!

@@
 
+\title{Topic and tone of political news articles in German online media.}
+\date{\today}
+\author{Franziska Löw}
+
 \begin{document}
+\begin{titlepage}
+	\maketitle
+	\begin{abstract}
+		The aim of this paper is to investigate whether the political reporting of different content providers distinguishes itself and whether this reporting has an influence on the opinion-forming process of the voters.
+
+		\textbf{Keywords} Structural Topic Model, Sentiment Analysis, Unsupervised Machine Learning, Text Mining
+
+	\end{abstract}
+
+\end{titlepage}
 
@@
 According to a study on the media coverage of the German-speaking population, nearly 40\% of respondents used the internet at least once a week in 2017 to inform themselves about the current news compared to 34\% in 2016 \citep{vuma_arbeitsgemeinschaft_verbrauchs-_und_medienanalyse_verbrauchs-_2017}.
-Recognizing the importance of media pluralism, the European Commission has endorsed several initiatives to discuss and promote media diversity in the European Union \citep{_media_2014}.
+Recognizing the importance of media pluralism, the European Commission has endorsed several initiatives to discuss and promote media diversity in the European Union\footnote{https://ec.europa.eu/digital-single-market/en/policies/media-freedom-and-pluralism}.
 
-This paper examines the media pluralism in the market for German-language online news.
-More specifically, I use a data set of German online news articles about domestic politics dated from 01.06.2017 to 01.03.2018 from seven German news content providers.
+A resulting question is whether the political reporting of different content providers distinguishes itself and whether this reporting has an influence on the opinion-forming process of the voters.
+The aim of this paper is to investigate these questions with the use of up-to-date text mining methods.
+For this purpose, German online news articles about domestic politics are analyze to examine the media pluralism in the market for German-language online news.
 German federal elections took place on 24th of September 2017 and the formation of the government has taken up a period of about five month.
-The articles considered here thus inform their readers both about the election promises of the parties (before the election) and about the coalition talks (after the election).
-They thus make an important contribution to the public's opinion-forming process.
+The articles considered here dated from 01.06.2017 to 01.03.2018 and thus inform their readers both about the election promises of the parties (before the election) and about the coalition talks (after the election).
+They therefore make an important contribution to the public's opinion-forming process.
 The empirical strategy follows a novel approach combining "the two Ts": Topic and Tone \citep{hansen_shocking_2016}.
 That is, first the topics covered in the articles are identified, to find out how these topics are discussed (tone).
-The final step is to check whether the tonality of reporting is reflected in the survey results on voting preferences.
+The final step is to check whether the tonality of reporting is reflected in the survey results on voting preferences calculating the cross-correlation coefficients.
 More precisely, the research strategy is as follows:
@@
 	\item\label{item_1} \textbf{Discovering Topics (Section \ref{subsection_topic})} To discover the latent topics in the corpus, the structural topic modeling (STM) developed by \citet{roberts_model_2016} is applied.
-The STM is an unsupervised machine learning approach that models topics as multinomial distributions of words and documents as multinomial distributions of topics, allowing to incorporate external variables that effect both, topical content and topical prevalence.
+The STM is an unsupervised machine learning approach that models topics as multinomial distributions of words and documents (as a synonym for news articles) as multinomial distributions of topics, allowing to incorporate external variables that effect both, topical content and topical prevalence.
 I estimate a model, where the newswire service is included as a control for both the topical content and the topical prevalence.
-The result of the generative process of STM are the posterior distributions for topic prevalence and topical content, which can then be used to measure the similarity between the news providers in the further course of the paper: (1) $\beta$ is a $K$-by-$V$ matrix (where $K=$ number of topics and $V=$ vocabulary) containing the probability distribution for topic $k$ over the words in the predefined vocabulary.
-(2) $\theta$ is a $D$-by-$V$ matrix of the document-topic distributions, where the entry $\theta_{dk}$ can be interpreted as the proportion of words in document $d$ which arise from topic $k$, or rather as the probability that document $d$ deals about topic $k$.
-As the prevalence of topics are allowed to vary across news wires, the posterior topic-probability $\theta_{dk}$ of an article (document) can be used to estimate the conditional expectation of topic prevalence for given article characteristics.
+The result of the generative process of STM are the posterior distributions for topic prevalence in a document and the content of a topic.
+The latter is used to label the topics according to an event or issue discussed in the media.
+The probability distribution of topics for each document is used to assign a topic to each news article.
 	\item\label{item_2} \textbf{Measuring Tone (Section \ref{subsection_tone})} After assigning a topic to each article (document), a dictionary-based sentiment analysis is conducted to estimate how topics are discussed differently by different news wires.
-	\item\label{item_3} \textbf{Comparing with polls} In order to check whether the transmitted content from the online media is reflected in the voting preferences, we compare the values from \ref{item_2} with the survey values of the Sunday survey ("Sonntagsumfrage") graphically and mathematically.
-The latter is done by means of correlations.
-Therefore, no causal relationships are calculated.
+	\item\label{item_3} \textbf{Comparing with polls} In order to check whether the transmitted content from the online media is reflected in the voting preferences, we compare the values from \ref{item_2} with the survey values of the Sunday survey ("Sonntagsumfrage").
 
@@
 
-Approach \ref{item_1} has been used in \citet{roberts_model_2016}, among others, to examine differences in the content of news providers.
-However, I extend the analysis by comparing the sentiment score for a given topic between the news provider, to identify which topics are discussed similar or differently (\ref{item_2}).
+Approach \ref{item_1} has been used in \citet{roberts_model_2016}, among others, to examine differences in the content of eastern and western news providers regarding "the rise of China".
+However, I extend the analysis by comparing the sentiment score for a given topic an news provider, to identify which topics are discussed similar or differently (\ref{item_2}).
 \citet{hansen_shocking_2016} applied a similar approach to a dataset of 142 FOMC decision statements to measure the effect of those statements on macroeconomic variables.
-An additional extension is the comparison with current poll values (\ref{item_3}).
+An additional extension is the comparison with current election poll values (\ref{item_3}).
 
 The remaining course of the paper is as follows: In Section \ref{ch_onlinenews} the characteristics of the market for online news in Germany are outlined.
+\ref{ch_elections} give a brief overview about political trends in Germany in recent month.
 The data used to conduct the model is described in Section \ref{ch_data}.
@@
 The empirical analysis containing the above mentioned steps is conducted in Section \ref{ch_empirical}.
+
+% -------------------------
+% Background Bundestagswahl
+% -------------------------
+\section{Background on the federal election in Germany (2017)}\label{ch_elections}
+
+The articles analyzed in this paper cover a period from June 1, 2017 to March 1, 2018 and thus cover both the most important election campaign topics for the Bundestag elections on September 24, 2017 and the process of forming a government that lasted until February 2018.
+After four years in a grand coalition with the Social Democrats (SPD), German Chancellor Angela Merkel, member of the Conservative Party (CDU), ran for re-election.
+The SPD nominated Martin Schulz as candidate for chancellor.
+
+On the right side of the political spectrum, AfD (alternative for Germany) managed to be elected to the German Bundestag for the first time in 2017.
+The political debate about the high refugee numbers of the past years brought the AfD a political upswing by taking up the dissatisfaction of parts of the population and using it to raise its own profile.
+Leading party members of the AfD as well as party supporters repeatedly accused the mass media in the course of the reporting on the federal elections to report unilaterally and to present the AfD intentionally badly.
+
+After the election, the formation of a government was difficult due to the large number of parties elected to the Bundestag and the considerable loss of votes by the major parties CDU/CSU and SPD.
+Since all parties rejected a merger with the AfD, numerically only two coalitions with an absolute parliamentary majority were possible: a grand coalition ("GroKo") of CDU/CSU and SPD, and a Jamaica coalition (coalition of CDU/CSU, FDP (economic liberal party) and B90/Die Grünen (Bündnis 90/Die Grünen, green party).
+The grand coalition was initially rejected by the SPD.
+The four-week exploratory talks on the possible formation of a Jamaica coalition officially failed on 19 November 2017 after the FDP announced its withdrawal from the negotiations.
+FDP party leader Christian Lindner said that there had been no trust between the parties during the negotiations.
+The main points of contention were climate and refugee policy.
+CDU and CSU regretted this result, while B90/Die Grünen sharply criticized the withdrawal of the Liberals.
+The then Green leader Cem Özdemir accused the FDP of lacking the will to reach an agreement.
+
+After the failure of the Jamaica coalition, a possible re-election or a minority government as alternatives were discussed in the media before the SPD decided to hold coalition talks with the CDU/CSU.
+This led to great resistance from the party base, which called for a party-internal vote on a grand coalition.
+After the party members voted in favor of the grand coalition, a government was formed 171 days after the federal elections.
+
+Figure \ref{fig_polls} shows that support for the two major popular parties has been declining in recent months since August 2017, with the CDU again showing positive survey results since November.
+However, the value of the SPD has been falling since March 2017.
+At the same time, the AfD in particular has been recording increasingly positive survey results since June 2017.
+Section \ref{ch_correlation} examines whether there is a correlation between the survey results and the way the parties are reported in the media.
+
+\begin{figure}[H]
+\begin{center}
+	\caption{Election Polls}
+	\includegraphics[width=0.8\textwidth]{../figs/polls.png}
+	\label{fig_polls}
+	\end{center}
+\end{figure}
 
@@
 In addition to the quantity of the audience, the demographic characteristics of recipients also have an influence on the willingness to pay on the advertiser site.
-Online advertising makes it possible to target ads to particular consumers in real time.
 
@@
 content aligned with the tastes of the majority.
-\citep{gabszewicz_press_2001} study the problem of diversity of the political content of newspapers.
+\citet{gabszewicz_press_2001} study the problem of diversity of the political content of newspapers.
 They find that the maximum differentiation only prevails if the readers sufficiently value the political differentiation between the newspapers the advertising market is small enough.
@@
 In addition, there is a strict advertising ban and prohibition of regional reporting.
-
-However, given today's media landscape, the role of public media provider and its mandate is questioned.
-The basic justification for a public media offer can be roughly divided into two categories: On the one hand, possible market failure and on the other hand, ensuring diversity.
-The former involves the pursuit of non-economic (e.
-g.
-democratic, social and cultural) objectives, as well as the provision of information that would not be made available by the market due to a lack of willingness to pay.
-Ensuring the diversity of media content is intended to counteract possible media bias.
-As stated above, this paper examines content diversity in the market of online news, by comparing the topic prevalence between the news providers.
 
@@
 
-I conduct the estimation on a sample of 14,937 online news articles from six news provider about domestic politics\footnote{Bild.de, DIE WELT, FOCUS ONLINE, SPIEGEL ONLINE, Stern.de, ZEIT ONLINE, Tagesschau.de}, of which only Tagesschau.de belongs to the group of public provider.
+I conduct the estimation on a sample of 14,937 online news articles from seven news provider about domestic politics\footnote{Bild.de, DIE WELT, FOCUS ONLINE, SPIEGEL ONLINE, stern.de, ZEIT ONLINE, Tagesschau.de}, of which only Tagesschau.de belongs to the group of public provider.
 The reason for this is that the content structure of Tagesschau.de is most similar to that of the private providers.
 ZDF.de offers predominantly video content and DLF website mainly offers audio content in the form of interviews, which makes it hard to include it in the model.
-The articles are dated from 01.06.2017 to 01.03.2018.\footnote{German federal elections took place on 24th of September 2017.} I first extract all online articles using the the Webhose.io API.\footnote{For more information see https://docs.webhose.io/v1.0/docs/getting-started.
+The articles are dated from 01.06.2017 to 01.03.2018.
+I first extract all online articles using the the Webhose.io API.\footnote{For more information see https://docs.webhose.io/v1.0/docs/getting-started.
 The scraping code was written in Python and can be made available on request.} Then all articles from the section "domestic policy" are filtered by checking the URL structure.
@@
 % ------------------
-
 A central task in text mining is to extract low-dimensional information from documents that are high-dimensional by nature \citep{bholat_text_2015}.
@@
 ., ,, !, ?, etc.) and all numbers from our corpus.
-After completing this steps we were left with 55.235 unique terms in our vocabulary.
+After completing this steps we were left with 68.576 unique terms in our vocabulary.
 
@@
 They also use different measures of distance between the topic-word distributions of the same topic within different models.
-In section \ref{ch_similarity} a similar approach is applied to measure similarity between the same topic for different covariate levels.
 
@@
 This process revealed that a model with 50 topics best reflects the structure in the corpus.
-Furthermore, the publisher of the article is used as covariates in the topic prevalence and topical content.
+Furthermore, the media outlet of the article is used as covariates in the topic prevalence and topical content.
 In other words, the corresponding newswire of an article influences the probability distribution of topics and how the topics are discussed.
@@
 Subsequently "the two T's" (Topic and Tone) of the corpus are analyzed according to the following approaches: (1) The document-topic probability $\theta$ is used, to estimate the conditional expectation of topic prevalence for given document characteristics (See section \ref{subsection_topic}).
-A set of topics is selected, that most distinctly discuss a particular party (or a topic related to a party).
+A set of topics is selected, that most distinctly discuss a particular party or a topic related to the federal elections.
 (2) Articles that are assigned to the selected topics with the highest probability are then used to conduct a dictionary-based analysis (see section \ref{subsection_tone}).
+In order to check whether the sentiment value of certain topics are correlated with the results of voting preferences, the cross-correlation function between these two concepts is calculated in \ref{ch_correlation}.
 
@@
 
-In order to get an initial overview of the results, Figure \ref{fig_topic_proportion} displays the topics ordered by their expected frequency across the corpus (left side of the Figure) and the expected proportion of a topic in public media minus the expected proportion of topic use in private media (right side of the Figure).
-Thus topics more associated with public media appear to the right of zero.
+In order to get an initial overview of the results, Figure \ref{fig_topic_proportion} displays the topics ordered by their expected frequency across the corpus.
 To assign a label to each topic, I looked at the most frequent words in that topic and the most representative articles \citep{roberts_model_2016}.
 
-It becomes apparent that the topic (topic 4) about the coalition talks between CDU/CSU and SPD - the "Great coalition" or "GroKo" (from the German word Große Koalition) - is the topic with the highest expected frequency in the whole corpus, followed by the topic about the so-called Jamaica parties (CDU/CSU, FDP and Bündnis 90/Die Grünen), which was the first alternative to be negotiated directly after the elections.
+It becomes apparent that the topic (topic 4) about the coalition talks between CDU/CSU and SPD - the "Grand coalition" or "GroKo" (from the German word Große Koalition) - is the topic with the highest expected frequency in the whole corpus, followed by the topic about the so-called Jamaica parties (CDU/CSU, FDP and B90/Die Grünen), which was the first alternative to be negotiated directly after the elections.
 The Figure also shows, that topics related to refugees in Germany (topics 12 and 42) are quite frequent within the corpus.
-We will select the following topics from the whole set (topic are ordered regarding their overall corpus frequency):
-
-\begin{enumerate}
-	\item Topic 4: Covering the debates about the great coalition talks, mainly after the failure of the Jamaica coalition talks. 
-	\item Topic 27: Covering the Jamaica coalition talks, mainly focusing on the smaller players Bündnis 90/Die Grünen and FDP.
-	\item Topic 23: About issues regarding the CSU, mainly about the competition between Horst Seehofer and Markus Söder and the negotiations with the CDU.
-	\item Topic 37: Covering debates of AfD and DIE LINKE in the parliament (Deutscher Bundestag).
-	\item Topic 17: Covering votes within the SPD, mainly regarding the vote about a possible coalition with CDU/CSU ("GroKo")
-	\item Topic 26: Discussing the failure of the Jamaica coalition talks and the two possible alternatives: Reelections or a great coalition.
-	\item Topic 13: About Angela Merkel, mainly right before the election.
-	\item Topic 1: About the SPD, mainly about the election campaign and Martin Schulz as candidate for the chancellor.
-	\item Topic 32: About the AfD, mainly about Alice Weidel and Alexander Gauland, voted as parliamentary party leaders after the resignation of Frauke Petry.
-	\item Topic 30: About the AfD, mainly about the resignation of Frauke Petry and Jörg Meuthen.
-	\item Topic 2: About Bündnis 90/Die Grünen, mainly covering issues regarding the party's personell debates.
-	\item Topic 22: About SPD, mainly covering issues regarding the party's personell debates
-	\item Topic 20: About the AfD, mainly about their relation to right-wing extremist groups.
-	\item Topic 46: Covering issues regarding the CDU.
-\end{enumerate}
 
@@
 
+We will select the following topics from the whole set (topics are ordered regarding their overall corpus frequency).
+The most frequent words of these topics can be seen in the appendix \ref{fig_plotquote}:
+
+\begin{enumerate}
+	\item Topic 4: Covering the debates about the great coalition talks, mainly after the failure of the Jamaica coalition talks. 
+	\item Topic 27: Covering the Jamaica coalition talks, mainly focusing on the smaller players Bündnis B90/Die Grünen and FDP.
+	\item Topic 23: About issues regarding the CSU, mainly about the competition between Horst Seehofer and Markus Söder and the negotiations with the CDU.
+	\item Topic 37: Covering debates of AfD and DIE LINKE in the parliament (Deutscher Bundestag).
+	\item Topic 17: Covering votes within the SPD, mainly regarding the vote about a possible coalition with CDU/CSU ("GroKo")
+	\item Topic 26: Discussing the failure of the Jamaica coalition talks and the two possible alternatives: Reelections or a great coalition.
+	\item Topic 13: About Angela Merkel, mainly right before the election.
+	\item Topic 1: About the SPD, mainly about the election campaign and Martin Schulz as candidate for the chancellor.
+	\item Topic 32: About the AfD, mainly about Alice Weidel and Alexander Gauland, voted as parliamentary party leaders after the resignation of Frauke Petry.
+	\item Topic 30: About the AfD, mainly about the resignation of Frauke Petry and Jörg Meuthen.
+	\item Topic 2: About B90/Die Grünen, mainly covering issues regarding the party's personell debates.
+	\item Topic 22: About SPD, mainly covering issues regarding the party's personell debates
+	\item Topic 20: About the AfD, mainly about their relation to right-wing extremist groups.
+	\item Topic 46: Covering issues regarding the CDU.
+\end{enumerate}
+
 Next, the differences of topic prevalence for given document characteristics can be estimated \citep{roberts_model_2016}.
@@
 \begin{equation}\label{eq_1}
-	\theta_d=\alpha+\beta x_{ownership}+\epsilon
+	\theta_d=\alpha+\beta x_{newswire}+\epsilon
 \end{equation}
@@
 
-Barplot um die Topic-Tendenzen innerhalb eines Mediums zu betrachten, Radarplot um die Unterschiede besser dazustellen.
-Barplot: 
-- Insgesamt alle Themen negativ (bis auf topic 23 bei tagesschau.de). 
-- Bei Bild.de sind die Themen, die die Koalitionsverhandlungen (26,27,4) und die SPD (1,17) am stärksten negativ. Auch die Themen bezüglich der AfD (20,30,32,37) werden stärker negativ besprochen.
-- WELT ONLINE: Zwei Themen bezüglich der AfD (32,20) am stärksten negativ, sowie die Topics bzgl. der Jamaika Koalition (27) und der Großen Koalition (4).
-- FOCUS ONLINE sind es vor allem Themen, die die SPD betreffen (27, 17, 4, 1), die einen negativen Sentiment Wert haben. Auch topic 32 und 37 sind vergleichsweise stark negativ.
-- Bei SPIEGEL ONLINE ist zunächst auffällig, dass hier der Unterschied des Sentiment Wertes zwischen den einzelnen Themen weniger stark ist.
-Dabei stechen die Themen 13, als vergleichsweise weniger negativ heraus (allerdings sind diese Themen auch bei den anderen Medien die, die am wenigsten negativ besprochen werden.)
-- Auch bei stern.de ist der Unterschied des Sentiment Wertes weniger groß und insgesamt weniger stark negativ.
-Am positivsten (bzw.
-am wenigsten negativ) schneidet das Theme zur CDU (46) und zu Martin Schulz (10).
-- Tagesschau.de ist bei den meisten Themen am wenigsten negativ , bzw.
-sogar einmal positiv.
-Dies trifft allerdings nicht auf topic 23 (CSU) zu, wo tagesschau.de im Vergleich zu den anderen Medien am stärksten negativ ist.
-- Wie schon bei Bild.de, schneiden die Themen in Bezug auf die Koalitionsverhandlungen (27 und 4) auch bei ZEIT ONLINE eher schlecht ab.
-Allerdings sind die Themen rund um die AfD (30, 32,37 und 20) noch negativer als bei Bild.de.
+We use two different Figures to analyze the differences between the media outlets graphically: We use the bar plot to examine the polarity tendencies of the individual topics within a medium (\ref{fig_sentscore_site}) and the radar plot to observe the differences between the media (\ref{fig_sentscore_radar}).
+
+Starting with the bar plot it becomes apparent that all topics are discussed negatively, except topic 23 at Tagesschau.de.
+At Bild.de, the topics that include the coalition negotiations (26,27,4) and the SPD (1,17) are the most negative.
+The topics relating to AfD (20,30,32,37) are also discussed more negatively.
+Looking at the values of WELT ONLINE, two of the AfD topics have the most negative value (32.20).
+Topic 27 concerning the Jamaica Coalition (27) and the Grand Coalition (4) also score relatively negatively.
+Concerning FOCUS ONLINE, it is mainly topics that relate to the SPD (27, 17, 4, 1) that have a strong negative sentiment value, together with topic 32 and 37.
+Turning to SPIEGEL ONLINE, it is noticeable that the difference in sentiment value between the individual topics is less pronounced.
+Topics 13 and 10 stand out as comparatively less negative.
+However, these issues are also the least negatively discussed in the other media.
+Also at stern.de the difference in sentiment value is less significant and overall less negative.
+The topics regarding CDU (46) and Martin Schulz (10) score the most positively (or least negatively).
+Tagesschau.de is the least negative on most topics, or even once positive.
+However, this does not apply to topic 23 (CSU), where tagesschau.de is most negative in comparison to the other media.
+As with Bild.de, the issues relating to the coalition negotiations (27 and 4) also come off rather badly with ZEIT ONLINE.
+However, the issues surrounding AfD (30, 32, 37 and 20) are even more negative than at Bild.de.
 
@@
 	\begin{center}
-			\includegraphics[width=\textwidth,keepaspectratio]{../figs/sentscore_radar.png}
+			\includegraphics[width=0.8\textwidth,keepaspectratio]{../figs/sentscore_radar.png}
 			\label{fig_sentscore_radar}
@@
 
-% ----------------------
-% Appendix
-% ----------------------
+\subsection{News sentiment and poll data}\label{ch_correlation}
+
+This section seeks to examine the temporal association between sentiment reflected in online news content and phone survey poll results in Germany.
+Specifically, it aims to find the extent to which online sentiment and phone survey results correlate.
+I use the data from the "Sonntagsumfrage" (Sunday survey) from infratest dimap\footnote{https://www.infratest-dimap.de/umfragen-analysen/bundesweit/sonntagsfrage/}.
+The institution regularly asks at least 1000 German citizens the question: "Which party would you choose if federal elections take place next Sunday?" The survey thus measures the current election tendencies and therefore reflects an intermediate state in the opinion-forming process of the electoral population.
+
+Much of the research on online content and political trends have focused on traditional weblogs and social media websites, such as Twitter, Facebook, MySpace, and YouTube.
+These studies have shown that social media is used to spread political opinions and that these considerations reflect the political landscape of the offline world.
+\citet{tumasjan_predicting_2010} investigate Tweets between August 13th and September 19th, 2009, prior to the German national elections to examine whether Twitter messages reflect the current offline political sentiment and whether it can be used to predict the popularity of parties or coalitions in the real world.
+With regard to the later question, they compare the share of attention the political parties receive on Twitter with the election result to examine whether the activity on Twitter can serve as a predictor of the election outcome.
+They found that the number of tweets reflects the election result and even comes close to traditional election polls.
+
+\citet{fu_analyzing_2013} use a corpus of online posts from discussion forums and blogs to examine the extent to which online sentiment reflected in social media content can predict phone survey results in Hong Kong.
+They build a sentiment classifier conducting a support vector machine analysis on a training set of 2,000 manually labeled posts.
+In order to evaluate the temporal relationship between the time series of the online sentiment score and the results of the telephone survey, a cross correlation analysis was conducted, using the Box and Jenkins autoregressive integrated moving average (ARIMA) method \citep{box_time_2008}.
+Estimating the cross-correlation functions of the residuals, they find that online sentiment scores can lead phone survey results by about 8–15 days.
+
+In a more recent conference paper, \citet{padmaja_evaluating_2014} identify the scope of negation in news articles for two political parties in India (BJP and UPA) to analyze how the choice of certain words used in these texts influence the sentiments of public in polls.
+Comparing three different sentiment analysis methods (two machine learning and one dictionary method), they observe that the choice of certain words used in political text was influencing the Sentiments in favor of BJP.
+They conclude that this sentiment bias might be one of the causes for the election results in 2014.
+
+In the present paper, the comparison between monthly average of both the sentiment value of individual topics and the survey value of the parties is calculated using the cross-correlation function.
+It is important to notice, that the results from this analysis will give an indication whether correlation between the two time series exist, but it does not give any evidence about the causal relationship.
+None of the following interpretation of the cross-correlation coefficients is intended to describe a causal relationship.
+
+Based on the contemporary coefficients of the cross-correlation estimation shown in Figure \ref{fig_ccf}, the most noticeable topics for each party are evaluated below.
+The AfD's survey results correlate negatively with topics relating to the SPD.
+The strongest positive correlation with regard to AfD-related topics can be found for topic 30.
+Since there are no isolated topics about the FDP, the issues surrounding the Jamaica negotiations are examined, which show a negative correlation.
+It is also striking that the poll results of the FDP correlate strongly negatively with the CSU topic (23).
+With regard to B90/Die Grünen, there is also a negative correlation to the Jamaica topics, however, it is slightly above the correlation-coefficient of the FDP.
+It is striking that there seems to be a strong negative correlation between the SPD issues and the poll results of the Left Party.
+Conversely, the survey results of the SPD correlate very positively with the SPD topics.
+The CDU's survey results correlate most positively with topics relating to coalition negotiations.
+
+\begin{figure}[H]
+	\caption{Cross-Correlation at lag 0}
+	\begin{center}
+			\includegraphics[width=\textwidth,keepaspectratio]{../figs/ccf.png}
+			\label{fig_ccf}
+	\end{center}
+\end{figure}
+
+These results suggest that there is a link between the way parties are reported and the political trends within the population.
+It is obvious to assume that media reporting influences the electorate in its opinion-forming, even if this cannot be proven in this analysis.
+
+\section{Conclusion}
+
+The purpose of this paper was to examine (1) whether the political reporting of different content providers distinguishes itself and (2) whether this reporting has an influence on the opinion-forming process of the voters.
+Regarding (1) the analysis revealed that there are differences between the media considered, both in terms of topic prevalence and the way in which these topics are discussed.
+Although the issues are discussed negatively overall, there are still differences, especially regarding to the coalition negotiations.
+The smallest differences can be found for topic concerning the AfD.
+With regard to (2), the analysis has shown that the tonality of topics discussed by the SPD shows a strong positive correlation to current survey results.
+For CDU/CSU, issues relating to the various coalition negotiations tend to correlate positively with the survey results.
+Overall, there seems to be a link between reporting on political issues and electoral preferences.
+Further research should focus on the exact causal relationships between these two concepts.
+
 \section*{Appendix}
 
+\begin{figure}[H]
+	\includegraphics[width=.49\textwidth]{../figs/plotquote1.png}
+	\caption{}
+\end{figure}
+
+\begin{figure}[H]
+	\includegraphics[width=.49\textwidth]{../figs/plotquote2.png}
+	\caption{}
+\end{figure}
+	% 4
+\begin{figure}[H]
+	\includegraphics[width=.49\textwidth]{../figs/plotquote4.png}
+	\caption{}
+\end{figure}
+
+	% 10
+\begin{figure}[H]
+	\includegraphics[width=.49\textwidth]{../figs/plotquote10.png}
+	\caption{}
+\end{figure}
+
+	% 13
+\begin{figure}[H]
+	\includegraphics[width=.49\textwidth]{../figs/plotquote13.png}
+	\caption{}
+\end{figure}
+	% 17
+\begin{figure}[H]
+	\includegraphics[width=.49\textwidth]{../figs/plotquote17.png}
+	\caption{}
+\end{figure}
+
+	% 20
+\begin{figure}[H]
+	\includegraphics[width=.49\textwidth]{../figs/plotquote20.png}
+	\caption{}
+\end{figure}
+	% 23
+\begin{figure}[H]
+	\includegraphics[width=.49\textwidth]{../figs/plotquote23.png}
+	\caption{}
+\end{figure}
+	% 26
+\begin{figure}[H]
+	\includegraphics[width=.49\textwidth]{../figs/plotquote26.png}
+	\caption{}
+\end{figure}
+	% 27
+\begin{figure}[H]
+	\includegraphics[width=.49\textwidth]{../figs/plotquote27.png}
+	\caption{}
+\end{figure}
+	% 30
+\begin{figure}[H]
+	\includegraphics[width=.49\textwidth]{../figs/plotquote30.png}
+	\caption{}
+\end{figure}
+	% 32
+\begin{figure}[H]
+	\includegraphics[width=.49\textwidth]{../figs/plotquote32.png}
+	\caption{}
+\end{figure}
+	% 37
+\begin{figure}[H]
+	\includegraphics[width=.49\textwidth]{../figs/plotquote37.png}
+	\caption{}
+\end{figure}
+	% 46
+\begin{figure}[H]
+	\includegraphics[width=.49\textwidth]{../figs/plotquote46.png}
+	\caption{}
+\end{figure}
+
 \end{document}

### 2018-03-20 paper/docs/03_marketDescription.Rmd
cleaning

--- 2018-02-08 paper/R/03_marektDescription.Rmd
@@
 keepsite <- c("Tagesschau.de", "SPIEGEL ONLINE", "ZEIT ONLINE", 
-              "Bild.de", "DIE WELT", "FOCUS ONLINE")
+              "Bild.de", "DIE WELT", "FOCUS ONLINE", "stern.de")
 ```
@@
       legend.text       =  element_text(size=6),
-      axis.text.y       = element_text(size = 8)
+      axis.text       = element_text(size = 6)
     ) +
@@
 filename = "../figs/reach.png", device = "png",
-width = 6, height = 4,
+width = 7, height = 4,
         dpi = 600

### 2018-03-20 paper/docs/04_Modelresults_50.Rmd
cleaning

@@
 I conduct a STM (Strucutral Topic Model) estimation on a sample of 14,936 online news articles from seven news provider about domestic politics: Bild.de, DIE WELT, FOCUS ONLINE, SPIEGEL ONLINE, Stern.de, ZEIT ONLINE, Tagesschau.de.
-The articles are dated from 01.06.2017 to 31.12.2017 (German federal elections took place on 24th of September 2017.).
+The articles are dated from 01.06.2017 to 01.03.2018 (German federal elections took place on 24th of September 2017.).
 I first extract all online articles using the the [Eventregistry API](http://eventregistry.org/documentation).
 Then all articles from the section "domestic policy" are filtered by checking the URL structure.
+The data cleaning process is documented [here](https://github.com/franziloew/textmining/blob/gh-pages/paper/docs/02_cleanAndCombine.Rmd).
 
@@
 I will included the news provider as a control for both the topical content and the topical prevalence.
-Additional, the month an article was published is included as a control for the topical prevalence.
-The number of topics is set to 35.
+The number of topics is set to 50.
 
@@
 
-In order to get an initial overview of the results, the figure below displays the topics ordered by their expected frequency across the corpus (left side of the Figure) and the expected proportion of a topic in public media minus the expected proportion of topic use in private media (right side of the Figure).
-Thus topics more associated with public media appear to the right of zero.
+In order to get an initial overview of the results, the figure below displays the topics ordered by their expected frequency across the corpus.
 To assign a label to each topic, I looked at the most frequent words in that topic and the most representative articles.
@@
 
-ggsave(plot = p1, filename = "../figs/estimates.png", device = "png",width = 8, height = 6,
+ggsave(plot = p1, filename = "../figs/estimates.png", device = "png",width = 9, height = 6,
 dpi = 600)
@@
 ggsave(filename = "../figs/sentscore_monthly.png", plot = p1,  width = 9,
-       height = 5)
+       height = 6)
 ```
@@
   theme(axis.text.y = element_text(size =8),
-        axis.text.x = element_text(size=6, angle = 90),
-        axis.title.x = element_text(size = 8))
+        axis.text.x = element_text(size=4, angle = 90),
+        axis.title.x = element_text(size = 5))
 
@@
 
-```{r eval=FALSE, fig.height=10, fig.width=10, include=FALSE}
+```{r eval=FALSE, fig.height=8, fig.width=10, include=FALSE}
 sentDF.values %>%
-  group_by(site, topic_name) %>%
-  summarise(sentiment = mean(sentiment, na.rm=T)) %>%
-  spread(key=topic_name, value=sentiment) -> radar
-
-radar %>%
-  ggRadar(aes(color=site), 
-          rescale = F,
-          alpha = 0, legend.position = "right") +
-  labs(title = "Sentiment score Jun 2017-March 2018",
-       subtitle = "unweighted") +
-  guides(col = guide_legend(nrow = 1)) +
-  theme(legend.position = "bottom")
-```
-
-```{r eval=FALSE, include=FALSE}
-sentDF.values %>%
+  mutate(topic_name = ifelse(grepl("B90", topic_name),
+                             "B90/\nDie Grünen", topic_name),
+         topic_name = ifelse(grepl("17", topic_name),
+                             "17: Debates\nwithin SPD", topic_name),
+         topic_name = ifelse(grepl("13", topic_name),
+                             "13: A.Merkel,\nelection campaign", topic_name),
+         topic_name = ifelse(grepl("30", topic_name),
+                             "30: AfD,\nF.Petry & Meuthen", topic_name),
+         topic_name = ifelse(grepl("32", topic_name),
+                             "32: AfD,\nGauland & Weidel", topic_name),
+         topic_name = ifelse(grepl("37", topic_name),
+                             "37: AfD & DIE LINKE\nin parliament", topic_name),
+         topic_name = ifelse(grepl("20", topic_name),
+                             "20: AfD, right-wing\nradicalism", topic_name)
+         ) %>%
   group_by(site, topic_name) %>%
@@
        subtitle = "weighted") +
-  guides(col = guide_legend(nrow = 1)) +
-  theme(legend.position = "bottom",
-        axis.text = element_text(size = 8))
+  guides(col = guide_legend(ncol = 1)) +
+  theme(legend.position = "right",
+        axis.text.x = element_text(size = 10),
+        axis.text.y = element_blank(),
+        axis.ticks.y = element_blank())
 
@@
 
-A)
-```{r fig.height=12, fig.width=10}
-### by time
-# group1 <- sentDF.values %>%
-#   group_by(yearmonth, topic_name, topic) %>%
-#   summarise(sentiment = mean(sentiment, na.rm=T),
-#             obs = n()) %>%
-#   ungroup() %>%
-#   left_join(., tally_month, by="yearmonth") %>%
-#   mutate(w = obs / total_obs,
-#          sentiment_w = sentiment * w,
-#          sentiment_n = normalize_data(sentiment_w))
-
-### by time and site
-# group2 <- sentDF.values %>%
-#   group_by(yearmonth, topic_name, topic, site) %>%
-#   summarise(sentiment = mean(sentiment, na.rm=T),
-#             obs = n()) %>%
-#   ungroup() %>%
-#   left_join(., tally_month_site, by=c("yearmonth","site")) %>%
-#   mutate(w = obs / total_obs,
-#          sentiment_w = sentiment * w,
-#          sentiment_n = normalize_data(sentiment_w))
-```
-
-B) Normalize each time series by its own.
-
 ```{r}
@@
 ![Cross-correlation](../figs/ccf.png)
+
 ##### 3.1.2. By Media
@@
 
-```{r}
-plot_Poll_Sent <- function(filters, party_str, color_str) {
+For each party, we plot the topics that most strongly correlate with the poll data.
+
+```{r}
+plot_Poll_Sent <- function(topics_number, party_str, color_str) {
 
@@
   plot1 <- group1 %>%
-    filter(grepl(filters, topic_name))
+    filter(topic %in% topic_number)
 
   p1 <- ggplot() +
-    # geom_col(data=plot1, aes(yearmonth, sentiment_n,
-    #                          group = topic_name,
-    #                          fill = topic_name),
-    #          position = "dodge",
-    #          alpha = 0.5) +
-    # scale_fill_manual(values = col) +
+    geom_col(data=plot1, aes(yearmonth, sentiment_n,
+                             group = topic_name,
+                             fill = topic_name),
+             position = "dodge",
+             alpha = 0.5) +
+    scale_fill_manual(values = col) +
 
@@
               show.legend = F) +
-    #scale_color_manual(values = col) +
+    scale_color_manual(values = col) +
     guides(fill = guide_legend(ncol=3)) +
@@
   plot2 <- group2 %>%
-    filter(grepl(filters, topic_name))
+    filter(topic %in% topic_number)
 
@@
     # scale_fill_manual(values = col) +
-    # scale_color_manual(values = col) +
 
@@
     facet_wrap(~site, ncol = 2) +
+    scale_color_manual(values = col) +
 
@@
 ```{r fig.height=12, fig.width=10}
-filters <- paste(":", sep="|")
+topic_number <- c(10,13,23,26)
 
 ### Plot 1  
-plot_Poll_Sent(filters, "Union", "black")
+plot_Poll_Sent(topic_number, "Union", "black")
 ```
@@
 ```{r fig.height=12, fig.width=10}
-filters <- paste("SPD","Great Coalition", sep="|")
-
-plot_Poll_Sent(filters, "SPD", "black")
+topic_number <- c(1,17,22)
+
+plot_Poll_Sent(topic_number, "SPD", "black")
 ```
@@
 ```{r fig.height=12, fig.width=10}
-filters <- paste("AfD", sep="|")
-
-plot_Poll_Sent(filters, "AfD", "black")
+topic_number <- c(17,22, 30)
+
+plot_Poll_Sent(topic_number, "AfD", "black")
 ```
@@
 ```{r fig.height=12, fig.width=10}
-filters <- paste("Jamaica", sep="|")
-
-plot_Poll_Sent(filters, "FDP", "black")
+topic_number <- c(23,26,27)
+
+plot_Poll_Sent(topic_number, "FDP", "black")
 ```
@@
 ```{r fig.height=12, fig.width=10}
-filters <- paste("Grüne","Jamaica", sep="|")
-
-plot_Poll_Sent(filters, "Grüne", "black")
-```
+topic_number <- c(26,27,17)
+
+plot_Poll_Sent(topic_number, "Grüne", "black")
+```
+
+#### DIE LINKE
+```{r fig.height=12, fig.width=10}
+topic_number <- c(1,17,22)
+
+plot_Poll_Sent(topic_number, "Linke", "black")
+```

### 2018-03-29 paper/docs/04_Modelresults_50.Rmd
add more description

@@
 library(Matrix)
+library(psych)
+library(xtable)
+library(quanteda)
 
@@
 The number of topics is set to 50.
+
+# Data Exploratory Analysis
 
@@
 ![plot1](../figs/timeline.png)
+
+## Word Count
+
+```{r}
+output <- describeBy(btw$text_length, btw$site, mat=T)%>%
+  select(group1, n, mean, sd, median, min, max, se)
+rownames(output) <- c()
+
+print(xtable(output, type="latex"), file="../writing/tables/wordcount.tex" )
+
+describeBy(btw$text_length, btw$site)
+```
+
+```{r}
+btw$text_length.cut <- cut(btw$text_length, c(seq(0,2000,1), Inf))
+btw <- btw %>% group_by(site) %>%
+  mutate(text_length.mean = mean(text_length)) %>%
+  ungroup()
+
+ggsave(plot = {
+  btw %>%
+    ggplot(aes(as.numeric(text_length.cut),
+                       group = site)) +
+    geom_histogram(aes(y=..density..), alpha=.8, fill = col[3]) + 
+    scale_x_continuous(labels = c(seq(0,1500,500), ">2000")) +
+    facet_wrap(~site, ncol = 4) +
+    labs(x = "Word count", color = "") +
+    theme(axis.title = element_text(size = 8),
+          axis.text = element_text(size = 6))
+
+}, filename = "../figs/wordcount.png", width = 8, height = 4)
+```
+
+![Word Count](../figs/wordcount.png)
+
+## Wordclouds
+
+To summarise the content of the texts, wordclouds help to get a first impression, as they represent the number of words in a corpus.
+Intuitively the term frequency (tf) of a word is a measure of how important that word may be.
+The following word cloud is derived from the whole corpus.
+As can be seen, problems arise with high frequency words.
+For example "die", "der", and "in" are extremly common but unrelated to the quantity of interest.
+These terms, often called "stop words", are important to the grammatical structure of a text, but typically don't add any additional meaning and can therefore be neglected.
+We use a pre-defined stop word list from the Snowball stemmer project\footnote{http://svn.tartarus.org/snowball/trunk/website/algorithms/*/stop.txt} together with a customized list of stop-words that are redundant superfluous or distorting.
+We also remove punctuation character (e.g.
+., ,, !, ?, etc.) and all numbers from our corpus.
+
+### Unprocessed Text
+```{r message=FALSE, warning=FALSE}
+all.corpus <- corpus(btw$text)
+df.corpus <- dfm(all.corpus, removePunct = TRUE, removeSymbols = T)
+```
+
+```{r message=FALSE, warning=FALSE}
+png("../figs/wordcloud.png")
+textplot_wordcloud(df.corpus, max.word=300)
+dev.off()
+```
+![Wordcloud 1](../figs/wordcloud.png)
+
+### Processed Text
+
+After completing this steps we were left with 68.576 unique terms in our vocabulary.
+The following wordclouds is derived from the corpus for each news provider.
+It becomes evident that these are texts discussing domestic policy issues.
+The SPD in particular seems to be higly frequent.
+However, at first glance, there are no obvious differences between the corpus of the different news provider.
+
+```{r eval=FALSE, include=FALSE}
+wordclouds <- function(select_site) {
+  corp <- btw %>% filter(site %in% select_site)
+  corp <- corpus(corp$text_cleaned1)
+  corp <- dfm(corp)
+
+  textplot_wordcloud(corp, max.word=200)
+}
+```
+
+```{r eval=FALSE, include=FALSE}
+for (i in unique(btw$site)) {
+  png(paste0("../figs/wordcloud_",i,".png"))
+  wordclouds(i)
+  dev.off()
+}
+```
+
+<img src="../figs/wordcloud_Bild.de.png", width = "49%" title="Bild.de">
+<img src="../figs/wordcloud_DIE WELT.png", width = "49%" title="DIE WELT">
+<img src="../figs/wordcloud_FOCUS ONLINE.png", width = "49%" title="FOCUS ONLINE">
+<img src="../figs/wordcloud_SPIEGEL ONLINE.png", width = "49%" title="SPIEGEL ONLINE">
+<img src="../figs/wordcloud_stern.de.png", width = "49%" title="Stern.de">
+<img src="../figs/wordcloud_Tagesschau.de.png", width = "49%" title="Tagesschau.de">
+<img src="../figs/wordcloud_ZEIT ONLINE.png", width = "49%" title="ZEIT ONLINE">
 

### 2018-03-29 paper/writing/doc_backup.tex
add more description

@@
 
+% ----------------------
+% the online news market
+% ----------------------
+\section{The online news market}\label{ch_onlinenews}
+% Kapitel raus? Bzw. mit Kapitel 4 zusammenlegen.
+
+The market for media content in Germany is characterized by the coexistence of public and private broadcasters.
+By shifting media content to the Internet, the dual system, which has been shaping the German television and radio landscape since the introduction of private broadcasting in the early 1980s, is facing a radical change.
+Since 2000, public broadcasting has expanded its range of services, particularly in the digital media sector.
+In 2017, 22 own websites and 100 apps were operated by public broadcasters on which they offer their content.
+As a result, public broadcasting no longer only competes with private television and radio stations, but also enters the market for online news.
+In the following, the characteristics of the market for online news in Germany are briefly described.
+
+Private media outlets naturally appear as two-sided platforms, that allow interaction between two categories of consumers: audiences and advertisers.
+As the demand on both consumer-sides are linked via indirect network externalities, the market in which media outlets operate are referred to as two-sided or multi-sided markets.
+The theoretical literature on two-sided markets originates from the analysis of credit card markets \citep{rochet_platform_2003} and was later transferred to the concept of other industries, such as dating agencies, real estate agents, and internet “business-to-business” websites \citep{caillaud_chicken_2003}.
+The basic concept of two-sided markets was already discussed decades ago in several economic studies, especially on media markets \citep{corden_maximisation_1952}, \citep{gustafsson_circulation_1978}, \citep{blair_pricing_1993}.
+However, comprehensive analyses have only been carried out in the last ten years, starting with the works of \citet{rochet_platform_2003}, \citet{evans_empirical_2003} and \citet{armstrong_competition_2006}.
+
+Advertising-supported media such as online newspapers are typical examples of two-sided markets where the newspaper can be conceived as platforms that allow interaction between audiences ("eyeballs") and advertisers.
+The newspaper creates (or buys) content to attract viewers which in turn attract advertisers who pay for readers' attention \citep{evans_industrial_2005}.
+The size and characteristics of the audience has a positive effect on the advertisers' willingness to pay, as advertisements are typically sold based on cost per viewer, often expressed in terms of the cost of reaching a thousand viewers (CPM).
+Advertising can also have an effect on the recipients, which can be either negative or positive, depending on the quality of the advertising.
+Based on the strength of the indirect network effects, private publishers maximize their revenue by balancing the demand from advertisers and subscribers using different business models \citep{evans_economics_2008}.
+Many traditional newspapers follow the subscription/advertising model, where the publisher charges both market sides: The audience pays a fee to obtain access to the content, and advertisers pay to obtain access to the viewers.
+Many online news agencies provide part of their editorial content for free and hide another, more exclusive part behind a paywall.
+However, since the Internet has considerably simplified the possibilities for obtaining information and thus reduced the marginal utility of content, such a business model can only be efficient if the content behind the paywall is very exclusive.
+As a result, many publishers rely on a free-media model, in which the publishers do not charge viewers for access to the media at all, in order to attract as many eyeballs as possible to their platform, and thus, exploit the indirect network effects on the advertising site.
+In fact, most advertising-financed online magazines earn a large part of their gross margin from advertising \citep{evans_industrial_2005}.
+In order to maximize their profits, these companies have an interest in attracting as many readers as possible.
+In addition to the quantity of the audience, the demographic characteristics of recipients also have an influence on the willingness to pay on the advertiser site.
+
+The two-sided market structure of the private news market results in news platforms striving to choose their content in such a way that its reach is as large as possible in order to maximize profits from advertising revenues.
+\citet{steiner_program_1952} concluded, that profit-maximizing media owners may choose to offer the same content, i.e.
+content aligned with the tastes of the majority.
+\citet{gabszewicz_press_2001} study the problem of diversity of the political content of newspapers.
+They find that the maximum differentiation only prevails if the readers sufficiently value the political differentiation between the newspapers the advertising market is small enough.
+On the other hand, advertising may also have a positive impact on the media, as it enables publishers to report independently of political parties.
+\citet{ellman_what_2009} analyze a theoretical framework of a two-sided market for newspaper, where readers value accuracy and advertisers value advert-receptive readers.
+They found that advertising increases the intensity of competition for readers and therefore raises accuracy of media coverage.
+However, in the monopolistic case, newspapers under-report news that sufficiently reduces advertiser profits.
+
+Given the crucial role of the media in shaping opinion and promoting democracy, pluralism of opinion and accuracy of information is a major concern of public authorities.
+Public broadcasting in Germany originated in the post-war period and has always had the task of providing the entire population with independent media.
+This media offer is intended to guarantee diversity of opinion within the media landscape and to be economically and politically independent.
+The former is given by the fact that the public media are financed by compulsory fees.
+To take into account the distinct nature of digital media, the Interstate Broadcasting Agreement (Rundfunkstaatsvertrag) also regulates the scope for action of online services offered by public service broadcasting since 2007.
+Accordingly, public media are not allowed to distribute purchased content and must - depending on the category of content - set a time limit on its accessibility.
+In addition, there is a strict advertising ban and prohibition of regional reporting.
+
+The market for media content in Germany is characterized by the coexistence of public and private broadcasters.
+By shifting media content to the Internet, the dual system, which has been shaping the German television and radio landscape since the introduction of private broadcasting in the early 1980s, is facing a radical change.
+Since 2000, public broadcasting has expanded its range of services, particularly in the digital media sector.
+As a result, public broadcasting no longer only competes with private television and radio stations, but also enters the market for online news.
+
 \section{Generative Process}

### 2018-03-29 paper/writing/structure.tex
finish that writing
add more description

@@
 \section{Introduction}
+% Noch deutlicher beschreiben, was eigentlich gemacht wird. Besser motivieren
+% Paper von Ralf, Melissa, Tobias zitieren.
 
 Pluralism is an essential principle of democratic societies.
-An important pillar of this principle is an opinion-forming process that incorporates as many different perspectives as possible.
+An important pillar of this principle is an opinion-forming process that incorporates the different perspectives represented in the society.
 For the process of forming opinions, information conveyed by the media, in particular the mass media of journalism, plays a decisive role.
@@
 Securing the diversity of opinion-forming processes and preventing concentration processes in the media sector is an essential prerequisite for a functioning democracy.
+An important question is therefore whether the political reporting of different content providers distinguishes itself and whether this reporting has an influence on the opinion-forming process of the voters.
+The aim of this paper is to investigate these questions with the use of up-to-date text mining methods.
 
+A number of different factors have an influence on the diversity of media content.
+These include the market structure for journalistic content and the digitization of the industry.
 Media outlets (TV, Radio, Newspaper) usually operate in two-sided markets, where they serve two customer groups (content consumer and advertiser) that are connected via indirect network effects.
+The two-sided market structure of the private news market results in news platforms striving to choose their content in such a way that its reach is as large as possible in order to maximize profits from advertising revenues.
+\citet{steiner_program_1952} concluded, that profit-maximizing media owners may choose to offer the same content, i.e.
+content aligned with the tastes of the majority.
+\citet{gabszewicz_press_2001} study the problem of diversity of the political content of newspapers.
+They find that the maximum differentiation only prevails if the readers sufficiently value the political differentiation between the newspapers the advertising market is small enough.
+On the other hand, advertising may also have a positive impact on the media, as it enables publishers to report independently of political parties.
+\citet{ellman_what_2009} analyze a theoretical framework of a two-sided market for newspaper, where readers value accuracy and advertisers value advert-receptive readers.
+They found that advertising increases the intensity of competition for readers and therefore raises accuracy of media coverage.
+However, in the monopolistic case, newspapers under-report news that sufficiently reduces advertiser profits.
+
 The new developments in digital media provide new opportunities and challenges for media outlets.
@@
 Recognizing the importance of media pluralism, the European Commission has endorsed several initiatives to discuss and promote media diversity in the European Union\footnote{https://ec.europa.eu/digital-single-market/en/policies/media-freedom-and-pluralism}.
+One way to ensure the independence and diversity of the media landscape is through public funded media.
+In Germany public broadcasting originated in the post-war period and is financed by compulsory fees.
+To take into account the distinct nature of digital media, the Interstate Broadcasting Agreement (Rundfunkstaatsvertrag) also regulates the scope for action of online services offered by public service broadcasting since 2007.
+Accordingly, public media are not allowed to distribute purchased content and must - depending on the category of content - set a time limit on its accessibility.
+In addition, there is a strict advertising ban and prohibition of regional reporting.
 
-A resulting question is whether the political reporting of different content providers distinguishes itself and whether this reporting has an influence on the opinion-forming process of the voters.
-The aim of this paper is to investigate these questions with the use of up-to-date text mining methods.
-For this purpose, German online news articles about domestic politics are analyze to examine the media pluralism in the market for German-language online news.
+With the purpose of examining the media pluralism in the market for German-language online news, this paper analyzes German online news articles about domestic politics.
 German federal elections took place on 24th of September 2017 and the formation of the government has taken up a period of about five month.
@@
 
+% Der erste Absatz ist z.B. ziemlich knapp. Ebenso sind „Measuring Tone“ und „Comparing with polls“ sehr knapp im Vergleich zu „Dicovering topics“ beschrieben.
+
 \end{enumerate}
@@
 
-The remaining course of the paper is as follows: In Section \ref{ch_onlinenews} the characteristics of the market for online news in Germany are outlined.
-\ref{ch_elections} give a brief overview about political trends in Germany in recent month.
+The remaining course of the paper is as follows: The following Section \ref{ch_elections} gives an overview about political trends in the past six month (June 2017 to March 2018).
 The data used to conduct the model is described in Section \ref{ch_data}.
@@
 After the election, the formation of a government was difficult due to the large number of parties elected to the Bundestag and the considerable loss of votes by the major parties CDU/CSU and SPD.
-Since all parties rejected a merger with the AfD, numerically only two coalitions with an absolute parliamentary majority were possible: a grand coalition ("GroKo") of CDU/CSU and SPD, and a Jamaica coalition (coalition of CDU/CSU, FDP (economic liberal party) and B90/Die Grünen (Bündnis 90/Die Grünen, green party).
+Since all parties rejected a coalition with the AfD, numerically only two coalitions with an absolute parliamentary majority were possible: a grand coalition ("GroKo") of CDU/CSU and SPD, and a Jamaica coalition (coalition of CDU/CSU, FDP (economic liberal party) and B90/Die Grünen (Bündnis 90/Die Grünen, green party)).
 The grand coalition was initially rejected by the SPD.
@@
 
-% ----------------------
-% the online news market
-% ----------------------
-\section{The online news market}\label{ch_onlinenews}
-
-The market for media content in Germany is characterized by the coexistence of public and private broadcasters.
-By shifting media content to the Internet, the dual system, which has been shaping the German television and radio landscape since the introduction of private broadcasting in the early 1980s, is facing a radical change.
-Since 2000, public broadcasting has expanded its range of services, particularly in the digital media sector.
-In 2017, 22 own websites and 100 apps were operated by public broadcasters on which they offer their content.
-As a result, public broadcasting no longer only competes with private television and radio stations, but also enters the market for online news.
-In the following, the characteristics of the market for online news in Germany are briefly described.
-
-Private media outlets naturally appear as two-sided platforms, that allow interaction between two categories of consumers: audiences and advertisers.
-As the demand on both consumer-sides are linked via indirect network externalities, the market in which media outlets operate are referred to as two-sided or multi-sided markets.
-The theoretical literature on two-sided markets originates from the analysis of credit card markets \citep{rochet_platform_2003} and was later transferred to the concept of other industries, such as dating agencies, real estate agents, and internet “business-to-business” websites \citep{caillaud_chicken_2003}.
-The basic concept of two-sided markets was already discussed decades ago in several economic studies, especially on media markets \citep{corden_maximisation_1952}, \citep{gustafsson_circulation_1978}, \citep{blair_pricing_1993}.
-However, comprehensive analyses have only been carried out in the last ten years, starting with the works of \citet{rochet_platform_2003}, \citet{evans_empirical_2003} and \citet{armstrong_competition_2006}.
-
-Advertising-supported media such as online newspapers are typical examples of two-sided markets where the newspaper can be conceived as platforms that allow interaction between audiences ("eyeballs") and advertisers.
-The newspaper creates (or buys) content to attract viewers which in turn attract advertisers who pay for readers' attention \citep{evans_industrial_2005}.
-The size and characteristics of the audience has a positive effect on the advertisers' willingness to pay, as advertisements are typically sold based on cost per viewer, often expressed in terms of the cost of reaching a thousand viewers (CPM).
-Advertising can also have an effect on the recipients, which can be either negative or positive, depending on the quality of the advertising.
-Based on the strength of the indirect network effects, private publishers maximize their revenue by balancing the demand from advertisers and subscribers using different business models \citep{evans_economics_2008}.
-Many traditional newspapers follow the subscription/advertising model, where the publisher charges both market sides: The audience pays a fee to obtain access to the content, and advertisers pay to obtain access to the viewers.
-Many online news agencies provide part of their editorial content for free and hide another, more exclusive part behind a paywall.
-However, since the Internet has considerably simplified the possibilities for obtaining information and thus reduced the marginal utility of content, such a business model can only be efficient if the content behind the paywall is very exclusive.
-As a result, many publishers rely on a free-media model, in which the publishers do not charge viewers for access to the media at all, in order to attract as many eyeballs as possible to their platform, and thus, exploit the indirect network effects on the advertising site.
-In fact, most advertising-financed online magazines earn a large part of their gross margin from advertising \citep{evans_industrial_2005}.
-In order to maximize their profits, these companies have an interest in attracting as many readers as possible.
-In addition to the quantity of the audience, the demographic characteristics of recipients also have an influence on the willingness to pay on the advertiser site.
-
-The two-sided market structure of the private news market results in news platforms striving to choose their content in such a way that its reach is as large as possible in order to maximize profits from advertising revenues.
-\citet{steiner_program_1952} concluded, that profit-maximizing media owners may choose to offer the same content, i.e.
-content aligned with the tastes of the majority.
-\citet{gabszewicz_press_2001} study the problem of diversity of the political content of newspapers.
-They find that the maximum differentiation only prevails if the readers sufficiently value the political differentiation between the newspapers the advertising market is small enough.
-On the other hand, advertising may also have a positive impact on the media, as it enables publishers to report independently of political parties.
-\citet{ellman_what_2009} analyze a theoretical framework of a two-sided market for newspaper, where readers value accuracy and advertisers value advert-receptive readers.
-They found that advertising increases the intensity of competition for readers and therefore raises accuracy of media coverage.
-However, in the monopolistic case, newspapers under-report news that sufficiently reduces advertiser profits.
-
-Given the crucial role of the media in shaping opinion and promoting democracy, pluralism of opinion and accuracy of information is a major concern of public authorities.
-Public broadcasting in Germany originated in the post-war period and has always had the task of providing the entire population with independent media.
-This media offer is intended to guarantee diversity of opinion within the media landscape and to be economically and politically independent.
-The former is given by the fact that the public media are financed by compulsory fees.
-To take into account the distinct nature of digital media, the Interstate Broadcasting Agreement (Rundfunkstaatsvertrag) also regulates the scope for action of online services offered by public service broadcasting since 2007.
-Accordingly, public media are not allowed to distribute purchased content and must - depending on the category of content - set a time limit on its accessibility.
-In addition, there is a strict advertising ban and prohibition of regional reporting.
-
 % -----
@@
 \section{Dataset and data preparation}\label{ch_data}
+% Viel mehr Datenbeschreibung / deskriptive Statistik
+% Warum wurden grade diese Medien ausgesucht?
 
-Figure \ref{fig_reach} shows the largest providers of online news in terms of daily pageviews.\footnote{The figure shows the estimated percentage of daily pageviews on the internet that occurred on a specific website.} It is striking that SPIEGEL ONLINE has the greatest reach over the entire course of time followed by Bild.de.
-Public websites like Deutschlandfunk.de or Tagesschau.de have a rather small share in that market.
-
-\begin{figure}[H]
-	\caption{Percentage of daily pageviews}
-	\includegraphics[width=\textwidth]{../figs/reach.png}
-	\label{fig_reach}
-\end{figure}
-
-I conduct the estimation on a sample of 14,937 online news articles from seven news provider about domestic politics\footnote{Bild.de, DIE WELT, FOCUS ONLINE, SPIEGEL ONLINE, stern.de, ZEIT ONLINE, Tagesschau.de}, of which only Tagesschau.de belongs to the group of public provider.
-The reason for this is that the content structure of Tagesschau.de is most similar to that of the private providers.
-ZDF.de offers predominantly video content and DLF website mainly offers audio content in the form of interviews, which makes it hard to include it in the model.
+I conduct the estimation on a sample of 14,937 online news articles from seven german news provider about domestic politics\footnote{Bild.de, DIE WELT, FOCUS ONLINE, SPIEGEL ONLINE, stern.de, ZEIT ONLINE, Tagesschau.de}.
 The articles are dated from 01.06.2017 to 01.03.2018.
 I first extract all online articles using the the Webhose.io API.\footnote{For more information see https://docs.webhose.io/v1.0/docs/getting-started.
-The scraping code was written in Python and can be made available on request.} Then all articles from the section "domestic policy" are filtered by checking the URL structure.
-
-Figure \ref{fig_distr1} shows the distribution of the number of articles from the respective news sources by date. There is a high peak around the federal elections on September, 24th.
+The scraping code was written in Python and can be made available on request.} Then all articles from the section "domestic policy" are filtered by using the URL of an article.
+Figure \ref{fig_distr1} shows the distribution of the number of articles from the respective news sources by date.
+There is a high peak around the federal elections on September, 24th.
 
@@
 
+Overall, the selected news providers are among the top ten German online news providers in the period under review, with only Tagesschau.de belonging to the public media.
+The reason for this is that the content structure of Tagesschau.de is most similar to that of the private providers.
+ZDF.de offers predominantly video content and DLF website mainly offers audio content in the form of interviews, which makes it hard to include it in the model.
+
 % ------------------
@@
 % ------------------
+% Mehr beschreiben was hier gemacht wird. Was ist z.b. eine stop-word list?
+
 A central task in text mining is to extract low-dimensional information from documents that are high-dimensional by nature \citep{bholat_text_2015}.
 This is related to the task of reducing the number of unique language elements in order to reduce the dimensionality of data (to avoid unnecessary computational complexity and overfitting) while at the same time keeping those words that reflect the content of a document.
-Any useful representation of text will throw away some information, the trick is to include the relevant information for our needs, and exclude the extraneous information.
+Any useful representation of text will throw away some information, the trick is to include the relevant information that is needed, and exclude the extraneous information.
 A common strategy to use text as data and reduce the dimensionality, is to pre-process the text by imposing some preliminary restrictions (stop-word removal, tokenization) based on the nature of the data (twitter text, newspaper articles, speeches, etc.) to reduce the number of language elements \citep{gentzkow_text_2017}.
+
 Intuitively the term frequency (tf) of a word is a measure of how important that word may be.
@@
 \section{The structural topic model}\label{ch_model}
+% Kapitel mehr mit eigenen Worten beschreiben.
 
@@
 
-STM has been applied to multiple academic fields: \citet{roberts_structural_2014} uses STM to analyse open-ended responses from surveys and experiments, \citet{farrell_corporate_2016} applies the model to scientific texts on climate change, revealing links between corporate funding and the framing of scientific studies.
+STM has been applied to multiple academic fields: \citet{roberts_structural_2014} uses STM to analyze open-ended responses from surveys and experiments, \citet{farrell_corporate_2016} applies the model to scientific texts on climate change, revealing links between corporate funding and the framing of scientific studies.
 \citet{mishler_using_2015} show that "STM can be used to detect significant events such as the downing of Malaysia Air Flight 17" when applied to twitter data.
@@
 In other words, the corresponding newswire of an article influences the probability distribution of topics and how the topics are discussed.
-To address problems due to non-convexity, we rely on the spectral initialization approach advocated by \citet{roberts_navigating_2016}.
 
@@
 \section{Empirical Evaluation}\label{ch_empirical}
+% Besser strukturieren. Tabellen mit Ergebnissen zeigen (nicht nur Abbildungen).
 
@@
 
-We will select the following topics from the whole set (topics are ordered regarding their overall corpus frequency).
-The most frequent words of these topics can be seen in the appendix \ref{fig_plotquote}:
+We will select the following topics from the whole set (topics are ordered regarding their overall corpus frequency). The most frequent words of these topics can be seen in the appendix:
 
@@
 The stm-package provides a function that uses the method of composition to incorporate uncertainty in the dependent variable, drawing a set of topic proportions from the variational posterior repeated times and compute the coefficients as the average over all results \citep{roberts_stm:_2016}.
+% Letzten satz umschreiben! hört sich sonst so an als würde ich nicht wissen, was die macht. 
+% Formel erklären!
 
@@
 \citet{hansen_shocking_2016} use a similar approach to measure "the two Ts" (Topic and tone).
-They explore the effects of FOMC statements on both market and real economic variables.
+They explore the effects of FOMC (Federal Open Market Committee) statements on both market and real economic variables.
 To understand the multi-dimensional information a statement is transmitting, they apply LDA on a corpus of 142 FOMC decision statements split into sentences (topic).
@@
 \end{figure}
+% Anders darstellen. 
+% Eventuell auch Lags zeigen.
 
@@
 
+% 1, 2
 \begin{figure}[H]
-	\includegraphics[width=.49\textwidth]{../figs/plotquote1.png}
-	\caption{}
+	\begin{center}
+		\begin{subfigure}[normla]{0.49\textwidth}
+			\includegraphics[width=\textwidth]{../figs/plotquote1.png}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.49\textwidth}
+			\includegraphics[width=\textwidth]{../figs/plotquote2.png}
+		\end{subfigure}
+	\end{center}
 \end{figure}
 
+% 4, 10
 \begin{figure}[H]
-	\includegraphics[width=.49\textwidth]{../figs/plotquote2.png}
-	\caption{}
-\end{figure}
-	% 4
-\begin{figure}[H]
-	\includegraphics[width=.49\textwidth]{../figs/plotquote4.png}
-	\caption{}
+	\begin{center}
+		\begin{subfigure}[normla]{0.49\textwidth}
+			\includegraphics[width=\textwidth]{../figs/plotquote4.png}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.49\textwidth}
+			\includegraphics[width=\textwidth]{../figs/plotquote10.png}
+		\end{subfigure}
+	\end{center}
 \end{figure}
 
-	% 10
+% 13, 17
 \begin{figure}[H]
-	\includegraphics[width=.49\textwidth]{../figs/plotquote10.png}
-	\caption{}
+	\begin{center}
+		\begin{subfigure}[normla]{0.49\textwidth}
+			\includegraphics[width=\textwidth]{../figs/plotquote13.png}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.49\textwidth}
+			\includegraphics[width=\textwidth]{../figs/plotquote17.png}
+		\end{subfigure}
+	\end{center}
 \end{figure}
 
-	% 13
+% 20, 23
 \begin{figure}[H]
-	\includegraphics[width=.49\textwidth]{../figs/plotquote13.png}
-	\caption{}
-\end{figure}
-	% 17
-\begin{figure}[H]
-	\includegraphics[width=.49\textwidth]{../figs/plotquote17.png}
-	\caption{}
+	\begin{center}
+		\begin{subfigure}[normla]{0.49\textwidth}
+			\includegraphics[width=\textwidth]{../figs/plotquote20.png}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.49\textwidth}
+			\includegraphics[width=\textwidth]{../figs/plotquote23.png}
+		\end{subfigure}
+	\end{center}
 \end{figure}
 
-	% 20
+% 26, 27
 \begin{figure}[H]
-	\includegraphics[width=.49\textwidth]{../figs/plotquote20.png}
-	\caption{}
+	\begin{center}
+		\begin{subfigure}[normla]{0.49\textwidth}
+			\includegraphics[width=\textwidth]{../figs/plotquote26.png}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.49\textwidth}
+			\includegraphics[width=\textwidth]{../figs/plotquote27.png}
+		\end{subfigure}
+	\end{center}
 \end{figure}
-	% 23
+
+% 30, 32
 \begin{figure}[H]
-	\includegraphics[width=.49\textwidth]{../figs/plotquote23.png}
-	\caption{}
+	\begin{center}
+		\begin{subfigure}[normla]{0.49\textwidth}
+			\includegraphics[width=\textwidth]{../figs/plotquote30.png}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.49\textwidth}
+			\includegraphics[width=\textwidth]{../figs/plotquote32.png}
+		\end{subfigure}
+	\end{center}
 \end{figure}
-	% 26
+
+% 37, 46
 \begin{figure}[H]
-	\includegraphics[width=.49\textwidth]{../figs/plotquote26.png}
-	\caption{}
-\end{figure}
-	% 27
-\begin{figure}[H]
-	\includegraphics[width=.49\textwidth]{../figs/plotquote27.png}
-	\caption{}
-\end{figure}
-	% 30
-\begin{figure}[H]
-	\includegraphics[width=.49\textwidth]{../figs/plotquote30.png}
-	\caption{}
-\end{figure}
-	% 32
-\begin{figure}[H]
-	\includegraphics[width=.49\textwidth]{../figs/plotquote32.png}
-	\caption{}
-\end{figure}
-	% 37
-\begin{figure}[H]
-	\includegraphics[width=.49\textwidth]{../figs/plotquote37.png}
-	\caption{}
-\end{figure}
-	% 46
-\begin{figure}[H]
-	\includegraphics[width=.49\textwidth]{../figs/plotquote46.png}
-	\caption{}
+	\begin{center}
+		\begin{subfigure}[normla]{0.49\textwidth}
+			\includegraphics[width=\textwidth]{../figs/plotquote37.png}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.49\textwidth}
+			\includegraphics[width=\textwidth]{../figs/plotquote46.png}
+		\end{subfigure}
+	\end{center}
 \end{figure}

### 2018-03-31 paper/docs/04_Modelresults_50.Rmd
add wordclouds

@@
 
-The Figures below show the distribution of the number of articles from the respective news sources by date. There is a high peak around the federal elections on September, 24th.
+The Figures below show the distribution of the number of articles from the respective news sources by date.
+There is a high peak around the federal elections on September, 24th and another one shortly after the failure of the Jamaica coalition talks on November, 19th (indicated by the red dotted lines).
+The Figure on the right shows, that DIE WELT published most articles on domestic policy, followed by stern.de and FOCUS ONLINE.
 
@@
   geom_vline(aes(xintercept=as.Date("2017-09-24")),
+             linetype = 2, color=col[5]) +
+  geom_vline(aes(xintercept=as.Date("2017-11-19")),
              linetype = 2, color=col[5]) +
@@
 
+Most of the articles have a word length between 200 and 1000 words (articles with less than 200 words were filtered out in advance, as these are mostly reader comments).
+The distribution at Bild.de, DIE WELT, FOCUS ONLINE and stern.de is left-skewed, whereby stern.de has comparatively many articles with a word length of over 2000.
+
+The longest article at Tagesschau.de has 2006 words, nevertheless the median value is comparatively large (see the Table below). ZEIT ONLINE has the highest median value of 459 words.
+
 ```{r}
@@
                        group = site)) +
-    geom_histogram(aes(y=..density..), alpha=.8, fill = col[3]) + 
+    geom_histogram(alpha=.8, fill = col[3]) + 
     scale_x_continuous(labels = c(seq(0,1500,500), ">2000")) +
@@
 As can be seen, problems arise with high frequency words.
-For example "die", "der", and "in" are extremly common but unrelated to the quantity of interest.
+For example "die", "der", and "in" are extremely common but unrelated to the quantity of interest.
 These terms, often called "stop words", are important to the grammatical structure of a text, but typically don't add any additional meaning and can therefore be neglected.
-We use a pre-defined stop word list from the Snowball stemmer project\footnote{http://svn.tartarus.org/snowball/trunk/website/algorithms/*/stop.txt} together with a customized list of stop-words that are redundant superfluous or distorting.
+We use a pre-defined stop word list from the Snowball stemmer project\footnote{http://svn.tartarus.org/snowball/trunk/website/algorithms/*/stop.txt} together with a customized list of stop-words that are redundant or distorting.
 We also remove punctuation character (e.g.
@@
 After completing this steps we were left with 68.576 unique terms in our vocabulary.
-The following wordclouds is derived from the corpus for each news provider.
+The following wordclouds are derived from the corpus for each news provider.
 It becomes evident that these are texts discussing domestic policy issues.

### 2018-03-31 paper/writing/structure.tex
add wordclouds

@@
 \usepackage{pdflscape}
+\usepackage{geometry}
+\geometry{a4paper,left=40mm,right=30mm, top=1cm, bottom=2cm}
 
@@
 The scraping code was written in Python and can be made available on request.} Then all articles from the section "domestic policy" are filtered by using the URL of an article.
+Overall, the selected news providers are among the top ten German online news providers - in terms of unique user\footnote{The term unique user refers to a number of different visitors to a website within a certain period of time.
+Multiple visits from the same user are only considered once.} - in the period under review, with only Tagesschau.de belonging to the public media.
+The reason for this is that the content structure of Tagesschau.de is most similar to that of the private providers.
+ZDF.de offers predominantly video content and DLF (Deutschlandfunk) website mainly offers audio content in the form of interviews, which makes it hard to include it in the model.
+
  Figure \ref{fig_distr1} shows the distribution of the number of articles from the respective news sources by date.
-There is a high peak around the federal elections on September, 24th.
+There is a high peak around the federal elections on September, 24th and another one shortly after the failure of the Jamaica coalition talks on November, 19th (indicated by the red dotted lines).
+Figure \ref{fig_distr2} shows, that DIE WELT published most articles on domestic policy, followed by stern.de and FOCUS ONLINE.
 
@@
 
-Overall, the selected news providers are among the top ten German online news providers in the period under review, with only Tagesschau.de belonging to the public media.
-The reason for this is that the content structure of Tagesschau.de is most similar to that of the private providers.
-ZDF.de offers predominantly video content and DLF website mainly offers audio content in the form of interviews, which makes it hard to include it in the model.
+Looking at the histograms of the word counts (Figure \ref{fig_wordcount}), it becomes evident that most of the articles have a word length between 200 and 1000 words (articles with less than 200 words were filtered out in advance, as these are mostly reader comments).
+The distribution at Bild.de, DIE WELT, FOCUS ONLINE and stern.de is left-skewed, whereby stern.de has comparatively many articles with a word length of over 2000.
 
-% ------------------
-% Text Pre-Procesing
-% ------------------
-% Mehr beschreiben was hier gemacht wird. Was ist z.b. eine stop-word list?
+\begin{figure}[H]
+	\caption{Word Count}
+	\begin{center}
+		\includegraphics[width=\textwidth]{../figs/wordcount.png}
+		\caption{Word counts}
+		\label{fig_wordcount}
+	\end{center}
+\end{figure}
 
-A central task in text mining is to extract low-dimensional information from documents that are high-dimensional by nature \citep{bholat_text_2015}.
-This is related to the task of reducing the number of unique language elements in order to reduce the dimensionality of data (to avoid unnecessary computational complexity and overfitting) while at the same time keeping those words that reflect the content of a document.
-Any useful representation of text will throw away some information, the trick is to include the relevant information that is needed, and exclude the extraneous information.
-A common strategy to use text as data and reduce the dimensionality, is to pre-process the text by imposing some preliminary restrictions (stop-word removal, tokenization) based on the nature of the data (twitter text, newspaper articles, speeches, etc.) to reduce the number of language elements \citep{gentzkow_text_2017}.
+The longest article at Tagesschau.de has 2006 words, nevertheless the median value is comparatively large (see the Table below). ZEIT ONLINE has the highest median value of 459 words.
 
+\include{tables/wordcount}
+
+To summarize the content of the texts, wordclouds help to get a first impression, as the frequency of words in a corpus are represented by their size.
 Intuitively the term frequency (tf) of a word is a measure of how important that word may be.
-There are words in a document, however, that occur many times but may not be important like articles, conjunctions, and so on.
+The word cloud in Figure \ref{fig_wordcloud1} is derived from all articles within the dataset.
+As can be seen, problems arise with words that are highly frequent.
+For example "die", "der", and "in" are extremely common but unrelated to the quantity of interest.
 These terms, often called "stop words", are important to the grammatical structure of a text, but typically don't add any additional meaning and can therefore be neglected.
-We use a pre-defined stop word list from the Snowball stemmer project\footnote{http://svn.tartarus.org/snowball/trunk/website/algorithms/*/stop.txt} together with a customized list of stop-words that are redundant superfluous or distorting.
-We also remove punctuation character (e.g.
-., ,, !, ?, etc.) and all numbers from our corpus.
+A common strategy to reduce the number of language elements is to pre-process the text by imposing some preliminary restrictions (stop-word removal and stemming) based on the nature of the data (twitter text, newspaper articles, speeches, etc.) \citep{gentzkow_text_2017}.
+In fact, to use text as data and reduce the dimensionality to avoid unnecessary computational complexity and overfitting, pre-processsing the text is a central task in text mining \citep{bholat_text_2015}.
+
+\begin{figure}[H]
+	\begin{center}
+		\includegraphics[width=\textwidth]{../figs/wordcloud.png}
+		\caption{Word Cloud (whole corpus)}
+		\label{fig_wordcloud1}
+	\end{center}
+\end{figure}
+
+Stemming is a process by which different morphological variants of a word are traced back to their common root.
+For example, ‘voting’ and ‘vote’ would be treated as two instances of the same token after the stemming process.
+There are many different techniques for the stemming process.
+I use the widely used Porter-Stemmer algorithm, which is based on a set of shortening rules that are applied to a word until it has a minimum number of syllables.\footnote{https://tartarus.org/martin/PorterStemmer/} To remove distorting words, the pre-defined stop word list from the Snowball project\footnote{http://snowball.tartarus.org/algorithms/german/stop.txt} together with a customized list of stop-words is used.
+Additionally punctuation character (e.g.
+., ,, !, ?, etc.) and all numbers are removed from our corpus.
 After completing this steps we were left with 68.576 unique terms in our vocabulary.
+The following wordclouds are derived from the corpus for each news provider.
+It becomes evident that these are texts discussing domestic policy issues.
+The SPD in particular seems to be highly frequent.
+However, at first glance, there are no obvious differences between the corpus of the different news provider.
 
-After pre-processing, each document $d$ is a finite list of terms.
-Each unique term in the corpus is indexed by some $v \in \lbrace 1,...,V \rbrace$ where $V$ is the number of unique terms.
-For each document $d \in \lbrace 1,...,D \rbrace$ we compute the number of occurrences of term $v$ in document $d$ to obtain the count $x_{d,v}$.
-The $D$ x $V$ matrix $\boldsymbol{X}$ of all such counts is called the document-term matrix.
-This representation is often referred to as the bag of words model, since the order in which words are used within a document is completely disregarded.
+\begin{figure}[H]
+	\caption{Word Clouds}
+	\begin{center}
+		\begin{subfigure}[normla]{0.3\textwidth}
+			\includegraphics[width=\textwidth]{../figs/wordcloud_Bild.png}
+			\caption{Bild.de}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.3\textwidth}
+			\includegraphics[width=\textwidth]{../figs/wordcloud_DIEWELT.png}
+			\caption{DIE WELT}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.3\textwidth}
+			\includegraphics[width=\textwidth]{../figs/wordcloud_FOCUSONLINE.png}
+			\caption{FOCUS ONLINE}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.3\textwidth}
+			\includegraphics[width=\textwidth]{../figs/wordcloud_SPIEGELONLINE.png}
+			\caption{SPIEGEL ONLINE}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.3\textwidth}
+			\includegraphics[width=\textwidth]{../figs/wordcloud_stern.png}
+			\caption{Stern.de}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.3\textwidth}
+			\includegraphics[width=\textwidth]{../figs/wordcloud_Tagesschau.png}
+			\caption{Tagesschau.de}
+		\end{subfigure}
+		\begin{subfigure}[normla]{0.3\textwidth}
+			\includegraphics[width=\textwidth]{../figs/wordcloud_ZEITONLINE.png}
+			\caption{ZEIT ONLINE}
+		\end{subfigure}
+	\end{center}
+\end{figure}
 
+% --------------------
+% Document-term-matrix
+% --------------------
+To use the data for statistical analysis, the next step is to divide the whole corpus into individual documents and to represent these documents as a finite list of unique terms.
+In this setting, each news article represents a document $d$, whereby each of these documents can be assigned to a news website.
+Next, for each document $d \in \lbrace 1,...,D \rbrace$ the number of occurrences of term $v$ in document $d$ is computed, to obtain the count $x_{d,v}$.\footnote{Each unique term in the corpus is indexed by some $v \in \lbrace 1,...,V \rbrace$ where $V$ is the number of unique terms.} The $D$ x $V$ matrix $\boldsymbol{X}$ of all such counts is called the document-term matrix.
+This representation is often referred to as the bag of words model, since the order in which words are used within a document is disregarded.
+The sum of all documents forms what is called the corpus.
 % ----------------------
@@
 
-The structural topic model (STM) developed by \citet{roberts_model_2016} allows to incorporate document specific covariates (e.g.
-the author or date of a document).
-STM is a recent extension of the standard topic modeling technique, labeled as "latent Dirichlet allocation" (LDA), which refers to the Bayesian model in \citet{blei_latent_2003} that treats each word in a topic and each topic in a document as generated from a Dirichlet - distributed prior.\footnote{See also \citet{griffiths_probabilistic_2002}, \citet{griffiths_finding_2004} and \citet{hofmann_probabilistic_1999}.
-\citet{pritchard_inference_2000} introduced the same model in genetics for factorizing gene expression as a function of latent populations.} Topic models formalize the idea that documents are formed by hidden variables (topics) that generate correlations among observed terms.
-Since its introduction into text analysis, LDA has become hugely popular and especially useful in political science.\footnote{see \citet{blei_probabilistic_2012}, \citet{grimmer_text_2013} and \citet{wiedmann_text_2016} for an overview in social science and \citet{gentzkow_text_2017} give an overview of text mining applications in economics.} \citet{wiedmann_text_2016} uses topic model methods on large amounts of news articles from two german newspapers published between 1959 and 2011, to reveal how democratic demarcation was performed in Germany over the past six decades.
+To find out the latent structure of each document, a Structural topic model (STM) is estimated.
+In general, topic models formalize the idea that documents are formed by hidden variables (topics) that generate correlations among observed terms.
+They belong to the group of unsupervised generative models, meaning that the true attributes (topics) cannot be observed.
+One crucial assumption to be made for such models is the number of topics that occur over the entire corpus ($K$).
+Each individual topic potentially contains all of the unique terms within the vocabulary $V$ with different probability.
+Therefore, each topic $k$ can be represented as a probability vector $\beta_k$ over all unique terms $V$.
+Simultaneously, each individual document $d$ in the corpus can be represented as a probability distribution $\theta_d$ over the $K$ topics.
+To generate each individual word $w_{d,n}$ in a document $d$ for the $n^{th}$ word-position, (1) a topic allocation $z_{d,n}$ is drawn from the topic distribution for that document $\theta_d$.
+(2) Then, a word is drawn from the term distribution for the selected topic $\beta_{z_{d,n}}$.
+
+The STM developed by \citet{roberts_model_2016} is a recent extension of the standard topic modeling technique, labeled as "latent Dirichlet allocation" (LDA), which refers to the Bayesian model in \citet{blei_latent_2003} that treats each word in a topic and each topic in a document as generated from a Dirichlet - distributed prior.\footnote{See also \citet{griffiths_probabilistic_2002}, \citet{griffiths_finding_2004} and \citet{hofmann_probabilistic_1999}.
+\citet{pritchard_inference_2000} introduced the same model in genetics for factorizing gene expression as a function of latent populations.} Since its introduction into text analysis, LDA has become hugely popular and especially useful in political science.\footnote{see \citet{blei_probabilistic_2012}, \citet{grimmer_text_2013} and \citet{wiedmann_text_2016} for an overview in social science and \citet{gentzkow_text_2017} give an overview of text mining applications in economics.} \citet{wiedmann_text_2016} uses topic model methods on large amounts of news articles from two german newspapers published between 1959 and 2011, to reveal how democratic demarcation was performed in Germany over the past six decades.
 \citet{paul_cross-collection_2017} compares editorial differences between media sources, using cross-collection latent Dirichlet allocation (ccLDA), an LDA-based approach that incorporates differences in document metadata.
@@
 
-STM has been applied to multiple academic fields: \citet{roberts_structural_2014} uses STM to analyze open-ended responses from surveys and experiments, \citet{farrell_corporate_2016} applies the model to scientific texts on climate change, revealing links between corporate funding and the framing of scientific studies.
+The STM allows to incorporate document specific covariates (e.g.
+the author or date of a document).
+The model has been applied to multiple academic fields: \citet{roberts_structural_2014} uses STM to analyze open-ended responses from surveys and experiments, \citet{farrell_corporate_2016} applies the model to scientific texts on climate change, revealing links between corporate funding and the framing of scientific studies.
 \citet{mishler_using_2015} show that "STM can be used to detect significant events such as the downing of Malaysia Air Flight 17" when applied to twitter data.
@@
  As mentioned above, the STM allows to incorporate observed document metadata which is able to affect both topical prevalence and topical content.
-The following description of the generative model - the process of filling a word-position in a document - of the STM is based on \citet{roberts_structural_2013} and \citet{roberts_stm:_2016}.
-For each document $d$ and a given number of topics $K$, a document-specific topic-prevalence vector $d(\boldsymbol{\theta}_d)$ is drawn from a logistic-normal distribution, where the parameters are a function of the covariate values:
+These assumptions are reflected in the prior distributions.
+The following describes the generative process for filling the $n^{th}$ word-position in document $d$ in the case of the STM \citep{roberts_structural_2013}: As in the case of conventional models, (1) a specific topic $z_{dn}$ is assigned, according to the topic distribution for that document $\theta$ through the process:
 
 \begin{equation}
-	\boldsymbol{\theta}_d|\boldsymbol{x}_{d\gamma},\boldsymbol{\Sigma} \sim \textrm{LogisticNormal}(\mu = \boldsymbol{x}_{d\gamma}\boldsymbol{\Sigma}).
+	z_{dn}|\theta_d \sim \textrm{Multinomial}(\theta_d).
 \end{equation}
 
-$\boldsymbol{x}_d\gamma$ lists the values of all metadata covariates for document $d$, where $\gamma$ relates these covariate values to the topic-prevalence.
-The structure of $\boldsymbol{\Sigma}$ implies the possibility of correlations across documents in the topic-prevalence vector.
-
-According to $\theta$, a specific topic $z_{dn}$ is assigned for the $n^{th}$ word-position in the document through the process:
+To incorporate the covariate values for that document, a topic-prevalence vector $\theta_d$ is drawn from a logistic-normal distribution:
 
 \begin{equation}
-	z_{dn}|\boldsymbol{\theta}_d \sim \textrm{Multinomial}(\boldsymbol{\theta}_d).
+	\theta_d|x_{d\gamma},\Sigma \sim \textrm{LogisticNormal}(\mu = x_{d\gamma}\Sigma),
 \end{equation}
 
-Conditional in the topic chosen, a specific word, $w_{dn}$, is chosen from the overall corpus vocabulary $V$, using the following process:
+where $x_d\gamma$ lists the values of all metadata covariates for document $d$, where $\gamma$ relates these covariate values to the topic-prevalence.
+The structure of $\Sigma$ implies the possibility of correlations across documents in the topic-prevalence vector.
+
+Then again, (2) conditional in the topic chosen ($z_{dn}$), a specific word $w_{dn}$, is chosen from the overall corpus vocabulary $V$, using the following process:
 
@@
 
-where the word probability $\beta_{dkv}$ is parameterized in terms of log-transformed rate deviations from the rates of a corpus-wide background distribution $m_v$.
+where the word probability $\beta_{dkv}$ is parameterized in terms of log-transformed rate deviations from the rates of a corpus-wide background distribution $m_v$ \citep{roberts_structural_2013}.
 The log-transformed rate deviations can then be specified by a collection of parameters $\lbrace \boldsymbol{\kappa} \rbrace$, where $\kappa^{(t)}$ is a $K$-by-$V$ matrix containing the log-transformed rate deviations for each topic $k$ and term $v$, over the baseline log-transformed rate for term $v$.
@@
 The STM maximizes the posterior likelihood that the observed data were generated by the above data-generating process using an iterative approximation-based variational expectation-maximization algorithm\footnote{A technical description of this maximization process can be found in \citet{roberts_model_2016}} available in R's stm package \citep{roberts_stm:_2016}.
-The process gives us two posterior distribution parameter: (1) $\beta$ is a $K$-by-$V$ matrix (where $K=$ number of topics and $V=$ vocabulary), where the entry $\beta_{kvc}$ can be interpreted as the probability of observing the $v$-th word in topic $k$ for the covariate level $c$.
+
+This process generates two posterior distribution parameter: (1) $\beta$ is a $K$-by-$V$ matrix (where $K=$ number of topics and $V=$ vocabulary), where the entry $\beta_{kvc}$ can be interpreted as the probability of observing the $v$-th word in topic $k$ for the covariate level $c$.
 (2) $\theta$ is a $D$-by-$V$ matrix of the document-topic distributions, where the entry $\theta_{dk}$ can be interpreted as the proportion of words in document $d$ which arise from topic $k$, or rather as the probability that document $d$ deals about topic $k$.
-These probability distributions are used to compare the content of public and private news providers in section \ref{ch_empirical}.
+These probability distributions are used to compare the content of the different news provider in section \ref{ch_empirical}.
 
@@
 Inference of mixed-membership models, such as the one applied in this paper, has been a thread of research in applied statistics in the past few years \citep{blei_latent_2003} \citep{erosheva_mixed-membership_2004} \citep{braun_variational_2010}.
-Topic models are usually imprecise as the function to be optimized has multiple modes, such that the model results can be sensitive to the starting values.
+Topic models are usually imprecise as the function to be optimized has multiple modes, such that the model results can be sensitive to the starting values (e.g.
+the number of topics).
 Since an ex ante valuation of a model is hardly possible, I compute a variety of different models and compare their posterior probability.

### 2018-04-05 paper/writing/structure.tex
add more feedback

@@
 \usepackage{geometry}
-\geometry{a4paper,left=40mm,right=30mm, top=1cm, bottom=2cm}
+\geometry{a4paper,left=40mm,right=30mm, top=2cm, bottom=2cm}
 
@@
 After the election, the formation of a government was difficult due to the large number of parties elected to the Bundestag and the considerable loss of votes by the major parties CDU/CSU and SPD.
-Since all parties rejected a coalition with the AfD, numerically only two coalitions with an absolute parliamentary majority were possible: a grand coalition ("GroKo") of CDU/CSU and SPD, and a Jamaica coalition (coalition of CDU/CSU, FDP (economic liberal party) and B90/Die Grünen (Bündnis 90/Die Grünen, green party)).
+Since all parties rejected a coalition with the AfD, numerically only two coalitions with an absolute parliamentary majority were possible: a grand coalition ("GroKo" - from the German word Große Koalition) of CDU/CSU and SPD, and a Jamaica coalition (coalition of CDU/CSU, FDP (economic liberal party) and B90/Die Grünen (Bündnis 90/Die Grünen, green party)).
 The grand coalition was initially rejected by the SPD.
@@
 
- Figure \ref{fig_distr1} shows the distribution of the number of articles from the respective news sources by date.
+ Figure \ref{fig_distr1} shows the distribution of the number of articles by date.
 There is a high peak around the federal elections on September, 24th and another one shortly after the failure of the Jamaica coalition talks on November, 19th (indicated by the red dotted lines).
@@
 		\includegraphics[width=\textwidth]{../figs/wordcount.png}
-		\caption{Word counts}
 		\label{fig_wordcount}
@@
 
-The longest article at Tagesschau.de has 2006 words, nevertheless the median value is comparatively large (see the Table below). ZEIT ONLINE has the highest median value of 459 words.
+The longest article at Tagesschau.de has 2006 words, nevertheless the median value is comparatively large (see Table \label{t_wordcloud}). ZEIT ONLINE has the highest median value of 459 words.
 
-\include{tables/wordcount}
+\input{tables/wordcount}
 
@@
 As can be seen, problems arise with words that are highly frequent.
-For example "die", "der", and "in" are extremely common but unrelated to the quantity of interest.
+For example "die" ("the"), "und" ("and"), and "in" ("in") are extremely common but unrelated to the quantity of interest.
 These terms, often called "stop words", are important to the grammatical structure of a text, but typically don't add any additional meaning and can therefore be neglected.
@@
 	\begin{center}
-		\includegraphics[width=\textwidth]{../figs/wordcloud.png}
+		\includegraphics[width=0.7\textwidth]{../figs/wordcloud.png}
 		\caption{Word Cloud (whole corpus)}
@@
 Stemming is a process by which different morphological variants of a word are traced back to their common root.
-For example, ‘voting’ and ‘vote’ would be treated as two instances of the same token after the stemming process.
+For example, "voting" and "vote" would be treated as two instances of the same token after the stemming process.
 There are many different techniques for the stemming process.
-I use the widely used Porter-Stemmer algorithm, which is based on a set of shortening rules that are applied to a word until it has a minimum number of syllables.\footnote{https://tartarus.org/martin/PorterStemmer/} To remove distorting words, the pre-defined stop word list from the Snowball project\footnote{http://snowball.tartarus.org/algorithms/german/stop.txt} together with a customized list of stop-words is used.
+I apply the widely used Porter-Stemmer algorithm, which is based on a set of shortening rules that are applied to a word until it has a minimum number of syllables.\footnote{https://tartarus.org/martin/PorterStemmer/} To remove distorting words, the pre-defined stop word list from the Snowball project\footnote{http://snowball.tartarus.org/algorithms/german/stop.txt} together with a customized list of stop-words is used.
 Additionally punctuation character (e.g.
@@
 However, at first glance, there are no obvious differences between the corpus of the different news provider.
+
+% --------------------
+% Document-term-matrix
+% --------------------
+To use the data for statistical analysis, the next step is to divide the whole corpus into individual documents and to represent these documents as a finite list of unique terms.
+In this setting, each news article represents a document $d$, whereby each of these documents can be assigned to a news website.
+Next, for each document $d \in \lbrace 1,...,D \rbrace$ the number of occurrences of term $v$ in document $d$ is computed, to obtain the count $x_{d,v}$, where each unique term in the corpus is indexed by some $v \in \lbrace 1,...,V \rbrace$ where $V$ is the number of unique terms.
+The $D$ x $V$ matrix $\boldsymbol{X}$ of all such counts is called the document-term matrix.
+This representation is often referred to as the bag of words model, since the order in which words are used within a document is disregarded.
+The sum of all documents forms what is called the corpus.
 
@@
 
-% --------------------
-% Document-term-matrix
-% --------------------
-To use the data for statistical analysis, the next step is to divide the whole corpus into individual documents and to represent these documents as a finite list of unique terms.
-In this setting, each news article represents a document $d$, whereby each of these documents can be assigned to a news website.
-Next, for each document $d \in \lbrace 1,...,D \rbrace$ the number of occurrences of term $v$ in document $d$ is computed, to obtain the count $x_{d,v}$.\footnote{Each unique term in the corpus is indexed by some $v \in \lbrace 1,...,V \rbrace$ where $V$ is the number of unique terms.} The $D$ x $V$ matrix $\boldsymbol{X}$ of all such counts is called the document-term matrix.
-This representation is often referred to as the bag of words model, since the order in which words are used within a document is disregarded.
-The sum of all documents forms what is called the corpus.
 % ----------------------
@@
 One crucial assumption to be made for such models is the number of topics that occur over the entire corpus ($K$).
+
 Each individual topic potentially contains all of the unique terms within the vocabulary $V$ with different probability.
-Therefore, each topic $k$ can be represented as a probability vector $\beta_k$ over all unique terms $V$.
+Therefore, each topic $k$ can be represented as a probability vector $\phi_k$ over all unique terms $V$.
 Simultaneously, each individual document $d$ in the corpus can be represented as a probability distribution $\theta_d$ over the $K$ topics.
-To generate each individual word $w_{d,n}$ in a document $d$ for the $n^{th}$ word-position, (1) a topic allocation $z_{d,n}$ is drawn from the topic distribution for that document $\theta_d$.
-(2) Then, a word is drawn from the term distribution for the selected topic $\beta_{z_{d,n}}$.
+To generate each individual word $w_{d,n}$ in a document $d$ for the $n^{th}$ word-position, a topic allocation $z_{d,n}$ is drawn from the topic distribution for that document $\theta_d$.
+Then, a word is drawn from the term distribution for the selected topic $\phi_{z_{d,n}}$.
 
@@
 They use a dataset of 623 news articles from August 2008 from two American media outlets - msnbc.com and foxnews.com - to compare how they discuss topics.
-Reviewing the top words of the word-topic distribution, they find some content differences between the two.
+Reviewing the top words of the word-topic distribution, they find some content differences between the two media sources under review.
 
@@
 This approach is similar to \citet{roberts_model_2016}.
-They also use different measures of distance between the topic-word distributions of the same topic within different models.
 
@@
 These assumptions are reflected in the prior distributions.
-The following describes the generative process for filling the $n^{th}$ word-position in document $d$ in the case of the STM \citep{roberts_structural_2013}: As in the case of conventional models, (1) a specific topic $z_{dn}$ is assigned, according to the topic distribution for that document $\theta$ through the process:
+The following describes the generative process for filling the $n^{th}$ word-position in document $d$ in the case of the STM \citep{roberts_structural_2013}: As in the case of conventional models, first a specific topic $z_{dn}$ is assigned, according to the topic distribution for that document $\theta$ through the process:
 
@@
 \begin{equation}
-	\theta_d|x_{d\gamma},\Sigma \sim \textrm{LogisticNormal}(\mu = x_{d\gamma}\Sigma),
+	\theta_d|y_{d\gamma},\Sigma \sim \textrm{LogisticNormal}(\mu = y_{d\gamma}\Sigma),
 \end{equation}
 
-where $x_d\gamma$ lists the values of all metadata covariates for document $d$, where $\gamma$ relates these covariate values to the topic-prevalence.
+where $y_d\gamma$ lists the values of all metadata covariates for document $d$, where $\gamma$ relates these covariate values to the topic-prevalence.
 The structure of $\Sigma$ implies the possibility of correlations across documents in the topic-prevalence vector.
 
-Then again, (2) conditional in the topic chosen ($z_{dn}$), a specific word $w_{dn}$, is chosen from the overall corpus vocabulary $V$, using the following process:
+Conditional in the topic chosen ($z_{dn}$), a specific word $w_{dn}$, is chosen from the overall corpus vocabulary $V$, using the following process:
 
 \begin{equation}
-	w_{dn}|z_{dn},\beta_{dkv} \sim \textrm{Multinomial}(\beta_{dk1},...,\beta_{dkV}),
+	w_{dn}|z_{dn},\phi_{dkv} \sim \textrm{Multinomial}(\phi_{dk1},...,\phi_{dkV}),
 \end{equation}
 
-where the word probability $\beta_{dkv}$ is parameterized in terms of log-transformed rate deviations from the rates of a corpus-wide background distribution $m_v$ \citep{roberts_structural_2013}.
+where the word probability $\phi_{dkv}$ is parameterized in terms of log-transformed rate deviations from the rates of a corpus-wide background distribution $m_v$ \citep{roberts_structural_2013}.
 The log-transformed rate deviations can then be specified by a collection of parameters $\lbrace \boldsymbol{\kappa} \rbrace$, where $\kappa^{(t)}$ is a $K$-by-$V$ matrix containing the log-transformed rate deviations for each topic $k$ and term $v$, over the baseline log-transformed rate for term $v$.
@@
 \begin{equation}
-	\beta_{dkv}|z_{dn}=\frac{\textrm{exp}(m_v+\kappa^{(t)}_{kv},\kappa^{(c)}_{y_dv}+\kappa^{(i)}_{y_dkv})}{\sum_v \textrm{exp}(m_v+\kappa^{(t)}_{kv},\kappa^{(c)}_{y_dv}+\kappa^{(i)}_{y_dkv})}.
+	\phi_{dkv}|z_{dn}=\frac{\textrm{exp}(m_v+\kappa^{(t)}_{kv},\kappa^{(c)}_{y_dv}+\kappa^{(i)}_{y_dkv})}{\sum_v \textrm{exp}(m_v+\kappa^{(t)}_{kv},\kappa^{(c)}_{y_dv}+\kappa^{(i)}_{y_dkv})}.
 \end{equation}
@@
 
-This process generates two posterior distribution parameter: (1) $\beta$ is a $K$-by-$V$ matrix (where $K=$ number of topics and $V=$ vocabulary), where the entry $\beta_{kvc}$ can be interpreted as the probability of observing the $v$-th word in topic $k$ for the covariate level $c$.
-(2) $\theta$ is a $D$-by-$V$ matrix of the document-topic distributions, where the entry $\theta_{dk}$ can be interpreted as the proportion of words in document $d$ which arise from topic $k$, or rather as the probability that document $d$ deals about topic $k$.
-These probability distributions are used to compare the content of the different news provider in section \ref{ch_empirical}.
+This process generates two posterior distribution parameter:
+
+\begin{enumerate}
+	\item $\phi$ is a $K$-by-$V$ matrix (where $K=$ number of topics and $V=$ vocabulary), where the entry $\phi_{kvc}$ can be interpreted as the probability of observing the $v$-th word in topic $k$ for the covariate level $c$ (the news website).
+	\item $\theta$ is a $D$-by-$V$ matrix (where $D=$ number of documents and $V=$ vocabulary) of the document-topic distributions, where the entry $\theta_{dk}$ can be interpreted as the proportion of words in document $d$ which arise from topic $k$, or rather as the probability that document $d$ deals about topic $k$.
+\end{enumerate}
+
+In Section \ref{subsection_topic} $\theta$ is used to estimate the conditional expectation of topic prevalence for given document characteristics.
+To calculate the sentiment value, in Section \ref{subsection_tone} each document $d$ is assigned to the topic with the highest probability ($\max (\theta_{k})$ for each document $d$).
 
@@
 This process revealed that a model with 50 topics best reflects the structure in the corpus.
-Furthermore, the media outlet of the article is used as covariates in the topic prevalence and topical content.
-In other words, the corresponding newswire of an article influences the probability distribution of topics and how the topics are discussed.
+Furthermore, the news website of the article is used as covariates in the topic prevalence and the topical content.
+In other words, the corresponding news website of an article influences the probability distribution of topics and how the topics are discussed.
 
@@
 This section summarizes the results of the STM.
-Subsequently "the two T's" (Topic and Tone) of the corpus are analyzed according to the following approaches: (1) The document-topic probability $\theta$ is used, to estimate the conditional expectation of topic prevalence for given document characteristics (See section \ref{subsection_topic}).
+Subsequently "the two T's" (Topic and Tone) of the corpus are analyzed according to the following approaches: (1) The document-topic probability $\theta_{dk}$ is used, to estimate the conditional expectation of topic prevalence for given document characteristics (See section \ref{subsection_topic}).
 A set of topics is selected, that most distinctly discuss a particular party or a topic related to the federal elections.
@@
 
-It becomes apparent that the topic (topic 4) about the coalition talks between CDU/CSU and SPD - the "Grand coalition" or "GroKo" (from the German word Große Koalition) - is the topic with the highest expected frequency in the whole corpus, followed by the topic about the so-called Jamaica parties (CDU/CSU, FDP and B90/Die Grünen), which was the first alternative to be negotiated directly after the elections.
+It becomes apparent that topic 4 about the coalition talks between CDU/CSU and SPD - the "Grand coalition" or "GroKo" - is the topic with the highest expected frequency in the whole corpus, followed by the topic about the so-called Jamaica parties (CDU/CSU, FDP and B90/Die Grünen), which was the first alternative to be negotiated directly after the elections.
 The Figure also shows, that topics related to refugees in Germany (topics 12 and 42) are quite frequent within the corpus.
@@
 
-We will select the following topics from the whole set (topics are ordered regarding their overall corpus frequency). The most frequent words of these topics can be seen in the appendix:
+We will select the following topics from the whole set. The most frequent words of these topics at each news website can be seen in Appendix \ref{apx_tf}:
 
 \begin{enumerate}
+	\item Topic 1: About the SPD, mainly about the election campaign and Martin Schulz as candidate for the chancellor.	
+	\item Topic 2: About B90/Die Grünen, mainly covering issues regarding the party's personell debates.
 	\item Topic 4: Covering the debates about the great coalition talks, mainly after the failure of the Jamaica coalition talks.
+	\item Topic 13: About Angela Merkel, mainly right before the election. 
+	\item Topic 17: Covering votes within the SPD, mainly regarding the vote about a possible coalition with CDU/CSU ("GroKo").	
+	\item Topic 20: About the AfD, mainly about their relation to right-wing extremist groups.
+	\item Topic 22: About SPD, mainly covering issues regarding the party's personell debates
+	\item Topic 23: About issues regarding the CSU, mainly about the competition between Horst Seehofer and Markus Söder and the negotiations with the CDU.
+	\item Topic 26: Discussing the failure of the Jamaica coalition talks and the two possible alternatives: Reelections or a great coalition.
 	\item Topic 27: Covering the Jamaica coalition talks, mainly focusing on the smaller players Bündnis B90/Die Grünen and FDP.	
-	\item Topic 23: About issues regarding the CSU, mainly about the competition between Horst Seehofer and Markus Söder and the negotiations with the CDU.
+	\item Topic 30: About the AfD, mainly about the resignation of Frauke Petry and Jörg Meuthen.
+	\item Topic 32: About the AfD, mainly about Alice Weidel and Alexander Gauland, voted as parliamentary party leaders after the resignation of Frauke Petry.
 	\item Topic 37: Covering debates of AfD and DIE LINKE in the parliament (Deutscher Bundestag).
-	\item Topic 17: Covering votes within the SPD, mainly regarding the vote about a possible coalition with CDU/CSU ("GroKo")
-	\item Topic 26: Discussing the failure of the Jamaica coalition talks and the two possible alternatives: Reelections or a great coalition.
-	\item Topic 13: About Angela Merkel, mainly right before the election.
-	\item Topic 1: About the SPD, mainly about the election campaign and Martin Schulz as candidate for the chancellor.
-	\item Topic 32: About the AfD, mainly about Alice Weidel and Alexander Gauland, voted as parliamentary party leaders after the resignation of Frauke Petry.
-	\item Topic 30: About the AfD, mainly about the resignation of Frauke Petry and Jörg Meuthen.
-	\item Topic 2: About B90/Die Grünen, mainly covering issues regarding the party's personell debates.
-	\item Topic 22: About SPD, mainly covering issues regarding the party's personell debates
-	\item Topic 20: About the AfD, mainly about their relation to right-wing extremist groups.
 	\item Topic 46: Covering issues regarding the CDU.
@@
 Next, the differences of topic prevalence for given document characteristics can be estimated \citep{roberts_model_2016}.
-More specifically, I estimate a linear model, where the documents are observations, the dependent variable is the posterior probability of a topic and the covariates are the metadata of documents (see equation \ref{eq_1}).
-The stm-package provides a function that uses the method of composition to incorporate uncertainty in the dependent variable, drawing a set of topic proportions from the variational posterior repeated times and compute the coefficients as the average over all results \citep{roberts_stm:_2016}.
-% Letzten satz umschreiben! hört sich sonst so an als würde ich nicht wissen, was die macht. 
-% Formel erklären!
+For each topic $k$ a linear model is estimated, where the documents $d$ are observations, the dependent variable is the posterior probability of that topic ($\theta_{d}$) and the covariates are dummy variables that are 1 if the document was published by the respective website and 0 otherwise (see equation \ref{eq_1}).
+As the dependent variable is a vector containing proportions that sum up to 1, the QR decomposition of the model is computed prior to the estimation of the coefficients.
+To incorporate uncertainty in the dependent variable, a set of topic proportions are drawn from the variational posterior (the unnormalized topic proportions) repeated times.
+Then, the coefficients are computed as the average over all results \citep{roberts_stm:_2016}.
 
 \begin{equation}\label{eq_1}
-	\theta_d=\alpha+\beta x_{newswire}+\epsilon
+\begin{split}
+	\theta_{d}=\beta_0+\beta_1 x_{\text{FOCUS ONLINE,d}}+\beta_2 x_{\text{SPIEGEL ONLINE,d}}+\\
+	\beta_3 x_{\text{stern.de,d}}+\beta_4 x_{\text{Tagesschau.de,d}}+\beta_5 x_{\text{DIE WELT,d}}+\\
+	\beta_6 x_{\text{ZEIT ONLINE,d}}+\epsilon
+\end{split}
 \end{equation}
@@
 
+\subsection{Most frequent words}\label{apx_tf}
 % 1, 2

### 2018-04-05 paper/writing/tables/coeff2.tex
add tables for regression results

% latex table generated in R 3.4.2 by xtable 1.8-2 package
% Thu Apr  5 15:04:12 2018
\begin{table}[ht]
\centering
\resizebox{\textwidth}{!}{
\begin{tabular}{rllrrrr}
  \hline
 & topic\_name & parameter & Estimate & Std. Error & t value & p \\ 
  \hline
70 & 10: M.Schulz, vs. A.Merkel & ZEIT ONLINE & 0.01 & 0.00 & 3.60 & 0.00 \\ 
  71 & 11: politics \& democracy in GER & (Intercept) & 0.01 & 0.00 & 4.88 & 0.00 \\ 
  72 & 11: politics \& democracy in GER & FOCUS ONLINE & 0.00 & 0.00 & 0.92 & 0.36 \\ 
  73 & 11: politics \& democracy in GER & SPIEGEL ONLINE & -0.00 & 0.00 & -1.32 & 0.19 \\ 
  74 & 11: politics \& democracy in GER & stern.de & -0.00 & 0.00 & -1.57 & 0.12 \\ 
  75 & 11: politics \& democracy in GER & Tagesschau.de & -0.00 & 0.00 & -1.79 & 0.07 \\ 
  76 & 11: politics \& democracy in GER & DIE WELT & 0.00 & 0.00 & 1.25 & 0.21 \\ 
  77 & 11: politics \& democracy in GER & ZEIT ONLINE & 0.01 & 0.00 & 3.54 & 0.00 \\ 
  78 & 12: Deportation of criminal Refugees & (Intercept) & 0.03 & 0.00 & 6.49 & 0.00 \\ 
  79 & 12: Deportation of criminal Refugees & FOCUS ONLINE & 0.03 & 0.01 & 4.86 & 0.00 \\ 
  80 & 12: Deportation of criminal Refugees & SPIEGEL ONLINE & 0.00 & 0.01 & 0.19 & 0.85 \\ 
  81 & 12: Deportation of criminal Refugees & stern.de & 0.00 & 0.01 & 0.81 & 0.42 \\ 
  82 & 12: Deportation of criminal Refugees & Tagesschau.de & 0.02 & 0.01 & 3.35 & 0.00 \\ 
  83 & 12: Deportation of criminal Refugees & DIE WELT & 0.02 & 0.01 & 3.21 & 0.00 \\ 
  84 & 12: Deportation of criminal Refugees & ZEIT ONLINE & -0.01 & 0.01 & -0.96 & 0.34 \\ 
  85 & 13: A.Merkel, election campaign & (Intercept) & 0.02 & 0.00 & 9.43 & 0.00 \\ 
  86 & 13: A.Merkel, election campaign & FOCUS ONLINE & 0.00 & 0.00 & 0.55 & 0.58 \\ 
  87 & 13: A.Merkel, election campaign & SPIEGEL ONLINE & 0.00 & 0.00 & 1.01 & 0.31 \\ 
  88 & 13: A.Merkel, election campaign & stern.de & 0.01 & 0.00 & 2.73 & 0.01 \\ 
  89 & 13: A.Merkel, election campaign & Tagesschau.de & -0.01 & 0.00 & -1.71 & 0.09 \\ 
  90 & 13: A.Merkel, election campaign & DIE WELT & 0.00 & 0.00 & 0.33 & 0.74 \\ 
  91 & 13: A.Merkel, election campaign & ZEIT ONLINE & 0.00 & 0.00 & 1.13 & 0.26 \\ 
  92 & 14: Text processing fail & (Intercept) & 0.01 & 0.00 & 9.65 & 0.00 \\ 
  93 & 14: Text processing fail & FOCUS ONLINE & -0.01 & 0.00 & -6.04 & 0.00 \\ 
  94 & 14: Text processing fail & SPIEGEL ONLINE & -0.01 & 0.00 & -7.20 & 0.00 \\ 
  95 & 14: Text processing fail & stern.de & -0.01 & 0.00 & -7.04 & 0.00 \\ 
  96 & 14: Text processing fail & Tagesschau.de & -0.01 & 0.00 & -6.19 & 0.00 \\ 
  97 & 14: Text processing fail & DIE WELT & -0.01 & 0.00 & -6.39 & 0.00 \\ 
  98 & 14: Text processing fail & ZEIT ONLINE & -0.01 & 0.00 & -4.30 & 0.00 \\ 
  99 & 15: Israel, antisemitism, D.Trump & (Intercept) & 0.03 & 0.00 & 8.95 & 0.00 \\ 
  100 & 15: Israel, antisemitism, D.Trump & FOCUS ONLINE & -0.01 & 0.00 & -1.39 & 0.17 \\ 
  101 & 15: Israel, antisemitism, D.Trump & SPIEGEL ONLINE & -0.01 & 0.00 & -1.44 & 0.15 \\ 
  102 & 15: Israel, antisemitism, D.Trump & stern.de & -0.01 & 0.00 & -1.66 & 0.10 \\ 
  103 & 15: Israel, antisemitism, D.Trump & Tagesschau.de & -0.01 & 0.00 & -1.98 & 0.05 \\ 
  104 & 15: Israel, antisemitism, D.Trump & DIE WELT & -0.01 & 0.00 & -1.63 & 0.10 \\ 
  105 & 15: Israel, antisemitism, D.Trump & ZEIT ONLINE & -0.01 & 0.00 & -1.24 & 0.21 \\ 
  106 & 16: Mix: political talkshows, Refugees & (Intercept) & 0.01 & 0.00 & 4.58 & 0.00 \\ 
  107 & 16: Mix: political talkshows, Refugees & FOCUS ONLINE & 0.00 & 0.00 & 1.20 & 0.23 \\ 
  108 & 16: Mix: political talkshows, Refugees & SPIEGEL ONLINE & -0.00 & 0.00 & -1.50 & 0.13 \\ 
  109 & 16: Mix: political talkshows, Refugees & stern.de & -0.00 & 0.00 & -1.31 & 0.19 \\ 
  110 & 16: Mix: political talkshows, Refugees & Tagesschau.de & -0.01 & 0.00 & -2.88 & 0.00 \\ 
  111 & 16: Mix: political talkshows, Refugees & DIE WELT & 0.00 & 0.00 & 2.05 & 0.04 \\ 
  112 & 16: Mix: political talkshows, Refugees & ZEIT ONLINE & -0.00 & 0.00 & -1.54 & 0.12 \\ 
  113 & 17: Debates within SPD & (Intercept) & 0.04 & 0.00 & 10.09 & 0.00 \\ 
  114 & 17: Debates within SPD & FOCUS ONLINE & -0.01 & 0.00 & -1.36 & 0.17 \\ 
  115 & 17: Debates within SPD & SPIEGEL ONLINE & -0.01 & 0.00 & -2.20 & 0.03 \\ 
  116 & 17: Debates within SPD & stern.de & -0.00 & 0.00 & -0.40 & 0.69 \\ 
  117 & 17: Debates within SPD & Tagesschau.de & -0.01 & 0.00 & -3.04 & 0.00 \\ 
  118 & 17: Debates within SPD & DIE WELT & -0.01 & 0.00 & -2.61 & 0.01 \\ 
  119 & 17: Debates within SPD & ZEIT ONLINE & -0.01 & 0.00 & -1.70 & 0.09 \\ 
  120 & 18: Election in Niedersachsen & (Intercept) & 0.02 & 0.00 & 5.93 & 0.00 \\ 
  121 & 18: Election in Niedersachsen & FOCUS ONLINE & -0.00 & 0.00 & -0.72 & 0.47 \\ 
  122 & 18: Election in Niedersachsen & SPIEGEL ONLINE & 0.01 & 0.00 & 1.67 & 0.10 \\ 
  123 & 18: Election in Niedersachsen & stern.de & 0.01 & 0.00 & 1.91 & 0.06 \\ 
  124 & 18: Election in Niedersachsen & Tagesschau.de & 0.00 & 0.00 & 0.46 & 0.65 \\ 
  125 & 18: Election in Niedersachsen & DIE WELT & 0.00 & 0.00 & 0.49 & 0.62 \\ 
  126 & 18: Election in Niedersachsen & ZEIT ONLINE & 0.01 & 0.00 & 2.37 & 0.02 \\ 
  127 & 19: N.Lammert & (Intercept) & 0.00 & 0.00 & 5.17 & 0.00 \\ 
  128 & 19: N.Lammert & FOCUS ONLINE & -0.00 & 0.00 & -1.48 & 0.14 \\ 
  129 & 19: N.Lammert & SPIEGEL ONLINE & -0.00 & 0.00 & -0.71 & 0.48 \\ 
  130 & 19: N.Lammert & stern.de & -0.00 & 0.00 & -1.64 & 0.10 \\ 
  131 & 19: N.Lammert & Tagesschau.de & -0.00 & 0.00 & -2.38 & 0.02 \\ 
  132 & 19: N.Lammert & DIE WELT & -0.00 & 0.00 & -1.80 & 0.07 \\ 
  133 & 19: N.Lammert & ZEIT ONLINE & 0.00 & 0.00 & 1.50 & 0.13 \\ 
  134 & 20: AfD, right-wing radicalism & (Intercept) & 0.02 & 0.00 & 6.12 & 0.00 \\ 
  135 & 20: AfD, right-wing radicalism & FOCUS ONLINE & -0.00 & 0.00 & -0.66 & 0.51 \\ 
  136 & 20: AfD, right-wing radicalism & SPIEGEL ONLINE & -0.00 & 0.00 & -0.75 & 0.45 \\ 
  137 & 20: AfD, right-wing radicalism & stern.de & -0.00 & 0.00 & -0.86 & 0.39 \\ 
  138 & 20: AfD, right-wing radicalism & Tagesschau.de & 0.00 & 0.00 & 0.06 & 0.95 \\ 
  139 & 20: AfD, right-wing radicalism & DIE WELT & 0.00 & 0.00 & 0.49 & 0.62 \\ 
  140 & 20: AfD, right-wing radicalism & ZEIT ONLINE & -0.00 & 0.00 & -0.50 & 0.62 \\ 
   \hline
\end{tabular}
}
\end{table}

### 2018-04-05 paper/docs/04_Modelresults_50.Rmd
add tables

@@
          signifcant = ifelse(p <= 0.5,"yes","no")) %>%
-  left_join(., topics.df, by="topic")
+  left_join(., topics.df, by="topic") %>%
+  mutate(parameter = ifelse(parameter == "welt.de", "DIE WELT", parameter),
+         parameter = ifelse(parameter == "zeit.de", "ZEIT ONLINE", parameter),
+         parameter = ifelse(parameter == "focus.de", "FOCUS ONLINE", parameter),
+         parameter = ifelse(parameter == "spiegel.de", "SPIEGEL ONLINE", parameter),
+         parameter = ifelse(parameter == "tagesschau.de", "Tagesschau.de", parameter))
+```
+
+```{r}
+nr <- nrow(coeff)/5
+
+coeff_tab <- coeff %>%
+  select(topic_name,parameter,Estimate, `Std. Error`, `t value`, p)
+
+print(xtable(coeff_tab[1:nr,], type="latex"), file="../writing/tables/coeff1.tex" )
+print(xtable(coeff_tab[nr:(nr*2),], type="latex"), file="../writing/tables/coeff2.tex" )
+print(xtable(coeff_tab[(nr*2):(nr*3),], type="latex"), file="../writing/tables/coeff3.tex" )
+print(xtable(coeff_tab[(nr*3):(nr*4),], type="latex"), file="../writing/tables/coeff4.tex" )
+print(xtable(coeff_tab[(nr*4):(nr*5),], type="latex"), file="../writing/tables/coeff5.tex" )
 ```
@@
   filter(topic %in% keep) %>%
-  filter(parameter %in% stmOut$settings$covariates$yvarlevels) %>%
+  filter(parameter != "(Intercept)") %>%
   ggplot(aes(x = reorder(topic_name,topic, decreasing=F), y = Estimate, fill=factor(signifcant))) +
@@
         axis.text.x = element_text(angle=90))
-
 ggsave(plot = p1, filename = "../figs/estimates.png", device = "png",width = 9, height = 6,

### 2018-04-06 paper/docs/04_Modelresults_50.Rmd
add new ccf

@@
 
-ggsave(filename = "../figs/sentscore_monthly.png", plot = p1,  width = 9,
+ggsave(filename = "../figs/sentscore_monthly.png", plot = p1, 
        height = 6)
@@
   #geom_line(color = col[2], size = 0.8) +
-  geom_text(size = 2) +
+  #geom_text(size = 2) +
   geom_hline(yintercept = 0, linetype = 2,
@@
   labs(x="", y="Sentiment Score (weighted)",
-       title = "",
-       subtitle = "Numbers indicate the ") +
+       title = "") +
   theme(axis.text.y = element_text(size =8),
@@
 
-ggsave(filename = "../figs/sentscore_site.png", plot = p1, width = 9,
+ggsave(filename = "../figs/sentscore_site.png", plot = p1, 
        height = 5)
@@
 
-```{r}
-plot_ccf <- function(corr1, corr2, ...){
-
-  # Create empty matrix
-  corr <- expand.grid(names(corr1), names(corr2))
-  corr$correlation <- NA
-
-  x <- 1
-
-  for (corr1Id in 1:ncol(corr2)) {
-    c1 = corr2[,corr1Id]
-    #print(names(corr2[,corr1Id]))
-
-    for(corr2Id in 1:ncol(corr1)) {
-      c2 = corr1[,corr2Id]
-      #print(names(corr1[,corr2Id]))
-      correlation = ccf(c1, c2, lag.max = 0,
-                      na.action = na.contiguous, plot=F)
-      corr[x,3] <- correlation$acf[1]
-
-      x<- x+1
-    }
-  }
-
-      ### Plot Corr ##
-      ggplot(corr, aes(Var2, Var1,
-                 fill = correlation,
-                 label = round(correlation,2))) +
-        geom_tile(color="white", ...) +
-        geom_text(size = 3.5, color = col[5]) +
-        viridis::scale_fill_viridis(limits=c(-1, 1)) +
-        labs(x="", y="", fill="",
-             title = "",
-             ...)
-}
-```
-
 ##### 3.1.1. Overall
-```{r fig.height=6, fig.width=8}
+```{r}
 group1 %>%
@@
 polls_monthly %>% select(- yearmonth) -> corr2
-
-p <- plot_ccf(corr1, corr2, alpha = 0.8,
+```
+
+```{r}
+# Create empty matrix
+corr <- expand.grid(names(corr1), names(corr2))
+
+corr$`-3` <- NA
+corr$`-2` <- NA
+corr$`-1` <- NA
+corr$`0` <- NA
+corr$`1` <- NA
+corr$`2` <- NA
+corr$`3` <- NA
+
+x <- 1
+
+for (corr1Id in 1:ncol(corr2)) {
+  c1 = corr2[,corr1Id]
+
+  for(corr2Id in 1:ncol(corr1)) {
+    c2 = corr1[,corr2Id]
+    correlation = ccf(c1, c2, lag.max = 3,
+                      na.action = na.contiguous, plot=F)
+
+    corr[x,"-3"] <- correlation$acf[1]
+    corr[x,"-2"] <- correlation$acf[2]
+    corr[x,"-1"] <- correlation$acf[3]
+    corr[x,"0"] <- correlation$acf[4]
+    corr[x,"1"] <- correlation$acf[5]
+    corr[x,"2"] <- correlation$acf[6]
+    corr[x,"3"] <- correlation$acf[7]
+
+    x<- x+1
+  }
+}
+
+corr <- corr %>%
+  gather(lag, correlation, `-3`:`3`) %>%
+  mutate(lag = as.numeric(lag))
+```
+
+```{r fig.height=6, fig.width=8}
+p <- corr %>%
+  filter(lag == 0) %>%
+  ggplot(aes(Var2, Var1,
+                 fill = correlation,
+                 label = round(correlation,2))) +
+        geom_tile(color="white", alpha=0.8) +
+        geom_text(size = 3.5) +
+        #viridis::scale_fill_viridis(limits=c(-1, 1)) +
+        labs(x="", y="", fill="",
+             title = "",
              subtitle = "Election polls vs. topic sentiment value (monthly)")
@@
 ![Cross-correlation](../figs/ccf.png)
+
+The variance of the cross-correlation coefficient under the null hypothesis of zero correlation is approx $1/n$ where $n$ is the length of the series.
+The coefficients are also asymptotically normal.
+So approximate critical values (at the 5% level) are $±2/\sqrt{n}$.
+
+```{r}
+critical_val <- 2/sqrt(nrow(corr1))
+```
+
+```{r}
+# insert linebreak for long strings
+linebreak <- function(s) {
+  gsub('(.{1,12})(\\s|$)', '\\1\n', s)
+}
+```
+
+```{r fig.height=7, fig.width=14}
+p <- ggplot(corr, aes(lag, correlation,
+                 #fill = Var1,
+                 group=Var2)) +
+  geom_col(fill = col[3]) +
+  scale_x_continuous(breaks = c(-3:3)) +
+  labs(x="Lag",y="Cross Correlation") +
+  geom_hline(yintercept = critical_val, linetype = 2, color = col[5]) +
+  geom_hline(yintercept = -(critical_val), linetype = 2, color = col[5]) +
+  facet_grid(Var2~Var1, labeller=labeller(Var1 = linebreak)) +
+  theme(strip.text = element_text(size=12),
+        strip.text.y = element_text(size=12),
+        axis.text = element_text(size = 10),
+        axis.title = element_text(size=12))
+
+ggsave(filename = "../figs/ccf2.png", plot = p,
+       width = 16,
+       height = 10,
+       dpi = 600)
+```
 

### 2018-04-06 paper/writing/structure.tex
add tables for regression results
add new ccf

@@
 
-We will select the following topics from the whole set. The most frequent words of these topics at each news website can be seen in Appendix \ref{apx_tf}:
+The remaining analysis is limited to topics closely related to one or more parties.
+For this reason, the following topics were selected.
+The most frequent words of these topics at each news website can be seen in Appendix \ref{apx_tf}:
 
@@
 
-Next, the differences of topic prevalence for given document characteristics can be estimated \citep{roberts_model_2016}.
-For each topic $k$ a linear model is estimated, where the documents $d$ are observations, the dependent variable is the posterior probability of that topic ($\theta_{d}$) and the covariates are dummy variables that are 1 if the document was published by the respective website and 0 otherwise (see equation \ref{eq_1}).
+To estimate the differences of topic prevalence of the mentioned topics for the different websites, a linear model is calculated for each topic $k$, where the documents $D$ are observations, the dependent variable is the posterior probability of the respective topic ($\theta_{d}$) and the covariates are dummy variables that are 1 if the document was published by the respective website and 0 otherwise (see equation \ref{eq_1}).
 As the dependent variable is a vector containing proportions that sum up to 1, the QR decomposition of the model is computed prior to the estimation of the coefficients.
 To incorporate uncertainty in the dependent variable, a set of topic proportions are drawn from the variational posterior (the unnormalized topic proportions) repeated times.
-Then, the coefficients are computed as the average over all results \citep{roberts_stm:_2016}.
+Then, the coefficients are computed as the average over all results \citep{roberts_model_2016}.
 
@@
 
-Figure \ref{fig_estimateEffects} shows the regression results for the above selected topics.
+Figure \ref{fig_estimateEffects} shows the regression results for the above selected topics (See Appendix \ref{apx_coeff} for the result tables).
 The coefficients indicate the deviation from the base value of Bild.de.
@@
 
-The following figure shows the results of the analysis for each topic on a monthly basis, aggregated on all newspaper.
+The following figure shows the results of the analysis for each topic on a monthly basis, aggregated on all newspapers.
 Each sentiment value is weighted by the relative share of the topic in the overall reporting of that month.
@@
 
-If aggregated by news provider, some differences between the sites are discernible (Figure \ref{fig_sentscore_site}\footnote{The numbers reflect the number of observations.}).
+If aggregated by news provider, some differences between the sites are discernible (Figure \ref{fig_sentscore_site}).
 To begin with, it can be noted that on average all topics are discussed negatively by all news providers, except topic 22, which mainly covers the personnel debates of the SPD and has a positive value at Tagesschau.de.
@@
 
-We use two different Figures to analyze the differences between the media outlets graphically: We use the bar plot to examine the polarity tendencies of the individual topics within a medium (\ref{fig_sentscore_site}) and the radar plot to observe the differences between the media (\ref{fig_sentscore_radar}).
+We use two different Figures to analyze the differences between the media outlets graphically: We use the bar plot to examine the polarity tendencies of the individual topics within a medium (Figure \ref{fig_sentscore_site}) and the radar plot to observe the differences between the media (Figure \ref{fig_sentscore_radar}).
 
@@
 \begin{figure}[H]
-	\caption{Sentiment Score by news wire}
+	\caption{Sentiment Score by news website}
 	\begin{center}
@@
 A good overview of how differently the topics are discussed by the providers is shown in Figure \ref{fig_sentscore_radar}.
-It gets evident that the sentiment value of the media differs most notably with regard to topic 27 and topic 4, i.
+It becomes evident that the sentiment value of the media differs most notably with regard to topic 27 and topic 4, i.
 e.
@@
 
-After the above figures have been analyzed, the following points can be summarized: (a) The sentiment value of the SPD is decreasing over time, especially in regard to internal votes.
-(b) The topics relating to the coalition talks on Jamaica (26, 27) and the grand coalition (4) are discussed rather critically, but they also show the greatest differences within the media.
+After the above figures have been analyzed, the following points can be summarized:
+
+\begin{enumerate}
+	\item The sentiment value of the SPD is decreasing over time, especially in regard to internal votes. 
+	\item The topics relating to the coalition talks on Jamaica (26, 27) and the grand coalition (4) are discussed rather critically, but they also show the greatest differences within the media.
 In contrast, the tonality of the topics in relation to the AfD shows rather small differences.
-(c) Overall, the sentiment value at Tagesschau.de is the least negative and only shows a comparatively strong negative value at topic 23, concerning the CSU.
+	\item Overall, the sentiment value at Tagesschau.de is the least negative and only shows a comparatively strong negative value at topic 23, concerning the CSU.
+\end{enumerate}
 
@@
 Specifically, it aims to find the extent to which online sentiment and phone survey results correlate.
-I use the data from the "Sonntagsumfrage" (Sunday survey) from infratest dimap\footnote{https://www.infratest-dimap.de/umfragen-analysen/bundesweit/sonntagsfrage/}.
-The institution regularly asks at least 1000 German citizens the question: "Which party would you choose if federal elections take place next Sunday?" The survey thus measures the current election tendencies and therefore reflects an intermediate state in the opinion-forming process of the electoral population.
+I use the data from the "Sonntagsumfrage" (Sunday survey) from infratest dimap.\footnote{https://www.infratest-dimap.de/umfragen-analysen/bundesweit/sonntagsfrage/} The institution regularly asks at least 1000 German citizens the question: "Which party would you choose if federal elections take place next Sunday?" The survey thus measures the current election tendencies and therefore reflects an intermediate state in the opinion-forming process of the electoral population.
 
@@
 \begin{figure}[H]
-	\caption{Cross-Correlation at lag 0}
+	\caption{Cross-Correlation}
 	\begin{center}
-			\includegraphics[width=\textwidth,keepaspectratio]{../figs/ccf.png}
+			\includegraphics[width=\textwidth,keepaspectratio]{../figs/ccf2.png}
 			\label{fig_ccf}
@@
 
+\printbibliography
 \section*{Appendix}
 
-\subsection{Most frequent words}\label{apx_tf}
+\subsection*{Most frequent words\label{apx_tf}
 % 1, 2
@@
 
+\subsection*{Regression Results}\label{apx_coeff}
+
+\input{tables/coeff1}
+\input{tables/coeff2}
+\input{tables/coeff3}
+\input{tables/coeff4}
+\input{tables/coeff5}
+
 \end{document}

### 2018-04-09 paper/docs/func/functions.R
add linebreak function

@@ -213,3 +213,11 @@ calculate_week = function(week, year) {
   week(date) = week
   return(date)
 }
+
+###################################
+# insert linebreak for long strings
+###################################
+
+linebreak <- function(s) {
+  gsub('(.{1,12})(\\s|$)', '\\1\n', s)
+}

### 2018-04-09 paper/docs/04_Modelresults_50.Rmd
ccf

@@
 ```{r}
-nr <- nrow(coeff)/5
-
 coeff_tab <- coeff %>%
+  filter(topic %in% keep) %>%
   select(topic_name,parameter,Estimate, `Std. Error`, `t value`, p)
 
-print(xtable(coeff_tab[1:nr,], type="latex"), file="../writing/tables/coeff1.tex" )
-print(xtable(coeff_tab[nr:(nr*2),], type="latex"), file="../writing/tables/coeff2.tex" )
-print(xtable(coeff_tab[(nr*2):(nr*3),], type="latex"), file="../writing/tables/coeff3.tex" )
-print(xtable(coeff_tab[(nr*3):(nr*4),], type="latex"), file="../writing/tables/coeff4.tex" )
-print(xtable(coeff_tab[(nr*4):(nr*5),], type="latex"), file="../writing/tables/coeff5.tex" )
+print(xtable(coeff_tab[1:56,], type="latex"), file="../writing/tables/coeff1.tex" )
+print(xtable(coeff_tab[57:nrow(coeff_tab),], type="latex"), file="../writing/tables/coeff2.tex" )
 ```
@@
 
+```{r}
+keep <- c(1,2,4,10,13,17,20,22,23,26,27,30,32,37,46)
+```
+
 The idea of Sentiment analysis is to determine the attitude of a writer through online text data toward certain topic or the overall tonality of a document.
@@
            label = obs)) +
-  facet_wrap(~topic_name, nrow = 3) +
+  facet_wrap(~topic_name, nrow = 3, labeller=labeller(topic_name = linebreak)) +
   geom_col(fill = col[3], alpha = 0.8) +
@@
              color = "black") +
-  labs(x="", y="Sentiment Score (weighted)",
+  labs(x="", y="Sentiment Score",
         title = "",
@@
   scale_x_date(breaks = date_breaks("1 month"), 
-               labels = date_format("%B", tz ="CET")) +
-  theme(axis.text.y = element_text(size=8),
-        axis.text.x = element_text(size = 8, angle = 90))
+               labels = date_format("%b", tz ="CET")) +
+  theme(strip.text = element_text(size=14),
+    axis.text.y = element_text(size=10),
+        axis.text.x = element_text(size = 10, angle = 45))
 
 ggsave(filename = "../figs/sentscore_monthly.png", plot = p1, 
-       height = 6)
+       height = 10, width = 12)
 ```
@@
   facet_wrap(~site, ncol = 7) +
-  labs(x="", y="Sentiment Score (weighted)",
+  labs(x="", y="Sentiment Score",
        title = "") +
-  theme(axis.text.y = element_text(size =8),
-        axis.text.x = element_text(size=4, angle = 90),
-        axis.title.x = element_text(size = 5))
+  theme(strip.text = element_text(size = 11),
+    axis.text.y = element_text(size = 12),
+        axis.text.x = element_text(size=8, angle = 90),
+        axis.title.x = element_text(size = 12))
 
 ggsave(filename = "../figs/sentscore_site.png", plot = p1, 
-       height = 5)
+       height = 8, width = 12)
 ```
@@
 sentDF.values %>%
-  mutate(topic_name = ifelse(grepl("B90", topic_name),
-                             "B90/\nDie Grünen", topic_name),
-         topic_name = ifelse(grepl("17", topic_name),
-                             "17: Debates\nwithin SPD", topic_name),
-         topic_name = ifelse(grepl("13", topic_name),
-                             "13: A.Merkel,\nelection campaign", topic_name),
-         topic_name = ifelse(grepl("30", topic_name),
-                             "30: AfD,\nF.Petry & Meuthen", topic_name),
-         topic_name = ifelse(grepl("32", topic_name),
-                             "32: AfD,\nGauland & Weidel", topic_name),
-         topic_name = ifelse(grepl("37", topic_name),
-                             "37: AfD & DIE LINKE\nin parliament", topic_name),
-         topic_name = ifelse(grepl("20", topic_name),
-                             "20: AfD, right-wing\nradicalism", topic_name)
-         ) %>%
+mutate(topic_name = linebreak(topic_name)) %>%
   group_by(site, topic_name) %>%
@@
           alpha = 0) +
-  labs(title = "Sentiment scores Jun 2017-March 2018",
-       subtitle = "weighted") +
+  labs(title = "Sentiment scores Jun 2017-March 2018") +
   guides(col = guide_legend(ncol = 1)) +
@@
 
-ggsave(filename = "../figs/sentscore_radar.png", 
+ggsave(filename = "../figs/sentscore_radar.png", width = 9,
+       height = 7,
        plot = p)
@@
     c2 = corr1[,corr2Id]
-    correlation = ccf(c1, c2, lag.max = 3,
+    correlation = ccf(c2, c1, lag.max = 3,
                       na.action = na.contiguous, plot=F)
@@
 The coefficients are also asymptotically normal.
-So approximate critical values (at the 5% level) are $±2/\sqrt{n}$.
+So approximate critical values (at the 5% level) are $\pm 2/\sqrt{n}$.
 
@@
 critical_val <- 2/sqrt(nrow(corr1))
-```
-
-```{r}
-# insert linebreak for long strings
-linebreak <- function(s) {
-  gsub('(.{1,12})(\\s|$)', '\\1\n', s)
-}
 ```
@@
   geom_col(fill = col[3]) +
-  scale_x_continuous(breaks = c(-3:3)) +
-  labs(x="Lag",y="Cross Correlation") +
+  #scale_x_continuous(breaks = c(-3:3)) +
+  labs(x="Lag",y="Cross Correlation",
+       caption = "The red dotted lines indicate the critical values at the 5% significance value\nThe black dotted lines indicate the lag 0 on the x-axis.") +
   geom_hline(yintercept = critical_val, linetype = 2, color = col[5]) +
   geom_hline(yintercept = -(critical_val), linetype = 2, color = col[5]) +
+  geom_vline(xintercept = 0, linetype = 3, size=0.5) +
   facet_grid(Var2~Var1, labeller=labeller(Var1 = linebreak)) +
-  theme(strip.text = element_text(size=12),
-        strip.text.y = element_text(size=12),
-        axis.text = element_text(size = 10),
-        axis.title = element_text(size=12))
+  theme(strip.text = element_text(size=13),
+        axis.text = element_text(size = 12),
+        axis.title = element_text(size=14),
+        plot.caption = element_text(size = 10, hjust = 0))
 
 ggsave(filename = "../figs/ccf2.png", plot = p,
-       width = 16,
-       height = 10,
+       width = 18,
+       height = 12,
        dpi = 600)

### 2018-04-09 paper/writing/structure.tex
ccf

@@
 The articles analyzed in this paper cover a period from June 1, 2017 to March 1, 2018 and thus cover both the most important election campaign topics for the Bundestag elections on September 24, 2017 and the process of forming a government that lasted until February 2018.
-After four years in a grand coalition with the Social Democrats (SPD), German Chancellor Angela Merkel, member of the Conservative Party (CDU), ran for re-election.
+After four years in a grand coalition with the Social Democrats (SPD), German Chancellor Angela Merkel, member of the Conservative Party (CDU/CSU), ran for re-election.
 The SPD nominated Martin Schulz as candidate for chancellor.
@@
 
-After the election, the formation of a government was difficult due to the large number of parties elected to the Bundestag and the considerable loss of votes by the major parties CDU/CSU and SPD.
-Since all parties rejected a coalition with the AfD, numerically only two coalitions with an absolute parliamentary majority were possible: a grand coalition ("GroKo" - from the German word Große Koalition) of CDU/CSU and SPD, and a Jamaica coalition (coalition of CDU/CSU, FDP (economic liberal party) and B90/Die Grünen (Bündnis 90/Die Grünen, green party)).
+After the election, the formation of a government was difficult due to the large number of parties elected to the Bundestag and the considerable loss of votes by the major parties CDU/CSU/CSU and SPD.
+Since all parties rejected a coalition with the AfD, numerically only two coalitions with an absolute parliamentary majority were possible: a grand coalition ("GroKo" - from the German word Große Koalition) of CDU/CSU/CSU and SPD, and a Jamaica coalition (coalition of CDU/CSU/CSU, FDP (economic liberal party) and B90/Die Grünen (Bündnis 90/Die Grünen, green party)).
 The grand coalition was initially rejected by the SPD.
@@
 The main points of contention were climate and refugee policy.
-CDU and CSU regretted this result, while B90/Die Grünen sharply criticized the withdrawal of the Liberals.
+CDU/CSU and CSU regretted this result, while B90/Die Grünen sharply criticized the withdrawal of the Liberals.
 The then Green leader Cem Özdemir accused the FDP of lacking the will to reach an agreement.
 
-After the failure of the Jamaica coalition, a possible re-election or a minority government as alternatives were discussed in the media before the SPD decided to hold coalition talks with the CDU/CSU.
+After the failure of the Jamaica coalition, a possible re-election or a minority government as alternatives were discussed in the media before the SPD decided to hold coalition talks with the CDU/CSU/CSU.
 This led to great resistance from the party base, which called for a party-internal vote on a grand coalition.
@@
 
-Figure \ref{fig_polls} shows that support for the two major popular parties has been declining in recent months since August 2017, with the CDU again showing positive survey results since November.
+Figure \ref{fig_polls} shows that support for the two major popular parties has been declining in recent months since August 2017, with the CDU/CSU again showing positive survey results since November.
 However, the value of the SPD has been falling since March 2017.
@@
 
-It becomes apparent that topic 4 about the coalition talks between CDU/CSU and SPD - the "Grand coalition" or "GroKo" - is the topic with the highest expected frequency in the whole corpus, followed by the topic about the so-called Jamaica parties (CDU/CSU, FDP and B90/Die Grünen), which was the first alternative to be negotiated directly after the elections.
+It becomes apparent that topic 4 about the coalition talks between CDU/CSU/CSU and SPD - the "Grand coalition" or "GroKo" - is the topic with the highest expected frequency in the whole corpus, followed by the topic about the so-called Jamaica parties (CDU/CSU/CSU, FDP and B90/Die Grünen), which was the first alternative to be negotiated directly after the elections.
 The Figure also shows, that topics related to refugees in Germany (topics 12 and 42) are quite frequent within the corpus.
@@
 	\item Topic 13: About Angela Merkel, mainly right before the election. 
-	\item Topic 17: Covering votes within the SPD, mainly regarding the vote about a possible coalition with CDU/CSU ("GroKo").	
+	\item Topic 17: Covering votes within the SPD, mainly regarding the vote about a possible coalition with CDU/CSU/CSU ("GroKo").	
 	\item Topic 20: About the AfD, mainly about their relation to right-wing extremist groups.
 	\item Topic 22: About SPD, mainly covering issues regarding the party's personell debates
-	\item Topic 23: About issues regarding the CSU, mainly about the competition between Horst Seehofer and Markus Söder and the negotiations with the CDU.
+	\item Topic 23: About issues regarding the CSU, mainly about the competition between Horst Seehofer and Markus Söder and the negotiations with the CDU/CSU.
 	\item Topic 26: Discussing the failure of the Jamaica coalition talks and the two possible alternatives: Reelections or a great coalition.
@@
 	\item Topic 37: Covering debates of AfD and DIE LINKE in the parliament (Deutscher Bundestag).
-	\item Topic 46: Covering issues regarding the CDU.
+	\item Topic 46: Covering issues regarding the CDU/CSU.
 \end{enumerate}
@@
 The coefficients indicate the deviation from the base value of Bild.de.
-Starting from above it becomes apparent that the topic prevalence of topic 46 (regarding the CDU) is significantly less for Tagesschau.de and Stern.de.
+Starting from above it becomes apparent that the topic prevalence of topic 46 (regarding the CDU/CSU) is significantly less for Tagesschau.de and Stern.de.
 The other media do not show any significant difference to Bild.de for this topic.
@@
 An exception is topic 27 concerning the Jamaica coalition negotiations, which shows a positive sentiment value for a short period of time (October 2017).
-In the following month (November 2017), after it became clear that there would be no coalition between the CDU/CSU, FDP and Die Grünen, the value of this topic as well as that of topic 26 drops rapidly, but then rises again in February.
-Concerning the issues that discuss the great coalition between CDU/CSU and SPD, it is evident that the overall tone is in which this topic is discussed is generally decreasing from November 2017 to January 2018, but in the following February, the sentiment value of this topic rises.
+In the following month (November 2017), after it became clear that there would be no coalition between the CDU/CSU/CSU, FDP and Die Grünen, the value of this topic as well as that of topic 26 drops rapidly, but then rises again in February.
+Concerning the issues that discuss the great coalition between CDU/CSU/CSU and SPD, it is evident that the overall tone is in which this topic is discussed is generally decreasing from November 2017 to January 2018, but in the following February, the sentiment value of this topic rises.
 However, the sentiment score of topics that deal with the SPD (1, 17, 22) is diminishing in the course of time, with topic 17 recording the largest decline.
@@
 Also at stern.de the difference in sentiment value is less significant and overall less negative.
-The topics regarding CDU (46) and Martin Schulz (10) score the most positively (or least negatively).
+The topics regarding CDU/CSU (46) and Martin Schulz (10) score the most positively (or least negatively).
 Tagesschau.de is the least negative on most topics, or even once positive.
@@
 FOCUS ONLINE thus reports comparatively more negatively on the debates within the SPD.
-This includes in particular the vote on a possible coalition with CDU/CSU.
+This includes in particular the vote on a possible coalition with CDU/CSU/CSU.
 For topic 1, which also deals with the SPD, the value of FOCUS ONLINE is rather negative, only undercut by Bild.de.
@@
 	\item The sentiment value of the SPD is decreasing over time, especially in regard to internal votes. 
-	\item The topics relating to the coalition talks on Jamaica (26, 27) and the grand coalition (4) are discussed rather critically, but they also show the greatest differences within the media.
+	\item The topics relating to the coalition talks on Jamaica (26, 27) and the grand coalition (4) are discussed rather critically, but they also show the greatest differences between the media.
 In contrast, the tonality of the topics in relation to the AfD shows rather small differences.
@@
 \subsection{News sentiment and poll data}\label{ch_correlation}
+% add ccf table
 
-This section seeks to examine the temporal association between sentiment reflected in online news content and phone survey poll results in Germany.
-Specifically, it aims to find the extent to which online sentiment and phone survey results correlate.
+This section seeks to examine the association between sentiment reflected in online news content and phone survey poll results in Germany.
+Specifically, it aims to find the extent to which online sentiment and phone survey results correlate given a number of lags.
 I use the data from the "Sonntagsumfrage" (Sunday survey) from infratest dimap.\footnote{https://www.infratest-dimap.de/umfragen-analysen/bundesweit/sonntagsfrage/} The institution regularly asks at least 1000 German citizens the question: "Which party would you choose if federal elections take place next Sunday?" The survey thus measures the current election tendencies and therefore reflects an intermediate state in the opinion-forming process of the electoral population.
@@
 In a more recent conference paper, \citet{padmaja_evaluating_2014} identify the scope of negation in news articles for two political parties in India (BJP and UPA) to analyze how the choice of certain words used in these texts influence the sentiments of public in polls.
-Comparing three different sentiment analysis methods (two machine learning and one dictionary method), they observe that the choice of certain words used in political text was influencing the Sentiments in favor of BJP.
+Comparing three different sentiment analysis methods (two machine learning and one dictionary method), they observe that the choice of certain words used in political text was influencing the sentiments in favor of BJP.
 They conclude that this sentiment bias might be one of the causes for the election results in 2014.
 
-In the present paper, the comparison between monthly average of both the sentiment value of individual topics and the survey value of the parties is calculated using the cross-correlation function.
-It is important to notice, that the results from this analysis will give an indication whether correlation between the two time series exist, but it does not give any evidence about the causal relationship.
-None of the following interpretation of the cross-correlation coefficients is intended to describe a causal relationship.
+In the present paper, the relationship between monthly average of both the sentiment value of individual topics ($x_t$) and the survey value of the parties ($y_t$) is estimated using the cross correlation function (CCF).
+Thus, the CCF between $x_{t+h}$ and $y_t$ for $h\pm 1$,$h \pm 2$,$h \pm 3$ is computed.
+A negative value for $h$ is a correlation between the topic sentiment value at a time before $t$ and the survey value at time $t$.
+The correlation value for $h=0$ indicates the contemporary correlation between the two time series.
+Based on the coefficients of the cross correlation estimation shown in Figure \ref{fig_ccf}, the significant correlations between topic sentiment and survey value are evaluated for each party.
+It is important to note that no causal relationships are described below, but that only the correlation between the two time series is described.
 
-Based on the contemporary coefficients of the cross-correlation estimation shown in Figure \ref{fig_ccf}, the most noticeable topics for each party are evaluated below.
-The AfD's survey results correlate negatively with topics relating to the SPD.
-The strongest positive correlation with regard to AfD-related topics can be found for topic 30.
-Since there are no isolated topics about the FDP, the issues surrounding the Jamaica negotiations are examined, which show a negative correlation.
-It is also striking that the poll results of the FDP correlate strongly negatively with the CSU topic (23).
-With regard to B90/Die Grünen, there is also a negative correlation to the Jamaica topics, however, it is slightly above the correlation-coefficient of the FDP.
-It is striking that there seems to be a strong negative correlation between the SPD issues and the poll results of the Left Party.
-Conversely, the survey results of the SPD correlate very positively with the SPD topics.
-The CDU's survey results correlate most positively with topics relating to coalition negotiations.
+The survey results of the AfD correlate negatively with topics relating to the SPD (17, 22) at lag 0.
+Thus, if the SPD was more negatively reported, the poll value of the AfD increased in the same month (and vice versa).
+Another significant negative correlation exists between the reporting on the GroKo (4) and the survey value of AfD at lag -1 ($x_{t-1}$).
+So if the GroKo was more negatively reported in one month, the survey value of the AfD increased in the following month (and vice versa).
+For the FDP, too, only negative correlation coefficients can be detected, with the strongest negative correlation existing for the topic relating to the CSU (23).
+If the CSU got off worse in the online news, the poll value of the FDP have gone up.
+Another interesting observation is that the FDP's poll results correlate negatively with issues relating to the Jamaica coalition at lag 1 ($x_{t+1}$).
+So if the poll results for the FDP rose in one month, the following month the FDP was reported more negatively.
+The Green Party survey results show no negative correlation with any of the topics, except topic 30 at lag 1.
+It is striking that there seems to be a strong negative correlation between the SPD topics (1, 17,22) and the poll results of the left party (DIE LINKE).
+This means that the poll value of the left party has climbed if the topics related to the SPD were discussed more negatively.
+Same applies to the reporting on the GroKo (30) for lag -1.
+Conversely, the SPD's survey results correlate strongly positively with these topics, and also with topic 30 with a delay of one month.
+The CDU/CSU's survey results correlate most positively with topics relating to coalition negotiations.
+For the CDU/CSU, too, only significant negative correlations are discernible: the survey results correlate negatively with the topic of the Schulz v Merkel debate (10) and negatively with topic 30 with a delay of one month ($x_{t+1}$).
 
@@
 \end{figure}
-% Anders darstellen. 
-% Eventuell auch Lags zeigen.
 
-These results suggest that there is a link between the way parties are reported and the political trends within the population.
-It is obvious to assume that media reporting influences the electorate in its opinion-forming, even if this cannot be proven in this analysis.
+After the above figure have been analyzed, the following points can be summarized:
+
+\begin{enumerate}
+	\item Only the survey results of the SPD correlate positively with the emotional value of the topics.
+There seems to be a strong correlation between the way topics concerning the SPD are discussed in the online news and the poll results.
+	\item The poll results of the Left Party, on the other hand, seem to correlate negatively with the reporting on the SPD. 
+	\item Similar tendencies can also be seen with regard to the AfD, since here too the survey results correlate significantly negatively with the topics about the SPD and the grand coalition. 
+\end{enumerate}
+
+Summarizing the analyses from this and the previous section, it can be observed that the positive correlation between the emotional value of the reporting and the survey value of a party is particularly large if the reporting is conspicuously negative.
 
@@
 
-The purpose of this paper was to examine (1) whether the political reporting of different content providers distinguishes itself and (2) whether this reporting has an influence on the opinion-forming process of the voters.
+The purpose of this paper was to examine (1) whether the political reporting of different media differs in terms of topic frequency and topic tonality and (2) whether this reporting correlates with the opinion-forming process of the voters.
 Regarding (1) the analysis revealed that there are differences between the media considered, both in terms of topic prevalence and the way in which these topics are discussed.
-Although the issues are discussed negatively overall, there are still differences, especially regarding to the coalition negotiations.
+Although overall all topics are discussed negatively, there are still differences, especially regarding the coalition negotiations.
 The smallest differences can be found for topic concerning the AfD.
 With regard to (2), the analysis has shown that the tonality of topics discussed by the SPD shows a strong positive correlation to current survey results.
-For CDU/CSU, issues relating to the various coalition negotiations tend to correlate positively with the survey results.
 Overall, there seems to be a link between reporting on political issues and electoral preferences.
@@
 \subsection*{Regression Results}\label{apx_coeff}
-
+\todo{round estimates}
 \input{tables/coeff1}
 \input{tables/coeff2}
-\input{tables/coeff3}
-\input{tables/coeff4}
-\input{tables/coeff5}
 

### 2018-04-09 paper/writing/tables/coeff2.tex
ccf

@@
 % latex table generated in R 3.4.2 by xtable 1.8-2 package
-% Thu Apr  5 15:04:12 2018
+% Mon Apr  9 18:06:44 2018
 \begin{table}[ht]
@@
   \hline
-70 & 10: M.Schulz, vs. A.Merkel & ZEIT ONLINE & 0.01 & 0.00 & 3.60 & 0.00 \\ 
-  71 & 11: politics \& democracy in GER & (Intercept) & 0.01 & 0.00 & 4.88 & 0.00 \\ 
-  72 & 11: politics \& democracy in GER & FOCUS ONLINE & 0.00 & 0.00 & 0.92 & 0.36 \\ 
-  73 & 11: politics \& democracy in GER & SPIEGEL ONLINE & -0.00 & 0.00 & -1.32 & 0.19 \\ 
-  74 & 11: politics \& democracy in GER & stern.de & -0.00 & 0.00 & -1.57 & 0.12 \\ 
-  75 & 11: politics \& democracy in GER & Tagesschau.de & -0.00 & 0.00 & -1.79 & 0.07 \\ 
-  76 & 11: politics \& democracy in GER & DIE WELT & 0.00 & 0.00 & 1.25 & 0.21 \\ 
-  77 & 11: politics \& democracy in GER & ZEIT ONLINE & 0.01 & 0.00 & 3.54 & 0.00 \\ 
-  78 & 12: Deportation of criminal Refugees & (Intercept) & 0.03 & 0.00 & 6.49 & 0.00 \\ 
-  79 & 12: Deportation of criminal Refugees & FOCUS ONLINE & 0.03 & 0.01 & 4.86 & 0.00 \\ 
-  80 & 12: Deportation of criminal Refugees & SPIEGEL ONLINE & 0.00 & 0.01 & 0.19 & 0.85 \\ 
-  81 & 12: Deportation of criminal Refugees & stern.de & 0.00 & 0.01 & 0.81 & 0.42 \\ 
-  82 & 12: Deportation of criminal Refugees & Tagesschau.de & 0.02 & 0.01 & 3.35 & 0.00 \\ 
-  83 & 12: Deportation of criminal Refugees & DIE WELT & 0.02 & 0.01 & 3.21 & 0.00 \\ 
-  84 & 12: Deportation of criminal Refugees & ZEIT ONLINE & -0.01 & 0.01 & -0.96 & 0.34 \\ 
-  85 & 13: A.Merkel, election campaign & (Intercept) & 0.02 & 0.00 & 9.43 & 0.00 \\ 
-  86 & 13: A.Merkel, election campaign & FOCUS ONLINE & 0.00 & 0.00 & 0.55 & 0.58 \\ 
-  87 & 13: A.Merkel, election campaign & SPIEGEL ONLINE & 0.00 & 0.00 & 1.01 & 0.31 \\ 
-  88 & 13: A.Merkel, election campaign & stern.de & 0.01 & 0.00 & 2.73 & 0.01 \\ 
-  89 & 13: A.Merkel, election campaign & Tagesschau.de & -0.01 & 0.00 & -1.71 & 0.09 \\ 
-  90 & 13: A.Merkel, election campaign & DIE WELT & 0.00 & 0.00 & 0.33 & 0.74 \\ 
-  91 & 13: A.Merkel, election campaign & ZEIT ONLINE & 0.00 & 0.00 & 1.13 & 0.26 \\ 
-  92 & 14: Text processing fail & (Intercept) & 0.01 & 0.00 & 9.65 & 0.00 \\ 
-  93 & 14: Text processing fail & FOCUS ONLINE & -0.01 & 0.00 & -6.04 & 0.00 \\ 
-  94 & 14: Text processing fail & SPIEGEL ONLINE & -0.01 & 0.00 & -7.20 & 0.00 \\ 
-  95 & 14: Text processing fail & stern.de & -0.01 & 0.00 & -7.04 & 0.00 \\ 
-  96 & 14: Text processing fail & Tagesschau.de & -0.01 & 0.00 & -6.19 & 0.00 \\ 
-  97 & 14: Text processing fail & DIE WELT & -0.01 & 0.00 & -6.39 & 0.00 \\ 
-  98 & 14: Text processing fail & ZEIT ONLINE & -0.01 & 0.00 & -4.30 & 0.00 \\ 
-  99 & 15: Israel, antisemitism, D.Trump & (Intercept) & 0.03 & 0.00 & 8.95 & 0.00 \\ 
-  100 & 15: Israel, antisemitism, D.Trump & FOCUS ONLINE & -0.01 & 0.00 & -1.39 & 0.17 \\ 
-  101 & 15: Israel, antisemitism, D.Trump & SPIEGEL ONLINE & -0.01 & 0.00 & -1.44 & 0.15 \\ 
-  102 & 15: Israel, antisemitism, D.Trump & stern.de & -0.01 & 0.00 & -1.66 & 0.10 \\ 
-  103 & 15: Israel, antisemitism, D.Trump & Tagesschau.de & -0.01 & 0.00 & -1.98 & 0.05 \\ 
-  104 & 15: Israel, antisemitism, D.Trump & DIE WELT & -0.01 & 0.00 & -1.63 & 0.10 \\ 
-  105 & 15: Israel, antisemitism, D.Trump & ZEIT ONLINE & -0.01 & 0.00 & -1.24 & 0.21 \\ 
-  106 & 16: Mix: political talkshows, Refugees & (Intercept) & 0.01 & 0.00 & 4.58 & 0.00 \\ 
-  107 & 16: Mix: political talkshows, Refugees & FOCUS ONLINE & 0.00 & 0.00 & 1.20 & 0.23 \\ 
-  108 & 16: Mix: political talkshows, Refugees & SPIEGEL ONLINE & -0.00 & 0.00 & -1.50 & 0.13 \\ 
-  109 & 16: Mix: political talkshows, Refugees & stern.de & -0.00 & 0.00 & -1.31 & 0.19 \\ 
-  110 & 16: Mix: political talkshows, Refugees & Tagesschau.de & -0.01 & 0.00 & -2.88 & 0.00 \\ 
-  111 & 16: Mix: political talkshows, Refugees & DIE WELT & 0.00 & 0.00 & 2.05 & 0.04 \\ 
-  112 & 16: Mix: political talkshows, Refugees & ZEIT ONLINE & -0.00 & 0.00 & -1.54 & 0.12 \\ 
-  113 & 17: Debates within SPD & (Intercept) & 0.04 & 0.00 & 10.09 & 0.00 \\ 
-  114 & 17: Debates within SPD & FOCUS ONLINE & -0.01 & 0.00 & -1.36 & 0.17 \\ 
-  115 & 17: Debates within SPD & SPIEGEL ONLINE & -0.01 & 0.00 & -2.20 & 0.03 \\ 
-  116 & 17: Debates within SPD & stern.de & -0.00 & 0.00 & -0.40 & 0.69 \\ 
-  117 & 17: Debates within SPD & Tagesschau.de & -0.01 & 0.00 & -3.04 & 0.00 \\ 
-  118 & 17: Debates within SPD & DIE WELT & -0.01 & 0.00 & -2.61 & 0.01 \\ 
-  119 & 17: Debates within SPD & ZEIT ONLINE & -0.01 & 0.00 & -1.70 & 0.09 \\ 
-  120 & 18: Election in Niedersachsen & (Intercept) & 0.02 & 0.00 & 5.93 & 0.00 \\ 
-  121 & 18: Election in Niedersachsen & FOCUS ONLINE & -0.00 & 0.00 & -0.72 & 0.47 \\ 
-  122 & 18: Election in Niedersachsen & SPIEGEL ONLINE & 0.01 & 0.00 & 1.67 & 0.10 \\ 
-  123 & 18: Election in Niedersachsen & stern.de & 0.01 & 0.00 & 1.91 & 0.06 \\ 
-  124 & 18: Election in Niedersachsen & Tagesschau.de & 0.00 & 0.00 & 0.46 & 0.65 \\ 
-  125 & 18: Election in Niedersachsen & DIE WELT & 0.00 & 0.00 & 0.49 & 0.62 \\ 
-  126 & 18: Election in Niedersachsen & ZEIT ONLINE & 0.01 & 0.00 & 2.37 & 0.02 \\ 
-  127 & 19: N.Lammert & (Intercept) & 0.00 & 0.00 & 5.17 & 0.00 \\ 
-  128 & 19: N.Lammert & FOCUS ONLINE & -0.00 & 0.00 & -1.48 & 0.14 \\ 
-  129 & 19: N.Lammert & SPIEGEL ONLINE & -0.00 & 0.00 & -0.71 & 0.48 \\ 
-  130 & 19: N.Lammert & stern.de & -0.00 & 0.00 & -1.64 & 0.10 \\ 
-  131 & 19: N.Lammert & Tagesschau.de & -0.00 & 0.00 & -2.38 & 0.02 \\ 
-  132 & 19: N.Lammert & DIE WELT & -0.00 & 0.00 & -1.80 & 0.07 \\ 
-  133 & 19: N.Lammert & ZEIT ONLINE & 0.00 & 0.00 & 1.50 & 0.13 \\ 
-  134 & 20: AfD, right-wing radicalism & (Intercept) & 0.02 & 0.00 & 6.12 & 0.00 \\ 
-  135 & 20: AfD, right-wing radicalism & FOCUS ONLINE & -0.00 & 0.00 & -0.66 & 0.51 \\ 
-  136 & 20: AfD, right-wing radicalism & SPIEGEL ONLINE & -0.00 & 0.00 & -0.75 & 0.45 \\ 
-  137 & 20: AfD, right-wing radicalism & stern.de & -0.00 & 0.00 & -0.86 & 0.39 \\ 
-  138 & 20: AfD, right-wing radicalism & Tagesschau.de & 0.00 & 0.00 & 0.06 & 0.95 \\ 
-  139 & 20: AfD, right-wing radicalism & DIE WELT & 0.00 & 0.00 & 0.49 & 0.62 \\ 
-  140 & 20: AfD, right-wing radicalism & ZEIT ONLINE & -0.00 & 0.00 & -0.50 & 0.62 \\ 
+57 & 23: CSU, Söder \& Seehover & (Intercept) & 0.04 & 0.00 & 9.36 & 0.00 \\ 
+  58 & 23: CSU, Söder \& Seehover & FOCUS ONLINE & -0.00 & 0.00 & -0.74 & 0.46 \\ 
+  59 & 23: CSU, Söder \& Seehover & SPIEGEL ONLINE & 0.01 & 0.00 & 1.29 & 0.20 \\ 
+  60 & 23: CSU, Söder \& Seehover & stern.de & -0.00 & 0.00 & -0.36 & 0.72 \\ 
+  61 & 23: CSU, Söder \& Seehover & Tagesschau.de & -0.01 & 0.01 & -1.13 & 0.26 \\ 
+  62 & 23: CSU, Söder \& Seehover & DIE WELT & -0.01 & 0.00 & -1.16 & 0.25 \\ 
+  63 & 23: CSU, Söder \& Seehover & ZEIT ONLINE & 0.00 & 0.01 & 0.44 & 0.66 \\ 
+  64 & 26: Jamaica fail, Reelections or GroKo? & (Intercept) & 0.03 & 0.00 & 12.15 & 0.00 \\ 
+  65 & 26: Jamaica fail, Reelections or GroKo? & FOCUS ONLINE & -0.00 & 0.00 & -1.17 & 0.24 \\ 
+  66 & 26: Jamaica fail, Reelections or GroKo? & SPIEGEL ONLINE & -0.00 & 0.00 & -1.12 & 0.26 \\ 
+  67 & 26: Jamaica fail, Reelections or GroKo? & stern.de & -0.01 & 0.00 & -3.56 & 0.00 \\ 
+  68 & 26: Jamaica fail, Reelections or GroKo? & Tagesschau.de & -0.01 & 0.00 & -2.61 & 0.01 \\ 
+  69 & 26: Jamaica fail, Reelections or GroKo? & DIE WELT & -0.01 & 0.00 & -3.37 & 0.00 \\ 
+  70 & 26: Jamaica fail, Reelections or GroKo? & ZEIT ONLINE & -0.01 & 0.00 & -1.44 & 0.15 \\ 
+  71 & 27: Jamaica Coalition debates & (Intercept) & 0.07 & 0.00 & 14.34 & 0.00 \\ 
+  72 & 27: Jamaica Coalition debates & FOCUS ONLINE & -0.03 & 0.01 & -5.20 & 0.00 \\ 
+  73 & 27: Jamaica Coalition debates & SPIEGEL ONLINE & -0.01 & 0.01 & -1.40 & 0.16 \\ 
+  74 & 27: Jamaica Coalition debates & stern.de & -0.03 & 0.01 & -5.13 & 0.00 \\ 
+  75 & 27: Jamaica Coalition debates & Tagesschau.de & -0.02 & 0.01 & -2.75 & 0.01 \\ 
+  76 & 27: Jamaica Coalition debates & DIE WELT & -0.01 & 0.01 & -1.38 & 0.17 \\ 
+  77 & 27: Jamaica Coalition debates & ZEIT ONLINE & -0.00 & 0.01 & -0.51 & 0.61 \\ 
+  78 & 30: AfD, F.Petry \& Meuthen & (Intercept) & 0.03 & 0.00 & 7.87 & 0.00 \\ 
+  79 & 30: AfD, F.Petry \& Meuthen & FOCUS ONLINE & -0.00 & 0.00 & -1.25 & 0.21 \\ 
+  80 & 30: AfD, F.Petry \& Meuthen & SPIEGEL ONLINE & 0.00 & 0.00 & 0.49 & 0.62 \\ 
+  81 & 30: AfD, F.Petry \& Meuthen & stern.de & -0.00 & 0.00 & -0.95 & 0.34 \\ 
+  82 & 30: AfD, F.Petry \& Meuthen & Tagesschau.de & -0.01 & 0.00 & -3.23 & 0.00 \\ 
+  83 & 30: AfD, F.Petry \& Meuthen & DIE WELT & -0.01 & 0.00 & -2.64 & 0.01 \\ 
+  84 & 30: AfD, F.Petry \& Meuthen & ZEIT ONLINE & 0.00 & 0.00 & 0.92 & 0.36 \\ 
+  85 & 32: AfD, Gauland \& Weidel & (Intercept) & 0.02 & 0.00 & 6.84 & 0.00 \\ 
+  86 & 32: AfD, Gauland \& Weidel & FOCUS ONLINE & 0.00 & 0.00 & 0.14 & 0.89 \\ 
+  87 & 32: AfD, Gauland \& Weidel & SPIEGEL ONLINE & -0.00 & 0.00 & -0.17 & 0.86 \\ 
+  88 & 32: AfD, Gauland \& Weidel & stern.de & 0.01 & 0.00 & 1.63 & 0.10 \\ 
+  89 & 32: AfD, Gauland \& Weidel & Tagesschau.de & -0.01 & 0.00 & -1.37 & 0.17 \\ 
+  90 & 32: AfD, Gauland \& Weidel & DIE WELT & 0.01 & 0.00 & 1.49 & 0.14 \\ 
+  91 & 32: AfD, Gauland \& Weidel & ZEIT ONLINE & 0.01 & 0.00 & 1.25 & 0.21 \\ 
+  92 & 37: AfD \& DIE LINKE in parliament & (Intercept) & 0.02 & 0.00 & 7.01 & 0.00 \\ 
+  93 & 37: AfD \& DIE LINKE in parliament & FOCUS ONLINE & 0.01 & 0.00 & 1.16 & 0.25 \\ 
+  94 & 37: AfD \& DIE LINKE in parliament & SPIEGEL ONLINE & 0.01 & 0.00 & 2.83 & 0.00 \\ 
+  95 & 37: AfD \& DIE LINKE in parliament & stern.de & 0.00 & 0.00 & 0.19 & 0.85 \\ 
+  96 & 37: AfD \& DIE LINKE in parliament & Tagesschau.de & 0.01 & 0.00 & 1.09 & 0.28 \\ 
+  97 & 37: AfD \& DIE LINKE in parliament & DIE WELT & 0.00 & 0.00 & 0.37 & 0.71 \\ 
+  98 & 37: AfD \& DIE LINKE in parliament & ZEIT ONLINE & 0.01 & 0.00 & 2.13 & 0.03 \\ 
+  99 & 46: CDU & (Intercept) & 0.02 & 0.00 & 7.35 & 0.00 \\ 
+  100 & 46: CDU & FOCUS ONLINE & -0.00 & 0.00 & -0.32 & 0.75 \\ 
+  101 & 46: CDU & SPIEGEL ONLINE & 0.00 & 0.00 & 0.71 & 0.48 \\ 
+  102 & 46: CDU & stern.de & -0.01 & 0.00 & -1.98 & 0.05 \\ 
+  103 & 46: CDU & Tagesschau.de & -0.01 & 0.00 & -3.37 & 0.00 \\ 
+  104 & 46: CDU & DIE WELT & -0.00 & 0.00 & -0.52 & 0.60 \\ 
+  105 & 46: CDU & ZEIT ONLINE & -0.00 & 0.00 & -0.08 & 0.93 \\ 
    \hline

### 2018-04-10 paper/docs/04_Modelresults_50.Rmd
typos

@@
 
-print(xtable(coeff_tab[1:56,], type="latex"), file="../writing/tables/coeff1.tex" )
-print(xtable(coeff_tab[57:nrow(coeff_tab),], type="latex"), file="../writing/tables/coeff2.tex" )
+print(xtable(coeff_tab[1:56,], type="latex", digits=3), 
+      file="../writing/tables/coeff1.tex" )
+print(xtable(coeff_tab[57:nrow(coeff_tab),], type="latex", digits=3), 
+      file="../writing/tables/coeff2.tex" )
 ```
@@
            label = obs)) +
-  facet_wrap(~topic_name, nrow = 3, labeller=labeller(topic_name = linebreak)) +
+  facet_wrap(~topic_name, nrow = 3, 
+             labeller=labeller(topic_name = linebreak)) +
   geom_col(fill = col[3], alpha = 0.8) +
@@
   scale_x_date(breaks = date_breaks("1 month"), 
-               labels = date_format("%b", tz ="CET")) +
+               labels = date_format("%b-%y", tz ="CET")) +
   theme(strip.text = element_text(size=14),
     axis.text.y = element_text(size=10),
-        axis.text.x = element_text(size = 10, angle = 45))
+    axis.title.y = element_text(size=12),
+        axis.text.x = element_text(size = 12, angle = 45))
 
 ggsave(filename = "../figs/sentscore_monthly.png", plot = p1, 
-       height = 10, width = 12)
+       height = 10, width = 13)
 ```
@@
   theme(strip.text = element_text(size = 11),
-    axis.text.y = element_text(size = 12),
+    axis.text.y = element_text(size = 14),
         axis.text.x = element_text(size=8, angle = 90),
@@
 
+Cross correlation at lag 0
+```{r}
+# Table
+corr %>% 
+  filter(lag == 0) %>%
+  select(-lag) %>% 
+  spread(Var2, correlation) -> corr_tab
+
+print(xtable(corr_tab, type="latex", digits=3,
+                   caption = "Cross Correlation at lag 0"),
+      file="../writing/tables/corr.tex" )
+```
+
 ```{r fig.height=6, fig.width=8}
+# Figure
 p <- corr %>%

### 2018-04-10 paper/writing/structure.tex
typos

@@
 
-The sentiment analysis is conducted with those documents that are assigned to one of the above selected topics with the highest probability.
+The sentiment analysis is performed with the documents for which one of the above topics has the highest posterior probability and if this probability is greater than 30\%.
 A dictionary-based method is then applied on the remaining 5611 documents with the aim to measure the tone (or sentiment) of a document.
@@
 To conduct such an analysis, a lists of words (dictionary) associated with a given emotion, such as negativity is pre-defined by the analyst.
-The document is then deconstructed into individual words and the frequencies of words contained in a given dictionary are then calculated.
+The document is then deconstructed into individual words and the frequencies of words contained in a given dictionary are calculated.
 
-Such lexical or “bag-of-words” approaches are widely presented in the finance literature to  determine  the  effect  of  central  banks’  monetary  policy  communications on asset prices and real variables (\citet{nyman_news_2018} \citep{tetlock_giving_2007}, \citep{tetlock_more_2008}).
+Such lexical or “bag-of-words” approaches are widely presented in the finance literature to determine the effect of central banks' monetary policy communications on asset prices and real variables (\citet{nyman_news_2018} \citep{tetlock_giving_2007}, \citep{tetlock_more_2008}).
 \citet{hansen_shocking_2016} use a similar approach to measure "the two Ts" (Topic and tone).
@@
 available here: http://wortschatz.uni-leipzig.de/de/download}, is a publicly available German-language resource for sentiment analysis, opinion mining etc.
-The current version of SentiWS (v1.8b) contains 1,650 positive and 1,818 negative words, which sum up to 15,649 positive and 15,632 negative word forms incl.
-their inflections, respectively.
+The current version of SentiWS (v1.8b) contains 1,650 positive and 1,818 negative words, which sum up to 15,649 positive and 15,632 negative word forms including their inflections, respectively.
 The sentiment score for each document $d$ is calculated  based on the weighted polarity values for a word, defined on an interval between -1 and 1.
@@
 
-The following figure shows the results of the analysis for each topic on a monthly basis, aggregated on all newspapers.
+Figure \ref{fig_sentscore_monthly} shows the results of the analysis for each topic on a monthly basis, aggregated on all newspapers.
 Each sentiment value is weighted by the relative share of the topic in the overall reporting of that month.
@@
 An exception is topic 27 concerning the Jamaica coalition negotiations, which shows a positive sentiment value for a short period of time (October 2017).
-In the following month (November 2017), after it became clear that there would be no coalition between the CDU/CSU/CSU, FDP and Die Grünen, the value of this topic as well as that of topic 26 drops rapidly, but then rises again in February.
-Concerning the issues that discuss the great coalition between CDU/CSU/CSU and SPD, it is evident that the overall tone is in which this topic is discussed is generally decreasing from November 2017 to January 2018, but in the following February, the sentiment value of this topic rises.
+In the following month (November 2017), after it became clear that there would be no coalition between the CDU/CSU, FDP and Die Grünen, the value of this topic as well as that of topic 26 drops rapidly, but then rises again in February.
+Concerning the issues that discuss the great coalition between CDU/CSU and SPD, it is evident that the overall tone in which this topic is discussed is generally decreasing from November 2017 to January 2018, but in the following February, the sentiment value of this topic rises.
 However, the sentiment score of topics that deal with the SPD (1, 17, 22) is diminishing in the course of time, with topic 17 recording the largest decline.
@@
 
-If aggregated by news provider, some differences between the sites are discernible (Figure \ref{fig_sentscore_site}).
-To begin with, it can be noted that on average all topics are discussed negatively by all news providers, except topic 22, which mainly covers the personnel debates of the SPD and has a positive value at Tagesschau.de.
-One striking feature is the way in which the Jamaica negotiations and their failure are reported (topics 27 and 26).
-Although all providers discuss this topics in a negative light, Bild.de reports them particularly negative.
-The same applies to the reports on the grand coalition, where the value of ZEIT ONLINE is the most negative.
-
-We use two different Figures to analyze the differences between the media outlets graphically: We use the bar plot to examine the polarity tendencies of the individual topics within a medium (Figure \ref{fig_sentscore_site}) and the radar plot to observe the differences between the media (Figure \ref{fig_sentscore_radar}).
+In order to analyze the differences between the news websites, two different figures are considered: The bar plot is used to examine the polarity tendencies of the individual topics for a the respective website (Figure \ref{fig_sentscore_site}) and the radar plot is considered to observe the differences between the websites (Figure \ref{fig_sentscore_radar}).
 
 Starting with the bar plot it becomes apparent that all topics are discussed negatively, except topic 23 at Tagesschau.de.
-At Bild.de, the topics that include the coalition negotiations (26,27,4) and the SPD (1,17) are the most negative.
+At Bild.de, the topics that include the coalition negotiations (26, 27, 4) and the SPD (1, 17) are the most negative.
 The topics relating to AfD (20,30,32,37) are also discussed more negatively.
-Looking at the values of WELT ONLINE, two of the AfD topics have the most negative value (32.20).
-Topic 27 concerning the Jamaica Coalition (27) and the Grand Coalition (4) also score relatively negatively.
-Concerning FOCUS ONLINE, it is mainly topics that relate to the SPD (27, 17, 4, 1) that have a strong negative sentiment value, together with topic 32 and 37.
+Looking at the values of DIE WELT, two of the AfD topics have the most negative value (32, 20).
+Topic 27 concerning the Jamaica Coalition and the Grand Coalition (4) also score relatively negatively.
+Concerning FOCUS ONLINE, it is mainly topics that relate to the SPD (27, 17, 4, 1) that have a strong negative sentiment value, together with topic 32 and 37 - both related to AfD.
 Turning to SPIEGEL ONLINE, it is noticeable that the difference in sentiment value between the individual topics is less pronounced.
-Topics 13 and 10 stand out as comparatively less negative.
+Topics 13 (election campaign of A.Merkel) and 10 (A.Merkel vs M.Schulz) stand out as comparatively less negative.
 However, these issues are also the least negatively discussed in the other media.
@@
 A good overview of how differently the topics are discussed by the providers is shown in Figure \ref{fig_sentscore_radar}.
-It becomes evident that the sentiment value of the media differs most notably with regard to topic 27 and topic 4, i.
-e.
+It becomes evident that the sentiment value of the media differs most notably with regard to topic 27 and topic 4, i.e.
 the topics on which the coalition negotiations are reported.
@@
 \begin{figure}[H]
-	\caption{Sentiment Score by news wire}
+	\caption{Radar Plot of Sentiment Scores}
 	\begin{center}
@@
 \begin{enumerate}
-	\item The sentiment value of the SPD is decreasing over time, especially in regard to internal votes. 
+	\item The sentiment value of the SPD is decreasing over time, especially regarding debates within the party (topic 17). 
 	\item The topics relating to the coalition talks on Jamaica (26, 27) and the grand coalition (4) are discussed rather critically, but they also show the greatest differences between the media. 
-In contrast, the tonality of the topics in relation to the AfD shows rather small differences.
+	\item In contrast, the tonality of the topics in relation to the AfD shows rather small differences. 
 	\item Overall, the sentiment value at Tagesschau.de is the least negative and only shows a comparatively strong negative value at topic 23, concerning the CSU.
@@
 \subsection{News sentiment and poll data}\label{ch_correlation}
-% add ccf table
 
@@
 The correlation value for $h=0$ indicates the contemporary correlation between the two time series.
-Based on the coefficients of the cross correlation estimation shown in Figure \ref{fig_ccf}, the significant correlations between topic sentiment and survey value are evaluated for each party.
-It is important to note that no causal relationships are described below, but that only the correlation between the two time series is described.
+Based on the coefficients of the cross correlation estimation shown in Figure \ref{fig_ccf}, the significant correlations between topic sentiment and survey value are evaluated for each party.\footnote{The value of the cross correlation coefficients for lag 0 can be found in the Appendix (Table \ref{apx_corr})} It is important to note that no causal relationships are described below, but that only the correlation between the two time series is described.
 
@@
 The Green Party survey results show no negative correlation with any of the topics, except topic 30 at lag 1.
-It is striking that there seems to be a strong negative correlation between the SPD topics (1, 17,22) and the poll results of the left party (DIE LINKE).
+It is striking that there seems to be a strong negative correlation between the SPD topics (1, 17, 22) and the poll results of the left party (DIE LINKE).
 This means that the poll value of the left party has climbed if the topics related to the SPD were discussed more negatively.
@@
 Conversely, the SPD's survey results correlate strongly positively with these topics, and also with topic 30 with a delay of one month.
-The CDU/CSU's survey results correlate most positively with topics relating to coalition negotiations.
 For the CDU/CSU, too, only significant negative correlations are discernible: the survey results correlate negatively with the topic of the Schulz v Merkel debate (10) and negatively with topic 30 with a delay of one month ($x_{t+1}$).
@@
 
+\pagebreak
+
 \printbibliography
+
+\pagebreak
+
 \section*{Appendix}
 
-\subsection*{Most frequent words\label{apx_tf}
+\subsection*{Most frequent words}\label{apx_tf}
 % 1, 2
@@
 \subsection*{Regression Results}\label{apx_coeff}
-\todo{round estimates}
 \input{tables/coeff1}
@@
 
+\subsection*{Cross Correlation Coefficient}
+\input{tables/corr}
+
 \end{document}

### 2018-04-10 paper/writing/tables/coeff2.tex
typos

@@
 % latex table generated in R 3.4.2 by xtable 1.8-2 package
-% Mon Apr  9 18:06:44 2018
+% Tue Apr 10 09:26:23 2018
 \begin{table}[ht]
@@
   \hline
-57 & 23: CSU, Söder \& Seehover & (Intercept) & 0.04 & 0.00 & 9.36 & 0.00 \\ 
-  58 & 23: CSU, Söder \& Seehover & FOCUS ONLINE & -0.00 & 0.00 & -0.74 & 0.46 \\ 
-  59 & 23: CSU, Söder \& Seehover & SPIEGEL ONLINE & 0.01 & 0.00 & 1.29 & 0.20 \\ 
-  60 & 23: CSU, Söder \& Seehover & stern.de & -0.00 & 0.00 & -0.36 & 0.72 \\ 
-  61 & 23: CSU, Söder \& Seehover & Tagesschau.de & -0.01 & 0.01 & -1.13 & 0.26 \\ 
-  62 & 23: CSU, Söder \& Seehover & DIE WELT & -0.01 & 0.00 & -1.16 & 0.25 \\ 
-  63 & 23: CSU, Söder \& Seehover & ZEIT ONLINE & 0.00 & 0.01 & 0.44 & 0.66 \\ 
-  64 & 26: Jamaica fail, Reelections or GroKo? & (Intercept) & 0.03 & 0.00 & 12.15 & 0.00 \\ 
-  65 & 26: Jamaica fail, Reelections or GroKo? & FOCUS ONLINE & -0.00 & 0.00 & -1.17 & 0.24 \\ 
-  66 & 26: Jamaica fail, Reelections or GroKo? & SPIEGEL ONLINE & -0.00 & 0.00 & -1.12 & 0.26 \\ 
-  67 & 26: Jamaica fail, Reelections or GroKo? & stern.de & -0.01 & 0.00 & -3.56 & 0.00 \\ 
-  68 & 26: Jamaica fail, Reelections or GroKo? & Tagesschau.de & -0.01 & 0.00 & -2.61 & 0.01 \\ 
-  69 & 26: Jamaica fail, Reelections or GroKo? & DIE WELT & -0.01 & 0.00 & -3.37 & 0.00 \\ 
-  70 & 26: Jamaica fail, Reelections or GroKo? & ZEIT ONLINE & -0.01 & 0.00 & -1.44 & 0.15 \\ 
-  71 & 27: Jamaica Coalition debates & (Intercept) & 0.07 & 0.00 & 14.34 & 0.00 \\ 
-  72 & 27: Jamaica Coalition debates & FOCUS ONLINE & -0.03 & 0.01 & -5.20 & 0.00 \\ 
-  73 & 27: Jamaica Coalition debates & SPIEGEL ONLINE & -0.01 & 0.01 & -1.40 & 0.16 \\ 
-  74 & 27: Jamaica Coalition debates & stern.de & -0.03 & 0.01 & -5.13 & 0.00 \\ 
-  75 & 27: Jamaica Coalition debates & Tagesschau.de & -0.02 & 0.01 & -2.75 & 0.01 \\ 
-  76 & 27: Jamaica Coalition debates & DIE WELT & -0.01 & 0.01 & -1.38 & 0.17 \\ 
-  77 & 27: Jamaica Coalition debates & ZEIT ONLINE & -0.00 & 0.01 & -0.51 & 0.61 \\ 
-  78 & 30: AfD, F.Petry \& Meuthen & (Intercept) & 0.03 & 0.00 & 7.87 & 0.00 \\ 
-  79 & 30: AfD, F.Petry \& Meuthen & FOCUS ONLINE & -0.00 & 0.00 & -1.25 & 0.21 \\ 
-  80 & 30: AfD, F.Petry \& Meuthen & SPIEGEL ONLINE & 0.00 & 0.00 & 0.49 & 0.62 \\ 
-  81 & 30: AfD, F.Petry \& Meuthen & stern.de & -0.00 & 0.00 & -0.95 & 0.34 \\ 
-  82 & 30: AfD, F.Petry \& Meuthen & Tagesschau.de & -0.01 & 0.00 & -3.23 & 0.00 \\ 
-  83 & 30: AfD, F.Petry \& Meuthen & DIE WELT & -0.01 & 0.00 & -2.64 & 0.01 \\ 
-  84 & 30: AfD, F.Petry \& Meuthen & ZEIT ONLINE & 0.00 & 0.00 & 0.92 & 0.36 \\ 
-  85 & 32: AfD, Gauland \& Weidel & (Intercept) & 0.02 & 0.00 & 6.84 & 0.00 \\ 
-  86 & 32: AfD, Gauland \& Weidel & FOCUS ONLINE & 0.00 & 0.00 & 0.14 & 0.89 \\ 
-  87 & 32: AfD, Gauland \& Weidel & SPIEGEL ONLINE & -0.00 & 0.00 & -0.17 & 0.86 \\ 
-  88 & 32: AfD, Gauland \& Weidel & stern.de & 0.01 & 0.00 & 1.63 & 0.10 \\ 
-  89 & 32: AfD, Gauland \& Weidel & Tagesschau.de & -0.01 & 0.00 & -1.37 & 0.17 \\ 
-  90 & 32: AfD, Gauland \& Weidel & DIE WELT & 0.01 & 0.00 & 1.49 & 0.14 \\ 
-  91 & 32: AfD, Gauland \& Weidel & ZEIT ONLINE & 0.01 & 0.00 & 1.25 & 0.21 \\ 
-  92 & 37: AfD \& DIE LINKE in parliament & (Intercept) & 0.02 & 0.00 & 7.01 & 0.00 \\ 
-  93 & 37: AfD \& DIE LINKE in parliament & FOCUS ONLINE & 0.01 & 0.00 & 1.16 & 0.25 \\ 
-  94 & 37: AfD \& DIE LINKE in parliament & SPIEGEL ONLINE & 0.01 & 0.00 & 2.83 & 0.00 \\ 
-  95 & 37: AfD \& DIE LINKE in parliament & stern.de & 0.00 & 0.00 & 0.19 & 0.85 \\ 
-  96 & 37: AfD \& DIE LINKE in parliament & Tagesschau.de & 0.01 & 0.00 & 1.09 & 0.28 \\ 
-  97 & 37: AfD \& DIE LINKE in parliament & DIE WELT & 0.00 & 0.00 & 0.37 & 0.71 \\ 
-  98 & 37: AfD \& DIE LINKE in parliament & ZEIT ONLINE & 0.01 & 0.00 & 2.13 & 0.03 \\ 
-  99 & 46: CDU & (Intercept) & 0.02 & 0.00 & 7.35 & 0.00 \\ 
-  100 & 46: CDU & FOCUS ONLINE & -0.00 & 0.00 & -0.32 & 0.75 \\ 
-  101 & 46: CDU & SPIEGEL ONLINE & 0.00 & 0.00 & 0.71 & 0.48 \\ 
-  102 & 46: CDU & stern.de & -0.01 & 0.00 & -1.98 & 0.05 \\ 
-  103 & 46: CDU & Tagesschau.de & -0.01 & 0.00 & -3.37 & 0.00 \\ 
-  104 & 46: CDU & DIE WELT & -0.00 & 0.00 & -0.52 & 0.60 \\ 
-  105 & 46: CDU & ZEIT ONLINE & -0.00 & 0.00 & -0.08 & 0.93 \\ 
+57 & 23: CSU, Söder \& Seehover & (Intercept) & 0.035 & 0.004 & 9.361 & 0.000 \\ 
+  58 & 23: CSU, Söder \& Seehover & FOCUS ONLINE & -0.003 & 0.005 & -0.739 & 0.460 \\ 
+  59 & 23: CSU, Söder \& Seehover & SPIEGEL ONLINE & 0.006 & 0.005 & 1.286 & 0.199 \\ 
+  60 & 23: CSU, Söder \& Seehover & stern.de & -0.002 & 0.004 & -0.358 & 0.720 \\ 
+  61 & 23: CSU, Söder \& Seehover & Tagesschau.de & -0.006 & 0.005 & -1.132 & 0.257 \\ 
+  62 & 23: CSU, Söder \& Seehover & DIE WELT & -0.005 & 0.005 & -1.157 & 0.247 \\ 
+  63 & 23: CSU, Söder \& Seehover & ZEIT ONLINE & 0.002 & 0.005 & 0.437 & 0.662 \\ 
+  64 & 26: Jamaica fail, Reelections or GroKo? & (Intercept) & 0.035 & 0.003 & 12.152 & 0.000 \\ 
+  65 & 26: Jamaica fail, Reelections or GroKo? & FOCUS ONLINE & -0.004 & 0.004 & -1.174 & 0.240 \\ 
+  66 & 26: Jamaica fail, Reelections or GroKo? & SPIEGEL ONLINE & -0.004 & 0.004 & -1.121 & 0.262 \\ 
+  67 & 26: Jamaica fail, Reelections or GroKo? & stern.de & -0.012 & 0.003 & -3.560 & 0.000 \\ 
+  68 & 26: Jamaica fail, Reelections or GroKo? & Tagesschau.de & -0.010 & 0.004 & -2.608 & 0.009 \\ 
+  69 & 26: Jamaica fail, Reelections or GroKo? & DIE WELT & -0.012 & 0.004 & -3.374 & 0.001 \\ 
+  70 & 26: Jamaica fail, Reelections or GroKo? & ZEIT ONLINE & -0.006 & 0.004 & -1.442 & 0.149 \\ 
+  71 & 27: Jamaica Coalition debates & (Intercept) & 0.066 & 0.005 & 14.338 & 0.000 \\ 
+  72 & 27: Jamaica Coalition debates & FOCUS ONLINE & -0.029 & 0.006 & -5.204 & 0.000 \\ 
+  73 & 27: Jamaica Coalition debates & SPIEGEL ONLINE & -0.009 & 0.006 & -1.400 & 0.161 \\ 
+  74 & 27: Jamaica Coalition debates & stern.de & -0.028 & 0.005 & -5.130 & 0.000 \\ 
+  75 & 27: Jamaica Coalition debates & Tagesschau.de & -0.018 & 0.006 & -2.752 & 0.006 \\ 
+  76 & 27: Jamaica Coalition debates & DIE WELT & -0.007 & 0.005 & -1.376 & 0.169 \\ 
+  77 & 27: Jamaica Coalition debates & ZEIT ONLINE & -0.003 & 0.006 & -0.509 & 0.611 \\ 
+  78 & 30: AfD, F.Petry \& Meuthen & (Intercept) & 0.026 & 0.003 & 7.873 & 0.000 \\ 
+  79 & 30: AfD, F.Petry \& Meuthen & FOCUS ONLINE & -0.005 & 0.004 & -1.248 & 0.212 \\ 
+  80 & 30: AfD, F.Petry \& Meuthen & SPIEGEL ONLINE & 0.002 & 0.004 & 0.490 & 0.624 \\ 
+  81 & 30: AfD, F.Petry \& Meuthen & stern.de & -0.004 & 0.004 & -0.950 & 0.342 \\ 
+  82 & 30: AfD, F.Petry \& Meuthen & Tagesschau.de & -0.014 & 0.004 & -3.234 & 0.001 \\ 
+  83 & 30: AfD, F.Petry \& Meuthen & DIE WELT & -0.011 & 0.004 & -2.640 & 0.008 \\ 
+  84 & 30: AfD, F.Petry \& Meuthen & ZEIT ONLINE & 0.004 & 0.004 & 0.918 & 0.359 \\ 
+  85 & 32: AfD, Gauland \& Weidel & (Intercept) & 0.023 & 0.003 & 6.837 & 0.000 \\ 
+  86 & 32: AfD, Gauland \& Weidel & FOCUS ONLINE & 0.001 & 0.004 & 0.141 & 0.888 \\ 
+  87 & 32: AfD, Gauland \& Weidel & SPIEGEL ONLINE & -0.001 & 0.004 & -0.170 & 0.865 \\ 
+  88 & 32: AfD, Gauland \& Weidel & stern.de & 0.007 & 0.004 & 1.627 & 0.104 \\ 
+  89 & 32: AfD, Gauland \& Weidel & Tagesschau.de & -0.006 & 0.005 & -1.371 & 0.170 \\ 
+  90 & 32: AfD, Gauland \& Weidel & DIE WELT & 0.006 & 0.004 & 1.494 & 0.135 \\ 
+  91 & 32: AfD, Gauland \& Weidel & ZEIT ONLINE & 0.006 & 0.005 & 1.246 & 0.213 \\ 
+  92 & 37: AfD \& DIE LINKE in parliament & (Intercept) & 0.025 & 0.003 & 7.013 & 0.000 \\ 
+  93 & 37: AfD \& DIE LINKE in parliament & FOCUS ONLINE & 0.005 & 0.004 & 1.159 & 0.246 \\ 
+  94 & 37: AfD \& DIE LINKE in parliament & SPIEGEL ONLINE & 0.013 & 0.005 & 2.827 & 0.005 \\ 
+  95 & 37: AfD \& DIE LINKE in parliament & stern.de & 0.001 & 0.004 & 0.190 & 0.850 \\ 
+  96 & 37: AfD \& DIE LINKE in parliament & Tagesschau.de & 0.005 & 0.005 & 1.089 & 0.276 \\ 
+  97 & 37: AfD \& DIE LINKE in parliament & DIE WELT & 0.002 & 0.004 & 0.369 & 0.712 \\ 
+  98 & 37: AfD \& DIE LINKE in parliament & ZEIT ONLINE & 0.010 & 0.005 & 2.128 & 0.033 \\ 
+  99 & 46: CDU & (Intercept) & 0.019 & 0.003 & 7.348 & 0.000 \\ 
+  100 & 46: CDU & FOCUS ONLINE & -0.001 & 0.003 & -0.321 & 0.748 \\ 
+  101 & 46: CDU & SPIEGEL ONLINE & 0.002 & 0.003 & 0.707 & 0.479 \\ 
+  102 & 46: CDU & stern.de & -0.006 & 0.003 & -1.979 & 0.048 \\ 
+  103 & 46: CDU & Tagesschau.de & -0.011 & 0.003 & -3.373 & 0.001 \\ 
+  104 & 46: CDU & DIE WELT & -0.002 & 0.003 & -0.523 & 0.601 \\ 
+  105 & 46: CDU & ZEIT ONLINE & -0.000 & 0.004 & -0.085 & 0.932 \\ 
    \hline

### 2018-04-10 paper/docs/func/functions.R

@@ -219,5 +219,9 @@ calculate_week = function(week, year) {
 ###################################
 
 linebreak <- function(s) {
-  gsub('(.{1,12})(\\s|$)', '\\1\n', s)
+  gsub('(.{1,15})(\\s|$)', '\\1\n', s)
+}
+
+linebreak_n <- function(s,n) {
+  gsub(paste0('(.{1,',n,'})(\\s|$)'), '\\1\n', s)
 }

### 2018-04-10 paper/docs/04_Modelresults_50.Rmd
change plots

@@
           alpha = 0) +
-  labs(title = "Sentiment scores Jun 2017-March 2018") +
-  guides(col = guide_legend(ncol = 1)) +
-  theme(legend.position = "right",
-        axis.text.x = element_text(size = 10),
+  labs(title = "") +
+  guides(col = guide_legend(ncol = 7)) +
+  theme(legend.position = "bottom",
+        legend.text = element_text(size=14),
+        legend.title = element_text(size=0),
+        axis.text.x = element_text(size = 16),
         axis.text.y = element_blank(),
@@
 
-ggsave(filename = "../figs/sentscore_radar.png", width = 9,
-       height = 7,
+ggsave(filename = "../figs/sentscore_radar.png", width = 12,
+       height = 10,
        plot = p)

### 2018-04-15 paper/docs/04_Modelresults_50.Rmd
push current paper status

@@
 ---
-title: "Whats reported in the news?"
+title: "Topic and tone of political news articles in German online media."
 subtitle: ""
 author: "Franziska Löw"
-date: ""
+date: "April 2018"
 output: 
@@
   theme(
-    axis.text = element_text(size = 6),
+    axis.text.x = element_text(size = 9),
       legend.position   = "none"
@@
 filename = "../figs/bar.png", device = "png", 
-width = 6, height = 4,
+width = 7, height = 4,
         dpi = 600)
@@
   scale_color_manual(values = col) +
-  labs(x="", y="number of articles",color="") +
+  labs(x="", y="Number of Articles",color="") +
   scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
@@
 
-<img src="../figs/wordcloud_Bild.de.png", width = "49%" title="Bild.de">
-<img src="../figs/wordcloud_DIE WELT.png", width = "49%" title="DIE WELT">
-<img src="../figs/wordcloud_FOCUS ONLINE.png", width = "49%" title="FOCUS ONLINE">
-<img src="../figs/wordcloud_SPIEGEL ONLINE.png", width = "49%" title="SPIEGEL ONLINE">
-<img src="../figs/wordcloud_stern.de.png", width = "49%" title="Stern.de">
-<img src="../figs/wordcloud_Tagesschau.de.png", width = "49%" title="Tagesschau.de">
-<img src="../figs/wordcloud_ZEIT ONLINE.png", width = "49%" title="ZEIT ONLINE">
+<img src="../figs/wordcloud_Bild.png", width = "49%" title="Bild.de">
+<img src="../figs/wordcloud_DIEWELT.png", width = "49%" title="DIE WELT">
+<img src="../figs/wordcloud_FOCUSONLINE.png", width = "49%" title="FOCUS ONLINE">
+<img src="../figs/wordcloud_SPIEGELONLINE.png", width = "49%" title="SPIEGEL ONLINE">
+<img src="../figs/wordcloud_stern.png", width = "49%" title="Stern.de">
+<img src="../figs/wordcloud_Tagesschau.png", width = "49%" title="Tagesschau.de">
+<img src="../figs/wordcloud_ZEITONLINE.png", width = "49%" title="ZEIT ONLINE">
 
@@
 ```
-
-<!-- <img src="../figs/radarchart_2017-06.png", width = "49%"> -->
-<!-- <img src="../figs/radarchart_2017-07.png", width = "49%"> -->
-<!-- <img src="../figs/radarchart_2017-09.png", width = "49%"> -->
-<!-- <img src="../figs/radarchart_2017-10.png", width = "49%"> -->
-<!-- <img src="../figs/radarchart_2017-11.png", width = "49%"> -->
-<!-- <img src="../figs/radarchart_2017-12.png", width = "49%"> -->
-<!-- <img src="../figs/radarchart_2018-01.png", width = "49%"> -->
-<!-- <img src="../figs/radarchart_2018-02.png", width = "49%"> -->
 
@@
          Union = normalize_data(Union))
-
-polls_monthly %>%
-  gather(key = party, value = poll, AfD:Union) %>%
-  ggplot(aes(yearmonth, poll, color = party)) +
-  geom_line() +
-  scale_color_manual(values =  c("deepskyblue", "gold", "limegreen", "deeppink", "red", "black")) +
-  labs(x="", y="", title = "Survey Value", 
-       subtitle = "weekly", color = "") +
-  geom_vline(xintercept = as.Date("2017-09-24"), 
-             linetype = 2, color = col[3]) +
-  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%b", tz="CET")) +
-    theme(axis.text.x = element_text(size = 10))
 ```
@@
 ```
-
-Cross correlation at lag 0
-```{r}
-# Table
-corr %>% 
-  filter(lag == 0) %>%
-  select(-lag) %>% 
-  spread(Var2, correlation) -> corr_tab
-
-print(xtable(corr_tab, type="latex", digits=3,
-                   caption = "Cross Correlation at lag 0"),
-      file="../writing/tables/corr.tex" )
-```
-
-```{r fig.height=6, fig.width=8}
-# Figure
-p <- corr %>%
-  filter(lag == 0) %>%
-  ggplot(aes(Var2, Var1,
-                 fill = correlation,
-                 label = round(correlation,2))) +
-        geom_tile(color="white", alpha=0.8) +
-        geom_text(size = 3.5) +
-        #viridis::scale_fill_viridis(limits=c(-1, 1)) +
-        labs(x="", y="", fill="",
-             title = "",
-             subtitle = "Election polls vs. topic sentiment value (monthly)")
-
-ggsave(filename = "../figs/ccf.png", plot = p,
-       height = 6, width = 8, dpi = 600)
-```
-
-![Cross-correlation](../figs/ccf.png)
 
@@
 
-##### 3.1.2. By Media
+![Cross-correlation 2](../figs/ccf2.png)
+
+Cross correlation at lag 0
+```{r}
+# Table
+corr %>% 
+  filter(lag == 0) %>%
+  select(-lag) %>% 
+  spread(Var2, correlation) -> corr_tab
+
+print(xtable(corr_tab, type="latex", digits=3,
+                   caption = "Cross Correlation at lag 0"),
+      file="../writing/tables/corr.tex" )
+```
+
+```{r fig.height=6, fig.width=8}
+# Figure
+p <- corr %>%
+  filter(lag == 0) %>%
+  ggplot(aes(Var2, Var1,
+                 fill = correlation,
+                 label = round(correlation,2))) +
+        geom_tile(color="white", alpha=0.8) +
+        geom_text(size = 3.5) +
+        #viridis::scale_fill_viridis(limits=c(-1, 1)) +
+        labs(x="", y="", fill="",
+             title = "",
+             subtitle = "Election polls vs. topic sentiment value (monthly)")
+
+ggsave(filename = "../figs/ccf.png", plot = p,
+       height = 6, width = 8, dpi = 600)
+```
+
+![Cross-correlation](../figs/ccf.png)
+
 ```{r eval=FALSE, include=FALSE}
@@
 
-<img src="../figs/corrplot_Bild.de.png", width = "49%">
-<img src="../figs/corrplot_DIE WELT.png", width = "49%">
-<img src="../figs/corrplot_FOCUS ONLINE.png", width = "49%">
-<img src="../figs/corrplot_SPIEGEL ONLINE.png", width = "49%">
-<img src="../figs/corrplot_stern.de.png", width = "49%">
-<img src="../figs/corrplot_Tagesschau.de.png", width = "49%">
-<img src="../figs/corrplot_ZEIT ONLINE.png", width = "49%">
-
-#### 3.2. Graphical analysis
-
-For each party, we plot the topics that most strongly correlate with the poll data.
-
-```{r}
+<!-- <img src="../figs/corrplot_Bild.de.png", width = "49%"> -->
+<!-- <img src="../figs/corrplot_DIE WELT.png", width = "49%"> -->
+<!-- <img src="../figs/corrplot_FOCUS ONLINE.png", width = "49%"> -->
+<!-- <img src="../figs/corrplot_SPIEGEL ONLINE.png", width = "49%"> -->
+<!-- <img src="../figs/corrplot_stern.de.png", width = "49%"> -->
+<!-- <img src="../figs/corrplot_Tagesschau.de.png", width = "49%"> -->
+<!-- <img src="../figs/corrplot_ZEIT ONLINE.png", width = "49%"> -->
+
+<!-- #### 3.2. Graphical analysis -->
+
+<!-- For each party, we plot the topics that most strongly correlate with the poll data.  -->
+
+```{r eval=FALSE, include=FALSE}
 plot_Poll_Sent <- function(topics_number, party_str, color_str) {
@@
 ##### 3.2.1. CDU
-```{r fig.height=12, fig.width=10}
+```{r eval=FALSE, fig.height=12, fig.width=10, include=FALSE}
 topic_number <- c(10,13,23,26)
@@
 #### SPD
-```{r fig.height=12, fig.width=10}
+```{r eval=FALSE, fig.height=12, fig.width=10, include=FALSE}
 topic_number <- c(1,17,22)
@@
 ##### 3.2.3. AfD
-```{r fig.height=12, fig.width=10}
+```{r eval=FALSE, fig.height=12, fig.width=10, include=FALSE}
 topic_number <- c(17,22, 30)
@@
 #### FDP
-```{r fig.height=12, fig.width=10}
+```{r eval=FALSE, fig.height=12, fig.width=10, include=FALSE}
 topic_number <- c(23,26,27)
@@
 #### Grüne
-```{r fig.height=12, fig.width=10}
+```{r eval=FALSE, fig.height=12, fig.width=10, include=FALSE}
 topic_number <- c(26,27,17)
@@
 #### DIE LINKE
-```{r fig.height=12, fig.width=10}
+```{r eval=FALSE, fig.height=12, fig.width=10, include=FALSE}
 topic_number <- c(1,17,22)

### 2018-04-15 paper/writing/structure.tex
push current paper status

@@
 \usepackage{geometry}
-\geometry{a4paper,left=40mm,right=30mm, top=2cm, bottom=2cm}
+\geometry{a4paper,left=30mm,right=20mm, top=2cm, bottom=2cm}
 
@@
 
+\tableofcontents
+
 \section{Introduction}
-% Noch deutlicher beschreiben, was eigentlich gemacht wird. Besser motivieren
 % Paper von Ralf, Melissa, Tobias zitieren.
 
-Pluralism is an essential principle of democratic societies.
-An important pillar of this principle is an opinion-forming process that incorporates the different perspectives represented in the society.
+Pluralism of media is an essential principle of democratic societies.
 For the process of forming opinions, information conveyed by the media, in particular the mass media of journalism, plays a decisive role.
 They create the preconditions for making the social and cultural diversity of modern societies visible and manageable.
-Securing the diversity of opinion-forming processes and preventing concentration processes in the media sector is an essential prerequisite for a functioning democracy.
+For this reason, securing the diversity of opinion-forming processes and preventing concentration processes in the media sector is an essential prerequisite for a functioning democracy.
 An important question is therefore whether the political reporting of different content providers distinguishes itself and whether this reporting has an influence on the opinion-forming process of the voters.
 The aim of this paper is to investigate these questions with the use of up-to-date text mining methods.
+The analysis is based on online news articles from leading German news websites before, during and after the German parliamentary elections in September 2017.
+The internet as a source of information is gaining in importance, especially in a political context.
+According to a study on the media coverage of the German-speaking population, nearly 40\% of respondents used the internet at least once a week in 2017 to inform themselves about the current news compared to 34\% in 2016 \citep{vuma_arbeitsgemeinschaft_verbrauchs-_und_medienanalyse_verbrauchs-_2017}.
 
-A number of different factors have an influence on the diversity of media content.
-These include the market structure for journalistic content and the digitization of the industry.
+The new developments in digital media provide new opportunities and challenges for media outlets.
+The costs of providing and disseminating information have been reduced and the speed of information exchange has increased enormously.
+At first glance, these developments seem to have a positive effect on the provision of information.
+However, this also means that the incentive for media to produce primary information declines since the Internet has reduced the marginal utility of content.
+A study of French news websites from 2013 shows that only 38 percent of the online articles contained original content, with the remainder being copies of those originals \citep{cage_information_2017}.
+A multitude of factors influence the diversity of online media, including the market structure and the increasing digitization of the industry.
 Media outlets (TV, Radio, Newspaper) usually operate in two-sided markets, where they serve two customer groups (content consumer and advertiser) that are connected via indirect network effects.
@@
 \citet{ellman_what_2009} analyze a theoretical framework of a two-sided market for newspaper, where readers value accuracy and advertisers value advert-receptive readers.
-They found that advertising increases the intensity of competition for readers and therefore raises accuracy of media coverage.
-However, in the monopolistic case, newspapers under-report news that sufficiently reduces advertiser profits.
+They found that advertising increases the intensity of competition for readers and therefore raises accuracy of media coverage, whereas in the monopolistic case, newspapers under-report news that sufficiently reduces advertiser profits.
 
-The new developments in digital media provide new opportunities and challenges for media outlets.
-The costs of providing and disseminating information have been reduced and the speed of information exchange has increased enormously.
-At first glance, these developments seem to have a positive effect on the provision of information.
-However, it also means that the incentive for media to produce primary information declines since the Internet has reduced the marginal utility of content.
-A study of French news websites from 2013 shows that only 38 percent of the online articles contained original content, with the remainder being copies of those originals \citep{cage_information_2017}.
-At the same time, the number of people who find out about current news on the Internet is increasing.
-According to a study on the media coverage of the German-speaking population, nearly 40\% of respondents used the internet at least once a week in 2017 to inform themselves about the current news compared to 34\% in 2016 \citep{vuma_arbeitsgemeinschaft_verbrauchs-_und_medienanalyse_verbrauchs-_2017}.
 Recognizing the importance of media pluralism, the European Commission has endorsed several initiatives to discuss and promote media diversity in the European Union\footnote{https://ec.europa.eu/digital-single-market/en/policies/media-freedom-and-pluralism}.
@@
 The empirical strategy follows a novel approach combining "the two Ts": Topic and Tone \citep{hansen_shocking_2016}.
-That is, first the topics covered in the articles are identified, to find out how these topics are discussed (tone).
-The final step is to check whether the tonality of reporting is reflected in the survey results on voting preferences calculating the cross-correlation coefficients.
+This means that the topics discussed in the articles are identified first (topic), followed by an analysis of how they are discussed with the various news websites (tone).
+The final step is to check whether the tonality of reporting is reflected in the survey results on voting preferences calculating the cross correlation coefficients.
 More precisely, the research strategy is as follows:
@@
 The STM is an unsupervised machine learning approach that models topics as multinomial distributions of words and documents (as a synonym for news articles) as multinomial distributions of topics, allowing to incorporate external variables that effect both, topical content and topical prevalence.
-I estimate a model, where the newswire service is included as a control for both the topical content and the topical prevalence.
-The result of the generative process of STM are the posterior distributions for topic prevalence in a document and the content of a topic.
+I estimate a model, where the news website is included as a control for both the topical content and the topical prevalence.
+The result of the generative process of STM are two posterior distributions: One for the topic prevalence in an article and one for the content of a topic.
 The latter is used to label the topics according to an event or issue discussed in the media.
-The probability distribution of topics for each document is used to assign a topic to each news article.
-	\item\label{item_2} \textbf{Measuring Tone (Section \ref{subsection_tone})} After assigning a topic to each article (document), a dictionary-based sentiment analysis is conducted to estimate how topics are discussed differently by different news wires.
-	\item\label{item_3} \textbf{Comparing with polls} In order to check whether the transmitted content from the online media is reflected in the voting preferences, we compare the values from \ref{item_2} with the survey values of the Sunday survey ("Sonntagsumfrage").
-
-% Der erste Absatz ist z.B. ziemlich knapp. Ebenso sind „Measuring Tone“ und „Comparing with polls“ sehr knapp im Vergleich zu „Dicovering topics“ beschrieben.
-
+The topic prevalence of an article (or the posterior distribution) is used to assign a topic to each news article.
+	\item\label{item_2} \textbf{Measuring Tone (Section \ref{subsection_tone})} After assigning a topic to each article, a dictionary-based sentiment analysis is conducted to estimate how topics are discussed differently by different news websites.
+The idea of a sentiment analysis is to determine the attitude of a writer toward the overall tonality of a document.
+To conduct such an analysis, a lists of words (dictionary) associated with a given emotion, such as negativity is pre-defined by the analyst.
+The document is then deconstructed into individual words and the frequencies of words contained in a given dictionary are calculated.
+	\item\label{item_3} \textbf{Comparing with polls} In order to check whether the transmitted content from the online media is reflected in the voting preferences, the relationship between monthly average of the emotional value of individual topics from \ref{item_2} and the survey value of a specific party is estimated using the cross correlation function (CCF).
 \end{enumerate}
@@
 However, I extend the analysis by comparing the sentiment score for a given topic an news provider, to identify which topics are discussed similar or differently (\ref{item_2}).
-\citet{hansen_shocking_2016} applied a similar approach to a dataset of 142 FOMC decision statements to measure the effect of those statements on macroeconomic variables.
+\citet{hansen_shocking_2016} applied a similar approach to a dataset of 142 FOMC (Federal Open Market Committee) decision statements to measure the effect of those statements on macroeconomic variables.
 An additional extension is the comparison with current election poll values (\ref{item_3}).
@@
 The articles analyzed in this paper cover a period from June 1, 2017 to March 1, 2018 and thus cover both the most important election campaign topics for the Bundestag elections on September 24, 2017 and the process of forming a government that lasted until February 2018.
-After four years in a grand coalition with the Social Democrats (SPD), German Chancellor Angela Merkel, member of the Conservative Party (CDU/CSU), ran for re-election.
+After four years in a grand coalition with the Social Democrats (SPD), German Chancellor Angela Merkel, member of the Conservative Party (CDU/CSU, also known as Union), ran for re-election.
 The SPD nominated Martin Schulz as candidate for chancellor.
@@
 
-After the election, the formation of a government was difficult due to the large number of parties elected to the Bundestag and the considerable loss of votes by the major parties CDU/CSU/CSU and SPD.
-Since all parties rejected a coalition with the AfD, numerically only two coalitions with an absolute parliamentary majority were possible: a grand coalition ("GroKo" - from the German word Große Koalition) of CDU/CSU/CSU and SPD, and a Jamaica coalition (coalition of CDU/CSU/CSU, FDP (economic liberal party) and B90/Die Grünen (Bündnis 90/Die Grünen, green party)).
+After the election, the formation of a government was difficult due to the large number of parties elected to the Bundestag and the considerable loss of votes by the major parties CDU/CSU and SPD.
+Since all parties rejected a coalition with the AfD, numerically only two coalitions with an absolute parliamentary majority were possible: a grand coalition ("GroKo" - from the German word Große Koalition) of CDU/CSU and SPD, and a Jamaica coalition (coalition of CDU/CSU, FDP (economic liberal party) and B90/Die Grünen (Bündnis 90/Die Grünen, green party)).
 The grand coalition was initially rejected by the SPD.
@@
 The main points of contention were climate and refugee policy.
-CDU/CSU and CSU regretted this result, while B90/Die Grünen sharply criticized the withdrawal of the Liberals.
+CDU and CSU regretted this result, while B90/Die Grünen sharply criticized the withdrawal of the Liberals.
 The then Green leader Cem Özdemir accused the FDP of lacking the will to reach an agreement.
 
-After the failure of the Jamaica coalition, a possible re-election or a minority government as alternatives were discussed in the media before the SPD decided to hold coalition talks with the CDU/CSU/CSU.
+After the failure of the Jamaica coalition, a possible re-election or a minority government as alternatives were discussed in the media before the SPD decided to hold coalition talks with the CDU/CSU.
 This led to great resistance from the party base, which called for a party-internal vote on a grand coalition.
@@
 \section{Dataset and data preparation}\label{ch_data}
-% Viel mehr Datenbeschreibung / deskriptive Statistik
-% Warum wurden grade diese Medien ausgesucht?
 
@@
 
-The longest article at Tagesschau.de has 2006 words, nevertheless the median value is comparatively large (see Table \label{t_wordcloud}). ZEIT ONLINE has the highest median value of 459 words.
+The longest article at Tagesschau.de has 2006 words, nevertheless the median value is comparatively large (see Table \label{t_wordcount}). ZEIT ONLINE has the highest median value of 459 words.
 
@@
 For example "die" ("the"), "und" ("and"), and "in" ("in") are extremely common but unrelated to the quantity of interest.
-These terms, often called "stop words", are important to the grammatical structure of a text, but typically don't add any additional meaning and can therefore be neglected.
+These terms, often called stop words, are important to the grammatical structure of a text, but typically don't add any additional meaning and can therefore be neglected.
 A common strategy to reduce the number of language elements is to pre-process the text by imposing some preliminary restrictions (stop-word removal and stemming) based on the nature of the data (twitter text, newspaper articles, speeches, etc.) \citep{gentzkow_text_2017}.
@@
 \begin{figure}[H]
+	\caption{Word Cloud (whole corpus)}
 	\begin{center}
-		\includegraphics[width=0.7\textwidth]{../figs/wordcloud.png}
-		\caption{Word Cloud (whole corpus)}
+		\includegraphics[width=0.8\textwidth]{../figs/wordcloud.png}
 		\label{fig_wordcloud1}
@@
 In this setting, each news article represents a document $d$, whereby each of these documents can be assigned to a news website.
-Next, for each document $d \in \lbrace 1,...,D \rbrace$ the number of occurrences of term $v$ in document $d$ is computed, to obtain the count $x_{d,v}$, where each unique term in the corpus is indexed by some $v \in \lbrace 1,...,V \rbrace$ where $V$ is the number of unique terms.
+Next, for each document $d \in \lbrace 1,...,D \rbrace$ the number of occurrences of term $v$ in document $d$ is computed, to obtain the count $x_{d,v}$, where each unique term in the corpus is indexed by some $v \in \lbrace 1,...,V \rbrace$ and where $V$ is the number of unique terms.
 The $D$ x $V$ matrix $\boldsymbol{X}$ of all such counts is called the document-term matrix.
@@
 \section{The structural topic model}\label{ch_model}
-% Kapitel mehr mit eigenen Worten beschreiben.
 
-To find out the latent structure of each document, a Structural topic model (STM) is estimated.
+To find out the latent structure of each document, a structural topic model (STM) is estimated.
 In general, topic models formalize the idea that documents are formed by hidden variables (topics) that generate correlations among observed terms.
@@
 To generate each individual word $w_{d,n}$ in a document $d$ for the $n^{th}$ word-position, a topic allocation $z_{d,n}$ is drawn from the topic distribution for that document $\theta_d$.
-Then, a word is drawn from the term distribution for the selected topic $\phi_{z_{d,n}}$.
+Then, a word is drawn from the term distribution for the selected topic $\phi_{z_{d,n}}$.\footnote{A more detailed description of the generative process of the STM can be found in Section \ref{ch_generativeProcess}}
 
-The STM developed by \citet{roberts_model_2016} is a recent extension of the standard topic modeling technique, labeled as "latent Dirichlet allocation" (LDA), which refers to the Bayesian model in \citet{blei_latent_2003} that treats each word in a topic and each topic in a document as generated from a Dirichlet - distributed prior.\footnote{See also \citet{griffiths_probabilistic_2002}, \citet{griffiths_finding_2004} and \citet{hofmann_probabilistic_1999}.
+The STM developed by \citet{roberts_model_2016} is a recent extension of the standard topic modeling technique, labeled as latent Dirichlet allocation (LDA), which refers to the Bayesian model in \citet{blei_latent_2003} that treats each word in a topic and each topic in a document as generated from a Dirichlet - distributed prior.\footnote{See also \citet{griffiths_probabilistic_2002}, \citet{griffiths_finding_2004} and \citet{hofmann_probabilistic_1999}.
 \citet{pritchard_inference_2000} introduced the same model in genetics for factorizing gene expression as a function of latent populations.} Since its introduction into text analysis, LDA has become hugely popular and especially useful in political science.\footnote{see \citet{blei_probabilistic_2012}, \citet{grimmer_text_2013} and \citet{wiedmann_text_2016} for an overview in social science and \citet{gentzkow_text_2017} give an overview of text mining applications in economics.} \citet{wiedmann_text_2016} uses topic model methods on large amounts of news articles from two german newspapers published between 1959 and 2011, to reveal how democratic demarcation was performed in Germany over the past six decades.
@@
 In Section \ref{subsection_topic} $\theta$ is used to estimate the conditional expectation of topic prevalence for given document characteristics.
-To calculate the sentiment value, in Section \ref{subsection_tone} each document $d$ is assigned to the topic with the highest probability ($\max (\theta_{k})$ for each document $d$).
+In order to calculate the sentiment value in Section \ref{subsection_tone} each document $d$ is assigned to the topic with the highest probability ($\max (\theta_{k})$ for each document $d$).
 
@@
 \section{Empirical Evaluation}\label{ch_empirical}
-% Besser strukturieren. Tabellen mit Ergebnissen zeigen (nicht nur Abbildungen).
 
@@
 (2) Articles that are assigned to the selected topics with the highest probability are then used to conduct a dictionary-based analysis (see section \ref{subsection_tone}).
-In order to check whether the sentiment value of certain topics are correlated with the results of voting preferences, the cross-correlation function between these two concepts is calculated in \ref{ch_correlation}.
+In order to check whether the sentiment value of certain topics are correlated with the results of voting preferences, the cross correlation function between these two concepts is calculated in \ref{ch_correlation}.
 
@@
 
-It becomes apparent that topic 4 about the coalition talks between CDU/CSU/CSU and SPD - the "Grand coalition" or "GroKo" - is the topic with the highest expected frequency in the whole corpus, followed by the topic about the so-called Jamaica parties (CDU/CSU/CSU, FDP and B90/Die Grünen), which was the first alternative to be negotiated directly after the elections.
-The Figure also shows, that topics related to refugees in Germany (topics 12 and 42) are quite frequent within the corpus.
+It becomes apparent that topic 4 about the coalition talks between CDU/CSU and SPD - the "Grand coalition" or "GroKo" - is the topic with the highest expected frequency in the whole corpus, followed by the topic about the so-called Jamaica parties (CDU/CSU, FDP and B90/Die Grünen), which was the first alternative to be negotiated directly after the elections.
 
@@
 
-To estimate the differences of topic prevalence of the mentioned topics for the different websites, a linear model is calculated for each topic $k$, where the documents $D$ are observations, the dependent variable is the posterior probability of the respective topic ($\theta_{d}$) and the covariates are dummy variables that are 1 if the document was published by the respective website and 0 otherwise (see equation \ref{eq_1}).
+To estimate the differences of topic prevalence of the mentioned topics for the different websites, a linear model is calculated for each topic $k$, where the documents are observations, the dependent variable is the posterior probability of the respective topic ($\theta_{d}$) and the covariates are dummy variables that are 1 if the document was published by the respective website and 0 otherwise (see equation \ref{eq_1}).
 As the dependent variable is a vector containing proportions that sum up to 1, the QR decomposition of the model is computed prior to the estimation of the coefficients.
@@
 
-\pagebreak
+\appendix
+\section{Appendices}
 
-\section*{Appendix}
-
-\subsection*{Most frequent words}\label{apx_tf}
+\subsection{Most frequent words}\label{apx_tf}
 % 1, 2
@@
 
-\subsection*{Regression Results}\label{apx_coeff}
+\subsection{Regression Results}\label{apx_coeff}
 \input{tables/coeff1}
@@
 
-\subsection*{Cross Correlation Coefficient}
+\subsection{Cross Correlation Coefficient}
 \input{tables/corr}

### 2018-04-15 paper/writing/tables/coeff2.tex
push current paper status

--- 2018-04-09 paper/writing/tables/coeff2.tex
@@
 % latex table generated in R 3.4.2 by xtable 1.8-2 package
-% Mon Apr  9 18:06:44 2018
+% Sun Apr 15 20:40:13 2018
 \begin{table}[ht]
 \centering
-\resizebox{\textwidth}{!}{
 \begin{tabular}{rllrrrr}
@@
   \hline
-57 & 23: CSU, Söder \& Seehover & (Intercept) & 0.04 & 0.00 & 9.36 & 0.00 \\ 
-  58 & 23: CSU, Söder \& Seehover & FOCUS ONLINE & -0.00 & 0.00 & -0.74 & 0.46 \\ 
-  59 & 23: CSU, Söder \& Seehover & SPIEGEL ONLINE & 0.01 & 0.00 & 1.29 & 0.20 \\ 
-  60 & 23: CSU, Söder \& Seehover & stern.de & -0.00 & 0.00 & -0.36 & 0.72 \\ 
-  61 & 23: CSU, Söder \& Seehover & Tagesschau.de & -0.01 & 0.01 & -1.13 & 0.26 \\ 
-  62 & 23: CSU, Söder \& Seehover & DIE WELT & -0.01 & 0.00 & -1.16 & 0.25 \\ 
-  63 & 23: CSU, Söder \& Seehover & ZEIT ONLINE & 0.00 & 0.01 & 0.44 & 0.66 \\ 
-  64 & 26: Jamaica fail, Reelections or GroKo? & (Intercept) & 0.03 & 0.00 & 12.15 & 0.00 \\ 
-  65 & 26: Jamaica fail, Reelections or GroKo? & FOCUS ONLINE & -0.00 & 0.00 & -1.17 & 0.24 \\ 
-  66 & 26: Jamaica fail, Reelections or GroKo? & SPIEGEL ONLINE & -0.00 & 0.00 & -1.12 & 0.26 \\ 
-  67 & 26: Jamaica fail, Reelections or GroKo? & stern.de & -0.01 & 0.00 & -3.56 & 0.00 \\ 
-  68 & 26: Jamaica fail, Reelections or GroKo? & Tagesschau.de & -0.01 & 0.00 & -2.61 & 0.01 \\ 
-  69 & 26: Jamaica fail, Reelections or GroKo? & DIE WELT & -0.01 & 0.00 & -3.37 & 0.00 \\ 
-  70 & 26: Jamaica fail, Reelections or GroKo? & ZEIT ONLINE & -0.01 & 0.00 & -1.44 & 0.15 \\ 
-  71 & 27: Jamaica Coalition debates & (Intercept) & 0.07 & 0.00 & 14.34 & 0.00 \\ 
-  72 & 27: Jamaica Coalition debates & FOCUS ONLINE & -0.03 & 0.01 & -5.20 & 0.00 \\ 
-  73 & 27: Jamaica Coalition debates & SPIEGEL ONLINE & -0.01 & 0.01 & -1.40 & 0.16 \\ 
-  74 & 27: Jamaica Coalition debates & stern.de & -0.03 & 0.01 & -5.13 & 0.00 \\ 
-  75 & 27: Jamaica Coalition debates & Tagesschau.de & -0.02 & 0.01 & -2.75 & 0.01 \\ 
-  76 & 27: Jamaica Coalition debates & DIE WELT & -0.01 & 0.01 & -1.38 & 0.17 \\ 
-  77 & 27: Jamaica Coalition debates & ZEIT ONLINE & -0.00 & 0.01 & -0.51 & 0.61 \\ 
-  78 & 30: AfD, F.Petry \& Meuthen & (Intercept) & 0.03 & 0.00 & 7.87 & 0.00 \\ 
-  79 & 30: AfD, F.Petry \& Meuthen & FOCUS ONLINE & -0.00 & 0.00 & -1.25 & 0.21 \\ 
-  80 & 30: AfD, F.Petry \& Meuthen & SPIEGEL ONLINE & 0.00 & 0.00 & 0.49 & 0.62 \\ 
-  81 & 30: AfD, F.Petry \& Meuthen & stern.de & -0.00 & 0.00 & -0.95 & 0.34 \\ 
-  82 & 30: AfD, F.Petry \& Meuthen & Tagesschau.de & -0.01 & 0.00 & -3.23 & 0.00 \\ 
-  83 & 30: AfD, F.Petry \& Meuthen & DIE WELT & -0.01 & 0.00 & -2.64 & 0.01 \\ 
-  84 & 30: AfD, F.Petry \& Meuthen & ZEIT ONLINE & 0.00 & 0.00 & 0.92 & 0.36 \\ 
-  85 & 32: AfD, Gauland \& Weidel & (Intercept) & 0.02 & 0.00 & 6.84 & 0.00 \\ 
-  86 & 32: AfD, Gauland \& Weidel & FOCUS ONLINE & 0.00 & 0.00 & 0.14 & 0.89 \\ 
-  87 & 32: AfD, Gauland \& Weidel & SPIEGEL ONLINE & -0.00 & 0.00 & -0.17 & 0.86 \\ 
-  88 & 32: AfD, Gauland \& Weidel & stern.de & 0.01 & 0.00 & 1.63 & 0.10 \\ 
-  89 & 32: AfD, Gauland \& Weidel & Tagesschau.de & -0.01 & 0.00 & -1.37 & 0.17 \\ 
-  90 & 32: AfD, Gauland \& Weidel & DIE WELT & 0.01 & 0.00 & 1.49 & 0.14 \\ 
-  91 & 32: AfD, Gauland \& Weidel & ZEIT ONLINE & 0.01 & 0.00 & 1.25 & 0.21 \\ 
-  92 & 37: AfD \& DIE LINKE in parliament & (Intercept) & 0.02 & 0.00 & 7.01 & 0.00 \\ 
-  93 & 37: AfD \& DIE LINKE in parliament & FOCUS ONLINE & 0.01 & 0.00 & 1.16 & 0.25 \\ 
-  94 & 37: AfD \& DIE LINKE in parliament & SPIEGEL ONLINE & 0.01 & 0.00 & 2.83 & 0.00 \\ 
-  95 & 37: AfD \& DIE LINKE in parliament & stern.de & 0.00 & 0.00 & 0.19 & 0.85 \\ 
-  96 & 37: AfD \& DIE LINKE in parliament & Tagesschau.de & 0.01 & 0.00 & 1.09 & 0.28 \\ 
-  97 & 37: AfD \& DIE LINKE in parliament & DIE WELT & 0.00 & 0.00 & 0.37 & 0.71 \\ 
-  98 & 37: AfD \& DIE LINKE in parliament & ZEIT ONLINE & 0.01 & 0.00 & 2.13 & 0.03 \\ 
-  99 & 46: CDU & (Intercept) & 0.02 & 0.00 & 7.35 & 0.00 \\ 
-  100 & 46: CDU & FOCUS ONLINE & -0.00 & 0.00 & -0.32 & 0.75 \\ 
-  101 & 46: CDU & SPIEGEL ONLINE & 0.00 & 0.00 & 0.71 & 0.48 \\ 
-  102 & 46: CDU & stern.de & -0.01 & 0.00 & -1.98 & 0.05 \\ 
-  103 & 46: CDU & Tagesschau.de & -0.01 & 0.00 & -3.37 & 0.00 \\ 
-  104 & 46: CDU & DIE WELT & -0.00 & 0.00 & -0.52 & 0.60 \\ 
-  105 & 46: CDU & ZEIT ONLINE & -0.00 & 0.00 & -0.08 & 0.93 \\ 
+57 & 23: CSU, Söder \& Seehover & (Intercept) & 0.035 & 0.004 & 8.855 & 0.000 \\ 
+  58 & 23: CSU, Söder \& Seehover & FOCUS ONLINE & -0.004 & 0.005 & -0.816 & 0.414 \\ 
+  59 & 23: CSU, Söder \& Seehover & SPIEGEL ONLINE & 0.006 & 0.005 & 1.140 & 0.254 \\ 
+  60 & 23: CSU, Söder \& Seehover & stern.de & -0.002 & 0.005 & -0.335 & 0.738 \\ 
+  61 & 23: CSU, Söder \& Seehover & Tagesschau.de & -0.006 & 0.005 & -1.137 & 0.256 \\ 
+  62 & 23: CSU, Söder \& Seehover & DIE WELT & -0.005 & 0.005 & -1.148 & 0.251 \\ 
+  63 & 23: CSU, Söder \& Seehover & ZEIT ONLINE & 0.002 & 0.005 & 0.398 & 0.691 \\ 
+  64 & 26: Jamaica fail, Reelections or GroKo? & (Intercept) & 0.035 & 0.003 & 12.650 & 0.000 \\ 
+  65 & 26: Jamaica fail, Reelections or GroKo? & FOCUS ONLINE & -0.004 & 0.003 & -1.099 & 0.272 \\ 
+  66 & 26: Jamaica fail, Reelections or GroKo? & SPIEGEL ONLINE & -0.004 & 0.004 & -1.042 & 0.297 \\ 
+  67 & 26: Jamaica fail, Reelections or GroKo? & stern.de & -0.012 & 0.003 & -3.530 & 0.000 \\ 
+  68 & 26: Jamaica fail, Reelections or GroKo? & Tagesschau.de & -0.010 & 0.004 & -2.718 & 0.007 \\ 
+  69 & 26: Jamaica fail, Reelections or GroKo? & DIE WELT & -0.012 & 0.003 & -3.759 & 0.000 \\ 
+  70 & 26: Jamaica fail, Reelections or GroKo? & ZEIT ONLINE & -0.005 & 0.004 & -1.366 & 0.172 \\ 
+  71 & 27: Jamaica Coalition debates & (Intercept) & 0.066 & 0.005 & 13.757 & 0.000 \\ 
+  72 & 27: Jamaica Coalition debates & FOCUS ONLINE & -0.029 & 0.006 & -5.224 & 0.000 \\ 
+  73 & 27: Jamaica Coalition debates & SPIEGEL ONLINE & -0.009 & 0.006 & -1.491 & 0.136 \\ 
+  74 & 27: Jamaica Coalition debates & stern.de & -0.028 & 0.006 & -4.955 & 0.000 \\ 
+  75 & 27: Jamaica Coalition debates & Tagesschau.de & -0.017 & 0.006 & -2.805 & 0.005 \\ 
+  76 & 27: Jamaica Coalition debates & DIE WELT & -0.007 & 0.006 & -1.331 & 0.183 \\ 
+  77 & 27: Jamaica Coalition debates & ZEIT ONLINE & -0.003 & 0.007 & -0.529 & 0.597 \\ 
+  78 & 30: AfD, F.Petry \& Meuthen & (Intercept) & 0.025 & 0.003 & 7.563 & 0.000 \\ 
+  79 & 30: AfD, F.Petry \& Meuthen & FOCUS ONLINE & -0.005 & 0.004 & -1.124 & 0.261 \\ 
+  80 & 30: AfD, F.Petry \& Meuthen & SPIEGEL ONLINE & 0.003 & 0.004 & 0.597 & 0.550 \\ 
+  81 & 30: AfD, F.Petry \& Meuthen & stern.de & -0.003 & 0.004 & -0.839 & 0.401 \\ 
+  82 & 30: AfD, F.Petry \& Meuthen & Tagesschau.de & -0.013 & 0.005 & -2.896 & 0.004 \\ 
+  83 & 30: AfD, F.Petry \& Meuthen & DIE WELT & -0.010 & 0.004 & -2.590 & 0.010 \\ 
+  84 & 30: AfD, F.Petry \& Meuthen & ZEIT ONLINE & 0.005 & 0.005 & 1.080 & 0.280 \\ 
+  85 & 32: AfD, Gauland \& Weidel & (Intercept) & 0.024 & 0.004 & 6.497 & 0.000 \\ 
+  86 & 32: AfD, Gauland \& Weidel & FOCUS ONLINE & 0.000 & 0.005 & 0.101 & 0.919 \\ 
+  87 & 32: AfD, Gauland \& Weidel & SPIEGEL ONLINE & -0.001 & 0.005 & -0.185 & 0.853 \\ 
+  88 & 32: AfD, Gauland \& Weidel & stern.de & 0.007 & 0.004 & 1.538 & 0.124 \\ 
+  89 & 32: AfD, Gauland \& Weidel & Tagesschau.de & -0.006 & 0.004 & -1.427 & 0.154 \\ 
+  90 & 32: AfD, Gauland \& Weidel & DIE WELT & 0.006 & 0.004 & 1.333 & 0.183 \\ 
+  91 & 32: AfD, Gauland \& Weidel & ZEIT ONLINE & 0.006 & 0.005 & 1.125 & 0.261 \\ 
+  92 & 37: AfD \& DIE LINKE in parliament & (Intercept) & 0.024 & 0.004 & 6.758 & 0.000 \\ 
+  93 & 37: AfD \& DIE LINKE in parliament & FOCUS ONLINE & 0.005 & 0.004 & 1.110 & 0.267 \\ 
+  94 & 37: AfD \& DIE LINKE in parliament & SPIEGEL ONLINE & 0.013 & 0.005 & 2.736 & 0.006 \\ 
+  95 & 37: AfD \& DIE LINKE in parliament & stern.de & 0.001 & 0.004 & 0.196 & 0.845 \\ 
+  96 & 37: AfD \& DIE LINKE in parliament & Tagesschau.de & 0.005 & 0.005 & 1.065 & 0.287 \\ 
+  97 & 37: AfD \& DIE LINKE in parliament & DIE WELT & 0.002 & 0.004 & 0.424 & 0.671 \\ 
+  98 & 37: AfD \& DIE LINKE in parliament & ZEIT ONLINE & 0.011 & 0.005 & 2.267 & 0.023 \\ 
+  99 & 46: CDU & (Intercept) & 0.019 & 0.002 & 8.091 & 0.000 \\ 
+  100 & 46: CDU & FOCUS ONLINE & -0.001 & 0.003 & -0.313 & 0.755 \\ 
+  101 & 46: CDU & SPIEGEL ONLINE & 0.002 & 0.003 & 0.682 & 0.495 \\ 
+  102 & 46: CDU & stern.de & -0.006 & 0.003 & -2.189 & 0.029 \\ 
+  103 & 46: CDU & Tagesschau.de & -0.011 & 0.003 & -3.565 & 0.000 \\ 
+  104 & 46: CDU & DIE WELT & -0.002 & 0.003 & -0.582 & 0.561 \\ 
+  105 & 46: CDU & ZEIT ONLINE & -0.000 & 0.003 & -0.039 & 0.969 \\ 
    \hline
 \end{tabular}
-}
 \end{table}

### 2018-04-17 paper/writing/structure.tex
change intro

@@
 
-Pluralism of media is an essential principle of democratic societies.
-For the process of forming opinions, information conveyed by the media, in particular the mass media of journalism, plays a decisive role.
-They create the preconditions for making the social and cultural diversity of modern societies visible and manageable.
-For this reason, securing the diversity of opinion-forming processes and preventing concentration processes in the media sector is an essential prerequisite for a functioning democracy.
-An important question is therefore whether the political reporting of different content providers distinguishes itself and whether this reporting has an influence on the opinion-forming process of the voters.
-The aim of this paper is to investigate these questions with the use of up-to-date text mining methods.
-The analysis is based on online news articles from leading German news websites before, during and after the German parliamentary elections in September 2017.
-The internet as a source of information is gaining in importance, especially in a political context.
+The discussion about the influence of digital media on the political opinion-forming process has gained momentum since the presidential elections in the USA in October 2016 at the latest.
+Overall, the importance of the Internet as a source of information for political topics has been very strong in recent years.
 According to a study on the media coverage of the German-speaking population, nearly 40\% of respondents used the internet at least once a week in 2017 to inform themselves about the current news compared to 34\% in 2016 \citep{vuma_arbeitsgemeinschaft_verbrauchs-_und_medienanalyse_verbrauchs-_2017}.
 
-The new developments in digital media provide new opportunities and challenges for media outlets.
-The costs of providing and disseminating information have been reduced and the speed of information exchange has increased enormously.
-At first glance, these developments seem to have a positive effect on the provision of information.
-However, this also means that the incentive for media to produce primary information declines since the Internet has reduced the marginal utility of content.
-A study of French news websites from 2013 shows that only 38 percent of the online articles contained original content, with the remainder being copies of those originals \citep{cage_information_2017}.
-A multitude of factors influence the diversity of online media, including the market structure and the increasing digitization of the industry.
-Media outlets (TV, Radio, Newspaper) usually operate in two-sided markets, where they serve two customer groups (content consumer and advertiser) that are connected via indirect network effects.
-The two-sided market structure of the private news market results in news platforms striving to choose their content in such a way that its reach is as large as possible in order to maximize profits from advertising revenues.
-\citet{steiner_program_1952} concluded, that profit-maximizing media owners may choose to offer the same content, i.e.
-content aligned with the tastes of the majority.
-\citet{gabszewicz_press_2001} study the problem of diversity of the political content of newspapers.
-They find that the maximum differentiation only prevails if the readers sufficiently value the political differentiation between the newspapers the advertising market is small enough.
-On the other hand, advertising may also have a positive impact on the media, as it enables publishers to report independently of political parties.
-\citet{ellman_what_2009} analyze a theoretical framework of a two-sided market for newspaper, where readers value accuracy and advertisers value advert-receptive readers.
-They found that advertising increases the intensity of competition for readers and therefore raises accuracy of media coverage, whereas in the monopolistic case, newspapers under-report news that sufficiently reduces advertiser profits.
-
-Recognizing the importance of media pluralism, the European Commission has endorsed several initiatives to discuss and promote media diversity in the European Union\footnote{https://ec.europa.eu/digital-single-market/en/policies/media-freedom-and-pluralism}.
-One way to ensure the independence and diversity of the media landscape is through public funded media.
-In Germany public broadcasting originated in the post-war period and is financed by compulsory fees.
-To take into account the distinct nature of digital media, the Interstate Broadcasting Agreement (Rundfunkstaatsvertrag) also regulates the scope for action of online services offered by public service broadcasting since 2007.
-Accordingly, public media are not allowed to distribute purchased content and must - depending on the category of content - set a time limit on its accessibility.
-In addition, there is a strict advertising ban and prohibition of regional reporting.
-
+The pluralism nor only of online media, but of media in general is an essential principle of democratic societies.
+For the process of forming opinions, information conveyed by the media, in particular the mass media of journalism, plays a decisive role.
+An important question is therefore whether there are convergence tendencies within the mass media - that is, whether popular media tend to report on certain political topics in the same or similar ways and whether this reporting has an influence on the opinion-forming process of the voters.
 With the purpose of examining the media pluralism in the market for German-language online news, this paper analyzes German online news articles about domestic politics.

### 2018-04-23 paper/docs/04_Modelresults_50.Rmd
change word count fig

@@
 
+library(ggridges)
 library(igraph)
 library(corrplot)
-library(patchwork)
+#library(patchwork)
 library(ggpmisc)
-library(ggraph)
+#library(ggraph)
 library(ggiraph)
@@
   btw %>%
-    ggplot(aes(as.numeric(text_length.cut),
-                       group = site)) +
-    geom_histogram(alpha=.8, fill = col[3]) + 
-    scale_x_continuous(labels = c(seq(0,1500,500), ">2000")) +
-    facet_wrap(~site, ncol = 4) +
-    labs(x = "Word count", color = "") +
-    theme(axis.title = element_text(size = 8),
-          axis.text = element_text(size = 6))
+    ggplot(aes(as.numeric(text_length.cut), site)) +
+    geom_density_ridges(scale = 4,
+                        fill = col[3], alpha = .8,
+                        color = "white") +
+    theme_ridges() +
+    labs(x = "Word count", y = "") +
+    scale_x_continuous(expand = c(0,0), 
+                       labels = c(seq(0,1500,500), ">2000"))
 

### 2018-05-08 paper/R/04_Modelresults_50.Rmd
paper submission

--- 2018-04-23 paper/docs/04_Modelresults_50.Rmd
@@
 library(stm)
+#library(tm)
 library(readxl)
@@
 library(ggpmisc)
-#library(ggraph)
-library(ggiraph)
 library(tidygraph)
@@
 library(scales)      # Scales
+library(wordcloud)
 
@@
     theme(
+      axis.title = element_text(size = 12),
       plot.title = element_text(size = 14,
@@
 
-rm(list=ls())
+#rm(list=ls())
 col <- rcartocolor::carto_pal(12, "Bold")
@@
   ggplot(aes(site)) +
-  geom_bar(fill=col[8], alpha = 0.8) +
+  geom_bar(fill=col[3], alpha = 0.8) +
   labs(x="", y="Number of articles") +
+    coord_flip() +
   theme(
-    axis.text.x = element_text(size = 9),
+    axis.text.y = element_text(size = 12),
       legend.position   = "none"
@@
 filename = "../figs/bar.png", device = "png", 
-width = 7, height = 4,
+width = 6, height = 4,
         dpi = 600)
@@
   labs(x="", y="Number of Articles",color="") +
-  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
+  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%b\n%y", tz="CET")) +
   theme(
@@
       axis.title.x      = element_blank(),
-      axis.text       = element_text(size = 8)
+      axis.text       = element_text(size = 10)
     )
@@
 
-print(xtable(output, type="latex"), file="../writing/tables/wordcount.tex" )
+print(xtable(output, type="latex", caption = "Summary statistics of text length",
+             ref = "t_wordcount"), 
+      file="../writing/tables/wordcount.tex" )
 
@@
                         color = "white") +
-    theme_ridges() +
     labs(x = "Word count", y = "") +
     scale_x_continuous(expand = c(0,0), 
-                       labels = c(seq(0,1500,500), ">2000"))
+                       breaks = c(seq(0,2000,200)),
+                       labels = c(seq(0,1800,200), ">2000")) +
+    theme(axis.text = element_text(size = 12))
 
@@
 ### Unprocessed Text
-```{r message=FALSE, warning=FALSE}
-all.corpus <- corpus(btw$text)
-df.corpus <- dfm(all.corpus, removePunct = TRUE, removeSymbols = T)
-```
-
-```{r message=FALSE, warning=FALSE}
-png("../figs/wordcloud.png")
-textplot_wordcloud(df.corpus, max.word=300)
+
+```{r eval=FALSE, include=FALSE}
+png("../figs/wordcloud.png", width = 350, height = 350)
+wordcloud(btw$text, max.words = 100)
 dev.off()
 ```
-![Wordcloud 1](../figs/wordcloud.png)
+![Wordcloud](../figs/wordcloud.png)
 
@@
 wordclouds <- function(select_site) {
-  corp <- btw %>% filter(site %in% select_site)
-  corp <- corpus(corp$text_cleaned1)
-  corp <- dfm(corp)
-
-  textplot_wordcloud(corp, max.word=200)
+  tempdf <- btw %>% filter(site %in% select_site)
+
+  wordcloud(tempdf$text_cleaned, max.word=50)
 }
@@
 for (i in unique(btw$site)) {
-  png(paste0("../figs/wordcloud_",i,".png"))
+  png(paste0("../figs/wordcloud_",i,".png"), 
+      width = 350, height = 350)
   wordclouds(i)
@@
 k <- stmOut$settings$dim$K
-sagelabs <- sageLabels(stmOut, 20)
+sagelabs <- sageLabels(stmOut, 15)
 ```
@@
 
-```{r message=FALSE, warning=FALSE}
+```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
 p <- ggplot(frequency, aes(x=reorder(topic_name, frequency), y=frequency)) + 
@@
 
-```{r fig.height=8, fig.width=12, message=FALSE, warning=FALSE}
+```{r eval=FALSE, fig.height=8, fig.width=12, message=FALSE, warning=FALSE, include=FALSE}
 p <- freq %>%
@@
 
-```{r eval=FALSE, include=FALSE}
-btw.2 %>% filter(topic == 46) %>%
-  filter(!grepl("Geißler", title)) %>%
-  select(title, url, site) %>%
-  htmlTable::htmlTable(align = "l")
-```
-
 We will conduct our further analysis on 15 selected topics which relate to political parties.
@@
 To identify which of these differences is significant, the conditional expectation of topic prevalence for given document characteristics can be estimated.
-More specifically, I estimate a linear model, where the documents are observations, the dependent variable is the posterior probability of a topic and the covariates are the metadata of documents (see equation below).
-
-$$
-\theta_d=\alpha+\beta x_{ownership}+\epsilon
-$$
+More specifically, I estimate a linear model, where the documents are observations, the dependent variable is the posterior probability of a topic and the covariates are the metadata of documents.
 
@@
 
-```{r}
+```{r eval=FALSE, include=FALSE}
 coeff_tab <- coeff %>%
@@
 
-print(xtable(coeff_tab[1:56,], type="latex", digits=3), 
+print(xtable(coeff_tab[1:56,], type="latex", 
+             digits=3), 
+      include.rownames = F,
       file="../writing/tables/coeff1.tex" )
-print(xtable(coeff_tab[57:nrow(coeff_tab),], type="latex", digits=3), 
+print(xtable(coeff_tab[57:nrow(coeff_tab),], 
+             type="latex", 
+             digits=3),
+      include.rownames = F,
       file="../writing/tables/coeff2.tex" )
+
+# add "\begin{adjustbox}{width=\textwidth,totalheight=\textheight,keepaspectratio}" and delete "\begin{table}" in latex document.
 ```
@@
   theme(legend.position = "top", 
-        axis.text.y = element_text(size=9),
+        axis.text.y = element_text(size=11),
         axis.text.x = element_text(angle=90))
@@
 
-```{r eval=FALSE, fig.height=8, fig.width=4}
+```{r eval=FALSE, include=FALSE}
 for (topic in keep) {
 
-  png(filename = paste0("../figs/plotquote",topic,".png"), width = 300,
+  png(filename = paste0("../figs/plotquote",topic,".png"), width =500,
       height = 700)
@@
                   paste(sagelabs$cov.betas[[7]]$problabels[topic,], collapse="\n"))),
-          text.cex = 0.8, width = 40,
-          main = paste(topics.df$topic_name[topics.df$topic==topic])
+          text.cex = 1.3, width = 50,
+          main = paste0("Topic: ", topics.df$topic[topics.df$topic==topic])
           )
@@
 
+```{r}
+samp <- sent %>% dplyr::sample_n(10)
+
+print(xtable(samp, type="latex", label = "t_sentdict",
+             caption = "Sentiment Dictionary (Sample)"), 
+      file="../writing/tables/sent_dict.tex" )
+
+knitr::kable(samp)
+```
+
 #### 2.2.2. Apply the dictionary on the artciles.
@@
 
-The following figure shows the results of the analysis for each topic on a monthly basis, aggregated on all newspaper.
+The following table shows the results of the analysis for each topic on a monthly basis, aggregated on all newspaper.
 Each sentiment value is weighted by the relative share of the topic in the overall reporting of that month.
@@
   mutate(w = obs / total_obs,
-         sentiment_w = sentiment * w)
-
+         sentiment_w = sentiment * w) %>%
+  dplyr::arrange(topic) %>%
+  select(yearmonth, topic_name, obs, sentiment_w) %>%
+  ungroup()
+```
+
+```{r eval=FALSE, include=FALSE}
+# save to latex files
+num <- nrow(p)/2
+num1 <- num+1
+
+p.tab <- p %>%
+  transmute(date = as.character(yearmonth),
+             topic = topic_name,
+             `Number of Obs.` = obs,
+             `sentiment value * 1000` = sentiment_w*1000
+             )
+
+print(xtable(p.tab[1:num,], 
+             type="latex"
+             ), include.rownames = F,
+      file="../writing/tables/sentscore_monthly1.tex" )
+
+print(xtable(p.tab[num1:nrow(p.tab),], 
+             type="latex"
+             ), include.rownames = F,
+      file="../writing/tables/sentscore_monthly2.tex" )
+
+# add "\begin{adjustbox}{width=\textwidth}" and delete "\begin{table}" in latex document. 
+```
+
+```{r}
+p %>%
+  knitr::kable()
+```
+
+$$
+\text{normalized_w} = \frac{w - \min{(W)}}{\max{(W)}-\min{(W)}}
+$$
+
+```{r eval=FALSE, include=FALSE}
 p1 <- ggplot(p, 
-       aes(yearmonth, sentiment_w, 
+       aes(yearmonth, normalize_data(sentiment_w), 
            group = topic_name,
            label = obs)) +
-  facet_wrap(~topic_name, nrow = 3, 
-             labeller=labeller(topic_name = linebreak)) +
+  facet_wrap(~topic_name, nrow = 5) +
   geom_col(fill = col[3], alpha = 0.8) +
   geom_line(color = col[5], size = 0.6) +
-  #geom_text() +
   geom_hline(yintercept = 0, linetype = 2,
@@
     axis.title.y = element_text(size=12),
-        axis.text.x = element_text(size = 12, angle = 45))
+        axis.text.x = element_text(size = 12, angle = 90))
 
 ggsave(filename = "../figs/sentscore_monthly.png", plot = p1,
-       height = 10, width = 13)
+       height = 12, width = 12)
 ```
@@
   mutate(w = obs/total_obs,
-         sentiment_w = sentiment * w)
-
+         sentiment_w = sentiment * w) %>%
+  select(site, topic_name, obs, topic, sentiment_w) %>%
+  ungroup()
+```
+
+```{r eval=FALSE, include=FALSE}
+# save to latex files
+num <- nrow(p)/2
+num1 <- num+1
+
+p.tab <- p %>%
+  transmute(`News website` = site,
+             topic = topic_name,
+             `Number of Obs.` = obs,
+             `sentiment value * 1000` = sentiment_w*1000
+             )
+
+print(xtable(p.tab[1:num,], 
+             type="latex"), 
+      include.rownames = F,
+      file="../writing/tables/sentscore_site1.tex" )
+
+print(xtable(p.tab[num1:nrow(p.tab),],
+             type="latex"
+             ), 
+      include.rownames = F,
+      file="../writing/tables/sentscore_site2.tex" )
+
+# add "\begin{adjustbox}{width=\textwidth}" and delete "\begin{table}" in latex
+```
+
+```{r}
+p %>%
+  knitr::kable()
+```
+
+```{r eval=FALSE, include=FALSE}
 p1 <- ggplot(p, 
        aes(reorder(topic_name, topic), 
-           sentiment_w, 
+           normalize_data(sentiment_w), 
            group = site,
@@
     axis.text.y = element_text(size = 14),
-        axis.text.x = element_text(size=8, angle = 90),
-        axis.title.x = element_text(size = 12))
+        axis.text.x = element_text(size=10, angle = 90),
+        axis.title.x = element_text(size = 14))
 
@@
          sentiment_w = sentiment * w) %>%
+  #mutate(sentiment_w = normalize_data(sentiment_w)) %>%
   select(site, topic_name, sentiment_w) %>%
   spread(key=topic_name, value=sentiment_w) -> radar
-
-p <- radar %>%
-  ggRadar(aes(color=site), 
+```
+
+```{r eval=FALSE, include=FALSE}
+p <- ggRadar(radar, aes(color=site),
           rescale = F,
@@
   scale_x_date(breaks = date_breaks("1 month"), 
-               labels=date_format("%b", tz="CET")) +
+               labels=date_format("%b\n%y", tz="CET")) +
     geom_vline(xintercept = as.Date("2017-09-24"), 
@@
     guides(color = guide_legend(nrow = 1,
-                                label.theme = element_text(size = 6,
+                                label.theme = element_text(size = 10,
                                                            angle=0))) +
-  theme(axis.text = element_text(size=6),
+  theme(axis.text = element_text(size=10),
         legend.position = "bottom")
@@
 print(xtable(corr_tab, type="latex", digits=3,
+             label = "t_ccf",
                    caption = "Cross Correlation at lag 0"),

### 2018-05-08 paper/docs/func/functions.R

@@ -1,227 +1,0 @@
-Mode = function(x){ 
-  ta = table(x)
-  tam = max(ta)
-  if (all(ta == tam))
-    mod = NA
-  else
-    if(is.numeric(x))
-      mod = as.numeric(names(ta)[ta == tam])
-  else
-    mod = names(ta)[ta == tam]
-  return(mod)
-}
-
-#############################
-## Topic proportion by Ylevel
-#############################
-plotNewspaperHistogram <- function(topic){
-  tab <- tapply(stmOut$theta[,topic], stmOut$settings$covariates$betaindex, mean)
-  tab <- as.data.frame(tab) %>% 
-    mutate(site=stmOut$settings$covariates$yvarlevels)
-  
-  ggplot(data=tab, aes(x=site, y=tab)) +
-    geom_col(fill=col[3]) +
-    coord_flip() +
-    theme(axis.text = element_text(size=8),
-          axis.title = element_text(size=10)) +
-    labs(x="", y=paste("expected frequency of topic",topics.df[topic,2], sep=" ")) 
-}
-
-##################################
-## Topic correlation within Ylevel
-##################################
-topicCorrelation <- function(ylevel) {
-  cormat <- cor(stmOut$theta[stmOut$settings$covariates$betaindex==ylevel,])
-  adjmat <- ifelse(cormat > .05,1,0)
-  
-  corr <- list()
-  corr$posadj <- adjmat
-  corr$poscor <- cormat*adjmat
-  corr$cor <- ifelse(abs(cormat)>.05,cormat,0)
-  
-  x <- corr$posadj[1:nrow(corr$posadj),1:nrow(corr$posadj)]
-  
-  g<- graph.adjacency(x, mode="undirected", weighted=TRUE, diag=FALSE)
-  
-  E(g)$size <- 1
-  E(g)$lty <- 2
-  E(g)$color <- "black"
-  V(g)$label <- topics[,2]
-  layout <- layout_nicely
-  
-  plot.igraph(g, layout=layout_nicely, vertex.color="white", label.font = "Roboto",
-              vertex.frame.color="grey", vertex.size=1, vertex.label.cex=.7, edge.color="red",
-              edge.width=1, main=paste("Topic correlation", stmOut$settings$covariates$yvarlevels[ylevel]))
-}
-
-##################################
-## Topic correlation Network
-##################################
[…]

### 2019-05-13 paper/externals/facebook-news-analysis-master/func/02-topic-modelling-functions.R
create docs folder

@@ -1,289 +1,0 @@
-# Topic Modelling Functions
-# mail@tjpalanca.com
-# 15 Feb 2017
-
-# This section contains functions that assist with topic modelling.
-
-stemWords <- function(df, patterns, lang) {
-  # Applies a simple, conservative stemming algorithm
-  #
-  # Args:
-  #   df:       data frame containing words (`word`)
-  #   patterns: list of regex expressions containing the prefixes, suffixes, and mid-fixes
-  #   lang:     en_US or tl_PH, depending on the language in question
-  # 
-  # Returns:
-  #   A unique mapping between the identified words and the suggested stem
-  
-  df %>% 
-    # Get all distinct words
-    distinct(word) %>%
-    # Filter to language
-    filter(hunspell_check(word, lang)) %>% 
-    # Remove words too short for any modification
-    filter(str_length(word) > 3) %>% 
-    # Generate pattern matches
-    mutate(
-      pattern = 
-        map(
-          word,
-          function(word, patterns) patterns[map_lgl(patterns, ~str_detect(word, .))],
-          patterns = patterns
-        )
-    ) %>% 
-    unnest(pattern) %>% 
-    # Remove pattern from word
-    mutate(stem_word = str_replace(word, pattern, "")) %>%
-    # Add pattern exceptions if no words pass spell check
-    mutate(
-      stem_word = 
-        map(
-          stem_word,
-          function(stem_word) {
-            append(
-              stem_word,
-              c(
-                # ENGLISH
-                ifelse(
-                  lang == "en_US",
-                  paste0(stem_word, "e"), NA
-                ),
-                ifelse(
-                  lang == "en_US" & 
-                    str_detect(stem_word, "i$"), 
-                  stem_word %>% str_replace("i$", "y"), NA
-                ),
-                ifelse(
-                  lang == "en_US" &
-                    str_sub(stem_word, -1, -1) == str_sub(stem_word, -2, -2),
-                  str_sub(stem_word, 1, -2), NA
-                ),
-                # TAGALOG
-                ifelse(
-                  lang == "tl_PH",
-                  str_replace_all(stem_word, "u", "o"), NA
-                ),
-                ifelse(
-                  lang == "tl_PH",
-                  str_replace(stem_word, "r$", "d$"), NA
-                )
[…]

### 2019-05-13 paper/externals/roberts_paper/China.R

@@ -1,387 +1,0 @@
-##
-# This file replicates the China analyses.
-# We note that this work was done before many 
-# of the modern features for stm were in place.
-# As such much of the code below is written in
-# a more complex way than would now be necessary.
-# Please see the most recent version of the stm package
-# for more.
-
-library(Matrix)
-library(stm) #should work on version 1.1.3 but may not exactly replicate after.
-library(stringr)
-
-K <- 100
-
-#Raw texts not provided due to intellectually property constraints
-#here is the preprocessing:
-# meta <- read.csv("Sample.csv")
-# processed <- textProcessor(meta$V6, metadata=meta)
-# out <- prepDocuments(processed$documents, processed$vocab, processed$meta, lower.thresh=100)
-# out$meta$sourc <- as.factor(out$meta$Source)
-
-#stm was then run via the specification below
-#mod.spectral <- stm(documents = out$documents, vocab = out$vocab, K =
-#                    K, prevalence = ~  sourc + s(as.numeric(Date)), 
-#                    data = out$meta, max.em.its = 200, init.type="Spectral")
-load("ChinaModelOut.RData")
-load("ChinaData.RData")
-
-sagelabs <- sageLabels(mod.spectral, 25)
-out$meta$Date <- as.numeric(as.Date(as.character(out$meta$Date)))
-
-effect <- estimateEffect(c(1:100)~ sourc + s(Date), mod.spectral, metadata=out$meta, uncertainty="None")
-plot.estimateEffect(effect, "Date", topics=c(63), method="continuous", npoints=500)
-
-#Label topics based on Xinhua
-
-sagelabs$cov.betas[[5]]$problabels
-#Topic 1: general china
-#2: taiwan
-#3: general china
-#4: Korea, mongolia
-#5: Hong Kong return
-#6: Visiting other nations
-#7: Japanese relations
-#8: WTO and international trade
-#9: Announccments
-#10: Dollar financial markets
-#11: China state council
-#12: Economic numbers
-#13: Promoting cooperation between states
-#14: Banks and loans, financial crisis?
-#15: ASEAN
-#16: big numbers?
-#17: Chinese ambassador, visits to other countries
[…]

### 2019-05-13 paper/externals/roberts_paper/Figure2_CosinePlot.R

@@ -1,147 +1,0 @@
-## Monte Carlo's in the style of 4.1 of Roberts, Stewart and Airoldi
-# Stewart 2.21.15
-
-
-# Simulation of text data from the following model:
-# beta_k ~ Dirichlet(eta)
-# N_d ~ Poisson(lambda)
-# x_d ~ Uniform(0,10)
-# theta_d ~ LogisticNormal(c(.5,alpha*cos(x_d)), diag(sig2))
-# w_{d,n} ~ Mult(theta_d%*%beta)
-
-library(stm)
-library(clue) #for aligning topics
-library(lda)  #for lda
-
-simulate <- function(n.docs=100, V=50, 
-                     eta=.05, lambda=50, sig2=.5, 
-                     alpha=1,
-                     theta.only=FALSE) {
-  #Generate  
-  X <- runif(n.docs, 0, 1)
-  theta <- t(sapply(X, function(x) {
-   gaussian <- stm:::rmvnorm(1, c(.5, alpha*cos(10*x)), diag(rep(sig2, 2)))
-   stm:::softmax(c(gaussian,0))
-   }))
-  
-  if(theta.only) {
-    #if we only want theta, just stop here.
-    return(list(theta=theta, X=X))
-  }
-  
-  #Draw the topic word distributions
-  beta <- matrix(rgamma(V*3, eta), nrow=3, ncol=V)
-
-  #Words
-  NWords <- rpois(n.docs, lambda) 
-  
-  #Expected Count Matrix
-  ecm <- theta%*%beta
-  
-  #Simulate the observed data
-  documents <- vector(mode="list", length=n.docs)
-  for (d in 1:nrow(theta)) {
-    w <- rmultinom(1, NWords[d], ecm[d,])
-    documents[[d]] <- rbind(which(w>0), w[w>0])
-  }
-  
-  #stm won't like it if there are words which are never used, so we drop them out here
-  prepped <- prepDocuments(documents, 1:V, lower.thresh=0, verbose=FALSE)
-  
-  return(list(documents=prepped$documents, vocab=prepped$vocab, X=X, theta=theta))
-}
-
-eval.sim <- function(simobj, lda.alpha=.05, lda.eta=.05, lda.nits=100, 
-                     stm.df=5, lda.burnin=TRUE, stm.init="LDA", span=2/3, 
-                     #setting lda.burn=TRUE averages over a bunch of draws
-                     lda.only=FALSE,...) {
-  
[…]

### 2019-05-13 paper/externals/roberts_paper/Figure3_Plot.R

@@ -1,149 +1,0 @@
-############
-# This is code to make Figure 3 in Roberts, Stewart and Airoldi (2016)
-# it is primarily for documentation purposes as much of the code
-# has been supplanted by other alternatives.
-# this sequentially calculates coverage you need based on the simulated
-# models that are given in the Simulation.R script in this folder.
-#############
-
-
-library(Matrix)
-library(devtools)
-library(stm)
-library(clue)
-library(pdist)
-
-#Load the original model
-load("Truth.RData")
-load("ChinaSimData.RData")
-
-
-
-###
-# Create a function to sample for one document
-###
-
-#there are now better version of this in stm
-#see thetaPosterior
-rtheta <- function(nsims, lambda, Sigma, choleskydecomp) {
-  mat <- stm:::rmvnorm(nsims, lambda, Sigma, choleskydecomp)
-  mat <- cbind(mat, 0)
-  return(exp(mat - stm:::row.lse(mat)))
-}
-#test <- rtheta(1000, lambda[1,], Sigma, choleskydecomp)
-
-binnedcover <- vector(mode="list", length=100)
-bias <- vector(mode="list", length=100)
-L1error <- vector(mode="list", length=100)
-true <- mod.out.replicate$theta
-
-for(i in 1:100) {
-  load(sprintf("estimated%i.RData", i))
-  cost <- pdist(t(mod.out.replicate$theta), t(hopeful$theta))
-  align <- solve_LSAP(as.matrix(cost), maximum=FALSE)
-  
-  #Calculate the global approximation to nu
-  Sigma <- hopeful$sigma
-  mu <- hopeful$mu$mu
-  lambda <- hopeful$eta
-  covariance <- crossprod(lambda-t(mu)) 
-  #rescale by the number of documents
-  covariance <- covariance/nrow(lambda)
-  #subtract off the effect from the global covariance
-  Sigma <- Sigma - covariance
-  choleskydecomp <- chol(Sigma)
-  est <- hopeful$theta[,align]
-  
-  
-  cover <- vector(mode="list", length=nrow(lambda))
-  cis <- vector(mode="list", length=nrow(lambda))
-  for(d in 1:nrow(lambda)) {
-    draws <- rtheta(2500, lambda[d,], Sigma, choleskydecomp)
[…]

### 2019-05-13 paper/externals/roberts_paper/Figure3_Simulation.R

@@ -1,42 +1,0 @@
-#The setup for the simulation reported in Roberts, Stewart and Airodi (2016)
-#is included below.  This was parallelized over a cluster computing system
-#Due to changes in the underlying package we would not expect this to replicate
-#exactly.
-
-library(Matrix)
-library(devtools)
-library(stm)
-library(clue)
-library(pdist)
-
-#the lines below expect an integer that came from the run on the cluster computer
-iteration <- as.integer(commandArgs(TRUE))+1
-set.seed(iteration)
-
-load("Truth.RData") #a reference model
-load("ChinaSimData.RData") #the version of the documents that go with this model
-#we create a simulation based on the observed data.
-
-beta <- lapply(mod.out.replicate$beta$logbeta, exp)
-theta <- mod.out.replicate$theta
-theta <- t(apply(theta, 1, function(x) {
-               y <- rep(0, length(x)) 
-               y[which.max(x)] <- 1
-               return(y)}))
-
-Nd <- unlist(lapply(out$documents, function(x) sum(x[2,])))
-index <- mod.out.replicate$settings$covariates$betaindex
-sim.docs <- vector(mode="list", length=length(out$documents))
-V <- length(out$vocab)
-for(i in 1:length(sim.docs)) {
-  prob <- theta[i,]%*%beta[[index[i]]]
-  x <- table(sample(x = 1:V, prob = prob, size = Nd[i],replace = TRUE))
-  sim.docs[[i]] <- rbind(as.integer(names(x)), as.integer(x))
-}
-
-sim.estimate <- stm(documents = sim.docs, vocab = out$vocab, K = 100, 
-               prevalence = ~  sourc + s(as.numeric(date)), 
-               content = ~ sourc, 
-               data = out$meta, max.em.its = 500, init.type="Spectral")
-save(sim.estimate, file=sprintf("estimated%i.RData", iteration))
-

### 2019-05-13 paper/externals/roberts_paper/Figure4_RunModelsClusterScript.R

@@ -1,83 +1,0 @@
-#Below is the original code that was put on a cluster system
-#to run the models that would form the basis of Figure 4
-#in Roberts, Stewart and Airoldi (2016)
-
-#this is primarily as a record of the various parameters that were
-#chosen.  The subfolders DMR and SAGE include the reference implementations
-#that were used.
-
-cur <- getwd()
-library(matrixStats)
-library(stringr)
-#library(splines)
-#library(Matrix)
-
-K <- 60
-
-
-#workingdir <- "/nfs/projects_nobackup/l/ldaglm/stmdev/rcode/stm/R"
-#setwd(workingdir)
-#library(matrixStats)
-#install.packages(repos=NULL,pkgs="stm_0.03.19.tar.gz", type="source")
-#library(stm)
-library(lda)
-library(stm)
-#code <- list.files()
-#for(i in 1:length(code)){
-#    source(code[i])
-#  }
-
-iter <- as.integer(commandArgs(TRUE))
-
-setwd("/nfs/projects_nobackup/l/ldaglm/HoldOut")
-
-meta <- read.csv("Sample.csv")
-
-processed <- textProcessor(meta$V6, metadata=meta)
-out <- prepDocuments(processed$documents, processed$vocab, processed$meta, lower.thresh=100)
-out$meta$sourc <- as.factor(out$meta$Source)
-
-setwd("/nfs/projects_nobackup/l/ldaglm/HoldOut/HeldOutAtScale")
-
-#heldout <- make.heldout(out$documents, out$vocab)
-#save(heldout, file=paste("HeldOut", iter, "_Topics", K, ".RData", sep=""))
-load(paste("HeldOut", iter, "_Topics", "100", ".RData", sep=""))
-
-setwd("/nfs/projects_nobackup/l/ldaglm/HoldOut/SpectralAtScale")
-#stm spectral
-mod.spectral <- stm(documents = heldout$documents, vocab = heldout$vocab, K = K, prevalence = ~  sourc +
-        s(as.numeric(Date)), content = ~ sourc, data = out$meta, max.em.its = 200, init.type="Spectral")
-
-mod.spectral.save <- list("settings"=mod.spectral$settings, "beta"=mod.spectral$beta, "theta"=mod.spectral$theta)
[…]

### 2019-05-13 paper/externals/roberts_paper/SAGE.R

@@ -1,161 +1,0 @@
-##Sparse Additive Generative (SAGE) Model of Text
-## Originally due to Eisenstein, Ahmed and Xing (2011) ICML
-## Coded up by Brandon Stewart
-
-SAGE <- function(documents, vocab, K, 
-                 content, data, interactions=TRUE,
-                 em.converge.thresh=.001, max.em.its=500, 
-                 doc.converge.thresh=.001, max.doc.its=5,
-                 verbose=TRUE, 
-                 kappatau.converge.thresh=.001, 
-                 max.kappatau.its=100,
-                 mstep.converge.thresh=.001, 
-                 max.mstep.its=10) {
-  ############
-  # Set things up
-  ############
-  
-  # Process the content covariate
-  if(inherits(content, "formula")) {
-    termobj <- terms(content, data=data)
-    if(attr(termobj, "response")==1) stop("Response variables should not be included in content formula.")
-    if(nrow(attr(termobj, "factors"))!=1) stop("Currently content can only contain one variable.")
-    if(is.null(data)) {
-      yvar <- eval(attr(termobj, "variables"))[[1]]
-    } else {
-      char <- rownames(attr(termobj, "factors"))[1]
-      yvar <- data[[char]]
-    }
-    yvar <- as.factor(yvar)
-  } else {
-    yvar <- as.factor(content)
-  }
-  yvarlevels <- levels(yvar)
-  betaindex <- as.numeric(yvar)
-  
-  #Initialize Parameters
-  N <- length(documents)
-  A <- length(unique(betaindex))
-  beta.mode <- ifelse(A==1, "SAGE", "TAI")
-  current.params <- init.paramsSAGE(K, documents, vocab, num.views=A)
-  
-  wcountvec <- unlist(lapply(documents, function(x) rep(x[1,], times=x[2,])),use.names=FALSE)
-  wcounts <- list(Group.1=sort(unique(wcountvec)))
-  V <- length(wcounts$Group.1)  
-  wcounts$x <- tabulate(wcountvec)
-  rm(wcountvec)
-  
-  settings <- list(dim=list(K=K, A=A, V=V, wcounts=wcounts),
-                   verbose=verbose,
-                   convergence=list(max.em.its=max.em.its, 
-                                    em.converge.thresh=em.converge.thresh),
-                   covariates=list(betaindex=betaindex, 
-                                   yvarlevels=yvarlevels),
[…]

### 2019-05-13 paper/externals/roberts_paper/SAGEaux.R

@@ -1,140 +1,0 @@
-##initializations, convergence checks, matrix stats
-
-##
-#A series of fast softmax functions mostly wrappers around matrixStats package functions
-##
-logsoftmax <- function(x) {
-  x - lse(x)
-}
-
-lse <- function(x) {
-  logSumExp(x)
-}
-
-row.lse <- function(mat) {
-  rowLogSumExps(mat)
-}
-col.lse <- function(mat) {
-  colLogSumExps(mat)
-}
-
-softmax <- function(x) {
-  exp(x - lse(x))
-}
-
-safelog <- function(x) {
-  out <- log(x)
-  out[which(out< -1000)] <- -1000
-  out
-}
-
-
-###
-# Kappa initialization
-###
-
-#initialize the parameters.  
-init.paramsSAGE <- function(K, documents, vocab, num.views, it.num=50, alpha.gibbs=.01, eta.gibbs=.01) {
-  resetdocs <- documents
-  for (i in 1:length(documents)) {
-    resetdocs[[i]][1,] <- as.integer(resetdocs[[i]][1,]-1)
-  }
-  
-  mod <- lda.collapsed.gibbs.sampler(resetdocs, K, vocab, num.iterations=it.num, alpha=alpha.gibbs,
-                                     eta=eta.gibbs)
-  gamma <- t(mod$document_sums) + .Machine$double.eps
-  topics <- mod$topics + .Machine$double.eps
-  logbeta <- log(topics) - log(rowSums(topics))
-  logbetalist <- list()
-  for(i in 1:num.views) {
-    logbetalist[[i]] <- logbeta
-  }
-  kappa <- kappa.init(documents, K, length(vocab), A=num.views, interactions=TRUE)
-  
-  current.params <- list(global=list(alpha=rep(1/K,K), logbeta=logbetalist, kappa=kappa), 
-                         local=list(gamma=gamma),
-                         params=list(K=K, num.views=num.views, V=length(vocab)))
-  return(current.params)
-}
-
-
-
-
-kappa.init <- function(documents, K, V, A, interactions) {
-  kappa.out <- list()
-  #Calculate the baseline log-probability (m)
-  freq <- matrix(unlist(documents),nrow=2) #break it into a matrix
-  freq <- split(freq[2,], freq[1,]) #shift into list by word type
-  m <- unlist(lapply(freq, sum)) #sum over the word types
-  m <- m/sum(m)
-  #m <- log(m)
-  m <- log(m) - log(mean(m)) #logit of m
[…]

### 2019-05-13 paper/externals/roberts_paper/SAGEkapp.R

@@ -1,200 +1,0 @@
-## Functions for Estimation (Sparse) Additive Topics (Kappa)
-##########
-#Contents: Kappa Estimation function, optimization of specific kappa, kappa likelihood/gradient.
-
-# For the most complex case Kappa has 3 portions: 
-#   topics, aspects and interactions (TAI).
-# For Topics: we want to marginalize over the aspects.
-# For Aspects: we want to marginalize over the topics.
-# For Interaction: we just want the subset.
-# In each case, c.k will be a vocab length vector.
-
-estKappa <- function(beta.ss, kappa, settings) {
-  verbose <- settings$verbose
-  # Step 1: Precalulating some marginalizations
-  if(length(beta.ss)==1) {
-    KbyV <- beta.ss[[1]]
-    KbyA <- matrix(rowSums(KbyV), ncol=1)
-  } else {
-    KbyV <- Reduce("+", beta.ss) #marginalize over aspects
-    KbyA <- do.call(cbind, lapply(beta.ss, rowSums)) #marginalize over words
-  }
-  
-  # Step 2: Loop over the Kappa Updates
-  converged.outer <- FALSE
-  outer.it <- 1
-  
-  while(!converged.outer) {
-    compare <- abs(unlist(kappa$params)) <.001 #comparison for checking convergence at the end of the loop
-    for(i in 1:length(kappa$params)) {
-      kappa <- opt.kappak(i, kappa, beta.ss, 
-                          settings$tau$mode, settings$tau$tol, settings$tau$maxit, settings$tau$prior,
-                          KbyV, KbyA)
-      if(verbose) cat(".")
-    }
-    if(verbose) cat("\n")  #end the update line
-    
-    #convergence checks for tolerance 
-    current <- abs(unlist(kappa$params)) < .001
-    sparseagree <- mean(compare==current)
-    
-    converged.outer <- sparseagree > settings$kappa$mstep$tol
-    
-    #convergence checks fo iterations
-    ifelse(outer.it==settings$kappa$mstep$maxit, converged.outer <- TRUE, outer.it <- outer.it + 1)
-  }
-  
-  # Step 3: Construct Beta and Return 
[…]

### 2019-05-13 paper/externals/roberts_paper/SAGErunscript.R

@@ -1,17 +1,0 @@
-require(lda)
-require(matrixStats)
-library(stm)
-
-out <- prepDocuments(poliblog5k.docs, poliblog5k.voc, poliblog5k.meta,subsample=500,lower.thresh=20,upper.thresh=200)
-documents <- out$documents
-vocab <- out$vocab
-meta <- out$meta
-K <- 50
-source("SAGE.R")
-source("SAGEkapp.R")
-source("SAGEaux.R")
-mod <- SAGE(documents, vocab, K, content=~rating, data=meta, max.em.its=3)
-
-#where things are
-mod$model$local$theta  #theta
-mod$model$global$logbeta #list of logbetas

### 2019-05-13 paper/externals/roberts_paper/dmr.R

@@ -1,206 +1,0 @@
-# Dirichlet Multinomial Regression model
-# (original model due to Mimno and McCallum 2008)
-# this is an implementation using variational inference.
-
-#This was used as a comparison in Roberts, Stewart, Airoldi
-#it relies on non-exported stm functions and is quite memory
-#inefficient.  If you want to use this model for real, we
-#recommend using the code written by David Mimno for Mallet.
-
-dmr.control <- function(documents,vocab, K, X, 
-                        sig2=c(10, rep(.5, times=(ncol(X)-1))), 
-                        eta=.01, 
-                        tol=.01,maxits=10000,
-                        verbose=TRUE, printevery=5) {
-  doc.to.ijv <- stm:::doc.to.ijv
-  ijv.to.doc <- stm:::ijv.to.doc
-
-  #Create the data.
-  # three equal length vectors: the document id, word indices, the count of each word
-  # note this is the simple-triplet-matrix i,j,v respectively.
-  dat <- doc.to.ijv(documents)
-  
-  #test for -indexing
-  if(0 %in% dat$j) {
-    ldadoc <- ijv.to.doc(dat$i,dat$j,dat$v)
-  } else {
-    ldadoc <- ijv.to.doc(dat$i,dat$j-1,dat$v)
-  }
-  
-  ##
-  #Initializing
-  ##
-  #Need to track four things:
-  # phi  is the K by V matrix of counts of words by topic
-  # theta is the D length list of expected counts in each document
-  # NZ is the is the K length vector containing counts in the topics.
-  # gamma is the token length list, where each element is a K-length vector
-  
-  #Use a few passes of Gibbs to get things started
-  init <- lda::lda.collapsed.gibbs.sampler(ldadoc,K,vocab, num.iterations=100, alpha=.01, eta=.01)
-  #NB: no point in doing burnin because the statistics have to sink up and it doesn't give us the 
-  #    proper values for phi, so it isn't possible to work back a meaningful use of those.
-  
-  #theta
-  x <- init$document_sums
-  theta <- split(x, col(x))
-  rm(x)
-  #phi
-  phi <- init$topics
-  
-  #topic sums
-  NZ <- rowSums(phi)
-  #gamma
-  gvec <- unlist(init$assignments)+1 #offset the zero index.
-  gvec <- split(gvec, 1:length(gvec))
[…]

### 2019-05-13 paper/externals/roberts_paper/ppc.R

@@ -1,45 +1,0 @@
-#This is the code for the posterior predictive checks
-#which appear in Figure 5 of Roberts,Stewart,Airoldi
-
-
-library(stm)
-#load some auxiliary functions
-source("ppcfunctions.R")
-
-#Background you don't need to run
-#load("ChinaModelOut.RData")
-
-#meta <- read.csv("../Sample.csv")
-#processed <- textProcessor(meta$V6, metadata=meta)
-#out <- prepDocuments(processed$documents, processed$vocab, processed$meta, lower.thresh=100)
-#out$meta$sourc <- as.factor(out$meta$Source)
-
-#documents <- out$documents
-#vocab <- out$vocab
-#rm(out,meta,processed)
-#mod <- mod.spectral
-#rm(mod.spectral)
-#set.seed(01238)
-#ppc.out <- ppc(mod,documents)
-#save(documents, mod, ppc.out, file="ppc.RData")
-
-#now load up the file created above
-load("ppc.RData")
-
-#the two lines below are not strictly necessary
-#because the object ppc.out is in the loaded file
-set.seed(01238)
-ppc.out <- ppc(mod,documents)
-
-#make some labels
-vocab <- mod$vocab
-labs <- sageLabels(mod, n=10)
-labs2 <- match(labs$marginal$prob,vocab)
-labs2 <- matrix(labs2, nrow=100)
-
-pdf(file="ppc.pdf", width=12, height=4)
-par(mfrow=c(1,3))
-plot.ppc(ppc.out, labs2[58,], 58, vocab, main="SARS/Avian Flu")
-plot.ppc(ppc.out, labs2[21,], 21, vocab, main="Tibet and Human Rights")
-plot.ppc(ppc.out, labs2[41,], 41, vocab, xlim=c(0,5), main="North Korea")
-dev.off()

### 2019-05-13 paper/externals/roberts_paper/ppcfunctions.R

@@ -1,105 +1,0 @@
-
-ppc <- function(mod, documents, nsims=20) {
-  if(!require(data.table)) stop("Install data.table to use this function.")
-  nsims <- nsims + 1 #add one for the original data
-  theta <- mod$theta
-  betaindex <- mod$settings$covariates$betaindex
-  beta <- lapply(mod$beta$logbeta, exp)
-  K <- mod$settings$dim$K
-  V <- mod$settings$dim$V
-  # Create the data structures
-  # H1- maintain docs by topic counts
-  # H2- maintain the doc-topic-word counts
-  H1 <- vector(mode="list",length=nsims)
-  H2 <- vector(mode="list",length=nsims)
-  N <- length(documents)
-  ctevery <- ifelse(N>100, floor(N/100), 1)
-  
-  for(s in 1:nsims) {
-    #store the doc topic counts and the document-topic-vocab object
-    doctopiccounts <- matrix(0, nrow=length(documents), ncol=K)
-    dkv.storage <- vector(mode="list", length(documents))
-    for(i in 1:length(documents)) {
-      #pull components out and calculate phi
-      doc <- documents[[i]]
-      thetad <- theta[i,]
-      doc.ct <- doc[2,]
-      betasub <- beta[[betaindex[i]]][,doc[1,]]
-      EB <- thetad*betasub #calculate exp(eta)\beta for each word
-      EB <- t(EB)/colSums(EB) #transpose and norm by (now) the row
-      
-      #replicate out the probabilities to sample realizations
-      phi <- EB[rep(1:length(doc.ct), times=doc.ct),]
-      draws <- apply(phi, 1, function(x) sample(1:K, size=1,prob=x))    
-      #sum up the draws by topic and store.
-      tab <- tabulate(draws, nbins=K)
-      doctopiccounts[i,] <- tab
-      
-      #If observed, use that, if not sample
-      if(s==1) {        
-        #bind to the observed words
-        dkv.storage[[i]] <- cbind(i, draws, rep(doc[1,], times=doc[2,]))
-      } else {
-        #Sample the Words in Blocks by Topic
-        words <- vector(mode="list", length=K)
-        for(k in 1:length(tab)) {
-          if(tab[k]==0) next
[…]
